### 2021-03-26 mnras_template.tex
Initial Overleaf Import

% mnras_template.tex 
%
% LaTeX template for creating an MNRAS paper
%
% v3.0 released 14 May 2015
% (version numbers match those of mnras.cls)
%
% Copyright (C) Royal Astronomical Society 2015
% Authors:
% Keith T. Smith (Royal Astronomical Society)

% Change log
%
% v3.0 May 2015
%    Renamed to match the new package name
%    Version number matches mnras.cls
%    A few minor tweaksto wording
% v1.0 September 2013
%    Beta testing only - never publicly released
%    First version: a simple (ish) template for creating an MNRAS paper

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Basic setup. Most papers should leave these options alone.
\documentclass[fleqn,usenatbib]{mnras}

% MNRAS is set in Times font. If you don't have this installed (most LaTeX
% installations will e fine) or prefer the old Computer Modern fonts, comment
% out the following line
\usepackage{newtxtext,newtxmath}
% Depending on your LaTeX fonts installation, you might get better results with one of these:
%\usepackage{mathptmx}
%\usepackage{txfonts}

% Use vector fonts, so it zooms properly in on-screen viewing software
% Don't change these lines unless you know what you are doing
\usepackage[T1]{fontenc}
\usepackage{ae,aecompl}

%%%%% AUTHORS - PLACE YOUR OWN PACKAGES HERE %%%%%

% Only include extra packages if you really need them. Common packages are:
\usepackage{graphicx}	% Including figure files
\usepackage{amsmath}	% Advanced maths commands
\usepackage{amssymb}	% Extra maths symbols

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%% AUTHORS - PLACE YOUR OWN COMMANDS HERE %%%%%

% Please keep new commands to a minimum, and use \newcommand not \def to avoid
% overwriting existing commands. Example:
%\newcommand{\pcm}{\,cm$^{-2}$}	% per cm-squared

\newcommand\halpha{H${\alpha}$}
\newcommand\n{[\ion{N}{II}]$\lambda$6584}
\newcommand\oi{[\ion{O}{III}]$\lambda$5007}
\newcommand\s{[\ion{S}{II}]$\lambda$6737}
\newcommand\si{$\sigma$}
\newcommand\kms{$^{-1}$}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%% TITLE PAGE %%%%%%%%%%%%%%%%%%%

% Title of the paper, and the short title which is used in the headers.
% Keep the title short and informative.
\title[Turbulence in GEHRs]{Turbulence in giant extragalactic HII regions}

% The list of authors, and the short list which is used in the headers.
% If you need two or more lines of authors, add an extra line using \newauthor
\author[J. García-Vázquez et al.]{
J. García Vázquez,$^{1}$\thanks{E-mail: jgarciav1600@alumno.ipn.mx}
J. Zsargo,$^{1}$
W. J. Henney$^{2}$
and H. O. Castañeda$^{1}$
\\
% List of institutions
$^{1}$Escuela Superior de Física y Matemáticas, Insituto Politécnico Nacional, Ciudad de México, México.\\
$^{2}$Instunto de Radioastronomía y Astrofísica, Universidad Nacional Autonoma de México, Apartado postal 3-72, 58090 Morelia, Michoacán, Mexico\\
}

% These dates will be filled out by the publisher
\date{Accepted XXX. Received YYY; in original form ZZZ}

% Enter the current year, for the copyright statements etc.
\pubyear{2021}

% Don't change these lines
\begin{document}
\label{firstpage}
\pagerange{\pageref{firstpage}--\pageref{lastpage}}
\maketitle

% Abstract of the paper
\begin{abstract}

%We have used longslit spectroscopy observations obtained with the William Herschel Telescope with the aim of characterizing the turbulent state of the ionized gas in giant HII regions.
%For this purpose, the \halpha, \n, \oi\ and \s\ emission lines were investigated applying a statistical analysis on their velocities samples. 
%The correlations in our results are evidence that the velocity field can be consider as homogeneous turbulence, a statistically stationary process. This turbulent motions can be described by a power law with a mean index of 0.60$\pm$0.02 and a physical coherent scale up to $\sim$60 pc for NGC 604 and 1.04$\pm$0.01 with a correlation length up to $\sim$60 pc for NGC 595. 
%The physical interpretation of our results consider that an energy cascade is taking place for all the ionic species.
%Finally, we give our explanation for our results and fit them in the context of turbulence in giant HII regions.

\end{abstract}

% Select between one and six entries from the list of approved keywords.
% Don't make up new ones.
\begin{keywords}
HII regions -- ISM: individual object: NGC 604 -- ISM: kinematics and dynamics -- techniques: spectroscopic -- turbulence
\end{keywords}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%% BODY OF PAPER %%%%%%%%%%%%%%%%%%

\section{Introduction}

There is evidence that different phases of the interstellar medium exhibits a chaotic behavior \citep{franco1999interstellar,elmegreen2004interstellar,scalo2004interstellar}. Velocity fields shows complex motions in the plane-of-sky (POS) and a non-thermal broadening on their spectral lines, suggests disorder motions along the line-of-sight (LOS). The large lengths of astrophysical objects, ranging in scales from 10$^{6}$ to 10$^{17}$ m \citep{chepurnov2010extending}, is closely related to the existence of turbulent flows. The high Reynolds numbers (Re), in the order of 10$^{4}$ and 10$^{9}$, present in these objects \citep{lagrois2011} is taken as first approach to understand the relationship between turbulence and the observed movements. Despite numerous attempts in characterizing the turbulence in the photoionized gas, little understood on how the results indicate something about the physics of the object.

The mathematical techniques developed by \citet{kolm1,heisenberg1951stability} were first applied to astronomical observations by \citet{von1951methode} and \citet{munch1958internal}. Their aim was to investigate the projection of a three-dimensional function into the plane of the sky. This procedure using the structure function allowed to determine a distinction between homogeneous turbulence and pure random velocity fluctuations, in this case in the galactic HII region, the Orion Nebula. The analysis on the turbulence of the Orion Nebula was continued by \citet{castaneda1987} and \citet{1992ApJ...387..229O}. In more recent years \cite{medina2014} and \cite{arthur2016turbulence} used another statistical technique called velocity channel analysis (VCA) \citep{2000ApJ...537..720L}, along the structure function, to study the Orion nebula. Recently, the structure function was used with full 6D measurements (position-velocity) to study the motions of stars in the Orion Molecular Cloud Complex. \cite{2021ApJ...907L..40H} argue that newborn stars should reflect the turbulent kinematics of their natal clouds. Using this previous method they are free of the projected element that interfere with previous gas-based studies and their results agree with the scaling law proposed by \cite{1981MNRAS.194..809L}.

The first attempt at characterizing turbulence in a giant extragalactic HII region (GEHR) was done by \citet{1961MNRAS.122....1F} with the 30 Dor complex in the LMC, finding no indication of turbulent motions. \cite{2019arXiv191203543M} investigated the structure function in 30 Dor finding on their results that the structure function is entirely flat on scales from 3 to 200 pc. Also, \cite{2019arXiv191203543M} studied the motions in NGC 604, previously analyzed by \cite{tanco1997}. Both results shows that there is a two slope behavior for the structure function. The structure function in the GEHR NGC 595 was first obtained by \cite{lagrois2009multi} and the analysis was expanded by \cite{lagrois2011}. In all previous studies the Kolmogorov law does not apply to any result.

GEHRs are ideal objects for the study of turbulence in the interstellar medium. These objects have large dimensions ($ \geq $100 pc) and high luminosity ($10^{38}<$ L$_{H\alpha}<10^{40}$ erg s$^{-1}$). There is a strong interaction between the stars clusters ($\geq$100 stars with T$_{eff}\geq30,000\ $K) and the surrounding medium (n$_{e}$=1-10$^4$ cm$^{-3}$ and T$_{e}$=10,000 K) via the injection of mechanical energy and the momentum given to the ionized gas \citep{castaneda1992density}. This energy and momentum comes in the form of stellar winds (v$_{w}\sim$ 1000 km s$^{-1}$) of the O ($\dot{M}$=$10^{-5} M_{\odot}\ yr^{-1}$) and B ($\dot{M}$=$10^{-6.5} M_{\odot}\ yr^{-1}$) stars \citep{dyson1979}.

\citet{smith1970} discovered that the line width of GEHRs was supersonic, of the order of $\sigma \sim$ 17-26 km s\kms. \citet{melnick1977,terlevich1981} have shown an empirical relationship between the line width and the integrated properties of the HII regions as the diameter or the luminosity ($R \sim \sigma ^{\sim 2}$ ; $L \sim \sigma ^{\sim 4}$). They conclude that GEHR  follow this relations as self-gravity systems like globular clusters or elliptical galaxies. The idea of a virial system has been developed by \citet{1993ApJ...418..767T,munoz1996} into the \textit{Cometary Stirring Model} (CSM) with the aim to separate the mechanism that contribute to the line broadening. The stellar winds also tend to be used for an explanation of the line broadening and turbulence in GEHRs \citep{1994ApJ...425..720C}. This features seems to drive visually the regions with filaments, arcs and shells. On their spectra double and multiple emission features are signature of these objects. \cite{2020MNRAS.494...97S} argue that winds on ionizing clusters in GEHR must merge into a hot cluster because of the close proximity of the massive stars. \cite{2019ApJ...871...17U} propose that stellar feedback is an important source of energy to maintain turbulence in nearby galaxies.

Our objective is to characterize the turbulent regime for different ions in different GEHRs.  We compare our results with previous investigations.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Methods}\label{sec:met}

\subsection{Observations}\label{sec:obs}

The archival data used in this work was obtained with the ISIS spectrograph and the TAURUS-II Fabry Perot in the 4.2-m William Herschel Telescope (WHT) of del Roque de los Muchachos Observatory (ORM) in La Palma, Spain and was retrieved from the La Palma archive\footnote{\url{http://casu.ast.cam.ac.uk/casuadc/ingarch}}.

\citet{2000PASP..112.1138M} and \citep{maiz2004} provides details of the observational setup for the the ISIS instrument. In summary, the spectra were obtained (1998 18-19 August) using a position angle of 90$^{\circ}$ and the slit width was 1". Two different spectra were taken simultaneously for each position: one for the red arm, between 6390 and 6849 \r{A} and another on the blue arm between 4665 and 5065 \r{A}. The slit had a length of 200" and ten  positions  were observe with an exposure time ranging from 900 to 1200 s for every slit. The  data we used was reduced again by \citet{jen2013} using the IRAF \citep{1999ascl.soft11002N} astronomical software. The ISIS observations were used by \citet{TT2000} and \citet{maiz2004}.

For the TAURUS-II instrument, \cite{sabalisck1995supersonic} mentioned the main aspects of the observations (1990 July 31). The two-dimensional imaging spectroscopy was captured using an IPCS-II detector and the 125 $\mu$m etalon. The cumulative integration time per frame is 36 s with a seeing value of 1''. The format of the data cube was of 256*256*100 with a spatial scale of 0.26 pixel$^{-1}$. Finally, the reduction and analysis was done with the packages TAUCAL y TAUFITS \citep{1992ASPC...25..445L}.
The TAURUS-II observations were used by \cite{sabalisck1995supersonic}, \cite{tanco1997} and \cite{2019arXiv191203543M}.

\subsection{Data}

Figure \ref{fig:M604} shows the two-dimensional radial velocity map of NGC 604 in H$\alpha$. ISIS observations have been limited with the aim to match the zone cover by TAURUS instrument. The velocity scale on both instruments reflects the radial velocity in the reference frame of the region taking as a  reference point the most luminous pixel. This pixels has a value of -253.11 km/s. Figure \ref{fig:M595} shows the two-dimensional radial velocity map of NGC 595 in H$\alpha$.

\begin{figure}
\centering 
\includegraphics[width=2.5in]{Figures/6ISIS.png}
\includegraphics[width=2.5in]{Figures/6TAU.png}
\caption{Radial velocity maps of NGC 604 in H$\alpha$. Above: ISIS observations. Below: TAURUS observations. }
\label{fig:M604}
\end{figure}

\begin{figure}
\centering 
\includegraphics[width=2.5in]{Figures/5TAU.png}
\caption{Radial velocity maps of NGC 595 in H$\alpha$.}
\label{fig:M595}
\end{figure}

\begin{figure}
\centering 
\includegraphics[width=2.5in]{Figures/MV.png}
\includegraphics[width=2.5in]{Figures/MX.png}
\caption{Radial velocity maps of Hubble V and Hubble X in H$\alpha$.}
\label{fig:MHub}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Turbulence}\label{sec:turb}

The classic turbulence theory \citep{kolm1} assumes a three-dimensional isotropic, incompressible and subsonic flow, where an energy cascade is taking place. The energy cascades goes downward, from the largest vortices until it reaches dissipation with the smallest vortices. 
In this energy cascade three scales can be defined: the energy injection scale (Re $\rightarrow \infty$), $L_{EI}$, the dissipation scale (Re $\rightarrow$ 1), $L_{D}$ and the inertial scale ($L_{I}$) between the previous two. The energy cascade concept is described with an energy spectrum, $E(k) \propto k^{-\beta}$ where $k$ is the wave number for a scale $l$ ($k \equiv l^{-1}$).

If we consider the mean specific energy transfer, $\langle \epsilon \rangle$, the inertial range can be denoted as $\epsilon \sim \frac{v_{l}^{2}}{\tau_{l}}$, where $v_{l}^{2}$ is the kinetic energy per mass unit and $\tau_{l}$ the time related with velocity fluctuations. Since the total specific energy of a determined $l$ scale is of the order $\langle v_{l}^{2} \rangle$ and is the energy integral above the associated $k$, defined as:

\begin{equation}\label{eq:veles}
 \langle v_{l}^{2} \rangle = \int_{k}^{\infty} E(k)dk
\end{equation}

Considering that this energy is of the order of $(\epsilon l)^{\frac{2}{3}} \sim (\frac{\epsilon}{k})^{\frac{2}{3}}$ we can substitute in equation \ref{eq:veles} and obtain the Kolmogorov law:

\begin{equation}\label{eq:kolm}
E(k) \propto \epsilon^\frac{2}{3} k^{-\frac{5}{3}}
\end{equation}

We use the second order structure function, $S_{2}(l)$, defined as:

\begin{equation}\label{eq:S}
S_{2}(\boldsymbol{l})=\dfrac{\sum[V_{r}(\boldsymbol{x}+\boldsymbol{l})-V_{r}(\boldsymbol{x}) ]^{2}}{N(\boldsymbol{l})}
\end{equation}

as a statistical tool to investigate the relation between a velocity field and the presence of turbulent motions following the Kolmogorov theory. In equation \ref{eq:S}, $V_{r}(\boldsymbol{x})= V_{obs}(\boldsymbol{x})-\langle V_{obs}(\boldsymbol{x}) \rangle$ and N($\boldsymbol{l}$) the number of points at each separation. If we consider the quadratic velocities differences proportional to the left term in equation \ref{eq:kolm}:

\begin{equation}\label{eq:sfi}
(\Delta v)^{2} \sim (\epsilon l)^{\frac{2}{3}}
\end{equation}

the term $(\Delta v)^{2}$ can be identified as the structure function. The right term with index,  m=2/3, in equation \ref{eq:sfi} is related to the energy (the left term in equation \ref{eq:veles}). This index m serves as a reference for comparison between theory and observations.

For our fit we use the normalized structure function of the form $s(l)=2[1-C(l)]$ where $C(l)=1/[1+(l/l_{0})^{m_{2D}}]$. The term l$_{0}$ is the correlation length of the turbulence and $m_{2D}$ is the index that adjust our results \citep{1984ApJ...277..556S, arthur2016turbulence}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Results}\label{sec:res}

\subsection{NGC 604}

Figure \ref{fig:SF604} shows the structure function (Equation \ref{eq:S}) of NGC 604 for the H$\alpha$ emission line for the ISIS and TAURUS instruments. The $m_{2D}$ is 1.7 with a correlation length of 11 pc. The $\sigma$ for the ISIS instrument is 8.4 km/s and for TAURUS instrument 7.3 km/s. The fit to the power-law of the structure function is performed over the scales of 4 to 11 pc. The structure functions keep going up to scales of 70 pc, above these value the structure function falls steeply for the ISIS. As \cite{arthur2016turbulence} mentioned, the more pronounced steeping for small scales, below 4 pc in our case, is due to the spatial resolution of the observations. In comparison with TAURUS, ISIS values are higher but are able to maintain the form of the structure function.

\subsection{NGC 595}

Figure \ref{fig:SF595} shows the structure function of NGC 595 for the H$\alpha$ emission line for the TAURUS instruments. The $m_{2D}$ is 1.7 with a correlation length of 11 pc. The $\sigma$ is 6.6 km/s. In this case it is possible to fit values under 4 pc, but this small scale region is affected due to the seeing. The range of scale for this regions stays between 10 and 11 pc as in NGC 604. The values of the structure function rise until 30 pc. Scales larger than this shows a random around 2$\sigma$.

\begin{table}
\begin{center}\caption{Main results.}
\begin{tabular}{cccccc}\hline
Region   & L$_{c}$  & m$_{2D}$  & l$_{0}$ [pc] & $\sigma$ [km/s] & L$_{c}$/l$_{0}$ \\\hline
NGC 604 & 178  &     1.7   &     11       &    7.3        & 16 	\\
NGC 595 & 200  &     1.7   &     11      &    6.6        & 18 	\\
Hubble V & 90  &     1.8   &     3       &    2.8      & 30 	\\
Hubble X & 100  &     1.7   &     5       &    3.6      & 20 	\\
\end{tabular}\label{tab:Res}
\end{center}
\end{table}

\begin{figure}
\centering 
\includegraphics[width=3.5in]{Figures/SF604.pdf}
\caption{NGC 604 second-order structure functions for H$\alpha$ emission line for ISIS and TAURUS instruments. The figure also shows the structure functions presented in previous works.}
\label{fig:SF604}
\end{figure}

\begin{figure}
\centering 
\includegraphics[width=4in]{Figures/SF595.pdf}
\caption{NGC 595 second-order structure functions for H$\alpha$ emission line for TAURUS instrument. The figure also shows the structure functions presented in previous works.}
\label{fig:SF595}
\end{figure}

\begin{figure}
\centering 
\includegraphics[width=3in]{Figures/HV}
\caption{Hubble V second-order structure functions for H$\alpha$ emission line for TAURUS instrument.}
\label{fig:SFV}
\end{figure}

\begin{figure}
\centering 
\includegraphics[width=3in]{Figures/HX}
\caption{Hubble X second-order structure functions for H$\alpha$ emission line for TAURUS instrument.}
\label{fig:SFX}
\end{figure}

\clearpage

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Discussion}\label{sec:disc}

\subsection{Comparison with previous structure functions determinations}

In an idealized case, at scales larger than r$_{0}$ the structure function flattens as it tends towards the asymptotic value of 2$\sigma$ \citep{arthur2016turbulence}. Figure \ref{fig:SF604} shows that the structure functions, except for \cite{2019arXiv191203543M}, follow a periodic behavior around 2$\sigma$. Using as reference the TAURUS results, the wave starts at 35 pc with a series of $ >$2$\sigma$ values up to $\sim$100 pc. Then $<$2$\sigma$ values follow until the largest scales of 150 pc. Therefore this periodic behavior is related to scales of 100 pc across our sample box.

Figure \ref{fig:SF604} shows similarity in the TAURUS results and previous works \citep{tanco1997,2019arXiv191203543M}. The agreement lies that observations are the same but the procedure of calculating the structure function is different. \citep{2019arXiv191203543M} has $\sigma$ of 7.2 while we have 7.3 km/s. We note that our structure function results are more similar to \cite{2019arXiv191203543M} but the periodic behavior is strongly reduced on their results; \citep{tanco1997} also show this periodic pattern at large scales.

Figure \ref{fig:SF595} shows how there is no correspondence between our results and previous investigations. Our observations cover the brightest part of the region and have smaller resolution. \citet{lagrois2011} structure function results does not cover scales $<$10 pc.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Conclusions}\label{sec:disc}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section*{Acknowledgements}

The Acknowledgements section is not numbered. Here you can thank helpful
colleagues, acknowledge funding agencies, telescopes and facilities used etc.
Try to keep it short.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%% REFERENCES %%%%%%%%%%%%%%%%%%

\bibliographystyle{mnras}
\bibliography{bibphd}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%% APPENDICES %%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Don't change these lines
\bsp	% typesetting comment
\label{lastpage}
\end{document}

% End of mnras_template.tex

### 2021-03-26 mnras_template.tex
Fix typos in addresses

@@
 % List of institutions
-$^{1}$Escuela Superior de Física y Matemáticas, Insituto Politécnico Nacional, Ciudad de México, México.\\
-$^{2}$Instunto de Radioastronomía y Astrofísica, Universidad Nacional Autonoma de México, Apartado postal 3-72, 58090 Morelia, Michoacán, Mexico\\
+$^{1}$Escuela Superior de Física y Matemáticas, Instituto Politécnico Nacional, Ciudad de México, México.\\
+$^{2}$Instituto de Radioastronomía y Astrofísica, Universidad Nacional Autonoma de México, Apartado postal 3-72, 58090 Morelia, Michoacán, Mexico\\
 }

### 2021-03-30 mnras_template.tex
Javier changes 27–30 March

@@
 
-%We have used longslit spectroscopy observations obtained with the William Herschel Telescope with the aim of characterizing the turbulent state of the ionized gas in giant HII regions.
-%For this purpose, the \halpha, \n, \oi\ and \s\ emission lines were investigated applying a statistical analysis on their velocities samples. 
-%The correlations in our results are evidence that the velocity field can be consider as homogeneous turbulence, a statistically stationary process.
-This turbulent motions can be described by a power law with a mean index of 0.60$\pm$0.02 and a physical coherent scale up to $\sim$60 pc for NGC 604 and 1.04$\pm$0.01 with a correlation length up to $\sim$60 pc for NGC 595.
-%The physical interpretation of our results consider that an energy cascade is taking place for all the ionic species.
-%Finally, we give our explanation for our results and fit them in the context of turbulence in giant HII regions.
-
+We used the radial velocity field in H$\alpha$ emission with the aim of characterizing the turbulent state of the ionized gas in giant HII regions.
+For this purpose we use long-slit spectroscopy and Fabry-Perot observations obtained with the William Herschel Telescope.
+Each velocity sample was investigated applying the second order structure function.
+The correlations in our results are evidence that the velocity field can be consider in a turbulent state.
+This turbulent motions are described by a power-law with a mean index of 1.7.
+The physical interpretation of the power-law behavior consider that an energy cascade is taking place in the photoionized gas.
 \end{abstract}
@@
 \begin{keywords}
-HII regions -- ISM: individual object: NGC 604 -- ISM: kinematics and dynamics -- techniques: spectroscopic -- turbulence
+HII regions -- ISM
 \end{keywords}
@@
 
-There is evidence that different phases of the interstellar medium exhibits a chaotic behavior \citep{franco1999interstellar,elmegreen2004interstellar,scalo2004interstellar}.
-Velocity fields shows complex motions in the plane-of-sky (POS) and a non-thermal broadening on their spectral lines, suggests disorder motions along the line-of-sight (LOS).
-The large lengths of astrophysical objects, ranging in scales from 10$^{6}$ to 10$^{17}$ m \citep{chepurnov2010extending}, is closely related to the existence of turbulent flows.
-The high Reynolds numbers (Re), in the order of 10$^{4}$ and 10$^{9}$, present in these objects \citep{lagrois2011} is taken as first approach to understand the relationship between turbulence and the observed movements.
+Different phases of the interstellar medium exhibits a chaotic behavior \citep{franco1999interstellar,elmegreen2004interstellar,scalo2004interstellar}.
+Velocity fields shows complex motions in the plane-of-sky (POS), and a non-thermal broadening on their spectral lines suggests disorder motions along the line-of-sight (LOS).
+The large lengths of astrophysical objects, ranging in scales from 10$^{6}$ to 10$^{17}$ m \citep{chepurnov2010extending}, and the high Reynolds numbers (Re), in the order of 10$^{4}$ and 10$^{9}$, of these objects \citep{lagrois2011} is related to the existence of turbulent flows.
 Despite numerous attempts in characterizing the turbulence in the photoionized gas, little understood on how the results indicate something about the physics of the object.
@@
 Their aim was to investigate the projection of a three-dimensional function into the plane of the sky.
-This procedure using the structure function allowed to determine a distinction between homogeneous turbulence and pure random velocity fluctuations, in this case in the galactic HII region, the Orion Nebula.
-The analysis on the turbulence of the Orion Nebula was continued by \citet{castaneda1987} and \citet{1992ApJ...387..229O}.
-In more recent years \cite{medina2014} and \cite{arthur2016turbulence} used another statistical technique called velocity channel analysis (VCA) \citep{2000ApJ...537..720L}, along the structure function, to study the Orion nebula.
+This procedure using the structure function allowed to determine a distinction between homogeneous turbulence and pure random velocity fluctuations, for the galactic HII region, the Orion Nebula.
+The analysis on the turbulence of the Orion Nebula was continued by \citet{castaneda1988} and \citet{1992ApJ...387..229O}.
+In more recent years \cite{medina2014} and \cite{arthur2016turbulence} used another statistical technique called velocity channel analysis (VCA) \citep{2000ApJ...537..720L}, along the structure function to study the same region.
 Recently, the structure function was used with full 6D measurements (position-velocity) to study the motions of stars in the Orion Molecular Cloud Complex.
@@
 \cite{2019arXiv191203543M} investigated the structure function in 30 Dor finding on their results that the structure function is entirely flat on scales from 3 to 200 pc.
-Also, \cite{2019arXiv191203543M} studied the motions in NGC 604, previously analyzed by \cite{tanco1997}.
+Also, \cite{2019arXiv191203543M} studied the motions in NGC 604, a GEHR previously analyzed by \cite{tanco1997}.
 Both results shows that there is a two slope behavior for the structure function.
@@
 \citet{melnick1977,terlevich1981} have shown an empirical relationship between the line width and the integrated properties of the HII regions as the diameter or the luminosity ($R \sim \sigma ^{\sim 2}$ ; $L \sim \sigma ^{\sim 4}$).
-They conclude that GEHR  follow this relations as self-gravity systems like globular clusters or elliptical galaxies.
+Correlations between kinematics and physical properties of GEHR have been common tools to study this excess.
+They conclude that GEHRs follow this relations as self-gravity systems like globular clusters or elliptical galaxies.
 The idea of a virial system has been developed by \citet{1993ApJ...418..767T,munoz1996} into the \textit{Cometary Stirring Model} (CSM) with the aim to separate the mechanism that contribute to the line broadening.
@@
 
-\citet{2000PASP..112.1138M} and \citep{maiz2004} provides details of the observational setup for the the ISIS instrument.
-In summary, the spectra were obtained (1998 18-19 August) using a position angle of 90$^{\circ}$ and the slit width was 1".
+\citet{2000PASP..112.1138M} and \citep{maiz2004} provides details of the observational setup for the the ISIS instrument (1998 18-19 August).
+In summary, the spectra were obtained  using a position angle of 90$^{\circ}$ and the slit width was 1".
 Two different spectra were taken simultaneously for each position: one for the red arm, between 6390 and 6849 \r{A} and another on the blue arm between 4665 and 5065 \r{A}.
@@
 This pixels has a value of -253.11 km/s.
-Figure \ref{fig:M595} shows the two-dimensional radial velocity map of NGC 595 in H$\alpha$.
+Figure \ref{fig:M595} and \ref{fig:MHub} shows the two-dimensional radial velocity map in H$\alpha$ of NGC 595, Hubble V and Hubble X, respectively.
 
@@
 
-\subsection{NGC 604}
-
 Figure \ref{fig:SF604} shows the structure function (Equation \ref{eq:S}) of NGC 604 for the H$\alpha$ emission line for the ISIS and TAURUS instruments.
@@
 
-\subsection{NGC 595}
-
-Figure \ref{fig:SF595} shows the structure function of NGC 595 for the H$\alpha$ emission line for the TAURUS instruments.
+Figure \ref{fig:SF595} shows the structure function of NGC 595 for the H$\alpha$ emission line.
 The $m_{2D}$ is 1.7 with a correlation length of 11 pc.
@@
 The values of the structure function rise until 30 pc.
-Scales larger than this shows a random around 2$\sigma$.
+Scales larger than this shows a random pattern around 2$\sigma$.
+
+Figure \ref{fig:SFV} shows the structure function of Hubble V for the H$\alpha$ emission line.
+The $m_{2D}$ is 1.8 with a correlation length of 4 pc and a $\sigma$ of 2.8 km/s.
+The structure function values keep going up and reach a maximum at $\sim$28 pc, above this value there is no clear pattern.
+
+Figure \ref{fig:SFX} shows the structure function of Hubble V for the H$\alpha$ emission line.
+The $m_{2D}$ is 1.7 with a correlation length of 4 pc.
+The $\sigma$ of the region is 3.6 km/s.
+For this region, the structure functions keeps its tendency of going up to a scale o $\sim$ 18 pc.
 
@@
 \centering 
-\includegraphics[width=3in]{Figures/HV}
+\includegraphics[width=2.5in]{Figures/HV}
 \caption{Hubble V second-order structure functions for H$\alpha$ emission line for TAURUS instrument.}
@@
 \centering 
-\includegraphics[width=3in]{Figures/HX}
+\includegraphics[width=2.5in]{Figures/HX}
 \caption{Hubble X second-order structure functions for H$\alpha$ emission line for TAURUS instrument.}
@@
 Then $<$2$\sigma$ values follow until the largest scales of 150 pc.
-Therefore this periodic behavior is related to scales of 100 pc across our sample box.
+Therefore this periodic behavior is related to scales of $\sim$100 pc across our sample box.
 
@@
 
-\section{Conclusions}\label{sec:disc}
+\section{Conclusions}\label{sec:concl}
 

### 2021-04-02 mnras_template.tex
Javier edits up to April 2

@@
 % Keep the title short and informative.
-\title[Turbulence in GEHRs]{Turbulence in giant extragalactic HII regions}
+\title[Turbulence in GHRs]{Turbulence in giant HII regions}
 
@@
 The correlations in our results are evidence that the velocity field can be consider in a turbulent state.
-This turbulent motions are described by a power-law with a mean index of 1.7.
+This turbulent motions are described by a power-law with a mean index of 1.7 and a correlation length of 11 pc.
 The physical interpretation of the power-law behavior consider that an energy cascade is taking place in the photoionized gas.
@@
 Velocity fields shows complex motions in the plane-of-sky (POS), and a non-thermal broadening on their spectral lines suggests disorder motions along the line-of-sight (LOS).
-The large lengths of astrophysical objects, ranging in scales from 10$^{6}$ to 10$^{17}$ m \citep{chepurnov2010extending}, and the high Reynolds numbers (Re), in the order of 10$^{4}$ and 10$^{9}$, of these objects \citep{lagrois2011} is related to the existence of turbulent flows.
-Despite numerous attempts in characterizing the turbulence in the photoionized gas, little understood on how the results indicate something about the physics of the object.
+The large lengths of astrophysical objects, ranging in scales from 10$^{6}$ to 10$^{17}$ m \citep{chepurnov2010extending}, and the high Reynolds numbers (Re), in the order of 10$^{4}$ and 10$^{9}$, of these objects \citep{lagrois2011} are related to the existence of turbulent flows.
+Despite numerous attempts in characterizing the turbulence in the photoionized gas, little is understood on the nature of the problem.
 
@@
 The analysis on the turbulence of the Orion Nebula was continued by \citet{castaneda1988} and \citet{1992ApJ...387..229O}.
-In more recent years \cite{medina2014} and \cite{arthur2016turbulence} used another statistical technique called velocity channel analysis (VCA) \citep{2000ApJ...537..720L}, along the structure function to study the same region.
+In more recent years \cite{arthur2016turbulence} used another statistical technique called velocity channel analysis (VCA) \citep{2000ApJ...537..720L}, along the structure function to study the same region.
 Recently, the structure function was used with full 6D measurements (position-velocity) to study the motions of stars in the Orion Molecular Cloud Complex.
@@
 
-\citet{smith1970} discovered that the line width of GEHRs was supersonic, of the order of $\sigma \sim$ 17-26 km s\kms.
+\citet{smith1970} discovered that the line width of GEHRs was supersonic in the order of $\sigma \sim$ 17-26 km s\kms.
 \citet{melnick1977,terlevich1981} have shown an empirical relationship between the line width and the integrated properties of the HII regions as the diameter or the luminosity ($R \sim \sigma ^{\sim 2}$ ; $L \sim \sigma ^{\sim 4}$).
@@
 
-Our objective is to characterize the turbulent regime for different ions in different GEHRs. We compare our results with previous investigations.
+NGC 604 is the brigthest giant HII region of M33 galaxy, located at the distance of 840 kpc (1'' = 4.1 pc) \citep{2015KamKinematics} with a length of 400 pc.
+It has a luminosity in L$_{H_\alpha}$ = 10$^{39.42}$ erg s$^{-1}$ \citep{2002MNRAS.329..481B} and in L$_{X}$=9.3$\times$ 10$^{35}$ erg s$^{-1}$ \citep{2008ApJ...685..919T}.
+\cite{2012ApJ...761....3M} derive an average age of 4$\pm$1 Myr and a total stellar mass of 1.6$^{+1.6}_{-1.0} \times$ 10$^{5}$M$_{\odot}$ for the region.
+The stellar population has been identified and classified by \cite{1996ApJ...456..174H} (and references therein).
+Recently, \citet{2011MNRAS.411..235E} focused on studying the Wolf-Rayet (WR) and red super giants (RSGs) stars population.
+\citet{2012AJ....143...43F} focused on the massive young stellar objects (MYSOs).
+The average ages for the stars, was determined to be from 3 to 5 Myr \citep{1996ApJ...456..174H} and with the RSGs as an older population have an age of 12.4 $\pm$ 2.1 Myr \citep{2011MNRAS.411..235E}.
+This suggest that two episodes of star formation, at least, have taken place in the GEHR.
+
+NGC 595 is the second brightest giant HII region in the M33 galaxy with a length of 300 pc.
+The electronic temperature is 7,670 $\pm$116 K \citep{2010MNRAS.402.1635R}.
+\cite{1983A&A...119..185V} made an estimate of the total masses of HI and HII in the nebula to obtain values of M$_{HI}=$ 1.2 $\times$ 10 $^{6}$ M$_{\odot}$ and M$_{HII} =$ 4.6 $\times$ 10 $^{5}$ M$_{\odot}$, and a ionizing luminosity of the star cluster is estimated at 5 $\times$ 10$^{50}$ erg s $^{1}$.
+\cite{1996AJ....111.1128M} estimate an age of 4.5 Myrs consistent with \cite{1993AJ....105.1400D}.
+It has approximately 250 stars of the OB type, 13 Supergiants and 9 WR \citep{1996AJ....111.1128M}, ten WRs confirmed with spectroscopy \cite{1993AJ....105.1400D}, nine of the WN type and a WC, located near the bright core of the region.
+
+The dwarf irregular galaxy, NGC 6822, is located at a distance of 500 kpc (1'' = 2.4 pc) \citep{1996AJ....112.1928G} and the brightest HII regions are Hubble V (HV) and Hubble X (HX).
+HV has a characteristic length of 100 pc and a luminosity at its core of in L$_{H_\alpha}$ = 1 $\times$ 10$^{49}$ H$\alpha$ photons s$^{-1}$ \citep{1999PASP..111.1382O}.
+HX has a characteristic length of 140 pc and a luminosity at its core of in L$_{H_\alpha}$ = 2.4 $\times$ 10$^{49}$ H$\alpha$ photons s$^{-1}$ \citep{1999PASP..111.1382O}.
+Two recognized OB associations \citep{1991ApJ...379..621H,1992AJ....104.1374W} are identified within the region of HV and HX.
+HV is located near 'Hodge OB 8', and HX is located near 'Hodge OB13'  \citep{1999PASP..111.1382O}.
+
+Our objective is to characterize the turbulent regime in different GEHRs. We compare our results with previous investigations.
+
+\subsection{Turbulence}\label{sec:turb}
+
+The classic turbulence theory \citep{kolm1} assumes a three-dimensional isotropic, incompressible and subsonic flow where an energy cascade is taking place.
+The energy cascade goes from the largest vortices where the energy in injected until it reaches dissipation with the smallest vortices.
+In the energy cascade three scales are defined based on their Reynolds number.
+The energy injection scale (Re $\rightarrow \infty$), $L_{EI}$, the dissipation scale (Re $\rightarrow$ 1), $L_{D}$ and the inertial scale ($L_{I}$) between the previous two.
+Since the energy distributions depends on the scale, the energy cascade concept is described with an energy spectrum, $E(k) \propto k^{-\beta}$ where $k$ is the wave number for a scale $l$ ($k \equiv l^{-1}$).
+
+We can consider that  the mean specific energy transfer, $\langle \epsilon \rangle$, in the inertial range can be denoted as $\epsilon \sim \frac{v_{l}^{2}}{\tau_{l}}$, where $v_{l}^{2}$ is the kinetic energy per mass unit and $\tau_{l}$ the time related with velocity fluctuations.
+Since the total specific energy of a determined $l$ scale is of the order $\langle v_{l}^{2} \rangle$, the energy integral above the associated $k$, defined as:
+
+\begin{equation}\label{eq:veles}
+ \langle v_{l}^{2} \rangle = \int_{k}^{\infty} E(k)dk
+\end{equation}
+
+Following that this energy is of the order of $(\epsilon l)^{\frac{2}{3}} \sim (\frac{\epsilon}{k})^{\frac{2}{3}}$ we can substitute in equation \ref{eq:veles} and obtain the Kolmogorov law:
+
+\begin{equation}\label{eq:kolm}
+E(k) \propto \epsilon^\frac{2}{3} k^{-\frac{5}{3}}
+\end{equation}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-The archival data used in this work was obtained with the ISIS spectrograph and the TAURUS-II Fabry Perot in the 4.2-m William Herschel Telescope (WHT) of del Roque de los Muchachos Observatory (ORM) in La Palma, Spain and was retrieved from the La Palma archive\footnote{\url{http://casu.ast.cam.ac.uk/casuadc/ingarch}}.
+The archival data used in this work was obtained with the long-slit ISIS and the Fabry Perot TAURUS-II instruments in the 4.2-m William Herschel Telescope (WHT) of del Roque de los Muchachos Observatory (ORM) in La Palma, Spain and was retrieved from the La Palma archive\footnote{\url{http://casu.ast.cam.ac.uk/casuadc/ingarch}}.
 
@@
 Figure \ref{fig:M604} shows the two-dimensional radial velocity map of NGC 604 in H$\alpha$.
-ISIS observations have been limited with the aim to match the zone cover by TAURUS instrument.
+ISIS observations (above) have been limited with the aim to match the zone covered by TAURUS instrument.
 The velocity scale on both instruments reflects the radial velocity in the reference frame of the region taking as a reference point the most luminous pixel.
@@
 
+\subsection{The second order structure function}
+
+We use the second order structure function, $S_{2}(l)$, defined as:
+
+\begin{equation}\label{eq:S}
+S_{2}(\boldsymbol{l})=\dfrac{\sum[V_{r}(\boldsymbol{x}+\boldsymbol{l})-V_{r}(\boldsymbol{x}) ]^{2}}{N(\boldsymbol{l})}
+\end{equation}
+
+as a statistical tool to investigate the relation between a velocity field and the presence of turbulent motions following the Kolmogorov theory.
+In equation \ref{eq:S}, $V_{r}(\boldsymbol{x})= V_{obs}(\boldsymbol{x})-\langle V_{obs}(\boldsymbol{x}) \rangle$ and N($\boldsymbol{l}$) the number of points at each separation.
+
+We can consider the quadratic velocities differences proportional to the left term in equation \ref{eq:kolm}:
+
+\begin{equation}\label{eq:sfi}
+(\Delta v)^{2} \sim (\epsilon l)^{\frac{2}{3}}
+\end{equation}
+
+the term $(\Delta v)^{2}$ can be identified as the structure function.
+The right term with index,  m=2/3, in equation \ref{eq:sfi} is related to the energy (the left term in equation \ref{eq:veles}).
+This index m serves as a reference for comparison between theory and observations.
+
+For our fit we use the normalized structure function of the form $s(l)=2[1-C(l)]$ where $C(l)=1/[1+(l/l_{0})^{m_{2D}}]$.
+The term l$_{0}$ is the correlation length of the turbulence and $m_{2D}$ is the index that adjust our results \citep{1984ApJ...277..556S, arthur2016turbulence}.
+
 \begin{figure}
@@
 \includegraphics[width=2.5in]{Figures/6ISIS.png}
-\includegraphics[width=2.5in]{Figures/6TAU.png}
+\includegraphics[width=2.5in]{Figures/M6T}
 \caption{Radial velocity maps of NGC 604 in H$\alpha$. Above: ISIS observations. Below: TAURUS observations. }
@@
 \centering 
-\includegraphics[width=2.5in]{Figures/5TAU.png}
+\includegraphics[width=2.5in]{Figures/M5T.png}
 \caption{Radial velocity maps of NGC 595 in H$\alpha$.}
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Results}\label{sec:res}
 
-\section{Turbulence}\label{sec:turb}
-
-The classic turbulence theory \citep{kolm1} assumes a three-dimensional isotropic, incompressible and subsonic flow, where an energy cascade is taking place.
-The energy cascades goes downward, from the largest vortices until it reaches dissipation with the smallest vortices.
-In this energy cascade three scales can be defined: the energy injection scale (Re $\rightarrow \infty$), $L_{EI}$, the dissipation scale (Re $\rightarrow$ 1), $L_{D}$ and the inertial scale ($L_{I}$) between the previous two.
-The energy cascade concept is described with an energy spectrum, $E(k) \propto k^{-\beta}$ where $k$ is the wave number for a scale $l$ ($k \equiv l^{-1}$).
-
-If we consider the mean specific energy transfer, $\langle \epsilon \rangle$, the inertial range can be denoted as $\epsilon \sim \frac{v_{l}^{2}}{\tau_{l}}$, where $v_{l}^{2}$ is the kinetic energy per mass unit and $\tau_{l}$ the time related with velocity fluctuations.
-Since the total specific energy of a determined $l$ scale is of the order $\langle v_{l}^{2} \rangle$ and is the energy integral above the associated $k$, defined as:
-
-\begin{equation}\label{eq:veles}
- \langle v_{l}^{2} \rangle = \int_{k}^{\infty} E(k)dk
-\end{equation}
-
-Considering that this energy is of the order of $(\epsilon l)^{\frac{2}{3}} \sim (\frac{\epsilon}{k})^{\frac{2}{3}}$ we can substitute in equation \ref{eq:veles} and obtain the Kolmogorov law:
-
-\begin{equation}\label{eq:kolm}
-E(k) \propto \epsilon^\frac{2}{3} k^{-\frac{5}{3}}
-\end{equation}
-
-We use the second order structure function, $S_{2}(l)$, defined as:
-
-\begin{equation}\label{eq:S}
-S_{2}(\boldsymbol{l})=\dfrac{\sum[V_{r}(\boldsymbol{x}+\boldsymbol{l})-V_{r}(\boldsymbol{x}) ]^{2}}{N(\boldsymbol{l})}
-\end{equation}
-
-as a statistical tool to investigate the relation between a velocity field and the presence of turbulent motions following the Kolmogorov theory.
-In equation \ref{eq:S}, $V_{r}(\boldsymbol{x})= V_{obs}(\boldsymbol{x})-\langle V_{obs}(\boldsymbol{x}) \rangle$ and N($\boldsymbol{l}$) the number of points at each separation.
-If we consider the quadratic velocities differences proportional to the left term in equation \ref{eq:kolm}:
-
-\begin{equation}\label{eq:sfi}
-(\Delta v)^{2} \sim (\epsilon l)^{\frac{2}{3}}
-\end{equation}
-
-the term $(\Delta v)^{2}$ can be identified as the structure function.
-The right term with index,  m=2/3, in equation \ref{eq:sfi} is related to the energy (the left term in equation \ref{eq:veles}).
-This index m serves as a reference for comparison between theory and observations.
-
-For our fit we use the normalized structure function of the form $s(l)=2[1-C(l)]$ where $C(l)=1/[1+(l/l_{0})^{m_{2D}}]$.
-The term l$_{0}$ is the correlation length of the turbulence and $m_{2D}$ is the index that adjust our results \citep{1984ApJ...277..556S, arthur2016turbulence}.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Results}\label{sec:res}
+Table \ref{tab:Res} shows the parameters we use to analyze our results.
+These are, the parameters obtained with a power-law fit of the structure function the index, m$_{2D}$, and the correlation length, l$_{0}$ and the ratio L$_{b}$/l$_{0}$, where L$_{b}$ is the horizontal size in pc of our sample box.
 
@@
 The $m_{2D}$ is 1.7 with a correlation length of 11 pc.
-The $\sigma$ for the ISIS instrument is 8.4 km/s and for TAURUS instrument 7.3 km/s.
+The $\sigma$ for the ISIS instrument is 8.4 km/s and for TAURUS instrument is 7.3 km/s.
 The fit to the power-law of the structure function is performed over the scales of 4 to 11 pc.
@@
 As \cite{arthur2016turbulence} mentioned, the more pronounced steeping for small scales, below 4 pc in our case, is due to the spatial resolution of the observations.
-In comparison with TAURUS, ISIS values are higher but are able to maintain the form of the structure function.
+In comparison with TAURUS values, ISIS values are higher but are able to maintain the form of the structure function.
 
@@
 The $\sigma$ is 6.6 km/s.
-In this case it is possible to fit values under 4 pc, but this small scale region is affected due to the seeing.
-The range of scale for this regions stays between 10 and 11 pc as in NGC 604.
 The values of the structure function rise until 30 pc.
-Scales larger than this shows a random pattern around 2$\sigma$.
 
@@
 The $m_{2D}$ is 1.8 with a correlation length of 4 pc and a $\sigma$ of 2.8 km/s.
-The structure function values keep going up and reach a maximum at $\sim$28 pc, above this value there is no clear pattern.
+The structure function values keep going up and reach a maximum at $\sim$28 pc.
 
@@
 \begin{tabular}{cccccc}\hline
-Region   & L$_{c}$  & m$_{2D}$  & l$_{0}$ [pc] & $\sigma$ [km/s] & L$_{c}$/l$_{0}$ \\\hline
-NGC 604 & 178  &     1.7   &     11       &    7.3        & 16 	\\
-NGC 595 & 200  &     1.7   &     11      &    6.6        & 18 	\\
-Hubble V & 90  &     1.8   &     3       &    2.8      & 30 	\\
-Hubble X & 100  &     1.7   &     5       &    3.6      & 20 	\\
+Region   &  m$_{2D}$  & l$_{0}$ [pc] & $\sigma$ [km/s] & L$_{b}$ [pc]  & L$_{b}$/l$_{0}$ \\\hline
+NGC 604 &     1.7   &     11       &    7.3         & 170  &  15.4 	\\
+NGC 595 &      1.7   &     11      &    6.6        & 200  & 18.1 \\
+Hubble V &   1.8   &     3       &    2.8      & 68  &     22.6  	\\
+Hubble X &     1.7   &     5       &    3.6      & 61  &  12.2 	\\
 \end{tabular}\label{tab:Res}
@@
 \includegraphics[width=3.5in]{Figures/SF604.pdf}
-\caption{NGC 604 second-order structure functions for H$\alpha$ emission line for ISIS and TAURUS instruments. The figure also shows the structure functions presented in previous works.}
+\caption{NGC 604 second-order structure functions for H$\alpha$ emission line for ISIS and TAURUS instruments.
+The figure also shows the structure functions presented in previous works.
+The green area represents the scales affected by observational seeing.
+The vertical line indicate the value of he correlation length.
+The horizontal line denote the value of $\sigma$.}
 \label{fig:SF604}
@@
 \includegraphics[width=4in]{Figures/SF595.pdf}
-\caption{NGC 595 second-order structure functions for H$\alpha$ emission line for TAURUS instrument. The figure also shows the structure functions presented in previous works.}
+\caption{NGC 595 second-order structure functions for H$\alpha$ emission line for TAURUS instrument.
+The figure also shows the structure functions presented in previous works.
+Same information as Figure \ref{fig:SF604}.}
 \label{fig:SF595}
@@
 \centering 
-\includegraphics[width=2.5in]{Figures/HV}
-\caption{Hubble V second-order structure functions for H$\alpha$ emission line for TAURUS instrument.}
+\includegraphics[width=2.5in]{Figures/SFHV}
+\caption{Hubble V second-order structure functions for H$\alpha$ emission line for TAURUS instrument. Same information as Figure \ref{fig:SF604}.}
 \label{fig:SFV}
@@
 \centering 
-\includegraphics[width=2.5in]{Figures/HX}
-\caption{Hubble X second-order structure functions for H$\alpha$ emission line for TAURUS instrument.}
+\includegraphics[width=2.5in]{Figures/SFHX}
+\caption{Hubble X second-order structure functions for H$\alpha$ emission line for TAURUS instrument. Same information as Figure \ref{fig:SF604}.}
 \label{fig:SFX}
@@
 In an idealized case, at scales larger than r$_{0}$ the structure function flattens as it tends towards the asymptotic value of 2$\sigma$ \citep{arthur2016turbulence}.
-Figure \ref{fig:SF604} shows that the structure functions, except for \cite{2019arXiv191203543M}, follow a periodic behavior around 2$\sigma$.
+Figure \ref{fig:SF604} shows that the structure functions for NGC 604, except for \cite{2019arXiv191203543M}, follow a periodic behavior around 2$\sigma$.
 Using as reference the TAURUS results, the wave starts at 35 pc with a series of $ >$2$\sigma$ values up to $\sim$100 pc.
@@
 
+For NGC 595, above 30 pc a random pattern is around 2$\sigma$. Also, we can see this behavior for Hubble V, above 28 pc and Hubble X above 18 pc.
+
 Figure \ref{fig:SF604} shows similarity in the TAURUS results and previous works \citep{tanco1997,2019arXiv191203543M}.
@@
 \citep{2019arXiv191203543M} has $\sigma$ of 7.2 while we have 7.3 km/s.
-We note that our structure function results are more similar to \cite{2019arXiv191203543M} but the periodic behavior is strongly reduced on their results; \citep{tanco1997} also show this periodic pattern at large scales.
+We note that our structure function results are more similar to \cite{2019arXiv191203543M} but the periodic behavior is strongly reduced on their results.
+\citep{tanco1997} also show this periodic pattern at large scales.
 
@@
 \section{Conclusions}\label{sec:concl}
+
+\begin{enumerate}
+    \item The giant HII regions in  M 33, NGC 604 and NGC 595 shows the same index and correlation lengths of 1.7 and 11 pc.
+These despite the noted differences on their physical properties and stellar populations.
+For NGC 604 wee find agreement in the structure function results between our data and previous publications.
+For NGC 595 our results are different from previous structure functions.
+
+    \item Structure functions are presented for the first time for Hubble X and Hubble V, in NGC 6822.
+Hubble V shows and index of 1.8 and a correlation length of 4 pc, while Hubble X results are 1.7 and 5 pc.
+
+\end{enumerate}
 

### 2021-04-09 mnras_template.tex
Javier changes: week to Thursday 8 April

@@
 
-The first attempt at characterizing turbulence in a giant extragalactic HII region (GEHR) was done by \citet{1961MNRAS.122....1F} with the 30 Dor complex in the LMC, finding no indication of turbulent motions.
+The first attempt at characterizing turbulence in a giant extragalactic HII region, GEHR, was done by \citet{1961MNRAS.122....1F} with the 30 Dor complex in the LMC, finding no indication of turbulent motions.
 \cite{2019arXiv191203543M} investigated the structure function in 30 Dor finding on their results that the structure function is entirely flat on scales from 3 to 200 pc.
@@
 
-NGC 604 is the brigthest giant HII region of M33 galaxy, located at the distance of 840 kpc (1'' = 4.1 pc) \citep{2015KamKinematics} with a length of 400 pc.
+NGC 604 is the brigthest giant HII region in the M33 galaxy, located at the distance of 840 kpc (1'' = 4.1 pc) \citep{2015KamKinematics} with a length of 400 pc.
 It has a luminosity in L$_{H_\alpha}$ = 10$^{39.42}$ erg s$^{-1}$ \citep{2002MNRAS.329..481B} and in L$_{X}$=9.3$\times$ 10$^{35}$ erg s$^{-1}$ \citep{2008ApJ...685..919T}.
@@
 
+\subsection{Structure function power indices}
+
+It is possible to compute the m$_{3D}$ index from m$_{2D}$ if we assume that the m$_{3D}$ index lies between the limits of projection smoothing and a sheet-like distribution \citep{arthur2016turbulence}, throgught the relationship  m$_{2D}$ - 1 $<$ m$_{3D}$ $<$ m$_{2D}$.
+We have 0.8 $<$ m$_{3D}$ $<$ 1.7, been m$_{3D}$ above the Kolmogorv prediction.
+This shouldn't be a surprise since physical conditions in GEHRs are different from the homogeneous and incompressible ideal model \citep{munch1958internal, castaneda1988,lagrois2011}.
+
 \clearpage

### 2021-04-09 mnras_template.tex
Start writing section on Galactic regions

@@
 
-We used the radial velocity field in H$\alpha$ emission with the aim of characterizing the turbulent state of the ionized gas in giant HII regions.
-For this purpose we use long-slit spectroscopy and Fabry-Perot observations obtained with the William Herschel Telescope.
-Each velocity sample was investigated applying the second order structure function.
-The correlations in our results are evidence that the velocity field can be consider in a turbulent state.
-This turbulent motions are described by a power-law with a mean index of 1.7 and a correlation length of 11 pc.
+We study the turbulent velocity fluctuations in the ionized gas of four giant HII regions using the radial velocity field in the H$\alpha$ emission line.
+The data was acquired by long-slit spectroscopy and Fabry-Perot observations obtained with the William Herschel Telescope.
+Each velocity sample is statistically analyzed with the second order structure function.
+The correlations in our results shows evidence that the velocity field can be consider in a turbulent state.
+This turbulent motions are described by a power-law with a mean index of 1.7 for different sized regions at different distances.
 The physical interpretation of the power-law behavior consider that an energy cascade is taking place in the photoionized gas.
@@
 
-Different phases of the interstellar medium exhibits a chaotic behavior \citep{franco1999interstellar,elmegreen2004interstellar,scalo2004interstellar}.
-Velocity fields shows complex motions in the plane-of-sky (POS), and a non-thermal broadening on their spectral lines suggests disorder motions along the line-of-sight (LOS).
-The large lengths of astrophysical objects, ranging in scales from 10$^{6}$ to 10$^{17}$ m \citep{chepurnov2010extending}, and the high Reynolds numbers (Re), in the order of 10$^{4}$ and 10$^{9}$, of these objects \citep{lagrois2011} are related to the existence of turbulent flows.
+Previous studies \citep{1999intu.conf.....F,2004ARA&A..42..211E,scalo2004interstellar} have shown that different phases of the interstellar medium exhibits a chaotic behavior on their velocity field.
+Complex motions are measured in the plane-of-sky (POS), and a non-thermal broadening on their spectral lines suggests disorder motions along the line-of-sight (LOS).
 Despite numerous attempts in characterizing the turbulence in the photoionized gas, little is understood on the nature of the problem.
 
-The mathematical techniques developed by \citet{kolm1,heisenberg1951stability} were first applied to astronomical observations by \citet{von1951methode} and \citet{munch1958internal}.
+\citet{smith1970} discovered that the line width of GEHRs was supersonic in the order of $\sigma \sim$ 17-26 km s\kms.
+\citet{melnick1977,terlevich1981} have shown an empirical relationship between the line width and the integrated properties of the HII regions as the diameter or the luminosity ($R \sim \sigma ^{\sim 2}$ ; $L \sim \sigma ^{\sim 4}$).
+Correlations between kinematics and physical properties of GEHR have been common tools to study this excess.
+They conclude that GEHRs follow this relations as self-gravity systems like globular clusters or elliptical galaxies.
+The idea of a virial system has been developed by \citet{1993ApJ...418..767T,munoz1996} into the \textit{Cometary Stirring Model} (CSM) with the aim to separate the mechanism that contribute to the line broadening.
+
+The stellar winds also tend to be used for an explanation of the line broadening and turbulence in GEHRs \citep{1994ApJ...425..720C}.
+This features seems to drive visually the regions with filaments, arcs and shells.
+On their spectra double and multiple emission features are signature of these objects.
+\cite{2020MNRAS.494...97S} argue that winds on ionizing clusters in GEHR must merge into a hot cluster because of the close proximity of the massive stars.
+\cite{2019ApJ...871...17U} propose that stellar feedback is an important source of energy to maintain turbulence in nearby galaxies.
+
+%The large lengths of astrophysical objects, ranging in scales from 10$^{6}$ to 10$^{17}$ m \citep{2010ApJ...710..853C}, and the high Reynolds numbers (Re), in the order of 10$^{4}$ and 10$^{9}$, of these objects \citep{lagrois2011} are related to the existence of turbulent flows.
+
+The mathematical techniques developed by \citet{kolm1,1948ZPhy..124..628H} were first applied to astronomical observations by \citet{von1951methode} and \citet{munch1958internal}.
 Their aim was to investigate the projection of a three-dimensional function into the plane of the sky.
 This procedure using the structure function allowed to determine a distinction between homogeneous turbulence and pure random velocity fluctuations, for the galactic HII region, the Orion Nebula.
+
 The analysis on the turbulence of the Orion Nebula was continued by \citet{castaneda1988} and \citet{1992ApJ...387..229O}.
@@
 Also, \cite{2019arXiv191203543M} studied the motions in NGC 604, a GEHR previously analyzed by \cite{tanco1997}.
-Both results shows that there is a two slope behavior for the structure function.
-The structure function in the GEHR NGC 595 was first obtained by \cite{lagrois2009multi} and the analysis was expanded by \cite{lagrois2011}.
+The structure function in the GEHR NGC 595 was first obtained by \cite{lagrois2009multi} and the statistical analysis was expanded by \cite{lagrois2011}.
 In all previous studies the Kolmogorov law does not apply to any result.
 
-GEHRs are ideal objects for the study of turbulence in the interstellar medium.
+%GEHRs are ideal objects for the study of turbulence.
 These objects have large dimensions ($ \geq $100 pc) and high luminosity ($10^{38}<$ L$_{H\alpha}<10^{40}$ erg s$^{-1}$).
@@
 
-\citet{smith1970} discovered that the line width of GEHRs was supersonic in the order of $\sigma \sim$ 17-26 km s\kms.
-\citet{melnick1977,terlevich1981} have shown an empirical relationship between the line width and the integrated properties of the HII regions as the diameter or the luminosity ($R \sim \sigma ^{\sim 2}$ ; $L \sim \sigma ^{\sim 4}$).
-Correlations between kinematics and physical properties of GEHR have been common tools to study this excess.
-They conclude that GEHRs follow this relations as self-gravity systems like globular clusters or elliptical galaxies.
-The idea of a virial system has been developed by \citet{1993ApJ...418..767T,munoz1996} into the \textit{Cometary Stirring Model} (CSM) with the aim to separate the mechanism that contribute to the line broadening.
-The stellar winds also tend to be used for an explanation of the line broadening and turbulence in GEHRs \citep{1994ApJ...425..720C}.
-This features seems to drive visually the regions with filaments, arcs and shells.
-On their spectra double and multiple emission features are signature of these objects.
-\cite{2020MNRAS.494...97S} argue that winds on ionizing clusters in GEHR must merge into a hot cluster because of the close proximity of the massive stars.
-\cite{2019ApJ...871...17U} propose that stellar feedback is an important source of energy to maintain turbulence in nearby galaxies.
-
-NGC 604 is the brigthest giant HII region in the M33 galaxy, located at the distance of 840 kpc (1'' = 4.1 pc) \citep{2015KamKinematics} with a length of 400 pc.
+NGC 604 is the brightest giant HII region in the M33 galaxy visually dominated by a big loop, many shells and different size filaments.
+It is located at the distance of 840 kpc (1'' = 4.1 pc) \citep{2015KamKinematics} with a length of 400 pc.
 It has a luminosity in L$_{H_\alpha}$ = 10$^{39.42}$ erg s$^{-1}$ \citep{2002MNRAS.329..481B} and in L$_{X}$=9.3$\times$ 10$^{35}$ erg s$^{-1}$ \citep{2008ApJ...685..919T}.
 \cite{2012ApJ...761....3M} derive an average age of 4$\pm$1 Myr and a total stellar mass of 1.6$^{+1.6}_{-1.0} \times$ 10$^{5}$M$_{\odot}$ for the region.
-The stellar population has been identified and classified by \cite{1996ApJ...456..174H} (and references therein).
+
+%The stellar population has been identified and classified by \cite{1996ApJ...456..174H} (and references therein).
 Recently, \citet{2011MNRAS.411..235E} focused on studying the Wolf-Rayet (WR) and red super giants (RSGs) stars population.
@@
 This suggest that two episodes of star formation, at least, have taken place in the GEHR.
+\citep{1984A&A...141...49H} identified a gradient from the west to the SE of the nebula of 30 km s$^{1}$.
 
@@
 \cite{1996AJ....111.1128M} estimate an age of 4.5 Myrs consistent with \cite{1993AJ....105.1400D}.
-It has approximately 250 stars of the OB type, 13 Supergiants and 9 WR \citep{1996AJ....111.1128M}, ten WRs confirmed with spectroscopy \cite{1993AJ....105.1400D}, nine of the WN type and a WC, located near the bright core of the region.
+
+%It has approximately 250 stars of the OB type, 13 Supergiants and 9 WR \citep{1996AJ....111.1128M}, ten WRs confirmed with spectroscopy \cite{1993AJ....105.1400D}, nine of the WN type and a WC, located near the bright core of the region.
 
@@
 HX has a characteristic length of 140 pc and a luminosity at its core of in L$_{H_\alpha}$ = 2.4 $\times$ 10$^{49}$ H$\alpha$ photons s$^{-1}$ \citep{1999PASP..111.1382O}.
-Two recognized OB associations \citep{1991ApJ...379..621H,1992AJ....104.1374W} are identified within the region of HV and HX.
+
+%Two recognized OB associations \citep{1991ApJ...379..621H,1992AJ....104.1374W} are identified within the region of HV and HX.
 HV is located near 'Hodge OB 8', and HX is located near 'Hodge OB13'  \citep{1999PASP..111.1382O}.
 
-Our objective is to characterize the turbulent regime in different GEHRs. We compare our results with previous investigations.
+Our objective is to characterize the turbulent regime in different GEHRs... We compare our results with previous investigations...
 
@@
 The classic turbulence theory \citep{kolm1} assumes a three-dimensional isotropic, incompressible and subsonic flow where an energy cascade is taking place.
-The energy cascade goes from the largest vortices where the energy in injected until it reaches dissipation with the smallest vortices.
+%The energy cascade goes from the largest vortices where the energy in injected until it reaches dissipation with the smallest vortices.
 In the energy cascade three scales are defined based on their Reynolds number.
 The energy injection scale (Re $\rightarrow \infty$), $L_{EI}$, the dissipation scale (Re $\rightarrow$ 1), $L_{D}$ and the inertial scale ($L_{I}$) between the previous two.
-Since the energy distributions depends on the scale, the energy cascade concept is described with an energy spectrum, $E(k) \propto k^{-\beta}$ where $k$ is the wave number for a scale $l$ ($k \equiv l^{-1}$).
+Since the energy distributions depends on the scale, the energy cascade concept is described with an energy spectrum, $E(k) \propto k$ where $k$ is the wave number for a determined scale $l$ ($k \equiv l^{-1}$).
 
-We can consider that  the mean specific energy transfer, $\langle \epsilon \rangle$, in the inertial range can be denoted as $\epsilon \sim \frac{v_{l}^{2}}{\tau_{l}}$, where $v_{l}^{2}$ is the kinetic energy per mass unit and $\tau_{l}$ the time related with velocity fluctuations.
+Is possible to consider that the mean specific energy transfer, $\langle \epsilon \rangle$, in the inertial range can be denoted as $\epsilon \sim \frac{v_{l}^{2}}{\tau_{l}}$; where $v_{l}^{2}$ is the kinetic energy per mass unit and $\tau_{l}$ the time related with velocity fluctuations.
+
 Since the total specific energy of a determined $l$ scale is of the order $\langle v_{l}^{2} \rangle$, the energy integral above the associated $k$, defined as:
@@
 
-Following that this energy is of the order of $(\epsilon l)^{\frac{2}{3}} \sim (\frac{\epsilon}{k})^{\frac{2}{3}}$ we can substitute in equation \ref{eq:veles} and obtain the Kolmogorov law:
+This energy,of the order of $(\epsilon l)^{\frac{2}{3}} \sim (\frac{\epsilon}{k})^{\frac{2}{3}}$, can be substituted in equation \ref{eq:veles}, obtaining the Kolmogorov law:
 
@@
 In summary, the spectra were obtained  using a position angle of 90$^{\circ}$ and the slit width was 1".
-Two different spectra were taken simultaneously for each position: one for the red arm, between 6390 and 6849 \r{A} and another on the blue arm between 4665 and 5065 \r{A}.
 The slit had a length of 200" and ten  positions  were observe with an exposure time ranging from 900 to 1200 s for every slit.
@@
 
+\subsection{Regions in the Milky Way and Large Magellanic Cloud}
+\label{sec:regions-milky-way}
+
+We measure the second-order velocity structure function for a number of more compact and lower luminosity regions:
+the Orion Nebula \citep{arthur2016turbulence}; 
+the Lagoon Nebula \citep{Damiani:2017b};
+the Carina Nebula \citep{Damiani:2016a};
+the Tarantula Nebula (30~Dor) in the LMC \citep{Castro:2018a}.
+
+In order to study the structure function 
+We include
+
 \section{Results}\label{sec:res}
 
-Table \ref{tab:Res} shows the parameters we use to analyze our results.
-These are, the parameters obtained with a power-law fit of the structure function the index, m$_{2D}$, and the correlation length, l$_{0}$ and the ratio L$_{b}$/l$_{0}$, where L$_{b}$ is the horizontal size in pc of our sample box.
+Table \ref{tab:Res} shows the main parameters we obtain.
+These are: the parameters obtained with a power-law fit of the structure function the index, m$_{2D}$, and the correlation length, l$_{0}$ and the ratio L$_{b}$/l$_{0}$, where L$_{b}$ is the horizontal size in pc of our sample box.
 
@@
 % End of mnras_template.tex
+%%% Local Variables:
+%%% mode: latex
+%%% TeX-master: t
+%%% End:

### 2021-04-22 mnras_template.tex
Javier changes up to April 22

@@
 
-\subsection{Regions in the Milky Way and Large Magellanic Cloud}
-\label{sec:regions-milky-way}
-
-We measure the second-order velocity structure function for a number of more compact and lower luminosity regions:
-the Orion Nebula \citep{arthur2016turbulence}; 
-the Lagoon Nebula \citep{Damiani:2017b};
-the Carina Nebula \citep{Damiani:2016a};
-the Tarantula Nebula (30~Dor) in the LMC \citep{Castro:2018a}.
-
-In order to study the structure function 
-We include
-
 \section{Results}\label{sec:res}
@@
 % End of mnras_template.tex
-%%% Local Variables:
-%%% mode: latex
-%%% TeX-master: t
-%%% End:

### 2021-05-03 mnras_template.tex
Re-write the abstract

--- 2021-04-09 mnras_template.tex
@@
 % Basic setup. Most papers should leave these options alone.
-\documentclass[fleqn,usenatbib]{mnras}
+\documentclass[fleqn,usenatbib, useAMS, a4paper]{mnras}
 
@@
 % out the following line
-\usepackage{newtxtext,newtxmath}
+\usepackage{newtxtext}
+\usepackage[varg,varvw,smallerops]{newtxmath}
 % Depending on your LaTeX fonts installation, you might get better results with one of these:
@@
 
+% A better \ion command that works in more circumstances
+\newcommand\ION[2]{#1\,\scalebox{0.9}[0.8]{\uppercase{#2}}}
+\newcounter{ionstage}
+\renewcommand{\ion}[2]{\setcounter{ionstage}{#2}% 
+  \ensuremath{\mathrm{#1\,\scriptstyle\Roman{ionstage}}}}
+\newcommand\hii{\ion{H}{2}}
+\newcommand\pos{\ensuremath{_{\mathrm{pos}}}}
+\newcommand\los{\ensuremath{_{\mathrm{los}}}}
+
 \newcommand\halpha{H${\alpha}$}
@@
 % Keep the title short and informative.
-\title[Turbulence in GHRs]{Turbulence in giant HII regions}
+\title[Turbulence in H II regiosn]{Turbulence in compact to giant HII regions}
 
@@
 \begin{abstract}
-
-We study the turbulent velocity fluctuations in the ionized gas of four giant HII regions using the radial velocity field in the H$\alpha$ emission line.
+  Fluctuations of centroid velocities on the plane of the sky are a powerful tool for studying the turbulent dynamics of emission line regions.
+  We apply the technique to archival observations of a diverse sample of 8 \hii{} regions
+  in the Milky Way and other Local Group galaxies,
+  which span more than two orders of magnitude in size and luminosity.
+  By fitting a simple functional form to the second-order velocity structure function,
+  we extract three parameters for the fluctuations in each region:
+  total velocity dispersion, \(\sigma\),
+  autocorrelation length, \(r_0\), and power-law slope, \(m\).
+  The velocity dispersion is found to correlate primarily with luminosity,
+  while the autocorrelation length correlates primarily with the size of the region.
+  The power-law slope shows an apparent correlation with distance,
+  but this is probably an artifact of poor spatial resolution for the most distant regions.
+  \textbf{Add a sentence about the conclusions!}
+  % We study the turbulent velocity fluctuations in the ionized gas of four giant HII regions using the radial velocity field in the H$\alpha$ emission line.
 The data was acquired by long-slit spectroscopy and Fabry-Perot observations obtained with the William Herschel Telescope.

### 2021-06-25 mnras_template.tex
Javier changes up to 2021-06-25

@@
 \usepackage{amssymb}	% Extra maths symbols
+\usepackage{multicol}
 
@@
 \newcommand\ION[2]{#1\,\scalebox{0.9}[0.8]{\uppercase{#2}}}
+
 \newcounter{ionstage}
@@
   \ensuremath{\mathrm{#1\,\scriptstyle\Roman{ionstage}}}}
+
 \newcommand\hii{\ion{H}{2}}
@@
 % Keep the title short and informative.
-\title[Turbulence in H II regiosn]{Turbulence in compact to giant HII regions}
+\title[Turbulence in H II regions]{Turbulence in compact to giant HII regions}
 
@@
 
-Previous studies \citep{1999intu.conf.....F,2004ARA&A..42..211E,scalo2004interstellar} have shown that different phases of the interstellar medium exhibits a chaotic behavior on their velocity field.
-Complex motions are measured in the plane-of-sky (POS), and a non-thermal broadening on their spectral lines suggests disorder motions along the line-of-sight (LOS).
-Despite numerous attempts in characterizing the turbulence in the photoionized gas, little is understood on the nature of the problem.
+The large lengths of astrophysical objects, ranging in scales from 10$^{6}$ to 10$^{17}$ m \citep{2010ApJ...710..853C}, and the high Reynolds numbers (Re), in the order of 10$^{4}$ - 10$^{9}$, are the main properties that builds the idea of a turbulent interstellar medium.
+Previous studies \citep{1999intu.conf.....F,2004ARA&A..42..211E,scalo2004interstellar} revealed that different phases of the interstellar medium show fluctuations on their velocity field, evidence of random motions.
+The usual picture considers that interstellar turbulence is driven on different scales by various energetic processes.
+Also, It is thought that the formation of structures like filaments and shells in the diffuse medium is determined by large-scale turbulence.
+Stars are the mainly mechanism proposed to account for the large input of kinetic energy through UV radiation, but the dominant energetic sources an their relation to turbulence still is unclear.
 
+The classic turbulence theory \citep{kolm1} assumes a three-dimensional isotropic, incompressible and subsonic flow where an energy cascade is taking place.
+The interstellar matter does not have those physical properties and our observations are in two-dimensions.
+But as mentioned above the idea of an energy cascade is used to understand our observations.
+The energy cascade goes from the largest vortices where the energy in injected until it reaches dissipation with the smallest vortices.
+In the energy cascade three scales are defined based on their Reynolds number.
+The energy injection scale (Re $\rightarrow \infty$), $L_{EI}$, the dissipation scale (Re $\rightarrow$ 1), $L_{D}$ and the inertial scale, $L_{I}$, between the previous two.
+Since the energy distributions depends on the scale, the energy cascade concept is described with an energy spectrum, $E(k) \propto k$ where $k$ is the wave number for a determined scale $l$ ($k \equiv r^{-1}$).
+
+The fluctuations associated with the centroid velocities on the plane-of-sky (POS) of photoionized regions have been characterized several times using the second order structure function (the Fourier transform of the energy spectrum, $E(k)$).
+This studies span from galactic HII regions like Orion \citep{von1951methode,munch1958internal,castaneda1988,1992ApJ...387..229O,arthur2016turbulence} to giant HII regions \citep{1961MNRAS.122....1F,lagrois2009multi,lagrois2011}, like NGC 604 in the M 33 galaxy \citep{tanco1997,2019arXiv191203543M}.
+
+The procedure using the structure function allow us to determine a distinction between homogeneous turbulence and pure random velocity fluctuations in the photoionized gas, but despite the previous evidence of this fluctuations not been random, little is understood about their nature.
+Several problems arise in the study of these fluctuation.
+Intrinsic with observations there is the projection of a three-dimensional function into the plane-of-sky \citep{von1951methode,munch1958internal}.
+Other statistical techniques like velocity channel analysis (VCA) \citep{2000ApJ...537..720L} have been proved to better recreate the spectrum of the velocity field \citep{medina2014,arthur2016turbulence}.
+More recently, the structure function was used with full 6D measurements (position-velocity) to study the motions of stars in the Orion Molecular Cloud Complex.
+\cite{2021ApJ...907L..40H} argue that newborn stars should reflect the turbulent kinematics of their natal clouds.
+Using this previous method they are free of the projected element that interfere with previous gas-based studies and their results agree with the scaling law proposed by \cite{1981MNRAS.194..809L}.
+
+The non-thermal broadening on the spectral emission lines also has been suggested as evidence of disorder motions along the line-of-sight (LOS).
 \citet{smith1970} discovered that the line width of GEHRs was supersonic in the order of $\sigma \sim$ 17-26 km s\kms.
 \citet{melnick1977,terlevich1981} have shown an empirical relationship between the line width and the integrated properties of the HII regions as the diameter or the luminosity ($R \sim \sigma ^{\sim 2}$ ; $L \sim \sigma ^{\sim 4}$).
-Correlations between kinematics and physical properties of GEHR have been common tools to study this excess.
 They conclude that GEHRs follow this relations as self-gravity systems like globular clusters or elliptical galaxies.
 The idea of a virial system has been developed by \citet{1993ApJ...418..767T,munoz1996} into the \textit{Cometary Stirring Model} (CSM) with the aim to separate the mechanism that contribute to the line broadening.
-
 The stellar winds also tend to be used for an explanation of the line broadening and turbulence in GEHRs \citep{1994ApJ...425..720C}.
@@
 
-%The large lengths of astrophysical objects, ranging in scales from 10$^{6}$ to 10$^{17}$ m \citep{2010ApJ...710..853C}, and the high Reynolds numbers (Re), in the order of 10$^{4}$ and 10$^{9}$, of these objects \citep{lagrois2011} are related to the existence of turbulent flows.
+Despite different issues that are related with the nature of the problem of turbulence in HII regions, the vast majority of research using the second-order structure function consider individual regions and hence different methodology.
+\cite{1987ApJ...317..686O} has determined the structure functions for a sample of galactic HII regions but isn't conclusive about them.
+The individuality of previous works and the need to understand the relationship between the measured turbulent properties for different classes of HII regions has lead us to develop this investigation.
 
-The mathematical techniques developed by \citet{kolm1,1948ZPhy..124..628H} were first applied to astronomical observations by \citet{von1951methode} and \citet{munch1958internal}.
-Their aim was to investigate the projection of a three-dimensional function into the plane of the sky.
-This procedure using the structure function allowed to determine a distinction between homogeneous turbulence and pure random velocity fluctuations, for the galactic HII region, the Orion Nebula.
+Using archival data we perform the second-order structure function on a sample of HII regions.
+Our sample spans in size from 4 pc to 400 pc and has luminosities between 10\(^{37}\) - 10\(^{39}\) erg s\(^{-1}\); from galactic to extragalactic HII regions.
+We apply an uniform methodology of a functional form of the structure function to characterize the turbulent using the  autocorrelation length, \(r_0\), and power-law slope, \(m\).
+Our results are compared with physical properties of each region, which reveal correlations between them, and are also compared with previous investigations.
+With this work we aim to fill a gap in statistical analysis of turbulence between galactic and giant HII regions.
 
-The analysis on the turbulence of the Orion Nebula was continued by \citet{castaneda1988} and \citet{1992ApJ...387..229O}.
-In more recent years \cite{arthur2016turbulence} used another statistical technique called velocity channel analysis (VCA) \citep{2000ApJ...537..720L}, along the structure function to study the same region.
-Recently, the structure function was used with full 6D measurements (position-velocity) to study the motions of stars in the Orion Molecular Cloud Complex.
-\cite{2021ApJ...907L..40H} argue that newborn stars should reflect the turbulent kinematics of their natal clouds.
-Using this previous method they are free of the projected element that interfere with previous gas-based studies and their results agree with the scaling law proposed by \cite{1981MNRAS.194..809L}.
+\section{HII regions sample}
 
-The first attempt at characterizing turbulence in a giant extragalactic HII region, GEHR, was done by \citet{1961MNRAS.122....1F} with the 30 Dor complex in the LMC, finding no indication of turbulent motions.
-\cite{2019arXiv191203543M} investigated the structure function in 30 Dor finding on their results that the structure function is entirely flat on scales from 3 to 200 pc.
-Also, \cite{2019arXiv191203543M} studied the motions in NGC 604, a GEHR previously analyzed by \cite{tanco1997}.
-The structure function in the GEHR NGC 595 was first obtained by \cite{lagrois2009multi} and the statistical analysis was expanded by \cite{lagrois2011}.
-In all previous studies the Kolmogorov law does not apply to any result.
+\subsection{Regions in the Milky Way and Large Magellanic Cloud}
+\label{sec:regions-milky-way}
 
-%GEHRs are ideal objects for the study of turbulence.
-These objects have large dimensions ($ \geq $100 pc) and high luminosity ($10^{38}<$ L$_{H\alpha}<10^{40}$ erg s$^{-1}$).
-There is a strong interaction between the stars clusters ($\geq$100 stars with T$_{eff}\geq30,000\ $K) and the surrounding medium (n$_{e}$=1-10$^4$ cm$^{-3}$ and T$_{e}$=10,000 K) via the injection of mechanical energy and the momentum given to the ionized gas \citep{castaneda1992density}.
-This energy and momentum comes in the form of stellar winds (v$_{w}\sim$ 1000 km s$^{-1}$) of the O ($\dot{M}$=$10^{-5} M_{\odot}\ yr^{-1}$) and B ($\dot{M}$=$10^{-6.5} M_{\odot}\ yr^{-1}$) stars \citep{dyson1979}.
+We used previous published observational data to measure the second-order velocity structure function for a number of compact and lower luminosity regions.
+
+We use data from \cite{1987A&A...176..347H} of the Orion Nebula (M42) located at 440 pc \citep{2008AJ....136.1566O}.
+Its physical and kinematics properties along its stellar population are well documented in the review of \cite{2001ARA&A..39...99O}.
+The main ionizing star is $\theta^{1}$Ori C (spectral type $\sim$O7) with fast stellar wind, and 3 B-type stars from the Trapezium cluster.
+The position of Orion near the side of the Orion Molecular Cloud (OMC-1) make it an ongoing star formation region and a example of a blister HII region \citep{arthur2016turbulence}.
+
+Archival data from \cite{Damiani:2016a} and \cite{Damiani:2017b} are use to study the Carina nebula and Lagoon nebula, respectively.
+
+The Carina Nebula is located at a distance of 2.35$\pm$0.05 kpc \citep{2006ApJ...644.1151S}.
+Young clusters like Trumpler 14 and 16, and Collinder 228 together they form the Car OB1 association.
+This OB association has more than 60 stars earlier than B0, and several Wolf-Rayet stars.
+The most star is a luminous blue variable, $\eta$ Car \citep{Damiani:2016a}.
+
+The Lagoon Nebula (M8, NGC6523) is located at a distance of 1 250 pc \citep{2005A&A...430..941P}.
+It is present on the nebula the young stellar cluster NGC6530.
+The region is illuminated by different massive stars of spectral types O and B, the hottest being 9 Sgr, type O4V \citep{Damiani:2017b}.
+Optically, the brightest part of the nebula is called 'Hourglass nebula' which surrounds and obscures the star Herschel 36, type O7 \citep{1986AJ.....91..870W}.
+
+\subsection{Regions in Local Group galaxies}
+
+Using observations observations from \cite{Castro:2018a} (private communication) we study the Tarantula Nebula (30~Dor) in the LMC.
+At a distance of 49.9 kpc \citep{2013Natur.495...76P} is the most luminous star-forming complex in the Local Group \citep{1984ApJ...287..116K}.
+The star forming region NGC 2070 host the massive star cluster R136.
+
+\subsubsection{Giant extragalactic regions}
+
+\paragraph{Observations}\label{sec:obs}
+
+The archival data used in this work for the extragalactic giant regions was obtained with the Fabry Perot TAURUS-II instrument in the 4.2-m William Herschel Telescope (WHT) of del Roque de los Muchachos Observatory (ORM) in La Palma, Spain and was retrieved from the La Palma archive\footnote{\url{http://casu.ast.cam.ac.uk/casuadc/ingarch}}.
+\cite{sabalisck1995supersonic} mentioned the main aspects of the observations (1990 July 31).
+The two-dimensional imaging spectroscopy was captured using an IPCS-II detector and the 125 $\mu$m etalon.
+The cumulative integration time per frame is 36 s with a seeing value of 1''.
+The format of the data cube was of 256*256*100 with a spatial scale of 0.26 pixel$^{-1}$.
+Finally, the reduction and analysis was done with the packages TAUCAL y TAUFITS \citep{1992ASPC...25..445L}.
+The NGC 604 TAURUS-II observations were used by \cite{sabalisck1995supersonic}, \cite{tanco1997} and \cite{2019arXiv191203543M}.
 
@@
 
-%The stellar population has been identified and classified by \cite{1996ApJ...456..174H} (and references therein).
+The stellar population has been identified and classified by \cite{1996ApJ...456..174H} (and references therein).
 Recently, \citet{2011MNRAS.411..235E} focused on studying the Wolf-Rayet (WR) and red super giants (RSGs) stars population.
@@
 This suggest that two episodes of star formation, at least, have taken place in the GEHR.
-\citep{1984A&A...141...49H} identified a gradient from the west to the SE of the nebula of 30 km s$^{1}$.
+\citep{1984A&A...141...49H} identified a gradient from the west to the SE of the nebula of 30 km s$^{-1}$.
 
@@
 
-%It has approximately 250 stars of the OB type, 13 Supergiants and 9 WR \citep{1996AJ....111.1128M}, ten WRs confirmed with spectroscopy \cite{1993AJ....105.1400D}, nine of the WN type and a WC, located near the bright core of the region.
+It has approximately 250 stars of the OB type, 13 Supergiants and 9 WR \citep{1996AJ....111.1128M}, ten WRs confirmed with spectroscopy \cite{1993AJ....105.1400D}, nine of the WN type and a WC, located near the bright core of the region.
 
@@
 
-Our objective is to characterize the turbulent regime in different GEHRs... We compare our results with previous investigations...
+%It also shows some physical quantities of each region, among other parameters used in our analysis.
 
-\subsection{Turbulence}\label{sec:turb}
+\begin{table*}
+\begin{center}\caption{Sumary of properties \citep{1984ApJ...287..116K}.}
+\begin{tabular}{cccccccc}\hline
+HII    &  Dist.  & Diameter & log L(H$_{\alpha}$) & SFR      &  $ \langle N_{e} \rangle_{rms}$    & M(H$^{+}$) & Filling  \\
+Region     &  [kpc] &  [pc]     &  [erg/s]            & [ ]      & [cm$^{-3}$] & [M$_{\odot}$] & Factor \\ \hline
+NGC 604   &   840  & 400     &    39.65     & 0.011    & 3  & 7$\times$10$^{5}$ & 0.1 \\
+NGC 595   &   840  & 400     &    39.36     & 0.009    & 4  &  \\
+Hubble X  &   500  & 160     &    38.6      &  0.004   &  5 & 23 000& 0.02\\
+Hubble V  &   500  & 130     &    38.87     &  0.005   &  8 &    &\\
+30 Dor    &   50   & 98.9    &    39.76     & 0.0130   & 250&    &\\
+Carina    &   2.35 & 15      &    39.6      & 0.01     & 500&    & 0.05 \\
+NGC 346   &   61.7 & 64      &    38.67     & 0.0021   & 100&    &     \\
+Lagoon    &   1.25 & 25      &    37.47     & 0.0001   &  60& 900& 0.012\\
+Orion     &   0.4  & 5       &    37        & 0.000053 & 150& 50 & 0.027\\
 
-The classic turbulence theory \citep{kolm1} assumes a three-dimensional isotropic, incompressible and subsonic flow where an energy cascade is taking place.
-%The energy cascade goes from the largest vortices where the energy in injected until it reaches dissipation with the smallest vortices.
-In the energy cascade three scales are defined based on their Reynolds number.
-The energy injection scale (Re $\rightarrow \infty$), $L_{EI}$, the dissipation scale (Re $\rightarrow$ 1), $L_{D}$ and the inertial scale ($L_{I}$) between the previous two.
-Since the energy distributions depends on the scale, the energy cascade concept is described with an energy spectrum, $E(k) \propto k$ where $k$ is the wave number for a determined scale $l$ ($k \equiv l^{-1}$).
+\end{tabular}\label{tab:Reg}
+\end{center}
+\end{table*}
 
-Is possible to consider that the mean specific energy transfer, $\langle \epsilon \rangle$, in the inertial range can be denoted as $\epsilon \sim \frac{v_{l}^{2}}{\tau_{l}}$; where $v_{l}^{2}$ is the kinetic energy per mass unit and $\tau_{l}$ the time related with velocity fluctuations.
-
-Since the total specific energy of a determined $l$ scale is of the order $\langle v_{l}^{2} \rangle$, the energy integral above the associated $k$, defined as:
-
-\begin{equation}\label{eq:veles}
- \langle v_{l}^{2} \rangle = \int_{k}^{\infty} E(k)dk
-\end{equation}
-
-This energy,of the order of $(\epsilon l)^{\frac{2}{3}} \sim (\frac{\epsilon}{k})^{\frac{2}{3}}$, can be substituted in equation \ref{eq:veles}, obtaining the Kolmogorov law:
-
-\begin{equation}\label{eq:kolm}
-E(k) \propto \epsilon^\frac{2}{3} k^{-\frac{5}{3}}
-\end{equation}
+%\cite{2002MNRAS.329..481B} 39.42 38.95 38.21 38.30  39.46 37.36  37.08
 
@@
 
-\subsection{Observations}\label{sec:obs}
+\subsection{The second order structure function}
 
-The archival data used in this work was obtained with the long-slit ISIS and the Fabry Perot TAURUS-II instruments in the 4.2-m William Herschel Telescope (WHT) of del Roque de los Muchachos Observatory (ORM) in La Palma, Spain and was retrieved from the La Palma archive\footnote{\url{http://casu.ast.cam.ac.uk/casuadc/ingarch}}.
+One of the fundamental properties of turbulent clouds must be spatial fluctuations in velocity and density \citep{1984ApJ...277..556S}.
+They are observed as projected spatial fluctuations in the average line-of-sight velocity and integrated column density.
+By means of describing their statistical properties, these fluctuations can be considered as a product of a stochastic  field.
 
-\citet{2000PASP..112.1138M} and \citep{maiz2004} provides details of the observational setup for the the ISIS instrument (1998 18-19 August).
-In summary, the spectra were obtained  using a position angle of 90$^{\circ}$ and the slit width was 1".
-The slit had a length of 200" and ten  positions  were observe with an exposure time ranging from 900 to 1200 s for every slit.
-The  data we used was reduced again by \citet{jen2013} using the IRAF \citep{1999ascl.soft11002N} astronomical software.
-The ISIS observations were used by \citet{TT2000} and \citet{maiz2004}.
+The statistical tool we use is the second-order structure function, $B(r)$, defined as:
 
-For the TAURUS-II instrument, \cite{sabalisck1995supersonic} mentioned the main aspects of the observations (1990 July 31).
-The two-dimensional imaging spectroscopy was captured using an IPCS-II detector and the 125 $\mu$m etalon.
-The cumulative integration time per frame is 36 s with a seeing value of 1''.
-The format of the data cube was of 256*256*100 with a spatial scale of 0.26 pixel$^{-1}$.
-Finally, the reduction and analysis was done with the packages TAUCAL y TAUFITS \citep{1992ASPC...25..445L}.
-The TAURUS-II observations were used by \cite{sabalisck1995supersonic}, \cite{tanco1997} and \cite{2019arXiv191203543M}.
+\begin{equation}\label{eq:S}
+B(\boldsymbol{r})=\dfrac{\sum[V_{r}(\boldsymbol{x}+\boldsymbol{r})-V_{r}(\boldsymbol{x}) ]^{2}}{N(\boldsymbol{r})}
+\end{equation}
+
+where, $V_{r}(\boldsymbol{x})= V_{obs}(\boldsymbol{x})-\langle V_{obs}(\boldsymbol{x}) \rangle$ and N($\boldsymbol{r}$) is the number of points at each separation, called lag.
+
+As a justification for the use of the structure function, we can consider that any relation between the line width and line-of-sight depth can be interpreted in terms of a correlation between velocity spread and scale size.
+This follows if we have an optically thin spectral line where it will have a width which is related to the total radial velocity dispersion of all fluctuations sampled along the line-of-sight \citep{1984ApJ...277..556S}.
+
+For our fit we use the functional form of the structure function:
+
+\begin{equation}\label{eq:b}
+b(r)=2[1-C(r)]\zeta
+\end{equation}
+
+where $C(r)=1/[1+(r/r_{0})^{m}]$ \citep{1984ApJ...277..556S,arthur2016turbulence}.
+The term $r_{0}$ is the correlation length of the turbulence and $m$ is the index that adjust our results.
+The term $\zeta$ is a correction for small scales considering a seeing, $s_{0}$, an has the form $tanh^{2}[(r/2s_{0})^2]$.
 
@@
 
-Figure \ref{fig:M604} shows the two-dimensional radial velocity map of NGC 604 in H$\alpha$.
-ISIS observations (above) have been limited with the aim to match the zone covered by TAURUS instrument.
-The velocity scale on both instruments reflects the radial velocity in the reference frame of the region taking as a reference point the most luminous pixel.
-This pixels has a value of -253.11 km/s.
-Figure \ref{fig:M595} and \ref{fig:MHub} shows the two-dimensional radial velocity map in H$\alpha$ of NGC 595, Hubble V and Hubble X, respectively.
+The Table \ref{tab:Data} shows the statistical properties of each individual sample.
+The mean, \(\mu\), and the variance, \(\sigma^{2}\), along the number of points of each sample.
+The last column shows previous publications where the data was used.
+In appendix \ref{sec:VelMaps} we show in the Figure \ref{fig:hist} the histograms of the velocity samples of each HII region where we applied equation \ref{eq:S}.
+The Figures \ref{fig:M604}-\ref{fig:MOrion} show the two-dimensional radial velocity map of each region.
 
-\subsection{The second order structure function}
+\begin{table}
+\begin{center}\caption{General statistical properties of the centroid velocities.
+a) \cite{tanco1997} b) \cite{2019arXiv191203543M} c) \cite{Castro:2018a} d) \cite{Damiani:2016a} e) \cite{Damiani:2017b} f) \cite{1987A&A...176..338H} g) \cite{1987A&A...176..347H}.}
+\begin{tabular}{cccccc}\hline
+HII    &  $\mu$   & $\sigma^{2}$        &  No. of  &\(s_0\)& Previously  \\
+   Region       &  [km/s]  &  [km$^{2}$/s$^{2}$] &  points   &[pc]& used in:\\\hline
+NGC 604   &  3.56    &    54.63            &    9 510    &1.73&  a,b     \\
+NGC 595   &  2.82    &    44.13            &    8 765    &1.73&  -     \\
+Hubble V  & -1.23    &    7.87             &    5 832    &1.02&   -    \\
+Hubble X  & -5.95    &    12.9             &    6 925    &1.02&  -     \\
+30Dor     & 265.56*  &    252.79           &    363 059    &0.08&   c    \\
+Carina    & -8.83    &    17.89         &   855    &&   d    \\
+NGC 346   &          &       31.36           &    112 796   &&       \\
+Lagoon    & 3.21 / -6.26 &     8.95 / 7.53    &    566 / 1 176    &&  f / e   \\
+Orion     &     -1.25    &     10.43    &    359    &&    g   \\
+\end{tabular}\label{tab:Data}
+\end{center}
+\end{table}
 
-We use the second order structure function, $S_{2}(l)$, defined as:
+\section{Results}\label{sec:results}
 
-\begin{equation}\label{eq:S}
-S_{2}(\boldsymbol{l})=\dfrac{\sum[V_{r}(\boldsymbol{x}+\boldsymbol{l})-V_{r}(\boldsymbol{x}) ]^{2}}{N(\boldsymbol{l})}
-\end{equation}
+Table \ref{tab:Res} presents the main parameters we obtain from the analysis on the fluctuations of the velocities.
+The first column is the velocity dispersion, \(\sigma\), of each sample of centroid velocities.
+The second column is the correlation length, \(r_0\).
+The third column is the index \(m\) that is used to fit our results.
+This index is used as a reference for comparison between theory and observations.
+In the forth column we show the separation where the value 2\(\sigma\) is reached.
+We also show the ratio \(r_{max}/r_{0}\), where \(r_{max}\) is the maximum separation or lag in pc; this value is related to the size of each sample box.
+With the aim to investigate how statistically homogeneous the regions are, we also show the value of $\sigma_{LOS}$.
+In the appendix \ref{sec:StructFunct} the Figures \ref{fig:SF604}-\ref{fig:SFM42} show the second-order structure functions of the different HII regions for the \halpha\ emission line.
 
-as a statistical tool to investigate the relation between a velocity field and the presence of turbulent motions following the Kolmogorov theory.
-In equation \ref{eq:S}, $V_{r}(\boldsymbol{x})= V_{obs}(\boldsymbol{x})-\langle V_{obs}(\boldsymbol{x}) \rangle$ and N($\boldsymbol{l}$) the number of points at each separation.
+The power-law fit in the structure function for the both regions in the M33 galaxy in is performed above scales of 1.7 pc.
+For NGC 604 the index is 1.7 with a correlation length of 9 pc.
+The structure functions keep going up to scales of 70 pc following a periodic pattern.
+In an idealized case, at scales larger than r$_{0}$ the structure function flattens as it tends towards the asymptotic value of 2$\sigma$ \citep{arthur2016turbulence}.
+Figure \ref{fig:SF604} shows that the structure functions for NGC 604, follow a periodic behavior around 2$\sigma$.
+We can think of a wave starting around 30 pc, with a series of $ >$2$\sigma$ values up to $\sim$100 pc.
+Then $<$2$\sigma$ values follow until the scales of 150 pc.
+Therefore we relate periodic behavior to scales of magnitude $\sim$100 pc across our sample box.
+For NGC 595 the values obtained are 1.55 and 8.8.
+The structure function goes up until 30 pc, reaching values above 2$\sigma$ before falling.
 
-We can consider the quadratic velocities differences proportional to the left term in equation \ref{eq:kolm}:
+For NGC 6822 regions, Hubble X and Hubble V, the $m$ index is 1.5 and 1.4, with a correlation length of 3.5 and 2.7 pc, respectively.
+Both regions reach a maximum of 2$\sigma$ around 20 pc.
+The 30Dor nebula \citep{Castro:2018a} has a correlation length of 2.7 pc and and index of 1.22.
 
-\begin{equation}\label{eq:sfi}
-(\Delta v)^{2} \sim (\epsilon l)^{\frac{2}{3}}
-\end{equation}
+The Carina observations allow us to measure a blue shifted and a red shifted layer \cite{Damiani:2016a}.
+Also, it is possible to combine the moments from the sum of two components \citep{2008RMxAA..44..181G}; for this sample we show our results.
+Carina has an index of 1 with a correlation length of 0.55 pc.
+The structure function shows large-scale oscillatory pattern, with peaks at \(\sim\) 3, 6 and 10 pc.
+The galactic region Lagoon nebula \citep{Damiani:2017b} presents a correlation length of 1.5 pc and a index of 1.15.
+For this region the structure function reach a constant value of 12 km$^{2}$/s$^{2}$ from 2 to 6 pc.
+For scales greater than 6 pc large-scale correlation is found up to 15 pc.
+M42 results shows an index of 0.75 with a correlation length of 0.65.
 
-the term $(\Delta v)^{2}$ can be identified as the structure function.
-The right term with index,  m=2/3, in equation \ref{eq:sfi} is related to the energy (the left term in equation \ref{eq:veles}).
-This index m serves as a reference for comparison between theory and observations.
-
-For our fit we use the normalized structure function of the form $s(l)=2[1-C(l)]$ where $C(l)=1/[1+(l/l_{0})^{m_{2D}}]$.
-The term l$_{0}$ is the correlation length of the turbulence and $m_{2D}$ is the index that adjust our results \citep{1984ApJ...277..556S, arthur2016turbulence}.
-
-\begin{figure}
-\centering 
-\includegraphics[width=2.5in]{Figures/6ISIS.png}
-\includegraphics[width=2.5in]{Figures/M6T}
-\caption{Radial velocity maps of NGC 604 in H$\alpha$. Above: ISIS observations. Below: TAURUS observations. }
-\label{fig:M604}
-\end{figure}
-
-\begin{figure}
-\centering 
-\includegraphics[width=2.5in]{Figures/M5T.png}
-\caption{Radial velocity maps of NGC 595 in H$\alpha$.}
-\label{fig:M595}
-\end{figure}
-
-\begin{figure}
-\centering 
-\includegraphics[width=2.5in]{Figures/MV.png}
-\includegraphics[width=2.5in]{Figures/MX.png}
-\caption{Radial velocity maps of Hubble V and Hubble X in H$\alpha$.}
-\label{fig:MHub}
-\end{figure}
-
-\subsection{Regions in the Milky Way and Large Magellanic Cloud}
-\label{sec:regions-milky-way}
-
-We measure the second-order velocity structure function for a number of more compact and lower luminosity regions:
-the Orion Nebula \citep{arthur2016turbulence}; 
-the Lagoon Nebula \citep{Damiani:2017b};
-the Carina Nebula \citep{Damiani:2016a};
-the Tarantula Nebula (30~Dor) in the LMC \citep{Castro:2018a}.
-
-In order to study the structure function 
-We include
-
-\section{Results}\label{sec:res}
-
-Table \ref{tab:Res} shows the main parameters we obtain.
-These are: the parameters obtained with a power-law fit of the structure function the index, m$_{2D}$, and the correlation length, l$_{0}$ and the ratio L$_{b}$/l$_{0}$, where L$_{b}$ is the horizontal size in pc of our sample box.
-
-Figure \ref{fig:SF604} shows the structure function (Equation \ref{eq:S}) of NGC 604 for the H$\alpha$ emission line for the ISIS and TAURUS instruments.
-The $m_{2D}$ is 1.7 with a correlation length of 11 pc.
-The $\sigma$ for the ISIS instrument is 8.4 km/s and for TAURUS instrument is 7.3 km/s.
-The fit to the power-law of the structure function is performed over the scales of 4 to 11 pc.
-The structure functions keep going up to scales of 70 pc, above these value the structure function falls steeply for the ISIS.
-As \cite{arthur2016turbulence} mentioned, the more pronounced steeping for small scales, below 4 pc in our case, is due to the spatial resolution of the observations.
-In comparison with TAURUS values, ISIS values are higher but are able to maintain the form of the structure function.
-
-Figure \ref{fig:SF595} shows the structure function of NGC 595 for the H$\alpha$ emission line.
-The $m_{2D}$ is 1.7 with a correlation length of 11 pc.
-The $\sigma$ is 6.6 km/s.
-The values of the structure function rise until 30 pc.
-
-Figure \ref{fig:SFV} shows the structure function of Hubble V for the H$\alpha$ emission line.
-The $m_{2D}$ is 1.8 with a correlation length of 4 pc and a $\sigma$ of 2.8 km/s.
-The structure function values keep going up and reach a maximum at $\sim$28 pc.
-
-Figure \ref{fig:SFX} shows the structure function of Hubble V for the H$\alpha$ emission line.
-The $m_{2D}$ is 1.7 with a correlation length of 4 pc.
-The $\sigma$ of the region is 3.6 km/s.
-For this region, the structure functions keeps its tendency of going up to a scale o $\sim$ 18 pc.
+The highest \(\sigma\) is 15.8 km s\(^{-1}\) for 30Dor.
+This is two times higher than NGC 604 that has a value of 7.4 km s\(^{-1}\).
+NGC 346 is next with a value of 5.6 km s\(^{-1}\), followed by Carina with 4.22 km s\(^{-1}\).
+Hubble X and M42 have a value of 3.59 and 3.23 km s\(^{-1}\), respectively.
+With the lowest values is Hubble V with 2.8 km s\(^{-1}\) and Lagoon with 2.7 km s\(^{-1}\).
 
@@
 \begin{center}\caption{Main results.}
-\begin{tabular}{cccccc}\hline
-Region   &  m$_{2D}$  & l$_{0}$ [pc] & $\sigma$ [km/s] & L$_{b}$ [pc]  & L$_{b}$/l$_{0}$ \\\hline
-NGC 604 &     1.7   &     11       &    7.3         & 170  &  15.4 	\\
-NGC 595 &      1.7   &     11      &    6.6        & 200  & 18.1 \\
-Hubble V &   1.8   &     3       &    2.8      & 68  &     22.6  	\\
-Hubble X &     1.7   &     5       &    3.6      & 61  &  12.2 	\\
+\begin{tabular}{cccccccc}\hline
+HII    &  \(\sigma\) &   \(r_0\) &    \(m\)   & r$_{2\sigma}$ &  \(r_{max}\)/\(r_0\) & \(\sigma_{LOS}\)& \(l_T\) \\
+    Region    &  [km/s]  &   [pc]    &       & [pc] &  &[km/s]&    [pc] \\\hline
+NGC 604   &  7.39    &   9.09    &   1.7  & 27  & 14.7 &  7.69&  5.1 \\
+NGC 595   &  6.64    &   8.82    &   1.55 & 20  & 21.4 & 5.74& 4.4 \\
+Hubble V  &  2.80    &   2.78    &   1.4  &  12  & 19.9 & & 1.56 \\ 
+Hubble X  &  3.59    &   3.55    &   1.5  &  15  & 22.1 & & 1.95 \\       
+30 Dor    &  15.8    &   2.7     &   1.22 &  11  & 8.9 &  & 0.69 \\  
+Carina    &  4.22    &   0.55    &    1   &   2   &  16.1  &  2.7&  \\
+NGC 346   &   5.6    &  1.05     &    1.5    &      &  & & \\
+Lagoon    &  2.7     &   1.5     &   1.15 &   6   & 10.1 &&     \\  
+M42       &  3.23    &   0.65    &   0.75 &  -   & 27.6 & 6	& \\
+
 \end{tabular}\label{tab:Res}
@@
 
-\begin{figure}
-\centering 
-\includegraphics[width=3.5in]{Figures/SF604.pdf}
-\caption{NGC 604 second-order structure functions for H$\alpha$ emission line for ISIS and TAURUS instruments.
-The figure also shows the structure functions presented in previous works.
-The green area represents the scales affected by observational seeing.
-The vertical line indicate the value of he correlation length.
-The horizontal line denote the value of $\sigma$.}
-\label{fig:SF604}
-\end{figure}
-
-\begin{figure}
-\centering 
-\includegraphics[width=4in]{Figures/SF595.pdf}
-\caption{NGC 595 second-order structure functions for H$\alpha$ emission line for TAURUS instrument.
-The figure also shows the structure functions presented in previous works.
-Same information as Figure \ref{fig:SF604}.}
-\label{fig:SF595}
-\end{figure}
-
-\begin{figure}
-\centering 
-\includegraphics[width=2.5in]{Figures/SFHV}
-\caption{Hubble V second-order structure functions for H$\alpha$ emission line for TAURUS instrument. Same information as Figure \ref{fig:SF604}.}
-\label{fig:SFV}
-\end{figure}
-
-\begin{figure}
-\centering 
-\includegraphics[width=2.5in]{Figures/SFHX}
-\caption{Hubble X second-order structure functions for H$\alpha$ emission line for TAURUS instrument. Same information as Figure \ref{fig:SF604}.}
-\label{fig:SFX}
-\end{figure}
-
 \subsection{Structure function power indices}
 
-It is possible to compute the m$_{3D}$ index from m$_{2D}$ if we assume that the m$_{3D}$ index lies between the limits of projection smoothing and a sheet-like distribution \citep{arthur2016turbulence}, throgught the relationship  m$_{2D}$ - 1 $<$ m$_{3D}$ $<$ m$_{2D}$.
-We have 0.8 $<$ m$_{3D}$ $<$ 1.7, been m$_{3D}$ above the Kolmogorv prediction.
-This shouldn't be a surprise since physical conditions in GEHRs are different from the homogeneous and incompressible ideal model \citep{munch1958internal, castaneda1988,lagrois2011}.
+The index \(m\) seems biased to \(m>\)1.5 for the extragalactic regions and \(m\sim\)1 for nearby regions.
+This could be attributed to a data quality issue since we are not able to resolve distant regions in the same way we do with nearby objects.
+Since we are not observing all the inertial range on distant regions there is the possibility that \(m\) is not a reliable parameter.
 
-\clearpage
+It is possible to compute the m$_{3D}$ index from m$_{2D}$ ($m$ till now) if we assume that the m$_{3D}$ index lies between the limits of projection smoothing and a sheet-like distribution \citep{arthur2016turbulence}.
+This can be assumed throughout the relationship m$_{2D}$ - 1 $<$ m$_{3D}$ $<$ m$_{2D}$.
+We have 0.65 $<$ m$_{3D}$ $<$ 1.7.
+
+\subsection{Significance on the length scale}
+
+Ideally the correlation length, \(r_0\), should represent the scale of dominant energy injection.
+
+\cite{sabalisck1995supersonic} studied NGC 604 revealing that the kinematics of the region behave different considering different scales.
+High emission knots on the region encompasses supersonic global velocity dispersion values of 14 $<$ \(\sigma_{LOS}\) $<$ 20 km s\(^{-1}\).
+This knots are well fitted with Gaussian profiles thus, defining the kinematic core \cite{munoz1996}.
+A characteristic radius for them is \(\sim\) 7 pc.
+\cite{yang1996} identified 5 expanding shells within NGC 604, and one of them (Shell 3 on their paper) fall into our observations.
+This shells is 40 pc in diameter with an expansion velocity above 50 km s\(^{-1}\).
+This scales are related to the presence of strong stellar winds caused by massive stars.
+For the NGC 604 case, there is no clear relation between the \(r_0\) and some particular energy injection mechanism...
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Discussion}\label{sec:discussion}
+
+\subsection{Comparison with previous structure functions}
+
+Figure \ref{fig:SF604} shows similarity in our results and previous studies from \cite{tanco1997} and \cite{2019arXiv191203543M} for TAURUS-II data.
+\citep{2019arXiv191203543M} report $\sigma$ of 7.2 km/s while we have 7.3 km/s.
+Despite the agreement in observations analysis and interpretations are different.
+As mentioned by \cite{2019arXiv191203543M} some problems and inconsistencies arise in the results of \cite{tanco1997}; they don't consider a lower limit based on the observational seeing and that lead them to conclude about a double regime acting on the velocity spectrum.
+None of the previous studies present a power-law index to compare our results, but  Fig.
+\ref{fig:SF604} shows that the difference lies on the structure function or lag value and no on the form of the plot.
+With this assumption we can establish the same index of 1.7 for NGC 604 TAURUS-II observations.
+
+For our NGC 595 results there is no correspondence in the structure function between our results and previous investigations.
+Our observations cover the brightest part of the region and have smaller resolution.
+\citet{lagrois2009multi} and \citet{lagrois2011} structure functions results does not cover scales $<$10 pc, where in our results the correlation is taking place.
+\citet{lagrois2011} used the data from \citet{lagrois2009multi} to complement the structure function analysis with the auto correlation function and filters to the velocity field to get rid of non-turbulent movements.
+Their sigma is 5.92$\pm$0.15 km/s as a comparison of 6.6 km/s for our data.
+There correlation length is 43 pc.
+The high difference is because the consider that this happen at 2$\sigma$ (equation 13 on their paper).
+The power-law index the provided is 1.55$\pm$0.01.
+
+The first attempt at characterizing turbulence in a giant extragalactic HII region, GEHR, was done by \citet{1961MNRAS.122....1F} with the 30 Dor complex in the LMC, finding no indication of turbulent motions.
+\cite{2019arXiv191203543M} investigated the structure function in 30 Dor finding on their results that the structure function is entirely flat on scales from 3 to 200 pc.
+In the context of the high-resolution observations it is possible to see why their results do not reflect the turbulent structure of the nebula; their observations cover a region where the large-scale velocity fluctuations are uncorrelated.
+There is a good agreement with the results from \cite{2019arXiv191203543M} (Figure 15 Top on their work), while \citet{1961MNRAS.122....1F} results does not overlap ours.
+
+%Figure \ref{fig:SFM8} show the structure functions of M8 previously published by \citep{1987ApJ...317..686O} and the structure function computed in this work from observations of \cite{1987A&A...176..338H}.
+
+\subsection{L vs $\sigma$}
+
+%\begin{figure}
+%\centering 
+%\includegraphics[width=3in]{Figures/lvss.pdf}
+%\caption{}
+%\label{fig:}
+%\end{figure}
+
+%\begin{figure}
+%\centering 
+%\includegraphics[width=3in]{Figures/sfrvssig.pdf}
+%\caption{\citet{2006CRPhy...7..433B}}
+%\label{fig:}
+%\end{figure}
+%%%%%%%%%%%%%%%%
 
@@
 
-\section{Discussion}\label{sec:disc}
+\section{Conclusions}\label{sec:conclusions}
 
-\subsection{Comparison with previous structure functions determinations}
+%\begin{enumerate}
+%    \item The giant HII regions in  M 33, NGC 604 and NGC 595 shows an index of 1.7 and 1.55, respectively.
 
-In an idealized case, at scales larger than r$_{0}$ the structure function flattens as it tends towards the asymptotic value of 2$\sigma$ \citep{arthur2016turbulence}.
-Figure \ref{fig:SF604} shows that the structure functions for NGC 604, except for \cite{2019arXiv191203543M}, follow a periodic behavior around 2$\sigma$.
-Using as reference the TAURUS results, the wave starts at 35 pc with a series of $ >$2$\sigma$ values up to $\sim$100 pc.
-Then $<$2$\sigma$ values follow until the largest scales of 150 pc.
-Therefore this periodic behavior is related to scales of $\sim$100 pc across our sample box.
+%    \item The structure functions are presented for the first time for Hubble X and Hubble V, in NGC 6822.
+Hubble V shows and index of 1.65 and a correlation length of 3 pc, while Hubble X results are 1.6 and 4 pc.
 
-For NGC 595, above 30 pc a random pattern is around 2$\sigma$. Also, we can see this behavior for Hubble V, above 28 pc and Hubble X above 18 pc.
+%    \item The structure function of 30 Dor is presented for the first time using high-resolution observations that allows to observe scales $>$0.1 pc.
+A correlated structure function is obtained with a correlation lenght of 2.7 pc and a power-law index of 1.15.
+This new results show that previous studies on 30 Dor structure functions were analyzing large scales where no velocity fluctuations are present.
 
-Figure \ref{fig:SF604} shows similarity in the TAURUS results and previous works \citep{tanco1997,2019arXiv191203543M}.
-The agreement lies that observations are the same but the procedure of calculating the structure function is different.
-\citep{2019arXiv191203543M} has $\sigma$ of 7.2 while we have 7.3 km/s.
-We note that our structure function results are more similar to \cite{2019arXiv191203543M} but the periodic behavior is strongly reduced on their results.
-\citep{tanco1997} also show this periodic pattern at large scales.
-
-Figure \ref{fig:SF595} shows how there is no correspondence between our results and previous investigations.
-Our observations cover the brightest part of the region and have smaller resolution.
-\citet{lagrois2011} structure function results does not cover scales $<$10 pc.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Conclusions}\label{sec:concl}
-
-\begin{enumerate}
-    \item The giant HII regions in  M 33, NGC 604 and NGC 595 shows the same index and correlation lengths of 1.7 and 11 pc.
-These despite the noted differences on their physical properties and stellar populations.
-For NGC 604 wee find agreement in the structure function results between our data and previous publications.
-For NGC 595 our results are different from previous structure functions.
-
-    \item Structure functions are presented for the first time for Hubble X and Hubble V, in NGC 6822.
-Hubble V shows and index of 1.8 and a correlation length of 4 pc, while Hubble X results are 1.7 and 5 pc.
-
-\end{enumerate}
+%\end{enumerate}
 
@@
 
-The Acknowledgements section is not numbered. Here you can thank helpful
-colleagues, acknowledge funding agencies, telescopes and facilities used etc.
-Try to keep it short.
+We are grateful to Norberto Castro Rodríguez for providing maps of emission line velocity moments for 30 Doradus derived from MUSE-VLT observations.
 
@@
 
+\clearpage
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\appendix
+
+\section{Velocity maps}\label{sec:VelMaps}
+
+\begin{figure*}
+\centering
+\begin{multicols}{4}
+\includegraphics[width=1.5in]{Figures/Hist/604}\par
+\includegraphics[width=1.5in]{Figures/Hist/595.pdf}\par
+\includegraphics[width=1.5in]{Figures/Hist/Hubble V.pdf}\par
+\includegraphics[width=1.5in]{Figures/Hist/Hubble X.pdf}\par
+\end{multicols}
+\begin{multicols}{4}
+\includegraphics[width=1.5in]{Figures/Hist/M8.pdf}\par
+\includegraphics[width=1.5in]{Figures/Hist/Car.pdf}\par
+\includegraphics[width=1.5in]{Figures/Hist/Orion.pdf}\par
+\includegraphics[width=1.5in]{Figures/Hist/30Dor.pdf}\par
+\end{multicols}
+\caption{}
+\label{fig:hist}
+\end{figure*}
+
+\begin{figure}
+\centering 
+\includegraphics[width=2.5in]{Figures/M6T}
+\caption{Radial velocity maps of NGC 604 in H$\alpha$.  }
+\label{fig:M604}
+\end{figure}
+
+\begin{figure}
+\centering 
+\includegraphics[width=2.5in]{Figures/M5T}
+\caption{Radial velocity map of NGC 595 in H$\alpha$.}
+\label{fig:M595}
+\end{figure}
+
+\begin{figure}
+\centering 
+\includegraphics[width=2.5in]{Figures/MV}
+\caption{Radial velocity map of Hubble V in H$\alpha$.}
+\label{fig:MHV}
+\end{figure}
+
+\begin{figure}
+\centering 
+\includegraphics[width=2.5in]{Figures/MX}
+\caption{Radial velocity map of Hubble X in H$\alpha$.}
+\label{fig:MHX}
+\end{figure}
+
+\begin{figure}
+\centering 
+\includegraphics[width=2.5in]{Figures/M30D}
+\caption{Radial velocity map of 30 Dor in H$\alpha$ \citep{Castro:2018a}.}
+\label{fig:M30Dor}
+\end{figure}
+
+\begin{figure}
+\centering 
+\includegraphics[width=2.5in]{Figures/Car}
+\caption{Radial velocity map of Carina in H$\alpha$ taken from \cite{Damiani:2016a}.}
+\label{fig:MCar}
+\end{figure}
+
+\begin{figure}
+\centering 
+\includegraphics[width=3in]{Figures/M8H.png}
+\includegraphics[width=3.5in]{Figures/M8}
+\caption{Radial velocity map of M8 in H$\alpha$. Taken from \citep{Damiani:2017b} and \cite{1987A&A...176..338H}.}
+\label{fig:MM8}
+\end{figure}
+
+\begin{figure}
+\centering 
+\includegraphics[width=3in]{Figures/OrionL}
+\caption{Radial velocity map of Orion in H$\alpha$ taken from \cite{1987A&A...176..347H}.}
+\label{fig:MOrion}
+\end{figure}
+
+\clearpage
+
+\section{Second order structure functions}\label{sec:StructFunct}
+
+Here we present the plots of the second order structure functions...
+
+\begin{figure}
+\centering 
+\includegraphics[width=2in]{Figures/SFplots/604}
+\caption{NGC 604 second-order structure functions for H$\alpha$ emission line from the ISIS and TAURUS instruments (Fig.
+\ref{fig:M604}).
+The figure also shows the structure functions presented in previous works \citep{tanco1997,2019arXiv191203543M}.
+The green area represents the scales affected by observational seeing.
+The vertical line indicate the value of rhe correlation length , r$_{0}$.
+The solid horizontal line denote the value of $\sigma$.
+The double dotted horizontal line indicates 2$\sigma$.
+Black plots are structure functions calculated in this work and gray plots are from previous works.
+}
+\label{fig:SF604}
+\end{figure}
+
+\begin{figure}
+\centering 
+\includegraphics[width=2in]{Figures/SFplots/595}
+\caption{NGC 595 second-order structure functions for H$\alpha$ emission line from the TAURUS instrument (Fig. \ref{fig:M595}). Same information as Figure \ref{fig:SF604}.}
+\label{fig:SF595}
+\end{figure}
+
+\begin{figure}
+\centering 
+\includegraphics[width=2in]{Figures/SFplots/hubbleV}
+\caption{Hubble V second-order structure functions for H$\alpha$ emission line from the TAURUS instrument \ref{fig:MHV}). Same information as Figure \ref{fig:SF604}.}
+\label{fig:SFV}
+\end{figure}
+
+\begin{figure}
+\centering 
+\includegraphics[width=2in]{Figures/SFplots/hubbleX.pdf}
+\caption{Hubble X second-order structure functions for H$\alpha$ emission line from the TAURUS instrument \ref{fig:MHX}). Same information as Figure \ref{fig:SF604}.}
+\label{fig:SFX}
+\end{figure}
+
+\begin{figure}
+\centering 
+\includegraphics[width=2in]{Figures/SFplots/tarantula}
+\caption{30 Dor second-order structure functions for H$\alpha$ emission line \citep{Castro:2018a}.
+The figure also shows the structure functions presented in previous works \citep{2019arXiv191203543M}.
+Same information as Figure \ref{fig:SF604}.}
+\label{fig:SF30Dor}
+\end{figure}
+
+\begin{figure}
+\centering 
+\includegraphics[width=2in]{Figures/SFplots/carina}
+\caption{Carina second-order structure functions for H$\alpha$ emission line taken from. Same information as Figure \ref{fig:SF604}.}
+\label{fig:SFCar}
+\end{figure}
+
+\begin{figure}
+\centering 
+\includegraphics[width=2in]{Figures/SFplots/M8}
+\caption{M8 second-order structure functions for H$\alpha$ emission line \ref{fig:MM8}) from  \cite{Damiani:2017b} and \cite{1987A&A...176..338H}.
+The figure also shows the structure functions presented in previous works \citep{1987ApJ...317..686O}.
+Same information as Figure \ref{fig:SF604}.}
+\label{fig:SFM8}
+\end{figure}
+
+\begin{figure}
+\centering 
+\includegraphics[width=2in]{Figures/SFplots/M42}
+\caption{M42 second-order structure functions for H$\alpha$ emission line taken from \cite{1987A&A...176..347H} \ref{fig:MOrion}).
+he figure also shows the structure functions presented in previous works \citep{von1951methode,munch1958internal,arthur2016turbulence}.
+Same information as Figure \ref{fig:SF604}.}
+\label{fig:SFM42}
+\end{figure}
 

### 2021-06-25 mnras_template.tex
LOS vs POS variations
Fix compilation errors
Add missing editor to one reference. Change all \cite{} -> \citet{}

@@
 More recently, the structure function was used with full 6D measurements (position-velocity) to study the motions of stars in the Orion Molecular Cloud Complex.
-\cite{2021ApJ...907L..40H} argue that newborn stars should reflect the turbulent kinematics of their natal clouds.
-Using this previous method they are free of the projected element that interfere with previous gas-based studies and their results agree with the scaling law proposed by \cite{1981MNRAS.194..809L}.
+\citet{2021ApJ...907L..40H} argue that newborn stars should reflect the turbulent kinematics of their natal clouds.
+Using this previous method they are free of the projected element that interfere with previous gas-based studies and their results agree with the scaling law proposed by \citet{1981MNRAS.194..809L}.
 
@@
 On their spectra double and multiple emission features are signature of these objects.
-\cite{2020MNRAS.494...97S} argue that winds on ionizing clusters in GEHR must merge into a hot cluster because of the close proximity of the massive stars.
-\cite{2019ApJ...871...17U} propose that stellar feedback is an important source of energy to maintain turbulence in nearby galaxies.
+\citet{2020MNRAS.494...97S} argue that winds on ionizing clusters in GEHR must merge into a hot cluster because of the close proximity of the massive stars.
+\citet{2019ApJ...871...17U} propose that stellar feedback is an important source of energy to maintain turbulence in nearby galaxies.
 
 Despite different issues that are related with the nature of the problem of turbulence in HII regions, the vast majority of research using the second-order structure function consider individual regions and hence different methodology.
-\cite{1987ApJ...317..686O} has determined the structure functions for a sample of galactic HII regions but isn't conclusive about them.
+\citet{1987ApJ...317..686O} has determined the structure functions for a sample of galactic HII regions but isn't conclusive about them.
 The individuality of previous works and the need to understand the relationship between the measured turbulent properties for different classes of HII regions has lead us to develop this investigation.
@@
 
-We use data from \cite{1987A&A...176..347H} of the Orion Nebula (M42) located at 440 pc \citep{2008AJ....136.1566O}.
-Its physical and kinematics properties along its stellar population are well documented in the review of \cite{2001ARA&A..39...99O}.
+We use data from \citet{1987A&A...176..347H} of the Orion Nebula (M42) located at 440 pc \citep{2008AJ....136.1566O}.
+Its physical and kinematics properties along its stellar population are well documented in the review of \citet{2001ARA&A..39...99O}.
 The main ionizing star is $\theta^{1}$Ori C (spectral type $\sim$O7) with fast stellar wind, and 3 B-type stars from the Trapezium cluster.
@@
 
-Archival data from \cite{Damiani:2016a} and \cite{Damiani:2017b} are use to study the Carina nebula and Lagoon nebula, respectively.
+Archival data from \citet{Damiani:2016a} and \citet{Damiani:2017b} are use to study the Carina nebula and Lagoon nebula, respectively.
 
@@
 
-Using observations observations from \cite{Castro:2018a} (private communication) we study the Tarantula Nebula (30~Dor) in the LMC.
+Using observations observations from \citet{Castro:2018a} (private communication) we study the Tarantula Nebula (30~Dor) in the LMC.
 At a distance of 49.9 kpc \citep{2013Natur.495...76P} is the most luminous star-forming complex in the Local Group \citep{1984ApJ...287..116K}.
@@
 The archival data used in this work for the extragalactic giant regions was obtained with the Fabry Perot TAURUS-II instrument in the 4.2-m William Herschel Telescope (WHT) of del Roque de los Muchachos Observatory (ORM) in La Palma, Spain and was retrieved from the La Palma archive\footnote{\url{http://casu.ast.cam.ac.uk/casuadc/ingarch}}.
-\cite{sabalisck1995supersonic} mentioned the main aspects of the observations (1990 July 31).
+\citet{sabalisck1995supersonic} mentioned the main aspects of the observations (1990 July 31).
 The two-dimensional imaging spectroscopy was captured using an IPCS-II detector and the 125 $\mu$m etalon.
@@
 Finally, the reduction and analysis was done with the packages TAUCAL y TAUFITS \citep{1992ASPC...25..445L}.
-The NGC 604 TAURUS-II observations were used by \cite{sabalisck1995supersonic}, \cite{tanco1997} and \cite{2019arXiv191203543M}.
+The NGC 604 TAURUS-II observations were used by \citet{sabalisck1995supersonic}, \citet{tanco1997} and \citet{2019arXiv191203543M}.
 
@@
 It has a luminosity in L$_{H_\alpha}$ = 10$^{39.42}$ erg s$^{-1}$ \citep{2002MNRAS.329..481B} and in L$_{X}$=9.3$\times$ 10$^{35}$ erg s$^{-1}$ \citep{2008ApJ...685..919T}.
-\cite{2012ApJ...761....3M} derive an average age of 4$\pm$1 Myr and a total stellar mass of 1.6$^{+1.6}_{-1.0} \times$ 10$^{5}$M$_{\odot}$ for the region.
+\citet{2012ApJ...761....3M} derive an average age of 4$\pm$1 Myr and a total stellar mass of 1.6$^{+1.6}_{-1.0} \times$ 10$^{5}$M$_{\odot}$ for the region.
 
-The stellar population has been identified and classified by \cite{1996ApJ...456..174H} (and references therein).
+The stellar population has been identified and classified by \citet{1996ApJ...456..174H} (and references therein).
 Recently, \citet{2011MNRAS.411..235E} focused on studying the Wolf-Rayet (WR) and red super giants (RSGs) stars population.
@@
 The electronic temperature is 7,670 $\pm$116 K \citep{2010MNRAS.402.1635R}.
-\cite{1983A&A...119..185V} made an estimate of the total masses of HI and HII in the nebula to obtain values of M$_{HI}=$ 1.2 $\times$ 10 $^{6}$ M$_{\odot}$ and M$_{HII} =$ 4.6 $\times$ 10 $^{5}$ M$_{\odot}$, and a ionizing luminosity of the star cluster is estimated at 5 $\times$ 10$^{50}$ erg s $^{1}$.
-\cite{1996AJ....111.1128M} estimate an age of 4.5 Myrs consistent with \cite{1993AJ....105.1400D}.
+\citet{1983A&A...119..185V} made an estimate of the total masses of HI and HII in the nebula to obtain values of M$_{HI}=$ 1.2 $\times$ 10 $^{6}$ M$_{\odot}$ and M$_{HII} =$ 4.6 $\times$ 10 $^{5}$ M$_{\odot}$, and a ionizing luminosity of the star cluster is estimated at 5 $\times$ 10$^{50}$ erg s $^{1}$.
+\citet{1996AJ....111.1128M} estimate an age of 4.5 Myrs consistent with \citet{1993AJ....105.1400D}.
 
-It has approximately 250 stars of the OB type, 13 Supergiants and 9 WR \citep{1996AJ....111.1128M}, ten WRs confirmed with spectroscopy \cite{1993AJ....105.1400D}, nine of the WN type and a WC, located near the bright core of the region.
+It has approximately 250 stars of the OB type, 13 Supergiants and 9 WR \citep{1996AJ....111.1128M}, ten WRs confirmed with spectroscopy \citet{1993AJ....105.1400D}, nine of the WN type and a WC, located near the bright core of the region.
 
@@
 
-%\cite{2002MNRAS.329..481B} 39.42 38.95 38.21 38.30  39.46 37.36  37.08
+%\citet{2002MNRAS.329..481B} 39.42 38.95 38.21 38.30  39.46 37.36  37.08
 
@@
 \begin{table}
-\begin{center}\caption{General statistical properties of the centroid velocities.
-a) \cite{tanco1997} b) \cite{2019arXiv191203543M} c) \cite{Castro:2018a} d) \cite{Damiani:2016a} e) \cite{Damiani:2017b} f) \cite{1987A&A...176..338H} g) \cite{1987A&A...176..347H}.}
+  \begin{center}
+    \caption{General statistical properties of the centroid velocities.
+      a) \citet{tanco1997}
+      b) \citet{2019arXiv191203543M}
+      c) \citet{Castro:2018a}
+      d) \citet{Damiani:2016a}
+      e) \citet{Damiani:2017b}
+      f) \citet{1987A&A...176..338H}
+      g) \citet{1987A&A...176..347H}.
+    } 
 \begin{tabular}{cccccc}\hline
@@
 
-The Carina observations allow us to measure a blue shifted and a red shifted layer \cite{Damiani:2016a}.
+The Carina observations allow us to measure a blue shifted and a red shifted layer \citet{Damiani:2016a}.
 Also, it is possible to combine the moments from the sum of two components \citep{2008RMxAA..44..181G}; for this sample we show our results.
@@
 
-\cite{sabalisck1995supersonic} studied NGC 604 revealing that the kinematics of the region behave different considering different scales.
+\citet{sabalisck1995supersonic} studied NGC 604 revealing that the kinematics of the region behave different considering different scales.
 High emission knots on the region encompasses supersonic global velocity dispersion values of 14 $<$ \(\sigma_{LOS}\) $<$ 20 km s\(^{-1}\).
-This knots are well fitted with Gaussian profiles thus, defining the kinematic core \cite{munoz1996}.
+This knots are well fitted with Gaussian profiles thus, defining the kinematic core \citet{munoz1996}.
 A characteristic radius for them is \(\sim\) 7 pc.
-\cite{yang1996} identified 5 expanding shells within NGC 604, and one of them (Shell 3 on their paper) fall into our observations.
+\citet{yang1996} identified 5 expanding shells within NGC 604, and one of them (Shell 3 on their paper) fall into our observations.
 This shells is 40 pc in diameter with an expansion velocity above 50 km s\(^{-1}\).
@@
 
-Figure \ref{fig:SF604} shows similarity in our results and previous studies from \cite{tanco1997} and \cite{2019arXiv191203543M} for TAURUS-II data.
+Figure \ref{fig:SF604} shows similarity in our results and previous studies from \citet{tanco1997} and \citet{2019arXiv191203543M} for TAURUS-II data.
 \citep{2019arXiv191203543M} report $\sigma$ of 7.2 km/s while we have 7.3 km/s.
 Despite the agreement in observations analysis and interpretations are different.
-As mentioned by \cite{2019arXiv191203543M} some problems and inconsistencies arise in the results of \cite{tanco1997}; they don't consider a lower limit based on the observational seeing and that lead them to conclude about a double regime acting on the velocity spectrum.
+As mentioned by \citet{2019arXiv191203543M} some problems and inconsistencies arise in the results of \citet{tanco1997}; they don't consider a lower limit based on the observational seeing and that lead them to conclude about a double regime acting on the velocity spectrum.
 None of the previous studies present a power-law index to compare our results, but  Fig.
@@
 The first attempt at characterizing turbulence in a giant extragalactic HII region, GEHR, was done by \citet{1961MNRAS.122....1F} with the 30 Dor complex in the LMC, finding no indication of turbulent motions.
-\cite{2019arXiv191203543M} investigated the structure function in 30 Dor finding on their results that the structure function is entirely flat on scales from 3 to 200 pc.
+\citet{2019arXiv191203543M} investigated the structure function in 30 Dor finding on their results that the structure function is entirely flat on scales from 3 to 200 pc.
 In the context of the high-resolution observations it is possible to see why their results do not reflect the turbulent structure of the nebula; their observations cover a region where the large-scale velocity fluctuations are uncorrelated.
-There is a good agreement with the results from \cite{2019arXiv191203543M} (Figure 15 Top on their work), while \citet{1961MNRAS.122....1F} results does not overlap ours.
+There is a good agreement with the results from \citet{2019arXiv191203543M} (Figure 15 Top on their work), while \citet{1961MNRAS.122....1F} results does not overlap ours.
 
-%Figure \ref{fig:SFM8} show the structure functions of M8 previously published by \citep{1987ApJ...317..686O} and the structure function computed in this work from observations of \cite{1987A&A...176..338H}.
+%Figure \ref{fig:SFM8} show the structure functions of M8 previously published by \citep{1987ApJ...317..686O} and the structure function computed in this work from observations of \citet{1987A&A...176..338H}.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+Relationship between plane-of-sky and line-of-sight velocity dispersion.  Comparison with \citet{Rozas:2006b}.
 
@@
 \includegraphics[width=2.5in]{Figures/Car}
-\caption{Radial velocity map of Carina in H$\alpha$ taken from \cite{Damiani:2016a}.}
+\caption{Radial velocity map of Carina in H$\alpha$ taken from \citet{Damiani:2016a}.}
 \label{fig:MCar}
@@
 \includegraphics[width=3.5in]{Figures/M8}
-\caption{Radial velocity map of M8 in H$\alpha$. Taken from \citep{Damiani:2017b} and \cite{1987A&A...176..338H}.}
+\caption{Radial velocity map of M8 in H$\alpha$. Taken from \citep{Damiani:2017b} and \citet{1987A&A...176..338H}.}
 \label{fig:MM8}
@@
 \includegraphics[width=3in]{Figures/OrionL}
-\caption{Radial velocity map of Orion in H$\alpha$ taken from \cite{1987A&A...176..347H}.}
+\caption{Radial velocity map of Orion in H$\alpha$ taken from \citet{1987A&A...176..347H}.}
 \label{fig:MOrion}
@@
 \includegraphics[width=2in]{Figures/SFplots/M8}
-\caption{M8 second-order structure functions for H$\alpha$ emission line \ref{fig:MM8}) from  \cite{Damiani:2017b} and \cite{1987A&A...176..338H}.
+\caption{M8 second-order structure functions for H$\alpha$ emission line \ref{fig:MM8}) from  \citet{Damiani:2017b} and \citet{1987A&A...176..338H}.
 The figure also shows the structure functions presented in previous works \citep{1987ApJ...317..686O}.
@@
 \includegraphics[width=2in]{Figures/SFplots/M42}
-\caption{M42 second-order structure functions for H$\alpha$ emission line taken from \cite{1987A&A...176..347H} \ref{fig:MOrion}).
+\caption{M42 second-order structure functions for H$\alpha$ emission line taken from \citet{1987A&A...176..347H} \ref{fig:MOrion}).
 he figure also shows the structure functions presented in previous works \citep{von1951methode,munch1958internal,arthur2016turbulence}.

### 2021-06-25 mnras_template.tex
Fix package incompatibility in older latex versions
This caused an error on the overleaf site but was not a problem for me
locally

See https://tex.stackexchange.com/questions/564490/command-bbbk-already-defined-ol-bbbk-mathordamsb7c-when-i-try-t
Really fix the amssymb compatibility this time I hope
I made a mistake in the previous fix
Add hard line breaks throughout.
This is just to make diffs work better

@@
 \usepackage{graphicx}	% Including figure files
+\let\Bbbk\relax
 \usepackage{amsmath}	% Advanced maths commands
@@
 As mentioned by \citet{2019arXiv191203543M} some problems and inconsistencies arise in the results of \citet{tanco1997}; they don't consider a lower limit based on the observational seeing and that lead them to conclude about a double regime acting on the velocity spectrum.
-None of the previous studies present a power-law index to compare our results, but  Fig.
-\ref{fig:SF604} shows that the difference lies on the structure function or lag value and no on the form of the plot.
+None of the previous studies present a power-law index to compare our results, but Fig.~\ref{fig:SF604} shows that the difference lies on the structure function or lag value and no on the form of the plot.
 With this assumption we can establish the same index of 1.7 for NGC 604 TAURUS-II observations.
@@
 
-Relationship between plane-of-sky and line-of-sight velocity dispersion.  Comparison with \citet{Rozas:2006b}.
+Relationship between plane-of-sky and line-of-sight velocity dispersion.
+ Comparison with \citet{Rozas:2006b}.
 
@@
 \includegraphics[width=2in]{Figures/SFplots/604}
-\caption{NGC 604 second-order structure functions for H$\alpha$ emission line from the ISIS and TAURUS instruments (Fig.
-\ref{fig:M604}).
+\caption{NGC 604 second-order structure functions for H$\alpha$ emission line from the ISIS and TAURUS instruments (Fig. \ref{fig:M604}).
 The figure also shows the structure functions presented in previous works \citep{tanco1997,2019arXiv191203543M}.
@@
 \includegraphics[width=2in]{Figures/SFplots/595}
-\caption{NGC 595 second-order structure functions for H$\alpha$ emission line from the TAURUS instrument (Fig. \ref{fig:M595}). Same information as Figure \ref{fig:SF604}.}
+\caption{NGC 595 second-order structure functions for H$\alpha$ emission line from the TAURUS instrument (Fig. \ref{fig:M595}).
+Same information as Figure \ref{fig:SF604}.}
 \label{fig:SF595}
@@
 \includegraphics[width=2in]{Figures/SFplots/hubbleV}
-\caption{Hubble V second-order structure functions for H$\alpha$ emission line from the TAURUS instrument \ref{fig:MHV}). Same information as Figure \ref{fig:SF604}.}
+\caption{Hubble V second-order structure functions for H$\alpha$ emission line from the TAURUS instrument \ref{fig:MHV}).
+Same information as Figure \ref{fig:SF604}.}
 \label{fig:SFV}
@@
 \includegraphics[width=2in]{Figures/SFplots/hubbleX.pdf}
-\caption{Hubble X second-order structure functions for H$\alpha$ emission line from the TAURUS instrument \ref{fig:MHX}). Same information as Figure \ref{fig:SF604}.}
+\caption{Hubble X second-order structure functions for H$\alpha$ emission line from the TAURUS instrument \ref{fig:MHX}).
+Same information as Figure \ref{fig:SF604}.}
 \label{fig:SFX}
@@
 \includegraphics[width=2in]{Figures/SFplots/carina}
-\caption{Carina second-order structure functions for H$\alpha$ emission line taken from. Same information as Figure \ref{fig:SF604}.}
+\caption{Carina second-order structure functions for H$\alpha$ emission line taken from.
+Same information as Figure \ref{fig:SF604}.}
 \label{fig:SFCar}

### 2021-07-30 mnras_template.tex
Javier vacation changes up to 2021 July 30

--- 2021-06-25 mnras_template.tex
@@
   Fluctuations of centroid velocities on the plane of the sky are a powerful tool for studying the turbulent dynamics of emission line regions.
-  We apply the technique to archival observations of a diverse sample of 8 \hii{} regions
+  We apply the technique to archival \halpha\ observations of a diverse sample of 8 \hii{} regions
   in the Milky Way and other Local Group galaxies,
@@
 
-The large lengths of astrophysical objects, ranging in scales from 10$^{6}$ to 10$^{17}$ m \citep{2010ApJ...710..853C}, and the high Reynolds numbers (Re), in the order of 10$^{4}$ - 10$^{9}$, are the main properties that builds the idea of a turbulent interstellar medium.
-Previous studies \citep{1999intu.conf.....F,2004ARA&A..42..211E,scalo2004interstellar} revealed that different phases of the interstellar medium show fluctuations on their velocity field, evidence of random motions.
+It is known that the speed of sound in a HII region is of the order of \(c_{HII} \sim\) 13 km s\kms.
+\citet{smith1970} discovered that the probable velocities of internal motions of extragalactic HII regions, \(\sigma_{W}\) (line width integrated over the whole HII region), were in the range of $\sim$ 19-34 km s\kms\ covering supersonic values.
+\citet{skillman1984kinematics} found broad profiles in giant extragalactic HII regions (GEHRs) that have a FWHM\(>\)30km s\kms. 
+This property is mainly used to distinguish between 'normal' and 'giant' HII regions. Other differences are their size, luminosity and their stellar population. 
+For the velocity to be supersonic it is necessary a continuous mechanism to maintain the observed motions, as supersonic motions are expected to dissipate energy via shocks \citep{1994Ap&SS.216..285C}.
+Also, this non-thermal broadening on the spectral emission lines has been suggested as evidence of disorder motions along the line-of-sight (LOS) of the ionized gas. 
+Turbulence is suggested as a mechanism that can stir the medium and maintain the supersonic velocities.
+
+The large lengths of astrophysical objects, ranging in scales from 10$^{6}$ to 10$^{17}$ m \citep{2010ApJ...710..853C}, and the high Reynolds numbers (Re), in the order of 10$^{4}$ - 10$^{9}$, are the main properties that supports the idea of a turbulent interstellar medium.
+Previous studies \citep{1999intu.conf.....F,2004ARA&A..42..211E,scalo2004interstellar} revealed that different phases of the interstellar medium show fluctuations on their velocity field that can be interpreted as evidence of random motions.
 The usual picture considers that interstellar turbulence is driven on different scales by various energetic processes.
-Also, It is thought that the formation of structures like filaments and shells in the diffuse medium is determined by large-scale turbulence.
-Stars are the mainly mechanism proposed to account for the large input of kinetic energy through UV radiation, but the dominant energetic sources an their relation to turbulence still is unclear.
+Also, it is thought that the formation of structures like filaments and shells in the diffuse medium is determined by large-scale turbulence.
+Stars are the mainly mechanism proposed to account for the large input of kinetic energy through UV radiation, but the dominant energetic sources and their relation to turbulence still is unclear.
+
+\citet{melnick1977,terlevich1981} were the first to shown an empirical relationship between the line width and the integrated properties of the HII regions as the diameter or the luminosity ($r \sim \sigma ^{\sim 2}$ ; $L_{H} \sim \sigma ^{\sim 4}$).
+They conclude that GEHRs follow this relations as self-gravity systems like globular clusters or elliptical galaxies.
+The work of \citet{1988A&A...201..199A} confirmed these relationships considering the discrepancies of previous investigations obtaining \(L_{H_{\alpha}} \propto \sigma^{3.9}\) and \(r \propto \sigma^{1.84}\).
+\citet{2012MNRAS.422.3339W} have found that clumps and HII regions follow scaling relations over the range of z = 0-2 for \halpha\ size, velocity dispersion, luminosity and mass finding \(\sigma \propto r^{0.42}\), \(L_{H_{\alpha}} \propto r^{2.72}\) and \(L_{H_{\alpha}} \propto \sigma^{4.18}\).
+This results imply that the same process are seen at high redshifts and the current epoch in star forming regions.
+\citet{2015MNRAS.449.3568M} found that the relation is also found in dwarf galaxies with a \(L_{H_{\alpha}} \propto \sigma^{5}\).
+
+The idea of a virial system has been developed by \citet{1993ApJ...418..767T,munoz1996} into the \textit{Cometary Stirring Model} (CSM) with the aim to separate the mechanism that contribute to the line broadening.
+The stellar winds also tend to be used for an explanation of the line broadening and turbulence in GEHRs \citep{1994ApJ...425..720C}.
+This features seems to drive visually the regions with filaments, arcs and shells.
+On their spectra double and multiple emission features are signature of these objects.
+\citet{2020MNRAS.494...97S} argue that winds on ionizing clusters in GEHR must merge into a hot cluster because of the close proximity of the massive stars.
+\citet{2019ApJ...871...17U} propose that stellar feedback is an important source of energy to maintain turbulence in nearby galaxies.
 
@@
 The fluctuations associated with the centroid velocities on the plane-of-sky (POS) of photoionized regions have been characterized several times using the second order structure function (the Fourier transform of the energy spectrum, $E(k)$).
-This studies span from galactic HII regions like Orion \citep{von1951methode,munch1958internal,castaneda1988,1992ApJ...387..229O,arthur2016turbulence} to giant HII regions \citep{1961MNRAS.122....1F,lagrois2009multi,lagrois2011}, like NGC 604 in the M 33 galaxy \citep{tanco1997,2019arXiv191203543M}.
+This studies span from galactic HII regions \citep{1986ApJ...300..624R} like Orion \citep{von1951methode,munch1958internal,castaneda1988,1992ApJ...387..229O,arthur2016turbulence} to giant HII regions \citep{1961MNRAS.122....1F,lagrois2009multi,lagrois2011}, like NGC 604 in the M 33 galaxy \citep{tanco1997,2019arXiv191203543M}.
 
@@
 
-The non-thermal broadening on the spectral emission lines also has been suggested as evidence of disorder motions along the line-of-sight (LOS).
-\citet{smith1970} discovered that the line width of GEHRs was supersonic in the order of $\sigma \sim$ 17-26 km s\kms.
-\citet{melnick1977,terlevich1981} have shown an empirical relationship between the line width and the integrated properties of the HII regions as the diameter or the luminosity ($R \sim \sigma ^{\sim 2}$ ; $L \sim \sigma ^{\sim 4}$).
-They conclude that GEHRs follow this relations as self-gravity systems like globular clusters or elliptical galaxies.
-The idea of a virial system has been developed by \citet{1993ApJ...418..767T,munoz1996} into the \textit{Cometary Stirring Model} (CSM) with the aim to separate the mechanism that contribute to the line broadening.
-The stellar winds also tend to be used for an explanation of the line broadening and turbulence in GEHRs \citep{1994ApJ...425..720C}.
-This features seems to drive visually the regions with filaments, arcs and shells.
-On their spectra double and multiple emission features are signature of these objects.
-\citet{2020MNRAS.494...97S} argue that winds on ionizing clusters in GEHR must merge into a hot cluster because of the close proximity of the massive stars.
-\citet{2019ApJ...871...17U} propose that stellar feedback is an important source of energy to maintain turbulence in nearby galaxies.
-
 Despite different issues that are related with the nature of the problem of turbulence in HII regions, the vast majority of research using the second-order structure function consider individual regions and hence different methodology.
@@
 We apply an uniform methodology of a functional form of the structure function to characterize the turbulent using the  autocorrelation length, \(r_0\), and power-law slope, \(m\).
-Our results are compared with physical properties of each region, which reveal correlations between them, and are also compared with previous investigations.
-With this work we aim to fill a gap in statistical analysis of turbulence between galactic and giant HII regions.
+Our results are compared with physical properties of each region and are also compared with previous investigations.
+With this work we aim to fill a gap with an uniform statistical analysis of turbulence between galactic and giant HII regions.
+
+The paper follows the next order...
+Section 2...
 
 \section{HII regions sample}
+
+We used previous published observational data to measure the second-order velocity structure function for a number of compact and lower luminosity regions.
+Table \ref{tab:Reg} shows the HII regions names
+with physical properties of each region.
 
@@
 
-We used previous published observational data to measure the second-order velocity structure function for a number of compact and lower luminosity regions.
-
 We use data from \citet{1987A&A...176..347H} of the Orion Nebula (M42) located at 440 pc \citep{2008AJ....136.1566O}.
 Its physical and kinematics properties along its stellar population are well documented in the review of \citet{2001ARA&A..39...99O}.
-The main ionizing star is $\theta^{1}$Ori C (spectral type $\sim$O7) with fast stellar wind, and 3 B-type stars from the Trapezium cluster.
+The main ionizing star is \(\theta^{1}\)Ori C (spectral type \(\sim\)O7) with fast stellar wind, and 3 B-type stars from the Trapezium cluster.
 The position of Orion near the side of the Orion Molecular Cloud (OMC-1) make it an ongoing star formation region and a example of a blister HII region \citep{arthur2016turbulence}.
 
-Archival data from \citet{Damiani:2016a} and \citet{Damiani:2017b} are use to study the Carina nebula and Lagoon nebula, respectively.
+A 106 cm-Cassegrain telescope at Observatorium Hoher List was used with a Fabry-Pérot interferometer having the étalon a separation of 0.5 mm. 
+Interferograms have been taken with different pointing directions of the telescope's optical axis in the nebula. 
+The exposures are overlapped and fall into one square of a grid with a width of 1' sentered at \(\theta^{1}\)Ori C \citep{1987A&A...176..347H}.
 
@@
 
-\subsection{Regions in Local Group galaxies}
+Archival data from \citet{Damiani:2016a} and \citet{Damiani:2017b} are use to study the Carina nebula and Lagoon nebula, respectively. 
+The ESO VLT/FLAMES multi-fiber spectograph was used for observations (Gaia-ESO Survey internal release \(iDR4\)) of Lagoon nebula  and Carina nebula \citep{2002Msngr.110....1P}. 
+Mainly the spectra were obtained with the Giraffe HR15N setup (\(R \sim19 000\), wavelength range 6444-6818 A) which allow to observe \halpha\ emission line. 
+The Survey targets are low-mass stars ranging down to magnitude V \(\sim\) 18.5.
 
@@
 
-\subsubsection{Giant extragalactic regions}
+NGC 2070 was observed as part of the MUSE SV (Science Verification) programme at the Very LArge Telescope (VLT). 
+Four overlapping fields, each with an individual field of 1' \(\times\) 1' and a pixel scale of 0.2''/pixel were observed. 
+The data were reduced using the MUSE pipeline based on ESOREX recipes, with final astrometric calibration using the catalogue of \citet{1999A&A...341...98S}. 
+The final spectra span 495-9366 A, with a resolving power of \(R \sim3 000\) around \halpha\  \citep{Castro:2018a}.
 
-\paragraph{Observations}\label{sec:obs}
+\begin{table*}
+\begin{center}\caption{Sumary of properties \citep{1984ApJ...287..116K} \citep{1986ApJ...300..624R}}
+\begin{tabular}{ccccccccc}\hline
+HII    &  Dist.  & Diameter & log L(H$_{\alpha}$) & SFR      &  $ \langle N_{e} \rangle_{rms}$    & M(H$^{+}$) & Filling & \(\sigma_{W}\) \\
+Region     &  [kpc] &  [pc]     &  [erg/s]            & [ ]      & [cm$^{-3}$] & [M$_{\odot}$] & Factor & [km/s] \\ \hline
+NGC 604   &   840  & 400     &    39.65     & 0.011    & 3  & 7 $\times$ 10$^{5}$ & 0.1 & 23.1 \\
+NGC 595   &   840  & 400     &    39.36     & 0.009    & 4  & 4.6 $\times$ 10$^{5}$ & & 27.1 \\
+Hubble X  &   500  & 160     &    38.6      &  0.004   &  5 & 23 000& 0.02 & 13.4 \\
+Hubble V  &   500  & 130     &    38.87     &  0.005   &  8 &    & & 14.7 \\
+30 Dor    &   50   & 98.9    &    39.76     & 0.0130   & 250&    & & 31.7 \\
+Carina    &   2.35 & 15      &    39.6      & 0.01     & 500&    & 0.05 & \\
+NGC 346   &   61.7 & 64      &    38.67     & 0.0021   & 100&    &     & \\
+Lagoon    &   1.25 & 25      &    37.47     & 0.0001   &  60& 900& 0.012 & \\
+Orion     &   0.4  & 5       &    37        & 0.000053 & 150& 50 & 0.027 & \\
+\end{tabular}\label{tab:Reg}
+\end{center}
+\end{table*}
 
-The archival data used in this work for the extragalactic giant regions was obtained with the Fabry Perot TAURUS-II instrument in the 4.2-m William Herschel Telescope (WHT) of del Roque de los Muchachos Observatory (ORM) in La Palma, Spain and was retrieved from the La Palma archive\footnote{\url{http://casu.ast.cam.ac.uk/casuadc/ingarch}}.
-\citet{sabalisck1995supersonic} mentioned the main aspects of the observations (1990 July 31).
-The two-dimensional imaging spectroscopy was captured using an IPCS-II detector and the 125 $\mu$m etalon.
-The cumulative integration time per frame is 36 s with a seeing value of 1''.
-The format of the data cube was of 256*256*100 with a spatial scale of 0.26 pixel$^{-1}$.
-Finally, the reduction and analysis was done with the packages TAUCAL y TAUFITS \citep{1992ASPC...25..445L}.
-The NGC 604 TAURUS-II observations were used by \citet{sabalisck1995supersonic}, \citet{tanco1997} and \citet{2019arXiv191203543M}.
+\subsection{Regions in M33 galaxy and NGC 6822}
 
@@
 
-NGC 595 is the second brightest giant HII region in the M33 galaxy with a length of 300 pc.
+NGC 595 is the second brightest giant HII region in the M33 galaxy.
 The electronic temperature is 7,670 $\pm$116 K \citep{2010MNRAS.402.1635R}.
@@
 
-%It also shows some physical quantities of each region, among other parameters used in our analysis.
-
-\begin{table*}
-\begin{center}\caption{Sumary of properties \citep{1984ApJ...287..116K}.}
-\begin{tabular}{cccccccc}\hline
-HII    &  Dist.  & Diameter & log L(H$_{\alpha}$) & SFR      &  $ \langle N_{e} \rangle_{rms}$    & M(H$^{+}$) & Filling  \\
-Region     &  [kpc] &  [pc]     &  [erg/s]            & [ ]      & [cm$^{-3}$] & [M$_{\odot}$] & Factor \\ \hline
-NGC 604   &   840  & 400     &    39.65     & 0.011    & 3  & 7$\times$10$^{5}$ & 0.1 \\
-NGC 595   &   840  & 400     &    39.36     & 0.009    & 4  &  \\
-Hubble X  &   500  & 160     &    38.6      &  0.004   &  5 & 23 000& 0.02\\
-Hubble V  &   500  & 130     &    38.87     &  0.005   &  8 &    &\\
-30 Dor    &   50   & 98.9    &    39.76     & 0.0130   & 250&    &\\
-Carina    &   2.35 & 15      &    39.6      & 0.01     & 500&    & 0.05 \\
-NGC 346   &   61.7 & 64      &    38.67     & 0.0021   & 100&    &     \\
-Lagoon    &   1.25 & 25      &    37.47     & 0.0001   &  60& 900& 0.012\\
-Orion     &   0.4  & 5       &    37        & 0.000053 & 150& 50 & 0.027\\
-
-\end{tabular}\label{tab:Reg}
-\end{center}
-\end{table*}
+The archival data used in this work for the extragalactic giant regions was obtained with the Fabry Perot TAURUS-II instrument in the 4.2-m William Herschel Telescope (WHT) of del Roque de los Muchachos Observatory (ORM) in La Palma, Spain and was retrieved from the La Palma archive\footnote{\url{http://casu.ast.cam.ac.uk/casuadc/ingarch}}.
+\citet{sabalisck1995supersonic} mentioned the main aspects of the observations (1990 July 31).
+The two-dimensional imaging spectroscopy was captured using an IPCS-II detector and the 125 $\mu$m etalon.
+The cumulative integration time per frame is 36 s with a seeing value of 1''.
+The format of the data cube was of 256*256*100 with a spatial scale of 0.26 pixel$^{-1}$.
+Finally, the reduction and analysis was done with the packages TAUCAL y TAUFITS \citep{1992ASPC...25..445L}.
+The NGC 604 TAURUS-II observations were used by \citet{sabalisck1995supersonic}, \citet{tanco1997} and \citet{2019arXiv191203543M}.
 
@@
 They are observed as projected spatial fluctuations in the average line-of-sight velocity and integrated column density.
-By means of describing their statistical properties, these fluctuations can be considered as a product of a stochastic  field.
+By means of describing the statistical properties of these fluctuations they can be assumed as a product of a stochastic field statistical tools.
 
-The statistical tool we use is the second-order structure function, $B(r)$, defined as:
+The statistical function we use to study the velocity field of the HII regions is the second-order structure function, $B(r)$, defined as:
 
@@
 
-where, $V_{r}(\boldsymbol{x})= V_{obs}(\boldsymbol{x})-\langle V_{obs}(\boldsymbol{x}) \rangle$ and N($\boldsymbol{r}$) is the number of points at each separation, called lag.
+where, $V_{r}(\boldsymbol{x})= V_{obs}(\boldsymbol{x})-\langle V_{obs}(\boldsymbol{x}) \rangle$ and N($\boldsymbol{r}$) is the number of points at each separation \(r\), called lag.
 
-As a justification for the use of the structure function, we can consider that any relation between the line width and line-of-sight depth can be interpreted in terms of a correlation between velocity spread and scale size.
+As a justification for the use of the structure function we can consider that any relation between the line width and line-of-sight depth can be interpreted in terms of a correlation between velocity spread and scale size.
 This follows if we have an optically thin spectral line where it will have a width which is related to the total radial velocity dispersion of all fluctuations sampled along the line-of-sight \citep{1984ApJ...277..556S}.
 
-For our fit we use the functional form of the structure function:
+We also use the functional form of the structure function:
 
 \begin{equation}\label{eq:b}
-b(r)=2[1-C(r)]\zeta
+b(r)=2[1-C(r)]\zeta+\eta
 \end{equation}
@@
 where $C(r)=1/[1+(r/r_{0})^{m}]$ \citep{1984ApJ...277..556S,arthur2016turbulence}.
-The term $r_{0}$ is the correlation length of the turbulence and $m$ is the index that adjust our results.
-The term $\zeta$ is a correction for small scales considering a seeing, $s_{0}$, an has the form $tanh^{2}[(r/2s_{0})^2]$.
+The term $r_{0}$ is the correlation length of the turbulence, the value of \(r\) in pc where equation \ref{eq:S} reach the value of \(\sigma^2\), and $m$ is the index that adjust our results.
+The term $\zeta$ is a correction for small scales considering a Gaussian seeing, $s_{0}$, and has the form $tanh^{2}[(r/2s_{0})^2]$, and \(\eta\) is the observational noise.
+
+The results and the errors of $r_{0}$ and $m$ are obtained using equations \ref{eq:S} and \ref{eq:b} in a chi-square (\(\chi^2)\) statistic in order to do a non-linear least-squares fit of a model to our data.
+In this way we avoid one fundamental problem in the interpretation of the structure function results.
+The slope in the majority of previous studies and hence, the correlation length, is obtained by eye.
+The canonical way to find it is to determine a particular range of ascending values in the structure function results. 
+If this increase in values is reversed it is commonly assumed that one particular range has been found. 
+In some cases this procedure keeps going up to large scales, having two or more inertial regimes giving as a interpretation multiple energy injection scales.
+Since the results using the canonical method aren't conclusive we choose the chi-square (\(\chi^2)\) statistic to present the significance of our results.
+This way we can maintain consistency in our analysis of multiple regions and keep the possibility open to enhance our sample with future consistency.
 
@@
 The last column shows previous publications where the data was used.
-In appendix \ref{sec:VelMaps} we show in the Figure \ref{fig:hist} the histograms of the velocity samples of each HII region where we applied equation \ref{eq:S}.
-The Figures \ref{fig:M604}-\ref{fig:MOrion} show the two-dimensional radial velocity map of each region.
+For the first 4 regions in Table \ref{tab:Data} the value of \(\mu\) is the observed radial velocity accounting for heliocentric correction and subtracting the corrected radial velocity value of the most luminous pixel.
 
-\begin{table}
+%In appendix \ref{sec:VelMaps} we show in the Figure \ref{fig:hist} the histograms of the velocity samples of each HII region where we applied equation \ref{eq:S}.
+%The Figures \ref{fig:M604}-\ref{fig:MOrion} show the two-dimensional radial velocity map of each region.
+
+\begin{table*}
   \begin{center}
@@
       e) \citet{Damiani:2017b}
-      f) \citet{1987A&A...176..338H}
-      g) \citet{1987A&A...176..347H}.
+      f) \citet{1987A&A...176..347H}
+      g) \citet{arthur2016turbulence}.
     } 
@@
 Hubble X  & -5.95    &    12.9             &    6 925    &1.02&  -     \\
-30Dor     & 265.56*  &    252.79           &    363 059    &0.08&   c    \\
+30Dor     & 265.56*  &    252.79           &    363 059    &0.2&   c    \\
 Carina    & -8.83    &    17.89         &   855    &&   d    \\
 NGC 346   &          &       31.36           &    112 796   &&       \\
-Lagoon    & 3.21 / -6.26 &     8.95 / 7.53    &    566 / 1 176    &&  f / e   \\
-Orion     &     -1.25    &     10.43    &    359    &&    g   \\
+Lagoon    & -6.26 &    7.53    &    1 176    &&   e   \\
+Orion Large     &     -1.25    &     10.43    &    359    &&    f   \\
+Orion Small     &         &        &        &&    g   \\
 \end{tabular}\label{tab:Data}
 \end{center}
-\end{table}
+\end{table*}
 
@@
 With the aim to investigate how statistically homogeneous the regions are, we also show the value of $\sigma_{LOS}$.
-In the appendix \ref{sec:StructFunct} the Figures \ref{fig:SF604}-\ref{fig:SFM42} show the second-order structure functions of the different HII regions for the \halpha\ emission line.
 
+The final column shows the Taylor scale, \(l_T\), which measures the average spatial extent of velocity gradients. \citet{1999ApJ...524..895M} define this scale as \citet{1987A&A...176..347H}
+
+\begin{equation}\label{eq:TS}
+l_T=\dfrac{\sigma r_s}{\sigma_{r_s}}
+\end{equation}
+
+where \(r_s\) is the smallest separation \(r\) and \(\sigma_{r_s}\) the value of the structure function at that separation.
+It is possible to calculate how this Taylor micro-scale is related to the correlation length by:
+
+\begin{equation}\label{eq:TS1}
+l_T=\dfrac{r_s}{\sqrt{2}}(\dfrac{r_0}{r_s})^{m/2}
+\end{equation}
+
+%In the appendix \ref{sec:StructFunct} the Figures \ref{fig:SF604}-\ref{fig:SFM42} show the second-order structure functions of the different HII regions for the \halpha\ emission line.
 The power-law fit in the structure function for the both regions in the M33 galaxy in is performed above scales of 1.7 pc.
-For NGC 604 the index is 1.7 with a correlation length of 9 pc.
+For NGC 604 the index is correspond to 1.95 with a correlation length of 8.75 pc.
 The structure functions keep going up to scales of 70 pc following a periodic pattern.
 In an idealized case, at scales larger than r$_{0}$ the structure function flattens as it tends towards the asymptotic value of 2$\sigma$ \citep{arthur2016turbulence}.
-Figure \ref{fig:SF604} shows that the structure functions for NGC 604, follow a periodic behavior around 2$\sigma$.
+The structure functions for NGC 604, follow a periodic behavior around 2$\sigma$.
 We can think of a wave starting around 30 pc, with a series of $ >$2$\sigma$ values up to $\sim$100 pc.
@@
 Therefore we relate periodic behavior to scales of magnitude $\sim$100 pc across our sample box.
-For NGC 595 the values obtained are 1.55 and 8.8.
+For NGC 595 the values obtained are 1.75 and 9 pc.
 The structure function goes up until 30 pc, reaching values above 2$\sigma$ before falling.
 
-For NGC 6822 regions, Hubble X and Hubble V, the $m$ index is 1.5 and 1.4, with a correlation length of 3.5 and 2.7 pc, respectively.
+For NGC 6822 regions, Hubble X and Hubble V, the $m$ index is 1.7 and 1.62, with a correlation length of 3.62 and 2.7 pc, respectively.
 Both regions reach a maximum of 2$\sigma$ around 20 pc.
 The 30Dor nebula \citep{Castro:2018a} has a correlation length of 2.7 pc and and index of 1.22.
+NGC 346 has a correlation length of 1.4 and an index of 1.13.
 
@@
 The structure function shows large-scale oscillatory pattern, with peaks at \(\sim\) 3, 6 and 10 pc.
-The galactic region Lagoon nebula \citep{Damiani:2017b} presents a correlation length of 1.5 pc and a index of 1.15.
+
+The galactic region Lagoon nebula \citep{Damiani:2017b} presents a correlation length of 1.378 pc and a index of 1.13.
 For this region the structure function reach a constant value of 12 km$^{2}$/s$^{2}$ from 2 to 6 pc.
 For scales greater than 6 pc large-scale correlation is found up to 15 pc.
-M42 results shows an index of 0.75 with a correlation length of 0.65.
+
+For Orion (M42) we have the opportunity to study two different observations with different implications.
+\citet{1987A&A...176..347H} observations allow us to study the large scale of the nebula, covering 4 pc, while \cite{arthur2016turbulence} allow us to study the small scales up to 0.4 pc.
+Large scales results shows an index of 0.84 with a correlation length of 0.9 pc while the small scales have 1.44 and 0.062 pc.
+
+\begin{table*}
+\begin{center}\caption{Main results.}
+\begin{tabular}{cccccccccc}\hline
+HII    &  \(\sigma\) &   \(r_0\) &    \(m\)   & r$_{2\sigma}$* &  \(r_{max}\)/\(r_0\)* & \(\sigma_{LOS}\)& \(l_T\)* & \(Re\)*& - \\
+Region    &  [km/s] &  [pc]    &        & [pc] &      &[km/s]& [pc] & &  \\ \hline
+NGC 604   &  7.39   &  8.75\(^{+0.68}_{-0.75}\)    &   1.95\(^{+0.12}_{-0.14}\)  & 27   & 14.7 & 7.69 &  5.1 & &  \\
+NGC 595   &  6.64   &  8.99\(^{+0.58}_{-0.71}\)    &   1.75\(^{+0.10}_{-0.10}\) & 20   & 21.4 & 5.74 & 4.4  & &  \\
+Hubble V  &  2.80   &  2.7\(^{+0.24}_{-0.14}\)   &   1.62\(^{+0.11}_{-0..09}\)  & 12   & 19.9 &      & 1.56 & &  \\ 
+Hubble X  &  3.59   &  3.62\(^{+0.18}_{-0.15}\)    &   1.7\(^{+0.08}_{-0.09}\) & 15   & 22.1 &      & 1.95 & &  \\   
+30 Dor    &  15.8    &   2.69\(^{+0.08}_{-0.03}\)    &   1.22\(^{+0.022}_{-0.007}\) & 11   & 8.9  &      & 0.69 & &  \\
+Carina    &  4.22    &   0.55    &    1   & 2    & 16.1 & 2.7  &      & &  \\
+NGC 346   &   5.6    &  1.4\(^{+0.05}_{-0.75}\)     &    1.13\(^{+0.03}_{-0.03}\) &     &     &     &  & &  \\
+Lagoon    &  2.7     &   1.78\(^{+0.07}_{-0.07}\)     &   1.36\(^{+0.04}_{-0.03}\) &  6   & 10.1 &      &      & &  \\ 
+Orion Large &  3.23    &   0.84\(^{+0.37}_{-0.24}\)    &   0.9\(^{+0.04}_{-0.04}\) &  -   & 27.6 &   6  &      & &  \\
+Orion Small &   3.1 & 0.062\(^{+0.003}_{-0.001}\)      &  1.44\(^{+0.11}_{-0.01}\)  &     &  &  6   &      &  & \\
+
+\end{tabular}\label{tab:Res}
+\end{center}
+\end{table*}
+
+\subsection{Plane of sky radial velocity dispersion \(\sigma\)}
 
@@
 
-\begin{table}
-\begin{center}\caption{Main results.}
-\begin{tabular}{cccccccc}\hline
-HII    &  \(\sigma\) &   \(r_0\) &    \(m\)   & r$_{2\sigma}$ &  \(r_{max}\)/\(r_0\) & \(\sigma_{LOS}\)& \(l_T\) \\
-    Region    &  [km/s]  &   [pc]    &       & [pc] &  &[km/s]&    [pc] \\\hline
-NGC 604   &  7.39    &   9.09    &   1.7  & 27  & 14.7 &  7.69&  5.1 \\
-NGC 595   &  6.64    &   8.82    &   1.55 & 20  & 21.4 & 5.74& 4.4 \\
-Hubble V  &  2.80    &   2.78    &   1.4  &  12  & 19.9 & & 1.56 \\ 
-Hubble X  &  3.59    &   3.55    &   1.5  &  15  & 22.1 & & 1.95 \\       
-30 Dor    &  15.8    &   2.7     &   1.22 &  11  & 8.9 &  & 0.69 \\  
-Carina    &  4.22    &   0.55    &    1   &   2   &  16.1  &  2.7&  \\
-NGC 346   &   5.6    &  1.05     &    1.5    &      &  & & \\
-Lagoon    &  2.7     &   1.5     &   1.15 &   6   & 10.1 &&     \\  
-M42       &  3.23    &   0.65    &   0.75 &  -   & 27.6 & 6	& \\
+\subsection{Structure function power indices \(m\)}
 
-\end{tabular}\label{tab:Res}
-\end{center}
-\end{table}
+The index \(m\) seems biased to \(m>\)1.6 for the extragalactic regions and \(m\sim\)1 for nearby regions.
+This could be attributed to a data quality issue since we are not able to resolve distant regions in the same way we do with nearby objects.
+Since we are not observing all the inertial range on distant regions \(m\) should be taken a secondary parameter.
 
-\subsection{Structure function power indices}
+We can compute the m$_{3D}$ index from m$_{2D}$ ($m$ till now) if we assume that the m$_{3D}$ index lies between the limits of projection smoothing and a sheet-like distribution following the procedure by \cite{arthur2016turbulence}.
+This can be assumed throughout the relationship m$_{2D}$ - 1 $<$ m$_{3D}$ $<$ m$_{2D}$.
+For our observations we have 0.9 $<$ m$_{3D}$ $<$ 1.95.
 
-The index \(m\) seems biased to \(m>\)1.5 for the extragalactic regions and \(m\sim\)1 for nearby regions.
-This could be attributed to a data quality issue since we are not able to resolve distant regions in the same way we do with nearby objects.
-Since we are not observing all the inertial range on distant regions there is the possibility that \(m\) is not a reliable parameter.
-
-It is possible to compute the m$_{3D}$ index from m$_{2D}$ ($m$ till now) if we assume that the m$_{3D}$ index lies between the limits of projection smoothing and a sheet-like distribution \citep{arthur2016turbulence}.
-This can be assumed throughout the relationship m$_{2D}$ - 1 $<$ m$_{3D}$ $<$ m$_{2D}$.
-We have 0.65 $<$ m$_{3D}$ $<$ 1.7.
-
-\subsection{Significance on the length scale}
+\subsection{Significance on the length scale \(r_0\)}
 
 Ideally the correlation length, \(r_0\), should represent the scale of dominant energy injection. 
+Since it is unclear what are the mechanisms driving the turbulence, thought a lot of options are candidates, it is difficult to pinpoint one particular as main responsible. 
+The possibility the correlation length reveals the answer to the cause of observed motions is a long shot, but it is clear that each velocity field has a corresponding \(r_0\) value. 
+The range covered our results goes from 0.07 to 9 pc, a small range in comparison with the two order magnitude difference in size and luminosity.
 
+With the aim to relate each \(r_0\) with each region we invoke previous studies on the kinematics of the ionized gas. 
 \citet{sabalisck1995supersonic} studied NGC 604 revealing that the kinematics of the region behave different considering different scales.
 High emission knots on the region encompasses supersonic global velocity dispersion values of 14 $<$ \(\sigma_{LOS}\) $<$ 20 km s\(^{-1}\).
-This knots are well fitted with Gaussian profiles thus, defining the kinematic core \citet{munoz1996}.
+This knots are well fitted with Gaussian profiles thus, defining the kinematic core \citep{munoz1996}.
 A characteristic radius for them is \(\sim\) 7 pc.
@@
 
-Figure \ref{fig:SF604} shows similarity in our results and previous studies from \citet{tanco1997} and \citet{2019arXiv191203543M} for TAURUS-II data.
+Orion...
+
+The first attempt at characterizing turbulence in a giant extragalactic HII region, GEHR, was done by \citet{1961MNRAS.122....1F} with the 30 Dor complex in the LMC, finding no indication of turbulent motions.
+\citet{2019arXiv191203543M} investigated the structure function in 30 Dor finding on their results that the structure function is entirely flat on scales from 3 to 200 pc.
+In the context of the high-resolution observations it is possible to see why their results do not reflect the turbulent structure of the nebula; their observations cover a region where the large-scale velocity fluctuations are uncorrelated.
+There is a good agreement with the results from \citet{2019arXiv191203543M} (Figure 15 Top on their work), while \citet{1961MNRAS.122....1F} results does not overlap ours.
+
+Figure X shows similarity in our results and previous studies from \citet{tanco1997} and \citet{2019arXiv191203543M} for TAURUS-II data.
 \citep{2019arXiv191203543M} report $\sigma$ of 7.2 km/s while we have 7.3 km/s.
@@
 As mentioned by \citet{2019arXiv191203543M} some problems and inconsistencies arise in the results of \citet{tanco1997}; they don't consider a lower limit based on the observational seeing and that lead them to conclude about a double regime acting on the velocity spectrum.
-None of the previous studies present a power-law index to compare our results, but  Fig.
-\ref{fig:SF604} shows that the difference lies on the structure function or lag value and no on the form of the plot.
+None of the previous studies present a power-law index to compare our results, but Fig. X shows that the difference lies on the structure function or lag value and no on the form of the plot.
 With this assumption we can establish the same index of 1.7 for NGC 604 TAURUS-II observations.
@@
 The high difference is because the consider that this happen at 2$\sigma$ (equation 13 on their paper).
-The power-law index the provided is 1.55$\pm$0.01.
+The power-law index they provide is 1.55$\pm$0.01.
 
-The first attempt at characterizing turbulence in a giant extragalactic HII region, GEHR, was done by \citet{1961MNRAS.122....1F} with the 30 Dor complex in the LMC, finding no indication of turbulent motions.
-\citet{2019arXiv191203543M} investigated the structure function in 30 Dor finding on their results that the structure function is entirely flat on scales from 3 to 200 pc.
-In the context of the high-resolution observations it is possible to see why their results do not reflect the turbulent structure of the nebula; their observations cover a region where the large-scale velocity fluctuations are uncorrelated.
-There is a good agreement with the results from \citet{2019arXiv191203543M} (Figure 15 Top on their work), while \citet{1961MNRAS.122....1F} results does not overlap ours.
+\subsection{Scaling relations}
 
-%Figure \ref{fig:SFM8} show the structure functions of M8 previously published by \citep{1987ApJ...317..686O} and the structure function computed in this work from observations of \citet{1987A&A...176..338H}.
+\subsubsection{Correlations}
 
-\subsection{L vs $\sigma$}
+As mentioned in the introduction scaling relations between parameters like size and luminosity are common tools to study HII regions along dwarf galaxies and high-redshift star formation regions.
+Those relationships, particularly in GEHRs, made them candidates as standard candles.
+We are using these quantities along the distance, \(r_0\) and \(m\) to determine the correlations between physical and turbulent parameters.
 
-%\begin{figure}
-%\centering 
-%\includegraphics[width=3in]{Figures/lvss.pdf}
-%\caption{}
-%\label{fig:}
-%\end{figure}
+Using the first three columns in Tables \ref{tab:Reg} and \ref{tab:Res}, we obtain the Pearson correlation coefficient between luminosity and \(\sigma\), size and \(r_0\), and distance and \(m\).
+They are respectively, 0.71, 0.96 and 0.73.
+
+\subsubsection{L vs \(\sigma\)}
+
+\begin{figure}
+\centering 
+\includegraphics[width=3in]{Figures/lvss.pdf}
+\caption{}
+\label{fig:}
+\end{figure}
 
@@
 %\end{figure}
-%%%%%%%%%%%%%%%%
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+Relationship between plane-of-sky and line-of-sight velocity dispersion.
+Comparison with \citet{Rozas:2006b}.
 
-Relationship between plane-of-sky and line-of-sight velocity dispersion.  Comparison with \citet{Rozas:2006b}.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-\clearpage
+%\clearpage
 
@@
 
-\appendix
+%\appendix
 
-\section{Velocity maps}\label{sec:VelMaps}
+%\section{Velocity maps}\label{sec:VelMaps}
 
-\begin{figure*}
-\centering
-\begin{multicols}{4}
-\includegraphics[width=1.5in]{Figures/Hist/604}\par
-\includegraphics[width=1.5in]{Figures/Hist/595.pdf}\par
-\includegraphics[width=1.5in]{Figures/Hist/Hubble V.pdf}\par
-\includegraphics[width=1.5in]{Figures/Hist/Hubble X.pdf}\par
-\end{multicols}
-\begin{multicols}{4}
-\includegraphics[width=1.5in]{Figures/Hist/M8.pdf}\par
-\includegraphics[width=1.5in]{Figures/Hist/Car.pdf}\par
-\includegraphics[width=1.5in]{Figures/Hist/Orion.pdf}\par
-\includegraphics[width=1.5in]{Figures/Hist/30Dor.pdf}\par
-\end{multicols}
-\caption{}
-\label{fig:hist}
-\end{figure*}
+%\begin{figure*}
+%\centering
+%\begin{multicols}{4}
+%\includegraphics[width=1.5in]{Figures/Hist/604}\par
+%\includegraphics[width=1.5in]{Figures/Hist/595.pdf}\par
+%\includegraphics[width=1.5in]{Figures/Hist/Hubble V.pdf}\par
+%\includegraphics[width=1.5in]{Figures/Hist/Hubble X.pdf}\par
+%\end{multicols}
+%\begin{multicols}{4}
+%\includegraphics[width=1.5in]{Figures/Hist/M8.pdf}\par
+%\includegraphics[width=1.5in]{Figures/Hist/Car.pdf}\par
+%\includegraphics[width=1.5in]{Figures/Hist/Orion.pdf}\par
+%\includegraphics[width=1.5in]{Figures/Hist/30Dor.pdf}\par
+%\end{multicols}
+%\caption{}
+%\label{fig:hist}
+%\end{figure*}
 
-\begin{figure}
-\centering 
-\includegraphics[width=2.5in]{Figures/M6T}
-\caption{Radial velocity maps of NGC 604 in H$\alpha$.  }
-\label{fig:M604}
-\end{figure}
+%\begin{figure}
+%\centering 
+%\includegraphics[width=2.5in]{Figures/M6T}
+%\caption{Radial velocity maps of NGC 604 in H$\alpha$.  }
+%\label{fig:M604}
+%\end{figure}
 
-\begin{figure}
-\centering 
-\includegraphics[width=2.5in]{Figures/M5T}
-\caption{Radial velocity map of NGC 595 in H$\alpha$.}
-\label{fig:M595}
-\end{figure}
+%\begin{figure}
+%\centering 
+%\includegraphics[width=2.5in]{Figures/M5T}
+%\caption{Radial velocity map of NGC 595 in H$\alpha$.}
+%\label{fig:M595}
+%\end{figure}
 
-\begin{figure}
-\centering 
-\includegraphics[width=2.5in]{Figures/MV}
-\caption{Radial velocity map of Hubble V in H$\alpha$.}
-\label{fig:MHV}
-\end{figure}
+%\begin{figure}
+%\centering 
+%\includegraphics[width=2.5in]{Figures/MV}
+%\caption{Radial velocity map of Hubble V in H$\alpha$.}
+%\label{fig:MHV}
+%\end{figure}
 
-\begin{figure}
-\centering 
-\includegraphics[width=2.5in]{Figures/MX}
-\caption{Radial velocity map of Hubble X in H$\alpha$.}
-\label{fig:MHX}
-\end{figure}
+%\begin{figure}
+%\centering 
+%\includegraphics[width=2.5in]{Figures/MX}
+%\caption{Radial velocity map of Hubble X in H$\alpha$.}
+%\label{fig:MHX}
+%\end{figure}
 
-\begin{figure}
-\centering 
-\includegraphics[width=2.5in]{Figures/M30D}
-\caption{Radial velocity map of 30 Dor in H$\alpha$ \citep{Castro:2018a}.}
-\label{fig:M30Dor}
-\end{figure}
+%\begin{figure}
+%\centering 
+%\includegraphics[width=2.5in]{Figures/M30D}
+%\caption{Radial velocity map of 30 Dor in H$\alpha$ \citep{Castro:2018a}.}
+%\label{fig:M30Dor}
+%\end{figure}
 
-\begin{figure}
-\centering 
-\includegraphics[width=2.5in]{Figures/Car}
-\caption{Radial velocity map of Carina in H$\alpha$ taken from \citet{Damiani:2016a}.}
-\label{fig:MCar}
-\end{figure}
+%\begin{figure}
+%\centering 
+%\includegraphics[width=2.5in]{Figures/Car}
+%\caption{Radial velocity map of Carina in H$\alpha$ taken from \citet{Damiani:2016a}.}
+%\label{fig:MCar}
+%\end{figure}
 
-\begin{figure}
-\centering 
-\includegraphics[width=3in]{Figures/M8H.png}
-\includegraphics[width=3.5in]{Figures/M8}
-\caption{Radial velocity map of M8 in H$\alpha$. Taken from \citep{Damiani:2017b} and \citet{1987A&A...176..338H}.}
-\label{fig:MM8}
-\end{figure}
+%\begin{figure}
+%\centering 
+%\includegraphics[width=3in]{Figures/M8H.png}
+%\includegraphics[width=3.5in]{Figures/M8}
+%\caption{Radial velocity map of M8 in H$\alpha$. Taken from \citep{Damiani:2017b} and \citet{1987A&A...176..338H}.}
+%\label{fig:MM8}
+%\end{figure}
 
-\begin{figure}
-\centering 
-\includegraphics[width=3in]{Figures/OrionL}
-\caption{Radial velocity map of Orion in H$\alpha$ taken from \citet{1987A&A...176..347H}.}
-\label{fig:MOrion}
-\end{figure}
+%\begin{figure}
+%\centering 
+%\includegraphics[width=3in]{Figures/OrionL}
+%\caption{Radial velocity map of Orion in H$\alpha$ taken from \citet{1987A&A...176..347H}.}
+%\label{fig:MOrion}
+%\end{figure}
 
-\clearpage
+%\clearpage
 
-\section{Second order structure functions}\label{sec:StructFunct}
+%\section{Second order structure functions}\label{sec:StructFunct}
 
-Here we present the plots of the second order structure functions...
+%Here we present the plots of the second order structure functions...
 
-\begin{figure}
-\centering 
-\includegraphics[width=2in]{Figures/SFplots/604}
-\caption{NGC 604 second-order structure functions for H$\alpha$ emission line from the ISIS and TAURUS instruments (Fig.
-\ref{fig:M604}).
-The figure also shows the structure functions presented in previous works \citep{tanco1997,2019arXiv191203543M}.
-The green area represents the scales affected by observational seeing.
-The vertical line indicate the value of rhe correlation length , r$_{0}$.
-The solid horizontal line denote the value of $\sigma$.
-The double dotted horizontal line indicates 2$\sigma$.
-Black plots are structure functions calculated in this work and gray plots are from previous works.
-}
-\label{fig:SF604}
-\end{figure}
+%\begin{figure}
+%\centering 
+%\includegraphics[width=2in]{Figures/SFplots/604}
+%\caption{NGC 604 second-order structure functions for H$\alpha$ emission line from the ISIS and TAURUS instruments (Fig. \ref{}).
+%The figure also shows the structure functions presented in previous works \citep{tanco1997,2019arXiv191203543M}.
+%The green area represents the scales affected by observational seeing.
+%The vertical line indicate the value of rhe correlation length , r$_{0}$.
+%The solid horizontal line denote the value of $\sigma$.
+%The double dotted horizontal line indicates 2$\sigma$.
+%Black plots are structure functions calculated in this work and gray plots are from previous works.
+%}
+%\label{fig:SF604}
+%\end{figure}
 
-\begin{figure}
-\centering 
-\includegraphics[width=2in]{Figures/SFplots/595}
-\caption{NGC 595 second-order structure functions for H$\alpha$ emission line from the TAURUS instrument (Fig. \ref{fig:M595}). Same information as Figure \ref{fig:SF604}.}
-\label{fig:SF595}
-\end{figure}
+%\begin{figure}
+%\centering 
+%\includegraphics[width=2in]{Figures/SFplots/595}
+%\caption{NGC 595 second-order structure functions for H$\alpha$ emission line from the TAURUS instrument (Fig. \ref{}).
+%Same information as Figure \ref{fig:SF604}.}
+%\label{fig:SF595}
+%\end{figure}
 
-\begin{figure}
-\centering 
-\includegraphics[width=2in]{Figures/SFplots/hubbleV}
-\caption{Hubble V second-order structure functions for H$\alpha$ emission line from the TAURUS instrument \ref{fig:MHV}). Same information as Figure \ref{fig:SF604}.}
-\label{fig:SFV}
-\end{figure}
+%\begin{figure}
+%\centering 
+%\includegraphics[width=2in]{Figures/SFplots/hubbleV}
+%\caption{Hubble V second-order structure functions for H$\alpha$ emission line from the TAURUS instrument \ref{}).
+%Same information as Figure \ref{fig:SF604}.}
+%\label{fig:SFV}
+%\end{figure}
 
-\begin{figure}
-\centering 
-\includegraphics[width=2in]{Figures/SFplots/hubbleX.pdf}
-\caption{Hubble X second-order structure functions for H$\alpha$ emission line from the TAURUS instrument \ref{fig:MHX}). Same information as Figure \ref{fig:SF604}.}
-\label{fig:SFX}
-\end{figure}
+%\begin{figure}
+%\centering 
+%\includegraphics[width=2in]{Figures/SFplots/hubbleX.pdf}
+%\caption{Hubble X second-order structure functions for H$\alpha$ emission line from the TAURUS instrument \ref{}).
+%Same information as Figure \ref{fig:SF604}.}
+%\label{fig:SFX}
+%\end{figure}
 
-\begin{figure}
-\centering 
-\includegraphics[width=2in]{Figures/SFplots/tarantula}
-\caption{30 Dor second-order structure functions for H$\alpha$ emission line \citep{Castro:2018a}.
-The figure also shows the structure functions presented in previous works \citep{2019arXiv191203543M}.
-Same information as Figure \ref{fig:SF604}.}
-\label{fig:SF30Dor}
-\end{figure}
+%\begin{figure}
+%\centering 
+%\includegraphics[width=2in]{Figures/SFplots/tarantula}
+%\caption{30 Dor second-order structure functions for H$\alpha$ emission line \citep{Castro:2018a}.
+%The figure also shows the structure functions presented in previous works \citep{2019arXiv191203543M}.
+%Same information as Figure \ref{fig:SF604}.}
+%\label{fig:SF30Dor}
+%\end{figure}
 
-\begin{figure}
-\centering 
-\includegraphics[width=2in]{Figures/SFplots/carina}
-\caption{Carina second-order structure functions for H$\alpha$ emission line taken from. Same information as Figure \ref{fig:SF604}.}
-\label{fig:SFCar}
-\end{figure}
+%\begin{figure}
+%\centering 
+%\includegraphics[width=2in]{Figures/SFplots/carina}
+%\caption{Carina second-order structure functions for H$\alpha$ emission line taken from.
+%Same information as Figure \ref{fig:SF604}.}
+%\label{fig:SFCar}
+%\end{figure}
 
-\begin{figure}
-\centering 
-\includegraphics[width=2in]{Figures/SFplots/M8}
-\caption{M8 second-order structure functions for H$\alpha$ emission line \ref{fig:MM8}) from  \citet{Damiani:2017b} and \citet{1987A&A...176..338H}.
-The figure also shows the structure functions presented in previous works \citep{1987ApJ...317..686O}.
-Same information as Figure \ref{fig:SF604}.}
-\label{fig:SFM8}
-\end{figure}
+%\begin{figure}
+%\centering 
+%\includegraphics[width=2in]{Figures/SFplots/M8}
+%\caption{M8 second-order structure functions for H$\alpha$ emission line \ref{}) from  \citet{Damiani:2017b} and \citet{1987A&A...176..338H}.
+%The figure also shows the structure functions presented in previous works \citep{1987ApJ...317..686O}.
+%Same information as Figure \ref{fig:SF604}.}
+%\label{fig:SFM8}
+%\end{figure}
 
-\begin{figure}
-\centering 
-\includegraphics[width=2in]{Figures/SFplots/M42}
-\caption{M42 second-order structure functions for H$\alpha$ emission line taken from \citet{1987A&A...176..347H} \ref{fig:MOrion}).
-he figure also shows the structure functions presented in previous works \citep{von1951methode,munch1958internal,arthur2016turbulence}.
-Same information as Figure \ref{fig:SF604}.}
-\label{fig:SFM42}
-\end{figure}
+%\begin{figure}
+%\centering 
+%\includegraphics[width=2in]{Figures/SFplots/M42}
+%\caption{M42 second-order structure functions for H$\alpha$ emission line taken from \citet{1987A&A...176..347H} \ref{}).
+%he figure also shows the structure functions presented in previous works \citep{von1951methode,munch1958internal,arthur2016turbulence}.
+%Same information as Figure \ref{fig:SF604}.}
+%\label{fig:SFM42}
+%\end{figure}
 

### 2021-07-30 mnras_template.tex
Will change - not sure what

@@
   Fluctuations of centroid velocities on the plane of the sky are a powerful tool for studying the turbulent dynamics of emission line regions.
-  We apply the technique to archival \halpha\ observations of a diverse sample of 8 \hii{} regions
+  We apply the technique to archival \halpha\ observations of a diverse sample of 9 \hii{} regions
   in the Milky Way and other Local Group galaxies,
@@
 
+\definecolor{WillCommentColor}{rgb}{0.6,0.11,0.4}
+\newcommand\WILL[1]{\textbf{\color{WillCommentColor}#1}}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \section{Introduction}
+\WILL{I think it would be best to lead with a description of the dynamics of H II regions before mentioning the turbulence}.
 
@@
 Previous studies \citep{1999intu.conf.....F,2004ARA&A..42..211E,scalo2004interstellar} revealed that different phases of the interstellar medium show fluctuations on their velocity field that can be interpreted as evidence of random motions.
+
 The usual picture considers that interstellar turbulence is driven on different scales by various energetic processes.
@@
 Lagoon    &   1.25 & 25      &    37.47     & 0.0001   &  60& 900& 0.012 & \\
-Orion     &   0.4  & 5       &    37        & 0.000053 & 150& 50 & 0.027 & \\
+Orion     &   0.4  & 5       &    37        & 0.000053 & 150& 50 & 0.027 & \\\hline
 \end{tabular}\label{tab:Reg}
@@
 
-\subsection{Regions in M33 galaxy and NGC 6822}
+\subsection{Regions in M33 and NGC 6822}
 
@@
 This follows if we have an optically thin spectral line where it will have a width which is related to the total radial velocity dispersion of all fluctuations sampled along the line-of-sight \citep{1984ApJ...277..556S}.
+In these sense the structure function is used as a tool to investigate the projection of a three.dimensional correlation function onto the plane of sky \citep{arthur2016turbulence}.
 
@@
 The term $\zeta$ is a correction for small scales considering a Gaussian seeing, $s_{0}$, and has the form $tanh^{2}[(r/2s_{0})^2]$, and \(\eta\) is the observational noise. 
+In this idealized case, at scales larger than r$_{0}$ the structure function flattens as it tends towards the asymptotic value of 2$\sigma$ \citep{arthur2016turbulence}.
 
-The results and the errors of $r_{0}$ and $m$ are obtained using equations \ref{eq:S} and \ref{eq:b} in a chi-square (\(\chi^2)\) statistic in order to do a non-linear least-squares fit of a model to our data.
+\subsection{Application to our HII regions sample}
+
+The results and the errors of $r_{0}$ and $m$ are obtained using equations \ref{eq:S} and \ref{eq:b} in a chi-square (\(\chi^2)\) statistic in order to do a non-linear least-squares fit of a model to our data \citep{newville_matthew_2014_11813}.
 In this way we avoid one fundamental problem in the interpretation of the structure function results.
 The slope in the majority of previous studies and hence, the correlation length, is obtained by eye.
-The canonical way to find it is to determine a particular range of ascending values in the structure function results. 
-If this increase in values is reversed it is commonly assumed that one particular range has been found. 
-In some cases this procedure keeps going up to large scales, having two or more inertial regimes giving as a interpretation multiple energy injection scales.
-Since the results using the canonical method aren't conclusive we choose the chi-square (\(\chi^2)\) statistic to present the significance of our results.
-This way we can maintain consistency in our analysis of multiple regions and keep the possibility open to enhance our sample with future consistency.
+The traditional way to find it is to determine a particular range of ascending values in the structure function results. 
+If this increase in values is stopped it is commonly assumed that one particular range has been found. 
+In some cases this procedure keeps going up to large scales, giving two or more inertial regimes;this has lead to the interpretation of multiple energy injection scales.
+Since the previous described method isn't conclusive we choose the chi-square (\(\chi^2)\) statistic to present the significance of our results. 
+This way we can maintain consistency in our analysis.
 
@@
 \begin{tabular}{cccccc}\hline
-HII    &  $\mu$   & $\sigma^{2}$        &  No. of  &\(s_0\)& Previously  \\
-   Region       &  [km/s]  &  [km$^{2}$/s$^{2}$] &  points   &[pc]& used in:\\\hline
-NGC 604   &  3.56    &    54.63            &    9 510    &1.73&  a,b     \\
-NGC 595   &  2.82    &    44.13            &    8 765    &1.73&  -     \\
-Hubble V  & -1.23    &    7.87             &    5 832    &1.02&   -    \\
-Hubble X  & -5.95    &    12.9             &    6 925    &1.02&  -     \\
-30Dor     & 265.56*  &    252.79           &    363 059    &0.2&   c    \\
-Carina    & -8.83    &    17.89         &   855    &&   d    \\
-NGC 346   &          &       31.36           &    112 796   &&       \\
-Lagoon    & -6.26 &    7.53    &    1 176    &&   e   \\
-Orion Large     &     -1.25    &     10.43    &    359    &&    f   \\
-Orion Small     &         &        &        &&    g   \\
+HII         &$\mu$   &$\sigma^{2}$       &No. of  &\(s_0\)* & Previously \\
+Region      &[km/s]  &[km$^{2}$/s$^{2}$] &points  &[pc]     & used in:   \\ \hline
+NGC 604     &3.56    &54.63              &9 510   &1.73     &a,b         \\
+NGC 595     &2.82    &44.13              &8 765   &1.73     &-           \\
+Hubble V    &-1.23   &7.87               &5 832   &1.02     &-           \\
+Hubble X    &-5.95   &12.9               &6 925   &1.02     &-           \\
+30Dor       &265.56* &252.79             &363 059 &0.2      &c           \\
+Carina      &-8.83   &17.89              &855     &         &d           \\
+NGC 346     &        &31.36              &112 796 &         &            \\
+Lagoon      &-6.26   &7.53               &1 176   &         &e           \\
+Orion Large &-1.25   &10.43              &359     &         &f           \\
+Orion Small &        &9.61               &        &         &g            \\ \hline
 \end{tabular}\label{tab:Data}
@@
 
-Table \ref{tab:Res} presents the main parameters we obtain from the analysis on the fluctuations of the velocities.
-The first column is the velocity dispersion, \(\sigma\), of each sample of centroid velocities.
-The second column is the correlation length, \(r_0\).
-The third column is the index \(m\) that is used to fit our results.
-This index is used as a reference for comparison between theory and observations.
-In the forth column we show the separation where the value 2\(\sigma\) is reached.
+Table \ref{tab:Res} presents the three parameters we obtain from the analysis on the fluctuations of the velocities using the second order structure function.
+The second column is the velocity dispersion \(\sigma\) of each sample of centroid velocities.
+The third column is the correlation length \(r_0\).
+The index \(m\) is shown in the forth column;
+this index is used as a reference for comparison between theory and observations.
+In the fifth column we show the reduced chi-square value obtained using a non-linear regression algorithm. 
+Finally we show the mean velocity dispersion across the line-of-sight \(\sigma_{LOS}\) with the aim to investigate how statistically homogeneous the regions are.
+
+%In the appendix \ref{sec:StructFunct} the Figures \ref{fig:SF604}-\ref{fig:SFM42} show the second-order structure functions of the different HII regions for the \halpha\ emission line.
+
+The power-law fit in the structure function for the both regions in the M33 galaxy in is performed above scales of 1.7 pc.
+For NGC 604 the index is correspond to 1.95 with a correlation length of 8.75 pc. For NGC 595 the values obtained are 1.75 and 9 pc.
+For NGC 6822 regions, Hubble X and Hubble V, the $m$ index is 1.7 and 1.62, with a correlation length of 3.62 and 2.7 pc, respectively.
+The 30Dor nebula \citep{Castro:2018a} has a correlation length of 2.7 pc and an index of 1.22.
+NGC 346 correlation length is 1.4 pc and its index is 1.13.
+
+The Carina observations allow us to measure a blue shifted and a red shifted layer \citet{Damiani:2016a}.
+It is possible to combine the moments from the sum of two components \citep{2008RMxAA..44..181G}, we use this combined sample for the structure function analysis.
+Carina has an index of 0.82 with a correlation length of 0.94 pc.
+The galactic region Lagoon nebula \citep{Damiani:2017b} presents a correlation length of 1.78 pc and a index of 1.56.
+
+For Orion we have the opportunity to study two different observations.
+\citet{1987A&A...176..347H} observations allow us to study the large scale of the nebula, covering 4 pc, while \cite{arthur2016turbulence} allow us to study the small scales up to 0.4 pc.
+Large scales results shows an index of 0.9 with a correlation length of 0.84 pc while the small scales have 1.44 and 0.062 pc.
+
+\begin{table*}
+\begin{center}\caption{Main results.}
+\begin{tabular}{ccccccccc}\hline
+HII         &\(\sigma\) &\(r_0\)                     &\(m\)   &Reduced &\(\langle \sigma_{LOS} \rangle \) \\
+Region      &[km/s]     &[pc]                        &                           &chi-square &  [km/s]\\ \hline
+NGC 604     &7.39       &8.75\(^{+0.68}_{-0.75}\)    &1.95\(^{+0.12}_{-0.14}\)   &0.81 &16.2  \\
+NGC 595     &6.64       &8.99\(^{+0.58}_{-0.71}\)    &1.75\(^{+0.10}_{-0.10}\)   &0.47 &18.3  \\
+Hubble V    &2.80       &2.7\(^{+0.24}_{-0.14}\)     &1.62\(^{+0.11}_{-0.09}\)   &0.19 &13.4  \\ 
+Hubble X    &3.59       &3.62\(^{+0.18}_{-0.15}\)    &1.7\(^{+0.08}_{-0.09}\)    &0.13 &12.3  \\   
+30 Dor      &15.8       &2.69\(^{+0.08}_{-0.03}\)    &1.22\(^{+0.022}_{-0.007}\) &0.49 &31.7* \\
+Carina      &4.22       &0.94\(^{+0.94}_{-0.13}\)    &0.82\(^{+0.08}_{ -0.08}\)  &0.39 &22.4   \\
+NGC 346     & 5.6       &1.4\(^{+0.05}_{-0.75}\)     &1.13\(^{+0.03}_{-0.03}\)   &0.34 &  \\
+Lagoon      &2.7        &1.78\(^{+0.07}_{-0.07}\)    &1.56\(^{+0.05}_{-0.05}\)   &0.59 &13.6     \\ 
+Orion Large &3.23       &0.84\(^{+0.37}_{-0.24}\)    &0.9\(^{+0.04}_{-0.04}\)    &0.27 &6  \\
+Orion Small &3.1        & 0.062\(^{+0.003}_{-0.001}\)&1.44\(^{+0.11}_{-0.01}\)   &0.64 &6 \\\hline	  
+\end{tabular}\label{tab:Res}
+\end{center}
+\end{table*}
+
+%\begin{table*}
+%\begin{center}\caption{Main results.}
+%\begin{tabular}{ccccccccccc}\hline
+%HII    &  \(\sigma\) &   \(r_0\) &    \(m\)   &Reduced& r$_{2\sigma}$* &  \(r_{max}\)/\(r_0\)* & \(\langle \sigma_{LOS} \rangle \) & \(l_T\)* & \(Re\)*& - \\
+%Region    &  [km/s] &  [pc]    &&   chi-square     & [pc] &      &[km/s]& [pc] & &  \\ \hline
+%NGC 604   &  7.39   &  8.75\(^{+0.68}_{-0.75}\)    &   1.95\(^{+0.12}_{-0.14}\)  &0.81& 27   & 14.7 & 16.2 &  5.1 & &  \\
+%NGC 595   &  6.64   &  8.99\(^{+0.58}_{-0.71}\)    &   1.75\(^{+0.10}_{-0.10}\) &0.47& 20   & 21.4 & 18.3 & 4.4  & &  \\
+%Hubble V  &  2.80   &  2.7\(^{+0.24}_{-0.14}\)   &   1.62\(^{+0.11}_{-0.09}\)  & 0.19& 12   & 19.9 &  13.4    & 1.56 & &  \\ 
+%Hubble X  &  3.59   &  3.62\(^{+0.18}_{-0.15}\)    &   1.7\(^{+0.08}_{-0.09}\) &0.13& 15   & 22.1 &  12.3    & 1.95 & &  \\   
+%30 Dor    &  15.8    &   2.69\(^{+0.08}_{-0.03}\)    &   1.22\(^{+0.022}_{-0.007}\) &0.49& 11   & 8.9  &      & 0.69 & &  \\
+%Carina    &  4.22    &    0.94\(^{+0.94}_{-0.13}\)     &    0.82\(^{+0.08}_{ -0.08}\)   &0.39& 2    & 16.1 & 22.4  &      & &  \\
+%NGC 346   &   5.6    &  1.4\(^{+0.05}_{-0.75}\)     &    1.13\(^{+0.03}_{-0.03}\) &0.34&     &     &     &  & &  \\
+%Lagoon    &  2.7     &   1.78\(^{+0.07}_{-0.07}\)     &   1.56\(^{+0.05}_{-0.05}\) &0.59&  6   & 10.1 &  13.6    &      & &  \\ 
+%Orion Large &  3.23    &   0.84\(^{+0.37}_{-0.24}\)    &   0.9\(^{+0.04}_{-0.04}\) &0.27&  -   & 27.6 &   6  &      & &  \\
+%Orion Small &   3.1 & 0.062\(^{+0.003}_{-0.001}\)      &  1.44\(^{+0.11}_{-0.01}\)  &0.64&     &  &  6   &      &  & \\	  
+%\end{tabular}\label{tab:Res}
+%\end{center}
+%\end{table*}
+
+%\subsection{Plane of sky radial velocity dispersion \(\sigma\)}
+
+The highest \(\sigma\) is 15.8 km s\(^{-1}\) for 30Dor.
+This is two times higher than NGC 604 that has a value of 7.4 km s\(^{-1}\), followed by NGC 595 with 6.64 km s\(^{-1}\).
+NGC 346 is next with a value of 5.6 km s\(^{-1}\), followed by Carina with 4.22 km s\(^{-1}\).
+Hubble X and M42 have a value of 3.59 and 3.23 km s\(^{-1}\), respectively.
+Hubble V has 2.8 km s\(^{-1}\) and last mof all sample is Lagoon with 2.7 km s\(^{-1}\).
+
+\subsection{Structure function power indices \(m\)}
+
+It is possible that the index \(m\) is biased to \(m>\)1.6 for the extragalactic regions and \(m<\)1.5 for nearby regions.
+This could be attributed to a data quality issues because the inability to resolve distant regions in the same way we do with nearby objects.
+Since we are not observing all the inertial range on distant regions the \(m\) parameter  should be taken with some caution.
+
+We can compute the $m_{3D}$ index from the two dimensional \(m\), if we assume that the $m_{3D}$ index lies between the limits of projection smoothing and a sheet-like distribution. 
+For our observations we have 0.82 $<$ m$_{3D}$ $<$ 1.95.
+This is done following the procedure by \cite{arthur2016turbulence} assuming the relationship m$_{2D}$ - 1 $<$ m$_{3D}$ $<$ m$_{2D}$.
+This give us a considerable large range of 1. 
+Though \cite{arthur2016turbulence} are comparing emission lines and not regions we can conclude that the index \(m\) still is far away as a unique parameter for measuring turbulence and that the three-dimensional behavior would probably encompass a wide range of indices as seen in the two-dimensional observations.
+
+\subsection{Significance on the length scale \(r_0\)}
+
+Ideally the correlation length \(r_0\), should represent the scale of dominant energy injection. 
+Since it is unclear what are the mechanisms driving the turbulence, thought a lot of options are candidates, it is difficult to pinpoint one particular as main responsible. 
+The possibility that the correlation length reveals the answer to the cause of observed motions is a long shot, but it is clear that each velocity field has a corresponding \(r_0\) value. 
+The range covered in our results goes from 0.06 to 9 pc, a small range in comparison with the two order magnitude difference in size and luminosity.
+
+\subsection{Other significant scales}
+
+In the Table \ref{tab:ResII} the second column show the separation where the value 2\(\sigma\) is reached.
 We also show the ratio \(r_{max}/r_{0}\), where \(r_{max}\) is the maximum separation or lag in pc; this value is related to the size of each sample box. 
-With the aim to investigate how statistically homogeneous the regions are, we also show the value of $\sigma_{LOS}$.
-
-The final column shows the Taylor scale, \(l_T\), which measures the average spatial extent of velocity gradients. \citet{1999ApJ...524..895M} define this scale as \citet{1987A&A...176..347H}
+The forth column shows the Taylor scale, \(l_T\), which measures the average spatial extent of velocity gradients. \citet{1999ApJ...524..895M} define this scale as:
 
@@
 where \(r_s\) is the smallest separation \(r\) and \(\sigma_{r_s}\) the value of the structure function at that separation.
+
 It is possible to calculate how this Taylor micro-scale is related to the correlation length by:
@@
 
-%In the appendix \ref{sec:StructFunct} the Figures \ref{fig:SF604}-\ref{fig:SFM42} show the second-order structure functions of the different HII regions for the \halpha\ emission line.
-The power-law fit in the structure function for the both regions in the M33 galaxy in is performed above scales of 1.7 pc.
-For NGC 604 the index is correspond to 1.95 with a correlation length of 8.75 pc.
-The structure functions keep going up to scales of 70 pc following a periodic pattern.
-In an idealized case, at scales larger than r$_{0}$ the structure function flattens as it tends towards the asymptotic value of 2$\sigma$ \citep{arthur2016turbulence}.
-The structure functions for NGC 604, follow a periodic behavior around 2$\sigma$.
-We can think of a wave starting around 30 pc, with a series of $ >$2$\sigma$ values up to $\sim$100 pc.
-Then $<$2$\sigma$ values follow until the scales of 150 pc.
-Therefore we relate periodic behavior to scales of magnitude $\sim$100 pc across our sample box.
-For NGC 595 the values obtained are 1.75 and 9 pc.
-The structure function goes up until 30 pc, reaching values above 2$\sigma$ before falling.
+Finally in te table we present the Reynolds Number...
 
-For NGC 6822 regions, Hubble X and Hubble V, the $m$ index is 1.7 and 1.62, with a correlation length of 3.62 and 2.7 pc, respectively.
-Both regions reach a maximum of 2$\sigma$ around 20 pc.
-The 30Dor nebula \citep{Castro:2018a} has a correlation length of 2.7 pc and and index of 1.22.
-NGC 346 has a correlation length of 1.4 and an index of 1.13.
-
-The Carina observations allow us to measure a blue shifted and a red shifted layer \citet{Damiani:2016a}.
-Also, it is possible to combine the moments from the sum of two components \citep{2008RMxAA..44..181G}; for this sample we show our results.
-Carina has an index of 1 with a correlation length of 0.55 pc.
-The structure function shows large-scale oscillatory pattern, with peaks at \(\sim\) 3, 6 and 10 pc.
-
-The galactic region Lagoon nebula \citep{Damiani:2017b} presents a correlation length of 1.378 pc and a index of 1.13.
-For this region the structure function reach a constant value of 12 km$^{2}$/s$^{2}$ from 2 to 6 pc.
-For scales greater than 6 pc large-scale correlation is found up to 15 pc.
-
-For Orion (M42) we have the opportunity to study two different observations with different implications.
-\citet{1987A&A...176..347H} observations allow us to study the large scale of the nebula, covering 4 pc, while \cite{arthur2016turbulence} allow us to study the small scales up to 0.4 pc.
-Large scales results shows an index of 0.84 with a correlation length of 0.9 pc while the small scales have 1.44 and 0.062 pc.
-
-\begin{table*}
-\begin{center}\caption{Main results.}
-\begin{tabular}{cccccccccc}\hline
-HII    &  \(\sigma\) &   \(r_0\) &    \(m\)   & r$_{2\sigma}$* &  \(r_{max}\)/\(r_0\)* & \(\sigma_{LOS}\)& \(l_T\)* & \(Re\)*& - \\
-Region    &  [km/s] &  [pc]    &        & [pc] &      &[km/s]& [pc] & &  \\ \hline
-NGC 604   &  7.39   &  8.75\(^{+0.68}_{-0.75}\)    &   1.95\(^{+0.12}_{-0.14}\)  & 27   & 14.7 & 7.69 &  5.1 & &  \\
-NGC 595   &  6.64   &  8.99\(^{+0.58}_{-0.71}\)    &   1.75\(^{+0.10}_{-0.10}\) & 20   & 21.4 & 5.74 & 4.4  & &  \\
-Hubble V  &  2.80   &  2.7\(^{+0.24}_{-0.14}\)   &   1.62\(^{+0.11}_{-0..09}\)  & 12   & 19.9 &      & 1.56 & &  \\ 
-Hubble X  &  3.59   &  3.62\(^{+0.18}_{-0.15}\)    &   1.7\(^{+0.08}_{-0.09}\) & 15   & 22.1 &      & 1.95 & &  \\   
-30 Dor    &  15.8    &   2.69\(^{+0.08}_{-0.03}\)    &   1.22\(^{+0.022}_{-0.007}\) & 11   & 8.9  &      & 0.69 & &  \\
-Carina    &  4.22    &   0.55    &    1   & 2    & 16.1 & 2.7  &      & &  \\
-NGC 346   &   5.6    &  1.4\(^{+0.05}_{-0.75}\)     &    1.13\(^{+0.03}_{-0.03}\) &     &     &     &  & &  \\
-Lagoon    &  2.7     &   1.78\(^{+0.07}_{-0.07}\)     &   1.36\(^{+0.04}_{-0.03}\) &  6   & 10.1 &      &      & &  \\ 
-Orion Large &  3.23    &   0.84\(^{+0.37}_{-0.24}\)    &   0.9\(^{+0.04}_{-0.04}\) &  -   & 27.6 &   6  &      & &  \\
-Orion Small &   3.1 & 0.062\(^{+0.003}_{-0.001}\)      &  1.44\(^{+0.11}_{-0.01}\)  &     &  &  6   &      &  & \\
-
-\end{tabular}\label{tab:Res}
+\begin{table}
+\begin{center}\caption{Scales...}
+\begin{tabular}{cccccc}\hline
+HII         &r$_{2\sigma}$ &\(r_{max}\)/\(r_0\)  &\(l_T\) & \(Re\)* \\
+Region      &[pc]          &                     &[pc]    &   \\ \hline
+NGC 604     &28.73         &15.49                &5.35    &   \\
+NGC 595     &18.50         &21.01                &5.57    &   \\
+Hubble V    &11.61         &19.95                &1.80    &   \\ 
+Hubble X    &21.99         &21.67                &1.97    &   \\   
+30 Dor      &11.26         &8.99                 &0.59    &   \\
+Carina      &1.93          &31.55                &0.402   &   \\
+NGC 346     &5.78          &10.73                &0.39    &   \\
+Lagoon      &6.14          &10.68                &0.66    &   \\ 
+Orion Large &-             &2.98                 &0.24    &   \\
+Orion Small &0.162         &10.42                &0.019   &   \\ \hline	  
+\end{tabular}\label{tab:ResII}
 \end{center}
-\end{table*}
-
-\subsection{Plane of sky radial velocity dispersion \(\sigma\)}
-
-The highest \(\sigma\) is 15.8 km s\(^{-1}\) for 30Dor.
-This is two times higher than NGC 604 that has a value of 7.4 km s\(^{-1}\).
-NGC 346 is next with a value of 5.6 km s\(^{-1}\), followed by Carina with 4.22 km s\(^{-1}\).
-Hubble X and M42 have a value of 3.59 and 3.23 km s\(^{-1}\), respectively.
-With the lowest values is Hubble V with 2.8 km s\(^{-1}\) and Lagoon with 2.7 km s\(^{-1}\).
-
-\subsection{Structure function power indices \(m\)}
-
-The index \(m\) seems biased to \(m>\)1.6 for the extragalactic regions and \(m\sim\)1 for nearby regions.
-This could be attributed to a data quality issue since we are not able to resolve distant regions in the same way we do with nearby objects.
-Since we are not observing all the inertial range on distant regions \(m\) should be taken a secondary parameter.
-
-We can compute the m$_{3D}$ index from m$_{2D}$ ($m$ till now) if we assume that the m$_{3D}$ index lies between the limits of projection smoothing and a sheet-like distribution following the procedure by \cite{arthur2016turbulence}.
-This can be assumed throughout the relationship m$_{2D}$ - 1 $<$ m$_{3D}$ $<$ m$_{2D}$.
-For our observations we have 0.9 $<$ m$_{3D}$ $<$ 1.95.
-
-\subsection{Significance on the length scale \(r_0\)}
-
-Ideally the correlation length, \(r_0\), should represent the scale of dominant energy injection. 
-Since it is unclear what are the mechanisms driving the turbulence, thought a lot of options are candidates, it is difficult to pinpoint one particular as main responsible. 
-The possibility the correlation length reveals the answer to the cause of observed motions is a long shot, but it is clear that each velocity field has a corresponding \(r_0\) value. 
-The range covered our results goes from 0.07 to 9 pc, a small range in comparison with the two order magnitude difference in size and luminosity.
-
-With the aim to relate each \(r_0\) with each region we invoke previous studies on the kinematics of the ionized gas. 
-\citet{sabalisck1995supersonic} studied NGC 604 revealing that the kinematics of the region behave different considering different scales.
-High emission knots on the region encompasses supersonic global velocity dispersion values of 14 $<$ \(\sigma_{LOS}\) $<$ 20 km s\(^{-1}\).
-This knots are well fitted with Gaussian profiles thus, defining the kinematic core \citep{munoz1996}.
-A characteristic radius for them is \(\sim\) 7 pc.
-\citet{yang1996} identified 5 expanding shells within NGC 604, and one of them (Shell 3 on their paper) fall into our observations.
-This shells is 40 pc in diameter with an expansion velocity above 50 km s\(^{-1}\).
-This scales are related to the presence of strong stellar winds caused by massive stars.
-For the NGC 604 case, there is no clear relation between the \(r_0\) and some particular energy injection mechanism...
-
+\end{table}  
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
+%\subsection{Scaling relations}
+\subsection{Correlations between physical properties and turbulent parameters}
+
+As we mentioned in the introduction, the scaling relations between parameters like size and luminosity are common tools to study HII regions along dwarf galaxies and high-redshift star formation regions; in the past those relationships, particularly in GEHRs, made them candidates as standard candles.
+We apply these methods with the turbulent parameters \(r_0\) and index \(m\).
+
+Using the first three columns in Tables \ref{tab:Reg} and \ref{tab:Res}, we obtain the Pearson correlation coefficient $r$.
+Between luminosity (L) and \(\sigma\) it is 0.71, between distance (D) and \(m\) the value is 0.73, and finally between size (R) and \(r_0\) we have 0.96.
+By means of a significance test and assuming that a uncorrelated sample produces our results, for the first two relationships we have a probability value $p$ of 0.02 and for the remaining one of 6.57 10\(^{-6}\).
+Applying and ordinary least-square regression we find a form Y = aX + b; this values laong the previous ones y shown in Table \ref{tab:RestStats}.
+
+The relationship between L vs \(\sigma\) is one of the most studied.
+This relationship help us understanding how the star formation affects the gas motions and how star formation is regulated by feedback processes.
+Figure \ref{fig:sigvsl} shows different studies of the L vs \(\sigma\) relationship.
+In this case it is normally used the deconvolution of the observed lines taking account thermal broadening and instrumental broadening leaving the \(\sigma_{LOS}\).
+
+\begin{table*}
+\begin{center}\caption{Parameters of the linear regression (Y = aX + b).}
+\begin{tabular}{cccccc}\hline
+Y               &X         &a               &b                &r     & p                \\ \hline
+log \(r_0\)     &log \(R\) &0.65\(\pm\)0.06 &-0.83\(\pm\)0.11 & 0.96 & 6.57 10\(^{-6}\)             \\ 
+log \(\sigma\)  &log \(L\) &0.16\(\pm\)0.05 &-5.54\(\pm\)2.13 & 0.71 & 0.019              \\
+log \(m\)       &log \(D\) &0.05\(\pm\)0.02 &-0.05\(\pm\)0.03 & 0.73 & 0.019  \\ 
+*log \(\sigma\)  &log \(\sigma_{LOS}\) &0.77\(\pm\)0.28 &-0.21\(\pm\)0.32 &0.72 & 0.02 \\ \hline
+\end{tabular}\label{tab:RestStats}
+\end{center}
+\end{table*}
+
+\begin{figure}
+\centering 
+\includegraphics[width=3in]{Figures/lvss.pdf}
+\caption{}
+\label{fig:sigvsl}
+\end{figure}
+
+\begin{figure}
+\centering 
+\includegraphics[width=2in]{Figures/sigmas.pdf}
+\caption{}
+\label{fig:sigvssig}
+\end{figure}
+
+%Relationship between plane-of-sky and line-of-sight velocity dispersion.
+
 \subsection{Comparison with previous structure functions}
 
-Orion...
+A complete analysis on different emissions lines of the structure function on Orion was carried out by \citet{arthur2016turbulence} and reference therein.
+They observed a tendency that higher ionization lines presents higher values on the magnitude dispersion and the steepness of the structure function slope.
+This results just consider one component on the Gaussian fit. 
+The power-law index obtained by \citet{arthur2016turbulence} are \(m \sim 1.2 \pm 0.1\) for \halpha\ and [OIII] emission lines and for [SII] they found \(m \sim 0.8 \pm 0.1\).
+The correlation length for all lines is \(\approx\) 0.1-0.2 pc.
+For the same \halpha\ observation we obtained a value of 1.44.
+As a comparison for the large scales \citep{1987A&A...176..347H} the value is 0.9 with a considerable agreement with previous results.
+The change in the index could be attributed to the multiple scales of energy injection that are present in the nebula.
 
@@
 In the context of the high-resolution observations it is possible to see why their results do not reflect the turbulent structure of the nebula; their observations cover a region where the large-scale velocity fluctuations are uncorrelated.
-There is a good agreement with the results from \citet{2019arXiv191203543M} (Figure 15 Top on their work), while \citet{1961MNRAS.122....1F} results does not overlap ours.
+There is a good agreement with the results from \citet{2019arXiv191203543M} (Figure 15 Top on their work), while \citet{1961MNRAS.122....1F} results does not overlap with ours.
 
@@
 
-\subsection{Scaling relations}
+\subsection{What turbulence can tell us about kinematics of the ionized gas?}
 
-\subsubsection{Correlations}
-
-As mentioned in the introduction scaling relations between parameters like size and luminosity are common tools to study HII regions along dwarf galaxies and high-redshift star formation regions.
-Those relationships, particularly in GEHRs, made them candidates as standard candles.
-We are using these quantities along the distance, \(r_0\) and \(m\) to determine the correlations between physical and turbulent parameters.
-
-Using the first three columns in Tables \ref{tab:Reg} and \ref{tab:Res}, we obtain the Pearson correlation coefficient between luminosity and \(\sigma\), size and \(r_0\), and distance and \(m\).
-They are respectively, 0.71, 0.96 and 0.73.
-
-\subsubsection{L vs \(\sigma\)}
-
-\begin{figure}
-\centering 
-\includegraphics[width=3in]{Figures/lvss.pdf}
-\caption{}
-\label{fig:}
-\end{figure}
-
-%\begin{figure}
-%\centering 
-%\includegraphics[width=3in]{Figures/sfrvssig.pdf}
-%\caption{\citet{2006CRPhy...7..433B}}
-%\label{fig:}
-%\end{figure}
-
-Relationship between plane-of-sky and line-of-sight velocity dispersion.
-Comparison with \citet{Rozas:2006b}.
+With the aim to relate each \(r_0\) with each region we invoke previous studies on the kinematics of the ionized gas. 
+\citet{sabalisck1995supersonic} studied NGC 604 revealing that the kinematics of the region behave different considering different scales.
+High emission knots on the region encompasses supersonic global velocity dispersion values of 14 $<$ \(\sigma_{LOS}\) $<$ 20 km s\(^{-1}\).
+This knots are well fitted with Gaussian profiles thus, defining the kinematic core \citep{munoz1996}.
+A characteristic radius for them is \(\sim\) 7 pc.
+\citet{yang1996} identified 5 expanding shells within NGC 604, and one of them (Shell 3 on their paper) fall into our observations.
+This shells is 40 pc in diameter with an expansion velocity above 50 km s\(^{-1}\).
+This scales are related to the presence of strong stellar winds caused by massive stars.
+For the NGC 604 case, there is no clear relation between the \(r_0\) and some particular energy injection mechanism...
 

### 2021-09-03 mnras_template.tex
Javier changes to Aug 20
Javier changes up to 2021-09-03

@@
 % If you need two or more lines of authors, add an extra line using \newauthor
-\author[J. García-Vázquez et al.]{
+\author[J. García Vázquez et al.]{
 J. García Vázquez,$^{1}$\thanks{E-mail: jgarciav1600@alumno.ipn.mx}
@@
   Fluctuations of centroid velocities on the plane of the sky are a powerful tool for studying the turbulent dynamics of emission line regions.
-  We apply the technique to archival \halpha\ observations of a diverse sample of 9 \hii{} regions
-  in the Milky Way and other Local Group galaxies,
-  which span more than two orders of magnitude in size and luminosity.
-  By fitting a simple functional form to the second-order velocity structure function,
-  we extract three parameters for the fluctuations in each region:
-  total velocity dispersion, \(\sigma\),
-  autocorrelation length, \(r_0\), and power-law slope, \(m\).
+  To characterize these fluctuations we apply a statistical analysis using the second-order structure function to archival \halpha\ observations of a diverse sample of 9 \hii{} regions.
+  This regions are located in the Milky Way and other Local Group galaxies, and
+  span more than two orders of magnitude in size and luminosity.
+  By fitting a simple functional form of the structure function to our results
+  we extract three parameters related to the fluctuations in each region: the
+  total velocity dispersion \(\sigma\), which spans from 3 to 15 km s\(^{-1}\), the
+  autocorrelation length \(r_0\), which covers 0.06 - 8 pc, and the power-law slope \(m\), which ranges from 0.82 to 1.95.
   The velocity dispersion is found to correlate primarily with luminosity,
@@
   but this is probably an artifact of poor spatial resolution for the most distant regions.
+  A comparison between \(\sigma\) and \(\sigma_{POS}\) shows that this last value is at roughly the double for all regions.
   \textbf{Add a sentence about the conclusions!}
@@
 
-\definecolor{WillCommentColor}{rgb}{0.6,0.11,0.4}
-\newcommand\WILL[1]{\textbf{\color{WillCommentColor}#1}}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \section{Introduction}
-\WILL{I think it would be best to lead with a description of the dynamics of H II regions before mentioning the turbulence}.
 
@@
 Turbulence is suggested as a mechanism that can stir the medium and maintain the supersonic velocities. 
-
 The large lengths of astrophysical objects, ranging in scales from 10$^{6}$ to 10$^{17}$ m \citep{2010ApJ...710..853C}, and the high Reynolds numbers (Re), in the order of 10$^{4}$ - 10$^{9}$, are the main properties that supports the idea of a turbulent interstellar medium.
 Previous studies \citep{1999intu.conf.....F,2004ARA&A..42..211E,scalo2004interstellar} revealed that different phases of the interstellar medium show fluctuations on their velocity field that can be interpreted as evidence of random motions.
-
 The usual picture considers that interstellar turbulence is driven on different scales by various energetic processes.
@@
 
-The paper follows the next order...
-Section 2...
+The paper follows the next order: in Section \ref{sec:HIIsample} we describe the observational data and some main kinematics properties of each region.
+In Section \ref{sec:met} we present the statistical method used in this work.
+Section \ref{sec:results} presents the structure function of each region along with the turbulent parameters obtained by a non-linear regression method.
+In Section \ref{sec:discussion} we discuss our findings in the context of previous works.
 
-\section{HII regions sample}
+\section{HII regions sample}\label{sec:HIIsample}
 
-We used previous published observational data to measure the second-order velocity structure function for a number of compact and lower luminosity regions.
+We use previous published observational data to measure the second-order velocity structure function for a number of nine HII regions. 
 Table \ref{tab:Reg} shows the HII regions names
-with physical properties of each region.
+with the main physical properties of each region. 
+These regions are located in the Milky Way, the Magellanic clouds and in the M 33 and NGC 6822 galaxies.
 
-\subsection{Regions in the Milky Way and Large Magellanic Cloud}
+\subsection{Regions in the Milky Way and Magellanic Clouds}
 \label{sec:regions-milky-way}
 
-We use data from \citet{1987A&A...176..347H} of the Orion Nebula (M42) located at 440 pc \citep{2008AJ....136.1566O}.
-Its physical and kinematics properties along its stellar population are well documented in the review of \citet{2001ARA&A..39...99O}.
+Orion is a galactic HII region located at a distance of 440 pc \citep{2008AJ....136.1566O}.
 The main ionizing star is \(\theta^{1}\)Ori C (spectral type \(\sim\)O7) with fast stellar wind, and 3 B-type stars from the Trapezium cluster.
 The position of Orion near the side of the Orion Molecular Cloud (OMC-1) make it an ongoing star formation region and a example of a blister HII region \citep{arthur2016turbulence}.
+Its physical and kinematics properties along its stellar population are well documented in the review of \citet{2001ARA&A..39...99O}.
 
-A 106 cm-Cassegrain telescope at Observatorium Hoher List was used with a Fabry-Pérot interferometer having the étalon a separation of 0.5 mm. 
+We use data from \citet{1987A&A...176..347H} and \citep{arthur2016turbulence} to study of turbulence in the Orion Nebula.
+\cite{1987A&A...176..347H} observations were obtained using a 106 cm-Cassegrain telescope at Observatorium Hoher List. 
+A Fabry-Pérot interferometer was used having the étalon a separation of 0.5 mm. 
 Interferograms have been taken with different pointing directions of the telescope's optical axis in the nebula. 
-The exposures are overlapped and fall into one square of a grid with a width of 1' sentered at \(\theta^{1}\)Ori C \citep{1987A&A...176..347H}.
+The exposures are overlapped and fall into one square of a grid with a width of 1' centered at \(\theta^{1}\)Ori C.
 
-The Carina Nebula is located at a distance of 2.35$\pm$0.05 kpc \citep{2006ApJ...644.1151S}.
-Young clusters like Trumpler 14 and 16, and Collinder 228 together they form the Car OB1 association.
-This OB association has more than 60 stars earlier than B0, and several Wolf-Rayet stars.
+\citet{arthur2016turbulence} observations were initially published by \citet{2008RMxAA..44..181G}.
+The data were obtained with the echelle spectrograph attached to the 4 m telescope at Kitti Peak National Observatory.
+These observation cover 3 \(\times\) 5 arcmin\(^{2}\)of the Orion nebula and the data consist of 96, 300 arcsec North-South orientated slits at 2 arcsec intervals with a width of 0.8 arcsec.
+The velocity resolution is 8 km s\(^{-1}\).
+
+The Carina nebula is located at a distance of 2.35$\pm$0.05 kpc \citep{2006ApJ...644.1151S}.
+Young clusters like Trumpler 14 and 16, and Collinder 228 together form the Car OB1 association.
+This OB association has more than 65 stars earlier than B0, and several Wolf-Rayet stars.
 The most star is a luminous blue variable, $\eta$ Car \citep{Damiani:2016a}.
+The stellar content has lead to identify the Carina nebula as a star formation region, and as such it presents several phenomena related with young stras as (\citet{2006ApJ...644.1151S} and reference therein): evaporating protoplanetary discs, erosion of large dust pillars and the triggering of a second generation of embedded stars, Herbig-Haro objects, to mention some.
+All of these phenomena are consequence of the UV radiation and stellar winds from star clusters in the HII region.
 
-The Lagoon Nebula (M8, NGC6523) is located at a distance of 1 250 pc \citep{2005A&A...430..941P}.
-It is present on the nebula the young stellar cluster NGC6530.
+The Lagoon Nebula (M8, NGC6523) is located at a distance of 1 250 pc \citep{2005A&A...430..941P} and contains the young stellar cluster NGC6530.
 The region is illuminated by different massive stars of spectral types O and B, the hottest being 9 Sgr, type O4V \citep{Damiani:2017b}.
 Optically, the brightest part of the nebula is called 'Hourglass nebula' which surrounds and obscures the star Herschel 36, type O7 \citep{1986AJ.....91..870W}. 
+The velocity field shows several expanding shells, related to the cluster NGC 6530, the O stars 9 Sgr and Herschel 36, and the massive protostar M8East-IR.
+A blueshifted, neutral layer is also in very good agreement with predictions of champagne-flow models of blister HII regions \citep{Damiani:2017b}.
 
@@
 
-Using observations observations from \citet{Castro:2018a} (private communication) we study the Tarantula Nebula (30~Dor) in the LMC.
-At a distance of 49.9 kpc \citep{2013Natur.495...76P} is the most luminous star-forming complex in the Local Group \citep{1984ApJ...287..116K}.
-The star forming region NGC 2070 host the massive star cluster R136.
-
-NGC 2070 was observed as part of the MUSE SV (Science Verification) programme at the Very LArge Telescope (VLT). 
+Using observations from \citet{Castro:2018a} (private communication) we study the Tarantula Nebula (30 Doradus).
+This nebula us located in the LMC (Large Magellanic Cloud) at a distance of 49.9 kpc \citep{2013Natur.495...76P} and is the most luminous star-forming complex in the Local Group \citep{1984ApJ...287..116K}.
+It host the star forming region NGC 2070 that contains the massive star cluster R136.
+NGC 2070 was observed as part of the MUSE SV (Science Verification) programme at the Very Large Telescope (VLT). 
 Four overlapping fields, each with an individual field of 1' \(\times\) 1' and a pixel scale of 0.2''/pixel were observed. 
@@
 
-\begin{table*}
-\begin{center}\caption{Sumary of properties \citep{1984ApJ...287..116K} \citep{1986ApJ...300..624R}}
-\begin{tabular}{ccccccccc}\hline
-HII    &  Dist.  & Diameter & log L(H$_{\alpha}$) & SFR      &  $ \langle N_{e} \rangle_{rms}$    & M(H$^{+}$) & Filling & \(\sigma_{W}\) \\
-Region     &  [kpc] &  [pc]     &  [erg/s]            & [ ]      & [cm$^{-3}$] & [M$_{\odot}$] & Factor & [km/s] \\ \hline
-NGC 604   &   840  & 400     &    39.65     & 0.011    & 3  & 7 $\times$ 10$^{5}$ & 0.1 & 23.1 \\
-NGC 595   &   840  & 400     &    39.36     & 0.009    & 4  & 4.6 $\times$ 10$^{5}$ & & 27.1 \\
-Hubble X  &   500  & 160     &    38.6      &  0.004   &  5 & 23 000& 0.02 & 13.4 \\
-Hubble V  &   500  & 130     &    38.87     &  0.005   &  8 &    & & 14.7 \\
-30 Dor    &   50   & 98.9    &    39.76     & 0.0130   & 250&    & & 31.7 \\
-Carina    &   2.35 & 15      &    39.6      & 0.01     & 500&    & 0.05 & \\
-NGC 346   &   61.7 & 64      &    38.67     & 0.0021   & 100&    &     & \\
-Lagoon    &   1.25 & 25      &    37.47     & 0.0001   &  60& 900& 0.012 & \\
-Orion     &   0.4  & 5       &    37        & 0.000053 & 150& 50 & 0.027 & \\\hline
-\end{tabular}\label{tab:Reg}
-\end{center}
-\end{table*}
+NGC 346 is the most active star-formation region in the SMC (Small Magellanic Cloud) located at a distance of 60 kpc. 
+It has more than 30 O stars that ionize N66, the largest HII region \citep{2011ApJ...740...10D}.
+\citet{2008ApJ...688.1050G} propose an expanding H II region or bubble blown by the winds of the massive progenitor as a mechanism that shapes the recent star formation in this region in addition to the photoionizing process of the OB stars.
+This mechanism is similar to shell-like H ii regions, with a central cluster in a cavity, and with ongoing star formation triggered around their periphery.
 
@@
 
+\begin{table*}
+\begin{center}\caption{Sumary of properties \citep{1984ApJ...287..116K} \citep{1986ApJ...300..624R}}
+\begin{tabular}{ccccccccc}\hline
+HII    &  Dist.  & Diameter & log L(H$_{\alpha}$) & SFR      &  $ \langle N_{e} \rangle_{rms}$    & M(H$^{+}$) & Filling & \(\sigma_{W}\) \\
+Region     &  [kpc] &  [pc]     &  [erg/s]            & [ ]      & [cm$^{-3}$] & [M$_{\odot}$] & Factor & [km/s] \\ \hline
+NGC 604   &   840  & 400     &    39.65     & 0.011    & 3  & 7 $\times$ 10$^{5}$ & 0.1 & 23.1 \\
+NGC 595   &   840  & 400     &    39.36     & 0.009    & 4  & 4.6 $\times$ 10$^{5}$ & & 27.1 \\
+Hubble X  &   500  & 160     &    38.6      &  0.004   &  5 & 23 000& 0.02 & 13.4 \\
+Hubble V  &   500  & 130     &    38.87     &  0.005   &  8 &    & & 14.7 \\
+30 Dor    &   50   & 98.9    &    39.76     & 0.0130   & 250&    & & 31.7 \\
+Carina    &   2.35 & 15      &    39.6      & 0.01     & 500&    & 0.05 & \\
+NGC 346   &   61.7 & 64      &    38.67     & 0.0021   & 100&    &     & \\
+Lagoon    &   1.25 & 25      &    37.47     & 0.0001   &  60& 900& 0.012 & \\
+Orion     &   0.4  & 5       &    37        & 0.000053 & 150& 50 & 0.027 & \\\hline
+\end{tabular}\label{tab:Reg}
+\end{center}
+\end{table*}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-\subsection{Application to our HII regions sample}
+\subsection{Application to our HII regions sample}\label{sec:apply}
 
@@
 
+\section{Results}\label{sec:results}
+
 \subsection{Data}
 
-The Table \ref{tab:Data} shows the statistical properties of each individual sample.
-The mean, \(\mu\), and the variance, \(\sigma^{2}\), along the number of points of each sample.
-The last column shows previous publications where the data was used. 
-For the first 4 regions in Table \ref{tab:Data} the value of \(\mu\) is the observed radial velocity accounting for heliocentric correction and subtracting the corrected radial velocity value of the most luminous pixel.
+The Figure \ref{fig:hist} shows the histograms of each individual sample with the variance  \(\sigma^{2}\), along the number of points of each sample.
 
-%In appendix \ref{sec:VelMaps} we show in the Figure \ref{fig:hist} the histograms of the velocity samples of each HII region where we applied equation \ref{eq:S}.
-%The Figures \ref{fig:M604}-\ref{fig:MOrion} show the two-dimensional radial velocity map of each region.
+%\begin{table*}
+%  \begin{center}
+%    \caption{General statistical properties of the centroid velocities.} 
+%\begin{tabular}{cccc}\hline
+%HII         &$\mu$   &$\sigma^{2}$       &No. of  \\
+%Region      &[km/s]  &[km$^{2}$/s$^{2}$] &points  \\ \hline
+%NGC 604     &3.56    &54.63              &9 510    \\
+%NGC 595     &2.82    &44.13              &8 765    \\
+%Hubble V    &-1.23   &7.87               &5 832   \\
+%Hubble X    &-5.95   &12.9               &6 925   \\
+%30Dor       &265.56* &252.79             &363 059 \\
+%Carina      &-8.83   &17.89              &855     \\
+%NGC 346     &        &31.36              &112 796 \\
+%Lagoon      &-6.26   &7.53               &1 176   \\
+%Orion Large &-1.25   &10.43              &359     \\
+%Orion Small &        &9.61               &        \\ \hline
+%\end{tabular}\label{tab:Data}
+%\end{center}
+%\end{table*}
 
-\begin{table*}
-  \begin{center}
-    \caption{General statistical properties of the centroid velocities.
-      a) \citet{tanco1997}
-      b) \citet{2019arXiv191203543M}
-      c) \citet{Castro:2018a}
-      d) \citet{Damiani:2016a}
-      e) \citet{Damiani:2017b}
-      f) \citet{1987A&A...176..347H}
-      g) \citet{arthur2016turbulence}.
-    } 
-\begin{tabular}{cccccc}\hline
-HII         &$\mu$   &$\sigma^{2}$       &No. of  &\(s_0\)* & Previously \\
-Region      &[km/s]  &[km$^{2}$/s$^{2}$] &points  &[pc]     & used in:   \\ \hline
-NGC 604     &3.56    &54.63              &9 510   &1.73     &a,b         \\
-NGC 595     &2.82    &44.13              &8 765   &1.73     &-           \\
-Hubble V    &-1.23   &7.87               &5 832   &1.02     &-           \\
-Hubble X    &-5.95   &12.9               &6 925   &1.02     &-           \\
-30Dor       &265.56* &252.79             &363 059 &0.2      &c           \\
-Carina      &-8.83   &17.89              &855     &         &d           \\
-NGC 346     &        &31.36              &112 796 &         &            \\
-Lagoon      &-6.26   &7.53               &1 176   &         &e           \\
-Orion Large &-1.25   &10.43              &359     &         &f           \\
-Orion Small &        &9.61               &        &         &g            \\ \hline
-\end{tabular}\label{tab:Data}
-\end{center}
-\end{table*}
+\begin{figure*}
+\centering
+\begin{multicols}{3}
+\includegraphics[width=1.5in]{Figures/Hist/604}\par
+\includegraphics[width=1.5in]{Figures/Hist/595}\par
+\includegraphics[width=1.5in]{Figures/Hist/346}\par
+\end{multicols}
+\begin{multicols}{3}
+\includegraphics[width=1.5in]{Figures/Hist/Hubble V}\par
+\includegraphics[width=1.5in]{Figures/Hist/Hubble X}\par
+\includegraphics[width=1.5in]{Figures/Hist/30Dor}\par
+\end{multicols}
+\begin{multicols}{3}
+\includegraphics[width=1.5in]{Figures/Hist/M8}\par
+\includegraphics[width=1.5in]{Figures/Hist/Car}\par
+\includegraphics[width=1.5in]{Figures/Hist/OrionS}\par
+\end{multicols}
+\caption{Histograms of the centroid velocities of our sample of HII regions. }
+\label{fig:hist}
+\end{figure*}
 
-\section{Results}\label{sec:results}
+\subsection{HII regions structure functions}
 
@@
 
-\begin{table*}
-\begin{center}\caption{Main results.}
-\begin{tabular}{ccccccccc}\hline
-HII         &\(\sigma\) &\(r_0\)                     &\(m\)   &Reduced &\(\langle \sigma_{LOS} \rangle \) \\
-Region      &[km/s]     &[pc]                        &                           &chi-square &  [km/s]\\ \hline
-NGC 604     &7.39       &8.75\(^{+0.68}_{-0.75}\)    &1.95\(^{+0.12}_{-0.14}\)   &0.81 &16.2  \\
-NGC 595     &6.64       &8.99\(^{+0.58}_{-0.71}\)    &1.75\(^{+0.10}_{-0.10}\)   &0.47 &18.3  \\
-Hubble V    &2.80       &2.7\(^{+0.24}_{-0.14}\)     &1.62\(^{+0.11}_{-0.09}\)   &0.19 &13.4  \\ 
-Hubble X    &3.59       &3.62\(^{+0.18}_{-0.15}\)    &1.7\(^{+0.08}_{-0.09}\)    &0.13 &12.3  \\   
-30 Dor      &15.8       &2.69\(^{+0.08}_{-0.03}\)    &1.22\(^{+0.022}_{-0.007}\) &0.49 &31.7* \\
-Carina      &4.22       &0.94\(^{+0.94}_{-0.13}\)    &0.82\(^{+0.08}_{ -0.08}\)  &0.39 &22.4   \\
-NGC 346     & 5.6       &1.4\(^{+0.05}_{-0.75}\)     &1.13\(^{+0.03}_{-0.03}\)   &0.34 &  \\
-Lagoon      &2.7        &1.78\(^{+0.07}_{-0.07}\)    &1.56\(^{+0.05}_{-0.05}\)   &0.59 &13.6     \\ 
-Orion Large &3.23       &0.84\(^{+0.37}_{-0.24}\)    &0.9\(^{+0.04}_{-0.04}\)    &0.27 &6  \\
-Orion Small &3.1        & 0.062\(^{+0.003}_{-0.001}\)&1.44\(^{+0.11}_{-0.01}\)   &0.64 &6 \\\hline	  
-\end{tabular}\label{tab:Res}
-\end{center}
-\end{table*}
-
-%\begin{table*}
-%\begin{center}\caption{Main results.}
-%\begin{tabular}{ccccccccccc}\hline
-%HII    &  \(\sigma\) &   \(r_0\) &    \(m\)   &Reduced& r$_{2\sigma}$* &  \(r_{max}\)/\(r_0\)* & \(\langle \sigma_{LOS} \rangle \) & \(l_T\)* & \(Re\)*& - \\
-%Region    &  [km/s] &  [pc]    &&   chi-square     & [pc] &      &[km/s]& [pc] & &  \\ \hline
-%NGC 604   &  7.39   &  8.75\(^{+0.68}_{-0.75}\)    &   1.95\(^{+0.12}_{-0.14}\)  &0.81& 27   & 14.7 & 16.2 &  5.1 & &  \\
-%NGC 595   &  6.64   &  8.99\(^{+0.58}_{-0.71}\)    &   1.75\(^{+0.10}_{-0.10}\) &0.47& 20   & 21.4 & 18.3 & 4.4  & &  \\
-%Hubble V  &  2.80   &  2.7\(^{+0.24}_{-0.14}\)   &   1.62\(^{+0.11}_{-0.09}\)  & 0.19& 12   & 19.9 &  13.4    & 1.56 & &  \\ 
-%Hubble X  &  3.59   &  3.62\(^{+0.18}_{-0.15}\)    &   1.7\(^{+0.08}_{-0.09}\) &0.13& 15   & 22.1 &  12.3    & 1.95 & &  \\   
-%30 Dor    &  15.8    &   2.69\(^{+0.08}_{-0.03}\)    &   1.22\(^{+0.022}_{-0.007}\) &0.49& 11   & 8.9  &      & 0.69 & &  \\
-%Carina    &  4.22    &    0.94\(^{+0.94}_{-0.13}\)     &    0.82\(^{+0.08}_{ -0.08}\)   &0.39& 2    & 16.1 & 22.4  &      & &  \\
-%NGC 346   &   5.6    &  1.4\(^{+0.05}_{-0.75}\)     &    1.13\(^{+0.03}_{-0.03}\) &0.34&     &     &     &  & &  \\
-%Lagoon    &  2.7     &   1.78\(^{+0.07}_{-0.07}\)     &   1.56\(^{+0.05}_{-0.05}\) &0.59&  6   & 10.1 &  13.6    &      & &  \\ 
-%Orion Large &  3.23    &   0.84\(^{+0.37}_{-0.24}\)    &   0.9\(^{+0.04}_{-0.04}\) &0.27&  -   & 27.6 &   6  &      & &  \\
-%Orion Small &   3.1 & 0.062\(^{+0.003}_{-0.001}\)      &  1.44\(^{+0.11}_{-0.01}\)  &0.64&     &  &  6   &      &  & \\	  
-%\end{tabular}\label{tab:Res}
-%\end{center}
-%\end{table*}
-
-%\subsection{Plane of sky radial velocity dispersion \(\sigma\)}
-
 The highest \(\sigma\) is 15.8 km s\(^{-1}\) for 30Dor.
@@
 Hubble V has 2.8 km s\(^{-1}\) and last mof all sample is Lagoon with 2.7 km s\(^{-1}\).
+
+\begin{figure*}
+\centering
+\begin{multicols}{3}
+\includegraphics[width=2in]{Figures/SFplots/604.pdf}\par
+\includegraphics[width=2in]{Figures/SFplots/595.pdf}\par
+\includegraphics[width=2in]{Figures/SFplots/346.pdf}\par
+\end{multicols}
+\begin{multicols}{3}
+\includegraphics[width=2in]{Figures/SFplots/Hubble V.pdf}\par
+\includegraphics[width=2in]{Figures/SFplots/Hubble X.pdf}\par
+\includegraphics[width=2in]{Figures/SFplots/tarantula.pdf}\par
+\end{multicols}
+\begin{multicols}{3}
+\includegraphics[width=2in]{Figures/SFplots/Carina.pdf}\par
+\includegraphics[width=2in]{Figures/SFplots/M8.pdf}\par
+\includegraphics[width=2in]{Figures/SFplots/OS.pdf}\par
+\end{multicols}
+\caption{Second-order structure functions for the velocity centroid images of the \(H\alpha\) emission line investigated in this work.
+The first two rows consider extragalactic regions while the last row shows galactic regions.}
+\label{fig:SFs}
+\end{figure*}
+
+\begin{table*}
+\begin{center}\caption{Main results.
+ a) \citet{tanco1997}
+      b) \citet{2019arXiv191203543M}
+      c) \citet{Castro:2018a}
+      d) \citet{Damiani:2016a}
+      e) \citet{Damiani:2017b}
+      f) \citet{1987A&A...176..347H}
+      g) \citet{arthur2016turbulence}.}
+\begin{tabular}{ccccccccc}\hline
+HII         &\(\sigma\) &\(r_0\)                     &\(m\)    &\(\langle \sigma_{LOS} \rangle \) & Previously\\
+Region      &[km/s]     &[pc]                        &                           &  [km/s]& used in:\\ \hline
+NGC 604     &7.39       &8.75\(^{+0.68}_{-0.75}\)    &1.95\(^{+0.12}_{-0.14}\)   &16.2  &a,b \\
+NGC 595     &6.64       &8.99\(^{+0.58}_{-0.71}\)    &1.75\(^{+0.10}_{-0.10}\)   &18.3  &- \\
+Hubble V    &2.80       &2.7\(^{+0.24}_{-0.14}\)     &1.62\(^{+0.11}_{-0.09}\)   &13.4  &- \\ 
+Hubble X    &3.59       &3.62\(^{+0.18}_{-0.15}\)    &1.7\(^{+0.08}_{-0.09}\)    &12.3  &- \\   
+30 Dor      &15.8       &2.69\(^{+0.08}_{-0.03}\)    &1.22\(^{+0.022}_{-0.007}\) &31.7* &c\\
+Carina      &4.22       &0.53\(^{+0.12}_{-0.11}\)    &1.19\(^{+0.20}_{ -0.16}\)  &22.4  &d\\
+NGC 346     & 5.6       &1.4\(^{+0.05}_{-0.75}\)     &1.13\(^{+0.03}_{-0.03}\)   &10.2* &-\\
+Lagoon      &2.7        &1.78\(^{+0.07}_{-0.07}\)    &1.56\(^{+0.05}_{-0.05}\)   &13.6  &e\\ 
+Orion Large &3.23       &0.84\(^{+0.37}_{-0.24}\)    &0.9\(^{+0.04}_{-0.04}\)    &6     &f \\
+Orion Small &3.1        & 0.062\(^{+0.003}_{-0.001}\)&1.44\(^{+0.11}_{-0.01}\)   &6     &g \\\hline	  
+\end{tabular}\label{tab:Res}
+\end{center}
+\end{table*}
 
@@
 
-\subsection{Other significant scales}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Discussion}\label{sec:discussion}
+
+\subsection{Comparison with previous structure functions}
+
+In Section \ref{sec:apply} we mentioned the reduced chi-square method we are using for determining the correlation length and the index of the slope.
+Since this is the first time this method is applied to a sample of HII regions (at least for our knowledge), the results are bounded to be different from previous investigations, including the one that have the same observations as \citet{arthur2016turbulence} and \citet{2019arXiv191203543M}.
+We will focus on the interpretation of each investigation results and leave the comparison of values as second issue.
+
+A complete analysis on different emissions lines of the structure function on Orion was carried out by \citet{arthur2016turbulence} and reference therein. 
+They observed a tendency that higher ionization lines presents higher values on the magnitude dispersion and the steepness of the structure function slope. 
+This results just consider one component on the Gaussian fit. 
+The power-law index obtained by \citet{arthur2016turbulence} are \(m \sim 1.2 \pm 0.1\) for \halpha\ and [OIII] emission lines and for [SII] they found \(m \sim 0.8 \pm 0.1\). 
+The correlation length for all lines is \(\approx\) 0.05 pc. For the same \halpha\ observation we obtained a value of 1.44 and a correlation length of 0.062 pc. 
+As a comparison for the large scales \citep{1987A&A...176..347H} the value is 0.9 with a considerable agreement with previous results. 
+The change in the index could be attributed to the multiple scales of energy injection that are present in the nebula.
+
+The first attempt at characterizing turbulence in a giant extragalactic HII region, GEHR, was done by \citet{1961MNRAS.122....1F} with the 30 Doradus complex in the LMC, finding no indication of turbulent motions between scale of 10 and 100 pc.
+\citet{2019arXiv191203543M} also investigated the structure function in 30 Doradus finding on their results that the structure function is entirely flat on scales from 3 to 200 pc.
+In the context of the high-resolution observations it is possible to see why their results do not reflect the turbulent structure of the nebula; their observations cover a region where the large-scale velocity fluctuations are uncorrelated.
+There is a good agreement with the single-Gaussian fit results from \citet{2019arXiv191203543M} (Figure 15 Top on their work), while \citet{1961MNRAS.122....1F} results do not overlap with ours.
+From the previous this is the first time turbulence structure is found in 30 Doradus through the structure function.
+
+There is broad agreement in our results and previous studies considering NGC 604 from \citet{tanco1997} and \citet{2019arXiv191203543M}, and using the same TAURUS-II data.
+Despite this general agreement the interpretations in each study is different.
+\citet{tanco1997} conclude about a double regime acting on the kinetic energy spectrum.
+According to this double cascading, turbulence is being forced at scales of \(\approx\)10 pc while and energy cascade has developed down to the smallest scales and other, as an inverse cascade, extends up to scale of \(\approx\)70 pc.
+Interesting enough, \citet{tanco1997} mentioned various characteristic scale lengths, the most notorious is the \(\approx\)10 pc, a value close to our correlation length of \(\approx\)9 pc, and they interpret it as possible source on energy associated with the expansion of shocks coming from wind bubbles.
+None of the previous studies present a power-law index for the structure function to compare our results.
+\citet{2019arXiv191203543M} addresses some issues with TAURUS II data while comparing profiles between the previous instrument TAURUS I where there exist a difference between observations (see section 4.1 on their paper).
+As we agree with them in the importance of observing NGC 604 at higher spatial resolution, we have prove that a consistent method in analyzing structure function is key to obtaining trustworthy results.
+
+For our NGC 595 \halpha\ emission line results there is no correspondence in the structure function between our results and previous investigations.
+Our observations cover the brightest part of the region and have smaller resolution.
+\citet{lagrois2009multi} and \citet{lagrois2011} structure functions results does not cover scales $<$10 pc, where in our results the correlation is taking place.
+\citet{lagrois2011} used the data from \citet{lagrois2009multi} to complement the structure function analysis with the auto correlation function and filters to the velocity field to get rid of non-turbulent movements.
+Their sigma is 5.92$\pm$0.15 km/s with a correlation length is 43 pc.
+The high difference is because the consider that this happen at 2$\sigma$ (equation 13 on their paper).
+The power-law index they provide is 1.55$\pm$0.01.
+
+\subsection{Correlations between physical properties and turbulent parameters}
+
+As we mentioned in the introduction, the scaling relations between parameters like size and luminosity are common tools to study HII regions along dwarf galaxies and high-redshift star formation regions; in the past those relationships, particularly in GEHRs, made them candidates as standard candles.
+We apply these methods with the turbulent parameters \(r_0\) and index \(m\).
+
+Using the first three columns in Tables \ref{tab:Reg} and \ref{tab:Res}, we obtain the Pearson correlation coefficient $r$.
+Between luminosity (L) and \(\sigma\) it is 0.71, between distance (D) and \(m\) the value is 0.73, and finally between size (R) and \(r_0\) we have 0.96.
+By means of a significance test and assuming that a uncorrelated sample produces our results, for the first two relationships we have a probability value $p$ of 0.02 and for the remaining one of <10\(^{-5}\).
+Applying and ordinary least-square regression (OLS) we find a form Y = aX + b; this values along the previous ones is shown in Table \ref{tab:RestStats}.
+
+The relationship between L vs \(\sigma\) is one of the most studied. 
+This relationship help us understanding how the star formation affects the gas motions and how star formation is regulated by feedback processes. 
+Figure \ref{fig:sigvsl} shows different studies of the L vs \(\sigma\) relationship \citep{1988A&A...201..199A,Rozas:2006b,2015MNRAS.449.3568M}. 
+In this case it is normally used the deconvolution of the observed lines taking account thermal broadening and instrumental broadening leaving the \(\sigma_{LOS}\). 
+For the data present in Figure \ref{fig:sigvsl}, excluding \(\sigma_{POS}\), we obtain using the same OLS \(log \sigma_{LOS} = 0.145 \pm 0.008 (logL_{H\alpha}) - (4.42 \pm 0.336) \).
+Since the R-squared is 0.596 it is not possible just to invert the OLS results for a comparison with the more classical relationship.
+Inverting axes we obtain \(log L_{H\alpha} = 4.09 \pm 0.23 log (\sigma_{LOS}) + (34.17 \pm 0.32) \), being in accord to previous relationships.
+
+It is also possible to use our results from Table \ref{tab:Res} for a comparison with other relationship, in this case considering the separation \(r\).
+Using the mean slope index \(\langle m \rangle \), 1.4, we can assume \(\Delta V^{2} \propto r^{1.4} \) and obtain \(r \propto V^{1.5} \), close to what previous studies have determined.
+
+\begin{table*}
+\begin{center}\caption{Parameters of the linear regression (Y = aX + b).}
+\begin{tabular}{cccccc}\hline
+Y                    &X         &a               &b                &r     & p                \\ \hline
+log \(r_0\)          &log \(R\) &0.65\(\pm\)0.06 &-0.83\(\pm\)0.11 & 0.96 & <10\(^{-5}\)    \\ 
+log \(\sigma\)       &log \(L\) &0.16\(\pm\)0.05 &-5.54\(\pm\)2.13 & 0.71 & 0.02             \\
+log \(m\)            &log \(D\) &0.05\(\pm\)0.02 &-0.05\(\pm\)0.03 & 0.73 & 0.02  \\ 
+*log \(\sigma_{LOS}\) &log \(L\) &0.145\(\pm\)0.008 &-4.42\(\pm\)0.33 & 0.77 & <10\(^{-5}\)  \\ 
+*log \(L\) &log \(\sigma_{LOS}\) &4.09\(\pm\)0.23 &34.17\(\pm\)0.32 & 0.77 & <10\(^{-5}\)  \\ 
+log \(\sigma\)       &log \(\sigma_{LOS}\) &0.77\(\pm\)0.28 &-0.21\(\pm\)0.32 &0.72 & 0.02 \\ \hline
+\end{tabular}\label{tab:RestStats}
+\end{center}
+\end{table*}
+
+\begin{figure}
+\centering 
+\includegraphics[width=3in]{Figures/lvss.pdf}
+\caption{}
+\label{fig:sigvsl}
+\end{figure}
+
+\subsection{Relationship between plane-of-sky and line-of-sight velocity dispersion.}
+
+The analysis employed until now is not conclusive about the true velocity fluctuations observed in each nebula. 
+As pointed out by \citet{arthur2016turbulence} other techniques also allow us to study these fluctuations. 
+Following their procedure, it is possible to see from Table \ref{tab:Res} that the line-of-sight velocity dispersion is roughly twice the plane-of-sky velocity dispersion.
+In the case of homogeneous turbulent velocity we can consider the effect of 'project smearing', \citet{arthur2016turbulence} and reference therein, where the projection from three to two dimensions over a line-of-sight depth \(H\) reduces the plane-of-sky amplitude if \(r_{0} < H\).
+With a value of \(\sigma / \sigma_{LOS}\) = 0.5 we obtain \(r_{0} / H \approx\) 0.02-0.1 \citep{1984ApJ...277..556S}.
+
+%Trying to answer if the observed turbulence can account for the non-thermal line broadening can be used as a diagnostic...
+
+\begin{figure}
+\centering 
+\includegraphics[width=2in]{Figures/sigmas.pdf}
+\caption{}
+\label{fig:sigvssig}
+\end{figure}
+
+\subsection{What turbulence scales can tell us about kinematics of the ionized gas?}
 
@@
 
-Finally in te table we present the Reynolds Number...
+Finally in the table we present the Reynolds Number...
 
 \begin{table}
-\begin{center}\caption{Scales...}
+\begin{center}\caption{Other significant turbulent scales}
 \begin{tabular}{cccccc}\hline
@@
 \end{table}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Discussion}\label{sec:discussion}
-
-%\subsection{Scaling relations}
-\subsection{Correlations between physical properties and turbulent parameters}
-
-As we mentioned in the introduction, the scaling relations between parameters like size and luminosity are common tools to study HII regions along dwarf galaxies and high-redshift star formation regions; in the past those relationships, particularly in GEHRs, made them candidates as standard candles.
-We apply these methods with the turbulent parameters \(r_0\) and index \(m\).
-
-Using the first three columns in Tables \ref{tab:Reg} and \ref{tab:Res}, we obtain the Pearson correlation coefficient $r$.
-Between luminosity (L) and \(\sigma\) it is 0.71, between distance (D) and \(m\) the value is 0.73, and finally between size (R) and \(r_0\) we have 0.96.
-By means of a significance test and assuming that a uncorrelated sample produces our results, for the first two relationships we have a probability value $p$ of 0.02 and for the remaining one of 6.57 10\(^{-6}\).
-Applying and ordinary least-square regression we find a form Y = aX + b; this values laong the previous ones y shown in Table \ref{tab:RestStats}.
-
-The relationship between L vs \(\sigma\) is one of the most studied.
-This relationship help us understanding how the star formation affects the gas motions and how star formation is regulated by feedback processes.
-Figure \ref{fig:sigvsl} shows different studies of the L vs \(\sigma\) relationship.
-In this case it is normally used the deconvolution of the observed lines taking account thermal broadening and instrumental broadening leaving the \(\sigma_{LOS}\).
-
-\begin{table*}
-\begin{center}\caption{Parameters of the linear regression (Y = aX + b).}
-\begin{tabular}{cccccc}\hline
-Y               &X         &a               &b                &r     & p                \\ \hline
-log \(r_0\)     &log \(R\) &0.65\(\pm\)0.06 &-0.83\(\pm\)0.11 & 0.96 & 6.57 10\(^{-6}\)             \\ 
-log \(\sigma\)  &log \(L\) &0.16\(\pm\)0.05 &-5.54\(\pm\)2.13 & 0.71 & 0.019              \\
-log \(m\)       &log \(D\) &0.05\(\pm\)0.02 &-0.05\(\pm\)0.03 & 0.73 & 0.019  \\ 
-*log \(\sigma\)  &log \(\sigma_{LOS}\) &0.77\(\pm\)0.28 &-0.21\(\pm\)0.32 &0.72 & 0.02 \\ \hline
-\end{tabular}\label{tab:RestStats}
-\end{center}
-\end{table*}
-
-\begin{figure}
-\centering 
-\includegraphics[width=3in]{Figures/lvss.pdf}
-\caption{}
-\label{fig:sigvsl}
-\end{figure}
-
-\begin{figure}
-\centering 
-\includegraphics[width=2in]{Figures/sigmas.pdf}
-\caption{}
-\label{fig:sigvssig}
-\end{figure}
-
-%Relationship between plane-of-sky and line-of-sight velocity dispersion.
-
-\subsection{Comparison with previous structure functions}
-
-A complete analysis on different emissions lines of the structure function on Orion was carried out by \citet{arthur2016turbulence} and reference therein.
-They observed a tendency that higher ionization lines presents higher values on the magnitude dispersion and the steepness of the structure function slope.
-This results just consider one component on the Gaussian fit. 
-The power-law index obtained by \citet{arthur2016turbulence} are \(m \sim 1.2 \pm 0.1\) for \halpha\ and [OIII] emission lines and for [SII] they found \(m \sim 0.8 \pm 0.1\).
-The correlation length for all lines is \(\approx\) 0.1-0.2 pc.
-For the same \halpha\ observation we obtained a value of 1.44.
-As a comparison for the large scales \citep{1987A&A...176..347H} the value is 0.9 with a considerable agreement with previous results.
-The change in the index could be attributed to the multiple scales of energy injection that are present in the nebula.
-
-The first attempt at characterizing turbulence in a giant extragalactic HII region, GEHR, was done by \citet{1961MNRAS.122....1F} with the 30 Dor complex in the LMC, finding no indication of turbulent motions.
-\citet{2019arXiv191203543M} investigated the structure function in 30 Dor finding on their results that the structure function is entirely flat on scales from 3 to 200 pc.
-In the context of the high-resolution observations it is possible to see why their results do not reflect the turbulent structure of the nebula; their observations cover a region where the large-scale velocity fluctuations are uncorrelated.
-There is a good agreement with the results from \citet{2019arXiv191203543M} (Figure 15 Top on their work), while \citet{1961MNRAS.122....1F} results does not overlap with ours.
-
-Figure X shows similarity in our results and previous studies from \citet{tanco1997} and \citet{2019arXiv191203543M} for TAURUS-II data.
-\citep{2019arXiv191203543M} report $\sigma$ of 7.2 km/s while we have 7.3 km/s.
-Despite the agreement in observations analysis and interpretations are different.
-As mentioned by \citet{2019arXiv191203543M} some problems and inconsistencies arise in the results of \citet{tanco1997}; they don't consider a lower limit based on the observational seeing and that lead them to conclude about a double regime acting on the velocity spectrum.
-None of the previous studies present a power-law index to compare our results, but Fig. X shows that the difference lies on the structure function or lag value and no on the form of the plot.
-With this assumption we can establish the same index of 1.7 for NGC 604 TAURUS-II observations.
-
-For our NGC 595 results there is no correspondence in the structure function between our results and previous investigations.
-Our observations cover the brightest part of the region and have smaller resolution.
-\citet{lagrois2009multi} and \citet{lagrois2011} structure functions results does not cover scales $<$10 pc, where in our results the correlation is taking place.
-\citet{lagrois2011} used the data from \citet{lagrois2009multi} to complement the structure function analysis with the auto correlation function and filters to the velocity field to get rid of non-turbulent movements.
-Their sigma is 5.92$\pm$0.15 km/s as a comparison of 6.6 km/s for our data.
-There correlation length is 43 pc.
-The high difference is because the consider that this happen at 2$\sigma$ (equation 13 on their paper).
-The power-law index they provide is 1.55$\pm$0.01.
-
-\subsection{What turbulence can tell us about kinematics of the ionized gas?}
 
@@
 For the NGC 604 case, there is no clear relation between the \(r_0\) and some particular energy injection mechanism...
+%it is also the nearest analog of more extreme star-forming regions, such as 30 Doradus in the Large Magellanic Cloud.
 
@@
 
+JGV acknowledges and thanks CONACYT for the PhD research scholarship.
 We are grateful to Norberto Castro Rodríguez for providing maps of emission line velocity moments for 30 Doradus derived from MUSE-VLT observations.
@@
 
-%\begin{figure*}
-%\centering
-%\begin{multicols}{4}
-%\includegraphics[width=1.5in]{Figures/Hist/604}\par
-%\includegraphics[width=1.5in]{Figures/Hist/595.pdf}\par
-%\includegraphics[width=1.5in]{Figures/Hist/Hubble V.pdf}\par
-%\includegraphics[width=1.5in]{Figures/Hist/Hubble X.pdf}\par
-%\end{multicols}
-%\begin{multicols}{4}
-%\includegraphics[width=1.5in]{Figures/Hist/M8.pdf}\par
-%\includegraphics[width=1.5in]{Figures/Hist/Car.pdf}\par
-%\includegraphics[width=1.5in]{Figures/Hist/Orion.pdf}\par
-%\includegraphics[width=1.5in]{Figures/Hist/30Dor.pdf}\par
-%\end{multicols}
-%\caption{}
-%\label{fig:hist}
-%\end{figure*}
+%The Figures \ref{fig:M604}-\ref{fig:MOrion} show the two-dimensional radial velocity map of each region.
 
@@
 
-%\clearpage
-
-%\section{Second order structure functions}\label{sec:StructFunct}
-
-%Here we present the plots of the second order structure functions...
-
-%\begin{figure}
-%\centering 
-%\includegraphics[width=2in]{Figures/SFplots/604}
-%\caption{NGC 604 second-order structure functions for H$\alpha$ emission line from the ISIS and TAURUS instruments (Fig. \ref{}).
-%The figure also shows the structure functions presented in previous works \citep{tanco1997,2019arXiv191203543M}.
-%The green area represents the scales affected by observational seeing.
-%The vertical line indicate the value of rhe correlation length , r$_{0}$.
-%The solid horizontal line denote the value of $\sigma$.
-%The double dotted horizontal line indicates 2$\sigma$.
-%Black plots are structure functions calculated in this work and gray plots are from previous works.
-%}
-%\label{fig:SF604}
-%\end{figure}
-
-%\begin{figure}
-%\centering 
-%\includegraphics[width=2in]{Figures/SFplots/595}
-%\caption{NGC 595 second-order structure functions for H$\alpha$ emission line from the TAURUS instrument (Fig. \ref{}).
-%Same information as Figure \ref{fig:SF604}.}
-%\label{fig:SF595}
-%\end{figure}
-
-%\begin{figure}
-%\centering 
-%\includegraphics[width=2in]{Figures/SFplots/hubbleV}
-%\caption{Hubble V second-order structure functions for H$\alpha$ emission line from the TAURUS instrument \ref{}).
-%Same information as Figure \ref{fig:SF604}.}
-%\label{fig:SFV}
-%\end{figure}
-
-%\begin{figure}
-%\centering 
-%\includegraphics[width=2in]{Figures/SFplots/hubbleX.pdf}
-%\caption{Hubble X second-order structure functions for H$\alpha$ emission line from the TAURUS instrument \ref{}).
-%Same information as Figure \ref{fig:SF604}.}
-%\label{fig:SFX}
-%\end{figure}
-
-%\begin{figure}
-%\centering 
-%\includegraphics[width=2in]{Figures/SFplots/tarantula}
-%\caption{30 Dor second-order structure functions for H$\alpha$ emission line \citep{Castro:2018a}.
-%The figure also shows the structure functions presented in previous works \citep{2019arXiv191203543M}.
-%Same information as Figure \ref{fig:SF604}.}
-%\label{fig:SF30Dor}
-%\end{figure}
-
-%\begin{figure}
-%\centering 
-%\includegraphics[width=2in]{Figures/SFplots/carina}
-%\caption{Carina second-order structure functions for H$\alpha$ emission line taken from.
-%Same information as Figure \ref{fig:SF604}.}
-%\label{fig:SFCar}
-%\end{figure}
-
-%\begin{figure}
-%\centering 
-%\includegraphics[width=2in]{Figures/SFplots/M8}
-%\caption{M8 second-order structure functions for H$\alpha$ emission line \ref{}) from  \citet{Damiani:2017b} and \citet{1987A&A...176..338H}.
-%The figure also shows the structure functions presented in previous works \citep{1987ApJ...317..686O}.
-%Same information as Figure \ref{fig:SF604}.}
-%\label{fig:SFM8}
-%\end{figure}
-
-%\begin{figure}
-%\centering 
-%\includegraphics[width=2in]{Figures/SFplots/M42}
-%\caption{M42 second-order structure functions for H$\alpha$ emission line taken from \citet{1987A&A...176..347H} \ref{}).
-%he figure also shows the structure functions presented in previous works \citep{von1951methode,munch1958internal,arthur2016turbulence}.
-%Same information as Figure \ref{fig:SF604}.}
-%\label{fig:SFM42}
-%\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%% END %%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 

### 2021-09-10 mnras_template.tex
Fix fig names to remove spaces
Javier changes 1021-09-10

@@
 \begin{multicols}{3}
-\includegraphics[width=1.5in]{Figures/Hist/Hubble V}\par
-\includegraphics[width=1.5in]{Figures/Hist/Hubble X}\par
+\includegraphics[width=1.5in]{Figures/Hist/Hubble-V}\par
+\includegraphics[width=1.5in]{Figures/Hist/Hubble-X}\par
 \includegraphics[width=1.5in]{Figures/Hist/30Dor}\par
@@
 
+\subsection{Correlations between turbulent parameters}
+
+\begin{figure}
+\centering 
+\includegraphics[width=2in]{Figures/mr0.pdf}
+\caption{ }
+\label{fig:mr0}
+\end{figure}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 *log \(L\) &log \(\sigma_{LOS}\) &4.09\(\pm\)0.23 &34.17\(\pm\)0.32 & 0.77 & <10\(^{-5}\)  \\ 
-log \(\sigma\)       &log \(\sigma_{LOS}\) &0.77\(\pm\)0.28 &-0.21\(\pm\)0.32 &0.72 & 0.02 \\ \hline
+log \(\sigma\)       &log \(\sigma_{LOS}\) &0.72\(\pm\)0.27 &-0.14\(\pm\)0.31 &0.68 & 0.02 \\ \hline
 \end{tabular}\label{tab:RestStats}
@@
 \includegraphics[width=2in]{Figures/sigmas.pdf}
-\caption{}
+\caption{Log \(\sigma_{LOS}\) vs Log \(\sigma\) plot.
+The values are taken from Table \ref{tab:Res}.
+The solid-gray line indicate perfect correlation and the dotted-black line indicate the relation in Table \ref{tab:RestStats}.
+The size of the markers indicate the distance to the region, the bigger the marker the farther the region.
+}
 \label{fig:sigvssig}

### 2021-09-10 strucfunc_paper.tex
Change name of main file
Load some more latex packages

--- 2021-09-10 mnras_template.tex
@@
 
+\usepackage{savesym}
+\savesymbol{tablenum}
+\usepackage{siunitx}
+\restoresymbol{SIX}{tablenum}
+
 % MNRAS is set in Times font. If you don't have this installed (most LaTeX
@@
 \usepackage{multicol}
+
+\usepackage{xcolor}
+\hypersetup{colorlinks=True, linkcolor=blue!50!black, citecolor=black,
+  urlcolor=blue!50!black}
 
@@
 \newcommand\s{[\ion{S}{II}]$\lambda$6737}
-\newcommand\si{$\sigma$}
 \newcommand\kms{$^{-1}$}
@@
 The values are taken from Table \ref{tab:Res}.
-The solid-gray line indicate perfect correlation and the dotted-black line indicate the relation in Table \ref{tab:RestStats}.
+The solid-gray line indicate one-to-one correlation and the dotted-black line indicate the relation in Table \ref{tab:RestStats}.
 The size of the markers indicate the distance to the region, the bigger the marker the farther the region.

### 2021-09-29 strucfunc_paper.tex
Customization of hyperref and siunitx packages
Add two new figures for HII region sample and velocity maps

@@
 \usepackage{xcolor}
+
+%% Package set-up
+
+% Use more muted colors for links
 \hypersetup{colorlinks=True, linkcolor=blue!50!black, citecolor=black,
   urlcolor=blue!50!black}
+
+% Tweaks to siunitx configuration
+\sisetup{
+  % explicit""+" is useful for velocities
+  retain-explicit-plus = true,
+  % prefer 10^6 over 1 x 10^6
+  retain-unity-mantissa = false,
+  % Use x +/- e instead of x(e)  
+  separate-uncertainty = true,
+  % Make sure to pick up bold font when used in section heading for instance
+  detect-weight = true,
+}
 
@@
 \newcommand\kms{$^{-1}$}
+
+\newcommand\ha{\ensuremath{\text{H}\alpha}}
 
@@
 \section{HII regions sample}\label{sec:HIIsample}
+
+\begin{figure*}
+  \centering
+  \includegraphics[width=\linewidth]{Figures/hii-region-mosaic}
+  \caption{The sample of nine \hii{} regions used in this study.}
+  \label{fig:hii-regions}
+\end{figure*}
+
+\begin{figure*}
+  \centering
+  \includegraphics[width=\linewidth]{Figures/velocity-maps-mosaic}
+  \caption{
+    Maps of the mean \ha{} velocity for each of the regions in our sample.
+    All velocities are relative to the systemic velocity of each region,
+    with more negative velocities shown in blue and more positive velocities in red.
+    The range of velocities is different for each region, as indicated on the individual maps.
+    The correlation length of the velocity fluctuations in each region
+    is shown as the radius of a yellow circle and labeled with its value in parsecs. 
+  }
+  \label{fig:velocity-maps}
+\end{figure*}
 

### 2021-10-01 strucfunc_paper.tex
Javier changes 2021-09-30
Progress on the caption to Fig 1

@@
 \newcommand\ha{\ensuremath{\text{H}\alpha}}
+\newcommand\Wav[1]{\ensuremath{\lambda #1}}
 
@@
   \includegraphics[width=\linewidth]{Figures/hii-region-mosaic}
-  \caption{The sample of nine \hii{} regions used in this study.}
+  \caption{
+    The sample of nine \hii{} regions employed in this study,
+    arranged from top to bottom in order of distance.
+    White shapes show the approximate extents of the
+    emission line maps that we use for studying the ionized gas kinematics.
+    Scale bars show the equivalent linear length scales at the distance to each region.
+    For Orion, two fields are shown: the Extended Orion Nebula,
+    sampled at a scale of \SI{0.1}{pc}, and the central Huygens region,
+    sampled at a scale of \SI{0.004}{pc}.
+    All images are combinations of optical narrow-band and wide-band filters.
+    In most cases, red/orange/pink represents \ha{} or other emission lines
+    emitted by the ionized gas,
+    while blue/white represents continuum starlight from young high-mass stars.
+    In some cases, green (for Hubble~X and NGC~604) or blue (for NGC~595)
+    represents the [\ion{O}{3}] \Wav{5007} emission line.
+    Image credits as follows.
+    Orion Nebula:
+    \textit{HST} Treasury Program on the Orion Nebula Cluster \citep{Robberto:2013a}.
+    M8 Lagoon: R. Jay Gabany (\url{https://www.cosmotography.com/index.html}).
+    Carina: ESO/Digitized Sky Survey~2, Davide De Martin
+    (\url{https://www.eso.org/public/images/eso0905b})
+    NGC~346: NASA, ESA and A. Nota (ESA/STScI) \citep{Nota:2006x}.
+    30 Doradus: Robert Gendler, Roberto Colombari,
+    Hubble Legacy Archive, European Southern Observatories
+    (\url{http://www.robgendlerastropics.com/Tarantula-HST-ESO.html}).
+    Hubble~X:
+    Hubble~V:
+    NGC~595:
+    NGC~604:
+  }
   \label{fig:hii-regions}
@@
 \centering
-\begin{multicols}{3}
-\includegraphics[width=1.5in]{Figures/Hist/604}\par
-\includegraphics[width=1.5in]{Figures/Hist/595}\par
-\includegraphics[width=1.5in]{Figures/Hist/346}\par
-\end{multicols}
-\begin{multicols}{3}
-\includegraphics[width=1.5in]{Figures/Hist/Hubble-V}\par
-\includegraphics[width=1.5in]{Figures/Hist/Hubble-X}\par
-\includegraphics[width=1.5in]{Figures/Hist/30Dor}\par
-\end{multicols}
-\begin{multicols}{3}
-\includegraphics[width=1.5in]{Figures/Hist/M8}\par
-\includegraphics[width=1.5in]{Figures/Hist/Car}\par
-\includegraphics[width=1.5in]{Figures/Hist/OrionS}\par
-\end{multicols}
+\includegraphics[width=5in]{Figures/Hist/Hist}\par
 \caption{Histograms of the centroid velocities of our sample of HII regions. }

### 2021-10-01 strucfunc_paper.tex
Finish the caption for Figure 1
Include credits and links for all the images used

@@
 
-\section{HII regions sample}\label{sec:HIIsample}
+\section{\boldmath Sample of \hii{} regions}\label{sec:HIIsample}
 
@@
     represents the [\ion{O}{3}] \Wav{5007} emission line.
-    Image credits as follows.
-    Orion Nebula:
+    \textit{Image credits as follows.}
+    \textbf{Orion Nebula}:
     \textit{HST} Treasury Program on the Orion Nebula Cluster \citep{Robberto:2013a}.
-    M8 Lagoon: R. Jay Gabany (\url{https://www.cosmotography.com/index.html}).
-    Carina: ESO/Digitized Sky Survey~2, Davide De Martin
-    (\url{https://www.eso.org/public/images/eso0905b})
-    NGC~346: NASA, ESA and A. Nota (ESA/STScI) \citep{Nota:2006x}.
-    30 Doradus: Robert Gendler, Roberto Colombari,
-    Hubble Legacy Archive, European Southern Observatories
-    (\url{http://www.robgendlerastropics.com/Tarantula-HST-ESO.html}).
-    Hubble~X:
-    Hubble~V:
-    NGC~595:
-    NGC~604:
+    \textbf{M8 Lagoon}: \href{https://www.cosmotography.com/index.html}{R.~Jay Gabany}.
+    \textbf{Carina}: \href{https://www.eso.org/public/images/eso0905b}{
+      ESO/Digitized Sky Survey~2, Davide De Martin}.
+    \textbf{NGC~346}:
+    NASA, ESA and A. Nota (ESA/STScI) \citep{Nota:2006x}.
+    \textbf{30 Doradus}:
+    \href{http://www.robgendlerastropics.com/Tarantula-HST-ESO.html}{
+      Robert Gendler, Roberto Colombari,
+      Hubble Legacy Archive, European Southern Observatories}.
+    \textbf{Hubble~X}:
+    \href{https://hubblesite.org/contents/media/images/2001/01/1012-Image.html}
+    {C. R. O'Dell (Vanderbilt University),
+      NASA and The Hubble Heritage Team (STScI/AURA)}.
+    \textbf{Hubble~V}:
+    \href{https://hubblesite.org/contents/media/images/2001/39/1126-Image.html}
+    {C. R. O'Dell (Vanderbilt University)
+      and L. Bianchi (Johns Hopkins University and Osservatorio Astronomico, Torinese, Italy),
+      NASA, ESA, and The Hubble Heritage Team (STScI/AURA)}.
+    \textbf{NGC~595}:
+    \href{https://esahubble.org/images/heic1901c/}
+    {NASA, ESA,
+      and M. Durbin, J. Dalcanton, and B. F. Williams (University of Washington)}.
+    \textbf{NGC~604}:
+    \href{https://hubblesite.org/contents/media/images/2003/30/1423-Image.html}
+    {NASA and The Hubble Heritage Team (AURA/STScI)}.
   }

### 2021-10-13 strucfunc_paper.tex
Add figures for inner and outer observed scales

@@
 \section{Introduction}
+
 \WILL{I think it would be best to lead with a description of the dynamics of H II regions before mentioning the turbulence}.
@@
 
-%\appendix
+\appendix
+
+\section{Degradation of the structure function due to observational limitations}
+\label{sec:degr-struct-funct}
+
+\subsection{Finite box effects}
+\label{sec:finite-box-effects}
+
+\begin{figure}
+  \begin{tabular}{@{} l @{}}
+    (a)\\
+    \includegraphics[width=\linewidth]{Figures/fake-finite-box-images}
+    \\[\bigskipamount]
+    (b)\\
+    \includegraphics[width=\linewidth]{Figures/fake-finite-box-strucfunc}
+  \end{tabular}
+  \caption{Effects of finite box size on the structure function.
+    (a)~Construction of simulated turbulent velocity fields of different sizes
+    by repeated division of an initial field of size \(512 \times 512\) pixels.
+    The \(j\)th level of division yields \(N = 4^j\) fields,
+    each of linear size \(L \times L\) where \(L = 2^{9 - j}\). 
+    (b)~Resultant structure functions.
+  }
+  \label{fig:finite-box}
+\end{figure}
+
+\begin{figure}
+  \includegraphics[width=\linewidth]{Figures/fake-finite-box-effect}
+  \caption{
+    Reduction of apparent velocity variance and correlation length
+    due to finite box size.
+  }
+  \label{fig:finite-box-effect}
+\end{figure}
+
+\subsection{Effects of seeing}
+\label{sec:effects-seeing-struc}
+
+\begin{figure}
+  \begin{tabular}{@{} l @{}}
+    (a)\\
+    \includegraphics[width=\linewidth]{Figures/fake-seeing-nonp-thumbnails}\\
+    (b)\\
+    \includegraphics[width=\linewidth]{Figures/fake-seeing-nonp-reduction}
+  \end{tabular}
+  \caption{Effects of seeing on the structure function.
+    (a)~Each row shows a different simulated random velocity field on a \(256^2\) grid
+    (see text for details).
+    The left column shows the original field,
+    while the remaining columns show the effects of smoothing by a gaussian kernel
+    with RMS width \(s_0\) from 1 to 32 pixels.
+    The same color scale is used for all columns, ranging from \(-3\) to \(+3\) times
+    the standard deviation of the unsmoothed map.
+    (b)~Relative change in the second-order structure function due to the gaussian smoothing.
+    Solid lines with symbols show the average over the 4 maps of
+    \(B(r, s_0) / B(r, s_0 = 0)\) as a function of separation \(r\),
+    with a separation of \(2 s_0\) indicated by a large filled circle on each curve.
+    Dashed lines shows the empirical fit discussed in the text.
+    The dotted line shows the correlation length of the original fields,
+    while colored plus symbols show the apparent correlation length of the smoothed fields.
+  }
+  \label{fig:seeing-reduction}
+\end{figure}
 

### 2021-10-28 strucfunc_paper.tex
Use the new strucfunc figures in the paper
But I am not happy with the layout yet.

@@
 
-We use previous published observational data to measure the second-order velocity structure function for a number of nine HII regions. 
-Table \ref{tab:Reg} shows the HII regions names
-with the main physical properties of each region. 
-These regions are located in the Milky Way, the Magellanic clouds and in the M 33 and NGC 6822 galaxies.
+We use previous published observational data to measure the second-order velocity structure function for a number of nine HII regions located in the Milky Way, the Magellanic clouds and in the M 33 and NGC 6822 galaxies.
+Table \ref{tab:Reg} shows the names with the main physical properties of each region.
 
@@
 
-Orion is a galactic HII region located at a distance of 440 pc \citep{2008AJ....136.1566O}.
-The main ionizing star is \(\theta^{1}\)Ori C (spectral type \(\sim\)O7) with fast stellar wind, and 3 B-type stars from the Trapezium cluster.
-The position of Orion near the side of the Orion Molecular Cloud (OMC-1) make it an ongoing star formation region and a example of a blister HII region \citep{arthur2016turbulence}.
-Its physical and kinematics properties along its stellar population are well documented in the review of \citet{2001ARA&A..39...99O}.
+Orion (M42) is the prototype galactic HII region and one on the best objects studied in the sky.
+Located at a distance of 440 pc \citep{2008AJ....136.1566O} its main physical and kinematics properties, along its stellar population are documented in \citet{2001ARA&A..39...99O}.
+The main ionizing star is \(\theta^{1}\)Ori C (spectral type \(\sim\)O7) and with other 3 B-type stars they form the Trapezium cluster.
+The position of Orion near the side of the Orion Molecular Cloud (OMC-1) make it an ongoing star formation region and a example of a blister HII region.
+Some of these young stars are accountable for stellar jets and Herbig-Haro objects seen in the nebula \citep{arthur2016turbulence}.
 
-We use data from \citet{1987A&A...176..347H} and \citep{arthur2016turbulence} to study of turbulence in the Orion Nebula.
-\cite{1987A&A...176..347H} observations were obtained using a 106 cm-Cassegrain telescope at Observatorium Hoher List. 
-A Fabry-Pérot interferometer was used having the étalon a separation of 0.5 mm. 
-Interferograms have been taken with different pointing directions of the telescope's optical axis in the nebula. 
-The exposures are overlapped and fall into one square of a grid with a width of 1' centered at \(\theta^{1}\)Ori C.
-
-\citet{arthur2016turbulence} observations were initially published by \citet{2008RMxAA..44..181G}.
-The data were obtained with the echelle spectrograph attached to the 4 m telescope at Kitti Peak National Observatory.
-These observation cover 3 \(\times\) 5 arcmin\(^{2}\)of the Orion nebula and the data consist of 96, 300 arcsec North-South orientated slits at 2 arcsec intervals with a width of 0.8 arcsec.
-The velocity resolution is 8 km s\(^{-1}\).
-
-The Carina nebula is located at a distance of 2.35$\pm$0.05 kpc \citep{2006ApJ...644.1151S}.
+The Carina nebula is a large star-forming complex located at a distance of 2 350 pc \citep{2006ApJ...644.1151S}.
 Young clusters like Trumpler 14 and 16, and Collinder 228 together form the Car OB1 association.
@@
 The most star is a luminous blue variable, $\eta$ Car \citep{Damiani:2016a}.
-The stellar content has lead to identify the Carina nebula as a star formation region, and as such it presents several phenomena related with young stras as (\citet{2006ApJ...644.1151S} and reference therein): evaporating protoplanetary discs, erosion of large dust pillars and the triggering of a second generation of embedded stars, Herbig-Haro objects, to mention some.
-All of these phenomena are consequence of the UV radiation and stellar winds from star clusters in the HII region.
+As a star formation region,it presents several phenomena related with young stars as: evaporating protoplanetary discs, erosion of large dust pillars and the triggering of a second generation of embedded stars, Herbig-Haro objects, to mention some, \citet{2008hsf2.book..138S} and reference therein.
+An approaching and receding kinematics components are known in the nebula.
 
@@
 A blueshifted, neutral layer is also in very good agreement with predictions of champagne-flow models of blister HII regions \citep{Damiani:2017b}.
+The properties of the nebula are reviewed by \citet{2008hsf2.book..533T}.
 
-Archival data from \citet{Damiani:2016a} and \citet{Damiani:2017b} are use to study the Carina nebula and Lagoon nebula, respectively. 
-The ESO VLT/FLAMES multi-fiber spectograph was used for observations (Gaia-ESO Survey internal release \(iDR4\)) of Lagoon nebula  and Carina nebula \citep{2002Msngr.110....1P}. 
-Mainly the spectra were obtained with the Giraffe HR15N setup (\(R \sim19 000\), wavelength range 6444-6818 A) which allow to observe \halpha\ emission line. 
-The Survey targets are low-mass stars ranging down to magnitude V \(\sim\) 18.5.
+The Tarantula Nebula (30 Doradus) is a luminous star-forming region in the LMC (Large Magellanic Cloud) and is the most luminous complex in the Local Group \citep{1984ApJ...287..116K}.
+The nebula is located at a distance of 49.9 kpc \citep{2013Natur.495...76P}.
+It host the star forming region NGC 2070 that contains the massive star cluster R136. 
+The star formation rate gas increased recently, 1-3 Myr ago \citep{2016ApJ...833..154C}, and the central ionized region spans for 40 pc.
+This nebula is used as a comparison for extragalactic star-forming regions.
 
-Using observations from \citet{Castro:2018a} (private communication) we study the Tarantula Nebula (30 Doradus).
-This nebula us located in the LMC (Large Magellanic Cloud) at a distance of 49.9 kpc \citep{2013Natur.495...76P} and is the most luminous star-forming complex in the Local Group \citep{1984ApJ...287..116K}.
-It host the star forming region NGC 2070 that contains the massive star cluster R136.
-NGC 2070 was observed as part of the MUSE SV (Science Verification) programme at the Very Large Telescope (VLT). 
-Four overlapping fields, each with an individual field of 1' \(\times\) 1' and a pixel scale of 0.2''/pixel were observed. 
-The data were reduced using the MUSE pipeline based on ESOREX recipes, with final astrometric calibration using the catalogue of \citet{1999A&A...341...98S}. 
-The final spectra span 495-9366 A, with a resolving power of \(R \sim3 000\) around \halpha\  \citep{Castro:2018a}.
-
-NGC 346 is the most active star-formation region in the SMC (Small Magellanic Cloud) located at a distance of 60 kpc. 
+NGC 346 is the most active star-formation region in the SMC (Small Magellanic Cloud) located at a distance of 62 kpc \citep{2001ApJ...562..303D}. 
 It has more than 30 O stars that ionize N66, the largest HII region \citep{2011ApJ...740...10D}.
@@
 
-\subsection{Regions in M33 and NGC 6822}
-
-NGC 604 is the brightest giant HII region in the M33 galaxy visually dominated by a big loop, many shells and different size filaments.
-It is located at the distance of 840 kpc (1'' = 4.1 pc) \citep{2015KamKinematics} with a length of 400 pc.
-It has a luminosity in L$_{H_\alpha}$ = 10$^{39.42}$ erg s$^{-1}$ \citep{2002MNRAS.329..481B} and in L$_{X}$=9.3$\times$ 10$^{35}$ erg s$^{-1}$ \citep{2008ApJ...685..919T}.
-\citet{2012ApJ...761....3M} derive an average age of 4$\pm$1 Myr and a total stellar mass of 1.6$^{+1.6}_{-1.0} \times$ 10$^{5}$M$_{\odot}$ for the region.
-
-The stellar population has been identified and classified by \citet{1996ApJ...456..174H} (and references therein).
-Recently, \citet{2011MNRAS.411..235E} focused on studying the Wolf-Rayet (WR) and red super giants (RSGs) stars population.
-\citet{2012AJ....143...43F} focused on the massive young stellar objects (MYSOs).
- The average ages for the stars, was determined to be from 3 to 5 Myr \citep{1996ApJ...456..174H} and with the RSGs as an older population have an age of 12.4 $\pm$ 2.1 Myr \citep{2011MNRAS.411..235E}.
-This suggest that two episodes of star formation, at least, have taken place in the GEHR.
-\citep{1984A&A...141...49H} identified a gradient from the west to the SE of the nebula of 30 km s$^{-1}$.
-
-NGC 595 is the second brightest giant HII region in the M33 galaxy.
-The electronic temperature is 7,670 $\pm$116 K \citep{2010MNRAS.402.1635R}.
-\citet{1983A&A...119..185V} made an estimate of the total masses of HI and HII in the nebula to obtain values of M$_{HI}=$ 1.2 $\times$ 10 $^{6}$ M$_{\odot}$ and M$_{HII} =$ 4.6 $\times$ 10 $^{5}$ M$_{\odot}$, and a ionizing luminosity of the star cluster is estimated at 5 $\times$ 10$^{50}$ erg s $^{1}$.
-\citet{1996AJ....111.1128M} estimate an age of 4.5 Myrs consistent with \citet{1993AJ....105.1400D}.
-
-It has approximately 250 stars of the OB type, 13 Supergiants and 9 WR \citep{1996AJ....111.1128M}, ten WRs confirmed with spectroscopy \citet{1993AJ....105.1400D}, nine of the WN type and a WC, located near the bright core of the region.
-
-The dwarf irregular galaxy, NGC 6822, is located at a distance of 500 kpc (1'' = 2.4 pc) \citep{1996AJ....112.1928G} and the brightest HII regions are Hubble V (HV) and Hubble X (HX).
-HV has a characteristic length of 100 pc and a luminosity at its core of in L$_{H_\alpha}$ = 1 $\times$ 10$^{49}$ H$\alpha$ photons s$^{-1}$ \citep{1999PASP..111.1382O}.
-HX has a characteristic length of 140 pc and a luminosity at its core of in L$_{H_\alpha}$ = 2.4 $\times$ 10$^{49}$ H$\alpha$ photons s$^{-1}$ \citep{1999PASP..111.1382O}.
-
+The dwarf irregular galaxy, NGC 6822, is located at a distance of 500 kpc (1'' = 2.4 pc) \citep{2012A&A...540A.135S} and the brightest HII regions are Hubble V (HV) and Hubble X (HX).
+%HV has a characteristic length of 100 pc and a luminosity at its core of in L$_{H_\alpha}$ = 1 $\times$ 10$^{49}$ H$\alpha$ photons s$^{-1}$ \citep{1999PASP..111.1382O}.
+%HX has a characteristic length of 140 pc and a luminosity at its core of in L$_{H_\alpha}$ = 2.4 $\times$ 10$^{49}$ H$\alpha$ photons s$^{-1}$ \citep{1999PASP..111.1382O}.
 %Two recognized OB associations \citep{1991ApJ...379..621H,1992AJ....104.1374W} are identified within the region of HV and HX.
@@
 
-The archival data used in this work for the extragalactic giant regions was obtained with the Fabry Perot TAURUS-II instrument in the 4.2-m William Herschel Telescope (WHT) of del Roque de los Muchachos Observatory (ORM) in La Palma, Spain and was retrieved from the La Palma archive\footnote{\url{http://casu.ast.cam.ac.uk/casuadc/ingarch}}.
+%NGC 604 is the brightest giant HII region in the M33 galaxy visually dominated by a big loop, many shells and different size filaments.
+%It is located at the distance of 840 kpc (1'' = 4.1 pc) \citep{2015KamKinematics} with a length of 400 pc.
+%It has a luminosity in L$_{H_\alpha}$ = 10$^{39.42}$ erg s$^{-1}$ \citep{2002MNRAS.329..481B} and in L$_{X}$=9.3$\times$ 10$^{35}$ erg s$^{-1}$ \citep{2008ApJ...685..919T}.
+%\citet{2012ApJ...761....3M} derive an average age of 4$\pm$1 Myr and a total stellar mass of 1.6$^{+1.6}_{-1.0} \times$ 10$^{5}$M$_{\odot}$ for the region.
+%The stellar population has been identified and classified by \citet{1996ApJ...456..174H} (and references therein).
+%Recently, \citet{2011MNRAS.411..235E} focused on studying the Wolf-Rayet (WR) and red super giants (RSGs) stars population.
+%\citet{2012AJ....143...43F} focused on the massive young stellar objects (MYSOs).
+%The average ages for the stars, was determined to be from 3 to 5 Myr \citep{1996ApJ...456..174H} and with the RSGs as an older population have an age of 12.4 $\pm$ 2.1 Myr \citep{2011MNRAS.411..235E}.
+%This suggest that two episodes of star formation, at least, have taken place in the GEHR.
+%\citep{1984A&A...141...49H} identified a gradient from the west to the SE of the nebula of 30 km s$^{-1}$.
+
+%NGC 595 is the second brightest giant HII region in the M33 galaxy.
+%The electronic temperature is 7,670 $\pm$116 K \citep{2010MNRAS.402.1635R}.
+%\citet{1983A&A...119..185V} made an estimate of the total masses of HI and HII in the nebula to obtain values of M$_{HI}=$ 1.2 $\times$ 10 $^{6}$ M$_{\odot}$ and M$_{HII} =$ 4.6 $\times$ 10 $^{5}$ M$_{\odot}$, and a ionizing luminosity of the star cluster is estimated at 5 $\times$ 10$^{50}$ erg s $^{1}$.
+%\citet{1996AJ....111.1128M} estimate an age of 4.5 Myrs consistent with \citet{1993AJ....105.1400D}.
+%It has approximately 250 stars of the OB type, 13 Supergiants and 9 WR \citep{1996AJ....111.1128M}, ten WRs confirmed with spectroscopy \citet{1993AJ....105.1400D}, nine of the WN type and a WC, located near the bright core of the region.
+
+\subsection{Observations}
+
+We use data from \citet{1987A&A...176..347H} and \citet{arthur2016turbulence} to study of turbulence in the Orion Nebula.
+\cite{1987A&A...176..347H} observations were obtained using a 106 cm-Cassegrain telescope at Observatorium Hoher List. 
+A Fabry-Pérot interferometer was used with a étalon a separation of 0.5 mm. 
+Interferograms have been taken with different pointing directions of the telescope's optical axis in the nebula. 
+The exposures are overlapped and fall into one square of a grid with a width of 1' centered at \(\theta^{1}\)Ori C.
+
+\citet{arthur2016turbulence} observations were initially published by \citet{2008RMxAA..44..181G}. 
+The data was obtained with the echelle spectrograph attached to the 4 m telescope at Kitti Peak National Observatory (KPNO).
+These observation cover 3 \(\times\) 5 arcmin\(^{2}\) of the central (Huygens) part of the Orion nebula.
+The data consist of 96, North-South orientated 300 arcsec slits at 2 arcsec intervals with a width of 0.8 arcsec with a velocity resolution of 8 km s\(^{-1}\).
+
+Archival data from \citet{Damiani:2016a} and \citet{Damiani:2017b} are use to study the Carina nebula and Lagoon nebula, respectively. 
+The ESO VLT/FLAMES multi-fiber spectograph \citep{2002Msngr.110....1P} was used for these observations (Gaia-ESO Survey internal release \(iDR4\)). 
+The Survey targets are low-mass stars ranging down to magnitude V \(\sim\) 18.5.
+Mainly the spectra were obtained with the spectographs Giraffe (HR15N setup \(R \sim19 000\), wavelength range 6444-6818 \AA) and the UVES (setup 580, R \(\sim\)4700, range 4768-6830 \AA).
+
+Using observations from \citet{Castro:2018a} (private communication) we study 30 Dor.
+NGC 2070 was observed as part of the MUSE SV (Science Verification) programme at the Very Large Telescope (VLT) in August 2014, when the instrument was new. 
+Four overlapping fields, each with an individual field of 1' \(\times\) 1' and a pixel scale of 0.2''/pixel were observed with exposure times of 4 \(\times\) 10s, 4 \(\times\) 60s, and 4 \(\times\) 600s.
+The table 1 on their work summarize the propertie of each field.
+The data were reduced using the MUSE pipeline based on ESOREX recipes, with final astrometric calibration using the catalog of \citet{1999A&A...341...98S}. 
+The final spectra span 4595-9366 \AA, with a resolving power of \(R \sim3 000\) around \halpha\  \citep{Castro:2018a}.
+
+The archival data used in this work for the extragalactic giant regions, NGC 604, NGC 595, Hubble X and Hubble V was obtained with the Fabry Perot TAURUS-II instrument in the 4.2-m William Herschel Telescope (WHT) of del Roque de los Muchachos Observatory (ORM) in La Palma, Spain and was retrieved from the La Palma archive\footnote{\url{http://casu.ast.cam.ac.uk/casuadc/ingarch}}.
 \citet{sabalisck1995supersonic} mentioned the main aspects of the observations (1990 July 31).
@@
 
-%\citet{2002MNRAS.329..481B} 39.42 38.95 38.21 38.30  39.46 37.36  37.08
-
 \begin{table*}
@@
 Region     &  [kpc] &  [pc]     &  [erg/s]            & [ ]      & [cm$^{-3}$] & [M$_{\odot}$] & Factor & [km/s] \\ \hline
-NGC 604   &   840  & 400     &    39.65     & 0.011    & 3  & 7 $\times$ 10$^{5}$ & 0.1 & 23.1 \\
-NGC 595   &   840  & 400     &    39.36     & 0.009    & 4  & 4.6 $\times$ 10$^{5}$ & & 27.1 \\
-Hubble X  &   500  & 160     &    38.6      &  0.004   &  5 & 23 000& 0.02 & 13.4 \\
-Hubble V  &   500  & 130     &    38.87     &  0.005   &  8 &    & & 14.7 \\
-30 Dor    &   50   & 98.9    &    39.76     & 0.0130   & 250&    & & 31.7 \\
-Carina    &   2.35 & 15      &    39.6      & 0.01     & 500&    & 0.05 & \\
-NGC 346   &   61.7 & 64      &    38.67     & 0.0021   & 100&    &     & \\
+NGC 604 &820$\pm$30  & 400    &   39.65    & 0.011 & 3  & 7 $\times$ 10$^{5}$ & 0.1 & 23.1 \\
+NGC 595 &820$\pm$30  & 400    &   39.36    & 0.009 & 4  & 4.6 $\times$ 10$^{5}$ & & 27.1 \\
+Hubble X  &   490$\pm$40  & 160     &    38.6      &  0.004   &  5 & 23 000& 0.02 & 13.4 \\
+Hubble V  &   490$\pm$40  & 130     &    38.87     &  0.005   &  8 &    & & 14.7 \\
+30 Dor    &   49.97$\pm$0.19    & 98.9    &    39.76     & 0.0130   & 250&    & & 31.7 \\
+Carina    &   2.35$\pm$0.05  & 15      &    39.6      & 0.01     & 500&    & 0.05 & \\
+NGC 346   &   61.9$\pm$1.1 & 64      &    38.67     & 0.0021   & 100&    &     & \\
 Lagoon    &   1.25 & 25      &    37.47     & 0.0001   &  60& 900& 0.012 & \\
-Orion     &   0.4  & 5       &    37        & 0.000053 & 150& 50 & 0.027 & \\\hline
+Orion     &   0.436$\pm$0.02  & 5       &    37        & 0.000053 & 150& 50 & 0.027 & \\\hline
 \end{tabular}\label{tab:Reg}
@@
 \end{table*}
+
+%2013ApJ...773...69G M33 dist
 
@@
 
-\subsection{The second order structure function}
+%\subsection{The second order structure function}
 
-One of the fundamental properties of turbulent clouds must be spatial fluctuations in velocity and density \citep{1984ApJ...277..556S}.
-They are observed as projected spatial fluctuations in the average line-of-sight velocity and integrated column density.
-By means of describing the statistical properties of these fluctuations they can be assumed as a product of a stochastic field statistical tools.
+%One of the fundamental properties of turbulent clouds must be spatial fluctuations in velocity and density \citep{1984ApJ...277..556S}.
+%They are observed as projected spatial fluctuations in the average line-of-sight velocity and integrated column density.
+%By means of describing the statistical properties of these fluctuations they can be assumed as a product of a stochastic field statistical tools.
 
-The statistical function we use to study the velocity field of the HII regions is the second-order structure function, $B(r)$, defined as:
+%The statistical function we use to study the velocity field of the HII regions is the second-order structure function, $B(r)$, defined as:
 
-\begin{equation}\label{eq:S}
-B(\boldsymbol{r})=\dfrac{\sum[V_{r}(\boldsymbol{x}+\boldsymbol{r})-V_{r}(\boldsymbol{x}) ]^{2}}{N(\boldsymbol{r})}
-\end{equation}
+%\begin{equation}\label{eq:S}
+%B(\boldsymbol{r})=\dfrac{\sum[V_{r}(\boldsymbol{x}+\boldsymbol{r})-V_{r}(\boldsymbol{x}) ]^{2}}{N(\boldsymbol{r})}
+%\end{equation}
 
-where, $V_{r}(\boldsymbol{x})= V_{obs}(\boldsymbol{x})-\langle V_{obs}(\boldsymbol{x}) \rangle$ and N($\boldsymbol{r}$) is the number of points at each separation \(r\), called lag.
+%where, $V_{r}(\boldsymbol{x})= V_{obs}(\boldsymbol{x})-\langle V_{obs}(\boldsymbol{x}) \rangle$ and N($\boldsymbol{r}$) is the number of points at each separation \(r\), called lag.
 
-As a justification for the use of the structure function we can consider that any relation between the line width and line-of-sight depth can be interpreted in terms of a correlation between velocity spread and scale size.
-This follows if we have an optically thin spectral line where it will have a width which is related to the total radial velocity dispersion of all fluctuations sampled along the line-of-sight \citep{1984ApJ...277..556S}.
-In these sense the structure function is used as a tool to investigate the projection of a three.dimensional correlation function onto the plane of sky \citep{arthur2016turbulence}.
+%As a justification for the use of the structure function we can consider that any relation between the line width and line-of-sight depth can be interpreted in terms of a correlation between velocity spread and scale size.
+%This follows if we have an optically thin spectral line where it will have a width which is related to the total radial velocity dispersion of all fluctuations sampled along the line-of-sight \citep{1984ApJ...277..556S}.
+%In these sense the structure function is used as a tool to investigate the projection of a three.dimensional correlation function onto the plane of sky \citep{arthur2016turbulence}.
 
-We also use the functional form of the structure function:
+%We also use the functional form of the structure function:
 
-\begin{equation}\label{eq:b}
-b(r)=2[1-C(r)]\zeta+\eta
-\end{equation}
+%\begin{equation}\label{eq:b}
+%b(r)=2[1-C(r)]\zeta+\eta
+%\end{equation}
 
-where $C(r)=1/[1+(r/r_{0})^{m}]$ \citep{1984ApJ...277..556S,arthur2016turbulence}.
-The term $r_{0}$ is the correlation length of the turbulence, the value of \(r\) in pc where equation \ref{eq:S} reach the value of \(\sigma^2\), and $m$ is the index that adjust our results.
-The term $\zeta$ is a correction for small scales considering a Gaussian seeing, $s_{0}$, and has the form $tanh^{2}[(r/2s_{0})^2]$, and \(\eta\) is the observational noise. 
-In this idealized case, at scales larger than r$_{0}$ the structure function flattens as it tends towards the asymptotic value of 2$\sigma$ \citep{arthur2016turbulence}.
+%where $C(r)=1/[1+(r/r_{0})^{m}]$ \citep{1984ApJ...277..556S,arthur2016turbulence}.
+%The term $r_{0}$ is the correlation length of the turbulence, the value of \(r\) in pc where equation \ref{eq:S} reach the value of \(\sigma^2\), and $m$ is the index that adjust our results.
+%The term $\zeta$ is a correction for small scales considering a Gaussian seeing, $s_{0}$, and has the form $tanh^{2}[(r/2s_{0})^2]$, and \(\eta\) is the observational noise. 
+%In this idealized case, at scales larger than r$_{0}$ the structure function flattens as it tends towards the asymptotic value of 2$\sigma$ \citep{arthur2016turbulence}.
 
-\subsection{Application to our HII regions sample}\label{sec:apply}
+%\subsection{Application to our HII regions sample}\label{sec:apply}
 
-The results and the errors of $r_{0}$ and $m$ are obtained using equations \ref{eq:S} and \ref{eq:b} in a chi-square (\(\chi^2)\) statistic in order to do a non-linear least-squares fit of a model to our data \citep{newville_matthew_2014_11813}.
-In this way we avoid one fundamental problem in the interpretation of the structure function results.
+%The results and the errors of $r_{0}$ and $m$ are obtained using equations \ref{eq:S} and \ref{eq:b} in a chi-square (\(\chi^2)\) statistic in order to do a non-linear least-squares fit of a model to our data \citep{newville_matthew_2014_11813}.
+%In this way we avoid one fundamental problem in the interpretation of the structure function results.
 The slope in the majority of previous studies and hence, the correlation length, is obtained by eye.
-The traditional way to find it is to determine a particular range of ascending values in the structure function results. 
-If this increase in values is stopped it is commonly assumed that one particular range has been found. 
-In some cases this procedure keeps going up to large scales, giving two or more inertial regimes;this has lead to the interpretation of multiple energy injection scales.
-Since the previous described method isn't conclusive we choose the chi-square (\(\chi^2)\) statistic to present the significance of our results. 
-This way we can maintain consistency in our analysis.
+%The traditional way to find it is to determine a particular range of ascending values in the structure function results.
+%If this increase in values is stopped it is commonly assumed that one particular range has been found.
+%In some cases this procedure keeps going up to large scales, giving two or more inertial regimes;this has lead to the interpretation of multiple energy injection scales.
+%Since the previous described method isn't conclusive we choose the chi-square (\(\chi^2)\) statistic to present the significance of our results. 
+%This way we can maintain consistency in our analysis.
 
@@
 
-The Figure \ref{fig:hist} shows the histograms of each individual sample with the variance  \(\sigma^{2}\), along the number of points of each sample.
+The Figure \ref{fig:hist}....
 
@@
 
-Table \ref{tab:Res} presents the three parameters we obtain from the analysis on the fluctuations of the velocities using the second order structure function.
-The second column is the velocity dispersion \(\sigma\) of each sample of centroid velocities.
-The third column is the correlation length \(r_0\).
-The index \(m\) is shown in the forth column;
-this index is used as a reference for comparison between theory and observations.
-In the fifth column we show the reduced chi-square value obtained using a non-linear regression algorithm. 
-Finally we show the mean velocity dispersion across the line-of-sight \(\sigma_{LOS}\) with the aim to investigate how statistically homogeneous the regions are.
+Figure \ref{fig:SFs}...
+
+Table \ref{tab:Res}...
+
+%Table \ref{tab:Res} presents the three parameters we obtain from the analysis on the fluctuations of the velocities using the second order structure function.
+%The second column is the velocity dispersion \(\sigma\) of each sample of centroid velocities.
+%The third column is the correlation length \(r_0\).
+%The index \(m\) is shown in the forth column;
+%this index is used as a reference for comparison between theory and observations.
+%In the fifth column we show the reduced chi-square value obtained using a non-linear regression algorithm. 
+%Finally we show the mean velocity dispersion across the line-of-sight \(\sigma_{LOS}\) with the aim to investigate how statistically homogeneous the regions are.
 
@@
 
-The power-law fit in the structure function for the both regions in the M33 galaxy in is performed above scales of 1.7 pc.
-For NGC 604 the index is correspond to 1.95 with a correlation length of 8.75 pc. For NGC 595 the values obtained are 1.75 and 9 pc.
-For NGC 6822 regions, Hubble X and Hubble V, the $m$ index is 1.7 and 1.62, with a correlation length of 3.62 and 2.7 pc, respectively.
-The 30Dor nebula \citep{Castro:2018a} has a correlation length of 2.7 pc and an index of 1.22.
-NGC 346 correlation length is 1.4 pc and its index is 1.13.
+%The power-law fit in the structure function for the both regions in the M33 galaxy in is performed above scales of 1.7 pc.
+%For NGC 604 the index is correspond to 1.95 with a correlation length of 8.75 pc. For NGC 595 the values obtained are 1.75 and 9 pc.
+%For NGC 6822 regions, Hubble X and Hubble V, the $m$ index is 1.7 and 1.62, with a correlation length of 3.62 and 2.7 pc, respectively.
+%The 30Dor nebula \citep{Castro:2018a} has a correlation length of 2.7 pc and an index of 1.22.
+%NGC 346 correlation length is 1.4 pc and its index is 1.13.
 
-The Carina observations allow us to measure a blue shifted and a red shifted layer \citet{Damiani:2016a}.
+%The Carina observations allow us to measure a blue shifted and a red shifted layer \citet{Damiani:2016a}.
 It is possible to combine the moments from the sum of two components \citep{2008RMxAA..44..181G}, we use this combined sample for the structure function analysis.
-Carina has an index of 0.82 with a correlation length of 0.94 pc.
-The galactic region Lagoon nebula \citep{Damiani:2017b} presents a correlation length of 1.78 pc and a index of 1.56.
+%Carina has an index of 0.82 with a correlation length of 0.94 pc.
+%The galactic region Lagoon nebula \citep{Damiani:2017b} presents a correlation length of 1.78 pc and a index of 1.56.
 
-For Orion we have the opportunity to study two different observations.
+%For Orion we have the opportunity to study two different observations.
 \citet{1987A&A...176..347H} observations allow us to study the large scale of the nebula, covering 4 pc, while \cite{arthur2016turbulence} allow us to study the small scales up to 0.4 pc.
@@
 
-The highest \(\sigma\) is 15.8 km s\(^{-1}\) for 30Dor.
-This is two times higher than NGC 604 that has a value of 7.4 km s\(^{-1}\), followed by NGC 595 with 6.64 km s\(^{-1}\).
-NGC 346 is next with a value of 5.6 km s\(^{-1}\), followed by Carina with 4.22 km s\(^{-1}\).
-Hubble X and M42 have a value of 3.59 and 3.23 km s\(^{-1}\), respectively.
-Hubble V has 2.8 km s\(^{-1}\) and last mof all sample is Lagoon with 2.7 km s\(^{-1}\).
+%The highest \(\sigma\) is 15.8 km s\(^{-1}\) for 30Dor.
+%This is two times higher than NGC 604 that has a value of 7.4 km s\(^{-1}\), followed by NGC 595 with 6.64 km s\(^{-1}\).
+%NGC 346 is next with a value of 5.6 km s\(^{-1}\), followed by Carina with 4.22 km s\(^{-1}\).
+%Hubble X and M42 have a value of 3.59 and 3.23 km s\(^{-1}\), respectively.
+%Hubble V has 2.8 km s\(^{-1}\) and last mof all sample is Lagoon with 2.7 km s\(^{-1}\).
 
@@
   \centering
-\begin{multicols}{3}
-\includegraphics[width=2in]{Figures/SFplots/604.pdf}\par
-\includegraphics[width=2in]{Figures/SFplots/595.pdf}\par
-\includegraphics[width=2in]{Figures/SFplots/346.pdf}\par
-\end{multicols}
-\begin{multicols}{3}
-\includegraphics[width=2in]{Figures/SFplots/Hubble V.pdf}\par
-\includegraphics[width=2in]{Figures/SFplots/Hubble X.pdf}\par
-\includegraphics[width=2in]{Figures/SFplots/tarantula.pdf}\par
-\end{multicols}
-\begin{multicols}{3}
-\includegraphics[width=2in]{Figures/SFplots/Carina.pdf}\par
-\includegraphics[width=2in]{Figures/SFplots/M8.pdf}\par
-\includegraphics[width=2in]{Figures/SFplots/OS.pdf}\par
-\end{multicols}
-\caption{Second-order structure functions for the velocity centroid images of the \(H\alpha\) emission line investigated in this work.
+  \includegraphics[width=0.8\linewidth]{Figures/strucfunc-fit-A}
+  \label{fig:strucfunc-fit-A}
+  \caption{Second-order structure functions for the velocity centroid images of the \(H\alpha\) emission line}
+\end{figure*}
+
+\begin{figure*}
+  \centering
+  \includegraphics[width=0.8\linewidth]{Figures/strucfunc-fit-B}
+  \label{fig:strucfunc-fit-B}
+  \caption{Second-order structure functions for the velocity centroid images of the \(H\alpha\) emission line}
+\end{figure*}
+
+\begin{figure*}
+  \centering
+  \includegraphics[width=0.8\linewidth]{Figures/strucfunc-fit-C}
+  \label{fig:strucfunc-fit-C}
+  \caption{Second-order structure functions for the velocity centroid images of the \(H\alpha\) emission line}
+\end{figure*}
+
+% \begin{figure*}
+% \centering
+% \begin{multicols}{3}
+% \includegraphics[width=2in]{Figures/SFplots/604.pdf}\par
+% \includegraphics[width=2in]{Figures/SFplots/595.pdf}\par
+% \includegraphics[width=2in]{Figures/SFplots/346.pdf}\par
+% \end{multicols}
+% \begin{multicols}{3}
+% \includegraphics[width=2in]{Figures/SFplots/Hubble V.pdf}\par
+% \includegraphics[width=2in]{Figures/SFplots/Hubble X.pdf}\par
+% \includegraphics[width=2in]{Figures/SFplots/tarantula.pdf}\par
+% \end{multicols}
+% \begin{multicols}{3}
+% \includegraphics[width=2in]{Figures/SFplots/Carina.pdf}\par
+% \includegraphics[width=2in]{Figures/SFplots/M8.pdf}\par
+% \includegraphics[width=2in]{Figures/SFplots/OS.pdf}\par
+% \end{multicols}
+% \caption{Second-order structure functions for the velocity centroid images of the \(H\alpha\) emission line investigated in this work.
 The first two rows consider extragalactic regions while the last row shows galactic regions.}
-\label{fig:SFs}
-\end{figure*}
+% \label{fig:SFs}
+% \end{figure*}
 
@@
  \begin{tabular}{ccccccccc}\hline
-HII         &\(\sigma\) &\(r_0\)                     &\(m\)    &\(\langle \sigma_{LOS} \rangle \) & Previously\\
-Region      &[km/s]     &[pc]                        &                           &  [km/s]& used in:\\ \hline
-NGC 604     &7.39       &8.75\(^{+0.68}_{-0.75}\)    &1.95\(^{+0.12}_{-0.14}\)   &16.2  &a,b \\
-NGC 595     &6.64       &8.99\(^{+0.58}_{-0.71}\)    &1.75\(^{+0.10}_{-0.10}\)   &18.3  &- \\
-Hubble V    &2.80       &2.7\(^{+0.24}_{-0.14}\)     &1.62\(^{+0.11}_{-0.09}\)   &13.4  &- \\ 
-Hubble X    &3.59       &3.62\(^{+0.18}_{-0.15}\)    &1.7\(^{+0.08}_{-0.09}\)    &12.3  &- \\   
-30 Dor      &15.8       &2.69\(^{+0.08}_{-0.03}\)    &1.22\(^{+0.022}_{-0.007}\) &31.7* &c\\
-Carina      &4.22       &0.53\(^{+0.12}_{-0.11}\)    &1.19\(^{+0.20}_{ -0.16}\)  &22.4  &d\\
-NGC 346     & 5.6       &1.4\(^{+0.05}_{-0.75}\)     &1.13\(^{+0.03}_{-0.03}\)   &10.2* &-\\
-Lagoon      &2.7        &1.78\(^{+0.07}_{-0.07}\)    &1.56\(^{+0.05}_{-0.05}\)   &13.6  &e\\ 
-Orion Large &3.23       &0.84\(^{+0.37}_{-0.24}\)    &0.9\(^{+0.04}_{-0.04}\)    &6     &f \\
-Orion Small &3.1        & 0.062\(^{+0.003}_{-0.001}\)&1.44\(^{+0.11}_{-0.01}\)   &6     &g \\\hline	  
+ HII         &\(\sigma^{2}\) &\(r_0\)                     &\(m\)    &\(\langle \sigma_{LOS} \rangle \) & Previously\\
+ Region      &[km/s]$^{2}$     &[pc]                        &                           &  [km/s]& used in:\\ \hline
+ NGC 604     &      &8.75\(^{+0.68}_{-0.75}\)    &1.95\(^{+0.12}_{-0.14}\)   &16.2  &a,b \\
+ NGC 595     &       &8.99\(^{+0.58}_{-0.71}\)    &1.75\(^{+0.10}_{-0.10}\)   &18.3  &- \\
+ Hubble V    &      &2.7\(^{+0.24}_{-0.14}\)     &1.62\(^{+0.11}_{-0.09}\)   &13.4  &- \\ 
+ Hubble X    &       &3.62\(^{+0.18}_{-0.15}\)    &1.7\(^{+0.08}_{-0.09}\)    &12.3  &- \\   
+ 30 Dor      &        &2.69\(^{+0.08}_{-0.03}\)    &1.22\(^{+0.022}_{-0.007}\) &31.7* &c\\
+ Carina      &        &0.53\(^{+0.12}_{-0.11}\)    &1.19\(^{+0.20}_{ -0.16}\)  &22.4  &d\\
+ NGC 346     &        &1.4\(^{+0.05}_{-0.75}\)     &1.13\(^{+0.03}_{-0.03}\)   &10.2* &-\\
+ Lagoon      &        &1.78\(^{+0.07}_{-0.07}\)    &1.56\(^{+0.05}_{-0.05}\)   &13.6  &e\\ 
+ Orion Large &        &0.84\(^{+0.37}_{-0.24}\)    &0.9\(^{+0.04}_{-0.04}\)    &6     &f \\
+ Orion Small &        & 0.062\(^{+0.003}_{-0.001}\)&1.44\(^{+0.11}_{-0.01}\)   &6     &g \\\hline	  
  \end{tabular}\label{tab:Res}
@@
 
-\subsection{Structure function power indices \(m\)}
+%\subsection{Structure function power indices \(m\)}
 
-It is possible that the index \(m\) is biased to \(m>\)1.6 for the extragalactic regions and \(m<\)1.5 for nearby regions.
-This could be attributed to a data quality issues because the inability to resolve distant regions in the same way we do with nearby objects.
-Since we are not observing all the inertial range on distant regions the \(m\) parameter  should be taken with some caution.
+%It is possible that the index \(m\) is biased to \(m>\)1.6 for the extragalactic regions and \(m<\)1.5 for nearby regions.
+%This could be attributed to a data quality issues because the inability to resolve distant regions in the same way we do with nearby objects.
+%Since we are not observing all the inertial range on distant regions the \(m\) parameter  should be taken with some caution.
 
-We can compute the $m_{3D}$ index from the two dimensional \(m\), if we assume that the $m_{3D}$ index lies between the limits of projection smoothing and a sheet-like distribution. 
-For our observations we have 0.82 $<$ m$_{3D}$ $<$ 1.95.
-This is done following the procedure by \cite{arthur2016turbulence} assuming the relationship m$_{2D}$ - 1 $<$ m$_{3D}$ $<$ m$_{2D}$.
-This give us a considerable large range of 1. 
-Though \cite{arthur2016turbulence} are comparing emission lines and not regions we can conclude that the index \(m\) still is far away as a unique parameter for measuring turbulence and that the three-dimensional behavior would probably encompass a wide range of indices as seen in the two-dimensional observations.
+%We can compute the $m_{3D}$ index from the two dimensional \(m\), if we assume that the $m_{3D}$ index lies between the limits of projection smoothing and a sheet-like distribution. 
+%For our observations we have 0.82 $<$ m$_{3D}$ $<$ 1.95.
+%This is done following the procedure by \cite{arthur2016turbulence} assuming the relationship m$_{2D}$ - 1 $<$ m$_{3D}$ $<$ m$_{2D}$.
+%This give us a considerable large range of 1. 
+%Though \cite{arthur2016turbulence} are comparing emission lines and not regions we can conclude that the index \(m\) still is far away as a unique parameter for measuring turbulence and that the three-dimensional behavior would probably encompass a wide range of indices as seen in the two-dimensional observations.
 
-\subsection{Significance on the length scale \(r_0\)}
+%\subsection{Significance on the length scale \(r_0\)}
 
-Ideally the correlation length \(r_0\), should represent the scale of dominant energy injection. 
-Since it is unclear what are the mechanisms driving the turbulence, thought a lot of options are candidates, it is difficult to pinpoint one particular as main responsible. 
-The possibility that the correlation length reveals the answer to the cause of observed motions is a long shot, but it is clear that each velocity field has a corresponding \(r_0\) value. 
-The range covered in our results goes from 0.06 to 9 pc, a small range in comparison with the two order magnitude difference in size and luminosity.
+%Ideally the correlation length \(r_0\), should represent the scale of dominant energy injection. 
+%Since it is unclear what are the mechanisms driving the turbulence, thought a lot of options are candidates, it is difficult to pinpoint one particular as main responsible. 
+%The possibility that the correlation length reveals the answer to the cause of observed motions is a long shot, but it is clear that each velocity field has a corresponding \(r_0\) value. 
+%The range covered in our results goes from 0.06 to 9 pc, a small range in comparison with the two order magnitude difference in size and luminosity.
 
 \subsection{Correlations between turbulent parameters}
+
+Figure \ref{fig:mr0}
 
@@
 
-In Section \ref{sec:apply} we mentioned the reduced chi-square method we are using for determining the correlation length and the index of the slope.
+%In Section \ref{sec:apply} we mentioned the reduced chi-square method we are using for determining the correlation length and the index of the slope.
 Since this is the first time this method is applied to a sample of HII regions (at least for our knowledge), the results are bounded to be different from previous investigations, including the one that have the same observations as \citet{arthur2016turbulence} and \citet{2019arXiv191203543M}.
@@
 
-A complete analysis on different emissions lines of the structure function on Orion was carried out by \citet{arthur2016turbulence} and reference therein. 
-They observed a tendency that higher ionization lines presents higher values on the magnitude dispersion and the steepness of the structure function slope. 
-This results just consider one component on the Gaussian fit. 
-The power-law index obtained by \citet{arthur2016turbulence} are \(m \sim 1.2 \pm 0.1\) for \halpha\ and [OIII] emission lines and for [SII] they found \(m \sim 0.8 \pm 0.1\). 
-The correlation length for all lines is \(\approx\) 0.05 pc. For the same \halpha\ observation we obtained a value of 1.44 and a correlation length of 0.062 pc. 
-As a comparison for the large scales \citep{1987A&A...176..347H} the value is 0.9 with a considerable agreement with previous results. 
-The change in the index could be attributed to the multiple scales of energy injection that are present in the nebula.
+%A complete analysis on different emissions lines of the structure function on Orion was carried out by \citet{arthur2016turbulence} and reference therein. 
+%They observed a tendency that higher ionization lines presents higher values on the magnitude dispersion and the steepness of the structure function slope. 
+%This results just consider one component on the Gaussian fit. 
+%The power-law index obtained by \citet{arthur2016turbulence} are \(m \sim 1.2 \pm 0.1\) for \halpha\ and [OIII] emission lines and for [SII] they found \(m \sim 0.8 \pm 0.1\). 
+%The correlation length for all lines is \(\approx\) 0.05 pc. For the same \halpha\ observation we obtained a value of 1.44 and a correlation length of 0.062 pc. 
+%As a comparison for the large scales \citep{1987A&A...176..347H} the value is 0.9 with a considerable agreement with previous results. 
+%The change in the index could be attributed to the multiple scales of energy injection that are present in the nebula.
 
-The first attempt at characterizing turbulence in a giant extragalactic HII region, GEHR, was done by \citet{1961MNRAS.122....1F} with the 30 Doradus complex in the LMC, finding no indication of turbulent motions between scale of 10 and 100 pc.
-\citet{2019arXiv191203543M} also investigated the structure function in 30 Doradus finding on their results that the structure function is entirely flat on scales from 3 to 200 pc.
-In the context of the high-resolution observations it is possible to see why their results do not reflect the turbulent structure of the nebula; their observations cover a region where the large-scale velocity fluctuations are uncorrelated.
-There is a good agreement with the single-Gaussian fit results from \citet{2019arXiv191203543M} (Figure 15 Top on their work), while \citet{1961MNRAS.122....1F} results do not overlap with ours.
-From the previous this is the first time turbulence structure is found in 30 Doradus through the structure function.
+%The first attempt at characterizing turbulence in a giant extragalactic HII region, GEHR, was done by \citet{1961MNRAS.122....1F} with the 30 Doradus complex in the LMC, finding no indication of turbulent motions between scale of 10 and 100 pc.
+%\citet{2019arXiv191203543M} also investigated the structure function in 30 Doradus finding on their results that the structure function is entirely flat on scales from 3 to 200 pc.
+%In the context of the high-resolution observations it is possible to see why their results do not reflect the turbulent structure of the nebula; their observations cover a region where the large-scale velocity fluctuations are uncorrelated.
+%There is a good agreement with the single-Gaussian fit results from \citet{2019arXiv191203543M} (Figure 15 Top on their work), while \citet{1961MNRAS.122....1F} results do not overlap with ours.
+%From the previous this is the first time turbulence structure is found in 30 Doradus through the structure function.
 
-There is broad agreement in our results and previous studies considering NGC 604 from \citet{tanco1997} and \citet{2019arXiv191203543M}, and using the same TAURUS-II data.
-Despite this general agreement the interpretations in each study is different.
-\citet{tanco1997} conclude about a double regime acting on the kinetic energy spectrum.
-According to this double cascading, turbulence is being forced at scales of \(\approx\)10 pc while and energy cascade has developed down to the smallest scales and other, as an inverse cascade, extends up to scale of \(\approx\)70 pc.
-Interesting enough, \citet{tanco1997} mentioned various characteristic scale lengths, the most notorious is the \(\approx\)10 pc, a value close to our correlation length of \(\approx\)9 pc, and they interpret it as possible source on energy associated with the expansion of shocks coming from wind bubbles.
-None of the previous studies present a power-law index for the structure function to compare our results.
-\citet{2019arXiv191203543M} addresses some issues with TAURUS II data while comparing profiles between the previous instrument TAURUS I where there exist a difference between observations (see section 4.1 on their paper).
-As we agree with them in the importance of observing NGC 604 at higher spatial resolution, we have prove that a consistent method in analyzing structure function is key to obtaining trustworthy results.
+%There is broad agreement in our results and previous studies considering NGC 604 from \citet{tanco1997} and \citet{2019arXiv191203543M}, and using the same TAURUS-II data.
+%Despite this general agreement the interpretations in each study is different.
+%\citet{tanco1997} conclude about a double regime acting on the kinetic energy spectrum.
+%According to this double cascading, turbulence is being forced at scales of \(\approx\)10 pc while and energy cascade has developed down to the smallest scales and other, as an inverse cascade, extends up to scale of \(\approx\)70 pc.
+%Interesting enough, \citet{tanco1997} mentioned various characteristic scale lengths, the most notorious is the \(\approx\)10 pc, a value close to our correlation length of \(\approx\)9 pc, and they interpret it as possible source on energy associated with the expansion of shocks coming from wind bubbles.
+%None of the previous studies present a power-law index for the structure function to compare our results.
+%\citet{2019arXiv191203543M} addresses some issues with TAURUS II data while comparing profiles between the previous instrument TAURUS I where there exist a difference between observations (see section 4.1 on their paper).
+%As we agree with them in the importance of observing NGC 604 at higher spatial resolution, we have prove that a consistent method in analyzing structure function is key to obtaining trustworthy results.
 
-For our NGC 595 \halpha\ emission line results there is no correspondence in the structure function between our results and previous investigations.
-Our observations cover the brightest part of the region and have smaller resolution.
-\citet{lagrois2009multi} and \citet{lagrois2011} structure functions results does not cover scales $<$10 pc, where in our results the correlation is taking place.
-\citet{lagrois2011} used the data from \citet{lagrois2009multi} to complement the structure function analysis with the auto correlation function and filters to the velocity field to get rid of non-turbulent movements.
-Their sigma is 5.92$\pm$0.15 km/s with a correlation length is 43 pc.
-The high difference is because the consider that this happen at 2$\sigma$ (equation 13 on their paper).
-The power-law index they provide is 1.55$\pm$0.01.
+%For our NGC 595 \halpha\ emission line results there is no correspondence in the structure function between our results and previous investigations.
+%Our observations cover the brightest part of the region and have smaller resolution.
+%\citet{lagrois2009multi} and \citet{lagrois2011} structure functions results does not cover scales $<$10 pc, where in our results the correlation is taking place.
+%\citet{lagrois2011} used the data from \citet{lagrois2009multi} to complement the structure function analysis with the auto correlation function and filters to the velocity field to get rid of non-turbulent movements.
+%Their sigma is 5.92$\pm$0.15 km/s with a correlation length is 43 pc.
+%The high difference is because the consider that this happen at 2$\sigma$ (equation 13 on their paper).
+%The power-law index they provide is 1.55$\pm$0.01.
 
@@
 
-As we mentioned in the introduction, the scaling relations between parameters like size and luminosity are common tools to study HII regions along dwarf galaxies and high-redshift star formation regions; in the past those relationships, particularly in GEHRs, made them candidates as standard candles.
-We apply these methods with the turbulent parameters \(r_0\) and index \(m\).
+Table \ref{tab:RestStats}...
 
-Using the first three columns in Tables \ref{tab:Reg} and \ref{tab:Res}, we obtain the Pearson correlation coefficient $r$.
+Figure \ref{fig:sigvsl}...
+
+Figure \ref{fig:sigvssig}...
+
+%As we mentioned in the introduction, the scaling relations between parameters like size and luminosity are common tools to study HII regions along dwarf galaxies and high-redshift star formation regions; in the past those relationships, particularly in GEHRs, made them candidates as standard candles.
+%We apply these methods with the turbulent parameters \(r_0\) and index \(m\).
+
+%Using the first three columns in Tables \ref{tab:Reg} and \ref{tab:Res}, we obtain the Pearson correlation coefficient $r$.
 Between luminosity (L) and \(\sigma\) it is 0.71, between distance (D) and \(m\) the value is 0.73, and finally between size (R) and \(r_0\) we have 0.96.
-By means of a significance test and assuming that a uncorrelated sample produces our results, for the first two relationships we have a probability value $p$ of 0.02 and for the remaining one of <10\(^{-5}\).
-Applying and ordinary least-square regression (OLS) we find a form Y = aX + b; this values along the previous ones is shown in Table \ref{tab:RestStats}.
+%By means of a significance test and assuming that a uncorrelated sample produces our results, for the first two relationships we have a probability value $p$ of 0.02 and for the remaining one of <10\(^{-5}\).
+%Applying and ordinary least-square regression (OLS) we find a form Y = aX + b; this values along the previous ones is shown in Table \ref{tab:RestStats}.
 
-The relationship between L vs \(\sigma\) is one of the most studied. 
-This relationship help us understanding how the star formation affects the gas motions and how star formation is regulated by feedback processes. 
-Figure \ref{fig:sigvsl} shows different studies of the L vs \(\sigma\) relationship \citep{1988A&A...201..199A,Rozas:2006b,2015MNRAS.449.3568M}. 
-In this case it is normally used the deconvolution of the observed lines taking account thermal broadening and instrumental broadening leaving the \(\sigma_{LOS}\). 
-For the data present in Figure \ref{fig:sigvsl}, excluding \(\sigma_{POS}\), we obtain using the same OLS \(log \sigma_{LOS} = 0.145 \pm 0.008 (logL_{H\alpha}) - (4.42 \pm 0.336) \).
-Since the R-squared is 0.596 it is not possible just to invert the OLS results for a comparison with the more classical relationship.
-Inverting axes we obtain \(log L_{H\alpha} = 4.09 \pm 0.23 log (\sigma_{LOS}) + (34.17 \pm 0.32) \), being in accord to previous relationships.
+%The relationship between L vs \(\sigma\) is one of the most studied. 
+%This relationship help us understanding how the star formation affects the gas motions and how star formation is regulated by feedback processes. 
+%Figure \ref{fig:sigvsl} shows different studies of the L vs \(\sigma\) relationship \citep{1988A&A...201..199A,Rozas:2006b,2015MNRAS.449.3568M}. 
+%In this case it is normally used the deconvolution of the observed lines taking account thermal broadening and instrumental broadening leaving the \(\sigma_{LOS}\). 
+%For the data present in Figure \ref{fig:sigvsl}, excluding \(\sigma_{POS}\), we obtain using the same OLS \(log \sigma_{LOS} = 0.145 \pm 0.008 (logL_{H\alpha}) - (4.42 \pm 0.336) \).
+%Since the R-squared is 0.596 it is not possible just to invert the OLS results for a comparison with the more classical relationship. 
+%Inverting axes we obtain \(log L_{H\alpha} = 4.09 \pm 0.23 log (\sigma_{LOS}) + (34.17 \pm 0.32) \), being in accord to previous relationships.
 
-It is also possible to use our results from Table \ref{tab:Res} for a comparison with other relationship, in this case considering the separation \(r\).
-Using the mean slope index \(\langle m \rangle \), 1.4, we can assume \(\Delta V^{2} \propto r^{1.4} \) and obtain \(r \propto V^{1.5} \), close to what previous studies have determined.
+%It is also possible to use our results from Table \ref{tab:Res} for a comparison with other relationship, in this case considering the separation \(r\).
+%Using the mean slope index \(\langle m \rangle \), 1.4, we can assume \(\Delta V^{2} \propto r^{1.4} \) and obtain \(r \propto V^{1.5} \), close to what previous studies have determined.
 
@@
 
-The analysis employed until now is not conclusive about the true velocity fluctuations observed in each nebula. 
-As pointed out by \citet{arthur2016turbulence} other techniques also allow us to study these fluctuations. 
-Following their procedure, it is possible to see from Table \ref{tab:Res} that the line-of-sight velocity dispersion is roughly twice the plane-of-sky velocity dispersion.
-In the case of homogeneous turbulent velocity we can consider the effect of 'project smearing', \citet{arthur2016turbulence} and reference therein, where the projection from three to two dimensions over a line-of-sight depth \(H\) reduces the plane-of-sky amplitude if \(r_{0} < H\).
-With a value of \(\sigma / \sigma_{LOS}\) = 0.5 we obtain \(r_{0} / H \approx\) 0.02-0.1 \citep{1984ApJ...277..556S}.
+%The analysis employed until now is not conclusive about the true velocity fluctuations observed in each nebula. 
+%As pointed out by \citet{arthur2016turbulence} other techniques also allow us to study these fluctuations. 
+%Following their procedure, it is possible to see from Table \ref{tab:Res} that the line-of-sight velocity dispersion is roughly twice the plane-of-sky velocity dispersion.
+%In the case of homogeneous turbulent velocity we can consider the effect of 'project smearing', \citet{arthur2016turbulence} and reference therein, where the projection from three to two dimensions over a line-of-sight depth \(H\) reduces the plane-of-sky amplitude if \(r_{0} < H\).
+%With a value of \(\sigma / \sigma_{LOS}\) = 0.5 we obtain \(r_{0} / H \approx\) 0.02-0.1 \citep{1984ApJ...277..556S}.
 
@@
 
-\subsection{What turbulence scales can tell us about kinematics of the ionized gas?}
+%\subsection{What turbulence scales can tell us about kinematics of the ionized gas?}
 
-In the Table \ref{tab:ResII} the second column show the separation where the value 2\(\sigma\) is reached.
-We also show the ratio \(r_{max}/r_{0}\), where \(r_{max}\) is the maximum separation or lag in pc; this value is related to the size of each sample box. 
-The forth column shows the Taylor scale, \(l_T\), which measures the average spatial extent of velocity gradients. \citet{1999ApJ...524..895M} define this scale as:
+%In the Table \ref{tab:ResII} the second column show the separation where the value 2\(\sigma\) is reached.
+%We also show the ratio \(r_{max}/r_{0}\), where \(r_{max}\) is the maximum separation or lag in pc; this value is related to the size of each sample box. 
+%The forth column shows the Taylor scale, \(l_T\), which measures the average spatial extent of velocity gradients. \citet{1999ApJ...524..895M} define this scale as:
 
-\begin{equation}\label{eq:TS}
-l_T=\dfrac{\sigma r_s}{\sigma_{r_s}}
-\end{equation}
+%\begin{equation}\label{eq:TS}
+%l_T=\dfrac{\sigma r_s}{\sigma_{r_s}}
+%\end{equation}
 
-where \(r_s\) is the smallest separation \(r\) and \(\sigma_{r_s}\) the value of the structure function at that separation.
+%where \(r_s\) is the smallest separation \(r\) and \(\sigma_{r_s}\) the value of the structure function at that separation.
 
-It is possible to calculate how this Taylor micro-scale is related to the correlation length by:
+%It is possible to calculate how this Taylor micro-scale is related to the correlation length by:
 
-\begin{equation}\label{eq:TS1}
-l_T=\dfrac{r_s}{\sqrt{2}}(\dfrac{r_0}{r_s})^{m/2}
-\end{equation}
+%\begin{equation}\label{eq:TS1}
+%l_T=\dfrac{r_s}{\sqrt{2}}(\dfrac{r_0}{r_s})^{m/2}
+%\end{equation}
 
-Finally in the table we present the Reynolds Number...
+%Finally in the table we present the Reynolds Number...
 
@@
 
-With the aim to relate each \(r_0\) with each region we invoke previous studies on the kinematics of the ionized gas. 
-\citet{sabalisck1995supersonic} studied NGC 604 revealing that the kinematics of the region behave different considering different scales.
-High emission knots on the region encompasses supersonic global velocity dispersion values of 14 $<$ \(\sigma_{LOS}\) $<$ 20 km s\(^{-1}\).
-This knots are well fitted with Gaussian profiles thus, defining the kinematic core \citep{munoz1996}.
-A characteristic radius for them is \(\sim\) 7 pc.
-\citet{yang1996} identified 5 expanding shells within NGC 604, and one of them (Shell 3 on their paper) fall into our observations.
-This shells is 40 pc in diameter with an expansion velocity above 50 km s\(^{-1}\).
-This scales are related to the presence of strong stellar winds caused by massive stars.
-For the NGC 604 case, there is no clear relation between the \(r_0\) and some particular energy injection mechanism...
+%With the aim to relate each \(r_0\) with each region we invoke previous studies on the kinematics of the ionized gas. 
+%\citet{sabalisck1995supersonic} studied NGC 604 revealing that the kinematics of the region behave different considering %different scales.
+%High emission knots on the region encompasses supersonic global velocity dispersion values of 14 $<$ \(\sigma_{LOS}\) $<$ 20 km s\(^{-1}\).
+%This knots are well fitted with Gaussian profiles thus, defining the kinematic core \citep{munoz1996}.
+%A characteristic radius for them is \(\sim\) 7 pc.
+%\citet{yang1996} identified 5 expanding shells within NGC 604, and one of them (Shell 3 on their paper) fall into our observations.
+%This shells is 40 pc in diameter with an expansion velocity above 50 km s\(^{-1}\).
+%This scales are related to the presence of strong stellar winds caused by massive stars.
+%For the NGC 604 case, there is no clear relation between the \(r_0\) and some particular energy injection mechanism...
 %it is also the nearest analog of more extreme star-forming regions, such as 30 Doradus in the Large Magellanic Cloud.

### 2021-10-28 strucfunc_paper.tex
Javier changes to 2021-10-28

@@
  \centering
-  \includegraphics[width=0.8\linewidth]{Figures/strucfunc-fit-A}
-  \label{fig:strucfunc-fit-A}
-  \caption{Second-order structure functions for the velocity centroid images of the \(H\alpha\) emission line}
+ \begin{multicols}{3}
+ \includegraphics[width=2in]{Figures/SFplots/604.pdf}\par
+ \includegraphics[width=2in]{Figures/SFplots/595.pdf}\par
+ \includegraphics[width=2in]{Figures/SFplots/346.pdf}\par
+ \end{multicols}
+ \begin{multicols}{3}
+ \includegraphics[width=2in]{Figures/SFplots/Hubble V.pdf}\par
+ \includegraphics[width=2in]{Figures/SFplots/Hubble X.pdf}\par
+ \includegraphics[width=2in]{Figures/SFplots/tarantula.pdf}\par
+ \end{multicols}
+ \begin{multicols}{3}
+ \includegraphics[width=2in]{Figures/SFplots/Carina.pdf}\par
+ \includegraphics[width=2in]{Figures/SFplots/M8.pdf}\par
+ \includegraphics[width=2in]{Figures/SFplots/OS.pdf}\par
+ \end{multicols}
+ \caption{Second-order structure functions for the velocity centroid images of the \(H\alpha\) emission line investigated in this work.
+The first two rows consider extragalactic regions while the last row shows galactic regions.}
+ \label{fig:SFs}
 \end{figure*}
-
-\begin{figure*}
-  \centering
-  \includegraphics[width=0.8\linewidth]{Figures/strucfunc-fit-B}
-  \label{fig:strucfunc-fit-B}
-  \caption{Second-order structure functions for the velocity centroid images of the \(H\alpha\) emission line}
-\end{figure*}
-
-\begin{figure*}
-  \centering
-  \includegraphics[width=0.8\linewidth]{Figures/strucfunc-fit-C}
-  \label{fig:strucfunc-fit-C}
-  \caption{Second-order structure functions for the velocity centroid images of the \(H\alpha\) emission line}
-\end{figure*}
-
-% \begin{figure*}
-% \centering
-% \begin{multicols}{3}
-% \includegraphics[width=2in]{Figures/SFplots/604.pdf}\par
-% \includegraphics[width=2in]{Figures/SFplots/595.pdf}\par
-% \includegraphics[width=2in]{Figures/SFplots/346.pdf}\par
-% \end{multicols}
-% \begin{multicols}{3}
-% \includegraphics[width=2in]{Figures/SFplots/Hubble V.pdf}\par
-% \includegraphics[width=2in]{Figures/SFplots/Hubble X.pdf}\par
-% \includegraphics[width=2in]{Figures/SFplots/tarantula.pdf}\par
-% \end{multicols}
-% \begin{multicols}{3}
-% \includegraphics[width=2in]{Figures/SFplots/Carina.pdf}\par
-% \includegraphics[width=2in]{Figures/SFplots/M8.pdf}\par
-% \includegraphics[width=2in]{Figures/SFplots/OS.pdf}\par
-% \end{multicols}
-% \caption{Second-order structure functions for the velocity centroid images of the \(H\alpha\) emission line investigated in this work.
-The first two rows consider extragalactic regions while the last row shows galactic regions.}
-% \label{fig:SFs}
-% \end{figure*}
 

### 2021-11-19 Corr.tex
Javier changes 2021-11-19

\begin{table*}
\begin{center}
\caption{Linear regressions values in the form Y = aX + b between our turbulent parameters obtained using the chi-square statistic and properties of each region (Table \ref{tab:Reg}). The fifth column, $r$, is the Pearson correlation coefficient and the last column is the $p$-value. This results were obtained using the procedure in \citet{2007ApJ...665.1489K}.}
\begin{tabular}{cccccc}
\hline
            Y &                   X &                 a &                 b &       $r$ &      $p$ \\
\hline
    log $r_0$ &             log $R$ &    0.67$\pm$0.071 &  -0.798$\pm$0.127 &   0.978 &   <10\(^{-5}\) \\
 log $\sigma$ &            log L(H) &   0.175$\pm$0.094 &  -6.032$\pm$3.649 &   0.711 &  0.021 \\
 log $\sigma$ &  log $\sigma_{LOS}$ &   0.793$\pm$0.457 &  -0.186$\pm$0.526 &   0.662 &  0.037 \\
      log $m$ &            log Dist &  -0.135$\pm$0.094 &   1.262$\pm$0.182 &  -0.603 &  0.065 \\
 log $\sigma$ &         log $r_{0}$ &    0.219$\pm$0.19 &    0.65$\pm$0.122 &    0.53 &  0.115 \\
      log $m$ &        log $\sigma$ &   -0.196$\pm$0.26 &   0.154$\pm$0.194 &  -0.431 &  0.214 \\
      log $m$ &         log $r_{0}$ &   -0.056$\pm$0.09 &   0.027$\pm$0.059 &  -0.364 &  0.301 \\
\hline
\end{tabular}\label{tab:RestStats}
\end{center}
\end{table*}

%<10\(^{-5}\)

### 2021-11-19 extrastuff.tex
Javier changes 2021-11-19

%The idea of a virial system has been developed by \citet{1993ApJ...418..767T,munoz1996} into the \textit{Cometary Stirring Model} (CSM) with the aim to separate the mechanism that contribute to the line broadening.
%The stellar winds also tend to be used for an explanation of the line broadening and turbulence in GEHRs \citep{1994ApJ...425..720C}.
%This features seems to drive visually the regions with filaments, arcs and shells.
%On their spectra double and multiple emission features are signature of these objects.
%\citet{2020MNRAS.494...97S} argue that winds on ionizing clusters in GEHR must merge into a hot cluster because of the close proximity of the massive stars.
%\citet{2019ApJ...871...17U} propose that stellar feedback is an important source of energy to maintain turbulence in nearby galaxies.

%The classic turbulence theory \citep{kolm1} assumes a three-dimensional isotropic, incompressible and subsonic flow where an energy cascade is taking place.
%The interstellar matter does not have those physical properties and our observations are in two-dimensions.
%But as mentioned above the idea of an energy cascade is used to understand our observations.
%The energy cascade goes from the largest vortices where the energy in injected until it reaches dissipation with the smallest vortices.
%In the energy cascade three scales are defined based on their Reynolds number.
%The energy injection scale (Re $\rightarrow \infty$), $L_{EI}$, the dissipation scale (Re $\rightarrow$ 1), $L_{D}$ and the inertial scale, $L_{I}$, between the previous two.
%Since the energy distributions depends on the scale, the energy cascade concept is described with an energy spectrum, $E(k) \propto k$ where $k$ is the wave number for a determined scale $l$ ($k \equiv r^{-1}$).

%Other statistical techniques like velocity channel analysis (VCA) \citep{2000ApJ...537..720L} have been proved to better recreate the spectrum of the velocity field \citep{medina2014,arthur2016turbulence}.
%More recently, the structure function was used with full 6D measurements (position-velocity) to study the motions of stars in the Orion Molecular Cloud Complex.
%\citet{2021ApJ...907L..40H} argue that newborn stars should reflect the turbulent kinematics of their natal clouds.
%Using this previous method they are free of the projected element that interfere with previous gas-based studies and their results agree with the scaling law proposed by \citet{1981MNRAS.194..809L}.

%It is known that the speed of sound in a HII region is of the order of \(c_{HII} \sim\) 13 km s\kms.
%\citet{smith1970} discovered that the probable velocities of internal motions of extragalactic HII regions, \(\sigma_{W}\) (line width integrated over the whole HII region), were in the range of $\sim$ 19-34 km s\kms\ covering supersonic values.
%For the velocity to be supersonic it is necessary a continuous mechanism to maintain the observed motions, as supersonic motions are expected to dissipate energy via shocks \citep{1994Ap&SS.216..285C}.
%Turbulence is suggested as a mechanism that can stir the medium and maintain the supersonic velocities.
%The large lengths of astrophysical objects, ranging in scales from 10$^{6}$ to 10$^{17}$ m \citep{2010ApJ...710..853C}, and the high Reynolds numbers (Re), in the order of 10$^{4}$ - 10$^{9}$, are properties that supports the idea of a turbulent interstellar medium.

%The relationship between L vs \(\sigma\) is one of the most studied. 
%This relationship help us understanding how the star formation affects the gas motions and how star formation is regulated by feedback processes. 
%Figure \ref{fig:sigvsl} shows different studies of the L vs \(\sigma\) relationship \citep{1988A&A...201..199A,Rozas:2006b,2015MNRAS.449.3568M}. 
%In this case it is normally used the deconvolution of the observed lines taking account thermal broadening and instrumental broadening leaving the \(\sigma_{LOS}\). 
%For the data present in Figure \ref{fig:sigvsl}, excluding \(\sigma_{POS}\), we obtain using the same OLS \(log \sigma_{LOS} = 0.145 \pm 0.008 (logL_{H\alpha}) - (4.42 \pm 0.336) \).
%Since the R-squared is 0.596 it is not possible just to invert the OLS results for a comparison with the more classical relationship. 
%Inverting axes we obtain \(log L_{H\alpha} = 4.09 \pm 0.23 log (\sigma_{LOS}) + (34.17 \pm 0.32) \), being in accord to previous relationships.

%\subsection{What turbulence scales can tell us about kinematics of the ionized gas?}

%In the Table \ref{tab:ResII} the second column show the separation where the value 2\(\sigma\) is reached.
%We also show the ratio \(r_{max}/r_{0}\), where \(r_{max}\) is the maximum separation or lag in pc; this value is related to the size of each sample box. 
%The forth column shows the Taylor scale, \(l_T\), which measures the average spatial extent of velocity gradients. \citet{1999ApJ...524..895M} define this scale as:

%\begin{equation}\label{eq:TS}
%l_T=\dfrac{\sigma r_s}{\sigma_{r_s}}
%\end{equation}

%where \(r_s\) is the smallest separation \(r\) and \(\sigma_{r_s}\) the value of the structure function at that separation.

%It is possible to calculate how this Taylor micro-scale is related to the correlation length by:

%\begin{equation}\label{eq:TS1}
%l_T=\dfrac{r_s}{\sqrt{2}}(\dfrac{r_0}{r_s})^{m/2}
%\end{equation}

%Finally in the table we present the Reynolds Number...

%\begin{table}
%\begin{center}\caption{Other significant turbulent scales}
%\begin{tabular}{cccccc}\hline
%HII         &r$_{2\sigma}$ &\(r_{max}\)/\(r_0\)  &\(l_T\) & \(Re\)* \\
%Region      &[pc]          &                     &[pc]    &   \\ \hline
%NGC 604     &28.73         &15.49                &5.35    &   \\
%NGC 595     &18.50         &21.01                &5.57    &   \\
%Hubble V    &11.61         &19.95                &1.80    &   \\ 
%Hubble X    &21.99         &21.67                &1.97    &   \\   
%30 Dor      &11.26         &8.99                 &0.59    &   \\
%Carina      &1.93          &31.55                &0.402   &   \\
%NGC 346     &5.78          &10.73                &0.39    &   \\
%Lagoon      &6.14          &10.68                &0.66    &   \\ 
%Orion Large &-             &2.98                 &0.24    &   \\
%Orion Small &0.162         &10.42                &0.019   &   \\ \hline	  
%\end{tabular}\label{tab:ResII}
%\end{center}
%\end{table}

%With the aim to relate each \(r_0\) with each region we invoke previous studies on the kinematics of the ionized gas. 
%\citet{sabalisck1995supersonic} studied NGC 604 revealing that the kinematics of the region behave different considering %different scales.
%High emission knots on the region encompasses supersonic global velocity dispersion values of 14 $<$ \(\sigma_{LOS}\) $<$ 20 km s\(^{-1}\).
%This knots are well fitted with Gaussian profiles thus, defining the kinematic core \citep{munoz1996}.
%A characteristic radius for them is \(\sim\) 7 pc.
%\citet{yang1996} identified 5 expanding shells within NGC 604, and one of them (Shell 3 on their paper) fall into our observations.
%This shells is 40 pc in diameter with an expansion velocity above 50 km s\(^{-1}\).
%This scales are related to the presence of strong stellar winds caused by massive stars.
%For the NGC 604 case, there is no clear relation between the \(r_0\) and some particular energy injection mechanism...
%it is also the nearest analog of more extreme star-forming regions, such as 30 Doradus in the Large Magellanic Cloud.

%%%%%%%%%%%%%%%other

The groundwork for the statistical study of turbulence was laid by \citet{taylor1935i,taylor1935ii} and \citet{karman1937statistical} and later developed by \citet{kolm1,kolm2} and \citet{heisenberg1951stability}. 
These mathematical techniques were first applied to astronomical observations by \citet{von1951methode} and \citet{munch1958internal} allowing to determine a distinction between homogeneous turbulence and pure random velocity fluctuations in the Orion Nebula.

\section{Turbulence}\label{sec:turb}

The classic turbulence theory \citep{kolm1} assumes a three-dimensional isotropic, incompressible and subsonic flow, where an energy cascade, with different $l$ sizes in an auto-similar configuration, is taking place. 
The energy cascades goes downward, from the large vortices until it reaches dissipation with the smallest vortices.
In this energy cascade three scales can be defined: the energy injection scale (Re $\rightarrow \infty$), $L_{EI}$, the dissipation scale (Re $\rightarrow$ 1), $L_{D}$ and the inertial scale ($L_{I}$) between the previous two.

In the mathematical description of the Kolmogorov theory the energy transfer, $\epsilon$, in the inertial range can be denoted as $\epsilon \sim \frac{v_{l}^{2}}{\tau_{l}}$, where $v_{l}^{2}$ is the kinetic energy per mass unit and $\tau_{l}$ the time related with velocity fluctuations. 
Kolmogorov states the relationship \citep{Leqism}:

\begin{equation}\label{eq:velsca}
v_{l} \sim (\epsilon l)^{\frac{1}{3}}
\end{equation}

The energy cascade concept can  be described with an energy spectrum, $E(k) \propto k^{-\beta}$ where $k$ is the wave number for a scale $l$ ($k \equiv l^{-1}$). The total specific energy of a determined $l$ scale is of the order $\langle v_{l}^{2} \rangle$ and is the energy integral above the associated $k$, defined as:

\begin{equation}\label{eq:veles}
 \langle v_{l}^{2} \rangle = \int_{k}^{\infty} E(k)dk
\end{equation}

Considering that this energy is of the order of $(\epsilon l)^{\frac{2}{3}} \sim (\frac{\epsilon}{k})^{\frac{2}{3}}$ we can substitute in equation \ref{eq:veles} and obtain the Kolmogorov law:

\begin{equation}\label{eq:kolm}
E(k) \propto \epsilon^\frac{2}{3} k^{-\frac{5}{3}}
\end{equation}

For subsonic (Kolmogorov) turbulence $\beta= -5/3$, and for supersonic turbulence the index is $\beta=-2$ \citep{burg}.

Equation \ref{eq:velsca} is related to the quadratic velocities differences by:

\begin{equation}\label{eq:sfi}
(\Delta v)^{2} \sim (\epsilon l)^{\frac{2}{3}}
\end{equation}

We show in the next section that the term $(\Delta v)^{2}$ can be defined as the structure function. The left term with index that we define as $\alpha= 2/3$ in equation \ref{eq:sfi} is directly related to the energy, the left term in equation \ref{eq:veles}. This index $\alpha$ serves as a reference for the Kolmogorov theory and it is used for direct comparison with observations.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Turbulence}\label{sec:turb}

The classic turbulence theory \citep{kolm1} assumes a three-dimensional isotropic, incompressible and subsonic flow, where an energy cascade, with different $l$ sizes in an auto-similar configuration, is taking place. 
The energy cascades goes downward, from the large vortices until it reaches dissipation with the smallest vortices.
In this energy cascade three scales can be defined: the energy injection scale (Re $\rightarrow \infty$), $L_{EI}$, the dissipation scale (Re $\rightarrow$ 1), $L_{D}$ and the inertial scale ($L_{I}$) between the previous two. The energy cascade concept is described with an energy spectrum, $E(k) \propto k^{-\beta}$ where $k$ is the wave number for a scale $l$ ($k \equiv l^{-1}$).Following the mathematical description of the Kolmogorov theory the mean specific energy transfer, $\langle \epsilon \rangle$, in the inertial range can be denoted as $\epsilon \sim \frac{v_{l}^{2}}{\tau_{l}}$, where $v_{l}^{2}$ is the kinetic energy per mass unit and $\tau_{l}$ the time related with velocity fluctuations. Since the total specific energy of a determined $l$ scale is of the order $\langle v_{l}^{2} \rangle$ and is the energy integral above the associated $k$, defined as:

\begin{equation}\label{eq:veles}
 \langle v_{l}^{2} \rangle = \int_{k}^{\infty} E(k)dk
\end{equation}

Considering that this energy is of the order of $(\epsilon l)^{\frac{2}{3}} \sim (\frac{\epsilon}{k})^{\frac{2}{3}}$ we can substitute in equation \ref{eq:veles} and obtain the Kolmogorov law:

\begin{equation}\label{eq:kolm}
E(k) \propto \epsilon^\frac{2}{3} k^{-\frac{5}{3}}
\end{equation}

Considering the quadratic velocities differences:

\begin{equation}\label{eq:sfi}
(\Delta v)^{2} \sim (\epsilon l)^{\frac{2}{3}}
\end{equation}

the term $(\Delta v)^{2}$ can be defined as the structure function. The left term with index that we define as $\alpha= 2/3$ in equation \ref{eq:sfi} is directly related to the energy, the left term in equation \ref{eq:veles}. This index $\alpha$ serves as a reference for the Kolmogorov theory and it is used for direct comparison with observations.

The techniques we used to study the radial velocity sample, $V_{r}(\boldsymbol{x})$, where $V_{r}(\boldsymbol{x})= V_{obs}(\boldsymbol{x})-\langle V_{obs}(\boldsymbol{x}) \rangle$ of a two dimensional field were the second order structure function, $S_{2}(l)$, and the auto correlation function, $R(l)$, defined as:

\begin{equation}\label{eq:S}
S_{2}(\boldsymbol{l})=\dfrac{\sum[V_{r}(\boldsymbol{x}+\boldsymbol{l})-V_{r}(\boldsymbol{x}) ]^{2}}{N(\boldsymbol{l})}
\end{equation}

where $\sigma^{2}$ is the variance of the sample and N($\boldsymbol{l}$) the number of points at each separation.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2021-11-19 strucfunc_paper.tex
Javier changes 2021-11-19

--- 2021-10-13 strucfunc_paper.tex
@@
   span more than two orders of magnitude in size and luminosity.
-  By fitting a simple functional form of the structure function to our results
-  we extract three parameters related to the fluctuations in each region: the
-  total velocity dispersion \(\sigma\), which spans from 3 to 15 km s\(^{-1}\), the
-  autocorrelation length \(r_0\), which covers 0.06 - 8 pc, and the power-law slope \(m\), which ranges from 0.82 to 1.95.
+  We proposed a functional form of the structure function that takes into account the observational seeing, the instrument noise and the size of the observational box.
+  By fitting this functional to our results we extract three parameters related to the fluctuations in each region: 
+  the total velocity dispersion \(\sigma\), which spans from 3 to 15 km s\(^{-1}\), the
+  autocorrelation length \(r_0\), which covers 0.06 - 8 pc, and the power-law slope \(m\), which ranges from 0.7 to 1.3.
   The velocity dispersion is found to correlate primarily with luminosity,
   while the autocorrelation length correlates primarily with the size of the region.
-  The power-law slope shows an apparent correlation with distance,
-  but this is probably an artifact of poor spatial resolution for the most distant regions.
   A comparison between \(\sigma\) and \(\sigma_{POS}\) shows that this last value is at roughly the double for all regions.
+  We found that our proposed functional form describe with more accuracy the inertial range and our methodology guarantees consistency for comparison between the galactic and giant HII regions.
   \textbf{Add a sentence about the conclusions!}
-  % We study the turbulent velocity fluctuations in the ionized gas of four giant HII regions using the radial velocity field in the H$\alpha$ emission line.
-The data was acquired by long-slit spectroscopy and Fabry-Perot observations obtained with the William Herschel Telescope.
-Each velocity sample is statistically analyzed with the second order structure function.
-The correlations in our results shows evidence that the velocity field can be consider in a turbulent state.
-This turbulent motions are described by a power-law with a mean index of 1.7 for different sized regions at different distances.
-The physical interpretation of the power-law behavior consider that an energy cascade is taking place in the photoionized gas.
 \end{abstract}
@@
 \begin{keywords}
-HII regions -- ISM
+HII regions -- ISM: kinematics and dynamics -- turbulence
 \end{keywords}
@@
 
-It is known that the speed of sound in a HII region is of the order of \(c_{HII} \sim\) 13 km s\kms.
-\citet{smith1970} discovered that the probable velocities of internal motions of extragalactic HII regions, \(\sigma_{W}\) (line width integrated over the whole HII region), were in the range of $\sim$ 19-34 km s\kms\ covering supersonic values.
-\citet{skillman1984kinematics} found broad profiles in giant extragalactic HII regions (GEHRs) that have a FWHM\(>\)30km s\kms. 
-This property is mainly used to distinguish between 'normal' and 'giant' HII regions. Other differences are their size, luminosity and their stellar population. 
-For the velocity to be supersonic it is necessary a continuous mechanism to maintain the observed motions, as supersonic motions are expected to dissipate energy via shocks \citep{1994Ap&SS.216..285C}.
-Also, this non-thermal broadening on the spectral emission lines has been suggested as evidence of disorder motions along the line-of-sight (LOS) of the ionized gas. 
-Turbulence is suggested as a mechanism that can stir the medium and maintain the supersonic velocities. 
-The large lengths of astrophysical objects, ranging in scales from 10$^{6}$ to 10$^{17}$ m \citep{2010ApJ...710..853C}, and the high Reynolds numbers (Re), in the order of 10$^{4}$ - 10$^{9}$, are the main properties that supports the idea of a turbulent interstellar medium.
-Previous studies \citep{1999intu.conf.....F,2004ARA&A..42..211E,scalo2004interstellar} revealed that different phases of the interstellar medium show fluctuations on their velocity field that can be interpreted as evidence of random motions.
+HII regions are far from been static objects.
+Initially, the gas of a HII region is ionized in a previously disturbed medium.
+When the formed star starts emitting, the energy and matter coming from it interacts with the surrounding medium, putting in motion a series of dynamical processes that have a considerable effect in the velocity field of the HII regions.
+Different investigations have shown a complex velocity structure particularly to each region. 
+Mainly, the excess in the thermal broadening on the spectral lines is interpreted as disorder motions along the line-of-sight (LOS).
+Motions like the expansion or rotation of the region can be accounted for, but after these are considered, still persist a random velocity component in the region.
+It has become customary to investigate this random component as turbulence in the ionized gas.
 
-The usual picture considers that interstellar turbulence is driven on different scales by various energetic processes.
-Also, it is thought that the formation of structures like filaments and shells in the diffuse medium is determined by large-scale turbulence.
-Stars are the mainly mechanism proposed to account for the large input of kinetic energy through UV radiation, but the dominant energetic sources and their relation to turbulence still is unclear.
-
-\citet{melnick1977,terlevich1981} were the first to shown an empirical relationship between the line width and the integrated properties of the HII regions as the diameter or the luminosity ($r \sim \sigma ^{\sim 2}$ ; $L_{H} \sim \sigma ^{\sim 4}$).
-They conclude that GEHRs follow this relations as self-gravity systems like globular clusters or elliptical galaxies.
-The work of \citet{1988A&A...201..199A} confirmed these relationships considering the discrepancies of previous investigations obtaining \(L_{H_{\alpha}} \propto \sigma^{3.9}\) and \(r \propto \sigma^{1.84}\).
-\citet{2012MNRAS.422.3339W} have found that clumps and HII regions follow scaling relations over the range of z = 0-2 for \halpha\ size, velocity dispersion, luminosity and mass finding \(\sigma \propto r^{0.42}\), \(L_{H_{\alpha}} \propto r^{2.72}\) and \(L_{H_{\alpha}} \propto \sigma^{4.18}\).
-This results imply that the same process are seen at high redshifts and the current epoch in star forming regions.
-\citet{2015MNRAS.449.3568M} found that the relation is also found in dwarf galaxies with a \(L_{H_{\alpha}} \propto \sigma^{5}\).
-
-The idea of a virial system has been developed by \citet{1993ApJ...418..767T,munoz1996} into the \textit{Cometary Stirring Model} (CSM) with the aim to separate the mechanism that contribute to the line broadening.
-The stellar winds also tend to be used for an explanation of the line broadening and turbulence in GEHRs \citep{1994ApJ...425..720C}.
-This features seems to drive visually the regions with filaments, arcs and shells.
-On their spectra double and multiple emission features are signature of these objects.
-\citet{2020MNRAS.494...97S} argue that winds on ionizing clusters in GEHR must merge into a hot cluster because of the close proximity of the massive stars.
-\citet{2019ApJ...871...17U} propose that stellar feedback is an important source of energy to maintain turbulence in nearby galaxies.
-
-The classic turbulence theory \citep{kolm1} assumes a three-dimensional isotropic, incompressible and subsonic flow where an energy cascade is taking place.
-The interstellar matter does not have those physical properties and our observations are in two-dimensions.
-But as mentioned above the idea of an energy cascade is used to understand our observations.
-The energy cascade goes from the largest vortices where the energy in injected until it reaches dissipation with the smallest vortices.
-In the energy cascade three scales are defined based on their Reynolds number.
-The energy injection scale (Re $\rightarrow \infty$), $L_{EI}$, the dissipation scale (Re $\rightarrow$ 1), $L_{D}$ and the inertial scale, $L_{I}$, between the previous two.
-Since the energy distributions depends on the scale, the energy cascade concept is described with an energy spectrum, $E(k) \propto k$ where $k$ is the wave number for a determined scale $l$ ($k \equiv r^{-1}$).
-
-The fluctuations associated with the centroid velocities on the plane-of-sky (POS) of photoionized regions have been characterized several times using the second order structure function (the Fourier transform of the energy spectrum, $E(k)$).
+The fluctuations associated with the centroid velocities on the plane-of-sky (POS) of photoionized regions have been characterized several times using the second order structure function.
 This studies span from galactic HII regions \citep{1986ApJ...300..624R} like Orion \citep{von1951methode,munch1958internal,castaneda1988,1992ApJ...387..229O,arthur2016turbulence} to giant HII regions \citep{1961MNRAS.122....1F,lagrois2009multi,lagrois2011}, like NGC 604 in the M 33 galaxy \citep{tanco1997,2019arXiv191203543M}.
 
-The procedure using the structure function allow us to determine a distinction between homogeneous turbulence and pure random velocity fluctuations in the photoionized gas, but despite the previous evidence of this fluctuations not been random, little is understood about their nature.
+The procedure using the structure function allow us to determine a distinction between homogeneous turbulence and pure random velocity fluctuations in the photoionized gas.
 Several problems arise in the study of these fluctuation.
-Intrinsic with observations there is the projection of a three-dimensional function into the plane-of-sky \citep{von1951methode,munch1958internal}.
-Other statistical techniques like velocity channel analysis (VCA) \citep{2000ApJ...537..720L} have been proved to better recreate the spectrum of the velocity field \citep{medina2014,arthur2016turbulence}.
-More recently, the structure function was used with full 6D measurements (position-velocity) to study the motions of stars in the Orion Molecular Cloud Complex.
-\citet{2021ApJ...907L..40H} argue that newborn stars should reflect the turbulent kinematics of their natal clouds.
-Using this previous method they are free of the projected element that interfere with previous gas-based studies and their results agree with the scaling law proposed by \citet{1981MNRAS.194..809L}.
+One of them is that there is no well-established theory for turbulence in astronomical conditions, these being that the medium is compressible and supersonic, and will result in the presence of shock waves \citep{lagrois2011,arthur2016turbulence}.
+On the other hand, it is known that these regions are created on the edge of molecular clouds, so they will reach a blister or champagne phase, introducing large-scale gradients not related with random motions \citep{Mivi1995}.
+Intrinsic with observations there is the projection of a three-dimensional function into the plane-of-sky \citep{von1951methode,munch1958internal,1964SvA.....8..210K} leading to a loss in information.
 
-Despite different issues that are related with the nature of the problem of turbulence in HII regions, the vast majority of research using the second-order structure function consider individual regions and hence different methodology.
-\citet{1987ApJ...317..686O} has determined the structure functions for a sample of galactic HII regions but isn't conclusive about them.
-The individuality of previous works and the need to understand the relationship between the measured turbulent properties for different classes of HII regions has lead us to develop this investigation.
+There are also a series of problems related to the observations that to date have not been formally addressed like the previous ones.
+These problems are that: 1) following observations, there is the seeing and noise due to the telescope and instrument, and 2) that the observations are mostly limited to only one part of the nebula.
+This has the consequence that when analyzing a turbulent field, the velocity fluctuations related to small and large scales will be affected due to artifacts introduced by the problems mentioned above.
+In turbulence theory, the largest and smallest scales are the most important as they relate to the energy transfer of the turbulence spectrum, which implies that it is necessary to consider them for a correct characterization of the turbulence in the velocity field.
+Disregarding the above has led previous investigations in HII regions to erroneous conclusions about the nature of this energy spectrum.
+
+To face these problems, we study the effects of seeing, noise and observational box size in an artificial velocity field to develop and propose a correct form that fits the results of a statistical analysis of the field of velocity of HII regions.
+This aims to leave little room for the interpretation of results and to characterize in a more precise way the turbulence in ionized nebulae, something that has not been considered in previous works.
+Also, we aim to fill a gap with an uniform statistical analysis of turbulence between galactic and giant HII regions.
 
 Using archival data we perform the second-order structure function on a sample of HII regions.
-Our sample spans in size from 4 pc to 400 pc and has luminosities between 10\(^{37}\) - 10\(^{39}\) erg s\(^{-1}\); from galactic to extragalactic HII regions.
-We apply an uniform methodology of a functional form of the structure function to characterize the turbulent using the  autocorrelation length, \(r_0\), and power-law slope, \(m\).
-Our results are compared with physical properties of each region and are also compared with previous investigations.
-With this work we aim to fill a gap with an uniform statistical analysis of turbulence between galactic and giant HII regions.
-
-The paper follows the next order: in Section \ref{sec:HIIsample} we describe the observational data and some main kinematics properties of each region.
-In Section \ref{sec:met} we present the statistical method used in this work.
-Section \ref{sec:results} presents the structure function of each region along with the turbulent parameters obtained by a non-linear regression method.
-In Section \ref{sec:discussion} we discuss our findings in the context of previous works.
+Our sample spans in size from 4 pc to 400 pc and has luminosities between 10\(^{37}\)-10\(^{39}\) erg s\(^{-1}\) going from galactic to extragalactic HII regions.
+We apply an uniform methodology of a functional form of the structure function to characterize the turbulent using the velocity field variance, $\sigma^2$, autocorrelation length, \(r_0\), and power-law slope, \(m\).
+Our results are compared with physical properties of each region and with previous investigations.
 
@@
 
-We use previous published observational data to measure the second-order velocity structure function for a number of nine HII regions. 
-Table \ref{tab:Reg} shows the HII regions names
-with the main physical properties of each region. 
-These regions are located in the Milky Way, the Magellanic clouds and in the M 33 and NGC 6822 galaxies.
+Previous works that apply a statistical analysis on the velocity field of HII regions  
+tend to consider just one region.
+With the aim to develop a more complete study we choose 9 objects in the \halpha\ emission line.
+This give us the opportunity to compare for first time the structure function of various objects following the same methodology.
+We use previous published observational data to measure characterize the velocity field o HII regions located in the Milky Way, the Magellanic clouds and in the M 33 and NGC 6822 galaxies. 
+Figure \ref{fig:hii-regions} shows the images of our sample.
+Table \ref{tab:Reg} shows the names with the physical properties of interest in each region.
 
@@
 
-\subsection{Regions in M33 and NGC 6822}
+The dwarf irregular galaxy, NGC 6822, is located at a distance of 500 kpc (1'' = 2.4 pc) \citep{2012A&A...540A.135S} and the brightest HII regions are Hubble X and Hubble V (HX and HV hereafter).
+HV has a characteristic length of 100 pc and a luminosity at its core of in L$_{H_\alpha}$ = 1 $\times$ 10$^{49}$ H$\alpha$ photons s$^{-1}$ \citep{1999PASP..111.1382O}.
+HX has a characteristic length of 140 pc and a luminosity at its core of in L$_{H_\alpha}$ = 2.4 $\times$ 10$^{49}$ H$\alpha$ photons s$^{-1}$ \citep{1999PASP..111.1382O}.
+Two recognized OB associations \citep{1991ApJ...379..621H,1992AJ....104.1374W} are identified within the region of HV and HX.
+HV is located near 'Hodge OB 8', and HX is located near 'Hodge OB13'  \citep{1999PASP..111.1382O}.
 
@@
 \citet{2012ApJ...761....3M} derive an average age of 4$\pm$1 Myr and a total stellar mass of 1.6$^{+1.6}_{-1.0} \times$ 10$^{5}$M$_{\odot}$ for the region.
-
 The stellar population has been identified and classified by \citet{1996ApJ...456..174H} (and references therein).
@@
 This suggest that two episodes of star formation, at least, have taken place in the GEHR.
-\citep{1984A&A...141...49H} identified a gradient from the west to the SE of the nebula of 30 km s$^{-1}$.
+%\citep{1984A&A...141...49H} identified a gradient from the west to the SE of the nebula of 30 km s$^{-1}$.
 
 NGC 595 is the second brightest giant HII region in the M33 galaxy.
-The electronic temperature is 7,670 $\pm$116 K \citep{2010MNRAS.402.1635R}.
+%The electronic temperature is 7,670 $\pm$116 K \citep{2010MNRAS.402.1635R}.
 \citet{1983A&A...119..185V} made an estimate of the total masses of HI and HII in the nebula to obtain values of M$_{HI}=$ 1.2 $\times$ 10 $^{6}$ M$_{\odot}$ and M$_{HII} =$ 4.6 $\times$ 10 $^{5}$ M$_{\odot}$, and a ionizing luminosity of the star cluster is estimated at 5 $\times$ 10$^{50}$ erg s $^{1}$.
 \citet{1996AJ....111.1128M} estimate an age of 4.5 Myrs consistent with \citet{1993AJ....105.1400D}.
-
 It has approximately 250 stars of the OB type, 13 Supergiants and 9 WR \citep{1996AJ....111.1128M}, ten WRs confirmed with spectroscopy \citet{1993AJ....105.1400D}, nine of the WN type and a WC, located near the bright core of the region.
 
-The dwarf irregular galaxy, NGC 6822, is located at a distance of 500 kpc (1'' = 2.4 pc) \citep{1996AJ....112.1928G} and the brightest HII regions are Hubble V (HV) and Hubble X (HX).
-HV has a characteristic length of 100 pc and a luminosity at its core of in L$_{H_\alpha}$ = 1 $\times$ 10$^{49}$ H$\alpha$ photons s$^{-1}$ \citep{1999PASP..111.1382O}.
-HX has a characteristic length of 140 pc and a luminosity at its core of in L$_{H_\alpha}$ = 2.4 $\times$ 10$^{49}$ H$\alpha$ photons s$^{-1}$ \citep{1999PASP..111.1382O}.
+\subsection{Observations}
 
-%Two recognized OB associations \citep{1991ApJ...379..621H,1992AJ....104.1374W} are identified within the region of HV and HX.
-HV is located near 'Hodge OB 8', and HX is located near 'Hodge OB13'  \citep{1999PASP..111.1382O}.
+We use data from \citet{1987A&A...176..347H} and \citet{arthur2016turbulence} to study of turbulence in the Orion Nebula.
+\cite{1987A&A...176..347H} observations were obtained using a 106 cm-Cassegrain telescope at Observatorium Hoher List. 
+A Fabry-Pérot interferometer was used with a étalon a separation of 0.5 mm. 
+Interferograms have been taken with different pointing directions of the telescope's optical axis in the nebula. 
+The exposures are overlapped and fall into one square of a grid with a width of 1' centered at \(\theta^{1}\)Ori C.
 
-The archival data used in this work for the extragalactic giant regions was obtained with the Fabry Perot TAURUS-II instrument in the 4.2-m William Herschel Telescope (WHT) of del Roque de los Muchachos Observatory (ORM) in La Palma, Spain and was retrieved from the La Palma archive\footnote{\url{http://casu.ast.cam.ac.uk/casuadc/ingarch}}.
+\citet{arthur2016turbulence} observations were initially published by \citet{2008RMxAA..44..181G}. 
+The data was obtained with the echelle spectrograph attached to the 4 m telescope at Kitti Peak National Observatory (KPNO).
+These observation cover 3 \(\times\) 5 arcmin\(^{2}\) of the central (Huygens) part of the Orion nebula.
+The data consist of 96, North-South orientated 300 arcsec slits at 2 arcsec intervals with a width of 0.8 arcsec with a velocity resolution of 8 km s\(^{-1}\).
+
+Archival data from \citet{Damiani:2016a} and \citet{Damiani:2017b} are use to study the Carina nebula and Lagoon nebula, respectively. 
+The ESO VLT/FLAMES multi-fiber spectograph \citep{2002Msngr.110....1P} was used for these observations (Gaia-ESO Survey internal release \(iDR4\)). 
+The Survey targets are low-mass stars ranging down to magnitude V \(\sim\) 18.5.
+Mainly the spectra were obtained with the spectographs Giraffe (HR15N setup \(R \sim19 000\), wavelength range 6444-6818 \AA) and the UVES (setup 580, R \(\sim\)4700, range 4768-6830 \AA).
+
+Using observations from \citet{Castro:2018a} (private communication) we study 30 Dor.
+NGC 2070 was observed as part of the MUSE SV (Science Verification) programme at the Very Large Telescope (VLT) in August 2014, when the instrument was new. 
+Four overlapping fields, each with an individual field of 1' \(\times\) 1' and a pixel scale of 0.2''/pixel were observed with exposure times of 4 \(\times\) 10s, 4 \(\times\) 60s, and 4 \(\times\) 600s.
+The table 1 on their work summarize the propertie of each field.
+The data were reduced using the MUSE pipeline based on ESOREX recipes, with final astrometric calibration using the catalog of \citet{1999A&A...341...98S}. 
+The final spectra span 4595-9366 \AA, with a resolving power of \(R \sim3 000\) around \halpha\  \citep{Castro:2018a}.
+
+The archival data used in this work for the extragalactic giant regions, NGC 604, NGC 595, Hubble X and Hubble V was obtained with the Fabry Perot TAURUS-II instrument in the 4.2-m William Herschel Telescope (WHT) of del Roque de los Muchachos Observatory (ORM) in La Palma, Spain and was retrieved from the La Palma archive\footnote{\url{http://casu.ast.cam.ac.uk/casuadc/ingarch}}.
 \citet{sabalisck1995supersonic} mentioned the main aspects of the observations (1990 July 31).
@@
 
-%\citet{2002MNRAS.329..481B} 39.42 38.95 38.21 38.30  39.46 37.36  37.08
-
 \begin{table*}
-\begin{center}\caption{Sumary of properties \citep{1984ApJ...287..116K} \citep{1986ApJ...300..624R}}
-\begin{tabular}{ccccccccc}\hline
-HII    &  Dist.  & Diameter & log L(H$_{\alpha}$) & SFR      &  $ \langle N_{e} \rangle_{rms}$    & M(H$^{+}$) & Filling & \(\sigma_{W}\) \\
-Region     &  [kpc] &  [pc]     &  [erg/s]            & [ ]      & [cm$^{-3}$] & [M$_{\odot}$] & Factor & [km/s] \\ \hline
-NGC 604   &   840  & 400     &    39.65     & 0.011    & 3  & 7 $\times$ 10$^{5}$ & 0.1 & 23.1 \\
-NGC 595   &   840  & 400     &    39.36     & 0.009    & 4  & 4.6 $\times$ 10$^{5}$ & & 27.1 \\
-Hubble X  &   500  & 160     &    38.6      &  0.004   &  5 & 23 000& 0.02 & 13.4 \\
-Hubble V  &   500  & 130     &    38.87     &  0.005   &  8 &    & & 14.7 \\
-30 Dor    &   50   & 98.9    &    39.76     & 0.0130   & 250&    & & 31.7 \\
-Carina    &   2.35 & 15      &    39.6      & 0.01     & 500&    & 0.05 & \\
-NGC 346   &   61.7 & 64      &    38.67     & 0.0021   & 100&    &     & \\
-Lagoon    &   1.25 & 25      &    37.47     & 0.0001   &  60& 900& 0.012 & \\
-Orion     &   0.4  & 5       &    37        & 0.000053 & 150& 50 & 0.027 & \\\hline
+\begin{center}\caption{Summary of properties.}
+\begin{tabular}{ccccc}\hline
+HII       &  Distance (D)          & Diameter (R) & log L(H$_{\alpha}$) &  \(\langle \sigma_{LOS} \rangle \) \\
+Region    &  [kpc]          &  [pc]    &  [erg/s]            &    [km/s]  \\ 
+\hline
+Orion small   & 0.436$\pm$0.02  & 0.6  &    37               &   6.0      \\
+Orion large   & 0.436$\pm$0.02  & 5    &    37               &   6.0      \\ 
+Lagoon    & 1.25$\pm$0.12   & 25       &    37.47            &   13.6     \\
+Carina    & 2.35$\pm$0.05   & 15       &    39.6             &   22.4     \\
+30 Dor    & 49.97$\pm$0.19  & 98.9     &    39.76            &   31.7     \\
+NGC 346   & 61.9$\pm$1.1    & 64       &    38.67            &   10.2     \\
+Hubble X  & 490$\pm$40      & 160      &    38.6             &   13.4     \\
+Hubble V  & 490$\pm$40      & 130      &    38.87            &   12.3     \\
+NGC 604   & 820$\pm$30      & 400      &    39.65            &   16.2     \\
+NGC 595   & 820$\pm$30      & 400      &    39.36            &   18.3     \\
+\hline
 \end{tabular}\label{tab:Reg}
@@
 \end{table*}
+
+%2013ApJ...773...69G M33 dist
+% \citep{1984ApJ...287..116K} \citep{1986ApJ...300..624R}
 
@@
 \section{Methods}\label{sec:met}
+
+\subsection{Turbulence}
+
+The classic turbulence theory \citep{kolm1} assumes a three-dimensional isotropic, incompressible and subsonic flow where an energy cascade is taking place.
+The energy cascade goes from the largest vortices where the energy in injected until it reaches dissipation with the smallest vortices.
+In the energy cascade three scales are defined based on their Reynolds number.
+The energy injection scale (Re $\rightarrow \infty$), $L_{EI}$, the dissipation scale (Re $\rightarrow$ 1), $L_{D}$ and the inertial scale, $L_{I}$, between the previous two.
+Since the energy distributions depends on the scale, the energy cascade concept is described with an energy spectrum, $E(k) \propto k$ where $k$ is the wave number for a determined scale $l$ ($k \equiv r^{-1}$).
+
+The total specific energy of a determined $l$ scale is of the order $\langle v_{l}^{2} \rangle$ and is the energy integral above the associated $k$, defined as:
+
+\begin{equation}\label{eq:veles}
+ \langle v_{l}^{2} \rangle = \int_{k}^{\infty} E(k)dk
+\end{equation}
+
+This energy is of the order of $(\epsilon l)^{\frac{2}{3}} \sim (\frac{\epsilon}{k})^{\frac{2}{3}}$. From the above equation we obtain the Kolmogorov law:
+
+\begin{equation}\label{eq:kolm}
+E(k) \propto \epsilon^\frac{2}{3} k^{-\frac{5}{3}}
+\end{equation}
+
+For Kolmogorov turbulence $\beta = -5 / 3$, and for supersonic turbulence the index is $\beta=-2$ \citep{burg}.
 
@@
 
-\begin{equation}\label{eq:S}
+\begin{equation}\label{eq:Br}
 B(\boldsymbol{r})=\dfrac{\sum[V_{r}(\boldsymbol{x}+\boldsymbol{r})-V_{r}(\boldsymbol{x}) ]^{2}}{N(\boldsymbol{r})}
@@
 This follows if we have an optically thin spectral line where it will have a width which is related to the total radial velocity dispersion of all fluctuations sampled along the line-of-sight \citep{1984ApJ...277..556S}.
-In these sense the structure function is used as a tool to investigate the projection of a three.dimensional correlation function onto the plane of sky \citep{arthur2016turbulence}.
-
-We also use the functional form of the structure function:
-
-\begin{equation}\label{eq:b}
-b(r)=2[1-C(r)]\zeta+\eta
-\end{equation}
-
-where $C(r)=1/[1+(r/r_{0})^{m}]$ \citep{1984ApJ...277..556S,arthur2016turbulence}.
-The term $r_{0}$ is the correlation length of the turbulence, the value of \(r\) in pc where equation \ref{eq:S} reach the value of \(\sigma^2\), and $m$ is the index that adjust our results.
-The term $\zeta$ is a correction for small scales considering a Gaussian seeing, $s_{0}$, and has the form $tanh^{2}[(r/2s_{0})^2]$, and \(\eta\) is the observational noise. 
-In this idealized case, at scales larger than r$_{0}$ the structure function flattens as it tends towards the asymptotic value of 2$\sigma$ \citep{arthur2016turbulence}.
+In these sense the structure function is used as a tool to investigate the projection of a three-dimensional correlation function onto the plane of sky \citep{arthur2016turbulence}.
 
@@
 
-The results and the errors of $r_{0}$ and $m$ are obtained using equations \ref{eq:S} and \ref{eq:b} in a chi-square (\(\chi^2)\) statistic in order to do a non-linear least-squares fit of a model to our data \citep{newville_matthew_2014_11813}.
+We use the functional form of the structure function in terms of the autocorrelation function:
+
+\begin{equation}\label{eq:ff}
+b(r;r_0,m) = 2\sigma^2(1-C(r))
+\end{equation}
+
+where $C(r)$ is a new form of the autocorrelation function in the form:
+
+\begin{equation}\label{eq:ffnew}
+C(r) = exp[-ln2(\frac{r}{r_0})^m]
+\end{equation}
+
+substituing the previourly form $C(r)=1/[1+(r/r_{0})^{m}]$ \citep{1984ApJ...277..556S,arthur2016turbulence}.
+
+The term $r_{0}$ is the correlation length of the turbulence, the value of \(r\) in pc where equation \ref{eq:Br} reach the value of \(\sigma^2\), and $m$ is the index that adjust our results.
+In this idealized case, at scales larger than r$_{0}$ the structure function flattens as it tends towards the asymptotic value of 2$\sigma$ \citep{arthur2016turbulence}.
+
+The model proposed to describe the seeing at small scales is:
+
+\begin{equation}\label{eq:ffs}
+S(r; s_0, r_0) = \frac{e^\frac{-s_0}{r_0}}{1+(\frac{2s_0}{r})^\frac{2}{3}}
+\end{equation}
+
+and the model that consider the effect of the observational box size is:
+
+\begin{equation}\label{eq:ffb}
+\beta(r_0) = 1 - exp[\frac{L_{box}}{3.6r_0}] 
+\end{equation}
+
+where $L_{box}$ is the diagonal length of the observational box.
+
+The final form of our proposed functional of the structure function is in the form:
+
+\begin{equation}\label{eq:fff}
+B(r) = b(r; \beta r_0, \beta m)*S(r; s_0, r_0)+B_{noise}
+\end{equation}
+
+The results obtained with equation \ref{eq:Br} are use in a non-linear least-squares
+fit to obtain the best values for the turbulent parameters. 
+We use equation \ref{eq:fff} in a chi-square analysis applying the equation:
+
+\begin{equation}\label{eq:chi}
+\chi^2 = \sum_i ^N \frac{[y_i^{measure}-y_i^{model} (\boldsymbol{v})]^2}{\epsilon_i ^2}
+\end{equation}
+
+using the package \textit{lmfit} \citep{newville_matthew_2014_11813}.
+
 In this way we avoid one fundamental problem in the interpretation of the structure function results. 
-The slope in the majority of previous studies and hence, the correlation length, is obtained by eye.
+The slope in the majority of previous studies and hence, the correlation length, is obtained without a formal procedure. 
 The traditional way to find it is to determine a particular range of ascending values in the structure function results. 
-If this increase in values is stopped it is commonly assumed that one particular range has been found. 
-In some cases this procedure keeps going up to large scales, giving two or more inertial regimes;this has lead to the interpretation of multiple energy injection scales.
-Since the previous described method isn't conclusive we choose the chi-square (\(\chi^2)\) statistic to present the significance of our results. 
-This way we can maintain consistency in our analysis.
+If this increase in values is stopped or reversed it is commonly assumed that one particular inertial range has been found. 
+In some cases this procedure keeps going up to large scales, giving two or more inertial regimes leading to the erroneous interpretation of multiple inertial scales.
 
@@
 
-The Figure \ref{fig:hist} shows the histograms of each individual sample with the variance  \(\sigma^{2}\), along the number of points of each sample.
-
-%\begin{table*}
-%  \begin{center}
-%    \caption{General statistical properties of the centroid velocities.} 
-%\begin{tabular}{cccc}\hline
-%HII         &$\mu$   &$\sigma^{2}$       &No. of  \\
-%Region      &[km/s]  &[km$^{2}$/s$^{2}$] &points  \\ \hline
-%NGC 604     &3.56    &54.63              &9 510    \\
-%NGC 595     &2.82    &44.13              &8 765    \\
-%Hubble V    &-1.23   &7.87               &5 832   \\
-%Hubble X    &-5.95   &12.9               &6 925   \\
-%30Dor       &265.56* &252.79             &363 059 \\
-%Carina      &-8.83   &17.89              &855     \\
-%NGC 346     &        &31.36              &112 796 \\
-%Lagoon      &-6.26   &7.53               &1 176   \\
-%Orion Large &-1.25   &10.43              &359     \\
-%Orion Small &        &9.61               &        \\ \hline
-%\end{tabular}\label{tab:Data}
-%\end{center}
-%\end{table*}
+The Figure \ref{fig:velocity-maps} shows the velocity maps of each HII region in the \halpha\ emission line.
+All velocities are relative to the systemic velocity of each region, with more negative velocities shown in blue and more positive velocities in red.
+The range of velocities is different for each region and is shown in each map.
+The more negative velocities are shown in blue and more positive velocities are shown in red.
+The Figure \ref{fig:hist} shows the probability density functions of our sample of HII regions.
+All the distributions are far from being consider Gaussian, implying that there are multiple kinematics components in the regions.
 
@@
  \includegraphics[width=5in]{Figures/Hist/Hist}\par
-\caption{Histograms of the centroid velocities of our sample of HII regions. }
+ \caption{Histograms of the centroid velocities in \halpha\ of our sample of HII regions. }
  \label{fig:hist}
@@
 
-Table \ref{tab:Res} presents the three parameters we obtain from the analysis on the fluctuations of the velocities using the second order structure function.
-The second column is the velocity dispersion \(\sigma\) of each sample of centroid velocities.
-The third column is the correlation length \(r_0\).
-The index \(m\) is shown in the forth column;
-this index is used as a reference for comparison between theory and observations.
-In the fifth column we show the reduced chi-square value obtained using a non-linear regression algorithm. 
-Finally we show the mean velocity dispersion across the line-of-sight \(\sigma_{LOS}\) with the aim to investigate how statistically homogeneous the regions are.
-
-%In the appendix \ref{sec:StructFunct} the Figures \ref{fig:SF604}-\ref{fig:SFM42} show the second-order structure functions of the different HII regions for the \halpha\ emission line.
-
-The power-law fit in the structure function for the both regions in the M33 galaxy in is performed above scales of 1.7 pc.
-For NGC 604 the index is correspond to 1.95 with a correlation length of 8.75 pc. For NGC 595 the values obtained are 1.75 and 9 pc.
-For NGC 6822 regions, Hubble X and Hubble V, the $m$ index is 1.7 and 1.62, with a correlation length of 3.62 and 2.7 pc, respectively.
-The 30Dor nebula \citep{Castro:2018a} has a correlation length of 2.7 pc and an index of 1.22.
-NGC 346 correlation length is 1.4 pc and its index is 1.13.
-
-The Carina observations allow us to measure a blue shifted and a red shifted layer \citet{Damiani:2016a}.
-It is possible to combine the moments from the sum of two components \citep{2008RMxAA..44..181G}, we use this combined sample for the structure function analysis.
-Carina has an index of 0.82 with a correlation length of 0.94 pc.
-The galactic region Lagoon nebula \citep{Damiani:2017b} presents a correlation length of 1.78 pc and a index of 1.56.
-
-For Orion we have the opportunity to study two different observations.
-\citet{1987A&A...176..347H} observations allow us to study the large scale of the nebula, covering 4 pc, while \cite{arthur2016turbulence} allow us to study the small scales up to 0.4 pc.
-Large scales results shows an index of 0.9 with a correlation length of 0.84 pc while the small scales have 1.44 and 0.062 pc.
-
-The highest \(\sigma\) is 15.8 km s\(^{-1}\) for 30Dor.
-This is two times higher than NGC 604 that has a value of 7.4 km s\(^{-1}\), followed by NGC 595 with 6.64 km s\(^{-1}\).
-NGC 346 is next with a value of 5.6 km s\(^{-1}\), followed by Carina with 4.22 km s\(^{-1}\).
-Hubble X and M42 have a value of 3.59 and 3.23 km s\(^{-1}\), respectively.
-Hubble V has 2.8 km s\(^{-1}\) and last mof all sample is Lagoon with 2.7 km s\(^{-1}\).
+Figures \ref{fig:strucfunc-fit-A}-\ref{fig:strucfunc-fit-C} shows the structure function of each region along with the fit obtained using the non-linear regression.
+Table \ref{tab:Res} presents the turbulent parameters we obtain the regression.
+The second column correspond to the variance \(\sigma^2\) of the velocity field.
+The index \(m\) is shown in the third column and is used as a reference for comparison between theory and observations.
+The fourth column is the correlation length \(r_0\).
 
@@
   \centering
-\begin{multicols}{3}
-\includegraphics[width=2in]{Figures/SFplots/604.pdf}\par
-\includegraphics[width=2in]{Figures/SFplots/595.pdf}\par
-\includegraphics[width=2in]{Figures/SFplots/346.pdf}\par
-\end{multicols}
-\begin{multicols}{3}
-\includegraphics[width=2in]{Figures/SFplots/Hubble V.pdf}\par
-\includegraphics[width=2in]{Figures/SFplots/Hubble X.pdf}\par
-\includegraphics[width=2in]{Figures/SFplots/tarantula.pdf}\par
-\end{multicols}
-\begin{multicols}{3}
-\includegraphics[width=2in]{Figures/SFplots/Carina.pdf}\par
-\includegraphics[width=2in]{Figures/SFplots/M8.pdf}\par
-\includegraphics[width=2in]{Figures/SFplots/OS.pdf}\par
-\end{multicols}
-\caption{Second-order structure functions for the velocity centroid images of the \(H\alpha\) emission line investigated in this work.
-The first two rows consider extragalactic regions while the last row shows galactic regions.}
-\label{fig:SFs}
+  \includegraphics[width=0.8\linewidth]{Figures/strucfunc-fit-A}
+  \caption{Second-order structure functions for the velocity centroid images of the \(H\alpha\) emission line}\label{fig:strucfunc-fit-A}
 \end{figure*}
 
-\begin{table*}
-\begin{center}\caption{Main results.
- a) \citet{tanco1997}
-      b) \citet{2019arXiv191203543M}
-      c) \citet{Castro:2018a}
-      d) \citet{Damiani:2016a}
-      e) \citet{Damiani:2017b}
-      f) \citet{1987A&A...176..347H}
-      g) \citet{arthur2016turbulence}.}
-\begin{tabular}{ccccccccc}\hline
-HII         &\(\sigma\) &\(r_0\)                     &\(m\)    &\(\langle \sigma_{LOS} \rangle \) & Previously\\
-Region      &[km/s]     &[pc]                        &                           &  [km/s]& used in:\\ \hline
-NGC 604     &7.39       &8.75\(^{+0.68}_{-0.75}\)    &1.95\(^{+0.12}_{-0.14}\)   &16.2  &a,b \\
-NGC 595     &6.64       &8.99\(^{+0.58}_{-0.71}\)    &1.75\(^{+0.10}_{-0.10}\)   &18.3  &- \\
-Hubble V    &2.80       &2.7\(^{+0.24}_{-0.14}\)     &1.62\(^{+0.11}_{-0.09}\)   &13.4  &- \\ 
-Hubble X    &3.59       &3.62\(^{+0.18}_{-0.15}\)    &1.7\(^{+0.08}_{-0.09}\)    &12.3  &- \\   
-30 Dor      &15.8       &2.69\(^{+0.08}_{-0.03}\)    &1.22\(^{+0.022}_{-0.007}\) &31.7* &c\\
-Carina      &4.22       &0.53\(^{+0.12}_{-0.11}\)    &1.19\(^{+0.20}_{ -0.16}\)  &22.4  &d\\
-NGC 346     & 5.6       &1.4\(^{+0.05}_{-0.75}\)     &1.13\(^{+0.03}_{-0.03}\)   &10.2* &-\\
-Lagoon      &2.7        &1.78\(^{+0.07}_{-0.07}\)    &1.56\(^{+0.05}_{-0.05}\)   &13.6  &e\\ 
-Orion Large &3.23       &0.84\(^{+0.37}_{-0.24}\)    &0.9\(^{+0.04}_{-0.04}\)    &6     &f \\
-Orion Small &3.1        & 0.062\(^{+0.003}_{-0.001}\)&1.44\(^{+0.11}_{-0.01}\)   &6     &g \\\hline	  
-\end{tabular}\label{tab:Res}
-\end{center}
-\end{table*}
+\begin{figure*}
+  \centering
+  \includegraphics[width=0.8\linewidth]{Figures/strucfunc-fit-B}
+  \label{fig:strucfunc-fit-B}
+  \caption{Second-order structure functions for the velocity centroid images of the \(H\alpha\) emission line}
+\end{figure*}
 
-\subsection{Structure function power indices \(m\)}
+\begin{figure*}
+  \centering
+  \includegraphics[width=0.8\linewidth]{Figures/strucfunc-fit-C}
+  \caption{Second-order structure functions for the velocity centroid images of the \(H\alpha\) emission line}\label{fig:strucfunc-fit-C}
+\end{figure*}
 
-It is possible that the index \(m\) is biased to \(m>\)1.6 for the extragalactic regions and \(m<\)1.5 for nearby regions.
-This could be attributed to a data quality issues because the inability to resolve distant regions in the same way we do with nearby objects.
-Since we are not observing all the inertial range on distant regions the \(m\) parameter  should be taken with some caution.
+\input{SFresults}
+%\begin{table*}
+% \begin{center}\caption{Main results.
+%  a) \citet{tanco1997}
+%      b) \citet{2019arXiv191203543M}
+%      c) \citet{Castro:2018a}
+%      d) \citet{Damiani:2016a}
+%      e) \citet{Damiani:2017b}
+%      f) \citet{1987A&A...176..347H}
+%      g) \citet{arthur2016turbulence}.}
+% \begin{tabular}{ccccccccc}\hline
+% HII         &\(\sigma^{2}\) &\(r_0\)                     &\(m\)    &\(\langle \sigma_{LOS} \rangle \) & Previously\\
+% Region      &[km/s]$^{2}$     &[pc]                        &                           &  [km/s]& used in:\\ \hline
+% NGC 604     & 80.93$\pm$25.31 &  9.12$\pm$2.98  & 0.82$\pm$0.20  & 16.2 & a,b \\
+% NGC 595     & 56.45$\pm$1.69  & 11.69$\pm$0.45  & 1.29$\pm$0.04  & 18.3 & - \\
+% Hubble X    & 15.55$\pm$1.50  &  3.90$\pm$0.28  & 0.94$\pm$0.12  & 13.4 & - \\ 
+% Hubble V    & 10.46$\pm$0.75  &  3.42$\pm$0.33  & 0.73$\pm$0.09  & 12.3 & - \\  
+% 30 Dor      & 350.87$\pm$21.59 & 4.60$\pm$0.43  & 0.84$\pm$0.03  & 31.7 & c\\
+% Carina      & 16.74$\pm$1.13  & 0.66$\pm$0.08  & 1.36$\pm$0.29  & 22.4 & d\\
+% NGC 346     & 38.03$\pm$1.09  & 1.90$\pm$0.09  & 0.78$\pm$0.02  & 10.2 & -\\
+% Lagoon      & 7.29$\pm$0.84   & 1.00$\pm$0.17  & 1.12$\pm$0.09  & 13.6 & e\\ 
+% Orion Large & 5.97$\pm$0.58   & 0.73$\pm$0.17  & 1.72$\pm$0.524 & 6.0 & f \\
+% Orion Small & 16.92$\pm$0.97  & 0.091$\pm$0.006 & 1.06$\pm$0.01 & 6.0 & g \\\hline	  
+% \end{tabular}\label{tab:Res}
+% \end{center}
+%\end{table*}
+
+\subsubsection{Velocity field \(\sigma\)}
+
+%The highest \(\sigma\) is 15.8 km s\(^{-1}\) for 30Dor.
+%This is two times higher than NGC 604 that has a value of 7.4 km s\(^{-1}\), followed by NGC 595 with 6.64 km s\(^{-1}\).
+%NGC 346 is next with a value of 5.6 km s\(^{-1}\), followed by Carina with 4.22 km s\(^{-1}\).
+%Hubble X and M42 have a value of 3.59 and 3.23 km s\(^{-1}\), respectively.
+%Hubble V has 2.8 km s\(^{-1}\) and last mof all sample is Lagoon with 2.7 km s\(^{-1}\).
+
+\subsubsection{Structure function power indices \(m\)}
+
+It has been proposed for comparison between two-dimensional observations and the three-dimensional value of the astronomical object what it is called projection smoothing \citep{von1951methode, munch1958internal,1987ApJ...317..686O}, where:
+
+\begin{equation}\label{eq:exp1}
+m_{2D}= m_{3D} + 1
+\end{equation}
+
+or when the astronomical object is almost two-dimensional (sheet-like) we have:
+
+\begin{equation}\label{eq:exp2}
+m_{2D} \sim m_{3D}
+\end{equation}
+
+If the extension of the region is compared with its depth the value of the index is $\frac{5}{3}$.
+While the case where the extension is much greater than its depth (two-dimensional) will have a value of $\frac{2}{3}$.
 
 We can compute the $m_{3D}$ index from the two dimensional \(m\), if we assume that the $m_{3D}$ index lies between the limits of projection smoothing and a sheet-like distribution. 
-For our observations we have 0.82 $<$ m$_{3D}$ $<$ 1.95.
-This is done following the procedure by \cite{arthur2016turbulence} assuming the relationship m$_{2D}$ - 1 $<$ m$_{3D}$ $<$ m$_{2D}$.
-This give us a considerable large range of 1. 
-Though \cite{arthur2016turbulence} are comparing emission lines and not regions we can conclude that the index \(m\) still is far away as a unique parameter for measuring turbulence and that the three-dimensional behavior would probably encompass a wide range of indices as seen in the two-dimensional observations.
+Following the procedure by \cite{arthur2016turbulence} and assuming the relationship m$_{2D}$ - 1 $<$ m$_{3D}$ $<$ m$_{2D}$ we have 0.36 $<$ m$_{3D}$ $<$ 0.72.
+Though \cite{arthur2016turbulence} are comparing emission lines and not regions, we can conclude that the index \(m\) still is far away as a unique parameter for measuring turbulence on ionized regions.
 
-\subsection{Significance on the length scale \(r_0\)}
+\subsubsection{Significance on the length scale \(r_0\)}
 
 Ideally the correlation length \(r_0\), should represent the scale of dominant energy injection. 
-Since it is unclear what are the mechanisms driving the turbulence, thought a lot of options are candidates, it is difficult to pinpoint one particular as main responsible. 
+Since it is unclear what are the mechanisms driving the turbulence, thought a lot of options are candidates, it is difficult to pinpoint one particular process as the main responsible. 
 The possibility that the correlation length reveals the answer to the cause of observed motions is a long shot, but it is clear that each velocity field has a corresponding \(r_0\) value. 
-The range covered in our results goes from 0.06 to 9 pc, a small range in comparison with the two order magnitude difference in size and luminosity.
-
-\subsection{Correlations between turbulent parameters}
-
-\begin{figure}
-\centering 
-\includegraphics[width=2in]{Figures/mr0.pdf}
-\caption{ }
-\label{fig:mr0}
-\end{figure}
+The range covered in our results goes from 0.09 to 11 pc.
 
@@
 
+\subsection{Correlations between physical properties and turbulent parameters}
+
+Scaling relations between parameters like size and luminosity are common tools to study HII regions, along dwarf galaxies and high-redshift star formation regions.
+\citet{melnick1977,terlevich1981} were the first to shown an empirical relationship between the line width and the integrated properties of the HII regions as the diameter or the luminosity ($r \sim \sigma ^{\sim 2}$ ; $L_{H} \sim \sigma ^{\sim 4}$).
+They conclude that GEHRs follow this relations as self-gravity systems like globular clusters or elliptical galaxies.
+The work of \citet{1988A&A...201..199A} confirmed these relationships considering the discrepancies of previous investigations obtaining \(L_{H_{\alpha}} \propto \sigma^{3.9}\) and \(r \propto \sigma^{1.84}\).
+\citet{2012MNRAS.422.3339W} have found that clumps and HII regions follow scaling relations over the range of z = 0-2 for \halpha\ size, velocity dispersion, luminosity and mass, finding \(\sigma \propto r^{0.42}\), \(L_{H_{\alpha}} \propto r^{2.72}\) and \(L_{H_{\alpha}} \propto \sigma^{4.18}\).
+This results imply that the same process are seen at high redshifts and the current epoch in star forming regions.
+\citet{2015MNRAS.449.3568M} found that the relation is also found in dwarf galaxies with a \(L_{H_{\alpha}} \propto \sigma^{5}\).
+
+With the aim to investigate the scaling relations for our sample of HII regions and the turbulent parameters obtained, we use the properties in Table \ref{tab:Reg} with the values in Table \ref{tab:Res} to adjust a fit in the form $X = aY +b$.
+For this procedure we use a hierarchical Bayesian approach using the package \textit{linmix} \citep{2007ApJ...665.1489K}.
+The results are shown in Table \ref{tab:RestStats} in ascending order for the $p$-value.
+In the Figures \ref{fig:rvsR}-\ref{fig:svss} are shown the correlations that are significant.
+
+The Figure \ref{fig:rvsR} shows the strongest correlation, being this between the correlation length $r_0$ and the size $R$ of the region.
+
+\input{Corr}
+
+\begin{figure}
+\centering 
+\includegraphics[width=3in]{Figures/rvsR}
+\caption{The log $r_0$-log $R$ plane derived form our results an data in the literature.
+A fit with slope of 0.67$\pm$0.07 is shown in solid black line that is the mean of all red lines that reflect the posterior of the Bayessian analysis.
+}
+\label{fig:rvsR}
+\end{figure}
+
+\begin{figure}
+\centering 
+\includegraphics[width=3in]{Figures/svsL}
+\caption{Same as Fig. \ref{fig:rvsR} but for the log $\sigma$-log $L(H_{\alpha})$ plane.}
+\label{fig:sigvsl}
+\end{figure}
+
+\begin{figure}
+\centering 
+\includegraphics[width=3in]{Figures/svss.pdf}
+\caption{Same as Fig. \ref{fig:rvsR} but for the log $\sigma$-log $\sigma_{LOS}$ plane.}
+\label{fig:svss}
+\end{figure}
+
+\subsubsection{Relationship between plane-of-sky and line-of-sight velocity dispersion.}
+
+The analysis employed until now is not conclusive about the true velocity fluctuations observed in each nebula. 
+As pointed out by \citet{arthur2016turbulence} other techniques also allow us to study these fluctuations. 
+Following their procedure, it is possible to see from Table \ref{tab:Res} that the line-of-sight velocity dispersion is roughly twice the plane-of-sky velocity dispersion.
+In the case of homogeneous turbulent velocity we can consider the effect of 'project smearing', \citet{arthur2016turbulence} and reference therein, where the projection from three to two dimensions over a line-of-sight depth \(H\) reduces the plane-of-sky amplitude if \(r_{0} < H\).
+With a value of \(\sigma / \sigma_{LOS}\) = 0.5 we obtain \(r_{0} / H \approx\) 0.02-0.1 \citep{1984ApJ...277..556S}.
+
 \subsection{Comparison with previous structure functions}
@@
 Since this is the first time this method is applied to a sample of HII regions (at least for our knowledge), the results are bounded to be different from previous investigations, including the one that have the same observations as \citet{arthur2016turbulence} and \citet{2019arXiv191203543M}.
-We will focus on the interpretation of each investigation results and leave the comparison of values as second issue.
 
@@
 The power-law index obtained by \citet{arthur2016turbulence} are \(m \sim 1.2 \pm 0.1\) for \halpha\ and [OIII] emission lines and for [SII] they found \(m \sim 0.8 \pm 0.1\). 
-The correlation length for all lines is \(\approx\) 0.05 pc. For the same \halpha\ observation we obtained a value of 1.44 and a correlation length of 0.062 pc. 
-As a comparison for the large scales \citep{1987A&A...176..347H} the value is 0.9 with a considerable agreement with previous results. 
-The change in the index could be attributed to the multiple scales of energy injection that are present in the nebula.
+The correlation length for all lines is \(\approx\) 0.05 pc. For the same \halpha\ observation we obtained a value of 1.06$\pm$0.01 and a correlation length of 0.092$\pm$0.007 pc.
 
@@
 There is a good agreement with the single-Gaussian fit results from \citet{2019arXiv191203543M} (Figure 15 Top on their work), while \citet{1961MNRAS.122....1F} results do not overlap with ours.
-From the previous this is the first time turbulence structure is found in 30 Doradus through the structure function.
+From this analysis this is the first time turbulence characterized in 30 Doradus using the structure function.
 
-There is broad agreement in our results and previous studies considering NGC 604 from \citet{tanco1997} and \citet{2019arXiv191203543M}, and using the same TAURUS-II data.
+There is broad agreement in our structure function results and previous studies that consider NGC 604, mainly because where are using the same data \citep{tanco1997,2019arXiv191203543M}. 
+from \citet{tanco1997} and \citet{2019arXiv191203543M}, and using the same TAURUS-II data.
 Despite this general agreement the interpretations in each study is different.
@@
 
-\subsection{Correlations between physical properties and turbulent parameters}
-
-As we mentioned in the introduction, the scaling relations between parameters like size and luminosity are common tools to study HII regions along dwarf galaxies and high-redshift star formation regions; in the past those relationships, particularly in GEHRs, made them candidates as standard candles.
-We apply these methods with the turbulent parameters \(r_0\) and index \(m\).
-
-Using the first three columns in Tables \ref{tab:Reg} and \ref{tab:Res}, we obtain the Pearson correlation coefficient $r$.
-Between luminosity (L) and \(\sigma\) it is 0.71, between distance (D) and \(m\) the value is 0.73, and finally between size (R) and \(r_0\) we have 0.96.
-By means of a significance test and assuming that a uncorrelated sample produces our results, for the first two relationships we have a probability value $p$ of 0.02 and for the remaining one of <10\(^{-5}\).
-Applying and ordinary least-square regression (OLS) we find a form Y = aX + b; this values along the previous ones is shown in Table \ref{tab:RestStats}.
-
-The relationship between L vs \(\sigma\) is one of the most studied. 
-This relationship help us understanding how the star formation affects the gas motions and how star formation is regulated by feedback processes. 
-Figure \ref{fig:sigvsl} shows different studies of the L vs \(\sigma\) relationship \citep{1988A&A...201..199A,Rozas:2006b,2015MNRAS.449.3568M}. 
-In this case it is normally used the deconvolution of the observed lines taking account thermal broadening and instrumental broadening leaving the \(\sigma_{LOS}\). 
-For the data present in Figure \ref{fig:sigvsl}, excluding \(\sigma_{POS}\), we obtain using the same OLS \(log \sigma_{LOS} = 0.145 \pm 0.008 (logL_{H\alpha}) - (4.42 \pm 0.336) \).
-Since the R-squared is 0.596 it is not possible just to invert the OLS results for a comparison with the more classical relationship.
-Inverting axes we obtain \(log L_{H\alpha} = 4.09 \pm 0.23 log (\sigma_{LOS}) + (34.17 \pm 0.32) \), being in accord to previous relationships.
-
-It is also possible to use our results from Table \ref{tab:Res} for a comparison with other relationship, in this case considering the separation \(r\).
-Using the mean slope index \(\langle m \rangle \), 1.4, we can assume \(\Delta V^{2} \propto r^{1.4} \) and obtain \(r \propto V^{1.5} \), close to what previous studies have determined.
-
-\begin{table*}
-\begin{center}\caption{Parameters of the linear regression (Y = aX + b).}
-\begin{tabular}{cccccc}\hline
-Y                    &X         &a               &b                &r     & p                \\ \hline
-log \(r_0\)          &log \(R\) &0.65\(\pm\)0.06 &-0.83\(\pm\)0.11 & 0.96 & <10\(^{-5}\)    \\ 
-log \(\sigma\)       &log \(L\) &0.16\(\pm\)0.05 &-5.54\(\pm\)2.13 & 0.71 & 0.02             \\
-log \(m\)            &log \(D\) &0.05\(\pm\)0.02 &-0.05\(\pm\)0.03 & 0.73 & 0.02  \\ 
-*log \(\sigma_{LOS}\) &log \(L\) &0.145\(\pm\)0.008 &-4.42\(\pm\)0.33 & 0.77 & <10\(^{-5}\)  \\ 
-*log \(L\) &log \(\sigma_{LOS}\) &4.09\(\pm\)0.23 &34.17\(\pm\)0.32 & 0.77 & <10\(^{-5}\)  \\ 
-log \(\sigma\)       &log \(\sigma_{LOS}\) &0.72\(\pm\)0.27 &-0.14\(\pm\)0.31 &0.68 & 0.02 \\ \hline
-\end{tabular}\label{tab:RestStats}
-\end{center}
-\end{table*}
-
-\begin{figure}
-\centering 
-\includegraphics[width=3in]{Figures/lvss.pdf}
-\caption{}
-\label{fig:sigvsl}
-\end{figure}
-
-\subsection{Relationship between plane-of-sky and line-of-sight velocity dispersion.}
-
-The analysis employed until now is not conclusive about the true velocity fluctuations observed in each nebula. 
-As pointed out by \citet{arthur2016turbulence} other techniques also allow us to study these fluctuations. 
-Following their procedure, it is possible to see from Table \ref{tab:Res} that the line-of-sight velocity dispersion is roughly twice the plane-of-sky velocity dispersion.
-In the case of homogeneous turbulent velocity we can consider the effect of 'project smearing', \citet{arthur2016turbulence} and reference therein, where the projection from three to two dimensions over a line-of-sight depth \(H\) reduces the plane-of-sky amplitude if \(r_{0} < H\).
-With a value of \(\sigma / \sigma_{LOS}\) = 0.5 we obtain \(r_{0} / H \approx\) 0.02-0.1 \citep{1984ApJ...277..556S}.
-
-%Trying to answer if the observed turbulence can account for the non-thermal line broadening can be used as a diagnostic...
-
-\begin{figure}
-\centering 
-\includegraphics[width=2in]{Figures/sigmas.pdf}
-\caption{Log \(\sigma_{LOS}\) vs Log \(\sigma\) plot.
-The values are taken from Table \ref{tab:Res}.
-The solid-gray line indicate one-to-one correlation and the dotted-black line indicate the relation in Table \ref{tab:RestStats}.
-The size of the markers indicate the distance to the region, the bigger the marker the farther the region.
-}
-\label{fig:sigvssig}
-\end{figure}
-
-\subsection{What turbulence scales can tell us about kinematics of the ionized gas?}
-
-In the Table \ref{tab:ResII} the second column show the separation where the value 2\(\sigma\) is reached.
-We also show the ratio \(r_{max}/r_{0}\), where \(r_{max}\) is the maximum separation or lag in pc; this value is related to the size of each sample box. 
-The forth column shows the Taylor scale, \(l_T\), which measures the average spatial extent of velocity gradients. \citet{1999ApJ...524..895M} define this scale as:
-
-\begin{equation}\label{eq:TS}
-l_T=\dfrac{\sigma r_s}{\sigma_{r_s}}
-\end{equation}
-
-where \(r_s\) is the smallest separation \(r\) and \(\sigma_{r_s}\) the value of the structure function at that separation.
-
-It is possible to calculate how this Taylor micro-scale is related to the correlation length by:
-
-\begin{equation}\label{eq:TS1}
-l_T=\dfrac{r_s}{\sqrt{2}}(\dfrac{r_0}{r_s})^{m/2}
-\end{equation}
-
-Finally in the table we present the Reynolds Number...
-
-\begin{table}
-\begin{center}\caption{Other significant turbulent scales}
-\begin{tabular}{cccccc}\hline
-HII         &r$_{2\sigma}$ &\(r_{max}\)/\(r_0\)  &\(l_T\) & \(Re\)* \\
-Region      &[pc]          &                     &[pc]    &   \\ \hline
-NGC 604     &28.73         &15.49                &5.35    &   \\
-NGC 595     &18.50         &21.01                &5.57    &   \\
-Hubble V    &11.61         &19.95                &1.80    &   \\ 
-Hubble X    &21.99         &21.67                &1.97    &   \\   
-30 Dor      &11.26         &8.99                 &0.59    &   \\
-Carina      &1.93          &31.55                &0.402   &   \\
-NGC 346     &5.78          &10.73                &0.39    &   \\
-Lagoon      &6.14          &10.68                &0.66    &   \\ 
-Orion Large &-             &2.98                 &0.24    &   \\
-Orion Small &0.162         &10.42                &0.019   &   \\ \hline	  
-\end{tabular}\label{tab:ResII}
-\end{center}
-\end{table}
-
-With the aim to relate each \(r_0\) with each region we invoke previous studies on the kinematics of the ionized gas. 
-\citet{sabalisck1995supersonic} studied NGC 604 revealing that the kinematics of the region behave different considering different scales.
-High emission knots on the region encompasses supersonic global velocity dispersion values of 14 $<$ \(\sigma_{LOS}\) $<$ 20 km s\(^{-1}\).
-This knots are well fitted with Gaussian profiles thus, defining the kinematic core \citep{munoz1996}.
-A characteristic radius for them is \(\sim\) 7 pc.
-\citet{yang1996} identified 5 expanding shells within NGC 604, and one of them (Shell 3 on their paper) fall into our observations.
-This shells is 40 pc in diameter with an expansion velocity above 50 km s\(^{-1}\).
-This scales are related to the presence of strong stellar winds caused by massive stars.
-For the NGC 604 case, there is no clear relation between the \(r_0\) and some particular energy injection mechanism...
-%it is also the nearest analog of more extreme star-forming regions, such as 30 Doradus in the Large Magellanic Cloud.
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-%\begin{enumerate}
-%    \item The giant HII regions in  M 33, NGC 604 and NGC 595 shows an index of 1.7 and 1.55, respectively.
+The previous analysis was able to characterize the turbulence by determining a single inertial scale where the ionized gas behavior can be described by means of a power law.
+To determine the inertial scale more precisely than in previous works, a new functional form was proposed for the second-order structure function that considers observational effects such as: seeing, noise and the size of the observational box.
+These effects had not been considered in detail before and have important consequences is the interpretation of the inertial scale.
 
-%    \item The structure functions are presented for the first time for Hubble X and Hubble V, in NGC 6822.
-Hubble V shows and index of 1.65 and a correlation length of 3 pc, while Hubble X results are 1.6 and 4 pc.
+The new functional form of the structure function accurately determines the important parameters related to turbulence which are: the correlation length, the exponent of a power law that fits the results and the real variance of the region.
+Compared to the majority of previous works, the previous parameters had been calculated using the criteria of each author.
+A chi-square adjustment was performed using Bayesian statistics to determine the confidence intervals for each parameter.
 
-%    \item The structure function of 30 Dor is presented for the first time using high-resolution observations that allows to observe scales $>$0.1 pc.
-A correlated structure function is obtained with a correlation lenght of 2.7 pc and a power-law index of 1.15.
-This new results show that previous studies on 30 Dor structure functions were analyzing large scales where no velocity fluctuations are present.
+This proposed analysis can be expanded to other HII regions with the possibility of comparing the results between them since the proposed method guarantees their homogeneity and the ability to develop a future catalog of these regions in a coherent way.
+It could even be used to investigate the velocity fields of other phases of the interstellar medium.
+The study of turbulence between ionized regions and the molecular clouds that give them birth can be carried out in a concise way, having the correct methods with the intention of advancing the understanding of the kinematic relationships between them.
 
-%\end{enumerate}
+\begin{enumerate}
+\item For 30 Doradus with an observational box size of 32 pc an index of 0.84$\pm$0.03 is obtained with an inertial scale between 0.1 and 5 pc, and with a variance of 350$\pm$21 km$^2$/s$^2$.
+
+\item For NGC 604 with an observational box size of 173 pc an index of 0.82$\pm$0.20 is obtained with an inertial scale between 2 and 9 pc, and with a variance of 81$\pm$25 km$^2$/s$^2$.
+
+\item For NGC 595 with an observational box size of 196 pc an index of 1.3$\pm$0.04 is obtained with an inertial scale between 0.5 and 12 pc, and with a variance of 56$\pm$1.6 km$^2$/s$^2$.
+
+\item For NGC 346 with an observational box size of 20 pc an index of 0.78$\pm$0.02 is obtained with an inertial scale between 0.06 and 2 pc, and with a variance of 38$\pm$1.0 km$^2$/s$^2$.
+
+\item For Orion small with an observational box size of 0.45 pc an index of 1.06$\pm$0.02 is obtained with an inertial scale between 0.002 and 0.09 pc, and with a variance of 17$\pm$1.0 km$^2$/s$^2$.
+
+\item For Carina with an observational box size of 20 pc an index of 1.36$\pm$0.30 is obtained with an inertial scale between 0.008 and 0.6 pc, and with a variance of 17$\pm$1.0 km$^2$/s$^2$.
+
+\item For Hubble X with an observational box size of 78 pc an index of 0.94$\pm$0.12 is obtained with an inertial scale between 0.5 and 4 pc, and with a variance of 15.5$\pm$1.5 km$^2$/s$^2$.
+
+\item For Hubble V with an observational box size of 61 pc an index of 0.72$\pm$0.09 is obtained with an inertial scale between 0.5 and 3 pc, and with a variance of 10.6$\pm$0.8 km$^2$/s$^2$.
+
+\item For Lagoon with an observational box size of 16 pc an index of 1.12$\pm$0.09 is obtained with an inertial scale between 0.005 and 1 pc, and with a variance of 7.2$\pm$0.8 km$^2$/s$^2$.
+
+\item For Orion large with an observational box size of 3 pc an index of 1.72$\pm$0.24 is obtained with an inertial scale between 0.1 and 0.7 pc, and with a variance of 6$\pm$0.5 km$^2$/s$^2$.
+
+\end{enumerate}
 
@@
 
-%\section{Velocity maps}\label{sec:VelMaps}
-
-%The Figures \ref{fig:M604}-\ref{fig:MOrion} show the two-dimensional radial velocity map of each region.
-
-%\begin{figure}
-%\centering 
-%\includegraphics[width=2.5in]{Figures/M6T}
-%\caption{Radial velocity maps of NGC 604 in H$\alpha$.  }
-%\label{fig:M604}
-%\end{figure}
-
-%\begin{figure}
-%\centering 
-%\includegraphics[width=2.5in]{Figures/M5T}
-%\caption{Radial velocity map of NGC 595 in H$\alpha$.}
-%\label{fig:M595}
-%\end{figure}
-
-%\begin{figure}
-%\centering 
-%\includegraphics[width=2.5in]{Figures/MV}
-%\caption{Radial velocity map of Hubble V in H$\alpha$.}
-%\label{fig:MHV}
-%\end{figure}
-
-%\begin{figure}
-%\centering 
-%\includegraphics[width=2.5in]{Figures/MX}
-%\caption{Radial velocity map of Hubble X in H$\alpha$.}
-%\label{fig:MHX}
-%\end{figure}
-
-%\begin{figure}
-%\centering 
-%\includegraphics[width=2.5in]{Figures/M30D}
-%\caption{Radial velocity map of 30 Dor in H$\alpha$ \citep{Castro:2018a}.}
-%\label{fig:M30Dor}
-%\end{figure}
-
-%\begin{figure}
-%\centering 
-%\includegraphics[width=2.5in]{Figures/Car}
-%\caption{Radial velocity map of Carina in H$\alpha$ taken from \citet{Damiani:2016a}.}
-%\label{fig:MCar}
-%\end{figure}
-
-%\begin{figure}
-%\centering 
-%\includegraphics[width=3in]{Figures/M8H.png}
-%\includegraphics[width=3.5in]{Figures/M8}
-%\caption{Radial velocity map of M8 in H$\alpha$. Taken from \citep{Damiani:2017b} and \citet{1987A&A...176..338H}.}
-%\label{fig:MM8}
-%\end{figure}
-
-%\begin{figure}
-%\centering 
-%\includegraphics[width=3in]{Figures/OrionL}
-%\caption{Radial velocity map of Orion in H$\alpha$ taken from \citet{1987A&A...176..347H}.}
-%\label{fig:MOrion}
-%\end{figure}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2021-11-26 Corr.tex
Javier changes 2021-11-26

@@
 \hline
-            Y &                   X &                 a &                 b &       $r$ &      $p$ \\
+            $Y$ &                   $X$ &                 $a$ &                 $b$ &       $r$ &      $p$ \\
 \hline
-    log $r_0$ &             log $R$ &    0.67$\pm$0.071 &  -0.798$\pm$0.127 &   0.978 &   <10\(^{-5}\) \\
- log $\sigma$ &            log L(H) &   0.175$\pm$0.094 &  -6.032$\pm$3.649 &   0.711 &  0.021 \\
- log $\sigma$ &  log $\sigma_{LOS}$ &   0.793$\pm$0.457 &  -0.186$\pm$0.526 &   0.662 &  0.037 \\
-      log $m$ &            log Dist &  -0.135$\pm$0.094 &   1.262$\pm$0.182 &  -0.603 &  0.065 \\
- log $\sigma$ &         log $r_{0}$ &    0.219$\pm$0.19 &    0.65$\pm$0.122 &    0.53 &  0.115 \\
-      log $m$ &        log $\sigma$ &   -0.196$\pm$0.26 &   0.154$\pm$0.194 &  -0.431 &  0.214 \\
-      log $m$ &         log $r_{0}$ &   -0.056$\pm$0.09 &   0.027$\pm$0.059 &  -0.364 &  0.301 \\
+    log $r_0$ &             log $R$ &   0.691$\pm$0.079 &   -0.85$\pm$0.148 &   0.984 &    <10\(^{-5}\) \\
+ log $\sigma$ &            log L(H) &   0.166$\pm$0.129 &  -5.698$\pm$5.002 &    0.64 &  0.06 \\
+ log $\sigma$ &  log $\sigma_{LOS}$ &    0.749$\pm$0.62 &  -0.132$\pm$0.729 &   0.575 &  0.10 \\
+ log $\sigma$ &         log $r_{0}$ &   0.195$\pm$0.207 &   0.679$\pm$0.139 &   0.493 &  0.17 \\
+      log $m$ &            log Dist &   -0.07$\pm$0.091 &   1.113$\pm$0.185 &  -0.436 &  0.24 \\
+      log $m$ &         log $r_{0}$ &  -0.031$\pm$0.086 &  -0.001$\pm$0.059 &  -0.295 &  0.44 \\
+      log $m$ &        log $\sigma$ &  -0.094$\pm$0.264 &   0.061$\pm$0.204 &  -0.241 &  0.53 \\
 \hline

### 2021-11-26 strucfunc_paper.tex
Corrections to LaTeX markup of equations
Javier changes 2021-11-26

@@
 
-We use data from \citet{1987A&A...176..347H} and \citet{arthur2016turbulence} to study of turbulence in the Orion Nebula.
-\cite{1987A&A...176..347H} observations were obtained using a 106 cm-Cassegrain telescope at Observatorium Hoher List. 
-A Fabry-Pérot interferometer was used with a étalon a separation of 0.5 mm. 
-Interferograms have been taken with different pointing directions of the telescope's optical axis in the nebula. 
-The exposures are overlapped and fall into one square of a grid with a width of 1' centered at \(\theta^{1}\)Ori C.
+%We use data from \citet{1987A&A...176..347H} and \citet{arthur2016turbulence} to study of turbulence in the Orion Nebula.
+%\cite{1987A&A...176..347H} observations were obtained using a 106 cm-Cassegrain telescope at Observatorium Hoher List. 
+%A Fabry-Pérot interferometer was used with a étalon a separation of 0.5 mm. 
+%Interferograms have been taken with different pointing directions of the telescope's optical axis in the nebula. 
+%The exposures are overlapped and fall into one square of a grid with a width of 1' centered at \(\theta^{1}\)Ori C.
 
-\citet{arthur2016turbulence} observations were initially published by \citet{2008RMxAA..44..181G}. 
+We use data from \citet{arthur2016turbulence} to study of turbulence in the Orion Nebula.
+Their observations were initially published by \citet{2008RMxAA..44..181G}. 
 The data was obtained with the echelle spectrograph attached to the 4 m telescope at Kitti Peak National Observatory (KPNO).
@@
 \begin{tabular}{ccccc}\hline
-HII       &  Distance (D)          & Diameter (R) & log L(H$_{\alpha}$) &  \(\langle \sigma_{LOS} \rangle \) \\
+HII       &  Distance ($D$)          & Diameter ($R$) & log L(H$_{\alpha}$) &  \(\langle \sigma_{\text{LOS}} \rangle \) \\
 Region    &  [kpc]          &  [pc]    &  [erg/s]            &    [km/s]  \\ 
 \hline
-Orion small   & 0.436$\pm$0.02  & 0.6  &    37               &   6.0      \\
-Orion large   & 0.436$\pm$0.02  & 5    &    37               &   6.0      \\ 
-Lagoon    & 1.25$\pm$0.12   & 25       &    37.47            &   13.6     \\
-Carina    & 2.35$\pm$0.05   & 15       &    39.6             &   22.4     \\
-30 Dor    & 49.97$\pm$0.19  & 98.9     &    39.76            &   31.7     \\
-NGC 346   & 61.9$\pm$1.1    & 64       &    38.67            &   10.2     \\
-Hubble X  & 490$\pm$40      & 160      &    38.6             &   13.4     \\
-Hubble V  & 490$\pm$40      & 130      &    38.87            &   12.3     \\
-NGC 604   & 820$\pm$30      & 400      &    39.65            &   16.2     \\
-NGC 595   & 820$\pm$30      & 400      &    39.36            &   18.3     \\
+Orion    & 0.436$\pm$0.02  & 0.6$\pm$0.06  &    37               &   6.0      \\
+%Orion large   & 0.436$\pm$0.02  & 5$\pm$0.5    &    37               &   6.0      \\ 
+Lagoon    & 1.25$\pm$0.12   & 25$\pm$2.5       &    37.47            &   13.6     \\
+Carina    & 2.35$\pm$0.05   & 15$\pm$1.5       &    39.6             &   22.4     \\
+30 Dor    & 49.97$\pm$0.19  & 98.9$\pm$9.8     &    39.76            &   31.7     \\
+NGC 346   & 61.9$\pm$1.1    & 64$\pm$6.4       &    38.67            &   10.2     \\
+Hubble X  & 490$\pm$40      & 160$\pm$16      &    38.6             &   13.4     \\
+Hubble V  & 490$\pm$40      & 130$\pm$13 &    38.87            &   12.3     \\
+NGC 604   & 820$\pm$30      & 400$\pm$40      &    39.65            &   16.2     \\
+NGC 595   & 820$\pm$30      & 400$\pm$40      &    39.36            &   18.3     \\
 \hline
@@
 
-The classic turbulence theory \citep{kolm1} assumes a three-dimensional isotropic, incompressible and subsonic flow where an energy cascade is taking place.
-The energy cascade goes from the largest vortices where the energy in injected until it reaches dissipation with the smallest vortices.
-In the energy cascade three scales are defined based on their Reynolds number.
-The energy injection scale (Re $\rightarrow \infty$), $L_{EI}$, the dissipation scale (Re $\rightarrow$ 1), $L_{D}$ and the inertial scale, $L_{I}$, between the previous two.
-Since the energy distributions depends on the scale, the energy cascade concept is described with an energy spectrum, $E(k) \propto k$ where $k$ is the wave number for a determined scale $l$ ($k \equiv r^{-1}$).
+The existence of turbulent flows in astrophysical objects, ranging in scales from 10$^{6}$ to 10$^{17}$ m \citep{2010ApJ...710..853C} is the consequence of the high Reynolds numbers, $Re$, between 10$^{4}$ and 10$^{9}$ \citep{1949ApJ...110..329C,lagrois2011} that characterized these objects.
+The classic turbulence theory assumes a three-dimensional isotropic, incompressible and subsonic flow that can be described using an energy spectrum \citep{kolm1}.
+The concept of the energy spectrum is based on the assumption that the energy is cascading down inside the flow from the largest to the smallest scales.
+The different scales in the energy cascade are defined based on their $Re$.
+In one side of the spectrum there is the energy, \(L\), injection scale that is related to the largest vortices, where $ Re \rightarrow \infty$.
+On the other side of the spectrum there is the dissipation of energy at small scales, \(l\), where $Re \rightarrow$ 1 and it is assumed that small vortices are responsible for the friction that dissipates the energy flux into thermal energy.
+In between there is the inertial range, \(l  << r << L\) , where in a stationary case there energy transfer is at a constant rate,.
+The energy cascade concept is described with an energy spectrum, $E(k) \propto k^{\beta}$ where $k$ is the wave number for a determined scale $r$ ($k \equiv r^{-1}$).
 
-The total specific energy of a determined $l$ scale is of the order $\langle v_{l}^{2} \rangle$ and is the energy integral above the associated $k$, defined as:
-
-\begin{equation}\label{eq:veles}
- \langle v_{l}^{2} \rangle = \int_{k}^{\infty} E(k)dk
+The total specific energy of a determined $r$ scale is of the order $\langle v_{r}^{2} \rangle$ and is the energy integral above the associated $k$, defined as:
+\begin{equation}\label{eq:energyspectrum}
+ \langle v_{r}^{2} \rangle = \int_{k}^{\infty} E(k)dk
 \end{equation}
-
-This energy is of the order of $(\epsilon l)^{\frac{2}{3}} \sim (\frac{\epsilon}{k})^{\frac{2}{3}}$. From the above equation we obtain the Kolmogorov law:
+%
+It is assumed that this energy is of the order of $(\epsilon r)^{\frac{2}{3}} \sim (\frac{\epsilon}{k})^{\frac{2}{3}}$ we differentiate Equation \ref{eq:energyspectrum} and obtained the final form of the spectrum:
 
@@
 \end{equation}
+%
+where \(\epsilon\) is the energy transfer rate and the value of $\beta = -5 / 3$ is the Kolmogorov index.
+%For supersonic turbulence the index is $\beta=-2$ \citep{burg}.
 
-For Kolmogorov turbulence $\beta = -5 / 3$, and for supersonic turbulence the index is $\beta=-2$ \citep{burg}.
+\subsection{The second-order structure function}
 
-\subsection{The second order structure function}
+One of the fundamental properties of turbulent clouds must be spatial fluctuations in velocity and density .
+These fluctuations are observed as projected spatial fluctuations in the average line-of-sight velocity and integrated column density.
+It is possible to describe the statistical properties of these fluctuations if they are assumed as a product of a stochastic field \citep{1984ApJ...277..556S}. 
+This previous assumption give us the ability to apply statistical tools to the velocity field and the analysis of the velocity pattern is reduced to the calculation of the averages and correlations.
 
-One of the fundamental properties of turbulent clouds must be spatial fluctuations in velocity and density \citep{1984ApJ...277..556S}.
-They are observed as projected spatial fluctuations in the average line-of-sight velocity and integrated column density.
-By means of describing the statistical properties of these fluctuations they can be assumed as a product of a stochastic field statistical tools.
-
-The statistical function we use to study the velocity field of the HII regions is the second-order structure function, $B(r)$, defined as:
+The second-order structure function of the velocity centroids, $B(r)$, is defined as:
 
 \begin{equation}\label{eq:Br}
-B(\boldsymbol{r})=\dfrac{\sum[V_{r}(\boldsymbol{x}+\boldsymbol{r})-V_{r}(\boldsymbol{x}) ]^{2}}{N(\boldsymbol{r})}
+B(\boldsymbol{r}) = \dfrac{\sum_{\text{pairs}}[V_{c}(\boldsymbol{x} + \boldsymbol{r}) - V_{c}(\boldsymbol{x}) ]^{2}} {N(\boldsymbol{r})}
 \end{equation}
+%
+where $N(\boldsymbol{r})$ is the number of pair points at each separation \(\boldsymbol{r}\), called lag. 
+In the Kolmogorov model \(B(r) \propto r^{2/3}\).
 
-where, $V_{r}(\boldsymbol{x})= V_{obs}(\boldsymbol{x})-\langle V_{obs}(\boldsymbol{x}) \rangle$ and N($\boldsymbol{r}$) is the number of points at each separation \(r\), called lag.
+The variance of the centroid velocity fluctuations is:
 
-As a justification for the use of the structure function we can consider that any relation between the line width and line-of-sight depth can be interpreted in terms of a correlation between velocity spread and scale size.
-This follows if we have an optically thin spectral line where it will have a width which is related to the total radial velocity dispersion of all fluctuations sampled along the line-of-sight \citep{1984ApJ...277..556S}.
-In these sense the structure function is used as a tool to investigate the projection of a three-dimensional correlation function onto the plane of sky \citep{arthur2016turbulence}.
+\begin{equation}\label{eq:variance}
+\sigma^2  = \frac{\sum_{\text{pixels}}[ V_c (\boldsymbol{x}) -\langle V_ c\rangle  ]^2}{N}
+\end{equation}
+%
+the, \(\langle V_c \rangle \) is the mean centroid velocity
+
+\begin{equation}\label{eq:mean}
+\langle V_c \rangle \  = \frac{\sum_{\text{pixels}}[ V_c (\boldsymbol{x})]}{N}
+\end{equation}
+%
+The summation in Equation \ref{eq:Br} is over all data pairs for each separation \(N(\boldsymbol{r})\).
+The summations in Equations \ref{eq:variance} and \ref{eq:mean} are over the total number of valid pixels in the (\textit{x},\textit{y})-plane.
 
@@
 
-We use the functional form of the structure function in terms of the autocorrelation function:
+The autocovariance function is:
 
-\begin{equation}\label{eq:ff}
-b(r;r_0,m) = 2\sigma^2(1-C(r))
+\begin{equation}\label{eq:Cr}
+C(\boldsymbol{r}) = \dfrac{\sum_{\text{pairs}}[V_{c}(\boldsymbol{x} + \boldsymbol{r}) \times V_{c}(\boldsymbol{x}) ]} {N(\boldsymbol{r})}
+\end{equation}
+%
+and is another statistical tool used in studying the turbulent flows.
+The interpretation of the Equation \ref{eq:Cr} depends on the assumption of homogeneity, which may be violated for astrophysical processes.
+Because of this, Equation \ref{eq:Br} is a better approach to characterize the velocity fluctuations even in the presence of large scale linear gradients and may be sensitive to a wider range of scales \citep{1984ApJ...277..556S}.
+
+For the homogeneous random field, Equations \ref{eq:Br} and \ref{eq:Cr} are related by:
+
+\begin{equation}\label{eq:functional}
+B(r) = 2\sigma^2 \bigl( 1 - C(r) \bigr)
 \end{equation}
 
-where $C(r)$ is a new form of the autocorrelation function in the form:
-
+Based on Equation \ref{eq:functional} we use the functional of the structure function in the form:
+%
+\begin{equation}\label{eq:ff}
+b(r; r_0, m) = 2\sigma^2 \bigl( 1 - C(r) \bigr)
+\end{equation}
+%
+where $C(r)$ is now the new form of the autocorrelation function in the proposed form:
+%
 \begin{equation}\label{eq:ffnew}
-C(r) = exp[-ln2(\frac{r}{r_0})^m]
+  C(r) = \exp \left[ -(\ln 2) \left( \frac{r}{r_0} \right)^m \right]
 \end{equation}
-
-substituing the previourly form $C(r)=1/[1+(r/r_{0})^{m}]$ \citep{1984ApJ...277..556S,arthur2016turbulence}.
+%
+substituting the previously $C(r)=1/[1+(r/r_{0})^{m}]$ \citep{1966igd..book.....K,1984ApJ...277..556S}.
 
@@
 The model proposed to describe the seeing at small scales is:
-
+%
 \begin{equation}\label{eq:ffs}
-S(r; s_0, r_0) = \frac{e^\frac{-s_0}{r_0}}{1+(\frac{2s_0}{r})^\frac{2}{3}}
+  S(r; s_0, r_0) = \frac{
+    e^{-s_0 / r_0}
+  }{
+    1+(2s_0 / r)^{2 / 3}
+  }
 \end{equation}
-
+%
 and the model that consider the effect of the observational box size is:
@@
 \begin{equation}\label{eq:ffb}
-\beta(r_0) = 1 - exp[\frac{L_{box}}{3.6r_0}] 
+% \beta(r_0) = 1 - exp[\frac{L_{box}}{3.6r_0}] 
+  \beta(r_0) = 1 - \exp \left[ -L_{\text{box}} / (3.6 r_0) \right] 
 \end{equation}
-
-where $L_{box}$ is the diagonal length of the observational box.
+%
+where $L_{\text{box}}$ is the diagonal length of the observational box.
 
 The final form of our proposed functional of the structure function is in the form:
-
+%
 \begin{equation}\label{eq:fff}
-B(r) = b(r; \beta r_0, \beta m)*S(r; s_0, r_0)+B_{noise}
+B(r) = b(r; \beta r_0, \beta m) \times S(r; s_0, r_0) + B_{\text{noise}}
 \end{equation}
@@
 We use equation \ref{eq:fff} in a chi-square analysis applying the equation:
-
+%
 \begin{equation}\label{eq:chi}
-\chi^2 = \sum_i ^N \frac{[y_i^{measure}-y_i^{model} (\boldsymbol{v})]^2}{\epsilon_i ^2}
+  \chi^2 = \sum_i ^N \frac{[y_i^{\text{measure}}-y_i^{\text{model}} (\boldsymbol{v})]^2}{\epsilon_i ^2}
 \end{equation}
-
+%
 using the package \textit{lmfit} \citep{newville_matthew_2014_11813}.
@@
 
+The true variance of the velocity fields obtained with the analysis in Section \ref{sec:apply} is shown in the second column in Table \ref{tab:Res}. 
+For all regions except for Carina and Lagoon there is an slight increase in the value of $\sigma$.
+
 %The highest \(\sigma\) is 15.8 km s\(^{-1}\) for 30Dor.
@@
 \subsubsection{Structure function power indices \(m\)}
+
+%As a justification for the use of the structure function we can consider that any relation between the line width and line-of-sight depth can be interpreted in terms of a correlation between velocity spread and scale size.
+%This follows if we have an optically thin spectral line where it will have a width which is related to the total radial velocity dispersion of all fluctuations sampled along the line-of-sight \citep{1984ApJ...277..556S}.
+%In these sense the structure function is used as a tool to investigate the projection of a three-dimensional correlation function onto the plane of sky \citep{arthur2016turbulence}.
 
@@
 Following the procedure by \cite{arthur2016turbulence} and assuming the relationship m$_{2D}$ - 1 $<$ m$_{3D}$ $<$ m$_{2D}$ we have 0.36 $<$ m$_{3D}$ $<$ 0.72.
-Though \cite{arthur2016turbulence} are comparing emission lines and not regions, we can conclude that the index \(m\) still is far away as a unique parameter for measuring turbulence on ionized regions.
 
@@
 Since it is unclear what are the mechanisms driving the turbulence, thought a lot of options are candidates, it is difficult to pinpoint one particular process as the main responsible. 
-The possibility that the correlation length reveals the answer to the cause of observed motions is a long shot, but it is clear that each velocity field has a corresponding \(r_0\) value. 
 The range covered in our results goes from 0.09 to 11 pc.
@@
 Scaling relations between parameters like size and luminosity are common tools to study HII regions, along dwarf galaxies and high-redshift star formation regions.
-\citet{melnick1977,terlevich1981} were the first to shown an empirical relationship between the line width and the integrated properties of the HII regions as the diameter or the luminosity ($r \sim \sigma ^{\sim 2}$ ; $L_{H} \sim \sigma ^{\sim 4}$).
+\citet{melnick1977,terlevich1981} were the first to shown an empirical relationship between the line width and the integrated properties of the HII regions as the diameter or the luminosity ($r \sim \sigma ^{\sim 2}$ ; $\text{L}_{\text{H}} \sim \sigma ^{\sim 4}$).
 They conclude that GEHRs follow this relations as self-gravity systems like globular clusters or elliptical galaxies.
-The work of \citet{1988A&A...201..199A} confirmed these relationships considering the discrepancies of previous investigations obtaining \(L_{H_{\alpha}} \propto \sigma^{3.9}\) and \(r \propto \sigma^{1.84}\).
-\citet{2012MNRAS.422.3339W} have found that clumps and HII regions follow scaling relations over the range of z = 0-2 for \halpha\ size, velocity dispersion, luminosity and mass, finding \(\sigma \propto r^{0.42}\), \(L_{H_{\alpha}} \propto r^{2.72}\) and \(L_{H_{\alpha}} \propto \sigma^{4.18}\).
+The work of \citet{1988A&A...201..199A} confirmed these relationships considering the discrepancies of previous investigations obtaining \(\text{L}_{\text{H}_{\alpha}} \propto \sigma^{3.9}\) and \(r \propto \sigma^{1.84}\).
+\citet{2012MNRAS.422.3339W} have found that clumps and HII regions follow scaling relations over the range of z = 0-2 for \halpha\ size, velocity dispersion, luminosity and mass, finding \(\sigma \propto r^{0.42}\), \(\text{L}_{\text{H}_{\alpha}} \propto r^{2.72}\) and \(\text{L}_{\text{H}_{\alpha}} \propto \sigma^{4.18}\).
 This results imply that the same process are seen at high redshifts and the current epoch in star forming regions.
-\citet{2015MNRAS.449.3568M} found that the relation is also found in dwarf galaxies with a \(L_{H_{\alpha}} \propto \sigma^{5}\).
+\citet{2015MNRAS.449.3568M} found that the relation is also found in dwarf galaxies with a \(\text{L}_{\text{H}_{\alpha}} \propto \sigma^{5}\).
 
-With the aim to investigate the scaling relations for our sample of HII regions and the turbulent parameters obtained, we use the properties in Table \ref{tab:Reg} with the values in Table \ref{tab:Res} to adjust a fit in the form $X = aY +b$.
+%\citet{1981MNRAS.194..809L}
+
+With the aim to investigate the scaling relations for our sample of HII regions and the turbulent parameters, we use the properties in Table \ref{tab:Reg} with the turbulent parameters in Table \ref{tab:Res} as the dependent variable to adjust a fit in the form $Y = aX +b$.
 For this procedure we use a hierarchical Bayesian approach using the package \textit{linmix} \citep{2007ApJ...665.1489K}.
-The results are shown in Table \ref{tab:RestStats} in ascending order for the $p$-value.
-In the Figures \ref{fig:rvsR}-\ref{fig:svss} are shown the correlations that are significant.
+The results are shown in Table \ref{tab:RestStats} in ascending order for the p-value.
+In the Figures \ref{fig:rvsR}-\ref{fig:svss} we show the correlations with a significance level lower than 0.10.
+In all the figures the slope of the fit shown in solid black line is the mean of all red lines that reflect the posterior of the Bayessian analysis.
 
 The Figure \ref{fig:rvsR} shows the strongest correlation, being this between the correlation length $r_0$ and the size $R$ of the region.
+The relationship we found is relation of $\log r_0 = (0.67 \pm 0.072) \log R-(0.797 \pm 0.131)$.
+
+The Figure \ref{fig:sigvsl} shows the log $\sigma$-log $\text{L}(\text{H}_{\alpha})$ plane.
+Since this relation is the most common it can be use for comparison with the investigations mentioned in at the beginning of the section.
+Our results give us a relation of $\log \sigma = (0.175 \pm 0.093) \log \text{L}(\text{H}_{\alpha})-(6.065 \pm 3.608)$.
+It is customary in the literature to present $\text{L} (\text{H}_{\alpha})$ as the dependent variable.
+In our case if we choose the upper positive error and take the inverse of slope we have \(\text{L}_{\text{H}_{\alpha}} \propto \sigma^{3.7}\). 
+Using the same procedure in \textit{linmix} and changing the variables we obtained $\log \text{L}(\text{H}_{\alpha}) = (3.32\pm 1.89) \log \sigma -(36.23 \pm 1.45)$.
+Both relations are close to the previously proposed \(\text{L}_{\text{H}_{\alpha}} \propto \sigma^{4}\)
 
@@
 \includegraphics[width=3in]{Figures/svss.pdf}
-\caption{Same as Fig. \ref{fig:rvsR} but for the log $\sigma$-log $\sigma_{LOS}$ plane.}
+\caption{Same as Fig. \ref{fig:rvsR} but for the log $\sigma$-log $\sigma_{\text{LOS}}$ plane. The dotted line represents slope equal to unity.}
 \label{fig:svss}
@@
 
-The analysis employed until now is not conclusive about the true velocity fluctuations observed in each nebula. 
-As pointed out by \citet{arthur2016turbulence} other techniques also allow us to study these fluctuations. 
-Following their procedure, it is possible to see from Table \ref{tab:Res} that the line-of-sight velocity dispersion is roughly twice the plane-of-sky velocity dispersion.
-In the case of homogeneous turbulent velocity we can consider the effect of 'project smearing', \citet{arthur2016turbulence} and reference therein, where the projection from three to two dimensions over a line-of-sight depth \(H\) reduces the plane-of-sky amplitude if \(r_{0} < H\).
-With a value of \(\sigma / \sigma_{LOS}\) = 0.5 we obtain \(r_{0} / H \approx\) 0.02-0.1 \citep{1984ApJ...277..556S}.
+The broad in the velocity width of the emission line represents the range of velocities along the line-of-sight (LOS), among thermal movements. 
+We can consider as a main broadening mechanisms the kinematical disorder along the LOS related to velocity gradients by the clumpiness on the molecular cloud and turbulent movements.
+On the plane-of-sky (POS) the consequences of those gradients and movements is measured in every pixel.
+The spatial variations on the velocity field would depend on the targeted pixel, depending on the motions inside the cloud (LOS component).
+This reasoning has lead to \citet{2011MNRAS.413..705L} to propose a direct relationship between \(\sigma_{\text{LOS}}\) and \(\sigma_{\text{POS}}\) (or just \(\sigma\) in this work).
+
+It have been mentioned that the projection of the velocity fluctuations reduces the actual amplitude in the line-of-sight \citep{1984ApJ...277..556S,arthur2016turbulence}.
+We can see from Table \ref{tab:Res} that the line-of-sight velocity dispersion is roughly twice the plane-of-sky velocity dispersion.
+In the case of homogeneous turbulent velocity we can consider the effect of \textit{project smearing} \citep{1984ApJ...277..556S}, where the projection from three to two dimensions over the line-of-sight depth \(H\), reduces the plane-of-sky amplitude for the condition \(r_{0} < H\).
+With a value of \(\sigma / \sigma_{\text{LOS}}\) = 0.5 we obtain \(r_{0} / H \sim\) 0.01-0.1.
+
+The Figure \ref{fig:svss} shows the log $\sigma$-log $\sigma_{\text{LOS}}$ plane with a relationship of $\log \sigma = (0.79 \pm 0.45) \log \sigma_{\text{LOS}}-(0.18 \pm 0.51)$ .
 
@@
 Their sigma is 5.92$\pm$0.15 km/s with a correlation length is 43 pc.
-The high difference is because the consider that this happen at 2$\sigma$ (equation 13 on their paper).
 The power-law index they provide is 1.55$\pm$0.01.
@@
 
-\item For Orion small with an observational box size of 0.45 pc an index of 1.06$\pm$0.02 is obtained with an inertial scale between 0.002 and 0.09 pc, and with a variance of 17$\pm$1.0 km$^2$/s$^2$.
+\item For Orion with an observational box size of 0.45 pc an index of 1.06$\pm$0.02 is obtained with an inertial scale between 0.002 and 0.09 pc, and with a variance of 17$\pm$1.0 km$^2$/s$^2$.
 
@@
 \item For Lagoon with an observational box size of 16 pc an index of 1.12$\pm$0.09 is obtained with an inertial scale between 0.005 and 1 pc, and with a variance of 7.2$\pm$0.8 km$^2$/s$^2$.
-
-\item For Orion large with an observational box size of 3 pc an index of 1.72$\pm$0.24 is obtained with an inertial scale between 0.1 and 0.7 pc, and with a variance of 6$\pm$0.5 km$^2$/s$^2$.
 

### 2021-12-02 strucfunc_paper.tex
Edits to equations
Updates from Overleaf

@@
 J. Zsargo,$^{1}$
-W. J. Henney$^{2}$
-and H. O. Castañeda$^{1}$
+and W. J. Henney$^{2}$
+%and H. O. Castañeda$^{1}$
 \\
@@
   span more than two orders of magnitude in size and luminosity.
-  We proposed a functional form of the structure function that takes into account the observational seeing, the instrument noise and the size of the observational box.
-  By fitting this functional to our results we extract three parameters related to the fluctuations in each region: 
-  the total velocity dispersion \(\sigma\), which spans from 3 to 15 km s\(^{-1}\), the
-  autocorrelation length \(r_0\), which covers 0.06 - 8 pc, and the power-law slope \(m\), which ranges from 0.7 to 1.3.
-  The velocity dispersion is found to correlate primarily with luminosity,
-  while the autocorrelation length correlates primarily with the size of the region.
+  We propose a functional form of the structure function that considers observational constraints.
+  By using a chi-square analysis fitting this functional to our results we extract three parameters related to the fluctuations in the velocity field in each region. 
+  The true velocity dispersion \(\sigma\), which spans from 3 to 15 km s\(^{-1}\), the
+  autocorrelation length \(r_0\) covering to 0.06 - 8 pc, and the power-law slope \(m\) of the velocity field, which ranges from 0.7 to 1.3.
+  The velocity dispersion is found to correlate primarily with luminosity and the autocorrelation length correlates primarily with the size of the region.
   A comparison between \(\sigma\) and \(\sigma_{POS}\) shows that this last value is at roughly the double for all regions.
   We found that our proposed functional form describe with more accuracy the inertial range and our methodology guarantees consistency for comparison between the galactic and giant HII regions.
-  \textbf{Add a sentence about the conclusions!}
 \end{abstract}
@@
 
-\WILL{I think it would be best to lead with a description of the dynamics of H II regions before mentioning the turbulence}.
-
 HII regions are far from been static objects.
 Initially, the gas of a HII region is ionized in a previously disturbed medium.
-When the formed star starts emitting, the energy and matter coming from it interacts with the surrounding medium, putting in motion a series of dynamical processes that have a considerable effect in the velocity field of the HII regions.
-Different investigations have shown a complex velocity structure particularly to each region. 
-Mainly, the excess in the thermal broadening on the spectral lines is interpreted as disorder motions along the line-of-sight (LOS).
-Motions like the expansion or rotation of the region can be accounted for, but after these are considered, still persist a random velocity component in the region.
+When the recently created star starts emitting, the energy and matter coming from it interacts with the surrounding medium, putting in motion a series of dynamical processes that have a considerable effect in the velocity field of the now HII region.
+Different investigations have shown that a complex velocity structure is particularly to each region. 
+The excess in the thermal broadening on the spectral lines is interpreted as disorder motions along the line-of-sight (LOS).
+Large-scale motions like the expansion or rotation of the region can be accounted for, but even after these are considered still persist a random component in the region velocity field.
 It has become customary to investigate this random component as turbulence in the ionized gas.
 
-The fluctuations associated with the centroid velocities on the plane-of-sky (POS) of photoionized regions have been characterized several times using the second order structure function.
+The fluctuations associated with the centroid velocities on the plane-of-sky (POS) of photoionized regions have been characterized several times using the second-order structure function.
 This studies span from galactic HII regions \citep{1986ApJ...300..624R} like Orion \citep{von1951methode,munch1958internal,castaneda1988,1992ApJ...387..229O,arthur2016turbulence} to giant HII regions \citep{1961MNRAS.122....1F,lagrois2009multi,lagrois2011}, like NGC 604 in the M 33 galaxy \citep{tanco1997,2019arXiv191203543M}.
@@
 Several problems arise in the study of these fluctuation.
-One of them is that there is no well-established theory for turbulence in astronomical conditions, these being that the medium is compressible and supersonic, and will result in the presence of shock waves \citep{lagrois2011,arthur2016turbulence}.
-On the other hand, it is known that these regions are created on the edge of molecular clouds, so they will reach a blister or champagne phase, introducing large-scale gradients not related with random motions \citep{Mivi1995}.
-Intrinsic with observations there is the projection of a three-dimensional function into the plane-of-sky \citep{von1951methode,munch1958internal,1964SvA.....8..210K} leading to a loss in information.
+One of them is that there is no well-established theory for turbulence in astronomical conditions; these being that the medium is compressible and supersonic.
+This conditions will develop shock waves in the HII region changing the energy balance \citep{lagrois2011,arthur2016turbulence}.
+Two it is known that these regions are created on the edge of molecular clouds, so they will reach a blister or champagne phase, introducing large-scale gradients not related with random motions \citep{Mivi1995}.
+And three, in regard with observations, there is the projection of a three-dimensional function into the plane-of-sky \citep{von1951methode,munch1958internal,1964SvA.....8..210K} leading to a loss in information of the velocity spectrum.
 
@@
 In turbulence theory, the largest and smallest scales are the most important as they relate to the energy transfer of the turbulence spectrum, which implies that it is necessary to consider them for a correct characterization of the turbulence in the velocity field.
-Disregarding the above has led previous investigations in HII regions to erroneous conclusions about the nature of this energy spectrum.
+Disregarding the above has led previous investigations in HII regions to erroneous conclusions about the nature of the energy spectrum.
 
-To face these problems, we study the effects of seeing, noise and observational box size in an artificial velocity field to develop and propose a correct form that fits the results of a statistical analysis of the field of velocity of HII regions.
+To face these problems, we study the effects of seeing, noise and observational box size using an artificial velocity field to develop and propose a better form that fits the results of a statistical analysis in the velocity field of HII regions.
 This aims to leave little room for the interpretation of results and to characterize in a more precise way the turbulence in ionized nebulae, something that has not been considered in previous works.
@@
 
-Previous works that apply a statistical analysis on the velocity field of HII regions  
-tend to consider just one region.
-With the aim to develop a more complete study we choose 9 objects in the \halpha\ emission line.
-This give us the opportunity to compare for first time the structure function of various objects following the same methodology.
-We use previous published observational data to measure characterize the velocity field o HII regions located in the Milky Way, the Magellanic clouds and in the M 33 and NGC 6822 galaxies. 
-Figure \ref{fig:hii-regions} shows the images of our sample.
-Table \ref{tab:Reg} shows the names with the physical properties of interest in each region.
+Previous investigations using the second-order structure function on the velocity field use, in majority, one HII region and their own methodology.
+This has the consequences that only the same authors can compare their results in a direct way and the gap in the interpretation between authors doesn't aid the understanding of the topic.
+To deal with this issue we choose 9 objects in the \halpha\ emission line and use the the same methodology in all the regions.
+This give us the opportunity to compare for first time the structure function of various objects.
+We use previous published observational data to characterize the velocity field o HII regions located in the Milky Way, the Magellanic clouds and in the M 33 and NGC 6822 galaxies. 
+Figure \ref{fig:hii-regions} shows the images of our HII region sample and Table \ref{tab:Reg} shows the the physical properties of interest in each region.
 
@@
 
-Orion (M42) is the prototype galactic HII region and one on the best objects studied in the sky.
+Orion (M42) is the prototype galactic HII region and one of the mores studied in the sky.
 Located at a distance of 440 pc \citep{2008AJ....136.1566O} its main physical and kinematics properties, along its stellar population are documented in \citet{2001ARA&A..39...99O}.
@@
 The most star is a luminous blue variable, $\eta$ Car \citep{Damiani:2016a}.
-As a star formation region,it presents several phenomena related with young stars as: evaporating protoplanetary discs, erosion of large dust pillars and the triggering of a second generation of embedded stars, Herbig-Haro objects, to mention some, \citet{2008hsf2.book..138S} and reference therein.
+As a star formation region, it presents several phenomena related with young stars as evaporating protoplanetary discs, erosion of large dust pillars and the triggering of a second generation of embedded stars, Herbig-Haro objects, to mention some, \citet{2008hsf2.book..138S} and reference therein.
 An approaching and receding kinematics components are known in the nebula.
@@
 
-Scaling relations between parameters like size and luminosity are common tools to study HII regions, along dwarf galaxies and high-redshift star formation regions.
+Relationship between the physical properties of HII regions, like size and luminosity, and the velocity dispersion have been used as tools for concluding scaling relations for these objects.
+These relations have also been studied in dwarf galaxies and high-redshift star formation regions.
 \citet{melnick1977,terlevich1981} were the first to shown an empirical relationship between the line width and the integrated properties of the HII regions as the diameter or the luminosity ($r \sim \sigma ^{\sim 2}$ ; $\text{L}_{\text{H}} \sim \sigma ^{\sim 4}$).
-They conclude that GEHRs follow this relations as self-gravity systems like globular clusters or elliptical galaxies.
+They conclude that GEHRs follow this relation because they behave as self-gravitatory systems like globular clusters or elliptical galaxies.
 The work of \citet{1988A&A...201..199A} confirmed these relationships considering the discrepancies of previous investigations obtaining \(\text{L}_{\text{H}_{\alpha}} \propto \sigma^{3.9}\) and \(r \propto \sigma^{1.84}\).
-\citet{2012MNRAS.422.3339W} have found that clumps and HII regions follow scaling relations over the range of z = 0-2 for \halpha\ size, velocity dispersion, luminosity and mass, finding \(\sigma \propto r^{0.42}\), \(\text{L}_{\text{H}_{\alpha}} \propto r^{2.72}\) and \(\text{L}_{\text{H}_{\alpha}} \propto \sigma^{4.18}\).
-This results imply that the same process are seen at high redshifts and the current epoch in star forming regions.
-\citet{2015MNRAS.449.3568M} found that the relation is also found in dwarf galaxies with a \(\text{L}_{\text{H}_{\alpha}} \propto \sigma^{5}\).
-
 %\citet{1981MNRAS.194..809L}
 
-With the aim to investigate the scaling relations for our sample of HII regions and the turbulent parameters, we use the properties in Table \ref{tab:Reg} with the turbulent parameters in Table \ref{tab:Res} as the dependent variable to adjust a fit in the form $Y = aX +b$.
+\citet{2012MNRAS.422.3339W} have found that clumps and HII regions follow scaling relations over the range of z = 0-2 for \halpha\ size, velocity dispersion, luminosity and mass, finding \(\sigma \propto r^{0.42}\), \(\text{L}_{\text{H}_{\alpha}} \propto r^{2.72}\) and \(\text{L}_{\text{H}_{\alpha}} \propto \sigma^{4.18}\), respectively.
+This results imply that the same process are seen at high redshifts and the current epoch in star forming regions.
+Recently, \citet{2015MNRAS.449.3568M} found that the relation in dwarf galaxies is \(\text{L}_{\text{H}_{\alpha}} \propto \sigma^{5}\).
+\citet{2018MNRAS.474.1250F} presented the relationship between integrated H$_{\beta}$ line luminosity and the velocity dispersion for new data of 36 giant HII regions obtaining \(\text{L}_{\text{H}_{\beta}} \propto \sigma^{5.02 \pm 0.21}\).
+
+This line of investigation is followed using the scaling relation as a research tool between the properties of the sample of HII regions and our results. 
+We use the properties in Table \ref{tab:Reg} with the turbulent parameters in Table \ref{tab:Res} as the dependent variable to adjust a fit in the form $Y = aX +b$. 
 For this procedure we use a hierarchical Bayesian approach using the package \textit{linmix} \citep{2007ApJ...665.1489K}.
 The results are shown in Table \ref{tab:RestStats} in ascending order for the p-value.
-In the Figures \ref{fig:rvsR}-\ref{fig:svss} we show the correlations with a significance level lower than 0.10.
+In the Figures \ref{fig:rvsR}-\ref{fig:svss} we show the correlations with a significance level  $p \leq $0.10.
 In all the figures the slope of the fit shown in solid black line is the mean of all red lines that reflect the posterior of the Bayessian analysis.
@@
 The Figure \ref{fig:rvsR} shows the strongest correlation, being this between the correlation length $r_0$ and the size $R$ of the region.
-The relationship we found is relation of $\log r_0 = (0.67 \pm 0.072) \log R-(0.797 \pm 0.131)$.
+The relationship we found is relation of $\log r_0 = (0.69 \pm 0.07) \log R-(0.85 \pm 0.14)$.
 
 The Figure \ref{fig:sigvsl} shows the log $\sigma$-log $\text{L}(\text{H}_{\alpha})$ plane.
-Since this relation is the most common it can be use for comparison with the investigations mentioned in at the beginning of the section.
-Our results give us a relation of $\log \sigma = (0.175 \pm 0.093) \log \text{L}(\text{H}_{\alpha})-(6.065 \pm 3.608)$.
+Since this relation is the most common it can be use for comparison with the investigations mentioned at the beginning of this section.
+Our results give us a relation of $\log \sigma = (0.16 \pm 0.12) \log \text{L}(\text{H}_{\alpha})-(5.6 \pm 5.0)$.
 It is customary in the literature to present $\text{L} (\text{H}_{\alpha})$ as the dependent variable.
-In our case if we choose the upper positive error and take the inverse of slope we have \(\text{L}_{\text{H}_{\alpha}} \propto \sigma^{3.7}\). 
+In our case if we choose the upper positive error and take the inverse of slope we have \(\text{L}_{\text{H}_{\alpha}} \propto \sigma^{3.5}\). 
 Using the same procedure in \textit{linmix} and changing the variables we obtained $\log \text{L}(\text{H}_{\alpha}) = (3.32\pm 1.89) \log \sigma -(36.23 \pm 1.45)$.
@@
 The broad in the velocity width of the emission line represents the range of velocities along the line-of-sight (LOS), among thermal movements. 
-We can consider as a main broadening mechanisms the kinematical disorder along the LOS related to velocity gradients by the clumpiness on the molecular cloud and turbulent movements.
+We can consider as a main broadening mechanisms, the kinematical disorder along the LOS related to velocity gradients by the clumpiness on the molecular cloud and turbulent movements.
 On the plane-of-sky (POS) the consequences of those gradients and movements is measured in every pixel.
-The spatial variations on the velocity field would depend on the targeted pixel, depending on the motions inside the cloud (LOS component).
+The spatial variations on the velocity field would depend on the targeted pixel, depending on the motions inside the cloud (the LOS component).
 This reasoning has lead to \citet{2011MNRAS.413..705L} to propose a direct relationship between \(\sigma_{\text{LOS}}\) and \(\sigma_{\text{POS}}\) (or just \(\sigma\) in this work).
@@
 
-The Figure \ref{fig:svss} shows the log $\sigma$-log $\sigma_{\text{LOS}}$ plane with a relationship of $\log \sigma = (0.79 \pm 0.45) \log \sigma_{\text{LOS}}-(0.18 \pm 0.51)$ .
+The Figure \ref{fig:svss} shows the log $\sigma$-log $\sigma_{\text{LOS}}$ plane with a relationship of $\log \sigma = (0.75 \pm 0.60) \log \sigma_{\text{LOS}}-(0.13 \pm 0.70)$ .
 

### 2021-12-07 strucfunc_paper.tex
New first paragraph of introduction

@@
 \section{Introduction}
+
+Photoionized regions around high-mass stars (\hii{} regions)
+show highly vigorous dynamics
+as a result of the star formation process and the energy and momentum
+injected by the newly-formed stars.
+Rather than manifesting a simple pattern such as expansion, infall, or rotation,
+the motions are frequently disordered or ``turbulent''
+and must be characterised by statistical techniques.
+In relatively low luminosity regions, such as the nearby Orion Nebula,
+the disordered motions are approximately transonic,
+with typical velocities of order \num{5} to \SI{10}{km.s^{-1}}
+\citep{castaneda1988, Garcia-Diaz:2008a}.
+In larger, higher luminosity regions,
+such as 30~Doradus in the Large Magellanic Cloud,
+the velocities are significantly supersonic,
+of order \SI{30}{km.s^{-1}} \citep{Torres-Flores:2013t, Castro:2018a}.
+The same tendency of increasing velocity dispersion (\(\sigma\))
+and luminosity (\(L\))
+continues up to the scale of entire galaxies
+with an approximate relation \(L \propto \sigma^n\) that spans
+more than 5 orders of magnitude in luminosity
+with a  power-law index \(n = 3\) to~\(7\)
+\cite{Rozas:2006b, Moiseev:2015a}.
+However, it is unclear whether a single physical mechanism
+underlies this relationship at all scales.
+The relative importance of gravity and the various stellar feedback mechanisms
+(heating, direct radiation pressure, stellar winds, cluster winds)
+are unclear in many cases and are frequently disputed \citep{Krumholz:2016a, Melnick:2021x}.
 
@@
 We use data from \citet{arthur2016turbulence} to study of turbulence in the Orion Nebula.
-Their observations were initially published by \citet{2008RMxAA..44..181G}. 
+Their observations were initially published by \citet{Garcia-Diaz:2008a}. 
 The data was obtained with the echelle spectrograph attached to the 4 m telescope at Kitti Peak National Observatory (KPNO).
@@
 The second-order structure function of the velocity centroids, $B(r)$, is defined as:
-
+%
 \begin{equation}\label{eq:Br}
-B(\boldsymbol{r}) = \dfrac{\sum_{\text{pairs}}[V_{c}(\boldsymbol{x} + \boldsymbol{r}) - V_{c}(\boldsymbol{x}) ]^{2}} {N(\boldsymbol{r})}
+  B(\boldsymbol{r}) = \dfrac{1}{N(\boldsymbol{r})}
+  \,
+  \sum_{\text{pairs}} \bigl[
+  V_{c}(\boldsymbol{x} + \boldsymbol{r}) - V_{c}(\boldsymbol{x})
+  \bigr]^{2}
 \end{equation}
@@
 The variance of the centroid velocity fluctuations is:
-
+%
 \begin{equation}\label{eq:variance}
-\sigma^2  = \frac{\sum_{\text{pixels}}[ V_c (\boldsymbol{x}) -\langle V_ c\rangle  ]^2}{N}
+\sigma^2  = \frac{1}{N} \sum_{\text{pixels}} \bigl[ V_c (\boldsymbol{x}) -\langle V_ c\rangle  \bigr]^2
 \end{equation}
@@
 the, \(\langle V_c \rangle \) is the mean centroid velocity
-
+%
 \begin{equation}\label{eq:mean}
-\langle V_c \rangle \  = \frac{\sum_{\text{pixels}}[ V_c (\boldsymbol{x})]}{N}
+\langle V_c \rangle \  = \frac{1}{N} \sum_{\text{pixels}} V_c (\boldsymbol{x})
 \end{equation}
@@
 This results imply that the same process are seen at high redshifts and the current epoch in star forming regions.
-Recently, \citet{2015MNRAS.449.3568M} found that the relation in dwarf galaxies is \(\text{L}_{\text{H}_{\alpha}} \propto \sigma^{5}\).
+Recently, \citet{Moiseev:2015a} found that the relation in dwarf galaxies is \(\text{L}_{\text{H}_{\alpha}} \propto \sigma^{5}\).
 \citet{2018MNRAS.474.1250F} presented the relationship between integrated H$_{\beta}$ line luminosity and the velocity dispersion for new data of 36 giant HII regions obtaining \(\text{L}_{\text{H}_{\beta}} \propto \sigma^{5.02 \pm 0.21}\).

### 2021-12-08 strucfunc_paper.tex
New second para of intro and half of third para

@@
 
+%% Will version 2021-12-07 of Intro first para (what we are studying)
 Photoionized regions around high-mass stars (\hii{} regions)
@@
 continues up to the scale of entire galaxies
-with an approximate relation \(L \propto \sigma^n\) that spans
+with an approximate relation \(L \propto \sigma^\alpha\) that spans
 more than 5 orders of magnitude in luminosity
-with a  power-law index \(n = 3\) to~\(7\)
-\cite{Rozas:2006b, Moiseev:2015a}.
-However, it is unclear whether a single physical mechanism
+with a  power-law index \(\alpha = 3\) to~\(7\)
+\cite{terlevich1981, Rozas:2006b, Chavez:2014a, Moiseev:2015a}.
+However, it is not known whether a single physical mechanism
 underlies this relationship at all scales.
@@
 
-HII regions are far from been static objects.
-Initially, the gas of a HII region is ionized in a previously disturbed medium.
-When the recently created star starts emitting, the energy and matter coming from it interacts with the surrounding medium, putting in motion a series of dynamical processes that have a considerable effect in the velocity field of the now HII region.
-Different investigations have shown that a complex velocity structure is particularly to each region. 
-The excess in the thermal broadening on the spectral lines is interpreted as disorder motions along the line-of-sight (LOS).
-Large-scale motions like the expansion or rotation of the region can be accounted for, but even after these are considered still persist a random component in the region velocity field.
-It has become customary to investigate this random component as turbulence in the ionized gas.
+% Javier initial version
+%
+% HII regions are far from been static objects.  Initially, the gas of
+% a HII region is ionized in a previously disturbed medium.  When the
+% recently created star starts emitting, the energy and matter coming
+% from it interacts with the surrounding medium, putting in motion a
+% series of dynamical processes that have a considerable effect in the
+% velocity field of the now HII region.  Different investigations have
+% shown that a complex velocity structure is particularly to each
+% region.  The excess in the thermal broadening on the spectral lines
+% is interpreted as disorder motions along the line-of-sight (LOS).
+% Large-scale motions like the expansion or rotation of the region can
+% be accounted for, but even after these are considered still persist
+% a random component in the region velocity field.  It has become
+% customary to investigate this random component as turbulence in the
+% ionized gas.
 
+%% Will version 2021-12-07 of Intro second para (how we are studying it)
+One of the simplest ways to measure the velocity dispersion of an \hii{} region
+is to use the Doppler width of a strong emission line, such as the
+optical hydrogen recombination line \ha{} \Wav{6563}.
+We will use \(\sigma\los\) to denote
+the root-mean-square (RMS) line-of-sight velocity dispersion determined in this way.
+Unfortunately, there are many processes that contribute to this width
+in addition to the line-of-sight turbulent velocity fluctuations,
+such as thermal and fine-structure broadening, instrumental broadening,
+dust scattering, 
+and large-scale expansion
+\citetext{see \citealp{Rozas:2006b} and \citealp{Garcia-Diaz:2008a}
+  for detailed discussion}.
+All except the last of these can in principal be approximately corrected for,
+which is a reasonable strategy to apply in the case of high-luminosity regions
+where the turbulent width is expected to be larger than the correction terms.
+However, for lower luminosity regions the turbulent velocities are much smaller,
+which limits the accuracy of such a correction process
+\citetextP{see section 3.4 of \citealp{Arthur:2016a}}.
+
+An alternative way to study turbulent motions is to measure
+the fluctuations on the plane of the sky of the velocity centroids of an emission line
+\citep{von1951methode}.
+We will denote the RMS magnitude of these fluctuations by \(\sigma\pos\).
+In addition to being unaffected by the various nuisance broadening mechanisms
+discussed in the previous paragraph,
+this also offers the opportunity to study the spatial scale of the fluctuations
+by measuring average velocity differences as a function of
+the angular separation between two points.
+Different mathematical tools can be used to study these spatial fluctuations,
+such as the autocorrelation function \citep{lagrois2011}
+and \(\Delta\)-variance \citep{Ossenkopf:2006a}.
+In this paper, we will concentrate on the second order structure function.
+
+% Javier's original para 2
 The fluctuations associated with the centroid velocities on the plane-of-sky (POS) of photoionized regions have been characterized several times using the second-order structure function.
@@
 \label{sec:degr-struct-funct}
+Studied in context of \(\Delta\)-variance by \citet{Bensch:2001l}.
 

### 2021-12-08 strucfunc_paper.tex
Finish Will's rewrite of the introduction

@@
 with a  power-law index \(\alpha = 3\) to~\(7\)
-\cite{terlevich1981, Rozas:2006b, Chavez:2014a, Moiseev:2015a}.
+\citep{terlevich1981, Rozas:2006b, Chavez:2014a, Moiseev:2015a}.
 However, it is not known whether a single physical mechanism
@@
 is to use the Doppler width of a strong emission line, such as the
-optical hydrogen recombination line \ha{} \Wav{6563}.
+optical hydrogen recombination line \ha{} \Wav{6563}
+\citetext{e.g., \citealp{1986ApJ...300..624R}}.
 We will use \(\sigma\los\) to denote
@@
 which limits the accuracy of such a correction process
-\citetextP{see section 3.4 of \citealp{Arthur:2016a}}.
+\citetext{see section 3.4 of \citealp{arthur2016turbulence}}.
 
@@
 and \(\Delta\)-variance \citep{Ossenkopf:2006a}.
-In this paper, we will concentrate on the second order structure function.
+In this work, we will concentrate on the second order structure function,
+\(B(r)\) (see section \ref{sec:second-order-struct}),
+which has been used in many previous studies of velocity fluctuations
+in \hii{} regions in our own Galaxy
+% Javier cited the wrong Roy & Joncas here - now corrected (should be 1985 not 1986)
+% Also, Medina+ 2014  better than Arthur+ 2016
+\citep{munch1958internal, castaneda1988, Roy:1985a, 1992ApJ...387..229O, medina2014}
+and in external galaxies
+\citep{1961MNRAS.122....1F, tanco1997, lagrois2009multi, lagrois2011, Melnick:2021x}.
 
 % Javier's original para 2
-The fluctuations associated with the centroid velocities on the plane-of-sky (POS) of photoionized regions have been characterized several times using the second-order structure function.
-This studies span from galactic HII regions \citep{1986ApJ...300..624R} like Orion \citep{von1951methode,munch1958internal,castaneda1988,1992ApJ...387..229O,arthur2016turbulence} to giant HII regions \citep{1961MNRAS.122....1F,lagrois2009multi,lagrois2011}, like NGC 604 in the M 33 galaxy \citep{tanco1997,2019arXiv191203543M}.
 
-The procedure using the structure function allow us to determine a distinction between homogeneous turbulence and pure random velocity fluctuations in the photoionized gas.
-Several problems arise in the study of these fluctuation.
-One of them is that there is no well-established theory for turbulence in astronomical conditions; these being that the medium is compressible and supersonic.
-This conditions will develop shock waves in the HII region changing the energy balance \citep{lagrois2011,arthur2016turbulence}.
-Two it is known that these regions are created on the edge of molecular clouds, so they will reach a blister or champagne phase, introducing large-scale gradients not related with random motions \citep{Mivi1995}.
-And three, in regard with observations, there is the projection of a three-dimensional function into the plane-of-sky \citep{von1951methode,munch1958internal,1964SvA.....8..210K} leading to a loss in information of the velocity spectrum.
+% The fluctuations associated with the centroid velocities on the plane-of-sky (POS) of photoionized regions have been characterized several times using the second-order structure function.
+% This studies span from galactic HII regions \citep{1986ApJ...300..624R} like Orion \citep{von1951methode,munch1958internal,castaneda1988,1992ApJ...387..229O,arthur2016turbulence} to giant HII regions \citep{1961MNRAS.122....1F,lagrois2009multi,lagrois2011}, like NGC 604 in the M 33 galaxy \citep{tanco1997,2019arXiv191203543M}.
 
-There are also a series of problems related to the observations that to date have not been formally addressed like the previous ones.
-These problems are that: 1) following observations, there is the seeing and noise due to the telescope and instrument, and 2) that the observations are mostly limited to only one part of the nebula.
-This has the consequence that when analyzing a turbulent field, the velocity fluctuations related to small and large scales will be affected due to artifacts introduced by the problems mentioned above.
-In turbulence theory, the largest and smallest scales are the most important as they relate to the energy transfer of the turbulence spectrum, which implies that it is necessary to consider them for a correct characterization of the turbulence in the velocity field.
-Disregarding the above has led previous investigations in HII regions to erroneous conclusions about the nature of the energy spectrum.
+% Will's 2021-12-08 new version of Intro para 4: description of our methodology
+In this paper,
+we employ archival data from a wide variety of integral field and multi-longslit
+spectrographic datasets to analyze spatially resolved \ha{} velocity maps for a sample of
+nine \hii{} regions (Figure~\ref{fig:hii-regions}),
+ranging in size from \SI{0.5}{pc} to \SI{200}{pc}
+and in \ha{} luminosity from \SI{e37}{erg.s^{-1}} to  \SI{e39}{erg.s^{-1}}.
+The observations and the physical characteristics of our sample
+are described in section~\ref{sec:HIIsample}.
 
-To face these problems, we study the effects of seeing, noise and observational box size using an artificial velocity field to develop and propose a better form that fits the results of a statistical analysis in the velocity field of HII regions.
-This aims to leave little room for the interpretation of results and to characterize in a more precise way the turbulence in ionized nebulae, something that has not been considered in previous works.
-Also, we aim to fill a gap with an uniform statistical analysis of turbulence between galactic and giant HII regions.
+We apply a uniform methodology to the analysis of the structure function
+by fitting a simple functional form that consists of a power law of slope \(m\)
+at small separations,
+transitioning to a constant value at separations larger than
+an autocorrelation length \(r_0\).
+This is described in section~\ref{sec:met}.
+We also take into account three observational limitations of the datasets:
+the finite angular resolution, \(s_0\) (set by pixel spacing or atmospheric seeing);
+the finite map size, \(L\);
+and a contribution of spatially uncorrelated noise, \(B_0\),
+to the observed structure function.
+In Appendix~\ref{sec:degr-struct-funct} we use simulated velocity maps to derive
+appropriate functional forms for the effects of \(s_0\), \(L\) and \(B_0\).
+In our fits, we marginalize over these nuisance parameters to obtain robust
+credibility limits for the parameters of astrophysical interest:
+\(\sigma\pos\), \(r_0\), and \(m\).
+The results of these fits are presented in section~\ref{sec:results}.
 
-Using archival data we perform the second-order structure function on a sample of HII regions.
-Our sample spans in size from 4 pc to 400 pc and has luminosities between 10\(^{37}\)-10\(^{39}\) erg s\(^{-1}\) going from galactic to extragalactic HII regions.
-We apply an uniform methodology of a functional form of the structure function to characterize the turbulent using the velocity field variance, $\sigma^2$, autocorrelation length, \(r_0\), and power-law slope, \(m\).
-Our results are compared with physical properties of each region and with previous investigations.
+In section~\ref{sec:discussion} we discuss the relation
+of our results to previous studies and the correlations that we find
+between the structure function parameters and other properties of
+the \hii{} regions in our sample.
+We also discuss the implications of our results for the existence of a
+Kolmogorov-type turbulent energy cascade and the nature of the driving mechanism
+for the velocity fluctuations.
+Finally, in section~\ref{sec:conclusions} we summarise our conclusions.
+
+%% Previous Javier version of final paragraphs of Intro. I think I
+%% have incorporated most of this in my own version, but more
+%% concisely.  However, I haven't mentioned the projection effects -
+%% maybe that would be tetter just in section 3
+
+% The procedure using the structure function allow us to determine a distinction between homogeneous turbulence and pure random velocity fluctuations in the photoionized gas.
+% Several problems arise in the study of these fluctuation.
+% One of them is that there is no well-established theory for turbulence in astronomical conditions; these being that the medium is compressible and supersonic.
+% This conditions will develop shock waves in the HII region changing the energy balance \citep{lagrois2011,arthur2016turbulence}.
+% Two it is known that these regions are created on the edge of molecular clouds, so they will reach a blister or champagne phase, introducing large-scale gradients not related with random motions \citep{Mivi1995}.
+% And three, in regard with observations, there is the projection of a three-dimensional function into the plane-of-sky \citep{von1951methode,munch1958internal,1964SvA.....8..210K} leading to a loss in information of the velocity spectrum.
+
+% There are also a series of problems related to the observations that to date have not been formally addressed like the previous ones.
+% These problems are that: 1) following observations, there is the seeing and noise due to the telescope and instrument, and 2) that the observations are mostly limited to only one part of the nebula.
+% This has the consequence that when analyzing a turbulent field, the velocity fluctuations related to small and large scales will be affected due to artifacts introduced by the problems mentioned above.
+% In turbulence theory, the largest and smallest scales are the most important as they relate to the energy transfer of the turbulence spectrum, which implies that it is necessary to consider them for a correct characterization of the turbulence in the velocity field.
+% Disregarding the above has led previous investigations in HII regions to erroneous conclusions about the nature of the energy spectrum.
+
+% To face these problems, we study the effects of seeing, noise and observational box size using an artificial velocity field to develop and propose a better form that fits the results of a statistical analysis in the velocity field of HII regions.
+% This aims to leave little room for the interpretation of results and to characterize in a more precise way the turbulence in ionized nebulae, something that has not been considered in previous works.
+% Also, we aim to fill a gap with an uniform statistical analysis of turbulence between galactic and giant HII regions.
+
+% Using archival data we perform the second-order structure function on a sample of HII regions.
+% Our sample spans in size from 4 pc to 400 pc and has luminosities between 10\(^{37}\)-10\(^{39}\) erg s\(^{-1}\) going from galactic to extragalactic HII regions.
+% We apply an uniform methodology of a functional form of the structure function to characterize the turbulent using the velocity field variance, $\sigma^2$, autocorrelation length, \(r_0\), and power-law slope, \(m\).
+% Our results are compared with physical properties of each region and with previous investigations.
 
@@
 \subsection{The second-order structure function}
-
-One of the fundamental properties of turbulent clouds must be spatial fluctuations in velocity and density .
+\label{sec:second-order-struct}
+One of the fundamental properties of turbulent clouds must be spatial fluctuations in velocity and density.
 These fluctuations are observed as projected spatial fluctuations in the average line-of-sight velocity and integrated column density.

### 2021-12-09 strucfunc_paper.tex
Make a start of reorganization of section 2

@@
 
-\section{\boldmath Sample of \hii{} regions}\label{sec:HIIsample}
+\section{\boldmath Observations of the \hii{} region sample}
+\label{sec:HIIsample}
 
@@
 
-Previous investigations using the second-order structure function on the velocity field use, in majority, one HII region and their own methodology.
-This has the consequences that only the same authors can compare their results in a direct way and the gap in the interpretation between authors doesn't aid the understanding of the topic.
-To deal with this issue we choose 9 objects in the \halpha\ emission line and use the the same methodology in all the regions.
-This give us the opportunity to compare for first time the structure function of various objects.
-We use previous published observational data to characterize the velocity field o HII regions located in the Milky Way, the Magellanic clouds and in the M 33 and NGC 6822 galaxies. 
-Figure \ref{fig:hii-regions} shows the images of our HII region sample and Table \ref{tab:Reg} shows the the physical properties of interest in each region.
+Previous investigations of the centroid velocity structure function in \hii{} regions
+have used a variety of methodologies, which makes it difficult to compare results
+between different regions.  \citet{arthur2016turbulence} summarise historical results
+for the Orion Nebula in their Table~5.
+The most significant differences are seen when different emission line tracers are used,
+but even when using the same line, there is some variance between different studies
+in the derived values for both the velocity dispersion \(\sigma\pos\) and power-law slope \(m\).
+It is therefore worthwhile to employ a uniform approach across a variety of different regions.
+To that end, we have selected 9 \hii{} regions,
+covering a broad range in size and luminosity,
+for which good quality mapping of the \ha{} line exists in the literature
+or in data archives.
+Figure~\ref{fig:hii-regions} shows optical images of
+each region in our sample
+and Table~\ref{tab:Reg} lists their most important physical parameters.
+The derived centroid \ha{} velocity maps are shown in Figure~\ref{fig:velocity-maps}.
+Our sample includes three Milky Way regions
+(at approximate distance of \num{0.5} to \SI{2}{kpc}),
+two regions in the Magellanic Clouds (\num{50} to \SI{60}{kpc}),
+and four regions in more distant galaxies of the Local Group
+(\num{500} to \SI{800}{kpc}).
+Further details of the observations and the sources themselves
+are given in the following two sections.
+
+\subsection{Spectroscopic datasets}
+
+%We use data from \citet{1987A&A...176..347H} and \citet{arthur2016turbulence} to study of turbulence in the Orion Nebula.
+%\cite{1987A&A...176..347H} observations were obtained using a 106 cm-Cassegrain telescope at Observatorium Hoher List. 
+%A Fabry-Pérot interferometer was used with a étalon a separation of 0.5 mm. 
+%Interferograms have been taken with different pointing directions of the telescope's optical axis in the nebula. 
+%The exposures are overlapped and fall into one square of a grid with a width of 1' centered at \(\theta^{1}\)Ori C.
+
+\subsubsection{Longslit echelle spectroscopy}
+\label{sec:longsl-echelle-spect}
+
+For the Orion Nebula, we use data obtained with the echelle spectrograph attached to the \SI{4}{m} telescope at Kitt Peak National Observatory (KPNO) initially published in
+\citet{Doi:2004a}.
+These observations cover a \(\SI{3}{arcmin} \times \SI{5}{arcmin}\) region of the
+central (Huygens) part of the Orion Nebula.
+The data consist of 96 North--South orientated \SI{300}{arcsec} slits,
+uniformly spaced at \SI{2}{arcsec} intervals with a width of \SI{0.8}{arcsec}
+with a velocity resolution of \SI{8}{km.s^{-1}}. 
+For the centroid velocities, we use the intensity-weighted
+mean velocities calculated by \citet{Garcia-Diaz:2008a},
+who used additional observations with East--West oriented slits
+to refine the inter-slit velocity calibration. 
+Unlike in the previous analysis of this dataset by \citet{arthur2016turbulence},
+we do not mask out regions affected by known high-velocity outflows.
+This decision was made for consistency with the analysis of more distant regions,
+where such a masking out is not possible.
+
+\subsubsection{FLAMES multi-fiber spectroscopy}
+\label{sec:flames-multi-fiber}
+
+Archival data from \citet{Damiani:2016a} and \citet{Damiani:2017b} are use to study the Carina nebula and Lagoon nebula, respectively. 
+The ESO VLT/FLAMES multi-fiber spectograph \citep{2002Msngr.110....1P} was used for these observations (Gaia-ESO Survey internal release \(iDR4\)). 
+The Survey targets are low-mass stars ranging down to magnitude V \(\sim\) 18.5.
+Mainly the spectra were obtained with the spectographs Giraffe (HR15N setup \(R \sim19 000\), wavelength range 6444-6818 \AA) and the UVES (setup 580, R \(\sim\)4700, range 4768-6830 \AA).
+
+\subsubsection{MUSE integral field spectroscopy}
+\label{sec:muse-integral-field}
+
+Using observations from \citet{Castro:2018a} (private communication) we study 30 Dor.
+NGC 2070 was observed as part of the MUSE SV (Science Verification) programme at the Very Large Telescope (VLT) in August 2014, when the instrument was new. 
+Four overlapping fields, each with an individual field of 1' \(\times\) 1' and a pixel scale of 0.2''/pixel were observed with exposure times of 4 \(\times\) 10s, 4 \(\times\) 60s, and 4 \(\times\) 600s.
+The table 1 on their work summarize the propertie of each field.
+The data were reduced using the MUSE pipeline based on ESOREX recipes, with final astrometric calibration using the catalog of \citet{1999A&A...341...98S}. 
+The final spectra span 4595-9366 \AA, with a resolving power of \(R \sim3 000\) around \halpha\  \citep{Castro:2018a}.
+
+\subsubsection{TAURUS-II Fabry-Perot spectroscopy}
+\label{sec:taurus-ii-fabry}
+
+The archival data used in this work for the extragalactic giant regions, NGC 604, NGC 595, Hubble X and Hubble V was obtained with the Fabry Perot TAURUS-II instrument in the 4.2-m William Herschel Telescope (WHT) of del Roque de los Muchachos Observatory (ORM) in La Palma, Spain and was retrieved from the La Palma archive\footnote{\url{http://casu.ast.cam.ac.uk/casuadc/ingarch}}.
+\citet{sabalisck1995supersonic} mentioned the main aspects of the observations (1990 July 31).
+The two-dimensional imaging spectroscopy was captured using an IPCS-II detector and the 125 $\mu$m etalon.
+The cumulative integration time per frame is 36 s with a seeing value of 1''.
+The format of the data cube was of 256*256*100 with a spatial scale of 0.26 pixel$^{-1}$.
+Finally, the reduction and analysis was done with the packages TAUCAL y TAUFITS \citep{1992ASPC...25..445L}.
+The NGC 604 TAURUS-II observations were used by \citet{sabalisck1995supersonic}, \citet{tanco1997} and \citet{2019arXiv191203543M}.
 
@@
 It has approximately 250 stars of the OB type, 13 Supergiants and 9 WR \citep{1996AJ....111.1128M}, ten WRs confirmed with spectroscopy \citet{1993AJ....105.1400D}, nine of the WN type and a WC, located near the bright core of the region.
-
-\subsection{Observations}
-
-%We use data from \citet{1987A&A...176..347H} and \citet{arthur2016turbulence} to study of turbulence in the Orion Nebula.
-%\cite{1987A&A...176..347H} observations were obtained using a 106 cm-Cassegrain telescope at Observatorium Hoher List. 
-%A Fabry-Pérot interferometer was used with a étalon a separation of 0.5 mm. 
-%Interferograms have been taken with different pointing directions of the telescope's optical axis in the nebula. 
-%The exposures are overlapped and fall into one square of a grid with a width of 1' centered at \(\theta^{1}\)Ori C.
-
-We use data from \citet{arthur2016turbulence} to study of turbulence in the Orion Nebula.
-Their observations were initially published by \citet{Garcia-Diaz:2008a}. 
-The data was obtained with the echelle spectrograph attached to the 4 m telescope at Kitti Peak National Observatory (KPNO).
-These observation cover 3 \(\times\) 5 arcmin\(^{2}\) of the central (Huygens) part of the Orion nebula.
-The data consist of 96, North-South orientated 300 arcsec slits at 2 arcsec intervals with a width of 0.8 arcsec with a velocity resolution of 8 km s\(^{-1}\).
-
-Archival data from \citet{Damiani:2016a} and \citet{Damiani:2017b} are use to study the Carina nebula and Lagoon nebula, respectively. 
-The ESO VLT/FLAMES multi-fiber spectograph \citep{2002Msngr.110....1P} was used for these observations (Gaia-ESO Survey internal release \(iDR4\)). 
-The Survey targets are low-mass stars ranging down to magnitude V \(\sim\) 18.5.
-Mainly the spectra were obtained with the spectographs Giraffe (HR15N setup \(R \sim19 000\), wavelength range 6444-6818 \AA) and the UVES (setup 580, R \(\sim\)4700, range 4768-6830 \AA).
-
-Using observations from \citet{Castro:2018a} (private communication) we study 30 Dor.
-NGC 2070 was observed as part of the MUSE SV (Science Verification) programme at the Very Large Telescope (VLT) in August 2014, when the instrument was new. 
-Four overlapping fields, each with an individual field of 1' \(\times\) 1' and a pixel scale of 0.2''/pixel were observed with exposure times of 4 \(\times\) 10s, 4 \(\times\) 60s, and 4 \(\times\) 600s.
-The table 1 on their work summarize the propertie of each field.
-The data were reduced using the MUSE pipeline based on ESOREX recipes, with final astrometric calibration using the catalog of \citet{1999A&A...341...98S}. 
-The final spectra span 4595-9366 \AA, with a resolving power of \(R \sim3 000\) around \halpha\  \citep{Castro:2018a}.
-
-The archival data used in this work for the extragalactic giant regions, NGC 604, NGC 595, Hubble X and Hubble V was obtained with the Fabry Perot TAURUS-II instrument in the 4.2-m William Herschel Telescope (WHT) of del Roque de los Muchachos Observatory (ORM) in La Palma, Spain and was retrieved from the La Palma archive\footnote{\url{http://casu.ast.cam.ac.uk/casuadc/ingarch}}.
-\citet{sabalisck1995supersonic} mentioned the main aspects of the observations (1990 July 31).
-The two-dimensional imaging spectroscopy was captured using an IPCS-II detector and the 125 $\mu$m etalon.
-The cumulative integration time per frame is 36 s with a seeing value of 1''.
-The format of the data cube was of 256*256*100 with a spatial scale of 0.26 pixel$^{-1}$.
-Finally, the reduction and analysis was done with the packages TAUCAL y TAUFITS \citep{1992ASPC...25..445L}.
-The NGC 604 TAURUS-II observations were used by \citet{sabalisck1995supersonic}, \citet{tanco1997} and \citet{2019arXiv191203543M}.
 

### 2021-12-09 strucfunc_paper.tex
Finish description of datasets and make a start on sample sources

@@
 %% Package set-up
+\usepackage{booktabs}
+\usepackage{array}   % for \newcolumntype macro
+\newcolumntype{L}{>{$}l<{$}} % math-mode version of lrc column types
+\newcolumntype{R}{>{$}r<{$}} 
+\newcolumntype{C}{>{$}c<{$}}
 
@@
 and in external galaxies
-\citep{1961MNRAS.122....1F, tanco1997, lagrois2009multi, lagrois2011, Melnick:2021x}.
+\citep{1961MNRAS.122....1F, Medina-Tanco:1997a, lagrois2009multi, lagrois2011, Melnick:2021x}.
 
@@
 
+Wherever possible, we calculate the centroid velocity directly as the first moment
+of the line intensity profile for each position on the nebula.
+So long as the signal-to-noise is high enough,
+this mean velocity can be calculated to a much higher precision
+than the nominal velocity resolution of the spectrograph. 
+In a few cases, as noted below, we are working with already reduced data,
+which are provided in the form of Gaussian fits to the line profiles.
+In the cases where multiple Gaussian components have been fitted,
+we take the flux-weighted mean velocity of these components to be the centroid.
+
 \subsubsection{Longslit echelle spectroscopy}
@@
 
-Archival data from \citet{Damiani:2016a} and \citet{Damiani:2017b} are use to study the Carina nebula and Lagoon nebula, respectively. 
-The ESO VLT/FLAMES multi-fiber spectograph \citep{2002Msngr.110....1P} was used for these observations (Gaia-ESO Survey internal release \(iDR4\)). 
-The Survey targets are low-mass stars ranging down to magnitude V \(\sim\) 18.5.
-Mainly the spectra were obtained with the spectographs Giraffe (HR15N setup \(R \sim19 000\), wavelength range 6444-6818 \AA) and the UVES (setup 580, R \(\sim\)4700, range 4768-6830 \AA).
+Archival data from \citet{Damiani:2016a} and \citet{Damiani:2017b} are used
+to study the Carina Nebula and Lagoon Nebula, respectively.
+These were obtained as a by-product of a study of young stars in their respective regions
+as part of the Gaia-ESO Spectroscopic Survey \citep{Gilmore:2012v, Randich:2013m}
+using VLT/FLAMES with the GIRAFFE and UVES spectrographs \citep{2002Msngr.110....1P}.
+The spectra are from multiple discrete fiber positions in each nebula
+(866 positions in Carina; 1089 in the Lagoon),
+visible as colored disks in Figure~\ref{fig:velocity-maps}.
+The angular separation between fibers varies across the maps with
+average nearest-neighbor distance of \SI{21 \pm 17}{arcsec}.
+The spectral resolution ranges from  \SI{6}{km.s^{-1}} (UVES) to \SI{16}{km.s^{-1}} (GIRAFFE).
+We do not have access to the individual spectra, but instead use the
+Gaussian fits to the line profiles from \citep{Damiani:2016a, Damiani:2017b},
+obtained from data tables downloaded from the CDS Vizier service.\footnote{%
+  \url{https://doi.org//10.26093/cds/vizier.35910074} and
+  \url{https://doi.org//10.26093/cds/vizier.36040135}.}
+For the Lagoon, we use single-Gaussian fits, while for Carina we take the
+flux-weighted mean of the blue and red component of two-Gaussian fits.
 
@@
 
-Using observations from \citet{Castro:2018a} (private communication) we study 30 Dor.
-NGC 2070 was observed as part of the MUSE SV (Science Verification) programme at the Very Large Telescope (VLT) in August 2014, when the instrument was new. 
-Four overlapping fields, each with an individual field of 1' \(\times\) 1' and a pixel scale of 0.2''/pixel were observed with exposure times of 4 \(\times\) 10s, 4 \(\times\) 60s, and 4 \(\times\) 600s.
-The table 1 on their work summarize the propertie of each field.
-The data were reduced using the MUSE pipeline based on ESOREX recipes, with final astrometric calibration using the catalog of \citet{1999A&A...341...98S}. 
-The final spectra span 4595-9366 \AA, with a resolving power of \(R \sim3 000\) around \halpha\  \citep{Castro:2018a}.
+For the Magellanic Cloud regions 30~Doradus and NGC~346 we use data obtained
+with the MUSE spectrograph \citep{Bacon:2010a, Bacon:2014a} on the VLT.\@
+Each exposure consists of a \(300 \times 300\) pixel spectral image with a plate scale
+of \SI{0.2}{arcsec.pixel^{-1}} and a spectral resolution of \SI{110}{km.s^{-1}}
+at \ha{}.
+For 30~Doradus, four separate exposures are mosaicked to give a square field of
+size \(\SI{2}{arcmin}\) \citep{Castro:2018a}. 
+We use centroid velocities of single Gaussian fits to the \ha{} line.\footnote{%
+  Data kindly provided by Norberto Castro Rodríguez, priv.~comm.
+}
+For NGC~346, we use a single field that was observed in 2016 as part of
+ESO observing program 098.D-0211(A) (P.I. W.-R.~Hamann).
+We obtained the pipeline-reduced data cubes from the ESO data archive\footnote{%
+  \url{http://archive.eso.org/wdb/wdb/eso/eso_archive_main/query?prog_id=098.D-0211(A)}
+}
+and extracted the \ha{} profile using tools in the MPDAF python library.\footnote{
+  \url{https://mpdaf.readthedocs.io/en/latest/}
+}
 
@@
 
-The archival data used in this work for the extragalactic giant regions, NGC 604, NGC 595, Hubble X and Hubble V was obtained with the Fabry Perot TAURUS-II instrument in the 4.2-m William Herschel Telescope (WHT) of del Roque de los Muchachos Observatory (ORM) in La Palma, Spain and was retrieved from the La Palma archive\footnote{\url{http://casu.ast.cam.ac.uk/casuadc/ingarch}}.
-\citet{sabalisck1995supersonic} mentioned the main aspects of the observations (1990 July 31).
-The two-dimensional imaging spectroscopy was captured using an IPCS-II detector and the 125 $\mu$m etalon.
-The cumulative integration time per frame is 36 s with a seeing value of 1''.
-The format of the data cube was of 256*256*100 with a spatial scale of 0.26 pixel$^{-1}$.
-Finally, the reduction and analysis was done with the packages TAUCAL y TAUFITS \citep{1992ASPC...25..445L}.
+The archival data used in this work for the extragalactic giant regions, NGC 604, NGC 595, Hubble X and Hubble V was obtained with the Fabry Perot TAURUS-II instrument
+\citep{Gordon:2000v}
+on the \SI{4.2}{m} William Herschel Telescope (WHT) of
+el Roque de los Muchachos Observatory (ORM) in La Palma, Spain
+and was retrieved from the La Palma archive\footnote{\url{http://casu.ast.cam.ac.uk/casuadc/ingarch}}.
+Each velocity image is \(256 \times 256\) pixels on the sky,
+with a spatial scale of \SI{0.26}{arcsec.pixel^{-1}}
+and a spectral resolution of \SI{40}{km.s^{-1}}.
+The NGC~604 observations were previously reported and analysed in
+\citet{sabalisck1995supersonic}, \citet{Medina-Tanco:1997a} and \citet{Melnick:2021x}.
+
+% \citet{sabalisck1995supersonic} mentioned the main aspects of the observations (1990 July 31).
+% The two-dimensional imaging spectroscopy was captured using an IPCS-II detector and the 125 $\mu$m etalon.
+% The cumulative integration time per frame is 36 s with a seeing value of 1''.
+% The format of the data cube was of 256*256*100 with a spatial scale of 0.26 pixel$^{-1}$.
+% Finally, the reduction and analysis was done with the packages TAUCAL y TAUFITS \citep{1992ASPC...25..445L}.
 The NGC 604 TAURUS-II observations were used by \citet{sabalisck1995supersonic}, \citet{tanco1997} and \citet{2019arXiv191203543M}.
 
-\subsection{Regions in the Milky Way and Magellanic Clouds}
+\subsection{Physical properties of the sample regions}
 \label{sec:regions-milky-way}
+
+\begin{table}
+\begin{center}\caption{Summary of properties of our \hii{} region sample}
+\begin{tabular}{l CCCC}\toprule
+\hii{}    &  \text{Distance,}\ D& \text{Diameter,}\ R & \log L(\ha) &  \langle \sigma\los \rangle \\
+  Region    &  [\si{kpc}]          &  [\si{pc}]    &  [\si{erg.s^{-1}}]            &    [\si{km.s^{-1}}]  \\ 
+\midrule
+Orion    & 0.436 \pm 0.02  & 0.6 \pm 0.06  &    37               &   6.0      \\
+%Orion large   & 0.436 \pm 0.02  & 5 \pm 0.5    &    37               &   6.0      \\ 
+Lagoon    & 1.25 \pm 0.12   & 25 \pm 2.5       &    37.47            &   13.6     \\
+Carina    & 2.35 \pm 0.05   & 15 \pm 1.5       &    39.6             &   22.4     \\
+30 Dor    & 50.0 \pm 0.2  & 98.9 \pm 9.8     &    39.76            &   31.7     \\
+NGC 346   & 62 \pm 1    & 64 \pm 6.4       &    38.67            &   10.2     \\
+Hubble X  & 490 \pm 40      & 160 \pm 16      &    38.6             &   13.4     \\
+Hubble V  & 490 \pm 40      & 130 \pm 13 &    38.87            &   12.3     \\
+NGC 604   & 820 \pm 30      & 400 \pm 40      &    39.65            &   16.2     \\
+NGC 595   & 820 \pm 30      & 400 \pm 40      &    39.36            &   18.3     \\
+\bottomrule
+\end{tabular}\label{tab:Reg}
+\end{center}
+\end{table}
+
+\subsubsection{Orion Nebula}
+\label{sec:orion-nebula}
 
@@
 Some of these young stars are accountable for stellar jets and Herbig-Haro objects seen in the nebula \citep{arthur2016turbulence}.
+
+\subsubsection{Carina Nebula}
+\label{sec:carina-nebula}
 
@@
 
+\subsubsection{Lagoon Nebula}
+\label{sec:lagoon-nebula}
+
 The Lagoon Nebula (M8, NGC6523) is located at a distance of 1 250 pc \citep{2005A&A...430..941P} and contains the young stellar cluster NGC6530.
@@
 
+\subsubsection{30 Doradus}
+\label{sec:30-doradus}
+
 The Tarantula Nebula (30 Doradus) is a luminous star-forming region in the LMC (Large Magellanic Cloud) and is the most luminous complex in the Local Group \citep{1984ApJ...287..116K}.
@@
 
+\subsubsection{NGC 346}
+\label{sec:ngc-346}
+
 NGC 346 is the most active star-formation region in the SMC (Small Magellanic Cloud) located at a distance of 62 kpc \citep{2001ApJ...562..303D}. 
@@
 This mechanism is similar to shell-like H ii regions, with a central cluster in a cavity, and with ongoing star formation triggered around their periphery.
+
+\subsubsection{Hubble X and Hubble V in NGC 6822}
+\label{sec:hubble-x-hubble}
 
@@
 HV is located near 'Hodge OB 8', and HX is located near 'Hodge OB13'  \citep{1999PASP..111.1382O}.
+
+\subsubsection{NGC~595 and NGC~604 in M33}
+\label{sec:ngc-595-ngc}
 
@@
 It has approximately 250 stars of the OB type, 13 Supergiants and 9 WR \citep{1996AJ....111.1128M}, ten WRs confirmed with spectroscopy \citet{1993AJ....105.1400D}, nine of the WN type and a WC, located near the bright core of the region.
-
-\begin{table*}
-\begin{center}\caption{Summary of properties.}
-\begin{tabular}{ccccc}\hline
-HII       &  Distance ($D$)          & Diameter ($R$) & log L(H$_{\alpha}$) &  \(\langle \sigma_{\text{LOS}} \rangle \) \\
-Region    &  [kpc]          &  [pc]    &  [erg/s]            &    [km/s]  \\ 
-\hline
-Orion    & 0.436$\pm$0.02  & 0.6$\pm$0.06  &    37               &   6.0      \\
-%Orion large   & 0.436$\pm$0.02  & 5$\pm$0.5    &    37               &   6.0      \\ 
-Lagoon    & 1.25$\pm$0.12   & 25$\pm$2.5       &    37.47            &   13.6     \\
-Carina    & 2.35$\pm$0.05   & 15$\pm$1.5       &    39.6             &   22.4     \\
-30 Dor    & 49.97$\pm$0.19  & 98.9$\pm$9.8     &    39.76            &   31.7     \\
-NGC 346   & 61.9$\pm$1.1    & 64$\pm$6.4       &    38.67            &   10.2     \\
-Hubble X  & 490$\pm$40      & 160$\pm$16      &    38.6             &   13.4     \\
-Hubble V  & 490$\pm$40      & 130$\pm$13 &    38.87            &   12.3     \\
-NGC 604   & 820$\pm$30      & 400$\pm$40      &    39.65            &   16.2     \\
-NGC 595   & 820$\pm$30      & 400$\pm$40      &    39.36            &   18.3     \\
-\hline
-\end{tabular}\label{tab:Reg}
-\end{center}
-\end{table*}
 
@@
 
-There is broad agreement in our structure function results and previous studies that consider NGC 604, mainly because where are using the same data \citep{tanco1997,2019arXiv191203543M}. 
-from \citet{tanco1997} and \citet{2019arXiv191203543M}, and using the same TAURUS-II data.
+There is broad agreement in our structure function results and previous studies that consider NGC 604, mainly because where are using the same data \citep{Medina-Tanco:1997a, Melnick:2021x}. 
+from \citet{Medina-Tanco:1997a} and \citet{Melnick:2021x}, and using the same TAURUS-II data.
 Despite this general agreement the interpretations in each study is different.
-\citet{tanco1997} conclude about a double regime acting on the kinetic energy spectrum.
+\citet{Medina-Tanco:1997a} conclude about a double regime acting on the kinetic energy spectrum.
 According to this double cascading, turbulence is being forced at scales of \(\approx\)10 pc while and energy cascade has developed down to the smallest scales and other, as an inverse cascade, extends up to scale of \(\approx\)70 pc.
-Interesting enough, \citet{tanco1997} mentioned various characteristic scale lengths, the most notorious is the \(\approx\)10 pc, a value close to our correlation length of \(\approx\)9 pc, and they interpret it as possible source on energy associated with the expansion of shocks coming from wind bubbles.
+Interesting enough, \citet{Medina-Tanco:1997a} mentioned various characteristic scale lengths, the most notorious is the \(\approx\)10 pc, a value close to our correlation length of \(\approx\)9 pc, and they interpret it as possible source on energy associated with the expansion of shocks coming from wind bubbles.
 None of the previous studies present a power-law index for the structure function to compare our results.
@@
 
-JGV acknowledges and thanks CONACYT for the PhD research scholarship.
+Based on observations made with KPNO telescopes
+\textit{complete KPNO acknowldgment}.
+Based on observations made with ESO Telescopes at the La Silla Paranal Observatory under programme IDs 076.C-0888 and 098.D-0211.
+Based on observations made as part of the Gaia-ESO Spectroscopic Survey
+\textit{complete Gaia-ESO acknowldgment}.
+Based on observations made with the WHT
+\textit{complete WHT acknowldgment}.
+JGV acknowledges and thanks CONACyT-Mexico for a PhD research scholarship.
 We are grateful to Norberto Castro Rodríguez for providing maps of emission line velocity moments for 30 Doradus derived from MUSE-VLT observations.

### 2021-12-17 strucfunc_paper.tex
Move turbulence section to discussion

@@
 
-\section{Methods}\label{sec:met}
+\section{Plane-of-sky velocity fluctuations}\label{sec:met}
+
+\subsection{The second-order structure function}
+\label{sec:second-order-struct}
+One of the fundamental properties of turbulent clouds must be spatial fluctuations in velocity and density.
+These fluctuations are observed as projected spatial fluctuations in the average line-of-sight velocity and integrated column density.
+It is possible to describe the statistical properties of these fluctuations if they are assumed as a product of a stochastic field \citep{1984ApJ...277..556S}. 
+This previous assumption give us the ability to apply statistical tools to the velocity field and the analysis of the velocity pattern is reduced to the calculation of the averages and correlations.
+
+The second-order structure function of the velocity centroids, $B(r)$, is defined as:
+%
+\begin{equation}\label{eq:Br}
+  B(\boldsymbol{r}) = \dfrac{1}{N(\boldsymbol{r})}
+  \,
+  \sum_{\text{pairs}} \bigl[
+  V_{c}(\boldsymbol{x} + \boldsymbol{r}) - V_{c}(\boldsymbol{x})
+  \bigr]^{2}
+\end{equation}
+%
+where $N(\boldsymbol{r})$ is the number of pair points at each separation \(\boldsymbol{r}\), called lag. 
+In the Kolmogorov model \(B(r) \propto r^{2/3}\).
+
+The variance of the centroid velocity fluctuations is:
+%
+\begin{equation}\label{eq:variance}
+\sigma^2  = \frac{1}{N} \sum_{\text{pixels}} \bigl[ V_c (\boldsymbol{x}) -\langle V_ c\rangle  \bigr]^2
+\end{equation}
+%
+the, \(\langle V_c \rangle \) is the mean centroid velocity
+%
+\begin{equation}\label{eq:mean}
+\langle V_c \rangle \  = \frac{1}{N} \sum_{\text{pixels}} V_c (\boldsymbol{x})
+\end{equation}
+%
+The summation in Equation \ref{eq:Br} is over all data pairs for each separation \(N(\boldsymbol{r})\).
+The summations in Equations \ref{eq:variance} and \ref{eq:mean} are over the total number of valid pixels in the (\textit{x},\textit{y})-plane.
+
+\subsection{Application to our HII regions sample}\label{sec:apply}
+
+The autocovariance function is:
+
+\begin{equation}\label{eq:Cr}
+C(\boldsymbol{r}) = \dfrac{\sum_{\text{pairs}}[V_{c}(\boldsymbol{x} + \boldsymbol{r}) \times V_{c}(\boldsymbol{x}) ]} {N(\boldsymbol{r})}
+\end{equation}
+%
+and is another statistical tool used in studying the turbulent flows.
+The interpretation of the Equation \ref{eq:Cr} depends on the assumption of homogeneity, which may be violated for astrophysical processes.
+Because of this, Equation \ref{eq:Br} is a better approach to characterize the velocity fluctuations even in the presence of large scale linear gradients and may be sensitive to a wider range of scales \citep{1984ApJ...277..556S}.
+
+For the homogeneous random field, Equations \ref{eq:Br} and \ref{eq:Cr} are related by:
+
+\begin{equation}\label{eq:functional}
+B(r; r_0, m) = 2\sigma^2 \bigl( 1 - C(r) \bigr)
+\end{equation}
+
+%Based on Equation \ref{eq:functional} we use the functional of the structure function in the form:
+%
+%\begin{equation}\label{eq:ff}
+%b(r; r_0, m) = 2\sigma^2 \bigl( 1 - C(r) \bigr)
+%\end{equation}
+%
+%where  is now the new form of the correlation function in the form:
+where $C(r)$ is a new form that we propose of the correlation function:
+%
+\begin{equation}\label{eq:ffnew}
+  C(r) = \exp \left[ -(\ln 2) \left( \frac{r}{r_0} \right)^m \right]
+\end{equation}
+%
+substituting the previously $C(r)=1/[1+(r/r_{0})^{m}]$ \citep{1966igd..book.....K,1984ApJ...277..556S}.
+
+The term $r_{0}$ is the correlation length of the turbulence, the value of \(r\) in pc where equation \ref{eq:Br} reach the value of \(\sigma^2\), and $m$ is the index that adjust our results.
+In this idealized case, at scales larger than r$_{0}$ the structure function flattens as it tends towards the asymptotic value of 2$\sigma$ \citep{arthur2016turbulence}.
+
+The model proposed to describe the seeing at small scales is:
+%
+\begin{equation}\label{eq:ffs}
+  S(r; s_0, r_0) = \frac{
+    e^{-s_0 / r_0}
+  }{
+    1+(2s_0 / r)^{2 / 3}
+  }
+\end{equation}
+%
+and the model that consider the effect of the observational box size is:
+
+\begin{equation}\label{eq:ffb}
+% \beta(r_0) = 1 - exp[\frac{L_{box}}{3.6r_0}] 
+  \beta(r_0) = 1 - \exp \left[ -L_{\text{box}} / (3.6 r_0) \right] 
+\end{equation}
+%
+where $L_{\text{box}}$ is the diagonal length of the observational box.
+
+The final form of our proposed functional of the structure function is in the form:
+%
+\begin{equation}\label{eq:fff}
+B(r) = b(r; \beta r_0, \beta m) \times S(r; s_0, r_0) + B_{\text{noise}}
+\end{equation}
+
+The results obtained with equation \ref{eq:Br} are use in a non-linear least-squares
+fit to obtain the best values for the turbulent parameters. 
+We use equation \ref{eq:fff} in a chi-square analysis applying the equation:
+%
+\begin{equation}\label{eq:chi}
+  \chi^2 = \sum_i ^N \frac{[y_i^{\text{measure}}-y_i^{\text{model}} (\boldsymbol{v})]^2}{\epsilon_i ^2}
+\end{equation}
+%
+using the package \textit{lmfit} \citep{newville_matthew_2014_11813}.
+
+In this way we avoid one fundamental problem in the interpretation of the structure function results. 
+The slope in the majority of previous studies and hence, the correlation length, is obtained without a formal procedure. 
+The traditional way to find it is to determine a particular range of ascending values in the structure function results. 
+If this increase in values is stopped or reversed it is commonly assumed that one particular inertial range has been found. 
+In some cases this procedure keeps going up to large scales, giving two or more inertial regimes leading to the erroneous interpretation of multiple inertial scales.
 
 \subsection{Turbulence}
+
+\textit{Will 2021-12-10: Moving this section to later for now. Maybe
+  this material could go in discussion}
 
@@
 %For supersonic turbulence the index is $\beta=-2$ \citep{burg}.
-
-\subsection{The second-order structure function}
-\label{sec:second-order-struct}
-One of the fundamental properties of turbulent clouds must be spatial fluctuations in velocity and density.
-These fluctuations are observed as projected spatial fluctuations in the average line-of-sight velocity and integrated column density.
-It is possible to describe the statistical properties of these fluctuations if they are assumed as a product of a stochastic field \citep{1984ApJ...277..556S}. 
-This previous assumption give us the ability to apply statistical tools to the velocity field and the analysis of the velocity pattern is reduced to the calculation of the averages and correlations.
-
-The second-order structure function of the velocity centroids, $B(r)$, is defined as:
-%
-\begin{equation}\label{eq:Br}
-  B(\boldsymbol{r}) = \dfrac{1}{N(\boldsymbol{r})}
-  \,
-  \sum_{\text{pairs}} \bigl[
-  V_{c}(\boldsymbol{x} + \boldsymbol{r}) - V_{c}(\boldsymbol{x})
-  \bigr]^{2}
-\end{equation}
-%
-where $N(\boldsymbol{r})$ is the number of pair points at each separation \(\boldsymbol{r}\), called lag. 
-In the Kolmogorov model \(B(r) \propto r^{2/3}\).
-
-The variance of the centroid velocity fluctuations is:
-%
-\begin{equation}\label{eq:variance}
-\sigma^2  = \frac{1}{N} \sum_{\text{pixels}} \bigl[ V_c (\boldsymbol{x}) -\langle V_ c\rangle  \bigr]^2
-\end{equation}
-%
-the, \(\langle V_c \rangle \) is the mean centroid velocity
-%
-\begin{equation}\label{eq:mean}
-\langle V_c \rangle \  = \frac{1}{N} \sum_{\text{pixels}} V_c (\boldsymbol{x})
-\end{equation}
-%
-The summation in Equation \ref{eq:Br} is over all data pairs for each separation \(N(\boldsymbol{r})\).
-The summations in Equations \ref{eq:variance} and \ref{eq:mean} are over the total number of valid pixels in the (\textit{x},\textit{y})-plane.
-
-\subsection{Application to our HII regions sample}\label{sec:apply}
-
-The autocovariance function is:
-
-\begin{equation}\label{eq:Cr}
-C(\boldsymbol{r}) = \dfrac{\sum_{\text{pairs}}[V_{c}(\boldsymbol{x} + \boldsymbol{r}) \times V_{c}(\boldsymbol{x}) ]} {N(\boldsymbol{r})}
-\end{equation}
-%
-and is another statistical tool used in studying the turbulent flows.
-The interpretation of the Equation \ref{eq:Cr} depends on the assumption of homogeneity, which may be violated for astrophysical processes.
-Because of this, Equation \ref{eq:Br} is a better approach to characterize the velocity fluctuations even in the presence of large scale linear gradients and may be sensitive to a wider range of scales \citep{1984ApJ...277..556S}.
-
-For the homogeneous random field, Equations \ref{eq:Br} and \ref{eq:Cr} are related by:
-
-\begin{equation}\label{eq:functional}
-B(r) = 2\sigma^2 \bigl( 1 - C(r) \bigr)
-\end{equation}
-
-Based on Equation \ref{eq:functional} we use the functional of the structure function in the form:
-%
-\begin{equation}\label{eq:ff}
-b(r; r_0, m) = 2\sigma^2 \bigl( 1 - C(r) \bigr)
-\end{equation}
-%
-where $C(r)$ is now the new form of the autocorrelation function in the proposed form:
-%
-\begin{equation}\label{eq:ffnew}
-  C(r) = \exp \left[ -(\ln 2) \left( \frac{r}{r_0} \right)^m \right]
-\end{equation}
-%
-substituting the previously $C(r)=1/[1+(r/r_{0})^{m}]$ \citep{1966igd..book.....K,1984ApJ...277..556S}.
-
-The term $r_{0}$ is the correlation length of the turbulence, the value of \(r\) in pc where equation \ref{eq:Br} reach the value of \(\sigma^2\), and $m$ is the index that adjust our results.
-In this idealized case, at scales larger than r$_{0}$ the structure function flattens as it tends towards the asymptotic value of 2$\sigma$ \citep{arthur2016turbulence}.
-
-The model proposed to describe the seeing at small scales is:
-%
-\begin{equation}\label{eq:ffs}
-  S(r; s_0, r_0) = \frac{
-    e^{-s_0 / r_0}
-  }{
-    1+(2s_0 / r)^{2 / 3}
-  }
-\end{equation}
-%
-and the model that consider the effect of the observational box size is:
-
-\begin{equation}\label{eq:ffb}
-% \beta(r_0) = 1 - exp[\frac{L_{box}}{3.6r_0}] 
-  \beta(r_0) = 1 - \exp \left[ -L_{\text{box}} / (3.6 r_0) \right] 
-\end{equation}
-%
-where $L_{\text{box}}$ is the diagonal length of the observational box.
-
-The final form of our proposed functional of the structure function is in the form:
-%
-\begin{equation}\label{eq:fff}
-B(r) = b(r; \beta r_0, \beta m) \times S(r; s_0, r_0) + B_{\text{noise}}
-\end{equation}
-
-The results obtained with equation \ref{eq:Br} are use in a non-linear least-squares
-fit to obtain the best values for the turbulent parameters. 
-We use equation \ref{eq:fff} in a chi-square analysis applying the equation:
-%
-\begin{equation}\label{eq:chi}
-  \chi^2 = \sum_i ^N \frac{[y_i^{\text{measure}}-y_i^{\text{model}} (\boldsymbol{v})]^2}{\epsilon_i ^2}
-\end{equation}
-%
-using the package \textit{lmfit} \citep{newville_matthew_2014_11813}.
-
-In this way we avoid one fundamental problem in the interpretation of the structure function results. 
-The slope in the majority of previous studies and hence, the correlation length, is obtained without a formal procedure. 
-The traditional way to find it is to determine a particular range of ascending values in the structure function results. 
-If this increase in values is stopped or reversed it is commonly assumed that one particular inertial range has been found. 
-In some cases this procedure keeps going up to large scales, giving two or more inertial regimes leading to the erroneous interpretation of multiple inertial scales.
 
@@
 Based on observations made with KPNO telescopes
-\textit{complete KPNO acknowldgment}.
+\textit{complete KPNO acknowledgment}.
 Based on observations made with ESO Telescopes at the La Silla Paranal Observatory under programme IDs 076.C-0888 and 098.D-0211.
 Based on observations made as part of the Gaia-ESO Spectroscopic Survey
-\textit{complete Gaia-ESO acknowldgment}.
+\textit{complete Gaia-ESO acknowledgment}.
 Based on observations made with the WHT
-\textit{complete WHT acknowldgment}.
+\textit{complete WHT acknowledgment}.
 JGV acknowledges and thanks CONACyT-Mexico for a PhD research scholarship.

### 2021-12-29 Corr.tex
Javier changes 2021-12-29

@@
 \hline
-    log $r_0$ &             log $R$ &   0.691$\pm$0.079 &   -0.85$\pm$0.148 &   0.984 &    <10\(^{-5}\) \\
- log $\sigma$ &            log L(H) &   0.166$\pm$0.129 &  -5.698$\pm$5.002 &    0.64 &  0.06 \\
- log $\sigma$ &  log $\sigma_{LOS}$ &    0.749$\pm$0.62 &  -0.132$\pm$0.729 &   0.575 &  0.10 \\
- log $\sigma$ &         log $r_{0}$ &   0.195$\pm$0.207 &   0.679$\pm$0.139 &   0.493 &  0.17 \\
-      log $m$ &            log Dist &   -0.07$\pm$0.091 &   1.113$\pm$0.185 &  -0.436 &  0.24 \\
-      log $m$ &         log $r_{0}$ &  -0.031$\pm$0.086 &  -0.001$\pm$0.059 &  -0.295 &  0.44 \\
-      log $m$ &        log $\sigma$ &  -0.094$\pm$0.264 &   0.061$\pm$0.204 &  -0.241 &  0.53 \\
+    log $r_0$ &             log $R$ &   0.684$\pm$0.068 &   -0.83$\pm$0.123 &   0.983 &    0.0 \\
+ log $\sigma$ &            log L(H) &   0.175$\pm$0.095 &  -6.039$\pm$3.673 &   0.716 &   0.02 \\
+ log $\sigma$ &  log $\sigma_{LOS}$ &   0.813$\pm$0.475 &  -0.208$\pm$0.543 &   0.668 &  0.035 \\
+      log $m$ &            log Dist &  -0.111$\pm$0.081 &   1.209$\pm$0.155 &  -0.592 &  0.072 \\
+ log $\sigma$ &         log $r_{0}$ &   0.221$\pm$0.182 &    0.65$\pm$0.122 &   0.545 &  0.103 \\
+      log $m$ &        log $\sigma$ &  -0.142$\pm$0.237 &    0.106$\pm$0.18 &  -0.421 &  0.226 \\
+      log $m$ &         log $r_{0}$ &  -0.046$\pm$0.084 &   0.015$\pm$0.055 &  -0.387 &  0.269 \\
 \hline

### 2021-12-29 extrastuff.tex
Javier changes 2021-11-26
Javier changes 2021-12-29

@@
+We use data from \citet{1987A&A...176..347H} and \citep{arthur2016turbulence} to study of turbulence in the Orion Nebula.
+\cite{1987A&A...176..347H} observations were obtained using a 106 cm-Cassegrain telescope at Observatorium Hoher List. 
+A Fabry-Pérot interferometer was used having the étalon a separation of 0.5 mm. 
+Interferograms have been taken with different pointing directions of the telescope's optical axis in the nebula. 
+The exposures are overlapped and fall into one square of a grid with a width of 1' centered at \(\theta^{1}\)Ori C.
+
 %The idea of a virial system has been developed by \citet{1993ApJ...418..767T,munoz1996} into the \textit{Cometary Stirring Model} (CSM) with the aim to separate the mechanism that contribute to the line broadening.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%The analysis employed until now is not conclusive about the true velocity fluctuations observed in each nebula. 
+%As pointed out by \citet{arthur2016turbulence} other techniques also allow us to study these fluctuations.

### 2021-12-29 strucfunc_paper.tex
Javier changes 2021-12-17
Javier changes 2021-12-29

@@
   The true velocity dispersion \(\sigma\), which spans from 3 to 15 km s\(^{-1}\), the
-  autocorrelation length \(r_0\) covering to 0.06 - 8 pc, and the power-law slope \(m\) of the velocity field, which ranges from 0.7 to 1.3.
+  autocorrelation length \(r_0\) covering to 0.06 - 8 pc, and the power-law slope \(m\) of the velocity field, which ranges from 0.7 to 1.5.
   The velocity dispersion is found to correlate primarily with luminosity and the autocorrelation length correlates primarily with the size of the region.
-  A comparison between \(\sigma\) and \(\sigma_{POS}\) shows that this last value is at roughly the double for all regions.
+  A comparison between \(\sigma\) and \(\sigma_{POS}\) shows that this last value is roughly the double for all regions.
   We found that our proposed functional form describe with more accuracy the inertial range and our methodology guarantees consistency for comparison between the galactic and giant HII regions.
@@
 \begin{equation}\label{eq:functional}
-B(r; r_0, m) = 2\sigma^2 \bigl( 1 - C(r) \bigr)
+b(r; r_0, \sigma^2, m) = 2\sigma^2 \bigl( 1 - C(r) \bigr)
 \end{equation}
@@
 \begin{equation}\label{eq:fff}
-B(r) = b(r; \beta r_0, \beta m) \times S(r; s_0, r_0) + B_{\text{noise}}
+B(r) = b(r; \beta r_0, \beta \sigma^2,m) \times S(r; s_0, r_0) + B_{\text{noise}}
 \end{equation}
@@
 
+\subsection{Velocity fields of the HII regions}
+
+\textit{Javier 2021-12-28: I'm not quite sure the correct section for this.
+Since they aren't results, per se, and until now I haven't develop to much discussion with them, I move it here so it end up like Methods and Data, before reporting our findings.
+}
+
+The Figure \ref{fig:velocity-maps} shows the velocity maps of each HII region in the \halpha\ emission line.
+All velocities are relative to the systemic velocity of each region, with more negative velocities shown in blue and more positive velocities in red.
+The range of velocities is different for each region and is shown in each map.
+The more negative velocities are shown in blue and more positive velocities are shown in red.
+The Figure \ref{fig:hist} shows the probability density functions of our sample of HII regions.
+All the distributions are far from being consider Gaussian, implying that there are multiple kinematics components in the regions.
+
+\begin{figure*}
+ \centering
+ \includegraphics[width=5in]{Figures/Hist}\par
+ \caption{Histograms of the centroid velocities in \halpha\ of our sample of HII regions. }
+ \label{fig:hist}
+\end{figure*}
+
+\section{Results}\label{sec:results}
+
 \subsection{Turbulence}
@@
 \textit{Will 2021-12-10: Moving this section to later for now. Maybe
-  this material could go in discussion}
+  this material could go in discussion.
+Javier 2021-12-28: In deciding the correct place for this part, if we ended up including it, I moved it to the results section.
+For now it makes sense to me because it is where the physical interpretation of the power law and the correlation length are presented for later report the results of each region.}
 
@@
 
-\section{Results}\label{sec:results}
-
-\subsection{Data}
-
-The Figure \ref{fig:velocity-maps} shows the velocity maps of each HII region in the \halpha\ emission line.
-All velocities are relative to the systemic velocity of each region, with more negative velocities shown in blue and more positive velocities in red.
-The range of velocities is different for each region and is shown in each map.
-The more negative velocities are shown in blue and more positive velocities are shown in red.
-The Figure \ref{fig:hist} shows the probability density functions of our sample of HII regions.
-All the distributions are far from being consider Gaussian, implying that there are multiple kinematics components in the regions.
-
-\begin{figure*}
- \centering
- \includegraphics[width=5in]{Figures/Hist/Hist}\par
- \caption{Histograms of the centroid velocities in \halpha\ of our sample of HII regions. }
- \label{fig:hist}
-\end{figure*}
-
 \subsection{HII regions structure functions}
@@
   \caption{Second-order structure functions for the velocity centroid images of the \(H\alpha\) emission line}\label{fig:strucfunc-fit-C}
+\end{figure*}
+
+\begin{figure*}
+  \centering
+  \includegraphics[width=0.8\linewidth]{Figures/strucfunc-fit-D}
+  \caption{Second-order structure functions for the velocity centroid images of the \(H\alpha\) emission line}\label{fig:strucfunc-fit-D}
 \end{figure*}
@@
 
+In the section \ref{sec:results} we showed that each HII region has a turbulent velocity field that can be characterized using the turbulence theory.
+The turbulent parameters obtained are unique to each velocity field.
+We proceed to develop scaling relations between them and between the physical properties of each region.
+We also do a comparison between our results with previous structure functions.
+
 \subsection{Correlations between physical properties and turbulent parameters}
@@
 
-This line of investigation is followed using the scaling relation as a research tool between the properties of the sample of HII regions and our results. 
+We follow through this analysis using the scaling relation as a research tool between the properties of the sample of HII regions and our results. 
 We use the properties in Table \ref{tab:Reg} with the turbulent parameters in Table \ref{tab:Res} as the dependent variable to adjust a fit in the form $Y = aX +b$. 
@@
 The results are shown in Table \ref{tab:RestStats} in ascending order for the p-value.
-In the Figures \ref{fig:rvsR}-\ref{fig:svss} we show the correlations with a significance level  $p \leq $0.10.
+In the Figures \ref{fig:rvsR}-\ref{fig:svss} we show the correlations with a significance level  $p < $0.05.
 In all the figures the slope of the fit shown in solid black line is the mean of all red lines that reflect the posterior of the Bayessian analysis.
@@
 The Figure \ref{fig:rvsR} shows the strongest correlation, being this between the correlation length $r_0$ and the size $R$ of the region.
-The relationship we found is relation of $\log r_0 = (0.69 \pm 0.07) \log R-(0.85 \pm 0.14)$.
+The relationship we found is relation of $\log r_0 = (0.68 \pm 0.06) \log R-(0.83 \pm 0.12)$.
 
@@
 Since this relation is the most common it can be use for comparison with the investigations mentioned at the beginning of this section.
-Our results give us a relation of $\log \sigma = (0.16 \pm 0.12) \log \text{L}(\text{H}_{\alpha})-(5.6 \pm 5.0)$.
+Our results give us a relation of $\log \sigma = (0.17 \pm 0.1) \log \text{L}(\text{H}_{\alpha})-(6 \pm 4.0)$.
 It is customary in the literature to present $\text{L} (\text{H}_{\alpha})$ as the dependent variable.
 In our case if we choose the upper positive error and take the inverse of slope we have \(\text{L}_{\text{H}_{\alpha}} \propto \sigma^{3.5}\). 
-Using the same procedure in \textit{linmix} and changing the variables we obtained $\log \text{L}(\text{H}_{\alpha}) = (3.32\pm 1.89) \log \sigma -(36.23 \pm 1.45)$.
+Using the same procedure in \textit{linmix} and changing the variables we obtained $\log \text{L}(\text{H}_{\alpha}) = (3.2\pm 2) \log \sigma -(36.23 \pm 1.45)$.
 Both relations are close to the previously proposed \(\text{L}_{\text{H}_{\alpha}} \propto \sigma^{4}\)
@@
 
-The Figure \ref{fig:svss} shows the log $\sigma$-log $\sigma_{\text{LOS}}$ plane with a relationship of $\log \sigma = (0.75 \pm 0.60) \log \sigma_{\text{LOS}}-(0.13 \pm 0.70)$ .
+The Figure \ref{fig:svss} shows the log $\sigma$-log $\sigma_{\text{LOS}}$ plane with a relationship of $\log \sigma = (0.81 \pm 0.47) \log \sigma_{\text{LOS}}-(0.2 \pm 0.54)$ .
 
@@
 
-In Section \ref{sec:apply} we mentioned the reduced chi-square method we are using for determining the correlation length and the index of the slope.
-Since this is the first time this method is applied to a sample of HII regions (at least for our knowledge), the results are bounded to be different from previous investigations, including the one that have the same observations as \citet{arthur2016turbulence} and \citet{2019arXiv191203543M}.
+In Section \ref{sec:apply} we mentioned the reduced chi-square method we are using for the determination of the correlation length and the index of the slope.
+Since this is the first time this method is applied to a sample of HII regions (at least for our knowledge), our results are bounded to be different from previous investigations, including the one that have the same observations as \citet{arthur2016turbulence} and \citet{2019arXiv191203543M}.
 
@@
 \textit{complete WHT acknowledgment}.
-JGV acknowledges and thanks CONACyT-Mexico for a PhD research scholarship.
 We are grateful to Norberto Castro Rodríguez for providing maps of emission line velocity moments for 30 Doradus derived from MUSE-VLT observations.
+JGV acknowledges and thanks CONACyT-Mexico for the PhD research scholarship.
 
@@
 
+For a correct analysis on the structure function it is necessary to consider the consequences that the observational box size and the seeing have on the results.
+To quantify the impact of these considerations on the final structure function, we perform a series of experiments using artificial turbulent velocity maps.
+In particular, our interest is to quantify how this observational limitations affect the determination of parameters such as the correlation length, \(r_0\), and the velocity field variance, \(\sigma^2 \).
+
+The artificial velocity maps are created using a modified version of the \textit{make$\_$extend} command from the \textit{turbustat} package \citep{Koch2019AJ....158....1K}.
+We create a turbulent velocity field that follows a given power law with and a proposed correlation length, and a variance value indicated as true \(\sigma^2\).
+Using this true \(\sigma^2\) we obtained the true \(r_0\), and these values are used as a reference in the following experiments to quantify the variations.
+The objective is to create a sample of multiple divided maps with different seeing width to compute the structure function in each and characterize the variations.
+
 \subsection{Finite box effects}
 \label{sec:finite-box-effects}
+
+The Figure \ref{fig:finite-box}a shows some of the simulated velocity fields we use to study the variations in the structure function with respect to the size of the observational box.
+Initially we have an original field of \(512 \times 512 \) pixels that are divided \(n\) times and produce \(N = 4^n\) fields, where each one has a linear size \(L \times L \) with \(L = 2^{9 -n}\).
+The structure function is calculated for each division and later we average all the divisions of the corresponding map.
+
+The Figure \ref{fig:finite-box}b shows in solid lines the normalized averaged structure functions for the maps in Figure \ref{fig:finite-box}a.
+The number \(N\) of divisions and the length \(L\) are indicated in each structure function.
+The shaded areas show the deviation that each average structure function has due to the different divisions. 
+\textit{(Note: I modified the Figure adding \(\sigma^2\) and \(r_0\) for each SF since I think it is easier and more directly to grasp the effect of reducing the box size.
+The figure is more 'noisy' but if it seems like it contribute to nothing we can change it back.)}
+
+The blue horizontal and vertical dashed lines show the true \(r_{0}\) and the value of \(\text{B}(r) / \sigma^2 = 1 \), respectively.
+The colored dotted lines indicate the averages, taking into account all the divisions of each map, of the apparent \(r_ {0}\) and the apparent \(\sigma^2 \).
+From this analysis it is clear that \(r_0\) and \(\sigma^ 2 \) decrease with respect to the true values as the size \(L\) of the observational box decreases. 
+This analysis is performed on different maps (no images are shown) given a different power law in the velocity spectrum and different correlation lengths, giving the same results.
+
+Figure \ref{fig:finite-box-effect} shows the ratio of the correlation length of each averaged map with respect to the true correlation length, \(\text{apparent } r_ 0 /\text{true } r_0 \), as well as the ratio between the averaged variance of each divided map and the true variance, \(\text{apparent } \sigma^2  / \text{true } \sigma^2\).
+We observe that for the values where \(L\), is 20 $> r_0 $ the change in the ratios is null.
+It is for the values where \( L < 10 r_0 \) a considerable decrease in both ratios is observed.
+This behavior is fulfilled for all simulated maps with different power law in the velocity spectrum and different correlation functions, indicated with different colored circles in Figure \ref{fig:finite-box-effect}.
+These variations of the ratios are used to characterize the effect that the decrease of the observational box size has in \(r_0\) and \(\sigma^2\).
+
+The fitted dashed line in Figure \ref{fig:finite-box-effect} is given by the equation:
+
+\begin{equation}\label{eq:ajustebox}
+\beta(r_0) = 1 - exp \left[ \frac{L}{3.6r_0} \right] 
+\end{equation}
+%
+and it is used in the functional form that fits the observational structure function when adjusting the results to obtain the reported parameters \(r_0\) and \(\sigma^2 \).
 
@@
     (b)\\
-    \includegraphics[width=\linewidth]{Figures/fake-finite-box-strucfunc}
+    \includegraphics[width=\linewidth]{Figures/fake-finite-box-strucfunc2}
   \end{tabular}
@@
 \label{sec:effects-seeing-struc}
+
+Ground-based astronomical observations are affected by the seeing produced by the atmosphere.
+When calculating the structure function of these observations, this seeing affects the results at small-scale separations due to the smoothing of velocity fluctuations between adjacent pixels.
+To study the consequences of the seeing we calculate the structure function of velocity maps where an artificial Gaussian seeing with different line widths has been introduced.
+The artificial velocity maps are created in the same way as to study the effect of the observational box.
+Seeing in velocity maps is added via the \textit{astropy} package using the \textit{Gaussian2DKernel} command.
+
+The rows in Figure \ref{fig:seeing-reduction}a show a synthetic velocity field of 512 \(\times\) 512 divided into four maps of 256 \(\times \) 256.
+The color scale is the same for all maps and it considers \(- 3\) to \(+ 3\) times the standard deviation.
+A Gaussian seeing, \(s_0 \) is applied to each division, with an RMS width ranging from 1 to 32 pixels, shown in the columns of Figure \ref{fig:seeing-reduction}. 
+The structure function is computed in these maps and the averaged considering the same seeing.
+
+The solid lines in Figure \ref{fig:seeing-reduction}b  show the ratio of the structure function of the averages of the maps with their respective seeing and the map without it: \(B (r, s_0 ) / B (r, s_0 = 0) \).
+The circle symbols indicate the value of 2\(s_0\) while the plus symbols indicate the apparent correlation length of smoothed map.
+The vertical dotted line indicates the true \(r_ {0} \).
+
+The dashed lines in Figure \ref{fig:seeing-reduction}b are  empirically fits for each ratio.
+To obtain this fit, we start from a convolution of an emission line and Gaussian seeing.
+The emission line has the form \(\text {I}(x, v) = \text{I}_0 \phi [v; \overline {v} (x), \sigma_0]\) and has uniform width and brightness where the only change with respect to position is the velocity centroid.
+The proposed seeing is \(\text{K}(x, s_0)\) of the form \(1 / \sqrt{2 \pi s_0} \exp^ {-x^ 2 / 2s_0 ^ 2} \).
+The convolution \(\text{I}(x, v) \otimes \text{K}(x, s_0) \) is performed to obtain the smoothed map, \(\text {\~I} (x, v) \).
+
+Then we calculate the average velocity difference of the original map, \(\Delta v \), and the smoothed map,b\(\tilde{\Delta v}\), in the points \( x = \{0, \delta \} \).
+This expansion gives a term that modifies the final form of the structure function, \(\text{\~B} (r)\), where the structure function without the seeing, \(\text{B}(r) \), is corrected by the term \(S_0(r; s_0)\) which has the form:
+
+\begin{equation}\label{eq:seeingcon}
+S (r;s_0) = \tanh^2 \left[ \left( \dfrac{r}{2s_0} \right)^2 \right]
+\end{equation}
+
+Subsequently, the equation \ref{eq:seeingcon} is empirically modified and we obtain:
+
+\begin{equation}\label{eq:seeingemp}
+S(r; s_0, r_0) =  \frac{e^\frac{-s_0}{r_0}}{2} \left(1 + \tanh{a \text{ln} \frac{r}{2s_0}} \right)
+\end{equation}
+%
+and the final form of the equation \ref{eq:seeingemp} after a mathematical simplification gives:
+
+\begin{equation}\label{eq:seeingemp2}
+S(r; s_0, r_0) = \frac{e^\frac{-s_0}{r_0}}{1+(\frac{2s_0}{r})^{2a}}
+\end{equation}
+%
+which describes the fit (dashed lines) in Figure \ref{fig:seeing-reduction}b.
+
+The equation \ref{eq:seeingemp2} is used to correct the observational structure function, \(\text{B}(r)\).
 

### 2022-01-03 strucfunc_paper.tex
Javier changes 2022-01-02

@@
 
-The blue horizontal and vertical dashed lines show the true \(r_{0}\) and the value of \(\text{B}(r) / \sigma^2 = 1 \), respectively.
+The blue horizontal and vertical dashed lines show the true \(r_{0}\) and the value of \(B(r) / \sigma^2 = 1 \), respectively.
 The colored dotted lines indicate the averages, taking into account all the divisions of each map, of the apparent \(r_ {0}\) and the apparent \(\sigma^2 \).
@@
 Then we calculate the average velocity difference of the original map, \(\Delta v \), and the smoothed map,b\(\tilde{\Delta v}\), in the points \( x = \{0, \delta \} \).
-This expansion gives a term that modifies the final form of the structure function, \(\text{\~B} (r)\), where the structure function without the seeing, \(\text{B}(r) \), is corrected by the term \(S_0(r; s_0)\) which has the form:
+This expansion gives a term that modifies the final form of the structure function, \(~B (r)\), where the structure function without the seeing, \(B(r) \), is corrected by the term \(S_0(r; s_0)\) which has the form:
 
@@
 
-The equation \ref{eq:seeingemp2} is used to correct the observational structure function, \(\text{B}(r)\).
+The equation \ref{eq:seeingemp2} is used to correct the observational structure function, \(B(r)\).
 

### 2022-01-04 strucfunc_paper.tex
Describe measurement and use of line moments in sec 2.1

@@
 %The exposures are overlapped and fall into one square of a grid with a width of 1' centered at \(\theta^{1}\)Ori C.
-
-Wherever possible, we calculate the centroid velocity directly as the first moment
-of the line intensity profile for each position on the nebula.
+\newcommand\xx{\ensuremath{\boldsymbol{x}}}
+Wherever possible, we calculate the centroid velocity \(V_c\)
+directly as the normalized first velocity moment of the spectral line intensity profile
+for each plane-of-sky position \(\xx\) on the nebula:
+\(V_{c}(\xx) = M_1(\xx) / M_0(\xx)\).
+The \(k\)th unnormalized moment \(M_k\) of the continuum-subtracted
+spectral intensity profile \(I(v)\)
+is defined as
+\begin{equation}
+  \label{eq:kth-moment}
+  M_k = \int_{\Delta v} I(v) \, v^k \, dv
+\end{equation}
+where the Doppler velocity \(v\) is calculated according to
+the \texttt{VOPT} convention
+\citetext{Eq.~[32] of \citealt{Greisen:2006a}}:
+\begin{equation}
+  \label{eq:optical-velocity}
+  v \equiv c\, (\lambda - \lambda_0) / \lambda_0 ,
+\end{equation}
+where \(\lambda\) is the observed wavelength,
+\(\lambda_0\) is the rest wavelength, and \(c\) is the speed of light.
+The spectral window \(\Delta v\) is chosen to be just large enough to include
+the entire \ha{} emission line.
 So long as the signal-to-noise is high enough,
@@
 we take the flux-weighted mean velocity of these components to be the centroid.
+
+The observed RMS spectral line width \(\sigma'\) can likewise be found from
+the second velocity moment as
+\begin{equation}
+  \label{eq:observed-sigma}
+  \sigma'(\xx)^2  = [M_2(\xx) / M_0(\xx)] - V_{c}(\xx)^2 .
+\end{equation}
+However, many different broadening mechanisms contribute to this width,
+including the finite spectral resolution \(\sigma_{\mathrm{ins}}\),
+fine-structure splitting \(\sigma_{\mathrm{fs}}\),
+and thermal Doppler broadening \(\sigma_{\mathrm{t}}\).
+In the approximation that all these broadening mechanisms are independent
+and described by Gaussian profiles, then the dispersion of
+line-of-sight velocities due to bulk motions \(\sigma\los\) can be found
+by subtracting these contributions in quadrature from the observed width:
+\begin{equation}
+  \label{eq:sigma-los}
+  \sigma\los^2 = \sigma'^2 - \sigma_{\mathrm{ins}}^2 - \sigma_{\mathrm{fs}}^2 - \sigma_{\mathrm{t}}^2 .
+\end{equation}
 
@@
   \sum_{\text{pairs}} \bigl[
-  V_{c}(\boldsymbol{x} + \boldsymbol{r}) - V_{c}(\boldsymbol{x})
+  V_{c}(\xx + \boldsymbol{r}) - V_{c}(\xx)
   \bigr]^{2}
@@
 \begin{equation}\label{eq:variance}
-\sigma^2  = \frac{1}{N} \sum_{\text{pixels}} \bigl[ V_c (\boldsymbol{x}) -\langle V_ c\rangle  \bigr]^2
+\sigma^2  = \frac{1}{N} \sum_{\text{pixels}} \bigl[ V_c (\xx) -\langle V_ c\rangle  \bigr]^2
 \end{equation}
@@
 \begin{equation}\label{eq:mean}
-\langle V_c \rangle \  = \frac{1}{N} \sum_{\text{pixels}} V_c (\boldsymbol{x})
+\langle V_c \rangle \  = \frac{1}{N} \sum_{\text{pixels}} V_c (\xx)
 \end{equation}
@@
 \begin{equation}\label{eq:Cr}
-C(\boldsymbol{r}) = \dfrac{\sum_{\text{pairs}}[V_{c}(\boldsymbol{x} + \boldsymbol{r}) \times V_{c}(\boldsymbol{x}) ]} {N(\boldsymbol{r})}
+C(\boldsymbol{r}) = \dfrac{\sum_{\text{pairs}}[V_{c}(\xx + \boldsymbol{r}) \times V_{c}(\xx) ]} {N(\boldsymbol{r})}
 \end{equation}

### 2022-01-05 strucfunc_paper.tex
Javier changes 2022-01-05

@@
 and a spectral resolution of \SI{40}{km.s^{-1}}.
-The NGC~604 observations were previously reported and analysed in
+The NGC~604 observations were previously reported and analyzed in
 \citet{sabalisck1995supersonic}, \citet{Medina-Tanco:1997a} and \citet{Melnick:2021x}.
@@
 
-Orion (M42) is the prototype galactic HII region and one of the mores studied in the sky.
-Located at a distance of 440 pc \citep{2008AJ....136.1566O} its main physical and kinematics properties, along its stellar population are documented in \citet{2001ARA&A..39...99O}.
+Orion (M42) is the prototype galactic HII region located at a distance of 440 pc \citep{2008AJ....136.1566O}.
 The main ionizing star is \(\theta^{1}\)Ori C (spectral type \(\sim\)O7) and with other 3 B-type stars they form the Trapezium cluster.
-The position of Orion near the side of the Orion Molecular Cloud (OMC-1) make it an ongoing star formation region and a example of a blister HII region.
-Some of these young stars are accountable for stellar jets and Herbig-Haro objects seen in the nebula \citep{arthur2016turbulence}.
+The position of Orion near the side of the Orion Molecular Cloud (OMC-1) make it an ongoing star formation with a large population of young star, some of which are the sources of stellar jets and Herbig-Haro objects \citep{1993ApJ...410..696O}.
+Its physical properties and kinematics, along its stellar population are documented in \citet{2001ARA&A..39...99O}.
 
@@
 The Carina nebula is a large star-forming complex located at a distance of 2 350 pc \citep{2006ApJ...644.1151S}.
-Young clusters like Trumpler 14 and 16, and Collinder 228 together form the Car OB1 association.
-This OB association has more than 65 stars earlier than B0, and several Wolf-Rayet stars.
-The most star is a luminous blue variable, $\eta$ Car \citep{Damiani:2016a}.
-As a star formation region, it presents several phenomena related with young stars as evaporating protoplanetary discs, erosion of large dust pillars and the triggering of a second generation of embedded stars, Herbig-Haro objects, to mention some, \citet{2008hsf2.book..138S} and reference therein.
-An approaching and receding kinematics components are known in the nebula.
+Young clusters like Trumpler 14 and 16, and Collinder 228 form the Car OB1 association, one of the largest OB associations on the Galaxy.
+This OB association has more than 65 stars earlier than B0, and several Wolf-Rayet (WR) stars.
+The most luminous star is the blue variable $\eta$ Car.
+As a star formation region, it presents several phenomena related with young stars as evaporating protoplanetary discs, erosion of large dust pillars and the triggering of a second generation of embedded stars and Herbig-Haro objects, to mention some \citetext{ see \citealp{2008hsf2.book..138S} and reference therein}.
+This region can be consider as a bridge between the detailed star-formation regions like Orion, and much more distant regions like 30 Doradus.
 
@@
 
-The Lagoon Nebula (M8, NGC6523) is located at a distance of 1 250 pc \citep{2005A&A...430..941P} and contains the young stellar cluster NGC6530.
-The region is illuminated by different massive stars of spectral types O and B, the hottest being 9 Sgr, type O4V \citep{Damiani:2017b}.
-Optically, the brightest part of the nebula is called 'Hourglass nebula' which surrounds and obscures the star Herschel 36, type O7 \citep{1986AJ.....91..870W}. 
-The velocity field shows several expanding shells, related to the cluster NGC 6530, the O stars 9 Sgr and Herschel 36, and the massive protostar M8East-IR.
+The Lagoon Nebula (M8, NGC6523) is located at a distance of 1 250 pc \citep{2005A&A...430..941P}.
+It contains the young stellar cluster NGC6530 and the region is illuminated by different massive stars of spectral types O and B, the hottest being 9 Sgr, type O4V \citep{Damiani:2017b}.
+Optically, the brightest part of the nebula is called 'Hourglass nebula' which surrounds and obscures the O7 star Herschel 36 \citep{1986AJ.....91..870W}. 
+The velocity field shows several expanding shells, related to the stellar population, and the massive protostar M8East-IR \citep{1984ApJ...278..170S} indicating that recent star formation. 
 A blueshifted, neutral layer is also in very good agreement with predictions of champagne-flow models of blister HII regions \citep{Damiani:2017b}. 
@@
 
-The Tarantula Nebula (30 Doradus) is a luminous star-forming region in the LMC (Large Magellanic Cloud) and is the most luminous complex in the Local Group \citep{1984ApJ...287..116K}.
-The nebula is located at a distance of 49.9 kpc \citep{2013Natur.495...76P}.
-It host the star forming region NGC 2070 that contains the massive star cluster R136. 
-The star formation rate gas increased recently, 1-3 Myr ago \citep{2016ApJ...833..154C}, and the central ionized region spans for 40 pc.
-This nebula is used as a comparison for extragalactic star-forming regions.
+The 30 Doradus (Tarantula Nebula) nebula is located at a distance of 49.9 kpc \citep{2013Natur.495...76P}
+It is a luminous star-forming region in the LMC (Large Magellanic Cloud) and is the most luminous complex in the Local Group \citep{1984ApJ...287..116K}.
+The central ionized region spans for 40 pc and host the massive, dense star cluster R136
+%\citep{1991IAUS..148..145W}. Note: check the format 
+It host the active star forming region NGC 2070 \citep{2013AJ....145...98W} where the star-formation rate has recently peaked \citep{2015ApJ...811...76C}. 
+NGC 2070 host a population of OB and WR stars \citep{2011A&A...530A.108E}.
+This nebula is commonly used as a comparison for extragalactic star-forming regions.
 
@@
 It has more than 30 O stars that ionize N66, the largest HII region \citep{2011ApJ...740...10D}.
-\citet{2008ApJ...688.1050G} propose an expanding H II region or bubble blown by the winds of the massive progenitor as a mechanism that shapes the recent star formation in this region in addition to the photoionizing process of the OB stars.
+\citet{2008ApJ...688.1050G} propose an expanding H II region or bubble blown by the winds of the massive progenitor as a mechanism that shapes the recent star formation in this region, in addition to the photoionizing process of the OB stars.
 This mechanism is similar to shell-like H ii regions, with a central cluster in a cavity, and with ongoing star formation triggered around their periphery.
@@
 \subsubsection{Hubble X and Hubble V in NGC 6822}
-\label{sec:hubble-x-hubble}
-
-The dwarf irregular galaxy, NGC 6822, is located at a distance of 500 kpc (1'' = 2.4 pc) \citep{2012A&A...540A.135S} and the brightest HII regions are Hubble X and Hubble V (HX and HV hereafter).
-HV has a characteristic length of 100 pc and a luminosity at its core of in L$_{H_\alpha}$ = 1 $\times$ 10$^{49}$ H$\alpha$ photons s$^{-1}$ \citep{1999PASP..111.1382O}.
-HX has a characteristic length of 140 pc and a luminosity at its core of in L$_{H_\alpha}$ = 2.4 $\times$ 10$^{49}$ H$\alpha$ photons s$^{-1}$ \citep{1999PASP..111.1382O}.
-Two recognized OB associations \citep{1991ApJ...379..621H,1992AJ....104.1374W} are identified within the region of HV and HX.
-HV is located near 'Hodge OB 8', and HX is located near 'Hodge OB13'  \citep{1999PASP..111.1382O}.
+\label{sec:6822-hubble}
+%Note to me: incomplete section. Find more regions info and finish asap.
+The dwarf irregular galaxy, NGC 6822, is located at a distance of 500 kpc \citep{2012A&A...540A.135S} and the brightest HII regions are Hubble X and Hubble V (HX and HV hereafter). %(1'' = 2.4 pc)
+HV has a characteristic length of 100 pc and HX has a characteristic length of 140 pc \citep{1999PASP..111.1382O}.
+Two recognized OB associations \citep{1991ApJ...379..621H,1992AJ....104.1374W} are identified within these HII regions.
+HV is located near 'Hodge OB 8' and HX is located near 'Hodge OB13'  \citep{1999PASP..111.1382O}.
+
+%HV has a luminosity at its core of in L$_{H_\alpha}$ = 1 $\times$ 10$^{49}$ H$\alpha$ photons s$^{-1}$ 
+%HX has a luminosity at its core of in L$_{H_\alpha}$ = 2.4 $\times$ 10$^{49}$ H$\alpha$ photons s$^{-1}$ \citep{1999PASP..111.1382O}.
 
 \subsubsection{NGC~595 and NGC~604 in M33}
-\label{sec:ngc-595-ngc}
-
-NGC 604 is the brightest giant HII region in the M33 galaxy visually dominated by a big loop, many shells and different size filaments.
-It is located at the distance of 840 kpc (1'' = 4.1 pc) \citep{2015KamKinematics} with a length of 400 pc.
-It has a luminosity in L$_{H_\alpha}$ = 10$^{39.42}$ erg s$^{-1}$ \citep{2002MNRAS.329..481B} and in L$_{X}$=9.3$\times$ 10$^{35}$ erg s$^{-1}$ \citep{2008ApJ...685..919T}.
-\citet{2012ApJ...761....3M} derive an average age of 4$\pm$1 Myr and a total stellar mass of 1.6$^{+1.6}_{-1.0} \times$ 10$^{5}$M$_{\odot}$ for the region.
-The stellar population has been identified and classified by \citet{1996ApJ...456..174H} (and references therein).
-Recently, \citet{2011MNRAS.411..235E} focused on studying the Wolf-Rayet (WR) and red super giants (RSGs) stars population.
+\label{sec:m33-ngc}
+
+M33 is the third largest galaxy in the Local Group located at the distance of 840 kpc and is of morphological type SA(s)cd \citep{2015KamKinematics}.
+The two brightest HII regions in the galaxy are NGC 604 and NGC 595.
+
+NGC 604 the second brightest region of the local group after 30Dor in the Large Magellanic Cloud and is forty times larger ($\sim $ 400 pc) and 6,000 times brighter than Orion in our Milky Way galaxy.
+It is the brightest giant HII region in the M33 galaxy visually dominated by a big loop, big shells and different size filaments.
+Using photometry from the HST \citet{1996ApJ...456..174H} identified that the stars are separated into a primary cluster within NGC 604, and a secondary to the north of the region.
+In the primary there are \(\sim\)200 OB stars, candidate to red supergiants (RSGs) and the presence of WR stars.
+For the northern cluster they find eight luminous stars and no evolved massive stars.
+More Recently, \citet{2011MNRAS.411..235E} studied 10 WR stars and propose at least 4 RSGs candidates.
 \citet{2012AJ....143...43F} focused on the massive young stellar objects (MYSOs).
-The average ages for the stars, was determined to be from 3 to 5 Myr \citep{1996ApJ...456..174H} and with the RSGs as an older population have an age of 12.4 $\pm$ 2.1 Myr \citep{2011MNRAS.411..235E}.
+The average ages for the stars, was determined to be from  \num{3} to \SI{5}{Myr} \citep{1996ApJ...456..174H} and with the RSGs as an older population have an age of 12.4\(\pm\)2.1 Myr \citep{2011MNRAS.411..235E}.
 This suggest that two episodes of star formation, at least, have taken place in the GEHR.
-%\citep{1984A&A...141...49H} identified a gradient from the west to the SE of the nebula of 30 km s$^{-1}$.
-
-NGC 595 is the second brightest giant HII region in the M33 galaxy.
+
+%It has a luminosity in L$_{H_\alpha}$ = 10$^{39.42}$ erg s$^{-1}$ \citep{2002MNRAS.329..481B} and in L$_{X}$=9.3$\times$ 10$^{35}$ erg s$^{-1}$ \citep{2008ApJ...685..919T}.
+%\citet{2012ApJ...761....3M} derive an average age of 4$\pm$1 Myr and a total stellar mass of 1.6$^{+1.6}_{-1.0} \times$ 10$^{5}$M$_{\odot}$ for the region.
+
+NGC 595 is the second brightest giant HII region in the M33 galaxy and has an \ha{} shell morphology that is related to the stellar winds of the several massive stars located in its interior.
+\citet{1993AJ....105.1400D} use optical photometry to propose 11 WR stars. 
+Using HST/WFPC-2 images \citet{1996AJ....111.1128M} found approximately 250 stars of the OB type, 13 Supergiants and 10 WR, confirming previous candidates.
+They derived and age of 4.5\(\pm\)1.0 Myr consistent with \citet{1993AJ....105.1400D}.
+\citet{2010MNRAS.402.1635R} used Integral Field Spectroscopy (IFS) to present a resolved study of the physical properties of the ionized gas and the ionized structure.
+They also confirm the presence of previous cataloged WR stars and detect new candidates, and propose classical emission-line ratios as metallicity calibrators.
+\citet{lagrois2011} present a kinematic study of the regions using optical emission lines and and radio 21 cm line observations.
+They proposed Champagne flows at the periphery of the molecular cloud leading to accelerated ionized material.
+
+%\citet{1983A&A...119..185V} made an estimate of the total masses of HI and HII in the nebula to obtain values of M$_{HI}=$ 1.2 $\times$ 10 $^{6}$ M$_{\odot}$ and M$_{HII} =$ 4.6 $\times$ 10 $^{5}$ M$_{\odot}$, and a ionizing luminosity of the star cluster is estimated at 5 $\times$ 10$^{50}$ erg s $^{1}$.
 %The electronic temperature is 7,670 $\pm$116 K \citep{2010MNRAS.402.1635R}.
-\citet{1983A&A...119..185V} made an estimate of the total masses of HI and HII in the nebula to obtain values of M$_{HI}=$ 1.2 $\times$ 10 $^{6}$ M$_{\odot}$ and M$_{HII} =$ 4.6 $\times$ 10 $^{5}$ M$_{\odot}$, and a ionizing luminosity of the star cluster is estimated at 5 $\times$ 10$^{50}$ erg s $^{1}$.
-\citet{1996AJ....111.1128M} estimate an age of 4.5 Myrs consistent with \citet{1993AJ....105.1400D}.
-It has approximately 250 stars of the OB type, 13 Supergiants and 9 WR \citep{1996AJ....111.1128M}, ten WRs confirmed with spectroscopy \citet{1993AJ....105.1400D}, nine of the WN type and a WC, located near the bright core of the region.
-
 %2013ApJ...773...69G M33 dist
 % \citep{1984ApJ...287..116K} \citep{1986ApJ...300..624R}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-Then we calculate the average velocity difference of the original map, \(\Delta v \), and the smoothed map,b\(\tilde{\Delta v}\), in the points \( x = \{0, \delta \} \).
+Then we calculate the average velocity difference of the original map, \(\Delta v \), and the smoothed map, \(\tilde{\Delta v}\), in the points \( x = \{0, \delta \} \).
 This expansion gives a term that modifies the final form of the structure function, \(~B (r)\), where the structure function without the seeing, \(B(r) \), is corrected by the term \(S_0(r; s_0)\) which has the form:

### 2022-01-08 strucfunc_paper.tex
Javier changes 2022-01-08

@@
 \begin{table}
-\begin{center}\caption{Summary of properties of our \hii{} region sample}
-\begin{tabular}{l CCCC}\toprule
+\begin{center}\caption{Summary of properties of our \hii{} region sample. }
+\begin{tabular}{cCCCC}\toprule
 \hii{}    &  \text{Distance,}\ D& \text{Diameter,}\ R & \log L(\ha) &  \langle \sigma\los \rangle \\
@@
 Orion     & 0.436 \pm 0.02  & 0.6 \pm 0.06    &    37       &   6.0      \\
-%Orion large   & 0.436 \pm 0.02  & 5 \pm 0.5    &    37               &   6.0      \\ 
-Lagoon    & 1.25 \pm 0.12   & 25 \pm 2.5       &    37.47            &   13.6     \\
-Carina    & 2.35 \pm 0.05   & 15 \pm 1.5       &    39.6             &   22.4     \\
-30 Dor    & 50.0 \pm 0.2  & 98.9 \pm 9.8     &    39.76            &   31.7     \\
-NGC 346   & 62 \pm 1    & 64 \pm 6.4       &    38.67            &   10.2     \\
-Hubble X  & 490 \pm 40      & 160 \pm 16      &    38.6             &   13.4     \\
-Hubble V  & 490 \pm 40      & 130 \pm 13 &    38.87            &   12.3     \\
-NGC 604   & 820 \pm 30      & 400 \pm 40      &    39.65            &   16.2     \\
-NGC 595   & 820 \pm 30      & 400 \pm 40      &    39.36            &   18.3     \\
+Lagoon    & 1.25 \pm 0.12   & 25 \pm 2.5      &    37.47    &   13.6 \pm 0.04     \\
+Carina    & 2.35 \pm 0.05   & 15 \pm 1.5      &    38.54    &   22.4 \pm 0.09    \\
+30 Dor    & 50.0 \pm 0.2    & 98.9 \pm 9.8    &    39.46    &   31.7     \\
+NGC 346   & 62 \pm 1        & 64 \pm 6.4      &    38.77    &   10.1     \\
+Hubble X  & 490 \pm 40      & 160 \pm 16      &    38.21    &   13.4     \\
+Hubble V  & 490 \pm 40      & 130 \pm 13      &    38.3     &   12.3     \\
+NGC 595   & 820 \pm 30      & 400 \pm 40      &    38.95    &   18.3 \pm 0.06     \\
+NGC 604   & 820 \pm 30      & 400 \pm 40      &    39.42    &   16.2 \pm 0.08     \\
 \bottomrule
@@
 
-Orion (M42) is the prototype galactic HII region located at a distance of 440 pc \citep{2008AJ....136.1566O}.
+The Orion Nebula (M42) is the prototype galactic HII region located at a distance of 440 pc \citep{2008AJ....136.1566O}.
 The main ionizing star is \(\theta^{1}\)Ori C (spectral type \(\sim\)O7) and with other 3 B-type stars they form the Trapezium cluster.
@@
 The Carina nebula is a large star-forming complex located at a distance of 2 350 pc \citep{2006ApJ...644.1151S}.
+Using the \ha{} luminosity as a diagnostic of the ionizing flux \(Q_0\) \citet{2007MNRAS.379.1279S} measured a value of \SI{e50.47}{photons.s^{-1}}.
 Young clusters like Trumpler 14 and 16, and Collinder 228 form the Car OB1 association, one of the largest OB associations on the Galaxy.
@@
 The most luminous star is the blue variable $\eta$ Car.
-As a star formation region, it presents several phenomena related with young stars as evaporating protoplanetary discs, erosion of large dust pillars and the triggering of a second generation of embedded stars and Herbig-Haro objects, to mention some \citetext{ see \citealp{2008hsf2.book..138S} and reference therein}.
+As a star formation region, it presents several phenomena related with young stars as evaporating protoplanetary discs, erosion of large dust pillars and the triggering of a second generation of embedded stars and Herbig-Haro objects, to mention some \citetext{see \citealp{2008hsf2.book..138S} and reference therein}.
 This region can be consider as a bridge between the detailed star-formation regions like Orion, and much more distant regions like 30 Doradus.
@@
 The Lagoon Nebula (M8, NGC6523) is located at a distance of 1 250 pc \citep{2005A&A...430..941P}.
+It has a luminosity in \ha{} of \SI{e37.47}{erg.s^{-1}}\citep{1984ApJ...287..116K}.
 It contains the young stellar cluster NGC6530 and the region is illuminated by different massive stars of spectral types O and B, the hottest being 9 Sgr, type O4V \citep{Damiani:2017b}.
@@
 It is a luminous star-forming region in the LMC (Large Magellanic Cloud) and is the most luminous complex in the Local Group \citep{1984ApJ...287..116K}.
-The central ionized region spans for 40 pc and host the massive, dense star cluster R136
-%\citep{1991IAUS..148..145W}. Note: check the format 
+The central ionized region spans for 40 pc and host the massive, dense star cluster R136 %\citep{1991IAUS..148..145W}. %Note: check the format
+The ionizing output \(Q_0\) of R136 is \SI{e51.4}{photons.s^{-1}} \citep{2020MNRAS.499.1918B}.
 It host the active star forming region NGC 2070 \citep{2013AJ....145...98W} where the star-formation rate has recently peaked \citep{2015ApJ...811...76C}. 
@@
 It has more than 30 O stars that ionize N66, the largest HII region \citep{2011ApJ...740...10D}.
-\citet{2008ApJ...688.1050G} propose an expanding H II region or bubble blown by the winds of the massive progenitor as a mechanism that shapes the recent star formation in this region, in addition to the photoionizing process of the OB stars.
-This mechanism is similar to shell-like H ii regions, with a central cluster in a cavity, and with ongoing star formation triggered around their periphery.
+N66 has an \ha{} luminosity of \SI{e38.77}{erg.s^{-1}}, almost 60 times higher compared to the Orion Nebula \citep{2010A&A...517A..39H,1984ApJ...287..116K}.
+\citet{2008ApJ...688.1050G} propose an expanding HII region or bubble blown by the winds of the massive progenitor as a mechanism that shapes the recent star formation in this region, in addition to the photoionizing process of the OB stars.
+This mechanism is similar to shell-like HII regions, with a central cluster in a cavity, and with ongoing star formation triggered around their periphery.
+Using a Gaussian single-component \citet{2003ApJ...586.1179D} find a corrected FWHM bulk turbulence of \SI{23.8}{km.s^{-1}}.
 
@@
 %Note to me: incomplete section. Find more regions info and finish asap.
-The dwarf irregular galaxy, NGC 6822, is located at a distance of 500 kpc \citep{2012A&A...540A.135S} and the brightest HII regions are Hubble X and Hubble V (HX and HV hereafter). %(1'' = 2.4 pc)
+The irregular dwarf galaxy, NGC 6822, is located at a distance of 500 kpc \citep{2012A&A...540A.135S} and the brightest HII regions are Hubble X and Hubble V (HX and HV hereafter). %(1'' = 2.4 pc)
 HV has a characteristic length of 100 pc and HX has a characteristic length of 140 pc \citep{1999PASP..111.1382O}.
-Two recognized OB associations \citep{1991ApJ...379..621H,1992AJ....104.1374W} are identified within these HII regions.
+Luminosity \ha{} for HV is \SI{e38.3}{erg.s^{-1}} and for HX is \SI{e38.21}{erg.s^{-1}} \citep{2002MNRAS.329..481B}.
+Two recognized OB associations are identified within these HII regions \citep{1991ApJ...379..621H,1992AJ....104.1374W}.
 HV is located near 'Hodge OB 8' and HX is located near 'Hodge OB13'  \citep{1999PASP..111.1382O}.
@@
 It is the brightest giant HII region in the M33 galaxy visually dominated by a big loop, big shells and different size filaments.
+It has a luminosity in \ha{} of \SI{e39.42}{erg.s^{-1}}\citep{2002MNRAS.329..481B}.
 Using photometry from the HST \citet{1996ApJ...456..174H} identified that the stars are separated into a primary cluster within NGC 604, and a secondary to the north of the region.
@@
 
-%It has a luminosity in L$_{H_\alpha}$ = 10$^{39.42}$ erg s$^{-1}$ \citep{2002MNRAS.329..481B} and in L$_{X}$=9.3$\times$ 10$^{35}$ erg s$^{-1}$ \citep{2008ApJ...685..919T}.
+% and in L$_{X}$=9.3$\times$ 10$^{35}$ erg s$^{-1}$ \citep{2008ApJ...685..919T}.
 %\citet{2012ApJ...761....3M} derive an average age of 4$\pm$1 Myr and a total stellar mass of 1.6$^{+1.6}_{-1.0} \times$ 10$^{5}$M$_{\odot}$ for the region.
@@
 NGC 595 is the second brightest giant HII region in the M33 galaxy and has an \ha{} shell morphology that is related to the stellar winds of the several massive stars located in its interior.
+It has a luminosity in \ha{} of \SI{e38.95}{erg.s^{-1}}\citep{2002MNRAS.329..481B}.
 \citet{1993AJ....105.1400D} use optical photometry to propose 11 WR stars. 

### 2022-01-08 strucfunc_paper.tex
Move velocity fields section

@@
 \subsection{Spectroscopic datasets}
-
+\label{sec:spectr-datas}
 %We use data from \citet{1987A&A...176..347H} and \citet{arthur2016turbulence} to study of turbulence in the Orion Nebula.
@@
 \end{equation}
+See sec~5.1 of \citet{Garcia-Diaz:2008a} for further details.
 
@@
 
+% \subsection{Velocity fields of the HII regions}
+
+% \textit{Javier 2021-12-28: I'm not quite sure the correct section for this.
+Since they aren't results, per se, and until now I haven't develop to much discussion with them, I move it here so it end up like Methods and Data, before reporting our findings.
+}
+
+Figure~\ref{fig:velocity-maps} shows maps of the \ha{} centroid velocity
+\(V_c\) for each \hii{} region in our sample,
+calculated as described above in section~\ref{sec:spectr-datas}
+and after subtracting the mean systemic velocity in each case.
+The color scheme ranges from the most negative velocities in blue
+to the most positive velocities in red,
+but the amplitude of the velocity fluctuations differs considerably between regions,
+as indicated by the color scale bar on each map,
+ranging from \SI{\pm 7}{km.s^{-1}} for the Lagoon
+up to  \SI{\pm 40}{km.s^{-1}} for 30~Doradus.
+This can be appreciated quantitatively in Figure~\ref{fig:hist},
+which shows the probability density function (PDF) of \(V_c\) for each region
+on a common velocity scale and arranged in order of decreasing amplitude
+of velocity fluctuations. 
+All the distributions are far from being consider Gaussian, implying that there are multiple kinematics components in the regions.
+
+\begin{figure*}
+ \centering
+ \includegraphics[width=5in]{Figures/Hist}\par
+ \caption{Histograms of the centroid velocities in \halpha\ of our sample of HII regions. }
+ \label{fig:hist}
+\end{figure*}
+
 \subsection{The second-order structure function}
@@
 In some cases this procedure keeps going up to large scales, giving two or more inertial regimes leading to the erroneous interpretation of multiple inertial scales.
-
-\subsection{Velocity fields of the HII regions}
-
-\textit{Javier 2021-12-28: I'm not quite sure the correct section for this.
-Since they aren't results, per se, and until now I haven't develop to much discussion with them, I move it here so it end up like Methods and Data, before reporting our findings.
-}
-
-The Figure \ref{fig:velocity-maps} shows the velocity maps of each HII region in the \halpha\ emission line.
-All velocities are relative to the systemic velocity of each region, with more negative velocities shown in blue and more positive velocities in red.
-The range of velocities is different for each region and is shown in each map.
-The more negative velocities are shown in blue and more positive velocities are shown in red.
-The Figure \ref{fig:hist} shows the probability density functions of our sample of HII regions.
-All the distributions are far from being consider Gaussian, implying that there are multiple kinematics components in the regions.
-
-\begin{figure*}
- \centering
- \includegraphics[width=5in]{Figures/Hist}\par
- \caption{Histograms of the centroid velocities in \halpha\ of our sample of HII regions. }
- \label{fig:hist}
-\end{figure*}
 

### 2022-01-13 Corr.tex
Javier changes 2022-01-13

@@
 \begin{center}
-\caption{Linear regressions values in the form Y = aX + b between our turbulent parameters obtained using the chi-square statistic and properties of each region (Table \ref{tab:Reg}).
+\caption{Linear regressions values in the form Y = aX + b between our turbulent parameters obtained using the chi-square statistic and properties of each region (Table \ref{tab:regions-properties}).
 The fifth column, $r$, is the Pearson correlation coefficient and the last column is the $p$-value.
@@
 \hline
-    log $r_0$ &             log $R$ &   0.684$\pm$0.068 &   -0.83$\pm$0.123 &   0.983 &    0.0 \\
- log $\sigma$ &            log L(H) &   0.175$\pm$0.095 &  -6.039$\pm$3.673 &   0.716 &   0.02 \\
- log $\sigma$ &  log $\sigma_{LOS}$ &   0.813$\pm$0.475 &  -0.208$\pm$0.543 &   0.668 &  0.035 \\
-      log $m$ &            log Dist &  -0.111$\pm$0.081 &   1.209$\pm$0.155 &  -0.592 &  0.072 \\
- log $\sigma$ &         log $r_{0}$ &   0.221$\pm$0.182 &    0.65$\pm$0.122 &   0.545 &  0.103 \\
-      log $m$ &        log $\sigma$ &  -0.142$\pm$0.237 &    0.106$\pm$0.18 &  -0.421 &  0.226 \\
-      log $m$ &         log $r_{0}$ &  -0.046$\pm$0.084 &   0.015$\pm$0.055 &  -0.387 &  0.269 \\
-\hline
+    log $r_0$ &             log $R$ &   0.69 $\pm$ 0.07 &   -0.83 $\pm$ 0.12 &   0.98 &    < 10\(^{-4}\) \\
+ log $\sigma$ &            log L(H) &   0.25 $\pm$ 0.10 &  -8.90 $\pm$ 3.63 &   0.83 &  0.003 \\
+ log $\sigma$ &  log $\sigma_{LOS}$ &   0.78 $\pm$ 0.46 &  -0.17 $\pm$ 0.54 &   0.66 &  0.036 \\
+      log $m$ &            log Dist &  -0.11 $\pm$ 0.08 &    1.21 $\pm$ 0.16 &  -0.59 &  0.072 \\
+ log $\sigma$ &         log $r_{0}$ &   0.22 $\pm$ 0.19 &   0.65 $\pm$ 0.12 &   0.54 &  0.103 \\
+      log $m$ &        log $\sigma$ &  -0.14 $\pm$ 0.24 &    0.11 $\pm$ 0.18 &   -0.42 &  0.227 \\
+      log $m$ &         log $r_{0}$ &   -0.04 $\pm$ 0.08 &   0.01 $\pm$ 0.05 &  -0.38 &   0.27 \\
+\bottomrule
 \end{tabular}\label{tab:RestStats}

### 2022-01-13 strucfunc_paper.tex
Javier changes 2022-01-13

@@
 each region in our sample
-and Table~\ref{tab:Reg} lists their most important physical parameters.
+and Table~\ref{tab:regions-properties} lists their most important physical parameters.
 The derived centroid \ha{} velocity maps are shown in Figure~\ref{fig:velocity-maps}.
@@
 \midrule
-Orion     & 0.436 \pm 0.02  & 0.6 \pm 0.06    &    37       &   6.0      \\
+Orion     & 0.436 \pm 0.02  & 0.6 \pm 0.06    &    37.18       &   6.0      \\
 Lagoon    & 1.25 \pm 0.12   & 25 \pm 2.5      &    37.47    &   13.6 \pm 0.04     \\
@@
 \bottomrule
-\end{tabular}\label{tab:Reg}
+\end{tabular}\label{tab:regions-properties}
 \end{center}
@@
 The Orion Nebula (M42) is the prototype galactic HII region located at a distance of 440 pc \citep{2008AJ....136.1566O}.
-The main ionizing star is \(\theta^{1}\)Ori C (spectral type \(\sim\)O7) and with other 3 B-type stars they form the Trapezium cluster.
+The O7 V star \(\theta^{1}\) Ori C is the most luminous and hottest star \citep{2006A&A...448..351S} with an ionizing flux \(Q_0\) of  \SI{e49.12}{photons.s^{-1}}. 
+With other 3 B-type stars they form the Trapezium cluster.
 The position of Orion near the side of the Orion Molecular Cloud (OMC-1) make it an ongoing star formation with a large population of young star, some of which are the sources of stellar jets and Herbig-Haro objects \citep{1993ApJ...410..696O}.
@@
 where $N(\boldsymbol{r})$ is the number of pair points at each separation \(\boldsymbol{r}\), called lag. 
-In the Kolmogorov model \(B(r) \propto r^{2/3}\).
-
 The variance of the centroid velocity fluctuations is:
@@
 
-The autocovariance function is:
+The autocovariance function:
 
@@
 %
-and is another statistical tool used in studying the turbulent flows.
+is another statistical tool used in studying the turbulent flows.
 The interpretation of the Equation \ref{eq:Cr} depends on the assumption of homogeneity, which may be violated for astrophysical processes.
@@
 
-For the homogeneous random field, Equations \ref{eq:Br} and \ref{eq:Cr} are related by:
+For an homogeneous random field equations \ref{eq:Br} and \ref{eq:Cr} are related by:
 
 \begin{equation}\label{eq:functional}
-b(r; r_0, \sigma^2, m) = 2\sigma^2 \bigl( 1 - C(r) \bigr)
-\end{equation}
-
-%Based on Equation \ref{eq:functional} we use the functional of the structure function in the form:
-%
-%\begin{equation}\label{eq:ff}
-%b(r; r_0, m) = 2\sigma^2 \bigl( 1 - C(r) \bigr)
-%\end{equation}
-%
-%where  is now the new form of the correlation function in the form:
-where $C(r)$ is a new form that we propose of the correlation function:
+B(r) = 2\sigma^2 \bigl( 1 - C(r) \bigr)
+\end{equation}
+
+We use a new functional for the structure function based on equation \ref{eq:functional}. 
+First we propose a new \(C(r)\) in the form:
 %
@@
 %
-substituting the previously $C(r)=1/[1+(r/r_{0})^{m}]$ \citep{1966igd..book.....K,1984ApJ...277..556S}.
-
-The term $r_{0}$ is the correlation length of the turbulence, the value of \(r\) in pc where equation \ref{eq:Br} reach the value of \(\sigma^2\), and $m$ is the index that adjust our results.
-In this idealized case, at scales larger than r$_{0}$ the structure function flattens as it tends towards the asymptotic value of 2$\sigma$ \citep{arthur2016turbulence}.
-
+The term \(r_{0}\)\ is the correlation length where the value of separation \(r\) reach the value of \(\sigma^2\) in the structure function and $m$ is the power-law index that fits the inertial scale.
+In an idealized case at scales larger than \(r_{0}\)\ the structure function flattens as it tends towards the asymptotic value of 2\(\sigma^2\) \citep{arthur2016turbulence}.
+This substitutes the previously \(C(r) = 1/[1+(r/r_{0})^{m}]\) from \citet{1966igd..book.....K} and
+\citet{1984ApJ...277..556S}.
+
+We also take into account in the new functional observational constraints like the seeing and observational box size (see Appendix~\ref{sec:degr-struct-funct} for details).
+
+The seeing becomes important at small scales and it is known that has an effect giving a more pronounced stepping in the structure function.
 The model proposed to describe the seeing at small scales is:
@@
 \end{equation}
-%
-and the model that consider the effect of the observational box size is:
+
+The model that consider the effect of the observational box size is:
 
@@
 % \beta(r_0) = 1 - exp[\frac{L_{box}}{3.6r_0}] 
-  \beta(r_0) = 1 - \exp \left[ -L_{\text{box}} / (3.6 r_0) \right] 
-\end{equation}
-%
-where $L_{\text{box}}$ is the diagonal length of the observational box.
-
-The final form of our proposed functional of the structure function is in the form:
-%
-\begin{equation}\label{eq:fff}
-B(r) = b(r; \beta r_0, \beta \sigma^2,m) \times S(r; s_0, r_0) + B_{\text{noise}}
-\end{equation}
-
-The results obtained with equation \ref{eq:Br} are use in a non-linear least-squares
-fit to obtain the best values for the turbulent parameters. 
-We use equation \ref{eq:fff} in a chi-square analysis applying the equation:
+  \beta(L_{\text{box}},r_0) = 1 - \exp \left[ \frac{-L_{\text{box}}} {3.6 r_0} \right] 
+\end{equation}
+%
+where the \(L_{\text{box}}\) value is the diagonal length of the observational box.
+
+Considering the previous models we obtain the final form of our proposed structure function functional:
+%
+\begin{equation}\label{eq:proposed-functional}
+B_{\text{func}}(r) = B(r; \beta r_0, \beta \sigma^2,m) \times S(r; s_0, r_0) + B_{\text{noise}}
+\end{equation}
+%
+where the term \( B_{\text{noise}}\) is a correction factor that considers the instrument noise at small scales.
+This noise would have the effect of flattening the structure function by removing the effects of the fluctuations which would be interpreted as an uncorrelated property.
+
+To maintain an uniform methodology across all the sample of HII regions the results obtained with equation \ref{eq:Br} are use in a non-linear least-squares fit to obtain the best fit for the analysis.
+For this purpose we use the \textit{python} package \textit{lmfit} \citep{newville_matthew_2014_11813} where the equation \ref{eq:Br} and \ref{eq:proposed-functional} are use in a chi-square analysis following:
 %
@@
 %
-using the package \textit{lmfit} \citep{newville_matthew_2014_11813}.
-
-In this way we avoid one fundamental problem in the interpretation of the structure function results. 
+
+In this way we want to avoid one fundamental problem in the interpretation of the structure function. 
 The slope in the majority of previous studies and hence, the correlation length, is obtained without a formal procedure. 
-The traditional way to find it is to determine a particular range of ascending values in the structure function results. 
+The traditional way to find the correlation length it is to determine a particular range of ascending values in the structure function. 
 If this increase in values is stopped or reversed it is commonly assumed that one particular inertial range has been found. 
@@
 %For supersonic turbulence the index is $\beta=-2$ \citep{burg}. 
+%In the Kolmogorov model \(B(r) \propto r^{2/3}\).
 
@@
 
+%Note to me: review bibliography and expand this section
 The true variance of the velocity fields obtained with the analysis in Section \ref{sec:apply} is shown in the second column in Table \ref{tab:Res}. 
@@
 
-It has been proposed for comparison between two-dimensional observations and the three-dimensional value of the astronomical object what it is called projection smoothing \citep{von1951methode, munch1958internal,1987ApJ...317..686O}, where:
+For the comparison between the two-dimensional structure function and the three-dimensional structure function relationships between the power-law were proposed.
+This procedure is called projection smoothing \citep{von1951methode, munch1958internal,1987ApJ...317..686O}.
 
@@
 
-We can compute the $m_{3D}$ index from the two dimensional \(m\), if we assume that the $m_{3D}$ index lies between the limits of projection smoothing and a sheet-like distribution. 
+We can compute the $m_{3D}$ index from the two dimensional \(m\), if we assume that the m$_{3D}$ index lies between the limits of projection smoothing and a sheet-like distribution. 
 Following the procedure by \cite{arthur2016turbulence} and assuming the relationship m$_{2D}$ - 1 $<$ m$_{3D}$ $<$ m$_{2D}$ we have 0.36 $<$ m$_{3D}$ $<$ 0.72.
@@
 
+%Intro for scaling relations
 Relationship between the physical properties of HII regions, like size and luminosity, and the velocity dispersion have been used as tools for concluding scaling relations for these objects.
@@
 
+%Previous research on scaling relations
 \citet{2012MNRAS.422.3339W} have found that clumps and HII regions follow scaling relations over the range of z = 0-2 for \halpha\ size, velocity dispersion, luminosity and mass, finding \(\sigma \propto r^{0.42}\), \(\text{L}_{\text{H}_{\alpha}} \propto r^{2.72}\) and \(\text{L}_{\text{H}_{\alpha}} \propto \sigma^{4.18}\), respectively.
@@
 
+%methods for our analysis
 We follow through this analysis using the scaling relation as a research tool between the properties of the sample of HII regions and our results. 
-We use the properties in Table \ref{tab:Reg} with the turbulent parameters in Table \ref{tab:Res} as the dependent variable to adjust a fit in the form $Y = aX +b$. 
+We use the properties in Table \ref{tab:regions-properties} with the turbulent parameters in Table \ref{tab:Res} as the dependent variable to adjust a fit in the form $Y = aX +b$. 
 For this procedure we use a hierarchical Bayesian approach using the package \textit{linmix} \citep{2007ApJ...665.1489K}.
@@
 
+%Size vs correlation length
+\textit{Note: Regarding the values and uncertainties of the size of the regions, table \ref{tab:regions-properties},  I was fearing that they might seem kind of arbitrary for the reviewers.
+So I had the idea of using the box size value instead of the size, and the box size minus the maximun separation r for the uncertainty for the regression analysis (not shown).
+The results are quite consistent with the size, R, value (see lines below) giving $\log r_0 = (0.77 \pm 0.12) \log box size-(0.80 \pm 0.18)$.
+There is a diminution for the Pearson correlation value from 0.98 to 0.95 and the p-value changes from 3.7e-07 to 4.49e-05.}
 The Figure \ref{fig:rvsR} shows the strongest correlation, being this between the correlation length $r_0$ and the size $R$ of the region.
-The relationship we found is relation of $\log r_0 = (0.68 \pm 0.06) \log R-(0.83 \pm 0.12)$.
-
+The relationship we found is relation of \(\log r_0 = (0.68 \pm 0.06) \log R-(0.83 \pm 0.12)\).
+
+\textit{Note: First I was using the luminosities values from the table of the Git page for the regression analysis.
+But I change them according to the bibliography when writing section 2.
+The values are quite consistent but for Carina there was some difference.
+From \SI{e39}{erg.s^{-1}} to \SI{e38}{erg.s^{-1}}.}
 The Figure \ref{fig:sigvsl} shows the log $\sigma$-log $\text{L}(\text{H}_{\alpha})$ plane.
 Since this relation is the most common it can be use for comparison with the investigations mentioned at the beginning of this section.
-Our results give us a relation of $\log \sigma = (0.17 \pm 0.1) \log \text{L}(\text{H}_{\alpha})-(6 \pm 4.0)$.
+Our results give us a relation of $\log \sigma = (0.25 \pm 0.1) \log \text{L}(\text{H}_{\alpha})-(9 \pm 4.0)$.
 It is customary in the literature to present $\text{L} (\text{H}_{\alpha})$ as the dependent variable.
 In our case if we choose the upper positive error and take the inverse of slope we have \(\text{L}_{\text{H}_{\alpha}} \propto \sigma^{3.5}\). 
-Using the same procedure in \textit{linmix} and changing the variables we obtained $\log \text{L}(\text{H}_{\alpha}) = (3.2\pm 2) \log \sigma -(36.23 \pm 1.45)$.
+Using the same procedure in \textit{linmix} and changing the variables we obtained $\log \text{L}(\text{H}_{\alpha}) = (3.2\pm 1.4) \log \sigma -(36 \pm 1)$.
 Both relations are close to the previously proposed \(\text{L}_{\text{H}_{\alpha}} \propto \sigma^{4}\)

### 2022-01-14 strucfunc_paper.tex
Javier changes 2022-01-14

@@
 \begin{equation}\label{eq:ffnew}
-  C(r) = \exp \left[ -(\ln 2) \left( \frac{r}{r_0} \right)^m \right]
+  C(r; r_0, m) = \exp \left[ -(\ln 2) \left( \frac{r}{r_0} \right)^m \right]
 \end{equation}
@@
 %
-\begin{equation}\label{eq:proposed-functional}
+\begin{equation}\label{eq:sf-functional}
 B_{\text{func}}(r) = B(r; \beta r_0, \beta \sigma^2,m) \times S(r; s_0, r_0) + B_{\text{noise}}
@@
 
-To maintain an uniform methodology across all the sample of HII regions the results obtained with equation \ref{eq:Br} are use in a non-linear least-squares fit to obtain the best fit for the analysis.
-For this purpose we use the \textit{python} package \textit{lmfit} \citep{newville_matthew_2014_11813} where the equation \ref{eq:Br} and \ref{eq:proposed-functional} are use in a chi-square analysis following:
+The results obtained with equation \ref{eq:Br} are use in a non-linear least-squares fit with the equation \ref{eq:sf-functional} used as an objective function.
+For this purpose we use the \textit{python} package \textit{lmfit} \citep{newville_matthew_2014_11813} where the equation \ref{eq:Br} and \ref{eq:sf-functional} are use in a chi-square statistic defined as:
+%
+%\begin{equation}\label{eq:chi}
+%  \chi^2 = \sum_i ^N \frac{[y_i^{\text{measure}}-y_i^{\text{model}} (\boldsymbol{v})]^2}{\epsilon_i ^2}
+%\end{equation}
+%
 %
 \begin{equation}\label{eq:chi}
-  \chi^2 = \sum_i ^N \frac{[y_i^{\text{measure}}-y_i^{\text{model}} (\boldsymbol{v})]^2}{\epsilon_i ^2}
-\end{equation}
-%
+  \chi^2 = \sum_i ^N \frac{[B(r)-B_{\text{func}}(r;r_0, \sigma^2, m, s_0, B_{\text{noise}})]^2}{\epsilon_i ^2}
+\end{equation}
+%
+which calculate a value \(\chi\) to be minimized scaled by the inverse of the uncertainty \(\epsilon\) in the data.
+The minimization procedure use the the method \textit{emcee} \citep{2013PASP..125..306F} which is a \textit{python} implementation of the affine-invariant ensemble sampler for Markov chain Monte Carlo (MCMC) by \citet{2010CAMCS...5...65G}.
+Using these procedure we obtain a sample of fits for the structure function.
+And for the turbulent parameters \(r_{0}\)\ , \(\sigma^2\) and \(m\), and for the observational constraints \(s_0\) and \( B_{\text{noise}}\), we obtain the best fit values with the confidence intervals up to three standard deviations.
 
@@
 %
-where \(\epsilon\) is the energy transfer rate and the value of $\beta = -5 / 3$ is the Kolmogorov index.
+where \(\epsilon\) is the energy transfer rate and the value of \(\beta = -5 / 3\) is the Kolmogorov index.
 %For supersonic turbulence the index is $\beta=-2$ \citep{burg}. 
@@
 
-Figures \ref{fig:strucfunc-fit-A}-\ref{fig:strucfunc-fit-C} shows the structure function of each region along with the fit obtained using the non-linear regression.
-Table \ref{tab:Res} presents the turbulent parameters we obtain the regression.
-The second column correspond to the variance \(\sigma^2\) of the velocity field.
+Figures \ref{fig:strucfunc-fit-A}-\ref{fig:strucfunc-fit-D} show on the left panels the observational structure function in solid blue dots that we compute using equation \ref{eq:Br} on the velocity fields of Fig.
+\ref{fig:velocity-maps}.
+The green dashed line indicate the model without instrumental effects using equation \ref{eq:functional}.
+The Figures also show in yellow solid line the mean of samples posterior using equation \ref{eq:sf-functional}.
+The vertical dashed line indicates the correlation length value \(r_0\) and the horizontal dashed line indicates the \(\sigma^2\) value.
+The vertical and horizontal dotted lines shows the value of the observational consideration \(s_0\) and the \(B_{\text{noise}}\) obtained after the analysis described in section~\ref{sec:met}.
+
+Table \ref{tab:Res} presents the turbulent parameters along the observational constraints.
+The second column correspond to the true variance \(\sigma^2\) of the velocity field.
 The index \(m\) is shown in the third column and is used as a reference for comparison between theory and observations.
-The fourth column is the correlation length \(r_0\).
+The fourth column is the correlation length in pc.
 
@@
 \input{SFresults}
-%\begin{table*}
-% \begin{center}\caption{Main results.
-%  a) \citet{tanco1997}
-%      b) \citet{2019arXiv191203543M}
-%      c) \citet{Castro:2018a}
-%      d) \citet{Damiani:2016a}
-%      e) \citet{Damiani:2017b}
-%      f) \citet{1987A&A...176..347H}
-%      g) \citet{arthur2016turbulence}.}
-% \begin{tabular}{ccccccccc}\hline
-% HII         &\(\sigma^{2}\) &\(r_0\)                     &\(m\)    &\(\langle \sigma_{LOS} \rangle \) & Previously\\
-% Region      &[km/s]$^{2}$     &[pc]                        &                           &  [km/s]& used in:\\ \hline
-% NGC 604     & 80.93$\pm$25.31 &  9.12$\pm$2.98  & 0.82$\pm$0.20  & 16.2 & a,b \\
-% NGC 595     & 56.45$\pm$1.69  & 11.69$\pm$0.45  & 1.29$\pm$0.04  & 18.3 & - \\
-% Hubble X    & 15.55$\pm$1.50  &  3.90$\pm$0.28  & 0.94$\pm$0.12  & 13.4 & - \\ 
-% Hubble V    & 10.46$\pm$0.75  &  3.42$\pm$0.33  & 0.73$\pm$0.09  & 12.3 & - \\  
-% 30 Dor      & 350.87$\pm$21.59 & 4.60$\pm$0.43  & 0.84$\pm$0.03  & 31.7 & c\\
-% Carina      & 16.74$\pm$1.13  & 0.66$\pm$0.08  & 1.36$\pm$0.29  & 22.4 & d\\
-% NGC 346     & 38.03$\pm$1.09  & 1.90$\pm$0.09  & 0.78$\pm$0.02  & 10.2 & -\\
-% Lagoon      & 7.29$\pm$0.84   & 1.00$\pm$0.17  & 1.12$\pm$0.09  & 13.6 & e\\ 
-% Orion Large & 5.97$\pm$0.58   & 0.73$\pm$0.17  & 1.72$\pm$0.524 & 6.0 & f \\
-% Orion Small & 16.92$\pm$0.97  & 0.091$\pm$0.006 & 1.06$\pm$0.01 & 6.0 & g \\\hline	  
-% \end{tabular}\label{tab:Res}
-% \end{center}
-%\end{table*}
 

### 2022-01-17 strucfunc_paper.tex
Javier changes 2022-01-17

@@
 \begin{tabular}{cCCCC}\toprule
-\hii{}    &  \text{Distance,}\ D& \text{Diameter,}\ R & \log L(\ha) &  \langle \sigma\los \rangle \\
+\hii{}    &  \text{Distance,}\ d& \text{Diameter,}\ D & \log L(\ha) &  \langle \sigma\los \rangle \\
   Region    &  [\si{kpc}]          &  [\si{pc}]    &  [\si{erg.s^{-1}}]            &    [\si{km.s^{-1}}]  \\ 
@@
 
-We can compute the $m_{3D}$ index from the two dimensional \(m\), if we assume that the m$_{3D}$ index lies between the limits of projection smoothing and a sheet-like distribution. 
-Following the procedure by \cite{arthur2016turbulence} and assuming the relationship m$_{2D}$ - 1 $<$ m$_{3D}$ $<$ m$_{2D}$ we have 0.36 $<$ m$_{3D}$ $<$ 0.72.
+We can compute the $m_{3D}$ index from the two dimensional \(m\), if we assume that the $m_{3D}$ index lies between the limits of projection smoothing and a sheet-like distribution. 
+Following the procedure by \cite{arthur2016turbulence} and assuming the relationship $m_{2D}$ - 1 $<$ $m_{3D}$ $<$ $m_{2D}$ we have 0.36 $<$ m$_{3D}$ $<$ 0.72.
 

### 2022-01-17 strucfunc_paper.tex
Minor edit to NGC 595 decription

@@
 
-NGC 604 the second brightest region of the local group after 30Dor in the Large Magellanic Cloud and is forty times larger ($\sim $ 400 pc) and 6,000 times brighter than Orion in our Milky Way galaxy.
-It is the brightest giant HII region in the M33 galaxy visually dominated by a big loop, big shells and different size filaments.
-It has a luminosity in \ha{} of \SI{e39.42}{erg.s^{-1}}\citep{2002MNRAS.329..481B}.
+NGC 604 is the second brightest \hii{} region in the Local Group after 30~Dor in the Large Magellanic Cloud and is forty times larger ($\sim $ 400 pc) and 6,000 times brighter than Orion in our Milky Way galaxy.
+It is the brightest giant \hii{} region in the M33 galaxy and is visually dominated by a big loop, big shells and different size filaments.
+It has a luminosity in \ha{} of \SI{e39.42}{erg.s^{-1}} \citep{2002MNRAS.329..481B}.
 Using photometry from the HST \citet{1996ApJ...456..174H} identified that the stars are separated into a primary cluster within NGC 604, and a secondary to the north of the region.

### 2022-01-19 strucfunc_paper.tex
Discussion of relation of CO and Ha kinematics

@@
 \newcommand\Wav[1]{\ensuremath{\lambda #1}}
+% Chemical formulae
+\newcommand*\chem[1]{\ensuremath{\mathrm{#1}}}
+\newcommand\csound{\ensuremath{c_{\text{s}}}}
 
@@
 up to  \SI{\pm 40}{km.s^{-1}} for 30~Doradus.
-This can be appreciated quantitatively in Figure~\ref{fig:hist},
-which shows the probability density function (PDF) of \(V_c\) for each region
-on a common velocity scale and arranged in order of decreasing amplitude
+This is illustrated quantitatively in Figure~\ref{fig:hist},
+where the probability density function (PDF) of \(V_c\) for each region
+is shown on a common velocity scale and arranged in order of decreasing amplitude
 of velocity fluctuations. 
@@
 The Figure \ref{fig:svss} shows the log $\sigma$-log $\sigma_{\text{LOS}}$ plane with a relationship of $\log \sigma = (0.81 \pm 0.47) \log \sigma_{\text{LOS}}-(0.2 \pm 0.54)$ .
+
+\subsubsection{Kinematic relationship between ionized gas, molecular gas, and stars}
+\label{sec:kinem-rela-betw}
+
+Naively, the relatively small observed CO velocity dispersion
+(\(\sigma(\chem{CO}) \ll \sigma(\ha)\) in all regions
+for both \(\sigma\los\) and \(\sigma\pos\))
+might be thought to rule out the molecular gas kinematics
+as a \emph{cause} of the ionized gas kinematics.
+However, this is not necessarily the case, so long as \emph{some} molecular gas
+exists at the higher velocities typical of the ionized gas.
+
+This is because a relatively small column of material
+(\(N(\chem{H}) \sim \SI{e20}{cm^{-2}}\))
+is sufficient to trap the ionization front,
+in which case the \ha{} surface brightness is limited by the
+incident ionizing flux
+\citetext{the Ferland mechanism,
+  see section~5.1 of \citealt{Baldwin:1991a}
+  and section~B.2.1 of \citealt{Ferland:2012a}
+}.
+On the other hand, the bulk of the CO emission will come from much larger
+column densities (\(N(\chem{H}) \sim \SI{e22}{cm^{-2}}\)),
+where the molecules are effectively shielded from dissociation.
+% If a given region can be considered as an ensemble of clouds of
+% different masses, then ... would require lower mass clouds to move
+% faster though, so needs dynamical relaxation
+
+\textbf{Check  if this is actually feasible before developing further}
+
+Very schematically, one could represent these processes as:
+\begin{equation}
+  \label{eq:1}
+  \sigma^2(\ha) \sim \zeta \sigma^2(\chem{CO}) + \eta
+\end{equation}
+where \(\zeta\) is a multiplicative factor
+due primarily to the saturation at the Ferland limit,
+and \(\eta \sim \csound^2\) is an additive factor due to additional turbulence
+generated by the transonic ionized photoevaporation flows.
+
+\textbf{Estimate these two factors by fitting to the observations}
 

### 2022-01-21 strucfunc_paper.tex
Javier changes 2022-01-21

@@
 Orion     & 0.436 \pm 0.02  & 0.6 \pm 0.06    &    37.18       &   6.0      \\
-Lagoon    & 1.25 \pm 0.12   & 25 \pm 2.5      &    37.47    &   13.6 \pm 0.04     \\
-Carina    & 2.35 \pm 0.05   & 15 \pm 1.5      &    38.54    &   22.4 \pm 0.09    \\
+Lagoon    & 1.25 \pm 0.12   & 25 \pm 2.5      &    37.47    &   13.6 \pm 0.8    \\
+Carina    & 2.35 \pm 0.05   & 15 \pm 1.5      &    38.54    &   22.4 \pm 2.7    \\
 30 Dor    & 50.0 \pm 0.2    & 98.9 \pm 9.8    &    39.46    &   31.7     \\
@@
 Hubble V  & 490 \pm 40      & 130 \pm 13      &    38.3     &   12.3     \\
-NGC 595   & 820 \pm 30      & 400 \pm 40      &    38.95    &   18.3 \pm 0.06     \\
-NGC 604   & 820 \pm 30      & 400 \pm 40      &    39.42    &   16.2 \pm 0.08     \\
+NGC 595   & 820 \pm 30      & 400 \pm 40      &    38.95    &   18.3 \pm 5.7     \\
+NGC 604   & 820 \pm 30      & 400 \pm 40      &    39.42    &   16.2 \pm 7.7     \\
 \bottomrule
@@
 
-\textit{Note: First I was using the luminosities values from the table of the Git page for the regression analysis.
-But I change them according to the bibliography when writing section 2.
-The values are quite consistent but for Carina there was some difference.
-From \SI{e39}{erg.s^{-1}} to \SI{e38}{erg.s^{-1}}.}
 The Figure \ref{fig:sigvsl} shows the log $\sigma$-log $\text{L}(\text{H}_{\alpha})$ plane.

### 2022-01-21 strucfunc_paper.tex
Figure caption for histograms

@@
  \includegraphics[width=5in]{Figures/Hist}\par
- \caption{Histograms of the centroid velocities in \halpha\ of our sample of HII regions. }
+ \caption{
+   Histograms of the plane-of-sky variation in the \ha{} centroid velocities.
+   Each panel shows the fraction of the observed spatial points
+   (pixels or fiber positions)
+   with a given velocity offset from the mean systemic velocity of each region.
+   The RMS width \(\sigma\pos\) of each distribution is marked,
+   as is the number of spatial points.
+   The bin width is \SI{1}{km.s^{-1}} and the regions are arranged
+   in order of decreasing \(\sigma\pos\).
+ }
  \label{fig:hist}

### 2022-01-25 Corr.tex
Javier changes 2022-01-22

@@
 \hline
-    log $r_0$ &             log $R$ &   0.69 $\pm$ 0.07 &   -0.83 $\pm$ 0.12 &   0.98 &    < 10\(^{-4}\) \\
- log $\sigma$ &            log L(H) &   0.25 $\pm$ 0.10 &  -8.90 $\pm$ 3.63 &   0.83 &  0.003 \\
- log $\sigma$ &  log $\sigma_{LOS}$ &   0.78 $\pm$ 0.46 &  -0.17 $\pm$ 0.54 &   0.66 &  0.036 \\
-      log $m$ &            log Dist &  -0.11 $\pm$ 0.08 &    1.21 $\pm$ 0.16 &  -0.59 &  0.072 \\
- log $\sigma$ &         log $r_{0}$ &   0.22 $\pm$ 0.19 &   0.65 $\pm$ 0.12 &   0.54 &  0.103 \\
-      log $m$ &        log $\sigma$ &  -0.14 $\pm$ 0.24 &    0.11 $\pm$ 0.18 &   -0.42 &  0.227 \\
-      log $m$ &         log $r_{0}$ &   -0.04 $\pm$ 0.08 &   0.01 $\pm$ 0.05 &  -0.38 &   0.27 \\
+ log $\sigma$ &            log L(H) &   0.28 $\pm$ 0.1 &  -9.87 $\pm$ 3.66 &   0.85 &  0.002 \\
+    log $r_0$ &             log $S$ &   0.73 $\pm$ 0.24 &  -1.17 $\pm$ 0.5 &   0.84 &  0.003 \\
+ log $\sigma$ &  log $\sigma_{LOS}$ &   0.76 $\pm$ 0.48 &  -0.14 $\pm$ 0.54 &   0.66 &   0.04 \\
+      log $m$ &            log Dist &  -0.11 $\pm$ 0.08 &   1.21 $\pm$ 0.16 &  -0.59 &   0.07 \\
+ log $\sigma$ &         log $r_{0}$ &   0.22 $\pm$ 0.18 &   0.65 $\pm$ 0.12 &   0.55 &  0.10 \\
+      log $m$ &        log $\sigma$ &  -0.14 $\pm$ 0.24 &   0.11 $\pm$ 0.18 &  -0.42 &  0.22 \\
+      log $m$ &         log $r_{0}$ &  -0.04 $\pm$ 0.08 &   0.01 $\pm$ 0.05 &  -0.39 &   0.27 \\
 \bottomrule

### 2022-01-25 strucfunc_paper.tex
Javier changes 2022-01-22

@@
 
-\subsection{Physical properties of the sample regions}
+\subsection{Physical properties of the sample regions. }
 \label{sec:regions-milky-way}
@@
 \begin{table}
-\begin{center}\caption{Summary of properties of our \hii{} region sample. }
+\begin{center}\caption{Summary of properties of our \hii{} region sample. Sizes taken from Table 2 of \citet{1984ApJ...287..116K}. Reference from the other properties are mentioned in the text.}
 \begin{tabular}{cCCCC}\toprule
-\hii{}    &  \text{Distance,}\ d& \text{Diameter,}\ D & \log L(\ha) &  \langle \sigma\los \rangle \\
+\hii{}    &  \text{Distance,}\ d& \text{Size,}\ S & \log L(\ha) &  \langle \sigma\los \rangle \\
   Region    &  [\si{kpc}]          &  [\si{pc}]    &  [\si{erg.s^{-1}}]            &    [\si{km.s^{-1}}]  \\ 
 \midrule
-Orion     & 0.436 \pm 0.02  & 0.6 \pm 0.06    &    37.18       &   6.0      \\
+Orion     & 0.436 \pm 0.02  & 5 \pm 0.5    &    37.18       &   6.0      \\
 Lagoon    & 1.25 \pm 0.12   & 25 \pm 2.5      &    37.47    &   13.6 \pm 0.8    \\
-Carina    & 2.35 \pm 0.05   & 15 \pm 1.5      &    38.54    &   22.4 \pm 2.7    \\
-30 Dor    & 50.0 \pm 0.2    & 98.9 \pm 9.8    &    39.46    &   31.7     \\
-NGC 346   & 62 \pm 1        & 64 \pm 6.4      &    38.77    &   10.1     \\
+Carina    & 2.35 \pm 0.05   & 200 \pm 20      &    38.54    &   22.4 \pm 2.7    \\
+30 Dor    & 50.0 \pm 0.2    & 370 \pm 37    &    39.46    &   31.7     \\
+NGC 346   & 62 \pm 1        & 220 \pm 22      &    38.77    &   10.1     \\
 Hubble X  & 490 \pm 40      & 160 \pm 16      &    38.21    &   13.4     \\
@@
 %Size vs correlation length
-\textit{Note: Regarding the values and uncertainties of the size of the regions, table \ref{tab:regions-properties},  I was fearing that they might seem kind of arbitrary for the reviewers.
-So I had the idea of using the box size value instead of the size, and the box size minus the maximun separation r for the uncertainty for the regression analysis (not shown).
-The results are quite consistent with the size, R, value (see lines below) giving $\log r_0 = (0.77 \pm 0.12) \log box size-(0.80 \pm 0.18)$.
-There is a diminution for the Pearson correlation value from 0.98 to 0.95 and the p-value changes from 3.7e-07 to 4.49e-05.}
-The Figure \ref{fig:rvsR} shows the strongest correlation, being this between the correlation length $r_0$ and the size $R$ of the region.
+The Figure \ref{fig:rvsR} shows the relation of the correlation length $r_0$ and the size \(S\) of the region.
 The relationship we found is relation of \(\log r_0 = (0.68 \pm 0.06) \log R-(0.83 \pm 0.12)\).
 
-The Figure \ref{fig:sigvsl} shows the log $\sigma$-log $\text{L}(\text{H}_{\alpha})$ plane.
+The Figure \ref{fig:sigvsl} shows the log \(\sigma\)-log $\text{L}(\text{H}_{\alpha})$ plane.
 Since this relation is the most common it can be use for comparison with the investigations mentioned at the beginning of this section.
@@
 \centering 
-\includegraphics[width=3in]{Figures/rvsR}
-\caption{The log $r_0$-log $R$ plane derived form our results an data in the literature.
-A fit with slope of 0.67$\pm$0.07 is shown in solid black line that is the mean of all red lines that reflect the posterior of the Bayessian analysis.
+\includegraphics[width=3in]{Figures/rvsS}
+\caption{The log \(r_0\) - log \(S\) plane derived form our results an data in the literature.
+A fit with slope of 0.67 $\pm$ 0.07 is shown in solid black line that is the mean of all red lines that reflect the posterior of the Bayessian analysis.
 }

### 2022-01-26 Corr.tex
Javier changes 2022-01-25

@@
  log $\sigma$ &  log $\sigma_{LOS}$ &   0.76 $\pm$ 0.48 &  -0.14 $\pm$ 0.54 &   0.66 &   0.04 \\
-      log $m$ &            log Dist &  -0.11 $\pm$ 0.08 &   1.21 $\pm$ 0.16 &  -0.59 &   0.07 \\
+      log $m$ &            log dist &  -0.11 $\pm$ 0.08 &   1.21 $\pm$ 0.16 &  -0.59 &   0.07 \\
  log $\sigma$ &         log $r_{0}$ &   0.22 $\pm$ 0.18 &   0.65 $\pm$ 0.12 &   0.55 &  0.10 \\

### 2022-01-26 strucfunc_paper.tex
Javier changes 2022-01-25

@@
 % This conditions will develop shock waves in the HII region changing the energy balance \citep{lagrois2011,arthur2016turbulence}.
-% Two it is known that these regions are created on the edge of molecular clouds, so they will reach a blister or champagne phase, introducing large-scale gradients not related with random motions \citep{Mivi1995}.
 % And three, in regard with observations, there is the projection of a three-dimensional function into the plane-of-sky \citep{von1951methode,munch1958internal,1964SvA.....8..210K} leading to a loss in information of the velocity spectrum.
@@
 \label{sec:spectr-datas}
-%We use data from \citet{1987A&A...176..347H} and \citet{arthur2016turbulence} to study of turbulence in the Orion Nebula.
-%\cite{1987A&A...176..347H} observations were obtained using a 106 cm-Cassegrain telescope at Observatorium Hoher List. 
-%A Fabry-Pérot interferometer was used with a étalon a separation of 0.5 mm. 
-%Interferograms have been taken with different pointing directions of the telescope's optical axis in the nebula. 
-%The exposures are overlapped and fall into one square of a grid with a width of 1' centered at \(\theta^{1}\)Ori C.
+
 \newcommand\xx{\ensuremath{\boldsymbol{x}}}
@@
 where such a masking out is not possible.
+
+\subsubsection{Fabry-Pérot étalon}
+\label{sec:fabry-perot-etalaon}
+
+We use \cite{1987A&A...176..347H} observations to analyze the Extended Orion Nebula.
+These observations were obtained using a 106 cm-Cassegrain telescope at Observatorium Hoher List. 
+A Fabry-Pérot interferometer was used with a étalon separation of 0.5 mm. 
+A number of fifteen interferograms have been taken with different pointing directions of the telescope's optical axis in the nebula with an exposure time between 10 and 40 minutes. 
+The exposures are overlapped and fall into one square of a grid with a width of 1' centered at \(\theta^{1}\)Ori C.
 
@@
 
-The Orion Nebula (M42) is the prototype galactic HII region located at a distance of 440 pc \citep{2008AJ....136.1566O}.
+The Orion Nebula (M42) is the prototype of a galactic HII region located at a distance of 440 pc \citetext{\SI{1}{\arcsecond} = \SI{0.001}{pc} ; \citealp{2008AJ....136.1566O}}.
 The O7 V star \(\theta^{1}\) Ori C is the most luminous and hottest star \citep{2006A&A...448..351S} with an ionizing flux \(Q_0\) of  \SI{e49.12}{photons.s^{-1}}. 
 With other 3 B-type stars they form the Trapezium cluster.
+The bright region that surrounds these massive ionizing stars is called the the Huygens region (Orion core henceforth).
+In the southwest direction of the Huygens region there is a drop in the brightness as one approach a much larger region called Extended Orion Nebula \citetext{EON henceforth;  \citealp{2008Sci...319..309G}}
 The position of Orion near the side of the Orion Molecular Cloud (OMC-1) make it an ongoing star formation with a large population of young star, some of which are the sources of stellar jets and Herbig-Haro objects \citep{1993ApJ...410..696O}.
@@
 
+\subsubsection{Lagoon Nebula}
+\label{sec:lagoon-nebula}
+
+The Lagoon Nebula (M8, NGC6523) is located at a distance of 1 250 pc \citetext{\SI{1}{\arcsecond} = \SI{0.006}{pc} ; \citealp{2005A&A...430..941P}}.
+It has a luminosity in \ha{} of \SI{e37.47}{erg.s^{-1}}\citep{1984ApJ...287..116K}.
+It contains the young stellar cluster NGC6530 and the region is illuminated by different massive stars of spectral types O and B, the hottest being 9 Sgr, type O4V \citep{Damiani:2017b}.
+Optically, the brightest part of the nebula is called 'Hourglass nebula' which surrounds and obscures the O7 star Herschel 36 \citep{1986AJ.....91..870W}. 
+The velocity field shows several expanding shells, related to the stellar population, and the massive protostar M8East-IR \citep{1984ApJ...278..170S} indicating that recent star formation. 
+A blueshifted, neutral layer is also in very good agreement with predictions of champagne-flow models of blister HII regions \citep{Damiani:2017b}. 
+The properties of the nebula are reviewed by \citet{2008hsf2.book..533T}.
+
 \subsubsection{Carina Nebula}
@@
 
-The Carina nebula is a large star-forming complex located at a distance of 2 350 pc \citep{2006ApJ...644.1151S}.
+The Carina nebula is a large star-forming complex located at a distance of 2 350 pc \citetext{\SI{1}{\arcsecond} = \SI{0.01}{pc} ; \citealp{2006ApJ...644.1151S}}.
 Using the \ha{} luminosity as a diagnostic of the ionizing flux \(Q_0\) \citet{2007MNRAS.379.1279S} measured a value of \SI{e50.47}{photons.s^{-1}}.
@@
 
-\subsubsection{Lagoon Nebula}
-\label{sec:lagoon-nebula}
-
-The Lagoon Nebula (M8, NGC6523) is located at a distance of 1 250 pc \citep{2005A&A...430..941P}.
-It has a luminosity in \ha{} of \SI{e37.47}{erg.s^{-1}}\citep{1984ApJ...287..116K}.
-It contains the young stellar cluster NGC6530 and the region is illuminated by different massive stars of spectral types O and B, the hottest being 9 Sgr, type O4V \citep{Damiani:2017b}.
-Optically, the brightest part of the nebula is called 'Hourglass nebula' which surrounds and obscures the O7 star Herschel 36 \citep{1986AJ.....91..870W}. 
-The velocity field shows several expanding shells, related to the stellar population, and the massive protostar M8East-IR \citep{1984ApJ...278..170S} indicating that recent star formation. 
-A blueshifted, neutral layer is also in very good agreement with predictions of champagne-flow models of blister HII regions \citep{Damiani:2017b}. 
-The properties of the nebula are reviewed by \citet{2008hsf2.book..533T}.
-
 \subsubsection{30 Doradus}
@@
 
-The 30 Doradus (Tarantula Nebula) nebula is located at a distance of 49.9 kpc \citep{2013Natur.495...76P}
+The 30 Doradus (Tarantula Nebula) nebula is located at a distance of 49.9 kpc \citetext{\SI{1}{\arcsecond} = \SI{0.24}{pc} ; \citealp{2013Natur.495...76P}}.
 It is a luminous star-forming region in the LMC (Large Magellanic Cloud) and is the most luminous complex in the Local Group \citep{1984ApJ...287..116K}.
@@
 
-NGC 346 is the most active star-formation region in the SMC (Small Magellanic Cloud) located at a distance of 62 kpc \citep{2001ApJ...562..303D}. 
+NGC 346 is the most active star-formation region in the SMC (Small Magellanic Cloud) located at a distance of 62 kpc \citetext{\SI{1}{\arcsecond} = \SI{0.30}{pc} ; \citealp{2001ApJ...562..303D}}. 
 It has more than 30 O stars that ionize N66, the largest HII region \citep{2011ApJ...740...10D}.
@@
 %Note to me: incomplete section. Find more regions info and finish asap.
-The irregular dwarf galaxy, NGC 6822, is located at a distance of 500 kpc \citep{2012A&A...540A.135S} and the brightest HII regions are Hubble X and Hubble V (HX and HV hereafter). %(1'' = 2.4 pc)
+The irregular dwarf galaxy, NGC 6822, is located at a distance of 500 kpc \citetext{\SI{1}{\arcsecond} = \SI{2.42}{pc} ; \citealp{2012A&A...540A.135S}} and the brightest HII regions are Hubble X and Hubble V (HX and HV hereafter).
+%(1'' = 2.4 pc)
 HV has a characteristic length of 100 pc and HX has a characteristic length of 140 pc \citep{1999PASP..111.1382O}.
@@
 
-M33 is the third largest galaxy in the Local Group located at the distance of 840 kpc and is of morphological type SA(s)cd \citep{2015KamKinematics}.
+M33 is the third largest galaxy in the Local Group located at the distance of 840 kpc \citetext{\SI{1}{\arcsecond} = \SI{4.07}{pc} ; \citealp{2015KamKinematics}} and is of morphological type SA(s)cd.
 The two brightest HII regions in the galaxy are NGC 604 and NGC 595.
@@
 
-%\citet{1983A&A...119..185V} made an estimate of the total masses of HI and HII in the nebula to obtain values of M$_{HI}=$ 1.2 $\times$ 10 $^{6}$ M$_{\odot}$ and M$_{HII} =$ 4.6 $\times$ 10 $^{5}$ M$_{\odot}$, and a ionizing luminosity of the star cluster is estimated at 5 $\times$ 10$^{50}$ erg s $^{1}$.
-%The electronic temperature is 7,670 $\pm$116 K \citep{2010MNRAS.402.1635R}.
-%2013ApJ...773...69G M33 dist
-% \citep{1984ApJ...287..116K} \citep{1986ApJ...300..624R}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \section{Plane-of-sky velocity fluctuations}\label{sec:met}
-
-% \subsection{Velocity fields of the HII regions}
-
-% \textit{Javier 2021-12-28: I'm not quite sure the correct section for this.
-Since they aren't results, per se, and until now I haven't develop to much discussion with them, I move it here so it end up like Methods and Data, before reporting our findings.
-}
 
@@
 
-\subsection{Application to our HII regions sample}\label{sec:apply}
+\subsection{Application to our HII regions sample}\label{sec:methods-apply}
 
@@
 %
-\begin{equation}\label{eq:ffnew}
+\begin{equation}\label{eq:new-correlation-form}
   C(r; r_0, m) = \exp \left[ -(\ln 2) \left( \frac{r}{r_0} \right)^m \right]
@@
 The minimization procedure use the the method \textit{emcee} \citep{2013PASP..125..306F} which is a \textit{python} implementation of the affine-invariant ensemble sampler for Markov chain Monte Carlo (MCMC) by \citet{2010CAMCS...5...65G}.
+The turbulent parameters \(r_{0}\)\ , \(\sigma^2\) and \(m\), and the observational constraints \(s_0\) and \( B_{\text{noise}}\) are the set of variables in the model to be optimized in the fit.
 Using these procedure we obtain a sample of fits for the structure function.
-And for the turbulent parameters \(r_{0}\)\ , \(\sigma^2\) and \(m\), and for the observational constraints \(s_0\) and \( B_{\text{noise}}\), we obtain the best fit values with the confidence intervals up to three standard deviations.
 
@@
 
+We present our second-order structure results plotted against separation in parsecs.
+
+\subsection{HII regions second-order structure functions and turbulent parameters}
+
+Figures \ref{fig:strucfunc-fit-A}-\ref{fig:strucfunc-fit-D} left panels show in solid and open blue circles the observational structure function that we compute using equation \ref{eq:Br} on the \ha{} velocity fields of Fig.
+\ref{fig:velocity-maps}.
+The solid circles indicate the range use in the non-linear regression analysis (see section~\ref{sec:methods-apply}), while the open circles are the points of the structure function that where left out.
+This was done to enhance the possibilities of a convergence since the structure function values at large separations are to follow the 2\(\sigma^2\) value according to theory.
+The light shaded areas in the plots show where the separation \(r\) is above half of the box size, \(L\), which is indicated with a vertical dotted line.
+
+The green dashed line indicate the mean samples posterior of the model structure function without instrumental effects using equation \ref{eq:functional} and \ref{eq:new-correlation-form}.
+The Figures also show in yellow solid line the mean of samples posterior using equation \ref{eq:sf-functional}.
+The vertical dashed line indicates the correlation length value \(r_0\) and the horizontal dashed line indicates the true variance of the velocity fields, \(\sigma^2\).
+The vertical and horizontal dotted lines shows the value of the observational considerations, the seeing, \(s_0\) and the value of the noise, \(B_{\text{noise}}\), respectively.
+For the dashed and dotted lines the overlapping translucent boxes indicate the spread of values up to two-sigma (dark shaded area) and three-sigma (light shaded area) obtained after the analysis described in section~\ref{sec:methods-apply}.
+
+The results shown on left panels on Figures \ref{fig:strucfunc-fit-A}-\ref{fig:strucfunc-fit-D} show a typical second-order structure function pattern, where there is a series of ascending values of  \ref{eq:Br} that tends to stabilize around the 2\(\sigma^2\) value indicating a loss in the correlations at large separations.
+The Carina nebula and Hubble X show this behavior.
+
+Since we are dealing with a sample of astronomical observations, it is thought that the values at large separations not following the previous pattern reflects movements that are not related to the ionized gas random motions.
+It is known that HII regions are created on the edge of molecular clouds, so they will reach a blister or champagne phase, introducing large-scale gradients \citep{Mivi1995}. 
+Also there is the expansion or rotation of each region.
+
+A more common pattern for structure functions of HII regions looks like a 'hook' where at large separations the structure function values start decreasing.
+This behavior is shown in the Orion core, 30 Doradus, Hubble V, NGC 595 and the EON.
+Less common is the behavior where at large separations there are also a series of ascending values in the structure function, like the Lagoon nebula or NGC 346, or a periodic behavior like NGC 604.
+The reasons of this change on the structure function at large-scales is out of the scope of this investigation.
+
+Table \ref{tab:Res} presents the turbulent parameters results along the obtained observational constraints.
+
+The second column correspond to the true variance \(\sigma^2\) of the velocity field.
+For all regions except for Carina, Lagoon and the EON there is an increase in this value.
+For 30 Doradus, which has the highest value, \(\sigma\) goes from \SI{16}{km.s^{-1}} to  \SI{19}{km.s^{-1}}.
+This is two times higher than NGC 604 that has a change of \SI{7}{km.s^{-1}} to \SI{9}{km.s^{-1}}, followed by NGC 595 with \SI{6.6}{km.s^{-1}} to \SI{7.5}{km.s^{-1}}.
+NGC 346 is next with a value of \SI{6}{km.s^{-1}} which is close to the value of the centroid velocities.
+Carina presents a value of \SI{4.2}{km.s^{-1}} which is the same as the velocity sample.
+The Orion core has a change from \SI{3}{km.s^{-1}} to \SI{4}{km.s^{-1}}.
+Hubble X has a value of \SI{3.9}{km.s^{-1}} which is very close with respect the \SI{3.6}{km.s^{-1}} value of the velocity field.
+The value for Hubble V increase from \SI{2.8}{km.s^{-1}} to \SI{3.3}{km.s^{-1}}.
+Lagoon presents a value of \SI{2.6}{km.s^{-1}} and the EON value decrease from \SI{3.2}{km.s^{-1}} to \SI{2.2}{km.s^{-1}}.
+The \(B_{\text{noise}}\) value is shown in the third column which would be the minimum squared velocity difference that could be measure by the instrument.
+
+The third column in Table \ref{tab:Res} shows the seeing value in parsecs, \(s_0\), which represent the minimum value of the separation which would valid for the observed structure function. 
+The forth column shows the correlation value \(r_0\) in parsecs.
+The \(r_0\) range covered in our results for the sample goes from 0.09 to 12 pc.
+The fifth column indicates the size of each observational box in parsecs.
+The index \(m\) is shown in the last column and is commonly used as a reference for comparison between observations and the theoretic value of 0.6.
+The range covered by the power-law index in our HII region sample goes from 0.7 to 1.5.
+If the extension of the HII region is compared with its depth (three-dimensional case) the value of the index is 1.6.
+While the case where the extension is much greater than its depth (two-dimensional case) the region will have a value of 0.6 \citep{von1951methode, munch1958internal,1987ApJ...317..686O}.
+The implications of these results is further developed on the next section.
+
+\begin{figure*}
+  \centering
+  \includegraphics[width=0.8\linewidth]{Figures/strucfunc-fit-A}
+  \caption{Second-order structure functions for the velocity centroid images of the \(H\alpha\) emission line}\label{fig:strucfunc-fit-A}
+\end{figure*}
+
+\begin{figure*}
+  \centering
+  \includegraphics[width=0.8\linewidth]{Figures/strucfunc-fit-B}
+  \label{fig:strucfunc-fit-B}
+  \caption{Second-order structure functions for the velocity centroid images of the \(H\alpha\) emission line}
+\end{figure*}
+
+\begin{figure*}
+  \centering
+  \includegraphics[width=0.8\linewidth]{Figures/strucfunc-fit-C}
+  \caption{Second-order structure functions for the velocity centroid images of the \(H\alpha\) emission line}\label{fig:strucfunc-fit-C}
+\end{figure*}
+
+\begin{figure*}
+  \centering
+  \includegraphics[width=0.8\linewidth]{Figures/strucfunc-fit-D}
+  \caption{Second-order structure functions for the velocity centroid images of the \(H\alpha\) emission line}\label{fig:strucfunc-fit-D}
+\end{figure*}
+
+\input{SFresults}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Discussion}\label{sec:discussion}
+
 \subsection{Turbulence}
@@
 \textit{Will 2021-12-10: Moving this section to later for now. Maybe
-  this material could go in discussion.
-Javier 2021-12-28: In deciding the correct place for this part, if we ended up including it, I moved it to the results section.
-For now it makes sense to me because it is where the physical interpretation of the power law and the correlation length are presented for later report the results of each region.}
+  this material could go in discussion.}
 
@@
 
-\subsection{HII regions structure functions}
-
-Figures \ref{fig:strucfunc-fit-A}-\ref{fig:strucfunc-fit-D} show on the left panels the observational structure function in solid blue dots that we compute using equation \ref{eq:Br} on the velocity fields of Fig.
-\ref{fig:velocity-maps}.
-The green dashed line indicate the model without instrumental effects using equation \ref{eq:functional}.
-The Figures also show in yellow solid line the mean of samples posterior using equation \ref{eq:sf-functional}.
-The vertical dashed line indicates the correlation length value \(r_0\) and the horizontal dashed line indicates the \(\sigma^2\) value.
-The vertical and horizontal dotted lines shows the value of the observational consideration \(s_0\) and the \(B_{\text{noise}}\) obtained after the analysis described in section~\ref{sec:met}.
-
-Table \ref{tab:Res} presents the turbulent parameters along the observational constraints.
-The second column correspond to the true variance \(\sigma^2\) of the velocity field.
-The index \(m\) is shown in the third column and is used as a reference for comparison between theory and observations.
-The fourth column is the correlation length in pc.
-
-\begin{figure*}
-  \centering
-  \includegraphics[width=0.8\linewidth]{Figures/strucfunc-fit-A}
-  \caption{Second-order structure functions for the velocity centroid images of the \(H\alpha\) emission line}\label{fig:strucfunc-fit-A}
-\end{figure*}
-
-\begin{figure*}
-  \centering
-  \includegraphics[width=0.8\linewidth]{Figures/strucfunc-fit-B}
-  \label{fig:strucfunc-fit-B}
-  \caption{Second-order structure functions for the velocity centroid images of the \(H\alpha\) emission line}
-\end{figure*}
-
-\begin{figure*}
-  \centering
-  \includegraphics[width=0.8\linewidth]{Figures/strucfunc-fit-C}
-  \caption{Second-order structure functions for the velocity centroid images of the \(H\alpha\) emission line}\label{fig:strucfunc-fit-C}
-\end{figure*}
-
-\begin{figure*}
-  \centering
-  \includegraphics[width=0.8\linewidth]{Figures/strucfunc-fit-D}
-  \caption{Second-order structure functions for the velocity centroid images of the \(H\alpha\) emission line}\label{fig:strucfunc-fit-D}
-\end{figure*}
-
-\input{SFresults}
-
-\subsubsection{Velocity field \(\sigma\)}
-
-%Note to me: review bibliography and expand this section
-The true variance of the velocity fields obtained with the analysis in Section \ref{sec:apply} is shown in the second column in Table \ref{tab:Res}. 
-For all regions except for Carina and Lagoon there is an slight increase in the value of $\sigma$.
-
-%The highest \(\sigma\) is 15.8 km s\(^{-1}\) for 30Dor.
-%This is two times higher than NGC 604 that has a value of 7.4 km s\(^{-1}\), followed by NGC 595 with 6.64 km s\(^{-1}\).
-%NGC 346 is next with a value of 5.6 km s\(^{-1}\), followed by Carina with 4.22 km s\(^{-1}\).
-%Hubble X and M42 have a value of 3.59 and 3.23 km s\(^{-1}\), respectively.
-%Hubble V has 2.8 km s\(^{-1}\) and last mof all sample is Lagoon with 2.7 km s\(^{-1}\).
-
-\subsubsection{Structure function power indices \(m\)}
-
-%As a justification for the use of the structure function we can consider that any relation between the line width and line-of-sight depth can be interpreted in terms of a correlation between velocity spread and scale size.
-%This follows if we have an optically thin spectral line where it will have a width which is related to the total radial velocity dispersion of all fluctuations sampled along the line-of-sight \citep{1984ApJ...277..556S}.
-%In these sense the structure function is used as a tool to investigate the projection of a three-dimensional correlation function onto the plane of sky \citep{arthur2016turbulence}.
-
-For the comparison between the two-dimensional structure function and the three-dimensional structure function relationships between the power-law were proposed.
-This procedure is called projection smoothing \citep{von1951methode, munch1958internal,1987ApJ...317..686O}.
-
-\begin{equation}\label{eq:exp1}
-m_{2D}= m_{3D} + 1
-\end{equation}
-
-or when the astronomical object is almost two-dimensional (sheet-like) we have:
-
-\begin{equation}\label{eq:exp2}
-m_{2D} \sim m_{3D}
-\end{equation}
-
-If the extension of the region is compared with its depth the value of the index is $\frac{5}{3}$.
-While the case where the extension is much greater than its depth (two-dimensional) will have a value of $\frac{2}{3}$.
-
-We can compute the $m_{3D}$ index from the two dimensional \(m\), if we assume that the $m_{3D}$ index lies between the limits of projection smoothing and a sheet-like distribution. 
-Following the procedure by \cite{arthur2016turbulence} and assuming the relationship $m_{2D}$ - 1 $<$ $m_{3D}$ $<$ $m_{2D}$ we have 0.36 $<$ m$_{3D}$ $<$ 0.72.
-
-\subsubsection{Significance on the length scale \(r_0\)}
-
-Ideally the correlation length \(r_0\), should represent the scale of dominant energy injection. 
-Since it is unclear what are the mechanisms driving the turbulence, thought a lot of options are candidates, it is difficult to pinpoint one particular process as the main responsible. 
-The range covered in our results goes from 0.09 to 11 pc.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Discussion}\label{sec:discussion}
+\subsection{Scaling relations between physical properties and turbulent parameters}
 
@@
 We also do a comparison between our results with previous structure functions.
-
-\subsection{Correlations between physical properties and turbulent parameters}
 
@@
 The relationship we found is relation of \(\log r_0 = (0.68 \pm 0.06) \log R-(0.83 \pm 0.12)\).
+%Ideally the correlation length \(r_0\), should represent the scale of dominant energy injection. 
+%Since it is unclear what are the mechanisms driving the turbulence, thought a lot of options are candidates, it is difficult to pinpoint one particular process as the main responsible.
 
@@
 
-The Figure \ref{fig:svss} shows the log $\sigma$-log $\sigma_{\text{LOS}}$ plane with a relationship of $\log \sigma = (0.81 \pm 0.47) \log \sigma_{\text{LOS}}-(0.2 \pm 0.54)$ .
+The Figure \ref{fig:svss} shows the log $\sigma$-log $\sigma_{\text{LOS}}$ plane with a relationship of $\log \sigma = (0.81 \pm 0.47) \log \sigma_{\text{LOS}}-(0.2 \pm 0.54)$.
+
+%As a justification for the use of the structure function we can consider that any relation between the line width and line-of-sight depth can be interpreted in terms of a correlation between velocity spread and scale size.
+
+%This follows if we have an optically thin spectral line where it will have a width which is related to the total radial velocity dispersion of all fluctuations sampled along the line-of-sight \citep{1984ApJ...277..556S}.
+%In these sense the structure function is used as a tool to investigate the projection of a three-dimensional correlation function onto the plane of sky \citep{arthur2016turbulence}.
+
+%For the comparison between the two-dimensional structure function and the three-dimensional structure function relationships between the power-law were proposed.
+%This procedure is called projection smoothing \citep{von1951methode, munch1958internal,1987ApJ...317..686O}.
+
+%\begin{equation}\label{eq:exp1}
+%m_{2D}= m_{3D} + 1
+%\end{equation}
+
+%or when the astronomical object is almost two-dimensional (sheet-like) we have:
+
+%\begin{equation}\label{eq:exp2}
+%m_{2D} \sim m_{3D}
+%\end{equation}
+
+%We can compute the $m_{3D}$ index from the two dimensional \(m\), if we assume that the $m_{3D}$ index lies between the limits of projection smoothing and a sheet-like distribution. 
+%Following the procedure by \cite{arthur2016turbulence} and assuming the relationship $m_{2D}$ - 1 $<$ $m_{3D}$ $<$ $m_{2D}$ we have 0.36 $<$ m$_{3D}$ $<$ 0.72.
 
@@
 
-In Section \ref{sec:apply} we mentioned the reduced chi-square method we are using for the determination of the correlation length and the index of the slope.
+In Section \ref{sec:methods-apply} we mentioned the reduced chi-square method we are using for the determination of the correlation length and the index of the slope.
 Since this is the first time this method is applied to a sample of HII regions (at least for our knowledge), our results are bounded to be different from previous investigations, including the one that have the same observations as \citet{arthur2016turbulence} and \citet{2019arXiv191203543M}.

### 2022-01-31 Corr.tex
Javier changes 2022-01-31

@@
 \hline
- log $\sigma$ &            log L(H) &   0.28 $\pm$ 0.1 &  -9.87 $\pm$ 3.66 &   0.85 &  0.002 \\
+ log $\sigma\pos$ &            log L(H) &   0.28 $\pm$ 0.1 &  -9.87 $\pm$ 3.66 &   0.85 &  0.002 \\
     log $r_0$ &             log $S$ &   0.73 $\pm$ 0.24 &  -1.17 $\pm$ 0.5 &   0.84 &  0.003 \\
- log $\sigma$ &  log $\sigma_{LOS}$ &   0.76 $\pm$ 0.48 &  -0.14 $\pm$ 0.54 &   0.66 &   0.04 \\
+ log $\sigma\pos$ &  log $\sigma_{\text{los}}$ &   0.76 $\pm$ 0.48 &  -0.14 $\pm$ 0.54 &   0.66 &   0.04 \\
       log $m$ &            log dist &  -0.11 $\pm$ 0.08 &   1.21 $\pm$ 0.16 &  -0.59 &   0.07 \\
- log $\sigma$ &         log $r_{0}$ &   0.22 $\pm$ 0.18 &   0.65 $\pm$ 0.12 &   0.55 &  0.10 \\
-      log $m$ &        log $\sigma$ &  -0.14 $\pm$ 0.24 &   0.11 $\pm$ 0.18 &  -0.42 &  0.22 \\
+ log $\sigma\pos$ &         log $r_{0}$ &   0.22 $\pm$ 0.18 &   0.65 $\pm$ 0.12 &   0.55 &  0.10 \\
+      log $m$ &        log $\sigma\pos$ &  -0.14 $\pm$ 0.24 &   0.11 $\pm$ 0.18 &  -0.42 &  0.22 \\
       log $m$ &         log $r_{0}$ &  -0.04 $\pm$ 0.08 &   0.01 $\pm$ 0.05 &  -0.39 &   0.27 \\

### 2022-01-31 strucfunc_paper.tex
Javier changes 2022-01-31

@@
   span more than two orders of magnitude in size and luminosity.
-  We propose a functional form of the structure function that considers observational constraints.
-  By using a chi-square analysis fitting this functional to our results we extract three parameters related to the fluctuations in the velocity field in each region. 
-  The true velocity dispersion \(\sigma\), which spans from 3 to 15 km s\(^{-1}\), the
-  autocorrelation length \(r_0\) covering to 0.06 - 8 pc, and the power-law slope \(m\) of the velocity field, which ranges from 0.7 to 1.5.
+  We propose a new functional form of the structure function that considers observational constraints.
+  This functional is used as an objective function for a chi-square analysis to adjust our results and extract three parameters related to the fluctuations in the velocity field for each region.
+  We obtain the true velocity dispersion \(\sigma\pos\), which spans from 3 to 19 km s\(^{-1}\), the
+  autocorrelation length \(r_0\) covering to 0.09 - 12 pc, and the power-law slope \(m\) of the velocity field, which ranges from 0.7 to 1.5.
   The velocity dispersion is found to correlate primarily with luminosity and the autocorrelation length correlates primarily with the size of the region.
-  A comparison between \(\sigma\) and \(\sigma_{POS}\) shows that this last value is roughly the double for all regions.
+  A comparison between \(\sigma\pos\) and \(\sigma_{los}\) shows that this last value is roughly the double for all regions.
   We found that our proposed functional form describe with more accuracy the inertial range and our methodology guarantees consistency for comparison between the galactic and giant HII regions.
@@
 
-% Javier initial version
-%
-% HII regions are far from been static objects.  Initially, the gas of
-% a HII region is ionized in a previously disturbed medium.  When the
-% recently created star starts emitting, the energy and matter coming
-% from it interacts with the surrounding medium, putting in motion a
-% series of dynamical processes that have a considerable effect in the
-% velocity field of the now HII region.  Different investigations have
-% shown that a complex velocity structure is particularly to each
-% region.  The excess in the thermal broadening on the spectral lines
-% is interpreted as disorder motions along the line-of-sight (LOS).
-% Large-scale motions like the expansion or rotation of the region can
-% be accounted for, but even after these are considered still persist
-% a random component in the region velocity field.  It has become
-% customary to investigate this random component as turbulence in the
-% ionized gas.
-
 %% Will version 2021-12-07 of Intro second para (how we are studying it)
@@
 
-% Javier's original para 2
-
-% The fluctuations associated with the centroid velocities on the plane-of-sky (POS) of photoionized regions have been characterized several times using the second-order structure function.
-% This studies span from galactic HII regions \citep{1986ApJ...300..624R} like Orion \citep{von1951methode,munch1958internal,castaneda1988,1992ApJ...387..229O,arthur2016turbulence} to giant HII regions \citep{1961MNRAS.122....1F,lagrois2009multi,lagrois2011}, like NGC 604 in the M 33 galaxy \citep{tanco1997,2019arXiv191203543M}.
-
 % Will's 2021-12-08 new version of Intro para 4: description of our methodology
@@
 %% maybe that would be tetter just in section 3
-
-% The procedure using the structure function allow us to determine a distinction between homogeneous turbulence and pure random velocity fluctuations in the photoionized gas.
-% Several problems arise in the study of these fluctuation.
-% One of them is that there is no well-established theory for turbulence in astronomical conditions; these being that the medium is compressible and supersonic.
-% This conditions will develop shock waves in the HII region changing the energy balance \citep{lagrois2011,arthur2016turbulence}.
-% And three, in regard with observations, there is the projection of a three-dimensional function into the plane-of-sky \citep{von1951methode,munch1958internal,1964SvA.....8..210K} leading to a loss in information of the velocity spectrum.
-
-% There are also a series of problems related to the observations that to date have not been formally addressed like the previous ones.
-% These problems are that: 1) following observations, there is the seeing and noise due to the telescope and instrument, and 2) that the observations are mostly limited to only one part of the nebula.
-% This has the consequence that when analyzing a turbulent field, the velocity fluctuations related to small and large scales will be affected due to artifacts introduced by the problems mentioned above.
-% In turbulence theory, the largest and smallest scales are the most important as they relate to the energy transfer of the turbulence spectrum, which implies that it is necessary to consider them for a correct characterization of the turbulence in the velocity field.
-% Disregarding the above has led previous investigations in HII regions to erroneous conclusions about the nature of the energy spectrum.
-
-% To face these problems, we study the effects of seeing, noise and observational box size using an artificial velocity field to develop and propose a better form that fits the results of a statistical analysis in the velocity field of HII regions.
-% This aims to leave little room for the interpretation of results and to characterize in a more precise way the turbulence in ionized nebulae, something that has not been considered in previous works.
-% Also, we aim to fill a gap with an uniform statistical analysis of turbulence between galactic and giant HII regions.
-
-% Using archival data we perform the second-order structure function on a sample of HII regions.
-% Our sample spans in size from 4 pc to 400 pc and has luminosities between 10\(^{37}\)-10\(^{39}\) erg s\(^{-1}\) going from galactic to extragalactic HII regions.
-% We apply an uniform methodology of a functional form of the structure function to characterize the turbulent using the velocity field variance, $\sigma^2$, autocorrelation length, \(r_0\), and power-law slope, \(m\).
-% Our results are compared with physical properties of each region and with previous investigations.
 
@@
 It is a luminous star-forming region in the LMC (Large Magellanic Cloud) and is the most luminous complex in the Local Group \citep{1984ApJ...287..116K}.
-The central ionized region spans for 40 pc and host the massive, dense star cluster R136 %\citep{1991IAUS..148..145W}. %Note: check the format
+The central ionized region spans for 40 pc and host the massive, dense star cluster R136 %\citep{1991IAUS..148..145W}. %Note: check the bibliographic format
 The ionizing output \(Q_0\) of R136 is \SI{e51.4}{photons.s^{-1}} \citep{2020MNRAS.499.1918B}.
@@
 %(1'' = 2.4 pc)
-HV has a characteristic length of 100 pc and HX has a characteristic length of 140 pc \citep{1999PASP..111.1382O}.
+%HV has a characteristic length of 100 pc and HX has a characteristic length of 140 pc \citep{1999PASP..111.1382O}.
 Luminosity \ha{} for HV is \SI{e38.3}{erg.s^{-1}} and for HX is \SI{e38.21}{erg.s^{-1}} \citep{2002MNRAS.329..481B}.
@@
 %
-the, \(\langle V_c \rangle \) is the mean centroid velocity
+the, \(\langle V_c \rangle \) is the mean centroid velocity:
 %
@@
 % \beta(r_0) = 1 - exp[\frac{L_{box}}{3.6r_0}] 
-  \beta(L_{\text{box}},r_0) = 1 - \exp \left[ \frac{-L_{\text{box}}} {3.6 r_0} \right] 
-\end{equation}
-%
-where the \(L_{\text{box}}\) value is the diagonal length of the observational box.
+  \beta(L,r_0) = 1 - \exp \left[ \frac{-L} {3.6 r_0} \right] 
+\end{equation}
+%
+where the \(L\) value is the diagonal length of the observational box.
 
@@
 where the term \( B_{\text{noise}}\) is a correction factor that considers the instrument noise at small scales.
-This noise would have the effect of flattening the structure function by removing the effects of the fluctuations which would be interpreted as an uncorrelated property.
+This noise would have the effect of flattening the structure function by removing the effects of the fluctuations which would be interpreted as an uncorrelated field.
 
@@
 \begin{equation}\label{eq:chi}
-  \chi^2 = \sum_i ^N \frac{[B(r)-B_{\text{func}}(r;r_0, \sigma^2, m, s_0, B_{\text{noise}})]^2}{\epsilon_i ^2}
-\end{equation}
-%
-which calculate a value \(\chi\) to be minimized scaled by the inverse of the uncertainty \(\epsilon\) in the data.
-The minimization procedure use the the method \textit{emcee} \citep{2013PASP..125..306F} which is a \textit{python} implementation of the affine-invariant ensemble sampler for Markov chain Monte Carlo (MCMC) by \citet{2010CAMCS...5...65G}.
-The turbulent parameters \(r_{0}\)\ , \(\sigma^2\) and \(m\), and the observational constraints \(s_0\) and \( B_{\text{noise}}\) are the set of variables in the model to be optimized in the fit.
-Using these procedure we obtain a sample of fits for the structure function.
+  \chi^2 = \sum_i ^N \frac{[B(r)-B_{\text{func}}(r;r_0, \sigma^2\pos, m, s_0, B_{\text{noise}})]^2}{\varepsilon_i ^2}
+\end{equation}
+%
+which calculate a value \(\chi\) to be minimized scaled by the inverse of the uncertainty \(\varepsilon\) in the data.
+The minimization procedure use the method \textit{emcee} \citep{2013PASP..125..306F} which is a \textit{python} implementation of the affine-invariant ensemble sampler for Markov chain Monte Carlo (MCMC) by \citet{2010CAMCS...5...65G}.
+The turbulent parameters \(r_{0}\)\ , \(\sigma^2\pos\) and \(m\), and the observational constraints \(s_0\) and \( B_{\text{noise}}\) are the set of variables in the model to be optimized in the fit.
+Using these procedure we obtain posteriors for the structure function.
 
@@
 If this increase in values is stopped or reversed it is commonly assumed that one particular inertial range has been found. 
-In some cases this procedure keeps going up to large scales, giving two or more inertial regimes leading to the erroneous interpretation of multiple inertial scales.
+In some cases this procedure keeps going up to large scales, giving two or more inertial regimes leading to an erroneous interpretation of multiple inertial scales.
 
@@
 
-We present our second-order structure results plotted against separation in parsecs.
+We present our second-order structure results plotted against separation in parsecs and the posteriors of the parameters used in the analysis.
 
@@
 The vertical and horizontal dotted lines shows the value of the observational considerations, the seeing, \(s_0\) and the value of the noise, \(B_{\text{noise}}\), respectively.
-For the dashed and dotted lines the overlapping translucent boxes indicate the spread of values up to two-sigma (dark shaded area) and three-sigma (light shaded area) obtained after the analysis described in section~\ref{sec:methods-apply}.
-
-The results shown on left panels on Figures \ref{fig:strucfunc-fit-A}-\ref{fig:strucfunc-fit-D} show a typical second-order structure function pattern, where there is a series of ascending values of  \ref{eq:Br} that tends to stabilize around the 2\(\sigma^2\) value indicating a loss in the correlations at large separations.
-The Carina nebula and Hubble X show this behavior.
+For the dashed and dotted lines the overlapping translucent boxes indicate the spread of values up to 2-sigma (dark shaded area) and 3-sigma (light shaded area) obtained after the analysis described in section~\ref{sec:methods-apply}.
+
+Figures \ref{fig:strucfunc-fit-A}-\ref{fig:strucfunc-fit-D} right panels show the corner plots \citep{2017ascl.soft02002F} of the turbulent parameters and observational constraints. 
+These plots shows the one and two dimensional projections of the posterior probability distributions of the parameters used in equation \ref{eq:chi}.
+They also show the marginalized distribution for each parameter independently in the histograms along the diagonal and then the marginalized two dimensional distributions in the other panels making possible to visualize all of the covariances between parameters \citep{2017ascl.soft02002F}.
+The contours in the plots reflect the 95\(\%\), 99\(\%\), 99.5\(\%\) and 99.9\(\%\) confidence intervals.
+
+The results shown on left panels on Figures \ref{fig:strucfunc-fit-A}-\ref{fig:strucfunc-fit-D} show a typical second-order structure function pattern, where there is a series of ascending values of  \ref{eq:Br} that tends to stabilize around the 2\(\sigma^2\) value, indicating a loss in the correlations at large separations.
+The Carina nebula and Hubble X follow this behavior.
 
@@
 
-The second column correspond to the true variance \(\sigma^2\) of the velocity field.
+The second column correspond to the true variance \(\sigma^2\pos\) of the velocity field.
 For all regions except for Carina, Lagoon and the EON there is an increase in this value.
@@
 The range covered by the power-law index in our HII region sample goes from 0.7 to 1.5.
-If the extension of the HII region is compared with its depth (three-dimensional case) the value of the index is 1.6.
-While the case where the extension is much greater than its depth (two-dimensional case) the region will have a value of 0.6 \citep{von1951methode, munch1958internal,1987ApJ...317..686O}.
 The implications of these results is further developed on the next section.
@@
 
-The existence of turbulent flows in astrophysical objects, ranging in scales from 10$^{6}$ to 10$^{17}$ m \citep{2010ApJ...710..853C} is the consequence of the high Reynolds numbers, $Re$, between 10$^{4}$ and 10$^{9}$ \citep{1949ApJ...110..329C,lagrois2011} that characterized these objects.
-The classic turbulence theory assumes a three-dimensional isotropic, incompressible and subsonic flow that can be described using an energy spectrum \citep{kolm1}.
-The concept of the energy spectrum is based on the assumption that the energy is cascading down inside the flow from the largest to the smallest scales.
-The different scales in the energy cascade are defined based on their $Re$.
-In one side of the spectrum there is the energy, \(L\), injection scale that is related to the largest vortices, where $ Re \rightarrow \infty$.
-On the other side of the spectrum there is the dissipation of energy at small scales, \(l\), where $Re \rightarrow$ 1 and it is assumed that small vortices are responsible for the friction that dissipates the energy flux into thermal energy.
-In between there is the inertial range, \(l  << r << L\) , where in a stationary case there energy transfer is at a constant rate,.
-The energy cascade concept is described with an energy spectrum, $E(k) \propto k^{\beta}$ where $k$ is the wave number for a determined scale $r$ ($k \equiv r^{-1}$).
-
-The total specific energy of a determined $r$ scale is of the order $\langle v_{r}^{2} \rangle$ and is the energy integral above the associated $k$, defined as:
-\begin{equation}\label{eq:energyspectrum}
- \langle v_{r}^{2} \rangle = \int_{k}^{\infty} E(k)dk
-\end{equation}
-%
-It is assumed that this energy is of the order of $(\epsilon r)^{\frac{2}{3}} \sim (\frac{\epsilon}{k})^{\frac{2}{3}}$ we differentiate Equation \ref{eq:energyspectrum} and obtained the final form of the spectrum:
-
-\begin{equation}\label{eq:kolm}
+The idea to treat the ionized regions from a fluid mechanic view is intuitive if we consider the continuum hypothesis. 
+We validate this hypothesis using the Knudsen number defined as \(Kn \equiv \lambda / l\), where \(\lambda\) is the mean free path of the medium and \(l\) a characteristic length of the phenomenon we are studying.
+Taking into account a \(\lambda_{\text{HII}}\) of \SI{2.7e-7}{pc} \citep{1941ApJ....93..369S} and a \(l_{\text{HII}}\) of \SI{1}{pc} for ionized regions we obtained \(Kn \approx 10^{-7}\), while in general the continuum approach is valid for \(Kn \ll 1\).
+
+A turbulent behavior in the flows is more common in fluid systems than a laminar one.
+These turbulent flows tends to be unsteady, irregular and chaotic, and the turbulent motions are observed in many scales. 
+The turbulent flows are associated with a high Reynolds numbers which is defined as \(Re = l v_{l} / \nu \), where \(v_{l}\) is a characteristic velocity in the fluid system and \(\nu\) is the kinematic viscosity of the medium.
+Experiments have shown that a flow which is laminar become turbulent when increasing the velocity (i.e., increasing the \(Re\)) and a large range of velocity fluctuation appear at all scales.
+A high \(Re\) reflects high ratio of the advection/difussion terms of the Navier-Stokes equations, being interpreted as that the inertial forces taking over the viscous ones.
+
+As astronomical observation made it possible to measure a large number of points with a high accuracy, it was found that velocities show a non-thermal component reflecting characteristic of earthly turbulent flows.
+The existence of turbulent flows in astrophysical objects, ranging in scales from 10\(^6\) to 10\(^{17}\) m \citep{2010ApJ...710..853C} is thought to be consequence of the high \(Re\), between 10\(^4\) and 10\(^9\) \citep{1949ApJ...110..329C,lagrois2011} that characterized these objects.
+
+The classic turbulence theory assumes a three-dimensional isotropic, incompressible and subsonic flow that can be described using an energy spectrum formed by vortices or eddies of different sizes \citep{kolm1}.
+The concept of the energy spectrum assumes that the energy is cascading down inside the flow from the largest to the smallest scales.
+The different scales in the energy cascade are defined based on their \(Re\).
+In one side of the spectrum there is the energy injection scale, \(L_I\), that is related to the largest vortices, called the integral scales, where \(Re \rightarrow \infty\).
+On the other side of the spectrum there is the dissipation of energy at small scales, \(l_I\), where  \(Re \rightarrow 1\) and it is assumed that small vortices are responsible for the friction that dissipates the energy flux into thermal energy.
+In between there is the inertial range, \(l_d  << l << L_I\), where in a stationary case the energy transfer is at a constant rate.
+
+The rate of transfer of specific energy \(\epsilon\) (energy per unit mass) in the inertial range is independent of the \(l\) scale having the form \(\epsilon \sim v_l^2 / \tau_l\), where the kinetic energy is of the order of \( v_l^2\) and the life time of a velocity fluctuation is \(\tau_l\), which can be can be put in terms of \(\tau_l \sim l / v_l\).
+Hence we obtain \( v_l \sim (\epsilon l)^{1/3}\) where \(\epsilon\) is invariant in the cascade.
+
+The energy cascade is described using the energy spectrum, $E(k) \propto k^{\beta}$ where \(k\) is the wave number for a determined scale \(l\) ($k \equiv l^{-1}$).
+The total specific energy of a determined $l$ scale is of the order \(\langle v_{l}^{2} \rangle \) and is the energy integral above the associated \(k\), defined as:
+
+\begin{equation}\label{eq:energy-spectrum}
+ \langle v_{l}^{2} \rangle = \int_{k}^{\infty} E(k)dk
+\end{equation}
+%
+If it is assumed that this energy is of the order of $(\epsilon l)^{\frac{2}{3}} \sim (\frac{\epsilon}{k})^{\frac{2}{3}}$ we can differentiate equation \ref{eq:energy-spectrum} and obtained the final form:
+
+\begin{equation}\label{eq:kolmogorov-law}
 E(k) \propto \epsilon^\frac{2}{3} k^{-\frac{5}{3}}
@@
 %
-where \(\epsilon\) is the energy transfer rate and the value of \(\beta = -5 / 3\) is the Kolmogorov index.
-%For supersonic turbulence the index is $\beta=-2$ \citep{burg}. 
-%In the Kolmogorov model \(B(r) \propto r^{2/3}\).
+where \(\beta = -5 / 3\) is the Kolmogorov law.
+For supersonic turbulence the index is $\beta=-2$ \citep{burg}.
+
+Using a statistical law that relates the moments \(M_n\) of order \(n\) with the increments in the velocity field for a separation \(\boldsymbol{r}\) \citep{Leqism}, we have:
+
+\begin{equation}\label{eq:velocity-moments}
+M_n = \langle \vert \boldsymbol{v}(\boldsymbol{x} + \boldsymbol{r})- \boldsymbol{v}(\boldsymbol{x})\vert^n \rangle \propto (\epsilon r)^{n/3}
+\end{equation}
+the average is over all the positions \(\boldsymbol{x}\) and directions \(\boldsymbol{r}\). 
+The Kolmogorov model predicts that the moment of order 2, the second-order structure function (equation \ref{eq:Br}), follows \(M_2 \propto r^{2/3}\).
 
@@
 
-In the section \ref{sec:results} we showed that each HII region has a turbulent velocity field that can be characterized using the turbulence theory.
+In the section \ref{sec:results} we showed that each \hii{} region of our sample has a turbulent velocity field that can be characterized using the turbulence theory.
 The turbulent parameters obtained are unique to each velocity field.
-We proceed to develop scaling relations between them and between the physical properties of each region.
-We also do a comparison between our results with previous structure functions.
+We proceed to develop scaling relations between them and also between the physical properties of each region.
 
 %Intro for scaling relations
-Relationship between the physical properties of HII regions, like size and luminosity, and the velocity dispersion have been used as tools for concluding scaling relations for these objects.
+Relationship between the physical properties of \hii{} regions, like size and luminosity, and the velocity dispersion have been used as tools for concluding scaling relations for these objects.
 These relations have also been studied in dwarf galaxies and high-redshift star formation regions.
-\citet{melnick1977,terlevich1981} were the first to shown an empirical relationship between the line width and the integrated properties of the HII regions as the diameter or the luminosity ($r \sim \sigma ^{\sim 2}$ ; $\text{L}_{\text{H}} \sim \sigma ^{\sim 4}$).
+\citet{melnick1977,terlevich1981} were the first to shown an empirical relationship between the line width and the integrated properties of the \hii{} regions as the diameter or the luminosity ($r \sim \sigma ^{\sim 2}$ ; $\text{L}_{\text{H}} \sim \sigma ^{\sim 4}$).
 They conclude that GEHRs follow this relation because they behave as self-gravitatory systems like globular clusters or elliptical galaxies.
@@
 %Previous research on scaling relations
-\citet{2012MNRAS.422.3339W} have found that clumps and HII regions follow scaling relations over the range of z = 0-2 for \halpha\ size, velocity dispersion, luminosity and mass, finding \(\sigma \propto r^{0.42}\), \(\text{L}_{\text{H}_{\alpha}} \propto r^{2.72}\) and \(\text{L}_{\text{H}_{\alpha}} \propto \sigma^{4.18}\), respectively.
+\citet{2012MNRAS.422.3339W} have found that clumps and \hii{} regions follow scaling relations over the range of z = 0-2 for \halpha\ size, velocity dispersion, luminosity and mass, finding \(\sigma \propto r^{0.42}\), \(\text{L}_{\text{H}_{\alpha}} \propto r^{2.72}\) and \(\text{L}_{\text{H}_{\alpha}} \propto \sigma^{4.18}\), respectively.
 This results imply that the same process are seen at high redshifts and the current epoch in star forming regions.
@@
 We follow through this analysis using the scaling relation as a research tool between the properties of the sample of HII regions and our results. 
-We use the properties in Table \ref{tab:regions-properties} with the turbulent parameters in Table \ref{tab:Res} as the dependent variable to adjust a fit in the form $Y = aX +b$. 
+We use the properties in Table \ref{tab:regions-properties} with the turbulent parameters in Table \ref{tab:Res} as the dependent variable to adjust a fit in the form \(Y = aX +b\). 
 For this procedure we use a hierarchical Bayesian approach using the package \textit{linmix} \citep{2007ApJ...665.1489K}.
@@
 
+The Figure \ref{fig:sigvsl} shows the log \(\sigma\pos\)-log \(\text{L}(\text{H}_{\alpha})\) plane.
+Since this relation is the most common it can be use for comparison with the investigations mentioned at the beginning of this section.
+Our results give us a relation of \(\log \sigma\pos = (0.28 \pm 0.1) \log \text{L}(\text{H}_{\alpha})-(10 \pm 4.0)\).
+It is customary in the literature to present \(\text{L} (\text{H}_{\alpha})\) as the dependent variable.
+In our case if we choose the upper uncertainty and take the inverse of slope we have \(\text{L}_{\text{H}_{\alpha}} \propto \sigma^{3.4}\). 
+Using the same procedure in \textit{linmix} and changing the variables we obtained \(\log \text{L}(\text{H}_{\alpha}) = (3.1\pm 1.3) \log \sigma\pos -(36 \pm 1)\).
+Both relations are close to the previously proposed \(\text{L}_{\text{H}} \propto \sigma^{4}\) relation.
+
 %Size vs correlation length
-The Figure \ref{fig:rvsR} shows the relation of the correlation length $r_0$ and the size \(S\) of the region.
-The relationship we found is relation of \(\log r_0 = (0.68 \pm 0.06) \log R-(0.83 \pm 0.12)\).
-%Ideally the correlation length \(r_0\), should represent the scale of dominant energy injection. 
-%Since it is unclear what are the mechanisms driving the turbulence, thought a lot of options are candidates, it is difficult to pinpoint one particular process as the main responsible.
-
-The Figure \ref{fig:sigvsl} shows the log \(\sigma\)-log $\text{L}(\text{H}_{\alpha})$ plane.
-Since this relation is the most common it can be use for comparison with the investigations mentioned at the beginning of this section.
-Our results give us a relation of $\log \sigma = (0.25 \pm 0.1) \log \text{L}(\text{H}_{\alpha})-(9 \pm 4.0)$.
-It is customary in the literature to present $\text{L} (\text{H}_{\alpha})$ as the dependent variable.
-In our case if we choose the upper positive error and take the inverse of slope we have \(\text{L}_{\text{H}_{\alpha}} \propto \sigma^{3.5}\). 
-Using the same procedure in \textit{linmix} and changing the variables we obtained $\log \text{L}(\text{H}_{\alpha}) = (3.2\pm 1.4) \log \sigma -(36 \pm 1)$.
-Both relations are close to the previously proposed \(\text{L}_{\text{H}_{\alpha}} \propto \sigma^{4}\)
+The Figure \ref{fig:rvsR} shows the relation of the correlation length \(r_0\) and the size \(S\) of the region. 
+The relationship we found is \(\log r_0 = (0.73 \pm 0.24) \log S - (1.17 \pm 0.5)\).
+The values of the \(S\) are taken from \citet{1984ApJ...287..116K} and correspond to the outer
+limits seen from visual inspection of the \ha{} photographs.
+In this sense these values would represent an upper limit of the size of each region.
+Since these objects do not posses a physical edges the size determination is not trivial.
+Due to the above, we chose these set values since they come from an unique source and are foreign to our calculations and observations, which imply that there is no bias in the scaling law we obtain.
+
+Ideally the correlation length \(r_0\), should represent the scale of dominant energy injection. 
+Since it is unclear what are the mechanisms driving the turbulence, thought a lot of options are candidates, it is difficult to pinpoint one particular process as the main responsible.
+
+%\subsubsection{Relationship between plane-of-sky and line-of-sight velocity dispersion.}
+%Note 26/01/22: Expand and polish from here
+
+The standard deviation of the velocity centroid and the mean non-thermal linewidth allow us to compare the relation between the kinematical disorder on the plane-of-the sky and along the line-of-sight  \citep{2011MNRAS.413..705L}.
+
+The broad in the velocity width of the emission line represents the range of velocities along the line-of-sight.%, among thermal movements. 
+We can consider as a main broadening mechanisms the kinematical disorder along the LOS related to velocity gradients by the clumpiness on the molecular cloud and turbulent movements.
+On the plane-of-sky the consequences of those gradients and movements is measured in every pixel. 
+The spatial variations on the velocity field would depend on the targeted pixel, depending on the motions inside the cloud (the LOS component).
+This reasoning has lead to \citet{2011MNRAS.413..705L} to propose a direct relationship between \(\sigma_{\text{LOS}}\) and \(\sigma\pos\).
+
+The Figure \ref{fig:svss} shows the log \(\sigma\)-log \(\sigma_{\text{los}}\) plane with a relationship of \(\log \sigma\pos = (0.76 \pm 0.48) \log \sigma_{\text{los}}-(0.14 \pm 0.54)\).
 
@@
 \end{figure}
-
-\subsubsection{Relationship between plane-of-sky and line-of-sight velocity dispersion.}
-
-The broad in the velocity width of the emission line represents the range of velocities along the line-of-sight (LOS), among thermal movements. 
-We can consider as a main broadening mechanisms, the kinematical disorder along the LOS related to velocity gradients by the clumpiness on the molecular cloud and turbulent movements.
-On the plane-of-sky (POS) the consequences of those gradients and movements is measured in every pixel.
-The spatial variations on the velocity field would depend on the targeted pixel, depending on the motions inside the cloud (the LOS component).
-This reasoning has lead to \citet{2011MNRAS.413..705L} to propose a direct relationship between \(\sigma_{\text{LOS}}\) and \(\sigma_{\text{POS}}\) (or just \(\sigma\) in this work).
-
-It have been mentioned that the projection of the velocity fluctuations reduces the actual amplitude in the line-of-sight \citep{1984ApJ...277..556S,arthur2016turbulence}.
-We can see from Table \ref{tab:Res} that the line-of-sight velocity dispersion is roughly twice the plane-of-sky velocity dispersion.
-In the case of homogeneous turbulent velocity we can consider the effect of \textit{project smearing} \citep{1984ApJ...277..556S}, where the projection from three to two dimensions over the line-of-sight depth \(H\), reduces the plane-of-sky amplitude for the condition \(r_{0} < H\).
-With a value of \(\sigma / \sigma_{\text{LOS}}\) = 0.5 we obtain \(r_{0} / H \sim\) 0.01-0.1.
-
-The Figure \ref{fig:svss} shows the log $\sigma$-log $\sigma_{\text{LOS}}$ plane with a relationship of $\log \sigma = (0.81 \pm 0.47) \log \sigma_{\text{LOS}}-(0.2 \pm 0.54)$.
-
-%As a justification for the use of the structure function we can consider that any relation between the line width and line-of-sight depth can be interpreted in terms of a correlation between velocity spread and scale size.
-
-%This follows if we have an optically thin spectral line where it will have a width which is related to the total radial velocity dispersion of all fluctuations sampled along the line-of-sight \citep{1984ApJ...277..556S}.
-%In these sense the structure function is used as a tool to investigate the projection of a three-dimensional correlation function onto the plane of sky \citep{arthur2016turbulence}.
-
-%For the comparison between the two-dimensional structure function and the three-dimensional structure function relationships between the power-law were proposed.
-%This procedure is called projection smoothing \citep{von1951methode, munch1958internal,1987ApJ...317..686O}.
-
-%\begin{equation}\label{eq:exp1}
-%m_{2D}= m_{3D} + 1
-%\end{equation}
-
-%or when the astronomical object is almost two-dimensional (sheet-like) we have:
-
-%\begin{equation}\label{eq:exp2}
-%m_{2D} \sim m_{3D}
-%\end{equation}
-
-%We can compute the $m_{3D}$ index from the two dimensional \(m\), if we assume that the $m_{3D}$ index lies between the limits of projection smoothing and a sheet-like distribution. 
-%Following the procedure by \cite{arthur2016turbulence} and assuming the relationship $m_{2D}$ - 1 $<$ $m_{3D}$ $<$ $m_{2D}$ we have 0.36 $<$ m$_{3D}$ $<$ 0.72.
 
@@
 
+\subsection{Projection smearing}
+
+As a justification for the use of the structure function we can consider that any relation between the line width and line-of-sight depth can be interpreted in terms of a correlation between velocity spread and scale size.
+This follows that if we have an optically thin spectral line where it will have a width which is related to the total radial velocity dispersion of all fluctuations sampled along the line-of-sight \citep{1984ApJ...277..556S}.
+In these sense the structure function is used as a tool to investigate the projection of a three-dimensional correlation function onto the plane of sky \citep{arthur2016turbulence}.
+
+It have been mentioned that the projection of the velocity fluctuations reduces the actual amplitude in the line-of-sight \citep{1984ApJ...277..556S,arthur2016turbulence}.
+We can see from Table \ref{tab:Res} that the line-of-sight velocity dispersion is roughly twice the plane-of-sky velocity dispersion.
+In the case of homogeneous turbulent velocity we can consider the effect of \textit{project smearing} \citep{1984ApJ...277..556S}, where the projection from three to two dimensions over the line-of-sight depth \(H\), reduces the plane-of-sky amplitude for the condition \(r_{0} < H\).
+With a value of \(\sigma\pos / \sigma_{\text{los}}\) = 0.5 we obtain \(r_{0} / H \sim\) 0.01-0.1.
+
+For the comparison between the two-dimensional structure function and the three-dimensional structure function relationships between the power-law were proposed:
+
+\begin{equation}\label{eq:projection-smearing-3d}
+m_{2D}= m_{3D} + 1
+\end{equation}
+
+or when the astronomical object is almost two-dimensional (sheet-like) we have:
+
+\begin{equation}\label{eq:projection-smearing-2d}
+m_{2D} \sim m_{3D}
+\end{equation}
+
+If the extension of the HII region is compared with its depth (three-dimensional case) the value of the index is 1.6. 
+While the case where the extension is much greater than its depth (two-dimensional case) the region will have a value of 0.6 \citep{von1951methode, munch1958internal,1987ApJ...317..686O}.
+
+We can compute the \(m_{3D}\) index from the two dimensional \(m\), if we assume that the \(m_{3D}\) index lies between the limits of projection smoothing and a sheet-like distribution. 
+Following the procedure by \cite{arthur2016turbulence} and assuming the relationship \(m_{2D} - 1 < m_{3D}\ < m_{2D}\) we have 0.54 \(< m_{3D} <\) 0.72.
+
 \subsection{Comparison with previous structure functions}
@@
 The first attempt at characterizing turbulence in a giant extragalactic HII region, GEHR, was done by \citet{1961MNRAS.122....1F} with the 30 Doradus complex in the LMC, finding no indication of turbulent motions between scale of 10 and 100 pc.
-\citet{2019arXiv191203543M} also investigated the structure function in 30 Doradus finding on their results that the structure function is entirely flat on scales from 3 to 200 pc.
+\citet{Melnick:2021x} also investigated the structure function in 30 Doradus finding on their results that the structure function is entirely flat on scales from 3 to 200 pc.
 In the context of the high-resolution observations it is possible to see why their results do not reflect the turbulent structure of the nebula; their observations cover a region where the large-scale velocity fluctuations are uncorrelated.
@@
 There is broad agreement in our structure function results and previous studies that consider NGC 604, mainly because where are using the same data \citep{Medina-Tanco:1997a, Melnick:2021x}.
-from \citet{Medina-Tanco:1997a} and \citet{Melnick:2021x}, and using the same TAURUS-II data.
+From \citet{Medina-Tanco:1997a} and \citet{Melnick:2021x}, and using the same TAURUS-II data.
 Despite this general agreement the interpretations in each study is different.
@@
 None of the previous studies present a power-law index for the structure function to compare our results.
-\citet{2019arXiv191203543M} addresses some issues with TAURUS II data while comparing profiles between the previous instrument TAURUS I where there exist a difference between observations (see section 4.1 on their paper).
+\citet{Melnick:2021x} addresses some issues with TAURUS II data while comparing profiles between the previous instrument TAURUS I where there exist a difference between observations (see section 4.1 on their paper).
 As we agree with them in the importance of observing NGC 604 at higher spatial resolution, we have prove that a consistent method in analyzing structure function is key to obtaining trustworthy results.
@@
 \citet{lagrois2011} used the data from \citet{lagrois2009multi} to complement the structure function analysis with the auto correlation function and filters to the velocity field to get rid of non-turbulent movements.
-Their sigma is 5.92$\pm$0.15 km/s with a correlation length is 43 pc.
-The power-law index they provide is 1.55$\pm$0.01.
+Their sigma is 5.92$\pm$0.15 km/s with a correlation length is 43 pc and the power-law index they provide is 1.55$\pm$0.01.
 
@@
 To determine the inertial scale more precisely than in previous works, a new functional form was proposed for the second-order structure function that considers observational effects such as: seeing, noise and the size of the observational box.
-These effects had not been considered in detail before and have important consequences is the interpretation of the inertial scale.
-
-The new functional form of the structure function accurately determines the important parameters related to turbulence which are: the correlation length, the exponent of a power law that fits the results and the real variance of the region.
-Compared to the majority of previous works, the previous parameters had been calculated using the criteria of each author.
-A chi-square adjustment was performed using Bayesian statistics to determine the confidence intervals for each parameter.
-
-This proposed analysis can be expanded to other HII regions with the possibility of comparing the results between them since the proposed method guarantees their homogeneity and the ability to develop a future catalog of these regions in a coherent way.
+These effects had not been considered in detail before and have important consequences in obtaining the inertial scale.
+
+The new functional form of the structure function is used as an objective function in a non-linear regression to accurately determine the important parameters related to turbulence which are: the correlation length, the exponent of a power law that fits the results and the real variance of the region.
+
+This proposed analysis can be expanded to other HII regions with the possibility of comparing the results between them since the method guarantees homogeneity and the ability to develop a future catalog of these regions in a coherent way.
 It could even be used to investigate the velocity fields of other phases of the interstellar medium.

### 2022-02-01 strucfunc_paper.tex
Javier changes 2022-02-01

@@
 \midrule
-Orion     & 0.436 \pm 0.02  & 5 \pm 0.5    &    37.18       &   6.0      \\
+Orion     & 0.436 \pm 0.02  & 5 \pm 0.5    &    37.18       &   6 \pm 1      \\
 Lagoon    & 1.25 \pm 0.12   & 25 \pm 2.5      &    37.47    &   13.6 \pm 0.8    \\
@@
 The fifth column indicates the size of each observational box in parsecs.
-The index \(m\) is shown in the last column and is commonly used as a reference for comparison between observations and the theoretic value of 0.6.
-The range covered by the power-law index in our HII region sample goes from 0.7 to 1.5.
+The index \(m\) is shown in the last column and the range covered by the power-law index in our HII region sample goes from 0.7 to 1.5.
 The implications of these results is further developed on the next section.
@@
 A high \(Re\) reflects high ratio of the advection/difussion terms of the Navier-Stokes equations, being interpreted as that the inertial forces taking over the viscous ones. 
-
-As astronomical observation made it possible to measure a large number of points with a high accuracy, it was found that velocities show a non-thermal component reflecting characteristic of earthly turbulent flows.
+Hence it is possible to assume that if viscosity is not dominant in a flow, this flow would be turbulent.
+
+As astronomical observation made it possible to measure a large number of points with a high accuracy, it was found that velocities show a non-thermal component reflecting characteristic of turbulent earthly flows.
 The existence of turbulent flows in astrophysical objects, ranging in scales from 10\(^6\) to 10\(^{17}\) m \citep{2010ApJ...710..853C} is thought to be consequence of the high \(Re\), between 10\(^4\) and 10\(^9\) \citep{1949ApJ...110..329C,lagrois2011} that characterized these objects.
@@
 
-\subsection{Scaling relations between physical properties and turbulent parameters}
+These mathematical techniques were first applied to astronomical observations by \citet{von1951methode} and \citet{munch1958internal} allowing to determine a distinction between homogeneous turbulence and pure random velocity fluctuations in the Orion Nebula.
+
+\subsection{Interpretation of the turbulent parameters and origins of interstellar turbulence}\label{sec:interpretation-origin}
+
+Ideally the correlation length \(r_0\) should represent the scale of dominant energy injection. 
+It is unclear what are the mechanisms driving the turbulence, thought a lot of options are candidates.
+The main energy sources are, of the order of kpc, the differential rotations of the galaxy that produces shear at large scale, at scales of the order of hundreds of pc supernova explosions inject a large amount of kinetic energy, at scales of several tens of pc the expansion of \hii{} regions is also a source of energy and bipolar flows and jets inject energy at small scales, bouth one tent of a pc.
+
+The index \(m\) is shown in the last column of Table \ref{tab:Res} and is commonly used as a reference for comparison between observations and the theoretic value of 0.67 (equation \ref{eq:velocity-moments}).
+
+\subsubsection{Projection smearing}\label{sec:projection-smearing}
+
+As a justification for the use of the structure function we can consider that any relation between the line width and line-of-sight depth can be interpreted in terms of a correlation between velocity spread and scale size.
+This follows that if we have an optically thin spectral line where it will have a width which is related to the total radial velocity dispersion of all fluctuations sampled along the line-of-sight \citep{1984ApJ...277..556S}.
+In these sense the structure function is used as a tool to investigate the projection of a three-dimensional correlation function onto the plane of sky \citep{arthur2016turbulence}.
+
+It have been mentioned that the projection of the velocity fluctuations reduces the actual amplitude in the line-of-sight \citep{1984ApJ...277..556S,arthur2016turbulence}.
+We can see from Table \ref{tab:Res} that the line-of-sight velocity dispersion is roughly twice the plane-of-sky velocity dispersion.
+In the case of homogeneous turbulent velocity we can consider the effect of \textit{project smearing} \citep{1984ApJ...277..556S}, where the projection from three to two dimensions over the line-of-sight depth \(H\), reduces the plane-of-sky amplitude for the condition \(r_{0} < H\).
+With a value of \(\sigma\pos / \sigma_{\text{los}}\) = 0.5 we obtain \(r_{0} / H \sim\) 0.02-0.1.
+
+For the comparison between the two-dimensional structure function and the three-dimensional structure function relationships between the power-law were proposed:
+
+\begin{equation}\label{eq:projection-smearing-3d}
+m_{2D}= m_{3D} + 1
+\end{equation}
+
+or when the astronomical object is almost two-dimensional (sheet-like) we have:
+
+\begin{equation}\label{eq:projection-smearing-2d}
+m_{2D} \sim m_{3D}
+\end{equation}
+
+If the extension of the HII region is compared with its depth (three-dimensional case) the value of the index is 1.6. 
+While the case where the extension is much greater than its depth (two-dimensional case) the region will have a value of 0.6 \citep{von1951methode, munch1958internal,1987ApJ...317..686O}.
+
+We can compute the \(m_{3D}\) index from the two dimensional \(m\), if we assume that the \(m_{3D}\) index lies between the limits of projection smoothing and a sheet-like distribution. 
+Following the procedure by \cite{arthur2016turbulence} and assuming the relationship \(m_{2D} - 1 < m_{3D}\ < m_{2D}\) we have 0.54 \(< m_{3D} <\) 0.72.
+
+\subsection{Scaling relations between physical properties and turbulent parameters}\label{sec:scaling-relations}
 
@@
 Due to the above, we chose these set values since they come from an unique source and are foreign to our calculations and observations, which imply that there is no bias in the scaling law we obtain.
-
-Ideally the correlation length \(r_0\), should represent the scale of dominant energy injection. 
-Since it is unclear what are the mechanisms driving the turbulence, thought a lot of options are candidates, it is difficult to pinpoint one particular process as the main responsible.
 
@@
 \textbf{Estimate these two factors by fitting to the observations}
-
-\subsection{Projection smearing}
-
-As a justification for the use of the structure function we can consider that any relation between the line width and line-of-sight depth can be interpreted in terms of a correlation between velocity spread and scale size.
-This follows that if we have an optically thin spectral line where it will have a width which is related to the total radial velocity dispersion of all fluctuations sampled along the line-of-sight \citep{1984ApJ...277..556S}.
-In these sense the structure function is used as a tool to investigate the projection of a three-dimensional correlation function onto the plane of sky \citep{arthur2016turbulence}.
-
-It have been mentioned that the projection of the velocity fluctuations reduces the actual amplitude in the line-of-sight \citep{1984ApJ...277..556S,arthur2016turbulence}.
-We can see from Table \ref{tab:Res} that the line-of-sight velocity dispersion is roughly twice the plane-of-sky velocity dispersion.
-In the case of homogeneous turbulent velocity we can consider the effect of \textit{project smearing} \citep{1984ApJ...277..556S}, where the projection from three to two dimensions over the line-of-sight depth \(H\), reduces the plane-of-sky amplitude for the condition \(r_{0} < H\).
-With a value of \(\sigma\pos / \sigma_{\text{los}}\) = 0.5 we obtain \(r_{0} / H \sim\) 0.01-0.1.
-
-For the comparison between the two-dimensional structure function and the three-dimensional structure function relationships between the power-law were proposed:
-
-\begin{equation}\label{eq:projection-smearing-3d}
-m_{2D}= m_{3D} + 1
-\end{equation}
-
-or when the astronomical object is almost two-dimensional (sheet-like) we have:
-
-\begin{equation}\label{eq:projection-smearing-2d}
-m_{2D} \sim m_{3D}
-\end{equation}
-
-If the extension of the HII region is compared with its depth (three-dimensional case) the value of the index is 1.6. 
-While the case where the extension is much greater than its depth (two-dimensional case) the region will have a value of 0.6 \citep{von1951methode, munch1958internal,1987ApJ...317..686O}.
-
-We can compute the \(m_{3D}\) index from the two dimensional \(m\), if we assume that the \(m_{3D}\) index lies between the limits of projection smoothing and a sheet-like distribution. 
-Following the procedure by \cite{arthur2016turbulence} and assuming the relationship \(m_{2D} - 1 < m_{3D}\ < m_{2D}\) we have 0.54 \(< m_{3D} <\) 0.72.
 

### 2022-02-01 strucfunc_paper.tex
Finish description of Fig 3 in text

@@
 of velocity fluctuations.
-All the distributions are far from being consider Gaussian, implying that there are multiple kinematics components in the regions.
+
+All of the distributions are significantly non-Gaussian
+and many show evidence of a multi-modal structure.
+Some, such as Orion core and Hubble~V, show a single dominant velocity component,
+but most show several distinct peaks,
+as many as four in the case of Carina.
+There is no clear tendency for the number of identifiable velocity components
+to increase with increasing velocity dispersion.
+Instead, both the widths of the individual peaks and the separation between them
+seem to increase in tandem.
+For most regions the PDFs are approximately symmetrical,
+but two regions show significant skewness:
+Orion~core has a smooth asymmetrical tail towards the blue,
+whereas NGC~346 has one towards the red.
 

### 2022-02-01 strucfunc_paper.tex
Finish section 3.1

@@
 calculated as described above in section~\ref{sec:spectr-datas}
-and after subtracting the mean systemic velocity in each case.
-The color scheme ranges from the most negative velocities in blue
-to the most positive velocities in red,
-but the amplitude of the velocity fluctuations differs considerably between regions,
-as indicated by the color scale bar on each map,
-ranging from \SI{\pm 7}{km.s^{-1}} for the Lagoon
-up to  \SI{\pm 40}{km.s^{-1}} for 30~Doradus.
-This is illustrated quantitatively in Figure~\ref{fig:hist},
-where the probability density function (PDF) of \(V_c\) for each region
-is shown on a common velocity scale and arranged in order of decreasing amplitude
-of velocity fluctuations.
-
-All of the distributions are significantly non-Gaussian
+and after subtracting the mean systemic velocity,
+\(\left\langle V_c\right\rangle\) in each case.
+% The color scheme ranges from the most negative velocities in blue
+% to the most positive velocities in red,
+% but the amplitude of the velocity fluctuations differs considerably between regions,
+% as indicated by the color scale bar on each map,
+% ranging from \SI{\pm 7}{km.s^{-1}} for the Lagoon
+% up to  \SI{\pm 40}{km.s^{-1}} for 30~Doradus.
+The overall amplitude of the plane-of-sky
+velocity fluctuations can be characterized by a dispersion,
+\(\sigma\pos\), defined as:
+\begin{equation}
+  \label{eq:sig-pos}
+  \sigma^2\pos =
+  \left\langle 
+  \bigl[ V_c (\xx_i) -\langle V_ c\rangle  \bigr]^2
+  \right \rangle ,
+\end{equation}
+where the average is performed over all observed points \(i\)
+in a given map.
+Note that \(\sigma\pos\) is also the RMS width of
+the probability density function (PDF) of \(V_c\).
+This PDF for each region is shown in Figure~\ref{fig:hist}
+on a common velocity scale and arranged in order of decreasing \(\sigma\pos\).
+It can be seen that the amplitude of the
+velocity fluctuations varies considerably between regions,
+with \(\sigma\pos\) in 30~Dor being more than 5 times higher than in 
+nearby regions such as Orion.
+
+All of the PDFs are significantly non-Gaussian
 and many show evidence of a multi-modal structure.
@@
 \label{sec:second-order-struct}
-One of the fundamental properties of turbulent clouds must be spatial fluctuations in velocity and density.                                     
-These fluctuations are observed as projected spatial fluctuations in the average line-of-sight velocity and integrated column density.
-It is possible to describe the statistical properties of these fluctuations if they are assumed as a product of a stochastic field \citep{1984ApJ...277..556S}. 
-This previous assumption give us the ability to apply statistical tools to the velocity field and the analysis of the velocity pattern is reduced to the calculation of the averages and correlations.
-
-The second-order structure function of the velocity centroids, $B(r)$, is defined as:
-%
+% One of the fundamental properties of turbulent clouds must be spatial fluctuations in velocity and density.                                     
+% These fluctuations are observed as projected spatial fluctuations in the average line-of-sight velocity and integrated column density.
+% It is possible to describe the statistical properties of these fluctuations if they are assumed as a product of a stochastic field \citep{1984ApJ...277..556S}. 
+% This previous assumption give us the ability to apply statistical tools to the velocity field and the analysis of the velocity pattern is reduced to the calculation of the averages and correlations.
+
+In order to probe the dependence of the velocity fluctuations
+on spatial scale,
+the primary tool that we employ is
+the second order structure function of differences in velocity centroids,
+$B(r)$, which is a function of the scalar separation or lag, \(r\),
+between two points on the plane of the sky:
+%
+\newcommand\Abs[1]{\vert #1\vert}
 \begin{equation}\label{eq:Br}
-  B(\boldsymbol{r}) = \dfrac{1}{N(\boldsymbol{r})}
-  \,
-  \sum_{\text{pairs}} \bigl[
-  V_{c}(\xx + \boldsymbol{r}) - V_{c}(\xx)
-  \bigr]^{2}
-\end{equation}
-%
-where $N(\boldsymbol{r})$ is the number of pair points at each separation \(\boldsymbol{r}\), called lag. 
-The variance of the centroid velocity fluctuations is:
-%
-\begin{equation}\label{eq:variance}
-\sigma^2  = \frac{1}{N} \sum_{\text{pixels}} \bigl[ V_c (\xx) -\langle V_ c\rangle  \bigr]^2
-\end{equation}
-%
-the, \(\langle V_c \rangle \) is the mean centroid velocity:
-%
-\begin{equation}\label{eq:mean}
-\langle V_c \rangle \  = \frac{1}{N} \sum_{\text{pixels}} V_c (\xx)
-\end{equation}
-%
-The summation in Equation \ref{eq:Br} is over all data pairs for each separation \(N(\boldsymbol{r})\).
-The summations in Equations \ref{eq:variance} and \ref{eq:mean} are over the total number of valid pixels in the (\textit{x},\textit{y})-plane.
+  B(r) = \left\langle 
+  \bigl[
+  V_{c}(\xx_j) - V_{c}(\xx_i)
+  \bigr]^{2} \right \rangle_{\Abs{\xx_j - \xx_i\!} \ \approx \ r} \ .
+\end{equation}
+The averaging is performed over all pairs of points
+\((i, j)\)
+whose scalar separation \(\Abs{\xx_j - \xx_i}\) is close to \(r\),
+irrespective of the orientation of the separation vector.
+In practice, we achieve this by binning the separations with a constant
+logarithmic width of \SI{0.15}{dex}.
+
+We will also employ the related quantity of the
+normalized spatial autocovariance or autocorrelation function:
+\begin{equation}
+  \label{eq:autocovar}
+  C(r) = \frac{1}{\sigma^2\pos}\left\langle 
+  \bigl[
+  V_{c}(\xx_j) \  V_{c}(\xx_i)
+  \bigr]^{2} \right \rangle_{\Abs{\xx_j - \xx_i\!} \ \approx \ r} \ .
+\end{equation}
+If the fluctuations are perfectly spatially homogeneous, then the
+two quantities are related \citep{1984ApJ...277..556S} as
+\begin{equation}\label{eq:functional}
+  B(r) = 2\sigma^2\pos \bigl[   1 - C(r)\bigr] .
+\end{equation}
+In less ideal situations, then \(B(r)\) is to be preferred since it is
+relatively unaffected by non-stationary effects \citep{1984ApJ...277..556S}.
+Nonetheless, \(C(r)\) is more amenable to heuristic reasoning in some cases,
+which we will take advantage of below.
 

### 2022-02-01 strucfunc_paper.tex
Updates from Overleaf

--- 2022-02-01 strucfunc_paper.tex
@@
 \subsection{Interpretation of the turbulent parameters and origins of interstellar turbulence}\label{sec:interpretation-origin}
+\textit{Note: Still working on this section}
+
+The structure function used in this work does not reveal the precise characteristic of turbulence, but the statistical results that it provides allow us to determine a distinction between correlated or random velocity fluctuations in the photoionized gas, in which the presence of correlations in the velocity field is a inherent property of turbulence.
+Although this work is not conclusive about the nature of photoionized gas turbulence and a precise description of the origin and implications of these turbulent motions is out of the scope of our investigation, we believe that the tools presented here (see section~\ref{sec:methods-apply}) guarantee a concise way for a comparison of a sample of different regions.
+The following sections addresses a vast series of turbulent problems that could be unravel, among other kinematical research, by expanding the sample of \hii{} regions.
 
@@
 It is unclear what are the mechanisms driving the turbulence, thought a lot of options are candidates.
-The main energy sources are, of the order of kpc, the differential rotations of the galaxy that produces shear at large scale, at scales of the order of hundreds of pc supernova explosions inject a large amount of kinetic energy, at scales of several tens of pc the expansion of \hii{} regions is also a source of energy and bipolar flows and jets inject energy at small scales, bouth one tent of a pc.
+The main energy sources are, of the order of kpc, the differential rotations of the galaxy that produces shear at large scale, at scales of the order of hundreds of pc supernova explosions inject a large amount of kinetic energy, at scales of several tens of pc the expansion of \hii{} regions is also a source of energy and bipolar flows, shocks, and jets inject energy at small scales, about one tenth of a pc.
+The velocity fluctuations are consequence of the combination of the various mechanism already mentioned and wouldn't be correct to attribute these fluctuations solely to one mechanism.
+The complexity of the extraction of pure turbulent motions from velocity profiles in nebulae is not just an observational problem, there is also the lack of precise information on how these mechanism contribute to the emission line broadening \citep{2011MNRAS.413..705L,arthur2016turbulence}.
+Many of the previous mechanisms, at least in some extent, affect all the \hii{} regions studied in this work.
+\cite{2011MNRAS.413..705L} also discuss the possibility of turbulent motions initiated by champagne flows and stellar winds.
+
+It is possible to consider from our sample the smallest and largest region for a comparison on the impact of the previous mechanism.
+The Orion core is affected by the stellar wind from \(\theta^1\) Ori C that will confine even the high ionization emission lines to a thick shell.
+Orion also present a champagne flow where the photoionized gas streams away from the ionization front.
+\citet{sabalisck1995supersonic} studied NGC 604 revealing that the kinematics of the region behave different considering different scales.
+High emission knots on the region encompasses supersonic global velocity dispersion values of 14 $<$ \(\sigma_{\text{los}}\) $<$ 20 km s\(^{-1}\).
+This knots are well fitted with Gaussian profiles thus, defining the kinematic core \citep{munoz1996}.
+A characteristic radius for them is \(\sim\) 7 pc.
+\citet{yang1996} identified 5 expanding shells within NGC 604, and one of them (Shell 3 on their paper) fall into our observations.
+This shells is 40 pc in diameter with an expansion velocity above 50 km s\(^{-1}\) in which the scales is related to the presence of strong stellar winds caused by the massive stars in the region.
+
+Although the Orion core and EON, and NGC 604 have different \(r_0\) is not clear if it truly reveal a concrete aspect of the energy input mechanism mentioned earlier.
+Orion mainly energy input comes from one star, meanwhile NGC 604 has more than 200 OB stars including WR stars. 
+The Orion core also presents Herbig-Haro objects, which aren't possible to resolve for more distant regions.
+Though the correlation length been particular to each region, and been correlated mainly with the size (see section~\ref{sec:scaling-relations}), it still needs further studies to reveal the true implication of this property.
 
@@
 
+%Luminosity vs centroid velocity dispersion
 The Figure \ref{fig:sigvsl} shows the log \(\sigma\pos\)-log \(\text{L}(\text{H}_{\alpha})\) plane.
@@
 
+%sigma pos vs sigma los
 The standard deviation of the velocity centroid and the mean non-thermal linewidth allow us to compare the relation between the kinematical disorder on the plane-of-the sky and along the line-of-sight  \citep{2011MNRAS.413..705L}.

### 2022-02-03 strucfunc_paper.tex
Begin rewrite of model strucfunc section

@@
 In less ideal situations, then \(B(r)\) is to be preferred since it is
-relatively unaffected by non-stationary effects \citep{1984ApJ...277..556S}.
+relatively unaffected by non-stationary effects
+such as large-scale linear gradients 
+\citep{1984ApJ...277..556S}.
 Nonetheless, \(C(r)\) is more amenable to heuristic reasoning in some cases,
@@
 
-\subsection{Application to our HII regions sample}\label{sec:methods-apply}
-
-The autocovariance function:
-
-\begin{equation}\label{eq:Cr}
-C(\boldsymbol{r}) = \dfrac{\sum_{\text{pairs}}[V_{c}(\xx + \boldsymbol{r}) \times V_{c}(\xx) ]} {N(\boldsymbol{r})}
-\end{equation}
-%
-is another statistical tool used in studying the turbulent flows.
-The interpretation of the Equation \ref{eq:Cr} depends on the assumption of homogeneity, which may be violated for astrophysical processes.
-Because of this, Equation \ref{eq:Br} is a better approach to characterize the velocity fluctuations even in the presence of large scale linear gradients and may be sensitive to a wider range of scales \citep{1984ApJ...277..556S}.
-
-For an homogeneous random field equations \ref{eq:Br} and \ref{eq:Cr} are related by:
-
-\begin{equation}\label{eq:functional}
-B(r) = 2\sigma^2 \bigl( 1 - C(r) \bigr)
-\end{equation}
-
-We use a new functional for the structure function based on equation \ref{eq:functional}. 
-First we propose a new \(C(r)\) in the form:
+\subsection{A heuristic model for the structure function}\label{sec:methods-apply}
+
+A common property of homogeneous fluctuating velocity fields is that neighboring points tend to have similar velocities
+(\(C(r) \approx 1\) for small \(r\)),
+whereas points that are far apart may have very different velocities
+(\(C(r) \ll 1\) for large \(r\)).
+The value of the separation that corresponds to
+the transition between these two regimes
+is called the correlation length, \(r_0\).
+In the simplest case,
+two points separated by \(r \gg r_0\) have totally uncorrelated velocities
+in the sense that knowledge of the velocity at the first point is of
+no help in predicting the velocity at the second point.
+At scales smaller than \(r_0\), the fluctuations often show a power-law behavior.
+
+We therefore propose the following 2-parameter model
+for the autocorrelation function:
 %
 \begin{equation}\label{eq:new-correlation-form}
-  C(r; r_0, m) = \exp \left[ -(\ln 2) \left( \frac{r}{r_0} \right)^m \right]
-\end{equation}
-%
+  C(r;\ r_0, m) = \exp \left[ -(\ln 2) \left( \frac{r}{r_0} \right)^m \right].
+\end{equation}
+%
+in which \(r_{0}\)\ is the correlation length (see above)
+and \(m\) is the power-law slope at small scales.
+This is constructed so that \(C(r) = 1/2\) at \(r = r_0\),
+while the exponential form ensures that \(C(r)\) rapidly approaches zero
+for larger separations.
+
 The term \(r_{0}\)\ is the correlation length where the value of separation \(r\) reach the value of \(\sigma^2\) in the structure function and $m$ is the power-law index that fits the inertial scale.

### 2022-02-08 Corr.tex
Javier changes 2022-02-07

--- 2022-01-26 Corr.tex
@@
 \hline
- log $\sigma$ &            log L(H) &   0.28 $\pm$ 0.1 &  -9.87 $\pm$ 3.66 &   0.85 &  0.002 \\
+ log $\sigma\pos$ &            log L(H) &   0.28 $\pm$ 0.1 &  -9.87 $\pm$ 3.66 &   0.85 &  0.002 \\
     log $r_0$ &             log $S$ &   0.73 $\pm$ 0.24 &  -1.17 $\pm$ 0.5 &   0.84 &  0.003 \\
- log $\sigma$ &  log $\sigma_{LOS}$ &   0.76 $\pm$ 0.48 &  -0.14 $\pm$ 0.54 &   0.66 &   0.04 \\
+% log $\sigma\pos$ &  log $\sigma_{\text{los}}$ &   0.76 $\pm$ 0.48 &  -0.14 $\pm$ 0.54 &   0.66 &   0.04 \\
       log $m$ &            log dist &  -0.11 $\pm$ 0.08 &   1.21 $\pm$ 0.16 &  -0.59 &   0.07 \\
- log $\sigma$ &         log $r_{0}$ &   0.22 $\pm$ 0.18 &   0.65 $\pm$ 0.12 &   0.55 &  0.10 \\
-      log $m$ &        log $\sigma$ &  -0.14 $\pm$ 0.24 &   0.11 $\pm$ 0.18 &  -0.42 &  0.22 \\
+ log $\sigma\pos$ &         log $r_{0}$ &   0.22 $\pm$ 0.18 &   0.65 $\pm$ 0.12 &   0.55 &  0.10 \\
+      log $m$ &        log $\sigma\pos$ &  -0.14 $\pm$ 0.24 &   0.11 $\pm$ 0.18 &  -0.42 &  0.22 \\
       log $m$ &         log $r_{0}$ &  -0.04 $\pm$ 0.08 &   0.01 $\pm$ 0.05 &  -0.39 &   0.27 \\

### 2022-02-08 strucfunc_paper.tex
Javier changes 2022-02-07

@@
 This was done to enhance the possibilities of a convergence since the structure function values at large separations are to follow the 2\(\sigma^2\) value according to theory.
-The light shaded areas in the plots show where the separation \(r\) is above half of the box size, \(L\), which is indicated with a vertical dotted line.
+The light shaded areas in the plots show where the separation \(r\) is above half of the box size \(L\), which is indicated with a vertical dotted line.
 
@@
 
-The results shown on left panels on Figures \ref{fig:strucfunc-fit-A}-\ref{fig:strucfunc-fit-D} show a typical second-order structure function pattern, where there is a series of ascending values of  \ref{eq:Br} that tends to stabilize around the 2\(\sigma^2\) value, indicating a loss in the correlations at large separations.
+The results shown on left panels on Figures \ref{fig:strucfunc-fit-A}-\ref{fig:strucfunc-fit-D} show a typical second-order structure function pattern, where there is a series of ascending values of  the structure function that tends to stabilize around the 2\(\sigma^2\) value, indicating a loss in the correlations at large separations.
 The Carina nebula and Hubble X follow this behavior.
 
-Since we are dealing with a sample of astronomical observations, it is thought that the values at large separations not following the previous pattern reflects movements that are not related to the ionized gas random motions.
+For astronomical observations it is thought that the values at large separations not following the previous pattern reflects movements that are not related to the ionized gas random motions.
 It is known that HII regions are created on the edge of molecular clouds, so they will reach a blister or champagne phase, introducing large-scale gradients \citep{Mivi1995}. 
@@
 Less common is the behavior where at large separations there are also a series of ascending values in the structure function, like the Lagoon nebula or NGC 346, or a periodic behavior like NGC 604.
-The reasons of this change on the structure function at large-scales is out of the scope of this investigation.
+The precise reasons of this change on the structure function at large-scales is out of the scope of this investigation.
 
@@
 
-\subsection{Turbulence}
+\subsection{Turbulence}\label{sec:turbulence-theory}
 
@@
 The structure function used in this work does not reveal the precise characteristic of turbulence, but the statistical results that it provides allow us to determine a distinction between correlated or random velocity fluctuations in the photoionized gas, in which the presence of correlations in the velocity field is a inherent property of turbulence.
-Although this work is not conclusive about the nature of photoionized gas turbulence and a precise description of the origin and implications of these turbulent motions is out of the scope of our investigation, we believe that the tools presented here (see section~\ref{sec:methods-apply}) guarantee a concise way for a comparison of a sample of different regions.
-The following sections addresses a vast series of turbulent problems that could be unravel, among other kinematical research, by expanding the sample of \hii{} regions.
+Although this work is not conclusive about the nature of photoionized gas turbulence and a precise description of the origin and implications of these turbulent motions is out of the scope of our investigation, we believe that the tools presented here (see section~\ref{sec:methods-apply}) guarantee a better approach to determine the structure function and a more concise way for a comparison of a sample of different regions.
+The following sections addresses a vast series of turbulent problems that could be unravel by expanding the sample, among more kinematical research of each \hii{} regions.
+
+\subsubsection{Correlation length \(r_0\)}
 
@@
 It is unclear what are the mechanisms driving the turbulence, thought a lot of options are candidates.
-The main energy sources are, of the order of kpc, the differential rotations of the galaxy that produces shear at large scale, at scales of the order of hundreds of pc supernova explosions inject a large amount of kinetic energy, at scales of several tens of pc the expansion of \hii{} regions is also a source of energy and bipolar flows, shocks, and jets inject energy at small scales, about one tenth of a pc.
+The main energy sources are, of the order of kpc, the differential rotations of the galaxy that produces shear at large scale, at scales of the order of hundreds of pc, supernova explosions inject a large amount of kinetic energy.
+At scales of several tens of pc the expansion of \hii{} regions is also a source of energy and bipolar flows, shocks, and jets inject energy at small scales, about one tenth of a pc.
+\cite{2011MNRAS.413..705L} also discuss the possibility of turbulent motions initiated by champagne flows and stellar winds. 
 The velocity fluctuations are consequence of the combination of the various mechanism already mentioned and wouldn't be correct to attribute these fluctuations solely to one mechanism.
 The complexity of the extraction of pure turbulent motions from velocity profiles in nebulae is not just an observational problem, there is also the lack of precise information on how these mechanism contribute to the emission line broadening \citep{2011MNRAS.413..705L,arthur2016turbulence}.
+
 Many of the previous mechanisms, at least in some extent, affect all the \hii{} regions studied in this work.
-\cite{2011MNRAS.413..705L} also discuss the possibility of turbulent motions initiated by champagne flows and stellar winds.
-
-It is possible to consider from our sample the smallest and largest region for a comparison on the impact of the previous mechanism.
-The Orion core is affected by the stellar wind from \(\theta^1\) Ori C that will confine even the high ionization emission lines to a thick shell.
+It is possible to consider from our sample the smallest and largest regions for a comparison on the impact of the previous mechanism.
+The Orion core is affected by the stellar wind from \(\theta^1\) Ori C \citep{2009AJ....137..367O} that will confine even the high ionization emission lines to a thick shell.
 Orion also present a champagne flow where the photoionized gas streams away from the ionization front.
 \citet{sabalisck1995supersonic} studied NGC 604 revealing that the kinematics of the region behave different considering different scales.
-High emission knots on the region encompasses supersonic global velocity dispersion values of 14 $<$ \(\sigma_{\text{los}}\) $<$ 20 km s\(^{-1}\).
-This knots are well fitted with Gaussian profiles thus, defining the kinematic core \citep{munoz1996}.
-A characteristic radius for them is \(\sim\) 7 pc.
-\citet{yang1996} identified 5 expanding shells within NGC 604, and one of them (Shell 3 on their paper) fall into our observations.
-This shells is 40 pc in diameter with an expansion velocity above 50 km s\(^{-1}\) in which the scales is related to the presence of strong stellar winds caused by the massive stars in the region.
+High emission knots on the region encompasses supersonic global velocity dispersion values of 14 $<$ \(\sigma_{\text{los}}\) $<$ \SI{20}{km.s^{-1}} with a characteristic radius of \(\sim\)\SI{7}{pc} and a Gaussian profile.
+Values of velocity dispersion $>$\SI{20}{km.s^{-1}} are found in low emission cavities where the lines present strong asymmetries.
+These cavities were identified as expanding shells \citep{yang1996} with diameters of \(\sim\)\SI{40}{pc} and a expansion velocity above \SI{50}{km.s^{-1}}
 
@@
 The Orion core also presents Herbig-Haro objects, which aren't possible to resolve for more distant regions.
-Though the correlation length been particular to each region, and been correlated mainly with the size (see section~\ref{sec:scaling-relations}), it still needs further studies to reveal the true implication of this property.
+Though the correlation length is particular to each region, and it is correlated mainly with the size (see section~\ref{sec:scaling-relations}), it still needs further studies to reveal the true implication of this value with respect the energy input mechanisms.
+
+\subsubsection{Structure function power-law index \(m\)}\label{sec:powe-index}
 
 The index \(m\) is shown in the last column of Table \ref{tab:Res} and is commonly used as a reference for comparison between observations and the theoretic value of 0.67 (equation \ref{eq:velocity-moments}).
-
-\subsubsection{Projection smearing}\label{sec:projection-smearing}
-
-As a justification for the use of the structure function we can consider that any relation between the line width and line-of-sight depth can be interpreted in terms of a correlation between velocity spread and scale size.
-This follows that if we have an optically thin spectral line where it will have a width which is related to the total radial velocity dispersion of all fluctuations sampled along the line-of-sight \citep{1984ApJ...277..556S}.
-In these sense the structure function is used as a tool to investigate the projection of a three-dimensional correlation function onto the plane of sky \citep{arthur2016turbulence}.
-
-It have been mentioned that the projection of the velocity fluctuations reduces the actual amplitude in the line-of-sight \citep{1984ApJ...277..556S,arthur2016turbulence}.
-We can see from Table \ref{tab:Res} that the line-of-sight velocity dispersion is roughly twice the plane-of-sky velocity dispersion.
-In the case of homogeneous turbulent velocity we can consider the effect of \textit{project smearing} \citep{1984ApJ...277..556S}, where the projection from three to two dimensions over the line-of-sight depth \(H\), reduces the plane-of-sky amplitude for the condition \(r_{0} < H\).
-With a value of \(\sigma\pos / \sigma_{\text{los}}\) = 0.5 we obtain \(r_{0} / H \sim\) 0.02-0.1.
+All indices are above this theoretic value and the interpretation of this difference is that the analyzed regions do not comply with the properties established in the development of the turbulence theory.
+
+From section~\ref{sec:regions-milky-way} we know that most of all assumption mentioned in section~\ref{sec:turbulence-theory} are not meet for our \hii{} region sample.
+\hii{} regions emerged from a molecular cloud with highly filamentary and clumpy density structure .
+There is a large increase in the temperature because of the photoionization and the density gradients with the pressure gradients accelerate the flow which occurs in multiple scale consequences of the fractal nature of the molecular cloud \citep{arthur2016turbulence}.
+This would result in a inhomogeneous structure characteristic of \hii{ } regions as it is possible to observe in Figure~\ref{fig:hii-regions}.
+The incompressible and subsonic conditions in the flow are clearly not meet since there is evidence of the presence of shock fronts and supersonic velocity values.
+This a a consequences of the inhomogeneous structure mentioned in the paragraph above and other processes as O star winds and radiation pressure which would also aid in the stirring of the gas.
+And as \hii{} regions are regarded as three-dimensional objects there is also the possibility of a sheet-like distribution which could overcome this assumption.
+
+For all these reason is expected that \hii{} regions power-law indices do not follow the classic 0.67 value.
+But despite the complex nature of \hii{} regions we observe a common pattern for the structure function and the value of the index falls in a certain limited range of values
+
+%\subsubsection{Projection smearing}\label{sec:projection-smearing}
+%As a justification for the use of the structure function we can consider that any relation between the line width and line-of-sight depth can be interpreted in terms of a correlation between velocity spread and scale size.
+%This follows that if we have an optically thin spectral line where it will have a width which is related to the total radial velocity dispersion of all fluctuations sampled along the line-of-sight \citep{1984ApJ...277..556S}.
+%In these sense the structure function is used as a tool to investigate the projection of a three-dimensional correlation function onto the plane of sky \citep{arthur2016turbulence}.
+
+%It have been mentioned that the projection of the velocity fluctuations reduces the actual amplitude in the line-of-sight \citep{1984ApJ...277..556S,arthur2016turbulence}.
+%We can see from Table \ref{tab:Res} that the line-of-sight velocity dispersion is roughly twice the plane-of-sky velocity dispersion.
+%In the case of homogeneous turbulent velocity we can consider the effect of \textit{project smearing} \citep{1984ApJ...277..556S}, where the projection from three to two dimensions over the line-of-sight depth \(H\), reduces the plane-of-sky amplitude for the condition \(r_{0} < H\).
+%With a value of \(\sigma\pos / \sigma_{\text{los}}\) = 0.5 we obtain \(r_{0} / H \sim\) 0.02-0.1.
 
@@
 Following the procedure by \cite{arthur2016turbulence} and assuming the relationship \(m_{2D} - 1 < m_{3D}\ < m_{2D}\) we have 0.54 \(< m_{3D} <\) 0.72.
+
+\subsubsection{Relationship between plane-of-sky and line-of-sight velocity dispersion.}
+
+%sigma pos vs sigma los
+The standard deviation of the velocity centroid and the mean non-thermal linewidth allow us to compare the relation between the kinematical disorder on the plane-of-the sky and along the line-of-sight  \citep{2011MNRAS.413..705L}.
+
+The broad in the velocity width of the emission line represents the range of velocities along the line-of-sight.%, among thermal movements. 
+We can consider as a main broadening mechanisms the kinematical disorder along the LOS related to velocity gradients by the clumpiness on the molecular cloud and turbulent movements.
+On the plane-of-sky the consequences of those gradients and movements is measured in every pixel. 
+The spatial variations on the velocity field would depend on the targeted pixel, depending on the motions inside the cloud (the LOS component).
+This reasoning has lead to \citet{2011MNRAS.413..705L} to propose a direct relationship between \(\sigma_{\text{LOS}}\) and \(\sigma\pos\).
+
+%The Figure \ref{fig:svss} shows the log \(\sigma\)-log \(\sigma_{\text{los}}\) plane with a relationship of \(\log \sigma\pos = (0.76 \pm 0.48) \log \sigma_{\text{los}}-(0.14 \pm 0.54)\).
 
@@
 The results are shown in Table \ref{tab:RestStats} in ascending order for the p-value.
-In the Figures \ref{fig:rvsR}-\ref{fig:svss} we show the correlations with a significance level  $p < $0.05.
+In the Figures \ref{fig:rvsR} and \ref{fig:sigvsl} we show the correlations with a significance level  $p < $0.05.
 In all the figures the slope of the fit shown in solid black line is the mean of all red lines that reflect the posterior of the Bayessian analysis.
@@
 
-%\subsubsection{Relationship between plane-of-sky and line-of-sight velocity dispersion.}
-%Note 26/01/22: Expand and polish from here
-
-%sigma pos vs sigma los
-The standard deviation of the velocity centroid and the mean non-thermal linewidth allow us to compare the relation between the kinematical disorder on the plane-of-the sky and along the line-of-sight  \citep{2011MNRAS.413..705L}.
-
-The broad in the velocity width of the emission line represents the range of velocities along the line-of-sight.%, among thermal movements. 
-We can consider as a main broadening mechanisms the kinematical disorder along the LOS related to velocity gradients by the clumpiness on the molecular cloud and turbulent movements.
-On the plane-of-sky the consequences of those gradients and movements is measured in every pixel. 
-The spatial variations on the velocity field would depend on the targeted pixel, depending on the motions inside the cloud (the LOS component).
-This reasoning has lead to \citet{2011MNRAS.413..705L} to propose a direct relationship between \(\sigma_{\text{LOS}}\) and \(\sigma\pos\).
-
-The Figure \ref{fig:svss} shows the log \(\sigma\)-log \(\sigma_{\text{los}}\) plane with a relationship of \(\log \sigma\pos = (0.76 \pm 0.48) \log \sigma_{\text{los}}-(0.14 \pm 0.54)\).
-
 \input{Corr}
@@
 
-\begin{figure}
-\centering 
-\includegraphics[width=3in]{Figures/svss.pdf}
-\caption{Same as Fig. \ref{fig:rvsR} but for the log $\sigma$-log $\sigma_{\text{LOS}}$ plane. The dotted line represents slope equal to unity.}
-\label{fig:svss}
-\end{figure}
+%\begin{figure}
+%\centering 
+%\includegraphics[width=3in]{Figures/svss.pdf}
+%\caption{Same as Fig. \ref{fig:rvsR} but for the log $\sigma$-log $\sigma_{\text{LOS}}$ plane. The dotted line represents slope equal to unity.}
+%\label{fig:svss}
+%\end{figure}
 

### 2022-02-08 strucfunc_paper.tex
Describe different regimes of structure function

@@
 \usepackage{multicol}
-
+\usepackage{enumerate}          % Better lists
 \usepackage{xcolor}
@@
 
-\subsection{A heuristic model for the structure function}\label{sec:methods-apply}
+\subsection{A heuristic model for the structure function}
+\label{sec:methods-apply}
 
@@
 
+In order to capture these two behaviors,
 We therefore propose the following 2-parameter model
@@
 for larger separations.
-
-The term \(r_{0}\)\ is the correlation length where the value of separation \(r\) reach the value of \(\sigma^2\) in the structure function and $m$ is the power-law index that fits the inertial scale.
-In an idealized case at scales larger than \(r_{0}\)\ the structure function flattens as it tends towards the asymptotic value of 2\(\sigma^2\) \citep{arthur2016turbulence}.
-This substitutes the previously \(C(r) = 1/[1+(r/r_{0})^{m}]\) from \citet{1966igd..book.....K} and
-\citet{1984ApJ...277..556S}.
+We use equation \eqref{eq:functional} to determine the structure function
+from this model autocorrelation function.
+The resultant model structure function has the following properties:
+\begin{enumerate}[1.]
+ \item Small scales: \(B(r) \propto r^m\) for \(r \ll r_0\);
+ \item Correlation scale: \(B(r_0) = \sigma^2\);
+ \item Large scales: \(B(r) \to 2 \sigma^2\) for \(r \gg r_0\).
+\end{enumerate}
+In a previous paper, we used a different functional form
+\citetext{See Fig.~13 of \citealp{arthur2016turbulence}}:
+\(C(r) = 1/[1+(r/r_{0})^{m}]\), as proposed in \citet{1984ApJ...277..556S},
+which behaves identically to equation~\eqref{eq:new-correlation-form}
+in the first two regimes, but is more gradual in its approach
+to the large-scale asymptote of \(2 \sigma^2\).
+However, we find that equation~\eqref{eq:new-correlation-form}
+provides a much improved fit to the observed structure functions
+of our sample regions.
+
+% The term \(r_{0}\)\ is the correlation length where the value of separation \(r\) reach the value of \(\sigma^2\) in the structure function and $m$ is the power-law index that fits the inertial scale.
+% In an idealized case at scales larger than \(r_{0}\)\ the structure function flattens as it tends towards the asymptotic value of 2\(\sigma^2\) \citep{arthur2016turbulence}.
+% This substitutes the previously \(C(r) = 1/[1+(r/r_{0})^{m}]\) from \citet{1966igd..book.....K} and
+% \citet{1984ApJ...277..556S}.
+
+\subsection{Effects of observational limitations}
+\label{sec:effect-observ-limit}
 
@@
 In some cases this procedure keeps going up to large scales, giving two or more inertial regimes leading to an erroneous interpretation of multiple inertial scales.
+
+\subsection{Limitations of the model structure function}
+\label{sec:limit-model-struct}
 

### 2022-02-08 strucfunc_paper.tex
Add some discussion of the largest scales

@@
 In order to capture these two behaviors,
-We therefore propose the following 2-parameter model
+We therefore propose the following idealized 2-parameter model
 for the autocorrelation function:
@@
 provides a much improved fit to the observed structure functions
-of our sample regions.
+of our sample regions (see following section).
 
@@
 
-\subsection{Effects of observational limitations}
+\subsubsection{Effects of observational limitations}
 \label{sec:effect-observ-limit}
@@
 
-\subsection{Limitations of the model structure function}
+\subsubsection{Additional effects omitted from the model structure function}
 \label{sec:limit-model-struct}
+
+For separations that are comparable to the diameter \(D\) of the \hii{} region,
+then the supposition of homogeneity must break down.
+For instance, if the amplitude of the velocity fluctuations is higher
+in the core of the region than in the outskirts,
+then the autocorrelation function will be U-shaped
+since all separations with \(r > D/2\) must be between two points in the outskirts,
+which will tend to be relatively well correlated simply because both velocities
+will be close to the mean.
+This yields a corresponding downturn in the structure function at the largest scales.
+
+Another example is if there were a periodic velocity fluctuation,
+with spatial wavelength \(\lambda\),
+then the autocorrelation function would become negative for \(r \approx \lambda/2, 3 \lambda / 2, \dots\),
+which yields periodic peaks in the structure function.
+Neither of these effects can be captured by our model structure function,
+which assumes that the autocorrelation is strictly positive
+and monotonically decreasing with \(r\).
+
+At the very smallest scales, the autocorrelation function is predicted to
+scale quadratically with \(r\)
 

### 2022-02-11 strucfunc_paper.tex
Javier changes 2022-02-11

@@
 Less common is the behavior where at large separations there are also a series of ascending values in the structure function, like the Lagoon nebula or NGC 346, or a periodic behavior like NGC 604.
-The precise reasons of this change on the structure function at large-scales is out of the scope of this investigation.
 
@@
 The main energy sources are, of the order of kpc, the differential rotations of the galaxy that produces shear at large scale, at scales of the order of hundreds of pc, supernova explosions inject a large amount of kinetic energy.
-At scales of several tens of pc the expansion of \hii{} regions is also a source of energy and bipolar flows, shocks, and jets inject energy at small scales, about one tenth of a pc.
-\cite{2011MNRAS.413..705L} also discuss the possibility of turbulent motions initiated by champagne flows and stellar winds. 
+At scales of several tens of pc the expansion of \hii{} regions and stellar winds are also a source of energy and bipolar flows, shocks,jets and champagne flows inject energy at small scales, about one tenth of a pc.
 The velocity fluctuations are consequence of the combination of the various mechanism already mentioned and wouldn't be correct to attribute these fluctuations solely to one mechanism.
@@
 
-The index \(m\) is shown in the last column of Table \ref{tab:Res} and is commonly used as a reference for comparison between observations and the theoretic value of 0.67 (equation \ref{eq:velocity-moments}).
-All indices are above this theoretic value and the interpretation of this difference is that the analyzed regions do not comply with the properties established in the development of the turbulence theory.
+The index \(m\) shown in the last column of Table \ref{tab:Res} is used for comparison between observations and the theoretical value of 0.67 (equation \ref{eq:velocity-moments}).
+All our indices are above this theoretical value and this is attributed to the fact that the analyzed regions do not comply with the assumptions established in the development of the turbulent theory.
 
@@
 \hii{} regions emerged from a molecular cloud with highly filamentary and clumpy density structure .
-There is a large increase in the temperature because of the photoionization and the density gradients with the pressure gradients accelerate the flow which occurs in multiple scale consequences of the fractal nature of the molecular cloud \citep{arthur2016turbulence}.
-This would result in a inhomogeneous structure characteristic of \hii{ } regions as it is possible to observe in Figure~\ref{fig:hii-regions}.
-The incompressible and subsonic conditions in the flow are clearly not meet since there is evidence of the presence of shock fronts and supersonic velocity values.
-This a a consequences of the inhomogeneous structure mentioned in the paragraph above and other processes as O star winds and radiation pressure which would also aid in the stirring of the gas.
-And as \hii{} regions are regarded as three-dimensional objects there is also the possibility of a sheet-like distribution which could overcome this assumption.
-
-For all these reason is expected that \hii{} regions power-law indices do not follow the classic 0.67 value.
-But despite the complex nature of \hii{} regions we observe a common pattern for the structure function and the value of the index falls in a certain limited range of values
-
-%\subsubsection{Projection smearing}\label{sec:projection-smearing}
-%As a justification for the use of the structure function we can consider that any relation between the line width and line-of-sight depth can be interpreted in terms of a correlation between velocity spread and scale size.
-%This follows that if we have an optically thin spectral line where it will have a width which is related to the total radial velocity dispersion of all fluctuations sampled along the line-of-sight \citep{1984ApJ...277..556S}.
-%In these sense the structure function is used as a tool to investigate the projection of a three-dimensional correlation function onto the plane of sky \citep{arthur2016turbulence}.
-
-%It have been mentioned that the projection of the velocity fluctuations reduces the actual amplitude in the line-of-sight \citep{1984ApJ...277..556S,arthur2016turbulence}.
-%We can see from Table \ref{tab:Res} that the line-of-sight velocity dispersion is roughly twice the plane-of-sky velocity dispersion.
+There is a large increase in the temperature because of the photoionization and the density gradients with the pressure gradients accelerate the flow which occurs in multiple scale, consequence of the fractal nature of the molecular cloud \citep{arthur2016turbulence}.
+The radiation pressure, stellar winds and region expansion, among other physical processes would create pressure-driven shock waves propagating faster than the speed of sound in the medium.
+This would regard conditions in \hii{} regions as compressible and supersonic.
+And as \hii{} regions are regarded as three-dimensional objects there is the possibility of a sheet-like distribution which could overcome this assumption.
+%This would result in a inhomogeneous density structure where arcs, filaments and shells are characteristic of \hii{ } regions as we can see from Figure~\ref{fig:hii-regions}.
+
+But despite the complex nature of \hii{} regions we observe a common pattern for the structure function and the value of the index we obtain falls in a certain limited range of values. 
+The differences with respect the theoretical value are often used as a diagnostic tools to identify properties that are not consider in the assumptions of the turbulence theory.
+
+For the comparison between the two-dimensional structure function and the three-dimensional structure function relationships between the power-law were proposed:
+
+\begin{equation}\label{eq:projection-smearing-3d}
+m_{2D}= m_{3D} + 1
+\end{equation}
+%
+or when the astronomical object is almost two-dimensional (sheet-like):
+%
+\begin{equation}\label{eq:projection-smearing-2d}
+m_{2D} \sim m_{3D}
+\end{equation}
+
+As a conclusion, if the extension of the HII region is compared with its depth (three-dimensional case) the value of the index is 1.6. 
+While the case where the extension is much greater than its depth (two-dimensional case) the region will have a value of 0.6 \citep{von1951methode, munch1958internal,1987ApJ...317..686O}.
+
+%We can compute the \(m_{3D}\) index from the two dimensional \(m\), if we assume that the \(m_{3D}\) index lies between the limits of projection smoothing and a sheet-like distribution. 
+%Following the procedure by \cite{arthur2016turbulence} and assuming the relationship \(m_{2D} - 1 < m_{3D}\ < m_{2D}\) we have 0.54 \(< m_{3D} <\) 0.72.
+
+\subsubsection{Relationship between plane-of-sky and line-of-sight velocity dispersion.}
+
+%The broad in the velocity width of the emission line represents the range of velocities along the line-of-sight.%, among thermal movements. 
+%We can consider as a main broadening mechanisms the kinematical disorder along the LOS related to %velocity gradients by the clumpiness on the molecular cloud and turbulent movements.
+%On the plane-of-sky the consequences of those gradients and movements is measured in every pixel. 
+%The spatial variations on the velocity field would depend on the targeted pixel, depending on the motions inside the cloud (the LOS component).
+%This reasoning has lead to \citet{2011MNRAS.413..705L} to propose a direct relationship between \(\sigma_{\text{LOS}}\) and \(\sigma\pos\).
+
+As a justification for the use of the structure function we can consider that any relation between the line width and line-of-sight depth can be interpreted in terms of a correlation between velocity spread and scale size.
+This follows that if we have an optically thin spectral line where it will have a width which is related to the total radial velocity dispersion of all fluctuations sampled along the line-of-sight \citep{1984ApJ...277..556S}.
+In these sense the structure function is used as a tool to investigate the projection of a three-dimensional correlation function onto the plane of sky \citep{arthur2016turbulence}.
+
+The standard deviation of the velocity centroid, \(\sigma\pos\), and the mean non-thermal linewidth, \(\sigma_{\text{LOS}}\), allow us to compare the relation between the kinematical disorder on the plane-of-the sky and along the line-of-sight  \citep{2011MNRAS.413..705L}.
+It have been mentioned that the projection of the velocity fluctuations reduces the actual amplitude in the line-of-sight \citep{1984ApJ...277..556S,arthur2016turbulence}.
+
+We can see from Table \ref{tab:Res} that the line-of-sight velocity dispersion is roughly twice the plane-of-sky velocity dispersion.
+
 %In the case of homogeneous turbulent velocity we can consider the effect of \textit{project smearing} \citep{1984ApJ...277..556S}, where the projection from three to two dimensions over the line-of-sight depth \(H\), reduces the plane-of-sky amplitude for the condition \(r_{0} < H\).
 %With a value of \(\sigma\pos / \sigma_{\text{los}}\) = 0.5 we obtain \(r_{0} / H \sim\) 0.02-0.1.
-
-For the comparison between the two-dimensional structure function and the three-dimensional structure function relationships between the power-law were proposed:
-
-\begin{equation}\label{eq:projection-smearing-3d}
-m_{2D}= m_{3D} + 1
-\end{equation}
-
-or when the astronomical object is almost two-dimensional (sheet-like) we have:
-
-\begin{equation}\label{eq:projection-smearing-2d}
-m_{2D} \sim m_{3D}
-\end{equation}
-
-If the extension of the HII region is compared with its depth (three-dimensional case) the value of the index is 1.6. 
-While the case where the extension is much greater than its depth (two-dimensional case) the region will have a value of 0.6 \citep{von1951methode, munch1958internal,1987ApJ...317..686O}.
-
-We can compute the \(m_{3D}\) index from the two dimensional \(m\), if we assume that the \(m_{3D}\) index lies between the limits of projection smoothing and a sheet-like distribution. 
-Following the procedure by \cite{arthur2016turbulence} and assuming the relationship \(m_{2D} - 1 < m_{3D}\ < m_{2D}\) we have 0.54 \(< m_{3D} <\) 0.72.
-
-\subsubsection{Relationship between plane-of-sky and line-of-sight velocity dispersion.}
-
-%sigma pos vs sigma los
-The standard deviation of the velocity centroid and the mean non-thermal linewidth allow us to compare the relation between the kinematical disorder on the plane-of-the sky and along the line-of-sight  \citep{2011MNRAS.413..705L}.
-
-The broad in the velocity width of the emission line represents the range of velocities along the line-of-sight.%, among thermal movements. 
-We can consider as a main broadening mechanisms the kinematical disorder along the LOS related to velocity gradients by the clumpiness on the molecular cloud and turbulent movements.
-On the plane-of-sky the consequences of those gradients and movements is measured in every pixel. 
-The spatial variations on the velocity field would depend on the targeted pixel, depending on the motions inside the cloud (the LOS component).
-This reasoning has lead to \citet{2011MNRAS.413..705L} to propose a direct relationship between \(\sigma_{\text{LOS}}\) and \(\sigma\pos\).
-
-%The Figure \ref{fig:svss} shows the log \(\sigma\)-log \(\sigma_{\text{los}}\) plane with a relationship of \(\log \sigma\pos = (0.76 \pm 0.48) \log \sigma_{\text{los}}-(0.14 \pm 0.54)\).
 

### 2022-02-13 strucfunc_paper.tex
Minor change
Add figure for the model structure function

@@
 
+\begin{figure*}
+ \centering
+ \includegraphics[width=\linewidth]{Figures/model-strucfunc-annotated}\par
+ \caption{
+   A model structure function for homogeneous fluctuations.
+   (a)~Idealized structure function (blue line) and effects
+   of observational limitations at small and large scales.
+   (b)~Examples of inhomogeneous effects at large scales,
+   which are not included in the model structure function.
+ }
+ \label{fig:model-strucfunc}
+\end{figure*}
+
 A common property of homogeneous fluctuating velocity fields is that neighboring points tend to have similar velocities
@@
 For separations that are comparable to the diameter \(D\) of the \hii{} region,
-then the supposition of homogeneity must break down.
+then the supposition of homogeneity may break down.
 For instance, if the amplitude of the velocity fluctuations is higher

### 2022-02-18 strucfunc_paper.tex
Javier changes 2022-02-17

@@
 
-We present our second-order structure results plotted against separation in parsecs and the posteriors of the parameters used in the analysis.
+We present our second-order structure results plotted against separation in parsecs and the posteriors of the parameters used in the analysis we describes in the previous section.
 
@@
   \includegraphics[width=0.8\linewidth]{Figures/strucfunc-fit-B}
-  \label{fig:strucfunc-fit-B}
-  \caption{Second-order structure functions for the velocity centroid images of the \(H\alpha\) emission line}
+  \caption{Second-order structure functions for the velocity centroid images of the \(H\alpha\) emission line}\label{fig:strucfunc-fit-B}
 \end{figure*}
@@
 
-These mathematical techniques were first applied to astronomical observations by \citet{von1951methode} and \citet{munch1958internal} allowing to determine a distinction between homogeneous turbulence and pure random velocity fluctuations in the Orion Nebula.
-
 \subsection{Interpretation of the turbulent parameters and origins of interstellar turbulence}\label{sec:interpretation-origin}
@@
 
-The structure function used in this work does not reveal the precise characteristic of turbulence, but the statistical results that it provides allow us to determine a distinction between correlated or random velocity fluctuations in the photoionized gas, in which the presence of correlations in the velocity field is a inherent property of turbulence.
-Although this work is not conclusive about the nature of photoionized gas turbulence and a precise description of the origin and implications of these turbulent motions is out of the scope of our investigation, we believe that the tools presented here (see section~\ref{sec:methods-apply}) guarantee a better approach to determine the structure function and a more concise way for a comparison of a sample of different regions.
-The following sections addresses a vast series of turbulent problems that could be unravel by expanding the sample, among more kinematical research of each \hii{} regions.
+In the next sections we discuss the use and interpretation of the turbulent parameters we obtain in the previous section.
+Also, we mentioned some physical processes that contribute to stirring the ionized gas and the possibility that they are responsible for the observed velocity fluctuations.
 
@@
 Ideally the correlation length \(r_0\) should represent the scale of dominant energy injection.
-It is unclear what are the mechanisms driving the turbulence, thought a lot of options are candidates.
+It is unclear what are the precise mechanisms driving the turbulence, thought a lot of options are candidates.
+The most probable scenario is that the velocity fluctuations are consequence of the combination of various mechanism.
 The main energy sources are, of the order of kpc, the differential rotations of the galaxy that produces shear at large scale, at scales of the order of hundreds of pc, supernova explosions inject a large amount of kinetic energy.
-At scales of several tens of pc the expansion of \hii{} regions and stellar winds are also a source of energy and bipolar flows, shocks,jets and champagne flows inject energy at small scales, about one tenth of a pc.
-The velocity fluctuations are consequence of the combination of the various mechanism already mentioned and wouldn't be correct to attribute these fluctuations solely to one mechanism.
-The complexity of the extraction of pure turbulent motions from velocity profiles in nebulae is not just an observational problem, there is also the lack of precise information on how these mechanism contribute to the emission line broadening \citep{2011MNRAS.413..705L,arthur2016turbulence}.
-
-Many of the previous mechanisms, at least in some extent, affect all the \hii{} regions studied in this work.
-It is possible to consider from our sample the smallest and largest regions for a comparison on the impact of the previous mechanism.
-The Orion core is affected by the stellar wind from \(\theta^1\) Ori C \citep{2009AJ....137..367O} that will confine even the high ionization emission lines to a thick shell.
-Orion also present a champagne flow where the photoionized gas streams away from the ionization front.
-\citet{sabalisck1995supersonic} studied NGC 604 revealing that the kinematics of the region behave different considering different scales.
-High emission knots on the region encompasses supersonic global velocity dispersion values of 14 $<$ \(\sigma_{\text{los}}\) $<$ \SI{20}{km.s^{-1}} with a characteristic radius of \(\sim\)\SI{7}{pc} and a Gaussian profile.
+At scales of several tens of pc the expansion of \hii{} regions and stellar winds are a source of energy and, bipolar flows, shocks, jets and champagne flows inject energy at small scales about one tenth of a pc.
+The lack of precise information on how these mechanism contribute to the emission line broadening make a non-trivial task to determine at what extent they play a role in the interstellar turbulence, contributing to the complexity of the extraction of pure turbulent motions from velocity profiles in nebulae \citep{2011MNRAS.413..705L,arthur2016turbulence}.
+
+Many of these mechanisms, at some extent, affect all the \hii{} regions studied in this work.
+We can use the kinematic analysis of the regions to investigate how previously identified energy injection mechanisms could be related to the correlation length.
+
+\citet{2009AJ....137..367O} present a three-dimensional study of the dynamic structure of the Orion nebula.
+The high-velocity stellar wind from \(\theta^1\) Ori C will confine the ionized gas, even the high ionization emission lines, to a thick shell.
+In one direction, at a distance of \SI{0.1}{pc} from the massive star a stationary shell of shocked material is formed when the ram pressure of the photoevaportation flow balances the thermal pressure of the shocked wind.
+In the other direction there is a free flow of the hypersonic wind.
+At a smaller scale of \SI{0.02}{pc} there is an interaction between the closest proplyd photoevaporation flow and the stellar wind which results in bowshocks.
+According to \citet{2001ApJ...561..830G} the influence of stellar wind interactions is restricted to the central 0.05 pc. 
+Orion also present a champagne flow where the photoionized gas streams away from the ionization front covering a distance of \(\sim\)\SI{1}{pc} from the molecular cloud \citep{1973ApJ...183..863Z}.
+
+Our correlation length results for the Orion Core and EON from table~\ref{tab:Res} despite been close to the scales mentioned above still aren't conclusive enough to determine a direct relation between them.
+As mentioned in \citet{arthur2016turbulence} the mechanism mentioned in the previous paragraph would play a secondary role in stirring up the gas motions and it would be necessary to determine if the velocity fluctuations arise from pure turbulent motion inside the ionized clouds or a consequences of density and brightness fluctuations.
+
+\citet{sabalisck1995supersonic} studied NGC 604 revealing that the high emission knots on the region encompasses supersonic global velocity dispersion values of 14 $<$ \(\sigma_{\text{los}}\) $<$ \SI{20}{km.s^{-1}}.
+This knots have a characteristic radius of \(\sim\)\SI{7}{pc} and a Gaussian profile.
 Values of velocity dispersion $>$\SI{20}{km.s^{-1}} are found in low emission cavities where the lines present strong asymmetries.
-These cavities were identified as expanding shells \citep{yang1996} with diameters of \(\sim\)\SI{40}{pc} and a expansion velocity above \SI{50}{km.s^{-1}}
-
-Although the Orion core and EON, and NGC 604 have different \(r_0\) is not clear if it truly reveal a concrete aspect of the energy input mechanism mentioned earlier.
+These cavities were identified as expanding shells by \cite{yang1996} with diameters of \(\sim\)\SI{40}{pc} and a expansion velocity above \SI{50}{km.s^{-1}}.
+According to table~\ref{tab:Res} the correlation length for NGC 604 is close to the scale of the bright knots in the region which aren't related to a particular energy injection mechanism.
+
+Although the Orion core and EON, and NGC 604 have different \(r_0\) is not clear if it truly reveal a concrete aspect of the energy input mechanism mentioned above.
 Orion mainly energy input comes from one star, meanwhile NGC 604 has more than 200 OB stars including WR stars. 
@@
 The index \(m\) shown in the last column of Table \ref{tab:Res} is used for comparison between observations and the theoretical value of 0.67 (equation \ref{eq:velocity-moments}).
-All our indices are above this theoretical value and this is attributed to the fact that the analyzed regions do not comply with the assumptions established in the development of the turbulent theory.
+All our indices are above this theoretical value and this is attributed to the fact that the \hii{} regions do not comply with the assumptions established in the development of the turbulent theory.
 
@@
 \hii{} regions emerged from a molecular cloud with highly filamentary and clumpy density structure .
-There is a large increase in the temperature because of the photoionization and the density gradients with the pressure gradients accelerate the flow which occurs in multiple scale, consequence of the fractal nature of the molecular cloud \citep{arthur2016turbulence}.
+There is a large increase in the temperature because of the photoionization, and the density gradients with the pressure gradients accelerate the flow which occurs on multiple scales consequence of the fractal nature of the molecular cloud \citep{arthur2016turbulence}.
 The radiation pressure, stellar winds and region expansion, among other physical processes would create pressure-driven shock waves propagating faster than the speed of sound in the medium.
-This would regard conditions in \hii{} regions as compressible and supersonic.
-And as \hii{} regions are regarded as three-dimensional objects there is the possibility of a sheet-like distribution which could overcome this assumption.
-%This would result in a inhomogeneous density structure where arcs, filaments and shells are characteristic of \hii{ } regions as we can see from Figure~\ref{fig:hii-regions}.
-
-But despite the complex nature of \hii{} regions we observe a common pattern for the structure function and the value of the index we obtain falls in a certain limited range of values. 
+This would make the flow compressible and supersonic in \hii{} regions.
+Also, as \hii{} regions are three-dimensional objects our structure function results comes from a projection of this three-dimensional structure to a two-dimensional velocity field.
+But despite the complex nature of \hii{} regions and observational limitations we obtain a common pattern for the structure function and the value of the power-law index falls in a certain limited range of values.
 The differences with respect the theoretical value are often used as a diagnostic tools to identify properties that are not consider in the assumptions of the turbulence theory.
 
-For the comparison between the two-dimensional structure function and the three-dimensional structure function relationships between the power-law were proposed:
-
-\begin{equation}\label{eq:projection-smearing-3d}
+To study the projection of a three-dimensional structure function to a two-dimensional structure function, known as projection smoothing \citep{von1951methode, munch1958internal,1987ApJ...317..686O}, relationships between the power-law indices were proposed:
+
+\begin{equation}\label{eq:projection-smoothing-3d}
 m_{2D}= m_{3D} + 1
@@
 %
-or when the astronomical object is almost two-dimensional (sheet-like):
-%
-\begin{equation}\label{eq:projection-smearing-2d}
+and  when the astronomical object present a sheet-like distribution of emitters we have the relation:
+%
+\begin{equation}\label{eq:projection-smoothing-2d}
 m_{2D} \sim m_{3D}
@@
 As a conclusion, if the extension of the HII region is compared with its depth (three-dimensional case) the value of the index is 1.6. 
-While the case where the extension is much greater than its depth (two-dimensional case) the region will have a value of 0.6 \citep{von1951methode, munch1958internal,1987ApJ...317..686O}.
-
-%We can compute the \(m_{3D}\) index from the two dimensional \(m\), if we assume that the \(m_{3D}\) index lies between the limits of projection smoothing and a sheet-like distribution. 
-%Following the procedure by \cite{arthur2016turbulence} and assuming the relationship \(m_{2D} - 1 < m_{3D}\ < m_{2D}\) we have 0.54 \(< m_{3D} <\) 0.72.
-
-\subsubsection{Relationship between plane-of-sky and line-of-sight velocity dispersion.}
-
-%The broad in the velocity width of the emission line represents the range of velocities along the line-of-sight.%, among thermal movements. 
-%We can consider as a main broadening mechanisms the kinematical disorder along the LOS related to %velocity gradients by the clumpiness on the molecular cloud and turbulent movements.
-%On the plane-of-sky the consequences of those gradients and movements is measured in every pixel. 
-%The spatial variations on the velocity field would depend on the targeted pixel, depending on the motions inside the cloud (the LOS component).
-%This reasoning has lead to \citet{2011MNRAS.413..705L} to propose a direct relationship between \(\sigma_{\text{LOS}}\) and \(\sigma\pos\).
+While the case where the extension is much greater than its depth (two-dimensional case) the region will have a value of 0.6 .
+
+The mean value \(m\) of our sample is \(\sim\)1. 
+Following the equation \ref{eq:projection-smoothing-3d} the \hii{} regions in our sample with \(m >\) 1 would present a depth which is in the order of magnitude comparable to the length of the observed box size \(L\) been closest to this value as \(m\) tends to 1.6.
+On the other hand, \hii{} regions with values \(m <\) 1 would present a thinner structure as they tend to the value of 0.6.
+This analysis should not be regarded as conclusive about the true structure of the regions and would require further observations with a combination of kinematics analysis to determine the best way to determine the depth of each region.
+As we show in section \ref{sec:sigmapos-vs-sigmalos} the ratio between \(\sigma\pos\) and \(\sigma_{\text{los}}\) can also be used to give an idea of the depth o the region.
+
+Deviations from the Kolmogorov model are expected in \hii{} regions as the photoionized flow in their interior has a different nature as the flows upon the theory is constructed. 
+Also magnetic fields would play a very important role in the dynamics of the gas motions.
+Despite these differences is clear that the self-similarity motions is a common behavior conserved at scales from parsecs to hundreds of parsecs. 
+With the advanced of the observational capabilities with more computational power for a better understanding of turbulent motions the gap between theory and observations is hoped to be reduced.
+
+\subsubsection{Relationship between plane-of-sky and line-of-sight velocity dispersion}\label{sec:sigmapos-vs-sigmalos}
 
 As a justification for the use of the structure function we can consider that any relation between the line width and line-of-sight depth can be interpreted in terms of a correlation between velocity spread and scale size.
-This follows that if we have an optically thin spectral line where it will have a width which is related to the total radial velocity dispersion of all fluctuations sampled along the line-of-sight \citep{1984ApJ...277..556S}.
+If we have an optically thin spectral line where it will have a width which is related to the total radial velocity dispersion of all fluctuations sampled along the line-of-sight \citep{1984ApJ...277..556S}.
+The standard deviation of the velocity centroid, \(\sigma\pos\), and the mean non-thermal linewidth, \(\sigma_{\text{los}}\), allow us to compare the relation between the kinematical disorder on the plane-of-the sky and along the line-of-sight  \citep{2011MNRAS.413..705L}.
 In these sense the structure function is used as a tool to investigate the projection of a three-dimensional correlation function onto the plane of sky \citep{arthur2016turbulence}.
 
-The standard deviation of the velocity centroid, \(\sigma\pos\), and the mean non-thermal linewidth, \(\sigma_{\text{LOS}}\), allow us to compare the relation between the kinematical disorder on the plane-of-the sky and along the line-of-sight  \citep{2011MNRAS.413..705L}.
-It have been mentioned that the projection of the velocity fluctuations reduces the actual amplitude in the line-of-sight \citep{1984ApJ...277..556S,arthur2016turbulence}.
-
-We can see from Table \ref{tab:Res} that the line-of-sight velocity dispersion is roughly twice the plane-of-sky velocity dispersion.
-
-%In the case of homogeneous turbulent velocity we can consider the effect of \textit{project smearing} \citep{1984ApJ...277..556S}, where the projection from three to two dimensions over the line-of-sight depth \(H\), reduces the plane-of-sky amplitude for the condition \(r_{0} < H\).
-%With a value of \(\sigma\pos / \sigma_{\text{los}}\) = 0.5 we obtain \(r_{0} / H \sim\) 0.02-0.1.
+We can consider as a main broadening mechanisms the kinematical disorder along the LOS related to velocity gradients by the clumpiness on the molecular cloud and turbulent movements.
+On the plane-of-sky the consequences of those gradients and movements is measured in every pixel. 
+The spatial variations on the velocity field would depend on the targeted pixel, depending on the motions inside the cloud.
+This reasoning has lead to  propose a relationship between \(\sigma_{\text{los}}\) and \(\sigma\pos\) \citep{2011MNRAS.413..705L}.
+
+In the Figure~\ref{fig:los-vs-pos} that the line-of-sight velocity dispersion is roughly twice the plane-of-sky velocity dispersion.
+In the case of homogeneous turbulent velocity we can consider the effect of \textit{project smearing} \citep{1984ApJ...277..556S}, where the projection from three to two dimensions over the line-of-sight depth \(H\), reduces the plane-of-sky amplitude for the condition \(r_{0} < H\).
+With a value of \(\sigma\pos / \sigma_{\text{los}}\) = 0.5 we obtain \(r_{0} / H \sim\) 0.02 - 0.1.
+This procedure implies depths of the order 10 to 50 times.
+In the lower limit \citet{arthur2016turbulence} mentioned the inconsistency for Orion since evidence has show that the emitting layer thickness is of the order of 0.01 - 0.3 pc.
+For the most distant regions the previous analysis would give depths of the order of magnitude of the observational box, but considering the analysis using the power-law index (section~\ref{sec:powe-index}) only NGC 595 would comply to this three dimensional structure.
+
+\begin{figure}
+\centering 
+\includegraphics[width=3in]{Figures/los-vs-pos}
+\caption{The $\sigma$-$\sigma_{\text{los}}$ plane. The dotted line represents slope equal to unity.}
+\label{fig:los-vs-pos}
+\end{figure}
 
@@
 The results are shown in Table \ref{tab:RestStats} in ascending order for the p-value.
-In the Figures \ref{fig:rvsR} and \ref{fig:sigvsl} we show the correlations with a significance level  $p < $0.05.
+In the Figures \ref{fig:sigvsl} and \ref{fig:rvsR} we show the correlations with a significance level  $p < $0.05.
 In all the figures the slope of the fit shown in solid black line is the mean of all red lines that reflect the posterior of the Bayessian analysis.
@@
 \centering 
+\includegraphics[width=3in]{Figures/svsL}
+\caption{The log \(\sigma\pos\) - log $L(H_{\alpha})$ plane derived form our results an data in the literature.
+A fit with slope of 0.27 $\pm$ 0.1 is shown in solid black line that is the mean of all red lines that reflect the posterior of the Bayessian analysis.
+}
+\label{fig:sigvsl}
+\end{figure}
+
+\begin{figure}
+\centering 
 \includegraphics[width=3in]{Figures/rvsS}
-\caption{The log \(r_0\) - log \(S\) plane derived form our results an data in the literature.
-A fit with slope of 0.67 $\pm$ 0.07 is shown in solid black line that is the mean of all red lines that reflect the posterior of the Bayessian analysis.
-}
+\caption{Same as Fig. \ref{fig:rvsR} but for the log \(r_0\) - log \(S\) plane. }
 \label{fig:rvsR}
 \end{figure}
-
-\begin{figure}
-\centering 
-\includegraphics[width=3in]{Figures/svsL}
-\caption{Same as Fig. \ref{fig:rvsR} but for the log $\sigma$-log $L(H_{\alpha})$ plane.}
-\label{fig:sigvsl}
-\end{figure}
-
-%\begin{figure}
-%\centering 
-%\includegraphics[width=3in]{Figures/svss.pdf}
-%\caption{Same as Fig. \ref{fig:rvsR} but for the log $\sigma$-log $\sigma_{\text{LOS}}$ plane. The dotted line represents slope equal to unity.}
-%\label{fig:svss}
-%\end{figure}
 
@@
 In Section \ref{sec:methods-apply} we mentioned the reduced chi-square method we are using for the determination of the correlation length and the index of the slope.
-Since this is the first time this method is applied to a sample of HII regions (at least for our knowledge), our results are bounded to be different from previous investigations, including the one that have the same observations as \citet{arthur2016turbulence} and \citet{2019arXiv191203543M}.
+Since this is the first time this method is applied to a sample of HII regions (at least for our knowledge), our results are bounded to be different from previous investigations, including the one that have the same observations as \citet{arthur2016turbulence} and \citet{Melnick:2021x}.
 
@@
 
-The first attempt at characterizing turbulence in a giant extragalactic HII region, GEHR, was done by \citet{1961MNRAS.122....1F} with the 30 Doradus complex in the LMC, finding no indication of turbulent motions between scale of 10 and 100 pc.
+The first attempt at characterizing turbulence in a giant extragalactic HII region, GEHR, was done by \citet{1961MNRAS.122....1F} with the 30 Doradus complex, finding no indication of turbulent motions between scale of 10 and 100 pc.
+These result is consistent with Fig. \ref{fig:strucfunc-fit-B}a showing that the turbulent motions are correlated at scales \(<\) \SI{5}{pc}.
 \citet{Melnick:2021x} also investigated the structure function in 30 Doradus finding on their results that the structure function is entirely flat on scales from 3 to 200 pc.
-In the context of the high-resolution observations it is possible to see why their results do not reflect the turbulent structure of the nebula; their observations cover a region where the large-scale velocity fluctuations are uncorrelated.
-There is a good agreement with the single-Gaussian fit results from \citet{2019arXiv191203543M} (Figure 15 Top on their work), while \citet{1961MNRAS.122....1F} results do not overlap with ours.
-From this analysis this is the first time turbulence characterized in 30 Doradus using the structure function.
-
-There is broad agreement in our structure function results and previous studies that consider NGC 604, mainly because where are using the same data \citep{Medina-Tanco:1997a, Melnick:2021x}.
-From \citet{Medina-Tanco:1997a} and \citet{Melnick:2021x}, and using the same TAURUS-II data.
+In the context of the high-resolution observations it is possible to see why their results do not reflect the turbulent structure of the nebula as their observations cover a region where the large-scale velocity fluctuations are uncorrelated as in the case of \citet{1961MNRAS.122....1F}.
+From the observations where are using this is the first time turbulence characterized in 30 Doradus using the structure function.
+
+For NGC 604 there is good agreement in our structure function results and previous studies because where are using the same TAURUS-II data as \citet{Melnick:2021x} and \citet{Medina-Tanco:1997a}.
 Despite this general agreement the interpretations in each study is different.
 \citet{Medina-Tanco:1997a} conclude about a double regime acting on the kinetic energy spectrum.
-According to this double cascading, turbulence is being forced at scales of \(\approx\)10 pc while and energy cascade has developed down to the smallest scales and other, as an inverse cascade, extends up to scale of \(\approx\)70 pc.
-Interesting enough, \citet{Medina-Tanco:1997a} mentioned various characteristic scale lengths, the most notorious is the \(\approx\)10 pc, a value close to our correlation length of \(\approx\)9 pc, and they interpret it as possible source on energy associated with the expansion of shocks coming from wind bubbles.
+According to this double cascade, turbulence is being forced at scales of \(\approx\) \SI{00}{pc} while and energy cascade has developed down to the smallest scales and other, as an inverse cascade, extends up to scale of \(\approx\) \SI{70}{pc}.
+\citet{Medina-Tanco:1997a} mentioned different characteristic scale lengths, the most notorious is the \(\approx\)10 pc, a value close to our correlation length of \(\approx\)9 pc, and they interpret it as possible source on energy associated with the expansion of shocks coming from wind bubbles.
+\citet{Melnick:2021x} addresses some issues with TAURUS II data while comparing profiles between the previous instrument TAURUS I where there exist a difference between observations (see section 4.1 on their paper).
+They mentioned that one problem with \citet{Medina-Tanco:1997a} structure function is that they didn't take into account the observational seeing.
+This would invalidate they results and \citet{Melnick:2021x} consider that taking out the structure function values that fall in this range would make the structure function flat and scales \(<\)\SI{10}{pc}.
+Finally they point out, and we agree, the importance of observing NGC 604 at higher spatial resolution, so they rule out \citet{Medina-Tanco:1997a} results. 
+Our Fig. \ref{fig:strucfunc-fit-C}e shows in fact that there is a velocity structure in NGC 604. 
+We have prove that a consistent and more precise method in analyzing structure function is key to obtaining trustworthy results.
 None of the previous studies present a power-law index for the structure function to compare our results.
-\citet{Melnick:2021x} addresses some issues with TAURUS II data while comparing profiles between the previous instrument TAURUS I where there exist a difference between observations (see section 4.1 on their paper).
-As we agree with them in the importance of observing NGC 604 at higher spatial resolution, we have prove that a consistent method in analyzing structure function is key to obtaining trustworthy results.
-
-For our NGC 595 \halpha\ emission line results there is no correspondence in the structure function between our results and previous investigations.
-Our observations cover the brightest part of the region and have smaller resolution.
-\citet{lagrois2009multi} and \citet{lagrois2011} structure functions results does not cover scales $<$10 pc, where in our results the correlation is taking place.
-\citet{lagrois2011} used the data from \citet{lagrois2009multi} to complement the structure function analysis with the auto correlation function and filters to the velocity field to get rid of non-turbulent movements.
-Their sigma is 5.92$\pm$0.15 km/s with a correlation length is 43 pc and the power-law index they provide is 1.55$\pm$0.01.
-
+
+For our NGC 595 \halpha\ emission line results there is no correspondence in the structure function from the previous investigations of \citet{lagrois2009multi} and \citet{lagrois2011}.
+Our observations cover the brightest part of the region and have smaller resolution than theirs.
+As a consequence \citet{lagrois2009multi} and \citet{lagrois2011} structure functions results does not cover scales $<$10 pc, where in our results the correlation is taking place.
+One big difference is that \citet{lagrois2011} apply a  filter to the velocity field to get rid of non-turbulent movements.
+As a comparison for the filtered turbulent parameters they present a correlation length of 43 pc and the power-law index they provide is 1.55 $\pm$ 0.01.
+Other difference in their methodology is that they use the normalized structure function value of 2 to obtain the correlation length.
+Using their unfiltered data the correlation length is \(\sim\) \SI{90}{pc} and using the same criteria as our it is \(\sim\) \SI{40}{pc} and the slope would be shallower. 
+Their velocity centroid \(\sigma\) is 5.92 $\pm$ 0.15 km s\(^{-1}\) while we have 7.48 $\pm$ 1.4 km s\(^{-1}\) which is consistent.
+Due to the different observations and methodologies a comparison between structure functions is not possible.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-This proposed analysis can be expanded to other HII regions with the possibility of comparing the results between them since the method guarantees homogeneity and the ability to develop a future catalog of these regions in a coherent way.
+The structure function used in this work does not reveal the precise characteristic of turbulence, but the statistical results that it provides allow us to determine a distinction between correlated or random velocity fluctuations in the photoionized gas, in which the presence of correlations in the velocity field is a inherent property of turbulence.
+Although this work is not conclusive about the nature of photoionized gas turbulence and a precise description of the origin and implications of these turbulent motions is out of the scope of our investigation, we believe that the tools presented here (see section~\ref{sec:methods-apply}) guarantee a more realistic approach to determine and understand the structure function.
+
+Our analysis can be expanded to other HII regions with the possibility of comparing the results between them since the method guarantees homogeneity and the ability to develop a future catalog of these regions in a coherent way.
 It could even be used to investigate the velocity fields of other phases of the interstellar medium.
@@
 
-\begin{enumerate}
-\item For 30 Doradus with an observational box size of 32 pc an index of 0.84$\pm$0.03 is obtained with an inertial scale between 0.1 and 5 pc, and with a variance of 350$\pm$21 km$^2$/s$^2$.
-
-\item For NGC 604 with an observational box size of 173 pc an index of 0.82$\pm$0.20 is obtained with an inertial scale between 2 and 9 pc, and with a variance of 81$\pm$25 km$^2$/s$^2$.
-
-\item For NGC 595 with an observational box size of 196 pc an index of 1.3$\pm$0.04 is obtained with an inertial scale between 0.5 and 12 pc, and with a variance of 56$\pm$1.6 km$^2$/s$^2$.
-
-\item For NGC 346 with an observational box size of 20 pc an index of 0.78$\pm$0.02 is obtained with an inertial scale between 0.06 and 2 pc, and with a variance of 38$\pm$1.0 km$^2$/s$^2$.
-
-\item For Orion with an observational box size of 0.45 pc an index of 1.06$\pm$0.02 is obtained with an inertial scale between 0.002 and 0.09 pc, and with a variance of 17$\pm$1.0 km$^2$/s$^2$.
-
-\item For Carina with an observational box size of 20 pc an index of 1.36$\pm$0.30 is obtained with an inertial scale between 0.008 and 0.6 pc, and with a variance of 17$\pm$1.0 km$^2$/s$^2$.
-
-\item For Hubble X with an observational box size of 78 pc an index of 0.94$\pm$0.12 is obtained with an inertial scale between 0.5 and 4 pc, and with a variance of 15.5$\pm$1.5 km$^2$/s$^2$.
-
-\item For Hubble V with an observational box size of 61 pc an index of 0.72$\pm$0.09 is obtained with an inertial scale between 0.5 and 3 pc, and with a variance of 10.6$\pm$0.8 km$^2$/s$^2$.
-
-\item For Lagoon with an observational box size of 16 pc an index of 1.12$\pm$0.09 is obtained with an inertial scale between 0.005 and 1 pc, and with a variance of 7.2$\pm$0.8 km$^2$/s$^2$.
-
-\end{enumerate}
+%\begin{enumerate}
+%\item For 30 Doradus with an observational box size of 32 pc an index of 0.84$\pm$0.03 is obtained with an inertial scale between 0.1 and 5 pc, and with a variance of 350$\pm$21 km$^2$/s$^2$.
+
+%\item For NGC 604 with an observational box size of 173 pc an index of 0.82$\pm$0.20 is obtained with an inertial scale between 2 and 9 pc, and with a variance of 81$\pm$25 km$^2$/s$^2$.
+
+%\item For NGC 595 with an observational box size of 196 pc an index of 1.3$\pm$0.04 is obtained with an inertial scale between 0.5 and 12 pc, and with a variance of 56$\pm$1.6 km$^2$/s$^2$.
+
+%\item For NGC 346 with an observational box size of 20 pc an index of 0.78$\pm$0.02 is obtained with an inertial scale between 0.06 and 2 pc, and with a variance of 38$\pm$1.0 km$^2$/s$^2$.
+
+%\item For Orion with an observational box size of 0.45 pc an index of 1.06$\pm$0.02 is obtained with an inertial scale between 0.002 and 0.09 pc, and with a variance of 17$\pm$1.0 km$^2$/s$^2$.
+
+%\item For Carina with an observational box size of 20 pc an index of 1.36$\pm$0.30 is obtained with an inertial scale between 0.008 and 0.6 pc, and with a variance of 17$\pm$1.0 km$^2$/s$^2$.
+
+%\item For Hubble X with an observational box size of 78 pc an index of 0.94$\pm$0.12 is obtained with an inertial scale between 0.5 and 4 pc, and with a variance of 15.5$\pm$1.5 km$^2$/s$^2$.
+
+%\item For Hubble V with an observational box size of 61 pc an index of 0.72$\pm$0.09 is obtained with an inertial scale between 0.5 and 3 pc, and with a variance of 10.6$\pm$0.8 km$^2$/s$^2$.
+
+%\item For Lagoon with an observational box size of 16 pc an index of 1.12$\pm$0.09 is obtained with an inertial scale between 0.005 and 1 pc, and with a variance of 7.2$\pm$0.8 km$^2$/s$^2$.
+
+%\end{enumerate}
 

### 2022-02-18 strucfunc_paper.tex
Expand caption for the model strucfunc figure

@@
  \caption{
-   A model structure function for homogeneous fluctuations.
-   (a)~Idealized structure function (blue line) and effects
-   of observational limitations at small and large scales.
+   Example of the model structure function for homogeneous fluctuations,
+   together with a realization of the corresponding velocity field
+   on a \(512 \times 512\) pixel grid.  
+   (a)~Idealized structure function (blue line)
+   for the parameters \(m = 1\) and \(r_0 = \SI{64}{pixels}\).
+   Red and green lines show the effects of observational limitations
+   at small scales (seeing and noise)
+   and at large scales (finite-map effects).
    (b)~Examples of inhomogeneous effects at large scales,
@@
  \item Small scales: \(B(r) \propto r^m\) for \(r \ll r_0\);
- \item Correlation scale: \(B(r_0) = \sigma^2\);
- \item Large scales: \(B(r) \to 2 \sigma^2\) for \(r \gg r_0\).
+ \item Correlation scale: \(B(r_0) = \sigma\pos^2\);
+ \item Large scales: \(B(r) \to 2 \sigma\pos^2\) for \(r \gg r_0\).
  \end{enumerate}
+An example is shown by the blue line in Figure~\ref{fig:model-strucfunc}a.
+
 In a previous paper, we used a different functional form
@@
 in the first two regimes, but is more gradual in its approach
-to the large-scale asymptote of \(2 \sigma^2\).
+to the large-scale asymptote of \(2 \sigma\pos^2\).
 However, we find that equation~\eqref{eq:new-correlation-form}

### 2022-02-18 strucfunc_paper.tex
Use new versions of strucfunc figures
and split them up into one figure per source

@@
 
+\newcommand\sffig[1]{%
+  \begin{tabular}{@{}ll@{}}
+    (a)& (b)\\
+    \includegraphics[width=0.45\linewidth]{Figures/sf-emcee-#1}
+       &  \includegraphics[width=0.45\linewidth]{Figures/corner-emcee-#1}
+  \end{tabular}%
+}
+
 \begin{figure*}
   \centering
-  \includegraphics[width=0.8\linewidth]{Figures/strucfunc-fit-A}
-  \caption{Second-order structure functions for the velocity centroid images of the \(H\alpha\) emission line}\label{fig:strucfunc-fit-A}
+  \sffig{OrionS}
+  \caption{
+    Second-order structure functions for the velocity centroid images of the \(H\alpha\) emission line from Orion core region.
+  }
+  \label{fig:strucfunc-fit-OrionS}
 \end{figure*}
-
 \begin{figure*}
   \centering
-  \includegraphics[width=0.8\linewidth]{Figures/strucfunc-fit-B}
-  \caption{Second-order structure functions for the velocity centroid images of the \(H\alpha\) emission line}\label{fig:strucfunc-fit-B}
+  \sffig{M8}
+  \caption{
+    Same as figure~\ref{fig:strucfunc-fit-OrionS} except for the Lagoon Nebula. 
+  }
+  \label{fig:strucfunc-fit-M8}
 \end{figure*}
-
 \begin{figure*}
   \centering
-  \includegraphics[width=0.8\linewidth]{Figures/strucfunc-fit-C}
-  \caption{Second-order structure functions for the velocity centroid images of the \(H\alpha\) emission line}\label{fig:strucfunc-fit-C}
+  \sffig{CarC}
+  \caption{
+    Same as figure~\ref{fig:strucfunc-fit-OrionS} except for the Carina Nebula. 
+  }
+  \label{fig:strucfunc-fit-CarC}
 \end{figure*}
@@
   \centering
-  \includegraphics[width=0.8\linewidth]{Figures/strucfunc-fit-D}
-  \caption{Second-order structure functions for the velocity centroid images of the \(H\alpha\) emission line}\label{fig:strucfunc-fit-D}
+  \sffig{N346}
+  \caption{
+    Same as figure~\ref{fig:strucfunc-fit-OrionS} except for the NGC~346 nebula in the SMC. 
+  }
+  \label{fig:strucfunc-fit-N346}
 \end{figure*}
+\begin{figure*}
+  \centering
+  \sffig{Dor}
+  \caption{
+    Same as figure~\ref{fig:strucfunc-fit-OrionS} except for the 30~Doradus nebula in the LMC Nebula. 
+  }
+  \label{fig:strucfunc-fit-Dor}
+\end{figure*}
+
+\begin{figure*}
+  \centering
+  \sffig{HV}
+  \caption{
+    Same as figure~\ref{fig:strucfunc-fit-OrionS} except for the Hubble~V nebula.
+  }
+  \label{fig:strucfunc-fit-HV}
+\end{figure*}
+\begin{figure*}
+  \centering
+  \sffig{HX}
+  \caption{
+    Same as figure~\ref{fig:strucfunc-fit-OrionS} except for the Hubble~X nebula.
+  }
+  \label{fig:strucfunc-fit-HX}
+\end{figure*}
+
+\begin{figure*}
+  \centering
+  \sffig{N595}
+  \caption{
+    Same as figure~\ref{fig:strucfunc-fit-OrionS} except for the NGC~595 nebula.
+  }
+  \label{fig:strucfunc-fit-N595}
+\end{figure*}
+\begin{figure*}
+  \centering
+  \sffig{N604H}
+  \caption{
+    Same as figure~\ref{fig:strucfunc-fit-OrionS} except for the NGC~604 nebula.
+  }
+  \label{fig:strucfunc-fit-N604H}
+\end{figure*}
+
+\begin{figure*}
+  \centering
+  \sffig{OrionLH}
+  \caption{
+    Same as figure~\ref{fig:strucfunc-fit-OrionS} except for the extended Orion Nebula.
+  }
+  \label{fig:strucfunc-fit-OrionLH}
+\end{figure*}
+
+% \begin{figure*}
+%   \centering
+%   \includegraphics[width=0.8\linewidth]{Figures/strucfunc-fit-A}
+%   \caption{Second-order structure functions for the velocity centroid images of the \(H\alpha\) emission line}\label{fig:strucfunc-fit-A}
+% \end{figure*}
+
+% \begin{figure*}
+%   \centering
+%   \includegraphics[width=0.8\linewidth]{Figures/strucfunc-fit-B}
+%   \caption{Second-order structure functions for the velocity centroid images of the \(H\alpha\) emission line}\label{fig:strucfunc-fit-B}
+% \end{figure*}
+
+% \begin{figure*}
+%   \centering
+%   \includegraphics[width=0.8\linewidth]{Figures/strucfunc-fit-C}
+%   \caption{Second-order structure functions for the velocity centroid images of the \(H\alpha\) emission line}\label{fig:strucfunc-fit-C}
+% \end{figure*}
+
+% \begin{figure*}
+%   \centering
+%   \includegraphics[width=0.8\linewidth]{Figures/strucfunc-fit-D}
+%   \caption{Second-order structure functions for the velocity centroid images of the \(H\alpha\) emission line}\label{fig:strucfunc-fit-D}
+% \end{figure*}
 

### 2022-02-18 strucfunc_paper.tex
Fix example strucfunc figure and references to observed figures

@@
 
-Figures \ref{fig:strucfunc-fit-A}-\ref{fig:strucfunc-fit-D} left panels show in solid and open blue circles the observational structure function that we compute using equation \ref{eq:Br} on the \ha{} velocity fields of Fig.
+Figures \ref{fig:strucfunc-fit-OrionS}-\ref{fig:strucfunc-fit-OrionLH} left panels show in solid and open blue circles the observational structure function that we compute using equation \ref{eq:Br} on the \ha{} velocity fields of Fig.
 \ref{fig:velocity-maps}.
@@
 
-Figures \ref{fig:strucfunc-fit-A}-\ref{fig:strucfunc-fit-D} right panels show the corner plots \citep{2017ascl.soft02002F} of the turbulent parameters and observational constraints. 
+Figures \ref{fig:strucfunc-fit-OrionS}-\ref{fig:strucfunc-fit-OrionLH} right panels show the corner plots \citep{2017ascl.soft02002F} of the turbulent parameters and observational constraints. 
 These plots shows the one and two dimensional projections of the posterior probability distributions of the parameters used in equation \ref{eq:chi}.
@@
 
-The results shown on left panels on Figures \ref{fig:strucfunc-fit-A}-\ref{fig:strucfunc-fit-D} show a typical second-order structure function pattern, where there is a series of ascending values of  the structure function that tends to stabilize around the 2\(\sigma^2\) value, indicating a loss in the correlations at large separations.
+The results shown on left panels on Figures \ref{fig:strucfunc-fit-OrionS}-\ref{fig:strucfunc-fit-OrionLH} show a typical second-order structure function pattern, where there is a series of ascending values of  the structure function that tends to stabilize around the 2\(\sigma^2\) value, indicating a loss in the correlations at large separations.
 The Carina nebula and Hubble X follow this behavior.
@@
 The first attempt at characterizing turbulence in a giant extragalactic HII region, GEHR, was done by \citet{1961MNRAS.122....1F} with the 30 Doradus complex, finding no indication of turbulent motions between scale of 10 and 100 pc.
-These result is consistent with Fig. \ref{fig:strucfunc-fit-B}a showing that the turbulent motions are correlated at scales \(<\) \SI{5}{pc}.
+These result is consistent with Fig. \ref{fig:strucfunc-fit-Dor} showing that the turbulent motions are correlated at scales \(<\) \SI{5}{pc}.
 \citet{Melnick:2021x} also investigated the structure function in 30 Doradus finding on their results that the structure function is entirely flat on scales from 3 to 200 pc.
@@
 Finally they point out, and we agree, the importance of observing NGC 604 at higher spatial resolution, so they rule out \citet{Medina-Tanco:1997a} results. 
-Our Fig. \ref{fig:strucfunc-fit-C}e shows in fact that there is a velocity structure in NGC 604. 
+Our Fig. \ref{fig:strucfunc-fit-N604H} shows in fact that there is a velocity structure in NGC 604. 
 We have prove that a consistent and more precise method in analyzing structure function is key to obtaining trustworthy results.

### 2022-02-22 Corr.tex
Javier changes 2022-02-22

--- 2022-01-26 Corr.tex
@@
 \hline
- log $\sigma$ &            log L(H) &   0.28 $\pm$ 0.1 &  -9.87 $\pm$ 3.66 &   0.85 &  0.002 \\
-    log $r_0$ &             log $S$ &   0.73 $\pm$ 0.24 &  -1.17 $\pm$ 0.5 &   0.84 &  0.003 \\
- log $\sigma$ &  log $\sigma_{LOS}$ &   0.76 $\pm$ 0.48 &  -0.14 $\pm$ 0.54 &   0.66 &   0.04 \\
-      log $m$ &            log dist &  -0.11 $\pm$ 0.08 &   1.21 $\pm$ 0.16 &  -0.59 &   0.07 \\
- log $\sigma$ &         log $r_{0}$ &   0.22 $\pm$ 0.18 &   0.65 $\pm$ 0.12 &   0.55 &  0.10 \\
-      log $m$ &        log $\sigma$ &  -0.14 $\pm$ 0.24 &   0.11 $\pm$ 0.18 &  -0.42 &  0.22 \\
-      log $m$ &         log $r_{0}$ &  -0.04 $\pm$ 0.08 &   0.01 $\pm$ 0.05 &  -0.39 &   0.27 \\
+ log $\sigma$ &            log L(H) &   0.29 $\pm$ 0.09 &  -10.24 $\pm$ 3.53 &   0.89 &  0.001 \\
+    log $r_0$ &             log $S$ &   0.78 $\pm$ 0.25 &   -1.31 $\pm$ 0.52 &   0.85 &  0.002 \\
+% log $\sigma$ &  log $\sigma_{LOS}$ &   0.83 $\pm$ 0.48 &   -0.24 $\pm$ 0.56 &   0.71 &   0.02 \\
+ log $\sigma$ &         log $r_{0}$ &   0.21 $\pm$ 0.17 &    0.66 $\pm$ 0.12 &   0.58 &   0.08 \\
+      log $m$ &            log Dist &  -0.09 $\pm$ 0.07 &    1.14 $\pm$ 0.14 &  -0.57 &   0.09 \\
+      log $m$ &        log $\sigma$ &  -0.11 $\pm$ 0.21 &    0.07 $\pm$ 0.16 &  -0.42 &   0.23 \\
+      log $m$ &         log $r_{0}$ &  -0.04 $\pm$ 0.07 &    -0.0 $\pm$ 0.05 &  -0.39 &   0.26 \\
 \bottomrule

### 2022-02-22 strucfunc_paper.tex
Javier changes 2022-02-22

@@
 
-We present our second-order structure results plotted against separation in parsecs and the posteriors of the parameters used in the analysis we describes in the previous section.
+We present the second-order structure results plotted against separation in parsecs and the posteriors of the turbulent parameters.
 
@@
 
+%structure functions plots descriptions
 Figures \ref{fig:strucfunc-fit-OrionS}-\ref{fig:strucfunc-fit-OrionLH} left panels show in solid and open blue circles the observational structure function that we compute using equation \ref{eq:Br} on the \ha{} velocity fields of Fig.
@@
 
+%corner plots descriptions
 Figures \ref{fig:strucfunc-fit-OrionS}-\ref{fig:strucfunc-fit-OrionLH} right panels show the corner plots \citep{2017ascl.soft02002F} of the turbulent parameters and observational constraints. 
@@
 
-The results shown on left panels on Figures \ref{fig:strucfunc-fit-OrionS}-\ref{fig:strucfunc-fit-OrionLH} show a typical second-order structure function pattern, where there is a series of ascending values of  the structure function that tends to stabilize around the 2\(\sigma^2\) value, indicating a loss in the correlations at large separations.
-The Carina nebula and Hubble X follow this behavior.
-
-For astronomical observations it is thought that the values at large separations not following the previous pattern reflects movements that are not related to the ionized gas random motions.
-It is known that HII regions are created on the edge of molecular clouds, so they will reach a blister or champagne phase, introducing large-scale gradients \citep{Mivi1995}. 
-Also there is the expansion or rotation of each region.
-
-A more common pattern for structure functions of HII regions looks like a 'hook' where at large separations the structure function values start decreasing.
-This behavior is shown in the Orion core, 30 Doradus, Hubble V, NGC 595 and the EON.
-Less common is the behavior where at large separations there are also a series of ascending values in the structure function, like the Lagoon nebula or NGC 346, or a periodic behavior like NGC 604.
-
-Table \ref{tab:Res} presents the turbulent parameters results along the obtained observational constraints.
-
-The second column correspond to the true variance \(\sigma^2\pos\) of the velocity field.
-For all regions except for Carina, Lagoon and the EON there is an increase in this value.
-For 30 Doradus, which has the highest value, \(\sigma\) goes from \SI{16}{km.s^{-1}} to  \SI{19}{km.s^{-1}}.
-This is two times higher than NGC 604 that has a change of \SI{7}{km.s^{-1}} to \SI{9}{km.s^{-1}}, followed by NGC 595 with \SI{6.6}{km.s^{-1}} to \SI{7.5}{km.s^{-1}}.
-NGC 346 is next with a value of \SI{6}{km.s^{-1}} which is close to the value of the centroid velocities.
-Carina presents a value of \SI{4.2}{km.s^{-1}} which is the same as the velocity sample.
-The Orion core has a change from \SI{3}{km.s^{-1}} to \SI{4}{km.s^{-1}}.
-Hubble X has a value of \SI{3.9}{km.s^{-1}} which is very close with respect the \SI{3.6}{km.s^{-1}} value of the velocity field.
-The value for Hubble V increase from \SI{2.8}{km.s^{-1}} to \SI{3.3}{km.s^{-1}}.
-Lagoon presents a value of \SI{2.6}{km.s^{-1}} and the EON value decrease from \SI{3.2}{km.s^{-1}} to \SI{2.2}{km.s^{-1}}.
+%structure functions descriptions
+On Figures \ref{fig:strucfunc-fit-OrionS}a-\ref{fig:strucfunc-fit-OrionLH}a we see that the second-order structure functions for our sample of \hii{} regions follows the patterns describe in Figure~\ref{fig:model-strucfunc}.
+For simplicity, in the next paragraphs where we describe the structure functions of our sample, the small scales would refer to the separations \(r < r_0\) and large scales would refer to separations \(r > r_0\).
+
+Figure~\ref{fig:strucfunc-fit-OrionS}a shows that the structure function of the Orion core behaves accordingly to the tapered case of inhomogeneous fluctuations (see Figure~\ref{fig:model-strucfunc}b).
+Small scales are consider above the separation of \SI{0.002}{pc} (\(s_0\)=\SI{2}{\arcsecond}), which only affects the first point.
+From there until separations of \SI{0.003}{pc} all points within this range fall below the true model showing that they affected at some extent by the seeing. 
+The correlation length for the Orion core is 0.07\(\pm\)0.01 pc with a \(\sigma^2\pos\) of 13\(\pm\)1 \(\text{km}^2 \text{s}^{-2}\).
+At large scales there is a small plateau around \SI{22}{km^{2}.s^{-2}} reached at \SI{0.25}{pc}.
+Above separations of \SI{0.3}{pc} the structure function decays a separation of \SI{0.5}{pc} with a value of \SI{7}{km^{2}.s^{-2}}.
+
+In the Figure~\ref{fig:strucfunc-fit-M8}a we see that the Lagoon nebula presents some particular behavior at small and large scales. 
+At small scales, considered above the separation of \SI{0.005}{pc} (\(s_0\)=\SI{0.83}{\arcsecond}), the structure function shows the characteristic ascending values despite not being as uniform as the other regions.
+In this case there aren't points affected by the seeing.
+However, there is a clear tendency of a power-law behavior that fits our model with a \(r_0\) of 1\(\pm\)0.2 pc and a \(\sigma^2\pos\) of 7\(\pm\)1 \(\text{km}^2 \text{s}^{-2}\).
+At large scales there is an indication of some periodic behavior with a very large amplitude of ascending \(B(r)\) at largest separation.
+The first maximum value of \(B(r)\) is \(\sim\)\SI{14}{km^{2}.s^{-2}} at a separation of \(\sim\)\SI{2.5}{pc}. 
+Then at \(\sim\)\SI{4.5}{pc} the minimum value, \(\sim\)\SI{11}{km^{2}.s^{-2}}, of the first oscillation is reached.
+From this point the structure function keeps going up until it reaches \SI{66}{km^{2}.s^{-2}} at \SI{20}{pc}.
+
+At small scales the Carina structure function, Figure~\ref{fig:strucfunc-fit-CarC}a, shows the most erratic behavior of all our sample.
+Despite this lack of uniformity, still it is possible to see a series of ascending values indicating the existence of correlations in the velocity field that fits our proposed model.
+The seeing is \SI{0.008}{pc} (\(s_0\)=\SI{1.3}{\arcsecond}) and there aren't any points that lie below the true model as in the Lagoon nebula.
+The correlation length is 0.56\(\pm\)0.04 pc at a \(\sigma^2\pos\) of 18\(\pm\)1 \(\text{km}^2 \text{s}^{-2}\).
+At larges scales the structure function of the Carina nebula follows a pattern that closely resembles the homogeneous fluctuation of Figure~\ref{fig:model-strucfunc}a.
+The structure function reaches a plateau around \SI{36}{km^{2}.s^{-2}} at \(\sim\) \SI{2}{pc}.
+When \(r >\)\SI{6}{pc} the structure functions resembles a periodic behavior with a small amplitude.
+
+For Carina and Lagoon nebula, the velocity fields are obtained from the FLAMES multi-fiber instrument (section~\ref{sec:flames-multi-fiber}). 
+We can see from Figure~\ref{fig:velocity-maps} that observations from this instrument do not give uniform maps as the other instruments. 
+Instead the discrete fiber positions are diversely located across the FOV.
+This would affect the structure function since the values are not adjacent as the other observations.
+This is reflected in the non uniform \(B(r)\) values at small scales that we point in the previous paragraphs.
+
+In the Figure~\ref{fig:strucfunc-fit-N346}a we show the structure function of NGC 346.
+For this region the points are above the seeing value which is \SI{0.07}{pc} (\(s_0\)=\SI{0.23}{\arcsecond}) but still the first 8 points lie below the true model.
+At separations above \SI{0.4}{pc} the structure functions observed values coincide with the true model. 
+The correlation length is 2\(\pm\)0.1 pc at a \(\sigma^2\pos\) of 37\(\pm\)1 \(\text{km}^2 \text{s}^{-2}\).
+For larger scales a periodic behavior is seen above \SI{9}{pc} with a \(B(r)\) value of \SI{70}{km^{2}.s^{-2}}.
+Starting from a separation of \SI{12}{pc} and a \(B(r)\) value of \SI{65}{km^{2}.s^{-2}} the structure function keeps ascending until it reaches \SI{146}{km^{2}.s^{-2}} at \SI{24}{pc}.
+
+The 30 Doradus structure function is shown in Figure~\ref{fig:strucfunc-fit-Dor}a.
+The seeing value for this regions is \SI{0.16}{pc} (\(s_0\)=\SI{0.7}{\arcsecond}) and just one point of the structure function is below this value.
+Until a separation of \SI{1.7}{pc} the structure function lies below the true model.
+The correlation length is 4\(\pm\)0.2 pc at a \(\sigma^2\pos\) of 300\(\pm\)9 \(\text{km}^2 \text{s}^{-2}\).
+As the Orion core, 30 Doradus structure function presents a behavior of tapered fluctuations.  
+The maximum \(B(r)\) value is \SI{655}{km^{2}.s^{-2}} at a separation of \SI{21}{pc}. 
+From there \(B(r)\) values descends until they reach \SI{250}{km^{2}.s^{-2}} at \SI{38}{pc}.
+
+In the Figure~\ref{fig:strucfunc-fit-HV}a we show the structure function of Hubble V.
+The structure function is well behaved with our model and present characteristics of tapered fluctuations with a small periodic behavior.
+The value of the seeing for this regions is \SI{0.5}{pc} (\(s_0\)=\SI{0.2}{\arcsecond})..
+Despite this seeing value, all the structure function points lies below the true model which would indicate that the seeing is affecting the observed structure function.
+The correlation length is 3.4\(\pm\)0.3 pc with a \(\sigma^2\pos\) of 10\(\pm\)1 \(\text{km}^2 \text{s}^{-2}\).
+The maximum \(B(r)\) value is \SI{18}{km^{2}.s^{-2}} at a separation of \SI{25}{pc}. 
+From there \(B(r)\) values descends until \SI{14}{km^{2}.s^{-2}} at \SI{45}{pc}, there is a rise in \(B(r)\) for the next point at \SI{50}{pc} with a value of \SI{15}{km^{2}.s^{-2}} and finally the structure functions descends at \SI{9}{km^{2}.s^{-2}} for a separation of \SI{70}{pc}.
+
+The Hubble X structure function is shown in Figure~\ref{fig:strucfunc-fit-HX}a.
+The seeing is \SI{0.006}{pc} (\(s_0\)=\SI{0.24}{\arcsecond}) and as in Hubble V the observed structure function lies below the true model.
+The correlation length is 4\(\pm\)0.4 pc at a \(\sigma^2\pos\) of 16\(\pm\)1 \(\text{km}^2 \text{s}^{-2}\).
+The structure functions presents at large scales the behavior of periodic fluctuations.
+A plateau is reached around \SI{25}{km^{2}.s^{-2}} at a separation of \SI{14}{pc} and a maximum \(B(r)\) value of \SI{31}{km^{2}.s^{-2}} at a separation of \SI{36}{pc}. 
+From this point the structure functions shows consistent values around \SI{24}{km^{2}.s^{-2}} and finally there is a rise in \(B(r)\) to \SI{29}{km^{2}.s^{-2}} at a separation of \SI{91}{pc}.
+
+In the Figure~\ref{fig:strucfunc-fit-N595}a we show the structure function of NGC 595.
+The seeing is \SI{0.5}{pc} (\(s_0\)=\SI{0.12}{\arcsecond}) and for this region only the first point is below the true model and starting from \SI{2}{pc} there is a good agreement between the observed structure function.
+The correlation length is 12\(\pm\)1 pc at a \(\sigma^2\pos\) of 56\(\pm\)2 \(\text{km}^2 \text{s}^{-2}\).
+At large scales the structure function behave following the tapered fluctuations behavior.
+A maximum \(B(r)\) value of \SI{104}{km^{2}.s^{-2}} is reached at \SI{33}{pc}. 
+From there the structure functions decays following and inhomogeneous pattern until it reaches \SI{54}{km^{2}.s^{-2}} at a separation of \SI{211}{pc}.
+
+Table \ref{tab:Res} presents the turbulent parameters results along the obtained observational constraints mentioned in the paragraphs above.
+The second column correspond to the variance \(\sigma^2\pos\) of the velocity field.
 The \(B_{\text{noise}}\) value is shown in the third column which would be the minimum squared velocity difference that could be measure by the instrument.
-
-The third column in Table \ref{tab:Res} shows the seeing value in parsecs, \(s_0\), which represent the minimum value of the separation which would valid for the observed structure function. 
-The forth column shows the correlation value \(r_0\) in parsecs.
+The forth column in Table \ref{tab:Res} shows the seeing value in parsecs, \(s_0\), which represent the minimum value of the separation which would valid for the observed structure function. 
+The fifth column shows the correlation value \(r_0\) in parsecs.
 The \(r_0\) range covered in our results for the sample goes from 0.09 to 12 pc.
-The fifth column indicates the size of each observational box in parsecs.
+The sixth column indicates the size of each observational box in parsecs.
 The index \(m\) is shown in the last column and the range covered by the power-law index in our HII region sample goes from 0.7 to 1.5.
-The implications of these results is further developed on the next section.
+The interpretation of our results is developed in the next section.
 
@@
 \subsection{Interpretation of the turbulent parameters and origins of interstellar turbulence}\label{sec:interpretation-origin}
-\textit{Note: Still working on this section}
 

### 2022-02-23 strucfunc_paper.tex
Describe seeing

@@
 
-We also take into account in the new functional observational constraints like the seeing and observational box size (see Appendix~\ref{sec:degr-struct-funct} for details).
-
-The seeing becomes important at small scales and it is known that has an effect giving a more pronounced stepping in the structure function.
-The model proposed to describe the seeing at small scales is:
-%
+Two observational effects can modify the observed structure function at the smallest scales.
+On the one hand, the blurring of the observed image by atmospheric seeing
+tends to reduce \(B(r)\) for small \(r\).
+In Appendix~\ref{sec:effects-seeing-struc}, we perform numerical experiments
+with synthetic velocity fields and find that
+a good approximation to the effects of seeing is to multiply
+the model structure function by a factor:
 \begin{equation}\label{eq:ffs}
@@
     1+(2s_0 / r)^{2 / 3}
-  }
-\end{equation}
+  } ,
+\end{equation}
+where \(s_0\) is the RMS width of the seeing profile.\footnote{%
+  Note that the full-width half maximum (FWHM) seeing width is
+  \(2 (2 \ln 2)^{1/2} s_0 \approx 2.35 s\).
+}
+An example is shown by the green line in Figure~\ref{fig:model-strucfunc}a.
+Note that the effect of seeing is to make the structure function 
+bend down away from the idealized power law, 
+becoming increasingly steep at scales smaller than \(s_0\),
+but having a noticeable effect at scales up to \(10 s_0\).
 

### 2022-02-26 strucfunc_paper.tex
Simplify the basic strucfunc equation by using 2^x

@@
 \begin{equation}\label{eq:new-correlation-form}
-  C(r;\ r_0, m) = \exp \left[ -(\ln 2) \left( \frac{r}{r_0} \right)^m \right].
+  C(r;\ r_0, m) = 2^{- \left( r/r_0 \right)^m} 
 \end{equation}
@@
 Two observational effects can modify the observed structure function at the smallest scales.
-On the one hand, the blurring of the observed image by atmospheric seeing
+The first is the blurring of the observed image by atmospheric seeing
 tends to reduce \(B(r)\) for small \(r\).
@@
 but having a noticeable effect at scales up to \(10 s_0\).
+
+The second effect is the presence of noise in the observational measurements.
+Although this affects all scales,
+it is most noticeable for small separations,
+where the intrinsic structure function is smallest.
+If the noise is spatially uncorrelated,
+then it can be represented as a constant term \(B_{\text{noise}}\).
+Combining the seeing and noise effects yields the corrected
+model structure function:
+\begin{multline}
+  \tilde{B}
+  \bigl( r; \ r_0, \sigma^2\pos, m, s_0, B_{\text{noise}} \bigr)
+  = \\
+  2\sigma^2\pos \left[
+    1 - 2^{- \left( r/r_0 \right)^m} 
+  \right]
+  \,  S(r; s_0, r_0) + B_{\text{noise}}
+\label{eq:sf-corrected}
+\end{multline}
 

### 2022-02-26 strucfunc_paper.tex
Updates from Overleaf

--- 2022-02-22 strucfunc_paper.tex
@@
 
+In the Figure~\ref{fig:strucfunc-fit-N604H}a we show the structure function of NGC 604.
+The structure function present clear characteristics of periodic oscillations at large scales.
+The seeing is \SI{2.2}{pc} (\(s_0\)=\SI{0.53}{\arcsecond}) and the structure function of this region lies below the true model for most of the separation range.
+The correlation length is 9\(\pm\)3 pc at a \(\sigma^2\pos\) of 81\(\pm\)25 \(\text{km}^2 \text{s}^{-2}\).
+A periodic pattern for the structure function appears with a maximum \(B(r)\) value of \SI{143}{km^{2}.s^{-2}} that is reached at \SI{60}{pc}, then the oscillation cause a minimum of \SI{54}{km^{2}.s^{-2}} at \SI{133}{pc} and finally it goes back up again at \SI{211}{pc} to a \(B(r)\) value of \SI{123}{km^{2}.s^{-2}}.
+
+The EON structure function is shown in Figure~\ref{fig:strucfunc-fit-OrionLH}a.
+This region presents a tapered behavior considering the inhomogeneous fluctuations of Figure~\ref{fig:model-strucfunc}b.
+This observations are heavily affected by the noise which presents a value of \SI{6}{km^{2}.s^{-2}} which is larger that the \(\sigma^2\pos\) \SI{5}{km^{2}.s^{-2}}.
+
 Table \ref{tab:Res} presents the turbulent parameters results along the obtained observational constraints mentioned in the paragraphs above.

### 2022-03-04 strucfunc_paper.tex
Javier changes 2022-03-04

@@
 
-We present the second-order structure results plotted against separation in parsecs and the posteriors of the turbulent parameters.
+In this section we present and describe the second-order structure results.
+The structure functions are plotted against separation in parsecs and we also show the posteriors of the turbulent parameters using the analysis discussed in section~\ref{sec:methods-apply}.
 
@@
 From there until separations of \SI{0.003}{pc} all points within this range fall below the true model showing that they affected at some extent by the seeing. 
-The correlation length for the Orion core is 0.07\(\pm\)0.01 pc with a \(\sigma^2\pos\) of 13\(\pm\)1 \(\text{km}^2 \text{s}^{-2}\).
-At large scales there is a small plateau around \SI{22}{km^{2}.s^{-2}} reached at \SI{0.25}{pc}.
-Above separations of \SI{0.3}{pc} the structure function decays a separation of \SI{0.5}{pc} with a value of \SI{7}{km^{2}.s^{-2}}.
-
-In the Figure~\ref{fig:strucfunc-fit-M8}a we see that the Lagoon nebula presents some particular behavior at small and large scales. 
-At small scales, considered above the separation of \SI{0.005}{pc} (\(s_0\)=\SI{0.83}{\arcsecond}), the structure function shows the characteristic ascending values despite not being as uniform as the other regions.
-In this case there aren't points affected by the seeing.
-However, there is a clear tendency of a power-law behavior that fits our model with a \(r_0\) of 1\(\pm\)0.2 pc and a \(\sigma^2\pos\) of 7\(\pm\)1 \(\text{km}^2 \text{s}^{-2}\).
+The correlation length for the Orion core is 0.07\(\pm\)0.01 pc, it has a \(\sigma^2\pos\) of 13\(\pm\)1 \(\text{km}^2 \text{s}^{-2}\) and an index of 1.07\(\pm\)0.02.
+At large scales there is a plateau around \SI{22}{km^{2}.s^{-2}} reached at \SI{0.25}{pc}.
+Above separations of \SI{0.3}{pc} the structure function decays reaching a separation of \SI{0.5}{pc} with a value of \SI{7}{km^{2}.s^{-2}}.
+
+In the Figure~\ref{fig:strucfunc-fit-M8}a we see that the Lagoon nebula presents a non-uni from behavior at small. 
+In this range considered above the separation of \SI{0.005}{pc} (\(s_0\)=\SI{0.83}{\arcsecond}) there aren't points affected by the seeing.
+The structure function shows the characteristic ascending values despite not being as uniform as the other regions.
+The turbulent parameters that fits our model are a \(r_0\) of 1\(\pm\)0.2 pc, a \(\sigma^2\pos\) of 7\(\pm\)1 \(\text{km}^2 \text{s}^{-2}\) and an index of 1.13\(\pm\)0.01.
 At large scales there is an indication of some periodic behavior with a very large amplitude of ascending \(B(r)\) at largest separation.
-The first maximum value of \(B(r)\) is \(\sim\)\SI{14}{km^{2}.s^{-2}} at a separation of \(\sim\)\SI{2.5}{pc}. 
-Then at \(\sim\)\SI{4.5}{pc} the minimum value, \(\sim\)\SI{11}{km^{2}.s^{-2}}, of the first oscillation is reached.
-From this point the structure function keeps going up until it reaches \SI{66}{km^{2}.s^{-2}} at \SI{20}{pc}.
+The first maximum value of \(B(r)\) in the order of 2\(\sigma^2\pos\) is \(\sim\)\SI{14}{km^{2}.s^{-2}} at a separation of \(\sim\)\SI{2.5}{pc}. 
+Considering an oscillating behavior at \SI{4.5}{pc} a minimum value of \SI{11}{km^{2}.s^{-2}} is reached.
+From this point the structure function keeps going up until it reaches \SI{66}{km^{2}.s^{-2}} around \SI{20}{pc}.
 
@@
 Despite this lack of uniformity, still it is possible to see a series of ascending values indicating the existence of correlations in the velocity field that fits our proposed model.
-The seeing is \SI{0.008}{pc} (\(s_0\)=\SI{1.3}{\arcsecond}) and there aren't any points that lie below the true model as in the Lagoon nebula.
-The correlation length is 0.56\(\pm\)0.04 pc at a \(\sigma^2\pos\) of 18\(\pm\)1 \(\text{km}^2 \text{s}^{-2}\).
+The seeing is \SI{0.008}{pc} (\(s_0\)=\SI{1.3}{\arcsecond}) and there aren't many points that lie below.
+The correlation length is 0.56\(\pm\)0.04 pc at a \(\sigma^2\pos\) of 18\(\pm\)1 \(\text{km}^2 \text{s}^{-2}\) and an index of 1.14\(\pm\)0.01.
 At larges scales the structure function of the Carina nebula follows a pattern that closely resembles the homogeneous fluctuation of Figure~\ref{fig:model-strucfunc}a.
@@
 This would affect the structure function since the values are not adjacent as the other observations.
-This is reflected in the non uniform \(B(r)\) values at small scales that we point in the previous paragraphs.
+This is reflected in the non uniform \(B(r)\) below  \(r_0\) that we pointed out in the previous paragraphs.
 
 In the Figure~\ref{fig:strucfunc-fit-N346}a we show the structure function of NGC 346.
-For this region the points are above the seeing value which is \SI{0.07}{pc} (\(s_0\)=\SI{0.23}{\arcsecond}) but still the first 8 points lie below the true model.
+For this region the points are above the seeing value which is \SI{0.07}{pc} (\(s_0\)=\SI{0.23}{\arcsecond}) but the first 8 points lie below the true model.
 At separations above \SI{0.4}{pc} the structure functions observed values coincide with the true model. 
-The correlation length is 2\(\pm\)0.1 pc at a \(\sigma^2\pos\) of 37\(\pm\)1 \(\text{km}^2 \text{s}^{-2}\).
-For larger scales a periodic behavior is seen above \SI{9}{pc} with a \(B(r)\) value of \SI{70}{km^{2}.s^{-2}}.
+The correlation length is 2\(\pm\)0.1 pc at a \(\sigma^2\pos\) of 37\(\pm\)1 \(\text{km}^2 \text{s}^{-2}\) and an index of 0.76\(\pm\)0.02.
+For scales above \SI{9}{pc} with a \(B(r)\) value of \SI{70}{km^{2}.s^{-2}} a periodic behavior is seen .
 Starting from a separation of \SI{12}{pc} and a \(B(r)\) value of \SI{65}{km^{2}.s^{-2}} the structure function keeps ascending until it reaches \SI{146}{km^{2}.s^{-2}} at \SI{24}{pc}.
@@
 Until a separation of \SI{1.7}{pc} the structure function lies below the true model.
-The correlation length is 4\(\pm\)0.2 pc at a \(\sigma^2\pos\) of 300\(\pm\)9 \(\text{km}^2 \text{s}^{-2}\).
+The correlation length is 4\(\pm\)0.2 pc at a \(\sigma^2\pos\) of 300\(\pm\)9 \(\text{km}^2 \text{s}^{-2}\) and an index of 0.84\(\pm\)0.04.
 As the Orion core, 30 Doradus structure function presents a behavior of tapered fluctuations.  
@@
 In the Figure~\ref{fig:strucfunc-fit-HV}a we show the structure function of Hubble V.
-The structure function is well behaved with our model and present characteristics of tapered fluctuations with a small periodic behavior.
-The value of the seeing for this regions is \SI{0.5}{pc} (\(s_0\)=\SI{0.2}{\arcsecond})..
+The value of the seeing for this regions is \SI{0.5}{pc} (\(s_0\)=\SI{0.2}{\arcsecond}).
 Despite this seeing value, all the structure function points lies below the true model which would indicate that the seeing is affecting the observed structure function.
-The correlation length is 3.4\(\pm\)0.3 pc with a \(\sigma^2\pos\) of 10\(\pm\)1 \(\text{km}^2 \text{s}^{-2}\).
+The correlation length is 3.4\(\pm\)0.3 pc at a \(\sigma^2\pos\) of 10\(\pm\)1 \(\text{km}^2 \text{s}^{-2}\) and an index of 0.74\(\pm\)0.10.
 The maximum \(B(r)\) value is \SI{18}{km^{2}.s^{-2}} at a separation of \SI{25}{pc}. 
-From there \(B(r)\) values descends until \SI{14}{km^{2}.s^{-2}} at \SI{45}{pc}, there is a rise in \(B(r)\) for the next point at \SI{50}{pc} with a value of \SI{15}{km^{2}.s^{-2}} and finally the structure functions descends at \SI{9}{km^{2}.s^{-2}} for a separation of \SI{70}{pc}.
+From there \(B(r)\) values descends until \SI{14}{km^{2}.s^{-2}} at \SI{45}{pc}, then it rises for the next point at \SI{50}{pc} with a value of \SI{15}{km^{2}.s^{-2}} and finally the structure functions descends at \SI{9}{km^{2}.s^{-2}} for a separation of \SI{70}{pc}.
 
@@
 The seeing is \SI{0.006}{pc} (\(s_0\)=\SI{0.24}{\arcsecond}) and as in Hubble V the observed structure function lies below the true model.
-The correlation length is 4\(\pm\)0.4 pc at a \(\sigma^2\pos\) of 16\(\pm\)1 \(\text{km}^2 \text{s}^{-2}\).
+The correlation length is 4\(\pm\)0.4 pc at a \(\sigma^2\pos\) of 16\(\pm\)1 \(\text{km}^2 \text{s}^{-2}\) and an index of 0.88\(\pm\)0.14.
 The structure functions presents at large scales the behavior of periodic fluctuations.
 A plateau is reached around \SI{25}{km^{2}.s^{-2}} at a separation of \SI{14}{pc} and a maximum \(B(r)\) value of \SI{31}{km^{2}.s^{-2}} at a separation of \SI{36}{pc}. 
-From this point the structure functions shows consistent values around \SI{24}{km^{2}.s^{-2}} and finally there is a rise in \(B(r)\) to \SI{29}{km^{2}.s^{-2}} at a separation of \SI{91}{pc}.
+From this point the structure functions shows consistent values around \SI{24}{km^{2}.s^{-2}} and finally there is a rise in \(B(r)\) up to \SI{29}{km^{2}.s^{-2}} at a separation of \SI{91}{pc}.
 
@@
 The seeing is \SI{0.5}{pc} (\(s_0\)=\SI{0.12}{\arcsecond}) and for this region only the first point is below the true model and starting from \SI{2}{pc} there is a good agreement between the observed structure function.
-The correlation length is 12\(\pm\)1 pc at a \(\sigma^2\pos\) of 56\(\pm\)2 \(\text{km}^2 \text{s}^{-2}\).
+The correlation length is 12\(\pm\)1 pc at a \(\sigma^2\pos\) of 56\(\pm\)2 \(\text{km}^2 \text{s}^{-2}\) and an index of 1.3\(\pm\)0.05.
 At large scales the structure function behave following the tapered fluctuations behavior.
@@
 The seeing is \SI{2.2}{pc} (\(s_0\)=\SI{0.53}{\arcsecond}) and the structure function of this region lies below the true model for most of the separation range.
-The correlation length is 9\(\pm\)3 pc at a \(\sigma^2\pos\) of 81\(\pm\)25 \(\text{km}^2 \text{s}^{-2}\).
+The correlation length is 9\(\pm\)3 pc at a \(\sigma^2\pos\) of 81\(\pm\)25 \(\text{km}^2 \text{s}^{-2}\) and has an index of 1.3\(\pm\)0.05.
 A periodic pattern for the structure function appears with a maximum \(B(r)\) value of \SI{143}{km^{2}.s^{-2}} that is reached at \SI{60}{pc}, then the oscillation cause a minimum of \SI{54}{km^{2}.s^{-2}} at \SI{133}{pc} and finally it goes back up again at \SI{211}{pc} to a \(B(r)\) value of \SI{123}{km^{2}.s^{-2}}.

### 2022-03-04 strucfunc_paper.tex
Edits to seeing and noise section

@@
 Two observational effects can modify the observed structure function at the smallest scales.
-The first is the blurring of the observed image by atmospheric seeing
-tends to reduce \(B(r)\) for small \(r\).
+The first is the blurring of the observed image by atmospheric seeing,
+which tends to reduce \(B(r)\) for small \(r\).
 In Appendix~\ref{sec:effects-seeing-struc}, we perform numerical experiments
@@
 
-The second effect is the presence of noise in the observational measurements.
+The second effect is the presence of instrumental noise
+in the observational measurements,
+such as Poisson noise from photon-counting statistics. 
 Although this affects all scales,
@@
 where the intrinsic structure function is smallest.
-If the noise is spatially uncorrelated,
-then it can be represented as a constant term \(B_{\text{noise}}\).
-Combining the seeing and noise effects yields the corrected
+If the noise is spatially uncorrelated
+(equal and independent uncertainties in the velocity
+measurement of each pixel),
+then its contribution to the structure function is independent of separation,
+which means it can be represented as a constant term \(B_{\text{noise}}\).
+
+Combining both the effects of seeing and noise yields the corrected
 model structure function:
@@
 \end{multline}
+
+An example model structure function that is affected by both seeing and noise
 

### 2022-03-11 strucfunc_paper.tex
Javier changes 2022-03-11

@@
 
-The Orion Nebula (M42) is the prototype of a galactic HII region located at a distance of 440 pc \citetext{\SI{1}{\arcsecond} = \SI{0.001}{pc} ; \citealp{2008AJ....136.1566O}}.
+The Orion Nebula (M42) is the prototype of a galactic HII region located at a distance of 440 pc \citetext{\SI{1}{\arcsecond} = \SI{0.002}{pc} ; \citealp{2008AJ....136.1566O}}.
 The O7 V star \(\theta^{1}\) Ori C is the most luminous and hottest star \citep{2006A&A...448..351S} with an ionizing flux \(Q_0\) of  \SI{e49.12}{photons.s^{-1}}. 
@@
 %
-which calculate a value \(\chi\) to be minimized scaled by the inverse of the uncertainty \(\varepsilon\) in the data.
-The minimization procedure use the method \textit{emcee} \citep{2013PASP..125..306F} which is a \textit{python} implementation of the affine-invariant ensemble sampler for Markov chain Monte Carlo (MCMC) by \citet{2010CAMCS...5...65G}.
-The turbulent parameters \(r_{0}\)\ , \(\sigma^2\pos\) and \(m\), and the observational constraints \(s_0\) and \( B_{\text{noise}}\) are the set of variables in the model to be optimized in the fit.
-Using these procedure we obtain posteriors for the structure function.
-
-In this way we want to avoid one fundamental problem in the interpretation of the structure function. 
-The slope in the majority of previous studies and hence, the correlation length, is obtained without a formal procedure. 
-The traditional way to find the correlation length it is to determine a particular range of ascending values in the structure function. 
-If this increase in values is stopped or reversed it is commonly assumed that one particular inertial range has been found. 
-In some cases this procedure keeps going up to large scales, giving two or more inertial regimes leading to an erroneous interpretation of multiple inertial scales.
+where the turbulent parameters are \(r_{0}\)\ , \(\sigma^2\pos\) and \(m\), and the observational constraints \(s_0\) and \( B_{\text{noise}}\).
+This procedure calculate a value \(\chi\) to be minimized scaled by the inverse of the uncertainty \(\varepsilon\) in the data.
+To obtain the confidence intervals we use the minimization procedure \textit{emcee} \citep{2013PASP..125..306F} which is a \textit{python} implementation of the affine-invariant ensemble sampler for Markov chain Monte Carlo (MCMC) by \citet{2010CAMCS...5...65G}.
+%Using these procedure we obtain the posteriors for our model and the parameters in equation~\ref{eq:chi}.
+
+%In this way we want to avoid one fundamental problem in the interpretation of the structure function. 
+%The slope in the majority of previous studies and hence, the correlation length, is obtained without a formal procedure. 
+%The traditional way to find the correlation length it is to determine a particular range of ascending values in the structure function. 
+%If this increase in values is stopped or reversed it is commonly assumed that one particular inertial range has been found. 
+%In some cases this procedure keeps going up to large scales, giving two or more inertial regimes leading to an erroneous interpretation of multiple inertial scales.
 
@@
 \ref{fig:velocity-maps}.
-The solid circles indicate the range use in the non-linear regression analysis (see section~\ref{sec:methods-apply}), while the open circles are the points of the structure function that where left out.
-This was done to enhance the possibilities of a convergence since the structure function values at large separations are to follow the 2\(\sigma^2\) value according to theory.
-The light shaded areas in the plots show where the separation \(r\) is above half of the box size \(L\), which is indicated with a vertical dotted line.
-
-The green dashed line indicate the mean samples posterior of the model structure function without instrumental effects using equation \ref{eq:functional} and \ref{eq:new-correlation-form}.
-The Figures also show in yellow solid line the mean of samples posterior using equation \ref{eq:sf-functional}.
-The vertical dashed line indicates the correlation length value \(r_0\) and the horizontal dashed line indicates the true variance of the velocity fields, \(\sigma^2\).
-The vertical and horizontal dotted lines shows the value of the observational considerations, the seeing, \(s_0\) and the value of the noise, \(B_{\text{noise}}\), respectively.
-For the dashed and dotted lines the overlapping translucent boxes indicate the spread of values up to 2-sigma (dark shaded area) and 3-sigma (light shaded area) obtained after the analysis described in section~\ref{sec:methods-apply}.
+In the plots the solid circles indicate the points we use in the non-linear regression analysis (see section~\ref{sec:methods-apply}), while the open circles are the points of the structure function that where left out.
+The criteria for the previous considerations is that the structure function at large separations is affected by the inhomogeneties of the velocity field (see section-\ref{sec:limit-model-struct}), hence the reason that large separation values are not considered for the fit of our model.
+In some cases, at the smallest separations we merge a couple of the structure functions points under the assumption that those would be heavily affected by the seeing and the rest would be coincident with the power-law behavior.
+The Figures shows in the orange solid thick line the best fit for the equation \ref{eq:sf-functional} which takes into account observational limitations on the structure function.
+The green dashed line indicate the theoretical model for the structure function using equation \ref{eq:functional}.
+
+Figures \ref{fig:strucfunc-fit-OrionS}-\ref{fig:strucfunc-fit-OrionLH} left panels show in dashed and dotted lines the parameters of our model.
+The vertical dashed line indicates the correlation length, \(r_0\), and the horizontal dashed line indicates the true variance of the velocity fields, \(\sigma^2\).
+The vertical and horizontal dotted lines shows the value of the observational considerations: the rms seeing, \(s_0\) and the value of the noise, \(B_{\text{noise}}\).
+For the dashed and dotted lines the overlapping translucent boxes indicate the confidence intervals in 1-sigma (dark shaded area) and 2-sigma (light shaded area) obtained from the MCMC analysis.
+The light shaded areas in the plot show where the separation \(r\) is above half of the box size, \(L\), which is indicated with a vertical dotted line.
+To present our results in the next paragraphs the small scales would refer to the separations \(r < r_0\) and large scales would refer to separations \(r > r_0\).
+
+Figure~\ref{fig:strucfunc-fit-OrionS}a shows the structure function of the Orion core.
+Valid scales are consider above the separation of \SI{0.002}{pc} (\(s_0\)=\SI{1}{\arcsecond}).
+In this case we merge the first three points.
+From there until separations of \SI{0.003}{pc} all points within this range fall below the true model showing that they are affected by the seeing. 
+The correlation length for the Orion core is \SI{0.07 \pm 0.01}{pc}, it has a \(\sigma^2\pos\) of \SI{12 \pm 1}{km^{2}.s^{-2}} and an index of \num{1.07 \pm 0.02}.
+The structure function of the Orion core behaves accordingly to the tapered case of inhomogeneous fluctuations (see Figure~\ref{fig:model-strucfunc}b).
+At large scales there is a plateau around \SI{22}{km^{2}.s^{-2}} reached at \SI{0.25}{pc}.
+Above separations of \SI{0.3}{pc} the structure function decays reaching a separation of \SI{0.5}{pc} with a value of \SI{7}{km^{2}.s^{-2}}.
+
+The Figure~\ref{fig:strucfunc-fit-M8}a shows the structure function of the Lagoon nebula.
+There aren't any points affected by the seeing which has a value of \SI{0.006}{pc} (\(s_0\)=\SI{1}{\arcsecond}).
+In this case we merge the first two points.
+The Lagoon nebula presents a non-uniform behavior below the correlation length but it is possible to see the characteristic ascending values of the structure function.
+The turbulent parameters that fits our model are a \(r_0\) of \SI{1 \pm 0.2}{pc}, a \(\sigma^2\pos\) of \SI{7 \pm 1}{km^{2}.s^{-2}} and an index of \num{1.13 \pm 0.01}.
+At large scales there is an indication of some periodic behavior with a very large amplitude of ascending \(B(r)\) at largest separation.
+The first maximum value of \(B(r)\) in the order of 2\(\sigma^2\pos\) is \(\sim\)\SI{14}{km^{2}.s^{-2}} at a separation of \(\sim\)\SI{2.5}{pc}. 
+Considering an oscillating behavior at \SI{4.5}{pc} a minimum value of \SI{11}{km^{2}.s^{-2}} is reached.
+From this point the structure function keeps going up until it reaches \SI{66}{km^{2}.s^{-2}} around \SI{20}{pc}.
+
+The Figure~\ref{fig:strucfunc-fit-CarC}a shows the structure function of the Carina nebula.
+The seeing is \SI{0.008}{pc} (\(s_0\)=\SI{1.3}{\arcsecond}) and there are just a couple of points that lie below the true model, indicating that the majority of points isn't affected by the seeing.
+For this region we merge the first two points of the structure function.
+As the Lagoon nebula, Carina also shows a non-uniform behavior below the correlation length.
+The correlation length is \SI{0.56 \pm 0.04}{pc} pc at a \(\sigma^2\pos\) of \SI{18 \pm 1}{km^{2}.s^{-2}}  and an index of \num{1.14 \pm 0.01}.
+At larges scales the structure function of the Carina nebula follows a pattern that closely resembles the homogeneous fluctuation of Figure~\ref{fig:model-strucfunc}a.
+The structure function reaches a plateau around \SI{36}{km^{2}.s^{-2}} at \(\sim\) \SI{2}{pc}.
+When \(r >\)\SI{6}{pc} the structure functions resembles a periodic behavior with a small amplitude.
+
+For Carina and Lagoon nebula, the velocity fields are obtained from the FLAMES multi-fiber instrument (section~\ref{sec:flames-multi-fiber}). 
+We can see from Figure~\ref{fig:velocity-maps} that observations from this instrument do not give uniform maps as the other instruments. 
+Instead the discrete fiber positions are diversely located across the FOV.
+This would affect the structure function since the values are not adjacent as the other observations.
+This is reflected in the non uniform \(B(r)\) below  \(r_0\) that we pointed out in the previous paragraphs.
+
+The Figure~\ref{fig:strucfunc-fit-N346}a shows the structure function of NGC 346.
+In this case we merge the first three points of the structure function.
+For this region the points are above the seeing value which is \SI{0.07}{pc} (\(s_0\)=\SI{0.23}{\arcsecond}) and the first ten points lie below the true model.
+At separations above \SI{0.4}{pc} the observed structure functions is coincident with the true model. 
+The correlation length is \SI{2 \pm 0.1}{pc} at a \(\sigma^2\pos\) of \SI{3 \pm 1}{km^{2}.s^{-2}} and an index of \num{0.76 \pm 0.02}.
+For scales above \SI{9}{pc} with a \(B(r)\) value of \SI{70}{km^{2}.s^{-2}} a periodic behavior is seen .
+Starting from a separation of \SI{12}{pc} and a \(B(r)\) value of \SI{65}{km^{2}.s^{-2}} the structure function keeps ascending until it reaches \SI{146}{km^{2}.s^{-2}} at \SI{24}{pc}.
+
+The 30 Doradus structure function is shown in Figure~\ref{fig:strucfunc-fit-Dor}a.
+In this case we merge the first five points of the structure function.
+The seeing value for this regions is \SI{0.16}{pc} (\(s_0\)=\SI{0.7}{\arcsecond}) and just one point of the structure function is below this value.
+Until a separation of \SI{1.7}{pc} the structure function lies below the true model.
+The correlation length is \SI{4 \pm 0.2}{pc} at a \(\sigma^2\pos\) of \SI{300 \pm 9}{km^{2}.s^{-2}} and an index of \num{0.84 \pm 0.04}.
+30 Doradus structure function presents a behavior of tapered fluctuations.  
+The maximum \(B(r)\) value is \SI{655}{km^{2}.s^{-2}} at a separation of \SI{21}{pc}. 
+From there \(B(r)\) values descends until they reach \SI{250}{km^{2}.s^{-2}} at \SI{38}{pc}.
+
+In the Figure~\ref{fig:strucfunc-fit-HV}a we show the structure function of Hubble V.
+For the observations coming from the TAURUS-II instrument there wasn't any merging of points.
+The value of the seeing for this regions is \SI{0.5}{pc} (\(s_0\)=\SI{0.2}{\arcsecond}).
+All the structure function points lies below the true model which would indicate that the seeing is affecting the observed structure function.
+The correlation length is \SI{3.4 \pm 0.3}{pc} at a \(\sigma^2\pos\) of  \SI{10 \pm 1}{km^{2}.s^{-2}} and an index of \num{0.74 \pm 0.10}.
+The maximum \(B(r)\) value is \SI{18}{km^{2}.s^{-2}} at a separation of \SI{25}{pc}. 
+From there \(B(r)\) values descends until \SI{14}{km^{2}.s^{-2}} at \SI{45}{pc}, then it rises for the next point at \SI{50}{pc} with a value of \SI{15}{km^{2}.s^{-2}} and finally the structure functions descends at \SI{9}{km^{2}.s^{-2}} for a separation of \SI{70}{pc}.
+
+The Hubble X structure function is shown in Figure~\ref{fig:strucfunc-fit-HX}a.
+The seeing is \SI{0.006}{pc} (\(s_0\)=\SI{0.24}{\arcsecond}) and as in Hubble V the observed structure function lies below the true model.
+The correlation length is \SI{4 \pm 0.4}{pc} at a \(\sigma^2\pos\) of \SI{16 \pm 1}{km^{2}.s^{-2}} and an index of \num{0.88 \pm 0.14}.
+The structure functions presents at large scales the behavior of periodic fluctuations with a small amplitude.
+A plateau is reached around \SI{25}{km^{2}.s^{-2}} at a separation of \SI{14}{pc} and a maximum \(B(r)\) value of \SI{31}{km^{2}.s^{-2}} at a separation of \SI{36}{pc}. 
+From this point the structure functions shows consistent values around \SI{24}{km^{2}.s^{-2}} and finally there is a rise for the last point to \SI{29}{km^{2}.s^{-2}} at a separation of \SI{91}{pc}.
+
+In the Figure~\ref{fig:strucfunc-fit-N595}a we show the structure function of NGC 595.
+The seeing is \SI{0.5}{pc} (\(s_0\)=\SI{0.12}{\arcsecond}) and for this region only the first two points are below the true model. 
+The correlation length is \SI{12 \pm 1}{pc} at a \(\sigma^2\pos\) of \SI{56 \pm 2}{km^{2}.s^{-2}} and an index of \num{1.3 \pm 0.05}.
+At large scales the structure function behave following the tapered fluctuations behavior.
+A maximum \(B(r)\) value of \SI{104}{km^{2}.s^{-2}} is reached at \SI{33}{pc}. 
+From there the structure functions decays following and inhomogeneous pattern until it reaches \SI{54}{km^{2}.s^{-2}} at a separation of \SI{211}{pc}.
+
+In the Figure~\ref{fig:strucfunc-fit-N604H}a we show the structure function of NGC 604.
+The seeing is \SI{1.2}{pc} (\(s_0\)=\SI{0.28}{\arcsecond}) and the structure function of this region lies below the true model for most of the separation range.
+The correlation length is \SI{9 \pm 3 }{pc} at a \(\sigma^2\pos\) of \SI{68 \pm 6}{km^{2}.s^{-2}} and has an index of \num{1.3 \pm 0.05}.
+The structure function present clear characteristics of periodic oscillations at large scales.
+A periodic pattern for the structure function appears with a maximum \(B(r)\) value of \SI{143}{km^{2}.s^{-2}} that is reached at \SI{60}{pc}, then the oscillation cause a minimum of \SI{54}{km^{2}.s^{-2}} at \SI{133}{pc} and finally it goes back up again at \SI{211}{pc} to a \(B(r)\) value of \SI{123}{km^{2}.s^{-2}}.
+
+The EON structure function is shown in Figure~\ref{fig:strucfunc-fit-OrionLH}a.
+This observations are heavily affected by the noise which presents a value of \SI{6}{km^{2}.s^{-2}} which is larger that the \(\sigma^2\pos\) \SI{5}{km^{2}.s^{-2}}.
 
@@
 The contours in the plots reflect the 95\(\%\), 99\(\%\), 99.5\(\%\) and 99.9\(\%\) confidence intervals.
-
-%structure functions descriptions
-On Figures \ref{fig:strucfunc-fit-OrionS}a-\ref{fig:strucfunc-fit-OrionLH}a we see that the second-order structure functions for our sample of \hii{} regions follows the patterns describe in Figure~\ref{fig:model-strucfunc}.
-For simplicity, in the next paragraphs where we describe the structure functions of our sample, the small scales would refer to the separations \(r < r_0\) and large scales would refer to separations \(r > r_0\).
-
-Figure~\ref{fig:strucfunc-fit-OrionS}a shows that the structure function of the Orion core behaves accordingly to the tapered case of inhomogeneous fluctuations (see Figure~\ref{fig:model-strucfunc}b).
-Small scales are consider above the separation of \SI{0.002}{pc} (\(s_0\)=\SI{2}{\arcsecond}), which only affects the first point.
-From there until separations of \SI{0.003}{pc} all points within this range fall below the true model showing that they affected at some extent by the seeing. 
-The correlation length for the Orion core is 0.07\(\pm\)0.01 pc, it has a \(\sigma^2\pos\) of 13\(\pm\)1 \(\text{km}^2 \text{s}^{-2}\) and an index of 1.07\(\pm\)0.02.
-At large scales there is a plateau around \SI{22}{km^{2}.s^{-2}} reached at \SI{0.25}{pc}.
-Above separations of \SI{0.3}{pc} the structure function decays reaching a separation of \SI{0.5}{pc} with a value of \SI{7}{km^{2}.s^{-2}}.
-
-In the Figure~\ref{fig:strucfunc-fit-M8}a we see that the Lagoon nebula presents a non-uni from behavior at small. 
-In this range considered above the separation of \SI{0.005}{pc} (\(s_0\)=\SI{0.83}{\arcsecond}) there aren't points affected by the seeing.
-The structure function shows the characteristic ascending values despite not being as uniform as the other regions.
-The turbulent parameters that fits our model are a \(r_0\) of 1\(\pm\)0.2 pc, a \(\sigma^2\pos\) of 7\(\pm\)1 \(\text{km}^2 \text{s}^{-2}\) and an index of 1.13\(\pm\)0.01.
-At large scales there is an indication of some periodic behavior with a very large amplitude of ascending \(B(r)\) at largest separation.
-The first maximum value of \(B(r)\) in the order of 2\(\sigma^2\pos\) is \(\sim\)\SI{14}{km^{2}.s^{-2}} at a separation of \(\sim\)\SI{2.5}{pc}. 
-Considering an oscillating behavior at \SI{4.5}{pc} a minimum value of \SI{11}{km^{2}.s^{-2}} is reached.
-From this point the structure function keeps going up until it reaches \SI{66}{km^{2}.s^{-2}} around \SI{20}{pc}.
-
-At small scales the Carina structure function, Figure~\ref{fig:strucfunc-fit-CarC}a, shows the most erratic behavior of all our sample.
-Despite this lack of uniformity, still it is possible to see a series of ascending values indicating the existence of correlations in the velocity field that fits our proposed model.
-The seeing is \SI{0.008}{pc} (\(s_0\)=\SI{1.3}{\arcsecond}) and there aren't many points that lie below.
-The correlation length is 0.56\(\pm\)0.04 pc at a \(\sigma^2\pos\) of 18\(\pm\)1 \(\text{km}^2 \text{s}^{-2}\) and an index of 1.14\(\pm\)0.01.
-At larges scales the structure function of the Carina nebula follows a pattern that closely resembles the homogeneous fluctuation of Figure~\ref{fig:model-strucfunc}a.
-The structure function reaches a plateau around \SI{36}{km^{2}.s^{-2}} at \(\sim\) \SI{2}{pc}.
-When \(r >\)\SI{6}{pc} the structure functions resembles a periodic behavior with a small amplitude.
-
-For Carina and Lagoon nebula, the velocity fields are obtained from the FLAMES multi-fiber instrument (section~\ref{sec:flames-multi-fiber}). 
-We can see from Figure~\ref{fig:velocity-maps} that observations from this instrument do not give uniform maps as the other instruments. 
-Instead the discrete fiber positions are diversely located across the FOV.
-This would affect the structure function since the values are not adjacent as the other observations.
-This is reflected in the non uniform \(B(r)\) below  \(r_0\) that we pointed out in the previous paragraphs.
-
-In the Figure~\ref{fig:strucfunc-fit-N346}a we show the structure function of NGC 346.
-For this region the points are above the seeing value which is \SI{0.07}{pc} (\(s_0\)=\SI{0.23}{\arcsecond}) but the first 8 points lie below the true model.
-At separations above \SI{0.4}{pc} the structure functions observed values coincide with the true model. 
-The correlation length is 2\(\pm\)0.1 pc at a \(\sigma^2\pos\) of 37\(\pm\)1 \(\text{km}^2 \text{s}^{-2}\) and an index of 0.76\(\pm\)0.02.
-For scales above \SI{9}{pc} with a \(B(r)\) value of \SI{70}{km^{2}.s^{-2}} a periodic behavior is seen .
-Starting from a separation of \SI{12}{pc} and a \(B(r)\) value of \SI{65}{km^{2}.s^{-2}} the structure function keeps ascending until it reaches \SI{146}{km^{2}.s^{-2}} at \SI{24}{pc}.
-
-The 30 Doradus structure function is shown in Figure~\ref{fig:strucfunc-fit-Dor}a.
-The seeing value for this regions is \SI{0.16}{pc} (\(s_0\)=\SI{0.7}{\arcsecond}) and just one point of the structure function is below this value.
-Until a separation of \SI{1.7}{pc} the structure function lies below the true model.
-The correlation length is 4\(\pm\)0.2 pc at a \(\sigma^2\pos\) of 300\(\pm\)9 \(\text{km}^2 \text{s}^{-2}\) and an index of 0.84\(\pm\)0.04.
-As the Orion core, 30 Doradus structure function presents a behavior of tapered fluctuations.  
-The maximum \(B(r)\) value is \SI{655}{km^{2}.s^{-2}} at a separation of \SI{21}{pc}. 
-From there \(B(r)\) values descends until they reach \SI{250}{km^{2}.s^{-2}} at \SI{38}{pc}.
-
-In the Figure~\ref{fig:strucfunc-fit-HV}a we show the structure function of Hubble V.
-The value of the seeing for this regions is \SI{0.5}{pc} (\(s_0\)=\SI{0.2}{\arcsecond}).
-Despite this seeing value, all the structure function points lies below the true model which would indicate that the seeing is affecting the observed structure function.
-The correlation length is 3.4\(\pm\)0.3 pc at a \(\sigma^2\pos\) of 10\(\pm\)1 \(\text{km}^2 \text{s}^{-2}\) and an index of 0.74\(\pm\)0.10.
-The maximum \(B(r)\) value is \SI{18}{km^{2}.s^{-2}} at a separation of \SI{25}{pc}. 
-From there \(B(r)\) values descends until \SI{14}{km^{2}.s^{-2}} at \SI{45}{pc}, then it rises for the next point at \SI{50}{pc} with a value of \SI{15}{km^{2}.s^{-2}} and finally the structure functions descends at \SI{9}{km^{2}.s^{-2}} for a separation of \SI{70}{pc}.
-
-The Hubble X structure function is shown in Figure~\ref{fig:strucfunc-fit-HX}a.
-The seeing is \SI{0.006}{pc} (\(s_0\)=\SI{0.24}{\arcsecond}) and as in Hubble V the observed structure function lies below the true model.
-The correlation length is 4\(\pm\)0.4 pc at a \(\sigma^2\pos\) of 16\(\pm\)1 \(\text{km}^2 \text{s}^{-2}\) and an index of 0.88\(\pm\)0.14.
-The structure functions presents at large scales the behavior of periodic fluctuations.
-A plateau is reached around \SI{25}{km^{2}.s^{-2}} at a separation of \SI{14}{pc} and a maximum \(B(r)\) value of \SI{31}{km^{2}.s^{-2}} at a separation of \SI{36}{pc}. 
-From this point the structure functions shows consistent values around \SI{24}{km^{2}.s^{-2}} and finally there is a rise in \(B(r)\) up to \SI{29}{km^{2}.s^{-2}} at a separation of \SI{91}{pc}.
-
-In the Figure~\ref{fig:strucfunc-fit-N595}a we show the structure function of NGC 595.
-The seeing is \SI{0.5}{pc} (\(s_0\)=\SI{0.12}{\arcsecond}) and for this region only the first point is below the true model and starting from \SI{2}{pc} there is a good agreement between the observed structure function.
-The correlation length is 12\(\pm\)1 pc at a \(\sigma^2\pos\) of 56\(\pm\)2 \(\text{km}^2 \text{s}^{-2}\) and an index of 1.3\(\pm\)0.05.
-At large scales the structure function behave following the tapered fluctuations behavior.
-A maximum \(B(r)\) value of \SI{104}{km^{2}.s^{-2}} is reached at \SI{33}{pc}. 
-From there the structure functions decays following and inhomogeneous pattern until it reaches \SI{54}{km^{2}.s^{-2}} at a separation of \SI{211}{pc}.
-
-In the Figure~\ref{fig:strucfunc-fit-N604H}a we show the structure function of NGC 604.
-The structure function present clear characteristics of periodic oscillations at large scales.
-The seeing is \SI{2.2}{pc} (\(s_0\)=\SI{0.53}{\arcsecond}) and the structure function of this region lies below the true model for most of the separation range.
-The correlation length is 9\(\pm\)3 pc at a \(\sigma^2\pos\) of 81\(\pm\)25 \(\text{km}^2 \text{s}^{-2}\) and has an index of 1.3\(\pm\)0.05.
-A periodic pattern for the structure function appears with a maximum \(B(r)\) value of \SI{143}{km^{2}.s^{-2}} that is reached at \SI{60}{pc}, then the oscillation cause a minimum of \SI{54}{km^{2}.s^{-2}} at \SI{133}{pc} and finally it goes back up again at \SI{211}{pc} to a \(B(r)\) value of \SI{123}{km^{2}.s^{-2}}.
-
-The EON structure function is shown in Figure~\ref{fig:strucfunc-fit-OrionLH}a.
-This region presents a tapered behavior considering the inhomogeneous fluctuations of Figure~\ref{fig:model-strucfunc}b.
-This observations are heavily affected by the noise which presents a value of \SI{6}{km^{2}.s^{-2}} which is larger that the \(\sigma^2\pos\) \SI{5}{km^{2}.s^{-2}}.
 

### 2022-03-11 strucfunc_paper.tex
Minor edit

@@
 HV is located near 'Hodge OB 8' and HX is located near 'Hodge OB13'  \citep{1999PASP..111.1382O}.
+\citet{1993PASJ...45..693T} realize a study on the kinematics of HX and HV.
 
@@
 the probability density function (PDF) of \(V_c\).
-This PDF for each region is shown in Figure~\ref{fig:hist}
+This PDF for each region is shown in Figure~\ref{fig:pdfs}
 on a common velocity scale and arranged in order of decreasing \(\sigma\pos\).
@@
  \centering
- \includegraphics[width=5in]{Figures/Hist}\par
+ \includegraphics[width=5in]{Figures/pdfs}\par
  \caption{
@@
  }
- \label{fig:hist}
+ \label{fig:pdfs}
 \end{figure*}
@@
 \label{sec:second-order-struct}
-% One of the fundamental properties of turbulent clouds must be spatial fluctuations in velocity and density.                                     
-% These fluctuations are observed as projected spatial fluctuations in the average line-of-sight velocity and integrated column density.
-% It is possible to describe the statistical properties of these fluctuations if they are assumed as a product of a stochastic field \citep{1984ApJ...277..556S}. 
-% This previous assumption give us the ability to apply statistical tools to the velocity field and the analysis of the velocity pattern is reduced to the calculation of the averages and correlations.
 
@@
   Note that the full-width half maximum (FWHM) seeing width is
-  \(2 (2 \ln 2)^{1/2} s_0 \approx 2.35 s\).
+  \(2 (2 \ln 2)^{1/2} s_0 \approx 2.35 s_0\).
 }
@@
   \,  S(r; s_0, r_0) + B_{\text{noise}}
-\label{eq:sf-corrected}
+\label{eq:sf-functional}
 \end{multline}
-
-An example model structure function that is affected by both seeing and noise
+An example of this equation is shown by the red line in Figure~\ref{fig:model-strucfunc}.
 
@@
 
-Considering the previous models we obtain the final form of our proposed structure function functional:
-%
-\begin{equation}\label{eq:sf-functional}
-B_{\text{func}}(r) = B(r; \beta r_0, \beta \sigma^2,m) \times S(r; s_0, r_0) + B_{\text{noise}}
-\end{equation}
-%
-where the term \( B_{\text{noise}}\) is a correction factor that considers the instrument noise at small scales.
-This noise would have the effect of flattening the structure function by removing the effects of the fluctuations which would be interpreted as an uncorrelated field.
-
-The results obtained with equation \ref{eq:Br} are use in a non-linear least-squares fit with the equation \ref{eq:sf-functional} used as an objective function.
-For this purpose we use the \textit{python} package \textit{lmfit} \citep{newville_matthew_2014_11813} where the equation \ref{eq:Br} and \ref{eq:sf-functional} are use in a chi-square statistic defined as:
-%
-%\begin{equation}\label{eq:chi}
-%  \chi^2 = \sum_i ^N \frac{[y_i^{\text{measure}}-y_i^{\text{model}} (\boldsymbol{v})]^2}{\epsilon_i ^2}
+%\begin{equation}\label{eq:sf-functional}
+%B_{\text{func}}(r) = B(r; \beta r_0, \beta \sigma^2,m) \times S(r; s_0, r_0) + B_{\text{noise}}
 %\end{equation}
-%
-%
-\begin{equation}\label{eq:chi}
-  \chi^2 = \sum_i ^N \frac{[B(r)-B_{\text{func}}(r;r_0, \sigma^2\pos, m, s_0, B_{\text{noise}})]^2}{\varepsilon_i ^2}
-\end{equation}
-%
-where the turbulent parameters are \(r_{0}\)\ , \(\sigma^2\pos\) and \(m\), and the observational constraints \(s_0\) and \( B_{\text{noise}}\).
-This procedure calculate a value \(\chi\) to be minimized scaled by the inverse of the uncertainty \(\varepsilon\) in the data.
-To obtain the confidence intervals we use the minimization procedure \textit{emcee} \citep{2013PASP..125..306F} which is a \textit{python} implementation of the affine-invariant ensemble sampler for Markov chain Monte Carlo (MCMC) by \citet{2010CAMCS...5...65G}.
-%Using these procedure we obtain the posteriors for our model and the parameters in equation~\ref{eq:chi}.
-
-%In this way we want to avoid one fundamental problem in the interpretation of the structure function. 
-%The slope in the majority of previous studies and hence, the correlation length, is obtained without a formal procedure. 
-%The traditional way to find the correlation length it is to determine a particular range of ascending values in the structure function. 
-%If this increase in values is stopped or reversed it is commonly assumed that one particular inertial range has been found. 
-%In some cases this procedure keeps going up to large scales, giving two or more inertial regimes leading to an erroneous interpretation of multiple inertial scales.
 
@@
 
+\subsubsection{Model fitting and estimation of confidence intervals}
+\label{sec:model-fit}
+
+The results obtained with equation \ref{eq:Br} are use in a non-linear least-squares fit with the equation \ref{eq:sf-functional} used as an objective function.
+For this purpose we use the \textit{python} package \textit{lmfit} \citep{newville_matthew_2014_11813} which implement a chi-square statistic defined as:
+%
+%\begin{equation}\label{eq:chi}
+%  \chi^2 = \sum_i ^N \frac{[y_i^{\text{measure}}-y_i^{\text{model}} (\boldsymbol{v})]^2}{\epsilon_i ^2}
+%\end{equation}
+%
+%
+\begin{equation}\label{eq:chi}
+  \chi^2 = \sum_i ^N \frac{[B(r)-B_{\text{func}}(r;r_0, \sigma^2\pos, m, s_0, B_{\text{noise}})]^2}{\varepsilon_i ^2}
+\end{equation}
+%
+where the turbulent parameters, \(r_{0}\)\, \(\sigma^2\pos\) and \(m\), and the observational constraints \(s_0\) and \( B_{\text{noise}}\), are the set of variables to be optimized in the fit.
+This procedure calculate a value \(\chi\) to be minimized scaled by the inverse of the uncertainty \(\varepsilon\) in the data using the Levenberg-Marquardt (LM) method.
+Then we proceed to obtain the confidence intervals using the minimization procedure \textit{emcee} \citep{2013PASP..125..306F} which is a implementation of the affine-invariant ensemble sampler for Markov chain Monte Carlo (MCMC) by \citet{2010CAMCS...5...65G}.
+
 \section{Results}\label{sec:results}
@@
 In this section we present and describe the second-order structure results.
-The structure functions are plotted against separation in parsecs and we also show the posteriors of the turbulent parameters using the analysis discussed in section~\ref{sec:methods-apply}.
-
-\subsection{HII regions second-order structure functions and turbulent parameters}
+The structure functions are plotted against separation in parsecs and we also show the posteriors of the parameters discussed in the previous section.
+
+\subsection{HII regions second-order structure functions}
 
@@
 \ref{fig:velocity-maps}.
-In the plots the solid circles indicate the points we use in the non-linear regression analysis (see section~\ref{sec:methods-apply}), while the open circles are the points of the structure function that where left out.
-The criteria for the previous considerations is that the structure function at large separations is affected by the inhomogeneties of the velocity field (see section-\ref{sec:limit-model-struct}), hence the reason that large separation values are not considered for the fit of our model.
+In the plots the solid circles indicate the points we use in the non-linear regression analysis (see section~\ref{sec:model-fit}), while the open circles are the points of the structure function that where left out.
+The criteria for the previous considerations is that the structure function at large separations is affected by the inhomogeneties of the velocity field (see section-\ref{sec:limit-model-struct}), hence the reason that large separation values are not used since they are not consider in our model.
 In some cases, at the smallest separations we merge a couple of the structure functions points under the assumption that those would be heavily affected by the seeing and the rest would be coincident with the power-law behavior.
@@
 The vertical dashed line indicates the correlation length, \(r_0\), and the horizontal dashed line indicates the true variance of the velocity fields, \(\sigma^2\).
-The vertical and horizontal dotted lines shows the value of the observational considerations: the rms seeing, \(s_0\) and the value of the noise, \(B_{\text{noise}}\).
+The vertical and horizontal dotted lines shows the value of the observational considerations: the rms seeing, \(s_0\) and the noise, \(B_{\text{noise}}\).
+These values were obtained using the LM method.
 For the dashed and dotted lines the overlapping translucent boxes indicate the confidence intervals in 1-sigma (dark shaded area) and 2-sigma (light shaded area) obtained from the MCMC analysis.
 The light shaded areas in the plot show where the separation \(r\) is above half of the box size, \(L\), which is indicated with a vertical dotted line.
-To present our results in the next paragraphs the small scales would refer to the separations \(r < r_0\) and large scales would refer to separations \(r > r_0\).
+%For the discussion of our results in the next paragraphs the small scales would refer to the separations \(r < r_0\) and large scales would refer to separations \(r > r_0\).
 
@@
 Valid scales are consider above the separation of \SI{0.002}{pc} (\(s_0\)=\SI{1}{\arcsecond}).
-In this case we merge the first three points.
-From there until separations of \SI{0.003}{pc} all points within this range fall below the true model showing that they are affected by the seeing. 
-The correlation length for the Orion core is \SI{0.07 \pm 0.01}{pc}, it has a \(\sigma^2\pos\) of \SI{12 \pm 1}{km^{2}.s^{-2}} and an index of \num{1.07 \pm 0.02}.
+In this case we merge the first three points of the structure function.
+From \SI{0.002}{pc} until \SI{0.003}{pc} all points fall below the true model showing that they are affected by the seeing. 
+The correlation length for the Orion core is \SI{0.07}{pc}, it has a \(\sigma^2\pos\) of \SI{12}{km^{2}.s^{-2}} and an index of \num{1.07}.
 The structure function of the Orion core behaves accordingly to the tapered case of inhomogeneous fluctuations (see Figure~\ref{fig:model-strucfunc}b).
-At large scales there is a plateau around \SI{22}{km^{2}.s^{-2}} reached at \SI{0.25}{pc}.
-Above separations of \SI{0.3}{pc} the structure function decays reaching a separation of \SI{0.5}{pc} with a value of \SI{7}{km^{2}.s^{-2}}.
+At \SI{0.25}{pc} there is a plateau around \SI{22}{km^{2}.s^{-2}}.
+Above separations of \SI{0.3}{pc} the structure function decays to a value of \SI{7}{km^{2}.s^{-2}} at  \SI{0.5}{pc}.
 
@@
 The Lagoon nebula presents a non-uniform behavior below the correlation length but it is possible to see the characteristic ascending values of the structure function.
-The turbulent parameters that fits our model are a \(r_0\) of \SI{1 \pm 0.2}{pc}, a \(\sigma^2\pos\) of \SI{7 \pm 1}{km^{2}.s^{-2}} and an index of \num{1.13 \pm 0.01}.
-At large scales there is an indication of some periodic behavior with a very large amplitude of ascending \(B(r)\) at largest separation.
+The turbulent parameters that fits our model are a \(r_0\) of \SI{1}{pc}, a \(\sigma^2\pos\) of \SI{7}{km^{2}.s^{-2}} and an index of \num{1.17}.
+At large scales there is an indication of some periodic behavior followed by ascending \(B(r)\) values at largest separation.
 The first maximum value of \(B(r)\) in the order of 2\(\sigma^2\pos\) is \(\sim\)\SI{14}{km^{2}.s^{-2}} at a separation of \(\sim\)\SI{2.5}{pc}. 
 Considering an oscillating behavior at \SI{4.5}{pc} a minimum value of \SI{11}{km^{2}.s^{-2}} is reached.
-From this point the structure function keeps going up until it reaches \SI{66}{km^{2}.s^{-2}} around \SI{20}{pc}.
+From this point the structure function ascends until it reaches \SI{66}{km^{2}.s^{-2}} around \SI{20}{pc}.
 
@@
 As the Lagoon nebula, Carina also shows a non-uniform behavior below the correlation length.
-The correlation length is \SI{0.56 \pm 0.04}{pc} pc at a \(\sigma^2\pos\) of \SI{18 \pm 1}{km^{2}.s^{-2}}  and an index of \num{1.14 \pm 0.01}.
-At larges scales the structure function of the Carina nebula follows a pattern that closely resembles the homogeneous fluctuation of Figure~\ref{fig:model-strucfunc}a.
+The correlation length is \SI{0.56}{pc} pc at a \(\sigma^2\pos\) of \SI{18}{km^{2}.s^{-2}} and an index of \num{1.14}.
+At larges scales the structure function of the Carina nebula follows a pattern that resembles the homogeneous fluctuation of Figure~\ref{fig:model-strucfunc}a.
 The structure function reaches a plateau around \SI{36}{km^{2}.s^{-2}} at \(\sim\) \SI{2}{pc}.
-When \(r >\)\SI{6}{pc} the structure functions resembles a periodic behavior with a small amplitude.
+When \(r >\)\SI{6}{pc} the structure functions shows a small amplitude periodic pattern around 2\(\sigma^2\pos\).
 
 For Carina and Lagoon nebula, the velocity fields are obtained from the FLAMES multi-fiber instrument (section~\ref{sec:flames-multi-fiber}). 
-We can see from Figure~\ref{fig:velocity-maps} that observations from this instrument do not give uniform maps as the other instruments. 
-Instead the discrete fiber positions are diversely located across the FOV.
+We can see from Figure~\ref{fig:velocity-maps} that observations from this instrument do not give uniform maps as the others. 
+Instead, the discrete fiber positions are diversely located across the FOV.
 This would affect the structure function since the values are not adjacent as the other observations.
@@
 In this case we merge the first three points of the structure function.
-For this region the points are above the seeing value which is \SI{0.07}{pc} (\(s_0\)=\SI{0.23}{\arcsecond}) and the first ten points lie below the true model.
+The seeing value is \SI{0.07}{pc} (\(s_0\)=\SI{0.23}{\arcsecond}).
+For this region the first ten points lie below the true model.
 At separations above \SI{0.4}{pc} the observed structure functions is coincident with the true model. 
-The correlation length is \SI{2 \pm 0.1}{pc} at a \(\sigma^2\pos\) of \SI{3 \pm 1}{km^{2}.s^{-2}} and an index of \num{0.76 \pm 0.02}.
-For scales above \SI{9}{pc} with a \(B(r)\) value of \SI{70}{km^{2}.s^{-2}} a periodic behavior is seen .
-Starting from a separation of \SI{12}{pc} and a \(B(r)\) value of \SI{65}{km^{2}.s^{-2}} the structure function keeps ascending until it reaches \SI{146}{km^{2}.s^{-2}} at \SI{24}{pc}.
+The correlation length is \SI{2}{pc} at a \(\sigma^2\pos\) of \SI{35}{km^{2}.s^{-2}} and an index of \num{0.80}.
+For scales above \SI{12}{pc} and a \(B(r)\) value of \SI{65}{km^{2}.s^{-2}} the structure function shows a pattern of ascending values until it reaches \SI{146}{km^{2}.s^{-2}} at \SI{24}{pc}.
 
@@
 The seeing value for this regions is \SI{0.16}{pc} (\(s_0\)=\SI{0.7}{\arcsecond}) and just one point of the structure function is below this value.
-Until a separation of \SI{1.7}{pc} the structure function lies below the true model.
-The correlation length is \SI{4 \pm 0.2}{pc} at a \(\sigma^2\pos\) of \SI{300 \pm 9}{km^{2}.s^{-2}} and an index of \num{0.84 \pm 0.04}.
-30 Doradus structure function presents a behavior of tapered fluctuations.  
+Until a separation of \SI{1.7}{pc} is reached, the structure function lies below the true model.
+The correlation length is \SI{4}{pc} at a \(\sigma^2\pos\) of \SI{297 \pm 9}{km^{2}.s^{-2}} and an index of \num{0.85}.
+At large separations 30 Doradus structure function presents a behavior of tapered fluctuations.  
 The maximum \(B(r)\) value is \SI{655}{km^{2}.s^{-2}} at a separation of \SI{21}{pc}. 
@@
 In the Figure~\ref{fig:strucfunc-fit-HV}a we show the structure function of Hubble V.
-For the observations coming from the TAURUS-II instrument there wasn't any merging of points.
+For the observations coming from the TAURUS-II instrument there wasn't any merging of points at small scales.
 The value of the seeing for this regions is \SI{0.5}{pc} (\(s_0\)=\SI{0.2}{\arcsecond}).
-All the structure function points lies below the true model which would indicate that the seeing is affecting the observed structure function.
-The correlation length is \SI{3.4 \pm 0.3}{pc} at a \(\sigma^2\pos\) of  \SI{10 \pm 1}{km^{2}.s^{-2}} and an index of \num{0.74 \pm 0.10}.
+All the structure function points lies below the true model.
+The correlation length is \SI{3.5}{pc} at a \(\sigma^2\pos\) of  \SI{10}{km^{2}.s^{-2}} and an index of \num{0.75}.
 The maximum \(B(r)\) value is \SI{18}{km^{2}.s^{-2}} at a separation of \SI{25}{pc}. 
-From there \(B(r)\) values descends until \SI{14}{km^{2}.s^{-2}} at \SI{45}{pc}, then it rises for the next point at \SI{50}{pc} with a value of \SI{15}{km^{2}.s^{-2}} and finally the structure functions descends at \SI{9}{km^{2}.s^{-2}} for a separation of \SI{70}{pc}.
+From there \(B(r)\) values descends until it reaches \SI{14}{km^{2}.s^{-2}} at \SI{45}{pc}, then it rises for the next point at \SI{50}{pc} with a value of \SI{15}{km^{2}.s^{-2}}.
+Finally the structure functions descends at \SI{9}{km^{2}.s^{-2}} for a separation of \SI{70}{pc}.
 
 The Hubble X structure function is shown in Figure~\ref{fig:strucfunc-fit-HX}a.
-The seeing is \SI{0.006}{pc} (\(s_0\)=\SI{0.24}{\arcsecond}) and as in Hubble V the observed structure function lies below the true model.
-The correlation length is \SI{4 \pm 0.4}{pc} at a \(\sigma^2\pos\) of \SI{16 \pm 1}{km^{2}.s^{-2}} and an index of \num{0.88 \pm 0.14}.
-The structure functions presents at large scales the behavior of periodic fluctuations with a small amplitude.
+The seeing is \SI{0.6}{pc} (\(s_0\)=\SI{0.24}{\arcsecond}) and as in Hubble V the observed structure function lies below the true model.
+The correlation length is \SI{4}{pc} at a \(\sigma^2\pos\) of \SI{15}{km^{2}.s^{-2}} and an index of \num{0.93}.
 A plateau is reached around \SI{25}{km^{2}.s^{-2}} at a separation of \SI{14}{pc} and a maximum \(B(r)\) value of \SI{31}{km^{2}.s^{-2}} at a separation of \SI{36}{pc}.
-From this point the structure functions shows consistent values around \SI{24}{km^{2}.s^{-2}} and finally there is a rise for the last point to \SI{29}{km^{2}.s^{-2}} at a separation of \SI{91}{pc}.
 
 In the Figure~\ref{fig:strucfunc-fit-N595}a we show the structure function of NGC 595.
-The seeing is \SI{0.5}{pc} (\(s_0\)=\SI{0.12}{\arcsecond}) and for this region only the first two points are below the true model. 
-The correlation length is \SI{12 \pm 1}{pc} at a \(\sigma^2\pos\) of \SI{56 \pm 2}{km^{2}.s^{-2}} and an index of \num{1.3 \pm 0.05}.
-At large scales the structure function behave following the tapered fluctuations behavior.
+The seeing is \SI{0.3}{pc} (\(s_0\)=\SI{0.1}{\arcsecond}) and for this region only the first two points are below the true model. 
+The correlation length is \SI{12}{pc} at a \(\sigma^2\pos\) of \SI{54}{km^{2}.s^{-2}} and an index of \num{1.3}.
+At large scales the structure function behaves following the tapered fluctuations pattern.
 A maximum \(B(r)\) value of \SI{104}{km^{2}.s^{-2}} is reached at \SI{33}{pc}. 
@@
 In the Figure~\ref{fig:strucfunc-fit-N604H}a we show the structure function of NGC 604.
-The seeing is \SI{1.2}{pc} (\(s_0\)=\SI{0.28}{\arcsecond}) and the structure function of this region lies below the true model for most of the separation range.
-The correlation length is \SI{9 \pm 3 }{pc} at a \(\sigma^2\pos\) of \SI{68 \pm 6}{km^{2}.s^{-2}} and has an index of \num{1.3 \pm 0.05}.
+The seeing is \SI{1.7}{pc} (\(s_0\)=\SI{0.42}{\arcsecond}) and the structure function of this region lies below the true model for most of the separation range.
+The correlation length is \SI{10}{pc} at a \(\sigma^2\pos\) of \SI{71}{km^{2}.s^{-2}} and has an index of \num{1}.
 The structure function present clear characteristics of periodic oscillations at large scales.
@@
 The EON structure function is shown in Figure~\ref{fig:strucfunc-fit-OrionLH}a.
-This observations are heavily affected by the noise which presents a value of \SI{6}{km^{2}.s^{-2}} which is larger that the \(\sigma^2\pos\) \SI{5}{km^{2}.s^{-2}}.
+This observations are heavily affected by the noise which presents a value of \SI{6}{km^{2}.s^{-2}} which is larger that the \(\sigma^2\pos\) value of \SI{4}{km^{2}.s^{-2}}.
 
@@
 These plots shows the one and two dimensional projections of the posterior probability distributions of the parameters used in equation \ref{eq:chi}.
-They also show the marginalized distribution for each parameter independently in the histograms along the diagonal and then the marginalized two dimensional distributions in the other panels making possible to visualize all of the covariances between parameters \citep{2017ascl.soft02002F}.
+They also show the distribution for each parameter independently in the histograms along the diagonal and then the marginalized two dimensional distributions in the other panels making possible to visualize all of the covariances between parameters \citep{2017ascl.soft02002F}.
 The contours in the plots reflect the 95\(\%\), 99\(\%\), 99.5\(\%\) and 99.9\(\%\) confidence intervals.
 
-Table \ref{tab:Res} presents the turbulent parameters results along the obtained observational constraints mentioned in the paragraphs above.
+Table \ref{tab:Res} presents the turbulent parameters and observational constraints values mentioned in the paragraphs above.
+The confidence intervals for these values are up to 2-sigma of the posteriors.
 The second column correspond to the variance \(\sigma^2\pos\) of the velocity field.
 The \(B_{\text{noise}}\) value is shown in the third column which would be the minimum squared velocity difference that could be measure by the instrument.
-The forth column in Table \ref{tab:Res} shows the seeing value in parsecs, \(s_0\), which represent the minimum value of the separation which would valid for the observed structure function. 
+The forth column in Table \ref{tab:Res} shows the rms seeing value in parsecs, \(s_0\), which represent the minimum value of the separation which would valid for the observed structure function. 
 The fifth column shows the correlation value \(r_0\) in parsecs.
@@
 The sixth column indicates the size of each observational box in parsecs.
-The index \(m\) is shown in the last column and the range covered by the power-law index in our HII region sample goes from 0.7 to 1.5.
-The interpretation of our results is developed in the next section.
+The index \(m\) is shown in the seventh column.
+The range covered by the power-law index goes from 0.7 to 1.5.
+The eighth column show the ratio \(L / r_0\)
+The last column shows the FWHM seeing in arcsec.
+%The interpretation of our results is developed in the next section.
 
@@
 
+In the next sections we discuss the application and interpretation of the turbulent parameters we obtained in our results.
+We present a resume of the turbulence theory and its validation to \hii{} regions.
+It is also mentioned some physical processes that contribute to stirring the ionized gas and the possibility that they are responsible for the observed velocity fluctuations.
+We present the most important correlations between the turbulent parameters and physical properties of our \hii{} region sample and finally we discuss our results in the context of previous structure functions.
+
 \subsection{Turbulence}\label{sec:turbulence-theory}
@@
 The idea to treat the ionized regions from a fluid mechanic view is intuitive if we consider the continuum hypothesis. 
-We validate this hypothesis using the Knudsen number defined as \(Kn \equiv \lambda / l\), where \(\lambda\) is the mean free path of the medium and \(l\) a characteristic length of the phenomenon we are studying.
-Taking into account a \(\lambda_{\text{HII}}\) of \SI{2.7e-7}{pc} \citep{1941ApJ....93..369S} and a \(l_{\text{HII}}\) of \SI{1}{pc} for ionized regions we obtained \(Kn \approx 10^{-7}\), while in general the continuum approach is valid for \(Kn \ll 1\).
+We validate this hypothesis using the Knudsen number defined as \(\text{Kn} \equiv \lambda / l\), where \(\lambda\) is the mean free path of the medium and \(l\) a characteristic length of the phenomenon we are studying.
+Taking into account a \(\lambda_{\text{HII}}\) of \SI{2.7e-7}{pc} \citep{1941ApJ....93..369S} and a \(l_{\text{HII}}\) of \SI{1}{pc} for ionized regions we obtained \(\text{Kn} \approx 10^{-7}\), while in general the continuum approach is valid for \(\text{Kn}\ll 1\).
 
@@
 These turbulent flows tends to be unsteady, irregular and chaotic, and the turbulent motions are observed in many scales. 
-The turbulent flows are associated with a high Reynolds numbers which is defined as \(Re = l v_{l} / \nu \), where \(v_{l}\) is a characteristic velocity in the fluid system and \(\nu\) is the kinematic viscosity of the medium.
-Experiments have shown that a flow which is laminar become turbulent when increasing the velocity (i.e., increasing the \(Re\)) and a large range of velocity fluctuation appear at all scales.
-A high \(Re\) reflects high ratio of the advection/difussion terms of the Navier-Stokes equations, being interpreted as that the inertial forces taking over the viscous ones. 
+The turbulent flows are associated with a high Reynolds numbers which is defined as \(\text{Re} = l v_{l} / \nu \), where \(v_{l}\) is a characteristic velocity in the fluid system and \(\nu\) is the kinematic viscosity of the medium.
+Experiments have shown that a flow which is laminar become turbulent when increasing the velocity (i.e., increasing the Re) and a large range of velocity fluctuation appear at all scales.
+A high Re reflects high ratio of the advection/difussion terms of the Navier-Stokes equations, being interpreted as that the inertial forces taking over the viscous ones. 
 Hence it is possible to assume that if viscosity is not dominant in a flow, this flow would be turbulent.
@@
 The concept of the energy spectrum assumes that the energy is cascading down inside the flow from the largest to the smallest scales.
-The different scales in the energy cascade are defined based on their \(Re\).
-In one side of the spectrum there is the energy injection scale, \(L_I\), that is related to the largest vortices, called the integral scales, where \(Re \rightarrow \infty\).
-On the other side of the spectrum there is the dissipation of energy at small scales, \(l_I\), where  \(Re \rightarrow 1\) and it is assumed that small vortices are responsible for the friction that dissipates the energy flux into thermal energy.
+The different scales in the energy cascade are defined based on their Re.
+In one side of the spectrum there is the energy injection scale, \(L_I\), that is related to the largest vortices, called the integral scales, where \(\text{Re} \rightarrow \infty\).
+On the other side of the spectrum there is the dissipation of energy at small scales, \(l_I\), where  \(\text{Re} \rightarrow 1\) and it is assumed that small vortices are responsible for the friction that dissipates the energy flux into thermal energy.
 In between there is the inertial range, \(l_d  << l << L_I\), where in a stationary case the energy transfer is at a constant rate.
@@
 \end{equation}
+%
 the average is over all the positions \(\boldsymbol{x}\) and directions \(\boldsymbol{r}\). 
@@
 
-\subsection{Interpretation of the turbulent parameters and origins of interstellar turbulence}\label{sec:interpretation-origin}
-
-In the next sections we discuss the use and interpretation of the turbulent parameters we obtain in the previous section.
-Also, we mentioned some physical processes that contribute to stirring the ionized gas and the possibility that they are responsible for the observed velocity fluctuations.
+\subsection{Origins of interstellar turbulence}\label{sec:origins-turbulence}
+
+In the particular case of GEHR, as supersonic motions dissipate energy by shocks in time scales relatively short compared with the age of the region, it is necessary an energy source to replenish continuously the energy lost.
+From the observed velocity  dispersion \(\sigma\), and assuming that we have an isotropic distribution of velocities,  we can estimate the 3D velocity dispersion by \(\sigma_\mathrm{3D} = \sqrt{3} \sigma\).
+The mass of the ionized gas together with the velocity dispersion \(\sigma_\mathrm{3D}\)  are used to estimate the kinetic energy in the GEHRs.
+As these objects have typically  masses of the ionized gas of \num{\sim e5} M\(_{\sun}\) and velocity dispersion values  of \SI{\sim 20}{km.s^{-1}} \citep{1984ApJ...287..116K}, typical kinetic energy of the ionized gas is \SI{\sim e51}{ergs}.
+
+In the standard Kolmogorov model, the energy spectrum of turbulence becomes dependent only on \(\epsilon\), the mean dissipation of energy per unit time per unit mass of fluid,  with the inertial forces transferring without losses kinetic energy from larger to smaller turbulent elements within the inertial range.
+Let \(L_c\) be the characteristic length of the largest eddies, and \(\delta v\) the typical velocity.
+
+We have then that \(\epsilon = (\delta v)^{3}/L\). In steady-state turbulence, equilibrium exists between the energy input and the energy dissipation rates. 
+Although the present observations indicate that turbulence in \hii{} regions may not follow the Kolmogorov model, with energy input occurring at different scales, so that a  truly inertial range may not exist at all, lets us make a crude estimation of the  amount of energy transferred between scales using this simple model.
+Assuming the above figures for the mass of the gas and velocity dispersion, \(\delta v = \sigma_\mathrm{3D}\),  and a \(L_c\) of \SI{100}{pc}, we obtain that the energy transfer rate \SI{\sim e37}{erg.s^{-1}}, and  the time scale for energy transfer, \(L/\delta v \), would be of few million years.
+
+There are several energy sources that could provide or contribute  to the energy required: of the order of kpc, the differential rotations of the galaxy that produces shear at large scale, at scales of the order of hundreds of pc, supernova explosions inject a large amount of kinetic energy.
+At scales of several tens of pc the expansion of \hii{} regions and stellar winds are a source of energy and, bipolar flows, shocks, jets and champagne flows inject energy at small scales about one tenth of a pc.
+
+The lack of precise information on how these mechanism contribute to the emission line broadening make a non-trivial task to determine at what extent they play a role in the interstellar turbulence, contributing to the complexity of the extraction of pure turbulent motions from velocity profiles in nebulae \citep{2011MNRAS.413..705L,arthur2016turbulence}.
+
+\subsection{Interpretation of the turbulent parameters}\label{sec:interpretation-parameters}
 
@@
 The most probable scenario is that the velocity fluctuations are consequence of the combination of various mechanism.
-The main energy sources are, of the order of kpc, the differential rotations of the galaxy that produces shear at large scale, at scales of the order of hundreds of pc, supernova explosions inject a large amount of kinetic energy.
-At scales of several tens of pc the expansion of \hii{} regions and stellar winds are a source of energy and, bipolar flows, shocks, jets and champagne flows inject energy at small scales about one tenth of a pc.
-The lack of precise information on how these mechanism contribute to the emission line broadening make a non-trivial task to determine at what extent they play a role in the interstellar turbulence, contributing to the complexity of the extraction of pure turbulent motions from velocity profiles in nebulae \citep{2011MNRAS.413..705L,arthur2016turbulence}.
-
 Many of these mechanisms, at some extent, affect all the \hii{} regions studied in this work.
@@
 
-Although the Orion core and EON, and NGC 604 have different \(r_0\) is not clear if it truly reveal a concrete aspect of the energy input mechanism mentioned above.
-Orion mainly energy input comes from one star, meanwhile NGC 604 has more than 200 OB stars including WR stars. 
+Although the Orion core, the EON, and NGC 604 have different \(r_0\) is not clear if it truly reveal a concrete aspect of the energy input mechanism mentioned above.
+Orion main energy input comes from one star, meanwhile NGC 604 has more than 200 OB stars including WR stars. 
 The Orion core also presents Herbig-Haro objects, which aren't possible to resolve for more distant regions.
@@
 \centering 
-\includegraphics[width=3in]{Figures/los-vs-pos}
+\includegraphics[width=3in]{Figures/corr-los-vs-pos}
 \caption{The $\sigma$-$\sigma_{\text{los}}$ plane. The dotted line represents slope equal to unity.}
@@
 \centering 
-\includegraphics[width=3in]{Figures/svsL}
+\includegraphics[width=3in]{Figures/corr-svsL}
 \caption{The log \(\sigma\pos\) - log $L(H_{\alpha})$ plane derived form our results an data in the literature.
@@
 \centering 
-\includegraphics[width=3in]{Figures/rvsS}
+\includegraphics[width=3in]{Figures/corr-rvsS}
 \caption{Same as Fig. \ref{fig:rvsR} but for the log \(r_0\) - log \(S\) plane. }
@@
 Their velocity centroid \(\sigma\) is 5.92 $\pm$ 0.15 km s\(^{-1}\) while we have 7.48 $\pm$ 1.4 km s\(^{-1}\) which is consistent.
-Due to the different observations and methodologies a comparison between structure functions is not possible.
+Due to the different observations and methodologies a direct comparison between structure functions is not possible.
+
+\subsection{Final remarks}
+
+The observations point out to the existence of spatial correlation between velocities, that could be interpreted as turbulence. 
+Arguments against the existence of true, isotropic turbulence can be raised as, for example: i) the histograms of velocity are not always Gaussian, ii) only a fraction of the integrated emission lines of the \hii{} regions show true Gaussian profiles.
+The asymmetry in the emission line indicates coherent mass flow motions, 
+and sometimes is considered incompatible with turbulence. However, turbulence is in fact 
+a mixture of coherent and chaotic flows. 
+Only at the regime of the so-called fully developed turbulence the non-linear phenomena dominate completely the movement and the chaotic flow prevail. 
+The problem here is that a straightforward test for any turbulent model is a big challenge, as we are in the presence of many entangled effects. 
+However, the circumstantial evidence in favor of the existence of turbulent motions in \hii{} regions is overwhelming, and many are the potential sources of energy to create and maintain turbulence during the lifetime of an \hii{} region.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-The previous analysis was able to characterize the turbulence by determining a single inertial scale where the ionized gas behavior can be described by means of a power law.
-To determine the inertial scale more precisely than in previous works, a new functional form was proposed for the second-order structure function that considers observational effects such as: seeing, noise and the size of the observational box.
-These effects had not been considered in detail before and have important consequences in obtaining the inertial scale.
-
-The new functional form of the structure function is used as an objective function in a non-linear regression to accurately determine the important parameters related to turbulence which are: the correlation length, the exponent of a power law that fits the results and the real variance of the region.
-
-The structure function used in this work does not reveal the precise characteristic of turbulence, but the statistical results that it provides allow us to determine a distinction between correlated or random velocity fluctuations in the photoionized gas, in which the presence of correlations in the velocity field is a inherent property of turbulence.
-Although this work is not conclusive about the nature of photoionized gas turbulence and a precise description of the origin and implications of these turbulent motions is out of the scope of our investigation, we believe that the tools presented here (see section~\ref{sec:methods-apply}) guarantee a more realistic approach to determine and understand the structure function.
-
-Our analysis can be expanded to other HII regions with the possibility of comparing the results between them since the method guarantees homogeneity and the ability to develop a future catalog of these regions in a coherent way.
-It could even be used to investigate the velocity fields of other phases of the interstellar medium.
-The study of turbulence between ionized regions and the molecular clouds that give them birth can be carried out in a concise way, having the correct methods with the intention of advancing the understanding of the kinematic relationships between them.
-
-%\begin{enumerate}
-%\item For 30 Doradus with an observational box size of 32 pc an index of 0.84$\pm$0.03 is obtained with an inertial scale between 0.1 and 5 pc, and with a variance of 350$\pm$21 km$^2$/s$^2$.
-
-%\item For NGC 604 with an observational box size of 173 pc an index of 0.82$\pm$0.20 is obtained with an inertial scale between 2 and 9 pc, and with a variance of 81$\pm$25 km$^2$/s$^2$.
-
-%\item For NGC 595 with an observational box size of 196 pc an index of 1.3$\pm$0.04 is obtained with an inertial scale between 0.5 and 12 pc, and with a variance of 56$\pm$1.6 km$^2$/s$^2$.
-
-%\item For NGC 346 with an observational box size of 20 pc an index of 0.78$\pm$0.02 is obtained with an inertial scale between 0.06 and 2 pc, and with a variance of 38$\pm$1.0 km$^2$/s$^2$.
-
-%\item For Orion with an observational box size of 0.45 pc an index of 1.06$\pm$0.02 is obtained with an inertial scale between 0.002 and 0.09 pc, and with a variance of 17$\pm$1.0 km$^2$/s$^2$.
-
-%\item For Carina with an observational box size of 20 pc an index of 1.36$\pm$0.30 is obtained with an inertial scale between 0.008 and 0.6 pc, and with a variance of 17$\pm$1.0 km$^2$/s$^2$.
-
-%\item For Hubble X with an observational box size of 78 pc an index of 0.94$\pm$0.12 is obtained with an inertial scale between 0.5 and 4 pc, and with a variance of 15.5$\pm$1.5 km$^2$/s$^2$.
-
-%\item For Hubble V with an observational box size of 61 pc an index of 0.72$\pm$0.09 is obtained with an inertial scale between 0.5 and 3 pc, and with a variance of 10.6$\pm$0.8 km$^2$/s$^2$.
-
-%\item For Lagoon with an observational box size of 16 pc an index of 1.12$\pm$0.09 is obtained with an inertial scale between 0.005 and 1 pc, and with a variance of 7.2$\pm$0.8 km$^2$/s$^2$.
-
-%\end{enumerate}
+%a single inertial scale where the ionized gas behavior can be described by means of a power law.
+
+Our analysis was able to characterize the velocity fields of a sample of \hii{} regions by determining a set of parameters unique to each velocity field which are: the correlation length, the exponent of a power law that fits the results through a determined range and the true velocity dispersion.
+To achieve this, a new functional form for the second-order structure function was proposed. 
+This new functional considers observational constraints such as the seeing, noise and the size of the observational box, effects that had not been considered before and play an important part in the interpretation of the structure function.
+Our proposed functional form is used as an objective function in a non-linear regression to accurately determine the set of parameters related to turbulence and to the observational constraints.
+
+The observed structure functions calculated in our work does not reveal the precise characteristic of turbulence, but the statistical results that it provides allow us to determine a distinction between correlated or random velocity fluctuations in the photoionized gas, in which the presence of correlations in the velocity field is a inherent property of turbulence.
+Although this work is not conclusive about the nature of photoionized gas turbulence and a precise description of the origin and implications of these turbulent motions is out of the scope of our investigation, we believe that the tools presented here (see section~\ref{sec:methods-apply}) guarantee a more realistic approach to determine and to the understanding the structure function.
+
+Our analysis can be easily be expanded to other \hii{} regions with the possibility of comparing the results between them since our method guarantees homogeneity, providing the possibility to develop a future catalog of \hii{} regions turbulent parameters in a concise way.
+By calculating the structure function of HII regions with different morphologies, ages, stellar content, and dynamics it would be possible to detect the presence and the importance of different sources of mechanical energy, since the structure function would be different from one object to the other as we show in the present investigation.
+
+Our methods could also been use to investigate the velocity fields of other phases of the interstellar medium.
+The study of turbulence between ionized regions and the molecular clouds that give them birth can be carried out with the aid of a correct methodology with the intention of advancing the understanding of the kinematic relationships between them.
 

### 2022-03-11 strucfunc_paper.tex
Start description of finite box effects

@@
 An example of this equation is shown by the red line in Figure~\ref{fig:model-strucfunc}.
-
-The model that consider the effect of the observational box size is:
+Note that seeing and noise have opposite effects on the slope
+of the structure function at intermediate scales:
+seeing tends to steepen the slope, while noise tends to flatten it.
+This can lead to a degeneracy between these two parameters
+when fitting observations over a limited range of separations.
+
+In Appendix~\ref{sec:finite-box-effects} we consider the effects
+on the structure function of the finite size \(L\) of the observational map.
+If the true correlation length \(r_0\) is more than a small fraction of the map size
+(approximately, \(r_0 > 0.1 L\)),
+then the apparent velocity variance \(\sigma^2'\) measured directly from the data
+is less than the true \(\sigma^2\) of the underlying fluctuations
+(see Figure~\ref{fig:finite-box-effect}).
+This is because the observed map is not large enough to sample
+the full range of velocity variations.
+At the same time, the apparent correlation length \(r_0'\) is smaller
+than the true value.
+
+However, this does not mean that the model structure function needs to be modified;
+equation
+In the limit that \(r_0 \gg L\), then \(r_0'\) becomes independent of
+
+finding that the apparent
 

### 2022-03-17 strucfunc_paper.tex
Javier changes 2022-03-16

--- 2022-03-11 strucfunc_paper.tex
@@
 %
-where the turbulent parameters are \(r_{0}\)\ , \(\sigma^2\pos\) and \(m\), and the observational constraints \(s_0\) and \( B_{\text{noise}}\).
+where the turbulent parameters, \(r_{0}\)\, \(\sigma^2\pos\) and \(m\), and the observational constraints \(s_0\) and \( B_{\text{noise}}\), are the set of variables to be optimized in the fit.
 This procedure calculate a value \(\chi\) to be minimized scaled by the inverse of the uncertainty \(\varepsilon\) in the data.
-To obtain the confidence intervals we use the minimization procedure \textit{emcee} \citep{2013PASP..125..306F} which is a \textit{python} implementation of the affine-invariant ensemble sampler for Markov chain Monte Carlo (MCMC) by \citet{2010CAMCS...5...65G}.
-%Using these procedure we obtain the posteriors for our model and the parameters in equation~\ref{eq:chi}.
-
-%In this way we want to avoid one fundamental problem in the interpretation of the structure function. 
-%The slope in the majority of previous studies and hence, the correlation length, is obtained without a formal procedure. 
-%The traditional way to find the correlation length it is to determine a particular range of ascending values in the structure function. 
-%If this increase in values is stopped or reversed it is commonly assumed that one particular inertial range has been found. 
-%In some cases this procedure keeps going up to large scales, giving two or more inertial regimes leading to an erroneous interpretation of multiple inertial scales.
+Then we proceed to obtain the confidence intervals we use the minimization procedure \textit{emcee} \citep{2013PASP..125..306F} which is a \textit{python} implementation of the affine-invariant ensemble sampler for Markov chain Monte Carlo (MCMC) by \citet{2010CAMCS...5...65G}.
 

### 2022-04-01 Corr.tex
Javier edits 2022-04-01

@@
 \hline
- log $\sigma$ &            log L(H) &   0.29 $\pm$ 0.09 &  -10.24 $\pm$ 3.53 &   0.89 &  0.001 \\
+ log $\sigma$ &            log L(H) &   0.28 $\pm$ 0.09 &  -10.02 $\pm$ 3.52 &   0.89 &  0.001 \\
     log $r_0$ &             log $S$ &   0.78 $\pm$ 0.25 &   -1.31 $\pm$ 0.52 &   0.85 &  0.002 \\
-% log $\sigma$ &  log $\sigma_{LOS}$ &   0.83 $\pm$ 0.48 &   -0.24 $\pm$ 0.56 &   0.71 &   0.02 \\
- log $\sigma$ &         log $r_{0}$ &   0.21 $\pm$ 0.17 &    0.66 $\pm$ 0.12 &   0.58 &   0.08 \\
+% log $\sigma$ &  log $\sigma_{LOS}$ &   0.82 $\pm$ 0.49 &   -0.22 $\pm$ 0.56 &   0.71 &   0.02 \\
+ log $\sigma$ &         log $r_{0}$ &   0.21 $\pm$ 0.17 &    0.66 $\pm$ 0.11 &   0.58 &  0.078 \\
       log $m$ &            log Dist &  -0.09 $\pm$ 0.07 &    1.14 $\pm$ 0.14 &  -0.57 &   0.09 \\
-      log $m$ &        log $\sigma$ &  -0.11 $\pm$ 0.21 &    0.07 $\pm$ 0.16 &  -0.42 &   0.23 \\
-      log $m$ &         log $r_{0}$ &  -0.04 $\pm$ 0.07 &    -0.0 $\pm$ 0.05 &  -0.39 &   0.26 \\
+      log $m$ &        log $\sigma$ &  -0.12 $\pm$ 0.22 &    0.08 $\pm$ 0.17 &  -0.43 &  0.211 \\
+      log $m$ &         log $r_{0}$ &  -0.04 $\pm$ 0.07 &    -0.0 $\pm$ 0.05 &   -0.4 &  0.257 \\
 \bottomrule

### 2022-04-01 strucfunc_paper.tex
Javier edits 2022-04-01
Add subscript

--- 2022-03-11 strucfunc_paper.tex
@@
 (approximately, \(r_0 > 0.1 L\)),
-then the apparent velocity variance \(\sigma^2'\) measured directly from the data
-is less than the true \(\sigma^2\) of the underlying fluctuations
+then the apparent velocity variance \(\sigma'\pos^2\) measured directly from the data
+is less than the true \(\sigma\pos^2\) of the underlying fluctuations
 (see Figure~\ref{fig:finite-box-effect}).

### 2022-04-08 strucfunc_paper.tex
Javier changes 2022-04-08

--- 2022-03-11 strucfunc_paper.tex
@@
 (approximately, \(r_0 > 0.1 L\)),
-then the apparent velocity variance \(\sigma^2'\) measured directly from the data
-is less than the true \(\sigma^2\) of the underlying fluctuations
+then the apparent velocity variance \(\sigma\pos^2\) measured directly from the data
+is less than the true \(\sigma\pos^2\) of the underlying fluctuations
 (see Figure~\ref{fig:finite-box-effect}).
@@
 In the plots the solid circles indicate the points we use in the non-linear regression analysis (see section~\ref{sec:model-fit}), while the open circles are the points of the structure function that where left out.
-The criteria for the previous considerations is that the structure function at large separations is affected by the inhomogeneties of the velocity field (see section-\ref{sec:limit-model-struct}), hence the reason that large separation values are not used since they are not consider in our model.
-In some cases, at the smallest separations we merge a couple of the structure functions points under the assumption that those would be heavily affected by the seeing and the rest would be coincident with the power-law behavior.
+The criteria for the previous considerations is that the structure function at large separations is affected by the inhomogeneties of the velocity field (see section-\ref{sec:limit-model-struct}).
+The points left our correspond to the largest separations that are not consider in our model. 
+In some cases, at the smallest separations we merge a couple of the structure functions points under the assumption that those would be heavily affected by the seeing.
 The Figures shows in the orange solid thick line the best fit for the equation \ref{eq:sf-functional} which takes into account observational limitations on the structure function.
@@
 The light shaded areas in the plot show where the separation \(r\) is above half of the box size, \(L\), which is indicated with a vertical dotted line.
-%For the discussion of our results in the next paragraphs the small scales would refer to the separations \(r < r_0\) and large scales would refer to separations \(r > r_0\).
 
@@
 At large scales there is an indication of some periodic behavior followed by ascending \(B(r)\) values at largest separation.
-The first maximum value of \(B(r)\) in the order of 2\(\sigma^2\pos\) is \(\sim\)\SI{14}{km^{2}.s^{-2}} at a separation of \(\sim\)\SI{2.5}{pc}. 
-Considering an oscillating behavior at \SI{4.5}{pc} a minimum value of \SI{11}{km^{2}.s^{-2}} is reached.
+A value of\(B(r)\) of order 2\(\sigma^2\pos\) is \(\sim\)\SI{14}{km^{2}.s^{-2}} at a separation of \(\sim\)\SI{2.5}{pc}. 
+Then there is a diminution at \SI{4.5}{pc} down to a value of \SI{11}{km^{2}.s^{-2}}.
 From this point the structure function ascends until it reaches \SI{66}{km^{2}.s^{-2}} around \SI{20}{pc}.
@@
 The correlation length is \SI{4}{pc} at a \(\sigma^2\pos\) of \SI{297 \pm 9}{km^{2}.s^{-2}} and an index of \num{0.85}.
-At large separations 30 Doradus structure function presents a behavior of tapered fluctuations.  
-The maximum \(B(r)\) value is \SI{655}{km^{2}.s^{-2}} at a separation of \SI{21}{pc}. 
+At large separations 30 Doradus structure function presents a behavior of tapered fluctuations. The maximum \(B(r)\) value is \SI{655}{km^{2}.s^{-2}} at a separation of \SI{21}{pc}. 
 From there \(B(r)\) values descends until they reach \SI{250}{km^{2}.s^{-2}} at \SI{38}{pc}.
@@
 A maximum \(B(r)\) value of \SI{104}{km^{2}.s^{-2}} is reached at \SI{33}{pc}. 
-From there the structure functions decays following and inhomogeneous pattern until it reaches \SI{54}{km^{2}.s^{-2}} at a separation of \SI{211}{pc}.
+From there the structure functions decays following a scatter pattern until it reaches \SI{54}{km^{2}.s^{-2}} at a separation of \SI{211}{pc}.
 
@@
 This observations are heavily affected by the noise which presents a value of \SI{6}{km^{2}.s^{-2}} which is larger that the \(\sigma^2\pos\) value of \SI{4}{km^{2}.s^{-2}}. 
-
 %corner plots descriptions
@@
 The contours in the plots reflect the 95\(\%\), 99\(\%\), 99.5\(\%\) and 99.9\(\%\) confidence intervals.
+A number of fits for the equations \ref{eq:sf-functional} and \ref{eq:functional} using samples of the posteriors are shown in thin translucent orange and green lines, respectively, showing the possible range of the confidence intervals.
 

### 2022-04-08 strucfunc_paper.tex
Typo

@@
 (approximately, \(r_0 > 0.1 L\)),
-then the apparent velocity variance \(\sigma\pos^2\) measured directly from the data
-is less than the true \(\sigma\pos^2\) of the underlying fluctuations
+then the apparent velocity variance \({\sigma'\pos}^2\) measured directly from the data
+is less than the true \({\sigma\pos}^2\) of the underlying fluctuations
 (see Figure~\ref{fig:finite-box-effect}).
@@
 In the next sections we discuss the application and interpretation of the turbulent parameters we obtained in our results.
-We present a resume of the turbulence theory and its validation to \hii{} regions.
-It is also mentioned some physical processes that contribute to stirring the ionized gas and the possibility that they are responsible for the observed velocity fluctuations.
+%We present a resume of the turbulence theory and its validation to \hii{} regions.
+%It is also mentioned some physical processes that contribute to stirring the ionized gas and the possibility that they are responsible for the observed velocity fluctuations.
 We present the most important correlations between the turbulent parameters and physical properties of our \hii{} region sample and finally we discuss our results in the context of previous structure functions.
 
-\subsection{Turbulence}\label{sec:turbulence-theory}
-
-\textit{Will 2021-12-10: Moving this section to later for now. Maybe
-  this material could go in discussion.}
-
-The idea to treat the ionized regions from a fluid mechanic view is intuitive if we consider the continuum hypothesis. 
-We validate this hypothesis using the Knudsen number defined as \(\text{Kn} \equiv \lambda / l\), where \(\lambda\) is the mean free path of the medium and \(l\) a characteristic length of the phenomenon we are studying.
-Taking into account a \(\lambda_{\text{HII}}\) of \SI{2.7e-7}{pc} \citep{1941ApJ....93..369S} and a \(l_{\text{HII}}\) of \SI{1}{pc} for ionized regions we obtained \(\text{Kn} \approx 10^{-7}\), while in general the continuum approach is valid for \(\text{Kn}\ll 1\).
-
-A turbulent behavior in the flows is more common in fluid systems than a laminar one.
-These turbulent flows tends to be unsteady, irregular and chaotic, and the turbulent motions are observed in many scales. 
-The turbulent flows are associated with a high Reynolds numbers which is defined as \(\text{Re} = l v_{l} / \nu \), where \(v_{l}\) is a characteristic velocity in the fluid system and \(\nu\) is the kinematic viscosity of the medium.
-Experiments have shown that a flow which is laminar become turbulent when increasing the velocity (i.e., increasing the Re) and a large range of velocity fluctuation appear at all scales.
-A high Re reflects high ratio of the advection/difussion terms of the Navier-Stokes equations, being interpreted as that the inertial forces taking over the viscous ones. 
-Hence it is possible to assume that if viscosity is not dominant in a flow, this flow would be turbulent.
-
-As astronomical observation made it possible to measure a large number of points with a high accuracy, it was found that velocities show a non-thermal component reflecting characteristic of turbulent earthly flows.
-The existence of turbulent flows in astrophysical objects, ranging in scales from 10\(^6\) to 10\(^{17}\) m \citep{2010ApJ...710..853C} is thought to be consequence of the high \(Re\), between 10\(^4\) and 10\(^9\) \citep{1949ApJ...110..329C,lagrois2011} that characterized these objects.
-
-The classic turbulence theory assumes a three-dimensional isotropic, incompressible and subsonic flow that can be described using an energy spectrum formed by vortices or eddies of different sizes \citep{kolm1}.
-The concept of the energy spectrum assumes that the energy is cascading down inside the flow from the largest to the smallest scales.
-The different scales in the energy cascade are defined based on their Re.
-In one side of the spectrum there is the energy injection scale, \(L_I\), that is related to the largest vortices, called the integral scales, where \(\text{Re} \rightarrow \infty\).
-On the other side of the spectrum there is the dissipation of energy at small scales, \(l_I\), where  \(\text{Re} \rightarrow 1\) and it is assumed that small vortices are responsible for the friction that dissipates the energy flux into thermal energy.
-In between there is the inertial range, \(l_d  << l << L_I\), where in a stationary case the energy transfer is at a constant rate.
-
-The rate of transfer of specific energy \(\epsilon\) (energy per unit mass) in the inertial range is independent of the \(l\) scale having the form \(\epsilon \sim v_l^2 / \tau_l\), where the kinetic energy is of the order of \( v_l^2\) and the life time of a velocity fluctuation is \(\tau_l\), which can be can be put in terms of \(\tau_l \sim l / v_l\).
-Hence we obtain \( v_l \sim (\epsilon l)^{1/3}\) where \(\epsilon\) is invariant in the cascade.
-
-The energy cascade is described using the energy spectrum, $E(k) \propto k^{\beta}$ where \(k\) is the wave number for a determined scale \(l\) ($k \equiv l^{-1}$).
-The total specific energy of a determined $l$ scale is of the order \(\langle v_{l}^{2} \rangle \) and is the energy integral above the associated \(k\), defined as:
-
-\begin{equation}\label{eq:energy-spectrum}
- \langle v_{l}^{2} \rangle = \int_{k}^{\infty} E(k)dk
-\end{equation}
-%
-If it is assumed that this energy is of the order of $(\epsilon l)^{\frac{2}{3}} \sim (\frac{\epsilon}{k})^{\frac{2}{3}}$ we can differentiate equation \ref{eq:energy-spectrum} and obtained the final form:
-
-\begin{equation}\label{eq:kolmogorov-law}
-E(k) \propto \epsilon^\frac{2}{3} k^{-\frac{5}{3}}
-\end{equation}
-%
-where \(\beta = -5 / 3\) is the Kolmogorov law.
-For supersonic turbulence the index is $\beta=-2$ \citep{burg}.
-
-Using a statistical law that relates the moments \(M_n\) of order \(n\) with the increments in the velocity field for a separation \(\boldsymbol{r}\) \citep{Leqism}, we have:
-
-\begin{equation}\label{eq:velocity-moments}
-M_n = \langle \vert \boldsymbol{v}(\boldsymbol{x} + \boldsymbol{r})- \boldsymbol{v}(\boldsymbol{x})\vert^n \rangle \propto (\epsilon r)^{n/3}
-\end{equation}
-%
-the average is over all the positions \(\boldsymbol{x}\) and directions \(\boldsymbol{r}\). 
-The Kolmogorov model predicts that the moment of order 2, the second-order structure function (equation \ref{eq:Br}), follows \(M_2 \propto r^{2/3}\).
-
-\subsection{Origins of interstellar turbulence}\label{sec:origins-turbulence}
-
-In the particular case of GEHR, as supersonic motions dissipate energy by shocks in time scales relatively short compared with the age of the region, it is necessary an energy source to replenish continuously the energy lost.
+%\subsection{Turbulence}\label{sec:turbulence-theory}
+
+%\textit{Will 2021-12-10: Moving this section to later for now. Maybe
+%  this material could go in discussion.}
+
+%The idea to treat the ionized regions from a fluid mechanic view is intuitive if we consider the continuum hypothesis. 
+%We validate this hypothesis using the Knudsen number defined as \(\text{Kn} \equiv \lambda / l\), where \(\lambda\) is the mean free path of the medium and \(l\) a characteristic length of the phenomenon we are studying.
+%Taking into account a \(\lambda_{\text{HII}}\) of \SI{2.7e-7}{pc} \citep{1941ApJ....93..369S} and a \(l_{\text{HII}}\) of \SI{1}{pc} for ionized regions we obtained \(\text{Kn} \approx 10^{-7}\), while in general the continuum approach is valid for \(\text{Kn}\ll 1\).
+
+%A turbulent behavior in the flows is more common in fluid systems than a laminar one.
+%These turbulent flows tends to be unsteady, irregular and chaotic, and the turbulent motions are observed in many scales. 
+%The turbulent flows are associated with a high Reynolds numbers which is defined as \(\text{Re} = l v_{l} / \nu \), where \(v_{l}\) is a characteristic velocity in the fluid system and \(\nu\) is the kinematic viscosity of the medium.
+%Experiments have shown that a flow which is laminar become turbulent when increasing the velocity (i.e., increasing the Re) and a large range of velocity fluctuation appear at all scales.
+%A high Re reflects high ratio of the advection/difussion terms of the Navier-Stokes equations, being interpreted as that the inertial forces taking over the viscous ones. 
+%Hence it is possible to assume that if viscosity is not dominant in a flow, this flow would be turbulent.
+
+%As astronomical observation made it possible to measure a large number of points with a high accuracy, it was found that velocities show a non-thermal component reflecting characteristic of turbulent earthly flows.
+%The existence of turbulent flows in astrophysical objects, ranging in scales from 10\(^6\) to 10\(^{17}\) m \citep{2010ApJ...710..853C} is thought to be consequence of the high \(Re\), between 10\(^4\) and 10\(^9\) \citep{1949ApJ...110..329C,lagrois2011} that characterized these objects.
+
+%The classic turbulence theory assumes a three-dimensional isotropic, incompressible and subsonic flow that can be described using an energy spectrum formed by vortices or eddies of different sizes \citep{kolm1}.
+%The concept of the energy spectrum assumes that the energy is cascading down inside the flow from the largest to the smallest scales.
+%The different scales in the energy cascade are defined based on their Re.
+%In one side of the spectrum there is the energy injection scale, \(L_I\), that is related to the largest vortices, called the integral scales, where \(\text{Re} \rightarrow \infty\).
+%On the other side of the spectrum there is the dissipation of energy at small scales, \(l_I\), where  \(\text{Re} \rightarrow 1\) and it is assumed that small vortices are responsible for the friction that dissipates the energy flux into thermal energy.
+%In between there is the inertial range, \(l_d  << l << L_I\), where in a stationary case the energy transfer is at a constant rate.
+
+%The rate of transfer of specific energy \(\epsilon\) (energy per unit mass) in the inertial range is independent of the \(l\) scale having the form \(\epsilon \sim v_l^2 / \tau_l\), where the kinetic energy is of the order of \( v_l^2\) and the life time of a velocity fluctuation is \(\tau_l\), which can be can be put in terms of \(\tau_l \sim l / v_l\).
+%Hence we obtain \( v_l \sim (\epsilon l)^{1/3}\) where \(\epsilon\) is invariant in the cascade.
+
+%The energy cascade is described using the energy spectrum, $E(k) \propto k^{\beta}$ where \(k\) is the wave number for a determined scale \(l\) ($k \equiv l^{-1}$).
+%The total specific energy of a determined $l$ scale is of the order \(\langle v_{l}^{2} \rangle \) and is the energy integral above the associated \(k\), defined as:
+
+%\begin{equation}\label{eq:energy-spectrum}
+% \langle v_{l}^{2} \rangle = \int_{k}^{\infty} E(k)dk
+%\end{equation}
+%
+%If it is assumed that this energy is of the order of $(\epsilon l)^{\frac{2}{3}} \sim (\frac{\epsilon}{k})^{\frac{2}{3}}$ we can differentiate equation \ref{eq:energy-spectrum} and obtained the final form:
+
+%\begin{equation}\label{eq:kolmogorov-law}
+%E(k) \propto \epsilon^\frac{2}{3} k^{-\frac{5}{3}}
+%\end{equation}
+%
+%where \(\beta = -5 / 3\) is the Kolmogorov law.
+%For supersonic turbulence the index is $\beta=-2$ \citep{burg}.
+
+%Using a statistical law that relates the moments \(M_n\) of order \(n\) with the increments in the velocity field for a separation \(\boldsymbol{r}\) \citep{Leqism}, we have:
+
+%\begin{equation}\label{eq:velocity-moments}
+%M_n = \langle \vert \boldsymbol{v}(\boldsymbol{x} + \boldsymbol{r})- \boldsymbol{v}(\boldsymbol{x})\vert^n \rangle \propto (\epsilon r)^{n/3}
+%\end{equation}
+%
+%the average is over all the positions \(\boldsymbol{x}\) and directions \(\boldsymbol{r}\). 
+%The Kolmogorov model predicts that the moment of order 2, the second-order structure function (equation \ref{eq:Br}), follows \(M_2 \propto r^{2/3}\).
+
+%\subsection{Origins of interstellar turbulence}\label{sec:origins-turbulence}
+
+%In the particular case of GEHR, as supersonic motions dissipate energy by shocks in time scales relatively short compared with the age of the region, it is necessary an energy source to replenish continuously the energy lost.
 From the observed velocity  dispersion \(\sigma\), and assuming that we have an isotropic distribution of velocities,  we can estimate the 3D velocity dispersion by \(\sigma_\mathrm{3D} = \sqrt{3} \sigma\).
 The mass of the ionized gas together with the velocity dispersion \(\sigma_\mathrm{3D}\)  are used to estimate the kinetic energy in the GEHRs.
-As these objects have typically  masses of the ionized gas of \num{\sim e5} M\(_{\sun}\) and velocity dispersion values  of \SI{\sim 20}{km.s^{-1}} \citep{1984ApJ...287..116K}, typical kinetic energy of the ionized gas is \SI{\sim e51}{ergs}.
-
-In the standard Kolmogorov model, the energy spectrum of turbulence becomes dependent only on \(\epsilon\), the mean dissipation of energy per unit time per unit mass of fluid,  with the inertial forces transferring without losses kinetic energy from larger to smaller turbulent elements within the inertial range.
+%As these objects have typically  masses of the ionized gas of \num{\sim e5} M\(_{\sun}\) and velocity dispersion values  of \SI{\sim 20}{km.s^{-1}} \citep{1984ApJ...287..116K}, typical kinetic energy of the ionized gas is \SI{\sim e51}{ergs}.
+
+%In the standard Kolmogorov model, the energy spectrum of turbulence becomes dependent only on \(\epsilon\), the mean dissipation of energy per unit time per unit mass of fluid,  with the inertial forces transferring without losses kinetic energy from larger to smaller turbulent elements within the inertial range.
 Let \(L_c\) be the characteristic length of the largest eddies, and \(\delta v\) the typical velocity.
 
-We have then that \(\epsilon = (\delta v)^{3}/L\). In steady-state turbulence, equilibrium exists between the energy input and the energy dissipation rates. 
-Although the present observations indicate that turbulence in \hii{} regions may not follow the Kolmogorov model, with energy input occurring at different scales, so that a  truly inertial range may not exist at all, lets us make a crude estimation of the  amount of energy transferred between scales using this simple model.
-Assuming the above figures for the mass of the gas and velocity dispersion, \(\delta v = \sigma_\mathrm{3D}\),  and a \(L_c\) of \SI{100}{pc}, we obtain that the energy transfer rate \SI{\sim e37}{erg.s^{-1}}, and  the time scale for energy transfer, \(L/\delta v \), would be of few million years.
-
+%We have then that \(\epsilon = (\delta v)^{3}/L\). In steady-state turbulence, equilibrium exists between the energy input and the energy dissipation rates. 
+%Although the present observations indicate that turbulence in \hii{} regions may not follow the Kolmogorov model, with energy input occurring at different scales, so that a  truly inertial range may not exist at all, lets us make a crude estimation of the  amount of energy transferred between scales using this simple model.
+%Assuming the above figures for the mass of the gas and velocity dispersion, \(\delta v = \sigma_\mathrm{3D}\),  and a \(L_c\) of \SI{100}{pc}, we obtain that the energy transfer rate \SI{\sim e37}{erg.s^{-1}}, and  the time scale for energy transfer, \(L/\delta v \), would be of few million years.
+
+%There are several energy sources that could provide or contribute  to the energy required: of the order of kpc, the differential rotations of the galaxy that produces shear at large scale, at scales of the order of hundreds of pc, supernova explosions inject a large amount of kinetic energy.
+%At scales of several tens of pc the expansion of \hii{} regions and stellar winds are a source of energy and, bipolar flows, shocks, jets and champagne flows inject energy at small scales about one tenth of a pc.
+
+%The lack of precise information on how these mechanism contribute to the emission line broadening make a non-trivial task to determine at what extent they play a role in the interstellar turbulence, contributing to the complexity of the extraction of pure turbulent motions from velocity profiles in nebulae \citep{2011MNRAS.413..705L,arthur2016turbulence}.
+
+\subsection{Interpretation of the turbulent parameters}\label{sec:interpretation-parameters}
+
+\subsubsection{Correlation length \(r_0\)}
+
+Ideally the correlation length \(r_0\) should represent the scale of dominant energy injection.
+It is unclear what are the precise mechanisms driving the turbulence in \hii{} regions, thought a lot of options are candidates.
+The most probable scenario is that the velocity fluctuations are consequence of the combination of various mechanism.
 There are several energy sources that could provide or contribute  to the energy required: of the order of kpc, the differential rotations of the galaxy that produces shear at large scale, at scales of the order of hundreds of pc, supernova explosions inject a large amount of kinetic energy.
 At scales of several tens of pc the expansion of \hii{} regions and stellar winds are a source of energy and, bipolar flows, shocks, jets and champagne flows inject energy at small scales about one tenth of a pc.
-
-The lack of precise information on how these mechanism contribute to the emission line broadening make a non-trivial task to determine at what extent they play a role in the interstellar turbulence, contributing to the complexity of the extraction of pure turbulent motions from velocity profiles in nebulae \citep{2011MNRAS.413..705L,arthur2016turbulence}.
-
-\subsection{Interpretation of the turbulent parameters}\label{sec:interpretation-parameters}
-
-\subsubsection{Correlation length \(r_0\)}
-
-Ideally the correlation length \(r_0\) should represent the scale of dominant energy injection.
-It is unclear what are the precise mechanisms driving the turbulence, thought a lot of options are candidates.
-The most probable scenario is that the velocity fluctuations are consequence of the combination of various mechanism.
 Many of these mechanisms, at some extent, affect all the \hii{} regions studied in this work.
@@
 The high-velocity stellar wind from \(\theta^1\) Ori C will confine the ionized gas, even the high ionization emission lines, to a thick shell.
-In one direction, at a distance of \SI{0.1}{pc} from the massive star a stationary shell of shocked material is formed when the ram pressure of the photoevaportation flow balances the thermal pressure of the shocked wind.
+In one direction, at a distance of \SI{0.1}{pc} from the ionizing massive star a stationary shell of shocked material is formed when the ram pressure of the photoevaportation flow balances the thermal pressure of the shocked wind.
 In the other direction there is a free flow of the hypersonic wind.
 At a smaller scale of \SI{0.02}{pc} there is an interaction between the closest proplyd photoevaporation flow and the stellar wind which results in bowshocks.
-According to \citet{2001ApJ...561..830G} the influence of stellar wind interactions is restricted to the central 0.05 pc. 
-Orion also present a champagne flow where the photoionized gas streams away from the ionization front covering a distance of \(\sim\)\SI{1}{pc} from the molecular cloud \citep{1973ApJ...183..863Z}.
-
-Our correlation length results for the Orion Core and EON from table~\ref{tab:Res} despite been close to the scales mentioned above still aren't conclusive enough to determine a direct relation between them.
-As mentioned in \citet{arthur2016turbulence} the mechanism mentioned in the previous paragraph would play a secondary role in stirring up the gas motions and it would be necessary to determine if the velocity fluctuations arise from pure turbulent motion inside the ionized clouds or a consequences of density and brightness fluctuations.
+According to \citet{2001ApJ...561..830G} the influence of stellar wind interactions is restricted to the central \SI{0.05}{pc}. 
+Orion also present a champagne flow where the photoionized gas streams away from the ionization front covering a distance of \SI{\sim 1}{pc} from the molecular cloud \citep{1973ApJ...183..863Z}.
+
+Our correlation length results for the Orion Core and EON from table~\ref{tab:Res}, \num{0.068} y \SI{0.39}{pc} respectively, despite been of the order of the scales mentioned above still aren't conclusive enough to determine a direct relation between them.
+As mentioned in \citet{arthur2016turbulence} the mechanism mentioned in the previous paragraph would play a secondary role in stirring up the gas motions and it would be necessary to specify if the velocity fluctuations arise from pure turbulent motion inside the ionized clouds or a consequences of density and brightness fluctuations.
 
@@
 
-\subsubsection{Structure function power-law index \(m\)}\label{sec:powe-index}
-
-The index \(m\) shown in the last column of Table \ref{tab:Res} is used for comparison between observations and the theoretical value of 0.67 (equation \ref{eq:velocity-moments}).
+\subsubsection{Structure function power-law index \(m\)}\label{sec:power-index}
+
+The index \(m\) shown in the last column of Table \ref{tab:Res} is used for comparison between observations and the theoretical value of 0.67.
 All our indices are above this theoretical value and this is attributed to the fact that the \hii{} regions do not comply with the assumptions established in the development of the turbulent theory.
 
-From section~\ref{sec:regions-milky-way} we know that most of all assumption mentioned in section~\ref{sec:turbulence-theory} are not meet for our \hii{} region sample.
+From section~\ref{sec:regions-milky-way} we know that most of all assumption mentioned in the theory of turbulence are not meet for our \hii{} region sample.
 \hii{} regions emerged from a molecular cloud with highly filamentary and clumpy density structure .
@@
 But despite the complex nature of \hii{} regions and observational limitations we obtain a common pattern for the structure function and the value of the power-law index falls in a certain limited range of values.
-The differences with respect the theoretical value are often used as a diagnostic tools to identify properties that are not consider in the assumptions of the turbulence theory.
-
-To study the projection of a three-dimensional structure function to a two-dimensional structure function, known as projection smoothing \citep{von1951methode, munch1958internal,1987ApJ...317..686O}, relationships between the power-law indices were proposed:
+The differences in the power-law index with respect the theoretical value are often used as a diagnostic tools to identify properties that are not consider in the assumptions of the turbulence theory.
+
+To study the projection of a three-dimensional structure function to a two-dimensional structure function, known as projection smoothing \citep{von1951methode, munch1958internal,1964SvA.....8..210K,1987ApJ...317..686O}, relationships between the power-law indices were proposed:
 
@@
 
-As a conclusion, if the extension of the HII region is compared with its depth (three-dimensional case) the value of the index is 1.6. 
-While the case where the extension is much greater than its depth (two-dimensional case) the region will have a value of 0.6 .
-
-The mean value \(m\) of our sample is \(\sim\)1. 
+As a conclusion, if the extension of the HII region is compared with its depth (three-dimensional case) the value of the index is \num{1.67}. 
+While the case where the extension is much greater than its depth (two-dimensional case) the region will have a value of \num{0.6}.
+From Table~\ref{tab:Res} we see that our results fall between these two previous values.
+
+The mean value \(m\) of our sample is \num{\sim 1}. 
 Following the equation \ref{eq:projection-smoothing-3d} the \hii{} regions in our sample with \(m >\) 1 would present a depth which is in the order of magnitude comparable to the length of the observed box size \(L\) been closest to this value as \(m\) tends to 1.6.
@@
 
-Deviations from the Kolmogorov model are expected in \hii{} regions as the photoionized flow in their interior has a different nature as the flows upon the theory is constructed. 
-Also magnetic fields would play a very important role in the dynamics of the gas motions.
-Despite these differences is clear that the self-similarity motions is a common behavior conserved at scales from parsecs to hundreds of parsecs. 
-With the advanced of the observational capabilities with more computational power for a better understanding of turbulent motions the gap between theory and observations is hoped to be reduced.
-
 \subsubsection{Relationship between plane-of-sky and line-of-sight velocity dispersion}\label{sec:sigmapos-vs-sigmalos}
@@
 The standard deviation of the velocity centroid, \(\sigma\pos\), and the mean non-thermal linewidth, \(\sigma_{\text{los}}\), allow us to compare the relation between the kinematical disorder on the plane-of-the sky and along the line-of-sight  \citep{2011MNRAS.413..705L}.
-In these sense the structure function is used as a tool to investigate the projection of a three-dimensional correlation function onto the plane of sky \citep{arthur2016turbulence}.
-
-We can consider as a main broadening mechanisms the kinematical disorder along the LOS related to velocity gradients by the clumpiness on the molecular cloud and turbulent movements.
+Considering the previous statements, the structure function is used as a tool to investigate the projection of a three-dimensional correlation function onto the plane of sky \citep{arthur2016turbulence}.
+
+We can consider as a main broadening mechanisms the kinematical disorder along the LOS related to velocity gradients by the clumpiness on the cloud and turbulent movements.
 On the plane-of-sky the consequences of those gradients and movements is measured in every pixel. 
-The spatial variations on the velocity field would depend on the targeted pixel, depending on the motions inside the cloud.
+The spatial variations on the velocity field would depend on the targeted pixel, at the same time depending on the motions inside the cloud.
 This reasoning has lead to  propose a relationship between \(\sigma_{\text{los}}\) and \(\sigma\pos\) \citep{2011MNRAS.413..705L}.
@@
 With a value of \(\sigma\pos / \sigma_{\text{los}}\) = 0.5 we obtain \(r_{0} / H \sim\) 0.02 - 0.1.
-This procedure implies depths of the order 10 to 50 times.
-In the lower limit \citet{arthur2016turbulence} mentioned the inconsistency for Orion since evidence has show that the emitting layer thickness is of the order of 0.01 - 0.3 pc.
-For the most distant regions the previous analysis would give depths of the order of magnitude of the observational box, but considering the analysis using the power-law index (section~\ref{sec:powe-index}) only NGC 595 would comply to this three dimensional structure.
+This procedure implies depths of the order 10 to 50 times the correlation length.
+In the lower limit \citet{arthur2016turbulence} mentioned the inconsistency for Orion since evidence has show that the emitting layer thickness is of the order of \num{0.01} - \SI{0.3}{pc}.
+For the most distant regions the previous analysis would give depths of the order of magnitude of the observational box, but considering the analysis using the power-law index (section~\ref{sec:power-index}) only NGC 595, which index is \num{1.36} would comply to this three dimensional structure.
 
@@
 \includegraphics[width=3in]{Figures/corr-los-vs-pos}
-\caption{The $\sigma$-$\sigma_{\text{los}}$ plane. The dotted line represents slope equal to unity.}
+\caption{The $\sigma$-$\sigma_{\text{los}}$ plane. The dotted line represents slope equal to unity and the dashed line represents a slope of two.}
 \label{fig:los-vs-pos}
@@
 
-In the section \ref{sec:results} we showed that each \hii{} region of our sample has a turbulent velocity field that can be characterized using the turbulence theory.
+In the section \ref{sec:results} we showed that each \hii{} region of our sample has a turbulent velocity field that can be characterized using the turbulence methods despite the results not being as the Kolmogorov model predicts.
 The turbulent parameters obtained are unique to each velocity field.
@@
 
-In Section \ref{sec:methods-apply} we mentioned the reduced chi-square method we are using for the determination of the correlation length and the index of the slope.
-Since this is the first time this method is applied to a sample of HII regions (at least for our knowledge), our results are bounded to be different from previous investigations, including the one that have the same observations as \citet{arthur2016turbulence} and \citet{Melnick:2021x}.
-
-A complete analysis on different emissions lines of the structure function on Orion was carried out by \citet{arthur2016turbulence} and reference therein. 
+In Section \ref{sec:methods-apply} we mentioned the model we propose for the structure function.
+Since this is the first time a model of this type is applied to a sample of HII regions (at least for our knowledge), our results are bounded to be different from previous investigations, including the one that have the same observations as \citet{arthur2016turbulence} and \citet{Medina-Tanco:1997a,Melnick:2021x}.
+
+A complete analysis on different emissions lines of the structure function on Orion was carried out by \citet{arthur2016turbulence}. 
 They observed a tendency that higher ionization lines presents higher values on the magnitude dispersion and the steepness of the structure function slope. 
@@
 The power-law index obtained by \citet{arthur2016turbulence} are \(m \sim 1.2 \pm 0.1\) for \halpha\ and [OIII] emission lines and for [SII] they found \(m \sim 0.8 \pm 0.1\). 
-The correlation length for all lines is \(\approx\) 0.05 pc. For the same \halpha\ observation we obtained a value of 1.06$\pm$0.01 and a correlation length of 0.092$\pm$0.007 pc.
+The correlation length for all lines is \(\approx\) 0.05 pc. For the same \halpha\ observation we obtained a value of \num{1.07} and a correlation length of \SI{0.068}{pc}.
 
@@
 \citet{Medina-Tanco:1997a} conclude about a double regime acting on the kinetic energy spectrum.
-According to this double cascade, turbulence is being forced at scales of \(\approx\) \SI{00}{pc} while and energy cascade has developed down to the smallest scales and other, as an inverse cascade, extends up to scale of \(\approx\) \SI{70}{pc}.
-\citet{Medina-Tanco:1997a} mentioned different characteristic scale lengths, the most notorious is the \(\approx\)10 pc, a value close to our correlation length of \(\approx\)9 pc, and they interpret it as possible source on energy associated with the expansion of shocks coming from wind bubbles.
+According to this double cascade, turbulence is being forced at scales of \(\approx\) \SI{10}{pc} while and energy cascade has developed down to the smallest scales and other, as an inverse cascade, extends up to scale of \(\approx\) \SI{70}{pc}.
+\citet{Medina-Tanco:1997a} mentioned different characteristic scale lengths, the most notorious is the \SI{\sim 10}{pc}, and they interpret it as possible source on energy associated with the expansion of shocks coming from wind bubbles.
 \citet{Melnick:2021x} addresses some issues with TAURUS II data while comparing profiles between the previous instrument TAURUS I where there exist a difference between observations (see section 4.1 on their paper).
 They mentioned that one problem with \citet{Medina-Tanco:1997a} structure function is that they didn't take into account the observational seeing.
-This would invalidate they results and \citet{Melnick:2021x} consider that taking out the structure function values that fall in this range would make the structure function flat and scales \(<\)\SI{10}{pc}.
+This would invalidate they results and \citet{Melnick:2021x} consider that taking out the structure function values that fall in this range would make the structure function flat at scales \(<\)\SI{10}{pc}.
 Finally they point out, and we agree, the importance of observing NGC 604 at higher spatial resolution, so they rule out \citet{Medina-Tanco:1997a} results. 
@@
 One big difference is that \citet{lagrois2011} apply a  filter to the velocity field to get rid of non-turbulent movements.
-As a comparison for the filtered turbulent parameters they present a correlation length of 43 pc and the power-law index they provide is 1.55 $\pm$ 0.01.
-Other difference in their methodology is that they use the normalized structure function value of 2 to obtain the correlation length.
-Using their unfiltered data the correlation length is \(\sim\) \SI{90}{pc} and using the same criteria as our it is \(\sim\) \SI{40}{pc} and the slope would be shallower. 
-Their velocity centroid \(\sigma\) is 5.92 $\pm$ 0.15 km s\(^{-1}\) while we have 7.48 $\pm$ 1.4 km s\(^{-1}\) which is consistent.
+As a comparison for the filtered turbulent parameters they present a correlation length of \SI{43}{pc} and the power-law index they provide is \num{1.55 \pm 0.01}.
+Other difference in their methodology is that they use the normalized structure function value of 2\(\sigma\pos\) to obtain the correlation length.
+%Using their unfiltered data the correlation length is \(\sim\) \SI{90}{pc} and using the same criteria as our it is \(\sim\) \SI{40}{pc} and the slope would be shallower. 
+Their velocity centroid \(\sigma\) is \SI{5.92 \pm 0.15}{km.s^{-1}} while we have \SI{7.48\pm 2}{km. s^{-1}} which fall within the uncertainties.
 Due to the different observations and methodologies a direct comparison between structure functions is not possible.

### 2022-04-14 strucfunc_paper.tex
Javier changes 2022-04-13

@@
 (approximately, \(r_0 > 0.1 L\)),
-then the apparent velocity variance \({\sigma'\pos}^2\) measured directly from the data
-is less than the true \({\sigma\pos}^2\) of the underlying fluctuations
+then the apparent velocity variance \(\sigma\pos^2\) measured directly from the data
+is less than the true \(\sigma\pos^2\) of the underlying fluctuations
 (see Figure~\ref{fig:finite-box-effect}).

### 2022-04-15 strucfunc_paper.tex
Finish revisions of section 3 and add new fig to appendix
Also, expand on figure caption for finite box figures

@@
 (approximately, \(r_0 > 0.1 L\)),
-then the apparent velocity variance \(\sigma\pos^2\) measured directly from the data
-is less than the true \(\sigma\pos^2\) of the underlying fluctuations
+then the apparent velocity variance measured directly from the data
+is less than the true \({\sigma\pos}^2\) of the underlying fluctuations
 (see Figure~\ref{fig:finite-box-effect}).
@@
 the full range of velocity variations.
-At the same time, the apparent correlation length \(r_0'\) is smaller
+At the same time, the apparent correlation length is smaller
 than the true value.
-
-However, this does not mean that the model structure function needs to be modified;
-equation
-In the limit that \(r_0 \gg L\), then \(r_0'\) becomes independent of
-
-finding that the apparent
-
-\begin{equation}\label{eq:ffb}
-% \beta(r_0) = 1 - exp[\frac{L_{box}}{3.6r_0}] 
-  \beta(L,r_0) = 1 - \exp \left[ \frac{-L} {3.6 r_0} \right] 
-\end{equation}
-%
-where the \(L\) value is the diagonal length of the observational box.
-
-%\begin{equation}\label{eq:sf-functional}
-%B_{\text{func}}(r) = B(r; \beta r_0, \beta \sigma^2,m) \times S(r; s_0, r_0) + B_{\text{noise}}
-%\end{equation}
+However, this does not mean that the model structure function needs to be modified.
+In the appendix we show that the model fitting is capable of determining the true fluctuation variance
+and true correlation length (both to within 10\%),
+so long as \(L > 3\, r_0\).
+This is a significant improvement over than direct empirical measurement,
+which requires \(L > 10\, r_0\) in order to be accurate
+(compare panels a and b of Figure~\ref{fig:finite-box-effect}).
 
@@
 which yields periodic peaks in the structure function.
-Neither of these effects can be captured by our model structure function,
+Both effects are illustrated in Figure~\ref{fig:model-strucfunc}b.
+Neither of them can be captured by our model structure function,
 which assumes that the autocorrelation is strictly positive
 and monotonically decreasing with \(r\).
-
-At the very smallest scales, the autocorrelation function is predicted to
-scale quadratically with \(r\)
+Instead, we restrict the model fitting range to scales less than \(L / 2\),
+where the influence of these effects should be minimal.
 
@@
     (b)~Resultant structure functions.
+    Colored lines show the average \(B(r)\) over all sub-images,
+    while the shaded areas show the standard deviation of \(B(r)\).
   }
@@
 \begin{figure}
+  \begin{tabular}{@{} l @{}}
+    (a)\\
     \includegraphics[width=\linewidth]{Figures/fake-finite-box-effect}
+    \\[\bigskipamount]
+    (b)\\
+    \includegraphics[width=\linewidth]{Figures/fake-finite-box-fits}
+  \end{tabular}
   \caption{
@@
     due to finite box size.
+    (a)~Empirical measurements of \(\sigma^2\) and \(r_0\).
+    Colored dots show mean results from different simulated velocity fields,
+    with varied power law slopes.
+    Colored shading shows the inter-quartile range over the different sub-images.
+    The dashed line is an approximate analytic fit to these results
+    (equation~\eqref{eq:ajustebox}).
+    (b)~Determination of \(\sigma^2\) and \(r_0\) from fitting the model
+    of equation~\eqref{eq:new-correlation-form}.
+    Colored dots are mean results from different simulated velocity fields,
+    while the dashed line is the same as in (a).
   }

### 2022-04-15 strucfunc_paper.tex
Reorganize results figures - move corner plots to appendix

@@
 
-\newcommand\sffig[1]{%
+\newlength\SFwidth
+\setlength\SFwidth{0.45\textwidth}
+\newcommand\SFtwograph[2]{%
+  \includegraphics[width=\SFwidth]{Figures/sf-emcee-#1}
+  &  \includegraphics[width=\SFwidth]{Figures/sf-emcee-#2}
+}
+\newcommand\SFtwocorner[2]{%
+  \includegraphics[width=\SFwidth]{Figures/corner-emcee-#1}
+  &  \includegraphics[width=\SFwidth]{Figures/corner-emcee-#2}
+}
+
+\newcommand\sffigg[2]{%
   \begin{tabular}{@{}ll@{}}
     (a)& (b)\\
-    \includegraphics[width=0.45\linewidth]{Figures/sf-emcee-#1}
-       &  \includegraphics[width=0.45\linewidth]{Figures/corner-emcee-#1}
+    \SFtwograph{#1}{#2}
+  \end{tabular}%
+}
+\newcommand\sffigggg[4]{%
+  \begin{tabular}{@{}ll@{}}
+    (a)& (b)\\
+    \SFtwograph{#1}{#2}\\
+    (c)& (d)\\
+    \SFtwograph{#3}{#4}\\
+  \end{tabular}%
+}
+\newcommand\sfcfig[1]{%
+  \includegraphics[width=\SFwidth]{Figures/corner-emcee-#1}%
+}  
+\newcommand\sfcfigg[2]{%
+  \begin{tabular}{@{}ll@{}}
+    (a)& (b)\\
+    \SFtwocorner{#1}{#2}
+  \end{tabular}%
+}
+\newcommand\sfcfigggg[4]{%
+  \begin{tabular}{@{}ll@{}}
+    (a)& (b)\\
+    \SFtwocorner{#1}{#2}\\
+    (c)& (d)\\
+    \SFtwocorner{#3}{#4}\\
   \end{tabular}%
@@
   \centering
-  \sffig{OrionS}
+  \sffigggg{OrionS}{M8}{OrionLH}{CarC}
   \caption{
-    Second-order structure functions for the velocity centroid images of the \(H\alpha\) emission line from Orion core region.
-  }
-  \label{fig:strucfunc-fit-OrionS}
+    Second-order structure functions
+    for the velocity centroid images
+    of the \ha{} emission line
+    from Galactic \hii{} regions.
+  }
+  \label{fig:strucfunc-fit-Galactic}
 \end{figure*}
+\begin{figure}
+  \centering
+  \includegraphics[width=\SFwidth]{Figures/corner-emcee-OrionS}
+  \caption{
+    Example corner plot of covariances between
+    model parameters of fits to the \ha{} structure function.
+    The example shown is for Orion,
+    while figures for the remaining regions are given in
+    Appendix~\ref{sec:addit-covar-corn}. 
+  }
+  \label{fig:corner-example-Orion}
+\end{figure}
+
 \begin{figure*}
   \centering
-  \sffig{M8}
+  \sffigg{N346}{Dor}
   \caption{
-    Same as figure~\ref{fig:strucfunc-fit-OrionS} except for the Lagoon Nebula. 
-  }
-  \label{fig:strucfunc-fit-M8}
+    Same as figure~\ref{fig:strucfunc-fit-Galactic}
+    except for Magellanic Cloud \hii{} regions. 
+  }
+  \label{fig:strucfunc-fit-MC}
 \end{figure*}
+
 \begin{figure*}
   \centering
-  \sffig{CarC}
+  \sffigggg{HV}{HX}{N595}{N604H}
   \caption{
-    Same as figure~\ref{fig:strucfunc-fit-OrionS} except for the Carina Nebula. 
-  }
-  \label{fig:strucfunc-fit-CarC}
+    Same as figure~\ref{fig:strucfunc-fit-Galactic}
+    except for \hii{} regions in more distant
+    Local Group Galaxies.
+  }
+  \label{fig:strucfunc-fit-ExtraGal}
 \end{figure*}
-
-\begin{figure*}
-  \centering
-  \sffig{N346}
-  \caption{
-    Same as figure~\ref{fig:strucfunc-fit-OrionS} except for the NGC~346 nebula in the SMC. 
-  }
-  \label{fig:strucfunc-fit-N346}
-\end{figure*}
-\begin{figure*}
-  \centering
-  \sffig{Dor}
-  \caption{
-    Same as figure~\ref{fig:strucfunc-fit-OrionS} except for the 30~Doradus nebula in the LMC Nebula. 
-  }
-  \label{fig:strucfunc-fit-Dor}
-\end{figure*}
-
-\begin{figure*}
-  \centering
-  \sffig{HV}
-  \caption{
-    Same as figure~\ref{fig:strucfunc-fit-OrionS} except for the Hubble~V nebula.
-  }
-  \label{fig:strucfunc-fit-HV}
-\end{figure*}
-\begin{figure*}
-  \centering
-  \sffig{HX}
-  \caption{
-    Same as figure~\ref{fig:strucfunc-fit-OrionS} except for the Hubble~X nebula.
-  }
-  \label{fig:strucfunc-fit-HX}
-\end{figure*}
-
-\begin{figure*}
-  \centering
-  \sffig{N595}
-  \caption{
-    Same as figure~\ref{fig:strucfunc-fit-OrionS} except for the NGC~595 nebula.
-  }
-  \label{fig:strucfunc-fit-N595}
-\end{figure*}
-\begin{figure*}
-  \centering
-  \sffig{N604H}
-  \caption{
-    Same as figure~\ref{fig:strucfunc-fit-OrionS} except for the NGC~604 nebula.
-  }
-  \label{fig:strucfunc-fit-N604H}
-\end{figure*}
-
-\begin{figure*}
-  \centering
-  \sffig{OrionLH}
-  \caption{
-    Same as figure~\ref{fig:strucfunc-fit-OrionS} except for the extended Orion Nebula.
-  }
-  \label{fig:strucfunc-fit-OrionLH}
-\end{figure*}
-
-% \begin{figure*}
-%   \centering
-%   \includegraphics[width=0.8\linewidth]{Figures/strucfunc-fit-A}
-%   \caption{Second-order structure functions for the velocity centroid images of the \(H\alpha\) emission line}\label{fig:strucfunc-fit-A}
-% \end{figure*}
-
-% \begin{figure*}
-%   \centering
-%   \includegraphics[width=0.8\linewidth]{Figures/strucfunc-fit-B}
-%   \caption{Second-order structure functions for the velocity centroid images of the \(H\alpha\) emission line}\label{fig:strucfunc-fit-B}
-% \end{figure*}
-
-% \begin{figure*}
-%   \centering
-%   \includegraphics[width=0.8\linewidth]{Figures/strucfunc-fit-C}
-%   \caption{Second-order structure functions for the velocity centroid images of the \(H\alpha\) emission line}\label{fig:strucfunc-fit-C}
-% \end{figure*}
-
-% \begin{figure*}
-%   \centering
-%   \includegraphics[width=0.8\linewidth]{Figures/strucfunc-fit-D}
-%   \caption{Second-order structure functions for the velocity centroid images of the \(H\alpha\) emission line}\label{fig:strucfunc-fit-D}
-% \end{figure*}
 
@@
 
+\section{Additional covariance corner plots for model fits}
+\label{sec:addit-covar-corn}
+Supplementary online-only material.
+\clearpage
+
+\begin{figure*}
+  \centering
+  \sfcfigggg{OrionS}{M8}{OrionLH}{CarC}
+  \caption{
+    Corner plots of covariances between
+    fitted model parameters
+    of \ha{} structure function
+    for Galactic \hii{} regions.
+  }
+  \label{fig:corner-Galactic}
+\end{figure*}
+
+\begin{figure*}
+  \centering
+  \sfcfigg{N346}{Dor}
+  \caption{
+    Same as figure~\ref{fig:corner-Galactic}
+    except for Magellanic Cloud \hii{} regions. 
+  }
+  \label{fig:corner-MC}
+\end{figure*}
+
+\begin{figure*}
+  \centering
+  \sfcfigggg{HV}{HX}{N595}{N604H}
+  \caption{
+    Same as figure~\ref{fig:corner-Galactic}
+    except for \hii{} regions in more distant
+    Local Group Galaxies.
+  }
+  \label{fig:corner-ExtraGal}
+\end{figure*}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2022-04-16 strucfunc_paper.tex
Major reorganization of paper
Move more things to appendices. All the corner plots and all the
descriptions of individual regions and their strucfunc fits.

@@
 
-\subsection{Physical properties of the sample regions. }
+\subsection{Physical properties of the sample regions}
 \label{sec:regions-milky-way}
@@
 
-\subsubsection{Orion Nebula}
-\label{sec:orion-nebula}
-
-The Orion Nebula (M42) is the prototype of a galactic HII region located at a distance of 440 pc \citetext{\SI{1}{\arcsecond} = \SI{0.002}{pc} ; \citealp{2008AJ....136.1566O}}.
-The O7 V star \(\theta^{1}\) Ori C is the most luminous and hottest star \citep{2006A&A...448..351S} with an ionizing flux \(Q_0\) of  \SI{e49.12}{photons.s^{-1}}. 
-With other 3 B-type stars they form the Trapezium cluster.
-The bright region that surrounds these massive ionizing stars is called the the Huygens region (Orion core henceforth).
-In the southwest direction of the Huygens region there is a drop in the brightness as one approach a much larger region called Extended Orion Nebula \citetext{EON henceforth;  \citealp{2008Sci...319..309G}}
-The position of Orion near the side of the Orion Molecular Cloud (OMC-1) make it an ongoing star formation with a large population of young star, some of which are the sources of stellar jets and Herbig-Haro objects \citep{1993ApJ...410..696O}.
-Its physical properties and kinematics, along its stellar population are documented in \citet{2001ARA&A..39...99O}.
-
-\subsubsection{Lagoon Nebula}
-\label{sec:lagoon-nebula}
-
-The Lagoon Nebula (M8, NGC6523) is located at a distance of 1 250 pc \citetext{\SI{1}{\arcsecond} = \SI{0.006}{pc} ; \citealp{2005A&A...430..941P}}.
-It has a luminosity in \ha{} of \SI{e37.47}{erg.s^{-1}}\citep{1984ApJ...287..116K}.
-It contains the young stellar cluster NGC6530 and the region is illuminated by different massive stars of spectral types O and B, the hottest being 9 Sgr, type O4V \citep{Damiani:2017b}.
-Optically, the brightest part of the nebula is called 'Hourglass nebula' which surrounds and obscures the O7 star Herschel 36 \citep{1986AJ.....91..870W}. 
-The velocity field shows several expanding shells, related to the stellar population, and the massive protostar M8East-IR \citep{1984ApJ...278..170S} indicating that recent star formation. 
-A blueshifted, neutral layer is also in very good agreement with predictions of champagne-flow models of blister HII regions \citep{Damiani:2017b}. 
-The properties of the nebula are reviewed by \citet{2008hsf2.book..533T}.
-
-\subsubsection{Carina Nebula}
-\label{sec:carina-nebula}
-
-The Carina nebula is a large star-forming complex located at a distance of 2 350 pc \citetext{\SI{1}{\arcsecond} = \SI{0.01}{pc} ; \citealp{2006ApJ...644.1151S}}.
-Using the \ha{} luminosity as a diagnostic of the ionizing flux \(Q_0\) \citet{2007MNRAS.379.1279S} measured a value of \SI{e50.47}{photons.s^{-1}}.
-Young clusters like Trumpler 14 and 16, and Collinder 228 form the Car OB1 association, one of the largest OB associations on the Galaxy.
-This OB association has more than 65 stars earlier than B0, and several Wolf-Rayet (WR) stars.
-The most luminous star is the blue variable $\eta$ Car.
-As a star formation region, it presents several phenomena related with young stars as evaporating protoplanetary discs, erosion of large dust pillars and the triggering of a second generation of embedded stars and Herbig-Haro objects, to mention some \citetext{see \citealp{2008hsf2.book..138S} and reference therein}.
-This region can be consider as a bridge between the detailed star-formation regions like Orion, and much more distant regions like 30 Doradus.
-
-\subsubsection{30 Doradus}
-\label{sec:30-doradus}
-
-The 30 Doradus (Tarantula Nebula) nebula is located at a distance of 49.9 kpc \citetext{\SI{1}{\arcsecond} = \SI{0.24}{pc} ; \citealp{2013Natur.495...76P}}.
-It is a luminous star-forming region in the LMC (Large Magellanic Cloud) and is the most luminous complex in the Local Group \citep{1984ApJ...287..116K}.
-The central ionized region spans for 40 pc and host the massive, dense star cluster R136 %\citep{1991IAUS..148..145W}. %Note: check the bibliographic format
-The ionizing output \(Q_0\) of R136 is \SI{e51.4}{photons.s^{-1}} \citep{2020MNRAS.499.1918B}.
-It host the active star forming region NGC 2070 \citep{2013AJ....145...98W} where the star-formation rate has recently peaked \citep{2015ApJ...811...76C}. 
-NGC 2070 host a population of OB and WR stars \citep{2011A&A...530A.108E}.
-This nebula is commonly used as a comparison for extragalactic star-forming regions.
-
-\subsubsection{NGC 346}
-\label{sec:ngc-346}
-
-NGC 346 is the most active star-formation region in the SMC (Small Magellanic Cloud) located at a distance of 62 kpc \citetext{\SI{1}{\arcsecond} = \SI{0.30}{pc} ; \citealp{2001ApJ...562..303D}}. 
-It has more than 30 O stars that ionize N66, the largest HII region \citep{2011ApJ...740...10D}.
-N66 has an \ha{} luminosity of \SI{e38.77}{erg.s^{-1}}, almost 60 times higher compared to the Orion Nebula \citep{2010A&A...517A..39H,1984ApJ...287..116K}.
-\citet{2008ApJ...688.1050G} propose an expanding HII region or bubble blown by the winds of the massive progenitor as a mechanism that shapes the recent star formation in this region, in addition to the photoionizing process of the OB stars.
-This mechanism is similar to shell-like HII regions, with a central cluster in a cavity, and with ongoing star formation triggered around their periphery.
-Using a Gaussian single-component \citet{2003ApJ...586.1179D} find a corrected FWHM bulk turbulence of \SI{23.8}{km.s^{-1}}.
-
-\subsubsection{Hubble X and Hubble V in NGC 6822}
-\label{sec:6822-hubble}
-%Note to me: incomplete section. Find more regions info and finish asap.
-The irregular dwarf galaxy, NGC 6822, is located at a distance of 500 kpc \citetext{\SI{1}{\arcsecond} = \SI{2.42}{pc} ; \citealp{2012A&A...540A.135S}} and the brightest HII regions are Hubble X and Hubble V (HX and HV hereafter).
-%(1'' = 2.4 pc)
-%HV has a characteristic length of 100 pc and HX has a characteristic length of 140 pc \citep{1999PASP..111.1382O}.
-Luminosity \ha{} for HV is \SI{e38.3}{erg.s^{-1}} and for HX is \SI{e38.21}{erg.s^{-1}} \citep{2002MNRAS.329..481B}.
-Two recognized OB associations are identified within these HII regions \citep{1991ApJ...379..621H,1992AJ....104.1374W}.
-HV is located near 'Hodge OB 8' and HX is located near 'Hodge OB13'  \citep{1999PASP..111.1382O}.
-\citet{1993PASJ...45..693T} realize a study on the kinematics of HX and HV.
-
-%HV has a luminosity at its core of in L$_{H_\alpha}$ = 1 $\times$ 10$^{49}$ H$\alpha$ photons s$^{-1}$ 
-%HX has a luminosity at its core of in L$_{H_\alpha}$ = 2.4 $\times$ 10$^{49}$ H$\alpha$ photons s$^{-1}$ \citep{1999PASP..111.1382O}.
-
-\subsubsection{NGC~595 and NGC~604 in M33}
-\label{sec:m33-ngc}
-
-M33 is the third largest galaxy in the Local Group located at the distance of 840 kpc \citetext{\SI{1}{\arcsecond} = \SI{4.07}{pc} ; \citealp{2015KamKinematics}} and is of morphological type SA(s)cd.
-The two brightest HII regions in the galaxy are NGC 604 and NGC 595.
-
-NGC 604 is the second brightest \hii{} region in the Local Group after 30~Dor in the Large Magellanic Cloud and is forty times larger ($\sim $ 400 pc) and 6,000 times brighter than Orion in our Milky Way galaxy.
-It is the brightest giant \hii{} region in the M33 galaxy and is visually dominated by a big loop, big shells and different size filaments.
-It has a luminosity in \ha{} of \SI{e39.42}{erg.s^{-1}} \citep{2002MNRAS.329..481B}.
-Using photometry from the HST \citet{1996ApJ...456..174H} identified that the stars are separated into a primary cluster within NGC 604, and a secondary to the north of the region.
-In the primary there are \(\sim\)200 OB stars, candidate to red supergiants (RSGs) and the presence of WR stars.
-For the northern cluster they find eight luminous stars and no evolved massive stars.
-More Recently, \citet{2011MNRAS.411..235E} studied 10 WR stars and propose at least 4 RSGs candidates.
-\citet{2012AJ....143...43F} focused on the massive young stellar objects (MYSOs).
-The average ages for the stars, was determined to be from  \num{3} to \SI{5}{Myr} \citep{1996ApJ...456..174H} and with the RSGs as an older population have an age of 12.4\(\pm\)2.1 Myr \citep{2011MNRAS.411..235E}.
-This suggest that two episodes of star formation, at least, have taken place in the GEHR.
-
-% and in L$_{X}$=9.3$\times$ 10$^{35}$ erg s$^{-1}$ \citep{2008ApJ...685..919T}.
-%\citet{2012ApJ...761....3M} derive an average age of 4$\pm$1 Myr and a total stellar mass of 1.6$^{+1.6}_{-1.0} \times$ 10$^{5}$M$_{\odot}$ for the region.
-
-NGC 595 is the second brightest giant HII region in the M33 galaxy and has an \ha{} shell morphology that is related to the stellar winds of the several massive stars located in its interior.
-It has a luminosity in \ha{} of \SI{e38.95}{erg.s^{-1}}\citep{2002MNRAS.329..481B}.
-\citet{1993AJ....105.1400D} use optical photometry to propose 11 WR stars. 
-Using HST/WFPC-2 images \citet{1996AJ....111.1128M} found approximately 250 stars of the OB type, 13 Supergiants and 10 WR, confirming previous candidates.
-They derived and age of 4.5\(\pm\)1.0 Myr consistent with \citet{1993AJ....105.1400D}.
-\citet{2010MNRAS.402.1635R} used Integral Field Spectroscopy (IFS) to present a resolved study of the physical properties of the ionized gas and the ionized structure.
-They also confirm the presence of previous cataloged WR stars and detect new candidates, and propose classical emission-line ratios as metallicity calibrators.
-\citet{lagrois2011} present a kinematic study of the regions using optical emission lines and and radio 21 cm line observations.
-They proposed Champagne flows at the periphery of the molecular cloud leading to accelerated ionized material.
+Table~\ref{tab:regions-properties} summarises the properties of the regions in our sample
+with data taken from the literature. Further details on each individual source is given in Appendix~\ref{sec:notes-individual-hii}.
 
@@
 In practice, we achieve this by binning the separations with a constant
-logarithmic width of \SI{0.15}{dex}.
+logarithmic width of \SI{0.05}{dex}.
 
@@
 no help in predicting the velocity at the second point.
-At scales smaller than \(r_0\), the fluctuations often show a power-law behavior.
+At scales smaller than \(r_0\), the fluctuations often show a power-law behavior
+as a function of \(r\).
 
@@
 
-\subsubsection{Effects of observational limitations}
+\subsubsection{Effects of observational limitations at small spatial scales}
 \label{sec:effect-observ-limit}
@@
 An example is shown by the green line in Figure~\ref{fig:model-strucfunc}a.
-Note that the effect of seeing is to make the structure function 
+The effect of seeing is to make the structure function 
 bend down away from the idealized power law, 
 becoming increasingly steep at scales smaller than \(s_0\),
-but having a noticeable effect at scales up to \(10 s_0\).
+but having a noticeable effect at scales up to \(10 \times s_0\).
 
@@
 
+\subsubsection{Effects of observational limitations at large spatial scales}
+\label{sec:effects-observ-limit-large}
+
 In Appendix~\ref{sec:finite-box-effects} we consider the effects
@@
 and monotonically decreasing with \(r\).
-Instead, we restrict the model fitting range to scales less than \(L / 2\),
-where the influence of these effects should be minimal.
+We deal with this limitation by not attempting to model scales larger than \(L / 2\),
+where the influence of these effects will be greatest.
 
@@
 
-\section{Results}\label{sec:results}
-
-In this section we present and describe the second-order structure results.
-The structure functions are plotted against separation in parsecs and we also show the posteriors of the parameters discussed in the previous section.
-
-\subsection{HII regions second-order structure functions}
-
-%structure functions plots descriptions
-Figures \ref{fig:strucfunc-fit-OrionS}-\ref{fig:strucfunc-fit-OrionLH} left panels show in solid and open blue circles the observational structure function that we compute using equation \ref{eq:Br} on the \ha{} velocity fields of Fig.
-\ref{fig:velocity-maps}.
-In the plots the solid circles indicate the points we use in the non-linear regression analysis (see section~\ref{sec:model-fit}), while the open circles are the points of the structure function that where left out.
-The criteria for the previous considerations is that the structure function at large separations is affected by the inhomogeneties of the velocity field (see section-\ref{sec:limit-model-struct}).
-The points left our correspond to the largest separations that are not consider in our model. 
-In some cases, at the smallest separations we merge a couple of the structure functions points under the assumption that those would be heavily affected by the seeing.
-The Figures shows in the orange solid thick line the best fit for the equation \ref{eq:sf-functional} which takes into account observational limitations on the structure function.
-The green dashed line indicate the theoretical model for the structure function using equation \ref{eq:functional}.
-
-Figures \ref{fig:strucfunc-fit-OrionS}-\ref{fig:strucfunc-fit-OrionLH} left panels show in dashed and dotted lines the parameters of our model.
-The vertical dashed line indicates the correlation length, \(r_0\), and the horizontal dashed line indicates the true variance of the velocity fields, \(\sigma^2\).
-The vertical and horizontal dotted lines shows the value of the observational considerations: the rms seeing, \(s_0\) and the noise, \(B_{\text{noise}}\).
-These values were obtained using the LM method.
-For the dashed and dotted lines the overlapping translucent boxes indicate the confidence intervals in 1-sigma (dark shaded area) and 2-sigma (light shaded area) obtained from the MCMC analysis.
-The light shaded areas in the plot show where the separation \(r\) is above half of the box size, \(L\), which is indicated with a vertical dotted line.
-
-Figure~\ref{fig:strucfunc-fit-OrionS}a shows the structure function of the Orion core.
-Valid scales are consider above the separation of \SI{0.002}{pc} (\(s_0\)=\SI{1}{\arcsecond}).
-In this case we merge the first three points of the structure function.
-From \SI{0.002}{pc} until \SI{0.003}{pc} all points fall below the true model showing that they are affected by the seeing. 
-The correlation length for the Orion core is \SI{0.07}{pc}, it has a \(\sigma^2\pos\) of \SI{12}{km^{2}.s^{-2}} and an index of \num{1.07}.
-The structure function of the Orion core behaves accordingly to the tapered case of inhomogeneous fluctuations (see Figure~\ref{fig:model-strucfunc}b).
-At \SI{0.25}{pc} there is a plateau around \SI{22}{km^{2}.s^{-2}}.
-Above separations of \SI{0.3}{pc} the structure function decays to a value of \SI{7}{km^{2}.s^{-2}} at  \SI{0.5}{pc}.
-
-The Figure~\ref{fig:strucfunc-fit-M8}a shows the structure function of the Lagoon nebula.
-There aren't any points affected by the seeing which has a value of \SI{0.006}{pc} (\(s_0\)=\SI{1}{\arcsecond}).
-In this case we merge the first two points.
-The Lagoon nebula presents a non-uniform behavior below the correlation length but it is possible to see the characteristic ascending values of the structure function.
-The turbulent parameters that fits our model are a \(r_0\) of \SI{1}{pc}, a \(\sigma^2\pos\) of \SI{7}{km^{2}.s^{-2}} and an index of \num{1.17}.
-At large scales there is an indication of some periodic behavior followed by ascending \(B(r)\) values at largest separation.
-A value of\(B(r)\) of order 2\(\sigma^2\pos\) is \(\sim\)\SI{14}{km^{2}.s^{-2}} at a separation of \(\sim\)\SI{2.5}{pc}. 
-Then there is a diminution at \SI{4.5}{pc} down to a value of \SI{11}{km^{2}.s^{-2}}.
-From this point the structure function ascends until it reaches \SI{66}{km^{2}.s^{-2}} around \SI{20}{pc}.
-
-The Figure~\ref{fig:strucfunc-fit-CarC}a shows the structure function of the Carina nebula.
-The seeing is \SI{0.008}{pc} (\(s_0\)=\SI{1.3}{\arcsecond}) and there are just a couple of points that lie below the true model, indicating that the majority of points isn't affected by the seeing.
-For this region we merge the first two points of the structure function.
-As the Lagoon nebula, Carina also shows a non-uniform behavior below the correlation length.
-The correlation length is \SI{0.56}{pc} pc at a \(\sigma^2\pos\) of \SI{18}{km^{2}.s^{-2}} and an index of \num{1.14}.
-At larges scales the structure function of the Carina nebula follows a pattern that resembles the homogeneous fluctuation of Figure~\ref{fig:model-strucfunc}a.
-The structure function reaches a plateau around \SI{36}{km^{2}.s^{-2}} at \(\sim\) \SI{2}{pc}.
-When \(r >\)\SI{6}{pc} the structure functions shows a small amplitude periodic pattern around 2\(\sigma^2\pos\).
-
-For Carina and Lagoon nebula, the velocity fields are obtained from the FLAMES multi-fiber instrument (section~\ref{sec:flames-multi-fiber}). 
-We can see from Figure~\ref{fig:velocity-maps} that observations from this instrument do not give uniform maps as the others. 
-Instead, the discrete fiber positions are diversely located across the FOV.
-This would affect the structure function since the values are not adjacent as the other observations.
-This is reflected in the non uniform \(B(r)\) below  \(r_0\) that we pointed out in the previous paragraphs.
-
-The Figure~\ref{fig:strucfunc-fit-N346}a shows the structure function of NGC 346.
-In this case we merge the first three points of the structure function.
-The seeing value is \SI{0.07}{pc} (\(s_0\)=\SI{0.23}{\arcsecond}).
-For this region the first ten points lie below the true model.
-At separations above \SI{0.4}{pc} the observed structure functions is coincident with the true model. 
-The correlation length is \SI{2}{pc} at a \(\sigma^2\pos\) of \SI{35}{km^{2}.s^{-2}} and an index of \num{0.80}.
-For scales above \SI{12}{pc} and a \(B(r)\) value of \SI{65}{km^{2}.s^{-2}} the structure function shows a pattern of ascending values until it reaches \SI{146}{km^{2}.s^{-2}} at \SI{24}{pc}.
-
-The 30 Doradus structure function is shown in Figure~\ref{fig:strucfunc-fit-Dor}a.
-In this case we merge the first five points of the structure function.
-The seeing value for this regions is \SI{0.16}{pc} (\(s_0\)=\SI{0.7}{\arcsecond}) and just one point of the structure function is below this value.
-Until a separation of \SI{1.7}{pc} is reached, the structure function lies below the true model.
-The correlation length is \SI{4}{pc} at a \(\sigma^2\pos\) of \SI{297 \pm 9}{km^{2}.s^{-2}} and an index of \num{0.85}.
-At large separations 30 Doradus structure function presents a behavior of tapered fluctuations. The maximum \(B(r)\) value is \SI{655}{km^{2}.s^{-2}} at a separation of \SI{21}{pc}. 
-From there \(B(r)\) values descends until they reach \SI{250}{km^{2}.s^{-2}} at \SI{38}{pc}.
-
-In the Figure~\ref{fig:strucfunc-fit-HV}a we show the structure function of Hubble V.
-For the observations coming from the TAURUS-II instrument there wasn't any merging of points at small scales.
-The value of the seeing for this regions is \SI{0.5}{pc} (\(s_0\)=\SI{0.2}{\arcsecond}).
-All the structure function points lies below the true model.
-The correlation length is \SI{3.5}{pc} at a \(\sigma^2\pos\) of  \SI{10}{km^{2}.s^{-2}} and an index of \num{0.75}.
-The maximum \(B(r)\) value is \SI{18}{km^{2}.s^{-2}} at a separation of \SI{25}{pc}. 
-From there \(B(r)\) values descends until it reaches \SI{14}{km^{2}.s^{-2}} at \SI{45}{pc}, then it rises for the next point at \SI{50}{pc} with a value of \SI{15}{km^{2}.s^{-2}}.
-Finally the structure functions descends at \SI{9}{km^{2}.s^{-2}} for a separation of \SI{70}{pc}.
-
-The Hubble X structure function is shown in Figure~\ref{fig:strucfunc-fit-HX}a.
-The seeing is \SI{0.6}{pc} (\(s_0\)=\SI{0.24}{\arcsecond}) and as in Hubble V the observed structure function lies below the true model.
-The correlation length is \SI{4}{pc} at a \(\sigma^2\pos\) of \SI{15}{km^{2}.s^{-2}} and an index of \num{0.93}.
-A plateau is reached around \SI{25}{km^{2}.s^{-2}} at a separation of \SI{14}{pc} and a maximum \(B(r)\) value of \SI{31}{km^{2}.s^{-2}} at a separation of \SI{36}{pc}.
-
-In the Figure~\ref{fig:strucfunc-fit-N595}a we show the structure function of NGC 595.
-The seeing is \SI{0.3}{pc} (\(s_0\)=\SI{0.1}{\arcsecond}) and for this region only the first two points are below the true model. 
-The correlation length is \SI{12}{pc} at a \(\sigma^2\pos\) of \SI{54}{km^{2}.s^{-2}} and an index of \num{1.3}.
-At large scales the structure function behaves following the tapered fluctuations pattern.
-A maximum \(B(r)\) value of \SI{104}{km^{2}.s^{-2}} is reached at \SI{33}{pc}. 
-From there the structure functions decays following a scatter pattern until it reaches \SI{54}{km^{2}.s^{-2}} at a separation of \SI{211}{pc}.
-
-In the Figure~\ref{fig:strucfunc-fit-N604H}a we show the structure function of NGC 604.
-The seeing is \SI{1.7}{pc} (\(s_0\)=\SI{0.42}{\arcsecond}) and the structure function of this region lies below the true model for most of the separation range.
-The correlation length is \SI{10}{pc} at a \(\sigma^2\pos\) of \SI{71}{km^{2}.s^{-2}} and has an index of \num{1}.
-The structure function present clear characteristics of periodic oscillations at large scales.
-A periodic pattern for the structure function appears with a maximum \(B(r)\) value of \SI{143}{km^{2}.s^{-2}} that is reached at \SI{60}{pc}, then the oscillation cause a minimum of \SI{54}{km^{2}.s^{-2}} at \SI{133}{pc} and finally it goes back up again at \SI{211}{pc} to a \(B(r)\) value of \SI{123}{km^{2}.s^{-2}}.
-
-The EON structure function is shown in Figure~\ref{fig:strucfunc-fit-OrionLH}a.
-This observations are heavily affected by the noise which presents a value of \SI{6}{km^{2}.s^{-2}} which is larger that the \(\sigma^2\pos\) value of \SI{4}{km^{2}.s^{-2}}. 
-%corner plots descriptions
-Figures \ref{fig:strucfunc-fit-OrionS}-\ref{fig:strucfunc-fit-OrionLH} right panels show the corner plots \citep{2017ascl.soft02002F} of the turbulent parameters and observational constraints. 
-These plots shows the one and two dimensional projections of the posterior probability distributions of the parameters used in equation \ref{eq:chi}.
-They also show the distribution for each parameter independently in the histograms along the diagonal and then the marginalized two dimensional distributions in the other panels making possible to visualize all of the covariances between parameters \citep{2017ascl.soft02002F}.
-The contours in the plots reflect the 95\(\%\), 99\(\%\), 99.5\(\%\) and 99.9\(\%\) confidence intervals.
-A number of fits for the equations \ref{eq:sf-functional} and \ref{eq:functional} using samples of the posteriors are shown in thin translucent orange and green lines, respectively, showing the possible range of the confidence intervals.
-
-Table \ref{tab:Res} presents the turbulent parameters and observational constraints values mentioned in the paragraphs above.
-The confidence intervals for these values are up to 2-sigma of the posteriors.
-The second column correspond to the variance \(\sigma^2\pos\) of the velocity field.
-The \(B_{\text{noise}}\) value is shown in the third column which would be the minimum squared velocity difference that could be measure by the instrument.
-The forth column in Table \ref{tab:Res} shows the rms seeing value in parsecs, \(s_0\), which represent the minimum value of the separation which would valid for the observed structure function. 
-The fifth column shows the correlation value \(r_0\) in parsecs.
-The \(r_0\) range covered in our results for the sample goes from 0.09 to 12 pc.
-The sixth column indicates the size of each observational box in parsecs.
-The index \(m\) is shown in the seventh column.
-The range covered by the power-law index goes from 0.7 to 1.5.
-The eighth column show the ratio \(L / r_0\)
-The last column shows the FWHM seeing in arcsec.
-%The interpretation of our results is developed in the next section.
+\section{Structure function fits}
+\label{sec:results}
 
@@
   \centering
-  \sffigg{N346}{Dor}
+  \sffigg{Dor}{N346}
   \caption{
@@
 \input{SFresults}
+
+In order to provide a uniform description of the velocity fluctuations,
+we fit the model structure function described above (equation~\eqref{eq:sf-functional})
+to each of the \hii{} regions in our sample.
+Results are shown in Figures~\ref{fig:strucfunc-fit-Galactic}, \ref{fig:strucfunc-fit-MC},
+and \ref{fig:strucfunc-fit-ExtraGal}, arranged in order of increasing distance.
+
+In this section we present and describe the second-order structure results.
+The structure functions are plotted against separation in parsecs and we also show the posteriors of the parameters discussed in the previous section.
+
+%structure functions plots descriptions
+Figures \ref{fig:strucfunc-fit-OrionS}-\ref{fig:strucfunc-fit-OrionLH} left panels show in solid and open blue circles the observational structure function that we compute using equation \ref{eq:Br} on the \ha{} velocity fields of Fig.
+\ref{fig:velocity-maps}.
+In the plots the solid circles indicate the points we use in the non-linear regression analysis (see section~\ref{sec:model-fit}), while the open circles are the points of the structure function that where left out.
+The criteria for the previous considerations is that the structure function at large separations is affected by the inhomogeneties of the velocity field (see section-\ref{sec:limit-model-struct}).
+The points left our correspond to the largest separations that are not consider in our model. 
+In some cases, at the smallest separations we merge a couple of the structure functions points under the assumption that those would be heavily affected by the seeing.
+The Figures shows in the orange solid thick line the best fit for the equation \ref{eq:sf-functional} which takes into account observational limitations on the structure function.
+The green dashed line indicate the theoretical model for the structure function using equation \ref{eq:functional}.
+
+Figures \ref{fig:strucfunc-fit-OrionS}-\ref{fig:strucfunc-fit-OrionLH} left panels show in dashed and dotted lines the parameters of our model.
+The vertical dashed line indicates the correlation length, \(r_0\), and the horizontal dashed line indicates the true variance of the velocity fields, \(\sigma^2\).
+The vertical and horizontal dotted lines shows the value of the observational considerations: the rms seeing, \(s_0\) and the noise, \(B_{\text{noise}}\).
+These values were obtained using the LM method.
+For the dashed and dotted lines the overlapping translucent boxes indicate the confidence intervals in 1-sigma (dark shaded area) and 2-sigma (light shaded area) obtained from the MCMC analysis.
+The light shaded areas in the plot show where the separation \(r\) is above half of the box size, \(L\), which is indicated with a vertical dotted line.
+
+For Carina and Lagoon nebula, the velocity fields are obtained from the FLAMES multi-fiber instrument (section~\ref{sec:flames-multi-fiber}). 
+We can see from Figure~\ref{fig:velocity-maps} that observations from this instrument do not give uniform maps as the others. 
+Instead, the discrete fiber positions are diversely located across the FOV.
+This would affect the structure function since the values are not adjacent as the other observations.
+This is reflected in the non uniform \(B(r)\) below  \(r_0\) that we pointed out in the previous paragraphs.
+
+%corner plots descriptions
+Figures \ref{fig:corner-example-Orion} show the corner plots \citep{2017ascl.soft02002F} of the turbulent parameters and observational constraints
+(further examples in Appendix~\ref{sec:addit-covar-corn}).
+These plots shows the one and two dimensional projections of the posterior probability distributions of the parameters used in equation \ref{eq:chi}.
+They also show the distribution for each parameter independently in the histograms along the diagonal and then the marginalized two dimensional distributions in the other panels making possible to visualize all of the covariances between parameters \citep{2017ascl.soft02002F}.
+The contours in the plots reflect the 95\(\%\), 99\(\%\), 99.5\(\%\) and 99.9\(\%\) confidence intervals.
+A number of fits for the equations \ref{eq:sf-functional} and \ref{eq:functional} using samples of the posteriors are shown in thin translucent orange and green lines, respectively, showing the possible range of the confidence intervals.
+
+Table \ref{tab:Res} presents the turbulent parameters and observational constraints values mentioned in the paragraphs above.
+The confidence intervals for these values are up to 2-sigma of the posteriors.
+The second column correspond to the variance \(\sigma^2\pos\) of the velocity field.
+The \(B_{\text{noise}}\) value is shown in the third column which would be the minimum squared velocity difference that could be measure by the instrument.
+The fourth column in Table \ref{tab:Res} shows the rms seeing value in parsecs, \(s_0\), which represent the minimum value of the separation which would valid for the observed structure function. 
+The fifth column shows the correlation value \(r_0\) in parsecs.
+The \(r_0\) range covered in our results for the sample goes from 0.09 to 12 pc.
+The sixth column indicates the size of each observational box in parsecs.
+The index \(m\) is shown in the seventh column.
+The range covered by the power-law index goes from 0.7 to 1.5.
+The eighth column show the ratio \(L / r_0\)
+The last column shows the FWHM seeing in arcsec.
+%The interpretation of our results is developed in the next section.
 
@@
 The first attempt at characterizing turbulence in a giant extragalactic HII region, GEHR, was done by \citet{1961MNRAS.122....1F} with the 30 Doradus complex, finding no indication of turbulent motions between scale of 10 and 100 pc.
-These result is consistent with Fig. \ref{fig:strucfunc-fit-Dor} showing that the turbulent motions are correlated at scales \(<\) \SI{5}{pc}.
+These result is consistent with Fig. \ref{fig:strucfunc-fit-MC}a showing that the turbulent motions are correlated at scales \(<\) \SI{5}{pc}.
 \citet{Melnick:2021x} also investigated the structure function in 30 Doradus finding on their results that the structure function is entirely flat on scales from 3 to 200 pc.
@@
 Finally they point out, and we agree, the importance of observing NGC 604 at higher spatial resolution, so they rule out \citet{Medina-Tanco:1997a} results. 
-Our Fig. \ref{fig:strucfunc-fit-N604H} shows in fact that there is a velocity structure in NGC 604. 
+Our Fig. \ref{fig:strucfunc-fit-ExtraGal}d shows in fact that there is a velocity structure in NGC 604. 
 We have prove that a consistent and more precise method in analyzing structure function is key to obtaining trustworthy results.
@@
 
+\section{\boldmath Notes on individual \hii{} regions}
+\label{sec:notes-individual-hii}
+For each region or pair of regions in our sample,
+we give a more description of its physical properties
+(supplementing section~\ref{sec:regions-milky-way})
+together with additional details of the model fit to the structure function
+(supplementing section~\ref{sec:results}).
+
+\subsection{Orion Nebula}
+\label{sec:orion-nebula}
+
+The Orion Nebula (M42) is the prototype of a galactic HII region located at a distance of 440 pc \citetext{\SI{1}{\arcsecond} = \SI{0.002}{pc} ; \citealp{2008AJ....136.1566O}}.
+The O7 V star \(\theta^{1}\) Ori C is the most luminous and hottest star \citep{2006A&A...448..351S} with an ionizing flux \(Q_0\) of  \SI{e49.12}{photons.s^{-1}}. 
+With other 3 B-type stars they form the Trapezium cluster.
+The bright region that surrounds these massive ionizing stars is called the the Huygens region (Orion core henceforth).
+In the southwest direction of the Huygens region there is a drop in the brightness as one approach a much larger region called Extended Orion Nebula \citetext{EON henceforth;  \citealp{2008Sci...319..309G}}
+The position of Orion near the side of the Orion Molecular Cloud (OMC-1) make it an ongoing star formation with a large population of young star, some of which are the sources of stellar jets and Herbig-Haro objects \citep{1993ApJ...410..696O}.
+Its physical properties and kinematics, along its stellar population are documented in \citet{2001ARA&A..39...99O}.
+
+Figure~\ref{fig:strucfunc-fit-Galactic}a shows the structure function of the Orion core.
+Valid scales are consider above the separation of \SI{0.002}{pc} (\(s_0\)=\SI{1}{\arcsecond}).
+In this case we merge the first three points of the structure function.
+From \SI{0.002}{pc} until \SI{0.003}{pc} all points fall below the true model showing that they are affected by the seeing. 
+The correlation length for the Orion core is \SI{0.07}{pc}, it has a \(\sigma^2\pos\) of \SI{12}{km^{2}.s^{-2}} and an index of \num{1.07}.
+The structure function of the Orion core behaves accordingly to the tapered case of inhomogeneous fluctuations (see Figure~\ref{fig:model-strucfunc}b).
+At \SI{0.25}{pc} there is a plateau around \SI{22}{km^{2}.s^{-2}}.
+Above separations of \SI{0.3}{pc} the structure function decays to a value of \SI{7}{km^{2}.s^{-2}} at  \SI{0.5}{pc}.
+
+The EON structure function is shown in Figure~\ref{fig:strucfunc-fit-Galactic}c.
+This observations are heavily affected by the noise which presents a value of \SI{6}{km^{2}.s^{-2}} which is larger that the \(\sigma^2\pos\) value of \SI{4}{km^{2}.s^{-2}}.
+
+\subsection{Lagoon Nebula}
+\label{sec:lagoon-nebula}
+
+The Lagoon Nebula (M8, NGC6523) is located at a distance of 1 250 pc \citetext{\SI{1}{\arcsecond} = \SI{0.006}{pc} ; \citealp{2005A&A...430..941P}}.
+It has a luminosity in \ha{} of \SI{e37.47}{erg.s^{-1}}\citep{1984ApJ...287..116K}.
+It contains the young stellar cluster NGC6530 and the region is illuminated by different massive stars of spectral types O and B, the hottest being 9 Sgr, type O4V \citep{Damiani:2017b}.
+Optically, the brightest part of the nebula is called 'Hourglass nebula' which surrounds and obscures the O7 star Herschel 36 \citep{1986AJ.....91..870W}. 
+The velocity field shows several expanding shells, related to the stellar population, and the massive protostar M8East-IR \citep{1984ApJ...278..170S} indicating that recent star formation. 
+A blueshifted, neutral layer is also in very good agreement with predictions of champagne-flow models of blister HII regions \citep{Damiani:2017b}. 
+The properties of the nebula are reviewed by \citet{2008hsf2.book..533T}.
+
+The Figure~\ref{fig:strucfunc-fit-Galactic}c shows the structure function of the Lagoon nebula.
+There aren't any points affected by the seeing which has a value of \SI{0.006}{pc} (\(s_0\)=\SI{1}{\arcsecond}).
+In this case we merge the first two points.
+The Lagoon nebula presents a non-uniform behavior below the correlation length but it is possible to see the characteristic ascending values of the structure function.
+The turbulent parameters that fits our model are a \(r_0\) of \SI{1}{pc}, a \(\sigma^2\pos\) of \SI{7}{km^{2}.s^{-2}} and an index of \num{1.17}.
+At large scales there is an indication of some periodic behavior followed by ascending \(B(r)\) values at largest separation.
+A value of\(B(r)\) of order 2\(\sigma^2\pos\) is \(\sim\)\SI{14}{km^{2}.s^{-2}} at a separation of \(\sim\)\SI{2.5}{pc}. 
+Then there is a diminution at \SI{4.5}{pc} down to a value of \SI{11}{km^{2}.s^{-2}}.
+From this point the structure function ascends until it reaches \SI{66}{km^{2}.s^{-2}} around \SI{20}{pc}.
+
+\subsection{Carina Nebula}
+\label{sec:carina-nebula}
+
+The Carina nebula is a large star-forming complex located at a distance of 2 350 pc \citetext{\SI{1}{\arcsecond} = \SI{0.01}{pc} ; \citealp{2006ApJ...644.1151S}}.
+Using the \ha{} luminosity as a diagnostic of the ionizing flux \(Q_0\) \citet{2007MNRAS.379.1279S} measured a value of \SI{e50.47}{photons.s^{-1}}.
+Young clusters like Trumpler 14 and 16, and Collinder 228 form the Car OB1 association, one of the largest OB associations on the Galaxy.
+This OB association has more than 65 stars earlier than B0, and several Wolf-Rayet (WR) stars.
+The most luminous star is the blue variable $\eta$ Car.
+As a star formation region, it presents several phenomena related with young stars as evaporating protoplanetary discs, erosion of large dust pillars and the triggering of a second generation of embedded stars and Herbig-Haro objects, to mention some \citetext{see \citealp{2008hsf2.book..138S} and reference therein}.
+This region can be consider as a bridge between the detailed star-formation regions like Orion, and much more distant regions like 30 Doradus.
+
+(The Figure~\ref{fig:strucfunc-fit-Galactic}d shows the structure function of the Carina nebula.
+The seeing is \SI{0.008}{pc} (\(s_0\)=\SI{1.3}{\arcsecond}) and there are just a couple of points that lie below the true model, indicating that the majority of points isn't affected by the seeing.
+For this region we merge the first two points of the structure function.
+As the Lagoon nebula, Carina also shows a non-uniform behavior below the correlation length.
+The correlation length is \SI{0.56}{pc} pc at a \(\sigma^2\pos\) of \SI{18}{km^{2}.s^{-2}} and an index of \num{1.14}.
+At larges scales the structure function of the Carina nebula follows a pattern that resembles the homogeneous fluctuation of Figure~\ref{fig:model-strucfunc}a.
+The structure function reaches a plateau around \SI{36}{km^{2}.s^{-2}} at \(\sim\) \SI{2}{pc}.
+When \(r >\)\SI{6}{pc} the structure functions shows a small amplitude periodic pattern around 2\(\sigma^2\pos\).
+
+\subsection{30 Doradus}
+\label{sec:30-doradus}
+
+The 30 Doradus (Tarantula Nebula) nebula is located at a distance of 49.9 kpc \citetext{\SI{1}{\arcsecond} = \SI{0.24}{pc} ; \citealp{2013Natur.495...76P}}.
+It is a luminous star-forming region in the LMC (Large Magellanic Cloud) and is the most luminous complex in the Local Group \citep{1984ApJ...287..116K}.
+The central ionized region spans for 40 pc and host the massive, dense star cluster R136 %\citep{1991IAUS..148..145W}. %Note: check the bibliographic format
+The ionizing output \(Q_0\) of R136 is \SI{e51.4}{photons.s^{-1}} \citep{2020MNRAS.499.1918B}.
+It host the active star forming region NGC 2070 \citep{2013AJ....145...98W} where the star-formation rate has recently peaked \citep{2015ApJ...811...76C}. 
+NGC 2070 host a population of OB and WR stars \citep{2011A&A...530A.108E}.
+This nebula is commonly used as a comparison for extragalactic star-forming regions.
+
+The 30 Doradus structure function is shown in Figure~\ref{fig:strucfunc-fit-MC}a.
+In this case we merge the first five points of the structure function.
+The seeing value for this regions is \SI{0.16}{pc} (\(s_0\)=\SI{0.7}{\arcsecond}) and just one point of the structure function is below this value.
+Until a separation of \SI{1.7}{pc} is reached, the structure function lies below the true model.
+The correlation length is \SI{4}{pc} at a \(\sigma^2\pos\) of \SI{297 \pm 9}{km^{2}.s^{-2}} and an index of \num{0.85}.
+At large separations 30 Doradus structure function presents a behavior of tapered fluctuations. The maximum \(B(r)\) value is \SI{655}{km^{2}.s^{-2}} at a separation of \SI{21}{pc}. 
+From there \(B(r)\) values descends until they reach \SI{250}{km^{2}.s^{-2}} at \SI{38}{pc}.
+
+\subsection{NGC 346}
+\label{sec:ngc-346}
+
+NGC 346 is the most active star-formation region in the SMC (Small Magellanic Cloud) located at a distance of 62 kpc \citetext{\SI{1}{\arcsecond} = \SI{0.30}{pc} ; \citealp{2001ApJ...562..303D}}. 
+It has more than 30 O stars that ionize N66, the largest HII region \citep{2011ApJ...740...10D}.
+N66 has an \ha{} luminosity of \SI{e38.77}{erg.s^{-1}}, almost 60 times higher compared to the Orion Nebula \citep{2010A&A...517A..39H,1984ApJ...287..116K}.
+\citet{2008ApJ...688.1050G} propose an expanding HII region or bubble blown by the winds of the massive progenitor as a mechanism that shapes the recent star formation in this region, in addition to the photoionizing process of the OB stars.
+This mechanism is similar to shell-like HII regions, with a central cluster in a cavity, and with ongoing star formation triggered around their periphery.
+Using a Gaussian single-component \citet{2003ApJ...586.1179D} find a corrected FWHM bulk turbulence of \SI{23.8}{km.s^{-1}}.
+
+The Figure~\ref{fig:strucfunc-fit-MC}b shows the structure function of NGC 346.
+In this case we merge the first three points of the structure function.
+The seeing value is \SI{0.07}{pc} (\(s_0\)=\SI{0.23}{\arcsecond}).
+For this region the first ten points lie below the true model.
+At separations above \SI{0.4}{pc} the observed structure functions is coincident with the true model. 
+The correlation length is \SI{2}{pc} at a \(\sigma^2\pos\) of \SI{35}{km^{2}.s^{-2}} and an index of \num{0.80}.
+For scales above \SI{12}{pc} and a \(B(r)\) value of \SI{65}{km^{2}.s^{-2}} the structure function shows a pattern of ascending values until it reaches \SI{146}{km^{2}.s^{-2}} at \SI{24}{pc}.
+
+\subsection{Hubble X and Hubble V in NGC 6822}
+\label{sec:6822-hubble}
+%Note to me: incomplete section. Find more regions info and finish asap.
+The irregular dwarf galaxy, NGC 6822, is located at a distance of 500 kpc \citetext{\SI{1}{\arcsecond} = \SI{2.42}{pc} ; \citealp{2012A&A...540A.135S}} and the brightest HII regions are Hubble X and Hubble V (HX and HV hereafter).
+%(1'' = 2.4 pc)
+%HV has a characteristic length of 100 pc and HX has a characteristic length of 140 pc \citep{1999PASP..111.1382O}.
+Luminosity \ha{} for HV is \SI{e38.3}{erg.s^{-1}} and for HX is \SI{e38.21}{erg.s^{-1}} \citep{2002MNRAS.329..481B}.
+Two recognized OB associations are identified within these HII regions \citep{1991ApJ...379..621H,1992AJ....104.1374W}.
+HV is located near 'Hodge OB 8' and HX is located near 'Hodge OB13'  \citep{1999PASP..111.1382O}.
+\citet{1993PASJ...45..693T} realize a study on the kinematics of HX and HV.
+
+%HV has a luminosity at its core of in L$_{H_\alpha}$ = 1 $\times$ 10$^{49}$ H$\alpha$ photons s$^{-1}$ 
+%HX has a luminosity at its core of in L$_{H_\alpha}$ = 2.4 $\times$ 10$^{49}$ H$\alpha$ photons s$^{-1}$ \citep{1999PASP..111.1382O}.
+
+In the Figure~\ref{fig:strucfunc-fit-ExtraGal}a we show the structure function of Hubble V.
+For the observations coming from the TAURUS-II instrument there wasn't any merging of points at small scales.
+The value of the seeing for this regions is \SI{0.5}{pc} (\(s_0\)=\SI{0.2}{\arcsecond}).
+All the structure function points lies below the true model.
+The correlation length is \SI{3.5}{pc} at a \(\sigma^2\pos\) of  \SI{10}{km^{2}.s^{-2}} and an index of \num{0.75}.
+The maximum \(B(r)\) value is \SI{18}{km^{2}.s^{-2}} at a separation of \SI{25}{pc}. 
+From there \(B(r)\) values descends until it reaches \SI{14}{km^{2}.s^{-2}} at \SI{45}{pc}, then it rises for the next point at \SI{50}{pc} with a value of \SI{15}{km^{2}.s^{-2}}.
+Finally the structure functions descends at \SI{9}{km^{2}.s^{-2}} for a separation of \SI{70}{pc}.
+
+The Hubble X structure function is shown in Figure~\ref{fig:strucfunc-fit-ExtraGal}b.
+The seeing is \SI{0.6}{pc} (\(s_0\)=\SI{0.24}{\arcsecond}) and as in Hubble V the observed structure function lies below the true model.
+The correlation length is \SI{4}{pc} at a \(\sigma^2\pos\) of \SI{15}{km^{2}.s^{-2}} and an index of \num{0.93}.
+A plateau is reached around \SI{25}{km^{2}.s^{-2}} at a separation of \SI{14}{pc} and a maximum \(B(r)\) value of \SI{31}{km^{2}.s^{-2}} at a separation of \SI{36}{pc}.
+
+\subsection{NGC~595 and NGC~604 in M33}
+\label{sec:m33-ngc}
+
+M33 is the third largest galaxy in the Local Group located at the distance of 840 kpc \citetext{\SI{1}{\arcsecond} = \SI{4.07}{pc} ; \citealp{2015KamKinematics}} and is of morphological type SA(s)cd.
+The two brightest HII regions in the galaxy are NGC 604 and NGC 595.
+
+NGC 604 is the second brightest \hii{} region in the Local Group after 30~Dor in the Large Magellanic Cloud and is forty times larger ($\sim $ 400 pc) and 6,000 times brighter than Orion in our Milky Way galaxy.
+It is the brightest giant \hii{} region in the M33 galaxy and is visually dominated by a big loop, big shells and different size filaments.
+It has a luminosity in \ha{} of \SI{e39.42}{erg.s^{-1}} \citep{2002MNRAS.329..481B}.
+Using photometry from the HST \citet{1996ApJ...456..174H} identified that the stars are separated into a primary cluster within NGC 604, and a secondary to the north of the region.
+In the primary there are \(\sim\)200 OB stars, candidate to red supergiants (RSGs) and the presence of WR stars.
+For the northern cluster they find eight luminous stars and no evolved massive stars.
+More Recently, \citet{2011MNRAS.411..235E} studied 10 WR stars and propose at least 4 RSGs candidates.
+\citet{2012AJ....143...43F} focused on the massive young stellar objects (MYSOs).
+The average ages for the stars, was determined to be from  \num{3} to \SI{5}{Myr} \citep{1996ApJ...456..174H} and with the RSGs as an older population have an age of 12.4\(\pm\)2.1 Myr \citep{2011MNRAS.411..235E}.
+This suggest that two episodes of star formation, at least, have taken place in the GEHR.
+
+% and in L$_{X}$=9.3$\times$ 10$^{35}$ erg s$^{-1}$ \citep{2008ApJ...685..919T}.
+%\citet{2012ApJ...761....3M} derive an average age of 4$\pm$1 Myr and a total stellar mass of 1.6$^{+1.6}_{-1.0} \times$ 10$^{5}$M$_{\odot}$ for the region.
+
+NGC 595 is the second brightest giant HII region in the M33 galaxy and has an \ha{} shell morphology that is related to the stellar winds of the several massive stars located in its interior.
+It has a luminosity in \ha{} of \SI{e38.95}{erg.s^{-1}}\citep{2002MNRAS.329..481B}.
+\citet{1993AJ....105.1400D} use optical photometry to propose 11 WR stars. 
+Using HST/WFPC-2 images \citet{1996AJ....111.1128M} found approximately 250 stars of the OB type, 13 Supergiants and 10 WR, confirming previous candidates.
+They derived and age of 4.5\(\pm\)1.0 Myr consistent with \citet{1993AJ....105.1400D}.
+\citet{2010MNRAS.402.1635R} used Integral Field Spectroscopy (IFS) to present a resolved study of the physical properties of the ionized gas and the ionized structure.
+They also confirm the presence of previous cataloged WR stars and detect new candidates, and propose classical emission-line ratios as metallicity calibrators.
+\citet{lagrois2011} present a kinematic study of the regions using optical emission lines and and radio 21 cm line observations.
+They proposed Champagne flows at the periphery of the molecular cloud leading to accelerated ionized material.
+
+In the Figure~\ref{fig:strucfunc-fit-ExtraGal}c we show the structure function of NGC 595.
+The seeing is \SI{0.3}{pc} (\(s_0\)=\SI{0.1}{\arcsecond}) and for this region only the first two points are below the true model. 
+The correlation length is \SI{12}{pc} at a \(\sigma^2\pos\) of \SI{54}{km^{2}.s^{-2}} and an index of \num{1.3}.
+At large scales the structure function behaves following the tapered fluctuations pattern.
+A maximum \(B(r)\) value of \SI{104}{km^{2}.s^{-2}} is reached at \SI{33}{pc}. 
+From there the structure functions decays following a scatter pattern until it reaches \SI{54}{km^{2}.s^{-2}} at a separation of \SI{211}{pc}.
+
+In the Figure~\ref{fig:strucfunc-fit-ExtraGal}d we show the structure function of NGC 604.
+The seeing is \SI{1.7}{pc} (\(s_0\)=\SI{0.42}{\arcsecond}) and the structure function of this region lies below the true model for most of the separation range.
+The correlation length is \SI{10}{pc} at a \(\sigma^2\pos\) of \SI{71}{km^{2}.s^{-2}} and has an index of \num{1}.
+The structure function present clear characteristics of periodic oscillations at large scales.
+A periodic pattern for the structure function appears with a maximum \(B(r)\) value of \SI{143}{km^{2}.s^{-2}} that is reached at \SI{60}{pc}, then the oscillation cause a minimum of \SI{54}{km^{2}.s^{-2}} at \SI{133}{pc} and finally it goes back up again at \SI{211}{pc} to a \(B(r)\) value of \SI{123}{km^{2}.s^{-2}}.
+
 \section{Degradation of the structure function due to observational limitations}
@@
 \label{sec:finite-box-effects}
-
-The Figure \ref{fig:finite-box}a shows some of the simulated velocity fields we use to study the variations in the structure function with respect to the size of the observational box.
-Initially we have an original field of \(512 \times 512 \) pixels that are divided \(n\) times and produce \(N = 4^n\) fields, where each one has a linear size \(L \times L \) with \(L = 2^{9 -n}\).
-The structure function is calculated for each division and later we average all the divisions of the corresponding map.
-
-The Figure \ref{fig:finite-box}b shows in solid lines the normalized averaged structure functions for the maps in Figure \ref{fig:finite-box}a.
-The number \(N\) of divisions and the length \(L\) are indicated in each structure function.
-The shaded areas show the deviation that each average structure function has due to the different divisions. 
-\textit{(Note: I modified the Figure adding \(\sigma^2\) and \(r_0\) for each SF since I think it is easier and more directly to grasp the effect of reducing the box size.
-The figure is more 'noisy' but if it seems like it contribute to nothing we can change it back.)}
-
-The blue horizontal and vertical dashed lines show the true \(r_{0}\) and the value of \(B(r) / \sigma^2 = 1 \), respectively.
-The colored dotted lines indicate the averages, taking into account all the divisions of each map, of the apparent \(r_ {0}\) and the apparent \(\sigma^2 \).
-From this analysis it is clear that \(r_0\) and \(\sigma^ 2 \) decrease with respect to the true values as the size \(L\) of the observational box decreases. 
-This analysis is performed on different maps (no images are shown) given a different power law in the velocity spectrum and different correlation lengths, giving the same results.
-
-Figure \ref{fig:finite-box-effect} shows the ratio of the correlation length of each averaged map with respect to the true correlation length, \(\text{apparent } r_ 0 /\text{true } r_0 \), as well as the ratio between the averaged variance of each divided map and the true variance, \(\text{apparent } \sigma^2  / \text{true } \sigma^2\).
-We observe that for the values where \(L\), is 20 $> r_0 $ the change in the ratios is null.
-It is for the values where \( L < 10 r_0 \) a considerable decrease in both ratios is observed.
-This behavior is fulfilled for all simulated maps with different power law in the velocity spectrum and different correlation functions, indicated with different colored circles in Figure \ref{fig:finite-box-effect}.
-These variations of the ratios are used to characterize the effect that the decrease of the observational box size has in \(r_0\) and \(\sigma^2\).
-
-The fitted dashed line in Figure \ref{fig:finite-box-effect} is given by the equation:
-
-\begin{equation}\label{eq:ajustebox}
-\beta(r_0) = 1 - exp \left[ \frac{L}{3.6r_0} \right] 
-\end{equation}
-%
-and it is used in the functional form that fits the observational structure function when adjusting the results to obtain the reported parameters \(r_0\) and \(\sigma^2 \).
 
@@
 
+The Figure \ref{fig:finite-box}a shows some of the simulated velocity fields we use to study the variations in the structure function with respect to the size of the observational box.
+Initially we have an original field of \(512 \times 512 \) pixels that are divided \(n\) times and produce \(N = 4^n\) fields, where each one has a linear size \(L \times L \) with \(L = 2^{9 -n}\).
+The structure function is calculated for each division and later we average all the divisions of the corresponding map.
+
+The Figure \ref{fig:finite-box}b shows in solid lines the normalized averaged structure functions for the maps in Figure \ref{fig:finite-box}a.
+The number \(N\) of divisions and the length \(L\) are indicated in each structure function.
+The shaded areas show the deviation that each average structure function has due to the different divisions. 
+\textit{(Note: I modified the Figure adding \(\sigma^2\) and \(r_0\) for each SF since I think it is easier and more directly to grasp the effect of reducing the box size.
+The figure is more 'noisy' but if it seems like it contribute to nothing we can change it back.)}
+
+The blue horizontal and vertical dashed lines show the true \(r_{0}\) and the value of \(B(r) / \sigma^2 = 1 \), respectively.
+The colored dotted lines indicate the averages, taking into account all the divisions of each map, of the apparent \(r_ {0}\) and the apparent \(\sigma^2 \).
+From this analysis it is clear that \(r_0\) and \(\sigma^ 2 \) decrease with respect to the true values as the size \(L\) of the observational box decreases. 
+This analysis is performed on different maps (no images are shown) given a different power law in the velocity spectrum and different correlation lengths, giving the same results.
+
+Figure \ref{fig:finite-box-effect} shows the ratio of the correlation length of each averaged map with respect to the true correlation length, \(\text{apparent } r_ 0 /\text{true } r_0 \), as well as the ratio between the averaged variance of each divided map and the true variance, \(\text{apparent } \sigma^2  / \text{true } \sigma^2\).
+We observe that for the values where \(L\), is 20 $> r_0 $ the change in the ratios is null.
+It is for the values where \( L < 10 r_0 \) a considerable decrease in both ratios is observed.
+This behavior is fulfilled for all simulated maps with different power law in the velocity spectrum and different correlation functions, indicated with different colored circles in Figure \ref{fig:finite-box-effect}.
+These variations of the ratios are used to characterize the effect that the decrease of the observational box size has in \(r_0\) and \(\sigma^2\).
+
+The fitted dashed line in Figure \ref{fig:finite-box-effect} is given by the equation:
+
+\begin{equation}\label{eq:ajustebox}
+\beta(r_0) = 1 - exp \left[ \frac{L}{3.6r_0} \right] 
+\end{equation}
+%
+and it is used in the functional form that fits the observational structure function when adjusting the results to obtain the reported parameters \(r_0\) and \(\sigma^2 \).
+
 \subsection{Effects of seeing}
 \label{sec:effects-seeing-struc}
-
-Ground-based astronomical observations are affected by the seeing produced by the atmosphere.
-When calculating the structure function of these observations, this seeing affects the results at small-scale separations due to the smoothing of velocity fluctuations between adjacent pixels.
-To study the consequences of the seeing we calculate the structure function of velocity maps where an artificial Gaussian seeing with different line widths has been introduced.
-The artificial velocity maps are created in the same way as to study the effect of the observational box.
-Seeing in velocity maps is added via the \textit{astropy} package using the \textit{Gaussian2DKernel} command.
-
-The rows in Figure \ref{fig:seeing-reduction}a show a synthetic velocity field of 512 \(\times\) 512 divided into four maps of 256 \(\times \) 256.
-The color scale is the same for all maps and it considers \(- 3\) to \(+ 3\) times the standard deviation.
-A Gaussian seeing, \(s_0 \) is applied to each division, with an RMS width ranging from 1 to 32 pixels, shown in the columns of Figure \ref{fig:seeing-reduction}. 
-The structure function is computed in these maps and the averaged considering the same seeing.
-
-The solid lines in Figure \ref{fig:seeing-reduction}b  show the ratio of the structure function of the averages of the maps with their respective seeing and the map without it: \(B (r, s_0 ) / B (r, s_0 = 0) \).
-The circle symbols indicate the value of 2\(s_0\) while the plus symbols indicate the apparent correlation length of smoothed map.
-The vertical dotted line indicates the true \(r_ {0} \).
-
-The dashed lines in Figure \ref{fig:seeing-reduction}b are  empirically fits for each ratio.
-To obtain this fit, we start from a convolution of an emission line and Gaussian seeing.
-The emission line has the form \(\text {I}(x, v) = \text{I}_0 \phi [v; \overline {v} (x), \sigma_0]\) and has uniform width and brightness where the only change with respect to position is the velocity centroid.
-The proposed seeing is \(\text{K}(x, s_0)\) of the form \(1 / \sqrt{2 \pi s_0} \exp^ {-x^ 2 / 2s_0 ^ 2} \).
-The convolution \(\text{I}(x, v) \otimes \text{K}(x, s_0) \) is performed to obtain the smoothed map, \(\text {\~I} (x, v) \).
-
-Then we calculate the average velocity difference of the original map, \(\Delta v \), and the smoothed map, \(\tilde{\Delta v}\), in the points \( x = \{0, \delta \} \).
-This expansion gives a term that modifies the final form of the structure function, \(~B (r)\), where the structure function without the seeing, \(B(r) \), is corrected by the term \(S_0(r; s_0)\) which has the form:
-
-\begin{equation}\label{eq:seeingcon}
-S (r;s_0) = \tanh^2 \left[ \left( \dfrac{r}{2s_0} \right)^2 \right]
-\end{equation}
-
-Subsequently, the equation \ref{eq:seeingcon} is empirically modified and we obtain:
-
-\begin{equation}\label{eq:seeingemp}
-S(r; s_0, r_0) =  \frac{e^\frac{-s_0}{r_0}}{2} \left(1 + \tanh{a \text{ln} \frac{r}{2s_0}} \right)
-\end{equation}
-%
-and the final form of the equation \ref{eq:seeingemp} after a mathematical simplification gives:
-
-\begin{equation}\label{eq:seeingemp2}
-S(r; s_0, r_0) = \frac{e^\frac{-s_0}{r_0}}{1+(\frac{2s_0}{r})^{2a}}
-\end{equation}
-%
-which describes the fit (dashed lines) in Figure \ref{fig:seeing-reduction}b.
-
-The equation \ref{eq:seeingemp2} is used to correct the observational structure function, \(B(r)\).
 
@@
 
+Ground-based astronomical observations are affected by the seeing produced by the atmosphere.
+When calculating the structure function of these observations, this seeing affects the results at small-scale separations due to the smoothing of velocity fluctuations between adjacent pixels.
+To study the consequences of the seeing we calculate the structure function of velocity maps where an artificial Gaussian seeing with different line widths has been introduced.
+The artificial velocity maps are created in the same way as to study the effect of the observational box.
+Seeing in velocity maps is added via the \textit{astropy} package using the \textit{Gaussian2DKernel} command.
+
+The rows in Figure \ref{fig:seeing-reduction}a show a synthetic velocity field of 512 \(\times\) 512 divided into four maps of 256 \(\times \) 256.
+The color scale is the same for all maps and it considers \(- 3\) to \(+ 3\) times the standard deviation.
+A Gaussian seeing, \(s_0 \) is applied to each division, with an RMS width ranging from 1 to 32 pixels, shown in the columns of Figure \ref{fig:seeing-reduction}. 
+The structure function is computed in these maps and the averaged considering the same seeing.
+
+The solid lines in Figure \ref{fig:seeing-reduction}b  show the ratio of the structure function of the averages of the maps with their respective seeing and the map without it: \(B (r, s_0 ) / B (r, s_0 = 0) \).
+The circle symbols indicate the value of 2\(s_0\) while the plus symbols indicate the apparent correlation length of smoothed map.
+The vertical dotted line indicates the true \(r_ {0} \).
+
+The dashed lines in Figure \ref{fig:seeing-reduction}b are  empirically fits for each ratio.
+To obtain this fit, we start from a convolution of an emission line and Gaussian seeing.
+The emission line has the form \(\text {I}(x, v) = \text{I}_0 \phi [v; \overline {v} (x), \sigma_0]\) and has uniform width and brightness where the only change with respect to position is the velocity centroid.
+The proposed seeing is \(\text{K}(x, s_0)\) of the form \(1 / \sqrt{2 \pi s_0} \exp^ {-x^ 2 / 2s_0 ^ 2} \).
+The convolution \(\text{I}(x, v) \otimes \text{K}(x, s_0) \) is performed to obtain the smoothed map, \(\text {\~I} (x, v) \).
+
+Then we calculate the average velocity difference of the original map, \(\Delta v \), and the smoothed map, \(\tilde{\Delta v}\), in the points \( x = \{0, \delta \} \).
+This expansion gives a term that modifies the final form of the structure function, \(~B (r)\), where the structure function without the seeing, \(B(r) \), is corrected by the term \(S_0(r; s_0)\) which has the form:
+
+\begin{equation}\label{eq:seeingcon}
+S (r;s_0) = \tanh^2 \left[ \left( \dfrac{r}{2s_0} \right)^2 \right]
+\end{equation}
+
+Subsequently, the equation \ref{eq:seeingcon} is empirically modified and we obtain:
+
+\begin{equation}\label{eq:seeingemp}
+S(r; s_0, r_0) =  \frac{e^\frac{-s_0}{r_0}}{2} \left(1 + \tanh{a \text{ln} \frac{r}{2s_0}} \right)
+\end{equation}
+%
+and the final form of the equation \ref{eq:seeingemp} after a mathematical simplification gives:
+
+\begin{equation}\label{eq:seeingemp2}
+S(r; s_0, r_0) = \frac{e^\frac{-s_0}{r_0}}{1+(\frac{2s_0}{r})^{2a}}
+\end{equation}
+%
+which describes the fit (dashed lines) in Figure \ref{fig:seeing-reduction}b.
+
+The equation \ref{eq:seeingemp2} is used to correct the observational structure function, \(B(r)\).
+
 \section{Additional covariance corner plots for model fits}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
+\clearpage
 % Don't change these lines

### 2022-04-17 strucfunc_paper.tex
Revise the description of the model fits
Not quite finished

@@
 \newcommand\los{\ensuremath{_{\mathrm{los}}}}
-
+\newcommand\noise{\ensuremath{_{\text{noise}}}}
 \newcommand\halpha{H${\alpha}$}
@@
 \begin{equation}\label{eq:ffs}
-   S(r; s_0, r_0) = \frac{
+   S(r) = \frac{
     e^{-s_0 / r_0}
@@
 \end{equation}
-where \(s_0\) is the RMS width of the seeing profile.\footnote{%
+where \(s_0\) is the RMS width of the seeing profile\footnote{%
   Note that the full-width half maximum (FWHM) seeing width is
@@
 }
+and \(r_0\) is the correlation length.
 An example is shown by the green line in Figure~\ref{fig:model-strucfunc}a.
@@
 then its contribution to the structure function is independent of separation,
-which means it can be represented as a constant term \(B_{\text{noise}}\).
+which means it can be represented as a constant term \(B\noise\).
 
@@
 model structure function:
-\begin{multline}
-  \tilde{B}
-  \bigl( r; \ r_0, \sigma^2\pos, m, s_0, B_{\text{noise}} \bigr)
-  = \\
+\begin{equation}
+  \tilde{B}(r)
+  = 
   2\sigma^2\pos \left[
@@
   \right]
-  \,  S(r; s_0, r_0) + B_{\text{noise}}
+  \,  S(r) + B\noise
 \label{eq:sf-functional}
-\end{multline}
+\end{equation}
 An example of this equation is shown by the red line in Figure~\ref{fig:model-strucfunc}.
@@
 
-\subsubsection{Model fitting and estimation of confidence intervals}
-\label{sec:model-fit}
-
-The results obtained with equation \ref{eq:Br} are use in a non-linear least-squares fit with the equation \ref{eq:sf-functional} used as an objective function.
-For this purpose we use the \textit{python} package \textit{lmfit} \citep{newville_matthew_2014_11813} which implement a chi-square statistic defined as:
-%
-%\begin{equation}\label{eq:chi}
-%  \chi^2 = \sum_i ^N \frac{[y_i^{\text{measure}}-y_i^{\text{model}} (\boldsymbol{v})]^2}{\epsilon_i ^2}
-%\end{equation}
-%
-%
-\begin{equation}\label{eq:chi}
-  \chi^2 = \sum_i ^N \frac{[B(r)-B_{\text{func}}(r;r_0, \sigma^2\pos, m, s_0, B_{\text{noise}})]^2}{\varepsilon_i ^2}
-\end{equation}
-%
-where the turbulent parameters, \(r_{0}\)\, \(\sigma^2\pos\) and \(m\), and the observational constraints \(s_0\) and \( B_{\text{noise}}\), are the set of variables to be optimized in the fit.
-This procedure calculate a value \(\chi\) to be minimized scaled by the inverse of the uncertainty \(\varepsilon\) in the data using the Levenberg-Marquardt (LM) method.
-Then we proceed to obtain the confidence intervals using the minimization procedure \textit{emcee} \citep{2013PASP..125..306F} which is a implementation of the affine-invariant ensemble sampler for Markov chain Monte Carlo (MCMC) by \citet{2010CAMCS...5...65G}.
-
 \section{Structure function fits}
@@
     Second-order structure functions
-    for the velocity centroid images
+    for velocity centroid images
     of the \ha{} emission line
     from Galactic \hii{} regions.
+    Blue symbols show the observed mean structure function
+    in each radial bin.
   }
@@
 \end{figure*}
+
+\begin{table}
+  \centering
+  \caption{Bounds of allowed values for parameters in model fits}
+  \label{tab:parameter-ranges}
+  \newlength\partabwidth
+  \setlength\partabwidth{0.7\linewidth}
+  \begin{tabular*}{\partabwidth}{@{\extracolsep{\fill}}l rr}
+    \toprule
+    Parameter & Lower & Upper\\
+    \midrule
+    \(\sigma^2\) & \(0.25\, \max [B]\)& \(2\, \max [B]\)\\
+    \(r_0\) & \(0.1\, L\) & \(2\, L\)\\
+    \(m\) & \(0.5\) & \(2.0\) \\
+    \(s_0\) & \SI{0.1}{arcsec}& \SI{1.5}{arcsec}\\
+    \(B\noise\) & \(0\) & \(3\, \min [B]\) \\
+    \bottomrule
+    \multicolumn{3}{@{}p{\partabwidth}@{}}{
+    Note: \(\max[B]\) and \(\min[B]\) are over all bins in the observed structure function.
+    }
+  \end{tabular*}
+\end{table}
+
 \begin{figure}
@@
 In order to provide a uniform description of the velocity fluctuations,
-we fit the model structure function described above (equation~\eqref{eq:sf-functional})
-to each of the \hii{} regions in our sample.
+we fit the model structure function
+\(\tilde{B}(r)\) of equation~\eqref{eq:sf-functional}
+to each \hii{} region in our sample.
 Results are shown in Figures~\ref{fig:strucfunc-fit-Galactic}, \ref{fig:strucfunc-fit-MC},
@@
 
-In this section we present and describe the second-order structure results.
-The structure functions are plotted against separation in parsecs and we also show the posteriors of the parameters discussed in the previous section.
+For the observational values (blue symbols),
+the structure function is the average value of equation~\eqref{eq:Br}
+over all pairs of points that contribute to each radial bin.
+The uncertainty of each bin (blue error bars) is estimated
+as the standard deviation of these values divided by the square root of
+the number of contributing pairs.
+For most sources a fixed bin size of \SI{0.05}{dex} is used,
+but for those observed with multi-fiber spectroscopy
+(Carina and M8, see section~\ref{sec:flames-multi-fiber}),
+where coverage is sparse at small separations,
+adjacent bins were merged to ensure at least 100 pairs contribute to each bin.
+Bins with separation less than \(L/2\) are used to constrain the model fitting (filled symbols),
+while larger separations (open symbols) are not used
+since they are more likely to be affected by a breakdown
+of the homogeneity assumption (see section~\ref{sec:limit-model-struct}).
+
+Non-linear weighted least square fitting of the model is performed
+using the Levenberg-Marquardt algorithm \citep{More:1978a} as implemented in the
+\texttt{lmfit} Python library \citep{newville_matthew_2014_11813}.
+The best-fit model \(\tilde{B}(r)\) is shown (heavy orange solid line),
+together with the corresponding underlying ``true model'' \(B(r)\) (heavy dashed green line),
+which does not include the effects of seeing or noise.
+Note that the true model \(B(r)\) depends on only 3 parameters:
+\(\sigma^2\), \(r_0\), and \(m\),
+whereas \(\tilde{B}(r)\) additionally depends on
+the observational nuisance parameters: \(s_0\) and \(B\noise\).
+The best-fit values of each of these parameters are shown by
+horizontal and vertical lines.
+
+The posterior distributions of model parameters
+that are consistent with the observations for each region are estimated
+using Markov Chain Monte Carlo (MCMC) ensemble sampling \citep{2010CAMCS...5...65G}
+as implemented in the \texttt{emcee} Python library \citep{2013PASP..125..306F}.
+A uniform prior distribution is assumed between upper and lower bounds
+for each parameter, as given in Table~\ref{tab:parameter-ranges}.
+To help ensure convergence of the MCMC algorithm,
+we used chain lengths that exceeded \num{50} times the
+estimated autocorrelation length for each parameter,
+which required \num{50000} to \num{150000} samples,
+depending on the source.
+Thin translucent lines in the figures show structure functions using the parameters of
+a random selection of \num{100} posterior samples from the MCMC chain,
+both for \(\tilde{B}(r)\) orange and \(B(r)\) (green).
+This gives an estimate in the uncertainty about the best-fit model.
+Credibility intervals for the parameters are estimated from percentiles
+of the posterior distribution and are indicated in the figures by shaded gray boxes
+around the best-fit parameter values
+(heavy shading for 68\% interval; light shading for 95\% interval).
 
@@
 The vertical dashed line indicates the correlation length, \(r_0\), and the horizontal dashed line indicates the true variance of the velocity fields, \(\sigma^2\).
-The vertical and horizontal dotted lines shows the value of the observational considerations: the rms seeing, \(s_0\) and the noise, \(B_{\text{noise}}\).
+The vertical and horizontal dotted lines shows the value of the observational considerations: the rms seeing, \(s_0\) and the noise, \(B\noise\).
 These values were obtained using the LM method.
@@
 The second column correspond to the variance \(\sigma^2\pos\) of the velocity field.
-The \(B_{\text{noise}}\) value is shown in the third column which would be the minimum squared velocity difference that could be measure by the instrument.
+The \(B\noise\) value is shown in the third column which would be the minimum squared velocity difference that could be measure by the instrument.
 The fourth column in Table \ref{tab:Res} shows the rms seeing value in parsecs, \(s_0\), which represent the minimum value of the separation which would valid for the observed structure function. 

### 2022-04-18 strucfunc_paper.tex
Small advance on the model fit section

@@
 and \ref{fig:strucfunc-fit-ExtraGal}, arranged in order of increasing distance.
+Best-fit values for the model parameters,
+together with 95\% credibility range,
+are given in Table~\ref{tab:Res}.
+
+\subsection{Technical details of the model fits}
+\label{sec:techn-deta-model}
 
@@
 the number of contributing pairs.
+\textit{But this is not true -- we use constant fractional error with adjustments for small and large separations.}
 For most sources a fixed bin size of \SI{0.05}{dex} is used,
@@
 The best-fit values of each of these parameters are shown by
-horizontal and vertical lines.
+horizontal and vertical lines in the figure and are summarised in Table~\ref{tab:Res}.
 
@@
 (heavy shading for 68\% interval; light shading for 95\% interval).
+The 95\% credibility interval for each parameter and for each source
+is also given in Table~\ref{tab:Res}.
+Figure~\ref{fig:corner-example-Orion} gives an example for Orion of
+the pairwise correlations in the posterior distributions of the model parameters,
+plotted using the \texttt{corner} Python library \citep{2017ascl.soft02002F}.
+Corresponding plots for the remaining sources are given in Appendix~\ref{sec:addit-covar-corn}.
+
+\subsection{Results of model fitting}
+\label{sec:results-model-fitt}
 

### 2022-04-18 strucfunc_paper.tex
Half way through description of Orion results
Still need to finish description of covariances, and then of non
homogeneous large-scale behavior

@@
     Appendix~\ref{sec:addit-covar-corn}.
+    Plots on the diagonal show the 1-dimensional histogram
+    of the posterior distribution of each parameter
+    (labeled at bottom),
+    as calculated by the MCMC method,
+    assuming a uniform prior distribution
+    within the limits given in Table~\ref{tab:parameter-ranges}.
+    Off-diagonal plots show the 2-dimensional histogram of the
+    joint posterior distribution each pair of parameters.
   }
@@
 are given in Table~\ref{tab:Res}.
-
-\subsection{Technical details of the model fits}
+After describing the methods used to
+measure the structure function and fit the model (section~\ref{sec:techn-deta-model}),
+we give details of the results in the example case of
+the inner Orion Nebula (\ref{sec:example-results-orion})
+and a broad overview of the results for other regions (\ref{sec:results-model-fitt}).
+Further details of the results for individual regions are
+given in Appendix~\ref{sec:notes-individual-hii}.
+
+\subsection{Technical details of structure function measurement and fitting}
 \label{sec:techn-deta-model}
@@
 
-\subsection{Results of model fitting}
+\subsection{Example results of model fitting to the Orion Nebula}
+\label{sec:example-results-orion}
+
+This dataset is among the highest quality of those in our sample,
+with more than \num{e5} spatial points and a factor of more than \num{500}
+between the smallest and largest separations.
+As a result, the observationally derived structure function (Figure~\ref{fig:strucfunc-fit-Galactic}a)
+is very smooth and the model fit is very well constrained,
+as evidenced by the tight credibility limits on the model parameters.
+The derived correlation length \(r_0 = \SI{0.068}{pc}\) is \num{7} times smaller
+than the box size, which indicates that there should be a moderate finite map effect
+(section \ref{sec:effects-observ-limit-large} and Appendix~\ref{sec:finite-box-effects}),
+but it is well within the range where the model fit can give reliable measurements
+(see Figure~\ref{fig:finite-box-effect}).
+The derived seeing parameter \(s_0 = \SI{0.002}{pc}\) is more than \num{30} times smaller
+than \(r_0\), meaning that the seeing has a negligible effect at the correlation scale and above.
+
+Figure~\ref{fig:corner-example-Orion} shows the covariances
+between parameters in the model fit.
+
+\subsection{Results of model fitting to other sources}
 \label{sec:results-model-fitt}
@@
 The average ages for the stars, was determined to be from  \num{3} to \SI{5}{Myr} \citep{1996ApJ...456..174H} and with the RSGs as an older population have an age of 12.4\(\pm\)2.1 Myr \citep{2011MNRAS.411..235E}.
+
 This suggest that two episodes of star formation, at least, have taken place in the GEHR.

### 2022-05-06 strucfunc_paper.tex
Unfinished changes
Minor changes to strucfunc descriptions

@@
 
-\subsection{Example results of model fitting to the Orion Nebula}
+\subsection{Example results of model fitting to the inner Orion Nebula}
 \label{sec:example-results-orion}
@@
 than \(r_0\), meaning that the seeing has a negligible effect at the correlation scale and above.
-
-Figure~\ref{fig:corner-example-Orion} shows the covariances
-between parameters in the model fit.
+Figure~\ref{fig:corner-example-Orion}  shows  the covariances  between
+parameters  in the  model fit,
+which in some cases show significant correlations.
+For example, \(\sigma^2\) and \(r_0\) are positively correlated,
+whereas \(m\) and \(s_0\) are negatively correlated.
 
@@
 \label{sec:results-model-fitt}
+
+The structure functions for the remaining Galactic sources
+are shown in Figure~\ref{fig:strucfunc-fit-Galactic}b--d.
+The data quality for these sources is considerably worse than for the inner Orion Nebula.
+
+while those in the Magellanic Clouds are shown in Figure~\ref{fig:strucfunc-fit-MC}
+and those in more distant galaxies in Figure~\ref{fig:strucfunc-fit-ExtraGal}.
 

### 2022-05-12 strucfunc_paper.tex
Javier changes 2022-05-10

@@
   \centering
-  \sffigggg{OrionS}{M8}{OrionLH}{CarC}
+  \sffigggg{OrionS}{OrionLH}{M8}{CarC}
   \caption{
@@
     \(\sigma^2\) & \(0.25\, \max [B]\)& \(2\, \max [B]\)\\
-    \(r_0\) & \(0.1\, L\) & \(2\, L\)\\
+    \(r_0\) & \(0.01\, L\) & \(2\, L\)\\
     \(m\) & \(0.5\) & \(2.0\) \\
@@
 
-\input{SFresults}
+\input{table-results}
 
@@
 of the homogeneity assumption (see section~\ref{sec:limit-model-struct}).
+This \(L/2\) constrain is not used for the regions observed with MUSE.
 
@@
 estimated autocorrelation length for each parameter,
-which required \num{50000} to \num{150000} samples,
-depending on the source.
+which required \num{50000} samples.
 Thin translucent lines in the figures show structure functions using the parameters of
@@
 plotted using the \texttt{corner} Python library \citep{2017ascl.soft02002F}.
-Corresponding plots for the remaining sources are given in Appendix~\ref{sec:addit-covar-corn}.
+Corresponding plots for the remaining sources and a table for the fitting parameters are given in Appendix~\ref{sec:addit-covar-corn}.
 
@@
 
+Particularly the EON observations, which are the oldest, the fitting procedure gives a noise value of \SI{5.6}{km^{2}.s^{-2}} larger that the \(\sigma^2\pos\) value of \SI{3}{km^{2}.s^{-2}}.
+The derived correlation length \(r_0 = \SI{0.05}{pc}\) is \num{6} times smaller
+than the box size, which is the minimum value for this ratio of our sample. 
+Hence we can confirm that the finite map has no effect in our results.
+The derived seeing parameter \(s_0 = \SI{0.002}{pc}\), consistent with the Orion core fit, is more than \num{250} times smaller than \(r_0\).
+This large ratio is because the separation of the pixels for the EON observations are at separations above the observational seeing, so these parameter has virtually no effect in our model for the EON case.
+The previous statement can be confirmed with the Fig. \ref{fig:corner-Galactic}b which shows the corner plot for the EON.
+The RMS seeing posterior is flat, meaning that the values in that range doesn't modify the fit.
+
+This behavior is also seen in the Carina nebula and Lagoon nebula.
+The observations for this regions are from the FLAMES multi-fiber instrument (section \ref{sec:flames-multi-fiber} ) in which the fibers separation  (see Figure \ref{fig:velocity-maps}) is above the observational seeing for the regions.
+
 while those in the Magellanic Clouds are shown in Figure~\ref{fig:strucfunc-fit-MC}
@@
 %structure functions plots descriptions
-Figures \ref{fig:strucfunc-fit-OrionS}-\ref{fig:strucfunc-fit-OrionLH} left panels show in solid and open blue circles the observational structure function that we compute using equation \ref{eq:Br} on the \ha{} velocity fields of Fig.
+%Figures \ref{fig:strucfunc-fit-OrionS}-\ref{fig:strucfunc-fit-OrionLH} left panels show in solid and open blue circles the observational structure function that we compute using equation \ref{eq:Br} on the \ha{} velocity fields of Fig.
 \ref{fig:velocity-maps}.
-In the plots the solid circles indicate the points we use in the non-linear regression analysis (see section~\ref{sec:model-fit}), while the open circles are the points of the structure function that where left out.
-The criteria for the previous considerations is that the structure function at large separations is affected by the inhomogeneties of the velocity field (see section-\ref{sec:limit-model-struct}).
-The points left our correspond to the largest separations that are not consider in our model. 
-In some cases, at the smallest separations we merge a couple of the structure functions points under the assumption that those would be heavily affected by the seeing.
-The Figures shows in the orange solid thick line the best fit for the equation \ref{eq:sf-functional} which takes into account observational limitations on the structure function.
-The green dashed line indicate the theoretical model for the structure function using equation \ref{eq:functional}.
-
-Figures \ref{fig:strucfunc-fit-OrionS}-\ref{fig:strucfunc-fit-OrionLH} left panels show in dashed and dotted lines the parameters of our model.
-The vertical dashed line indicates the correlation length, \(r_0\), and the horizontal dashed line indicates the true variance of the velocity fields, \(\sigma^2\).
-The vertical and horizontal dotted lines shows the value of the observational considerations: the rms seeing, \(s_0\) and the noise, \(B\noise\).
-These values were obtained using the LM method.
-For the dashed and dotted lines the overlapping translucent boxes indicate the confidence intervals in 1-sigma (dark shaded area) and 2-sigma (light shaded area) obtained from the MCMC analysis.
-The light shaded areas in the plot show where the separation \(r\) is above half of the box size, \(L\), which is indicated with a vertical dotted line.
-
-For Carina and Lagoon nebula, the velocity fields are obtained from the FLAMES multi-fiber instrument (section~\ref{sec:flames-multi-fiber}). 
-We can see from Figure~\ref{fig:velocity-maps} that observations from this instrument do not give uniform maps as the others. 
-Instead, the discrete fiber positions are diversely located across the FOV.
-This would affect the structure function since the values are not adjacent as the other observations.
-This is reflected in the non uniform \(B(r)\) below  \(r_0\) that we pointed out in the previous paragraphs.
+%In the plots the solid circles indicate the points we use in the non-linear regression analysis (see section~\ref{sec:model-fit}), while the open circles are the points of the structure function that where left out.
+%The criteria for the previous considerations is that the structure function at large separations is affected by the inhomogeneties of the velocity field (see section-\ref{sec:limit-model-struct}).
+%The points left our correspond to the largest separations that are not consider in our model. 
+%In some cases, at the smallest separations we merge a couple of the structure functions points under the assumption that those would be heavily affected by the seeing.
+%The Figures shows in the orange solid thick line the best fit for the equation \ref{eq:sf-functional} which takes into account observational limitations on the structure function.
+%The green dashed line indicate the theoretical model for the structure function using equation \ref{eq:functional}.
+
+%Figures \ref{fig:strucfunc-fit-OrionS}-\ref{fig:strucfunc-fit-OrionLH} left panels show in dashed and dotted lines the parameters of our model.
+%The vertical dashed line indicates the correlation length, \(r_0\), and the horizontal dashed line indicates the true variance of the velocity fields, \(\sigma^2\).
+%The vertical and horizontal dotted lines shows the value of the observational considerations: the rms seeing, \(s_0\) and the noise, \(B\noise\).
+%These values were obtained using the LM method.
+%For the dashed and dotted lines the overlapping translucent boxes indicate the confidence intervals in 1-sigma (dark shaded area) and 2-sigma (light shaded area) obtained from the MCMC analysis.
+%The light shaded areas in the plot show where the separation \(r\) is above half of the box size, \(L\), which is indicated with a vertical dotted line.
+
+%For Carina and Lagoon nebula, the velocity fields are obtained from the FLAMES multi-fiber instrument (section~\ref{sec:flames-multi-fiber}). 
+%We can see from Figure~\ref{fig:velocity-maps} that observations from this instrument do not give uniform maps as the others. 
+%Instead, the discrete fiber positions are diversely located across the FOV.
+%This would affect the structure function since the values are not adjacent as the other observations.
+%This is reflected in the non uniform \(B(r)\) below  \(r_0\) that we pointed out in the previous paragraphs.
 
 %corner plots descriptions
-Figures \ref{fig:corner-example-Orion} show the corner plots \citep{2017ascl.soft02002F} of the turbulent parameters and observational constraints
-(further examples in Appendix~\ref{sec:addit-covar-corn}).
-These plots shows the one and two dimensional projections of the posterior probability distributions of the parameters used in equation \ref{eq:chi}.
-They also show the distribution for each parameter independently in the histograms along the diagonal and then the marginalized two dimensional distributions in the other panels making possible to visualize all of the covariances between parameters \citep{2017ascl.soft02002F}.
-The contours in the plots reflect the 95\(\%\), 99\(\%\), 99.5\(\%\) and 99.9\(\%\) confidence intervals.
-A number of fits for the equations \ref{eq:sf-functional} and \ref{eq:functional} using samples of the posteriors are shown in thin translucent orange and green lines, respectively, showing the possible range of the confidence intervals.
-
-Table \ref{tab:Res} presents the turbulent parameters and observational constraints values mentioned in the paragraphs above.
-The confidence intervals for these values are up to 2-sigma of the posteriors.
-The second column correspond to the variance \(\sigma^2\pos\) of the velocity field.
-The \(B\noise\) value is shown in the third column which would be the minimum squared velocity difference that could be measure by the instrument.
-The fourth column in Table \ref{tab:Res} shows the rms seeing value in parsecs, \(s_0\), which represent the minimum value of the separation which would valid for the observed structure function. 
-The fifth column shows the correlation value \(r_0\) in parsecs.
-The \(r_0\) range covered in our results for the sample goes from 0.09 to 12 pc.
-The sixth column indicates the size of each observational box in parsecs.
-The index \(m\) is shown in the seventh column.
-The range covered by the power-law index goes from 0.7 to 1.5.
-The eighth column show the ratio \(L / r_0\)
-The last column shows the FWHM seeing in arcsec.
+%Figures \ref{fig:corner-example-Orion} show the corner plots \citep{2017ascl.soft02002F} of the turbulent parameters and observational constraints
+%(further examples in Appendix~\ref{sec:addit-covar-corn}).
+%These plots shows the one and two dimensional projections of the posterior probability distributions of the parameters used in equation \ref{eq:chi}.
+%They also show the distribution for each parameter independently in the histograms along the diagonal and then the marginalized two dimensional distributions in the other panels making possible to visualize all of the covariances between parameters \citep{2017ascl.soft02002F}.
+%The contours in the plots reflect the 95\(\%\), 99\(\%\), 99.5\(\%\) and 99.9\(\%\) confidence intervals.
+%A number of fits for the equations \ref{eq:sf-functional} and \ref{eq:functional} using samples of the posteriors are shown in thin translucent orange and green lines, respectively, showing the possible range of the confidence intervals.
+
+%Table \ref{tab:Res} presents the turbulent parameters and observational constraints values mentioned in the paragraphs above.
+%The confidence intervals for these values are up to 2-sigma of the posteriors.
+%The second column correspond to the variance \(\sigma^2\pos\) of the velocity field.
+%The \(B\noise\) value is shown in the third column which would be the minimum squared velocity difference that could be measure by the instrument.
+%The fourth column in Table \ref{tab:Res} shows the rms seeing value in parsecs, \(s_0\), which represent the minimum value of the separation which would valid for the observed structure function. 
+%The fifth column shows the correlation value \(r_0\) in parsecs.
+%The \(r_0\) range covered in our results for the sample goes from 0.09 to 12 pc.
+%The sixth column indicates the size of each observational box in parsecs.
+%The index \(m\) is shown in the seventh column.
+%The range covered by the power-law index goes from 0.7 to 1.5.
+%The eighth column show the ratio \(L / r_0\)
+%The last column shows the FWHM seeing in arcsec.
 %The interpretation of our results is developed in the next section.
@@
 (supplementing section~\ref{sec:regions-milky-way})
-together with additional details of the model fit to the structure function
+together with additional details of the structure function
 (supplementing section~\ref{sec:results}).
+
+%the model fit to
 
@@
 Figure~\ref{fig:strucfunc-fit-Galactic}a shows the structure function of the Orion core.
-Valid scales are consider above the separation of \SI{0.002}{pc} (\(s_0\)=\SI{1}{\arcsecond}).
 In this case we merge the first three points of the structure function.
-From \SI{0.002}{pc} until \SI{0.003}{pc} all points fall below the true model showing that they are affected by the seeing. 
-The correlation length for the Orion core is \SI{0.07}{pc}, it has a \(\sigma^2\pos\) of \SI{12}{km^{2}.s^{-2}} and an index of \num{1.07}.
+%From \SI{0.002}{pc} until \SI{0.003}{pc} all points fall below the true model showing that they are affected by the seeing. 
+%The correlation length for the Orion core is \SI{0.07}{pc}, it has a \(\sigma^2\pos\) of \SI{12}{km^{2}.s^{-2}} and an index of \num{1.07}.
 The structure function of the Orion core behaves accordingly to the tapered case of inhomogeneous fluctuations (see Figure~\ref{fig:model-strucfunc}b).
@@
 Above separations of \SI{0.3}{pc} the structure function decays to a value of \SI{7}{km^{2}.s^{-2}} at  \SI{0.5}{pc}.
-
-The EON structure function is shown in Figure~\ref{fig:strucfunc-fit-Galactic}c.
-This observations are heavily affected by the noise which presents a value of \SI{6}{km^{2}.s^{-2}} which is larger that the \(\sigma^2\pos\) value of \SI{4}{km^{2}.s^{-2}}.
 
@@
 The Figure~\ref{fig:strucfunc-fit-Galactic}c shows the structure function of the Lagoon nebula.
-There aren't any points affected by the seeing which has a value of \SI{0.006}{pc} (\(s_0\)=\SI{1}{\arcsecond}).
+%There aren't any points affected by the seeing which has a value of \SI{0.006}{pc} (\(s_0\)=\SI{1}{\arcsecond}).
 In this case we merge the first two points.
 The Lagoon nebula presents a non-uniform behavior below the correlation length but it is possible to see the characteristic ascending values of the structure function.
-The turbulent parameters that fits our model are a \(r_0\) of \SI{1}{pc}, a \(\sigma^2\pos\) of \SI{7}{km^{2}.s^{-2}} and an index of \num{1.17}.
+%The turbulent parameters that fits our model are a \(r_0\) of \SI{1}{pc}, a \(\sigma^2\pos\) of \SI{7}{km^{2}.s^{-2}} and an index of \num{1.17}.
 At large scales there is an indication of some periodic behavior followed by ascending \(B(r)\) values at largest separation.
@@
 (The Figure~\ref{fig:strucfunc-fit-Galactic}d shows the structure function of the Carina nebula.
-The seeing is \SI{0.008}{pc} (\(s_0\)=\SI{1.3}{\arcsecond}) and there are just a couple of points that lie below the true model, indicating that the majority of points isn't affected by the seeing.
+%The seeing is \SI{0.008}{pc} (\(s_0\)=\SI{1.3}{\arcsecond}) and there are just a couple of points that lie below the true model, indicating that the majority of points isn't affected by the seeing.
 For this region we merge the first two points of the structure function.
 As the Lagoon nebula, Carina also shows a non-uniform behavior below the correlation length.
-The correlation length is \SI{0.56}{pc} pc at a \(\sigma^2\pos\) of \SI{18}{km^{2}.s^{-2}} and an index of \num{1.14}.
+%The correlation length is \SI{0.56}{pc} pc at a \(\sigma^2\pos\) of \SI{18}{km^{2}.s^{-2}} and an index of \num{1.14}.
 At larges scales the structure function of the Carina nebula follows a pattern that resembles the homogeneous fluctuation of Figure~\ref{fig:model-strucfunc}a.
@@
 In this case we merge the first five points of the structure function.
-The seeing value for this regions is \SI{0.16}{pc} (\(s_0\)=\SI{0.7}{\arcsecond}) and just one point of the structure function is below this value.
-Until a separation of \SI{1.7}{pc} is reached, the structure function lies below the true model.
-The correlation length is \SI{4}{pc} at a \(\sigma^2\pos\) of \SI{297 \pm 9}{km^{2}.s^{-2}} and an index of \num{0.85}.
+%The seeing value for this regions is \SI{0.16}{pc} (\(s_0\)=\SI{0.7}{\arcsecond}) and just one %point of the structure function is below this value.
+%Until a separation of \SI{1.7}{pc} is reached, the structure function lies below the true model.
+%The correlation length is \SI{4}{pc} at a \(\sigma^2\pos\) of \SI{297 \pm 9}{km^{2}.s^{-2}} and an index of \num{0.85}.
 At large separations 30 Doradus structure function presents a behavior of tapered fluctuations. The maximum \(B(r)\) value is \SI{655}{km^{2}.s^{-2}} at a separation of \SI{21}{pc}. 
@@
 The Figure~\ref{fig:strucfunc-fit-MC}b shows the structure function of NGC 346.
-In this case we merge the first three points of the structure function.
-The seeing value is \SI{0.07}{pc} (\(s_0\)=\SI{0.23}{\arcsecond}).
+%In this case we merge the first three points of the structure function.
+%The seeing value is \SI{0.07}{pc} (\(s_0\)=\SI{0.23}{\arcsecond}).
 For this region the first ten points lie below the true model.
 At separations above \SI{0.4}{pc} the observed structure functions is coincident with the true model. 
-The correlation length is \SI{2}{pc} at a \(\sigma^2\pos\) of \SI{35}{km^{2}.s^{-2}} and an index of \num{0.80}.
+%The correlation length is \SI{2}{pc} at a \(\sigma^2\pos\) of \SI{35}{km^{2}.s^{-2}} and an index of \num{0.80}.
 For scales above \SI{12}{pc} and a \(B(r)\) value of \SI{65}{km^{2}.s^{-2}} the structure function shows a pattern of ascending values until it reaches \SI{146}{km^{2}.s^{-2}} at \SI{24}{pc}.
@@
 \label{sec:6822-hubble}
-%Note to me: incomplete section. Find more regions info and finish asap.
+%
 The irregular dwarf galaxy, NGC 6822, is located at a distance of 500 kpc \citetext{\SI{1}{\arcsecond} = \SI{2.42}{pc} ; \citealp{2012A&A...540A.135S}} and the brightest HII regions are Hubble X and Hubble V (HX and HV hereafter).
@@
 For the observations coming from the TAURUS-II instrument there wasn't any merging of points at small scales.
-The value of the seeing for this regions is \SI{0.5}{pc} (\(s_0\)=\SI{0.2}{\arcsecond}).
-All the structure function points lies below the true model.
-The correlation length is \SI{3.5}{pc} at a \(\sigma^2\pos\) of  \SI{10}{km^{2}.s^{-2}} and an index of \num{0.75}.
+%The value of the seeing for this regions is \SI{0.5}{pc} (\(s_0\)=\SI{0.2}{\arcsecond}).
+%All the structure function points lies below the true model.
+%The correlation length is \SI{3.5}{pc} at a \(\sigma^2\pos\) of  \SI{10}{km^{2}.s^{-2}} and an index of \num{0.75}.
 The maximum \(B(r)\) value is \SI{18}{km^{2}.s^{-2}} at a separation of \SI{25}{pc}. 
@@
 The Hubble X structure function is shown in Figure~\ref{fig:strucfunc-fit-ExtraGal}b.
-The seeing is \SI{0.6}{pc} (\(s_0\)=\SI{0.24}{\arcsecond}) and as in Hubble V the observed structure function lies below the true model.
-The correlation length is \SI{4}{pc} at a \(\sigma^2\pos\) of \SI{15}{km^{2}.s^{-2}} and an index of \num{0.93}.
+%The seeing is \SI{0.6}{pc} (\(s_0\)=\SI{0.24}{\arcsecond}) and as in Hubble V the observed structure function lies below the true model.
+%The correlation length is \SI{4}{pc} at a \(\sigma^2\pos\) of \SI{15}{km^{2}.s^{-2}} and an index of \num{0.93}.
 A plateau is reached around \SI{25}{km^{2}.s^{-2}} at a separation of \SI{14}{pc} and a maximum \(B(r)\) value of \SI{31}{km^{2}.s^{-2}} at a separation of \SI{36}{pc}.
@@
 The average ages for the stars, was determined to be from  \num{3} to \SI{5}{Myr} \citep{1996ApJ...456..174H} and with the RSGs as an older population have an age of 12.4\(\pm\)2.1 Myr \citep{2011MNRAS.411..235E}.
-
 This suggest that two episodes of star formation, at least, have taken place in the GEHR.
@@
 In the Figure~\ref{fig:strucfunc-fit-ExtraGal}c we show the structure function of NGC 595.
-The seeing is \SI{0.3}{pc} (\(s_0\)=\SI{0.1}{\arcsecond}) and for this region only the first two points are below the true model. 
-The correlation length is \SI{12}{pc} at a \(\sigma^2\pos\) of \SI{54}{km^{2}.s^{-2}} and an index of \num{1.3}.
+%The seeing is \SI{0.3}{pc} (\(s_0\)=\SI{0.1}{\arcsecond}) and for this region only the first two points are below the true model. 
+%The correlation length is \SI{12}{pc} at a \(\sigma^2\pos\) of \SI{54}{km^{2}.s^{-2}} and an index of \num{1.3}.
 At large scales the structure function behaves following the tapered fluctuations pattern.
@@
 In the Figure~\ref{fig:strucfunc-fit-ExtraGal}d we show the structure function of NGC 604.
-The seeing is \SI{1.7}{pc} (\(s_0\)=\SI{0.42}{\arcsecond}) and the structure function of this region lies below the true model for most of the separation range.
-The correlation length is \SI{10}{pc} at a \(\sigma^2\pos\) of \SI{71}{km^{2}.s^{-2}} and has an index of \num{1}.
+%The seeing is \SI{1.7}{pc} (\(s_0\)=\SI{0.42}{\arcsecond}) and the structure function of this region lies below the true model for most of the separation range.
+%The correlation length is \SI{10}{pc} at a \(\sigma^2\pos\) of \SI{71}{km^{2}.s^{-2}} and has an index of \num{1}.
 The structure function present clear characteristics of periodic oscillations at large scales.
@@
   \centering
-  \sfcfigggg{OrionS}{M8}{OrionLH}{CarC}
+  \sfcfigggg{OrionS}{OrionLH}{M8}{CarC}
   \caption{
@@
 \end{figure*}
+
+\input{table-fit-parameters}
 

### 2022-05-12 table-fit-parameters.tex
Javier changes 2022-05-10

\begin{table*}
\begin{center}\caption{Fitting parameters.}
\begin{tabular}{cCCCCCCCC}\toprule
\hii{}    &  \text{No. merged} & \text{Relatively}  & \text{Weight / No. points}     &  \text{Weight / No. points}     & \text{Max.}  & \text{Reduced} & \text{Autocorrelation } & \text{Acceptance}\\
Region    &  \text{points} & \text{uncertainty} & \text{Small scales} &  \text{Large scales} & \text{separation}  & \text{chi-square} & \text{time} & \text{fraction}\\
\midrule
Orion     & - & 0.02    &  -           &   -        & 0.5  & 0.82 & 60  & 0.55\\
EON       & - & 0.025   &  2.0 / 3     &   -        & 0.5  & 0.70 & 527 & 0.45\\
Lagoon    & 2 & 0.08    &  2.5 / 16    &   2.5 / 8  & 0.5  & 0.94 & 70  & 0.49\\
Carina    & 2 & 0.055   &  3.0 / 14    &   3.0 / 4  & 0.5  & 0.94 & 72  & 0.50\\
30 Dor    & 5 &  0.07   &  -           &   -        & 0.9  & 0.98 & 82  & 0.54\\
NGC 346   & 3 & 0.04    &  -           &   -        & 0.8  & 0.83 & 76  & 0.51\\
Hubble V  & - & 0.04    &  2.0 / 3     &   -        & 0.5  & 0.77 & 140 & 0.45\\
Hubble X  & - & 0.032   &  2.0 / 4     &   2.0 / 6  & 0.5  & 0.73 & 83  & 0.49\\
NGC 595   & - &  0.055  &  4.5 / 3     &   3.0 / 5  & 0.5  & 0.83 & 63  & 0.51\\
NGC 604   & - &  0.095  &   2.5 / 3    &   1.25 / 2 & 0.5  & 0.71 & 124 & 0.44\\
\bottomrule
\end{tabular}\label{tab:fitting-parameters}
\end{center}
\end{table*}

### 2022-05-13 strucfunc_paper.tex
Javier changes 2022-05-13

@@
 
-Particularly the EON observations, which are the oldest, the fitting procedure gives a noise value of \SI{5.6}{km^{2}.s^{-2}} larger that the \(\sigma^2\pos\) value of \SI{3}{km^{2}.s^{-2}}.
-The derived correlation length \(r_0 = \SI{0.05}{pc}\) is \num{6} times smaller
+%Particularly the EON observations, which are the oldest, the fitting procedure gives a noise value of \SI{5.6}{km^{2}.s^{-2}} larger that the \(\sigma^2\pos\) value of \SI{3}{km^{2}.s^{-2}}.
+For the EON the derived correlation length \(r_0 = \SI{0.05}{pc}\) is \num{6} times smaller
 than the box size, which is the minimum value for this ratio of our sample. 

### 2022-05-13 strucfunc_paper.tex
Finish description of remaining structure functions

--- 2022-05-12 strucfunc_paper.tex
@@
 are shown in Figure~\ref{fig:strucfunc-fit-Galactic}b--d.
-The data quality for these sources is considerably worse than for the inner Orion Nebula.
-
-Particularly the EON observations, which are the oldest, the fitting procedure gives a noise value of \SI{5.6}{km^{2}.s^{-2}} larger that the \(\sigma^2\pos\) value of \SI{3}{km^{2}.s^{-2}}.
-The derived correlation length \(r_0 = \SI{0.05}{pc}\) is \num{6} times smaller
-than the box size, which is the minimum value for this ratio of our sample. 
-Hence we can confirm that the finite map has no effect in our results.
-The derived seeing parameter \(s_0 = \SI{0.002}{pc}\), consistent with the Orion core fit, is more than \num{250} times smaller than \(r_0\).
-This large ratio is because the separation of the pixels for the EON observations are at separations above the observational seeing, so these parameter has virtually no effect in our model for the EON case.
-The previous statement can be confirmed with the Fig. \ref{fig:corner-Galactic}b which shows the corner plot for the EON.
-The RMS seeing posterior is flat, meaning that the values in that range doesn't modify the fit.
-
-This behavior is also seen in the Carina nebula and Lagoon nebula.
-The observations for this regions are from the FLAMES multi-fiber instrument (section \ref{sec:flames-multi-fiber} ) in which the fibers separation  (see Figure \ref{fig:velocity-maps}) is above the observational seeing for the regions.
-
-while those in the Magellanic Clouds are shown in Figure~\ref{fig:strucfunc-fit-MC}
+The data quality for these sources is not so high as for the inner Orion Nebula,
+with the result that the model parameters are not so well constrained.
+In particular, the relatively coarse spacing between nearest-neighbor spatial points
+(see sections~\ref{sec:fabry-perot-etalaon} and \ref{sec:flames-multi-fiber})
+means that the seeing has no effect on the observed structure function,
+so that \(s_0\) is indeterminate in the model fits
+(note the flat posterior histograms for \(s_0\) in Fig.~\ref{fig:corner-Galactic}bcd).
+In addition, the effects of noise are also much greater,
+as is apparent from visual inspection of the velocity fields
+(top row of Figure~\ref{fig:velocity-maps}).
+The principal effect of this on the model fits is to increase the uncertainty
+in the power law slope \(m\).
+The most extreme case is the Extended Orion Nebula (Fig.~\ref{fig:strucfunc-fit-Galactic}b--d),
+where noise dominates the structure function at all scales.
+
+% Particularly the EON observations, which are the oldest, the fitting procedure gives a noise value of \SI{5.6}{km^{2}.s^{-2}} larger that the \(\sigma^2\pos\) value of \SI{3}{km^{2}.s^{-2}}.
+% The derived correlation length \(r_0 = \SI{0.05}{pc}\) is \num{6} times smaller
+% than the box size, which is the minimum value for this ratio of our sample. 
+% Hence we can confirm that the finite map has no effect in our results.
+% The derived seeing parameter \(s_0 = \SI{0.002}{pc}\), consistent with the Orion core fit, is more than \num{250} times smaller than \(r_0\).
+% This large ratio is because the separation of the pixels for the EON observations are at separations above the observational seeing, so these parameter has virtually no effect in our model for the EON case.
+% The previous statement can be confirmed with the Fig. \ref{fig:corner-Galactic}b which shows the corner plot for the EON.
+% The RMS seeing posterior is flat, meaning that the values in that range doesn't modify the fit.
+
+% This behavior is also seen in the Carina nebula and Lagoon nebula.
+% The observations for this regions are from the FLAMES multi-fiber instrument (section \ref{sec:flames-multi-fiber} ) in which the fibers separation  (see Figure \ref{fig:velocity-maps}) is above the observational seeing for the regions.
+
+The structure functions for sources in the Magellanic Clouds are shown in Figure~\ref{fig:strucfunc-fit-MC}
 and those in more distant galaxies in Figure~\ref{fig:strucfunc-fit-ExtraGal}.
+The Magellanic cloud sources have generally high data quality due to the
+large number of independent spatial points in the MUSE observations
+(section~\ref{sec:muse-integral-field}).
+The relatively poor spectral resolution means that the \(B(r)\) cannot
+be measured down to such low values as in the inner Orion Nebula,
+but the larger amplitude of the fluctuations in these sources means
+that the fitted model parameters are still tightly constrained.
+
+For the more distant sources, the principal observational limitation is the seeing.
+The derived values of \(s_0\) exceed 10\% of the correlation length,
+leading to large uncertainties in the determination of the power law slope \(m\).
+On the other hand, the values of \(r_0\) and \(\sigma^2\) are still well-constrained.
+
+\subsection{Sanity check on derived values of nuisance parameters}
+\label{sec:sanity-check-derived}
+
+\subsection{Evidence for inhomogeneity at the largest scales}
+\label{sec:evid-inhom-at}
 

### 2022-05-16 table-fit-parameters.tex
Javier changes 2022-05-13

@@
 NGC 346   & 3 & 0.04    &  -           &   -        & 0.8  & 0.83 & 76  & 0.51\\
-Hubble V  & - & 0.04    &  2.0 / 3     &   -        & 0.5  & 0.77 & 140 & 0.45\\
+Hubble V  & - & 0.05    &  2.0 / 3     &   -        & 0.6  & 0.86 & 440 & 0.44\\
 Hubble X  & - & 0.032   &  2.0 / 4     &   2.0 / 6  & 0.5  & 0.73 & 83  & 0.49\\

### 2022-05-16 strucfunc_paper.tex
Write something on large scale inhomogeneity

@@
 
+At scales larger than \(L/2\),
+we see a variety of different shapes for the structure functions
+of our sample regions. 
+In some cases,
+such as Carina and Hubble~X,
+\(B(r)\) remains flat at a value of \(\approx 2\sigma^2\),
+which is consistent with uncorrelated homogeneous fluctuations
+at the largest scales.
+For other regions,
+such as the Orion Nebula (both inner and outer) and 30~Doradus,
+there is a clear downturn in \(B(r)\) at the largest separations.
+As discussed above in section~\ref{sec:limit-model-struct},
+this is what would be expected if the velocity fluctuations
+were inhomogeneous, with a larger amplitude in the center of the map
+and a smaller amplitude in the outskirts.
+A similar behavior, although not so marked, is shown by
+Hubble~V and NGC~595.
+The Orion Nebula is a particularly interesting case
+since the \(\sigma^2\) derived from the high-resolution dataset of the inner nebula on scales \(\approx \SI{0.1}{pc}\)
+is roughly twice as large as that derived from the lower resolution
+dataset of the Extended Orion Nebula on scales \(\approx \SI{1}{pc}\)
+(compare panels a and b of Figure~\ref{fig:strucfunc-fit-Galactic}).
+
 %structure functions plots descriptions

### 2022-05-17 strucfunc_paper.tex
Start section on nuisance parameters

@@
 
-\subsection{Sanity check on derived values of nuisance parameters}
+\subsection{On the reasonableness of the derived seeing widths and noise}
 \label{sec:sanity-check-derived}
+In the model fitting we allow the nuisance observational parameters
+\(s_0\) and \(B\noise\) to vary freely within a wide range
+(Table~\ref{tab:parameter-ranges}).
+This is necessary because of the heterogeneous nature of our source datasets
+and the fact that the details of the observational conditions
+are not available to us in all cases.
+However, it is worthwhile to do perform a sanity check on the values that are implied by our model fits.
+To that end, the last column in Table~\ref{tab:Res} gives the FWHM seeing width in arcsec.
 
@@
 at the largest scales.
+
 For other regions,
@@
 (compare panels a and b of Figure~\ref{fig:strucfunc-fit-Galactic}).
+This is further evidence that the amplitude of velocity fluctuations
+increases towards the center of the nebula in this source.
+
+In contrast, other regions,
+such as the Lagoon and NGC~346,
+show \(B(r)\) increasing at the largest separations,
+reaching values significantly larger than \(2\sigma^2\).
+This can be evidence for a large-scale linear velocity gradient
+across the region (see Figure~13 of \citealp{arthur2016turbulence})
+or a periodic fluctuation with \(\lambda > r_0\)
+(see section~\ref{sec:limit-model-struct} above).
+This latter effect may also explain the behavior of NGC~604,
+which shows oscillatory behavior of \(B(r)\),
+similar to the light blue line in Figure~\ref{fig:model-strucfunc}b.
 

### 2022-05-17 strucfunc_paper.tex
Improve description of model strucfunc fits

@@
 of the homogeneity assumption (see section~\ref{sec:limit-model-struct}).
-This \(L/2\) constrain is not used for the regions observed with MUSE.
+%This \(L/2\) constrain is not used for the regions observed with MUSE.
 
@@
 estimated autocorrelation length for each parameter,
-which required \num{50000} samples.
+which typically required of order \num{50000} samples.
 Thin translucent lines in the figures show structure functions using the parameters of
@@
 so that \(s_0\) is indeterminate in the model fits
-(note the flat posterior histograms for \(s_0\) in Fig.~\ref{fig:corner-Galactic}bcd).
+(note the flat posterior histograms for \(s_0\) in Fig.~\ref{fig:corner-Galactic}c and d).
 In addition, the effects of noise are also much greater,
@@
 in the power law slope \(m\).
-The most extreme case is the Extended Orion Nebula (Fig.~\ref{fig:strucfunc-fit-Galactic}b--d),
+The most extreme case is the Extended Orion Nebula (Fig.~\ref{fig:strucfunc-fit-Galactic}b),
 where noise dominates the structure function at all scales.
+The resultant degeneracy between parameters means that
+is not possible to obtain a satisfactory fit
+if all parameters are allowed to vary,
+so we instead chose to fix the power slope at \(m = 1.0\),
+which is close to the median value obtained for the other sources.
 
@@
 For the more distant sources, the principal observational limitation is the seeing.
-The derived values of \(s_0\) exceed 10\% of the correlation length,
-leading to large uncertainties in the determination of the power law slope \(m\).
+In three of the four sources,
+the derived values of \(s_0\) exceed 10\% of the correlation length.
+This implies that the true power law slope \(m\) is less steep than
+would be naively inferred from the observations
+(compare the green and orange curves in Figure~\ref{fig:strucfunc-fit-ExtraGal}),
+but at the same time the degeneracies between parameters
+(Figure~\ref{fig:corner-ExtraGal})
+lead to large uncertainties in the determination \(m\).
 On the other hand, the values of \(r_0\) and \(\sigma^2\) are still well-constrained.
@@
 However, it is worthwhile to do perform a sanity check on the values that are implied by our model fits.
-To that end, the last column in Table~\ref{tab:Res} gives the FWHM seeing width in arcsec.
+To that end, the last column in Table~\ref{tab:Res} lists the FWHM seeing width in arcsec for each fit.
 

### 2022-05-17 strucfunc_paper.tex
First half of description of sanity check on seeing
Show that mean values are reasonable, and discuss the low outlier of
NGC 595

@@
 are not available to us in all cases.
-However, it is worthwhile to do perform a sanity check on the values that are implied by our model fits.
-To that end, the last column in Table~\ref{tab:Res} lists the FWHM seeing width in arcsec for each fit.
+However, it is worthwhile to perform a sanity check on the values that are implied by our model fits.
+To that end, the last column in Table~\ref{tab:Res} lists the FWHM seeing width for each fit in units of arcsec.
+Disregarding the 3 sources where only upper limits can be determined,
+the mean and standard deviation are \SI{0.95(30)}{arcsec},
+which is perfectly consistent with expectations for seeing from ground-based observations.
+
+However, there are two outlier values that deserve closer attention.
+NGC~595 has the lowest value of \SI{0.2}{arcsec}, which seems
+unrealistically small, especially given the higher values
+derived for the other sources, such as NGC~604,
+that were obtained with the same instrument.
+On the other hand, the 95\% credibility range extends as high as \SI{0.7}{arcsec},
+which does overlap with the range for NGC~604.
+If one were to take a common compromise seeing of \SI{0.7}{arcsec}
+for both sources (\(s_0 = \SI{1.2}{pc}\)),
+then the anticorrelation between \(m\) and \(s_0\)
+(see Figure~\ref{fig:corner-ExtraGal}a, b)
+would decrease the inferred \(m\) for NGC~595 while increasing it for NGC~604,
+thus making the two slopes more closely similar.
 

### 2022-05-17 strucfunc_paper.tex
Javier edits 2022-05-17
Finish description of reasonableness of derived seeing
Talk about Orion Nebula value

@@
 On the other hand, the values of \(r_0\) and \(\sigma^2\) are still well-constrained.
-
 \subsection{On the reasonableness of the derived seeing widths and noise}
@@
 thus making the two slopes more closely similar.
+
+The inner Orion Nebula has the largest inferred seeing FWHM of \SI{2.4(4)}{arcsec},
+which is at least two times higher than the typical seeing measured during the observations
+\citep{Doi:2004a}.
+However, this can be explained by the fact that the velocity map is constructed
+by interpolating individual longslit observations onto a regular grid
+(section~\ref{sec:longsl-echelle-spect}).
+The seeing-limited resolution will only be achieved along the slits,
+whereas the resolution in the perpendicular direction is determined by the slit spacing of \SI{2}{arcsec}.
+Given, this the model-derived value of \(s_0\) for this source is reasonable.
 

### 2022-05-18 strucfunc_paper.tex
Add subscripts "obs" and "mod" to B(r)
This is to disambiguate the model and observed structure functions

@@
 \newcommand\noise{\ensuremath{_{\text{noise}}}}
+\newcommand\obs{\ensuremath{_{\mathrm{obs}}}}
+\newcommand\model{\ensuremath{_{\mathrm{mod}}}}
 \newcommand\halpha{H${\alpha}$}
@@
 \begin{equation}\label{eq:new-correlation-form}
-  C(r;\ r_0, m) = 2^{- \left( r/r_0 \right)^m} 
+  C\model(r;\ r_0, m) = 2^{- \left( r/r_0 \right)^m} 
 \end{equation}
@@
 and \(m\) is the power-law slope at small scales.
-This is constructed so that \(C(r) = 1/2\) at \(r = r_0\),
+This is constructed so that \(C\model(r) = 1/2\) at \(r = r_0\),
 while the exponential form ensures that \(C(r)\) rapidly approaches zero
 for larger separations.
-We use equation \eqref{eq:functional} to determine the structure function
-from this model autocorrelation function.
-The resultant model structure function has the following properties:
+We assume the validity of equation~\eqref{eq:functional} to determine the structure function
+from this model autocorrelation function:
+\begin{equation}
+  \label{eq:model-strucfunc-ideal}
+  B\model(r) = 2\sigma^2\pos \left[
+    1 - 2^{- \left( r/r_0 \right)^m} 
+  \right]
+\end{equation}
+This has the following properties:
 \begin{enumerate}[1.]
- \item Small scales: \(B(r) \propto r^m\) for \(r \ll r_0\);
- \item Correlation scale: \(B(r_0) = \sigma\pos^2\);
- \item Large scales: \(B(r) \to 2 \sigma\pos^2\) for \(r \gg r_0\).
+ \item Small scales: \(B\model(r) \propto r^m\) for \(r \ll r_0\);
+ \item Correlation scale: \(B\model(r_0) = \sigma\pos^2\);
+ \item Large scales: \(B\model(r) \to 2 \sigma\pos^2\) for \(r \gg r_0\).
  \end{enumerate}
@@
 \begin{equation}
-  \tilde{B}(r)
-  = 
-  2\sigma^2\pos \left[
-    1 - 2^{- \left( r/r_0 \right)^m} 
-  \right]
-  \,  S(r) + B\noise
+  \tilde{B}\model(r) = B\model(r) \,  S(r) + B\noise
   \label{eq:sf-functional}
@@
   \newlength\partabwidth
-  \setlength\partabwidth{0.7\linewidth}
-  \begin{tabular*}{\partabwidth}{@{\extracolsep{\fill}}l rr}
+  \setlength\partabwidth{0.8\linewidth}
+  \begin{tabular*}{\partabwidth}{
+    l @{\extracolsep{\fill}}
+    r 
+    r
+    }
     \toprule
@@
     \midrule
-    \(\sigma^2\) & \(0.25\, \max [B]\)& \(2\, \max [B]\)\\
+    \(\sigma^2\) & \(0.25\, \max [B\obs]\)& \(2\, \max [B\obs]\)\\
     \(r_0\) & \(0.01\, L\) & \(2\, L\)\\
@@
     \(s_0\) & \SI{0.1}{arcsec}& \SI{1.5}{arcsec}\\
-    \(B\noise\) & \(0\) & \(3\, \min [B]\) \\
+    \(B\noise\) & \(0\) & \(3\, \min [B\obs]\) \\
     \bottomrule
     \multicolumn{3}{@{}p{\partabwidth}@{}}{
-    Note: \(\max[B]\) and \(\min[B]\) are over all bins in the observed structure function.
+    Note: \(\max[B\obs]\) and \(\min[B\obs]\) are over all bins in the observed structure function with \(r < L/2\).
     }
@@
 we fit the model structure function
-\(\tilde{B}(r)\) of equation~\eqref{eq:sf-functional}
+\(\tilde{B}\mod(r)\) of equation~\eqref{eq:sf-functional}
 to each \hii{} region in our sample.
 Results are shown in Figures~\ref{fig:strucfunc-fit-Galactic}, \ref{fig:strucfunc-fit-MC},
-and \ref{fig:strucfunc-fit-ExtraGal}, arranged in order of increasing distance.
+and~\ref{fig:strucfunc-fit-ExtraGal}, arranged in order of increasing distance.
 Best-fit values for the model parameters,
@@
 
-For the observational values (blue symbols),
+For the observational values (\(B\obs(r)\); blue symbols),
 the structure function is the average value of equation~\eqref{eq:Br}
@@
 \texttt{lmfit} Python library \citep{newville_matthew_2014_11813}.
-The best-fit model \(\tilde{B}(r)\) is shown (heavy orange solid line),
-together with the corresponding underlying ``true model'' \(B(r)\) (heavy dashed green line),
+The best-fit model \(\tilde{B}\model(r)\) is shown (heavy orange solid line),
+together with the corresponding underlying ``true model'' \(B\model(r)\) (heavy dashed green line),
 which does not include the effects of seeing or noise.
-Note that the true model \(B(r)\) depends on only 3 parameters:
+Note that the true model \(B\model(r)\) depends on only 3 parameters:
 \(\sigma^2\), \(r_0\), and \(m\),
-whereas \(\tilde{B}(r)\) additionally depends on
+whereas \(\tilde{B}\model(r)\) additionally depends on
 the observational nuisance parameters: \(s_0\) and \(B\noise\).
@@
 a random selection of \num{100} posterior samples from the MCMC chain,
-both for \(\tilde{B}(r)\) orange and \(B(r)\) (green).
+both for \(\tilde{B}\model(r)\) orange and \(B\model(r)\) (green).
 This gives an estimate in the uncertainty about the best-fit model.
@@
 (section~\ref{sec:muse-integral-field}).
-The relatively poor spectral resolution means that the \(B(r)\) cannot
+The relatively poor spectral resolution means that the \(B\obs(r)\) cannot
 be measured down to such low values as in the inner Orion Nebula,
@@
 \citep{Doi:2004a}.
-However, this can be explained by the fact that the velocity map is constructed
+However, this can be at least partially explained by the fact that the velocity map is constructed
 by interpolating individual longslit observations onto a regular grid
@@
 such as Carina and Hubble~X,
-\(B(r)\) remains flat at a value of \(\approx 2\sigma^2\),
+\(B\obs(r)\) remains flat at a value of \(\approx 2\sigma^2\pos\),
 which is consistent with uncorrelated homogeneous fluctuations
@@
 such as the Orion Nebula (both inner and outer) and 30~Doradus,
-there is a clear downturn in \(B(r)\) at the largest separations.
+there is a clear downturn in \(B\obs(r)\) at the largest separations.
 As discussed above in section~\ref{sec:limit-model-struct},
@@
 The Orion Nebula is a particularly interesting case
-since the \(\sigma^2\) derived from the high-resolution dataset of the inner nebula on scales \(\approx \SI{0.1}{pc}\)
+since the \(\sigma^2\pos\) derived from the high-resolution dataset of the inner nebula on scales \(\approx \SI{0.1}{pc}\)
 is roughly twice as large as that derived from the lower resolution
@@
 such as the Lagoon and NGC~346,
-show \(B(r)\) increasing at the largest separations,
-reaching values significantly larger than \(2\sigma^2\).
+show \(B\obs(r)\) increasing at the largest separations,
+reaching values significantly larger than \(2\sigma^2\pos\).
 This can be evidence for a large-scale linear velocity gradient
@@
 This latter effect may also explain the behavior of NGC~604,
-which shows oscillatory behavior of \(B(r)\),
+which shows oscillatory behavior of \(B\obs(r)\),
 similar to the light blue line in Figure~\ref{fig:model-strucfunc}b.
@@
 
-In the section \ref{sec:results} we showed that each \hii{} region of our sample has a turbulent velocity field that can be characterized using the turbulence methods despite the results not being as the Kolmogorov model predicts.
-The turbulent parameters obtained are unique to each velocity field.
-We proceed to develop scaling relations between them and also between the physical properties of each region.
+In section \ref{sec:results} we show that each velocity field of our sample can be characterized by parameters that are particular for each \hii{} region.
+We used these parameters to develop scaling relations between them and the physical properties of each region.
 
 %Intro for scaling relations
-Relationship between the physical properties of \hii{} regions, like size and luminosity, and the velocity dispersion have been used as tools for concluding scaling relations for these objects.
-These relations have also been studied in dwarf galaxies and high-redshift star formation regions.
-\citet{melnick1977,terlevich1981} were the first to shown an empirical relationship between the line width and the integrated properties of the \hii{} regions as the diameter or the luminosity ($r \sim \sigma ^{\sim 2}$ ; $\text{L}_{\text{H}} \sim \sigma ^{\sim 4}$).
-They conclude that GEHRs follow this relation because they behave as self-gravitatory systems like globular clusters or elliptical galaxies.
-The work of \citet{1988A&A...201..199A} confirmed these relationships considering the discrepancies of previous investigations obtaining \(\text{L}_{\text{H}_{\alpha}} \propto \sigma^{3.9}\) and \(r \propto \sigma^{1.84}\).
+Correlations between the physical properties of \hii{} regions like size, luminosity, and the velocity dispersion have been used as tools for finding scaling relationships for these objects.
+These kind of relations have also been found in dwarf galaxies and high-redshift star formation regions.
+\citet{melnick1977,terlevich1981} were the first to shown an empirical relationship between the line width and the integrated properties of the \hii{} regions as the diameter or the luminosity (\(r \sim \sigma ^{\sim 2}\) ; \(\text{L}_{\text{H}} \sim \sigma ^{\sim 4}\)).
+In later years, \citet{1988A&A...201..199A} confirmed these relationships considering the discrepancies of previous investigations obtaining \(\text{L}_{\text{H}_{\alpha}} \propto \sigma^{3.9}\) and \(r \propto \sigma^{1.84}\).
 %\citet{1981MNRAS.194..809L}
-
-%Previous research on scaling relations
-\citet{2012MNRAS.422.3339W} have found that clumps and \hii{} regions follow scaling relations over the range of z = 0-2 for \halpha\ size, velocity dispersion, luminosity and mass, finding \(\sigma \propto r^{0.42}\), \(\text{L}_{\text{H}_{\alpha}} \propto r^{2.72}\) and \(\text{L}_{\text{H}_{\alpha}} \propto \sigma^{4.18}\), respectively.
+In recent years, \citet{2012MNRAS.422.3339W} have found that clumps and \hii{} regions follow scaling relations over the range of z = 0-2 for \halpha\ size, velocity dispersion, luminosity and mass, finding \(\sigma \propto r^{0.42}\), \(\text{L}_{\text{H}_{\alpha}} \propto r^{2.72}\) and \(\text{L}_{\text{H}_{\alpha}} \propto \sigma^{4.18}\), respectively.
 This results imply that the same process are seen at high redshifts and the current epoch in star forming regions.
@@
 %methods for our analysis
-We follow through this analysis using the scaling relation as a research tool between the properties of the sample of HII regions and our results. 
-We use the properties in Table \ref{tab:regions-properties} with the turbulent parameters in Table \ref{tab:Res} as the dependent variable to adjust a fit in the form \(Y = aX +b\). 
-For this procedure we use a hierarchical Bayesian approach using the package \textit{linmix} \citep{2007ApJ...665.1489K}.
+
+We implement a hierarchical Bayesian model for fitting a straight line using the \texttt{linmix} Python library based on \cite{2007ApJ...665.1489K}.
+The physical properties in Table \ref{tab:regions-properties} are the independent variable \(X\) and the turbulent parameters in Table \ref{tab:Res} are the dependent variable \(Y\). 
 The results are shown in Table \ref{tab:RestStats} in ascending order for the p-value.
-In the Figures \ref{fig:sigvsl} and \ref{fig:rvsR} we show the correlations with a significance level  $p < $0.05.
-In all the figures the slope of the fit shown in solid black line is the mean of all red lines that reflect the posterior of the Bayessian analysis.
+In the Figures \ref{fig:sigvsl} and \ref{fig:rvsR} we show the correlations with a significance level \(p < \num{0.05}\).
+The black solid line shows the input regression line and the red lines show some samples from the posterior distribution.
 
@@
 Due to the above, we chose these set values since they come from an unique source and are foreign to our calculations and observations, which imply that there is no bias in the scaling law we obtain.
+
+As for the power-law index \(m\) we can see from table \ref{tab:RestStats} that this parameter does not correlate with any other parameter or physical property.
 

### 2022-05-18 strucfunc_paper.tex
Final paragraph on the seeing
That perhaps it might be overestimated if B(r) is steepening towards
small scales.

@@
 whereas the resolution in the perpendicular direction is determined by the slit spacing of \SI{2}{arcsec}.
-Given, this the model-derived value of \(s_0\) for this source is reasonable.
+Given this, the model-derived value of \(s_0\) for this source is not unreasonable.
+
+On the other hand, it is perhaps significant that both
+the inner Orion Nebula and 30~Doradus,
+the two highest quality datasets in our sample,
+should both have a fitting-derived seeing width that is
+slightly larger than expected.
+Since our intrinsic model \(B\model(r)\) assumes a single power law
+for scales \(<r_0\),
+the only way of accommodating a steepening of \(B\obs(r)\) at small separations
+is via the seeing term \(S(r)\).
+But if the true \(B(r)\) really does steepen at small scales,
+then the seeing will be overestimated in the models.
+Unfortunately, the currently available data are insufficient to
+definitively decide this question.
 

### 2022-05-18 Corr.tex
Javier changes 2022-05-18 morning

--- 2022-02-22 Corr.tex
@@
 \hline
- log $\sigma$ &            log L(H) &   0.29 $\pm$ 0.09 &  -10.24 $\pm$ 3.53 &   0.89 &  0.001 \\
-    log $r_0$ &             log $S$ &   0.78 $\pm$ 0.25 &   -1.31 $\pm$ 0.52 &   0.85 &  0.002 \\
-% log $\sigma$ &  log $\sigma_{LOS}$ &   0.83 $\pm$ 0.48 &   -0.24 $\pm$ 0.56 &   0.71 &   0.02 \\
- log $\sigma$ &         log $r_{0}$ &   0.21 $\pm$ 0.17 &    0.66 $\pm$ 0.12 &   0.58 &   0.08 \\
-      log $m$ &            log Dist &  -0.09 $\pm$ 0.07 &    1.14 $\pm$ 0.14 &  -0.57 &   0.09 \\
-      log $m$ &        log $\sigma$ &  -0.11 $\pm$ 0.21 &    0.07 $\pm$ 0.16 &  -0.42 &   0.23 \\
-      log $m$ &         log $r_{0}$ &  -0.04 $\pm$ 0.07 &    -0.0 $\pm$ 0.05 &  -0.39 &   0.26 \\
+ log $\sigma$ &            log L(H) &   0.27 $\pm$ 0.13 &  -9.79 $\pm$ 4.91 &   0.86 &  0.003 \\
+    log $r_0$ &             log $S$ &    0.94 $\pm$ 0.3 &  -1.66 $\pm$ 0.66 &   0.85 &  0.004 \\
+ %log $\sigma$ &  log $\sigma_{LOS}$ &   0.89 $\pm$ 0.57 &  -0.26 $\pm$ 0.66 &   0.62 &   0.07 \\
+ log $\sigma$ &         log $r_{0}$ &   0.17 $\pm$ 0.21 &   0.69 $\pm$ 0.16 &    0.5 &  0.168 \\
+      log $m$ &            log Dist &   -0.06 $\pm$ 0.1 &    1.1 $\pm$ 0.21 &  -0.38 &   0.32 \\
+      log $m$ &         log $r_{0}$ &  -0.02 $\pm$ 0.09 &  -0.01 $\pm$ 0.07 &  -0.24 &  0.529 \\
+      log $m$ &        log $\sigma$ &  -0.05 $\pm$ 0.31 &   0.02 $\pm$ 0.24 &  -0.24 &  0.536 \\
 \bottomrule

### 2022-05-18 Corr.tex
Javier edits 2022-05-18 midday

@@
 \hline
- log $\sigma$ &            log L(H) &   0.27 $\pm$ 0.13 &  -9.79 $\pm$ 4.91 &   0.86 &  0.003 \\
-    log $r_0$ &             log $S$ &    0.94 $\pm$ 0.3 &  -1.66 $\pm$ 0.66 &   0.85 &  0.004 \\
- %log $\sigma$ &  log $\sigma_{LOS}$ &   0.89 $\pm$ 0.57 &  -0.26 $\pm$ 0.66 &   0.62 &   0.07 \\
- log $\sigma$ &         log $r_{0}$ &   0.17 $\pm$ 0.21 &   0.69 $\pm$ 0.16 &    0.5 &  0.168 \\
-      log $m$ &            log Dist &   -0.06 $\pm$ 0.1 &    1.1 $\pm$ 0.21 &  -0.38 &   0.32 \\
-      log $m$ &         log $r_{0}$ &  -0.02 $\pm$ 0.09 &  -0.01 $\pm$ 0.07 &  -0.24 &  0.529 \\
-      log $m$ &        log $\sigma$ &  -0.05 $\pm$ 0.31 &   0.02 $\pm$ 0.24 &  -0.24 &  0.536 \\
+ log $\sigma$ &            log L(H) &    0.27 $\pm$ 0.1 &  -9.57 $\pm$ 3.95 &   0.86 &  0.003 \\
+    log $r_0$ &             log $S$ &   0.94 $\pm$ 0.34 &  -1.67 $\pm$ 0.74 &   0.85 &  0.004 \\
+ %log $\sigma$ &  log $\sigma_{LOS}$ &   0.75 $\pm$ 0.59 &  -0.15 $\pm$ 0.69 &   0.62 &   0.07 \\
+ log $\sigma$ &         log $r_{0}$ &   0.17 $\pm$ 0.18 &   0.68 $\pm$ 0.13 &    0.5 &  0.168 \\
+      log $m$ &            log Dist &   -0.06 $\pm$ 0.1 &    1.11 $\pm$ 0.2 &  -0.38 &   0.32 \\
+      log $m$ &         log $r_{0}$ &  -0.03 $\pm$ 0.09 &    0.0 $\pm$ 0.06 &  -0.24 &  0.529 \\
+      log $m$ &        log $\sigma$ &  -0.12 $\pm$ 0.31 &   0.08 $\pm$ 0.23 &  -0.24 &  0.536 \\
 \bottomrule

### 2022-05-18 strucfunc_paper.tex
Javier edits 2022-05-18 midday

--- 2022-05-18 strucfunc_paper.tex
@@
 \includegraphics[width=3in]{Figures/corr-los-vs-pos}
-\caption{The $\sigma$-$\sigma_{\text{los}}$ plane. The dotted line represents slope equal to unity and the dashed line represents a slope of two.}
+\caption{The \(\sigma_{\text{pos}}\)-\(\sigma_{\text{los}}\) plane.
+The dotted line represents slope equal to unity and the dashed line represents a slope of two.
+The size of the markers represent the distance to each region.}
 \label{fig:los-vs-pos}
@@
 %methods for our analysis
-
 We implement a hierarchical Bayesian model for fitting a straight line using the \texttt{linmix} Python library based on \cite{2007ApJ...665.1489K}.
 The physical properties in Table \ref{tab:regions-properties} are the independent variable \(X\) and the turbulent parameters in Table \ref{tab:Res} are the dependent variable \(Y\).
-The results are shown in Table \ref{tab:RestStats} in ascending order for the p-value.
+For the physical properties we consider an uncertainty of the \num{10}\% of the value and for the turbulent parameters we used 1-\(\sigma\). 
+In the case of non-gaussian distribution we choose the highest value for the uncertainty.
+The results are shown in Table \ref{tab:RestStats} in ascending order for the \(p\)-value.
 In the Figures \ref{fig:sigvsl} and \ref{fig:rvsR} we show the correlations with a significance level \(p < \num{0.05}\).
-The black solid line shows the input regression line and the red lines show some samples from the posterior distribution.
+The black solid line shows the regression line and the red thin lines show some samples from the posterior distribution.
 
@@
 Since this relation is the most common it can be use for comparison with the investigations mentioned at the beginning of this section.
-Our results give us a relation of \(\log \sigma\pos = (0.28 \pm 0.1) \log \text{L}(\text{H}_{\alpha})-(10 \pm 4.0)\).
+Our results give us a relation of \(\log \sigma\pos = (0.27 \pm 0.1) \log \text{L}(\text{H}_{\alpha})-(10 \pm 4.0)\).
 It is customary in the literature to present \(\text{L} (\text{H}_{\alpha})\) as the dependent variable.
 In our case if we choose the upper uncertainty and take the inverse of slope we have \(\text{L}_{\text{H}_{\alpha}} \propto \sigma^{3.4}\). 
-Using the same procedure in \textit{linmix} and changing the variables we obtained \(\log \text{L}(\text{H}_{\alpha}) = (3.1\pm 1.3) \log \sigma\pos -(36 \pm 1)\).
-Both relations are close to the previously proposed \(\text{L}_{\text{H}} \propto \sigma^{4}\) relation.
+Using the same procedure in \texttt{linmix} and changing the variables we obtained \(\log \text{L}(\text{H}_{\alpha}) = (3.4\pm 1.5) \log \sigma\pos -(36 \pm 1)\).
+Both results are close to the previously proposed \(\text{L}_{\text{H}} \propto \sigma^{4}\) relation.
+The references for the \(\text{L}(\text{H}_{\alpha})\) value are given in Appendix~\ref{sec:notes-individual-hii}.
 
@@
 The Figure \ref{fig:rvsR} shows the relation of the correlation length \(r_0\) and the size \(S\) of the region. 
-The relationship we found is \(\log r_0 = (0.73 \pm 0.24) \log S - (1.17 \pm 0.5)\).
-The values of the \(S\) are taken from \citet{1984ApJ...287..116K} and correspond to the outer
+The relationship we found is \(\log r_0 = (0.93 \pm 0.33) \log S - (1.6 \pm 0.7)\).
+The values of \(S\) are taken from \citet{1984ApJ...287..116K} and correspond to the outer
 limits seen from visual inspection of the \ha{} photographs.
@@
 Since these objects do not posses a physical edges the size determination is not trivial.
-Due to the above, we chose these set values since they come from an unique source and are foreign to our calculations and observations, which imply that there is no bias in the scaling law we obtain.
+Due to the above, we chose these set values since they are from an unique source and are foreign to our calculations and observations, which reduced the bias in the scaling law we obtain.
 
@@
 \includegraphics[width=3in]{Figures/corr-svsL}
-\caption{The log \(\sigma\pos\) - log $L(H_{\alpha})$ plane derived form our results an data in the literature.
-A fit with slope of 0.27 $\pm$ 0.1 is shown in solid black line that is the mean of all red lines that reflect the posterior of the Bayessian analysis.
-}
+\caption{The log \(\sigma\pos\) - log $L(H_{\alpha})$ plane derived form our results an data in the literature. }
 \label{fig:sigvsl}
@@
 \includegraphics[width=3in]{Figures/corr-rvsS}
-\caption{Same as Fig. \ref{fig:rvsR} but for the log \(r_0\) - log \(S\) plane. }
+\caption{The log \(r_0\) - log \(S\) plane derived form our results an data in the literature. }
 \label{fig:rvsR}
@@
 They mentioned that one problem with \citet{Medina-Tanco:1997a} structure function is that they didn't take into account the observational seeing.
-This would invalidate they results and \citet{Melnick:2021x} consider that taking out the structure function values that fall in this range would make the structure function flat at scales \(<\)\SI{10}{pc}.
-Finally they point out, and we agree, the importance of observing NGC 604 at higher spatial resolution, so they rule out \citet{Medina-Tanco:1997a} results. 
+This would invalidate they results and \citet{Melnick:2021x} consider that taking out the structure function values that fall within this range would make the structure function flat at scales \(<\)\SI{10}{pc}, so they rule out \citet{Medina-Tanco:1997a} results.
+Finally they point out, and we agree, the importance of observing NGC 604 at higher spatial resolution. 
 Our Fig. \ref{fig:strucfunc-fit-ExtraGal}d shows in fact that there is a velocity structure in NGC 604. 
-We have prove that a consistent and more precise method in analyzing structure function is key to obtaining trustworthy results.
 None of the previous studies present a power-law index for the structure function to compare our results.
@@
 %Using their unfiltered data the correlation length is \(\sim\) \SI{90}{pc} and using the same criteria as our it is \(\sim\) \SI{40}{pc} and the slope would be shallower. 
-Their velocity centroid \(\sigma\) is \SI{5.92 \pm 0.15}{km.s^{-1}} while we have \SI{7.48\pm 2}{km. s^{-1}} which fall within the uncertainties.
+Their velocity centroid \(\sigma\) is \SI{5.92 \pm 0.15}{km.s^{-1}} while we have \SI{7.3\pm 2}{km. s^{-1}} which fall within the uncertainties.
 Due to the different observations and methodologies a direct comparison between structure functions is not possible.

### 2022-05-18 strucfunc_paper.tex
Minor edits

@@
 
-At scales larger than \(L/2\),
+At scales larger than \(L/2\)
 we see a variety of different shapes for the structure functions
 of our sample regions.
+These points are excluded from our model fits but we give
+a qualitative description in this section.
 In some cases,

### 2022-05-18 strucfunc_paper.tex
Improve strucfunc figure captions

@@
     from Galactic \hii{} regions.
-    Blue symbols show the observed mean structure function
-    in each radial bin.
+    The observed structure function \(B\obs(r)\) is shown by 
+    blue symbols, with filled symbols indicating those points
+    that are used to constrain the model fits.
+    The full model is shown in orange,
+    while the underlying ideal model
+    (without the effects of seeing or noise)
+    is shown in green.
+    See text for details of the fitting process.
+    (a)~Inner Orion Nebula.
+    (b)~Extended Orion Nebula.
+    (c)~M8, the Lagoon Nebula.
+    (d)~Carina Nebula.
   }
@@
     except for Magellanic Cloud \hii{} regions.
+    (a)~30 Doradus in the LMC.
+    (b)~NGC~346 in the SMC.    
   }
@@
     Local Group Galaxies.
+    (a)~Hubble~V in NGC~6822.
+    (b)~Hubble~X in NGC~6822.
+    (c)~NGC~595 in M33.
+    (d)~NGC~604 in M33.
   }
@@
 we fit the model structure function
-\(\tilde{B}\mod(r)\) of equation~\eqref{eq:sf-functional}
+\(\tilde{B}\model(r)\) of equation~\eqref{eq:sf-functional}
 to each \hii{} region in our sample.
@@
 The most extreme case is the Extended Orion Nebula (Fig.~\ref{fig:strucfunc-fit-Galactic}b),
-where noise dominates the structure function at all scales.
+where noise makes a significant contribution to the structure function at all scales.
 The resultant degeneracy between parameters means that

### 2022-05-27 Corr.tex
Javier changes 2022-05-27

@@
 \hline
- log $\sigma$ &            log L(H) &    0.27 $\pm$ 0.1 &  -9.57 $\pm$ 3.95 &   0.86 &  0.003 \\
+ log $\sigma\pos$ &            log L(H) &    0.27 $\pm$ 0.1 &  -9.57 $\pm$ 3.95 &   0.86 &  0.003 \\
     log $r_0$ &             log $S$ &   0.94 $\pm$ 0.34 &  -1.67 $\pm$ 0.74 &   0.85 &  0.004 \\
- %log $\sigma$ &  log $\sigma_{LOS}$ &   0.75 $\pm$ 0.59 &  -0.15 $\pm$ 0.69 &   0.62 &   0.07 \\
- log $\sigma$ &         log $r_{0}$ &   0.17 $\pm$ 0.18 &   0.68 $\pm$ 0.13 &    0.5 &  0.168 \\
+ %log $\sigma\pos$ &  log $\sigma_{LOS}$ &   0.75 $\pm$ 0.59 &  -0.15 $\pm$ 0.69 &   0.62 &   0.07 \\
+ log $\sigma\pos$ &         log $r_{0}$ &   0.17 $\pm$ 0.18 &   0.68 $\pm$ 0.13 &    0.5 &  0.168 \\
       log $m$ &            log Dist &   -0.06 $\pm$ 0.1 &    1.11 $\pm$ 0.2 &  -0.38 &   0.32 \\
       log $m$ &         log $r_{0}$ &  -0.03 $\pm$ 0.09 &    0.0 $\pm$ 0.06 &  -0.24 &  0.529 \\
-      log $m$ &        log $\sigma$ &  -0.12 $\pm$ 0.31 &   0.08 $\pm$ 0.23 &  -0.24 &  0.536 \\
+      log $m$ &        log $\sigma\pos$ &  -0.12 $\pm$ 0.31 &   0.08 $\pm$ 0.23 &  -0.24 &  0.536 \\
 \bottomrule

### 2022-05-27 strucfunc_paper.tex
Javier changes 2022-05-20
Reorganise order of subsections in discussion
Javier changes 2022-05-27

@@
 
-We use \cite{1987A&A...176..347H} observations to analyze the Extended Orion Nebula.
+We use \citet{1987A&A...176..347H} observations to analyze the Extended Orion Nebula.
 These observations were obtained using a 106 cm-Cassegrain telescope at Observatorium Hoher List. 
@@
 of the homogeneity assumption (see section~\ref{sec:limit-model-struct}).
-%This \(L/2\) constrain is not used for the regions observed with MUSE.
 
@@
 
-% Particularly the EON observations, which are the oldest, the fitting procedure gives a noise value of \SI{5.6}{km^{2}.s^{-2}} larger that the \(\sigma^2\pos\) value of \SI{3}{km^{2}.s^{-2}}.
-% The derived correlation length \(r_0 = \SI{0.05}{pc}\) is \num{6} times smaller
-% than the box size, which is the minimum value for this ratio of our sample. 
-% Hence we can confirm that the finite map has no effect in our results.
-% The derived seeing parameter \(s_0 = \SI{0.002}{pc}\), consistent with the Orion core fit, is more than \num{250} times smaller than \(r_0\).
-% This large ratio is because the separation of the pixels for the EON observations are at separations above the observational seeing, so these parameter has virtually no effect in our model for the EON case.
-% The previous statement can be confirmed with the Fig. \ref{fig:corner-Galactic}b which shows the corner plot for the EON.
-% The RMS seeing posterior is flat, meaning that the values in that range doesn't modify the fit.
-
-% This behavior is also seen in the Carina nebula and Lagoon nebula.
-% The observations for this regions are from the FLAMES multi-fiber instrument (section \ref{sec:flames-multi-fiber} ) in which the fibers separation  (see Figure \ref{fig:velocity-maps}) is above the observational seeing for the regions.
-
 The structure functions for sources in the Magellanic Clouds are shown in Figure~\ref{fig:strucfunc-fit-MC}
@@
 On the other hand, the values of \(r_0\) and \(\sigma^2\) are still well-constrained.
+
 \subsection{On the reasonableness of the derived seeing widths and noise}
@@
 
-%structure functions plots descriptions
-%Figures \ref{fig:strucfunc-fit-OrionS}-\ref{fig:strucfunc-fit-OrionLH} left panels show in solid and open blue circles the observational structure function that we compute using equation \ref{eq:Br} on the \ha{} velocity fields of Fig.
-\ref{fig:velocity-maps}.
-%In the plots the solid circles indicate the points we use in the non-linear regression analysis (see section~\ref{sec:model-fit}), while the open circles are the points of the structure function that where left out.
-%The criteria for the previous considerations is that the structure function at large separations is affected by the inhomogeneties of the velocity field (see section-\ref{sec:limit-model-struct}).
-%The points left our correspond to the largest separations that are not consider in our model. 
-%In some cases, at the smallest separations we merge a couple of the structure functions points under the assumption that those would be heavily affected by the seeing.
-%The Figures shows in the orange solid thick line the best fit for the equation \ref{eq:sf-functional} which takes into account observational limitations on the structure function.
-%The green dashed line indicate the theoretical model for the structure function using equation \ref{eq:functional}.
-
-%Figures \ref{fig:strucfunc-fit-OrionS}-\ref{fig:strucfunc-fit-OrionLH} left panels show in dashed and dotted lines the parameters of our model.
-%The vertical dashed line indicates the correlation length, \(r_0\), and the horizontal dashed line indicates the true variance of the velocity fields, \(\sigma^2\).
-%The vertical and horizontal dotted lines shows the value of the observational considerations: the rms seeing, \(s_0\) and the noise, \(B\noise\).
-%These values were obtained using the LM method.
-%For the dashed and dotted lines the overlapping translucent boxes indicate the confidence intervals in 1-sigma (dark shaded area) and 2-sigma (light shaded area) obtained from the MCMC analysis.
-%The light shaded areas in the plot show where the separation \(r\) is above half of the box size, \(L\), which is indicated with a vertical dotted line.
-
 %For Carina and Lagoon nebula, the velocity fields are obtained from the FLAMES multi-fiber instrument (section~\ref{sec:flames-multi-fiber}). 
@@
 
-%corner plots descriptions
-%Figures \ref{fig:corner-example-Orion} show the corner plots \citep{2017ascl.soft02002F} of the turbulent parameters and observational constraints
-%(further examples in Appendix~\ref{sec:addit-covar-corn}).
-%These plots shows the one and two dimensional projections of the posterior probability distributions of the parameters used in equation \ref{eq:chi}.
-%They also show the distribution for each parameter independently in the histograms along the diagonal and then the marginalized two dimensional distributions in the other panels making possible to visualize all of the covariances between parameters \citep{2017ascl.soft02002F}.
-%The contours in the plots reflect the 95\(\%\), 99\(\%\), 99.5\(\%\) and 99.9\(\%\) confidence intervals.
-%A number of fits for the equations \ref{eq:sf-functional} and \ref{eq:functional} using samples of the posteriors are shown in thin translucent orange and green lines, respectively, showing the possible range of the confidence intervals.
-
-%Table \ref{tab:Res} presents the turbulent parameters and observational constraints values mentioned in the paragraphs above.
-%The confidence intervals for these values are up to 2-sigma of the posteriors.
-%The second column correspond to the variance \(\sigma^2\pos\) of the velocity field.
-%The \(B\noise\) value is shown in the third column which would be the minimum squared velocity difference that could be measure by the instrument.
-%The fourth column in Table \ref{tab:Res} shows the rms seeing value in parsecs, \(s_0\), which represent the minimum value of the separation which would valid for the observed structure function. 
-%The fifth column shows the correlation value \(r_0\) in parsecs.
-%The \(r_0\) range covered in our results for the sample goes from 0.09 to 12 pc.
-%The sixth column indicates the size of each observational box in parsecs.
-%The index \(m\) is shown in the seventh column.
-%The range covered by the power-law index goes from 0.7 to 1.5.
-%The eighth column show the ratio \(L / r_0\)
-%The last column shows the FWHM seeing in arcsec.
-%The interpretation of our results is developed in the next section.
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-In the next sections we discuss the application and interpretation of the turbulent parameters we obtained in our results.
-%We present a resume of the turbulence theory and its validation to \hii{} regions.
-%It is also mentioned some physical processes that contribute to stirring the ionized gas and the possibility that they are responsible for the observed velocity fluctuations.
-We present the most important correlations between the turbulent parameters and physical properties of our \hii{} region sample and finally we discuss our results in the context of previous structure functions.
-
-%\subsection{Turbulence}\label{sec:turbulence-theory}
-
-%\textit{Will 2021-12-10: Moving this section to later for now. Maybe
-%  this material could go in discussion.}
-
-%The idea to treat the ionized regions from a fluid mechanic view is intuitive if we consider the continuum hypothesis. 
-%We validate this hypothesis using the Knudsen number defined as \(\text{Kn} \equiv \lambda / l\), where \(\lambda\) is the mean free path of the medium and \(l\) a characteristic length of the phenomenon we are studying.
-%Taking into account a \(\lambda_{\text{HII}}\) of \SI{2.7e-7}{pc} \citep{1941ApJ....93..369S} and a \(l_{\text{HII}}\) of \SI{1}{pc} for ionized regions we obtained \(\text{Kn} \approx 10^{-7}\), while in general the continuum approach is valid for \(\text{Kn}\ll 1\).
-
-%A turbulent behavior in the flows is more common in fluid systems than a laminar one.
-%These turbulent flows tends to be unsteady, irregular and chaotic, and the turbulent motions are observed in many scales. 
-%The turbulent flows are associated with a high Reynolds numbers which is defined as \(\text{Re} = l v_{l} / \nu \), where \(v_{l}\) is a characteristic velocity in the fluid system and \(\nu\) is the kinematic viscosity of the medium.
-%Experiments have shown that a flow which is laminar become turbulent when increasing the velocity (i.e., increasing the Re) and a large range of velocity fluctuation appear at all scales.
-%A high Re reflects high ratio of the advection/difussion terms of the Navier-Stokes equations, being interpreted as that the inertial forces taking over the viscous ones. 
-%Hence it is possible to assume that if viscosity is not dominant in a flow, this flow would be turbulent.
-
-%As astronomical observation made it possible to measure a large number of points with a high accuracy, it was found that velocities show a non-thermal component reflecting characteristic of turbulent earthly flows.
-%The existence of turbulent flows in astrophysical objects, ranging in scales from 10\(^6\) to 10\(^{17}\) m \citep{2010ApJ...710..853C} is thought to be consequence of the high \(Re\), between 10\(^4\) and 10\(^9\) \citep{1949ApJ...110..329C,lagrois2011} that characterized these objects.
-
-%The classic turbulence theory assumes a three-dimensional isotropic, incompressible and subsonic flow that can be described using an energy spectrum formed by vortices or eddies of different sizes \citep{kolm1}.
-%The concept of the energy spectrum assumes that the energy is cascading down inside the flow from the largest to the smallest scales.
-%The different scales in the energy cascade are defined based on their Re.
-%In one side of the spectrum there is the energy injection scale, \(L_I\), that is related to the largest vortices, called the integral scales, where \(\text{Re} \rightarrow \infty\).
-%On the other side of the spectrum there is the dissipation of energy at small scales, \(l_I\), where  \(\text{Re} \rightarrow 1\) and it is assumed that small vortices are responsible for the friction that dissipates the energy flux into thermal energy.
-%In between there is the inertial range, \(l_d  << l << L_I\), where in a stationary case the energy transfer is at a constant rate.
-
-%The rate of transfer of specific energy \(\epsilon\) (energy per unit mass) in the inertial range is independent of the \(l\) scale having the form \(\epsilon \sim v_l^2 / \tau_l\), where the kinetic energy is of the order of \( v_l^2\) and the life time of a velocity fluctuation is \(\tau_l\), which can be can be put in terms of \(\tau_l \sim l / v_l\).
-%Hence we obtain \( v_l \sim (\epsilon l)^{1/3}\) where \(\epsilon\) is invariant in the cascade.
-
-%The energy cascade is described using the energy spectrum, $E(k) \propto k^{\beta}$ where \(k\) is the wave number for a determined scale \(l\) ($k \equiv l^{-1}$).
-%The total specific energy of a determined $l$ scale is of the order \(\langle v_{l}^{2} \rangle \) and is the energy integral above the associated \(k\), defined as:
-
-%\begin{equation}\label{eq:energy-spectrum}
-% \langle v_{l}^{2} \rangle = \int_{k}^{\infty} E(k)dk
-%\end{equation}
-%
-%If it is assumed that this energy is of the order of $(\epsilon l)^{\frac{2}{3}} \sim (\frac{\epsilon}{k})^{\frac{2}{3}}$ we can differentiate equation \ref{eq:energy-spectrum} and obtained the final form:
-
-%\begin{equation}\label{eq:kolmogorov-law}
-%E(k) \propto \epsilon^\frac{2}{3} k^{-\frac{5}{3}}
-%\end{equation}
-%
-%where \(\beta = -5 / 3\) is the Kolmogorov law.
-%For supersonic turbulence the index is $\beta=-2$ \citep{burg}.
-
-%Using a statistical law that relates the moments \(M_n\) of order \(n\) with the increments in the velocity field for a separation \(\boldsymbol{r}\) \citep{Leqism}, we have:
-
-%\begin{equation}\label{eq:velocity-moments}
-%M_n = \langle \vert \boldsymbol{v}(\boldsymbol{x} + \boldsymbol{r})- \boldsymbol{v}(\boldsymbol{x})\vert^n \rangle \propto (\epsilon r)^{n/3}
-%\end{equation}
-%
-%the average is over all the positions \(\boldsymbol{x}\) and directions \(\boldsymbol{r}\). 
-%The Kolmogorov model predicts that the moment of order 2, the second-order structure function (equation \ref{eq:Br}), follows \(M_2 \propto r^{2/3}\).
-
-%\subsection{Origins of interstellar turbulence}\label{sec:origins-turbulence}
-
-%In the particular case of GEHR, as supersonic motions dissipate energy by shocks in time scales relatively short compared with the age of the region, it is necessary an energy source to replenish continuously the energy lost.
-From the observed velocity  dispersion \(\sigma\), and assuming that we have an isotropic distribution of velocities,  we can estimate the 3D velocity dispersion by \(\sigma_\mathrm{3D} = \sqrt{3} \sigma\).
-The mass of the ionized gas together with the velocity dispersion \(\sigma_\mathrm{3D}\)  are used to estimate the kinetic energy in the GEHRs.
-%As these objects have typically  masses of the ionized gas of \num{\sim e5} M\(_{\sun}\) and velocity dispersion values  of \SI{\sim 20}{km.s^{-1}} \citep{1984ApJ...287..116K}, typical kinetic energy of the ionized gas is \SI{\sim e51}{ergs}.
-
-%In the standard Kolmogorov model, the energy spectrum of turbulence becomes dependent only on \(\epsilon\), the mean dissipation of energy per unit time per unit mass of fluid,  with the inertial forces transferring without losses kinetic energy from larger to smaller turbulent elements within the inertial range.
-Let \(L_c\) be the characteristic length of the largest eddies, and \(\delta v\) the typical velocity.
-
-%We have then that \(\epsilon = (\delta v)^{3}/L\). In steady-state turbulence, equilibrium exists between the energy input and the energy dissipation rates. 
-%Although the present observations indicate that turbulence in \hii{} regions may not follow the Kolmogorov model, with energy input occurring at different scales, so that a  truly inertial range may not exist at all, lets us make a crude estimation of the  amount of energy transferred between scales using this simple model.
-%Assuming the above figures for the mass of the gas and velocity dispersion, \(\delta v = \sigma_\mathrm{3D}\),  and a \(L_c\) of \SI{100}{pc}, we obtain that the energy transfer rate \SI{\sim e37}{erg.s^{-1}}, and  the time scale for energy transfer, \(L/\delta v \), would be of few million years.
-
-%There are several energy sources that could provide or contribute  to the energy required: of the order of kpc, the differential rotations of the galaxy that produces shear at large scale, at scales of the order of hundreds of pc, supernova explosions inject a large amount of kinetic energy.
-%At scales of several tens of pc the expansion of \hii{} regions and stellar winds are a source of energy and, bipolar flows, shocks, jets and champagne flows inject energy at small scales about one tenth of a pc.
-
-%The lack of precise information on how these mechanism contribute to the emission line broadening make a non-trivial task to determine at what extent they play a role in the interstellar turbulence, contributing to the complexity of the extraction of pure turbulent motions from velocity profiles in nebulae \citep{2011MNRAS.413..705L,arthur2016turbulence}.
-
-\subsection{Interpretation of the turbulent parameters}\label{sec:interpretation-parameters}
-
-\subsubsection{Correlation length \(r_0\)}
-
-Ideally the correlation length \(r_0\) should represent the scale of dominant energy injection.
-It is unclear what are the precise mechanisms driving the turbulence in \hii{} regions, thought a lot of options are candidates.
-The most probable scenario is that the velocity fluctuations are consequence of the combination of various mechanism.
-There are several energy sources that could provide or contribute  to the energy required: of the order of kpc, the differential rotations of the galaxy that produces shear at large scale, at scales of the order of hundreds of pc, supernova explosions inject a large amount of kinetic energy.
-At scales of several tens of pc the expansion of \hii{} regions and stellar winds are a source of energy and, bipolar flows, shocks, jets and champagne flows inject energy at small scales about one tenth of a pc.
-Many of these mechanisms, at some extent, affect all the \hii{} regions studied in this work.
-We can use the kinematic analysis of the regions to investigate how previously identified energy injection mechanisms could be related to the correlation length.
-
-\citet{2009AJ....137..367O} present a three-dimensional study of the dynamic structure of the Orion nebula.
-The high-velocity stellar wind from \(\theta^1\) Ori C will confine the ionized gas, even the high ionization emission lines, to a thick shell.
-In one direction, at a distance of \SI{0.1}{pc} from the ionizing massive star a stationary shell of shocked material is formed when the ram pressure of the photoevaportation flow balances the thermal pressure of the shocked wind.
-In the other direction there is a free flow of the hypersonic wind.
-At a smaller scale of \SI{0.02}{pc} there is an interaction between the closest proplyd photoevaporation flow and the stellar wind which results in bowshocks.
-According to \citet{2001ApJ...561..830G} the influence of stellar wind interactions is restricted to the central \SI{0.05}{pc}. 
-Orion also present a champagne flow where the photoionized gas streams away from the ionization front covering a distance of \SI{\sim 1}{pc} from the molecular cloud \citep{1973ApJ...183..863Z}.
-
-Our correlation length results for the Orion Core and EON from table~\ref{tab:Res}, \num{0.068} y \SI{0.39}{pc} respectively, despite been of the order of the scales mentioned above still aren't conclusive enough to determine a direct relation between them.
-As mentioned in \citet{arthur2016turbulence} the mechanism mentioned in the previous paragraph would play a secondary role in stirring up the gas motions and it would be necessary to specify if the velocity fluctuations arise from pure turbulent motion inside the ionized clouds or a consequences of density and brightness fluctuations.
-
-\citet{sabalisck1995supersonic} studied NGC 604 revealing that the high emission knots on the region encompasses supersonic global velocity dispersion values of 14 $<$ \(\sigma_{\text{los}}\) $<$ \SI{20}{km.s^{-1}}.
-This knots have a characteristic radius of \(\sim\)\SI{7}{pc} and a Gaussian profile.
-Values of velocity dispersion $>$\SI{20}{km.s^{-1}} are found in low emission cavities where the lines present strong asymmetries.
-These cavities were identified as expanding shells by \cite{yang1996} with diameters of \(\sim\)\SI{40}{pc} and a expansion velocity above \SI{50}{km.s^{-1}}.
-According to table~\ref{tab:Res} the correlation length for NGC 604 is close to the scale of the bright knots in the region which aren't related to a particular energy injection mechanism.
-
-Although the Orion core, the EON, and NGC 604 have different \(r_0\) is not clear if it truly reveal a concrete aspect of the energy input mechanism mentioned above.
-Orion main energy input comes from one star, meanwhile NGC 604 has more than 200 OB stars including WR stars. 
-The Orion core also presents Herbig-Haro objects, which aren't possible to resolve for more distant regions.
-Though the correlation length is particular to each region, and it is correlated mainly with the size (see section~\ref{sec:scaling-relations}), it still needs further studies to reveal the true implication of this value with respect the energy input mechanisms.
-
-\subsubsection{Structure function power-law index \(m\)}\label{sec:power-index}
-
-The index \(m\) shown in the last column of Table \ref{tab:Res} is used for comparison between observations and the theoretical value of 0.67.
-All our indices are above this theoretical value and this is attributed to the fact that the \hii{} regions do not comply with the assumptions established in the development of the turbulent theory.
-
-From section~\ref{sec:regions-milky-way} we know that most of all assumption mentioned in the theory of turbulence are not meet for our \hii{} region sample.
-\hii{} regions emerged from a molecular cloud with highly filamentary and clumpy density structure .
-There is a large increase in the temperature because of the photoionization, and the density gradients with the pressure gradients accelerate the flow which occurs on multiple scales consequence of the fractal nature of the molecular cloud \citep{arthur2016turbulence}.
-The radiation pressure, stellar winds and region expansion, among other physical processes would create pressure-driven shock waves propagating faster than the speed of sound in the medium.
-This would make the flow compressible and supersonic in \hii{} regions.
-Also, as \hii{} regions are three-dimensional objects our structure function results comes from a projection of this three-dimensional structure to a two-dimensional velocity field.
-But despite the complex nature of \hii{} regions and observational limitations we obtain a common pattern for the structure function and the value of the power-law index falls in a certain limited range of values.
-The differences in the power-law index with respect the theoretical value are often used as a diagnostic tools to identify properties that are not consider in the assumptions of the turbulence theory.
-
-To study the projection of a three-dimensional structure function to a two-dimensional structure function, known as projection smoothing \citep{von1951methode, munch1958internal,1964SvA.....8..210K,1987ApJ...317..686O}, relationships between the power-law indices were proposed:
-
-\begin{equation}\label{eq:projection-smoothing-3d}
-m_{2D}= m_{3D} + 1
-\end{equation}
-%
-and  when the astronomical object present a sheet-like distribution of emitters we have the relation:
-%
-\begin{equation}\label{eq:projection-smoothing-2d}
-m_{2D} \sim m_{3D}
-\end{equation}
-
-As a conclusion, if the extension of the HII region is compared with its depth (three-dimensional case) the value of the index is \num{1.67}. 
-While the case where the extension is much greater than its depth (two-dimensional case) the region will have a value of \num{0.6}.
-From Table~\ref{tab:Res} we see that our results fall between these two previous values.
-
-The mean value \(m\) of our sample is \num{\sim 1}. 
-Following the equation \ref{eq:projection-smoothing-3d} the \hii{} regions in our sample with \(m >\) 1 would present a depth which is in the order of magnitude comparable to the length of the observed box size \(L\) been closest to this value as \(m\) tends to 1.6.
-On the other hand, \hii{} regions with values \(m <\) 1 would present a thinner structure as they tend to the value of 0.6.
-This analysis should not be regarded as conclusive about the true structure of the regions and would require further observations with a combination of kinematics analysis to determine the best way to determine the depth of each region.
-As we show in section \ref{sec:sigmapos-vs-sigmalos} the ratio between \(\sigma\pos\) and \(\sigma_{\text{los}}\) can also be used to give an idea of the depth o the region.
-
-\subsubsection{Relationship between plane-of-sky and line-of-sight velocity dispersion}\label{sec:sigmapos-vs-sigmalos}
-
-As a justification for the use of the structure function we can consider that any relation between the line width and line-of-sight depth can be interpreted in terms of a correlation between velocity spread and scale size.
-If we have an optically thin spectral line where it will have a width which is related to the total radial velocity dispersion of all fluctuations sampled along the line-of-sight \citep{1984ApJ...277..556S}.
-The standard deviation of the velocity centroid, \(\sigma\pos\), and the mean non-thermal linewidth, \(\sigma_{\text{los}}\), allow us to compare the relation between the kinematical disorder on the plane-of-the sky and along the line-of-sight  \citep{2011MNRAS.413..705L}.
-Considering the previous statements, the structure function is used as a tool to investigate the projection of a three-dimensional correlation function onto the plane of sky \citep{arthur2016turbulence}.
-
-We can consider as a main broadening mechanisms the kinematical disorder along the LOS related to velocity gradients by the clumpiness on the cloud and turbulent movements.
-On the plane-of-sky the consequences of those gradients and movements is measured in every pixel. 
-The spatial variations on the velocity field would depend on the targeted pixel, at the same time depending on the motions inside the cloud.
-This reasoning has lead to  propose a relationship between \(\sigma_{\text{los}}\) and \(\sigma\pos\) \citep{2011MNRAS.413..705L}.
-
-In the Figure~\ref{fig:los-vs-pos} that the line-of-sight velocity dispersion is roughly twice the plane-of-sky velocity dispersion.
-In the case of homogeneous turbulent velocity we can consider the effect of \textit{project smearing} \citep{1984ApJ...277..556S}, where the projection from three to two dimensions over the line-of-sight depth \(H\), reduces the plane-of-sky amplitude for the condition \(r_{0} < H\).
-With a value of \(\sigma\pos / \sigma_{\text{los}}\) = 0.5 we obtain \(r_{0} / H \sim\) 0.02 - 0.1.
-This procedure implies depths of the order 10 to 50 times the correlation length.
-In the lower limit \citet{arthur2016turbulence} mentioned the inconsistency for Orion since evidence has show that the emitting layer thickness is of the order of \num{0.01} - \SI{0.3}{pc}.
-For the most distant regions the previous analysis would give depths of the order of magnitude of the observational box, but considering the analysis using the power-law index (section~\ref{sec:power-index}) only NGC 595, which index is \num{1.36} would comply to this three dimensional structure.
-
-\begin{figure}
-\centering 
-\includegraphics[width=3in]{Figures/corr-los-vs-pos}
-\caption{The \(\sigma_{\text{pos}}\)-\(\sigma_{\text{los}}\) plane.
-The dotted line represents slope equal to unity and the dashed line represents a slope of two.
-The size of the markers represent the distance to each region.}
-\label{fig:los-vs-pos}
-\end{figure}
+In the following sections, the results shown previously are discussed and compared with the structure functions of previous investigations that analyzed \hii{} regions from our sample.
+We present the most important correlations between the turbulent parameters and the physical properties from the \hii{} region sample and finally an interpretation of the turbulent parameters is given.
+
+\subsection{Comparison with previous structure functions}
+
+In Section \ref{sec:methods-apply} we mentioned the model we propose for the structure function.
+Since this is the first time a model of this type is applied to a sample of HII regions, our results are bounded to be different from previous investigations, including the investigations that have the same observations as \citet{arthur2016turbulence} and \citet{Medina-Tanco:1997a,Melnick:2021x}.
+
+\citet{arthur2016turbulence} carried out a complete analysis by calculating the structure function of different emission lines in the inner Orion Nebula.
+They observed a tendency that higher ionization lines presents higher values on the magnitude dispersion and the steepness of the structure function slope. 
+Their results just consider one Gaussian component. 
+The power-law index obtained by \citet{arthur2016turbulence} are \(m \sim 1.2 \pm 0.1\) for \halpha\ and [OIII] emission lines and for [SII] they found \(m \sim 0.8 \pm 0.1\). 
+The correlation length for all lines is \SI{\approx 0.05}{pc}, value obtained when the structure function is equal to \(\sigma\pos^2\).
+For the same \halpha\ observation we obtained a value of \num{1.07} and a correlation length of \SI{0.068}{pc}. 
+Although the work of \citet{arthur2016turbulence} follows a different methodology, the values of \(r_0\) and \(\sigma\pos^2\) fall within the margin error.
+
+The first attempt at characterizing turbulence in a giant extragalactic HII region, GEHR, was done by \citet{1961MNRAS.122....1F} with the 30~Doradus complex, finding no indication of turbulent motions between scale of \num{10} and \SI{100}{pc}.
+\citet{Melnick:2021x} also investigated the structure function in 30 Doradus finding on their results that the structure function is entirely flat on scales from \num{3} to \SI{200}{pc}.
+The above does not coincide with our results, since we establish the existence of correlations up to the maximum value of the structure function that occurs at \SI{20}{pc}, separation where a value of 2\(\sigma\pos^2\) is reached.
+The VLT FLAMES/GIRAFFE observations of \citet{Melnick:2021x} may not have had the resolution to resolve the correlations at small separations, however an inspection of its velocity map (figure 7 in their work) shows that the velocity distribution it is far from completely random.
+This is the first time turbulence is characterized in 30~Doradus using the structure function.
+
+For NGC 604 there is good agreement in our structure function results and previous studies because where are using the same TAURUS-II data as \citet{Melnick:2021x} and \citet{Medina-Tanco:1997a}.
+Despite this general agreement the interpretations in each study is different.
+\citet{Medina-Tanco:1997a} conclude about a double regime acting on the kinetic energy spectrum.
+According to this double cascade, turbulence is being forced at scales of \(\approx\) \SI{10}{pc} while and energy cascade has developed down to the smallest scales and other, as an inverse cascade, extends up to scale of \(\approx\) \SI{70}{pc}.
+\citet{Medina-Tanco:1997a} mentioned different characteristic scale lengths, the most notorious is the \SI{\sim 10}{pc}, and they interpret it as possible source on energy associated with the expansion of shocks coming from wind bubbles.
+\citet{Melnick:2021x} addresses some issues with TAURUS II data while comparing profiles between the previous instrument TAURUS I where there exist a difference between observations (see section 4.1 on their paper).
+They mentioned that one problem with \citet{Medina-Tanco:1997a} structure function is that they didn't take into account the observational seeing.
+This would invalidate they results and \citet{Melnick:2021x} consider that taking out the structure function values that fall within this range would make the structure function flat at scales \(<\)\SI{10}{pc}, so they rule out \citet{Medina-Tanco:1997a} results.
+Finally they point out, and we agree, the importance of observing NGC 604 at higher spatial resolution. 
+Our Fig. \ref{fig:strucfunc-fit-ExtraGal}d shows in fact that there is a velocity structure in NGC 604. 
+None of the previous studies obtained a power-law index or correlation length for the structure function to compare our results.
+
+For our NGC 595 \halpha\ emission line results there is no correspondence in the structure function from the previous investigations of \citet{lagrois2009multi} and \citet{lagrois2011}.
+Our observations cover the brightest part of the region and have smaller resolution than theirs.
+As a consequence \citet{lagrois2009multi} and \citet{lagrois2011} structure functions results does not cover scales $<$10 pc, where in our results the correlation is taking place.
+One big difference is that \citet{lagrois2011} apply a  filter to the velocity field to get rid of non-turbulent movements.
+As a comparison for the filtered turbulent parameters they present a correlation length of \SI{43}{pc} and the power-law index they provide is \num{1.55 \pm 0.01}.
+Other difference in their methodology is that they use the normalized structure function value of 2\(\sigma\pos\) to obtain the correlation length.
+%Using their unfiltered data the correlation length is \(\sim\) \SI{90}{pc} and using the same criteria as our it is \(\sim\) \SI{40}{pc} and the slope would be shallower. 
+Their velocity centroid \(\sigma\) is \SI{5.92 \pm 0.15}{km.s^{-1}} while we have \SI{7.3\pm 2}{km. s^{-1}} which fall within the uncertainties.
+Due to the different observations and methodologies a direct comparison between structure functions is not possible.
 
@@
 %\citet{1981MNRAS.194..809L}
-In recent years, \citet{2012MNRAS.422.3339W} have found that clumps and \hii{} regions follow scaling relations over the range of z = 0-2 for \halpha\ size, velocity dispersion, luminosity and mass, finding \(\sigma \propto r^{0.42}\), \(\text{L}_{\text{H}_{\alpha}} \propto r^{2.72}\) and \(\text{L}_{\text{H}_{\alpha}} \propto \sigma^{4.18}\), respectively.
+In recent years, \citet{2012MNRAS.422.3339W} have found that clumps and \hii{} regions follow scaling relations over the range of z = 0-2 for the \halpha\ emission line with the size, velocity dispersion, luminosity and mass, finding \(\sigma \propto r^{0.42}\), \(\text{L}_{\text{H}_{\alpha}} \propto r^{2.72}\) and \(\text{L}_{\text{H}_{\alpha}} \propto \sigma^{4.18}\), respectively.
 This results imply that the same process are seen at high redshifts and the current epoch in star forming regions.
@@
 \includegraphics[width=3in]{Figures/corr-svsL}
-\caption{The log \(\sigma\pos\) - log $L(H_{\alpha})$ plane derived form our results an data in the literature. }
+\caption{The log \(\sigma\pos\) - log $L(H_{\alpha})$ plane derived form our results an data in the literature.
+The markers indicates galactic (triangles), Magellanic (squares) and extragalactic (circles) regions.
+}
 \label{fig:sigvsl}
@@
 
-\subsection{Comparison with previous structure functions}
-
-In Section \ref{sec:methods-apply} we mentioned the model we propose for the structure function.
-Since this is the first time a model of this type is applied to a sample of HII regions (at least for our knowledge), our results are bounded to be different from previous investigations, including the one that have the same observations as \citet{arthur2016turbulence} and \citet{Medina-Tanco:1997a,Melnick:2021x}.
-
-A complete analysis on different emissions lines of the structure function on Orion was carried out by \citet{arthur2016turbulence}. 
-They observed a tendency that higher ionization lines presents higher values on the magnitude dispersion and the steepness of the structure function slope. 
-This results just consider one component on the Gaussian fit. 
-The power-law index obtained by \citet{arthur2016turbulence} are \(m \sim 1.2 \pm 0.1\) for \halpha\ and [OIII] emission lines and for [SII] they found \(m \sim 0.8 \pm 0.1\). 
-The correlation length for all lines is \(\approx\) 0.05 pc. For the same \halpha\ observation we obtained a value of \num{1.07} and a correlation length of \SI{0.068}{pc}.
-
-The first attempt at characterizing turbulence in a giant extragalactic HII region, GEHR, was done by \citet{1961MNRAS.122....1F} with the 30 Doradus complex, finding no indication of turbulent motions between scale of 10 and 100 pc.
-These result is consistent with Fig. \ref{fig:strucfunc-fit-MC}a showing that the turbulent motions are correlated at scales \(<\) \SI{5}{pc}.
-\citet{Melnick:2021x} also investigated the structure function in 30 Doradus finding on their results that the structure function is entirely flat on scales from 3 to 200 pc.
-In the context of the high-resolution observations it is possible to see why their results do not reflect the turbulent structure of the nebula as their observations cover a region where the large-scale velocity fluctuations are uncorrelated as in the case of \citet{1961MNRAS.122....1F}.
-From the observations where are using this is the first time turbulence characterized in 30 Doradus using the structure function.
-
-For NGC 604 there is good agreement in our structure function results and previous studies because where are using the same TAURUS-II data as \citet{Melnick:2021x} and \citet{Medina-Tanco:1997a}.
-Despite this general agreement the interpretations in each study is different.
-\citet{Medina-Tanco:1997a} conclude about a double regime acting on the kinetic energy spectrum.
-According to this double cascade, turbulence is being forced at scales of \(\approx\) \SI{10}{pc} while and energy cascade has developed down to the smallest scales and other, as an inverse cascade, extends up to scale of \(\approx\) \SI{70}{pc}.
-\citet{Medina-Tanco:1997a} mentioned different characteristic scale lengths, the most notorious is the \SI{\sim 10}{pc}, and they interpret it as possible source on energy associated with the expansion of shocks coming from wind bubbles.
-\citet{Melnick:2021x} addresses some issues with TAURUS II data while comparing profiles between the previous instrument TAURUS I where there exist a difference between observations (see section 4.1 on their paper).
-They mentioned that one problem with \citet{Medina-Tanco:1997a} structure function is that they didn't take into account the observational seeing.
-This would invalidate they results and \citet{Melnick:2021x} consider that taking out the structure function values that fall within this range would make the structure function flat at scales \(<\)\SI{10}{pc}, so they rule out \citet{Medina-Tanco:1997a} results.
-Finally they point out, and we agree, the importance of observing NGC 604 at higher spatial resolution. 
-Our Fig. \ref{fig:strucfunc-fit-ExtraGal}d shows in fact that there is a velocity structure in NGC 604. 
-None of the previous studies present a power-law index for the structure function to compare our results.
-
-For our NGC 595 \halpha\ emission line results there is no correspondence in the structure function from the previous investigations of \citet{lagrois2009multi} and \citet{lagrois2011}.
-Our observations cover the brightest part of the region and have smaller resolution than theirs.
-As a consequence \citet{lagrois2009multi} and \citet{lagrois2011} structure functions results does not cover scales $<$10 pc, where in our results the correlation is taking place.
-One big difference is that \citet{lagrois2011} apply a  filter to the velocity field to get rid of non-turbulent movements.
-As a comparison for the filtered turbulent parameters they present a correlation length of \SI{43}{pc} and the power-law index they provide is \num{1.55 \pm 0.01}.
-Other difference in their methodology is that they use the normalized structure function value of 2\(\sigma\pos\) to obtain the correlation length.
-%Using their unfiltered data the correlation length is \(\sim\) \SI{90}{pc} and using the same criteria as our it is \(\sim\) \SI{40}{pc} and the slope would be shallower. 
-Their velocity centroid \(\sigma\) is \SI{5.92 \pm 0.15}{km.s^{-1}} while we have \SI{7.3\pm 2}{km. s^{-1}} which fall within the uncertainties.
-Due to the different observations and methodologies a direct comparison between structure functions is not possible.
-
-\subsection{Final remarks}
+\subsection{Relationship between plane-of-sky and line-of-sight velocity dispersion}\label{sec:sigmapos-vs-sigmalos}
+
+As a justification for the use of the structure function we can consider that any relation between the line width and line-of-sight depth can be interpreted in terms of a correlation between velocity spread and scale size.
+If we have an optically thin spectral line where it will have a width which is related to the total radial velocity dispersion of all fluctuations sampled along the line-of-sight \citep{1984ApJ...277..556S}.
+The standard deviation of the velocity centroid, \(\sigma\pos\), and the mean non-thermal linewidth, \(\sigma_{\text{los}}\), allow us to compare the relation between the kinematical disorder on the plane-of-the sky and along the line-of-sight  \citep{2011MNRAS.413..705L}.
+Considering the previous statements, the structure function is used as a tool to investigate the projection of a three-dimensional correlation function onto the plane of sky \citep{arthur2016turbulence}.
+
+We can consider as a main broadening mechanisms the kinematical disorder along the LOS related to velocity gradients by the clumpiness on the cloud and turbulent movements.
+On the plane-of-sky the consequences of those gradients and movements is measured in every pixel. 
+The spatial variations on the velocity field would depend on the targeted pixel, at the same time depending on the motions inside the cloud.
+This reasoning has lead to  propose a relationship between \(\sigma_{\text{los}}\) and \(\sigma\pos\) \citep{2011MNRAS.413..705L}.
+
+In the Figure~\ref{fig:los-vs-pos} that the line-of-sight velocity dispersion is roughly twice the plane-of-sky velocity dispersion.
+In the case of homogeneous turbulent velocity we can consider the effect of \textit{project smearing} \citep{1984ApJ...277..556S}, where the projection from three to two dimensions over the line-of-sight depth \(H\), reduces the plane-of-sky amplitude for the condition \(r_{0} < H\).
+With a value of \(\sigma\pos / \sigma_{\text{los}}\) = 0.5 we obtain \(r_{0} / H \sim\) 0.02 - 0.1.
+This procedure implies depths of the order 10 to 50 times the correlation length.
+In the lower limit \citet{arthur2016turbulence} mentioned the inconsistency for Orion since evidence has show that the emitting layer thickness is of the order of \num{0.01} - \SI{0.3}{pc}.
+For the most distant regions the previous analysis would give depths of the order of magnitude of the observational box, but considering the analysis using the power-law index (section~\ref{sec:power-index}) only NGC 595, which index is \num{1.36} would comply to this three dimensional structure.
+
+\begin{figure}
+\centering 
+\includegraphics[width=3in]{Figures/corr-los-vs-pos}
+\caption{The \(\sigma_{\text{pos}}\)-\(\sigma_{\text{los}}\) plane. The dotted line represents slope equal to unity and the dashed line represents a slope of two.}
+\label{fig:los-vs-pos}
+\end{figure}
+
+\subsection{Interpretation of the turbulent parameters}\label{sec:interpretation-parameters}
+
+\subsubsection{Correlation length \(r_0\)}
+
+Ideally the correlation length \(r_0\) should represent the scale of dominant energy injection.
+It is unclear what are the precise mechanisms driving the turbulence in \hii{} regions, thought a lot of options are candidates.
+The most probable scenario is that the velocity fluctuations are consequence of the combination of various mechanism.
+There are several energy sources that could provide or contribute  to the energy required: of the order of kpc, the differential rotations of the galaxy that produces shear at large scale, at scales of the order of hundreds of pc, supernova explosions inject a large amount of kinetic energy.
+At scales of several tens of pc the expansion of \hii{} regions and stellar winds are a source of energy and, bipolar flows, shocks, jets and champagne flows inject energy at small scales about one tenth of a pc.
+Many of these mechanisms, at some extent, affect all the \hii{} regions studied in this work.
+We can use the kinematic analysis of the regions to investigate how previously identified energy injection mechanisms could be related to the correlation length.
+
+\citet{2009AJ....137..367O} present a three-dimensional study of the dynamic structure of the Orion nebula.
+The high-velocity stellar wind from \(\theta^1\) Ori C will confine the ionized gas, even the high ionization emission lines, to a thick shell.
+In one direction, at a distance of \SI{0.1}{pc} from the ionizing massive star a stationary shell of shocked material is formed when the ram pressure of the photoevaportation flow balances the thermal pressure of the shocked wind.
+In the other direction there is a free flow of the hypersonic wind.
+At a smaller scale of \SI{0.02}{pc} there is an interaction between the closest proplyd photoevaporation flow and the stellar wind which results in bowshocks.
+According to \citet{2001ApJ...561..830G} the influence of stellar wind interactions is restricted to the central \SI{0.05}{pc}. 
+Orion also present a champagne flow where the photoionized gas streams away from the ionization front covering a distance of \SI{\sim 1}{pc} from the molecular cloud \citep{1973ApJ...183..863Z}.
+
+Our correlation length results for the Orion Core and EON from table~\ref{tab:Res}, \num{0.068} y \SI{0.39}{pc} respectively, despite been of the order of the scales mentioned above still aren't conclusive enough to determine a direct relation between them.
+As mentioned in \citet{arthur2016turbulence} the mechanism mentioned in the previous paragraph would play a secondary role in stirring up the gas motions and it would be necessary to specify if the velocity fluctuations arise from pure turbulent motion inside the ionized clouds or a consequences of density and brightness fluctuations.
+
+\citet{sabalisck1995supersonic} studied NGC 604 revealing that the high emission knots on the region encompasses supersonic global velocity dispersion values of 14 $<$ \(\sigma_{\text{los}}\) $<$ \SI{20}{km.s^{-1}}.
+This knots have a characteristic radius of \(\sim\)\SI{7}{pc} and a Gaussian profile.
+Values of velocity dispersion $>$\SI{20}{km.s^{-1}} are found in low emission cavities where the lines present strong asymmetries.
+These cavities were identified as expanding shells by \cite{yang1996} with diameters of \(\sim\)\SI{40}{pc} and a expansion velocity above \SI{50}{km.s^{-1}}.
+According to table~\ref{tab:Res} the correlation length for NGC 604 is close to the scale of the bright knots in the region which aren't related to a particular energy injection mechanism.
+
+Although the Orion core, the EON, and NGC 604 have different \(r_0\) is not clear if it truly reveal a concrete aspect of the energy input mechanism mentioned above.
+Orion main energy input comes from one star, meanwhile NGC 604 has more than 200 OB stars including WR stars. 
+The Orion core also presents Herbig-Haro objects, which aren't possible to resolve for more distant regions.
+Though the correlation length is particular to each region, and it is correlated mainly with the size (see section~\ref{sec:scaling-relations}), it still needs further studies to reveal the true implication of this value with respect the energy input mechanisms.
+
+\subsubsection{Structure function power-law index \(m\)}\label{sec:power-index}
+
+The index \(m\) shown in the last column of Table \ref{tab:Res} is used for comparison between observations and the theoretical value of 0.67.
+All our indices are above this theoretical value and this is attributed to the fact that the \hii{} regions do not comply with the assumptions established in the development of the turbulent theory.
+
+From section~\ref{sec:regions-milky-way} we know that most of all assumption mentioned in the theory of turbulence are not meet for our \hii{} region sample.
+\hii{} regions emerged from a molecular cloud with highly filamentary and clumpy density structure .
+There is a large increase in the temperature because of the photoionization, and the density gradients with the pressure gradients accelerate the flow which occurs on multiple scales consequence of the fractal nature of the molecular cloud \citep{arthur2016turbulence}.
+The radiation pressure, stellar winds and region expansion, among other physical processes would create pressure-driven shock waves propagating faster than the speed of sound in the medium.
+This would make the flow compressible and supersonic in \hii{} regions.
+Also, as \hii{} regions are three-dimensional objects our structure function results comes from a projection of this three-dimensional structure to a two-dimensional velocity field.
+But despite the complex nature of \hii{} regions and observational limitations we obtain a common pattern for the structure function and the value of the power-law index falls in a certain limited range of values.
+The differences in the power-law index with respect the theoretical value are often used as a diagnostic tools to identify properties that are not consider in the assumptions of the turbulence theory.
+
+To study the projection of a three-dimensional structure function to a two-dimensional structure function, known as projection smoothing \citep{von1951methode, munch1958internal,1964SvA.....8..210K,1987ApJ...317..686O}, relationships between the power-law indices were proposed:
+
+\begin{equation}\label{eq:projection-smoothing-3d}
+m_{2D}= m_{3D} + 1
+\end{equation}
+%
+and  when the astronomical object present a sheet-like distribution of emitters we have the relation:
+%
+\begin{equation}\label{eq:projection-smoothing-2d}
+m_{2D} \sim m_{3D}
+\end{equation}
+
+As a conclusion, if the extension of the HII region is compared with its depth (three-dimensional case) the value of the index is \num{1.67}. 
+While the case where the extension is much greater than its depth (two-dimensional case) the region will have a value of \num{0.6}.
+From Table~\ref{tab:Res} we see that our results fall between these two previous values.
+
+The mean value \(m\) of our sample is \num{\sim 1}. 
+Following the equation \ref{eq:projection-smoothing-3d} the \hii{} regions in our sample with \(m >\) 1 would present a depth which is in the order of magnitude comparable to the length of the observed box size \(L\) been closest to this value as \(m\) tends to 1.6.
+On the other hand, \hii{} regions with values \(m <\) 1 would present a thinner structure as they tend to the value of 0.6.
+This analysis should not be regarded as conclusive about the true structure of the regions and would require further observations with a combination of kinematics analysis to determine the best way to determine the depth of each region.
+As we show in section \ref{sec:sigmapos-vs-sigmalos} the ratio between \(\sigma\pos\) and \(\sigma_{\text{los}}\) can also be used to give an idea of the depth o the region.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Conclusions}\label{sec:conclusions}
 
@@
 However, the circumstantial evidence in favor of the existence of turbulent motions in \hii{} regions is overwhelming, and many are the potential sources of energy to create and maintain turbulence during the lifetime of an \hii{} region.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Conclusions}\label{sec:conclusions}
-
-%a single inertial scale where the ionized gas behavior can be described by means of a power law.
 
@@
 
-The 30 Doradus (Tarantula Nebula) nebula is located at a distance of 49.9 kpc \citetext{\SI{1}{\arcsecond} = \SI{0.24}{pc} ; \citealp{2013Natur.495...76P}}.
+The 30 Doradus (Tarantula Nebula) nebula is located at a distance of \SI{49.9}{kpc} \citetext{\SI{1}{\arcsecond} = \SI{0.24}{pc} ; \citealp{2013Natur.495...76P}}.
 It is a luminous star-forming region in the LMC (Large Magellanic Cloud) and is the most luminous complex in the Local Group \citep{1984ApJ...287..116K}.
-The central ionized region spans for 40 pc and host the massive, dense star cluster R136 %\citep{1991IAUS..148..145W}. %Note: check the bibliographic format
+The central ionized region spans for \SI{40}{pc} and host the massive, dense star cluster R136 %\citep{1991IAUS..148..145W}. %Note: check the bibliographic format
 The ionizing output \(Q_0\) of R136 is \SI{e51.4}{photons.s^{-1}} \citep{2020MNRAS.499.1918B}.
@@
 To quantify the impact of these considerations on the final structure function, we perform a series of experiments using artificial turbulent velocity maps.
-In particular, our interest is to quantify how this observational limitations affect the determination of parameters such as the correlation length, \(r_0\), and the velocity field variance, \(\sigma^2 \).
-
-The artificial velocity maps are created using a modified version of the \textit{make$\_$extend} command from the \textit{turbustat} package \citep{Koch2019AJ....158....1K}.
+In particular, our interest is to quantify how this observational limitations affect the determination of parameters such as the correlation length, \(r_0\), and the velocity field variance, \(\sigma\pos^2 \).
+
+The artificial velocity maps are created using a modified version of the \textit{make$\_$extend} command from the \texttt{turbustat} Python library \citep{Koch2019AJ....158....1K}.
 We create a turbulent velocity field that follows a given power law with and a proposed correlation length, and a variance value indicated as true \(\sigma^2\).
 Using this true \(\sigma^2\) we obtained the true \(r_0\), and these values are used as a reference in the following experiments to quantify the variations.
-The objective is to create a sample of multiple divided maps with different seeing width to compute the structure function in each and characterize the variations.
+The objective is to create a sample of multiple divided maps with different seeing width and size to compute the structure function in each and characterize the variations.
 
@@
     Colored dots show mean results from different simulated velocity fields,
-    with varied power law slopes.
+    with different power law slopes.
     Colored shading shows the inter-quartile range over the different sub-images.
@@
 The structure function is calculated for each division and later we average all the divisions of the corresponding map. 
-
 The Figure \ref{fig:finite-box}b shows in solid lines the normalized averaged structure functions for the maps in Figure \ref{fig:finite-box}a.
@@
 The shaded areas show the deviation that each average structure function has due to the different divisions. 
-\textit{(Note: I modified the Figure adding \(\sigma^2\) and \(r_0\) for each SF since I think it is easier and more directly to grasp the effect of reducing the box size.
+%\textit{(Note: I modified the Figure adding \(\sigma^2\) and \(r_0\) for each SF since I think it is easier and more directly to grasp the effect of reducing the box size.
 The figure is more 'noisy' but if it seems like it contribute to nothing we can change it back.)}
@@
 
-Figure \ref{fig:finite-box-effect} shows the ratio of the correlation length of each averaged map with respect to the true correlation length, \(\text{apparent } r_ 0 /\text{true } r_0 \), as well as the ratio between the averaged variance of each divided map and the true variance, \(\text{apparent } \sigma^2  / \text{true } \sigma^2\).
-We observe that for the values where \(L\), is 20 $> r_0 $ the change in the ratios is null.
-It is for the values where \( L < 10 r_0 \) a considerable decrease in both ratios is observed.
-This behavior is fulfilled for all simulated maps with different power law in the velocity spectrum and different correlation functions, indicated with different colored circles in Figure \ref{fig:finite-box-effect}.
-These variations of the ratios are used to characterize the effect that the decrease of the observational box size has in \(r_0\) and \(\sigma^2\).
-
-The fitted dashed line in Figure \ref{fig:finite-box-effect} is given by the equation:
+Figure \ref{fig:finite-box-effect}a shows the empirical ratios of the correlation length of each averaged map with respect to the true correlation length (\(\text{apparent } r_ 0 /\text{true } r_0 \) ), as well as the ratio between the averaged variance of each divided map and the true variance (\(\text{apparent } \sigma^2  / \text{true } \sigma^2\)).
+We observe that for the values where \(L> 20r_0 \) the change in the ratios is null.
+It is for the values where \( L < 10 r_0 \) where we found a decrease on both ratios.
+On the other hand, Figure \ref{fig:finite-box-effect}b shows the model-derived \(r_0\) and \(\sigma^ 2 \) values using the fitting procedure with the \texttt{lmfit} library.
+In this case we see that the model fitting works much better than the empirical measurement, which gives reliable values so long \(L > 3r_0 \)
+This behavior is fulfilled for all simulated maps with different power law in the velocity spectrum and  indicated with different colored circles in Figure \ref{fig:finite-box-effect}ab.
+The empirical variations of the ratios is described by the  dashed line in Figure \ref{fig:finite-box-effect}ab given by the equation:
 
@@
 \end{equation}
-%
-and it is used in the functional form that fits the observational structure function when adjusting the results to obtain the reported parameters \(r_0\) and \(\sigma^2 \).
 
@@
 The artificial velocity maps are created in the same way as to study the effect of the observational box.
-Seeing in velocity maps is added via the \textit{astropy} package using the \textit{Gaussian2DKernel} command.
+Seeing in velocity maps is added via the \texttt{astropy} Python library \citep{astropy:2013} using the \textit{Gaussian2DKernel} command.
 

### 2022-05-27 strucfunc_paper.tex
Compare with precious studies of Lagoon strucfunc

@@
 
+The structure function of the Lagoon Nebula was previously
+studied by \citet{Chakraborty:1999a} using the [\ion{O}{3}] \Wav{5007} line,
+finding an approximate power law behavior (\(m = 0.46\))
+on scales of \num{0.01} to \SI{0.2}{pc}.
+No flattening of the structure function at the largest scales
+was seen,
+but that is to be expected due to the finite box effect
+(see Appendix~\ref{sec:finite-box-effects})
+given that we determine the correlation length to be \(r_0 \approx   \SI{1}{pc}\) for this nebula,
+which is several times larger than the region mapped by \citet{Chakraborty:1999a}.
+On the other hand, the magnitude of the velocity dispersion found by these authors much larger than we measure.
+For instance, they find \(B(r) = \SI{278}{km^2.s^{-1}}\) at \SI{0.2}{pc}, whereas we find \(B(r) \approx \SI{2}{km^2.s^{-1}}\) at the same scale, which corresponds to a discrepancy of more than a factor of a hundred in \(\sigma^2\pos\).
+This may be due in part to the fact that \citet{Chakraborty:1999a}
+observed a small and atypical part of the nebula known as the
+Hourglass region, which includes a cluster of very young stars
+\citep{Arias:2006e}.
+
 The first attempt at characterizing turbulence in a giant extragalactic HII region, GEHR, was done by \citet{1961MNRAS.122....1F} with the 30~Doradus complex, finding no indication of turbulent motions between scale of \num{10} and \SI{100}{pc}.

### 2022-06-16 strucfunc_paper.tex
Add sentence on M8 literature comparison

@@
 which is several times larger than the region mapped by \citet{Chakraborty:1999a}.
-On the other hand, the magnitude of the velocity dispersion found by these authors much larger than we measure.
-For instance, they find \(B(r) = \SI{278}{km^2.s^{-1}}\) at \SI{0.2}{pc}, whereas we find \(B(r) \approx \SI{2}{km^2.s^{-1}}\) at the same scale, which corresponds to a discrepancy of more than a factor of a hundred in \(\sigma^2\pos\).
+On the other hand, the magnitude of the velocity dispersion found by these authors greatly exceeds our own measurements.
+For instance, they find \(B(r) = \SI{278}{km^2.s^{-2}}\) at \SI{0.2}{pc}, whereas we find \(B(r) \approx \SI{2}{km^2.s^{-2}}\) at the same scale, which corresponds to a discrepancy of more than a factor of a hundred in \(\sigma^2\pos\).
 This may be due in part to the fact that \citet{Chakraborty:1999a}
@@
 \citep{Arias:2006e}. 
+In the case of the Orion Nebula we found that the velocity dispersion
+of the central region was larger than that of the extended nebula
+and this could be an example of a similar phenomenon,
+albeit to a more extreme degree.
 

### 2022-06-19 strucfunc_paper.tex
Major reorganization of the comparison with previous studies
Descriptions of individual objects are now moved to the appendix

@@
 so long as \(L > 3\, r_0\).
-This is a significant improvement over than direct empirical measurement,
+This is a significant improvement over direct empirical measurement,
 which requires \(L > 10\, r_0\) in order to be accurate
@@
 
-In Section \ref{sec:methods-apply} we mentioned the model we propose for the structure function.
-Since this is the first time a model of this type is applied to a sample of HII regions, our results are bounded to be different from previous investigations, including the investigations that have the same observations as \citet{arthur2016turbulence} and \citet{Medina-Tanco:1997a,Melnick:2021x}.
-
-\citet{arthur2016turbulence} carried out a complete analysis by calculating the structure function of different emission lines in the inner Orion Nebula.
-They observed a tendency that higher ionization lines presents higher values on the magnitude dispersion and the steepness of the structure function slope. 
-Their results just consider one Gaussian component. 
-The power-law index obtained by \citet{arthur2016turbulence} are \(m \sim 1.2 \pm 0.1\) for \halpha\ and [OIII] emission lines and for [SII] they found \(m \sim 0.8 \pm 0.1\). 
-The correlation length for all lines is \SI{\approx 0.05}{pc}, value obtained when the structure function is equal to \(\sigma\pos^2\).
-For the same \halpha\ observation we obtained a value of \num{1.07} and a correlation length of \SI{0.068}{pc}. 
-Although the work of \citet{arthur2016turbulence} follows a different methodology, the values of \(r_0\) and \(\sigma\pos^2\) fall within the margin error.
-
-The structure function of the Lagoon Nebula was previously
-studied by \citet{Chakraborty:1999a} using the [\ion{O}{3}] \Wav{5007} line,
-finding an approximate power law behavior (\(m = 0.46\))
-on scales of \num{0.01} to \SI{0.2}{pc}.
-No flattening of the structure function at the largest scales
-was seen,
-but that is to be expected due to the finite box effect
-(see Appendix~\ref{sec:finite-box-effects})
-given that we determine the correlation length to be \(r_0 \approx   \SI{1}{pc}\) for this nebula,
-which is several times larger than the region mapped by \citet{Chakraborty:1999a}.
-On the other hand, the magnitude of the velocity dispersion found by these authors greatly exceeds our own measurements.
-For instance, they find \(B(r) = \SI{278}{km^2.s^{-2}}\) at \SI{0.2}{pc}, whereas we find \(B(r) \approx \SI{2}{km^2.s^{-2}}\) at the same scale, which corresponds to a discrepancy of more than a factor of a hundred in \(\sigma^2\pos\).
-This may be due in part to the fact that \citet{Chakraborty:1999a}
-observed a small and atypical part of the nebula known as the
-Hourglass region, which includes a cluster of very young stars
-\citep{Arias:2006e}. 
-In the case of the Orion Nebula we found that the velocity dispersion
-of the central region was larger than that of the extended nebula
-and this could be an example of a similar phenomenon,
-albeit to a more extreme degree.
-
-The first attempt at characterizing turbulence in a giant extragalactic HII region, GEHR, was done by \citet{1961MNRAS.122....1F} with the 30~Doradus complex, finding no indication of turbulent motions between scale of \num{10} and \SI{100}{pc}.
-\citet{Melnick:2021x} also investigated the structure function in 30 Doradus finding on their results that the structure function is entirely flat on scales from \num{3} to \SI{200}{pc}.
-The above does not coincide with our results, since we establish the existence of correlations up to the maximum value of the structure function that occurs at \SI{20}{pc}, separation where a value of 2\(\sigma\pos^2\) is reached.
-The VLT FLAMES/GIRAFFE observations of \citet{Melnick:2021x} may not have had the resolution to resolve the correlations at small separations, however an inspection of its velocity map (figure 7 in their work) shows that the velocity distribution it is far from completely random.
-This is the first time turbulence is characterized in 30~Doradus using the structure function.
-
-For NGC 604 there is good agreement in our structure function results and previous studies because where are using the same TAURUS-II data as \citet{Melnick:2021x} and \citet{Medina-Tanco:1997a}.
-Despite this general agreement the interpretations in each study is different.
-\citet{Medina-Tanco:1997a} conclude about a double regime acting on the kinetic energy spectrum.
-According to this double cascade, turbulence is being forced at scales of \(\approx\) \SI{10}{pc} while and energy cascade has developed down to the smallest scales and other, as an inverse cascade, extends up to scale of \(\approx\) \SI{70}{pc}.
-\citet{Medina-Tanco:1997a} mentioned different characteristic scale lengths, the most notorious is the \SI{\sim 10}{pc}, and they interpret it as possible source on energy associated with the expansion of shocks coming from wind bubbles.
-\citet{Melnick:2021x} addresses some issues with TAURUS II data while comparing profiles between the previous instrument TAURUS I where there exist a difference between observations (see section 4.1 on their paper).
-They mentioned that one problem with \citet{Medina-Tanco:1997a} structure function is that they didn't take into account the observational seeing.
-This would invalidate they results and \citet{Melnick:2021x} consider that taking out the structure function values that fall within this range would make the structure function flat at scales \(<\)\SI{10}{pc}, so they rule out \citet{Medina-Tanco:1997a} results.
-Finally they point out, and we agree, the importance of observing NGC 604 at higher spatial resolution. 
-Our Fig. \ref{fig:strucfunc-fit-ExtraGal}d shows in fact that there is a velocity structure in NGC 604. 
-None of the previous studies obtained a power-law index or correlation length for the structure function to compare our results.
-
-For our NGC 595 \halpha\ emission line results there is no correspondence in the structure function from the previous investigations of \citet{lagrois2009multi} and \citet{lagrois2011}.
-Our observations cover the brightest part of the region and have smaller resolution than theirs.
-As a consequence \citet{lagrois2009multi} and \citet{lagrois2011} structure functions results does not cover scales $<$10 pc, where in our results the correlation is taking place.
-One big difference is that \citet{lagrois2011} apply a  filter to the velocity field to get rid of non-turbulent movements.
-As a comparison for the filtered turbulent parameters they present a correlation length of \SI{43}{pc} and the power-law index they provide is \num{1.55 \pm 0.01}.
-Other difference in their methodology is that they use the normalized structure function value of 2\(\sigma\pos\) to obtain the correlation length.
-%Using their unfiltered data the correlation length is \(\sim\) \SI{90}{pc} and using the same criteria as our it is \(\sim\) \SI{40}{pc} and the slope would be shallower. 
-Their velocity centroid \(\sigma\) is \SI{5.92 \pm 0.15}{km.s^{-1}} while we have \SI{7.3\pm 2}{km. s^{-1}} which fall within the uncertainties.
-Due to the different observations and methodologies a direct comparison between structure functions is not possible.
+Comparison with prior studies is complicated by the
+diversity of methodologies that  have been employed.
+There is almost universal agreement on how to measure
+the velocity variance \(\sigma^2\pos\),
+although even here there can be small differences according
+to whether the centroid velocities come from gaussian fitting
+or velocity moments,
+and whether or not smooth large-scale trends are first removed.
+\citet{arthur2016turbulence} compared multiple studies of the
+inner Orion Nebula, finding agreement to within 20\%
+in \(\sigma^2\pos\) determinations
+for emission lines that trace the bulk of the fully ionized gas.
+
+There is less agreement in the literature on the best way
+define the correlation length, \(r_0\).
+Our own definition corresponds to the lag where the autocorrelation function
+has fallen to a value of one-half,
+\(C(r_0) = 1/2\) (see section~\ref{sec:methods-apply}),
+whereas other common choices are \(C(r) = e^{-1}\)
+\citep{Mivi1995}
+or the \textit{total decorrelation lag} \(\tau_0\) \citep{lagrois2011},
+which corresponds to \(C(\tau_0) = 0\).
+One disadvantage of this latter definition is that it
+can be sensitive to non-homogeneous behavior of the
+velocity field at large scales. 
+The conversion between these different conventions will also depend
+on the value of the power-law slope,
+but we typically find that \(\tau_0 / r_0 = \num{2}\) to \num{3}.
+
+The power law slope, \(m\), itself is probably the parameter that
+is most sensitive to methodological assumptions.
+The fundamental issue is that the observed structure function tends to
+show a negative curvature in log-log space at intermediate scales:
+\(d\log B/ d\log r < 0\).
+This is caused primarily by the steepening due to seeing at small scales
+together with the natural asymptotic flattening, 
+\(B(r) \to 2 \sigma^2\pos\), at large scales.
+As a result, the measured slope depends on the exact range of
+separations over which the power law is fitted.
+So long as the spatial dynamic range of the observations is high enough,
+then a reliable slope can nevertheless be obtained,
+as shown by \citet{arthur2016turbulence} for the case of the Orion Nebula.
+However, this requires that \(r_0\) should be at least an order of
+magnitude higher than the larger of the seeing width
+or the minimum separation between spatial points.
+This condition is not satisfied for roughly half of our sample regions,
+and the same is true for many previous studies.
+In such cases, our model-based approach is a more reliable way of
+determining the slope.
+
+% The diversity of methodologies used in prior studies 
+% In Section \ref{sec:methods-apply} we mentioned the model we propose for the structure function.
+% Since this is the first time a model of this type is applied to a sample of HII regions, our results are bounded to be different from previous investigations, including the investigations that have the same observations as \citet{arthur2016turbulence} and \citet{Medina-Tanco:1997a,Melnick:2021x}.
+
+SUMMARISE COMPARISONS DESCRIBED IN APPENDIX.
 
@@
 \appendix
-
-\section{\boldmath Notes on individual \hii{} regions}
-\label{sec:notes-individual-hii}
-For each region or pair of regions in our sample,
-we give a more description of its physical properties
-(supplementing section~\ref{sec:regions-milky-way})
-together with additional details of the structure function
-(supplementing section~\ref{sec:results}).
-
-%the model fit to
-
-\subsection{Orion Nebula}
-\label{sec:orion-nebula}
-
-The Orion Nebula (M42) is the prototype of a galactic HII region located at a distance of 440 pc \citetext{\SI{1}{\arcsecond} = \SI{0.002}{pc} ; \citealp{2008AJ....136.1566O}}.
-The O7 V star \(\theta^{1}\) Ori C is the most luminous and hottest star \citep{2006A&A...448..351S} with an ionizing flux \(Q_0\) of  \SI{e49.12}{photons.s^{-1}}. 
-With other 3 B-type stars they form the Trapezium cluster.
-The bright region that surrounds these massive ionizing stars is called the the Huygens region (Orion core henceforth).
-In the southwest direction of the Huygens region there is a drop in the brightness as one approach a much larger region called Extended Orion Nebula \citetext{EON henceforth;  \citealp{2008Sci...319..309G}}
-The position of Orion near the side of the Orion Molecular Cloud (OMC-1) make it an ongoing star formation with a large population of young star, some of which are the sources of stellar jets and Herbig-Haro objects \citep{1993ApJ...410..696O}.
-Its physical properties and kinematics, along its stellar population are documented in \citet{2001ARA&A..39...99O}.
-
-Figure~\ref{fig:strucfunc-fit-Galactic}a shows the structure function of the Orion core.
-In this case we merge the first three points of the structure function.
-%From \SI{0.002}{pc} until \SI{0.003}{pc} all points fall below the true model showing that they are affected by the seeing. 
-%The correlation length for the Orion core is \SI{0.07}{pc}, it has a \(\sigma^2\pos\) of \SI{12}{km^{2}.s^{-2}} and an index of \num{1.07}.
-The structure function of the Orion core behaves accordingly to the tapered case of inhomogeneous fluctuations (see Figure~\ref{fig:model-strucfunc}b).
-At \SI{0.25}{pc} there is a plateau around \SI{22}{km^{2}.s^{-2}}.
-Above separations of \SI{0.3}{pc} the structure function decays to a value of \SI{7}{km^{2}.s^{-2}} at  \SI{0.5}{pc}.
-
-\subsection{Lagoon Nebula}
-\label{sec:lagoon-nebula}
-
-The Lagoon Nebula (M8, NGC6523) is located at a distance of 1 250 pc \citetext{\SI{1}{\arcsecond} = \SI{0.006}{pc} ; \citealp{2005A&A...430..941P}}.
-It has a luminosity in \ha{} of \SI{e37.47}{erg.s^{-1}}\citep{1984ApJ...287..116K}.
-It contains the young stellar cluster NGC6530 and the region is illuminated by different massive stars of spectral types O and B, the hottest being 9 Sgr, type O4V \citep{Damiani:2017b}.
-Optically, the brightest part of the nebula is called 'Hourglass nebula' which surrounds and obscures the O7 star Herschel 36 \citep{1986AJ.....91..870W}. 
-The velocity field shows several expanding shells, related to the stellar population, and the massive protostar M8East-IR \citep{1984ApJ...278..170S} indicating that recent star formation. 
-A blueshifted, neutral layer is also in very good agreement with predictions of champagne-flow models of blister HII regions \citep{Damiani:2017b}. 
-The properties of the nebula are reviewed by \citet{2008hsf2.book..533T}.
-
-The Figure~\ref{fig:strucfunc-fit-Galactic}c shows the structure function of the Lagoon nebula.
-%There aren't any points affected by the seeing which has a value of \SI{0.006}{pc} (\(s_0\)=\SI{1}{\arcsecond}).
-In this case we merge the first two points.
-The Lagoon nebula presents a non-uniform behavior below the correlation length but it is possible to see the characteristic ascending values of the structure function.
-%The turbulent parameters that fits our model are a \(r_0\) of \SI{1}{pc}, a \(\sigma^2\pos\) of \SI{7}{km^{2}.s^{-2}} and an index of \num{1.17}.
-At large scales there is an indication of some periodic behavior followed by ascending \(B(r)\) values at largest separation.
-A value of\(B(r)\) of order 2\(\sigma^2\pos\) is \(\sim\)\SI{14}{km^{2}.s^{-2}} at a separation of \(\sim\)\SI{2.5}{pc}. 
-Then there is a diminution at \SI{4.5}{pc} down to a value of \SI{11}{km^{2}.s^{-2}}.
-From this point the structure function ascends until it reaches \SI{66}{km^{2}.s^{-2}} around \SI{20}{pc}.
-
-\subsection{Carina Nebula}
-\label{sec:carina-nebula}
-
-The Carina nebula is a large star-forming complex located at a distance of 2 350 pc \citetext{\SI{1}{\arcsecond} = \SI{0.01}{pc} ; \citealp{2006ApJ...644.1151S}}.
-Using the \ha{} luminosity as a diagnostic of the ionizing flux \(Q_0\) \citet{2007MNRAS.379.1279S} measured a value of \SI{e50.47}{photons.s^{-1}}.
-Young clusters like Trumpler 14 and 16, and Collinder 228 form the Car OB1 association, one of the largest OB associations on the Galaxy.
-This OB association has more than 65 stars earlier than B0, and several Wolf-Rayet (WR) stars.
-The most luminous star is the blue variable $\eta$ Car.
-As a star formation region, it presents several phenomena related with young stars as evaporating protoplanetary discs, erosion of large dust pillars and the triggering of a second generation of embedded stars and Herbig-Haro objects, to mention some \citetext{see \citealp{2008hsf2.book..138S} and reference therein}.
-This region can be consider as a bridge between the detailed star-formation regions like Orion, and much more distant regions like 30 Doradus.
-
-(The Figure~\ref{fig:strucfunc-fit-Galactic}d shows the structure function of the Carina nebula.
-%The seeing is \SI{0.008}{pc} (\(s_0\)=\SI{1.3}{\arcsecond}) and there are just a couple of points that lie below the true model, indicating that the majority of points isn't affected by the seeing.
-For this region we merge the first two points of the structure function.
-As the Lagoon nebula, Carina also shows a non-uniform behavior below the correlation length.
-%The correlation length is \SI{0.56}{pc} pc at a \(\sigma^2\pos\) of \SI{18}{km^{2}.s^{-2}} and an index of \num{1.14}.
-At larges scales the structure function of the Carina nebula follows a pattern that resembles the homogeneous fluctuation of Figure~\ref{fig:model-strucfunc}a.
-The structure function reaches a plateau around \SI{36}{km^{2}.s^{-2}} at \(\sim\) \SI{2}{pc}.
-When \(r >\)\SI{6}{pc} the structure functions shows a small amplitude periodic pattern around 2\(\sigma^2\pos\).
-
-\subsection{30 Doradus}
-\label{sec:30-doradus}
-
-The 30 Doradus (Tarantula Nebula) nebula is located at a distance of \SI{49.9}{kpc} \citetext{\SI{1}{\arcsecond} = \SI{0.24}{pc} ; \citealp{2013Natur.495...76P}}.
-It is a luminous star-forming region in the LMC (Large Magellanic Cloud) and is the most luminous complex in the Local Group \citep{1984ApJ...287..116K}.
-The central ionized region spans for \SI{40}{pc} and host the massive, dense star cluster R136 %\citep{1991IAUS..148..145W}. %Note: check the bibliographic format
-The ionizing output \(Q_0\) of R136 is \SI{e51.4}{photons.s^{-1}} \citep{2020MNRAS.499.1918B}.
-It host the active star forming region NGC 2070 \citep{2013AJ....145...98W} where the star-formation rate has recently peaked \citep{2015ApJ...811...76C}. 
-NGC 2070 host a population of OB and WR stars \citep{2011A&A...530A.108E}.
-This nebula is commonly used as a comparison for extragalactic star-forming regions.
-
-The 30 Doradus structure function is shown in Figure~\ref{fig:strucfunc-fit-MC}a.
-In this case we merge the first five points of the structure function.
-%The seeing value for this regions is \SI{0.16}{pc} (\(s_0\)=\SI{0.7}{\arcsecond}) and just one %point of the structure function is below this value.
-%Until a separation of \SI{1.7}{pc} is reached, the structure function lies below the true model.
-%The correlation length is \SI{4}{pc} at a \(\sigma^2\pos\) of \SI{297 \pm 9}{km^{2}.s^{-2}} and an index of \num{0.85}.
-At large separations 30 Doradus structure function presents a behavior of tapered fluctuations. The maximum \(B(r)\) value is \SI{655}{km^{2}.s^{-2}} at a separation of \SI{21}{pc}. 
-From there \(B(r)\) values descends until they reach \SI{250}{km^{2}.s^{-2}} at \SI{38}{pc}.
-
-\subsection{NGC 346}
-\label{sec:ngc-346}
-
-NGC 346 is the most active star-formation region in the SMC (Small Magellanic Cloud) located at a distance of 62 kpc \citetext{\SI{1}{\arcsecond} = \SI{0.30}{pc} ; \citealp{2001ApJ...562..303D}}. 
-It has more than 30 O stars that ionize N66, the largest HII region \citep{2011ApJ...740...10D}.
-N66 has an \ha{} luminosity of \SI{e38.77}{erg.s^{-1}}, almost 60 times higher compared to the Orion Nebula \citep{2010A&A...517A..39H,1984ApJ...287..116K}.
-\citet{2008ApJ...688.1050G} propose an expanding HII region or bubble blown by the winds of the massive progenitor as a mechanism that shapes the recent star formation in this region, in addition to the photoionizing process of the OB stars.
-This mechanism is similar to shell-like HII regions, with a central cluster in a cavity, and with ongoing star formation triggered around their periphery.
-Using a Gaussian single-component \citet{2003ApJ...586.1179D} find a corrected FWHM bulk turbulence of \SI{23.8}{km.s^{-1}}.
-
-The Figure~\ref{fig:strucfunc-fit-MC}b shows the structure function of NGC 346.
-%In this case we merge the first three points of the structure function.
-%The seeing value is \SI{0.07}{pc} (\(s_0\)=\SI{0.23}{\arcsecond}).
-For this region the first ten points lie below the true model.
-At separations above \SI{0.4}{pc} the observed structure functions is coincident with the true model. 
-%The correlation length is \SI{2}{pc} at a \(\sigma^2\pos\) of \SI{35}{km^{2}.s^{-2}} and an index of \num{0.80}.
-For scales above \SI{12}{pc} and a \(B(r)\) value of \SI{65}{km^{2}.s^{-2}} the structure function shows a pattern of ascending values until it reaches \SI{146}{km^{2}.s^{-2}} at \SI{24}{pc}.
-
-\subsection{Hubble X and Hubble V in NGC 6822}
-\label{sec:6822-hubble}
-%
-The irregular dwarf galaxy, NGC 6822, is located at a distance of 500 kpc \citetext{\SI{1}{\arcsecond} = \SI{2.42}{pc} ; \citealp{2012A&A...540A.135S}} and the brightest HII regions are Hubble X and Hubble V (HX and HV hereafter).
-%(1'' = 2.4 pc)
-%HV has a characteristic length of 100 pc and HX has a characteristic length of 140 pc \citep{1999PASP..111.1382O}.
-Luminosity \ha{} for HV is \SI{e38.3}{erg.s^{-1}} and for HX is \SI{e38.21}{erg.s^{-1}} \citep{2002MNRAS.329..481B}.
-Two recognized OB associations are identified within these HII regions \citep{1991ApJ...379..621H,1992AJ....104.1374W}.
-HV is located near 'Hodge OB 8' and HX is located near 'Hodge OB13'  \citep{1999PASP..111.1382O}.
-\citet{1993PASJ...45..693T} realize a study on the kinematics of HX and HV.
-
-%HV has a luminosity at its core of in L$_{H_\alpha}$ = 1 $\times$ 10$^{49}$ H$\alpha$ photons s$^{-1}$ 
-%HX has a luminosity at its core of in L$_{H_\alpha}$ = 2.4 $\times$ 10$^{49}$ H$\alpha$ photons s$^{-1}$ \citep{1999PASP..111.1382O}.
-
-In the Figure~\ref{fig:strucfunc-fit-ExtraGal}a we show the structure function of Hubble V.
-For the observations coming from the TAURUS-II instrument there wasn't any merging of points at small scales.
-%The value of the seeing for this regions is \SI{0.5}{pc} (\(s_0\)=\SI{0.2}{\arcsecond}).
-%All the structure function points lies below the true model.
-%The correlation length is \SI{3.5}{pc} at a \(\sigma^2\pos\) of  \SI{10}{km^{2}.s^{-2}} and an index of \num{0.75}.
-The maximum \(B(r)\) value is \SI{18}{km^{2}.s^{-2}} at a separation of \SI{25}{pc}. 
-From there \(B(r)\) values descends until it reaches \SI{14}{km^{2}.s^{-2}} at \SI{45}{pc}, then it rises for the next point at \SI{50}{pc} with a value of \SI{15}{km^{2}.s^{-2}}.
-Finally the structure functions descends at \SI{9}{km^{2}.s^{-2}} for a separation of \SI{70}{pc}.
-
-The Hubble X structure function is shown in Figure~\ref{fig:strucfunc-fit-ExtraGal}b.
-%The seeing is \SI{0.6}{pc} (\(s_0\)=\SI{0.24}{\arcsecond}) and as in Hubble V the observed structure function lies below the true model.
-%The correlation length is \SI{4}{pc} at a \(\sigma^2\pos\) of \SI{15}{km^{2}.s^{-2}} and an index of \num{0.93}.
-A plateau is reached around \SI{25}{km^{2}.s^{-2}} at a separation of \SI{14}{pc} and a maximum \(B(r)\) value of \SI{31}{km^{2}.s^{-2}} at a separation of \SI{36}{pc}.
-
-\subsection{NGC~595 and NGC~604 in M33}
-\label{sec:m33-ngc}
-
-M33 is the third largest galaxy in the Local Group located at the distance of 840 kpc \citetext{\SI{1}{\arcsecond} = \SI{4.07}{pc} ; \citealp{2015KamKinematics}} and is of morphological type SA(s)cd.
-The two brightest HII regions in the galaxy are NGC 604 and NGC 595.
-
-NGC 604 is the second brightest \hii{} region in the Local Group after 30~Dor in the Large Magellanic Cloud and is forty times larger ($\sim $ 400 pc) and 6,000 times brighter than Orion in our Milky Way galaxy.
-It is the brightest giant \hii{} region in the M33 galaxy and is visually dominated by a big loop, big shells and different size filaments.
-It has a luminosity in \ha{} of \SI{e39.42}{erg.s^{-1}} \citep{2002MNRAS.329..481B}.
-Using photometry from the HST \citet{1996ApJ...456..174H} identified that the stars are separated into a primary cluster within NGC 604, and a secondary to the north of the region.
-In the primary there are \(\sim\)200 OB stars, candidate to red supergiants (RSGs) and the presence of WR stars.
-For the northern cluster they find eight luminous stars and no evolved massive stars.
-More Recently, \citet{2011MNRAS.411..235E} studied 10 WR stars and propose at least 4 RSGs candidates.
-\citet{2012AJ....143...43F} focused on the massive young stellar objects (MYSOs).
-The average ages for the stars, was determined to be from  \num{3} to \SI{5}{Myr} \citep{1996ApJ...456..174H} and with the RSGs as an older population have an age of 12.4\(\pm\)2.1 Myr \citep{2011MNRAS.411..235E}.
-This suggest that two episodes of star formation, at least, have taken place in the GEHR.
-
-% and in L$_{X}$=9.3$\times$ 10$^{35}$ erg s$^{-1}$ \citep{2008ApJ...685..919T}.
-%\citet{2012ApJ...761....3M} derive an average age of 4$\pm$1 Myr and a total stellar mass of 1.6$^{+1.6}_{-1.0} \times$ 10$^{5}$M$_{\odot}$ for the region.
-
-NGC 595 is the second brightest giant HII region in the M33 galaxy and has an \ha{} shell morphology that is related to the stellar winds of the several massive stars located in its interior.
-It has a luminosity in \ha{} of \SI{e38.95}{erg.s^{-1}}\citep{2002MNRAS.329..481B}.
-\citet{1993AJ....105.1400D} use optical photometry to propose 11 WR stars. 
-Using HST/WFPC-2 images \citet{1996AJ....111.1128M} found approximately 250 stars of the OB type, 13 Supergiants and 10 WR, confirming previous candidates.
-They derived and age of 4.5\(\pm\)1.0 Myr consistent with \citet{1993AJ....105.1400D}.
-\citet{2010MNRAS.402.1635R} used Integral Field Spectroscopy (IFS) to present a resolved study of the physical properties of the ionized gas and the ionized structure.
-They also confirm the presence of previous cataloged WR stars and detect new candidates, and propose classical emission-line ratios as metallicity calibrators.
-\citet{lagrois2011} present a kinematic study of the regions using optical emission lines and and radio 21 cm line observations.
-They proposed Champagne flows at the periphery of the molecular cloud leading to accelerated ionized material.
-
-In the Figure~\ref{fig:strucfunc-fit-ExtraGal}c we show the structure function of NGC 595.
-%The seeing is \SI{0.3}{pc} (\(s_0\)=\SI{0.1}{\arcsecond}) and for this region only the first two points are below the true model. 
-%The correlation length is \SI{12}{pc} at a \(\sigma^2\pos\) of \SI{54}{km^{2}.s^{-2}} and an index of \num{1.3}.
-At large scales the structure function behaves following the tapered fluctuations pattern.
-A maximum \(B(r)\) value of \SI{104}{km^{2}.s^{-2}} is reached at \SI{33}{pc}. 
-From there the structure functions decays following a scatter pattern until it reaches \SI{54}{km^{2}.s^{-2}} at a separation of \SI{211}{pc}.
-
-In the Figure~\ref{fig:strucfunc-fit-ExtraGal}d we show the structure function of NGC 604.
-%The seeing is \SI{1.7}{pc} (\(s_0\)=\SI{0.42}{\arcsecond}) and the structure function of this region lies below the true model for most of the separation range.
-%The correlation length is \SI{10}{pc} at a \(\sigma^2\pos\) of \SI{71}{km^{2}.s^{-2}} and has an index of \num{1}.
-The structure function present clear characteristics of periodic oscillations at large scales.
-A periodic pattern for the structure function appears with a maximum \(B(r)\) value of \SI{143}{km^{2}.s^{-2}} that is reached at \SI{60}{pc}, then the oscillation cause a minimum of \SI{54}{km^{2}.s^{-2}} at \SI{133}{pc} and finally it goes back up again at \SI{211}{pc} to a \(B(r)\) value of \SI{123}{km^{2}.s^{-2}}.
 
@@
     (a)\\
-    \includegraphics[width=\linewidth]{Figures/fake-finite-box-effect}
+    \includegraphics[width=0.95\linewidth]{Figures/fake-finite-box-effect}
     \\[\bigskipamount]
     (b)\\
-    \includegraphics[width=\linewidth]{Figures/fake-finite-box-fits}
+    \includegraphics[width=0.95\linewidth]{Figures/fake-finite-box-fits}
   \end{tabular}
@@
 
+\section{\boldmath Notes on individual \hii{} regions}
+\label{sec:notes-individual-hii}
+For each region or pair of regions in our sample,
+we give a more description of its physical properties
+(supplementing section~\ref{sec:regions-milky-way})
+together with additional details of the structure function
+(supplementing section~\ref{sec:results}).
+
+%the model fit to
+
+\subsection{Orion Nebula}
+\label{sec:orion-nebula}
+
+The Orion Nebula (M42) is the prototype of a galactic HII region located at a distance of 440 pc \citetext{\SI{1}{\arcsecond} = \SI{0.002}{pc} ; \citealp{2008AJ....136.1566O}}.
+The O7 V star \(\theta^{1}\) Ori C is the most luminous and hottest star \citep{2006A&A...448..351S} with an ionizing flux \(Q_0\) of  \SI{e49.12}{photons.s^{-1}}. 
+With other 3 B-type stars they form the Trapezium cluster.
+The bright region that surrounds these massive ionizing stars is called the the Huygens region (Orion core henceforth).
+In the southwest direction of the Huygens region there is a drop in the brightness as one approach a much larger region called Extended Orion Nebula \citetext{EON henceforth;  \citealp{2008Sci...319..309G}}
+The position of Orion near the side of the Orion Molecular Cloud (OMC-1) make it an ongoing star formation with a large population of young star, some of which are the sources of stellar jets and Herbig-Haro objects \citep{1993ApJ...410..696O}.
+Its physical properties and kinematics, along its stellar population are documented in \citet{2001ARA&A..39...99O}.
+
+\subsubsection{Observed structure function and model fit}
+\label{sec:observ-struct-funct-orion}
+
+Figure~\ref{fig:strucfunc-fit-Galactic}a shows the structure function of the Orion core.
+In this case we merge the first three points of the structure function.
+%From \SI{0.002}{pc} until \SI{0.003}{pc} all points fall below the true model showing that they are affected by the seeing. 
+%The correlation length for the Orion core is \SI{0.07}{pc}, it has a \(\sigma^2\pos\) of \SI{12}{km^{2}.s^{-2}} and an index of \num{1.07}.
+The structure function of the Orion core behaves accordingly to the tapered case of inhomogeneous fluctuations (see Figure~\ref{fig:model-strucfunc}b).
+At \SI{0.25}{pc} there is a plateau around \SI{22}{km^{2}.s^{-2}}.
+Above separations of \SI{0.3}{pc} the structure function decays to a value of \SI{7}{km^{2}.s^{-2}} at  \SI{0.5}{pc}.
+
+\subsubsection{Comparison with previous studies}
+\label{sec:comparison-orion}
+
+\citet{arthur2016turbulence} carried out a complete analysis by calculating the structure function of different emission lines in the inner Orion Nebula.
+They observed a tendency that higher ionization lines presents higher values on the magnitude dispersion and the steepness of the structure function slope. 
+Their results just consider one Gaussian component. 
+The power-law index obtained by \citet{arthur2016turbulence} are \(m \sim 1.2 \pm 0.1\) for \halpha\ and [OIII] emission lines and for [SII] they found \(m \sim 0.8 \pm 0.1\). 
+The correlation length for all lines is \SI{\approx 0.05}{pc}, value obtained when the structure function is equal to \(\sigma\pos^2\).
+For the same \halpha\ observation we obtained a value of \num{1.07} and a correlation length of \SI{0.068}{pc}. 
+Although the work of \citet{arthur2016turbulence} follows a different methodology, the values of \(r_0\) and \(\sigma\pos^2\) fall within the margin error.
+
+\subsection{Lagoon Nebula}
+\label{sec:lagoon-nebula}
+
+The Lagoon Nebula (M8, NGC6523) is located at a distance of 1 250 pc \citetext{\SI{1}{\arcsecond} = \SI{0.006}{pc} ; \citealp{2005A&A...430..941P}}.
+It has a luminosity in \ha{} of \SI{e37.47}{erg.s^{-1}}\citep{1984ApJ...287..116K}.
+It contains the young stellar cluster NGC6530 and the region is illuminated by different massive stars of spectral types O and B, the hottest being 9 Sgr, type O4V \citep{Damiani:2017b}.
+Optically, the brightest part of the nebula is called 'Hourglass nebula' which surrounds and obscures the O7 star Herschel 36 \citep{1986AJ.....91..870W}. 
+The velocity field shows several expanding shells, related to the stellar population, and the massive protostar M8East-IR \citep{1984ApJ...278..170S} indicating that recent star formation. 
+A blueshifted, neutral layer is also in very good agreement with predictions of champagne-flow models of blister HII regions \citep{Damiani:2017b}. 
+The properties of the nebula are reviewed by \citet{2008hsf2.book..533T}.
+
+\subsubsection{Observed structure function and model fit}
+\label{sec:observ-struct-funct-lagoon}
+
+The Figure~\ref{fig:strucfunc-fit-Galactic}c shows the structure function of the Lagoon nebula.
+%There aren't any points affected by the seeing which has a value of \SI{0.006}{pc} (\(s_0\)=\SI{1}{\arcsecond}).
+In this case we merge the first two points.
+The Lagoon nebula presents a non-uniform behavior below the correlation length but it is possible to see the characteristic ascending values of the structure function.
+%The turbulent parameters that fits our model are a \(r_0\) of \SI{1}{pc}, a \(\sigma^2\pos\) of \SI{7}{km^{2}.s^{-2}} and an index of \num{1.17}.
+At large scales there is an indication of some periodic behavior followed by ascending \(B(r)\) values at largest separation.
+A value of\(B(r)\) of order 2\(\sigma^2\pos\) is \(\sim\)\SI{14}{km^{2}.s^{-2}} at a separation of \(\sim\)\SI{2.5}{pc}. 
+Then there is a diminution at \SI{4.5}{pc} down to a value of \SI{11}{km^{2}.s^{-2}}.
+From this point the structure function ascends until it reaches \SI{66}{km^{2}.s^{-2}} around \SI{20}{pc}.
+
+\subsubsection{Comparison with previous studies}
+\label{sec:comparison-lagoon}
+The structure function of the Lagoon Nebula was previously
+studied by \citet{Chakraborty:1999a} using the [\ion{O}{3}] \Wav{5007} line,
+finding an approximate power law behavior (\(m = 0.46\))
+on scales of \num{0.01} to \SI{0.2}{pc}.
+No flattening of the structure function at the largest scales
+was seen,
+but that is to be expected due to the finite box effect
+(see Appendix~\ref{sec:finite-box-effects})
+given that we determine the correlation length to be \(r_0 \approx   \SI{1}{pc}\) for this nebula,
+which is several times larger than the region mapped by \citet{Chakraborty:1999a}.
+On the other hand, the magnitude of the velocity dispersion found by these authors greatly exceeds our own measurements.
+For instance, they find \(B(r) = \SI{278}{km^2.s^{-2}}\) at \SI{0.2}{pc}, whereas we find \(B(r) \approx \SI{2}{km^2.s^{-2}}\) at the same scale, which corresponds to a discrepancy of more than a factor of a hundred in \(\sigma^2\pos\).
+This may be due in part to the fact that \citet{Chakraborty:1999a}
+observed a small and atypical part of the nebula known as the
+Hourglass region, which includes a cluster of very young stars
+\citep{Arias:2006e}. 
+In the case of the Orion Nebula we found that the velocity dispersion
+of the central region was larger than that of the extended nebula
+and this could be an example of a similar phenomenon,
+albeit to a more extreme degree.
+
+\subsection{Carina Nebula}
+\label{sec:carina-nebula}
+
+The Carina nebula is a large star-forming complex located at a distance of 2 350 pc \citetext{\SI{1}{\arcsecond} = \SI{0.01}{pc} ; \citealp{2006ApJ...644.1151S}}.
+Using the \ha{} luminosity as a diagnostic of the ionizing flux \(Q_0\) \citet{2007MNRAS.379.1279S} measured a value of \SI{e50.47}{photons.s^{-1}}.
+Young clusters like Trumpler 14 and 16, and Collinder 228 form the Car OB1 association, one of the largest OB associations on the Galaxy.
+This OB association has more than 65 stars earlier than B0, and several Wolf-Rayet (WR) stars.
+The most luminous star is the blue variable $\eta$ Car.
+As a star formation region, it presents several phenomena related with young stars as evaporating protoplanetary discs, erosion of large dust pillars and the triggering of a second generation of embedded stars and Herbig-Haro objects, to mention some \citetext{see \citealp{2008hsf2.book..138S} and reference therein}.
+This region can be consider as a bridge between the detailed star-formation regions like Orion, and much more distant regions like 30 Doradus.
+
+\subsubsection{Observed structure function and model fit}
+\label{sec:observ-struct-funct-carina}
+
+(The Figure~\ref{fig:strucfunc-fit-Galactic}d shows the structure function of the Carina nebula.
+%The seeing is \SI{0.008}{pc} (\(s_0\)=\SI{1.3}{\arcsecond}) and there are just a couple of points that lie below the true model, indicating that the majority of points isn't affected by the seeing.
+For this region we merge the first two points of the structure function.
+As the Lagoon nebula, Carina also shows a non-uniform behavior below the correlation length.
+%The correlation length is \SI{0.56}{pc} pc at a \(\sigma^2\pos\) of \SI{18}{km^{2}.s^{-2}} and an index of \num{1.14}.
+At larges scales the structure function of the Carina nebula follows a pattern that resembles the homogeneous fluctuation of Figure~\ref{fig:model-strucfunc}a.
+The structure function reaches a plateau around \SI{36}{km^{2}.s^{-2}} at \(\sim\) \SI{2}{pc}.
+When \(r >\)\SI{6}{pc} the structure functions shows a small amplitude periodic pattern around 2\(\sigma^2\pos\).
+
+\subsubsection{Comparison with previous studies}
+\label{sec:comparison-carina}
+
+We have found no previous studies of Carina's structure function in the literature.
+
+\subsection{30 Doradus}
+\label{sec:30-doradus}
+
+The 30 Doradus (Tarantula Nebula) nebula is located at a distance of \SI{49.9}{kpc} \citetext{\SI{1}{\arcsecond} = \SI{0.24}{pc} ; \citealp{2013Natur.495...76P}}.
+It is a luminous star-forming region in the LMC (Large Magellanic Cloud) and is the most luminous complex in the Local Group \citep{1984ApJ...287..116K}.
+The central ionized region spans for \SI{40}{pc} and host the massive, dense star cluster R136 %\citep{1991IAUS..148..145W}. %Note: check the bibliographic format
+The ionizing output \(Q_0\) of R136 is \SI{e51.4}{photons.s^{-1}} \citep{2020MNRAS.499.1918B}.
+It host the active star forming region NGC 2070 \citep{2013AJ....145...98W} where the star-formation rate has recently peaked \citep{2015ApJ...811...76C}. 
+NGC 2070 host a population of OB and WR stars \citep{2011A&A...530A.108E}.
+This nebula is commonly used as a comparison for extragalactic star-forming regions.
+
+\subsubsection{Observed structure function and model fit}
+\label{sec:observ-struct-funct-30dor}
+
+The 30 Doradus structure function is shown in Figure~\ref{fig:strucfunc-fit-MC}a.
+In this case we merge the first five points of the structure function.
+%The seeing value for this regions is \SI{0.16}{pc} (\(s_0\)=\SI{0.7}{\arcsecond}) and just one %point of the structure function is below this value.
+%Until a separation of \SI{1.7}{pc} is reached, the structure function lies below the true model.
+%The correlation length is \SI{4}{pc} at a \(\sigma^2\pos\) of \SI{297 \pm 9}{km^{2}.s^{-2}} and an index of \num{0.85}.
+At large separations 30 Doradus structure function presents a behavior of tapered fluctuations. The maximum \(B(r)\) value is \SI{655}{km^{2}.s^{-2}} at a separation of \SI{21}{pc}. 
+From there \(B(r)\) values descends until they reach \SI{250}{km^{2}.s^{-2}} at \SI{38}{pc}.
+
+\subsubsection{Comparison with previous studies}
+\label{sec:comparison-30dor}
+
+The first attempt at characterizing turbulence in a giant extragalactic HII region, GEHR, was done by \citet{1961MNRAS.122....1F} with the 30~Doradus complex, finding no indication of turbulent motions between scale of \num{10} and \SI{100}{pc}.
+\citet{Melnick:2021x} also investigated the structure function in 30 Doradus finding on their results that the structure function is entirely flat on scales from \num{3} to \SI{200}{pc}.
+The above does not coincide with our results, since we establish the existence of correlations up to the maximum value of the structure function that occurs at \SI{20}{pc}, separation where a value of 2\(\sigma\pos^2\) is reached.
+The VLT FLAMES/GIRAFFE observations of \citet{Melnick:2021x} may not have had the resolution to resolve the correlations at small separations, however an inspection of its velocity map (figure 7 in their work) shows that the velocity distribution it is far from completely random.
+This is the first time turbulence is characterized in 30~Doradus using the structure function.
+
+\subsection{NGC 346}
+\label{sec:ngc-346}
+
+NGC 346 is the most active star-formation region in the SMC (Small Magellanic Cloud) located at a distance of 62 kpc \citetext{\SI{1}{\arcsecond} = \SI{0.30}{pc} ; \citealp{2001ApJ...562..303D}}. 
+It has more than 30 O stars that ionize N66, the largest HII region \citep{2011ApJ...740...10D}.
+N66 has an \ha{} luminosity of \SI{e38.77}{erg.s^{-1}}, almost 60 times higher compared to the Orion Nebula \citep{2010A&A...517A..39H,1984ApJ...287..116K}.
+\citet{2008ApJ...688.1050G} propose an expanding HII region or bubble blown by the winds of the massive progenitor as a mechanism that shapes the recent star formation in this region, in addition to the photoionizing process of the OB stars.
+This mechanism is similar to shell-like HII regions, with a central cluster in a cavity, and with ongoing star formation triggered around their periphery.
+Using a Gaussian single-component \citet{2003ApJ...586.1179D} find a corrected FWHM bulk turbulence of \SI{23.8}{km.s^{-1}}.
+
+\subsubsection{Observed structure function and model fit}
+\label{sec:observ-struct-funct-346}
+
+The Figure~\ref{fig:strucfunc-fit-MC}b shows the structure function of NGC 346.
+%In this case we merge the first three points of the structure function.
+%The seeing value is \SI{0.07}{pc} (\(s_0\)=\SI{0.23}{\arcsecond}).
+For this region the first ten points lie below the true model.
+At separations above \SI{0.4}{pc} the observed structure functions is coincident with the true model. 
+%The correlation length is \SI{2}{pc} at a \(\sigma^2\pos\) of \SI{35}{km^{2}.s^{-2}} and an index of \num{0.80}.
+For scales above \SI{12}{pc} and a \(B(r)\) value of \SI{65}{km^{2}.s^{-2}} the structure function shows a pattern of ascending values until it reaches \SI{146}{km^{2}.s^{-2}} at \SI{24}{pc}.
+
+\subsubsection{Comparison with previous studies}
+\label{sec:comparison-346}
+
+We have found no previous studies of NGC~346's structure function in the literature.
+
+\subsection{Hubble X and Hubble V in NGC 6822}
+\label{sec:6822-hubble}
+%
+The irregular dwarf galaxy, NGC 6822, is located at a distance of 500 kpc \citetext{\SI{1}{\arcsecond} = \SI{2.42}{pc} ; \citealp{2012A&A...540A.135S}} and the brightest HII regions are Hubble X and Hubble V (HX and HV hereafter).
+%(1'' = 2.4 pc)
+%HV has a characteristic length of 100 pc and HX has a characteristic length of 140 pc \citep{1999PASP..111.1382O}.
+Luminosity \ha{} for HV is \SI{e38.3}{erg.s^{-1}} and for HX is \SI{e38.21}{erg.s^{-1}} \citep{2002MNRAS.329..481B}.
+Two recognized OB associations are identified within these HII regions \citep{1991ApJ...379..621H,1992AJ....104.1374W}.
+HV is located near 'Hodge OB 8' and HX is located near 'Hodge OB13'  \citep{1999PASP..111.1382O}.
+\citet{1993PASJ...45..693T} realize a study on the kinematics of HX and HV.
+
+%HV has a luminosity at its core of in L$_{H_\alpha}$ = 1 $\times$ 10$^{49}$ H$\alpha$ photons s$^{-1}$ 
+%HX has a luminosity at its core of in L$_{H_\alpha}$ = 2.4 $\times$ 10$^{49}$ H$\alpha$ photons s$^{-1}$ \citep{1999PASP..111.1382O}.
+
+\subsubsection{Observed structure function and model fit}
+\label{sec:observ-struct-funct-hubbles}
+
+In the Figure~\ref{fig:strucfunc-fit-ExtraGal}a we show the structure function of Hubble V.
+For the observations coming from the TAURUS-II instrument there wasn't any merging of points at small scales.
+%The value of the seeing for this regions is \SI{0.5}{pc} (\(s_0\)=\SI{0.2}{\arcsecond}).
+%All the structure function points lies below the true model.
+%The correlation length is \SI{3.5}{pc} at a \(\sigma^2\pos\) of  \SI{10}{km^{2}.s^{-2}} and an index of \num{0.75}.
+The maximum \(B(r)\) value is \SI{18}{km^{2}.s^{-2}} at a separation of \SI{25}{pc}. 
+From there \(B(r)\) values descends until it reaches \SI{14}{km^{2}.s^{-2}} at \SI{45}{pc}, then it rises for the next point at \SI{50}{pc} with a value of \SI{15}{km^{2}.s^{-2}}.
+Finally the structure functions descends at \SI{9}{km^{2}.s^{-2}} for a separation of \SI{70}{pc}.
+
+The Hubble X structure function is shown in Figure~\ref{fig:strucfunc-fit-ExtraGal}b.
+%The seeing is \SI{0.6}{pc} (\(s_0\)=\SI{0.24}{\arcsecond}) and as in Hubble V the observed structure function lies below the true model.
+%The correlation length is \SI{4}{pc} at a \(\sigma^2\pos\) of \SI{15}{km^{2}.s^{-2}} and an index of \num{0.93}.
+A plateau is reached around \SI{25}{km^{2}.s^{-2}} at a separation of \SI{14}{pc} and a maximum \(B(r)\) value of \SI{31}{km^{2}.s^{-2}} at a separation of \SI{36}{pc}.
+
+\subsubsection{Comparison with previous studies}
+\label{sec:comparison-carina}
+
+We have found no previous studies of the structure functions
+of Hubble~V or~X in the literature.
+
+\subsection{NGC~595 and NGC~604 in M33}
+\label{sec:m33-ngc}
+
+M33 is the third largest galaxy in the Local Group located at the distance of 840 kpc \citetext{\SI{1}{\arcsecond} = \SI{4.07}{pc} ; \citealp{2015KamKinematics}} and is of morphological type SA(s)cd.
+The two brightest HII regions in the galaxy are NGC 604 and NGC 595.
+
+NGC 604 is the second brightest \hii{} region in the Local Group after 30~Dor in the Large Magellanic Cloud and is forty times larger ($\sim $ 400 pc) and 6,000 times brighter than Orion in our Milky Way galaxy.
+It is the brightest giant \hii{} region in the M33 galaxy and is visually dominated by a big loop, big shells and different size filaments.
+It has a luminosity in \ha{} of \SI{e39.42}{erg.s^{-1}} \citep{2002MNRAS.329..481B}.
+Using photometry from the HST \citet{1996ApJ...456..174H} identified that the stars are separated into a primary cluster within NGC 604, and a secondary to the north of the region.
+In the primary there are \(\sim\)200 OB stars, candidate to red supergiants (RSGs) and the presence of WR stars.
+For the northern cluster they find eight luminous stars and no evolved massive stars.
+More Recently, \citet{2011MNRAS.411..235E} studied 10 WR stars and propose at least 4 RSGs candidates.
+\citet{2012AJ....143...43F} focused on the massive young stellar objects (MYSOs).
+The average ages for the stars, was determined to be from  \num{3} to \SI{5}{Myr} \citep{1996ApJ...456..174H} and with the RSGs as an older population have an age of 12.4\(\pm\)2.1 Myr \citep{2011MNRAS.411..235E}.
+This suggest that two episodes of star formation, at least, have taken place in the GEHR.
+
+% and in L$_{X}$=9.3$\times$ 10$^{35}$ erg s$^{-1}$ \citep{2008ApJ...685..919T}.
+%\citet{2012ApJ...761....3M} derive an average age of 4$\pm$1 Myr and a total stellar mass of 1.6$^{+1.6}_{-1.0} \times$ 10$^{5}$M$_{\odot}$ for the region.
+
+NGC 595 is the second brightest giant HII region in the M33 galaxy and has an \ha{} shell morphology that is related to the stellar winds of the several massive stars located in its interior.
+It has a luminosity in \ha{} of \SI{e38.95}{erg.s^{-1}}\citep{2002MNRAS.329..481B}.
+\citet{1993AJ....105.1400D} use optical photometry to propose 11 WR stars. 
+Using HST/WFPC-2 images \citet{1996AJ....111.1128M} found approximately 250 stars of the OB type, 13 Supergiants and 10 WR, confirming previous candidates.
+They derived and age of 4.5\(\pm\)1.0 Myr consistent with \citet{1993AJ....105.1400D}.
+\citet{2010MNRAS.402.1635R} used Integral Field Spectroscopy (IFS) to present a resolved study of the physical properties of the ionized gas and the ionized structure.
+They also confirm the presence of previous cataloged WR stars and detect new candidates, and propose classical emission-line ratios as metallicity calibrators.
+\citet{lagrois2011} present a kinematic study of the regions using optical emission lines and and radio 21 cm line observations.
+They proposed Champagne flows at the periphery of the molecular cloud leading to accelerated ionized material.
+
+\subsubsection{Observed structure function and model fit}
+\label{sec:observ-struct-funct-m33}
+
+In the Figure~\ref{fig:strucfunc-fit-ExtraGal}c we show the structure function of NGC 595.
+%The seeing is \SI{0.3}{pc} (\(s_0\)=\SI{0.1}{\arcsecond}) and for this region only the first two points are below the true model. 
+%The correlation length is \SI{12}{pc} at a \(\sigma^2\pos\) of \SI{54}{km^{2}.s^{-2}} and an index of \num{1.3}.
+At large scales the structure function behaves following the tapered fluctuations pattern.
+A maximum \(B(r)\) value of \SI{104}{km^{2}.s^{-2}} is reached at \SI{33}{pc}. 
+From there the structure functions decays following a scatter pattern until it reaches \SI{54}{km^{2}.s^{-2}} at a separation of \SI{211}{pc}.
+
+In the Figure~\ref{fig:strucfunc-fit-ExtraGal}d we show the structure function of NGC 604.
+%The seeing is \SI{1.7}{pc} (\(s_0\)=\SI{0.42}{\arcsecond}) and the structure function of this region lies below the true model for most of the separation range.
+%The correlation length is \SI{10}{pc} at a \(\sigma^2\pos\) of \SI{71}{km^{2}.s^{-2}} and has an index of \num{1}.
+The structure function present clear characteristics of periodic oscillations at large scales.
+A periodic pattern for the structure function appears with a maximum \(B(r)\) value of \SI{143}{km^{2}.s^{-2}} that is reached at \SI{60}{pc}, then the oscillation cause a minimum of \SI{54}{km^{2}.s^{-2}} at \SI{133}{pc} and finally it goes back up again at \SI{211}{pc} to a \(B(r)\) value of \SI{123}{km^{2}.s^{-2}}.
+
+\subsubsection{Comparison with previous studies}
+\label{sec:comparison-m33}
+
+For NGC 604 there is good agreement in our structure function results and previous studies because where are using the same TAURUS-II data as \citet{Melnick:2021x} and \citet{Medina-Tanco:1997a}.
+Despite this general agreement the interpretations in each study is different.
+\citet{Medina-Tanco:1997a} conclude about a double regime acting on the kinetic energy spectrum.
+According to this double cascade, turbulence is being forced at scales of \(\approx\) \SI{10}{pc} while and energy cascade has developed down to the smallest scales and other, as an inverse cascade, extends up to scale of \(\approx\) \SI{70}{pc}.
+\citet{Medina-Tanco:1997a} mentioned different characteristic scale lengths, the most notorious is the \SI{\sim 10}{pc}, and they interpret it as possible source on energy associated with the expansion of shocks coming from wind bubbles.
+\citet{Melnick:2021x} addresses some issues with TAURUS II data while comparing profiles between the previous instrument TAURUS I where there exist a difference between observations (see section 4.1 on their paper).
+They mentioned that one problem with \citet{Medina-Tanco:1997a} structure function is that they didn't take into account the observational seeing.
+This would invalidate they results and \citet{Melnick:2021x} consider that taking out the structure function values that fall within this range would make the structure function flat at scales \(<\)\SI{10}{pc}, so they rule out \citet{Medina-Tanco:1997a} results.
+Finally they point out, and we agree, the importance of observing NGC 604 at higher spatial resolution. 
+Our Fig. \ref{fig:strucfunc-fit-ExtraGal}d shows in fact that there is a velocity structure in NGC 604. 
+None of the previous studies obtained a power-law index or correlation length for the structure function to compare our results.
+
+For our NGC 595 \halpha\ emission line results there is no correspondence in the structure function from the previous investigations of \citet{lagrois2009multi} and \citet{lagrois2011}.
+Our observations cover the brightest part of the region and have smaller resolution than theirs.
+As a consequence \citet{lagrois2009multi} and \citet{lagrois2011} structure functions results does not cover scales $<$10 pc, where in our results the correlation is taking place.
+One big difference is that \citet{lagrois2011} apply a  filter to the velocity field to get rid of non-turbulent movements.
+As a comparison for the filtered turbulent parameters they present a correlation length of \SI{43}{pc} and the power-law index they provide is \num{1.55 \pm 0.01}.
+Other difference in their methodology is that they use the normalized structure function value of 2\(\sigma\pos\) to obtain the correlation length.
+%Using their unfiltered data the correlation length is \(\sim\) \SI{90}{pc} and using the same criteria as our it is \(\sim\) \SI{40}{pc} and the slope would be shallower. 
+Their velocity centroid \(\sigma\) is \SI{5.92 \pm 0.15}{km.s^{-1}} while we have \SI{7.3\pm 2}{km. s^{-1}} which fall within the uncertainties.
+Due to the different observations and methodologies a direct comparison between structure functions is not possible.
+
 \section{Additional covariance corner plots for model fits}
@@
 Supplementary online-only material.
-\clearpage
+%\clearpage
 

### 2022-06-19 strucfunc_paper.tex
Tidy up Orion section in appendix

@@
 \subsection{Comparison with previous structure functions}
-
+\label{sec:comp-with-prev}
 Comparison with prior studies is complicated by the
@@
 
-In section \ref{sec:results} we show that each velocity field of our sample can be characterized by parameters that are particular for each \hii{} region.
-We used these parameters to develop scaling relations between them and the physical properties of each region.
-
 %Intro for scaling relations
-Correlations between the physical properties of \hii{} regions like size, luminosity, and the velocity dispersion have been used as tools for finding scaling relationships for these objects.
-These kind of relations have also been found in dwarf galaxies and high-redshift star formation regions.
+Correlations between the physical properties of \hii{} regions like size, luminosity, and the velocity dispersion, have been used as tools for finding scaling relationships for these objects, which have also been found in dwarf galaxies and high-redshift star formation regions.
 \citet{melnick1977,terlevich1981} were the first to shown an empirical relationship between the line width and the integrated properties of the \hii{} regions as the diameter or the luminosity (\(r \sim \sigma ^{\sim 2}\) ; \(\text{L}_{\text{H}} \sim \sigma ^{\sim 4}\)).
@@
 %methods for our analysis
-We implement a hierarchical Bayesian model for fitting a straight line using the \texttt{linmix} Python library based on \cite{2007ApJ...665.1489K}.
-The physical properties in Table \ref{tab:regions-properties} are the independent variable \(X\) and the turbulent parameters in Table \ref{tab:Res} are the dependent variable \(Y\).
-For the physical properties we consider an uncertainty of the \num{10}\% of the value and for the turbulent parameters we used 1-\(\sigma\). 
+In section \ref{sec:results} we show that each velocity field of our sample can be characterized by parameters that are particular for each \hii{} region.
+We used these parameters to develop scaling relations between them and the physical properties of each region.
+To accomplish this we implement a hierarchical Bayesian model for fitting a straight line using the \texttt{linmix} Python library based on \cite{2007ApJ...665.1489K}.
+We use the physical properties in Table \ref{tab:regions-properties} as the independent variable \(X\) and the turbulent parameters in Table \ref{tab:Res} as the dependent variable \(Y\).
+In the following analysis we left out the EON to avoid redundancy in the fitting.
+For the physical properties we consider an uncertainty of the \num{10}\% of the value and for the turbulent parameters we use the 2-\(\sigma\) intervals. 
 In the case of non-gaussian distribution we choose the highest value for the uncertainty.
-The results are shown in Table \ref{tab:RestStats} in ascending order for the \(p\)-value.
-In the Figures \ref{fig:sigvsl} and \ref{fig:rvsR} we show the correlations with a significance level \(p < \num{0.05}\).
-The black solid line shows the regression line and the red thin lines show some samples from the posterior distribution.
+The main results are shown in Table \ref{tab:RestStats} in ascending order for the \(p\)-value.
+In the Figures \ref{fig:sigvsl} and \ref{fig:rvsR} we show the correlations with a significance level \(p < \num{0.05}\) which corresponds to the first two rows in Table \ref{tab:RestStats}.
+In the Figures the black solid line shows the input regression line and the red thin lines show some samples from the posterior distribution.
 
@@
 Since this relation is the most common it can be use for comparison with the investigations mentioned at the beginning of this section.
-Our results give us a relation of \(\log \sigma\pos = (0.27 \pm 0.1) \log \text{L}(\text{H}_{\alpha})-(10 \pm 4.0)\).
+Our results give us a relation of \(\log \sigma\pos = (0.26 \pm 0.11) \log \text{L}(\text{H}_{\alpha})-(9.3 \pm 4.3)\).
 It is customary in the literature to present \(\text{L} (\text{H}_{\alpha})\) as the dependent variable.
-In our case if we choose the upper uncertainty and take the inverse of slope we have \(\text{L}_{\text{H}_{\alpha}} \propto \sigma^{3.4}\). 
-Using the same procedure in \texttt{linmix} and changing the variables we obtained \(\log \text{L}(\text{H}_{\alpha}) = (3.4\pm 1.5) \log \sigma\pos -(36 \pm 1)\).
-Both results are close to the previously proposed \(\text{L}_{\text{H}} \propto \sigma^{4}\) relation.
+In our case if we choose the upper uncertainty and take the inverse of slope we have \(\text{L}_{\text{H}_{\alpha}} \propto \sigma^{2.6}\). 
+Using the same procedure in \textit{linmix} and changing the variables order we obtained \(\log \text{L}(\text{H}_{\alpha}) = (3.9\pm 2.6) \log \sigma\pos -(35.55 \pm 2)\) which is within the uncertainty of the previously proposed \(\text{L}_{\text{H}} \propto \sigma^{4}\) relations.
 The references for the \(\text{L}(\text{H}_{\alpha})\) value are given in Appendix~\ref{sec:notes-individual-hii}.
@@
 The Figure \ref{fig:rvsR} shows the relation of the correlation length \(r_0\) and the size \(S\) of the region. 
-The relationship we found is \(\log r_0 = (0.93 \pm 0.33) \log S - (1.6 \pm 0.7)\).
+The relationship we found is \(\log r_0 = (0.95 \pm 0.33) \log S - (1.6 \pm 0.7)\).
 The values of \(S\) are taken from \citet{1984ApJ...287..116K} and correspond to the outer
-limits seen from visual inspection of the \ha{} photographs.
-In this sense these values would represent an upper limit of the size of each region.
-Since these objects do not posses a physical edges the size determination is not trivial.
+limits seen from visual inspection of \ha{} photographs.
+These values would represent an upper limit of the size of each region.
+Since these objects do not posses physical edges the size determination is not trivial.
 Due to the above, we chose these set values since they are from an unique source and are foreign to our calculations and observations, which reduced the bias in the scaling law we obtain.
 
-As for the power-law index \(m\) we can see from table \ref{tab:RestStats} that this parameter does not correlate with any other parameter or physical property.
+%Size vs centroid velocity dispersion
+Other important relation commonly used in the study of the interstellar medium is the diameter (or size) versus velocity dispersion.
+Table \ref{tab:RestStats} shows this result for our sample in row 3. 
+This relation presents a significance level \(p > \num{0.05}\) but there are a couple of things worth mentioning.
+Historically this relation is important following the work of \citet{1981MNRAS.194..809L} where he presents it in the context of molecular cloud complexes of many clouds, individual clouds, and clumps, so that size scales are studied over \(\num{0.1} < L < \SI{100}{pc}\) obtaining \(\sigma = 1.10 L ^{0.38}\).
+This relation is interpreted in terms of turbulence, particularly the Kolmogorov model which predicts a index of \num{0.33} so that larger regions presents more turbulence, and smaller regions less turbulence.
+It has been argued that this correlation method is not as powerful as using statistical functions \citep{1984ApJ...277..556S} but it is interesting that the index is consistent within different phases of the interstellar medium (see first paragraph of this section).
+On the other hand, we obtain \(\log \sigma\pos = (0.24 \pm 0.17) \log S - (0.24 \pm 0.38)\) which despite the large uncertainty is comparable with previous investigations.
+
+%power-law index
+Finally, as for the power-law index \(m\) we can see from table \ref{tab:RestStats} that this parameter does not correlate with any other parameter or physical property, being the least reliable parameter for determining or concluding something about the nature of the physical processes inside the regions.
 
@@
 \includegraphics[width=3in]{Figures/corr-rvsS}
-\caption{The log \(r_0\) - log \(S\) plane derived form our results an data in the literature. }
+\caption{The log \(r_0\) - log \(S\) plane derived form our results an data in the literature. Markers represent the same regions as Fig. \ref{fig:sigvsl}. }
 \label{fig:rvsR}
@@
 
-\subsubsection{Kinematic relationship between ionized gas, molecular gas, and stars}
+\subsection{Relationship between plane-of-sky and mean line-of-sight velocity dispersion}\label{sec:sigmapos-vs-sigmalos}
+
+The second-order structure function measures the velocity fluctuations in the \hii{} regions under the assumption that exists an underlying velocity spectrum following an energy cascade.
+But this statistical technique is not unique in measuring the velocity fluctuations in the nebula and does not give information on the processes disturbing the ionized gas.
+Also, as mentioned in \citet{arthur2016turbulence} the possibility if these fluctuations can account for the non-thermal line broadening needs to be evaluated.
+
+Two parameters which are obtained from the velocity profile also measure the velocity fluctuations in the \hii{} regions: the standard deviation of the velocity centroids, \(\sigma\pos\), and the mean non-thermal linewidth, \(\langle \sigma_{\text{los}} \rangle\).
+These quantities allow us to compare the relation between the kinematical disorder on the plane-of-the-sky and along the line-of-sight \citep{2011MNRAS.413..705L}.
+
+As mentioned in the introduction, the \( \sigma_{\text{los}} \) parameter is estimated by correcting the observed linewidth for the contribution of broadening mechanism, equation \eqref{eq:sigma-los}, leaving just the random motions which are interpreted as turbulence along the line-of-sigth.
+This method is a simplification of the problem since it assume a Gaussian profile fit, which does not consider other components that could arise from different kinematics of the ionized gas and leaves out the broadening due to dust scattering.
+
+In the Figure~\ref{fig:los-vs-pos} we show the mean line-of-sight velocity dispersion versus the plane-of-sky velocity dispersion. 
+\citet{arthur2016turbulence} presents the same diagram for different emission lines of the Orion core nebula showing that the value \(\sigma_{\text{los}}\) is roughly twice as the \(\sigma\pos\) (figure 14 on their work), while the \citet{2011MNRAS.413..705L} diagram, for a sample of small-to-intermediate size \hii{} regions in M33, approach unity (figure 4 on their work).
+The Figure~\ref{fig:los-vs-pos} shows that for our sample of \hii{} regions the parameters follows a \(\sigma_{\text{los}}\) = \(n \sigma_{\text{pos}}\) relation with \(3 > n > 1\).
+
+The case of the reduction in the \(\sigma\pos\) can be interpreted by the effect of \textit{project smearing} \citep{1984ApJ...277..556S}.
+If we consider the case of homogeneous turbulent velocity, the projection from three to two dimensions over the line-of-sight depth \(H\), reduces the plane-of-sky amplitude for the condition \(r_{0} < H\).
+With a value of \(\sigma\pos / \sigma_{\text{los}}\) = 0.5 we obtain \(r_{0} / H \sim\) 0.02 - 0.1.
+This procedure implies depths of the order 10 to 50 times the correlation length.
+In the lower limit \citet{arthur2016turbulence} mentioned the inconsistency of this interpretation for the Orion core nebula, since evidence has shown that the emitting layer thickness is of the order of \num{0.01} - \SI{0.3}{pc}.
+For the most distant regions of our sample, the previous analysis would give depths of the order of magnitude of the observational box, but considering the analysis using the power-law index (see section~\ref{sec:power-index}) only NGC 595, which power-law index is \num{1.38}, would comply to this fully three-dimensional structure.
+On the other hand, \citet{arthur2016turbulence} proposed another interpretation in terms of large-scale, order motions and emissivity fluctuations.
+They consider an expanding shell where the mean velocity fluctuations on the plane of the sky are because the relative brightness of the redshifted and blueshifted hemispherers.
+In this case, the rms fractional variation in the emissivity on the scale diameter is found to be in the order of \(\sigma\pos / \sigma_{\text{los}}\).
+
+As for the \citet{2011MNRAS.413..705L} results, they consider that large fluctuations of the turbulent velocities, which are spread over the entire ionized extent of the nebula, monotonically increase with the plane-of-sky dispersion.
+In this scenario, the main broadening mechanisms the kinematical disorder along the line-of-sight is related to the velocity gradients of the clumpiness in the cloud and turbulent movements.
+On the plane-of-sky the consequences of those gradients and movements is measured in every pixel, consequently the spatial variations on the velocity field would depend on the targeted pixel, at the same time depending on the motions inside the cloud.
+Thus the \(\sigma\pos\) and \(\langle \sigma_{\text{los}} \rangle\) parameters increase monotonically as the amplitudes grows because the non-thermal dynamical processes in the \hii{} regions.
+They characterize this behavior for their \hii{} regions sample by fitting a linear relation of \(\langle \sigma_{\text{los}} \rangle = (1.04 \pm 0.14) \sigma\pos + (8.15 \pm 0.93) \) to their observed regions.
+
+\begin{figure}
+\centering 
+\includegraphics[width=3in]{Figures/corr-los-vs-pos}
+\caption{
+The \(\sigma_{\text{pos}}\)-\(\langle \sigma_{\text{los}} \rangle\) plane.
+The diagonal gray solid lines shows the relation \(\sigma_{\text{los}}\) = \(\sigma_{\text{pos}}\) and \(\sigma_{\text{los}}\) = 2\(\sigma_{\text{pos}}\).
+The dashed line corresponds to the linear fit obtained by \citet{2011MNRAS.413..705L} which correspond to a sample of small-to-intermediate size \hii{} regions in M33.
+Markers represent the same regions as Fig.
+\ref{fig:sigvsl}.
+}
+\label{fig:los-vs-pos}
+\end{figure}
+
+\subsection{Kinematic relationship between ionized gas, molecular gas, and stars}
 \label{sec:kinem-rela-betw}
@@
 
-\subsection{Relationship between plane-of-sky and line-of-sight velocity dispersion}\label{sec:sigmapos-vs-sigmalos}
-
-As a justification for the use of the structure function we can consider that any relation between the line width and line-of-sight depth can be interpreted in terms of a correlation between velocity spread and scale size.
-If we have an optically thin spectral line where it will have a width which is related to the total radial velocity dispersion of all fluctuations sampled along the line-of-sight \citep{1984ApJ...277..556S}.
-The standard deviation of the velocity centroid, \(\sigma\pos\), and the mean non-thermal linewidth, \(\sigma_{\text{los}}\), allow us to compare the relation between the kinematical disorder on the plane-of-the sky and along the line-of-sight  \citep{2011MNRAS.413..705L}.
-Considering the previous statements, the structure function is used as a tool to investigate the projection of a three-dimensional correlation function onto the plane of sky \citep{arthur2016turbulence}.
-
-We can consider as a main broadening mechanisms the kinematical disorder along the LOS related to velocity gradients by the clumpiness on the cloud and turbulent movements.
-On the plane-of-sky the consequences of those gradients and movements is measured in every pixel. 
-The spatial variations on the velocity field would depend on the targeted pixel, at the same time depending on the motions inside the cloud.
-This reasoning has lead to  propose a relationship between \(\sigma_{\text{los}}\) and \(\sigma\pos\) \citep{2011MNRAS.413..705L}.
-
-In the Figure~\ref{fig:los-vs-pos} that the line-of-sight velocity dispersion is roughly twice the plane-of-sky velocity dispersion.
-In the case of homogeneous turbulent velocity we can consider the effect of \textit{project smearing} \citep{1984ApJ...277..556S}, where the projection from three to two dimensions over the line-of-sight depth \(H\), reduces the plane-of-sky amplitude for the condition \(r_{0} < H\).
-With a value of \(\sigma\pos / \sigma_{\text{los}}\) = 0.5 we obtain \(r_{0} / H \sim\) 0.02 - 0.1.
-This procedure implies depths of the order 10 to 50 times the correlation length.
-In the lower limit \citet{arthur2016turbulence} mentioned the inconsistency for Orion since evidence has show that the emitting layer thickness is of the order of \num{0.01} - \SI{0.3}{pc}.
-For the most distant regions the previous analysis would give depths of the order of magnitude of the observational box, but considering the analysis using the power-law index (section~\ref{sec:power-index}) only NGC 595, which index is \num{1.36} would comply to this three dimensional structure.
-
-\begin{figure}
-\centering 
-\includegraphics[width=3in]{Figures/corr-los-vs-pos}
-\caption{The \(\sigma_{\text{pos}}\)-\(\sigma_{\text{los}}\) plane. The dotted line represents slope equal to unity and the dashed line represents a slope of two.}
-\label{fig:los-vs-pos}
-\end{figure}
-
 \subsection{Interpretation of the turbulent parameters}\label{sec:interpretation-parameters}
@@
 This analysis should not be regarded as conclusive about the true structure of the regions and would require further observations with a combination of kinematics analysis to determine the best way to determine the depth of each region.
-As we show in section \ref{sec:sigmapos-vs-sigmalos} the ratio between \(\sigma\pos\) and \(\sigma_{\text{los}}\) can also be used to give an idea of the depth o the region.
 
@@
 For each region or pair of regions in our sample,
-we give a more description of its physical properties
+we give a more detailed description of the physical properties
 (supplementing section~\ref{sec:regions-milky-way})
 together with additional details of the structure function
-(supplementing section~\ref{sec:results}).
+(supplementing section~\ref{sec:results})
+and comparison with previous results from the literature
+(supplementing section~\ref{sec:comp-with-prev}).
 
@@
 In this case we merge the first three points of the structure function.
-%From \SI{0.002}{pc} until \SI{0.003}{pc} all points fall below the true model showing that they are affected by the seeing. 
-%The correlation length for the Orion core is \SI{0.07}{pc}, it has a \(\sigma^2\pos\) of \SI{12}{km^{2}.s^{-2}} and an index of \num{1.07}.
-The structure function of the Orion core behaves accordingly to the tapered case of inhomogeneous fluctuations (see Figure~\ref{fig:model-strucfunc}b).
-At \SI{0.25}{pc} there is a plateau around \SI{22}{km^{2}.s^{-2}}.
-Above separations of \SI{0.3}{pc} the structure function decays to a value of \SI{7}{km^{2}.s^{-2}} at  \SI{0.5}{pc}.
+A detailed description of the model fit is given in
+section~\ref{sec:example-results-orion} and will
+not be repeated here.
+At the largest scales, which are not used in the model fitting,
+one sees a downturn in the structure function from
+\SI{22}{km^{2}.s^{-2}} for \(r < \SI{0.3}{pc}\) to
+\SI{7}{km^{2}.s^{-2}} at \(r = \SI{0.5}{pc}\)
+(open symbols in Figure~\ref{fig:strucfunc-fit-Galactic}a).
+This is similar to the behavior expected for tapered fluctuations
+(see section~\ref{sec:limit-model-struct} and Figure~\ref{fig:model-strucfunc}b)
+in which the velocity dispersion is higher in the center of the map
+than in the periphery.
 
@@
 \citet{arthur2016turbulence} carried out a complete analysis by calculating the structure function of different emission lines in the inner Orion Nebula.
-They observed a tendency that higher ionization lines presents higher values on the magnitude dispersion and the steepness of the structure function slope. 
+They observed a tendency that higher ionization lines presents higher  dispersion and the steepness of the structure function slope. 
 Their results just consider one Gaussian component. 

### 2022-06-24 Corr.tex
Javier changes 2022-06-24

--- 2022-05-18 Corr.tex
@@
 \hline
- log $\sigma$ &            log L(H) &    0.27 $\pm$ 0.1 &  -9.57 $\pm$ 3.95 &   0.86 &  0.003 \\
-    log $r_0$ &             log $S$ &   0.94 $\pm$ 0.34 &  -1.67 $\pm$ 0.74 &   0.85 &  0.004 \\
- %log $\sigma$ &  log $\sigma_{LOS}$ &   0.75 $\pm$ 0.59 &  -0.15 $\pm$ 0.69 &   0.62 &   0.07 \\
- log $\sigma$ &         log $r_{0}$ &   0.17 $\pm$ 0.18 &   0.68 $\pm$ 0.13 &    0.5 &  0.168 \\
-      log $m$ &            log Dist &   -0.06 $\pm$ 0.1 &    1.11 $\pm$ 0.2 &  -0.38 &   0.32 \\
-      log $m$ &         log $r_{0}$ &  -0.03 $\pm$ 0.09 &    0.0 $\pm$ 0.06 &  -0.24 &  0.529 \\
-      log $m$ &        log $\sigma$ &  -0.12 $\pm$ 0.31 &   0.08 $\pm$ 0.23 &  -0.24 &  0.536 \\
+    log $r_0$ &       log $S$ &   0.95 $\pm$ 0.33 &  -1.68 $\pm$ 0.71 &   0.86 &  0.003 \\
+ log $\sigma$ &      log L(H) &   0.26 $\pm$ 0.11 &  -9.19 $\pm$ 4.33 &   0.86 &  0.003 \\
+ log $\sigma$ &       log $S$ &   0.24 $\pm$ 0.17 &   0.24 $\pm$ 0.38 &   0.64 &   0.06 \\
+ log $\sigma$ &   log $r_{0}$ &   0.18 $\pm$ 0.17 &   0.69 $\pm$ 0.12 &   0.51 &  0.164 \\
+      log $m$ &      log Dist &  -0.02 $\pm$ 0.04 &   0.04 $\pm$ 0.08 &   -0.4 &   0.29 \\
+      log $m$ &  log $\sigma$ &  -0.18 $\pm$ 1.03 &   0.14 $\pm$ 0.74 &  -0.37 &  0.327 \\
+      log $m$ &   log $r_{0}$ &  -0.02 $\pm$ 0.07 &   0.01 $\pm$ 0.05 &  -0.28 &  0.469 \\
 \bottomrule

### 2022-06-24 strucfunc_paper.tex
Javier changes 2022-06-24

@@
 \subsection{Comparison with previous structure functions}
-\label{sec:comp-with-prev}
+
 Comparison with prior studies is complicated by the
@@
 For each region or pair of regions in our sample,
-we give a more detailed description of the physical properties
+we give a more description of its physical properties
 (supplementing section~\ref{sec:regions-milky-way})
 together with additional details of the structure function
-(supplementing section~\ref{sec:results})
-and comparison with previous results from the literature
-(supplementing section~\ref{sec:comp-with-prev}).
+(supplementing section~\ref{sec:results}).
 
@@
 In this case we merge the first three points of the structure function.
-A detailed description of the model fit is given in
-section~\ref{sec:example-results-orion} and will
-not be repeated here.
-At the largest scales, which are not used in the model fitting,
-one sees a downturn in the structure function from
-\SI{22}{km^{2}.s^{-2}} for \(r < \SI{0.3}{pc}\) to
-\SI{7}{km^{2}.s^{-2}} at \(r = \SI{0.5}{pc}\)
-(open symbols in Figure~\ref{fig:strucfunc-fit-Galactic}a).
-This is similar to the behavior expected for tapered fluctuations
-(see section~\ref{sec:limit-model-struct} and Figure~\ref{fig:model-strucfunc}b)
-in which the velocity dispersion is higher in the center of the map
-than in the periphery.
+%From \SI{0.002}{pc} until \SI{0.003}{pc} all points fall below the true model showing that they are affected by the seeing. 
+%The correlation length for the Orion core is \SI{0.07}{pc}, it has a \(\sigma^2\pos\) of \SI{12}{km^{2}.s^{-2}} and an index of \num{1.07}.
+The structure function of the Orion core behaves accordingly to the tapered case of inhomogeneous fluctuations (see Figure~\ref{fig:model-strucfunc}b).
+At \SI{0.25}{pc} there is a plateau around \SI{22}{km^{2}.s^{-2}}.
+Above separations of \SI{0.3}{pc} the structure function decays to a value of \SI{7}{km^{2}.s^{-2}} at  \SI{0.5}{pc}.
 
@@
 \citet{arthur2016turbulence} carried out a complete analysis by calculating the structure function of different emission lines in the inner Orion Nebula.
-They observed a tendency that higher ionization lines presents higher  dispersion and the steepness of the structure function slope. 
+They observed a tendency that higher ionization lines presents higher values on the magnitude dispersion and the steepness of the structure function slope. 
 Their results just consider one Gaussian component. 

### 2022-06-24 strucfunc_paper.tex
Small addition on EON

--- 2022-06-19 strucfunc_paper.tex
@@
 \SI{22}{km^{2}.s^{-2}} for \(r < \SI{0.3}{pc}\) to
-\SI{7}{km^{2}.s^{-2}} at \(r = \SI{0.5}{pc}\)
+\SI{7}{km^{2}.s^{-2}} at \(r  \SI{0.5}{pc}\)
 (open symbols in Figure~\ref{fig:strucfunc-fit-Galactic}a).
@@
 
+Figure~\ref{fig:strucfunc-fit-Galactic}b shows the structure function of the Extended Orion Nebula, which is ten times larger than the core in linear size,
+but observed at a much lower angular resolution
+(see Figures~\ref{fig:hii-regions} and~\ref{fig:velocity-maps}).
+The data for this region are the lowest quality of all the regions in
+our sample, and there are too many degeneracies between the parameters
+to achieve a credible fit using the full model.
+We therefore fix the power slope to \(m = 1\),
+which implies that noise makes a significant contribution at all scales
+in order to reproduce the observed flat structure function.
+In turn, this implies that the true \(\sigma^2\pos = \SI{5}{km^2.s^{-2}}\),
+which is lower than the \SI{7}{km^2.s^{-2}}
+that would be naively derived from the observations
+(compare green and orange lines in Figure~\ref{fig:strucfunc-fit-Galactic}b).
+
+The seeing width is much smaller than the angular scale of the observations
 \subsubsection{Comparison with previous studies}

### 2022-06-28 Corr.tex
Javier changes 2022-06-28

@@
       log $r_0$ &         log $S$ &   0.95 $\pm$ 0.33 &  -1.68 $\pm$ 0.71 &   0.86 &  0.003 \\
- log $\sigma$ &      log L(H) &   0.26 $\pm$ 0.11 &  -9.19 $\pm$ 4.33 &   0.86 &  0.003 \\
- log $\sigma$ &       log $S$ &   0.24 $\pm$ 0.17 &   0.24 $\pm$ 0.38 &   0.64 &   0.06 \\
- log $\sigma$ &   log $r_{0}$ &   0.18 $\pm$ 0.17 &   0.69 $\pm$ 0.12 &   0.51 &  0.164 \\
+   log \(\sigma\pos\) &        log L(H\(_\alpha\)) &    0.28 $\pm$ 0.1 &  -9.87 $\pm$ 3.78 &   0.86 &  0.003 \\
+ \(\sigma\pos\) &  $\sigma_{\text{los}}$ &   1.03 $\pm$ 0.46 &     7.7 $\pm$ 2.9 &   0.79 &   0.01 \\
+   log \(\sigma\pos\) &         log $S$ &   0.25 $\pm$ 0.17 &    0.2 $\pm$ 0.38 &   0.64 &   0.06 \\
         log $m$ &        log Dist &  -0.02 $\pm$ 0.04 &   0.04 $\pm$ 0.08 &   -0.4 &   0.29 \\
-      log $m$ &  log $\sigma$ &  -0.18 $\pm$ 1.03 &   0.14 $\pm$ 0.74 &  -0.37 &  0.327 \\
-      log $m$ &   log $r_{0}$ &  -0.02 $\pm$ 0.07 &   0.01 $\pm$ 0.05 &  -0.28 &  0.469 \\
+       \(\sigma\pos\) &         $r_{0}$ &    0.4 $\pm$ 0.65 &   4.68 $\pm$ 3.08 &   0.37 &  0.329 \\
+            $m$ &        \(\sigma\pos\) &  -0.02 $\pm$ 0.03 &   1.12 $\pm$ 0.21 &  -0.37 &  0.331 \\
+            $m$ &         $r_{0}$ &   0.02 $\pm$ 0.03 &   0.95 $\pm$ 0.16 &  -0.09 &  0.824 \\
 \bottomrule

### 2022-06-28 strucfunc_paper.tex
Javier changes 2022-06-28

@@
 \newcommand\csound{\ensuremath{c_{\text{s}}}}
+\newcommand\FNa{\textsuperscript{a}}
 
@@
 \midrule
-Orion     & 0.436 \pm 0.02  & 5 \pm 0.5    &    37.18       &   6 \pm 1      \\
-Lagoon    & 1.25 \pm 0.12   & 25 \pm 2.5      &    37.47    &   13.6 \pm 0.8    \\
-Carina    & 2.35 \pm 0.05   & 200 \pm 20      &    38.54    &   22.4 \pm 2.7    \\
-30 Dor    & 50.0 \pm 0.2    & 370 \pm 37    &    39.46    &   31.7     \\
-NGC 346   & 62 \pm 1        & 220 \pm 22      &    38.77    &   10.1     \\
-Hubble X  & 490 \pm 40      & 160 \pm 16      &    38.21    &   13.4     \\
-Hubble V  & 490 \pm 40      & 130 \pm 13      &    38.3     &   12.3     \\
-NGC 595   & 820 \pm 30      & 400 \pm 40      &    38.95    &   18.3 \pm 5.7     \\
-NGC 604   & 820 \pm 30      & 400 \pm 40      &    39.42    &   16.2 \pm 7.7     \\
+Orion     & 0.436 \pm 0.02  & 5 \pm 0.5    &    37.18       &   9.9 \pm 1.2\FNa        \\
+Lagoon    & 1.25 \pm 0.12   & 25 \pm 2.5      &    37.47    &   11.7 \pm 1.6    \\
+Carina    & 2.35 \pm 0.05   & 200 \pm 20      &    38.54    &   18.6 \pm 3.3\FNa      \\
+30 Dor    & 50.0 \pm 0.2    & 370 \pm 37    &    39.46    &   22 \pm 2.2    \\
+NGC 346   & 62 \pm 1        & 220 \pm 22      &    38.77    &   10.1 \pm 1.0     \\
+Hubble X  & 490 \pm 40      & 160 \pm 16      &    38.21    &   10.5 \pm 0.02\\
+Hubble V  & 490 \pm 40      & 130 \pm 13      &    38.3     &   10.3 \pm 0.03     \\
+NGC 595   & 820 \pm 30      & 400 \pm 40      &    38.95    &   16.8 \pm 0.1     \\
+NGC 604   & 820 \pm 30      & 400 \pm 40      &    39.42    &   17.8 \pm 0.30     \\
 \bottomrule
+\multicolumn{5}{l}{\FNa{}Value obtained from our observations.}
 \end{tabular}\label{tab:regions-properties}
@@
 
-Table~\ref{tab:regions-properties} summarises the properties of the regions in our sample
-with data taken from the literature. Further details on each individual source is given in Appendix~\ref{sec:notes-individual-hii}.
+Table~\ref{tab:regions-properties} summarizes the properties of the regions in our sample
+with data taken from the literature. Further details on each individual source and references are given in Appendix~\ref{sec:notes-individual-hii}.
 
@@
 We use the physical properties in Table \ref{tab:regions-properties} as the independent variable \(X\) and the turbulent parameters in Table \ref{tab:Res} as the dependent variable \(Y\).
-In the following analysis we left out the EON to avoid redundancy in the fitting.
-For the physical properties we consider an uncertainty of the \num{10}\% of the value and for the turbulent parameters we use the 2-\(\sigma\) intervals. 
+In the following analysis we left out the EON to avoid redundancy in the fitting process.
+For the physical properties we consider an uncertainty of \num{10}\% of the values for the size and the mean non-thermal linewidths for 30 Doradus and NGC 346.
+For the turbulent parameters we use the relative error considering the 2-\(\sigma\) intervals. 
 In the case of non-gaussian distribution we choose the highest value for the uncertainty.
 The main results are shown in Table \ref{tab:RestStats} in ascending order for the \(p\)-value.
-In the Figures \ref{fig:sigvsl} and \ref{fig:rvsR} we show the correlations with a significance level \(p < \num{0.05}\) which corresponds to the first two rows in Table \ref{tab:RestStats}.
-In the Figures the black solid line shows the input regression line and the red thin lines show some samples from the posterior distribution.
+In the Figures \ref{fig:sigvsl}, \ref{fig:rvsR} and \ref{fig:los-vs-pos} we show the plots for the correlations with a significance level \(p < \num{0.05}\) which corresponds to the first three rows in Table \ref{tab:RestStats}.
+In the Figures the black solid line shows the input regression line with its equation and the red thin lines show some samples from the posterior distribution.
 
@@
 The Figure \ref{fig:sigvsl} shows the log \(\sigma\pos\)-log \(\text{L}(\text{H}_{\alpha})\) plane.
+The references for the \(\text{L}(\text{H}_{\alpha})\) value are given in Appendix~\ref{sec:notes-individual-hii}.
 Since this relation is the most common it can be use for comparison with the investigations mentioned at the beginning of this section.
-Our results give us a relation of \(\log \sigma\pos = (0.26 \pm 0.11) \log \text{L}(\text{H}_{\alpha})-(9.3 \pm 4.3)\).
+Our results give us a relation of \(\log \sigma\pos = (0.27 \pm 0.10) \log \text{L}(\text{H}_{\alpha})-(9.9 \pm 4.0)\).
 It is customary in the literature to present \(\text{L} (\text{H}_{\alpha})\) as the dependent variable.
-In our case if we choose the upper uncertainty and take the inverse of slope we have \(\text{L}_{\text{H}_{\alpha}} \propto \sigma^{2.6}\). 
-Using the same procedure in \textit{linmix} and changing the variables order we obtained \(\log \text{L}(\text{H}_{\alpha}) = (3.9\pm 2.6) \log \sigma\pos -(35.55 \pm 2)\) which is within the uncertainty of the previously proposed \(\text{L}_{\text{H}} \propto \sigma^{4}\) relations.
-The references for the \(\text{L}(\text{H}_{\alpha})\) value are given in Appendix~\ref{sec:notes-individual-hii}.
+In our case if taking the inverse of slope we have \(\text{L}_{\text{H}_{\alpha}} \propto \sigma^{3.6}\). 
+Using the same procedure in \textit{linmix} and changing the variables order we obtained \(\log \text{L}(\text{H}_{\alpha}) = (2.8\pm 1.0) \log \sigma\pos -(36 \pm 4)\).
+Both values are close to the \(\text{L}_{\text{H}} \propto \sigma^{4}\) relations.
+The fact that this relation
 
@@
 Other important relation commonly used in the study of the interstellar medium is the diameter (or size) versus velocity dispersion.
-Table \ref{tab:RestStats} shows this result for our sample in row 3. 
+Table \ref{tab:RestStats} shows this result for our sample in the forth row. 
 This relation presents a significance level \(p > \num{0.05}\) but there are a couple of things worth mentioning.
@@
 It has been argued that this correlation method is not as powerful as using statistical functions \citep{1984ApJ...277..556S} but it is interesting that the index is consistent within different phases of the interstellar medium (see first paragraph of this section).
-On the other hand, we obtain \(\log \sigma\pos = (0.24 \pm 0.17) \log S - (0.24 \pm 0.38)\) which despite the large uncertainty is comparable with previous investigations.
+On the other hand, we obtain \(\log \sigma\pos = (0.25 \pm 0.17) \log S - (0.2 \pm 0.38)\) which despite the large uncertainty is comparable with previous investigations within the error.
 
 %power-law index
-Finally, as for the power-law index \(m\) we can see from table \ref{tab:RestStats} that this parameter does not correlate with any other parameter or physical property, being the least reliable parameter for determining or concluding something about the nature of the physical processes inside the regions.
+As for the power-law index \(m\) we can see from table \ref{tab:RestStats} that this parameter does not correlate with any other parameter or physical property, being the least reliable for determining or concluding something about the nature of the physical processes inside the regions.
+On the other hand, the lack of correlation and the presence of the power-law index may be interpreted as a universal property of the velocity fluctuations independent of the observed object, which is the main consideration in the turbulence theory.
 
@@
 
-\subsection{Relationship between plane-of-sky and mean line-of-sight velocity dispersion}\label{sec:sigmapos-vs-sigmalos}
+\subsubsection{Relationship between plane-of-sky and mean line-of-sight velocity dispersion}\label{sec:sigmapos-vs-sigmalos}
 
@@
 In the Figure~\ref{fig:los-vs-pos} we show the mean line-of-sight velocity dispersion versus the plane-of-sky velocity dispersion. 
-\citet{arthur2016turbulence} presents the same diagram for different emission lines of the Orion core nebula showing that the value \(\sigma_{\text{los}}\) is roughly twice as the \(\sigma\pos\) (figure 14 on their work), while the \citet{2011MNRAS.413..705L} diagram, for a sample of small-to-intermediate size \hii{} regions in M33, approach unity (figure 4 on their work).
-The Figure~\ref{fig:los-vs-pos} shows that for our sample of \hii{} regions the parameters follows a \(\sigma_{\text{los}}\) = \(n \sigma_{\text{pos}}\) relation with \(3 > n > 1\).
+\citet{arthur2016turbulence} presents the same diagram for different emission lines of the Orion core nebula showing that the value \(\sigma_{\text{los}}\) (after considering the dust scattering) is roughly twice as the \(\sigma\pos\) (figure 14 on their work), while the \citet{2011MNRAS.413..705L} diagram, for a sample of small-to-intermediate size \hii{} regions in M33, approach unity (figure 4 on their work).
+The Figure~\ref{fig:los-vs-pos} shows that for our sample of \hii{} regions the fit we obtained follows the result of \citet{2011MNRAS.413..705L}.
+The relationship we found is \( \langle \sigma\los \rangle = (1.03 \pm 0.46) \sigma\pos - (7.7 \pm 2.9)\).
 
@@
 For the most distant regions of our sample, the previous analysis would give depths of the order of magnitude of the observational box, but considering the analysis using the power-law index (see section~\ref{sec:power-index}) only NGC 595, which power-law index is \num{1.38}, would comply to this fully three-dimensional structure.
-On the other hand, \citet{arthur2016turbulence} proposed another interpretation in terms of large-scale, order motions and emissivity fluctuations.
+On the other hand, \citet{arthur2016turbulence} proposed another interpretation in terms of large-scale order motions, and emissivity fluctuations.
 They consider an expanding shell where the mean velocity fluctuations on the plane of the sky are because the relative brightness of the redshifted and blueshifted hemispherers.
@@
 The Lagoon Nebula (M8, NGC6523) is located at a distance of 1 250 pc \citetext{\SI{1}{\arcsecond} = \SI{0.006}{pc} ; \citealp{2005A&A...430..941P}}.
-It has a luminosity in \ha{} of \SI{e37.47}{erg.s^{-1}}\citep{1984ApJ...287..116K}.
+It has a luminosity in \ha{} of \SI{e37.47}{erg.s^{-1}} \citep{1984ApJ...287..116K}.
+The mean non-thermal linewidth in \ha{} is \SI{11.7 \pm 1.6}{km.s^{-1}} \citep{1973ApJ...183..851B}.
 It contains the young stellar cluster NGC6530 and the region is illuminated by different massive stars of spectral types O and B, the hottest being 9 Sgr, type O4V \citep{Damiani:2017b}.
@@
 The ionizing output \(Q_0\) of R136 is \SI{e51.4}{photons.s^{-1}} \citep{2020MNRAS.499.1918B}.
+The mean non-thermal linewidth in \ha{} is \SI{22}{km.s^{-1}} \citep{2013A&A...555A..60T}.
 It host the active star forming region NGC 2070 \citep{2013AJ....145...98W} where the star-formation rate has recently peaked \citep{2015ApJ...811...76C}. 
@@
 %(1'' = 2.4 pc)
-%HV has a characteristic length of 100 pc and HX has a characteristic length of 140 pc \citep{1999PASP..111.1382O}.
 Luminosity \ha{} for HV is \SI{e38.3}{erg.s^{-1}} and for HX is \SI{e38.21}{erg.s^{-1}} \citep{2002MNRAS.329..481B}.
+The mean non-thermal linewidth in \ha{} is \SI{10.5 \pm 0.02}{km.s^{-1}} for HX and \SI{10.3 \pm 0.03}{km.s^{-1}} \citep{1986A&A...160..374H}.
 Two recognized OB associations are identified within these HII regions \citep{1991ApJ...379..621H,1992AJ....104.1374W}.
@@
 \citet{1993PASJ...45..693T} realize a study on the kinematics of HX and HV.
-
-%HV has a luminosity at its core of in L$_{H_\alpha}$ = 1 $\times$ 10$^{49}$ H$\alpha$ photons s$^{-1}$ 
-%HX has a luminosity at its core of in L$_{H_\alpha}$ = 2.4 $\times$ 10$^{49}$ H$\alpha$ photons s$^{-1}$ \citep{1999PASP..111.1382O}.
 
@@
 It has a luminosity in \ha{} of \SI{e39.42}{erg.s^{-1}} \citep{2002MNRAS.329..481B}.
+The mean non-thermal linewidth in \ha{} is \SI{17.8 \pm 0.3}{km.s^{-1}} \citep{1986A&A...160..374H}.
 Using photometry from the HST \citet{1996ApJ...456..174H} identified that the stars are separated into a primary cluster within NGC 604, and a secondary to the north of the region.
@@
 It has a luminosity in \ha{} of \SI{e38.95}{erg.s^{-1}}\citep{2002MNRAS.329..481B}.
+The mean non-thermal linewidth in \ha{} is \SI{16.8 \pm 0.1}{km.s^{-1}} \citep{lagrois2009multi}.
 \citet{1993AJ....105.1400D} use optical photometry to propose 11 WR stars. 

### 2022-06-28 strucfunc_paper.tex
Updates from Overleaf

@@
 Using the same procedure in \textit{linmix} and changing the variables order we obtained \(\log \text{L}(\text{H}_{\alpha}) = (2.8\pm 1.0) \log \sigma\pos -(36 \pm 4)\).
-Both values are close to the \(\text{L}_{\text{H}} \propto \sigma^{4}\) relations.
-The fact that this relation
+Both values are close to the \(\text{L}_{\text{H}} \propto \sigma^{4}\) theoretical relation.
+The fact that this relationship holds in our results is of importance considering that the \(\sigma\pos\) is obtained using the structure function.
+This means that the proposed model describes
 

### 2022-06-29 Corr.tex
Javier changes 2022-06-28 evening

--- 2022-06-24 Corr.tex
@@
 \hline
-    log $r_0$ &       log $S$ &   0.95 $\pm$ 0.33 &  -1.68 $\pm$ 0.71 &   0.86 &  0.003 \\
- log $\sigma$ &      log L(H) &   0.26 $\pm$ 0.11 &  -9.19 $\pm$ 4.33 &   0.86 &  0.003 \\
- log $\sigma$ &       log $S$ &   0.24 $\pm$ 0.17 &   0.24 $\pm$ 0.38 &   0.64 &   0.06 \\
- log $\sigma$ &   log $r_{0}$ &   0.18 $\pm$ 0.17 &   0.69 $\pm$ 0.12 &   0.51 &  0.164 \\
-      log $m$ &      log Dist &  -0.02 $\pm$ 0.04 &   0.04 $\pm$ 0.08 &   -0.4 &   0.29 \\
-      log $m$ &  log $\sigma$ &  -0.18 $\pm$ 1.03 &   0.14 $\pm$ 0.74 &  -0.37 &  0.327 \\
-      log $m$ &   log $r_{0}$ &  -0.02 $\pm$ 0.07 &   0.01 $\pm$ 0.05 &  -0.28 &  0.469 \\
+      log $r_0$ &         log $D$ &   0.94 $\pm$ 0.33 &  -1.66 $\pm$ 0.72 &   0.86 &  0.003 \\
+   log \(\sigma\pos\) &        log L(H) &    0.28 $\pm$ 0.1 &  -9.86 $\pm$ 3.71 &   0.86 &  0.003 \\
+ \(\sigma\pos\) &  $\sigma_{\text{los}}$ &   1.03 $\pm$ 0.44 &   7.35 $\pm$ 2.83 &   0.78 &   0.01 \\
+   log \(\sigma\pos\) &         log $D$ &   0.26 $\pm$ 0.18 &   0.19 $\pm$ 0.39 &   0.64 &   0.06 \\
+        log $m$ &        log distance &  -0.02 $\pm$ 0.04 &   0.04 $\pm$ 0.08 &   -0.4 &   0.29 \\
+       \(\sigma\pos\) &         $r_{0}$ &    0.4 $\pm$ 0.69 &   4.61 $\pm$ 3.25 &   0.37 &  0.329 \\
+            $m$ &        \(\sigma\pos\) &  -0.01 $\pm$ 0.03 &   1.12 $\pm$ 0.21 &  -0.37 &  0.331 \\
+            $m$ &         $r_{0}$ &   0.02 $\pm$ 0.03 &   0.96 $\pm$ 0.16 &  -0.09 &  0.824 \\
 \bottomrule

### 2022-06-29 strucfunc_paper.tex
Javier changes 2022-06-28 evening

--- 2022-06-28 strucfunc_paper.tex
@@
 \begin{table}
-\begin{center}\caption{Summary of properties of our \hii{} region sample. Sizes taken from Table 2 of \citet{1984ApJ...287..116K}. Reference from the other properties are mentioned in the text.}
+\begin{center}\caption{Summary of properties of our \hii{} region sample.
+Diameters taken from Table 2 of \citet{1984ApJ...287..116K}.
+Mean non-thermal linewidth values, \(\langle \sigma\los \rangle\), shown here are corrected considering equation \eqref{eq:sigma-los} which takes into account \(\sigma_{\mathrm{fs}}\).
+Non-corrected \(\langle \sigma\los \rangle\) values and other properties references are mentioned in the text.
+}
 \begin{tabular}{cCCCC}\toprule
-\hii{}    &  \text{Distance,}\ d& \text{Size,}\ S & \log L(\ha) &  \langle \sigma\los \rangle \\
+\hii{}    &  \text{Distance} & \text{Diameter,}\ D & \log L(\ha) &  \langle \sigma\los \rangle \\
   Region    &  [\si{kpc}]          &  [\si{pc}]    &  [\si{erg.s^{-1}}]            &    [\si{km.s^{-1}}]  \\ 
@@
 Orion     & 0.436 \pm 0.02  & 5 \pm 0.5    &    37.18       &    9.9 \pm 1.2\FNa        \\
-Lagoon    & 1.25 \pm 0.12   & 25 \pm 2.5      &    37.47    &   11.7 \pm 1.6    \\
+Lagoon    & 1.25 \pm 0.12   & 25 \pm 2.5      &    37.47    &   11.2 \pm 1.6    \\
 Carina    & 2.35 \pm 0.05   & 200 \pm 20      &    38.54    &   18.6 \pm 3.3\FNa      \\
-30 Dor    & 50.0 \pm 0.2    & 370 \pm 37    &    39.46    &   22 \pm 2.2    \\
-NGC 346   & 62 \pm 1        & 220 \pm 22      &    38.77    &   10.1 \pm 1.0     \\
-Hubble X  & 490 \pm 40      & 160 \pm 16      &    38.21    &   10.5 \pm 0.02\\
-Hubble V  & 490 \pm 40      & 130 \pm 13      &    38.3     &   10.3 \pm 0.03     \\
-NGC 595   & 820 \pm 30      & 400 \pm 40      &    38.95    &   16.8 \pm 0.1     \\
-NGC 604   & 820 \pm 30      & 400 \pm 40      &    39.42    &   17.8 \pm 0.30     \\
+30 Dor    & 50.0 \pm 0.2    & 370 \pm 37    &    39.46    &     21.7 \pm 2.2    \\
+NGC 346   & 62 \pm 1        & 220 \pm 22      &    38.77    &    9.6 \pm 1.0     \\
+Hubble X  & 490 \pm 40      & 160 \pm 16      &    38.21    &   10.0 \pm 0.02\\
+Hubble V  & 490 \pm 40      & 130 \pm 13      &    38.3     &    9.8 \pm 0.03     \\
+NGC 595   & 820 \pm 30      & 400 \pm 40      &    38.95    &   16.5 \pm 0.1     \\
+NGC 604   & 820 \pm 30      & 400 \pm 40      &    39.42    &   17.5 \pm 0.30     \\
 \bottomrule
@@
 %Intro for scaling relations
+\textit{Maybe this paragraph it not necessary. Just a small intro and if needed previous results can be in a table for comparison. }
 Correlations between the physical properties of \hii{} regions like size, luminosity, and the velocity dispersion, have been used as tools for finding scaling relationships for these objects, which have also been found in dwarf galaxies and high-redshift star formation regions.
@@
 In the Figures \ref{fig:sigvsl}, \ref{fig:rvsR} and \ref{fig:los-vs-pos} we show the plots for the correlations with a significance level \(p < \num{0.05}\) which corresponds to the first three rows in Table \ref{tab:RestStats}.
-In the Figures the black solid line shows the input regression line with its equation and the red thin lines show some samples from the posterior distribution.
-
-%Luminosity vs centroid velocity dispersion
-The Figure \ref{fig:sigvsl} shows the log \(\sigma\pos\)-log \(\text{L}(\text{H}_{\alpha})\) plane.
-The references for the \(\text{L}(\text{H}_{\alpha})\) value are given in Appendix~\ref{sec:notes-individual-hii}.
-Since this relation is the most common it can be use for comparison with the investigations mentioned at the beginning of this section.
-Our results give us a relation of \(\log \sigma\pos = (0.27 \pm 0.10) \log \text{L}(\text{H}_{\alpha})-(9.9 \pm 4.0)\).
-It is customary in the literature to present \(\text{L} (\text{H}_{\alpha})\) as the dependent variable.
-In our case if taking the inverse of slope we have \(\text{L}_{\text{H}_{\alpha}} \propto \sigma^{3.6}\). 
-Using the same procedure in \textit{linmix} and changing the variables order we obtained \(\log \text{L}(\text{H}_{\alpha}) = (2.8\pm 1.0) \log \sigma\pos -(36 \pm 4)\).
-Both values are close to the \(\text{L}_{\text{H}} \propto \sigma^{4}\) relations.
-The fact that this relation
-
-%Size vs correlation length
-The Figure \ref{fig:rvsR} shows the relation of the correlation length \(r_0\) and the size \(S\) of the region. 
-The relationship we found is \(\log r_0 = (0.95 \pm 0.33) \log S - (1.6 \pm 0.7)\).
-The values of \(S\) are taken from \citet{1984ApJ...287..116K} and correspond to the outer
-limits seen from visual inspection of \ha{} photographs.
-These values would represent an upper limit of the size of each region.
-Since these objects do not posses physical edges the size determination is not trivial.
-Due to the above, we chose these set values since they are from an unique source and are foreign to our calculations and observations, which reduced the bias in the scaling law we obtain.
-
-%Size vs centroid velocity dispersion
-Other important relation commonly used in the study of the interstellar medium is the diameter (or size) versus velocity dispersion.
-Table \ref{tab:RestStats} shows this result for our sample in the forth row. 
-This relation presents a significance level \(p > \num{0.05}\) but there are a couple of things worth mentioning.
-Historically this relation is important following the work of \citet{1981MNRAS.194..809L} where he presents it in the context of molecular cloud complexes of many clouds, individual clouds, and clumps, so that size scales are studied over \(\num{0.1} < L < \SI{100}{pc}\) obtaining \(\sigma = 1.10 L ^{0.38}\).
-This relation is interpreted in terms of turbulence, particularly the Kolmogorov model which predicts a index of \num{0.33} so that larger regions presents more turbulence, and smaller regions less turbulence.
-It has been argued that this correlation method is not as powerful as using statistical functions \citep{1984ApJ...277..556S} but it is interesting that the index is consistent within different phases of the interstellar medium (see first paragraph of this section).
-On the other hand, we obtain \(\log \sigma\pos = (0.25 \pm 0.17) \log S - (0.2 \pm 0.38)\) which despite the large uncertainty is comparable with previous investigations within the error.
-
-%power-law index
-As for the power-law index \(m\) we can see from table \ref{tab:RestStats} that this parameter does not correlate with any other parameter or physical property, being the least reliable for determining or concluding something about the nature of the physical processes inside the regions.
-On the other hand, the lack of correlation and the presence of the power-law index may be interpreted as a universal property of the velocity fluctuations independent of the observed object, which is the main consideration in the turbulence theory.
+In the Figures the black solid line is the input regression line which is described by the equation in the plot, and the red thin lines are a random sample (\num{ \sim 400}) from the posterior distribution within one standard deviation from the slope and the \(Y\)-intercept value.
 
@@
 The markers indicates galactic (triangles), Magellanic (squares) and extragalactic (circles) regions.
+The black solid line is the input regression line which is described by the equation in the plot, and the red thin lines are a random sample (\num{ \sim 400}) from the posterior distribution within one standard deviation from the slope and the \(Y\)-intercept value.
 }
@@
 \includegraphics[width=3in]{Figures/corr-rvsS}
-\caption{The log \(r_0\) - log \(S\) plane derived form our results an data in the literature. Markers represent the same regions as Fig. \ref{fig:sigvsl}. }
+\caption{
+Same information as Fig. \ref{fig:sigvsl} but for the log \(r_0\) - log \(S\) plane derived form our results an data in the literature. 
+}
 \label{fig:rvsR}
 \end{figure}
-
-\subsubsection{Relationship between plane-of-sky and mean line-of-sight velocity dispersion}\label{sec:sigmapos-vs-sigmalos}
-
-The second-order structure function measures the velocity fluctuations in the \hii{} regions under the assumption that exists an underlying velocity spectrum following an energy cascade.
-But this statistical technique is not unique in measuring the velocity fluctuations in the nebula and does not give information on the processes disturbing the ionized gas.
-Also, as mentioned in \citet{arthur2016turbulence} the possibility if these fluctuations can account for the non-thermal line broadening needs to be evaluated.
-
-Two parameters which are obtained from the velocity profile also measure the velocity fluctuations in the \hii{} regions: the standard deviation of the velocity centroids, \(\sigma\pos\), and the mean non-thermal linewidth, \(\langle \sigma_{\text{los}} \rangle\).
-These quantities allow us to compare the relation between the kinematical disorder on the plane-of-the-sky and along the line-of-sight \citep{2011MNRAS.413..705L}.
-
-As mentioned in the introduction, the \( \sigma_{\text{los}} \) parameter is estimated by correcting the observed linewidth for the contribution of broadening mechanism, equation \eqref{eq:sigma-los}, leaving just the random motions which are interpreted as turbulence along the line-of-sigth.
-This method is a simplification of the problem since it assume a Gaussian profile fit, which does not consider other components that could arise from different kinematics of the ionized gas and leaves out the broadening due to dust scattering.
-
-In the Figure~\ref{fig:los-vs-pos} we show the mean line-of-sight velocity dispersion versus the plane-of-sky velocity dispersion. 
-\citet{arthur2016turbulence} presents the same diagram for different emission lines of the Orion core nebula showing that the value \(\sigma_{\text{los}}\) (after considering the dust scattering) is roughly twice as the \(\sigma\pos\) (figure 14 on their work), while the \citet{2011MNRAS.413..705L} diagram, for a sample of small-to-intermediate size \hii{} regions in M33, approach unity (figure 4 on their work).
-The Figure~\ref{fig:los-vs-pos} shows that for our sample of \hii{} regions the fit we obtained follows the result of \citet{2011MNRAS.413..705L}.
-The relationship we found is \( \langle \sigma\los \rangle = (1.03 \pm 0.46) \sigma\pos - (7.7 \pm 2.9)\).
-
-The case of the reduction in the \(\sigma\pos\) can be interpreted by the effect of \textit{project smearing} \citep{1984ApJ...277..556S}.
-If we consider the case of homogeneous turbulent velocity, the projection from three to two dimensions over the line-of-sight depth \(H\), reduces the plane-of-sky amplitude for the condition \(r_{0} < H\).
-With a value of \(\sigma\pos / \sigma_{\text{los}}\) = 0.5 we obtain \(r_{0} / H \sim\) 0.02 - 0.1.
-This procedure implies depths of the order 10 to 50 times the correlation length.
-In the lower limit \citet{arthur2016turbulence} mentioned the inconsistency of this interpretation for the Orion core nebula, since evidence has shown that the emitting layer thickness is of the order of \num{0.01} - \SI{0.3}{pc}.
-For the most distant regions of our sample, the previous analysis would give depths of the order of magnitude of the observational box, but considering the analysis using the power-law index (see section~\ref{sec:power-index}) only NGC 595, which power-law index is \num{1.38}, would comply to this fully three-dimensional structure.
-On the other hand, \citet{arthur2016turbulence} proposed another interpretation in terms of large-scale order motions, and emissivity fluctuations.
-They consider an expanding shell where the mean velocity fluctuations on the plane of the sky are because the relative brightness of the redshifted and blueshifted hemispherers.
-In this case, the rms fractional variation in the emissivity on the scale diameter is found to be in the order of \(\sigma\pos / \sigma_{\text{los}}\).
-
-As for the \citet{2011MNRAS.413..705L} results, they consider that large fluctuations of the turbulent velocities, which are spread over the entire ionized extent of the nebula, monotonically increase with the plane-of-sky dispersion.
-In this scenario, the main broadening mechanisms the kinematical disorder along the line-of-sight is related to the velocity gradients of the clumpiness in the cloud and turbulent movements.
-On the plane-of-sky the consequences of those gradients and movements is measured in every pixel, consequently the spatial variations on the velocity field would depend on the targeted pixel, at the same time depending on the motions inside the cloud.
-Thus the \(\sigma\pos\) and \(\langle \sigma_{\text{los}} \rangle\) parameters increase monotonically as the amplitudes grows because the non-thermal dynamical processes in the \hii{} regions.
-They characterize this behavior for their \hii{} regions sample by fitting a linear relation of \(\langle \sigma_{\text{los}} \rangle = (1.04 \pm 0.14) \sigma\pos + (8.15 \pm 0.93) \) to their observed regions.
 
@@
 \caption{
-The \(\sigma_{\text{pos}}\)-\(\langle \sigma_{\text{los}} \rangle\) plane.
-The diagonal gray solid lines shows the relation \(\sigma_{\text{los}}\) = \(\sigma_{\text{pos}}\) and \(\sigma_{\text{los}}\) = 2\(\sigma_{\text{pos}}\).
+Same information as Fig.
+\ref{fig:sigvsl} but for the \(\sigma_{\text{pos}}\)-\(\langle \sigma_{\text{los}} \rangle\) plane.
 The dashed line corresponds to the linear fit obtained by \citet{2011MNRAS.413..705L} which correspond to a sample of small-to-intermediate size \hii{} regions in M33.
-Markers represent the same regions as Fig.
-\ref{fig:sigvsl}.
 }
@@
 
-\subsection{Kinematic relationship between ionized gas, molecular gas, and stars}
-\label{sec:kinem-rela-betw}
-
-Naively, the relatively small observed CO velocity dispersion
-(\(\sigma(\chem{CO}) \ll \sigma(\ha)\) in all regions
-for both \(\sigma\los\) and \(\sigma\pos\))
-might be thought to rule out the molecular gas kinematics
-as a \emph{cause} of the ionized gas kinematics.
-However, this is not necessarily the case, so long as \emph{some} molecular gas
-exists at the higher velocities typical of the ionized gas.
-
-This is because a relatively small column of material
-(\(N(\chem{H}) \sim \SI{e20}{cm^{-2}}\))
-is sufficient to trap the ionization front,
-in which case the \ha{} surface brightness is limited by the
-incident ionizing flux
-\citetext{the Ferland mechanism,
-  see section~5.1 of \citealt{Baldwin:1991a}
-  and section~B.2.1 of \citealt{Ferland:2012a}
-}.
-On the other hand, the bulk of the CO emission will come from much larger
-column densities (\(N(\chem{H}) \sim \SI{e22}{cm^{-2}}\)),
-where the molecules are effectively shielded from dissociation.
-% If a given region can be considered as an ensemble of clouds of
-% different masses, then ... would require lower mass clouds to move
-% faster though, so needs dynamical relaxation
-
-\textbf{Check  if this is actually feasible before developing further}
-
-Very schematically, one could represent these processes as:
-\begin{equation}
-  \label{eq:1}
-  \sigma^2(\ha) \sim \zeta \sigma^2(\chem{CO}) + \eta
-\end{equation}
-where \(\zeta\) is a multiplicative factor
-due primarily to the saturation at the Ferland limit,
-and \(\eta \sim \csound^2\) is an additive factor due to additional turbulence
-generated by the transonic ionized photoevaporation flows.
-
-\textbf{Estimate these two factors by fitting to the observations}
-
-\subsection{Interpretation of the turbulent parameters}\label{sec:interpretation-parameters}
-
-\subsubsection{Correlation length \(r_0\)}
+\subsubsection{Luminosity vs centroid velocity dispersion}\label{sec:L-vs-sigmapos}
+
+The Figure \ref{fig:sigvsl} shows the log \(\sigma\pos\)-log \(\text{L}(\text{H}_{\alpha})\) plane.
+Since this relation is common in the literature it can be use to investigate how reliable are our results and can be used as comparison with the previous investigations.
+The fit we obtained give us a relation of \(\log \sigma\pos = (0.27 \pm 0.10) \log \text{L}(\text{H}_{\alpha})-(9.9 \pm 4.0)\).
+Since it is customary in the literature to present \(\text{L} (\text{H}_{\alpha})\) as the dependent variable we also calculate this relation.
+Taking the inverse of slope we have \(\text{L}_{\text{H}_{\alpha}} \propto \sigma^{3.6 \pm 1.4}\). 
+Using the same procedure in \textit{linmix} and changing the variables we obtain \(\log \text{L}(\text{H}_{\alpha}) = (2.8\pm 1.0) \log \sigma\pos -(36 \pm 4)\).
+Both results are close to the \(\text{L}_{\text{H}} \propto \sigma^{4}\) theoretical relation.
+
+The fact that this relationship holds in our results is interesting considering that the \(\sigma\pos\) is obtained using the structure function and the \(\text{L}(\text{H}_{\alpha})\) values comes from different sources unrelated to oour data (see the Appendix~\ref{sec:notes-individual-hii}).
+This means that the proposed model describes within certain accuracy the velocity field fluctuations and that the parameters obtained can be interpreted a true property of each \hii{} region velocity field .
+
+\subsubsection{Diameter vs correlation length}\label{sec:D-vs-r0}
+
+The Figure \ref{fig:rvsR} shows the relation of the correlation length \(r_0\) and the diameter \(D\) of the region. 
+The relationship we found is \(\log r_0 = (0.95 \pm 0.33) \log S - (1.6 \pm 0.7)\).
+The values of \(D\) are taken from \citet{1984ApJ...287..116K} and correspond to the outer
+limits seen from visual inspection of \ha{} photographs.
+These values would represent an upper limit of the size of each region.
+Since these objects do not posses physical edges the size determination is not trivial.
+Due to the above, we chose these set values since they are from an unique source and are foreign to our calculations and observations, which reduced the bias in the scaling law we obtain.
 
@@
 Many of these mechanisms, at some extent, affect all the \hii{} regions studied in this work.
-We can use the kinematic analysis of the regions to investigate how previously identified energy injection mechanisms could be related to the correlation length.
-
-\citet{2009AJ....137..367O} present a three-dimensional study of the dynamic structure of the Orion nebula.
-The high-velocity stellar wind from \(\theta^1\) Ori C will confine the ionized gas, even the high ionization emission lines, to a thick shell.
-In one direction, at a distance of \SI{0.1}{pc} from the ionizing massive star a stationary shell of shocked material is formed when the ram pressure of the photoevaportation flow balances the thermal pressure of the shocked wind.
-In the other direction there is a free flow of the hypersonic wind.
-At a smaller scale of \SI{0.02}{pc} there is an interaction between the closest proplyd photoevaporation flow and the stellar wind which results in bowshocks.
-According to \citet{2001ApJ...561..830G} the influence of stellar wind interactions is restricted to the central \SI{0.05}{pc}. 
-Orion also present a champagne flow where the photoionized gas streams away from the ionization front covering a distance of \SI{\sim 1}{pc} from the molecular cloud \citep{1973ApJ...183..863Z}.
-
-Our correlation length results for the Orion Core and EON from table~\ref{tab:Res}, \num{0.068} y \SI{0.39}{pc} respectively, despite been of the order of the scales mentioned above still aren't conclusive enough to determine a direct relation between them.
-As mentioned in \citet{arthur2016turbulence} the mechanism mentioned in the previous paragraph would play a secondary role in stirring up the gas motions and it would be necessary to specify if the velocity fluctuations arise from pure turbulent motion inside the ionized clouds or a consequences of density and brightness fluctuations.
-
-\citet{sabalisck1995supersonic} studied NGC 604 revealing that the high emission knots on the region encompasses supersonic global velocity dispersion values of 14 $<$ \(\sigma_{\text{los}}\) $<$ \SI{20}{km.s^{-1}}.
-This knots have a characteristic radius of \(\sim\)\SI{7}{pc} and a Gaussian profile.
-Values of velocity dispersion $>$\SI{20}{km.s^{-1}} are found in low emission cavities where the lines present strong asymmetries.
-These cavities were identified as expanding shells by \cite{yang1996} with diameters of \(\sim\)\SI{40}{pc} and a expansion velocity above \SI{50}{km.s^{-1}}.
-According to table~\ref{tab:Res} the correlation length for NGC 604 is close to the scale of the bright knots in the region which aren't related to a particular energy injection mechanism.
-
-Although the Orion core, the EON, and NGC 604 have different \(r_0\) is not clear if it truly reveal a concrete aspect of the energy input mechanism mentioned above.
-Orion main energy input comes from one star, meanwhile NGC 604 has more than 200 OB stars including WR stars. 
-The Orion core also presents Herbig-Haro objects, which aren't possible to resolve for more distant regions.
-Though the correlation length is particular to each region, and it is correlated mainly with the size (see section~\ref{sec:scaling-relations}), it still needs further studies to reveal the true implication of this value with respect the energy input mechanisms.
-
-\subsubsection{Structure function power-law index \(m\)}\label{sec:power-index}
-
-The index \(m\) shown in the last column of Table \ref{tab:Res} is used for comparison between observations and the theoretical value of 0.67.
+
+The dependence on \(r_0\) and the diameter can be interpreted in terms that each region presents a characteristic energy injection mechanism (or combination) and despite the presence of the different mechanisms in the regions there some unique combination that drives the input energy in each region.
+
+\subsubsection{Relationship between plane-of-sky and mean line-of-sight velocity dispersion}\label{sec:sigmapos-vs-sigmalos}
+
+The second-order structure function measures the velocity fluctuations in the \hii{} regions under the assumption that exists an underlying velocity spectrum following an energy cascade.
+But this statistical technique is not unique in measuring the velocity fluctuations in the nebula and does not give information on the processes disturbing the ionized gas.
+Also, as mentioned in \citet{arthur2016turbulence} the possibility if these fluctuations can account for the non-thermal line broadening needs to be evaluated.
+
+Two parameters which are obtained from the velocity profile also measure the velocity fluctuations in the \hii{} regions: the standard deviation of the velocity centroids, \(\sigma\pos\), and the mean non-thermal linewidth, \(\langle \sigma_{\text{los}} \rangle\).
+These quantities allow us to compare the relation between the kinematical disorder on the plane-of-the-sky and along the line-of-sight \citep{2011MNRAS.413..705L}.
+
+As mentioned in the introduction, the \( \sigma_{\text{los}} \) parameter is estimated by correcting the observed linewidth for the contribution of broadening mechanism, equation \eqref{eq:sigma-los}, leaving just the random motions which are interpreted as turbulence along the line-of-sigth.
+This method is a simplification of the problem since it assume a Gaussian profile fit, which does not consider other components that could arise from different kinematics of the ionized gas and leaves out the broadening due to dust scattering.
+
+In the Figure~\ref{fig:los-vs-pos} we show the mean line-of-sight velocity dispersion versus the plane-of-sky velocity dispersion. 
+\citet{arthur2016turbulence} presents the same diagram for different emission lines of the Orion core nebula showing that the value \(\sigma_{\text{los}}\) (after considering the dust scattering) is roughly twice as the \(\sigma\pos\) (figure 14 on their work), while the \citet{2011MNRAS.413..705L} diagram, for a sample of small-to-intermediate size \hii{} regions in M33, approach unity (figure 4 on their work).
+The Figure~\ref{fig:los-vs-pos} shows that for our sample of \hii{} regions the fit we obtained follows the result of \citet{2011MNRAS.413..705L}.
+The relationship we found is \( \langle \sigma\los \rangle = (1.03 \pm 0.46) \sigma\pos - (7.7 \pm 2.9)\).
+
+The case of the reduction in the \(\sigma\pos\) can be interpreted by the effect of \textit{project smearing} \citep{1984ApJ...277..556S}.
+If we consider the case of homogeneous turbulent velocity, the projection from three to two dimensions over the line-of-sight depth \(H\), reduces the plane-of-sky amplitude for the condition \(r_{0} < H\).
+With a value of \(\sigma\pos / \sigma_{\text{los}}\) = 0.5 we obtain \(r_{0} / H \sim\) 0.02 - 0.1.
+This procedure implies depths of the order 10 to 50 times the correlation length.
+In the lower limit \citet{arthur2016turbulence} mentioned the inconsistency of this interpretation for the Orion core nebula, since evidence has shown that the emitting layer thickness is of the order of \num{0.01} - \SI{0.3}{pc}.
+%For the most distant regions of our sample, the previous analysis would give depths of the order of magnitude of the observational box, but considering the analysis using the power-law index (see section~\ref{sec:power-index}) only NGC 595, which power-law index is \num{1.38}, would comply to this fully three-dimensional structure.
+On the other hand, \citet{arthur2016turbulence} proposed another interpretation in terms of large-scale order motions, and emissivity fluctuations.
+They consider an expanding shell where the mean velocity fluctuations on the plane of the sky are because the relative brightness of the redshifted and blueshifted hemispherers.
+In this case, the rms fractional variation in the emissivity on the scale diameter is found to be in the order of \(\sigma\pos / \sigma_{\text{los}}\).
+
+As for the \citet{2011MNRAS.413..705L} results, they consider that large fluctuations of the turbulent velocities, which are spread over the entire ionized extent of the nebula, monotonically increase with the plane-of-sky dispersion.
+In this scenario, the main broadening mechanisms the kinematical disorder along the line-of-sight is related to the velocity gradients of the clumpiness in the cloud and turbulent movements.
+On the plane-of-sky the consequences of those gradients and movements is measured in every pixel, consequently the spatial variations on the velocity field would depend on the targeted pixel, at the same time depending on the motions inside the cloud.
+Thus the \(\sigma\pos\) and \(\langle \sigma_{\text{los}} \rangle\) parameters increase monotonically as the amplitudes grows because the non-thermal dynamical processes in the \hii{} regions.
+They characterize this behavior for their \hii{} regions sample by fitting a linear relation of \(\langle \sigma_{\text{los}} \rangle = (1.04 \pm 0.14) \sigma\pos + (8.15 \pm 0.93) \) to their observed regions.
+
+\subsubsection{Diameter vs centroid velocity dispersion}
+
+Other important relation commonly used in the study of the interstellar medium is the diameter (or size) versus velocity dispersion.
+Table \ref{tab:RestStats} shows this result for our sample in the forth row. 
+This relation presents a significance level \(p > \num{0.05}\) but there are a couple of things worth mentioning.
+Historically this relation is important following the work of \citet{1981MNRAS.194..809L} where he presents it in the context of molecular cloud complexes of many clouds, individual clouds, and clumps, so that size scales are studied over \(\num{0.1} < L < \SI{100}{pc}\) obtaining \(\sigma = 1.10 L ^{0.38}\).
+
+This relation is interpreted in terms of turbulence, particularly the Kolmogorov model which predicts a index of \num{0.33} so that larger regions presents more turbulence, and smaller regions less turbulence.
+It has been argued that this correlation method is not as powerful as using statistical functions \citep{1984ApJ...277..556S} but it is interesting that the index is consistent within different phases of the interstellar medium (see first paragraph of this section).
+On the other hand, we obtain \(\log \sigma\pos = (0.25 \pm 0.17) \log S - (0.2 \pm 0.38)\) which despite the large uncertainty is comparable with previous investigations within the error.
+
+As we mentioned in section \ref{sec:L-vs-sigmapos} the fact that this relation holds up to previous investigation gives some certainty that the \(\sigma\pos\) value obtained via the proposed model of the structure function is valid.
+This implying that the structure function, while not an absolute diagnostic, is a powerful tool in the research of \hii{} regions kinematics.
+
+\subsection{Power-law index}
+
+The power-law index \(m\) shown in the last column of Table \ref{tab:Res} is used for comparison between the observations and the theoretical value of 0.67.
 All our indices are above this theoretical value and this is attributed to the fact that the \hii{} regions do not comply with the assumptions established in the development of the turbulent theory.
 
-From section~\ref{sec:regions-milky-way} we know that most of all assumption mentioned in the theory of turbulence are not meet for our \hii{} region sample.
 \hii{} regions emerged from a molecular cloud with highly filamentary and clumpy density structure .
@@
 
-To study the projection of a three-dimensional structure function to a two-dimensional structure function, known as projection smoothing \citep{von1951methode, munch1958internal,1964SvA.....8..210K,1987ApJ...317..686O}, relationships between the power-law indices were proposed:
-
-\begin{equation}\label{eq:projection-smoothing-3d}
-m_{2D}= m_{3D} + 1
-\end{equation}
+As for any relation of the power-law index \(m\) we can see from table \ref{tab:RestStats} that this parameter does not correlate with any other parameter or physical property, being the least reliable for determining or concluding something about the nature of the physical processes inside the regions.
+On the other hand, the lack of correlation and the presence of this power-law index describing the assumed energy cascade may be interpreted as a universal property of the velocity fluctuations independent of the observed object, which is the main consideration in the turbulence theory.
+
+%\subsection{Kinematic relationship between ionized gas, molecular gas, and stars}
+%\label{sec:kinem-rela-betw}
+
+%Naively, the relatively small observed CO velocity dispersion
+%(\(\sigma(\chem{CO}) \ll \sigma(\ha)\) in all regions
+%for both \(\sigma\los\) and \(\sigma\pos\))
+%might be thought to rule out the molecular gas kinematics
+%as a \emph{cause} of the ionized gas kinematics.
+%However, this is not necessarily the case, so long as \emph{some} molecular gas
+%exists at the higher velocities typical of the ionized gas.
+
+%This is because a relatively small column of material
+%(\(N(\chem{H}) \sim \SI{e20}{cm^{-2}}\))
+%is sufficient to trap the ionization front,
+%in which case the \ha{} surface brightness is limited by the
+%incident ionizing flux
+%\citetext{the Ferland mechanism,
+%  see section~5.1 of \citealt{Baldwin:1991a}
+%  and section~B.2.1 of \citealt{Ferland:2012a}
+%}.
+%On the other hand, the bulk of the CO emission will come from much larger
+%column densities (\(N(\chem{H}) \sim \SI{e22}{cm^{-2}}\)),
+%where the molecules are effectively shielded from dissociation.
+% If a given region can be considered as an ensemble of clouds of
+% different masses, then ... would require lower mass clouds to move
+% faster though, so needs dynamical relaxation
+
+%\textbf{Check  if this is actually feasible before developing further}
+
+%Very schematically, one could represent these processes as:
+%\begin{equation}
+%  \label{eq:1}
+%  \sigma^2(\ha) \sim \zeta \sigma^2(\chem{CO}) + \eta
+%\end{equation}
+%where \(\zeta\) is a multiplicative factor
+%due primarily to the saturation at the Ferland limit,
+%and \(\eta \sim \csound^2\) is an additive factor due to additional turbulence
+%generated by the transonic ionized photoevaporation flows.
+
+%\textbf{Estimate these two factors by fitting to the observations}
+
+%\subsection{Interpretation of the turbulent parameters}\label{sec:interpretation-parameters}
+
+%\subsubsection{Correlation length \(r_0\)}
+
+%Ideally the correlation length \(r_0\) should represent the scale of dominant energy injection.
+%It is unclear what are the precise mechanisms driving the turbulence in \hii{} regions, thought a lot of options are candidates.
+%The most probable scenario is that the velocity fluctuations are consequence of the combination of various mechanism.
+%There are several energy sources that could provide or contribute  to the energy required: of the order of kpc, the differential rotations of the galaxy that produces shear at large scale, at scales of the order of hundreds of pc, supernova explosions inject a large amount of kinetic energy.
+%At scales of several tens of pc the expansion of \hii{} regions and stellar winds are a source of energy and, bipolar flows, shocks, jets and champagne flows inject energy at small scales about one tenth of a pc.
+%Many of these mechanisms, at some extent, affect all the \hii{} regions studied in this work.
+%We can use the kinematic analysis of the regions to investigate how previously identified energy injection mechanisms could be related to the correlation length.
+
+%\citet{2009AJ....137..367O} present a three-dimensional study of the dynamic structure of the Orion nebula.
+%The high-velocity stellar wind from \(\theta^1\) Ori C will confine the ionized gas, even the high ionization emission lines, to a thick shell.
+%In one direction, at a distance of \SI{0.1}{pc} from the ionizing massive star a stationary shell of shocked material is formed when the ram pressure of the photoevaportation flow balances the thermal pressure of the shocked wind.
+%In the other direction there is a free flow of the hypersonic wind.
+%At a smaller scale of \SI{0.02}{pc} there is an interaction between the closest proplyd photoevaporation flow and the stellar wind which results in bowshocks.
+%According to \citet{2001ApJ...561..830G} the influence of stellar wind interactions is restricted to the central \SI{0.05}{pc}. 
+%Orion also present a champagne flow where the photoionized gas streams away from the ionization front covering a distance of \SI{\sim 1}{pc} from the molecular cloud \citep{1973ApJ...183..863Z}.
+
+%Our correlation length results for the Orion Core and EON from table~\ref{tab:Res}, \num{0.068} y \SI{0.39}{pc} respectively, despite been of the order of the scales mentioned above still aren't conclusive enough to determine a direct relation between them.
+%As mentioned in \citet{arthur2016turbulence} the mechanism mentioned in the previous paragraph would play a secondary role in stirring up the gas motions and it would be necessary to specify if the velocity fluctuations arise from pure turbulent motion inside the ionized clouds or a consequences of density and brightness fluctuations.
+
+%\citet{sabalisck1995supersonic} studied NGC 604 revealing that the high emission knots on the region encompasses supersonic global velocity dispersion values of 14 $<$ \(\sigma_{\text{los}}\) $<$ \SI{20}{km.s^{-1}}.
+%This knots have a characteristic radius of \(\sim\)\SI{7}{pc} and a Gaussian profile.
+%Values of velocity dispersion $>$\SI{20}{km.s^{-1}} are found in low emission cavities where the lines present strong asymmetries.
+%These cavities were identified as expanding shells by \cite{yang1996} with diameters of \(\sim\)\SI{40}{pc} and a expansion velocity above \SI{50}{km.s^{-1}}.
+%According to table~\ref{tab:Res} the correlation length for NGC 604 is close to the scale of the bright knots in the region which aren't related to a particular energy injection mechanism.
+
+%Although the Orion core, the EON, and NGC 604 have different \(r_0\) is not clear if it truly %reveal a concrete aspect of the energy input mechanism mentioned above.
+%Orion main energy input comes from one star, meanwhile NGC 604 has more than 200 OB stars including WR stars. 
+%The Orion core also presents Herbig-Haro objects, which aren't possible to resolve for more distant regions.
+%Though the correlation length is particular to each region, and it is correlated mainly with the size (see section~\ref{sec:scaling-relations}), it still needs further studies to reveal the true implication of this value with respect the energy input mechanisms.
+
+%\subsubsection{Structure function power-law index \(m\)}\label{sec:power-index}
+
+%The index \(m\) shown in the last column of Table \ref{tab:Res} is used for comparison between observations and the theoretical value of 0.67.
+%All our indices are above this theoretical value and this is attributed to the fact that the \hii{} regions do not comply with the assumptions established in the development of the turbulent theory.
+
+%From section~\ref{sec:regions-milky-way} we know that most of all assumption mentioned in the theory of turbulence are not meet for our \hii{} region sample.
+%\hii{} regions emerged from a molecular cloud with highly filamentary and clumpy density structure .
+%There is a large increase in the temperature because of the photoionization, and the density gradients with the pressure gradients accelerate the flow which occurs on multiple scales consequence of the fractal nature of the molecular cloud \citep{arthur2016turbulence}.
+%The radiation pressure, stellar winds and region expansion, among other physical processes would create pressure-driven shock waves propagating faster than the speed of sound in the medium.
+%This would make the flow compressible and supersonic in \hii{} regions.
+%Also, as \hii{} regions are three-dimensional objects our structure function results comes from a projection of this three-dimensional structure to a two-dimensional velocity field.
+%But despite the complex nature of \hii{} regions and observational limitations we obtain a common pattern for the structure function and the value of the power-law index falls in a certain limited range of values.
+%The differences in the power-law index with respect the theoretical value are often used as a diagnostic tools to identify properties that are not consider in the assumptions of the turbulence theory.
+
+%To study the projection of a three-dimensional structure function to a two-dimensional structure function, known as projection smoothing \citep{von1951methode, munch1958internal,1964SvA.....8..210K,1987ApJ...317..686O}, relationships between the power-law indices were proposed:
+
+%\begin{equation}\label{eq:projection-smoothing-3d}
+%m_{2D}= m_{3D} + 1
+%\end{equation}
 %
-and  when the astronomical object present a sheet-like distribution of emitters we have the relation:
+%and  when the astronomical object present a sheet-like distribution of emitters we have the relation:
 %
-\begin{equation}\label{eq:projection-smoothing-2d}
-m_{2D} \sim m_{3D}
-\end{equation}
-
-As a conclusion, if the extension of the HII region is compared with its depth (three-dimensional case) the value of the index is \num{1.67}. 
-While the case where the extension is much greater than its depth (two-dimensional case) the region will have a value of \num{0.6}.
-From Table~\ref{tab:Res} we see that our results fall between these two previous values.
-
-The mean value \(m\) of our sample is \num{\sim 1}. 
-Following the equation \ref{eq:projection-smoothing-3d} the \hii{} regions in our sample with \(m >\) 1 would present a depth which is in the order of magnitude comparable to the length of the observed box size \(L\) been closest to this value as \(m\) tends to 1.6.
-On the other hand, \hii{} regions with values \(m <\) 1 would present a thinner structure as they tend to the value of 0.6.
-This analysis should not be regarded as conclusive about the true structure of the regions and would require further observations with a combination of kinematics analysis to determine the best way to determine the depth of each region.
-
+%\begin{equation}\label{eq:projection-smoothing-2d}
+%m_{2D} \sim m_{3D}
+%\end{equation}
+
+%As a conclusion, if the extension of the HII region is compared with its depth (three-dimensional case) the value of the index is \num{1.67}. 
+%While the case where the extension is much greater than its depth (two-dimensional case) the region will have a value of \num{0.6}.
+%From Table~\ref{tab:Res} we see that our results fall between these two previous values.
+
+%The mean value \(m\) of our sample is \num{\sim 1}. 
+%Following the equation \ref{eq:projection-smoothing-3d} the \hii{} regions in our sample with \(m >\) 1 would present a depth which is in the order of magnitude comparable to the length of %the observed box size \(L\) been closest to this value as \(m\) tends to 1.6.
+%On the other hand, \hii{} regions with values \(m <\) 1 would present a thinner structure as they tend to the value of 0.6.
+%This analysis should not be regarded as conclusive about the true structure of the regions and would require further observations with a combination of kinematics analysis to determine the best way to determine the depth of each region.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2022-06-29 Corr.tex
Improve formatting of Table 4

--- 2022-06-24 Corr.tex
@@
 This results were obtained using the procedure in \citet{2007ApJ...665.1489K}.}
-\begin{tabular}{cccccc}
-\hline
-            $Y$ &                   $X$ &                 $a$ &                 $b$ &       $r$ &      $p$ \\
-\hline
-    log $r_0$ &       log $S$ &   0.95 $\pm$ 0.33 &  -1.68 $\pm$ 0.71 &   0.86 &  0.003 \\
- log $\sigma$ &      log L(H) &   0.26 $\pm$ 0.11 &  -9.19 $\pm$ 4.33 &   0.86 &  0.003 \\
- log $\sigma$ &       log $S$ &   0.24 $\pm$ 0.17 &   0.24 $\pm$ 0.38 &   0.64 &   0.06 \\
- log $\sigma$ &   log $r_{0}$ &   0.18 $\pm$ 0.17 &   0.69 $\pm$ 0.12 &   0.51 &  0.164 \\
-      log $m$ &      log Dist &  -0.02 $\pm$ 0.04 &   0.04 $\pm$ 0.08 &   -0.4 &   0.29 \\
-      log $m$ &  log $\sigma$ &  -0.18 $\pm$ 1.03 &   0.14 $\pm$ 0.74 &  -0.37 &  0.327 \\
-      log $m$ &   log $r_{0}$ &  -0.02 $\pm$ 0.07 &   0.01 $\pm$ 0.05 &  -0.28 &  0.469 \\
+\begin{tabular}{RRRRRR}
+  \toprule
+  Y &                   X &                 a &                 b &       r &      p \\
+  \midrule
+  \log r_0 &         \log D_{\hii} &   0.94 \pm 0.33 &  -1.66 \pm 0.72 &   0.86 &  \mathbf{0.003} \\
+  \log \sigma\pos &        \log L(\ha) &    0.28 \pm 0.10 &  -9.86 \pm 3.71 &   0.86 &  \mathbf{0.003} \\
+  \sigma\pos &  \sigma_{\text{los}} &   1.03 \pm 0.44 &   7.35 \pm 2.83 &   0.78 &   \mathbf{0.010} \\[\smallskipamount]
+  \log \sigma\pos &         \log D_{\hii} &   0.26 \pm 0.18 &   0.19 \pm 0.39 &   0.64 &   0.060 \\
+  \log m &        \log d &  -0.02 \pm 0.04 &   0.04 \pm 0.08 &   -0.40 &   0.290 \\
+  \sigma\pos &         r_{0} &    0.40 \pm 0.69 &   4.61 \pm 3.25 &   0.37 &  0.329 \\
+  m &        \sigma\pos &  -0.01 \pm 0.03 &   1.12 \pm 0.21 &  -0.37 &  0.331 \\
+  m &         r_{0} &   0.02 \pm 0.03 &   0.96 \pm  0.16 &  -0.09 &  0.824 \\
   \bottomrule
@@
 %<10\(^{-5}\)
+
+%%% Local Variables:
+%%% mode: latex
+%%% TeX-master: strucfunc_paper
+%%% End:

### 2022-07-01 strucfunc_paper.tex
Javier updates 2022-06-29

@@
 \begin{tabular}{cCCCC}\toprule
-\hii{}    &  \text{Distance} & \text{Diameter,}\ D & \log L(\ha) &  \langle \sigma\los \rangle \\
+\hii{}    &  \text{Distance,}\ d & \text{Diameter,}\ D & \log L(\ha) &  \langle \sigma\los \rangle \\
   Region    &  [\si{kpc}]          &  [\si{pc}]    &  [\si{erg.s^{-1}}]            &    [\si{km.s^{-1}}]  \\ 
@@
 The Figure \ref{fig:rvsR} shows the relation of the correlation length \(r_0\) and the diameter \(D\) of the region. 
-The relationship we found is \(\log r_0 = (0.95 \pm 0.33) \log S - (1.6 \pm 0.7)\).
+The relationship we found is \(\log r_0 = (0.95 \pm 0.33) \log D - (1.6 \pm 0.7)\).
 The values of \(D\) are taken from \citet{1984ApJ...287..116K} and correspond to the outer
@@
 It has been argued that this correlation method is not as powerful as using statistical functions \citep{1984ApJ...277..556S} but it is interesting that the index is consistent within different phases of the interstellar medium (see first paragraph of this section).
-On the other hand, we obtain \(\log \sigma\pos = (0.25 \pm 0.17) \log S - (0.2 \pm 0.38)\) which despite the large uncertainty is comparable with previous investigations within the error.
+On the other hand, we obtain \(\log \sigma\pos = (0.25 \pm 0.17) \log D - (0.2 \pm 0.38)\) which despite the large uncertainty is comparable with previous investigations within the error.
 

### 2022-07-08 strucfunc_paper.tex
Javier changes 2022-07-06

@@
 \begin{abstract}
-  Fluctuations of centroid velocities on the plane of the sky are a powerful tool for studying the turbulent dynamics of emission line regions.
-  To characterize these fluctuations we apply a statistical analysis using the second-order structure function to archival \halpha\ observations of a diverse sample of 9 \hii{} regions.
-  This regions are located in the Milky Way and other Local Group galaxies, and
-  span more than two orders of magnitude in size and luminosity.
-  We propose a new functional form of the structure function that considers observational constraints.
-  This functional is used as an objective function for a chi-square analysis to adjust our results and extract three parameters related to the fluctuations in the velocity field for each region.
-  We obtain the true velocity dispersion \(\sigma\pos\), which spans from 3 to 19 km s\(^{-1}\), the
-  autocorrelation length \(r_0\) covering to 0.09 - 12 pc, and the power-law slope \(m\) of the velocity field, which ranges from 0.7 to 1.5.
-  The velocity dispersion is found to correlate primarily with luminosity and the autocorrelation length correlates primarily with the size of the region.
-  A comparison between \(\sigma\pos\) and \(\sigma_{los}\) shows that this last value is roughly the double for all regions.
-  We found that our proposed functional form describe with more accuracy the inertial range and our methodology guarantees consistency for comparison between the galactic and giant HII regions.
+  Fluctuations of centroid velocities on the plane of the sky, which can be derived from spectroscopic and Fabry-Perot observations, are a powerful tool for studying the turbulent dynamics of emission line regions.
+  With the aim to characterize these velocities fluctuations we conduct a statistical analysis on a diverse sample of 9 \hii{} regions that spans more than two orders of magnitude in size and luminosity, and are located in the Milky Way and other Local Group galaxies.
+  We determine the second-order structure function of the observational centroid velocity \halpha\ two-dimensional map, and the observational structure function is fitted in a non-linear least square regression using a heuristic model for the second-order structure function as an objective function.
+  Finally we establish confidence intervals for the parameters provided by the fitting.
+  The model we use considers: nuisance parameters like the observational seeing (\(s_0\)) and the instrumental noise (\(B_{\text{noise}}\)), and the turbulent velocity field parameters like the velocity dispersion of the centroid velocity (\(\sigma\pos\)), the autocorrelation length (\(r_0\)) and a power-law index \(m\).
+  Our results are: \num{0.2}\(< s_0 \text{(FWHM) } <\)\SI{3.0}{arcsec},  \num{0.003}\(< B_{\text{noise}} <\)\SI{6.0}{km^{-2}.s^{-2}}, \num{3} \(< \sigma\pos <\) \SI{19}{km.s^{-1}},   \num{0.09}\(< r_0 <\) \SI{12}{pc} and  \num{0.7} \(< m <\)\num{1.5}.
+  We also find the relations \(\sigma\pos \propto L(H_\alpha)^{0.28 \pm 0.1}\), and \(r_0 \propto D^{0.95 \pm 0.32}\).
+  A comparison between \(\sigma\pos\) and the mean non-thermal linewidth, \(\langle \sigma_{los} \rangle\), shows that these values increase following a linear monotonically relation.
+%  Since the previous scale-relations results are within the uncertainty of previous investigation we conclude that the parameters obtained from our proposed model represents true kinematic properties of each region.
+ % Obtaining in a reliable method the parameters of an observational structure function in turn can be used to better characterize with certain accuracy the centroid velocities fluctuations which may reflect the turbulent nature of a \hii{} region.
+    %which have a strong influence on the slope that characterize the structure function behavior.
+
+  %our methodology guarantees consistency for comparison between the galactic and giant HII regions.
 \end{abstract}
@@
 for the velocity fluctuations.
-Finally, in section~\ref{sec:conclusions} we summarise our conclusions.
+Finally, in section~\ref{sec:conclusions} we present our conclusions.
 
@@
 
-We use \citet{1987A&A...176..347H} observations to analyze the Extended Orion Nebula.
-These observations were obtained using a 106 cm-Cassegrain telescope at Observatorium Hoher List. 
+We use \citet{1987A&A...176..347H} data to analyze the Extended Orion Nebula.
+Their observational data was obtained using a 106 cm-Cassegrain telescope at Observatorium Hoher List. 
 A Fabry-Pérot interferometer was used with a étalon separation of 0.5 mm. 
@@
 In the following sections, the results shown previously are discussed and compared with the structure functions of previous investigations that analyzed \hii{} regions from our sample.
-We present the most important correlations between the turbulent parameters and the physical properties from the \hii{} region sample and finally an interpretation of the turbulent parameters is given.
+We present the most important correlations between the turbulent parameters and the physical properties from the \hii{} region sample.
 

### 2022-07-08 strucfunc_paper.tex
Add a paragraph about the noise to sec 4.4

@@
 
+For most of our sources \(B\noise / \sigma^2\los < 0.03 \) and the noise
+has almost no effect on the structure function,
+apart from at the very smallest separations,
+resulting in a negligible influence on the other model parameters.
+The exceptions are the Galactic regions Lagoon, Carina,
+and especially the Extended Orion Nebula,
+for which the noise is sufficiently large that the observed
+structure function slope is significantly shallower than
+the inferred slope \(m\) of the true model.
+These sources also show the largest fluctuations of the
+observed \(B(r)\) around the smooth fit
+at intermediate scales
+(see in particular Figure~\ref{fig:strucfunc-fit-Galactic}d),
+which is probably due to the relatively small number of spectra.
+
 \subsection{Evidence for inhomogeneity at the largest scales}

### 2022-07-09 strucfunc_paper.tex
Added final paragraph for sec 5.1

--- 2022-07-08 strucfunc_paper.tex
@@
 
+For most of our sources \(B\noise / \sigma^2\pos < 0.03 \) and the noise
+has almost no effect on the structure function,
+apart from at the very smallest separations,
+resulting in a negligible influence on the other model parameters.
+The exceptions are the Galactic regions Lagoon, Carina,
+and especially the Extended Orion Nebula,
+for which the noise is sufficiently large that the slope
+of \(B\obs(r)\) is significantly shallower than
+the inferred slope \(m\) of the true model \(B\model(r)\).
+These sources also show the largest fluctuations
+\(B\obs(r)\) around the smooth fit
+at intermediate scales
+(see in particular Figure~\ref{fig:strucfunc-fit-Galactic}d),
+which is probably due to the relatively small number of spectra.
+
 \subsection{Evidence for inhomogeneity at the largest scales}
@@
 
-SUMMARISE COMPARISONS DESCRIBED IN APPENDIX.
+Detailed comparisons with previous results are given
+in section~\ref{sec:notes-individual-hii}.
+In summary, we agree with previous studies in cases where there
+is a good match in the exact area covered and in the angular resolution.
+In other cases, large discrepancies are found,
+which are probably to a combination of methodological differences
+and real variations due to the inhomogeneity of the
+velocity fluctuations on the largest scales.
 
@@
 For the same \halpha\ observation we obtained a value of \num{1.07} and a correlation length of \SI{0.068}{pc}. 
-Although the work of \citet{arthur2016turbulence} follows a different methodology, the values of \(r_0\) and \(\sigma\pos^2\) fall within the margin error.
+Although the work of \citet{arthur2016turbulence} follows a different methodology, the values of \(r_0\) and \(\sigma\pos^2\) fall within the margin of error of our own results.
 

### 2022-07-17 strucfunc_paper.tex
Javier changes 2022-07-14

@@
 \begin{abstract}
-  Fluctuations of centroid velocities on the plane of the sky, which can be derived from spectroscopic and Fabry-Perot observations, are a powerful tool for studying the turbulent dynamics of emission line regions.
-  With the aim to characterize these velocities fluctuations we conduct a statistical analysis on a diverse sample of 9 \hii{} regions that spans more than two orders of magnitude in size and luminosity, and are located in the Milky Way and other Local Group galaxies.
-  We determine the second-order structure function of the observational centroid velocity \halpha\ two-dimensional map, and the observational structure function is fitted in a non-linear least square regression using a heuristic model for the second-order structure function as an objective function.
-  Finally we establish confidence intervals for the parameters provided by the fitting.
-  The model we use considers: nuisance parameters like the observational seeing (\(s_0\)) and the instrumental noise (\(B_{\text{noise}}\)), and the turbulent velocity field parameters like the velocity dispersion of the centroid velocity (\(\sigma\pos\)), the autocorrelation length (\(r_0\)) and a power-law index \(m\).
-  Our results are: \num{0.2}\(< s_0 \text{(FWHM) } <\)\SI{3.0}{arcsec},  \num{0.003}\(< B_{\text{noise}} <\)\SI{6.0}{km^{-2}.s^{-2}}, \num{3} \(< \sigma\pos <\) \SI{19}{km.s^{-1}},   \num{0.09}\(< r_0 <\) \SI{12}{pc} and  \num{0.7} \(< m <\)\num{1.5}.
-  We also find the relations \(\sigma\pos \propto L(H_\alpha)^{0.28 \pm 0.1}\), and \(r_0 \propto D^{0.95 \pm 0.32}\).
-  A comparison between \(\sigma\pos\) and the mean non-thermal linewidth, \(\langle \sigma_{los} \rangle\), shows that these values increase following a linear monotonically relation.
-%  Since the previous scale-relations results are within the uncertainty of previous investigation we conclude that the parameters obtained from our proposed model represents true kinematic properties of each region.
- % Obtaining in a reliable method the parameters of an observational structure function in turn can be used to better characterize with certain accuracy the centroid velocities fluctuations which may reflect the turbulent nature of a \hii{} region.
-    %which have a strong influence on the slope that characterize the structure function behavior.
-
-  %our methodology guarantees consistency for comparison between the galactic and giant HII regions.
+  Fluctuations of centroid velocities on the plane of the sky derived from spectroscopic observations are a powerful tool for studying the turbulent dynamics of emission line regions.
+  With the aim to characterize these velocities fluctuations we conduct a statistical analysis on a diverse sample of 9 \hii{} regions that spans more than two orders of magnitude in size and luminosity located in the Milky Way and other Local Group galaxies.
+  We determine the second-order structure function of the centroid velocity two-dimensional map of the \halpha\ emission line.
+  We also proposed a heuristic model for the structure function which takes into account observational constraints like the seeing (\(s_0\)), instrumental noise (\(B_{\text{noise}}\)) and size of the field of view (\(L\)), and the turbulent velocity field parameters like the velocity dispersion of the centroid velocity (\(\sigma\pos\)), the autocorrelation length (\(r_0\)) and a power-law index (\(m\)).
+  The observational structure function is fitted using our heuristic model in a non-linear regression analysis which allow us to derive the parameters previously mentioned  with their respective confidence intervals.
+  Our results are: \(\num{0.2} < s_0 \text{(FWHM)} < \SI{3.0}{arcsec}\), \(\num{0.003} < B_{\text{noise}} < \SI{6.0}{km^{-2}.s^{-2}}\),  \(\num{3} < \sigma\pos < \SI{19}{km.s^{-1}}\), \(\num{0.07} < r_0 < \SI{12}{pc}\) and \(\num{0.7}< m < \num{1.5}\).
+  The derived parameters are used to determine scaling relations between the physical properties of the regions like \halpha\ luminosity (\(L(H_{\alpha})\)), diamater (\(D\)) and the mean non-thermal linewidth (\(\langle \sigma_{los} \rangle\)).
+  We find that these relations are \(\sigma\pos \propto L(H_{\alpha})^{0.28 \pm 0.10}\) and \(r_0 \propto D^{0.95 \pm 0.32}\), and that the \(\sigma\pos\) and \(\langle \sigma_{los} \rangle\), values increase following a linear monotonically relation.
+  Since the derived  scale-relations are within the uncertainty of previous investigations we conclude that the parameters obtained from our proposed model represents true kinematic properties of each region.
+  The methodology we present guarantees consistency for comparison between the galactic and giant HII regions. 
+%  The second-order structure function has proved to be a useful tool to determine the existence of the correlations between random velocities and distance across the \hii{} regions.
+
 \end{abstract}
@@
 \begin{keywords}
-HII regions -- ISM: kinematics and dynamics -- turbulence
+turbulence -- instrumentation: spectrographs -- ISM: HII regions, kinematics and dynamics
 \end{keywords}
@@
 the \hii{} regions in our sample.
-We also discuss the implications of our results for the existence of a
-Kolmogorov-type turbulent energy cascade and the nature of the driving mechanism
-for the velocity fluctuations.
+%We also discuss the implications of our results for the existence of a
+%Kolmogorov-type turbulent energy cascade and the nature of the driving mechanism
+%for the velocity fluctuations.
 Finally, in section~\ref{sec:conclusions} we present our conclusions.
@@
 (\num{500} to \SI{800}{kpc}).
-Further details of the observations and the sources themselves
-are given in the following two sections.
+Further details of the observations are given in the following section.
 
@@
 
-\subsubsection{TAURUS-II Fabry-Perot spectroscopy}
+\subsubsection{TAURUS-II Fabry-Perot interferometer}
 \label{sec:taurus-ii-fabry}
@@
   V_{c}(\xx_j) \  V_{c}(\xx_i)
-  \bigr]^{2} \right \rangle_{\Abs{\xx_j - \xx_i\!} \ \approx \ r} \ .
+  \bigr] \right \rangle_{\Abs{\xx_j - \xx_i\!} \ \approx \ r} \ .
 \end{equation}

### 2022-07-31 strucfunc_paper.tex
Javier changes 2022-07-31

@@
 
-In the following sections, the results shown previously are discussed and compared with the structure functions of previous investigations that analyzed \hii{} regions from our sample.
-We present the most important correlations between the turbulent parameters and the physical properties from the \hii{} region sample.
+In the section \ref{sec:comp-with-prev} we make a comparison of our methods and results with previous research that analyzes structural functions of some \hii{} regions of our sample.
+In the section \ref{sec:scaling-relations} we present the most important scaling relations between the derived turbulent parameters and the physical properties of the \hii{} regions.
+Finally, in the section \ref{power-law-index} we discuss the role of the derived power-law index in the context of turbulence in the ionized gas.
 
@@
 %Intro for scaling relations
-\textit{Maybe this paragraph it not necessary. Just a small intro and if needed previous results can be in a table for comparison. }
-Correlations between the physical properties of \hii{} regions like size, luminosity, and the velocity dispersion, have been used as tools for finding scaling relationships for these objects, which have also been found in dwarf galaxies and high-redshift star formation regions.
-\citet{melnick1977,terlevich1981} were the first to shown an empirical relationship between the line width and the integrated properties of the \hii{} regions as the diameter or the luminosity (\(r \sim \sigma ^{\sim 2}\) ; \(\text{L}_{\text{H}} \sim \sigma ^{\sim 4}\)).
-In later years, \citet{1988A&A...201..199A} confirmed these relationships considering the discrepancies of previous investigations obtaining \(\text{L}_{\text{H}_{\alpha}} \propto \sigma^{3.9}\) and \(r \propto \sigma^{1.84}\).
+%\textit{Maybe this paragraph it not necessary. Just a small intro and if needed previous results can be in a table for comparison. }
+%Correlations between the physical properties of \hii{} regions like size, luminosity, and the velocity dispersion, have been used as tools for finding scaling relationships for these objects, which have also been found in dwarf galaxies and high-redshift star formation regions.
+%\citet{melnick1977,terlevich1981} were the first to shown an empirical relationship between the line width and the integrated properties of the \hii{} regions as the diameter or the luminosity (\(r \sim \sigma ^{\sim 2}\) ; \(\text{L}_{\text{H}} \sim \sigma ^{\sim 4}\)).
+%In later years, \citet{1988A&A...201..199A} confirmed these relationships considering the discrepancies of previous investigations obtaining \(\text{L}_{\text{H}_{\alpha}} \propto \sigma^{3.9}\) and \(r \propto \sigma^{1.84}\).
 %\citet{1981MNRAS.194..809L}
-In recent years, \citet{2012MNRAS.422.3339W} have found that clumps and \hii{} regions follow scaling relations over the range of z = 0-2 for the \halpha\ emission line with the size, velocity dispersion, luminosity and mass, finding \(\sigma \propto r^{0.42}\), \(\text{L}_{\text{H}_{\alpha}} \propto r^{2.72}\) and \(\text{L}_{\text{H}_{\alpha}} \propto \sigma^{4.18}\), respectively.
-This results imply that the same process are seen at high redshifts and the current epoch in star forming regions.
-Recently, \citet{Moiseev:2015a} found that the relation in dwarf galaxies is \(\text{L}_{\text{H}_{\alpha}} \propto \sigma^{5}\).
-\citet{2018MNRAS.474.1250F} presented the relationship between integrated H$_{\beta}$ line luminosity and the velocity dispersion for new data of 36 giant HII regions obtaining \(\text{L}_{\text{H}_{\beta}} \propto \sigma^{5.02 \pm 0.21}\).
+%In recent years, \citet{2012MNRAS.422.3339W} have found that clumps and \hii{} regions follow scaling relations over the range of z = 0-2 for the \halpha\ emission line with the size, velocity dispersion, luminosity and mass, finding \(\sigma \propto r^{0.42}\), \(\text{L}_{\text{H}_{\alpha}} \propto r^{2.72}\) and \(\text{L}_{\text{H}_{\alpha}} \propto \sigma^{4.18}\), respectively.
+%This results imply that the same process are seen at high redshifts and the current epoch in star forming regions.
+%Recently, \citet{Moiseev:2015a} found that the relation in dwarf galaxies is \(\text{L}_{\text{H}_{\alpha}} \propto \sigma^{5}\).
+%\citet{2018MNRAS.474.1250F} presented the relationship between integrated H$_{\beta}$ line luminosity and the velocity dispersion for new data of 36 giant HII regions obtaining \(\text{L}_{\text{H}_{\beta}} \propto \sigma^{5.02 \pm 0.21}\).
 
 %methods for our analysis
-In section \ref{sec:results} we show that each velocity field of our sample can be characterized by parameters that are particular for each \hii{} region.
-We used these parameters to develop scaling relations between them and the physical properties of each region.
-To accomplish this we implement a hierarchical Bayesian model for fitting a straight line using the \texttt{linmix} Python library based on \cite{2007ApJ...665.1489K}.
-We use the physical properties in Table \ref{tab:regions-properties} as the independent variable \(X\) and the turbulent parameters in Table \ref{tab:Res} as the dependent variable \(Y\).
-In the following analysis we left out the EON to avoid redundancy in the fitting process.
-For the physical properties we consider an uncertainty of \num{10}\% of the values for the size and the mean non-thermal linewidths for 30 Doradus and NGC 346.
-For the turbulent parameters we use the relative error considering the 2-\(\sigma\) intervals. 
-In the case of non-gaussian distribution we choose the highest value for the uncertainty.
-The main results are shown in Table \ref{tab:RestStats} in ascending order for the \(p\)-value.
-In the Figures \ref{fig:sigvsl}, \ref{fig:rvsR} and \ref{fig:los-vs-pos} we show the plots for the correlations with a significance level \(p < \num{0.05}\) which corresponds to the first three rows in Table \ref{tab:RestStats}.
-In the Figures the black solid line is the input regression line which is described by the equation in the plot, and the red thin lines are a random sample (\num{ \sim 400}) from the posterior distribution within one standard deviation from the slope and the \(Y\)-intercept value.
+In section \ref{sec:results} we show that each \hii{} region of our sample can be characterized with parameters that are particular to each velocity field.
+We used these parameters to estimate the scaling relations between them and the main physical properties of each region.
+To accomplish this we implement a hierarchical Bayesian model for fitting a straight line using the \texttt{linmix} Python library which is based on the procedure of \cite{2007ApJ...665.1489K}.
+The physical properties in Table \ref{tab:regions-properties} are used as the independent variable \(X\) while the derived turbulent parameters of Table \ref{tab:Res} are used as the dependent variable \(Y\).
+In the following analysis we left out the EON to avoid redundancy of the regions.
+For physical properties values where uncertainties are not reported (size and luminosity), we consider an error of \num{10}\% of the value.
+The same criteria is used for the uncertainty values of the mean non-thermal linewidths for 30 Doradus and NGC 346.
+For the turbulent parameters we use the relative error considering the 2-\(\sigma\) interval. 
+Our main correlation results are shown in Table \ref{tab:RestStats} in ascending order for the \(p\)-value.
+In the Figs.
+\ref{fig:sigvsl}, \ref{fig:rvsR} and \ref{fig:los-vs-pos} we show the plots for the correlations with a significance level \(p < \num{0.05}\) which corresponds to the first three rows in Table \ref{tab:RestStats}.
+In the Figs.
+the black solid line is the input regression line which is described by the equation shown in the plot and the red thin lines are a random sample (\num{ \sim 400}) from the posterior distribution within one standard deviation from the slope and the \(Y\)-intercept value.
 
@@
 
-The Figure \ref{fig:sigvsl} shows the log \(\sigma\pos\)-log \(\text{L}(\text{H}_{\alpha})\) plane.
-Since this relation is common in the literature it can be use to investigate how reliable are our results and can be used as comparison with the previous investigations.
-The fit we obtained give us a relation of \(\log \sigma\pos = (0.27 \pm 0.10) \log \text{L}(\text{H}_{\alpha})-(9.9 \pm 4.0)\).
-Since it is customary in the literature to present \(\text{L} (\text{H}_{\alpha})\) as the dependent variable we also calculate this relation.
-Taking the inverse of slope we have \(\text{L}_{\text{H}_{\alpha}} \propto \sigma^{3.6 \pm 1.4}\). 
-Using the same procedure in \textit{linmix} and changing the variables we obtain \(\log \text{L}(\text{H}_{\alpha}) = (2.8\pm 1.0) \log \sigma\pos -(36 \pm 4)\).
-Both results are close to the \(\text{L}_{\text{H}} \propto \sigma^{4}\) theoretical relation.
-
-The fact that this relationship holds in our results is interesting considering that the \(\sigma\pos\) is obtained using the structure function and the \(\text{L}(\text{H}_{\alpha})\) values comes from different sources unrelated to oour data (see the Appendix~\ref{sec:notes-individual-hii}).
-This means that the proposed model describes within certain accuracy the velocity field fluctuations and that the parameters obtained can be interpreted a true property of each \hii{} region velocity field .
+The Fig. \ref{fig:sigvsl} shows the log \(\sigma\pos\)-log \(\text{L}(\text{H}_{\alpha})\) plane.
+This relation is commonly employ in the literature  and can be use to investigate how reliable is our derived velocity dispersion.
+The fit we obtain is \(\log \sigma\pos = (0.27 \pm 0.10) \log \text{L}(\text{H}_{\alpha})-(9.9 \pm 4.0)\).
+Since it is customary in the literature to present \(\text{L} (\text{H}_{\alpha})\) as the dependent variable we also calculate this relation: taking the inverse of slope in Fig.
+\ref{fig:sigvsl} we have \(\text{L}_{\text{H}_{\alpha}} \propto \sigma^{3.6 \pm 1.4}\) and using the same procedure in \textit{linmix} and changing the variables we obtain \(\log \text{L}(\text{H}_{\alpha}) = (2.8\pm 1.0) \log \sigma\pos -(36 \pm 4)\).
+
+The relationship \(\text{L}_{\text{H}} \propto \sigma^{\alpha}\) has been extensively investigated  in the context of giants \hii{} regions obtaining a value for \(\alpha\) of \( \sim 4\)\citep{terlevich1981,1988A&A...201..199A} and \num{2.87 \pm 0.2} \citep{Rozas:2006b}.
+Complementing previous results \citet{2012MNRAS.422.3339W} found that star-forming regions at \(z \sim 1.3\) and local \hii{} regions follow a relation with \(\alpha = 4.18 \pm 0.21\).
+\citet{Moiseev:2015a} found that this relation also holds for dwarf galaxies with a value of \(\alpha \sim 5\).
+\citet{2018MNRAS.474.1250F} presented the relationship between integrated H$_{\beta}$ line luminosity for new data of 36 giant HII regions obtaining \(\text{L}_{\text{H}_{\beta}} \propto \sigma^{5.02 \pm 0.21}\).
+Recently, \citet{2020ApJ...888..113W} studied the properties of high-\(z\) and local \hii{} galaxies among some GEHRs findig a value of \(\alpha \sim 5\).
+
+There are two main difference between the previous investigations and our results: one is that the velocity dispersion is obtained as the width of the emission line profile integrated over the whole object or as the non-thermal line-width, which is different from the plane of the sky dispersion we are using and that our sample is smaller in the number of data.
+The first problem is addressed in section \ref{sec:sigmapos-vs-sigmalos} where we discuss the relation between the line-of-sight and plane-of-sky velocities.
+But despite these problems, the fact that this relationship holds in our results (within the errors) is interesting considering that the \(\sigma\pos\) is derived from the structure function, while the \(\text{L}(\text{H}_{\alpha})\) values comes from different sources unrelated to our data (see the Appendix~\ref{sec:notes-individual-hii}).
+This means that the proposed structure function model describes within certain accuracy the velocity field fluctuations and that the parameters obtained can be interpreted as a true kinematic property of the \hii{} region velocity field.
 
@@
 These values would represent an upper limit of the size of each region.
-Since these objects do not posses physical edges the size determination is not trivial.
+Since these objects do not posses physical edges the determination of their size is not trivial.
 Due to the above, we chose these set values since they are from an unique source and are foreign to our calculations and observations, which reduced the bias in the scaling law we obtain.
@@
 Ideally the correlation length \(r_0\) should represent the scale of dominant energy injection.
-It is unclear what are the precise mechanisms driving the turbulence in \hii{} regions, thought a lot of options are candidates.
-The most probable scenario is that the velocity fluctuations are consequence of the combination of various mechanism.
-There are several energy sources that could provide or contribute  to the energy required: of the order of kpc, the differential rotations of the galaxy that produces shear at large scale, at scales of the order of hundreds of pc, supernova explosions inject a large amount of kinetic energy.
-At scales of several tens of pc the expansion of \hii{} regions and stellar winds are a source of energy and, bipolar flows, shocks, jets and champagne flows inject energy at small scales about one tenth of a pc.
-Many of these mechanisms, at some extent, affect all the \hii{} regions studied in this work.
-
-The dependence on \(r_0\) and the diameter can be interpreted in terms that each region presents a characteristic energy injection mechanism (or combination) and despite the presence of the different mechanisms in the regions there some unique combination that drives the input energy in each region.
+It is unclear what are the precise mechanisms driving the turbulence in \hii{} regions.
+There are several energy sources that could provide or contribute to the energy required: of the order of kpc we have the differential rotations of the galaxy that produces shear at large scale. 
+At scales of the order of hundreds of pc the supernova explosions inject a large amount of kinetic energy.
+At scales of several tens of pc the expansion of \hii{} regions and stellar winds are a source of energy, and bipolar flows, shocks, jets and champagne flows inject energy at small scales about one tenth of a pc.
+Many of these mechanisms, at some extent, affect all the \hii{} regions studied in this work, so the most probable scenario is that the velocity fluctuations are consequence of the combination of various mechanism.
+
+The dependence on \(r_0\) and the diameter can be interpreted in terms that each region presents a characteristic energy injection mechanism (or combination) and despite the presence of the different mechanisms there is some unique combination that drives the input energy in each region.
 
@@
 
-\subsection{Power-law index}
+\subsection{Power-law index}\label{power-law-index}
 

### 2022-08-05 strucfunc_paper.tex
Javier changes 2022-08-05

@@
   We determine the second-order structure function of the centroid velocity two-dimensional map of the \halpha\ emission line.
-  We also proposed a heuristic model for the structure function which takes into account observational constraints like the seeing (\(s_0\)), instrumental noise (\(B_{\text{noise}}\)) and size of the field of view (\(L\)), and the turbulent velocity field parameters like the velocity dispersion of the centroid velocity (\(\sigma\pos\)), the autocorrelation length (\(r_0\)) and a power-law index (\(m\)).
+  We also proposed a heuristic model for the structure function which takes into account observational constraints like the seeing (\(s_0\)), instrumental noise (\(B_{\text{noise}}\)) and size of the field of view (\(L_{\text{box}}\)), and the turbulent velocity field parameters like the velocity dispersion of the centroid velocity (\(\sigma\pos\)), the autocorrelation length (\(r_0\)) and a power-law index (\(m\)).
   The observational structure function is fitted using our heuristic model in a non-linear regression analysis which allow us to derive the parameters previously mentioned  with their respective confidence intervals.
@@
 the finite angular resolution, \(s_0\) (set by pixel spacing or atmospheric seeing);
-the finite map size, \(L\);
+the finite map size, \(L_{\text{box}}\);
 and a contribution of spatially uncorrelated noise, \(B_0\),
@@
 In Appendix~\ref{sec:degr-struct-funct} we use simulated velocity maps to derive
-appropriate functional forms for the effects of \(s_0\), \(L\) and \(B_0\).
+appropriate functional forms for the effects of \(s_0\), \(L_{\text{box}}\) and \(B_0\).
 In our fits, we marginalize over these nuisance parameters to obtain robust
@@
 
-\subsubsection{Fabry-Pérot étalon}
+\subsubsection{Fabry-Pérot observations}
 \label{sec:fabry-perot-etalaon}
 
-We use \citet{1987A&A...176..347H} data to analyze the Extended Orion Nebula.
-Their observational data was obtained using a 106 cm-Cassegrain telescope at Observatorium Hoher List. 
-A Fabry-Pérot interferometer was used with a étalon separation of 0.5 mm. 
+We use the velocity field presented in \citet{1987A&A...176..347H} to analyze the Extended Orion Nebula \citetext{EON henceforth;  \citealp{2008Sci...319..309G}}.
+the brightness following the southwest direction from the Huygens region.
+The observational data was obtained using a Fabry-Pérot interferometer with a étalon separation of 0.5 mm on the 106 cm-Cassegrain telescope at Observatorium Hoher List. 
 A number of fifteen interferograms have been taken with different pointing directions of the telescope's optical axis in the nebula with an exposure time between 10 and 40 minutes. 
-The exposures are overlapped and fall into one square of a grid with a width of 1' centered at \(\theta^{1}\)Ori C.
+The exposures are overlapped and fall into one square of a grid with a width of \SI{1}{arcmin} centered at \(\theta^{1}\)Ori C.
 
@@
 
-The archival data used in this work for the extragalactic giant regions, NGC 604, NGC 595, Hubble X and Hubble V was obtained with the Fabry Perot TAURUS-II instrument
+The archival data for the extragalactic giant regions (GEHRs), NGC 604, NGC 595, Hubble X and Hubble V was obtained with the Fabry Perot TAURUS-II instrument
 \citep{Gordon:2000v}
-on the \SI{4.2}{m} William Herschel Telescope (WHT) of
-el Roque de los Muchachos Observatory (ORM) in La Palma, Spain
-and was retrieved from the La Palma archive\footnote{\url{http://casu.ast.cam.ac.uk/casuadc/ingarch}}.
-Each velocity image is \(256 \times 256\) pixels on the sky,
-with a spatial scale of \SI{0.26}{arcsec.pixel^{-1}}
-and a spectral resolution of \SI{40}{km.s^{-1}}.
+on the \SI{4.2}{m} William Herschel Telescope (WHT) and was retrieved from the La Palma archive\footnote{\url{http://casu.ast.cam.ac.uk/casuadc/ingarch}}.
+The IPCS-II detector was used with a etalon of \SI{125}{\mu m}.
+Each data cube is \(256 \times 256 \times 100\) with a spatial scale of \SI{0.26}{arcsec.pixel^{-1}} with a total integration time of \SI{3600}{s} (\SI{36}{s} per frame).
+For more details on the observational setup see table~1 of \citet{sabalisck1995supersonic}.
+The reduction and analysis was done with the packages TAUCAL y TAUFITS \citep{1992ASPC...25..445L} and the emission spectrum was adjusted with a Gaussian fit.
 The NGC~604 observations were previously reported and analyzed in
 \citet{sabalisck1995supersonic}, \citet{Medina-Tanco:1997a} and \citet{Melnick:2021x}.
-
-% \citet{sabalisck1995supersonic} mentioned the main aspects of the observations (1990 July 31).
-% The two-dimensional imaging spectroscopy was captured using an IPCS-II detector and the 125 $\mu$m etalon.
-% The cumulative integration time per frame is 36 s with a seeing value of 1''.
-% The format of the data cube was of 256*256*100 with a spatial scale of 0.26 pixel$^{-1}$.
-% Finally, the reduction and analysis was done with the packages TAUCAL y TAUFITS \citep{1992ASPC...25..445L}.
-The NGC 604 TAURUS-II observations were used by \citet{sabalisck1995supersonic}, \citet{tanco1997} and \citet{2019arXiv191203543M}.
 
@@
 \midrule
-Orion     & 0.436 \pm 0.02  & 5 \pm 0.5    &    37.18       &    9.9 \pm 1.2\FNa        \\
+Orion     & 0.44 \pm 0.02  & 5 \pm 0.5    &    37.18       &    9.9 \pm 1.2\FNa        \\
 Lagoon    & 1.25 \pm 0.12   & 25 \pm 2.5      &    37.47    &   11.2 \pm 1.6    \\
@@
 Table~\ref{tab:regions-properties} summarizes the properties of the regions in our sample
-with data taken from the literature. Further details on each individual source and references are given in Appendix~\ref{sec:notes-individual-hii}.
+with data taken from the literature. Further details on each individual source and their references are given in Appendix~\ref{sec:notes-individual-hii}.
 
@@
 If the fluctuations are perfectly spatially homogeneous, then the
-two quantities are related \citep{1984ApJ...277..556S} as
+two quantities are related \citep{1984ApJ...277..556S} as:
 \begin{equation}\label{eq:functional}
@@
 In order to capture these two behaviors,
-We therefore propose the following idealized 2-parameter model
+we therefore propose the following idealized 2-parameter model
 for the autocorrelation function:
@@
 For the more distant sources, the principal observational limitation is the seeing.
-In three of the four sources,
+In three of the four sources (NGC 604, Hubble V and Hubble X),
 the derived values of \(s_0\) exceed 10\% of the correlation length.
@@
 
-There are two main difference between the previous investigations and our results: one is that the velocity dispersion is obtained as the width of the emission line profile integrated over the whole object or as the non-thermal line-width, which is different from the plane of the sky dispersion we are using and that our sample is smaller in the number of data.
+There are two main difference between the previous investigations and our results: one is that the velocity dispersion is obtained as the width of the emission line profile integrated over the whole object or as the non-thermal line-width, which is different from the plane of the sky dispersion we are using and that our sample is considerably smaller in the data points.
 The first problem is addressed in section \ref{sec:sigmapos-vs-sigmalos} where we discuss the relation between the line-of-sight and plane-of-sky velocities.
@@
 
-The second-order structure function measures the velocity fluctuations in the \hii{} regions under the assumption that exists an underlying velocity spectrum following an energy cascade.
-But this statistical technique is not unique in measuring the velocity fluctuations in the nebula and does not give information on the processes disturbing the ionized gas.
-Also, as mentioned in \citet{arthur2016turbulence} the possibility if these fluctuations can account for the non-thermal line broadening needs to be evaluated.
-
-Two parameters which are obtained from the velocity profile also measure the velocity fluctuations in the \hii{} regions: the standard deviation of the velocity centroids, \(\sigma\pos\), and the mean non-thermal linewidth, \(\langle \sigma_{\text{los}} \rangle\).
-These quantities allow us to compare the relation between the kinematical disorder on the plane-of-the-sky and along the line-of-sight \citep{2011MNRAS.413..705L}.
-
-As mentioned in the introduction, the \( \sigma_{\text{los}} \) parameter is estimated by correcting the observed linewidth for the contribution of broadening mechanism, equation \eqref{eq:sigma-los}, leaving just the random motions which are interpreted as turbulence along the line-of-sigth.
-This method is a simplification of the problem since it assume a Gaussian profile fit, which does not consider other components that could arise from different kinematics of the ionized gas and leaves out the broadening due to dust scattering.
-
-In the Figure~\ref{fig:los-vs-pos} we show the mean line-of-sight velocity dispersion versus the plane-of-sky velocity dispersion. 
-\citet{arthur2016turbulence} presents the same diagram for different emission lines of the Orion core nebula showing that the value \(\sigma_{\text{los}}\) (after considering the dust scattering) is roughly twice as the \(\sigma\pos\) (figure 14 on their work), while the \citet{2011MNRAS.413..705L} diagram, for a sample of small-to-intermediate size \hii{} regions in M33, approach unity (figure 4 on their work).
-The Figure~\ref{fig:los-vs-pos} shows that for our sample of \hii{} regions the fit we obtained follows the result of \citet{2011MNRAS.413..705L}.
-The relationship we found is \( \langle \sigma\los \rangle = (1.03 \pm 0.46) \sigma\pos - (7.7 \pm 2.9)\).
+The second-order structure function measures the velocity fluctuations in the \hii{} regions under the assumption that there exists an underlying velocity spectrum following an energy cascade.
+But this statistical technique is not unique in measuring the velocity fluctuations in the nebula.
+Two parameters which can be obtained from the velocity profile also measure the velocity fluctuations in the \hii{} regions: the standard deviation of the velocity centroids, \(\sigma\pos\), and the mean non-thermal linewidth, \(\langle \sigma_{\text{los}} \rangle\).
+These quantities allow us to compare the relationship between the kinematical disorder on the plane-of-the-sky and along the line-of-sight \citep{2011MNRAS.413..705L,arthur2016turbulence}.
+
+The \( \sigma_{\text{los}} \) parameter is estimated by correcting the observed linewidth for the contribution of broadening mechanism, equation \eqref{eq:sigma-los}, leaving just the random motions which are interpreted as random motions along the line-of-sigth.
+This method is a simplification of the problem since it assume a Gaussian profile fit, which does not consider other components that could arise from different kinematics processes of the ionized gas and leaves out the broadening due to dust scattering \citep{castaneda1988,1998ApJ...503..760H}.
+
+In the Fig.~\ref{fig:los-vs-pos} we show the mean line-of-sight velocity dispersion versus the plane-of-sky velocity dispersion plane.
+The relationship we obtain is \( \langle \sigma\los \rangle = (1.03 \pm 0.46) \sigma\pos + (7.7 \pm 2.9)\).
+\citet{arthur2016turbulence} presents the same diagram for different emission lines of the Orion core nebula showing that the value \(\sigma_{\text{los}}\) (after considering the dust scattering) is roughly twice as the \(\sigma\pos\) (figure 14 on their work), while the \citet{2011MNRAS.413..705L} diagram, for a sample of small-to-intermediate size \hii{} regions in M33, approach unity (figure 4 on their work) with a linear relation of \(\langle \sigma_{\text{los}} \rangle = (1.04 \pm 0.14) \sigma\pos + (8.15 \pm 0.93) \).
+
+As for the interpretation, it is possible to consider that large fluctuations of the turbulent velocities, which are spread over the entire ionized extent of the nebula, increase monotonically with the plane-of-sky dispersion.
+In this scenario, the main broadening mechanisms causing kinematical disorder along the line-of-sight are related to the velocity gradients of the clumpiness in the cloud and turbulent movements.
+On the plane-of-sky the consequences of those gradients and movements are measured in every pixel, consequently the spatial variations on the velocity field would depend on the targeted pixel, at the same time depending on the motions inside the cloud.
+Thus the \(\sigma\pos\) and \(\langle \sigma_{\text{los}} \rangle\) parameters increase in the same amount as the fluctuations grows \citep{2011MNRAS.413..705L}.
 
@@
 They consider an expanding shell where the mean velocity fluctuations on the plane of the sky are because the relative brightness of the redshifted and blueshifted hemispherers.
-In this case, the rms fractional variation in the emissivity on the scale diameter is found to be in the order of \(\sigma\pos / \sigma_{\text{los}}\).
-
-As for the \citet{2011MNRAS.413..705L} results, they consider that large fluctuations of the turbulent velocities, which are spread over the entire ionized extent of the nebula, monotonically increase with the plane-of-sky dispersion.
-In this scenario, the main broadening mechanisms the kinematical disorder along the line-of-sight is related to the velocity gradients of the clumpiness in the cloud and turbulent movements.
-On the plane-of-sky the consequences of those gradients and movements is measured in every pixel, consequently the spatial variations on the velocity field would depend on the targeted pixel, at the same time depending on the motions inside the cloud.
-Thus the \(\sigma\pos\) and \(\langle \sigma_{\text{los}} \rangle\) parameters increase monotonically as the amplitudes grows because the non-thermal dynamical processes in the \hii{} regions.
-They characterize this behavior for their \hii{} regions sample by fitting a linear relation of \(\langle \sigma_{\text{los}} \rangle = (1.04 \pm 0.14) \sigma\pos + (8.15 \pm 0.93) \) to their observed regions.
+In this case, the rms fractional variation in the emissivity on the scale diameter is found to be in the order of \(\sigma\pos / \sigma_{\text{los}}\) ratio.
 
@@
 
-Other important relation commonly used in the study of the interstellar medium is the diameter (or size) versus velocity dispersion.
+Other important relationship commonly used in the study of the interstellar medium is the diameter (or size) versus velocity dispersion.
 Table \ref{tab:RestStats} shows this result for our sample in the forth row. 
@@
 This relation is interpreted in terms of turbulence, particularly the Kolmogorov model which predicts a index of \num{0.33} so that larger regions presents more turbulence, and smaller regions less turbulence.
-It has been argued that this correlation method is not as powerful as using statistical functions \citep{1984ApJ...277..556S} but it is interesting that the index is consistent within different phases of the interstellar medium (see first paragraph of this section).
-On the other hand, we obtain \(\log \sigma\pos = (0.25 \pm 0.17) \log D - (0.2 \pm 0.38)\) which despite the large uncertainty is comparable with previous investigations within the error.
+It has been argued that this correlation method is not as powerful as using statistical functions \citep{1984ApJ...277..556S} but it is interesting that the index is consistent within different phases of the interstellar medium.
+We obtain \(\log \sigma\pos = (0.25 \pm 0.17) \log D - (0.2 \pm 0.38)\) which is comparable with \citet{1981MNRAS.194..809L} results.
 
@@
 
-The power-law index \(m\) shown in the last column of Table \ref{tab:Res} is used for comparison between the observations and the theoretical value of 0.67.
-All our indices are above this theoretical value and this is attributed to the fact that the \hii{} regions do not comply with the assumptions established in the development of the turbulent theory.
-
-\hii{} regions emerged from a molecular cloud with highly filamentary and clumpy density structure .
-There is a large increase in the temperature because of the photoionization, and the density gradients with the pressure gradients accelerate the flow which occurs on multiple scales consequence of the fractal nature of the molecular cloud \citep{arthur2016turbulence}.
+The power-law index \(m\) shown in the last column of Table \ref{tab:Res} is used for comparison between the observations derived index and the theoretical Kolmogorov value of 0.67.
+All our indices are above this theoretical value and this is attributed to the fact that the \hii{} regions do not comply with the conditions established in the development of the turbulent theory which assumes incompressible, subsonic and homogeneous three-dimensional flow.
+\hii{} regions emerged from a molecular cloud with highly filamentary and clumpy density structure.
+Inside the region there is a large increase in the temperature because of the photoionization, and the density gradients with the pressure gradients accelerate the flow which occurs on multiple scales consequence of the fractal nature of the molecular cloud \citep{arthur2016turbulence}.
 The radiation pressure, stellar winds and region expansion, among other physical processes would create pressure-driven shock waves propagating faster than the speed of sound in the medium.
-This would make the flow compressible and supersonic in \hii{} regions.
+This would make the flow compressible and supersonic in an inhomogenous gas cloud.
 Also, as \hii{} regions are three-dimensional objects our structure function results comes from a projection of this three-dimensional structure to a two-dimensional velocity field.
-But despite the complex nature of \hii{} regions and observational limitations we obtain a common pattern for the structure function and the value of the power-law index falls in a certain limited range of values.
-The differences in the power-law index with respect the theoretical value are often used as a diagnostic tools to identify properties that are not consider in the assumptions of the turbulence theory.
-
-As for any relation of the power-law index \(m\) we can see from table \ref{tab:RestStats} that this parameter does not correlate with any other parameter or physical property, being the least reliable for determining or concluding something about the nature of the physical processes inside the regions.
+But despite the complex nature of \hii{} regions and observational limitations, we obtain a common pattern for the structure function behaviour and the value of the power-law index falls in a certain limited range between \num{0.7} and \num{1.4}.
+
+The differences in the power-law index with respect the theoretical value are often used as a diagnostic tools to identify properties that are not consider in the assumptions of the turbulence theory \citetext{See table~1 of \citealp{arthur2016turbulence} and Sec.~1 of \citealp{lagrois2011}}.
+As an example there the so called \textit{projection smoothing} \citep{von1951methode,1987ApJ...317..686O} which is used to study the projection of a three-dimensional structure function on the plane.
+The relationships for the power-law are:
+
+\begin{equation}\label{eq:projection-smoothing-3d}
+m_{2D}= m_{3D} + 1
+\end{equation}
+%
+and  when the astronomical object present a sheet-like distribution of emitters we have the relation:
+%
+\begin{equation}\label{eq:projection-smoothing-2d}
+m_{2D} \sim m_{3D}
+\end{equation}
+
+As a conclusion, if the extension of the HII region is compared with its depth (three-dimensional case) the value of the index is \num{1.6}. 
+While the case where the extension is much greater than its depth (two-dimensional case) the region will have a value of \num{0.6}.
+From Table~\ref{tab:Res} we see that our results fall between these two previous values.
+
+As for any relation of the power-law index \(m\) and the physical properties of the \hii{} regions we can see from table \ref{tab:RestStats} that this parameter does not correlate with any other parameter or physical property, being the least reliable for determining or concluding something about the nature of the physical processes inside the regions.
 On the other hand, the lack of correlation and the presence of this power-law index describing the assumed energy cascade may be interpreted as a universal property of the velocity fluctuations independent of the observed object, which is the main consideration in the turbulence theory.
@@
 
-The observations point out to the existence of spatial correlation between velocities, that could be interpreted as turbulence. 
-Arguments against the existence of true, isotropic turbulence can be raised as, for example: i) the histograms of velocity are not always Gaussian, ii) only a fraction of the integrated emission lines of the \hii{} regions show true Gaussian profiles.
-The asymmetry in the emission line indicates coherent mass flow motions, 
-and sometimes is considered incompatible with turbulence. However, turbulence is in fact 
-a mixture of coherent and chaotic flows. 
-Only at the regime of the so-called fully developed turbulence the non-linear phenomena dominate completely the movement and the chaotic flow prevail. 
-The problem here is that a straightforward test for any turbulent model is a big challenge, as we are in the presence of many entangled effects. 
-However, the circumstantial evidence in favor of the existence of turbulent motions in \hii{} regions is overwhelming, and many are the potential sources of energy to create and maintain turbulence during the lifetime of an \hii{} region.
+%The observations point out to the existence of spatial correlation between velocities, that could be interpreted as turbulence. 
+%Arguments against the existence of true, isotropic turbulence can be raised as, for example: i) the histograms of velocity are not always Gaussian, ii) only a fraction of the integrated emission lines of the \hii{} regions show true Gaussian profiles.
+%The asymmetry in the emission line indicates coherent mass flow motions, 
+%and sometimes is considered incompatible with turbulence. However, turbulence is in fact 
+%a mixture of coherent and chaotic flows. 
+%Only at the regime of the so-called fully developed turbulence the non-linear phenomena dominate completely the movement and the chaotic flow prevail. 
+%The problem here is that a straightforward test for any turbulent model is a big challenge, as we are in the presence of many entangled effects. 
+%However, the circumstantial evidence in favor of the existence of turbulent motions in \hii{} regions is overwhelming, and many are the potential sources of energy to create and maintain turbulence during the lifetime of an \hii{} region.
 
@@
 
-For a correct analysis on the structure function it is necessary to consider the consequences that the observational box size and the seeing have on the results.
-To quantify the impact of these considerations on the final structure function, we perform a series of experiments using artificial turbulent velocity maps.
-In particular, our interest is to quantify how this observational limitations affect the determination of parameters such as the correlation length, \(r_0\), and the velocity field variance, \(\sigma\pos^2 \).
-
+To characterize the impact of the observational box size and the atmospheric seeing on the structure function we perform a series of experiments using artificial turbulent velocity maps.
+We quantify how these observational limitations affect the determination of astrophysical interest parameters such as the correlation length \(r_0\) and the velocity field variance \(\sigma\pos^2 \). 
 The artificial velocity maps are created using a modified version of the \textit{make$\_$extend} command from the \texttt{turbustat} Python library \citep{Koch2019AJ....158....1K}.
-We create a turbulent velocity field that follows a given power law with and a proposed correlation length, and a variance value indicated as true \(\sigma^2\).
-Using this true \(\sigma^2\) we obtained the true \(r_0\), and these values are used as a reference in the following experiments to quantify the variations.
-The objective is to create a sample of multiple divided maps with different seeing width and size to compute the structure function in each and characterize the variations.
+The modification add a tapering to the power law so that the generated fields are uncorrelated at large scales.
+The artificial fields follows a given power law with with a correlation length giving a variance value indicated as true \(\sigma^2\).
+Using this true \(\sigma^2\) we obtain the true \(r_0\) and these values are used as a reference in the experiments to quantify the variations.
 
@@
     each of linear size \(L \times L\) where \(L = 2^{9 - j}\).
+    The color scale is the same for all maps and it considers \(- 3\) to \(+ 3\) times the standard deviation.
     (b)~Resultant structure functions.
@@
 
-The Figure \ref{fig:finite-box}a shows some of the simulated velocity fields we use to study the variations in the structure function with respect to the size of the observational box.
-Initially we have an original field of \(512 \times 512 \) pixels that are divided \(n\) times and produce \(N = 4^n\) fields, where each one has a linear size \(L \times L \) with \(L = 2^{9 -n}\).
-The structure function is calculated for each division and later we average all the divisions of the corresponding map. 
-The Figure \ref{fig:finite-box}b shows in solid lines the normalized averaged structure functions for the maps in Figure \ref{fig:finite-box}a.
-The number \(N\) of divisions and the length \(L\) are indicated in each structure function.
-The shaded areas show the deviation that each average structure function has due to the different divisions. 
-%\textit{(Note: I modified the Figure adding \(\sigma^2\) and \(r_0\) for each SF since I think it is easier and more directly to grasp the effect of reducing the box size.
-The figure is more 'noisy' but if it seems like it contribute to nothing we can change it back.)}
-
-The blue horizontal and vertical dashed lines show the true \(r_{0}\) and the value of \(B(r) / \sigma^2 = 1 \), respectively.
+The Fig. \ref{fig:finite-box}a shows some of the artificial velocity fields used to study the variations in the structure function with respect to the size of the observational box.
+Initially we have a velocity field of \(512 \times 512 \) pixels that is divided \(n\) times (with \(n = 1 - 6\)) producing \(N = 4^n\) fields , where each one has a linear size \(L \times L \) with \(L = 2^{9 -n}\).
+The structure function is determined for each division and later we average all the divisions obtaining a characteristic structure function for \(L = 256, 128, 64,\) etc.
+
+In the Fig. \ref{fig:finite-box}b we show in solid lines the normalized averaged structure functions for the maps in Figure \ref{fig:finite-box}a.
+The number \(N\) of divisions and the length \(L\) are indicated for each structure function.
+The shaded areas show the deviation that each averaged structure function has due to the different divisions. 
+The horizontal and vertical blue dashed lines show the true \(r_{0}\) and the value of \(B(r) / \sigma^2 = 1 \), respectively.
 The colored dotted lines indicate the averages, taking into account all the divisions of each map, of the apparent \(r_ {0}\) and the apparent \(\sigma^2 \).
-From this analysis it is clear that \(r_0\) and \(\sigma^ 2 \) decrease with respect to the true values as the size \(L\) of the observational box decreases. 
+It is clear that \(r_0\) and \(\sigma^ 2 \) decrease with respect to the true values as the size \(L\) of the observational box decreases. 
 This analysis is performed on different maps (no images are shown) given a different power law in the velocity spectrum and different correlation lengths, giving the same results.
 
-Figure \ref{fig:finite-box-effect}a shows the empirical ratios of the correlation length of each averaged map with respect to the true correlation length (\(\text{apparent } r_ 0 /\text{true } r_0 \) ), as well as the ratio between the averaged variance of each divided map and the true variance (\(\text{apparent } \sigma^2  / \text{true } \sigma^2\)).
+Fig.
+\ref{fig:finite-box-effect}a shows the empirical ratios of the correlation length of each averaged map with respect to the true correlation length (\(\text{apparent } r_ 0 /\text{true } r_0 \) ) and the ratio between the averaged variance of each divided map and the true variance (\(\text{apparent } \sigma^2  / \text{true } \sigma^2\)).
 We observe that for the values where \(L> 20r_0 \) the change in the ratios is null.
-It is for the values where \( L < 10 r_0 \) where we found a decrease on both ratios.
-On the other hand, Figure \ref{fig:finite-box-effect}b shows the model-derived \(r_0\) and \(\sigma^ 2 \) values using the fitting procedure with the \texttt{lmfit} library.
-In this case we see that the model fitting works much better than the empirical measurement, which gives reliable values so long \(L > 3r_0 \)
-This behavior is fulfilled for all simulated maps with different power law in the velocity spectrum and  indicated with different colored circles in Figure \ref{fig:finite-box-effect}ab.
-The empirical variations of the ratios is described by the  dashed line in Figure \ref{fig:finite-box-effect}ab given by the equation:
+It is for the values where \( L < 10 r_0 \) where there is a decrease.
+This behavior is fulfilled for all simulated maps with different power law and correlation length in the velocity spectrum indicated with different colored circles in Figure \ref{fig:finite-box-effect}a.
+
+On the other hand, Fig. \ref{fig:finite-box-effect}b shows the model-derived \(r_0\) and \(\sigma^ 2 \) values using the fitting procedure with the \texttt{lmfit} library.
+In this case we see that the model fitting works much better than the empirical measurement, which gives reliable values so long \(L > 3r_0 \).
+
+The empirical variations of the ratios is described by the  dashed line in Fig. \ref{fig:finite-box-effect} a and b, and is given by the equation:
 
@@
 Ground-based astronomical observations are affected by the seeing produced by the atmosphere.
-When calculating the structure function of these observations, this seeing affects the results at small-scale separations due to the smoothing of velocity fluctuations between adjacent pixels.
-To study the consequences of the seeing we calculate the structure function of velocity maps where an artificial Gaussian seeing with different line widths has been introduced.
-The artificial velocity maps are created in the same way as to study the effect of the observational box.
-Seeing in velocity maps is added via the \texttt{astropy} Python library \citep{astropy:2013} using the \textit{Gaussian2DKernel} command.
-
-The rows in Figure \ref{fig:seeing-reduction}a show a synthetic velocity field of 512 \(\times\) 512 divided into four maps of 256 \(\times \) 256.
-The color scale is the same for all maps and it considers \(- 3\) to \(+ 3\) times the standard deviation.
-A Gaussian seeing, \(s_0 \) is applied to each division, with an RMS width ranging from 1 to 32 pixels, shown in the columns of Figure \ref{fig:seeing-reduction}. 
+When calculating the structure function of the observational data, the seeing affects the structure function results at small-scale separations due to the smoothing of velocity fluctuations between adjacent pixels.
+To study the effect of the seeing we calculate the structure function of simulated velocity maps where an artificial Gaussian seeing with different line widths has been introduced.
+The artificial velocity maps are created in the same way as in Section~\ref{sec:finite-box-effects}.
+The seeing in velocity maps is added via the \texttt{astropy} Python library \citep{astropy:2013} using the \textit{Gaussian2DKernel} command.
+
+Fig. \ref{fig:seeing-reduction}a shows column an artificial velocity field of 512 \(\times\) 512  divided into four maps of 256 \(\times \) 256 pixels each which are displayed in each row.
+A Gaussian seeing \(s_0 \) is applied to each division with an RMS width given by \(s_0 = 2^n\) pixels with \(n = 0-5\) shown in the different columns. 
 The structure function is computed in these maps and the averaged considering the same seeing.
 
-The solid lines in Figure \ref{fig:seeing-reduction}b  show the ratio of the structure function of the averages of the maps with their respective seeing and the map without it: \(B (r, s_0 ) / B (r, s_0 = 0) \).
-The circle symbols indicate the value of 2\(s_0\) while the plus symbols indicate the apparent correlation length of smoothed map.
-The vertical dotted line indicates the true \(r_ {0} \).
-
-The dashed lines in Figure \ref{fig:seeing-reduction}b are  empirically fits for each ratio.
+The solid lines in Figure \ref{fig:seeing-reduction}b show the ratio of the averaged structure function of the maps with their respective seeing to the unsmoothed map: \(B (r, s_0 ) / B (r, s_0 = 0) \).
+The circle symbols indicate the value of 2\(s_0\), the plus symbols indicate the apparent correlation length of the smoothed maps and the vertical dotted line indicates the true \(r_{0}\).
+
+The dashed lines in Figure \ref{fig:seeing-reduction}b are  empirically fits for each ratio and characterizes the decrease in the structure function for each value of seeing.
 To obtain this fit, we start from a convolution of an emission line and Gaussian seeing.
@@
 
-Then we calculate the average velocity difference of the original map, \(\Delta v \), and the smoothed map, \(\tilde{\Delta v}\), in the points \( x = \{0, \delta \} \).
-This expansion gives a term that modifies the final form of the structure function, \(~B (r)\), where the structure function without the seeing, \(B(r) \), is corrected by the term \(S_0(r; s_0)\) which has the form:
+Then we calculate the average velocity difference of the original map, \(\Delta v \), and the smoothed map, \(\tilde{\Delta v}\), in the arbitrary points \( x = \{0, \delta \} \).
+The expansion of the convolution at small separations gives a term \(S_0(r; s_0)\) that modifies the structure function which has the form:
 
@@
 
-\begin{equation}\label{eq:seeingemp}
-S(r; s_0, r_0) =  \frac{e^\frac{-s_0}{r_0}}{2} \left(1 + \tanh{a \text{ln} \frac{r}{2s_0}} \right)
-\end{equation}
+%\begin{equation}\label{eq:seeingemp}
+%S(r; s_0, r_0) =  \frac{e^\frac{-s_0}{r_0}}{2} \left(1 + \tanh{a \text{ln} \frac{r}{2s_0}} \right)
+%\end{equation}
 %
-and the final form of the equation \ref{eq:seeingemp} after a mathematical simplification gives:
+%and the final form of the equation \ref{eq:seeingemp} after a mathematical simplification gives:
 
@@
 %
-which describes the fit (dashed lines) in Figure \ref{fig:seeing-reduction}b.
-
-The equation \ref{eq:seeingemp2} is used to correct the observational structure function, \(B(r)\).
+which describes the dashed lines in Figure \ref{fig:seeing-reduction}b. 
+The equation \ref{eq:seeingemp2} is used to correct the observational structure function in equation \eqref{eq:sf-functional}.
 
@@
 With other 3 B-type stars they form the Trapezium cluster.
-The bright region that surrounds these massive ionizing stars is called the the Huygens region (Orion core henceforth).
-In the southwest direction of the Huygens region there is a drop in the brightness as one approach a much larger region called Extended Orion Nebula \citetext{EON henceforth;  \citealp{2008Sci...319..309G}}
+The bright region that surrounds these massive ionizing stars is called the the Huygens region.
+%In the southwest direction of the Huygens region there is a drop in the brightness as one approach a much larger region called Extended Orion Nebula \citetext{EON henceforth;  \citealp{2008Sci...319..309G}}
 The position of Orion near the side of the Orion Molecular Cloud (OMC-1) make it an ongoing star formation with a large population of young star, some of which are the sources of stellar jets and Herbig-Haro objects \citep{1993ApJ...410..696O}.

### 2022-08-06 strucfunc_paper.tex
Finish revisions to section 5.2
But still need to revise the subsections

@@
 Detailed comparisons with previous results are given
-in section~\ref{sec:notes-individual-hii}.
+in Appendix~\ref{sec:notes-individual-hii}.
 In summary, we agree with previous studies in cases where there
@@
 %methods for our analysis
-In section \ref{sec:results} we show that each \hii{} region of our sample can be characterized with parameters that are particular to each velocity field.
-We used these parameters to estimate the scaling relations between them and the main physical properties of each region.
-To accomplish this we implement a hierarchical Bayesian model for fitting a straight line using the \texttt{linmix} Python library which is based on the procedure of \cite{2007ApJ...665.1489K}.
-The physical properties in Table \ref{tab:regions-properties} are used as the independent variable \(X\) while the derived turbulent parameters of Table \ref{tab:Res} are used as the dependent variable \(Y\).
-In the following analysis we left out the EON to avoid redundancy of the regions.
-For physical properties values where uncertainties are not reported (size and luminosity), we consider an error of \num{10}\% of the value.
+We look for correlations and scaling relations 
+between the physical parameters of the \hii{} regions
+and the parameters of the fluctuating velocity fields
+that we derived in section~\ref{sec:results}.
+To accomplish this we implement a hierarchical Bayesian model for linear regression using the \texttt{linmix} Python library, which is based on the procedure of \cite{2007ApJ...665.1489K}.
+Thus we fit relations of the form
+\(Y = a X + b\)
+where \(X = \log_{10} x\) and \(Y = \log_{10} y\)
+with \(x, y \in \{d, D, L(\ha), \sigma\pos, r_0, m\}\)
+(taken from the physical properties in Table~\ref{tab:regions-properties}
+and the derived turbulent parameters of Table~\ref{tab:Res}).
+Note that, unlike with an Ordinary Least Squares method,
+the \citeauthor{2007ApJ...665.1489K} method
+uses an errors-in-variables model that is symmetric in \(X\) and \(Y\).
+Thus the fitted relation between the underlying variables
+is of the power-law form: \(y = 10^b\, x^a\).
+Since the main focus of this paper is the turbulent velocity field,
+we restrict consideration to correlations that include
+one of the three structure function parameters,
+\(\sigma\pos\), \(r_0\), or \(m\), as the  \(y\) variable. 
+Additionally, we fit a strictly linear relationship between
+the plane-of-sky and line-of-sight velocity dispersions:
+\(X = \sigma\pos\), \(Y = \sigma\los\).
+The reason for not taking the logarithm in this instance is
+both to facilitate comparison with previous studies
+and to allow for a zero-point offset in the relation.
+
+In the following analysis we omit the EON region since the
+model fits were relatively poorly constrained by the observations.
+For physical properties where uncertainties are not reported (size and luminosity), we assume an error of \num{10}\% of the value.
 The same criteria is used for the uncertainty values of the mean non-thermal linewidths for 30 Doradus and NGC 346.
-For the turbulent parameters we use the relative error considering the 2-\(\sigma\) interval. 
-Our main correlation results are shown in Table \ref{tab:RestStats} in ascending order for the \(p\)-value.
-In the Figs.
+For the turbulent parameters we use the relative error
+from our model fits, considering the 2-\(\sigma\) interval.
+
+Results for the most significant correlations,
+as measured by the Pearson correlation coefficient \(r\),
+are given in Table~\ref{tab:RestStats} in descending order of \(r^2\).
+We find three cases of highly significant correlations
+with significance level \(p < 0.01\),
+which are illustrated in
+Figures~\ref{fig:sigvsl}--\ref{fig:los-vs-pos}:
+\(r_0\)  versus \(D_{\hii}\), \(\sigma\pos\) versus \(L(\ha)\),
+and \(\sigma\los\) versus \(\sigma\pos\).
+Each of these is discussed in turn in the following sections.
+The remaining correlations
+are at best marginally significant (\(p > 0.05\)),
+including all correlations of the power law slope \(m\)
+with any other parameter.
+
+% In the Figs.
 \ref{fig:sigvsl}, \ref{fig:rvsR} and \ref{fig:los-vs-pos} we show the plots for the correlations with a significance level \(p < \num{0.05}\) which corresponds to the first three rows in Table \ref{tab:RestStats}.
-In the Figs.
+% In the Figs.
 the black solid line is the input regression line which is described by the equation shown in the plot and the red thin lines are a random sample (\num{ \sim 400}) from the posterior distribution within one standard deviation from the slope and the \(Y\)-intercept value.

### 2022-08-12 strucfunc_paper.tex
Improve some figure captions

@@
 and the derived turbulent parameters of Table~\ref{tab:Res}).
+Thus the fitted relation between the original variables
+is of the power-law form: \(y = 10^b\, x^a\).
 Note that, unlike with an Ordinary Least Squares method,
 the \citeauthor{2007ApJ...665.1489K} method
-uses an errors-in-variables model that is symmetric in \(X\) and \(Y\).
-Thus the fitted relation between the underlying variables
-is of the power-law form: \(y = 10^b\, x^a\).
+uses an errors-in-variables model that allows for
+measurement uncertainty in both \(X\) and \(Y\).
 Since the main focus of this paper is the turbulent velocity field,
@@
 \(\sigma\pos\), \(r_0\), or \(m\), as the  \(y\) variable. 
-Additionally, we fit a strictly linear relationship between
+In addition, we fit a strictly linear relationship between
 the plane-of-sky and line-of-sight velocity dispersions:
@@
 \includegraphics[width=3in]{Figures/corr-svsL}
-\caption{The log \(\sigma\pos\) - log $L(H_{\alpha})$ plane derived form our results an data in the literature.
-The markers indicates galactic (triangles), Magellanic (squares) and extragalactic (circles) regions.
-The black solid line is the input regression line which is described by the equation in the plot, and the red thin lines are a random sample (\num{ \sim 400}) from the posterior distribution within one standard deviation from the slope and the \(Y\)-intercept value.
-}
+\caption{
+  The relationship between plane-of-sky velocity dispersion,
+  \(\log_{10} \sigma\pos\),
+  and \hii{} region luminosity,
+  \(\log_{10} L(\ha)\),
+  derived from our results.
+  The markers indicates Galactic (triangles),
+  Magellanic (squares) and extragalactic (circles) regions.
+  The black solid line is the median linear regression,
+  with thin red lines showing 400 random samples from the posterior
+  distribution to indicate the uncertainty in the regression.}
 \label{fig:sigvsl}
@@
 \caption{
-Same information as Fig. \ref{fig:sigvsl} but for the log \(r_0\) - log \(S\) plane derived form our results an data in the literature. 
-}
+  As Figure~\ref{fig:sigvsl} but for the relationship between
+  correlation length of velocity fluctuations,
+  \(\log_{10} r_0\),
+  and  \hii{} region diameter,
+  \(\log_{10} D_{\hii}\).}
 \label{fig:rvsR}
@@
 \caption{
-Same information as Fig.
-\ref{fig:sigvsl} but for the \(\sigma_{\text{pos}}\)-\(\langle \sigma_{\text{los}} \rangle\) plane.
-The dashed line corresponds to the linear fit obtained by \citet{2011MNRAS.413..705L} which correspond to a sample of small-to-intermediate size \hii{} regions in M33.
+  As Figure~\ref{fig:sigvsl} but for the relationship between
+  line-of-sight non-thermal velocity dispersion,
+  \(\sigma\los\),
+  and plane-of-sky velocity dispersion,
+  \(\sigma\pos\).
+  The dashed line shows the the linear fit obtained by
+  \citet{2011MNRAS.413..705L} for a sample of
+  small-to-intermediate size \hii{} regions in the M33 galaxy. 
 }

### 2022-08-12 strucfunc_paper.tex
Re-order subsections in discussion

@@
    Red and green lines show the effects of observational limitations
-   at small scales (seeing and noise)
-   and at large scales (finite-map effects).
+   at small scales due to seeing and noise.
    (b)~Examples of inhomogeneous effects at large scales,
@@
 \input{Corr}
+\begin{figure}
+\centering 
+\includegraphics[width=3in]{Figures/corr-los-vs-pos}
+\caption{
+  The relationship between 
+  line-of-sight non-thermal velocity dispersion,
+  \(\sigma\los\),
+  and plane-of-sky dispersion of velocity centroids,
+  \(\sigma\pos\)
+  derived from our results.
+  Symbols indicate Galactic (triangles),
+  Magellanic (squares) and extragalactic (circles) regions.
+  The black solid line is the median linear regression,
+  with thin red lines showing 400 random samples from the posterior
+  distribution to indicate the uncertainty in the regression.  
+  The dashed line shows the the linear fit obtained by
+  \citet{2011MNRAS.413..705L} for a sample of
+  small-to-intermediate size \hii{} regions in the M33 galaxy. 
+}
+\label{fig:los-vs-pos}
+\end{figure}
 
@@
 \caption{
-  The relationship between plane-of-sky velocity dispersion,
+  The relationship between
+  plane-of-sky dispersion of velocity centroids,
   \(\log_{10} \sigma\pos\),
@@
   derived from our results.
-  The markers indicates Galactic (triangles),
-  Magellanic (squares) and extragalactic (circles) regions.
-  The black solid line is the median linear regression,
-  with thin red lines showing 400 random samples from the posterior
-  distribution to indicate the uncertainty in the regression.}
+  Symbols and line types are as in Figure~\ref{fig:sigvsl}. 
+}
 \label{fig:sigvsl}
@@
 \caption{
-  As Figure~\ref{fig:sigvsl} but for the relationship between
+  The relationship between
   correlation length of velocity fluctuations,
@@
   and  \hii{} region diameter,
-  \(\log_{10} D_{\hii}\).}
+  \(\log_{10} D_{\hii}\)
+  derived from our results.
+  Symbols and line types are as in Figure~\ref{fig:sigvsl}. 
+}
 \label{fig:rvsR}
 \end{figure}
-
-\begin{figure}
-\centering 
-\includegraphics[width=3in]{Figures/corr-los-vs-pos}
-\caption{
-  As Figure~\ref{fig:sigvsl} but for the relationship between
-  line-of-sight non-thermal velocity dispersion,
-  \(\sigma\los\),
-  and plane-of-sky velocity dispersion,
-  \(\sigma\pos\).
-  The dashed line shows the the linear fit obtained by
-  \citet{2011MNRAS.413..705L} for a sample of
-  small-to-intermediate size \hii{} regions in the M33 galaxy. 
-}
-\label{fig:los-vs-pos}
-\end{figure}
-
-\subsubsection{Luminosity vs centroid velocity dispersion}\label{sec:L-vs-sigmapos}
-
-The Fig. \ref{fig:sigvsl} shows the log \(\sigma\pos\)-log \(\text{L}(\text{H}_{\alpha})\) plane.
-This relation is commonly employ in the literature  and can be use to investigate how reliable is our derived velocity dispersion.
-The fit we obtain is \(\log \sigma\pos = (0.27 \pm 0.10) \log \text{L}(\text{H}_{\alpha})-(9.9 \pm 4.0)\).
-Since it is customary in the literature to present \(\text{L} (\text{H}_{\alpha})\) as the dependent variable we also calculate this relation: taking the inverse of slope in Fig.
-\ref{fig:sigvsl} we have \(\text{L}_{\text{H}_{\alpha}} \propto \sigma^{3.6 \pm 1.4}\) and using the same procedure in \textit{linmix} and changing the variables we obtain \(\log \text{L}(\text{H}_{\alpha}) = (2.8\pm 1.0) \log \sigma\pos -(36 \pm 4)\).
-
-The relationship \(\text{L}_{\text{H}} \propto \sigma^{\alpha}\) has been extensively investigated  in the context of giants \hii{} regions obtaining a value for \(\alpha\) of \( \sim 4\)\citep{terlevich1981,1988A&A...201..199A} and \num{2.87 \pm 0.2} \citep{Rozas:2006b}.
-Complementing previous results \citet{2012MNRAS.422.3339W} found that star-forming regions at \(z \sim 1.3\) and local \hii{} regions follow a relation with \(\alpha = 4.18 \pm 0.21\).
-\citet{Moiseev:2015a} found that this relation also holds for dwarf galaxies with a value of \(\alpha \sim 5\).
-\citet{2018MNRAS.474.1250F} presented the relationship between integrated H$_{\beta}$ line luminosity for new data of 36 giant HII regions obtaining \(\text{L}_{\text{H}_{\beta}} \propto \sigma^{5.02 \pm 0.21}\).
-Recently, \citet{2020ApJ...888..113W} studied the properties of high-\(z\) and local \hii{} galaxies among some GEHRs findig a value of \(\alpha \sim 5\).
-
-There are two main difference between the previous investigations and our results: one is that the velocity dispersion is obtained as the width of the emission line profile integrated over the whole object or as the non-thermal line-width, which is different from the plane of the sky dispersion we are using and that our sample is considerably smaller in the data points.
-The first problem is addressed in section \ref{sec:sigmapos-vs-sigmalos} where we discuss the relation between the line-of-sight and plane-of-sky velocities.
-But despite these problems, the fact that this relationship holds in our results (within the errors) is interesting considering that the \(\sigma\pos\) is derived from the structure function, while the \(\text{L}(\text{H}_{\alpha})\) values comes from different sources unrelated to our data (see the Appendix~\ref{sec:notes-individual-hii}).
-This means that the proposed structure function model describes within certain accuracy the velocity field fluctuations and that the parameters obtained can be interpreted as a true kinematic property of the \hii{} region velocity field.
-
-\subsubsection{Diameter vs correlation length}\label{sec:D-vs-r0}
-
-The Figure \ref{fig:rvsR} shows the relation of the correlation length \(r_0\) and the diameter \(D\) of the region. 
-The relationship we found is \(\log r_0 = (0.95 \pm 0.33) \log D - (1.6 \pm 0.7)\).
-The values of \(D\) are taken from \citet{1984ApJ...287..116K} and correspond to the outer
-limits seen from visual inspection of \ha{} photographs.
-These values would represent an upper limit of the size of each region.
-Since these objects do not posses physical edges the determination of their size is not trivial.
-Due to the above, we chose these set values since they are from an unique source and are foreign to our calculations and observations, which reduced the bias in the scaling law we obtain.
-
-Ideally the correlation length \(r_0\) should represent the scale of dominant energy injection.
-It is unclear what are the precise mechanisms driving the turbulence in \hii{} regions.
-There are several energy sources that could provide or contribute to the energy required: of the order of kpc we have the differential rotations of the galaxy that produces shear at large scale. 
-At scales of the order of hundreds of pc the supernova explosions inject a large amount of kinetic energy.
-At scales of several tens of pc the expansion of \hii{} regions and stellar winds are a source of energy, and bipolar flows, shocks, jets and champagne flows inject energy at small scales about one tenth of a pc.
-Many of these mechanisms, at some extent, affect all the \hii{} regions studied in this work, so the most probable scenario is that the velocity fluctuations are consequence of the combination of various mechanism.
-
-The dependence on \(r_0\) and the diameter can be interpreted in terms that each region presents a characteristic energy injection mechanism (or combination) and despite the presence of the different mechanisms there is some unique combination that drives the input energy in each region.
 
@@
 In this case, the rms fractional variation in the emissivity on the scale diameter is found to be in the order of \(\sigma\pos / \sigma_{\text{los}}\) ratio.
+
+\subsubsection{Luminosity vs centroid velocity dispersion}\label{sec:L-vs-sigmapos}
+
+The Fig. \ref{fig:sigvsl} shows the log \(\sigma\pos\)-log \(\text{L}(\text{H}_{\alpha})\) plane.
+This relation is commonly employ in the literature  and can be use to investigate how reliable is our derived velocity dispersion.
+The fit we obtain is \(\log \sigma\pos = (0.27 \pm 0.10) \log \text{L}(\text{H}_{\alpha})-(9.9 \pm 4.0)\).
+Since it is customary in the literature to present \(\text{L} (\text{H}_{\alpha})\) as the dependent variable we also calculate this relation: taking the inverse of slope in Fig.
+\ref{fig:sigvsl} we have \(\text{L}_{\text{H}_{\alpha}} \propto \sigma^{3.6 \pm 1.4}\) and using the same procedure in \textit{linmix} and changing the variables we obtain \(\log \text{L}(\text{H}_{\alpha}) = (2.8\pm 1.0) \log \sigma\pos -(36 \pm 4)\).
+
+The relationship \(\text{L}_{\text{H}} \propto \sigma^{\alpha}\) has been extensively investigated  in the context of giants \hii{} regions obtaining a value for \(\alpha\) of \( \sim 4\)\citep{terlevich1981,1988A&A...201..199A} and \num{2.87 \pm 0.2} \citep{Rozas:2006b}.
+Complementing previous results \citet{2012MNRAS.422.3339W} found that star-forming regions at \(z \sim 1.3\) and local \hii{} regions follow a relation with \(\alpha = 4.18 \pm 0.21\).
+\citet{Moiseev:2015a} found that this relation also holds for dwarf galaxies with a value of \(\alpha \sim 5\).
+\citet{2018MNRAS.474.1250F} presented the relationship between integrated H$_{\beta}$ line luminosity for new data of 36 giant HII regions obtaining \(\text{L}_{\text{H}_{\beta}} \propto \sigma^{5.02 \pm 0.21}\).
+Recently, \citet{2020ApJ...888..113W} studied the properties of high-\(z\) and local \hii{} galaxies among some GEHRs findig a value of \(\alpha \sim 5\).
+
+There are two main difference between the previous investigations and our results: one is that the velocity dispersion is obtained as the width of the emission line profile integrated over the whole object or as the non-thermal line-width, which is different from the plane of the sky dispersion we are using and that our sample is considerably smaller in the data points.
+The first problem is addressed in section \ref{sec:sigmapos-vs-sigmalos} where we discuss the relation between the line-of-sight and plane-of-sky velocities.
+But despite these problems, the fact that this relationship holds in our results (within the errors) is interesting considering that the \(\sigma\pos\) is derived from the structure function, while the \(\text{L}(\text{H}_{\alpha})\) values comes from different sources unrelated to our data (see the Appendix~\ref{sec:notes-individual-hii}).
+This means that the proposed structure function model describes within certain accuracy the velocity field fluctuations and that the parameters obtained can be interpreted as a true kinematic property of the \hii{} region velocity field.
+
+\subsubsection{Diameter vs correlation length}\label{sec:D-vs-r0}
+
+The Figure \ref{fig:rvsR} shows the relation of the correlation length \(r_0\) and the diameter \(D\) of the region. 
+The relationship we found is \(\log r_0 = (0.95 \pm 0.33) \log D - (1.6 \pm 0.7)\).
+The values of \(D\) are taken from \citet{1984ApJ...287..116K} and correspond to the outer
+limits seen from visual inspection of \ha{} photographs.
+These values would represent an upper limit of the size of each region.
+Since these objects do not posses physical edges the determination of their size is not trivial.
+Due to the above, we chose these set values since they are from an unique source and are foreign to our calculations and observations, which reduced the bias in the scaling law we obtain.
+
+Ideally the correlation length \(r_0\) should represent the scale of dominant energy injection.
+It is unclear what are the precise mechanisms driving the turbulence in \hii{} regions.
+There are several energy sources that could provide or contribute to the energy required: of the order of kpc we have the differential rotations of the galaxy that produces shear at large scale. 
+At scales of the order of hundreds of pc the supernova explosions inject a large amount of kinetic energy.
+At scales of several tens of pc the expansion of \hii{} regions and stellar winds are a source of energy, and bipolar flows, shocks, jets and champagne flows inject energy at small scales about one tenth of a pc.
+Many of these mechanisms, at some extent, affect all the \hii{} regions studied in this work, so the most probable scenario is that the velocity fluctuations are consequence of the combination of various mechanism.
+
+The dependence on \(r_0\) and the diameter can be interpreted in terms that each region presents a characteristic energy injection mechanism (or combination) and despite the presence of the different mechanisms there is some unique combination that drives the input energy in each region.
 

### 2022-08-19 strucfunc_paper.tex
Javier changes 2022-08-19

--- 2022-08-12 strucfunc_paper.tex
@@
 \begin{tabular}{cCCCC}\toprule
-\hii{}    &  \text{Distance,}\ d & \text{Diameter,}\ D & \log L(\ha) &  \langle \sigma\los \rangle \\
+\hii{}    &  \text{Distance,}\ d & \text{Diameter,}\ D_{\hii} & \log L(\ha) &  \langle \sigma\los \rangle \\
   Region    &  [\si{kpc}]          &  [\si{pc}]    &  [\si{erg.s^{-1}}]            &    [\si{km.s^{-1}}]  \\ 
@@
   The black solid line is the median linear regression,
-  with thin red lines showing 400 random samples from the posterior
+  with thin red lines showing 100 random samples from the posterior
   distribution to indicate the uncertainty in the regression.}

### 2022-08-19 strucfunc_paper.tex

--- 2022-08-12 strucfunc_paper.tex
@@
   The black solid line is the median linear regression,
-  with thin red lines showing 400 random samples from the posterior
+  with thin red lines showing 100 random samples from the posterior
   distribution to indicate the uncertainty in the regression.  

### 2022-08-19 strucfunc_paper.tex
Work last week on the correlations

@@
 
-\subsection{Scaling relations between physical properties and turbulent parameters}\label{sec:scaling-relations}
+\subsection{Scaling relations for turbulence parameters}\label{sec:scaling-relations}
 
@@
 
-\subsubsection{Relationship between plane-of-sky and mean line-of-sight velocity dispersion}\label{sec:sigmapos-vs-sigmalos}
+\subsubsection{Plane-of-sky vs line-of-sight
+  velocity dispersions}
+\label{sec:sigmapos-vs-sigmalos}
+
+In the Figure~\ref{fig:los-vs-pos} we show the
+mean non-thermal line-of-sight velocity dispersion
+\(\langle\sigma\los\rangle\)
+(obtained from the spectral line profiles)
+versus the plane-of-sky dispersion of mean velocities
+\(\sigma\pos\)
+(obtained from our structure function fits).
+The relationship we obtain is
+\( \langle \sigma\los \rangle = (1.03 \pm 0.46) \sigma\pos + (7.7 \pm 2.9)\),
+which can be compared with previous results
+using different types of samples.
+
+\citet{2011MNRAS.413..705L} surveyed
+a sample of small-to-intermediate size \hii{} regions in M33,
+finding
+\(\langle \sigma_{\text{los}} \rangle = (1.04 \pm 0.14) \sigma\pos + (8.15 \pm 0.93) \)
+for their sub-sample with higher resolution observations
+(21 sources).
+This is shown as the dashed line in Figure~\ref{fig:los-vs-pos},
+which can be seen to be almost identical to our own result. 
+Both fits are consistent with a slope of unity and an offset of
+\(\SI{8}{km.s^{-1}}\).
+
+\citet{arthur2016turbulence} calculate the relationship
+between \(\langle\sigma\los\rangle\) and \(\sigma\pos\) for different optical emission lines
+([\ion{S}{2}], [\ion{N}{2}], \ha, [\ion{O}{3}])
+in the Orion Nebula, finding \(\langle\sigma\los \approx 2 \sigma\pos\rangle\),
+which is shown by the MISSING line in Figure~\ref{fig:los-vs-pos}.
+Although this line is a fair representation of the low-\(\sigma\)
+points in our sample, it fails badly for highest dispersion source,
+30~Doradus.
+
+A clear outlier from the general trend
 
@@
 
-In the Fig.~\ref{fig:los-vs-pos} we show the mean line-of-sight velocity dispersion versus the plane-of-sky velocity dispersion plane.
-The relationship we obtain is \( \langle \sigma\los \rangle = (1.03 \pm 0.46) \sigma\pos + (7.7 \pm 2.9)\).
-\citet{arthur2016turbulence} presents the same diagram for different emission lines of the Orion core nebula showing that the value \(\sigma_{\text{los}}\) (after considering the dust scattering) is roughly twice as the \(\sigma\pos\) (figure 14 on their work), while the \citet{2011MNRAS.413..705L} diagram, for a sample of small-to-intermediate size \hii{} regions in M33, approach unity (figure 4 on their work) with a linear relation of \(\langle \sigma_{\text{los}} \rangle = (1.04 \pm 0.14) \sigma\pos + (8.15 \pm 0.93) \).
+At least three different
 

### 2022-08-31 strucfunc_paper.tex
More work on sec 5.2.1

@@
 
-Detailed comparisons with previous results are given
+Specific comparisons for individual sources are given
 in Appendix~\ref{sec:notes-individual-hii}.
@@
 which are illustrated in
-Figures~\ref{fig:sigvsl}--\ref{fig:los-vs-pos}:
-\(r_0\)  versus \(D_{\hii}\), \(\sigma\pos\) versus \(L(\ha)\),
-and \(\sigma\los\) versus \(\sigma\pos\).
+Figures~\ref{fig:los-vs-pos}--\ref{fig:rvsR}:
+\(\sigma\los\) versus \(\sigma\pos\), \(\sigma\pos\) versus \(L(\ha)\),
+and \(r_0\)  versus \(D_{\hii}\).
 Each of these is discussed in turn in the following sections.
@@
 
-In the Figure~\ref{fig:los-vs-pos} we show the
+In Figure~\ref{fig:los-vs-pos} we show the
 mean non-thermal line-of-sight velocity dispersion
@@
 in the Orion Nebula, finding \(\langle\sigma\los \approx 2 \sigma\pos\rangle\),
-which is shown by the MISSING line in Figure~\ref{fig:los-vs-pos}.
+which is shown by the dotted line in Figure~\ref{fig:los-vs-pos}.
 Although this line is a fair representation of the low-\(\sigma\)
@@
 
-A clear outlier from the general trend
-
-The second-order structure function measures the velocity fluctuations in the \hii{} regions under the assumption that there exists an underlying velocity spectrum following an energy cascade.
-But this statistical technique is not unique in measuring the velocity fluctuations in the nebula.
-Two parameters which can be obtained from the velocity profile also measure the velocity fluctuations in the \hii{} regions: the standard deviation of the velocity centroids, \(\sigma\pos\), and the mean non-thermal linewidth, \(\langle \sigma_{\text{los}} \rangle\).
-These quantities allow us to compare the relationship between the kinematical disorder on the plane-of-the-sky and along the line-of-sight \citep{2011MNRAS.413..705L,arthur2016turbulence}.
-
-The \( \sigma_{\text{los}} \) parameter is estimated by correcting the observed linewidth for the contribution of broadening mechanism, equation \eqref{eq:sigma-los}, leaving just the random motions which are interpreted as random motions along the line-of-sigth.
-This method is a simplification of the problem since it assume a Gaussian profile fit, which does not consider other components that could arise from different kinematics processes of the ionized gas and leaves out the broadening due to dust scattering \citep{castaneda1988,1998ApJ...503..760H}.
-
-At least three different
+% The second-order structure function measures the velocity fluctuations in the \hii{} regions under the assumption that there exists an underlying velocity spectrum following an energy cascade.
+% But this statistical technique is not unique in measuring the velocity fluctuations in the nebula.
+% Two parameters which can be obtained from the velocity profile also measure the velocity fluctuations in the \hii{} regions: the standard deviation of the velocity centroids, \(\sigma\pos\), and the mean non-thermal linewidth, \(\langle \sigma_{\text{los}} \rangle\).
+% These quantities allow us to compare the relationship between the kinematical disorder on the plane-of-the-sky and along the line-of-sight \citep{2011MNRAS.413..705L,arthur2016turbulence}.
+
+% The \( \sigma_{\text{los}} \) parameter is estimated by correcting the observed linewidth for the contribution of broadening mechanism, equation \eqref{eq:sigma-los}, leaving just the random motions which are interpreted as random motions along the line-of-sight.
+% This method is a simplification of the problem since it assume a Gaussian profile fit, which does not consider other components that could arise from different kinematics processes of the ionized gas and leaves out the broadening due to dust scattering \citep{castaneda1988,1998ApJ...503..760H}.
+
+\newcommand\LL{\mathcal{L}}
+At least three different explanations for the relation
+between \(\sigma\pos\) and \(\sigma\los\) have been proposed previously.
+The classic interpretation in terms of homogeneous turbulence
+is that \(\sigma\pos\) is reduced with respect to the ``true''
+internal velocity dispersion
+due to averaging over multiple independent turbulent cells
+along the line of sight,
+a process known as \textit{projection smearing}
+\citep{von1951methode, 1984ApJ...277..556S}.
+Assuming that \(\sigma\los\) measures the true dispersion,
+then one would expect to find \(\sigma\pos / \sigma\los = (\LL /H)^{1/2}\),
+where \(H\) is the line-of-sight depth of the emitting gas
+and \(\LL \equiv \int_0^\infty C(r)\, dr\) is the integral length scale of
+the fluctuations \citep{Pope:2000p}.
+% los/pos = sqrt(N) where N = H / L is # of independent cells
+% L is integral length scale: L = 1.44 r0 for m = 1
+% So H / r0 = 1.44 (los/pos)^2
+Using our model for the autocorrelation function from
+equation~\eqref{eq:new-correlation-form} and assuming \(m = 1\),
+one finds \(\LL = r_0 / \ln 2 \approx 1.44 r_0\),
+and thus \(H / r_0 \approx 1.44 (\sigma\los / \sigma\pos)^2\).
+From the results of Figure~\ref{fig:los-vs-pos} we therefore find
+\(H / r_0 \approx 6\) for the lower dispersion sources,
+falling to \(H / r_0 \approx 2\) for the higher dispersion sources.
+
+\newcommand\vexp{\ensuremath{v_{\text{exp}}}}
+An alternative interpretation,
+as discussed in \citep{2011MNRAS.413..705L},
+is that \(\sigma\los\) includes a contribution due to
+ordered large-scale velocity gradients
+(for instance, radial expansion)
+in addition to the turbulence,
+whereas \(\sigma\pos\) includes only the turbulent motions. 
+% Constant v_exp : sig_los = sqrt(sig_pos**2 + v_exp**2)
+Assuming a constant value \vexp{} for the ordered contribution,
+one would predict \(\sigma\los = (\sigma\pos^2 + \vexp^2)^{1/2}\),
+which is shown by the dot-dashed line in Figure~\ref{fig:los-vs-pos}
+for the case \(\vexp \approx \SI{8}{km.s^{-1}}\).
+It can seen that such a relationship reproduces the 
+observationally derived values equally as well as the linear fit.
+On the other hand, we can rule out the possibility that
+\vexp{} might increase in proportion to the turbulent velocity dispersion
+since that would predict that \(\sigma\los \propto \sigma\pos\),
+which is inconsistent with the observations as discussed above.
+
+However, as pointed out by \citet{arthur2016turbulence},
+the previous analysis is oversimplified since the presence
+of density fluctuations (or, more generally, emissivity fluctuations)
+means that the plane-of-sky dispersion of centroids is also affected
+by ordered large-scale velocity gradients along the line of sight.
+These leads to a third potential explanation of the
+\(\sigma\pos\)--\(\sigma\los\) relationship.
+In the limit that the direct effects of velocity fluctuations are
+negligible, the prediction is that \(\sigma\pos / \sigma\los \approx \)
 
@@
 
-The case of the reduction in the \(\sigma\pos\) can be interpreted by the effect of \textit{project smearing} \citep{1984ApJ...277..556S}.
+The case of the reduction in the \(\sigma\pos\) can be interpreted by the effect of \textit{project smearing} \citep{von1951methode, 1984ApJ...277..556S}.
 If we consider the case of homogeneous turbulent velocity, the projection from three to two dimensions over the line-of-sight depth \(H\), reduces the plane-of-sky amplitude for the condition \(r_{0} < H\).

### 2022-09-01 strucfunc_paper.tex
Add in the new figure of surface brightness fluctuations

@@
 An alternative interpretation,
-as discussed in \citep{2011MNRAS.413..705L},
+as discussed in \citet{2011MNRAS.413..705L},
 is that \(\sigma\los\) includes a contribution due to
@@
 of density fluctuations (or, more generally, emissivity fluctuations)
-means that the plane-of-sky dispersion of centroids is also affected
-by ordered large-scale velocity gradients along the line of sight.
-These leads to a third potential explanation of the
+means that the plane-of-sky dispersion of centroids \(\sigma\pos\)
+is \emph{not} independent of the 
+ordered large-scale velocity gradients along the line of sight.
+This leads to a third potential explanation of the
 \(\sigma\pos\)--\(\sigma\los\) relationship.
-In the limit that the direct effects of velocity fluctuations are
-negligible, the prediction is that \(\sigma\pos / \sigma\los \approx \)
-
+In the limit that the direct contribution of
+turbulent velocity fluctuations to \(\sigma\pos\) is negligible,
+the prediction is that \(\sigma\pos / \sigma\los \approx \sigma_{E/E_0}\)
+where \( \sigma_{E/E_0} = \langle \delta E^2 \rangle^{1/2} / E_0\) is the RMS fractional
+variation in emissivity \(\delta E\) (on scales \(\ge r_0\))
+with respect to the mean emissivity \(E_0\).
+
+\begin{figure}
+\centering 
+\includegraphics[width=\linewidth]{Figures/bright-hist-multi}
+\caption{
+  Panels a--g show histograms (blue) of the probability density function (PDF)
+  of the \ha{} surface brightness of \hii{} regions in our sample.
+  Smooth lines (orange) show fitted log-normal distributions.
+  Surface brightness maps were rebinned by averaging
+  into pixels of size \(0.5 r_0\) before calculating the PDF to suppress
+  fluctuations at scales smaller than the correlation length.
+  Panel h plots the ratio of velocity dispersions (see Figure~\ref{fig:los-vs-pos})
+  against the RMS fractional brightness fluctuations calculated from the PDFs.
+}
+\label{fig:brightness-pdfs}
+\end{figure}
+
+In order to empirically disentangle the relative importance
+of these three mechanisms, we require high quality measurements
+of a much larger sample of \hii{} regions
+than have so far been obtained.
+In the meantime
+is most important
+
+We therefore have an embarrassment of 
 As for the interpretation, it is possible to consider that large fluctuations of the turbulent velocities, which are spread over the entire ionized extent of the nebula, increase monotonically with the plane-of-sky dispersion.

### 2022-09-02 strucfunc_paper.tex
Javier changes 2022-09-02
Rearrange order of sections again

@@
 \author[J. García Vázquez et al.]{
-J. García Vázquez,$^{1}$\thanks{E-mail: jgarciav1600@alumno.ipn.mx}
-J. Zsargo,$^{1}$
+J. García Vázquez$^{1}$\thanks{E-mail: jgarciav1600@alumno.ipn.mx}
+%J. Zsargo,$^{1}$
 and W. J. Henney$^{2}$
@@
 which are illustrated in
-Figures~\ref{fig:los-vs-pos}--\ref{fig:rvsR}:
-\(\sigma\los\) versus \(\sigma\pos\), \(\sigma\pos\) versus \(L(\ha)\),
-and \(r_0\)  versus \(D_{\hii}\).
+Figures~\ref{fig:first-correlation}--\ref{fig:last-correlation}:
+\(r_0\)  versus \(D_{\hii}\), \(\sigma\los\) versus \(\sigma\pos\),
+and \(\sigma\pos\) versus \(L(\ha)\).
 Each of these is discussed in turn in the following sections.
@@
 including all correlations of the power law slope \(m\)
-with any other parameter.
+with any other parameter,
+but this is itself interesting and is
+also given its own section below.
 
@@
 \input{Corr}
+
+\begin{figure}
+\centering 
+\includegraphics[width=3in]{Figures/corr-rvsS}
+\caption{
+  The relationship between
+  correlation length of velocity fluctuations,
+  \(\log_{10} r_0\),
+  and  \hii{} region diameter,
+  \(\log_{10} D_{\hii}\)
+  derived from our results.
+  Symbols indicate Galactic (triangles),
+  Magellanic (squares) and extragalactic (circles) regions.
+}
+\label{fig:rvsR}
+% We have TWO labels to make it easier to re-order the figures without
+% worrying about changing the references in the text.  Just make sure
+% to move the following label to the correct figure.
+\label{fig:first-correlation}
+\end{figure}
+
 \begin{figure}
@@
   derived from our results.
-  Symbols and line types are as in Figure~\ref{fig:sigvsl}. 
+  Symbols indicate Galactic (triangles),
+  Magellanic (squares) and extragalactic (circles) regions.
 }
 \label{fig:sigvsl}
+% We have TWO labels to make it easier to re-order the figures without
+% worrying about changing the references in the text.  Just make sure
+% to move the following label to the correct figure.
+\label{fig:last-correlation}
 \end{figure}
 
-\begin{figure}
-\centering 
-\includegraphics[width=3in]{Figures/corr-rvsS}
-\caption{
-  The relationship between
-  correlation length of velocity fluctuations,
-  \(\log_{10} r_0\),
-  and  \hii{} region diameter,
-  \(\log_{10} D_{\hii}\)
-  derived from our results.
-  Symbols and line types are as in Figure~\ref{fig:sigvsl}. 
-}
-\label{fig:rvsR}
-\end{figure}
+\subsubsection{Diameter vs correlation length}\label{sec:D-vs-r0}
+
+Figure~\ref{fig:rvsR} shows the relation between the
+correlation length \(r_0\) of the velocity fluctuations
+and the diameter \(D_{\hii}\) of the \hii{} region. 
+The relationship we find is
+\(\log r_0 = (0.95 \pm 0.33) \log D_{\hii} - (1.6 \pm 0.7)\),
+which is very close to linear,
+implying that the correlation length is a fixed fraction
+\( r_0 /  \log D_{\hii} = \)
+.
+The values of \(D\) are taken from \citet{1984ApJ...287..116K} and correspond to the outer
+limits seen from visual inspection of \ha{} photographs.
+These values would represent an upper limit of the size of each region.
+Since these objects do not posses physical edges the determination of their size is not trivial.
+Due to the above, we chose these set values since they are from an unique source and are foreign to our calculations and observations, which reduced the bias in the scaling law we obtain.
+
+Ideally the correlation length \(r_0\) should represent the scale of dominant energy injection.
+It is unclear what are the precise mechanisms driving the turbulence in \hii{} regions.
+There are several energy sources that could provide or contribute to the energy required: of the order of kpc we have the differential rotations of the galaxy that produces shear at large scale. 
+At scales of the order of hundreds of pc the supernova explosions inject a large amount of kinetic energy.
+At scales of several tens of pc the expansion of \hii{} regions and stellar winds are a source of energy, and bipolar flows, shocks, jets and champagne flows inject energy at small scales about one tenth of a pc.
+Many of these mechanisms, at some extent, affect all the \hii{} regions studied in this work, so the most probable scenario is that the velocity fluctuations are consequence of the combination of various mechanism.
+
+The dependence on \(r_0\) and the diameter can be interpreted in terms that each region presents a characteristic energy injection mechanism (or combination) and despite the presence of the different mechanisms there is some unique combination that drives the input energy in each region.
+
+\subsubsection{The constancy of the power law slope}
+\label{sec:constancy-power-law}
 
@@
   Smooth lines (orange) show fitted log-normal distributions.
+  In order to suppress fluctuations on scales
+  smaller than the correlation length,
   Surface brightness maps were rebinned by averaging
-  into pixels of size \(0.5 r_0\) before calculating the PDF to suppress
-  fluctuations at scales smaller than the correlation length.
-  Panel h plots the ratio of velocity dispersions (see Figure~\ref{fig:los-vs-pos})
-  against the RMS fractional brightness fluctuations calculated from the PDFs.
+  into pixels of size \(0.5 r_0\) before calculating the PDF.
+  In panel~h is plotted for each source of the previous panels
+  the ratio of velocity dispersions
+  (see Figure~\ref{fig:los-vs-pos})
+  as a function of the
+  RMS fractional brightness fluctuations calculated from the PDFs.
 }
@@
 
-In order to empirically disentangle the relative importance
-of these three mechanisms, we require high quality measurements
+In order to disentangle the relative importance
+of these three mechanisms, it is necessary to consider
+additional factors.
+For instance, in Figure~\ref{fig:brightness-pdfs} we test
+the plausibility of the third explanation given above
+by comparing the ratio  \(\sigma\pos / \sigma\los \)
+with the RMS fractional variation in
+\ha{} surface brightness,
+\( \sigma_{S/S_0} = \langle \delta S^2 \rangle^{1/2} / S_0\).
+We calculate the latter from fitting a log-normal
+function to the probability distribution function
+of the surface brightness map after filtering out fluctuations
+on scales smaller than the velocity correlation length.
+The volumetric emissivity fluctuations are predicted to be
+proportional to the brightness fluctuations \citep{arthur2016turbulence}:
+\(\sigma_{E/E_0} = \sigma_{S/S_0} / R^{1/2}\) where \(R\)
+is the 2D-to-3D variance ratio \citep{Brunt:2010b}.
+For an emissivity power spectrum \(P(k) \sim k^{-3}\)
+and assuming a ratio of map size to correlation length
+of \(L / r_0 = 10\) (typical value from Table~\ref{tab:Res}),
+we find \(R \approx 0.2\) and hence \(\sigma_{E/E_0} \approx 2 \sigma_{S/S_0}\).
+% For P(k) ~ k^-3 we have R = 0.5 (1 - 1/x) / ln(x)
+% where x = L / r0 if we have suppressed variations on scales < r0
+% So with x = 10 (typical value) we have R = 0.2
+% For k = 4 we have R = 0.25 (1 - 1/x^2) / (1 - 1/x) = 0.275
+% For k = 2 we have R = 0.5 ln(x) / x = 0.115
+% 
+From panel 
+we require high quality measurements
 of a much larger sample of \hii{} regions
@@
 
-We therefore have an embarrassment of 
-As for the interpretation, it is possible to consider that large fluctuations of the turbulent velocities, which are spread over the entire ionized extent of the nebula, increase monotonically with the plane-of-sky dispersion.
-In this scenario, the main broadening mechanisms causing kinematical disorder along the line-of-sight are related to the velocity gradients of the clumpiness in the cloud and turbulent movements.
-On the plane-of-sky the consequences of those gradients and movements are measured in every pixel, consequently the spatial variations on the velocity field would depend on the targeted pixel, at the same time depending on the motions inside the cloud.
-Thus the \(\sigma\pos\) and \(\langle \sigma_{\text{los}} \rangle\) parameters increase in the same amount as the fluctuations grows \citep{2011MNRAS.413..705L}.
-
-The case of the reduction in the \(\sigma\pos\) can be interpreted by the effect of \textit{project smearing} \citep{von1951methode, 1984ApJ...277..556S}.
-If we consider the case of homogeneous turbulent velocity, the projection from three to two dimensions over the line-of-sight depth \(H\), reduces the plane-of-sky amplitude for the condition \(r_{0} < H\).
-With a value of \(\sigma\pos / \sigma_{\text{los}}\) = 0.5 we obtain \(r_{0} / H \sim\) 0.02 - 0.1.
-This procedure implies depths of the order 10 to 50 times the correlation length.
-In the lower limit \citet{arthur2016turbulence} mentioned the inconsistency of this interpretation for the Orion core nebula, since evidence has shown that the emitting layer thickness is of the order of \num{0.01} - \SI{0.3}{pc}.
-%For the most distant regions of our sample, the previous analysis would give depths of the order of magnitude of the observational box, but considering the analysis using the power-law index (see section~\ref{sec:power-index}) only NGC 595, which power-law index is \num{1.38}, would comply to this fully three-dimensional structure.
-On the other hand, \citet{arthur2016turbulence} proposed another interpretation in terms of large-scale order motions, and emissivity fluctuations.
-They consider an expanding shell where the mean velocity fluctuations on the plane of the sky are because the relative brightness of the redshifted and blueshifted hemispherers.
-In this case, the rms fractional variation in the emissivity on the scale diameter is found to be in the order of \(\sigma\pos / \sigma_{\text{los}}\) ratio.
+% As for the interpretation, it is possible to consider that large fluctuations of the turbulent velocities, which are spread over the entire ionized extent of the nebula, increase monotonically with the plane-of-sky dispersion.
+% In this scenario, the main broadening mechanisms causing kinematical disorder along the line-of-sight are related to the velocity gradients of the clumpiness in the cloud and turbulent movements.
+% On the plane-of-sky the consequences of those gradients and movements are measured in every pixel, consequently the spatial variations on the velocity field would depend on the targeted pixel, at the same time depending on the motions inside the cloud.
+% Thus the \(\sigma\pos\) and \(\langle \sigma_{\text{los}} \rangle\) parameters increase in the same amount as the fluctuations grows \citep{2011MNRAS.413..705L}.
+
+% The case of the reduction in the \(\sigma\pos\) can be interpreted by the effect of \textit{project smearing} \citep{von1951methode, 1984ApJ...277..556S}.
+% If we consider the case of homogeneous turbulent velocity, the projection from three to two dimensions over the line-of-sight depth \(H\), reduces the plane-of-sky amplitude for the condition \(r_{0} < H\).
+% With a value of \(\sigma\pos / \sigma_{\text{los}}\) = 0.5 we obtain \(r_{0} / H \sim\) 0.02 - 0.1.
+% This procedure implies depths of the order 10 to 50 times the correlation length.
+% In the lower limit \citet{arthur2016turbulence} mentioned the inconsistency of this interpretation for the Orion core nebula, since evidence has shown that the emitting layer thickness is of the order of \num{0.01} - \SI{0.3}{pc}.
+% %For the most distant regions of our sample, the previous analysis would give depths of the order of magnitude of the observational box, but considering the analysis using the power-law index (see section~\ref{sec:power-index}) only NGC 595, which power-law index is \num{1.38}, would comply to this fully three-dimensional structure.
+% On the other hand, \citet{arthur2016turbulence} proposed another interpretation in terms of large-scale order motions, and emissivity fluctuations.
+% They consider an expanding shell where the mean velocity fluctuations on the plane of the sky are because the relative brightness of the redshifted and blueshifted hemispherers.
+% In this case, the rms fractional variation in the emissivity on the scale diameter is found to be in the order of \(\sigma\pos / \sigma_{\text{los}}\) ratio.
 
@@
 This means that the proposed structure function model describes within certain accuracy the velocity field fluctuations and that the parameters obtained can be interpreted as a true kinematic property of the \hii{} region velocity field.
-
-\subsubsection{Diameter vs correlation length}\label{sec:D-vs-r0}
-
-The Figure \ref{fig:rvsR} shows the relation of the correlation length \(r_0\) and the diameter \(D\) of the region. 
-The relationship we found is \(\log r_0 = (0.95 \pm 0.33) \log D - (1.6 \pm 0.7)\).
-The values of \(D\) are taken from \citet{1984ApJ...287..116K} and correspond to the outer
-limits seen from visual inspection of \ha{} photographs.
-These values would represent an upper limit of the size of each region.
-Since these objects do not posses physical edges the determination of their size is not trivial.
-Due to the above, we chose these set values since they are from an unique source and are foreign to our calculations and observations, which reduced the bias in the scaling law we obtain.
-
-Ideally the correlation length \(r_0\) should represent the scale of dominant energy injection.
-It is unclear what are the precise mechanisms driving the turbulence in \hii{} regions.
-There are several energy sources that could provide or contribute to the energy required: of the order of kpc we have the differential rotations of the galaxy that produces shear at large scale. 
-At scales of the order of hundreds of pc the supernova explosions inject a large amount of kinetic energy.
-At scales of several tens of pc the expansion of \hii{} regions and stellar winds are a source of energy, and bipolar flows, shocks, jets and champagne flows inject energy at small scales about one tenth of a pc.
-Many of these mechanisms, at some extent, affect all the \hii{} regions studied in this work, so the most probable scenario is that the velocity fluctuations are consequence of the combination of various mechanism.
-
-The dependence on \(r_0\) and the diameter can be interpreted in terms that each region presents a characteristic energy injection mechanism (or combination) and despite the presence of the different mechanisms there is some unique combination that drives the input energy in each region.
 

### 2022-09-20 strucfunc_paper.tex
Javier changes 2022-09-20

@@
   Fluctuations of centroid velocities on the plane of the sky derived from spectroscopic observations are a powerful tool for studying the turbulent dynamics of emission line regions.
-  With the aim to characterize these velocities fluctuations we conduct a statistical analysis on a diverse sample of 9 \hii{} regions that spans more than two orders of magnitude in size and luminosity located in the Milky Way and other Local Group galaxies.
-  We determine the second-order structure function of the centroid velocity two-dimensional map of the \halpha\ emission line.
-  We also proposed a heuristic model for the structure function which takes into account observational constraints like the seeing (\(s_0\)), instrumental noise (\(B_{\text{noise}}\)) and size of the field of view (\(L_{\text{box}}\)), and the turbulent velocity field parameters like the velocity dispersion of the centroid velocity (\(\sigma\pos\)), the autocorrelation length (\(r_0\)) and a power-law index (\(m\)).
-  The observational structure function is fitted using our heuristic model in a non-linear regression analysis which allow us to derive the parameters previously mentioned  with their respective confidence intervals.
-  Our results are: \(\num{0.2} < s_0 \text{(FWHM)} < \SI{3.0}{arcsec}\), \(\num{0.003} < B_{\text{noise}} < \SI{6.0}{km^{-2}.s^{-2}}\),  \(\num{3} < \sigma\pos < \SI{19}{km.s^{-1}}\), \(\num{0.07} < r_0 < \SI{12}{pc}\) and \(\num{0.7}< m < \num{1.5}\).
-  The derived parameters are used to determine scaling relations between the physical properties of the regions like \halpha\ luminosity (\(L(H_{\alpha})\)), diamater (\(D\)) and the mean non-thermal linewidth (\(\langle \sigma_{los} \rangle\)).
-  We find that these relations are \(\sigma\pos \propto L(H_{\alpha})^{0.28 \pm 0.10}\) and \(r_0 \propto D^{0.95 \pm 0.32}\), and that the \(\sigma\pos\) and \(\langle \sigma_{los} \rangle\), values increase following a linear monotonically relation.
+  With the aim to characterize these velocities fluctuations we conduct a statistical analysis on a diverse sample of 9 \hii{} regions that spans more than two orders of magnitude in size and luminosity, and are located in the Milky Way and other Local Group galaxies.
+  For the statistical analysis we obtain the second-order structure function of the observed \halpha\ centroid velocity field.
+  We proposed a heuristic model for the structure function which takes into account observational constraints like the seeing (\(s_0\)), instrumental noise (\(B_{\text{noise}}\)) and size of the field of view (\(L_{\text{box}}\)).
+  The turbulent velocity field parameters like the velocity dispersion of the centroid velocity (\(\sigma\pos\)), the autocorrelation length (\(r_0\)) and a power-law index (\(m\)) are also considered in our heuristic model.
+  The observational structure function is fitted using our heuristic model in a non-linear regression analysis which allow us to derive the parameters representing each velocity field.
+  The results for the 9 \hii{} regions are: \(\num{0.2} < s_0 \text{(FWHM)} < \SI{3.0}{arcsec}\), \(\num{0.003} < B_{\text{noise}} < \SI{6.0}{km^{-2}.s^{-2}}\),  \(\num{3} < \sigma\pos < \SI{19}{km.s^{-1}}\), \(\num{0.07} < r_0 < \SI{12}{pc}\) and \(\num{0.7}< m < \num{1.5}\).
+  Later, the derived parameters are used to determine scaling relations between the physical properties of the regions like \halpha\ luminosity (\(L(H_{\alpha})\)), diamater (\(D\)) and the mean non-thermal linewidth (\(\langle \sigma_{los} \rangle\)).
+  We find that these relations are \(\sigma\pos \propto L(H_{\alpha})^{0.28 \pm 0.10}\) and \(r_0 \propto D^{0.95 \pm 0.32}\). 
+  Finally, the \(\sigma\pos\) and \(\langle \sigma_{los} \rangle\) relation increase following a linear relation.
   Since the derived  scale-relations are within the uncertainty of previous investigations we conclude that the parameters obtained from our proposed model represents true kinematic properties of each region.
-  The methodology we present guarantees consistency for comparison between the galactic and giant HII regions. 
-%  The second-order structure function has proved to be a useful tool to determine the existence of the correlations between random velocities and distance across the \hii{} regions.
+  The methodology we present guarantees consistency for comparison between the galactic and giant extragalactic HII regions.
 
@@
 and must be characterised by statistical techniques.
+
 In relatively low luminosity regions, such as the nearby Orion Nebula,
@@
 are described in section~\ref{sec:HIIsample}.
-
-We apply a uniform methodology to the analysis of the structure function
+For studying the turbulence we apply a uniform methodology to the analysis of the structure function
 by fitting a simple functional form that consists of a power law of slope \(m\)
@@
 The results of these fits are presented in section~\ref{sec:results}.
-
 In section~\ref{sec:discussion} we discuss the relation
@@
 We use the velocity field presented in \citet{1987A&A...176..347H} to analyze the Extended Orion Nebula \citetext{EON henceforth;  \citealp{2008Sci...319..309G}}.
-the brightness following the southwest direction from the Huygens region.
+The EON is an extended region in southwest direction from the Huygens region which presents a diminution in the brightness.
 The observational data was obtained using a Fabry-Pérot interferometer with a étalon separation of 0.5 mm on the 106 cm-Cassegrain telescope at Observatorium Hoher List. 
@@
 Lagoon    & 1.25 \pm 0.12   & 25 \pm 2.5      &    37.47    &   11.2 \pm 1.6    \\
-Carina    & 2.35 \pm 0.05   & 200 \pm 20      &    38.54    &   18.6 \pm 3.3\FNa      \\
+Carina    & 2.35 \pm 0.05   & 200 \pm 20      &    39.01    &   18.6 \pm 3.3\FNa      \\
 30 Dor    & 50.0 \pm 0.2    & 370 \pm 37    &    39.46    &     21.7 \pm 2.2    \\

### 2022-09-20 strucfunc_paper.tex
Finish unfinished sentence

@@
 implying that the correlation length is a fixed fraction
-\( r_0 /  \log D_{\hii} = \)
-.
+of the diameter:
+\( r_0 /  \log D_{\hii} = 0.02 \pm 0.01\).
+
 The values of \(D\) are taken from \citet{1984ApJ...287..116K} and correspond to the outer

### 2022-09-20 strucfunc_paper.tex
Add different length scales to correlation function section

@@
 
+\newcommand\LL{\mathcal{L}}
+Slightly different definitions of the correlation length
+are found in the literature.
+For instance the definition of \citet{Jaupart:2022i}
+in two dimensions is
+\begin{equation}
+  \label{eq:2}
+  \ell_c^2 = \frac{1}{4} \int C(r) \, d^2 r
+  = \frac{\pi}{2} \int_0^\infty r C(r) \, d r
+\end{equation}
+while the ``integral length scale'' \citep{Pope:2000p} is defined
+as
+\begin{equation}
+  \label{eq:3}
+  \LL \equiv \int_0^\infty C(r)\, dr .
+\end{equation}
+For our model structure function, these evaluate to
+\begin{equation}
+  \label{eq:4}
+  \LL = \frac{\Gamma(1/m)}{m\, (\ln 2)^{1/m}} \, r_0
+\end{equation}
+and
+\begin{equation}
+  \label{eq:4}
+   \ell_c^2 = \frac{\pi\,  \Gamma(2/m)}{2m\, (\ln 2)^{1/m}} \, r_0^2
+\end{equation}
+where \(\Gamma\) is the usual Gamma function.
+For example, if \(m = 1\) these become \(\LL \approx 1.443 r_0\)
+and \(\ell_c \approx 1.808 r_0\). 
 % The term \(r_{0}\)\ is the correlation length where the value of separation \(r\) reach the value of \(\sigma^2\) in the structure function and $m$ is the power-law index that fits the inertial scale.
@@
 
+\textit{Plan for this section 2022-09-20:
+  \begin{enumerate}[1]
+  \item Relation with box size -- show that correlation length is comfortably smaller and is not well correlated with L 
+  \item Statistical homogeneity, fact that r0 much less than D is good, but we really need to consider the scale over which conditions vary,  which presumably is smaller than D,  but hopefully still larger than r0.
+Discuss whether it might therefore be fruitful to map out variations in r0 on medium scales, as was done in some paper.
+  \item Fact that Jaupart also find that r0/D is about 1\%, and that they say that this has nothing to do with the injection scale. 
+  \end{enumerate}
+}
+
 The values of \(D\) are taken from \citet{1984ApJ...287..116K} and correspond to the outer
@@
 
-\newcommand\LL{\mathcal{L}}
 At least three different explanations for the relation

### 2022-11-11 strucfunc_paper.tex
Javier  changes 2022-11-11

@@
 J. García Vázquez$^{1}$\thanks{E-mail: jgarciav1600@alumno.ipn.mx}
-%J. Zsargo,$^{1}$
 and W. J. Henney$^{2}$
-%and H. O. Castañeda$^{1}$
 \\
@@
 % Enter the current year, for the copyright statements etc.
-\pubyear{2021}
+\pubyear{2023}
 
@@
 For more details on the observational setup see table~1 of \citet{sabalisck1995supersonic}.
-The reduction and analysis was done with the packages TAUCAL y TAUFITS \citep{1992ASPC...25..445L} and the emission spectrum was adjusted with a Gaussian fit.
+The reduction and analysis was done with the packages TAUCAL y TAUFITS \citep{1992ASPC...25..445L} and the emission spectrum was adjusted with a single Gaussian fit.
 The NGC~604 observations were previously reported and analyzed in
@@
 Diameters taken from Table 2 of \citet{1984ApJ...287..116K}.
-Mean non-thermal linewidth values, \(\langle \sigma\los \rangle\), shown here are corrected considering equation \eqref{eq:sigma-los} which takes into account \(\sigma_{\mathrm{fs}}\).
+Mean non-thermal linewidth values (\(\langle \sigma\los \rangle\)) shown here are corrected considering equation \eqref{eq:sigma-los} which takes into account \(\sigma_{\mathrm{fs}}\).
 Non-corrected \(\langle \sigma\los \rangle\) values and other properties references are mentioned in the text.
@@
   \label{eq:4}
-   \ell_c^2 = \frac{\pi\,  \Gamma(2/m)}{2m\, (\ln 2)^{1/m}} \, r_0^2
+   \ell_c^2 = \frac{\pi\,  \Gamma(2/m)}{2m\, (\ln 2)^{2/m}} \, r_0^2
 \end{equation}
@@
 a random selection of \num{100} posterior samples from the MCMC chain,
-both for \(\tilde{B}\model(r)\) orange and \(B\model(r)\) (green).
+both for \(\tilde{B}\model(r)\) (orange) and \(B\model(r)\) (green).
 This gives an estimate in the uncertainty about the best-fit model.
@@
 
-In the section \ref{sec:comp-with-prev} we make a comparison of our methods and results with previous research that analyzes structural functions of some \hii{} regions of our sample.
+In the section \ref{sec:comp-with-prev} we make a comparison of our methods and results with previous research that analyzes structure functions of some \hii{} regions of our sample.
 In the section \ref{sec:scaling-relations} we present the most important scaling relations between the derived turbulent parameters and the physical properties of the \hii{} regions.
@@
 
-The values of \(D\) are taken from \citet{1984ApJ...287..116K} and correspond to the outer
+The values of \(D_{\hii}\) are taken from \citet{1984ApJ...287..116K} and correspond to the outer
 limits seen from visual inspection of \ha{} photographs.
@@
 
-The dependence on \(r_0\) and the diameter can be interpreted in terms that each region presents a characteristic energy injection mechanism (or combination) and despite the presence of the different mechanisms there is some unique combination that drives the input energy in each region.
+%The dependence on \(r_0\) and the diameter may be interpreted in terms that each region presents a characteristic energy injection mechanism (or combination) and despite the presence of the different mechanisms there is some unique combination that drives the input energy in each region.
 

### 2022-11-11 strucfunc_paper.tex
Fixed a few spelling mistakes
And used \hii{} in more places in the text

@@
 % Keep the title short and informative.
-\title[Turbulence in H II regions]{Turbulence in compact to giant HII regions}
+\title[Turbulence in H II regions]{Turbulence in compact to giant H~II regions}
 
@@
 $^{1}$Escuela Superior de Física y Matemáticas, Instituto Politécnico Nacional, Ciudad de México, México.\\
-$^{2}$Instituto de Radioastronomía y Astrofísica, Universidad Nacional Autonoma de México, Apartado postal 3-72, 58090 Morelia, Michoacán, Mexico\\
+$^{2}$Instituto de Radioastronomía y Astrofísica, Universidad Nacional Autónoma de México, Apartado postal 3-72, 58090 Morelia, Michoacán, Mexico\\
 }
@@
   The results for the 9 \hii{} regions are: \(\num{0.2} < s_0 \text{(FWHM)} < \SI{3.0}{arcsec}\), \(\num{0.003} < B_{\text{noise}} < \SI{6.0}{km^{-2}.s^{-2}}\),  \(\num{3} < \sigma\pos < \SI{19}{km.s^{-1}}\), \(\num{0.07} < r_0 < \SI{12}{pc}\) and \(\num{0.7}< m < \num{1.5}\).
-  Later, the derived parameters are used to determine scaling relations between the physical properties of the regions like \halpha\ luminosity (\(L(H_{\alpha})\)), diamater (\(D\)) and the mean non-thermal linewidth (\(\langle \sigma_{los} \rangle\)).
+  Later, the derived parameters are used to determine scaling relations between the physical properties of the regions like \halpha\ luminosity (\(L(H_{\alpha})\)), diameter (\(D\)) and the mean non-thermal linewidth (\(\langle \sigma_{los} \rangle\)).
   We find that these relations are \(\sigma\pos \propto L(H_{\alpha})^{0.28 \pm 0.10}\) and \(r_0 \propto D^{0.95 \pm 0.32}\). 
@@
   Since the derived  scale-relations are within the uncertainty of previous investigations we conclude that the parameters obtained from our proposed model represents true kinematic properties of each region.
-  The methodology we present guarantees consistency for comparison between the galactic and giant extragalactic HII regions.
+  The methodology we present guarantees consistency for comparison between the galactic and giant extragalactic \hii{} regions.
 
@@
 \citet{Moiseev:2015a} found that this relation also holds for dwarf galaxies with a value of \(\alpha \sim 5\).
-\citet{2018MNRAS.474.1250F} presented the relationship between integrated H$_{\beta}$ line luminosity for new data of 36 giant HII regions obtaining \(\text{L}_{\text{H}_{\beta}} \propto \sigma^{5.02 \pm 0.21}\).
-Recently, \citet{2020ApJ...888..113W} studied the properties of high-\(z\) and local \hii{} galaxies among some GEHRs findig a value of \(\alpha \sim 5\).
+\citet{2018MNRAS.474.1250F} presented the relationship between integrated H$_{\beta}$ line luminosity for new data of 36 giant \hii{} regions obtaining \(\text{L}_{\text{H}_{\beta}} \propto \sigma^{5.02 \pm 0.21}\).
+Recently, \citet{2020ApJ...888..113W} studied the properties of high-\(z\) and local \hii{} galaxies among some GEHRs finding a value of \(\alpha \sim 5\).
 
@@
 The radiation pressure, stellar winds and region expansion, among other physical processes would create pressure-driven shock waves propagating faster than the speed of sound in the medium.
-This would make the flow compressible and supersonic in an inhomogenous gas cloud.
+This would make the flow compressible and supersonic in an inhomogeneous gas cloud.
 Also, as \hii{} regions are three-dimensional objects our structure function results comes from a projection of this three-dimensional structure to a two-dimensional velocity field.
@@
 
-As a conclusion, if the extension of the HII region is compared with its depth (three-dimensional case) the value of the index is \num{1.6}. 
+As a conclusion, if the extension of the \hii{} region is compared with its depth (three-dimensional case) the value of the index is \num{1.6}. 
 While the case where the extension is much greater than its depth (two-dimensional case) the region will have a value of \num{0.6}.
@@
 
-%As a conclusion, if the extension of the HII region is compared with its depth (three-dimensional case) the value of the index is \num{1.67}. 
+%As a conclusion, if the extension of the \hii{} region is compared with its depth (three-dimensional case) the value of the index is \num{1.67}. 
 %While the case where the extension is much greater than its depth (two-dimensional case) the region will have a value of \num{0.6}.
@@
 Our analysis can be easily be expanded to other \hii{} regions with the possibility of comparing the results between them since our method guarantees homogeneity, providing the possibility to develop a future catalog of \hii{} regions turbulent parameters in a concise way.
-By calculating the structure function of HII regions with different morphologies, ages, stellar content, and dynamics it would be possible to detect the presence and the importance of different sources of mechanical energy, since the structure function would be different from one object to the other as we show in the present investigation.
+By calculating the structure function of \hii{} regions with different morphologies, ages, stellar content, and dynamics it would be possible to detect the presence and the importance of different sources of mechanical energy, since the structure function would be different from one object to the other as we show in the present investigation.
 
@@
 The modification add a tapering to the power law so that the generated fields are uncorrelated at large scales.
-The artificial fields follows a given power law with with a correlation length giving a variance value indicated as true \(\sigma^2\).
+The artificial fields follows a given power law with a correlation length giving a variance value indicated as true \(\sigma^2\).
 Using this true \(\sigma^2\) we obtain the true \(r_0\) and these values are used as a reference in the experiments to quantify the variations.
@@
 
-The Orion Nebula (M42) is the prototype of a galactic HII region located at a distance of 440 pc \citetext{\SI{1}{\arcsecond} = \SI{0.002}{pc} ; \citealp{2008AJ....136.1566O}}.
+The Orion Nebula (M42) is the prototype of a galactic \hii{} region located at a distance of 440 pc \citetext{\SI{1}{\arcsecond} = \SI{0.002}{pc} ; \citealp{2008AJ....136.1566O}}.
 The O7 V star \(\theta^{1}\) Ori C is the most luminous and hottest star \citep{2006A&A...448..351S} with an ionizing flux \(Q_0\) of  \SI{e49.12}{photons.s^{-1}}. 
 With other 3 B-type stars they form the Trapezium cluster.
-The bright region that surrounds these massive ionizing stars is called the the Huygens region.
+The bright region that surrounds these massive ionizing stars is called the Huygens region.
 %In the southwest direction of the Huygens region there is a drop in the brightness as one approach a much larger region called Extended Orion Nebula \citetext{EON henceforth;  \citealp{2008Sci...319..309G}}
@@
 The velocity field shows several expanding shells, related to the stellar population, and the massive protostar M8East-IR \citep{1984ApJ...278..170S} indicating that recent star formation. 
-A blueshifted, neutral layer is also in very good agreement with predictions of champagne-flow models of blister HII regions \citep{Damiani:2017b}. 
+A blueshifted, neutral layer is also in very good agreement with predictions of champagne-flow models of blister \hii{} regions \citep{Damiani:2017b}. 
 The properties of the nebula are reviewed by \citet{2008hsf2.book..533T}.
@@
 
-The first attempt at characterizing turbulence in a giant extragalactic HII region, GEHR, was done by \citet{1961MNRAS.122....1F} with the 30~Doradus complex, finding no indication of turbulent motions between scale of \num{10} and \SI{100}{pc}.
+The first attempt at characterizing turbulence in a giant extragalactic \hii{} region, GEHR, was done by \citet{1961MNRAS.122....1F} with the 30~Doradus complex, finding no indication of turbulent motions between scale of \num{10} and \SI{100}{pc}.
 \citet{Melnick:2021x} also investigated the structure function in 30 Doradus finding on their results that the structure function is entirely flat on scales from \num{3} to \SI{200}{pc}.
@@
 NGC 346 is the most active star-formation region in the SMC (Small Magellanic Cloud) located at a distance of 62 kpc \citetext{\SI{1}{\arcsecond} = \SI{0.30}{pc} ; \citealp{2001ApJ...562..303D}}. 
-It has more than 30 O stars that ionize N66, the largest HII region \citep{2011ApJ...740...10D}.
+It has more than 30 O stars that ionize N66, the largest \hii{} region \citep{2011ApJ...740...10D}.
 N66 has an \ha{} luminosity of \SI{e38.77}{erg.s^{-1}}, almost 60 times higher compared to the Orion Nebula \citep{2010A&A...517A..39H,1984ApJ...287..116K}.
-\citet{2008ApJ...688.1050G} propose an expanding HII region or bubble blown by the winds of the massive progenitor as a mechanism that shapes the recent star formation in this region, in addition to the photoionizing process of the OB stars.
-This mechanism is similar to shell-like HII regions, with a central cluster in a cavity, and with ongoing star formation triggered around their periphery.
+\citet{2008ApJ...688.1050G} propose an expanding \hii{} region or bubble blown by the winds of the massive progenitor as a mechanism that shapes the recent star formation in this region, in addition to the photoionization from the OB stars.
+This mechanism is similar to shell-like \hii{} regions, with a central cluster in a cavity, and with ongoing star formation triggered around their periphery.
 Using a Gaussian single-component \citet{2003ApJ...586.1179D} find a corrected FWHM bulk turbulence of \SI{23.8}{km.s^{-1}}.
@@
 %
-The irregular dwarf galaxy, NGC 6822, is located at a distance of 500 kpc \citetext{\SI{1}{\arcsecond} = \SI{2.42}{pc} ; \citealp{2012A&A...540A.135S}} and the brightest HII regions are Hubble X and Hubble V (HX and HV hereafter).
+The irregular dwarf galaxy, NGC 6822, is located at a distance of 500 kpc \citetext{\SI{1}{\arcsecond} = \SI{2.42}{pc} ; \citealp{2012A&A...540A.135S}} and the brightest \hii{} regions are Hubble X and Hubble V (HX and HV hereafter).
 %(1'' = 2.4 pc)
@@
 The mean non-thermal linewidth in \ha{} is \SI{10.5 \pm 0.02}{km.s^{-1}} for HX and \SI{10.3 \pm 0.03}{km.s^{-1}} \citep{1986A&A...160..374H}.
-Two recognized OB associations are identified within these HII regions \citep{1991ApJ...379..621H,1992AJ....104.1374W}.
+Two recognized OB associations are identified within these \hii{} regions \citep{1991ApJ...379..621H,1992AJ....104.1374W}.
 HV is located near 'Hodge OB 8' and HX is located near 'Hodge OB13'  \citep{1999PASP..111.1382O}.
@@
 M33 is the third largest galaxy in the Local Group located at the distance of 840 kpc \citetext{\SI{1}{\arcsecond} = \SI{4.07}{pc} ; \citealp{2015KamKinematics}} and is of morphological type SA(s)cd.
-The two brightest HII regions in the galaxy are NGC 604 and NGC 595.
+The two brightest \hii{} regions in the galaxy are NGC 604 and NGC 595.
 
@@
 
-NGC 595 is the second brightest giant HII region in the M33 galaxy and has an \ha{} shell morphology that is related to the stellar winds of the several massive stars located in its interior.
+NGC 595 is the second brightest giant \hii{} region in the M33 galaxy and has an \ha{} shell morphology that is related to the stellar winds of the several massive stars located in its interior.
 It has a luminosity in \ha{} of \SI{e38.95}{erg.s^{-1}}\citep{2002MNRAS.329..481B}.

### 2022-11-18 strucfunc_paper.tex
Progress on the r0 vs D section

@@
    which are not included in the model structure function.
+   Note how hard it is to detect by eye the difference between these
+   fields and the one shown in panel~a, despite the important changes
+   in the large-scale end of the structure function.
  }
@@
 To accomplish this we implement a hierarchical Bayesian model for linear regression using the \texttt{linmix} Python library, which is based on the procedure of \cite{2007ApJ...665.1489K}.
-Thus we fit relations of the form
+We fit relations of the form
 \(Y = a X + b\)
@@
 which is very close to linear,
-implying that the correlation length is a fixed fraction
+implying that the correlation length is a constant fraction
 of the diameter:
-\( r_0 /  \log D_{\hii} = 0.02 \pm 0.01\).
-
-\textit{Plan for this section 2022-09-20:
-  \begin{enumerate}[1]
-  \item Relation with box size -- show that correlation length is comfortably smaller and is not well correlated with L 
-  \item Statistical homogeneity, fact that r0 much less than D is good, but we really need to consider the scale over which conditions vary,  which presumably is smaller than D,  but hopefully still larger than r0.
+\( r_0 /  D_{\hii} = 0.02 \pm 0.01\).
+
+However, \(r_0\) is also well correlated with
+the observed map size, \(L\),
+so it is important to check that the correlation lengths that we
+measure are true properties of the regions,
+and are not just artifacts of the finite map sizes.
+In Appendix~\ref{sec:finite-box-effects} we show that \(L\)
+has a significant effect on the naive apparent \(r_0\) when \(r_0 > 0.1 L\),
+but that an accurate \(r_0\) can still be recovered from model fitting
+so long as \(r_0 < 0.33 L\).
+From our results (Table~\ref{tab:Res}) we find that \(r_0 \approx (0.08 \pm 0.01) L\),
+which is comfortably small enough that the measured correlation lengths should
+be reliable.
+A clear indication that the derived \(r_0\) is not real would
+be a structure function that never flattens off, but rather keeps
+rising at all scales.
+We do not see such a behavior in any of our regions.
+The most similar is the Lagoon Nebula
+(Figure~\ref{fig:strucfunc-fit-Galactic}c),
+where the structure function does flatten at intermediate scales,
+but then rises again for separations of order \(L\).
+It may be that there is a second, outer correlation scale in this region,
+which we fail to measure because the observed map is to small.
+
+The small value of \( r_0 /   D_{\hii}\) that we obtain means that it
+would be feasible to study the spatial variation of the turbulence parameters
+within a given region. This is because parts of the nebula that are separated
+by a distance \(\gg r_0\) are essentially independent.
+In principle,  the variation of \(\sigma\pos\) could be
+measured in  a ``macro-pixels'' of size \(2 r_0\),
+but a minimum size of  \( 3 r_0\) is necessary to reliably determine \(r_0\)
+itself (Appendix~\ref{sec:finite-box-effects}),
+and it is quite possible that \(r_0\) might vary
+across the face of the nebulae.
+The best that could be done with the current \(L \times L\) velocity maps
+would therefore be about \(3\times3\) pixels, but this could be increased to
+about \(15\times15\) pixels if the entire \(D_{\hii} \times D_{\hii}\) region were mapped.
+
+% \textit{Plan for this section 2022-09-20:
+%   \begin{enumerate}[1]
+%   \item Relation with box size -- show that correlation length is comfortably smaller and is not well correlated with L 
+%   \item Statistical homogeneity, fact that r0 much less than D is good, but we really need to consider the scale over which conditions vary,  which presumably is smaller than D,  but hopefully still larger than r0.
 Discuss whether it might therefore be fruitful to map out variations in r0 on medium scales, as was done in some paper.
-  \item Fact that Jaupart also find that r0/D is about 1\%, and that they say that this has nothing to do with the injection scale. 
-  \end{enumerate}
-}
-
-The values of \(D_{\hii}\) are taken from \citet{1984ApJ...287..116K} and correspond to the outer
-limits seen from visual inspection of \ha{} photographs.
-These values would represent an upper limit of the size of each region.
-Since these objects do not posses physical edges the determination of their size is not trivial.
-Due to the above, we chose these set values since they are from an unique source and are foreign to our calculations and observations, which reduced the bias in the scaling law we obtain.
-
+%   \item Fact that Jaupart also find that r0/D is about 1\%, and that they say that this has nothing to do with the injection scale. 
+%   \end{enumerate}
+% }
+
+% The values of \(D_{\hii}\) are taken from \citet{1984ApJ...287..116K} and correspond to the outer
+% limits seen from visual inspection of \ha{} photographs.
+% These values would represent an upper limit of the size of each region.
+% Since these objects do not posses physical edges the determination of their size is not trivial.
+% Due to the above, we chose these set values since they are from an unique source and are foreign to our calculations and observations, which reduced the bias in the scaling law we obtain.
+
+Recent work on self-gravitating turbulence in molecular clouds
+such as Polaris and Orion~B
+\citep{Jaupart:2022i} has also found correlation lengths
+that are small compared with the size of the clouds,
+with results that are quantitatively similar to our own:
+\(r_0 / D \sim 0.01\), although it should be noted that these studies
+consider the column density fields, rather than velocities.
+\citep{Jaupart:2021a} XXX FINSH THIS
+
+However
 Ideally the correlation length \(r_0\) should represent the scale of dominant energy injection.

### 2022-11-19 strucfunc_paper.tex
Finish section 5.2.1

@@
 
-\newcommand\LL{\mathcal{L}}
+\newcommand\LL{\ensuremath{\mathcal{L}}}
 Slightly different definitions of the correlation length
@@
 
-Recent work on self-gravitating turbulence in molecular clouds
-such as Polaris and Orion~B
-\citep{Jaupart:2022i} has also found correlation lengths
-that are small compared with the size of the clouds,
-with results that are quantitatively similar to our own:
-\(r_0 / D \sim 0.01\), although it should be noted that these studies
-consider the column density fields, rather than velocities.
-\citep{Jaupart:2021a} XXX FINSH THIS
-
-However
-Ideally the correlation length \(r_0\) should represent the scale of dominant energy injection.
-It is unclear what are the precise mechanisms driving the turbulence in \hii{} regions.
-There are several energy sources that could provide or contribute to the energy required: of the order of kpc we have the differential rotations of the galaxy that produces shear at large scale. 
-At scales of the order of hundreds of pc the supernova explosions inject a large amount of kinetic energy.
-At scales of several tens of pc the expansion of \hii{} regions and stellar winds are a source of energy, and bipolar flows, shocks, jets and champagne flows inject energy at small scales about one tenth of a pc.
-Many of these mechanisms, at some extent, affect all the \hii{} regions studied in this work, so the most probable scenario is that the velocity fluctuations are consequence of the combination of various mechanism.
-
-%The dependence on \(r_0\) and the diameter may be interpreted in terms that each region presents a characteristic energy injection mechanism (or combination) and despite the presence of the different mechanisms there is some unique combination that drives the input energy in each region.
+The energy injection or driving scale of turbulence,
+\(\ell_E\), is commonly identified
+with the ``outer scale'' of the fluctuations 
+\citep{Haverkorn:2004r, 2010ApJ...710..853C}. 
+The outer scale has been given diverse definitions \citep{Klipp:2014a}
+but most commonly is either the integral scale \LL{},
+or the scale at which the structure function becomes flat.
+These are both of the same order as the correlation length \(r_0\) as we define it,
+see section~\ref{sec:methods-apply},
+but are typically larger by a factor of 1.5 to 2
+(for example, equation~\eqref{eq:4} for the integral scale).
+However, high resolution numerical simulations
+of driven isothermal turbulence \citep{Federrath:2021r}
+show a somewhat larger gap of a factor of 4 between the correlation length
+and the driving scale.  
+In either case, our results imply that the turbulence
+in \hii{} regions is driven on relatively small scales,
+between 2\% and 5\%  of the diameter of the \hii{} region.
+
+% However, \citep{Jaupart:2021a} point out that for supersonic turbulence
+% the correlation length and the integral scale can be much smaller than
+% the energy injection scale.
+% By analysing high resolution simulations of driven self-gravitating turbulence with Mach number \(M\)
+% \cite{},
+% they find that \(r_0 \sim \ell_E / M^2\).
+
+% Recent work on self-gravitating turbulence in molecular clouds
+% such as Polaris and Orion~B
+% \citep{Jaupart:2022i} has also found correlation lengths
+% that are small compared with the size of the clouds,
+% with results that are quantitatively similar to our own:
+% \(r_0 / D \sim 0.01\), although it should be noted that these studies
+% consider the column density fields, rather than velocities.
+
+% However
+% Ideally the correlation length \(r_0\) should represent the scale of dominant energy injection.
+% It is unclear what are the precise mechanisms driving the turbulence in \hii{} regions.
+% There are several energy sources that could provide or contribute to the energy required: of the order of kpc we have the differential rotations of the galaxy that produces shear at large scale. 
+% At scales of the order of hundreds of pc the supernova explosions inject a large amount of kinetic energy.
+% At scales of several tens of pc the expansion of \hii{} regions and stellar winds are a source of energy, and bipolar flows, shocks, jets and champagne flows inject energy at small scales about one tenth of a pc.
+% Many of these mechanisms, at some extent, affect all the \hii{} regions studied in this work, so the most probable scenario is that the velocity fluctuations are consequence of the combination of various mechanism.
 
@@
 \begin{equation}\label{eq:ajustebox}
-\beta(r_0) = 1 - exp \left[ \frac{L}{3.6r_0} \right] 
+\beta(r_0) = 1 - \exp \left[ \frac{L}{3.6r_0} \right] 
 \end{equation}

### 2022-11-19 strucfunc_paper.tex
Write first para on the power law slopes

@@
 or the scale at which the structure function becomes flat.
-These are both of the same order as the correlation length \(r_0\) as we define it,
-see section~\ref{sec:methods-apply},
+These are both of the same order as the correlation length \(r_0\)
+as we define it in section~\ref{sec:methods-apply},
 but are typically larger by a factor of 1.5 to 2
@@
 \label{sec:constancy-power-law}
+The slope \(m\) of the power-law portion of the structure function
+shows no significant correlation with any other parameter
+(see Table~\ref{tab:RestStats}),
+with a weighted mean value of \(m = 1.01\).
+The dispersion in fitted \(m\) values is 1.6 times higher than expected
+on the basis of the confidence limits for the individual regions,
+implying that there may be a real intrinsic dispersion of 0.17 in the slopes.
+However, a \(\chi^2\) test shows that this is only marginally significant
+(\(p = 0.11\), so we cannot reject the idea that all the slopes are identical.
 

### 2022-11-29 strucfunc_paper.tex
Javier changes 2022-11-28

@@
 
-In the section \ref{sec:comp-with-prev} we make a comparison of our methods and results with previous research that analyzes structure functions of some \hii{} regions of our sample.
-In the section \ref{sec:scaling-relations} we present the most important scaling relations between the derived turbulent parameters and the physical properties of the \hii{} regions.
-Finally, in the section \ref{power-law-index} we discuss the role of the derived power-law index in the context of turbulence in the ionized gas.
+%In the section \ref{sec:comp-with-prev} we make a comparison of our methods and results with previous research that analyzes structure functions of some \hii{} regions of our sample.
+%In the section \ref{sec:scaling-relations} we present the most important scaling relations between the derived turbulent parameters and the physical properties of the \hii{} regions.
+%Finally, in the section \ref{power-law-index} we discuss the role of the derived power-law index in the context of turbulence in the ionized gas.
 
@@
 determining the slope.
-
-% The diversity of methodologies used in prior studies 
-% In Section \ref{sec:methods-apply} we mentioned the model we propose for the structure function.
-% Since this is the first time a model of this type is applied to a sample of HII regions, our results are bounded to be different from previous investigations, including the investigations that have the same observations as \citet{arthur2016turbulence} and \citet{Medina-Tanco:1997a,Melnick:2021x}.
 
@@
 However, a \(\chi^2\) test shows that this is only marginally significant
-(\(p = 0.11\), so we cannot reject the idea that all the slopes are identical.
+(\(p = 0.11\)), so we cannot reject the idea that all the slopes are identical.
 
@@
 30~Doradus.
-
-% The second-order structure function measures the velocity fluctuations in the \hii{} regions under the assumption that there exists an underlying velocity spectrum following an energy cascade.
-% But this statistical technique is not unique in measuring the velocity fluctuations in the nebula.
-% Two parameters which can be obtained from the velocity profile also measure the velocity fluctuations in the \hii{} regions: the standard deviation of the velocity centroids, \(\sigma\pos\), and the mean non-thermal linewidth, \(\langle \sigma_{\text{los}} \rangle\).
-% These quantities allow us to compare the relationship between the kinematical disorder on the plane-of-the-sky and along the line-of-sight \citep{2011MNRAS.413..705L,arthur2016turbulence}.
-
-% The \( \sigma_{\text{los}} \) parameter is estimated by correcting the observed linewidth for the contribution of broadening mechanism, equation \eqref{eq:sigma-los}, leaving just the random motions which are interpreted as random motions along the line-of-sight.
-% This method is a simplification of the problem since it assume a Gaussian profile fit, which does not consider other components that could arise from different kinematics processes of the ionized gas and leaves out the broadening due to dust scattering \citep{castaneda1988,1998ApJ...503..760H}.
 
@@
 
-%the model fit to
-
 \subsection{Orion Nebula}
@@
 The Orion Nebula (M42) is the prototype of a galactic \hii{} region located at a distance of 440 pc \citetext{\SI{1}{\arcsecond} = \SI{0.002}{pc} ; \citealp{2008AJ....136.1566O}}.
-The O7 V star \(\theta^{1}\) Ori C is the most luminous and hottest star \citep{2006A&A...448..351S} with an ionizing flux \(Q_0\) of  \SI{e49.12}{photons.s^{-1}}. 
+The O7 V star \(\theta^{1}\) Ori C is the most luminous and hottest star with an ionizing flux \(Q_0\) of  \SI{e49.12}{photons.s^{-1}} \citep{2006A&A...448..351S} or \SI{e37.18}{erg.s^{-1}}. 
 With other 3 B-type stars they form the Trapezium cluster.
@@
 
-Figure~\ref{fig:strucfunc-fit-Galactic}a shows the structure function of the Orion core.
-In this case we merge the first three points of the structure function.
-A detailed description of the model fit is given in
-section~\ref{sec:example-results-orion} and will
-not be repeated here.
+%Figure~\ref{fig:strucfunc-fit-Galactic}a shows the structure function of the Orion core.
+%In this case we merge the first three points of the structure function.
+%A detailed description of the model fit is given in
+%section~\ref{sec:example-results-orion} and will
+%not be repeated here.
 At the largest scales, which are not used in the model fitting,
@@
 \SI{22}{km^{2}.s^{-2}} for \(r < \SI{0.3}{pc}\) to
-\SI{7}{km^{2}.s^{-2}} at \(r  \SI{0.5}{pc}\)
-(open symbols in Figure~\ref{fig:strucfunc-fit-Galactic}a).
-This is similar to the behavior expected for tapered fluctuations
-(see section~\ref{sec:limit-model-struct} and Figure~\ref{fig:model-strucfunc}b)
-in which the velocity dispersion is higher in the center of the map
-than in the periphery.
+\SI{7}{km^{2}.s^{-2}} at \(r  \SI{0.5}{pc}\).
+%This is similar to the behavior expected for tapered fluctuations
+%(see section~\ref{sec:limit-model-struct} and Figure~\ref{fig:model-strucfunc}b)
+%in which the velocity dispersion is higher in the center of the map
+%than in the periphery.
 
@@
 
-The seeing width is much smaller than the angular scale of the observations
+%The seeing width is much smaller than the angular scale of the observations
 \subsubsection{Comparison with previous studies}
@@
 The mean non-thermal linewidth in \ha{} is \SI{11.7 \pm 1.6}{km.s^{-1}} \citep{1973ApJ...183..851B}.
-It contains the young stellar cluster NGC6530 and the region is illuminated by different massive stars of spectral types O and B, the hottest being 9 Sgr, type O4V \citep{Damiani:2017b}.
+%It contains the young stellar cluster NGC6530 and the region is illuminated by different massive stars of spectral types O and B, the hottest being 9 Sgr, type O4V \citep{Damiani:2017b}.
 Optically, the brightest part of the nebula is called 'Hourglass nebula' which surrounds and obscures the O7 star Herschel 36 \citep{1986AJ.....91..870W}. 
-The velocity field shows several expanding shells, related to the stellar population, and the massive protostar M8East-IR \citep{1984ApJ...278..170S} indicating that recent star formation. 
-A blueshifted, neutral layer is also in very good agreement with predictions of champagne-flow models of blister \hii{} regions \citep{Damiani:2017b}. 
-The properties of the nebula are reviewed by \citet{2008hsf2.book..533T}.
+%The velocity field shows several expanding shells, related to the stellar population, and the massive %protostar M8East-IR \citep{1984ApJ...278..170S} indicating that recent star formation. 
+%A blueshifted, neutral layer is also in very good agreement with predictions of champagne-flow models of blister \hii{} regions \citep{Damiani:2017b}. 
+%The properties of the nebula are reviewed by \citet{2008hsf2.book..533T}.
 
@@
 %There aren't any points affected by the seeing which has a value of \SI{0.006}{pc} (\(s_0\)=\SI{1}{\arcsecond}).
-In this case we merge the first two points.
-The Lagoon nebula presents a non-uniform behavior below the correlation length but it is possible to see the characteristic ascending values of the structure function.
+%In this case we merge the first two points.
+%The Lagoon nebula presents a non-uniform behavior below the correlation length but it is possible to see the characteristic ascending values of the structure function.
 %The turbulent parameters that fits our model are a \(r_0\) of \SI{1}{pc}, a \(\sigma^2\pos\) of \SI{7}{km^{2}.s^{-2}} and an index of \num{1.17}.
@@
 Using the \ha{} luminosity as a diagnostic of the ionizing flux \(Q_0\) \citet{2007MNRAS.379.1279S} measured a value of \SI{e50.47}{photons.s^{-1}}.
-Young clusters like Trumpler 14 and 16, and Collinder 228 form the Car OB1 association, one of the largest OB associations on the Galaxy.
-This OB association has more than 65 stars earlier than B0, and several Wolf-Rayet (WR) stars.
+%Young clusters like Trumpler 14 and 16, and Collinder 228 form the Car OB1 association, one of the largest OB associations on the Galaxy.
+%This OB association has more than 65 stars earlier than B0, and several Wolf-Rayet (WR) stars.
 The most luminous star is the blue variable $\eta$ Car.
-As a star formation region, it presents several phenomena related with young stars as evaporating protoplanetary discs, erosion of large dust pillars and the triggering of a second generation of embedded stars and Herbig-Haro objects, to mention some \citetext{see \citealp{2008hsf2.book..138S} and reference therein}.
-This region can be consider as a bridge between the detailed star-formation regions like Orion, and much more distant regions like 30 Doradus.
+%As a star formation region, it presents several phenomena related with young stars as evaporating protoplanetary discs, erosion of large dust pillars and the triggering of a second generation of embedded stars and Herbig-Haro objects, to mention some \citetext{see \citealp{2008hsf2.book..138S} and reference therein}.
+%This region can be consider as a bridge between the detailed star-formation regions like Orion, and much more distant regions like 30 Doradus.
 
@@
 (The Figure~\ref{fig:strucfunc-fit-Galactic}d shows the structure function of the Carina nebula.
-%The seeing is \SI{0.008}{pc} (\(s_0\)=\SI{1.3}{\arcsecond}) and there are just a couple of points that lie below the true model, indicating that the majority of points isn't affected by the seeing.
-For this region we merge the first two points of the structure function.
-As the Lagoon nebula, Carina also shows a non-uniform behavior below the correlation length.
+%For this region we merge the first two points of the structure function.
+%As the Lagoon nebula, Carina also shows a non-uniform behavior below the correlation length.
 %The correlation length is \SI{0.56}{pc} pc at a \(\sigma^2\pos\) of \SI{18}{km^{2}.s^{-2}} and an index of \num{1.14}.
@@
 It host the active star forming region NGC 2070 \citep{2013AJ....145...98W} where the star-formation rate has recently peaked \citep{2015ApJ...811...76C}. 
-NGC 2070 host a population of OB and WR stars \citep{2011A&A...530A.108E}.
+%NGC 2070 host a population of OB and WR stars \citep{2011A&A...530A.108E}.
 This nebula is commonly used as a comparison for extragalactic star-forming regions.
@@
 The 30 Doradus structure function is shown in Figure~\ref{fig:strucfunc-fit-MC}a.
-In this case we merge the first five points of the structure function.
+%In this case we merge the first five points of the structure function.
 %The seeing value for this regions is \SI{0.16}{pc} (\(s_0\)=\SI{0.7}{\arcsecond}) and just one %point of the structure function is below this value.
@@
 N66 has an \ha{} luminosity of \SI{e38.77}{erg.s^{-1}}, almost 60 times higher compared to the Orion Nebula \citep{2010A&A...517A..39H,1984ApJ...287..116K}.
-\citet{2008ApJ...688.1050G} propose an expanding \hii{} region or bubble blown by the winds of the massive progenitor as a mechanism that shapes the recent star formation in this region, in addition to the photoionization from the OB stars.
-This mechanism is similar to shell-like \hii{} regions, with a central cluster in a cavity, and with ongoing star formation triggered around their periphery.
+%\citet{2008ApJ...688.1050G} propose an expanding \hii{} region or bubble blown by the winds of the massive progenitor as a mechanism that shapes the recent star formation in this region, in addition to the photoionization from the OB stars.
+%This mechanism is similar to shell-like \hii{} regions, with a central cluster in a cavity, and with ongoing star formation triggered around their periphery.
 Using a Gaussian single-component \citet{2003ApJ...586.1179D} find a corrected FWHM bulk turbulence of \SI{23.8}{km.s^{-1}}.
@@
 %The seeing value is \SI{0.07}{pc} (\(s_0\)=\SI{0.23}{\arcsecond}).
-For this region the first ten points lie below the true model.
+%For this region the first ten points lie below the true model.
 At separations above \SI{0.4}{pc} the observed structure functions is coincident with the true model. 
@@
 %
-The irregular dwarf galaxy, NGC 6822, is located at a distance of 500 kpc \citetext{\SI{1}{\arcsecond} = \SI{2.42}{pc} ; \citealp{2012A&A...540A.135S}} and the brightest \hii{} regions are Hubble X and Hubble V (HX and HV hereafter).
-%(1'' = 2.4 pc)
-Luminosity \ha{} for HV is \SI{e38.3}{erg.s^{-1}} and for HX is \SI{e38.21}{erg.s^{-1}} \citep{2002MNRAS.329..481B}.
+The irregular dwarf galaxy, NGC 6822, is located at a distance of 500 kpc \citetext{\SI{1}{\arcsecond} = \SI{2.42}{pc} ; \citealp{2012A&A...540A.135S}} and the brightest \hii{} regions are Hubble X and Hubble V.
+Luminosity IN \ha{} for Hubble V is \SI{e38.3}{erg.s^{-1}} and for Hubble X is \SI{e38.21}{erg.s^{-1}} \citep{2002MNRAS.329..481B}.
 The mean non-thermal linewidth in \ha{} is \SI{10.5 \pm 0.02}{km.s^{-1}} for HX and \SI{10.3 \pm 0.03}{km.s^{-1}} \citep{1986A&A...160..374H}.
 Two recognized OB associations are identified within these \hii{} regions \citep{1991ApJ...379..621H,1992AJ....104.1374W}.
-HV is located near 'Hodge OB 8' and HX is located near 'Hodge OB13'  \citep{1999PASP..111.1382O}.
-\citet{1993PASJ...45..693T} realize a study on the kinematics of HX and HV.
+%HV is located near 'Hodge OB 8' and HX is located near 'Hodge OB13'  \citep{1999PASP..111.1382O}.
+%\citet{1993PASJ...45..693T} realize a study on the kinematics of HX and HV.
 
@@
 In the Figure~\ref{fig:strucfunc-fit-ExtraGal}a we show the structure function of Hubble V.
-For the observations coming from the TAURUS-II instrument there wasn't any merging of points at small scales.
+%For the observations coming from the TAURUS-II instrument there wasn't any merging of points at small scales.
 %The value of the seeing for this regions is \SI{0.5}{pc} (\(s_0\)=\SI{0.2}{\arcsecond}).
@@
 
-M33 is the third largest galaxy in the Local Group located at the distance of 840 kpc \citetext{\SI{1}{\arcsecond} = \SI{4.07}{pc} ; \citealp{2015KamKinematics}} and is of morphological type SA(s)cd.
+M33 is the third largest galaxy in the Local Group located at the distance of 820 kpc \citetext{\SI{1}{\arcsecond} = \SI{4.07}{pc} ; \citealp{2015KamKinematics}} and is of morphological type SA(s)cd.
 The two brightest \hii{} regions in the galaxy are NGC 604 and NGC 595.
@@
 Using photometry from the HST \citet{1996ApJ...456..174H} identified that the stars are separated into a primary cluster within NGC 604, and a secondary to the north of the region.
-In the primary there are \(\sim\)200 OB stars, candidate to red supergiants (RSGs) and the presence of WR stars.
-For the northern cluster they find eight luminous stars and no evolved massive stars.
-More Recently, \citet{2011MNRAS.411..235E} studied 10 WR stars and propose at least 4 RSGs candidates.
-\citet{2012AJ....143...43F} focused on the massive young stellar objects (MYSOs).
-The average ages for the stars, was determined to be from  \num{3} to \SI{5}{Myr} \citep{1996ApJ...456..174H} and with the RSGs as an older population have an age of 12.4\(\pm\)2.1 Myr \citep{2011MNRAS.411..235E}.
-This suggest that two episodes of star formation, at least, have taken place in the GEHR.
+%In the primary there are \(\sim\)200 OB stars, candidate to red supergiants (RSGs) and the presence of WR stars.
+%For the northern cluster they find eight luminous stars and no evolved massive stars.
+%More Recently, \citet{2011MNRAS.411..235E} studied 10 WR stars and propose at least 4 RSGs candidates.
+%\citet{2012AJ....143...43F} focused on the massive young stellar objects (MYSOs).
+%The average ages for the stars, was determined to be from  \num{3} to \SI{5}{Myr} \citep{1996ApJ...456..174H} and with the RSGs as an older population have an age of 12.4\(\pm\)2.1 Myr \citep{2011MNRAS.411..235E}.
+%This suggest that two episodes of star formation, at least, have taken place in the GEHR.
 
@@
 Using HST/WFPC-2 images \citet{1996AJ....111.1128M} found approximately 250 stars of the OB type, 13 Supergiants and 10 WR, confirming previous candidates.
-They derived and age of 4.5\(\pm\)1.0 Myr consistent with \citet{1993AJ....105.1400D}.
-\citet{2010MNRAS.402.1635R} used Integral Field Spectroscopy (IFS) to present a resolved study of the physical properties of the ionized gas and the ionized structure.
-They also confirm the presence of previous cataloged WR stars and detect new candidates, and propose classical emission-line ratios as metallicity calibrators.
-\citet{lagrois2011} present a kinematic study of the regions using optical emission lines and and radio 21 cm line observations.
-They proposed Champagne flows at the periphery of the molecular cloud leading to accelerated ionized material.
+%They derived and age of 4.5\(\pm\)1.0 Myr consistent with \citet{1993AJ....105.1400D}.
+%\citet{2010MNRAS.402.1635R} used Integral Field Spectroscopy (IFS) to present a resolved study of the physical properties of the ionized gas and the ionized structure.
+%They also confirm the presence of previous cataloged WR stars and detect new candidates, and propose classical emission-line ratios as metallicity calibrators.
+%\citet{lagrois2011} present a kinematic study of the regions using optical emission lines and and radio 21 cm line observations.
+%They proposed Champagne flows at the periphery of the molecular cloud leading to accelerated ionized material.
 

### 2022-11-29 strucfunc_paper.tex
Write more on power law slopes
Still not finished

@@
 on the basis of the confidence limits for the individual regions,
-implying that there may be a real intrinsic dispersion of 0.17 in the slopes.
+implying that there may be a real intrinsic dispersion of \(\pm 0.17\) in the slopes.
 However, a \(\chi^2\) test shows that this is only marginally significant
-(\(p = 0.11\)), so we cannot reject the idea that all the slopes are identical.
+(\(p = 0.11\)), so we cannot rule out that all the slopes are identical.
+
+\newcommand\DDD{\ensuremath{_{\mathrm{3D}}}}
+For incompressible Kolmogorov turbulence,
+the predicted slope of the three-dimensional structure function is \(m\DDD = 2/3\),
+but intermittency and compressibility \citep{Schmidt:2008a}
+can increase this to \(m\DDD \approx 0.8\) in the subsonic regime,
+and up to \(m\DDD = 1\) in the supersonic regime.
+Comparison with our measurements is complicated by projection smoothing,
+which mean that \(m\DDD\) is only
+observed directly for separations larger than the line-of-sight depth
+of the emitting regions.
+For smaller separations, one potentially observes a steeper slope:
+\(m = m\DDD + 1 + \delta\kappa\),
+where \(\delta\kappa\) represents the effects of emissivity fluctuations
+along the line of sight \citep{Brunt:2004a},
+and varies from \(\delta\kappa = 0\) in the incompressible limit
+to \(\delta\kappa = -1\) in the case of strongly driven supersonic turbulence.
+
+It is therefore not surprising that we see no significant correlation
+between \(m\) and \(\sigma^2\pos\) 
+(\(p = 0.33\), Table~\ref{tab:RestStats}).
+Although theoretically one might expect a positive correlation of \(m\DDD\)
+with the amplitude of the velocity fluctuations
+due to the transition from subsonic
+to supersonic turbulence \citep{Galtier:2011a},
+this will be offset by a decrease in \(\delta\kappa\) 
+if the amplitude of the density fluctuations
+(and hence emissivity fluctuations) increases along
+with the velocity fluctuations.
+
+In figure
+
+We also find no clear evidence for a broken power-law in any of our
+structure functions, as has been suggested in previous studies.
+Although in some regions we do observe a steepening at the smallest scales
+(for example Figures~\ref{fig:strucfunc-fit-Galactic}a, \ref{fig:strucfunc-fit-MC}ab),
+this can be accounted for in our model fits by
+the spatial smoothing caused by atmospheric seeing.
+This has a noticeable effect on the structure function at scales of
+up to 5 times the FWHM of the seeing (Appendix~\ref{sec:effects-seeing-struc}).
+There is a hint in the highest quality datasets that there may also be
+a real steepening of the structure function at small scales
+(see section~\ref{sec:sanity-check-derived}),
+but higher spatial resolution observations are required in order to study this.
+
+Theoretically, one might expect a positive correlation of the slope with the
+amplitude of the velocity fluctuations, due to the transition from subsonic
+to supersonic turbulence \citep{Galtier:2011a}.
+However, the predicted change of slope is rather small,
+\(\delta m \approx 0.2\)
+\citep{Federrath:2021r},
+and only one of our sources (30~Dor) is clearly in the supersonic regime,
+so it is perhaps not surprising that we do not find a significant correlation
+(\(p = 0.33\), Table~\ref{tab:RestStats}).
+This is further complicated by the effect of projection along the line of sight
+
+Theoretically, one might expect
 

### 2022-12-09 strucfunc_paper.tex
Finish discussion of power law slope

@@
 
+\usepackage{upgreek}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-\newcommand\ha{\ensuremath{\text{H}\alpha}}
+\newcommand\ha{\ensuremath{\text{H}\upalpha}}
+\newcommand\hb{\ensuremath{\text{H}\upbeta}}
 \newcommand\Wav[1]{\ensuremath{\lambda #1}}
@@
 \newcommand\FNa{\textsuperscript{a}}
+\newcommand\Mach{\ensuremath{\mathcal{M}}}
 
@@
 A number of fifteen interferograms have been taken with different pointing directions of the telescope's optical axis in the nebula with an exposure time between 10 and 40 minutes. 
-The exposures are overlapped and fall into one square of a grid with a width of \SI{1}{arcmin} centered at \(\theta^{1}\)Ori C.
+The exposures are overlapped and fall into one square of a grid with a width of \SI{1}{arcmin} centered at \(\uptheta^{1}\)Ori C.
 
@@
 and up to \(m\DDD = 1\) in the supersonic regime.
-Comparison with our measurements is complicated by projection smoothing,
-which mean that \(m\DDD\) is only
+Comparison with our measurements is complicated by projection smoothing
+\citep{1984ApJ...277..556S},
+which implies that \(m\DDD\) is only
 observed directly for separations larger than the line-of-sight depth
@@
 \(m = m\DDD + 1 + \delta\kappa\),
-where \(\delta\kappa\) represents the effects of emissivity fluctuations
+where \(\delta\kappa\) represents the effects of emissivity fluctuations\footnote{%
+  Note that literature on turbulence in molecular clouds discuss fluctuations of \emph{density}
+  since they are mainly concerned with emission lines
+  whose emissivity is approximately linearly proportional to density.
+  In the case of photoionized regions, the emissivity of important lines such as \ha{}
+  is proportional to \emph{density-squared},
+  so in adopting the results of \citet{Brunt:2004a} we substitute emission measure
+  (or its proxy, \ha{} surface brightness)
+  in place of column density. 
+}
 along the line of sight \citep{Brunt:2004a},
@@
 to \(\delta\kappa = -1\) in the case of strongly driven supersonic turbulence.
-
+In this latter case, the effects of projection smoothing and emissivity fluctuations
+cancel out, leading once more to \(m \approx m\DDD\).
+
+The \hii{} regions of our sample span the transonic regime,
+from subsonic velocity fluctuations in the Galactic sources
+to supersonic fluctuations in the more luminous extragalactic sources. 
 It is therefore not surprising that we see no significant correlation
@@
 
-In figure
-
-We also find no clear evidence for a broken power-law in any of our
-structure functions, as has been suggested in previous studies.
+Evidence for just such an increase is shown in Figure~\ref{fig:brightness-pdfs}g,
+which shows how the fractional width of the probability distribution of
+large-scale \ha{} surface brightness fluctuations
+varies with the RMS turbulent Mach number, \Mach{},
+of the three-dimensional velocity fluctuations.
+The Mach number is estimated by assuming that the plane-of-sky velocity dispersion is
+a good estimate of the turbulent fluctuations in one dimension
+and that the turbulence is isotropic, yielding:
+\(\Mach = \sqrt{3} \sigma\pos / \csound\),
+where an ionized sound speed of \(\csound = \SI{11}{km.s^{-1}}\)
+is assumed for all sources.
+\newcommand\longsig[1]{\ensuremath{\langle \delta #1^2 \rangle^{1/2} / #1_0}}
+\newcommand\shortsig[1]{\ensuremath{\sigma_{#1/#1_0}}}
+The RMS fractional width of density fluctuations in a turbulent medium,
+\(\shortsig{\rho} \equiv \longsig{\rho}\),
+is predicted to depend linearly on the Mach number as
+\(\shortsig{\rho} = b \Mach\),
+where \(b\) depends on the nature of the turbulent driving \citep{Federrath:2010z},
+varying between \(b = 1/3\) for solenoidal driving and \(b = 1\) for compressive driving.
+This is shown by gray shading\footnote{%
+  In the figure, it is assumed that the relative fluctuations in surface brightness
+  and density are equal, which is a result of the
+  cancellation between two effects. First, that the volumetric \ha{} emissivity \(E\)
+  is proportional to density squared, so that \(\shortsig{E} = 2 \shortsig{\rho}\). 
+  Second, that fluctuations in surface brightness \(S\) are related to those in emissivity
+  by \(\shortsig{S} = R^{1/2} \shortsig{E}\), where \(R\)
+  is the 2D-to-3D variance ratio \citep{Brunt:2010b}.
+  For an emissivity power spectrum \(P(k) \sim k^{-3}\)
+  and assuming a ratio of map size to correlation length
+  of \(L / r_0 = 10\) (typical value from Table~\ref{tab:Res}),
+  we find \(R \approx 0.2\) and hence \(\shortsig{S} \approx \shortsig{\rho}\). 
+}
+in Figure~\ref{fig:brightness-pdfs}h,
+where it can be seen that many of the sources with subsonic velocity dispersions
+(\(\Mach < 1\)) fall to the right of the theoretical prediction,
+implying that other factors in addition to turbulence are responsible for
+producing the fluctuations in density and surface brightness in these regions
+(see also section 4.5 of \citealp{arthur2016turbulence}).
+For our highest luminosity source of 30~Dor on the other hand,
+the velocity dispersion is clearly supersonic (\(\Mach \approx 2.7\))
+and, although the surface brightness fluctuations are also larger than in the other sources,
+they are consistent with being caused by turbulence-induced density fluctuations.
+
+We find no clear evidence for a broken power-law in any of our
+structure functions, as has been claimed in previous studies.
 Although in some regions we do observe a steepening at the smallest scales
@@
 
-Theoretically, one might expect a positive correlation of the slope with the
-amplitude of the velocity fluctuations, due to the transition from subsonic
-to supersonic turbulence \citep{Galtier:2011a}.
-However, the predicted change of slope is rather small,
-\(\delta m \approx 0.2\)
-\citep{Federrath:2021r},
-and only one of our sources (30~Dor) is clearly in the supersonic regime,
-so it is perhaps not surprising that we do not find a significant correlation
-(\(p = 0.33\), Table~\ref{tab:RestStats}).
-This is further complicated by the effect of projection along the line of sight
-
-Theoretically, one might expect
+% Theoretically, one might expect a positive correlation of the slope with the
+% amplitude of the velocity fluctuations, due to the transition from subsonic
+% to supersonic turbulence \citep{Galtier:2011a}.
+% However, the predicted change of slope is rather small,
+% \(\delta m \approx 0.2\)
+% \citep{Federrath:2021r},
+% and only one of our sources (30~Dor) is clearly in the supersonic regime,
+% so it is perhaps not surprising that we do not find a significant correlation
+% (\(p = 0.33\), Table~\ref{tab:RestStats}).
+% This is further complicated by the effect of projection along the line of sight
 
@@
   smaller than the correlation length,
-  Surface brightness maps were rebinned by averaging
+  surface brightness maps were rebinned by averaging
   into pixels of size \(0.5 r_0\) before calculating the PDF.
-  In panel~h is plotted for each source of the previous panels
-  the ratio of velocity dispersions
-  (see Figure~\ref{fig:los-vs-pos})
-  as a function of the
+  Also shown are the RMS Mach number of three-dimensional
+  velocity fluctuations (panel~h)
+  and the ratio of plane-of-sky to line-of-sight velocity dispersions (panel~i),
+  each plotted as a function of the
   RMS fractional brightness fluctuations calculated from the PDFs.
@@
 
-The relationship \(\text{L}_{\text{H}} \propto \sigma^{\alpha}\) has been extensively investigated  in the context of giants \hii{} regions obtaining a value for \(\alpha\) of \( \sim 4\)\citep{terlevich1981,1988A&A...201..199A} and \num{2.87 \pm 0.2} \citep{Rozas:2006b}.
+The relationship \(\text{L}_{\ha} \propto \sigma^{\alpha}\) has been extensively investigated  in the context of giants \hii{} regions obtaining a value for \(\alpha\) of \( \sim 4\)\citep{terlevich1981,1988A&A...201..199A} and \num{2.87 \pm 0.2} \citep{Rozas:2006b}.
 Complementing previous results \citet{2012MNRAS.422.3339W} found that star-forming regions at \(z \sim 1.3\) and local \hii{} regions follow a relation with \(\alpha = 4.18 \pm 0.21\).
 \citet{Moiseev:2015a} found that this relation also holds for dwarf galaxies with a value of \(\alpha \sim 5\).
-\citet{2018MNRAS.474.1250F} presented the relationship between integrated H$_{\beta}$ line luminosity for new data of 36 giant \hii{} regions obtaining \(\text{L}_{\text{H}_{\beta}} \propto \sigma^{5.02 \pm 0.21}\).
+\citet{2018MNRAS.474.1250F} presented the relationship between integrated \hb{} line luminosity for new data of 36 giant \hii{} regions obtaining \(\text{L}_{\hb} \propto \sigma^{5.02 \pm 0.21}\).
 Recently, \citet{2020ApJ...888..113W} studied the properties of high-\(z\) and local \hii{} galaxies among some GEHRs finding a value of \(\alpha \sim 5\).
@@
 The first problem is addressed in section \ref{sec:sigmapos-vs-sigmalos} where we discuss the relation between the line-of-sight and plane-of-sky velocities.
-But despite these problems, the fact that this relationship holds in our results (within the errors) is interesting considering that the \(\sigma\pos\) is derived from the structure function, while the \(\text{L}(\text{H}_{\alpha})\) values comes from different sources unrelated to our data (see the Appendix~\ref{sec:notes-individual-hii}).
+But despite these problems, the fact that this relationship holds in our results (within the errors) is interesting considering that the \(\sigma\pos\) is derived from the structure function, while the \(\text{L}(\ha)\) values comes from different sources unrelated to our data (see the Appendix~\ref{sec:notes-individual-hii}).
 This means that the proposed structure function model describes within certain accuracy the velocity field fluctuations and that the parameters obtained can be interpreted as a true kinematic property of the \hii{} region velocity field.
@@
 The Orion Nebula (M42) is the prototype of a galactic \hii{} region located at a distance of 440 pc \citetext{\SI{1}{\arcsecond} = \SI{0.002}{pc} ; \citealp{2008AJ....136.1566O}}.
-The O7 V star \(\theta^{1}\) Ori C is the most luminous and hottest star with an ionizing flux \(Q_0\) of  \SI{e49.12}{photons.s^{-1}} \citep{2006A&A...448..351S} or \SI{e37.18}{erg.s^{-1}}. 
+The O7 V star \(\uptheta^{1}\) Ori C is the most luminous and hottest star with an ionizing flux \(Q_0\) of \SI{e49.12}{photons.s^{-1}} \citep{2006A&A...448..351S} which translates to luminosity in \ha{} of \SI{e37.18}{erg.s^{-1}}.
 With other 3 B-type stars they form the Trapezium cluster.
@@
 
-%Figure~\ref{fig:strucfunc-fit-Galactic}a shows the structure function of the Orion core.
-%In this case we merge the first three points of the structure function.
-%A detailed description of the model fit is given in
-%section~\ref{sec:example-results-orion} and will
-%not be repeated here.
-At the largest scales, which are not used in the model fitting,
-one sees a downturn in the structure function from
-\SI{22}{km^{2}.s^{-2}} for \(r < \SI{0.3}{pc}\) to
-\SI{7}{km^{2}.s^{-2}} at \(r  \SI{0.5}{pc}\).
-%This is similar to the behavior expected for tapered fluctuations
-%(see section~\ref{sec:limit-model-struct} and Figure~\ref{fig:model-strucfunc}b)
-%in which the velocity dispersion is higher in the center of the map
-%than in the periphery.
+\
+
+\textit{Orion core}
+
+\
+Figure~\ref{fig:strucfunc-fit-Galactic}a shows the structure function of the Orion core.
+A detailed description of the model fit is given in section~\ref{sec:example-results-orion} and will not be repeated here.
+Using the observed structure function and by simple linear interpolation the value of \(\sigma\pos^2 = \SI{9}{km^{2}.s^{-2}}\) is obtained at \(r_0 = \SI{0.05}{pc} \) (as comparison to the derived values from our model which are \(\sigma\pos^2 = \SI{13}{km^{2}.s^{-2}}\) and \(r_0 = \SI{0.07}{pc} \)).
+The observed value of \(2\sigma\pos^2\) corresponds to \(r = \SI{0.13}{pc} \) (this \(r\) value would be analog to the total decorrelation length \(\tau_0\), see section~\ref{sec:comp-with-prev}). 
+The maximum \(B(r)\) value correspond to \SI{23}{km^{2}.s^{-2}} at \(r = \SI{0.30}{pc}\).
+From this value the \(B(r)\) values decrease and it is possible to observe a downturn in the structure function from to \SI{7}{km^{2}.s^{-2}} at \(r =  \SI{0.5}{pc}\). 
+This 'hook' behavior is described by the tapered fluctuations (see section~\ref{sec:limit-model-struct}).
+If we consider the first valid point of \(B(r)\) to be above the derived value of \(s_0\), which corresponds to \SI{0.3}{km^{2}.s^{-2}} at \(r = \SI{0.003}{pc} \) and use a linear relation to calculate the slope for \(\sigma\pos^2\) and \(2\sigma\pos^2\) we obtain \num{0.66} and \num{0.89}, respectively, while our derived value is \num{1}.
+
+\textit{EON}
 
@@
 %The seeing width is much smaller than the angular scale of the observations
+
 \subsubsection{Comparison with previous studies}
@@
 The Lagoon Nebula (M8, NGC6523) is located at a distance of 1 250 pc \citetext{\SI{1}{\arcsecond} = \SI{0.006}{pc} ; \citealp{2005A&A...430..941P}}.
-It has a luminosity in \ha{} of \SI{e37.47}{erg.s^{-1}} \citep{1984ApJ...287..116K}.
+It contains the young stellar cluster NGC6530 and the region is illuminated by different massive stars of spectral types O and B, the hottest being 9 Sgr, type O4V \citep{Damiani:2017b}.
+Optically, the brightest part of the nebula is called 'Hourglass nebula' which surrounds and obscures the O7 star Herschel 36 \citep{1986AJ.....91..870W}.
+These stars gives an ionizing flux \(Q_0\) of \SI{e49.41}{photons.s^{-1}} (2 times higher compared to the Orion Nebula) and the luminosity in \ha{} of \SI{e37.47}{erg.s^{-1}} \citep{1984ApJ...287..116K}.
 The mean non-thermal linewidth in \ha{} is \SI{11.7 \pm 1.6}{km.s^{-1}} \citep{1973ApJ...183..851B}.
-%It contains the young stellar cluster NGC6530 and the region is illuminated by different massive stars of spectral types O and B, the hottest being 9 Sgr, type O4V \citep{Damiani:2017b}.
-Optically, the brightest part of the nebula is called 'Hourglass nebula' which surrounds and obscures the O7 star Herschel 36 \citep{1986AJ.....91..870W}. 
-%The velocity field shows several expanding shells, related to the stellar population, and the massive %protostar M8East-IR \citep{1984ApJ...278..170S} indicating that recent star formation. 
-%A blueshifted, neutral layer is also in very good agreement with predictions of champagne-flow models of blister \hii{} regions \citep{Damiani:2017b}. 
-%The properties of the nebula are reviewed by \citet{2008hsf2.book..533T}.
+The velocity field shows several expanding shells, related to the stellar population, and the massive protostar M8East-IR \citep{1984ApJ...278..170S} indicating that recent star formation. 
+A blueshifted, neutral layer is also in very good agreement with predictions of champagne-flow models of blister \hii{} regions \citep{Damiani:2017b}. 
+The properties of the nebula are reviewed by \citet{2008hsf2.book..533T}.
 
@@
 
+We follow the same procedure we use to describe the observed structure function of the Orion Nebula for the rest of the regions.
 The Figure~\ref{fig:strucfunc-fit-Galactic}c shows the structure function of the Lagoon nebula.
-%There aren't any points affected by the seeing which has a value of \SI{0.006}{pc} (\(s_0\)=\SI{1}{\arcsecond}).
-%In this case we merge the first two points.
-%The Lagoon nebula presents a non-uniform behavior below the correlation length but it is possible to see the characteristic ascending values of the structure function.
-%The turbulent parameters that fits our model are a \(r_0\) of \SI{1}{pc}, a \(\sigma^2\pos\) of \SI{7}{km^{2}.s^{-2}} and an index of \num{1.17}.
-At large scales there is an indication of some periodic behavior followed by ascending \(B(r)\) values at largest separation.
-A value of\(B(r)\) of order 2\(\sigma^2\pos\) is \(\sim\)\SI{14}{km^{2}.s^{-2}} at a separation of \(\sim\)\SI{2.5}{pc}. 
-Then there is a diminution at \SI{4.5}{pc} down to a value of \SI{11}{km^{2}.s^{-2}}.
-From this point the structure function ascends until it reaches \SI{66}{km^{2}.s^{-2}} around \SI{20}{pc}.
+This region presents a non-uniform behavior below the derived correlation length but still it is possible to see the characteristic ascending values of the structure function.
+The value of the observed \(\sigma\pos^2 = \SI{8}{km^{2}.s^{-2}}\) is obtained at \(r_0 = \SI{1}{pc} \) (in this case there is a good agreement with the derived values from our model which are \(\sigma\pos^2 = \SI{7}{km^{2}.s^{-2}}\) and \(r_0 = \SI{1}{pc} \)).
+The observed value of \(2\sigma\pos^2\) corresponds to \(r = \SI{2.5}{pc} \).
+From this point the structure function shows a 'reversed hook' behavior, which mean that there is a decrease in \(B(r)\) values up until \(r_0 = \SI{4}{pc} \)) for a value of \SI{11}{km^{2}.s^{-2}}, which from this point the structure function ascends until it reaches \SI{66}{km^{2}.s^{-2}} around \SI{20}{pc}.
+This may be because our observations doesn't cover and outer correlation region (see sections~\ref{sec:D-vs-r0}) or an indication of some periodic behavior (see sections~\ref{sec:limit-model-struct}).
+There aren't any points affected by the seeing (RMS) which has a value of \SI{0.01}{pc} (\(s_0\)=\SI{3.5}{\arcsecond}).
+If we consider the first point of this \(B(r)\) to be valid, which corresponds to \SI{0.55}{km^{2}.s^{-2}} at \(r = \SI{0.05}{pc} \) the slope for \(\sigma\pos^2\) and \(2\sigma\pos^2\) we obtain \num{0.89} and \num{0.86}, respectively, while our derived value is \num{1.26}.
 
@@
 The Carina nebula is a large star-forming complex located at a distance of 2 350 pc \citetext{\SI{1}{\arcsecond} = \SI{0.01}{pc} ; \citealp{2006ApJ...644.1151S}}.
-Using the \ha{} luminosity as a diagnostic of the ionizing flux \(Q_0\) \citet{2007MNRAS.379.1279S} measured a value of \SI{e50.47}{photons.s^{-1}}.
-%Young clusters like Trumpler 14 and 16, and Collinder 228 form the Car OB1 association, one of the largest OB associations on the Galaxy.
-%This OB association has more than 65 stars earlier than B0, and several Wolf-Rayet (WR) stars.
-The most luminous star is the blue variable $\eta$ Car.
-%As a star formation region, it presents several phenomena related with young stars as evaporating protoplanetary discs, erosion of large dust pillars and the triggering of a second generation of embedded stars and Herbig-Haro objects, to mention some \citetext{see \citealp{2008hsf2.book..138S} and reference therein}.
-%This region can be consider as a bridge between the detailed star-formation regions like Orion, and much more distant regions like 30 Doradus.
+It contains young clusters like Trumpler 14 and 16, and Collinder 228 from the Car OB1 association, one of the largest OB associations in the Galaxy.
+This OB association has more than 65 stars earlier than B0, and several Wolf-Rayet (WR) stars and the most luminous star is the blue variable $\eta$ Car.
+The ionizing flux \(Q_0\) is \SI{e50.95}{photons.s^{-1}} \citep{2008hsf2.book..138S} (60 times higher compared to the Orion Nebula) and the luminosity in \ha{} of \SI{e39.01}{erg.s^{-1}}.
+As a star formation region, it presents several phenomena related with young stars as evaporating protoplanetary discs, erosion of large dust pillars and the triggering of a second generation of embedded stars and Herbig-Haro objects, to mention some \citetext{see \citealp{2008hsf2.book..138S} and reference therein}.
+This region can be consider as a bridge between the detailed star-formation regions like Orion, and much more distant regions like 30 Doradus.
 
@@
 
-(The Figure~\ref{fig:strucfunc-fit-Galactic}d shows the structure function of the Carina nebula.
-%For this region we merge the first two points of the structure function.
-%As the Lagoon nebula, Carina also shows a non-uniform behavior below the correlation length.
-%The correlation length is \SI{0.56}{pc} pc at a \(\sigma^2\pos\) of \SI{18}{km^{2}.s^{-2}} and an index of \num{1.14}.
-At larges scales the structure function of the Carina nebula follows a pattern that resembles the homogeneous fluctuation of Figure~\ref{fig:model-strucfunc}a.
-The structure function reaches a plateau around \SI{36}{km^{2}.s^{-2}} at \(\sim\) \SI{2}{pc}.
-When \(r >\)\SI{6}{pc} the structure functions shows a small amplitude periodic pattern around 2\(\sigma^2\pos\).
+The Figure~\ref{fig:strucfunc-fit-Galactic}d shows the structure function of the Carina nebula.
+As the Lagoon nebula, the structure function of Carina also shows a non-uniform and a more disperse behavior below the correlation length.
+The value of the observed \(\sigma\pos^2 = \SI{18}{km^{2}.s^{-2}}\) is obtained at \(r_0 = \SI{0.5}{pc} \) (in this case there is a good agreement with the derived values from our model which are \(\sigma\pos^2 = \SI{18}{km^{2}.s^{-2}}\) and \(r_0 = \SI{0.5}{pc} \)).
+The observed value of \(2\sigma\pos^2\) corresponds to \(r = \SI{1.6}{pc} \).
+Above this separation, at larges scales, the structure function of the Carina nebula follows a pattern that resembles the homogeneous fluctuation of Figure~\ref{fig:model-strucfunc}a.
+Also, it can be argue that at large scales the behavior does not reflect purely the homogeneous fluctuations. 
+It seems that there are two  oscillating pattern at large scales.
+The first one, from \(r = \SI{1.7}{pc} \) to \SI{6}{pc} which has an spatial wavelength of \SI{\sim 2}{pc} and a dispersion of \SI{1}{km^{2}.s^{-2}}.
+The second one when \(r >\)\SI{6}{pc} until \SI{7}{pc} with a dispersion of \SI{3.5}{km^{2}.s^{-2}}.
+This fluctuations are around the value of 2\(\sigma^2\pos\) so it is possible that the dispersion is artificial because of the multi-fiber observations (see section~\ref{sec:flames-multi-fiber}).
+There aren't any points affected by the seeing (RMS) which has a value of \SI{0.015}{pc} (\(s_0\)=\SI{3.4}{\arcsecond}).
+If we consider the first point of this \(B(r)\) to be valid, which corresponds to \SI{4}{km^{2}.s^{-2}} at \(r = \SI{0.01}{pc} \) the slope for \(\sigma\pos^2\) and \(2\sigma\pos^2\) we obtain \num{0.38} and \num{0.43}, respectively, while our derived value is \num{1.16}.
 
@@
 It is a luminous star-forming region in the LMC (Large Magellanic Cloud) and is the most luminous complex in the Local Group \citep{1984ApJ...287..116K}.
-The central ionized region spans for \SI{40}{pc} and host the massive, dense star cluster R136 %\citep{1991IAUS..148..145W}. %Note: check the bibliographic format
-The ionizing output \(Q_0\) of R136 is \SI{e51.4}{photons.s^{-1}} \citep{2020MNRAS.499.1918B}.
+The central ionized region spans for \SI{40}{pc} and host the massive dense star cluster R136
+with ionizing output \(Q_0\) of is \SI{e51.40}{photons.s^{-1}} \citep{2020MNRAS.499.1918B} and the luminosity in \ha{} of \SI{e39.46}{erg.s^{-1}} (194 times higher compared to the Orion Nebula).
+%\citep{1991IAUS..148..145W}. %Note: check the bibliographic format
 The mean non-thermal linewidth in \ha{} is \SI{22}{km.s^{-1}} \citep{2013A&A...555A..60T}.
-It host the active star forming region NGC 2070 \citep{2013AJ....145...98W} where the star-formation rate has recently peaked \citep{2015ApJ...811...76C}. 
-%NGC 2070 host a population of OB and WR stars \citep{2011A&A...530A.108E}.
+It host the active star forming region NGC 2070 \citep{2013AJ....145...98W} where the star-formation rate has recently peaked \citep{2015ApJ...811...76C} and host a population of OB and WR stars \citep{2011A&A...530A.108E}.
 This nebula is commonly used as a comparison for extragalactic star-forming regions.
@@
 
-The 30 Doradus structure function is shown in Figure~\ref{fig:strucfunc-fit-MC}a.
-%In this case we merge the first five points of the structure function.
-%The seeing value for this regions is \SI{0.16}{pc} (\(s_0\)=\SI{0.7}{\arcsecond}) and just one %point of the structure function is below this value.
-%Until a separation of \SI{1.7}{pc} is reached, the structure function lies below the true model.
-%The correlation length is \SI{4}{pc} at a \(\sigma^2\pos\) of \SI{297 \pm 9}{km^{2}.s^{-2}} and an index of \num{0.85}.
-At large separations 30 Doradus structure function presents a behavior of tapered fluctuations. The maximum \(B(r)\) value is \SI{655}{km^{2}.s^{-2}} at a separation of \SI{21}{pc}. 
-From there \(B(r)\) values descends until they reach \SI{250}{km^{2}.s^{-2}} at \SI{38}{pc}.
+The 30~Doradus structure function is shown in Figure~\ref{fig:strucfunc-fit-MC}a.
+The value of the observed \(\sigma\pos^2 = \SI{252}{km^{2}.s^{-2}}\) is obtained at \(r_0 = \SI{3}{pc} \) (the derived values from our model are \(\sigma\pos^2 = \SI{7}{km^{297}.s^{-2}}\) and \(r_0 = \SI{4}{pc} \)).
+The observed value of \(2\sigma\pos^2\) corresponds to \(r = \SI{13}{pc} \).
+The maximum \(B(r)\) value correspond to \SI{654}{km^{2}.s^{-2}} at \(r = \SI{21}{pc}\).
+From this value the \(B(r)\) values decrease and it is possible to observe a downturn in the structure function from to \SI{250}{km^{2}.s^{-2}} at \(r =  \SI{38}{pc}\) following the tapered fluctuations behavior.
+The seeing (RMS) value derived for this regions is \SI{0.16}{pc} (\(s_0\)=\SI{1.5}{\arcsecond}) and just one point of the structure function is below this value.
+Considering the first point above this \(s_0\) value to be valid, which corresponds to \SI{15}{km^{2}.s^{-2}} at \(r = \SI{0.2}{pc} \) the slope for \(\sigma\pos^2\) and \(2\sigma\pos^2\) we obtain \num{1.04} and \num{0.84}, respectively, while our derived value is \num{0.85}.
 
@@
 The first attempt at characterizing turbulence in a giant extragalactic \hii{} region, GEHR, was done by \citet{1961MNRAS.122....1F} with the 30~Doradus complex, finding no indication of turbulent motions between scale of \num{10} and \SI{100}{pc}.
-\citet{Melnick:2021x} also investigated the structure function in 30 Doradus finding on their results that the structure function is entirely flat on scales from \num{3} to \SI{200}{pc}.
+\citet{Melnick:2021x} also investigated the structure function in 30~Doradus finding on their results that the structure function is entirely flat on scales from \num{3} to \SI{200}{pc}.
 The above does not coincide with our results, since we establish the existence of correlations up to the maximum value of the structure function that occurs at \SI{20}{pc}, separation where a value of 2\(\sigma\pos^2\) is reached.
@@
 It has more than 30 O stars that ionize N66, the largest \hii{} region \citep{2011ApJ...740...10D}.
-N66 has an \ha{} luminosity of \SI{e38.77}{erg.s^{-1}}, almost 60 times higher compared to the Orion Nebula \citep{2010A&A...517A..39H,1984ApJ...287..116K}.
-%\citet{2008ApJ...688.1050G} propose an expanding \hii{} region or bubble blown by the winds of the massive progenitor as a mechanism that shapes the recent star formation in this region, in addition to the photoionization from the OB stars.
-%This mechanism is similar to shell-like \hii{} regions, with a central cluster in a cavity, and with ongoing star formation triggered around their periphery.
+N66 has an ionizing output \(Q_0\) of \SI{e50.71}{photons.s^{-1}} (40 times higher compared to the Orion Nebula) and has a \ha{} luminosity of \SI{e38.77}{erg.s^{-1}} \citep{2010A&A...517A..39H,1984ApJ...287..116K}.
 Using a Gaussian single-component \citet{2003ApJ...586.1179D} find a corrected FWHM bulk turbulence of \SI{23.8}{km.s^{-1}}. 
+\citet{2008ApJ...688.1050G} propose an expanding \hii{} region or bubble blown by the winds of the massive progenitor as a mechanism that shapes the recent star formation in this region, in addition to the photoionization from the OB stars.
+This mechanism is similar to shell-like \hii{} regions, with a central cluster in a cavity, and with ongoing star formation triggered around their periphery.
 
@@
 The Figure~\ref{fig:strucfunc-fit-MC}b shows the structure function of NGC 346.
-%In this case we merge the first three points of the structure function.
-%The seeing value is \SI{0.07}{pc} (\(s_0\)=\SI{0.23}{\arcsecond}).
-%For this region the first ten points lie below the true model.
-At separations above \SI{0.4}{pc} the observed structure functions is coincident with the true model. 
-%The correlation length is \SI{2}{pc} at a \(\sigma^2\pos\) of \SI{35}{km^{2}.s^{-2}} and an index of \num{0.80}.
-For scales above \SI{12}{pc} and a \(B(r)\) value of \SI{65}{km^{2}.s^{-2}} the structure function shows a pattern of ascending values until it reaches \SI{146}{km^{2}.s^{-2}} at \SI{24}{pc}.
+The value of the observed \(\sigma\pos^2 = \SI{30}{km^{2}.s^{-2}}\) is obtained at \(r_0 = \SI{2.3}{pc} \) (in this case there is a good agreement with the derived values from our model which are \(\sigma\pos^2 = \SI{33}{km^{2}.s^{-2}}\) and \(r_0 = \SI{2.4}{pc} \)).
+The observed value of \(2\sigma\pos^2\) corresponds to \(r = \SI{10}{pc} \), though, at this scale the \(B(r)\) value is just below the \(2\sigma\pos^2\), but the structure function seems to plateau at those values.
+Above this scales the structure function shows a periodic pattern with a spatial wavelength of \SI{\sim 10}{pc} and a dispersion of \(\SI{6}{km^{2}.s^{-2}}\).
+Unlike the Carina nebula, this oscillating pattern is below the \(2\sigma\pos^2\) value.
+The seeing value is \SI{0.11}{pc} (\(s_0\)=\SI{0.9}{\arcsecond}) and just one point of the structure functions lies below this value.
+Considering the first point above this \(s_0\) value to be valid, which corresponds to \SI{2.5}{km^{2}.s^{-2}} at \(r = \SI{0.2}{pc} \) the slope for \(\sigma\pos^2\) and \(2\sigma\pos^2\) we obtain \num{1.01} and \num{0.81}, respectively, while our derived value is \num{0.95}.
 
@@
 %
-The irregular dwarf galaxy, NGC 6822, is located at a distance of 500 kpc \citetext{\SI{1}{\arcsecond} = \SI{2.42}{pc} ; \citealp{2012A&A...540A.135S}} and the brightest \hii{} regions are Hubble X and Hubble V.
-Luminosity IN \ha{} for Hubble V is \SI{e38.3}{erg.s^{-1}} and for Hubble X is \SI{e38.21}{erg.s^{-1}} \citep{2002MNRAS.329..481B}.
-The mean non-thermal linewidth in \ha{} is \SI{10.5 \pm 0.02}{km.s^{-1}} for HX and \SI{10.3 \pm 0.03}{km.s^{-1}} \citep{1986A&A...160..374H}.
-Two recognized OB associations are identified within these \hii{} regions \citep{1991ApJ...379..621H,1992AJ....104.1374W}.
-%HV is located near 'Hodge OB 8' and HX is located near 'Hodge OB13'  \citep{1999PASP..111.1382O}.
-%\citet{1993PASJ...45..693T} realize a study on the kinematics of HX and HV.
+The irregular dwarf galaxy, NGC 6822, is located at a distance of 500 kpc \citetext{\SI{1}{\arcsecond} = \SI{2.42}{pc} ; \citealp{2012A&A...540A.135S}} and host the \hii{} regions Hubble X and Hubble V which are the brightest regions in the galaxy.
+
+Hubble V is located near the 'Hodge OB 8' OB association with a number of \num{\sim 36} young stellar objects \citep{2021MNRAS.507.5106K} and its core is powered by an O3 V star \citep{1999PASP..111.1382O}.
+It has an ionizing output \(Q_0\) of \SI{e50.23}{photons.s^{-1}} (13 times higher compared to the Orion Nebula) and has a \ha{} luminosity of \SI{e38.30}{erg.s^{-1}}\citep{2002MNRAS.329..481B}.
+The mean non-thermal linewidth in \ha{} \SI{10.3 \pm 0.03}{km.s^{-1}} \citep{1986A&A...160..374H}.
+
+Hubble X is located near the 'Hodge OB 13' OB association with a number of \num{\sim 29} young stellar objects \citep{2021MNRAS.507.5106K} and its core is powered by and O4 V star \citep{1999PASP..111.1382O}.
+It has an ionizing output \(Q_0\) of \SI{e50.14}{photons.s^{-1}} (10 times higher compared to the Orion Nebula) and has a \ha{} luminosity of \SI{e38.21}{erg.s^{-1}} \citep{2002MNRAS.329..481B}.
+The mean non-thermal linewidth in \ha{} is \SI{10.5 \pm 0.02}{km.s^{-1}}  \citep{1986A&A...160..374H}.
+\citet{1993PASJ...45..693T} realize a study on the kinematics of both regions.
 
@@
 In the Figure~\ref{fig:strucfunc-fit-ExtraGal}a we show the structure function of Hubble V.
-%For the observations coming from the TAURUS-II instrument there wasn't any merging of points at small scales.
+The value of the observed \(\sigma\pos^2 = \SI{8}{km^{2}.s^{-2}}\) is obtained at \(r_0 = \SI{3}{pc} \) (while the derived values from our model are \(\sigma\pos^2 = \SI{10}{km^{2}.s^{-2}}\) and \(r_0 = \SI{3.6}{pc} \)).
+The observed value of \(2\sigma\pos^2\) corresponds to \(r = \SI{31}{pc} \).
+The maximum \(B(r)\) value is \SI{18}{km^{2}.s^{-2}} at a separation of \SI{25}{pc}. 
 %The value of the seeing for this regions is \SI{0.5}{pc} (\(s_0\)=\SI{0.2}{\arcsecond}).
-%All the structure function points lies below the true model.
-%The correlation length is \SI{3.5}{pc} at a \(\sigma^2\pos\) of  \SI{10}{km^{2}.s^{-2}} and an index of \num{0.75}.
-The maximum \(B(r)\) value is \SI{18}{km^{2}.s^{-2}} at a separation of \SI{25}{pc}. 
-From there \(B(r)\) values descends until it reaches \SI{14}{km^{2}.s^{-2}} at \SI{45}{pc}, then it rises for the next point at \SI{50}{pc} with a value of \SI{15}{km^{2}.s^{-2}}.
-Finally the structure functions descends at \SI{9}{km^{2}.s^{-2}} for a separation of \SI{70}{pc}.
+From this value the \(B(r)\) values decrease and we observe a downturn in the structure function to \SI{9}{km^{2}.s^{-2}} at \(r =  \SI{70}{pc}\) following the tapered fluctuations behavior.
+But unlike the Orion core or 30~Dor the downturn is not as smooth, since it presents a small variation at \(r = \SI{\sim 40}{pc} \) 
+The seeing (RMS) value derived for this regions is \SI{0.5}{pc} (\(s_0\)=\SI{0.2}{\arcsecond}) and just one point of the structure function fall in the confidence interval..
+Considering the first point above this \(s_0\) value to be valid, which corresponds to \SI{2.2}{km^{2}.s^{-2}} at \(r = \SI{0.89}{pc} \) the slope for \(\sigma\pos^2\) and \(2\sigma\pos^2\) we obtain \num{1.06} and \num{0.55}, respectively, while our derived value is \num{0.81}.
 
 The Hubble X structure function is shown in Figure~\ref{fig:strucfunc-fit-ExtraGal}b.
-%The seeing is \SI{0.6}{pc} (\(s_0\)=\SI{0.24}{\arcsecond}) and as in Hubble V the observed structure function lies below the true model.
-%The correlation length is \SI{4}{pc} at a \(\sigma^2\pos\) of \SI{15}{km^{2}.s^{-2}} and an index of \num{0.93}.
-A plateau is reached around \SI{25}{km^{2}.s^{-2}} at a separation of \SI{14}{pc} and a maximum \(B(r)\) value of \SI{31}{km^{2}.s^{-2}} at a separation of \SI{36}{pc}.
+The value of the observed \(\sigma\pos^2 = \SI{13}{km^{2}.s^{-2}}\) is obtained at \(r_0 = \SI{4}{pc} \) (while the derived values from our model are \(\sigma\pos^2 = \SI{15}{km^{2}.s^{-2}}\) and \(r_0 = \SI{4}{pc} \)).
+The observed value of \(2\sigma\pos^2\) corresponds to \(r = \SI{15}{pc} \).
+The maximum \(B(r)\) value of \SI{31}{km^{2}.s^{-2}} is reached at a separation of \SI{36}{pc}.
+From scales \(> \SI{15}{pc}\) we see that the structure functions fluctuates around \(2\sigma\pos^2\) with a spatial wavelength of \(\sim \SI{30}{pc}\) with a dispersion of \SI{2.3}{km^{2}.s^{-2}}.
+Since these large scales values fluctuates around \(2\sigma\pos^2\) is also possible that the structure function follows a purely homogeneous fluctuations behavior, just not as marked as it is shown in section~\ref{sec:limit-model-struct}.
+The seeing is \SI{0.6}{pc} (\(s_0\)=\SI{0.24}{\arcsecond}) and as in Hubble V there is just one point of the structure function that falls in the \(s_0\) confidence interval.
+Considering the first point above this \(s_0\) value to be valid, which corresponds to \SI{2.6}{km^{2}.s^{-2}} at \(r = \SI{0.86}{pc} \) the slope for \(\sigma\pos^2\) and \(2\sigma\pos^2\) we obtain \num{1.04} and \num{0.80}, respectively, while our derived value is \num{1.02}.
 
@@
 
-NGC 604 is the second brightest \hii{} region in the Local Group after 30~Dor in the Large Magellanic Cloud and is forty times larger ($\sim $ 400 pc) and 6,000 times brighter than Orion in our Milky Way galaxy.
-It is the brightest giant \hii{} region in the M33 galaxy and is visually dominated by a big loop, big shells and different size filaments.
-It has a luminosity in \ha{} of \SI{e39.42}{erg.s^{-1}} \citep{2002MNRAS.329..481B}.
+NGC 604 is the second brightest \hii{} region in the Local Group after 30~Dor.
+Using photometry from the HST \citet{1996ApJ...456..174H} identified that the stars are separated into a primary cluster within NGC 604, and a secondary to the north of the region.
+In the primary there are \(\sim\)200 OB stars, candidate to red supergiants (RSGs) and the presence of WR stars.
+For the northern cluster they find eight luminous stars and no evolved massive stars.
+More Recently, \citet{2011MNRAS.411..235E} studied 10 WR stars and propose at least 4 RSGs candidates.
+\citet{2012AJ....143...43F} focused on the massive young stellar objects (MYSOs).
+The ionizing output \(Q_0\) is \SI{e51.35}{photons.s^{-1}} (175 times higher compared to the Orion Nebula) and has a \ha{} of \SI{e39.42}{erg.s^{-1}} \citep{2002MNRAS.329..481B}.
 The mean non-thermal linewidth in \ha{} is \SI{17.8 \pm 0.3}{km.s^{-1}} \citep{1986A&A...160..374H}.
-Using photometry from the HST \citet{1996ApJ...456..174H} identified that the stars are separated into a primary cluster within NGC 604, and a secondary to the north of the region.
-%In the primary there are \(\sim\)200 OB stars, candidate to red supergiants (RSGs) and the presence of WR stars.
-%For the northern cluster they find eight luminous stars and no evolved massive stars.
-%More Recently, \citet{2011MNRAS.411..235E} studied 10 WR stars and propose at least 4 RSGs candidates.
-%\citet{2012AJ....143...43F} focused on the massive young stellar objects (MYSOs).
+It is the brightest giant \hii{} region in the M33 galaxy and is visually dominated by a predominant big loop, many expanding shells and different size filaments.
+
 %The average ages for the stars, was determined to be from  \num{3} to \SI{5}{Myr} \citep{1996ApJ...456..174H} and with the RSGs as an older population have an age of 12.4\(\pm\)2.1 Myr \citep{2011MNRAS.411..235E}.
 %This suggest that two episodes of star formation, at least, have taken place in the GEHR.
-
 % and in L$_{X}$=9.3$\times$ 10$^{35}$ erg s$^{-1}$ \citep{2008ApJ...685..919T}.
@@
 
-NGC 595 is the second brightest giant \hii{} region in the M33 galaxy and has an \ha{} shell morphology that is related to the stellar winds of the several massive stars located in its interior.
-It has a luminosity in \ha{} of \SI{e38.95}{erg.s^{-1}}\citep{2002MNRAS.329..481B}.
+NGC 595 is the second brightest giant \hii{} region in the M33 galaxy.
+Using HST/WFPC-2 images \citet{1996AJ....111.1128M} found approximately 250 stars of the OB type, 13 Supergiants and 10 WR, confirming previous candidates.
+\citet{1993AJ....105.1400D} use optical photometry to propose 11 WR stars. 
+The ionizing output \(Q_0\) is \SI{e50.88}{photons.s^{-1}} (60 times higher compared to the Orion Nebula) and has a luminosity in \ha{} of \SI{e38.95}{erg.s^{-1}}\citep{2002MNRAS.329..481B}.
 The mean non-thermal linewidth in \ha{} is \SI{16.8 \pm 0.1}{km.s^{-1}} \citep{lagrois2009multi}.
-\citet{1993AJ....105.1400D} use optical photometry to propose 11 WR stars. 
-Using HST/WFPC-2 images \citet{1996AJ....111.1128M} found approximately 250 stars of the OB type, 13 Supergiants and 10 WR, confirming previous candidates.
+\citet{lagrois2011} present a kinematic study of the regions using optical emission lines and and radio 21 cm line observations and find that \ha{} shell morphology that is related to the stellar winds of the several massive stars located in its interior.
+They proposed Champagne flows at the periphery of the molecular cloud leading to accelerated ionized material.
+
 %They derived and age of 4.5\(\pm\)1.0 Myr consistent with \citet{1993AJ....105.1400D}.
@@
 %They also confirm the presence of previous cataloged WR stars and detect new candidates, and propose classical emission-line ratios as metallicity calibrators.
-%\citet{lagrois2011} present a kinematic study of the regions using optical emission lines and and radio 21 cm line observations.
-%They proposed Champagne flows at the periphery of the molecular cloud leading to accelerated ionized material.
 
@@
 In the Figure~\ref{fig:strucfunc-fit-ExtraGal}c we show the structure function of NGC 595.
-%The seeing is \SI{0.3}{pc} (\(s_0\)=\SI{0.1}{\arcsecond}) and for this region only the first two points are below the true model. 
-%The correlation length is \SI{12}{pc} at a \(\sigma^2\pos\) of \SI{54}{km^{2}.s^{-2}} and an index of \num{1.3}.
-At large scales the structure function behaves following the tapered fluctuations pattern.
-A maximum \(B(r)\) value of \SI{104}{km^{2}.s^{-2}} is reached at \SI{33}{pc}. 
-From there the structure functions decays following a scatter pattern until it reaches \SI{54}{km^{2}.s^{-2}} at a separation of \SI{211}{pc}.
+The value of the observed \(\sigma\pos^2 = \SI{44}{km^{2}.s^{-2}}\) is obtained at \(r_0 = \SI{10}{pc} \) (while the derived values from our model are \(\sigma\pos^2 = \SI{53}{km^{2}.s^{-2}}\) and \(r_0 = \SI{11}{pc} \)).
+The observed value of \(2\sigma\pos^2\) corresponds to \(r = \SI{21}{pc} \).
+The maximum \(B(r)\) value is \SI{104}{km^{2}.s^{-2}} at a separation of \SI{30}{pc}. 
+For NGC 595 we see that the structure function plateau at this maximum \(B(r)\) value, which implies that the observed \(\sigma\pos^2\) is affected by the observational constraints.
+Until \(r_0 \sim \SI{55}{pc} \) the structure functions remains closely to the 'true' \(2\sigma\pos^2\), for the largest scale there is a decrease between  \(\SI{55}{pc} < r < \SI{110}{pc} \) where the structure function plateaus at the 'observed' \(2\sigma\pos^2\).
+Above \SI{110}{pc} we see a very disperse downturn  until \SI{54}{km^{2}.s^{-2}} at a separation of \SI{211}{pc}.
+The seeing (RMS) is \SI{2.1}{pc} (\(s_0\)=\SI{0.2}{\arcsecond}) and there are no points below this value.
+Considering the first point to be valid, which corresponds to \SI{2.5}{km^{2}.s^{-2}} at \(r = \SI{1.05}{pc} \) the slope for \(\sigma\pos^2\) and \(2\sigma\pos^2\) we obtain \num{1.27} and \num{1.18}, respectively, while our derived value is \num{1.38}.
 
 In the Figure~\ref{fig:strucfunc-fit-ExtraGal}d we show the structure function of NGC 604.
-%The seeing is \SI{1.7}{pc} (\(s_0\)=\SI{0.42}{\arcsecond}) and the structure function of this region lies below the true model for most of the separation range.
-%The correlation length is \SI{10}{pc} at a \(\sigma^2\pos\) of \SI{71}{km^{2}.s^{-2}} and has an index of \num{1}.
-The structure function present clear characteristics of periodic oscillations at large scales.
-A periodic pattern for the structure function appears with a maximum \(B(r)\) value of \SI{143}{km^{2}.s^{-2}} that is reached at \SI{60}{pc}, then the oscillation cause a minimum of \SI{54}{km^{2}.s^{-2}} at \SI{133}{pc} and finally it goes back up again at \SI{211}{pc} to a \(B(r)\) value of \SI{123}{km^{2}.s^{-2}}.
+The value of the observed \(\sigma\pos^2 = \SI{55}{km^{2}.s^{-2}}\) is obtained at \(r_0 = \SI{10}{pc} \) (while the derived values from our model are \(\sigma\pos^2 = \SI{86}{km^{2}.s^{-2}}\) and \(r_0 = \SI{12}{pc} \)).
+The observed value of \(2\sigma\pos^2\) corresponds to \(r = \SI{30}{pc} \).
+The maximum \(B(r)\) value is \SI{143}{km^{2}.s^{-2}} at a separation of \SI{55}{pc}. 
+NGC 604 structure function presents clear pattern of periodic oscillations between  \(\SI{30}{pc} < r < \SI{211}{pc} \).
+The spatial wavelength is \SI{ \sim 50}{pc}. 
+The minimum value of this periodic pattern is \SI{54}{km^{2}.s^{-2}} at \SI{135}{pc} 
+and finally it goes back up again at \SI{211}{pc} to a \(B(r)\) value of \SI{123}{km^{2}.s^{-2}}.
+The seeing is \SI{2.1}{pc} (\(s_0\)=\SI{1.2}{\arcsecond}) and the first three points structure function are below these value, which means that the seeing is heavily affecting this observations.
+This also is shown by the big difference bee tween the 'true model' (green dahed line) and our 'model' (solid orange lines).
+onsidering the first point above this \(s_0\) value to be valid, which corresponds to \SI{10}{km^{2}.s^{-2}} at \(r = \SI{3}{pc} \) the slope for \(\sigma\pos^2\) and \(2\sigma\pos^2\) we obtain \num{1.40} and \num{1.03}, respectively, while our derived value is \num{1.2}.
 

### 2022-12-09 strucfunc_paper.tex
Javier changes 2022-12-08

@@
 
-\usepackage{upgreek}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-\newcommand\ha{\ensuremath{\text{H}\upalpha}}
-\newcommand\hb{\ensuremath{\text{H}\upbeta}}
+\newcommand\ha{\ensuremath{\text{H}\alpha}}
 \newcommand\Wav[1]{\ensuremath{\lambda #1}}
@@
 \newcommand\FNa{\textsuperscript{a}}
-\newcommand\Mach{\ensuremath{\mathcal{M}}}
 
@@
 A number of fifteen interferograms have been taken with different pointing directions of the telescope's optical axis in the nebula with an exposure time between 10 and 40 minutes. 
-The exposures are overlapped and fall into one square of a grid with a width of \SI{1}{arcmin} centered at \(\uptheta^{1}\)Ori C.
+The exposures are overlapped and fall into one square of a grid with a width of \SI{1}{arcmin} centered at \(\theta^{1}\)Ori C.
 
@@
 and up to \(m\DDD = 1\) in the supersonic regime.
-Comparison with our measurements is complicated by projection smoothing
-\citep{1984ApJ...277..556S},
-which implies that \(m\DDD\) is only
+Comparison with our measurements is complicated by projection smoothing,
+which mean that \(m\DDD\) is only
 observed directly for separations larger than the line-of-sight depth
@@
 \(m = m\DDD + 1 + \delta\kappa\),
-where \(\delta\kappa\) represents the effects of emissivity fluctuations\footnote{%
-  Note that literature on turbulence in molecular clouds discuss fluctuations of \emph{density}
-  since they are mainly concerned with emission lines
-  whose emissivity is approximately linearly proportional to density.
-  In the case of photoionized regions, the emissivity of important lines such as \ha{}
-  is proportional to \emph{density-squared},
-  so in adopting the results of \citet{Brunt:2004a} we substitute emission measure
-  (or its proxy, \ha{} surface brightness)
-  in place of column density. 
-}
+where \(\delta\kappa\) represents the effects of emissivity fluctuations
 along the line of sight \citep{Brunt:2004a},
@@
 to \(\delta\kappa = -1\) in the case of strongly driven supersonic turbulence.
-In this latter case, the effects of projection smoothing and emissivity fluctuations
-cancel out, leading once more to \(m \approx m\DDD\).
-
-The \hii{} regions of our sample span the transonic regime,
-from subsonic velocity fluctuations in the Galactic sources
-to supersonic fluctuations in the more luminous extragalactic sources. 
+
 It is therefore not surprising that we see no significant correlation
@@
 
-Evidence for just such an increase is shown in Figure~\ref{fig:brightness-pdfs}g,
-which shows how the fractional width of the probability distribution of
-large-scale \ha{} surface brightness fluctuations
-varies with the RMS turbulent Mach number, \Mach{},
-of the three-dimensional velocity fluctuations.
-The Mach number is estimated by assuming that the plane-of-sky velocity dispersion is
-a good estimate of the turbulent fluctuations in one dimension
-and that the turbulence is isotropic, yielding:
-\(\Mach = \sqrt{3} \sigma\pos / \csound\),
-where an ionized sound speed of \(\csound = \SI{11}{km.s^{-1}}\)
-is assumed for all sources.
-\newcommand\longsig[1]{\ensuremath{\langle \delta #1^2 \rangle^{1/2} / #1_0}}
-\newcommand\shortsig[1]{\ensuremath{\sigma_{#1/#1_0}}}
-The RMS fractional width of density fluctuations in a turbulent medium,
-\(\shortsig{\rho} \equiv \longsig{\rho}\),
-is predicted to depend linearly on the Mach number as
-\(\shortsig{\rho} = b \Mach\),
-where \(b\) depends on the nature of the turbulent driving \citep{Federrath:2010z},
-varying between \(b = 1/3\) for solenoidal driving and \(b = 1\) for compressive driving.
-This is shown by gray shading\footnote{%
-  In the figure, it is assumed that the relative fluctuations in surface brightness
-  and density are equal, which is a result of the
-  cancellation between two effects. First, that the volumetric \ha{} emissivity \(E\)
-  is proportional to density squared, so that \(\shortsig{E} = 2 \shortsig{\rho}\). 
-  Second, that fluctuations in surface brightness \(S\) are related to those in emissivity
-  by \(\shortsig{S} = R^{1/2} \shortsig{E}\), where \(R\)
-  is the 2D-to-3D variance ratio \citep{Brunt:2010b}.
-  For an emissivity power spectrum \(P(k) \sim k^{-3}\)
-  and assuming a ratio of map size to correlation length
-  of \(L / r_0 = 10\) (typical value from Table~\ref{tab:Res}),
-  we find \(R \approx 0.2\) and hence \(\shortsig{S} \approx \shortsig{\rho}\). 
-}
-in Figure~\ref{fig:brightness-pdfs}h,
-where it can be seen that many of the sources with subsonic velocity dispersions
-(\(\Mach < 1\)) fall to the right of the theoretical prediction,
-implying that other factors in addition to turbulence are responsible for
-producing the fluctuations in density and surface brightness in these regions
-(see also section 4.5 of \citealp{arthur2016turbulence}).
-For our highest luminosity source of 30~Dor on the other hand,
-the velocity dispersion is clearly supersonic (\(\Mach \approx 2.7\))
-and, although the surface brightness fluctuations are also larger than in the other sources,
-they are consistent with being caused by turbulence-induced density fluctuations.
-
-We find no clear evidence for a broken power-law in any of our
-structure functions, as has been claimed in previous studies.
+In figure
+
+We also find no clear evidence for a broken power-law in any of our
+structure functions, as has been suggested in previous studies.
 Although in some regions we do observe a steepening at the smallest scales
@@
 
-% Theoretically, one might expect a positive correlation of the slope with the
-% amplitude of the velocity fluctuations, due to the transition from subsonic
-% to supersonic turbulence \citep{Galtier:2011a}.
-% However, the predicted change of slope is rather small,
-% \(\delta m \approx 0.2\)
-% \citep{Federrath:2021r},
-% and only one of our sources (30~Dor) is clearly in the supersonic regime,
-% so it is perhaps not surprising that we do not find a significant correlation
-% (\(p = 0.33\), Table~\ref{tab:RestStats}).
-% This is further complicated by the effect of projection along the line of sight
+Theoretically, one might expect a positive correlation of the slope with the
+amplitude of the velocity fluctuations, due to the transition from subsonic
+to supersonic turbulence \citep{Galtier:2011a}.
+However, the predicted change of slope is rather small,
+\(\delta m \approx 0.2\)
+\citep{Federrath:2021r},
+and only one of our sources (30~Dor) is clearly in the supersonic regime,
+so it is perhaps not surprising that we do not find a significant correlation
+(\(p = 0.33\), Table~\ref{tab:RestStats}).
+This is further complicated by the effect of projection along the line of sight
+
+Theoretically, one might expect
 
@@
   smaller than the correlation length,
-  surface brightness maps were rebinned by averaging
+  Surface brightness maps were rebinned by averaging
   into pixels of size \(0.5 r_0\) before calculating the PDF.
-  Also shown are the RMS Mach number of three-dimensional
-  velocity fluctuations (panel~h)
-  and the ratio of plane-of-sky to line-of-sight velocity dispersions (panel~i),
-  each plotted as a function of the
+  In panel~h is plotted for each source of the previous panels
+  the ratio of velocity dispersions
+  (see Figure~\ref{fig:los-vs-pos})
+  as a function of the
   RMS fractional brightness fluctuations calculated from the PDFs.
@@
 
-The relationship \(\text{L}_{\ha} \propto \sigma^{\alpha}\) has been extensively investigated  in the context of giants \hii{} regions obtaining a value for \(\alpha\) of \( \sim 4\)\citep{terlevich1981,1988A&A...201..199A} and \num{2.87 \pm 0.2} \citep{Rozas:2006b}.
+The relationship \(\text{L}_{\text{H}} \propto \sigma^{\alpha}\) has been extensively investigated  in the context of giants \hii{} regions obtaining a value for \(\alpha\) of \( \sim 4\)\citep{terlevich1981,1988A&A...201..199A} and \num{2.87 \pm 0.2} \citep{Rozas:2006b}.
 Complementing previous results \citet{2012MNRAS.422.3339W} found that star-forming regions at \(z \sim 1.3\) and local \hii{} regions follow a relation with \(\alpha = 4.18 \pm 0.21\).
 \citet{Moiseev:2015a} found that this relation also holds for dwarf galaxies with a value of \(\alpha \sim 5\).
-\citet{2018MNRAS.474.1250F} presented the relationship between integrated \hb{} line luminosity for new data of 36 giant \hii{} regions obtaining \(\text{L}_{\hb} \propto \sigma^{5.02 \pm 0.21}\).
+\citet{2018MNRAS.474.1250F} presented the relationship between integrated H$_{\beta}$ line luminosity for new data of 36 giant \hii{} regions obtaining \(\text{L}_{\text{H}_{\beta}} \propto \sigma^{5.02 \pm 0.21}\).
 Recently, \citet{2020ApJ...888..113W} studied the properties of high-\(z\) and local \hii{} galaxies among some GEHRs finding a value of \(\alpha \sim 5\).
@@
 The first problem is addressed in section \ref{sec:sigmapos-vs-sigmalos} where we discuss the relation between the line-of-sight and plane-of-sky velocities.
-But despite these problems, the fact that this relationship holds in our results (within the errors) is interesting considering that the \(\sigma\pos\) is derived from the structure function, while the \(\text{L}(\ha)\) values comes from different sources unrelated to our data (see the Appendix~\ref{sec:notes-individual-hii}).
+But despite these problems, the fact that this relationship holds in our results (within the errors) is interesting considering that the \(\sigma\pos\) is derived from the structure function, while the \(\text{L}(\text{H}_{\alpha})\) values comes from different sources unrelated to our data (see the Appendix~\ref{sec:notes-individual-hii}).
 This means that the proposed structure function model describes within certain accuracy the velocity field fluctuations and that the parameters obtained can be interpreted as a true kinematic property of the \hii{} region velocity field.
@@
 The Orion Nebula (M42) is the prototype of a galactic \hii{} region located at a distance of 440 pc \citetext{\SI{1}{\arcsecond} = \SI{0.002}{pc} ; \citealp{2008AJ....136.1566O}}.
-The O7 V star \(\uptheta^{1}\) Ori C is the most luminous and hottest star with an ionizing flux \(Q_0\) of \SI{e49.12}{photons.s^{-1}} \citep{2006A&A...448..351S} which translates to luminosity in \ha{} of \SI{e37.18}{erg.s^{-1}}.
+The O7 V star \(\theta^{1}\) Ori C is the most luminous and hottest star with an ionizing flux \(Q_0\) of \SI{e49.12}{photons.s^{-1}} \citep{2006A&A...448..351S} which translates to luminosity in \ha{} of \SI{e37.18}{erg.s^{-1}}.
 With other 3 B-type stars they form the Trapezium cluster.

### 2022-12-12 strucfunc_paper.tex
Add a new appendix on the emissivity fluctuations

--- 2022-12-09 strucfunc_paper.tex
@@
 
-Evidence for just such an increase is shown in Figure~\ref{fig:brightness-pdfs}g,
+Evidence for just such an increase is shown in Figure~\ref{fig:brightness-pdfs},
 which shows how the fractional width of the probability distribution of
@@
 varying between \(b = 1/3\) for solenoidal driving and \(b = 1\) for compressive driving.
-This is shown by gray shading\footnote{%
+This is shown by gray shading\footnote{\label{fn:brightness-fluctuations}%
   In the figure, it is assumed that the relative fluctuations in surface brightness
@@
   we find \(R \approx 0.2\) and hence \(\shortsig{S} \approx \shortsig{\rho}\).
+  We calculate \shortsig{S} by fitting a log-normal
+  function to the probability distribution function
+  of the surface brightness map after filtering out fluctuations
+  on scales smaller than the velocity correlation length.
 }
@@
 between \(\sigma\pos\) and \(\sigma\los\) have been proposed previously.
-The classic interpretation in terms of homogeneous turbulence
+The classic interpretation 
+in terms of homogeneous incompressible turbulence \citep{von1951methode}
 is that \(\sigma\pos\) is reduced with respect to the ``true''
@@
 along the line of sight,
-a process known as \textit{projection smearing}
-\citep{von1951methode, 1984ApJ...277..556S}.
+which is another manifestation of projection smearing, 
+as discussed above in section \ref{sec:constancy-power-law}.
 Assuming that \(\sigma\los\) measures the true dispersion,
@@
 where \(H\) is the line-of-sight depth of the emitting gas
-and \(\LL \equiv \int_0^\infty C(r)\, dr\) is the integral length scale of
-the fluctuations \citep{Pope:2000p}.
+and \(\LL\) is the integral length scale of
+the fluctuations defined in section~\ref{sec:methods-apply},
 % los/pos = sqrt(N) where N = H / L is # of independent cells
@@
 % So H / r0 = 1.44 (los/pos)^2
-Using our model for the autocorrelation function from
-equation~\eqref{eq:new-correlation-form} and assuming \(m = 1\),
-one finds \(\LL = r_0 / \ln 2 \approx 1.44 r_0\),
-and thus \(H / r_0 \approx 1.44 (\sigma\los / \sigma\pos)^2\).
-From the results of Figure~\ref{fig:los-vs-pos} we therefore find
+which yields \(H / r_0 \approx 1.44 (\sigma\los / \sigma\pos)^2\).
+From the results of Figure~\ref{fig:los-vs-pos} we would therefore find
 \(H / r_0 \approx 6\) for the lower dispersion sources,
 falling to \(H / r_0 \approx 2\) for the higher dispersion sources.
+However, such an analysis ignores the effect of density fluctuations,
+which would tend to reduce the effectiveness of projection smoothing
+compared with the incompressible case (see discussion of \(\delta\kappa\) above),
+so it is unclear if the results remain valid
+for the sources with supersonic velocity dispersion.
 
@@
 % Constant v_exp : sig_los = sqrt(sig_pos**2 + v_exp**2)
-Assuming a constant value \vexp{} for the ordered contribution,
+Assuming a constant value \vexp{} for the ordered contribution
+and that projection smoothing is negligible,
 one would predict \(\sigma\los = (\sigma\pos^2 + \vexp^2)^{1/2}\),
@@
 ordered large-scale velocity gradients along the line of sight.
+Indeed, the neglect of any projection smoothing for the turbulent contribution
+in the \citeauthor{2011MNRAS.413..705L} analysis is equivalent to
+assuming \(\delta\kappa = -1\), which \emph{requires} substantial density fluctuations. 
 This leads to a third potential explanation of the
@@
 In the limit that the direct contribution of
-turbulent velocity fluctuations to \(\sigma\pos\) is negligible,
-the prediction is that \(\sigma\pos / \sigma\los \approx \sigma_{E/E_0}\)
-where \( \sigma_{E/E_0} = \langle \delta E^2 \rangle^{1/2} / E_0\) is the RMS fractional
+turbulent velocity fluctuations is negligible
+and that \(\sigma\los\) is entirely due to expansion along the line of sight,
+then the prediction is that \(\sigma\pos / \sigma\los \approx \shortsig{E} / (1 + \shortsig{E})\)
+where \( \shortsig{E} = \longsig{E}\) is the RMS fractional
 variation in emissivity \(\delta E\) (on scales \(\ge r_0\))
@@
 
+\section{Apparent velocity fluctuations from emissivity fluctuations}
+\label{sec:appar-veloc-fluct}
+
+\begin{figure}
+  \centering
+  \includegraphics[width=\linewidth]{Figures/bright-to-vel-fluct-annotated}
+  \caption{
+    Toy model of emissivity variations in an ordered velocity field,
+    showing co-variation in fractional fluctuations of
+    emissivity, \(\sigma_E\),  and surface brightness, \(\sigma_S\)
+    together with fluctuations in the plane of sky of the mean velocity,
+    \(\sigma\pos\),
+    and the mean RMS line width, \(\sigma\los\).
+  }
+  \label{fig:bright-to-vel-fluct}
+\end{figure}
+
+In this appendix we describe a simple toy model to illustrate
+how fluctuations of emissivity,
+combined with an ordered velocity gradient along the line of sight,
+can give rise to apparent fluctuations on the plane of the sky
+of the mean velocity.
+The model is illustrated in the inset of Figure~\ref{fig:bright-to-vel-fluct}.
+It consists of two overlapping emission layers, A and B,
+with velocities along the line of sight \(v_A = 0\) and \(v_B = \beta\), respectively,
+which are observed along two lines of sight (LOS), 1 and 2.
+The emissivity of layer A is \(E_{A1} = E_{A2} = 1\) for both LOS,
+while the emissivity of layer B is \(E_{B1} = \alpha\) for LOS~1
+and \(E_{B2} = \alpha^{-1}\) for LOS~2, where \(\alpha\) is a positive constant.
+Both layers are assumed to have unit depth along line line of sight,
+such that the surface brightness for the two LOS are given by
+\(S_1 = 1 + \alpha\) and \(S_2 = 1 + \alpha^{-1}\).
+
+It then follows that the fractional standard deviation of the emissivity
+and surface brightness are given by:
+\begin{align}
+  \label{eq:toy}
+  \sigma_E &=
+  \frac{
+    \biggl[ 3\bigl(\alpha + \alpha^{-1}\bigr)^2 - 4\bigl(1 + \alpha + \alpha^{-1}\bigr)\biggr]^{1/2}
+  }{
+    2 + \alpha + \alpha^{-1}
+  }
+  \\
+  \sigma_S &=   \frac{\vert\alpha - 1\vert}{1 + \alpha} ,
+\end{align}
+while the RMS line width and standard deviation of the mean velocities on the plane of the sky
+are given by
+\begin{align}
+  \label{eq:toy}
+  \sigma\pos &=\frac{\vert\alpha - 1\vert}{2 (1 + \alpha)}
+  \\
+  \sigma\los &=   \frac{\alpha^{1/2}}{1 + \alpha}.
+\end{align}
+
 \section{Additional covariance corner plots for model fits}

### 2022-12-12 strucfunc_paper.tex
Finish new appendix

--- 2022-12-12 strucfunc_paper.tex
@@
 
+\section{Apparent velocity fluctuations from emissivity fluctuations}
+\label{sec:appar-veloc-fluct}
+
+\begin{figure}
+  \centering
+  \includegraphics[width=\linewidth]{Figures/bright-to-vel-fluct-annotated}
+  \caption{
+    Toy model of emissivity variations in an ordered velocity field,
+    showing co-variation of fractional dispersion of
+    emissivity, \(\sigma_E\), and surface brightness, \(\sigma_S\),
+    together with plane-of-sky dispersion in mean velocity,
+    \(\sigma\pos\),
+    and the mean RMS line width, \(\sigma\los\),
+    both in units of the inter-layer velocity difference \(\beta\).
+  }
+  \label{fig:bright-to-vel-fluct}
+\end{figure}
+
+In this appendix we describe a simple toy model to illustrate
+how fluctuations of emissivity,
+combined with an ordered velocity gradient along the line of sight,
+can give rise to apparent fluctuations on the plane of the sky
+of the mean velocity.
+The model is illustrated in the inset of Figure~\ref{fig:bright-to-vel-fluct}.
+It consists of two overlapping emission layers, A and B,
+with velocities along the line of sight \(v_A = 0\) and \(v_B = \beta\), respectively,
+which are observed along two lines of sight (LOS), 1 and 2.
+The emissivity of layer A is \(E_{A1} = E_{A2} = 1\) for both LOS,
+while the emissivity of layer B is \(E_{B1} = \alpha\) for LOS~1
+and \(E_{B2} = \alpha^{-1}\) for LOS~2, where \(\alpha\) is a positive constant.
+Both layers are assumed to have unit depth along line line of sight,
+such that the surface brightness for the two LOS are given by
+\(S_1 = 1 + \alpha\) and \(S_2 = 1 + \alpha^{-1}\).
+
+It then follows that the fractional standard deviation of the emissivity
+and surface brightness are given by:
+\begin{align}
+  \label{eq:toy}
+  \sigma_E &=
+  \frac{
+    \bigl[ 3\bigl(\alpha + \alpha^{-1}\bigr)^2 - 4\bigl(1 + \alpha + \alpha^{-1}\bigr)\bigr]^{1/2}
+  }{
+    2 + \alpha + \alpha^{-1}
+  }
+  \\
+  \sigma_S &=   \frac{\vert\alpha - 1\vert}{1 + \alpha} ,
+\end{align}
+while the RMS line width and standard deviation of the mean velocities on the plane of the sky
+are given by
+\begin{align}
+  \label{eq:toy}
+  \sigma\pos &=\frac{\vert\alpha - 1\vert \beta}{2 (1 + \alpha)}
+  \\
+  \sigma\los &=   \frac{\alpha^{1/2}\beta}{1 + \alpha}.
+\end{align}
+These are all shown in Figure~\ref{fig:bright-to-vel-fluct} as a function
+of the emissivity contrast \(\alpha\).
+It can be seen that \(\sigma_E\), \(\sigma_S\), and \(\sigma\pos/\beta\) all increase with \(\alpha\),
+reaching asymptotic values of \(\sqrt{3}\), \(1\), and \(0.5\),
+respectively as \(\alpha \to \infty\).\footnote{%
+  To reach higher relative brightness dispersion \(\sigma_S > 1\) would require
+  including more than two lines of sight in the model.
+}
+The line width \(\sigma\los/\beta\) behaves in the opposite sense, falling from
+a maximum value of \(0.5\) when \(\alpha = 0\) towards zero as \(\alpha \to \infty\),
+a result of the emission becoming increasingly dominated by one
+or the other of the two layers for high emissivity contrast.
+The dashed line shows the effect of including a small velocity gradient
+within each layer that contributes an additional width of \(\beta/4\),
+which is assumed to add in quadrature with \(\sigma\los\).
+
+The predictions of this model are compared with observations in
+panel~i of Figure~\ref{fig:brightness-pdfs}.
+
 \section{\boldmath Notes on individual \hii{} regions}
@@
 
-\section{Apparent velocity fluctuations from emissivity fluctuations}
-\label{sec:appar-veloc-fluct}
-
-\begin{figure}
-  \centering
-  \includegraphics[width=\linewidth]{Figures/bright-to-vel-fluct-annotated}
-  \caption{
-    Toy model of emissivity variations in an ordered velocity field,
-    showing co-variation in fractional fluctuations of
-    emissivity, \(\sigma_E\),  and surface brightness, \(\sigma_S\)
-    together with fluctuations in the plane of sky of the mean velocity,
-    \(\sigma\pos\),
-    and the mean RMS line width, \(\sigma\los\).
-  }
-  \label{fig:bright-to-vel-fluct}
-\end{figure}
-
-In this appendix we describe a simple toy model to illustrate
-how fluctuations of emissivity,
-combined with an ordered velocity gradient along the line of sight,
-can give rise to apparent fluctuations on the plane of the sky
-of the mean velocity.
-The model is illustrated in the inset of Figure~\ref{fig:bright-to-vel-fluct}.
-It consists of two overlapping emission layers, A and B,
-with velocities along the line of sight \(v_A = 0\) and \(v_B = \beta\), respectively,
-which are observed along two lines of sight (LOS), 1 and 2.
-The emissivity of layer A is \(E_{A1} = E_{A2} = 1\) for both LOS,
-while the emissivity of layer B is \(E_{B1} = \alpha\) for LOS~1
-and \(E_{B2} = \alpha^{-1}\) for LOS~2, where \(\alpha\) is a positive constant.
-Both layers are assumed to have unit depth along line line of sight,
-such that the surface brightness for the two LOS are given by
-\(S_1 = 1 + \alpha\) and \(S_2 = 1 + \alpha^{-1}\).
-
-It then follows that the fractional standard deviation of the emissivity
-and surface brightness are given by:
-\begin{align}
-  \label{eq:toy}
-  \sigma_E &=
-  \frac{
-    \biggl[ 3\bigl(\alpha + \alpha^{-1}\bigr)^2 - 4\bigl(1 + \alpha + \alpha^{-1}\bigr)\biggr]^{1/2}
-  }{
-    2 + \alpha + \alpha^{-1}
-  }
-  \\
-  \sigma_S &=   \frac{\vert\alpha - 1\vert}{1 + \alpha} ,
-\end{align}
-while the RMS line width and standard deviation of the mean velocities on the plane of the sky
-are given by
-\begin{align}
-  \label{eq:toy}
-  \sigma\pos &=\frac{\vert\alpha - 1\vert}{2 (1 + \alpha)}
-  \\
-  \sigma\los &=   \frac{\alpha^{1/2}}{1 + \alpha}.
-\end{align}
-
 \section{Additional covariance corner plots for model fits}

### 2022-12-12 strucfunc_paper.tex
Finish section 5.2.3

@@
 
+\begin{figure}
+\centering 
+\includegraphics[width=\linewidth]{Figures/bright-hist-multi}
+\caption{
+  Panels a--g show histograms (blue) of the probability density function (PDF)
+  of the \ha{} surface brightness of \hii{} regions in our sample.
+  Smooth lines (orange) show fitted log-normal distributions.
+  In order to suppress fluctuations on scales
+  smaller than the correlation length,
+  surface brightness maps were rebinned by averaging
+  into pixels of size \(0.5 r_0\) before calculating the PDF.
+  Also shown are the RMS Mach number of three-dimensional
+  velocity fluctuations (panel~h)
+  and the ratio of plane-of-sky to line-of-sight velocity dispersions (panel~i),
+  each plotted as a function of the
+  RMS fractional brightness fluctuations calculated from the PDFs.
+}
+\label{fig:brightness-pdfs}
+\end{figure}
+
 \subsubsection{Plane-of-sky vs line-of-sight
@@
 using different types of samples.
-
 \citet{2011MNRAS.413..705L} surveyed
@@
 \(\SI{8}{km.s^{-1}}\).
-
 \citet{arthur2016turbulence} calculate the relationship
@@
 turbulent velocity fluctuations is negligible
-and that \(\sigma\los\) is entirely due to expansion along the line of sight,
-then the prediction is that \(\sigma\pos / \sigma\los \approx \shortsig{E} / (1 + \shortsig{E})\)
-where \( \shortsig{E} = \longsig{E}\) is the RMS fractional
-variation in emissivity \(\delta E\) (on scales \(\ge r_0\))
-with respect to the mean emissivity \(E_0\).
-
-\begin{figure}
-\centering 
-\includegraphics[width=\linewidth]{Figures/bright-hist-multi}
-\caption{
-  Panels a--g show histograms (blue) of the probability density function (PDF)
-  of the \ha{} surface brightness of \hii{} regions in our sample.
-  Smooth lines (orange) show fitted log-normal distributions.
-  In order to suppress fluctuations on scales
-  smaller than the correlation length,
-  surface brightness maps were rebinned by averaging
-  into pixels of size \(0.5 r_0\) before calculating the PDF.
-  Also shown are the RMS Mach number of three-dimensional
-  velocity fluctuations (panel~h)
-  and the ratio of plane-of-sky to line-of-sight velocity dispersions (panel~i),
-  each plotted as a function of the
-  RMS fractional brightness fluctuations calculated from the PDFs.
-}
-\label{fig:brightness-pdfs}
-\end{figure}
-
-In order to disentangle the relative importance
-of these three mechanisms, it is necessary to consider
-additional factors.
-For instance, in Figure~\ref{fig:brightness-pdfs} we test
-the plausibility of the third explanation given above
-by comparing the ratio  \(\sigma\pos / \sigma\los \)
-with the RMS fractional variation in
-\ha{} surface brightness,
-\( \sigma_{S/S_0} = \langle \delta S^2 \rangle^{1/2} / S_0\).
-We calculate the latter from fitting a log-normal
-function to the probability distribution function
-of the surface brightness map after filtering out fluctuations
-on scales smaller than the velocity correlation length.
-The volumetric emissivity fluctuations are predicted to be
-proportional to the brightness fluctuations \citep{arthur2016turbulence}:
-\(\sigma_{E/E_0} = \sigma_{S/S_0} / R^{1/2}\) where \(R\)
-is the 2D-to-3D variance ratio \citep{Brunt:2010b}.
-For an emissivity power spectrum \(P(k) \sim k^{-3}\)
-and assuming a ratio of map size to correlation length
-of \(L / r_0 = 10\) (typical value from Table~\ref{tab:Res}),
-we find \(R \approx 0.2\) and hence \(\sigma_{E/E_0} \approx 2 \sigma_{S/S_0}\).
-% For P(k) ~ k^-3 we have R = 0.5 (1 - 1/x) / ln(x)
-% where x = L / r0 if we have suppressed variations on scales < r0
-% So with x = 10 (typical value) we have R = 0.2
-% For k = 4 we have R = 0.25 (1 - 1/x^2) / (1 - 1/x) = 0.275
-% For k = 2 we have R = 0.5 ln(x) / x = 0.115
-% 
-From panel 
-we require high quality measurements
-of a much larger sample of \hii{} regions
-than have so far been obtained.
-In the meantime
-is most important
+and that \(\sigma\los\) is entirely due to ordered expansion along the line of sight,
+then a non-zero \(\sigma\pos\) can arise only from emissivity fluctuations,
+which cause different parts of the ordered velocity field to be picked out
+for different lines of sight.
+A simple model of this process is explored in Appendix~\ref{sec:appar-veloc-fluct},
+where a relation between the surface brightness dispersion and the apparent
+velocity dispersions is derived.
+This is compared with the behavior of the ratio
+\(\sigma\pos / \sigma\los\) for
+our observed sample in panel~i of Figure~\ref{fig:brightness-pdfs},
+in which the solid and dashed lines show results for different assumptions
+about the effects of velocity gradients on \(\sigma\los\).
+Although the model does qualitatively reproduce the increase
+in \(\sigma\pos / \sigma\los\) with increasing \(\sigma_S\), the quantitative agreement
+is poor, with the model substantially overestimating the magnitude of
+plane-of-sky fluctuations as compared with the line-of-sight widths.
+This is evidence that the combination of a velocity gradient with
+emissivity fluctuations is insufficient on its own,
+and there must therefore be an additional disordered velocity component
+in order to explain our observations.
+
+In summary, our results are most consistent with a combination
+of expansion and disordered motions, in which the disordered component
+becomes increasingly dominant for the sources with higher velocity dispersion.
+We cannot rule out a role for either projection smoothing or emissivity fluctuations,
+but the contribution is probably minor in both cases.
 

### 2022-12-12 strucfunc_paper.tex
Finish section 5.2.4

@@
 
-The Fig. \ref{fig:sigvsl} shows the log \(\sigma\pos\)-log \(\text{L}(\text{H}_{\alpha})\) plane.
-This relation is commonly employ in the literature  and can be use to investigate how reliable is our derived velocity dispersion.
-The fit we obtain is \(\log \sigma\pos = (0.27 \pm 0.10) \log \text{L}(\text{H}_{\alpha})-(9.9 \pm 4.0)\).
-Since it is customary in the literature to present \(\text{L} (\text{H}_{\alpha})\) as the dependent variable we also calculate this relation: taking the inverse of slope in Fig.
+Figure~\ref{fig:sigvsl} shows the observed relation between \ha{} luminosity
+and plane-of-sky dispersion of velocity centroids for our sample,
+for which we obtain the power-law fit
+\(\log \sigma\pos = (0.25 \pm 0.10) \log L(\ha) - (9.9 \pm 4.0)\). 
+It is common to study the \(L\)--\(\sigma\) relationship,
+not only in individual \hii{} regions, but also in \hii{} galaxies,
+both in the local universe and at high redshift
+\citep{terlevich1981, Chavez:2014a}.
+In such studies, the velocity dispersion is invariably derived from the
+line widths (\(\sigma\los\)) since the spatially resolved observations
+necessary for measuring \(\sigma\pos\) are not available.
+A reliable empirical \(L\)--\(\sigma\) relationship allows the use of bright photoionized
+regions as standard candles in order to constrain cosmological parameters
+\citep{Chavez:2012a, 2020ApJ...888..113W, Gonzalez-Moran:2021d}.
+The luminosities of the regions used in these cosmological studies range from
+that of our own brightest source up to 100 times more luminous
+(\(L(\ha) = \num{e40}\) to \SI{e42}{erg.s^{-1}}),
+although other studies cover intermediate luminosity regions
+that bridge the two ranges \citep{moiseev2012, Yu:2019a}.
+
+Expressed in the customary form \(L \sim  \sigma^\alpha\), our result corresponds to
+\(\alpha = 4.0 \pm 1.6\), which is smaller than the value of \(\alpha \approx 5\) that is typically found
+for more luminous regions
+\citep{Moiseev:2015a, 2020ApJ...888..113W}
+but not significantly so, given the uncertainty.
+Studies that rely on \(\sigma\los\) generally find that
+\(\sigma\) becomes insensitive to luminosity below about \(L(\ha) = \SI{e40}{erg.s^{-1}}\),
+reaching a constant value of \(\sigma = \SI{15}{km.s^{-1}}\) \citep{Moiseev:2015a, Yu:2019a}.
+On the other hand,
+by using \(\sigma\pos\) instead of \(\sigma\los\),
+we succeed in extending the same power-law relation
+down to \(L(\ha) = \SI{2e37}{erg.s^{-1}}\) and \(\sigma = \SI{3}{km.s^{-1}}\).
+Given our analysis of the previous section, one possible explanation for this
+is that \(\sigma\pos\) is a better measure of the disordered turbulent motions within
+the \hii{} regions, whereas \(\sigma\los\) is also affected by large-scale ordered motions,
+which are always at least as large as the ionized sound speed.
+
+% The Fig. \ref{fig:sigvsl} shows the log \(\sigma\pos\)-log \(\text{L}(\text{H}_{\alpha})\) plane.
+% This relation is commonly employ in the literature  and can be use to investigate how reliable is our derived velocity dispersion.
+% The fit we obtain is \(\log \sigma\pos = (0.27 \pm 0.10) \log \text{L}(\text{H}_{\alpha})-(9.9 \pm 4.0)\).
+% Since it is customary in the literature to present \(\text{L} (\text{H}_{\alpha})\) as the dependent variable we also calculate this relation: taking the inverse of slope in Fig.
 \ref{fig:sigvsl} we have \(\text{L}_{\text{H}_{\alpha}} \propto \sigma^{3.6 \pm 1.4}\) and using the same procedure in \textit{linmix} and changing the variables we obtain \(\log \text{L}(\text{H}_{\alpha}) = (2.8\pm 1.0) \log \sigma\pos -(36 \pm 4)\).
 
-The relationship \(\text{L}_{\ha} \propto \sigma^{\alpha}\) has been extensively investigated  in the context of giants \hii{} regions obtaining a value for \(\alpha\) of \( \sim 4\)\citep{terlevich1981,1988A&A...201..199A} and \num{2.87 \pm 0.2} \citep{Rozas:2006b}.
-Complementing previous results \citet{2012MNRAS.422.3339W} found that star-forming regions at \(z \sim 1.3\) and local \hii{} regions follow a relation with \(\alpha = 4.18 \pm 0.21\).
-\citet{Moiseev:2015a} found that this relation also holds for dwarf galaxies with a value of \(\alpha \sim 5\).
-\citet{2018MNRAS.474.1250F} presented the relationship between integrated \hb{} line luminosity for new data of 36 giant \hii{} regions obtaining \(\text{L}_{\hb} \propto \sigma^{5.02 \pm 0.21}\).
-Recently, \citet{2020ApJ...888..113W} studied the properties of high-\(z\) and local \hii{} galaxies among some GEHRs finding a value of \(\alpha \sim 5\).
-
-There are two main difference between the previous investigations and our results: one is that the velocity dispersion is obtained as the width of the emission line profile integrated over the whole object or as the non-thermal line-width, which is different from the plane of the sky dispersion we are using and that our sample is considerably smaller in the data points.
-The first problem is addressed in section \ref{sec:sigmapos-vs-sigmalos} where we discuss the relation between the line-of-sight and plane-of-sky velocities.
-But despite these problems, the fact that this relationship holds in our results (within the errors) is interesting considering that the \(\sigma\pos\) is derived from the structure function, while the \(\text{L}(\ha)\) values comes from different sources unrelated to our data (see the Appendix~\ref{sec:notes-individual-hii}).
-This means that the proposed structure function model describes within certain accuracy the velocity field fluctuations and that the parameters obtained can be interpreted as a true kinematic property of the \hii{} region velocity field.
-
-\subsubsection{Diameter vs centroid velocity dispersion}
-
-Other important relationship commonly used in the study of the interstellar medium is the diameter (or size) versus velocity dispersion.
-Table \ref{tab:RestStats} shows this result for our sample in the forth row. 
-This relation presents a significance level \(p > \num{0.05}\) but there are a couple of things worth mentioning.
-Historically this relation is important following the work of \citet{1981MNRAS.194..809L} where he presents it in the context of molecular cloud complexes of many clouds, individual clouds, and clumps, so that size scales are studied over \(\num{0.1} < L < \SI{100}{pc}\) obtaining \(\sigma = 1.10 L ^{0.38}\).
-
-This relation is interpreted in terms of turbulence, particularly the Kolmogorov model which predicts a index of \num{0.33} so that larger regions presents more turbulence, and smaller regions less turbulence.
-It has been argued that this correlation method is not as powerful as using statistical functions \citep{1984ApJ...277..556S} but it is interesting that the index is consistent within different phases of the interstellar medium.
-We obtain \(\log \sigma\pos = (0.25 \pm 0.17) \log D - (0.2 \pm 0.38)\) which is comparable with \citet{1981MNRAS.194..809L} results.
-
-As we mentioned in section \ref{sec:L-vs-sigmapos} the fact that this relation holds up to previous investigation gives some certainty that the \(\sigma\pos\) value obtained via the proposed model of the structure function is valid.
-This implying that the structure function, while not an absolute diagnostic, is a powerful tool in the research of \hii{} regions kinematics.
-
-\subsection{Power-law index}\label{power-law-index}
-
-The power-law index \(m\) shown in the last column of Table \ref{tab:Res} is used for comparison between the observations derived index and the theoretical Kolmogorov value of 0.67.
-All our indices are above this theoretical value and this is attributed to the fact that the \hii{} regions do not comply with the conditions established in the development of the turbulent theory which assumes incompressible, subsonic and homogeneous three-dimensional flow.
-\hii{} regions emerged from a molecular cloud with highly filamentary and clumpy density structure.
-Inside the region there is a large increase in the temperature because of the photoionization, and the density gradients with the pressure gradients accelerate the flow which occurs on multiple scales consequence of the fractal nature of the molecular cloud \citep{arthur2016turbulence}.
-The radiation pressure, stellar winds and region expansion, among other physical processes would create pressure-driven shock waves propagating faster than the speed of sound in the medium.
-This would make the flow compressible and supersonic in an inhomogeneous gas cloud.
-Also, as \hii{} regions are three-dimensional objects our structure function results comes from a projection of this three-dimensional structure to a two-dimensional velocity field.
-But despite the complex nature of \hii{} regions and observational limitations, we obtain a common pattern for the structure function behaviour and the value of the power-law index falls in a certain limited range between \num{0.7} and \num{1.4}.
-
-The differences in the power-law index with respect the theoretical value are often used as a diagnostic tools to identify properties that are not consider in the assumptions of the turbulence theory \citetext{See table~1 of \citealp{arthur2016turbulence} and Sec.~1 of \citealp{lagrois2011}}.
-As an example there the so called \textit{projection smoothing} \citep{von1951methode,1987ApJ...317..686O} which is used to study the projection of a three-dimensional structure function on the plane.
-The relationships for the power-law are:
-
-\begin{equation}\label{eq:projection-smoothing-3d}
-m_{2D}= m_{3D} + 1
-\end{equation}
-%
-and  when the astronomical object present a sheet-like distribution of emitters we have the relation:
-%
-\begin{equation}\label{eq:projection-smoothing-2d}
-m_{2D} \sim m_{3D}
-\end{equation}
-
-As a conclusion, if the extension of the \hii{} region is compared with its depth (three-dimensional case) the value of the index is \num{1.6}. 
-While the case where the extension is much greater than its depth (two-dimensional case) the region will have a value of \num{0.6}.
-From Table~\ref{tab:Res} we see that our results fall between these two previous values.
-
-As for any relation of the power-law index \(m\) and the physical properties of the \hii{} regions we can see from table \ref{tab:RestStats} that this parameter does not correlate with any other parameter or physical property, being the least reliable for determining or concluding something about the nature of the physical processes inside the regions.
-On the other hand, the lack of correlation and the presence of this power-law index describing the assumed energy cascade may be interpreted as a universal property of the velocity fluctuations independent of the observed object, which is the main consideration in the turbulence theory.
+% The relationship \(\text{L}_{\ha} \propto \sigma^{\alpha}\) has been extensively investigated  in the context of giants \hii{} regions obtaining a value for \(\alpha\) of \( \sim 4\)\citep{terlevich1981,1988A&A...201..199A} and \num{2.87 \pm 0.2} \citep{Rozas:2006b}.
+% Complementing previous results \citet{2012MNRAS.422.3339W} found that star-forming regions at \(z \sim 1.3\) and local \hii{} regions follow a relation with \(\alpha = 4.18 \pm 0.21\).
+% \citet{Moiseev:2015a} found that this relation also holds for dwarf galaxies with a value of \(\alpha \sim 5\).
+% \citet{2018MNRAS.474.1250F} presented the relationship between integrated \hb{} line luminosity for new data of 36 giant \hii{} regions obtaining \(\text{L}_{\hb} \propto \sigma^{5.02 \pm 0.21}\).
+% Recently, \citet{2020ApJ...888..113W} studied the properties of high-\(z\) and local \hii{} galaxies among some GEHRs finding a value of \(\alpha \sim 5\).
+
+% There are two main difference between the previous investigations and our results: one is that the velocity dispersion is obtained as the width of the emission line profile integrated over the whole object or as the non-thermal line-width, which is different from the plane of the sky dispersion we are using and that our sample is considerably smaller in the data points.
+% The first problem is addressed in section \ref{sec:sigmapos-vs-sigmalos} where we discuss the relation between the line-of-sight and plane-of-sky velocities.
+% But despite these problems, the fact that this relationship holds in our results (within the errors) is interesting considering that the \(\sigma\pos\) is derived from the structure function, while the \(\text{L}(\ha)\) values comes from different sources unrelated to our data (see the Appendix~\ref{sec:notes-individual-hii}).
+% This means that the proposed structure function model describes within certain accuracy the velocity field fluctuations and that the parameters obtained can be interpreted as a true kinematic property of the \hii{} region velocity field.
+
+% \subsubsection{Diameter vs centroid velocity dispersion}
+
+% Other important relationship commonly used in the study of the interstellar medium is the diameter (or size) versus velocity dispersion.
+% Table \ref{tab:RestStats} shows this result for our sample in the forth row. 
+% This relation presents a significance level \(p > \num{0.05}\) but there are a couple of things worth mentioning.
+% Historically this relation is important following the work of \citet{1981MNRAS.194..809L} where he presents it in the context of molecular cloud complexes of many clouds, individual clouds, and clumps, so that size scales are studied over \(\num{0.1} < L < \SI{100}{pc}\) obtaining \(\sigma = 1.10 L ^{0.38}\).
+
+% This relation is interpreted in terms of turbulence, particularly the Kolmogorov model which predicts a index of \num{0.33} so that larger regions presents more turbulence, and smaller regions less turbulence.
+% It has been argued that this correlation method is not as powerful as using statistical functions \citep{1984ApJ...277..556S} but it is interesting that the index is consistent within different phases of the interstellar medium.
+% We obtain \(\log \sigma\pos = (0.25 \pm 0.17) \log D - (0.2 \pm 0.38)\) which is comparable with \citet{1981MNRAS.194..809L} results.
+
+% As we mentioned in section \ref{sec:L-vs-sigmapos} the fact that this relation holds up to previous investigation gives some certainty that the \(\sigma\pos\) value obtained via the proposed model of the structure function is valid.
+% This implying that the structure function, while not an absolute diagnostic, is a powerful tool in the research of \hii{} regions kinematics.
+
+% \subsection{Power-law index}\label{power-law-index}
+
+% The power-law index \(m\) shown in the last column of Table \ref{tab:Res} is used for comparison between the observations derived index and the theoretical Kolmogorov value of 0.67.
+% All our indices are above this theoretical value and this is attributed to the fact that the \hii{} regions do not comply with the conditions established in the development of the turbulent theory which assumes incompressible, subsonic and homogeneous three-dimensional flow.
+% \hii{} regions emerged from a molecular cloud with highly filamentary and clumpy density structure.
+% Inside the region there is a large increase in the temperature because of the photoionization, and the density gradients with the pressure gradients accelerate the flow which occurs on multiple scales consequence of the fractal nature of the molecular cloud \citep{arthur2016turbulence}.
+% The radiation pressure, stellar winds and region expansion, among other physical processes would create pressure-driven shock waves propagating faster than the speed of sound in the medium.
+% This would make the flow compressible and supersonic in an inhomogeneous gas cloud.
+% Also, as \hii{} regions are three-dimensional objects our structure function results comes from a projection of this three-dimensional structure to a two-dimensional velocity field.
+% But despite the complex nature of \hii{} regions and observational limitations, we obtain a common pattern for the structure function behaviour and the value of the power-law index falls in a certain limited range between \num{0.7} and \num{1.4}.
+
+% The differences in the power-law index with respect the theoretical value are often used as a diagnostic tools to identify properties that are not consider in the assumptions of the turbulence theory \citetext{See table~1 of \citealp{arthur2016turbulence} and Sec.~1 of \citealp{lagrois2011}}.
+% As an example there the so called \textit{projection smoothing} \citep{von1951methode,1987ApJ...317..686O} which is used to study the projection of a three-dimensional structure function on the plane.
+% The relationships for the power-law are:
+
+% \begin{equation}\label{eq:projection-smoothing-3d}
+% m_{2D}= m_{3D} + 1
+% \end{equation}
+% %
+% and  when the astronomical object present a sheet-like distribution of emitters we have the relation:
+% %
+% \begin{equation}\label{eq:projection-smoothing-2d}
+% m_{2D} \sim m_{3D}
+% \end{equation}
+
+% As a conclusion, if the extension of the \hii{} region is compared with its depth (three-dimensional case) the value of the index is \num{1.6}. 
+% While the case where the extension is much greater than its depth (two-dimensional case) the region will have a value of \num{0.6}.
+% From Table~\ref{tab:Res} we see that our results fall between these two previous values.
+
+% As for any relation of the power-law index \(m\) and the physical properties of the \hii{} regions we can see from table \ref{tab:RestStats} that this parameter does not correlate with any other parameter or physical property, being the least reliable for determining or concluding something about the nature of the physical processes inside the regions.
+% On the other hand, the lack of correlation and the presence of this power-law index describing the assumed energy cascade may be interpreted as a universal property of the velocity fluctuations independent of the observed object, which is the main consideration in the turbulence theory.
 

### 2022-12-13 strucfunc_paper.tex
Finish the conclusions

@@
 It can seen that such a relationship reproduces the 
-observationally derived values equally as well as the linear fit.
+observationally derived values almost as well as the linear fit.
 On the other hand, we can rule out the possibility that
@@
 means that the plane-of-sky dispersion of centroids \(\sigma\pos\)
-is \emph{not} independent of the 
+is not independent of the 
 ordered large-scale velocity gradients along the line of sight.
@@
 emissivity fluctuations is insufficient on its own,
-and there must therefore be an additional disordered velocity component
+and that we require an additional disordered velocity component
 in order to explain our observations.
@@
 is that \(\sigma\pos\) is a better measure of the disordered turbulent motions within
-the \hii{} regions, whereas \(\sigma\los\) is also affected by large-scale ordered motions,
+the \hii{} regions than \(\sigma\los\) since the latter
+is contaminated by large-scale ordered motions,
 which are always at least as large as the ionized sound speed.
@@
 
-%The observations point out to the existence of spatial correlation between velocities, that could be interpreted as turbulence. 
-%Arguments against the existence of true, isotropic turbulence can be raised as, for example: i) the histograms of velocity are not always Gaussian, ii) only a fraction of the integrated emission lines of the \hii{} regions show true Gaussian profiles.
-%The asymmetry in the emission line indicates coherent mass flow motions, 
-%and sometimes is considered incompatible with turbulence. However, turbulence is in fact 
-%a mixture of coherent and chaotic flows. 
-%Only at the regime of the so-called fully developed turbulence the non-linear phenomena dominate completely the movement and the chaotic flow prevail. 
-%The problem here is that a straightforward test for any turbulent model is a big challenge, as we are in the presence of many entangled effects. 
-%However, the circumstantial evidence in favor of the existence of turbulent motions in \hii{} regions is overwhelming, and many are the potential sources of energy to create and maintain turbulence during the lifetime of an \hii{} region.
-
-Our analysis was able to characterize the velocity fields of a sample of \hii{} regions by determining a set of parameters unique to each velocity field which are: the correlation length, the exponent of a power law that fits the results through a determined range and the true velocity dispersion.
-To achieve this, a new functional form for the second-order structure function was proposed. 
-This new functional considers observational constraints such as the seeing, noise and the size of the observational box, effects that had not been considered before and play an important part in the interpretation of the structure function.
-Our proposed functional form is used as an objective function in a non-linear regression to accurately determine the set of parameters related to turbulence and to the observational constraints.
-
-The observed structure functions calculated in our work does not reveal the precise characteristic of turbulence, but the statistical results that it provides allow us to determine a distinction between correlated or random velocity fluctuations in the photoionized gas, in which the presence of correlations in the velocity field is a inherent property of turbulence.
-Although this work is not conclusive about the nature of photoionized gas turbulence and a precise description of the origin and implications of these turbulent motions is out of the scope of our investigation, we believe that the tools presented here (see section~\ref{sec:methods-apply}) guarantee a more realistic approach to determine and to the understanding the structure function.
-
-Our analysis can be easily be expanded to other \hii{} regions with the possibility of comparing the results between them since our method guarantees homogeneity, providing the possibility to develop a future catalog of \hii{} regions turbulent parameters in a concise way.
-By calculating the structure function of \hii{} regions with different morphologies, ages, stellar content, and dynamics it would be possible to detect the presence and the importance of different sources of mechanical energy, since the structure function would be different from one object to the other as we show in the present investigation.
-
-Our methods could also been use to investigate the velocity fields of other phases of the interstellar medium.
-The study of turbulence between ionized regions and the molecular clouds that give them birth can be carried out with the aid of a correct methodology with the intention of advancing the understanding of the kinematic relationships between them.
+We have used the second-order structure function of velocity centroids
+on the plane of the sky to carry out a systematic study of the turbulent kinematics
+in a sample of 9 \hii{} regions spanning a wide range of luminosities and sizes.
+Our principal findings are as follows:
+\begin{enumerate}[1.]
+\item The velocity fluctuations range from subsonic (Mach number \(\Mach \approx 0.5\))
+  in the case of low-luminosity Galactic regions, such as the Orion Nebula,
+  up to supersonic (\(\Mach \approx 2.5\)) in the case of giant extragalactic regions
+  such as 30~Doradus in the Large Magellanic Cloud. 
+\item The correlation length of the velocity fluctuations is always a small fraction
+  (roughly 2\%) of the \hii{} region diameter, implying that turbulent energy
+  is injected on scales smaller than about 10\% of the size of each region.
+\item The power law slope of the structure function at scales smaller than
+  the correlation length is \(m \approx 1 \pm 0.2\) for all regions,
+  with no significant correlation with size, luminosity, or velocity amplitude.
+  This can be explained as due to a fortuitous cancellation
+  between, on the one hand, a steepening underlying velocity spectrum and,
+  on the other hand, a reduced role for projection smoothing as the turbulent fluctuations
+  pass from the subsonic to the supersonic regime. 
+\item The non-thermal component of the emission line widths (\(\sigma\los\)) is found
+  to be proportional to the amplitude of the plane-of-sky velocity centroid fluctuations
+  (\(\sigma\pos\)) with a slope of unity, but an offset such that
+  \(\sigma\los \approx \SI{10}{km.s^{-1}}\) when \(\sigma\pos = 0\).
+  This can be explained if \(\sigma\los\) is affected by ordered velocity fields,
+  such as radial expansion, which leave no imprint on \(\sigma\pos\),
+  implying that \(\sigma\pos\) is a better diagnostic of turbulent fluctuations than
+  \(\sigma\los\), even though it is more challenging to measure.
+\item On scales larger than the correlation length, a variety of behaviors are seen.
+  Some regions, such as Carina and Hubble~X show uncorrelated homogeneous fluctuations
+  at the largest scales, whereas others, such as Orion and 30~Doradus show evidence
+  for large-scale gradients in the amplitude of the velocity fluctuations
+  with more vigorous turbulence in the core of the nebula than in the outskirts.
+  In other regions, such as the Lagoon Nebula and NGC~346, there is evidence
+  for quasi-periodic oscillations on scales similar to the size
+  of the mapped region. 
+\end{enumerate}
+
+% Our analysis was able to characterize the velocity fields of a sample of \hii{} regions by determining a set of parameters unique to each velocity field which are: the correlation length, the exponent of a power law that fits the results through a determined range and the true velocity dispersion.
+% To achieve this, a new functional form for the second-order structure function was proposed. 
+% This new functional considers observational constraints such as the seeing, noise and the size of the observational box, effects that had not been considered before and play an important part in the interpretation of the structure function.
+% Our proposed functional form is used as an objective function in a non-linear regression to accurately determine the set of parameters related to turbulence and to the observational constraints.
+
+% The observed structure functions calculated in our work does not reveal the precise characteristic of turbulence, but the statistical results that it provides allow us to determine a distinction between correlated or random velocity fluctuations in the photoionized gas, in which the presence of correlations in the velocity field is a inherent property of turbulence.
+% Although this work is not conclusive about the nature of photoionized gas turbulence and a precise description of the origin and implications of these turbulent motions is out of the scope of our investigation, we believe that the tools presented here (see section~\ref{sec:methods-apply}) guarantee a more realistic approach to determine and to the understanding the structure function.
+
+% Our analysis can be easily be expanded to other \hii{} regions with the possibility of comparing the results between them since our method guarantees homogeneity, providing the possibility to develop a future catalog of \hii{} regions turbulent parameters in a concise way.
+% By calculating the structure function of \hii{} regions with different morphologies, ages, stellar content, and dynamics it would be possible to detect the presence and the importance of different sources of mechanical energy, since the structure function would be different from one object to the other as we show in the present investigation.
+
+% Our methods could also been use to investigate the velocity fields of other phases of the interstellar medium.
+% The study of turbulence between ionized regions and the molecular clouds that give them birth can be carried out with the aid of a correct methodology with the intention of advancing the understanding of the kinematic relationships between them.
 

### 2022-12-14 strucfunc_paper.tex
Javier changes 2022-12-13

@@
 where \(X = \log_{10} x\) and \(Y = \log_{10} y\)
-with \(x, y \in \{d, D, L(\ha), \sigma\pos, r_0, m\}\)
+with \(x, y \in \{d, D_{\hii}, L(\ha), \sigma\pos, r_0, m\}\)
 (taken from the physical properties in Table~\ref{tab:regions-properties}
@@
 (see Table~\ref{tab:RestStats}),
-with a weighted mean value of \(m = 1.01\).
+with a weighted mean value of \(m = 1.03\).
 The dispersion in fitted \(m\) values is 1.6 times higher than expected
@@
 The relationship we obtain is
-\( \langle \sigma\los \rangle = (1.03 \pm 0.46) \sigma\pos + (7.7 \pm 2.9)\),
+\( \langle \sigma\los \rangle = (1.04 \pm 0.44) \sigma\pos + (7.3 \pm 2.9)\),
 which can be compared with previous results
@@
 one would predict \(\sigma\los = (\sigma\pos^2 + \vexp^2)^{1/2}\),
-which is shown by the dot-dashed line in Figure~\ref{fig:los-vs-pos}
-for the case \(\vexp \approx \SI{8}{km.s^{-1}}\).
-It can seen that such a relationship reproduces the 
+which is shown by the blue shaded-area in Figure~\ref{fig:los-vs-pos}
+with an upper limit of \SI{12}{km.s^{-1}} and lower limit of \SI{8}{km.s^{-1}} for \(\vexp\).
+It can be seen that such a relationship reproduces the 
 observationally derived values almost as well as the linear fit.
@@
     (b)\\
-    \includegraphics[width=\linewidth]{Figures/fake-finite-box-strucfunc2}
+    \includegraphics[width=\linewidth]{Figures/fake-finite-box-strucfunc}
   \end{tabular}
@@
 (compare green and orange lines in Figure~\ref{fig:strucfunc-fit-Galactic}b).
+The derived correlation length is \SI{0.5}{pc} which is above the \SI{0.3}{pc} required to determine the true correlation length but below the \SI{0.9}{pc} which guarantees that the fit can reliable determine \(r_0\).
+The structure function at large scales resembles the tapered behavior of inhomogeneous fluctuations just like the core.
 
@@
 The correlation length for all lines is \SI{\approx 0.05}{pc}, value obtained when the structure function is equal to \(\sigma\pos^2\).
-For the same \halpha\ observation we obtained a value of \num{1.07} and a correlation length of \SI{0.068}{pc}. 
+For the same \halpha\ observations, but considering high-velocity objects, we obtained a value of \num{1.07} and a correlation length of \SI{0.068}{pc}. 
 Although the work of \citet{arthur2016turbulence} follows a different methodology, the values of \(r_0\) and \(\sigma\pos^2\) fall within the margin of error of our own results.
@@
 on scales of \num{0.01} to \SI{0.2}{pc}.
-No flattening of the structure function at the largest scales
-was seen,
-but that is to be expected due to the finite box effect
-(see Appendix~\ref{sec:finite-box-effects})
-given that we determine the correlation length to be \(r_0 \approx   \SI{1}{pc}\) for this nebula,
+No flattening of the structure function at the largest scales was seen, but that is to be expected due to the finite box effect (see Appendix~\ref{sec:finite-box-effects}).
+Given that we determine the correlation length to be \(r_0 \approx \SI{1}{pc}\) for this nebula,
 which is several times larger than the region mapped by \citet{Chakraborty:1999a}.

### 2022-12-14 strucfunc_paper.tex
Finish Appendix A1

@@
 \label{sec:degr-struct-funct}
-Studied in context of \(\Delta\)-variance by \citet{Bensch:2001l}.
-
-To characterize the impact of the observational box size and the atmospheric seeing on the structure function we perform a series of experiments using artificial turbulent velocity maps.
-We quantify how these observational limitations affect the determination of astrophysical interest parameters such as the correlation length \(r_0\) and the velocity field variance \(\sigma\pos^2 \). 
-The artificial velocity maps are created using a modified version of the \textit{make$\_$extend} command from the \texttt{turbustat} Python library \citep{Koch2019AJ....158....1K}.
-The modification add a tapering to the power law so that the generated fields are uncorrelated at large scales.
-The artificial fields follows a given power law with a correlation length giving a variance value indicated as true \(\sigma^2\).
-Using this true \(\sigma^2\) we obtain the true \(r_0\) and these values are used as a reference in the experiments to quantify the variations.
+% Studied in context of \(\Delta\)-variance by \citet{Bensch:2001l}.
+
+To characterize the impact of the finite map size
+and the atmospheric seeing on the structure function we perform a series of experiments using artificial turbulent velocity maps.
+We quantify how these observational limitations affect the determination of
+the structure function parameters, such as
+the correlation length \(r_0\) and the velocity field variance \(\sigma\pos^2\). 
+The artificial velocity maps are created using a modified version of the \texttt{make\textunderscore{}extend} command from the \texttt{turbustat} Python library \citep{Koch2019AJ....158....1K},
+which creates a two-dimensional fractional Brownian Motion field
+\citep{Miville-Deschenes:2003a}
+based on a power-law energy spectrum in wavenumber \(k\) 
+with random phases. 
+Our modification multiplies the energy spectrum by a
+low-wavenumber exponential taper:
+\(e^{-1 / 2 \pi r_0 k}\).
+As a result, the generated fields become uncorrelated at scales larger than \(r_0\)
+and the resulting structure function closely approximates our model form
+(section~\ref{sec:methods-apply}).
+
+% The artificial fields follows a given power law with a correlation length giving a variance value indicated as true \(\sigma^2\).
+% Using this true \(\sigma^2\) we obtain the true \(r_0\) and these values are used as a reference in the experiments to quantify the variations.
 
@@
     The dashed line is an approximate analytic fit to these results
-    (equation~\eqref{eq:ajustebox}).
+    (\(1 - e^{L / 3.6r_0}\)).
     (b)~Determination of \(\sigma^2\) and \(r_0\) from fitting the model
@@
 
-The Fig. \ref{fig:finite-box}a shows some of the artificial velocity fields used to study the variations in the structure function with respect to the size of the observational box.
-Initially we have a velocity field of \(512 \times 512 \) pixels that is divided \(n\) times (with \(n = 1 - 6\)) producing \(N = 4^n\) fields , where each one has a linear size \(L \times L \) with \(L = 2^{9 -n}\).
-The structure function is determined for each division and later we average all the divisions obtaining a characteristic structure function for \(L = 256, 128, 64,\) etc.
-
-In the Fig. \ref{fig:finite-box}b we show in solid lines the normalized averaged structure functions for the maps in Figure \ref{fig:finite-box}a.
-The number \(N\) of divisions and the length \(L\) are indicated for each structure function.
-The shaded areas show the deviation that each averaged structure function has due to the different divisions. 
-The horizontal and vertical blue dashed lines show the true \(r_{0}\) and the value of \(B(r) / \sigma^2 = 1 \), respectively.
-The colored dotted lines indicate the averages, taking into account all the divisions of each map, of the apparent \(r_ {0}\) and the apparent \(\sigma^2 \).
-It is clear that \(r_0\) and \(\sigma^ 2 \) decrease with respect to the true values as the size \(L\) of the observational box decreases. 
-This analysis is performed on different maps (no images are shown) given a different power law in the velocity spectrum and different correlation lengths, giving the same results.
-
-Fig.
-\ref{fig:finite-box-effect}a shows the empirical ratios of the correlation length of each averaged map with respect to the true correlation length (\(\text{apparent } r_ 0 /\text{true } r_0 \) ) and the ratio between the averaged variance of each divided map and the true variance (\(\text{apparent } \sigma^2  / \text{true } \sigma^2\)).
-We observe that for the values where \(L> 20r_0 \) the change in the ratios is null.
-It is for the values where \( L < 10 r_0 \) where there is a decrease.
-This behavior is fulfilled for all simulated maps with different power law and correlation length in the velocity spectrum indicated with different colored circles in Figure \ref{fig:finite-box-effect}a.
-
-On the other hand, Fig. \ref{fig:finite-box-effect}b shows the model-derived \(r_0\) and \(\sigma^ 2 \) values using the fitting procedure with the \texttt{lmfit} library.
-In this case we see that the model fitting works much better than the empirical measurement, which gives reliable values so long \(L > 3r_0 \).
-
-The empirical variations of the ratios is described by the  dashed line in Fig. \ref{fig:finite-box-effect} a and b, and is given by the equation:
-
-\begin{equation}\label{eq:ajustebox}
-\beta(r_0) = 1 - \exp \left[ \frac{L}{3.6r_0} \right] 
-\end{equation}
+Figure~\ref{fig:finite-box}a shows how we test for finite map effects by taking
+a simulated velocity field of size \(512 \times 512\) pixels and iteratively
+dividing the full map into \(2 \times 2\) tiles.
+On the \(j\)th iteration we have \(N = 4^j\) tiles,
+each of size \(L \times L \) pixels with \(L = 2^{9 - j}\).
+The figure shows the result for \(j = 1\), 2, 3, and 4, in which the full map
+was generated with a correlation length \(r_0 = 16\)~pixels.
+We then calculate the individual structure function for each tile and
+find the mean and standard deviation for each level of subdivision,
+showing the results in Figure~\ref{fig:finite-box}b.
+It can be seen that the mean structure functions for each level
+of subdivision (shown by colored dots and solid lines)
+overlap very closely with one another, apart from deviations
+due to edge effects when \(r > L/2\).
+On the other hand, there is considerable dispersion between
+individual tiles (shown by light colored shading) for the cases
+where \(L < r_0\).
+
+We next empirically measure the velocity variance and
+apparent correlation length for each tile.
+The velocity variance \(\sigma^2\) is found by
+directly averaging over the pixels in the tile using equation~\eqref{eq:sig-pos},
+while the apparent correlation length \(r_0\)
+is found as the separation \(r\) for which \(B(r) = \sigma^2\),
+using the tile's own empirically measured structure function and variance.
+In Figure~\ref{fig:finite-box-effect}a we show how these
+quantities deviate from the ``true'' values
+(as measured on the full \(512 \times 512\) map)
+as a function of the tile size \(L\).
+It can be seen that the true values are successfully recovered
+so long as the map size is more than ten times the correlation length,
+but the apparent values of \(r_0\) and \(\sigma^2\) are smaller than the true values
+when \(L < 10 r_0\), increasingly so as \(L\) becomes smaller.
+This can be intuitively understood as due to the fact that a tile that
+is small compared with the correlation length will
+fail to sample the full range of velocity fluctuations,
+leading to an underestimate of \(\sigma^2\).
+Then the fact that \(B(r)\) increases with \(r\) in the power law regime
+means there will be a concomitant underestimate of \(r_0\).
+
+However, it is possible to do a considerably better job
+of recovering the true \(\sigma^2\) and \(r_0\) by fitting our
+heuristic model structure function of equation~\eqref{eq:model-strucfunc-ideal}.
+This is shown in Figure~\ref{fig:finite-box-effect}b, where it can be seen
+that the true parameters are reliably recovered so long as \(L > 3 r_0\),
+which is a roughly \SI{0.5}{dex} improvement over the purely empirical method.
+In order for the model fitting to work, the tile size must be large enough
+that the structure function begins to show some flattening at the largest scales,
+which is why the results are still inaccurate for the smallest values of \(L\)
+that sample only the rising power-law portion of \(B(r)\).
 

### 2022-12-14 strucfunc_paper.tex
Slightly expand the conclusions

@@
 \item The correlation length of the velocity fluctuations is always a small fraction
-  (roughly 2\%) of the \hii{} region diameter, implying that turbulent energy
+  (roughly 2\%) of the \hii{} region diameter (section~\ref{sec:D-vs-r0}),
+  implying that turbulent energy
   is injected on scales smaller than about 10\% of the size of each region.
 \item The power law slope of the structure function at scales smaller than
-  the correlation length is \(m \approx 1 \pm 0.2\) for all regions,
-  with no significant correlation with size, luminosity, or velocity amplitude.
+  the correlation length is \(m \approx 1.0 \pm 0.2\) for all regions,
+  with no significant correlation with size, luminosity, or velocity amplitude
+  (section~\ref{sec:constancy-power-law}).
   This can be explained as due to a fortuitous cancellation
@@
   (\(\sigma\pos\)) with a slope of unity, but an offset such that
-  \(\sigma\los \approx \SI{10}{km.s^{-1}}\) when \(\sigma\pos = 0\).
+  \(\sigma\los \approx \SI{10}{km.s^{-1}}\) when \(\sigma\pos = 0\)
+  (section~\ref{sec:sigmapos-vs-sigmalos}).
   This can be explained if \(\sigma\los\) is affected by ordered velocity fields,
@@
   \(\sigma\los\), even though it is more challenging to measure.
-\item On scales larger than the correlation length, a variety of behaviors are seen.
+\item The amplitudes of \ha{} surface brightness fluctuations
+  and turbulent velocity fluctuations 
+  are only weakly correlated (Figure~\ref{fig:brightness-pdfs}h).
+  For regions with supersonic turbulence
+  these are consistent with the
+  predictions for turbulence-induced density fluctuations,
+  but for regions with subsonic turbulence the inferred density fluctuations
+  are too large to be caused by turbulence alone. 
+\item On scales much larger than the correlation length,
+  a variety of behaviors are seen (section~\ref{sec:evid-inhom-at}).
   Some regions, such as Carina and Hubble~X show uncorrelated homogeneous fluctuations
   at the largest scales, whereas others, such as Orion and 30~Doradus show evidence
-  for large-scale gradients in the amplitude of the velocity fluctuations
+  for radial gradients in the amplitude of the velocity fluctuations
   with more vigorous turbulence in the core of the nebula than in the outskirts.

### 2022-12-15 strucfunc_paper.tex
Javier changes 2022-12-14

@@
   With the aim to characterize these velocities fluctuations we conduct a statistical analysis on a diverse sample of 9 \hii{} regions that spans more than two orders of magnitude in size and luminosity, and are located in the Milky Way and other Local Group galaxies.
-  For the statistical analysis we obtain the second-order structure function of the observed \halpha\ centroid velocity field.
-  We proposed a heuristic model for the structure function which takes into account observational constraints like the seeing (\(s_0\)), instrumental noise (\(B_{\text{noise}}\)) and size of the field of view (\(L_{\text{box}}\)).
-  The turbulent velocity field parameters like the velocity dispersion of the centroid velocity (\(\sigma\pos\)), the autocorrelation length (\(r_0\)) and a power-law index (\(m\)) are also considered in our heuristic model.
-  The observational structure function is fitted using our heuristic model in a non-linear regression analysis which allow us to derive the parameters representing each velocity field.
+  In the statistical analysis we obtain the second-order structure function of the observed \halpha\ centroid velocity field.
+  We proposed a model for the structure function which takes into account observational constraints like the seeing (\(s_0\)), instrumental noise (\(B_{\text{noise}}\)) and size of the field of view (\(L\)).
+  The turbulent velocity field parameters like the velocity dispersion of the centroid velocity (\(\sigma\pos\)), the autocorrelation length (\(r_0\)) and a power-law index (\(m\)) are also considered in our model.
+  We fit our model to the observational structure function using a non-linear regression analysis which allow us to derive the parameters representing each velocity field.
   The results for the 9 \hii{} regions are: \(\num{0.2} < s_0 \text{(FWHM)} < \SI{3.0}{arcsec}\), \(\num{0.003} < B_{\text{noise}} < \SI{6.0}{km^{-2}.s^{-2}}\),  \(\num{3} < \sigma\pos < \SI{19}{km.s^{-1}}\), \(\num{0.07} < r_0 < \SI{12}{pc}\) and \(\num{0.7}< m < \num{1.5}\).
-  Later, the derived parameters are used to determine scaling relations between the physical properties of the regions like \halpha\ luminosity (\(L(H_{\alpha})\)), diameter (\(D\)) and the mean non-thermal linewidth (\(\langle \sigma_{los} \rangle\)).
+  The derived parameters are used to determine scaling relations between the physical properties of the regions like \halpha\ luminosity (\(L(H_{\alpha})\)), diameter (\(D\)) and the mean non-thermal linewidth (\(\langle \sigma_{los} \rangle\)).
   We find that these relations are \(\sigma\pos \propto L(H_{\alpha})^{0.28 \pm 0.10}\) and \(r_0 \propto D^{0.95 \pm 0.32}\).
-  Finally, the \(\sigma\pos\) and \(\langle \sigma_{los} \rangle\) relation increase following a linear relation.
-  Since the derived  scale-relations are within the uncertainty of previous investigations we conclude that the parameters obtained from our proposed model represents true kinematic properties of each region.
-  The methodology we present guarantees consistency for comparison between the galactic and giant extragalactic \hii{} regions.
+  The \(\sigma\pos\) and \(\langle \sigma_{los} \rangle\) increase following a linear relation.
+  From the previous relations we found that the for our sample the \Mach{} number ranges from \( 0.5 - 2.5\) and that for ionized regions the energy is injected on scales smaller than 10\% of the size of each region.
+  We explain the derived power law slope by considering the effect of projection smearing and emissivity fluctuations.
+  We show that for ionized regions, the latter one, can be related to density fluctuations and use its diagnostic no determine the presence of turbulence induced-density.
 
@@
 \citet{arthur2016turbulence} carried out a complete analysis by calculating the structure function of different emission lines in the inner Orion Nebula.
-They observed a tendency that higher ionization lines presents higher  dispersion and the steepness of the structure function slope. 
-Their results just consider one Gaussian component. 
-The power-law index obtained by \citet{arthur2016turbulence} are \(m \sim 1.2 \pm 0.1\) for \halpha\ and [OIII] emission lines and for [SII] they found \(m \sim 0.8 \pm 0.1\). 
-The correlation length for all lines is \SI{\approx 0.05}{pc}, value obtained when the structure function is equal to \(\sigma\pos^2\).
-For the same \halpha\ observations, but considering high-velocity objects, we obtained a value of \num{1.07} and a correlation length of \SI{0.068}{pc}. 
-Although the work of \citet{arthur2016turbulence} follows a different methodology, the values of \(r_0\) and \(\sigma\pos^2\) fall within the margin of error of our own results.
+On their work, they only consider one Gaussian component fit.
+They find tendency that higher ionization lines presents higher  dispersion and the steepness of the structure function slope. 
+They also make a comparison with previous work (see table~5 on their paper) founding a a broad agreement in results and the dependence between ionization energy and slope and dispersion value.
+The work by \citet{arthur2016turbulence} is the only one that has calculated the structure function for the \ha{} emission line, for this reason it will be the only one that we use for comparison.
+The power-law index obtained by \citet{arthur2016turbulence} are \(m \sim 1.2 \pm 0.1\) for \halpha\ and [OIII] emission lines and for [SII] and [NII] they found \(m \sim 0.8 \pm 0.1\). 
+The correlation length for all lines is \SI{\sim 0.05}{pc}, value obtained when the structure function is equal to \(\sigma\pos^2= \SI{9.37}{km^{2 }.s^{-2}}\)..
+For the same \halpha\ observations, but considering high-velocity objects, we obtained a value of \num{1.07 \pm 0.03}, a correlation length of \SI{0.068 \pm 0.004}{pc} and \(\sigma\pos^2 = \SI{13 \pm 1}{ km^{2}.s^{-2}}\).
+The difference with respect to this last value is due to the fact that \citet{arthur2016turbulence} masked areas with high values of centroid velocity (see figure~2 on their paper).
+Since there are the same observations there is a good agreement in the structure function.
 
@@
 \label{sec:comparison-lagoon}
-The structure function of the Lagoon Nebula was previously
-studied by \citet{Chakraborty:1999a} using the [\ion{O}{3}] \Wav{5007} line,
-finding an approximate power law behavior (\(m = 0.46\))
-on scales of \num{0.01} to \SI{0.2}{pc}.
-No flattening of the structure function at the largest scales was seen, but that is to be expected due to the finite box effect (see Appendix~\ref{sec:finite-box-effects}).
-Given that we determine the correlation length to be \(r_0 \approx \SI{1}{pc}\) for this nebula,
-which is several times larger than the region mapped by \citet{Chakraborty:1999a}.
+The Lagoon Nebula was previously studied by \citet{Chakraborty:1999a} using the [\ion{O}{3}] \Wav{5007} line.
+The structure function was computed on an area of \num{1} \(\times\) \SI{1}{arcmin^2} centered at Herschel 36.
+Compared to our data (from \num{0.1} and \SI{10}{pc}), this covers the small scales between \num{0.012} and \SI{0.3}{pc}.
+\citet{Chakraborty:1999a} findings are a power law behavior of \(m = 0.46\)
+for all its range.
+They mentioned the nebular gas physical conditions and the presence of gradients as responsible for the discrepancy of the theoretical 2/3 value.
+No flattening of the structure function at the largest scales was seen, but that is to be expected due to the finite box effect (see Appendix~\ref{sec:finite-box-effects}), but argue the possibility that the turbulent energy input is at more than one spacial scale.
+With the aid of the 2D-autocorrelation function (using \(1/e\)) they found a characteristic turbulent scale of \SI{0.12}{pc}.
+We found \(r_0 = \SI{1 \pm 0.1}{pc}\) for this nebula, which is several times larger than the region mapped by \citet{Chakraborty:1999a}.
 On the other hand, the magnitude of the velocity dispersion found by these authors greatly exceeds our own measurements.
@@
 albeit to a more extreme degree.
+\citet{Chakraborty:1999a} mentioned a good agreement between \citet{1986ApJ...304..767O}  which show different HII regions structure functions slopes between \(m = 0.18 - 0.45\) and \citet{1987ApJ...317..676O} which cover an area around 9 Sgr in M8.
+The first investigation in the Lagoon nebula structure function is from \citet{1970A&A.....8..486L} which claims that a value of \(m = 2/3\) satisfies their observations agreeing with the Kolmogorov Law.
 
@@
 
-The first attempt at characterizing turbulence in a giant extragalactic \hii{} region, GEHR, was done by \citet{1961MNRAS.122....1F} with the 30~Doradus complex, finding no indication of turbulent motions between scale of \num{10} and \SI{100}{pc}.
 \citet{Melnick:2021x} also investigated the structure function in 30~Doradus finding on their results that the structure function is entirely flat on scales from \num{3} to \SI{200}{pc}.
@@
 The VLT FLAMES/GIRAFFE observations of \citet{Melnick:2021x} may not have had the resolution to resolve the correlations at small separations, however an inspection of its velocity map (figure 7 in their work) shows that the velocity distribution it is far from completely random.
-This is the first time turbulence is characterized in 30~Doradus using the structure function.
+\citet{Melnick:2021x} \(\sigma\pos\) values range from \num{11.6} to \SI{18.2}{km.s^{-1}} for a diverse type of fits (see figure~15 on their paper).
+The first attempt at characterizing turbulence in a giant extragalactic \hii{} region, GEHR, was done by \citet{1961MNRAS.122....1F} with the 30~Doradus complex, finding no indication of turbulent motions between spatial scales of \num{10} and \SI{100}{pc}.
+The \citet{1961MNRAS.122....1F} is in broad agreement with the \citet{Melnick:2021x} results in which they consider profiles classified as singles.
+Our structure function falls between the two previous results: 
+From a spatial scale of \SI{5}{pc} up to \SI{40}{pc} (which covers small-to-intermediate scale for previous investigations and large scales for us) and from \(B(r)\) between \num{250} to \SI{600}{km^{2}.s^{-2}}.
+
+%This is the first time turbulence is characterized in 30~Doradus using the structure function.
 
@@
 
-For NGC 604 there is good agreement in our structure function results and previous studies because where are using the same TAURUS-II data as \citet{Melnick:2021x} and \citet{Medina-Tanco:1997a}.
-Despite this general agreement the interpretations in each study is different.
+For NGC 604 there is good agreement in our structure function results and previous studies.
+This mainly because where are using the same TAURUS-II data as \citet{Melnick:2021x} and \citet{Medina-Tanco:1997a}.
+Despite this general agreement, the interpretations in each study is different.
 \citet{Medina-Tanco:1997a} conclude about a double regime acting on the kinetic energy spectrum.

### 2022-12-15 strucfunc_paper.tex
More progress on Appendix A2

@@
 the correlation length \(r_0\) and the velocity field variance \(\sigma\pos^2\). 
-The artificial velocity maps are created using a modified version of the \texttt{make\textunderscore{}extend} command from the \texttt{turbustat} Python library \citep{Koch2019AJ....158....1K},
+The synthetic velocity maps are created using a modified version of the \texttt{make\textunderscore{}extend} command from the \texttt{turbustat} Python library \citep{Koch2019AJ....158....1K},
 which creates a two-dimensional fractional Brownian Motion field
@@
 (section~\ref{sec:methods-apply}).
+The maps generated by \texttt{turbustat} are spatially periodic,
+but we make them non-periodic by always dividing the full map into at least
+four tiles, which are each analyzed separately.
 
@@
 
-Ground-based astronomical observations are affected by the seeing produced by the atmosphere.
-When calculating the structure function of the observational data, the seeing affects the structure function results at small-scale separations due to the smoothing of velocity fluctuations between adjacent pixels.
+Ground-based optical observations are affected by atmospheric seeing,
+which limits the angular resolution of any observations.
+This changes the observed structure function by suppressing fluctuations
+between the most closely separated points.
+\citet{Bensch:2001l} studied the  analogous problem
+of beam smearing in the context of the \(\Delta\)-variance method \citep{Stutzki:1998a}, 
+deriving a leading order approximation for the effect,
+but an exact analytic treatment is difficult.
+We therefore prefer to empirically study the effect of seeing using the
+synthetic velocity maps described above.
+
+Figure~\ref{fig:seeing-reduction}a illustrates how four different
+synthetic velocity fields of size \(256\times256\) pixels
+and correlation length \(r_0 = \SI{15.1}{pixels}\)
+are affected by progressively broader gaussian seeing,
+with RMS width \(s_0 = 1\) to \SI{32}{pixels}.
+We calculate the structure function \(B(r)\) for each map and show
+in Figure~\ref{fig:seeing-reduction}b the average ratio between
+\(B(r)\) and the value in the absence of seeing,
+with different colors representing different values of \(s_0\).
+For small values of \(s_0\), the principle effect is seen at
+small separations,
+
 To study the effect of the seeing we calculate the structure function of simulated velocity maps where an artificial Gaussian seeing with different line widths has been introduced.

### 2022-12-15 strucfunc_paper.tex
Finish revision of Appendix A

@@
 \citep{Miville-Deschenes:2003a}
-based on a power-law energy spectrum in wavenumber \(k\) 
-with random phases. 
+based on a power-law energy spectrum in wavenumber \(k\), \(E(k) \propto k^{-n}\),
+where \(n = m + 2\) and with random phases. 
 Our modification multiplies the energy spectrum by a
@@
   \caption{Effects of seeing on the structure function.
-    (a)~Each row shows a different simulated random velocity field on a \(256^2\) grid
-    (see text for details).
+    (a)~Each row shows a different simulated random velocity field
+    on a \(256^2\) grid (see text for details).
     The left column shows the original field,
@@
 synthetic velocity fields of size \(256\times256\) pixels
-and correlation length \(r_0 = \SI{15.1}{pixels}\)
+and correlation length \(r_0 = \SI{16}{pixels}\)
 are affected by progressively broader gaussian seeing,
@@
 with different colors representing different values of \(s_0\).
+Results are shown for a power-law slope of \(m = 1.2\)
+but we find very similar behaviour for other values of \(m\) within the range
+seen in our observations.
 For small values of \(s_0\), the principle effect is seen at
-small separations,
-
-To study the effect of the seeing we calculate the structure function of simulated velocity maps where an artificial Gaussian seeing with different line widths has been introduced.
-The artificial velocity maps are created in the same way as in Section~\ref{sec:finite-box-effects}.
-The seeing in velocity maps is added via the \texttt{astropy} Python library \citep{astropy:2013} using the \textit{Gaussian2DKernel} command.
-
-Fig. \ref{fig:seeing-reduction}a shows column an artificial velocity field of 512 \(\times\) 512  divided into four maps of 256 \(\times \) 256 pixels each which are displayed in each row.
-A Gaussian seeing \(s_0 \) is applied to each division with an RMS width given by \(s_0 = 2^n\) pixels with \(n = 0-5\) shown in the different columns. 
-The structure function is computed in these maps and the averaged considering the same seeing.
-
-The solid lines in Figure \ref{fig:seeing-reduction}b show the ratio of the averaged structure function of the maps with their respective seeing to the unsmoothed map: \(B (r, s_0 ) / B (r, s_0 = 0) \).
-The circle symbols indicate the value of 2\(s_0\), the plus symbols indicate the apparent correlation length of the smoothed maps and the vertical dotted line indicates the true \(r_{0}\).
-
-The dashed lines in Figure \ref{fig:seeing-reduction}b are  empirically fits for each ratio and characterizes the decrease in the structure function for each value of seeing.
-To obtain this fit, we start from a convolution of an emission line and Gaussian seeing.
-The emission line has the form \(\text {I}(x, v) = \text{I}_0 \phi [v; \overline {v} (x), \sigma_0]\) and has uniform width and brightness where the only change with respect to position is the velocity centroid.
-The proposed seeing is \(\text{K}(x, s_0)\) of the form \(1 / \sqrt{2 \pi s_0} \exp^ {-x^ 2 / 2s_0 ^ 2} \).
-The convolution \(\text{I}(x, v) \otimes \text{K}(x, s_0) \) is performed to obtain the smoothed map, \(\text {\~I} (x, v) \).
-
-Then we calculate the average velocity difference of the original map, \(\Delta v \), and the smoothed map, \(\tilde{\Delta v}\), in the arbitrary points \( x = \{0, \delta \} \).
-The expansion of the convolution at small separations gives a term \(S_0(r; s_0)\) that modifies the structure function which has the form:
-
-\begin{equation}\label{eq:seeingcon}
-S (r;s_0) = \tanh^2 \left[ \left( \dfrac{r}{2s_0} \right)^2 \right]
+the smallest separations but the structure function is noticeably depressed
+for separations as large as \(r = 10 s_0\).
+As \(s_0\) increases to become comparable with \(r_0\),
+even the largest separations are significantly affected.
+At the same time the apparent correlation length begins to increase,
+as indicated by the plus symbols in the figure.
+
+We find that the following simple analytic function reproduces
+these results to within better than 10\%:
+\begin{equation}\label{eq:seeingemp2}
+S(r; s_0, r_0) = \frac{e^{-s_0 / r_0}}{1+(2s_0 / r)^{2a}} ,
 \end{equation}
-
-Subsequently, the equation \ref{eq:seeingcon} is empirically modified and we obtain:
-
-%\begin{equation}\label{eq:seeingemp}
-%S(r; s_0, r_0) =  \frac{e^\frac{-s_0}{r_0}}{2} \left(1 + \tanh{a \text{ln} \frac{r}{2s_0}} \right)
-%\end{equation}
-%
-%and the final form of the equation \ref{eq:seeingemp} after a mathematical simplification gives:
-
-\begin{equation}\label{eq:seeingemp2}
-S(r; s_0, r_0) = \frac{e^\frac{-s_0}{r_0}}{1+(\frac{2s_0}{r})^{2a}}
-\end{equation}
-%
-which describes the dashed lines in Figure \ref{fig:seeing-reduction}b. 
-The equation \ref{eq:seeingemp2} is used to correct the observational structure function in equation \eqref{eq:sf-functional}.
+which is shown by dashed lines in Figure \ref{fig:seeing-reduction}b.
+The optimum value of the index \(a\) in this equation varies slightly
+with the power law slope \(m\) of the true structure function,
+but a compromise value of \(a = 0.75\) works tolerably well for \(m = 0.7\) to \(1.3\).
+We therefore use this equation to represent the seeing
+in our structure function fits (section~\ref{sec:results}),
+with \(s_0\) as an additional free parameter for the models.
 

### 2022-12-15 strucfunc_paper.tex
Restore Hector as a co-author. Use official IRyA address

@@
 \author[J. García Vázquez et al.]{
-J. García Vázquez$^{1}$\thanks{E-mail: jgarciav1600@alumno.ipn.mx}
-and W. J. Henney$^{2}$
+  J. García Vázquez$^{1}$\thanks{
+    E-mail: \href{mailto:jgarciav1600@alumno.ipn.mx}{jgarciav1600@alumno.ipn.mx}
+  },
+  William J. Henney$^{2}$
+  and H. O. Castañeda$^{1}$\thanks{Deceased.}
 \\
 % List of institutions
-$^{1}$Escuela Superior de Física y Matemáticas, Instituto Politécnico Nacional, Ciudad de México, México.\\
-$^{2}$Instituto de Radioastronomía y Astrofísica, Universidad Nacional Autónoma de México, Apartado postal 3-72, 58090 Morelia, Michoacán, Mexico\\
+$^{1}$Escuela Superior de Física y Matemáticas, Instituto Politécnico Nacional, Ciudad de México, México C.P. 07738\\
+$^{2}$Instituto de Radioastronomía y Astrofísica,
+Universidad Nacional Autónoma de México,
+Antigua Carretera a Pátzcuaro \#8701,\\
+Ex-Hda. San José de la Huerta, 
+Morelia, Michoacán, México C.P. 58089\\
 }

### 2022-12-19 strucfunc_paper.tex
Javier changes 2022-12-19

@@
   We explain the derived power law slope by considering the effect of projection smearing and emissivity fluctuations.
-  We show that for ionized regions, the latter one, can be related to density fluctuations and use its diagnostic no determine the presence of turbulence induced-density.
+  We show that for ionized regions, the latter one, can be related to density fluctuations and use it as a diagnostic to determine the presence of turbulence-induced density fluctuations.
 
@@
 
-%In the section \ref{sec:comp-with-prev} we make a comparison of our methods and results with previous research that analyzes structure functions of some \hii{} regions of our sample.
-%In the section \ref{sec:scaling-relations} we present the most important scaling relations between the derived turbulent parameters and the physical properties of the \hii{} regions.
-%Finally, in the section \ref{power-law-index} we discuss the role of the derived power-law index in the context of turbulence in the ionized gas.
-
 \subsection{Comparison with previous structure functions}
@@
 \ref{fig:sigvsl}, \ref{fig:rvsR} and \ref{fig:los-vs-pos} we show the plots for the correlations with a significance level \(p < \num{0.05}\) which corresponds to the first three rows in Table \ref{tab:RestStats}.
-% In the Figs.
+In the Figs.
 the black solid line is the input regression line which is described by the equation shown in the plot and the red thin lines are a random sample (\num{ \sim 400}) from the posterior distribution within one standard deviation from the slope and the \(Y\)-intercept value.
@@
 and \(E_{B2} = \alpha^{-1}\) for LOS~2, where \(\alpha\) is a positive constant.
-Both layers are assumed to have unit depth along line line of sight,
+Both layers are assumed to have unit depth along line of sight,
 such that the surface brightness for the two LOS are given by
@@
 %In the southwest direction of the Huygens region there is a drop in the brightness as one approach a much larger region called Extended Orion Nebula \citetext{EON henceforth;  \citealp{2008Sci...319..309G}}
-The position of Orion near the side of the Orion Molecular Cloud (OMC-1) make it an ongoing star formation with a large population of young star, some of which are the sources of stellar jets and Herbig-Haro objects \citep{1993ApJ...410..696O}.
-Its physical properties and kinematics, along its stellar population are documented in \citet{2001ARA&A..39...99O}.
+The position of the Orion Nebula near the side of the Orion Molecular Cloud (OMC-1) make it an ongoing star formation with a large population of young star, some of which are the sources of stellar jets and Herbig-Haro objects \citep{1993ApJ...410..696O}.
+Its physical properties and kinematics, along its stellar population is documented in \citet{2001ARA&A..39...99O}.
 
@@
 
-\
 Figure~\ref{fig:strucfunc-fit-Galactic}a shows the structure function of the Orion core.
@@
 The power-law index obtained by \citet{arthur2016turbulence} are \(m \sim 1.2 \pm 0.1\) for \halpha\ and [OIII] emission lines and for [SII] and [NII] they found \(m \sim 0.8 \pm 0.1\). 
-The correlation length for all lines is \SI{\sim 0.05}{pc}, value obtained when the structure function is equal to \(\sigma\pos^2= \SI{9.37}{km^{2 }.s^{-2}}\)..
+The correlation length for all lines is \SI{\sim 0.05}{pc}, value obtained when the structure function is equal to \(\sigma\pos^2= \SI{9.37}{km^{2 }.s^{-2}}\).
 For the same \halpha\ observations, but considering high-velocity objects, we obtained a value of \num{1.07 \pm 0.03}, a correlation length of \SI{0.068 \pm 0.004}{pc} and \(\sigma\pos^2 = \SI{13 \pm 1}{ km^{2}.s^{-2}}\).
@@
 The structure function was computed on an area of \num{1} \(\times\) \SI{1}{arcmin^2} centered at Herschel 36.
-Compared to our data (from \num{0.1} and \SI{10}{pc}), this covers the small scales between \num{0.012} and \SI{0.3}{pc}.
-\citet{Chakraborty:1999a} findings are a power law behavior of \(m = 0.46\)
+Compared to our which data spans between \num{0.1} and \SI{10}{pc}), their results cover smaller scales, between \num{0.012} and \SI{0.3}{pc}.
+\citet{Chakraborty:1999a} report a  law behavior of \(m = 0.46\)
 for all its range.
@@
 The 30~Doradus structure function is shown in Figure~\ref{fig:strucfunc-fit-MC}a.
-The value of the observed \(\sigma\pos^2 = \SI{252}{km^{2}.s^{-2}}\) is obtained at \(r_0 = \SI{3}{pc} \) (the derived values from our model are \(\sigma\pos^2 = \SI{7}{km^{297}.s^{-2}}\) and \(r_0 = \SI{4}{pc} \)).
+The value of the observed \(\sigma\pos^2 = \SI{252}{km^{2}.s^{-2}}\) is obtained at \(r_0 = \SI{3}{pc} \) (the derived values from our model are \(\sigma\pos^2 = \SI{297}{km^{2}.s^{-2}}\) and \(r_0 = \SI{4}{pc} \)).
 The observed value of \(2\sigma\pos^2\) corresponds to \(r = \SI{13}{pc} \).
@@
 
-\citet{Melnick:2021x} also investigated the structure function in 30~Doradus finding on their results that the structure function is entirely flat on scales from \num{3} to \SI{200}{pc}.
-The above does not coincide with our results, since we establish the existence of correlations up to the maximum value of the structure function that occurs at \SI{20}{pc}, separation where a value of 2\(\sigma\pos^2\) is reached.
-The VLT FLAMES/GIRAFFE observations of \citet{Melnick:2021x} may not have had the resolution to resolve the correlations at small separations, however an inspection of its velocity map (figure 7 in their work) shows that the velocity distribution it is far from completely random.
+\citet{Melnick:2021x} also investigated the structure function in 30~Doradus finding that the structure function is entirely flat on scales from \num{3} to \SI{200}{pc}.
+This does not agree with our results, since we establish the existence of correlations up to the maximum value of the structure function that occurs at \SI{20}{pc}, separation where a value of 2\(\sigma\pos^2\) is reached.
+The VLT FLAMES/GIRAFFE observations of \citet{Melnick:2021x} may not have had the resolution to resolve the correlations at small separations, however an inspection of its velocity map (figure 7 in their work) shows that the velocity distribution is not completely random.
 \citet{Melnick:2021x} \(\sigma\pos\) values range from \num{11.6} to \SI{18.2}{km.s^{-1}} for a diverse type of fits (see figure~15 on their paper).
@@
 The \citet{1961MNRAS.122....1F} is in broad agreement with the \citet{Melnick:2021x} results in which they consider profiles classified as singles.
-Our structure function falls between the two previous results: 
-From a spatial scale of \SI{5}{pc} up to \SI{40}{pc} (which covers small-to-intermediate scale for previous investigations and large scales for us) and from \(B(r)\) between \num{250} to \SI{600}{km^{2}.s^{-2}}.
-
-%This is the first time turbulence is characterized in 30~Doradus using the structure function.
+The large scales of our structure function falls between the two previous results.
+The previous happens at \SI{5}{pc} and \SI{40}{pc} (which covers small-to-intermediate scale for previous investigations and large scales for us) and for \(B(r)\) between \num{250} to \SI{600}{km^{2}.s^{-2}} where our results show a downward 'hook' pattern.
 
@@
 
+NGC 595 is the second brightest giant \hii{} region in the M33 galaxy.
+Using HST/WFPC-2 images \citet{1996AJ....111.1128M} found approximately 250 stars of the OB type, 13 Supergiants and 10 WR, confirming previous candidates.
+\citet{1993AJ....105.1400D} use optical photometry to propose 11 WR stars. 
+The ionizing output \(Q_0\) is \SI{e50.88}{photons.s^{-1}} (60 times higher compared to the Orion Nebula) and has a luminosity in \ha{} of \SI{e38.95}{erg.s^{-1}}\citep{2002MNRAS.329..481B}.
+The mean non-thermal linewidth in \ha{} is \SI{16.8 \pm 0.1}{km.s^{-1}} \citep{lagrois2009multi}.
+\citet{lagrois2011} present a kinematic study of the regions using optical emission lines and and radio 21 cm line observations and find that \ha{} shell morphology that is related to the stellar winds of the several massive stars located in its interior.
+They proposed Champagne flows at the periphery of the molecular cloud leading to accelerated ionized material.
+
+%They derived and age of 4.5\(\pm\)1.0 Myr consistent with \citet{1993AJ....105.1400D}.
+%\citet{2010MNRAS.402.1635R} used Integral Field Spectroscopy (IFS) to present a resolved study of the physical properties of the ionized gas and the ionized structure.
+%They also confirm the presence of previous cataloged WR stars and detect new candidates, and propose classical emission-line ratios as metallicity calibrators.
+
 NGC 604 is the second brightest \hii{} region in the Local Group after 30~Dor.
@@
 %\citet{2012ApJ...761....3M} derive an average age of 4$\pm$1 Myr and a total stellar mass of 1.6$^{+1.6}_{-1.0} \times$ 10$^{5}$M$_{\odot}$ for the region.
-
-NGC 595 is the second brightest giant \hii{} region in the M33 galaxy.
-Using HST/WFPC-2 images \citet{1996AJ....111.1128M} found approximately 250 stars of the OB type, 13 Supergiants and 10 WR, confirming previous candidates.
-\citet{1993AJ....105.1400D} use optical photometry to propose 11 WR stars. 
-The ionizing output \(Q_0\) is \SI{e50.88}{photons.s^{-1}} (60 times higher compared to the Orion Nebula) and has a luminosity in \ha{} of \SI{e38.95}{erg.s^{-1}}\citep{2002MNRAS.329..481B}.
-The mean non-thermal linewidth in \ha{} is \SI{16.8 \pm 0.1}{km.s^{-1}} \citep{lagrois2009multi}.
-\citet{lagrois2011} present a kinematic study of the regions using optical emission lines and and radio 21 cm line observations and find that \ha{} shell morphology that is related to the stellar winds of the several massive stars located in its interior.
-They proposed Champagne flows at the periphery of the molecular cloud leading to accelerated ionized material.
-
-%They derived and age of 4.5\(\pm\)1.0 Myr consistent with \citet{1993AJ....105.1400D}.
-%\citet{2010MNRAS.402.1635R} used Integral Field Spectroscopy (IFS) to present a resolved study of the physical properties of the ionized gas and the ionized structure.
-%They also confirm the presence of previous cataloged WR stars and detect new candidates, and propose classical emission-line ratios as metallicity calibrators.
 
@@
 \label{sec:comparison-m33}
+For our NGC 595 \halpha\ emission line results there is no correspondence in the structure function from the previous investigations of \citet{lagrois2009multi} and \citet{lagrois2011}.
+Our observations cover the brightest part of the region and have smaller resolution than theirs.
+As a consequence \citet{lagrois2009multi} and \citet{lagrois2011} structure functions results does not cover scales $<$10 pc, where in our results the correlation is taking place.
+One big difference is that \citet{lagrois2011} apply a  filter to the velocity field to get rid of non-turbulent movements.
+As a comparison, for the filtered turbulent parameters they chose to represent the turbulent field, the derive a total  decorrelation length (\(C(\tau_0) = 0\)) of \SI{43}{pc} and the power-law index they provide is \num{1.55 \pm 0.01}.
+Their velocity centroid \(\sigma\) is \SI{5.92 \pm 0.15}{km.s^{-1}} while we have \SI{7.3\pm 2}{km. s^{-1}} which fall within the uncertainties.
+Due to the different observations and methodologies a direct comparison between structure functions is not possible.
 
@@
 
-For our NGC 595 \halpha\ emission line results there is no correspondence in the structure function from the previous investigations of \citet{lagrois2009multi} and \citet{lagrois2011}.
-Our observations cover the brightest part of the region and have smaller resolution than theirs.
-As a consequence \citet{lagrois2009multi} and \citet{lagrois2011} structure functions results does not cover scales $<$10 pc, where in our results the correlation is taking place.
-One big difference is that \citet{lagrois2011} apply a  filter to the velocity field to get rid of non-turbulent movements.
-As a comparison for the filtered turbulent parameters they present a correlation length of \SI{43}{pc} and the power-law index they provide is \num{1.55 \pm 0.01}.
-Other difference in their methodology is that they use the normalized structure function value of 2\(\sigma\pos\) to obtain the correlation length.
-%Using their unfiltered data the correlation length is \(\sim\) \SI{90}{pc} and using the same criteria as our it is \(\sim\) \SI{40}{pc} and the slope would be shallower. 
-Their velocity centroid \(\sigma\) is \SI{5.92 \pm 0.15}{km.s^{-1}} while we have \SI{7.3\pm 2}{km. s^{-1}} which fall within the uncertainties.
-Due to the different observations and methodologies a direct comparison between structure functions is not possible.
-
 \section{Additional covariance corner plots for model fits}

### 2022-12-19 strucfunc_paper.tex
New abstract

@@
 \begin{abstract}
-  Fluctuations of centroid velocities on the plane of the sky derived from spectroscopic observations are a powerful tool for studying the turbulent dynamics of emission line regions.
-  With the aim to characterize these velocities fluctuations we conduct a statistical analysis on a diverse sample of 9 \hii{} regions that spans more than two orders of magnitude in size and luminosity, and are located in the Milky Way and other Local Group galaxies.
-  In the statistical analysis we obtain the second-order structure function of the observed \halpha\ centroid velocity field.
-  We proposed a model for the structure function which takes into account observational constraints like the seeing (\(s_0\)), instrumental noise (\(B_{\text{noise}}\)) and size of the field of view (\(L\)).
-  The turbulent velocity field parameters like the velocity dispersion of the centroid velocity (\(\sigma\pos\)), the autocorrelation length (\(r_0\)) and a power-law index (\(m\)) are also considered in our model.
-  We fit our model to the observational structure function using a non-linear regression analysis which allow us to derive the parameters representing each velocity field.
-  The results for the 9 \hii{} regions are: \(\num{0.2} < s_0 \text{(FWHM)} < \SI{3.0}{arcsec}\), \(\num{0.003} < B_{\text{noise}} < \SI{6.0}{km^{-2}.s^{-2}}\),  \(\num{3} < \sigma\pos < \SI{19}{km.s^{-1}}\), \(\num{0.07} < r_0 < \SI{12}{pc}\) and \(\num{0.7}< m < \num{1.5}\).
-  The derived parameters are used to determine scaling relations between the physical properties of the regions like \halpha\ luminosity (\(L(H_{\alpha})\)), diameter (\(D\)) and the mean non-thermal linewidth (\(\langle \sigma_{los} \rangle\)).
-  We find that these relations are \(\sigma\pos \propto L(H_{\alpha})^{0.28 \pm 0.10}\) and \(r_0 \propto D^{0.95 \pm 0.32}\).
-  The \(\sigma\pos\) and \(\langle \sigma_{los} \rangle\) increase following a linear relation.
-  From the previous relations we found that the for our sample the \Mach{} number ranges from \( 0.5 - 2.5\) and that for ionized regions the energy is injected on scales smaller than 10\% of the size of each region.
-  We explain the derived power law slope by considering the effect of projection smearing and emissivity fluctuations.
-  We show that for ionized regions, the latter one, can be related to density fluctuations and use it as a diagnostic to determine the presence of turbulence-induced density fluctuations.
-
+  % Context
+  Radial velocity fluctuations on the plane of the sky
+  are a powerful tool for studying the turbulent dynamics of emission line regions.
+  % What we did
+  We conduct a systematic statistical analysis
+  of the observed \halpha\ centroid velocity field for
+  a diverse sample of 9 \hii{} regions,
+  spanning two orders of magnitude in size and luminosity,
+  that are located in the Milky Way and other Local Group galaxies
+  % How we did it
+  By fitting a simple analytic model to the second-order spatial structure function
+  of the velocity fluctuations, we extract three fundamental parameters:
+  the plane-of-sky velocity dispersion,
+  the correlation length,
+  and the power law slope.
+  We determine the credibility limits for these parameters in each region,
+  taking into account the observational limitations of noise,
+  atmospheric seeing, and the finite map size.
+  % What we found
+  The plane-of-sky velocity dispersion is found to be a better diagnostic
+  of turbulent motions than the line width, especially for lower
+  luminosity regions where the turbulence is subsonic.
+  The correlation length of velocity fluctuations is found to
+  be always roughly 2\% of the \hii{} region diameter,
+  implying that turbulence is driven on relatively small scales.
+  No evidence is found for a steepening of the power law slope of the structure function
+  in the transition from subsonic to supersonic turbulence,
+  which may be due to the countervailing effect of projection smoothing.
+  Ionized density fluctuations are too large to be explained by the action
+  of the turbulence in most cases, with the exception of the highest
+  luminosity sources.
+  A variety of behaviors are seen on scales larger than the correlation length,
+  with only a minority of sources showing evidence for homogeneity on the largest scales.
+  % In the statistical analysis we obtain the second-order structure function of the observed \halpha\ centroid velocity field.
+  % We proposed a model for the structure function which takes into account observational constraints like the seeing (\(s_0\)), instrumental noise (\(B_{\text{noise}}\)) and size of the field of view (\(L\)).
+  % The turbulent velocity field parameters like the velocity dispersion of the centroid velocity (\(\sigma\pos\)), the autocorrelation length (\(r_0\)) and a power-law index (\(m\)) are also considered in our model.
+  % We fit our model to the observational structure function using a non-linear regression analysis which allow us to derive the parameters representing each velocity field.
+  % The results for the 9 \hii{} regions are: \(\num{0.2} < s_0 \text{(FWHM)} < \SI{3.0}{arcsec}\), \(\num{0.003} < B_{\text{noise}} < \SI{6.0}{km^{-2}.s^{-2}}\),  \(\num{3} < \sigma\pos < \SI{19}{km.s^{-1}}\), \(\num{0.07} < r_0 < \SI{12}{pc}\) and \(\num{0.7}< m < \num{1.5}\).
+  % The derived parameters are used to determine scaling relations between the physical properties of the regions like \halpha\ luminosity (\(L(H_{\alpha})\)), diameter (\(D\)) and the mean non-thermal linewidth (\(\langle \sigma_{los} \rangle\)).
+  % We find that these relations are \(\sigma\pos \propto L(H_{\alpha})^{0.28 \pm 0.10}\) and \(r_0 \propto D^{0.95 \pm 0.32}\).
+  % The \(\sigma\pos\) and \(\langle \sigma_{los} \rangle\) increase following a linear relation.
+  % From the previous relations we found that the for our sample the \Mach{} number ranges from \( 0.5 - 2.5\) and that for ionized regions the energy is injected on scales smaller than 10\% of the size of each region.
+  % We explain the derived power law slope by considering the effect of projection smearing and emissivity fluctuations.
+  % We show that for ionized regions, the latter one, can be related to density fluctuations and use it as a diagnostic to determine the presence of turbulence-induced density fluctuations. 
 \end{abstract}
@@
 the number of contributing pairs.
-\textit{But this is not true -- we use constant fractional error with adjustments for small and large separations.}
 For most sources a fixed bin size of \SI{0.05}{dex} is used,

### 2022-12-19 strucfunc_paper.tex
Finish the acknowledgments

@@
 \usepackage{xcolor}
+
+\usepackage[spanish,es-minimal,english]{babel}
 
@@
 
-Based on observations made with KPNO telescopes
-\textit{complete KPNO acknowledgment}.
-Based on observations made with ESO Telescopes at the La Silla Paranal Observatory under programme IDs 076.C-0888 and 098.D-0211.
-Based on observations made as part of the Gaia-ESO Spectroscopic Survey
-\textit{complete Gaia-ESO acknowledgment}.
-Based on observations made with the WHT
-\textit{complete WHT acknowledgment}.
-We are grateful to Norberto Castro Rodríguez for providing maps of emission line velocity moments for 30 Doradus derived from MUSE-VLT observations.
-JGV acknowledges and thanks CONACyT-Mexico for the PhD research scholarship.
+Based in part on observations obtained at the Kitt Peak National Observatory,
+which is operated by the Association of Universities for Research in Astronomy, Inc.,
+under cooperative agreement with the National Science Foundation.
+Based in part on observations made with the MUSE and FLAMES spectrographs
+on VLT telescopes at the La Silla Paranal Observatory, ESO, Chile
+under programme IDs 188.B-3002, 076.C-0888 and 098.D-0211.
+Based in part on observations made with the William Herschel Telescope
+operated by the Isaac Newton Group of Telescopes,
+located at the Spanish
+\foreignlanguage{spanish}{Roque de los Muchachos}
+Observatory of the
+\foreignlanguage{spanish}{Instituto de Astrofisica de Canarias}
+on the island of La Palma. 
+We gratefully acknowledge financial support provided by
+\foreignlanguage{spanish}{%
+  Dirección General de Asuntos del Personal Académico,
+  Universidad Nacional Autónoma de México},
+through grant
+\foreignlanguage{spanish}{%
+  Programa de Apoyo a Proyectos de Investigación
+  e Inovación Tecnológica}
+IN109823.  
+We are grateful to Norberto Castro Rodríguez for providing maps of emission line velocity moments
+for 30~Doradus derived from MUSE-VLT observations.
+JGV acknowledges and thanks CONACyT-Mexico for a PhD research scholarship.
 

### 2022-12-19 strucfunc_paper.tex
Shorten abstract and add keywords

@@
   We conduct a systematic statistical analysis
-  of the observed \halpha\ centroid velocity field for
+  of the \halpha{} velocity field for
   a diverse sample of 9 \hii{} regions,
   spanning two orders of magnitude in size and luminosity,
-  that are located in the Milky Way and other Local Group galaxies
+  located in the Milky Way and other Local Group galaxies.
   % How we did it
-  By fitting a simple analytic model to the second-order spatial structure function
-  of the velocity fluctuations, we extract three fundamental parameters:
-  the plane-of-sky velocity dispersion,
+  By fitting a simple model to the second-order spatial structure function
+  of velocity fluctuations, we extract three fundamental parameters:
+  the velocity dispersion,
   the correlation length,
   and the power law slope.
-  We determine the credibility limits for these parameters in each region,
-  taking into account the observational limitations of noise,
+  We determine credibility limits for these parameters in each region,
+  accounting for observational limitations of noise,
   atmospheric seeing, and the finite map size.
@@
   implying that turbulence is driven on relatively small scales.
-  No evidence is found for a steepening of the power law slope of the structure function
+  No evidence is found for any steepening of the structure function
   in the transition from subsonic to supersonic turbulence,
-  which may be due to the countervailing effect of projection smoothing.
+  possibly due to the countervailing effect of projection smoothing.
   Ionized density fluctuations are too large to be explained by the action
-  of the turbulence in most cases, with the exception of the highest
-  luminosity sources.
+  of the turbulence in all but the highest luminosity sources.
   A variety of behaviors are seen on scales larger than the correlation length,
   with only a minority of sources showing evidence for homogeneity on the largest scales.
-  % In the statistical analysis we obtain the second-order structure function of the observed \halpha\ centroid velocity field.
-  % We proposed a model for the structure function which takes into account observational constraints like the seeing (\(s_0\)), instrumental noise (\(B_{\text{noise}}\)) and size of the field of view (\(L\)).
-  % The turbulent velocity field parameters like the velocity dispersion of the centroid velocity (\(\sigma\pos\)), the autocorrelation length (\(r_0\)) and a power-law index (\(m\)) are also considered in our model.
-  % We fit our model to the observational structure function using a non-linear regression analysis which allow us to derive the parameters representing each velocity field.
-  % The results for the 9 \hii{} regions are: \(\num{0.2} < s_0 \text{(FWHM)} < \SI{3.0}{arcsec}\), \(\num{0.003} < B_{\text{noise}} < \SI{6.0}{km^{-2}.s^{-2}}\),  \(\num{3} < \sigma\pos < \SI{19}{km.s^{-1}}\), \(\num{0.07} < r_0 < \SI{12}{pc}\) and \(\num{0.7}< m < \num{1.5}\).
-  % The derived parameters are used to determine scaling relations between the physical properties of the regions like \halpha\ luminosity (\(L(H_{\alpha})\)), diameter (\(D\)) and the mean non-thermal linewidth (\(\langle \sigma_{los} \rangle\)).
-  % We find that these relations are \(\sigma\pos \propto L(H_{\alpha})^{0.28 \pm 0.10}\) and \(r_0 \propto D^{0.95 \pm 0.32}\).
-  % The \(\sigma\pos\) and \(\langle \sigma_{los} \rangle\) increase following a linear relation.
-  % From the previous relations we found that the for our sample the \Mach{} number ranges from \( 0.5 - 2.5\) and that for ionized regions the energy is injected on scales smaller than 10\% of the size of each region.
-  % We explain the derived power law slope by considering the effect of projection smearing and emissivity fluctuations.
-  % We show that for ionized regions, the latter one, can be related to density fluctuations and use it as a diagnostic to determine the presence of turbulence-induced density fluctuations. 
 \end{abstract}
@@
 \begin{keywords}
-turbulence -- instrumentation: spectrographs -- ISM: HII regions, kinematics and dynamics
+HII regions -- ISM: kinematics and dynamics -- turbulence 
 \end{keywords}

### 2022-12-20 strucfunc_paper.tex
Javier changes before submission

@@
 % List of institutions
-$^{1}$Escuela Superior de Física y Matemáticas, Instituto Politécnico Nacional, Ciudad de México, México C.P. 07738\\
+$^{1}$Escuela Superior de Física y Matemáticas, Instituto Politécnico Nacional, U.P. Adolfo López Mateos, Zacatenco, Ciudad de México, México C.P. 07738\\
 $^{2}$Instituto de Radioastronomía y Astrofísica,
@@
 and whether or not smooth large-scale trends are first removed.
+Also, the field of view of the region would have an influence on \(\sigma^2\pos\).
 \citet{arthur2016turbulence} compared multiple studies of the

### 2022-12-20 table-fit-parameters.tex
Javier changes before submission

@@
 \begin{tabular}{cCCCCCCCC}\toprule
-\hii{}    &  \text{No. merged} & \text{Relatively}  & \text{Weight / No. points}     &  \text{Weight / No. points}     & \text{Max.}  & \text{Reduced} & \text{Autocorrelation } & \text{Acceptance}\\
-Region    &  \text{points} & \text{uncertainty} & \text{Small scales} &  \text{Large scales} & \text{separation}  & \text{chi-square} & \text{time} & \text{fraction}\\
+\hii{}    &  \text{No. points} & \text{Relatively}  & \text{Weight / No. points}     &  \text{Weight / No. points}     & \text{Max.}  & \text{Reduced} & \text{Autocorrelation } & \text{Acceptance}\\
+Region    &  \text{merged} & \text{uncertainty} & \text{Small scales} &  \text{Large scales} & \text{separation}  & \text{chi-square} & \text{time} & \text{fraction}\\
 \midrule
-Orion     & - & 0.02    &  -           &   -        & 0.5  & 0.82 & 60  & 0.55\\
-EON       & - & 0.025   &  2.0 / 3     &   -        & 0.5  & 0.70 & 527 & 0.45\\
-Lagoon    & 2 & 0.08    &  2.5 / 16    &   2.5 / 8  & 0.5  & 0.94 & 70  & 0.49\\
-Carina    & 2 & 0.055   &  3.0 / 14    &   3.0 / 4  & 0.5  & 0.94 & 72  & 0.50\\
-30 Dor    & 5 &  0.07   &  -           &   -        & 0.9  & 0.98 & 82  & 0.54\\
-NGC 346   & 3 & 0.04    &  -           &   -        & 0.8  & 0.83 & 76  & 0.51\\
-Hubble V  & - & 0.05    &  2.0 / 3     &   -        & 0.6  & 0.86 & 440 & 0.44\\
-Hubble X  & - & 0.032   &  2.0 / 4     &   2.0 / 6  & 0.5  & 0.73 & 83  & 0.49\\
-NGC 595   & - &  0.055  &  4.5 / 3     &   3.0 / 5  & 0.5  & 0.83 & 63  & 0.51\\
-NGC 604   & - &  0.095  &   2.5 / 3    &   1.25 / 2 & 0.5  & 0.71 & 124 & 0.44\\
+Orion     & 3 & 0.02    &  -           &   -        & 0.5L  & 0.82 & 60  & 0.55\\
+EON       & - & 0.03   &  2.0 / 3     &   3.0 / 3        & 0.7L  & 0.62 & 40 & 0.64\\
+Lagoon    & 2 & 0.08    &  2.5 / 16    &   2.5 / 8  & 0.5L  & 0.94 & 72  & 0.50\\
+Carina    & 2 & 0.055   &  3.0 / 14    &   3.0 / 4  & 0.5L  & 0.94 & 72  & 0.50\\
+30 Dor    & 5 &  0.07   &  -           &   -        & 0.9L  & 0.98 & 84  & 0.54\\
+NGC 346   & 3 & 0.02    &  -           &   -        & 0.5L  & 0.83 & 64  & 0.54\\
+Hubble V  & - & 0.05    &  2.0 / 3     &   -        & 0.6L  & 0.86 & 340 & 0.44\\
+Hubble X  & - & 0.032   &  2.0 / 4     &   2.0 / 6  & 0.5L  & 0.73 & 79  & 0.49\\
+NGC 595   & - &  0.055  &  4.5 / 3     &   3.0 / 5  & 0.5L  & 0.83 & 67  & 0.51\\
+NGC 604   & - &  0.08  &   2.0 / 3    &   1.5 / 2 & 0.5L  & 0.92 & 112 & 0.45\\
 \bottomrule

### 2023-04-14 strucfunc_paper.tex
Add data availability statement
Javier changes 2023-04-11

@@
 }
+
+%\usepackage{orcidlink}
 
@@
 the \hii{} regions in our sample.
-%We also discuss the implications of our results for the existence of a
-%Kolmogorov-type turbulent energy cascade and the nature of the driving mechanism
-%for the velocity fluctuations.
 Finally, in section~\ref{sec:conclusions} we present our conclusions.
@@
 % This means that the proposed structure function model describes within certain accuracy the velocity field fluctuations and that the parameters obtained can be interpreted as a true kinematic property of the \hii{} region velocity field.
-
-% \subsubsection{Diameter vs centroid velocity dispersion}
-
-% Other important relationship commonly used in the study of the interstellar medium is the diameter (or size) versus velocity dispersion.
-% Table \ref{tab:RestStats} shows this result for our sample in the forth row. 
-% This relation presents a significance level \(p > \num{0.05}\) but there are a couple of things worth mentioning.
-% Historically this relation is important following the work of \citet{1981MNRAS.194..809L} where he presents it in the context of molecular cloud complexes of many clouds, individual clouds, and clumps, so that size scales are studied over \(\num{0.1} < L < \SI{100}{pc}\) obtaining \(\sigma = 1.10 L ^{0.38}\).
-
-% This relation is interpreted in terms of turbulence, particularly the Kolmogorov model which predicts a index of \num{0.33} so that larger regions presents more turbulence, and smaller regions less turbulence.
-% It has been argued that this correlation method is not as powerful as using statistical functions \citep{1984ApJ...277..556S} but it is interesting that the index is consistent within different phases of the interstellar medium.
-% We obtain \(\log \sigma\pos = (0.25 \pm 0.17) \log D - (0.2 \pm 0.38)\) which is comparable with \citet{1981MNRAS.194..809L} results.
-
-% As we mentioned in section \ref{sec:L-vs-sigmapos} the fact that this relation holds up to previous investigation gives some certainty that the \(\sigma\pos\) value obtained via the proposed model of the structure function is valid.
-% This implying that the structure function, while not an absolute diagnostic, is a powerful tool in the research of \hii{} regions kinematics.
 
@@
 
+\section*{Data availability statement}
+\label{sec:data-avail-stat}
+All data and accompanying analysis programs used in this paper are available
+from the github repository \url{https://github.com/JavGVastro/PhD.Paper}.
+
 \bibliographystyle{mnras}
@@
 
-\section{Degradation of the structure function due to observational limitations}
+\textcolor{red}{\section{Degradation of the structure function due to observational limitations}}
 \label{sec:degr-struct-funct}
@@
 the correlation length \(r_0\) and the velocity field variance \(\sigma\pos^2\). 
-The synthetic velocity maps are created using a modified version of the \texttt{make\textunderscore{}extend} command from the \texttt{turbustat} Python library \citep{Koch2019AJ....158....1K},
-which creates a two-dimensional fractional Brownian Motion field
+The synthetic velocity maps are created using a modified version of the \textcolor{red}{\texttt{make\textunderscore{}3dfield}} command from the \texttt{turbustat} Python library \citep{Koch2019AJ....158....1K},
+which creates a \textcolor{red}{three-dimensional} fractional Brownian Motion field
 \citep{Miville-Deschenes:2003a}
 based on a power-law energy spectrum in wavenumber \(k\), \(E(k) \propto k^{-n}\),
-where \(n = m + 2\) and with random phases. 
+where \textcolor{red}{\(n = m + 3\)} and with random phases. 
 Our modification multiplies the energy spectrum by a
@@
 (section~\ref{sec:methods-apply}).
+
+\textcolor{red}{Then we proceed to create a 2D map from collapsing the 3D velocity field so we can take account of projection effects.
+We do this by obtaining the 1st-moment map of a PPV (position-position velocity) cube created using the \texttt{make\textunderscore{}ppv} command from \texttt{turbustat}.
+To create the PPV cube it was also necessary to create a 3D density field.
+The same \texttt{make\textunderscore{}3dfield} command was used to create  (along with the same parameters of the velocity field) a fluctuating density field.
+The density fluctuations are interpreted as emissivity fluctuations following as mentioned in section~\ref{sec:constancy-power-law}.}
+
 The maps generated by \texttt{turbustat} are spatially periodic,
@@
 
-% The artificial fields follows a given power law with a correlation length giving a variance value indicated as true \(\sigma^2\).
-% Using this true \(\sigma^2\) we obtain the true \(r_0\) and these values are used as a reference in the experiments to quantify the variations.
-
-\subsection{Finite box effects}
+\textcolor{red}{\subsection{Finite box effects}}
 \label{sec:finite-box-effects}
@@
     (a)\\
-    \includegraphics[width=\linewidth]{Figures/fake-finite-box-images}
+    \includegraphics[width=\linewidth]{Figures/fake-3d-finite-box-images-ems-fluct_sigE_1}
     \\[\bigskipamount]
     (b)\\
-    \includegraphics[width=\linewidth]{Figures/fake-finite-box-strucfunc}
+    \includegraphics[width=\linewidth]{Figures/fake-3d-finite-box-strucfunc-ems-fluct_sigE_1}
   \end{tabular}
@@
     (a)\\
-    \includegraphics[width=0.95\linewidth]{Figures/fake-finite-box-effect}
+    \includegraphics[width=0.95\linewidth]{Figures/fake-3d-finite-box-effect-ems-fluct_sigE_1}
     \\[\bigskipamount]
     (b)\\
-    \includegraphics[width=0.95\linewidth]{Figures/fake-finite-box-fits}
+    \includegraphics[width=0.95\linewidth]{Figures/fake-finite-box-fits-ems-fluct_sigE_1}
   \end{tabular}
@@
     The dashed line is an approximate analytic fit to these results
-    (\(1 - e^{L / 3.6r_0}\)).
+    (\textcolor{red}{\(1 - e^{L / 4.0r_0}\)}).
     (b)~Determination of \(\sigma^2\) and \(r_0\) from fitting the model
@@
 
-Figure~\ref{fig:finite-box}a shows how we test for finite map effects by taking
-a simulated velocity field of size \(512 \times 512\) pixels and iteratively
+\textcolor{red}{Figure~\ref{fig:finite-box}a} shows how we test for finite map effects by taking
+a simulated \textcolor{red}{1st moment map of} size \(512 \times 512\) pixels and iteratively
 dividing the full map into \(2 \times 2\) tiles.
@@
 The figure shows the result for \(j = 1\), 2, 3, and 4, in which the full map
-was generated with a correlation length \(r_0 = 16\)~pixels.
+was generated with a correlation length \textcolor{red}{\(r_0 = 32\)~pixels}.
 We then calculate the individual structure function for each tile and
 find the mean and standard deviation for each level of subdivision,
-showing the results in Figure~\ref{fig:finite-box}b.
+showing the results in \textcolor{red}{Figure~\ref{fig:finite-box}b}.
 It can be seen that the mean structure functions for each level
@@
 using the tile's own empirically measured structure function and variance.
-In Figure~\ref{fig:finite-box-effect}a we show how these
+In \textcolor{red}{Figure~\ref{fig:finite-box-effect}a} we show how these
 quantities deviate from the ``true'' values
@@
 heuristic model structure function of equation~\eqref{eq:model-strucfunc-ideal}.
-This is shown in Figure~\ref{fig:finite-box-effect}b, where it can be seen
-that the true parameters are reliably recovered so long as \(L > 3 r_0\),
+This is shown in \textcolor{red}{Figure~\ref{fig:finite-box-effect}b}, where it can be seen
+that the true parameters are reliably recovered so long as \textcolor{red}{\(L > 5 r_0\)},
 which is a roughly \SI{0.5}{dex} improvement over the purely empirical method.
@@
 
-\subsection{Effects of seeing}
+\textcolor{red}{\subsection{Effects of seeing}}
 \label{sec:effects-seeing-struc}
@@
     (a)\\
-    \includegraphics[width=\linewidth]{Figures/fake-seeing-nonp-thumbnails}\\
+    \includegraphics[width=\linewidth]{Figures/fake-3d-seeing-nonp-ems-fluct-thumbnails_sigE_1}\\
     (b)\\
-    \includegraphics[width=\linewidth]{Figures/fake-seeing-nonp-reduction}
+    \includegraphics[width=\linewidth]{Figures/fake-seeing-nonp-3d-ems-fluc_m4-reduction_sigE_1}
   \end{tabular}
@@
     \(B(r, s_0) / B(r, s_0 = 0)\) as a function of separation \(r\),
-    with a separation of \(2 s_0\) indicated by a large filled circle on each curve.
+    with a separation of \textcolor{red}{\(2.6 s_0\)} indicated by a large filled circle on each curve.
     Dashed lines shows the empirical fit discussed in the text.
@@
 
-Figure~\ref{fig:seeing-reduction}a illustrates how four different
-synthetic velocity fields of size \(256\times256\) pixels
-and correlation length \(r_0 = \SI{16}{pixels}\)
+\textcolor{red}{Figure~\ref{fig:seeing-reduction}a} illustrates how four different
+synthetic \textcolor{red}{1st-moment maps of} size \(256\times256\) pixels
+and correlation length \textcolor{red}{\(r_0 = \SI{32}{pixels}\)}
 are affected by progressively broader gaussian seeing,
@@
 with different colors representing different values of \(s_0\).
-Results are shown for a power-law slope of \(m = 1.2\)
+Results are shown for a power-law slope of \textcolor{red}{\(m = 1.0\)}
 but we find very similar behaviour for other values of \(m\) within the range
@@
 these results to within better than 10\%:
+
+%\begin{equation}\label{eq:seeingemp2}
+%S(r; s_0, r_0) = \frac{e^{-s_0 / r_0}}{1+(2s_0 / r)^{2a}} ,
+%\end{equation}
+
+\textcolor{red}{
 \begin{equation}\label{eq:seeingemp2}
-S(r; s_0, r_0) = \frac{e^{-s_0 / r_0}}{1+(2s_0 / r)^{2a}} ,
+S(r; s_0, r_0) = 
+  \left [
+\left (1+\frac{1.25 s_0}{r_0} \right) 
+\left(1+ \left (\frac{2.6 s_0}{r} \right) ^{2a} \right)
+  \right ]^{-1} ,
 \end{equation}
-which is shown by dashed lines in Figure \ref{fig:seeing-reduction}b.
+}
+
+which is shown by dashed lines in \textcolor{red}{Figure \ref{fig:seeing-reduction}b}.
 The optimum value of the index \(a\) in this equation varies slightly
@@
 The maximum \(B(r)\) value is \SI{104}{km^{2}.s^{-2}} at a separation of \SI{30}{pc}. 
-For NGC 595 we see that the structure function plateau at this maximum \(B(r)\) value, which implies that the observed \(\sigma\pos^2\) is affected by the observational constraints.
+%For NGC 595 we see that the structure function plateau at this maximum \(B(r)\) value, which implies that the observed \(\sigma\pos^2\) is affected by the observational constraints.
 Until \(r_0 \sim \SI{55}{pc} \) the structure functions remains closely to the 'true' \(2\sigma\pos^2\), for the largest scale there is a decrease between  \(\SI{55}{pc} < r < \SI{110}{pc} \) where the structure function plateaus at the 'observed' \(2\sigma\pos^2\).

### 2023-04-16 strucfunc_paper.tex
Fix up the layout of the sections marked in red
Don't use \textcolor{} around structural elements like section
headings since it messes up the spacing.. Instead, use \color{red}
inside the argument

@@
 \appendix
-
-\textcolor{red}{\section{Degradation of the structure function due to observational limitations}}
+\colorlet{RED}{red}
+\section{\color{red}Degradation of the structure function due to observational limitations}
 \label{sec:degr-struct-funct}
@@
 
-\textcolor{red}{\subsection{Finite box effects}}
+\subsection{\color{red}Finite box effects}
 \label{sec:finite-box-effects}
@@
     \\[\bigskipamount]
-    (b)\\
-    \includegraphics[width=\linewidth]{Figures/fake-3d-finite-box-strucfunc-ems-fluct_sigE_1}
+    (b)\\ \includegraphics[width=\linewidth]{Figures/fake-3d-finite-box-strucfunc-ems-fluct_sigE_1}
   \end{tabular}
@@
   \begin{tabular}{@{} l @{}}
-    (a)\\
-    \includegraphics[width=0.95\linewidth]{Figures/fake-3d-finite-box-effect-ems-fluct_sigE_1}
+    (a)\\ \includegraphics[width=0.95\linewidth]{Figures/fake-3d-finite-box-effect-ems-fluct_sigE_1}
     \\[\bigskipamount]
-    (b)\\
-    \includegraphics[width=0.95\linewidth]{Figures/fake-finite-box-fits-ems-fluct_sigE_1}
+    (b)\\ \includegraphics[width=0.95\linewidth]{Figures/fake-finite-box-fits-ems-fluct_sigE_1}
   \end{tabular}
@@
     The dashed line is an approximate analytic fit to these results
-    (\textcolor{red}{\(1 - e^{L / 4.0r_0}\)}).
+    (\(\color{red}1 - e^{L / 4.0r_0}\)).
     (b)~Determination of \(\sigma^2\) and \(r_0\) from fitting the model
@@
 
-\textcolor{red}{\subsection{Effects of seeing}}
+\subsection{\color{red}Effects of seeing}
 \label{sec:effects-seeing-struc}
@@
 these results to within better than 10\%:
-
 %\begin{equation}\label{eq:seeingemp2}
@@
 %\end{equation}
-
-\textcolor{red}{
-\begin{equation}\label{eq:seeingemp2}
+\begin{equation}\label{eq:seeingemp2}\color{red}
 S(r; s_0, r_0) = 
@@
 \end{equation}
-}
-
 which is shown by dashed lines in \textcolor{red}{Figure \ref{fig:seeing-reduction}b}.
@@
 
+\clearpage
 \section{\boldmath Notes on individual \hii{} regions}
@@
 
-The Orion Nebula (M42) is the prototype of a galactic \hii{} region located at a distance of 440 pc \citetext{\SI{1}{\arcsecond} = \SI{0.002}{pc} ; \citealp{2008AJ....136.1566O}}.
+The Orion Nebula (M42) is the prototype of a galactic \hii{} region located at a distance of 440 pc \citetext{\SI{1}{\arcsecond} = \SI{0.002}{pc}; \citealp{2008AJ....136.1566O}}.
 The O7 V star \(\uptheta^{1}\) Ori C is the most luminous and hottest star with an ionizing flux \(Q_0\) of \SI{e49.12}{photons.s^{-1}} \citep{2006A&A...448..351S} which translates to luminosity in \ha{} of \SI{e37.18}{erg.s^{-1}}.
@@
 
-\
-
-\textit{Orion core}
+\paragraph*{Orion core}
 
@@
 
-\textit{EON}
+\paragraph*{EON}
 
@@
 
-The Lagoon Nebula (M8, NGC6523) is located at a distance of 1 250 pc \citetext{\SI{1}{\arcsecond} = \SI{0.006}{pc} ; \citealp{2005A&A...430..941P}}.
+The Lagoon Nebula (M8, NGC6523) is located at a distance of 1250 pc \citetext{\SI{1}{\arcsecond} = \SI{0.006}{pc} ; \citealp{2005A&A...430..941P}}.
 It contains the young stellar cluster NGC6530 and the region is illuminated by different massive stars of spectral types O and B, the hottest being 9 Sgr, type O4V \citep{Damiani:2017b}.

### 2023-04-16 strucfunc_paper.tex
Rewrite description of projection of simulated maps

@@
 
-\textcolor{red}{Then we proceed to create a 2D map from collapsing the 3D velocity field so we can take account of projection effects.
-We do this by obtaining the 1st-moment map of a PPV (position-position velocity) cube created using the \texttt{make\textunderscore{}ppv} command from \texttt{turbustat}.
-To create the PPV cube it was also necessary to create a 3D density field.
-The same \texttt{make\textunderscore{}3dfield} command was used to create  (along with the same parameters of the velocity field) a fluctuating density field.
-The density fluctuations are interpreted as emissivity fluctuations following as mentioned in section~\ref{sec:constancy-power-law}.}
+{\color{red}%
+  In order to create 2D plane-of-sky velocity map, we first
+  create 3D cubes of fluctuating velocity and emissivity
+  with \texttt{make\textunderscore{}3dfield},
+  then transform to a PPV (position-position velocity) cube
+  using the \texttt{make\textunderscore{}ppv} command from \texttt{turbustat},
+  assuming thermal broadening with FWHM of \SI{20}{\kilo\meter\per\second},
+  as appropriate for a hydrogen line at \(T \approx \SI{e4}{K}\).
+  Finally, the first velocity moment map is obtained
+  by integrating along the velocity axis.
+
+  For the emissivity field, we assume a log-normal distribution
+  with RMS fractional width
+  \(\shortsig{E} = 1.0\) that is typical of our sources
+  (see footnote~\ref{fn:brightness-fluctuations} and Figure~\ref{fig:brightness-pdfs} above).
+  We further assume that there is no correlation between the emissivity
+  and velocity fluctuations and that their spatial correlation length
+  and power law indices are equal.\footnote{%
+    We have investigated departures from these assumptions and found that they
+    make very little difference to the results.
+  }
+}
 
@@
 with RMS width \(s_0 = 1\) to \SI{32}{pixels}.
+\textcolor{red}{%
+  Note that the seeing is applied to each velocity channel of the
+  PPV emissivity cube before integrating to find the 2D velocity map.
+}
 We calculate the structure function \(B(r)\) for each map and show

### 2023-04-17 strucfunc_paper.tex
Revisions to main body of  paper

@@
 \newcommand\Mach{\ensuremath{\mathcal{M}}}
+\newcommand\longsig[1]{\ensuremath{\langle \delta #1^2 \rangle^{1/2} / #1_0}}
+\newcommand\shortsig[1]{\ensuremath{\sigma_{#1/#1_0}}}
 
@@
 \begin{equation}\label{eq:ffs}
-   S(r) = \frac{
-    e^{-s_0 / r_0}
-  }{
-    1+(2s_0 / r)^{2 / 3}
-  } ,
+  \color{red}
+  S(r) =
+  \left[ \frac{1}{1 + a_1 s_0 / r_0} \right]
+  \left[ \frac{1}{1 + (a_2 s_0 / r)^{a_3}} \right]
+  ,
+  %  S(r) = \frac{
+  %   e^{-s_0 / r_0}
+  % }{
+  %   1+(2s_0 / r)^{2 / 3}
+  % } ,
 \end{equation}
@@
   \(2 (2 \ln 2)^{1/2} s_0 \approx 2.35 s_0\).
-}
+},
 and \(r_0\) is the correlation length.
+\textcolor{red}{%
+  The exact values of the constants \(a_1\), \(a_2\), \(a_3\)
+  are found to depend slightly on the power law slope \(m\)
+  and the magnitude of the emissivity fluctuations \(\shortsig{E}\)
+  (see Appendix~\ref{sec:degr-struct-funct}).
+  We adopt the compromise values \(a_1 = 1.25\),
+  \(a_2 = 2.6\), and \(a_3 = 1.5\), which fit the numerical results to
+  within 20\% for \(0.8 < m < 1.2\) and \(0.5 < \shortsig{E} < 2.0\).}
 An example is shown by the green line in Figure~\ref{fig:model-strucfunc}a.
@@
 but the larger amplitude of the fluctuations in these sources means
-that the fitted model parameters are still tightly constrained.
+that the fitted model parameters are nevertheless tightly constrained.
 
@@
 In other cases, large discrepancies are found,
-which are probably to a combination of methodological differences
+which are probably caused by a combination of methodological differences
 and real variations due to the inhomogeneity of the
@@
 In principle,  the variation of \(\sigma\pos\) could be
-measured in  a ``macro-pixels'' of size \(2 r_0\),
+measured in ``macro-pixels'' of size \(2 r_0\),
 but a minimum size of  \( 3 r_0\) is necessary to reliably determine \(r_0\)
@@
 is assumed for all sources.
-\newcommand\longsig[1]{\ensuremath{\langle \delta #1^2 \rangle^{1/2} / #1_0}}
-\newcommand\shortsig[1]{\ensuremath{\sigma_{#1/#1_0}}}
 The RMS fractional width of density fluctuations in a turbulent medium,
@@
 with \(s_0\) as an additional free parameter for the models.
+\clearpage
 
@@
 
-\clearpage
 \section{\boldmath Notes on individual \hii{} regions}

### 2023-04-18 strucfunc_paper.tex
Move appendix D to be a separate PDF file

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\newlength\SFwidth
+\setlength\SFwidth{0.45\textwidth}
+\newcommand\SFtwograph[2]{%
+  \includegraphics[width=\SFwidth]{Figures/sf-emcee-#1}
+  &  \includegraphics[width=\SFwidth]{Figures/sf-emcee-#2}
+}
+\newcommand\SFtwocorner[2]{%
+  \includegraphics[width=\SFwidth]{Figures/corner-emcee-#1}
+  &  \includegraphics[width=\SFwidth]{Figures/corner-emcee-#2}
+}
+
+\newcommand\sffigg[2]{%
+  \begin{tabular}{@{}ll@{}}
+    (a)& (b)\\
+    \SFtwograph{#1}{#2}
+  \end{tabular}%
+}
+\newcommand\sffigggg[4]{%
+  \begin{tabular}{@{}ll@{}}
+    (a)& (b)\\
+    \SFtwograph{#1}{#2}\\
+    (c)& (d)\\
+    \SFtwograph{#3}{#4}\\
+  \end{tabular}%
+}
+\newcommand\sfcfig[1]{%
+  \includegraphics[width=\SFwidth]{Figures/corner-emcee-#1}%
+}  
+\newcommand\sfcfigg[2]{%
+  \begin{tabular}{@{}ll@{}}
+    (a)& (b)\\
+    \SFtwocorner{#1}{#2}
+  \end{tabular}%
+}
+\newcommand\sfcfigggg[4]{%
+  \begin{tabular}{@{}ll@{}}
+    (a)& (b)\\
+    \SFtwocorner{#1}{#2}\\
+    (c)& (d)\\
+    \SFtwocorner{#3}{#4}\\
+  \end{tabular}%
+}
 
@@
 \label{sec:results}
-
-\newlength\SFwidth
-\setlength\SFwidth{0.45\textwidth}
-\newcommand\SFtwograph[2]{%
-  \includegraphics[width=\SFwidth]{Figures/sf-emcee-#1}
-  &  \includegraphics[width=\SFwidth]{Figures/sf-emcee-#2}
-}
-\newcommand\SFtwocorner[2]{%
-  \includegraphics[width=\SFwidth]{Figures/corner-emcee-#1}
-  &  \includegraphics[width=\SFwidth]{Figures/corner-emcee-#2}
-}
-
-\newcommand\sffigg[2]{%
-  \begin{tabular}{@{}ll@{}}
-    (a)& (b)\\
-    \SFtwograph{#1}{#2}
-  \end{tabular}%
-}
-\newcommand\sffigggg[4]{%
-  \begin{tabular}{@{}ll@{}}
-    (a)& (b)\\
-    \SFtwograph{#1}{#2}\\
-    (c)& (d)\\
-    \SFtwograph{#3}{#4}\\
-  \end{tabular}%
-}
-\newcommand\sfcfig[1]{%
-  \includegraphics[width=\SFwidth]{Figures/corner-emcee-#1}%
-}  
-\newcommand\sfcfigg[2]{%
-  \begin{tabular}{@{}ll@{}}
-    (a)& (b)\\
-    \SFtwocorner{#1}{#2}
-  \end{tabular}%
-}
-\newcommand\sfcfigggg[4]{%
-  \begin{tabular}{@{}ll@{}}
-    (a)& (b)\\
-    \SFtwocorner{#1}{#2}\\
-    (c)& (d)\\
-    \SFtwocorner{#3}{#4}\\
-  \end{tabular}%
-}
 
@@
 \label{sec:addit-covar-corn}
-Supplementary online-only material.
-%\clearpage
-
-\begin{figure*}
-  \centering
-  \sfcfigggg{OrionS}{OrionLH}{M8}{CarC}
-  \caption{
-    Corner plots of covariances between
-    fitted model parameters
-    of \ha{} structure function
-    for Galactic \hii{} regions.
-  }
-  \label{fig:corner-Galactic}
-\end{figure*}
-
-\begin{figure*}
-  \centering
-  \sfcfigg{N346}{Dor}
-  \caption{
-    Same as figure~\ref{fig:corner-Galactic}
-    except for Magellanic Cloud \hii{} regions. 
-  }
-  \label{fig:corner-MC}
-\end{figure*}
-
-\begin{figure*}
-  \centering
-  \sfcfigggg{HV}{HX}{N595}{N604H}
-  \caption{
-    Same as figure~\ref{fig:corner-Galactic}
-    except for \hii{} regions in more distant
-    Local Group Galaxies.
-  }
-  \label{fig:corner-ExtraGal}
-\end{figure*}
-
-\input{table-fit-parameters}
-
+Supplementary material
+\href{https://github.com/will-henney/javier-strucfunc-paper/blob/main/supplementary_material_strucfunc_paper.pdf}
+{available online}.
+%
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\clearpage
 % Don't change these lines

### 2023-04-18 strucfunc_paper.tex
Finish revision of Orion in Appendix C

@@
 %In the southwest direction of the Huygens region there is a drop in the brightness as one approach a much larger region called Extended Orion Nebula \citetext{EON henceforth;  \citealp{2008Sci...319..309G}}
-The position of the Orion Nebula near the side of the Orion Molecular Cloud (OMC-1) make it an ongoing star formation with a large population of young star, some of which are the sources of stellar jets and Herbig-Haro objects \citep{1993ApJ...410..696O}.
-Its physical properties and kinematics, along its stellar population is documented in \citet{2001ARA&A..39...99O}.
+The position of the Orion Nebula on the near side of the Orion Molecular Cloud (OMC-1) makes it an ongoing site of star formation with a large population of young stars,
+some of which are sources of stellar jets and Herbig-Haro objects \citep{1993ApJ...410..696O}.
+Its physical properties and kinematics, along with its stellar population is documented in \citet{2001ARA&A..39...99O}.
 
@@
 Using the observed structure function and by simple linear interpolation the value of \(\sigma\pos^2 = \SI{9}{km^{2}.s^{-2}}\) is obtained at \(r_0 = \SI{0.05}{pc} \) (as comparison to the derived values from our model which are \(\sigma\pos^2 = \SI{13}{km^{2}.s^{-2}}\) and \(r_0 = \SI{0.07}{pc} \)).
-The observed value of \(2\sigma\pos^2\) corresponds to \(r = \SI{0.13}{pc} \) (this \(r\) value would be analog to the total decorrelation length \(\tau_0\), see section~\ref{sec:comp-with-prev}). 
-The maximum \(B(r)\) value correspond to \SI{23}{km^{2}.s^{-2}} at \(r = \SI{0.30}{pc}\).
-From this value the \(B(r)\) values decrease and it is possible to observe a downturn in the structure function from to \SI{7}{km^{2}.s^{-2}} at \(r =  \SI{0.5}{pc}\). 
-This 'hook' behavior is described by the tapered fluctuations (see section~\ref{sec:limit-model-struct}).
-If we consider the first valid point of \(B(r)\) to be above the derived value of \(s_0\), which corresponds to \SI{0.3}{km^{2}.s^{-2}} at \(r = \SI{0.003}{pc} \) and use a linear relation to calculate the slope for \(\sigma\pos^2\) and \(2\sigma\pos^2\) we obtain \num{0.66} and \num{0.89}, respectively, while our derived value is \num{1}.
+The observed value of \(2\sigma\pos^2\) corresponds to \(r = \SI{0.13}{pc} \),
+which corresponds to the total decorrelation length \(\tau_0\), see section~\ref{sec:comp-with-prev}). 
+The maximum \(B(r)\) value is \SI{23}{km^{2}.s^{-2}} at \(r = \SI{0.30}{pc}\),
+beyond which the structure function declines to \SI{7}{km^{2}.s^{-2}} at \(r =  \SI{0.5}{pc}\). 
+This ``hook'' behavior can be explained by a radial gradient in the
+amplitude of the velocity fluctuations (see section~\ref{sec:limit-model-struct}).
+% If we consider the first valid point of \(B(r)\) to be above the derived value of \(s_0\), which corresponds to \SI{0.3}{km^{2}.s^{-2}} at \(r = \SI{0.003}{pc} \) and use a linear relation to calculate the slope for \(\sigma\pos^2\) and \(2\sigma\pos^2\) we obtain \num{0.66} and \num{0.89}, respectively, while our derived value is \num{1}.
 
@@
 to achieve a credible fit using the full model.
-We therefore fix the power slope to \(m = 1\),
-which implies that noise makes a significant contribution at all scales
+We therefore fix the power slope at \(m = 1\),
+which implies that noise must make a significant contribution at all scales
 in order to reproduce the observed flat structure function.
-In turn, this implies that the true \(\sigma^2\pos = \SI{5}{km^2.s^{-2}}\),
+In turn, this implies that a true \(\sigma^2\pos = \SI{5}{km^2.s^{-2}}\),
 which is lower than the \SI{7}{km^2.s^{-2}}
@@
 (compare green and orange lines in Figure~\ref{fig:strucfunc-fit-Galactic}b).
-The derived correlation length is \SI{0.5}{pc} which is above the \SI{0.3}{pc} required to determine the true correlation length but below the \SI{0.9}{pc} which guarantees that the fit can reliable determine \(r_0\).
-The structure function at large scales resembles the tapered behavior of inhomogeneous fluctuations just like the core.
+% The derived correlation length is \SI{0.5}{pc} which is above the \SI{0.3}{pc} required to determine the true correlation length but below the \SI{0.9}{pc} which guarantees that the fit can reliable determine \(r_0\).
+Comparing the extended nebula with the core for the size scales where they overlap
+(\num{0.1} to \SI{0.5}{pc}), one sees that \(B(r)\) is roughly four times smaller
+in the EON than in the core for the same value of \(r\).
+This is further evidence for a decline in the fluctuation amplitude with radius,
+as mentioned above.
+Also consistent with this is a hook-like downturn in \(B(r)\) for \(r > 2 pc\)
+for the EON region.
+The fact that the derived \(r_0\) is larger for the EON region than the core
+(\SI{0.5}{pc} versus \SI{0.07}{pc}) means that the correlation length is also inhomogeneous,
+tending to increase from the center to the outskirts of the nebula.
 
@@
 
-\citet{arthur2016turbulence} carried out a complete analysis by calculating the structure function of different emission lines in the inner Orion Nebula.
-On their work, they only consider one Gaussian component fit.
-They find tendency that higher ionization lines presents higher  dispersion and the steepness of the structure function slope. 
-They also make a comparison with previous work (see table~5 on their paper) founding a a broad agreement in results and the dependence between ionization energy and slope and dispersion value.
+\citet{arthur2016turbulence} calculated the structure function of different emission lines in the inner Orion Nebula with varying degrees of ionization. 
+They found that higher ionization lines show a larger velocity dispersion
+and a steeper structure function slope. 
+They also make a comparison with previous work (see Table~5 on their paper), finding a broad agreement in results and the dependence between ionization energy and slope and dispersion value.
 The work by \citet{arthur2016turbulence} is the only one that has calculated the structure function for the \ha{} emission line, for this reason it will be the only one that we use for comparison.
-The power-law index obtained by \citet{arthur2016turbulence} are \(m \sim 1.2 \pm 0.1\) for \halpha\ and [OIII] emission lines and for [SII] and [NII] they found \(m \sim 0.8 \pm 0.1\). 
+The power-law index obtained by \citet{arthur2016turbulence} are \(m \sim 1.2 \pm 0.1\) for \halpha\ and [\ion{O}{3}] emission lines and for [\ion{S}{2}] and [\ion{N}{2}] they found \(m \sim 0.8 \pm 0.1\).
 The correlation length for all lines is \SI{\sim 0.05}{pc}, value obtained when the structure function is equal to \(\sigma\pos^2= \SI{9.37}{km^{2 }.s^{-2}}\).
 For the same \halpha\ observations, but considering high-velocity objects, we obtained a value of \num{1.07 \pm 0.03}, a correlation length of \SI{0.068 \pm 0.004}{pc} and \(\sigma\pos^2 = \SI{13 \pm 1}{ km^{2}.s^{-2}}\).
-The difference with respect to this last value is due to the fact that \citet{arthur2016turbulence} masked areas with high values of centroid velocity (see figure~2 on their paper).
-Since there are the same observations there is a good agreement in the structure function.
+The difference with respect to this last value is due to the fact that \citet{arthur2016turbulence} masked areas with high values of centroid velocity (see Figure~2 on their paper).
+Since they are based on the same observational data,
+the differences of order 30\% between their results and our own
+are entirely due to the different methodologies employed.
 

### 2023-04-18 strucfunc_paper.tex
More tweaks to Orion section

@@
 They also make a comparison with previous work (see Table~5 on their paper), finding a broad agreement in results and the dependence between ionization energy and slope and dispersion value.
-The work by \citet{arthur2016turbulence} is the only one that has calculated the structure function for the \ha{} emission line, for this reason it will be the only one that we use for comparison.
-The power-law index obtained by \citet{arthur2016turbulence} are \(m \sim 1.2 \pm 0.1\) for \halpha\ and [\ion{O}{3}] emission lines and for [\ion{S}{2}] and [\ion{N}{2}] they found \(m \sim 0.8 \pm 0.1\).
-The correlation length for all lines is \SI{\sim 0.05}{pc}, value obtained when the structure function is equal to \(\sigma\pos^2= \SI{9.37}{km^{2 }.s^{-2}}\).
-For the same \halpha\ observations, but considering high-velocity objects, we obtained a value of \num{1.07 \pm 0.03}, a correlation length of \SI{0.068 \pm 0.004}{pc} and \(\sigma\pos^2 = \SI{13 \pm 1}{ km^{2}.s^{-2}}\).
-The difference with respect to this last value is due to the fact that \citet{arthur2016turbulence} masked areas with high values of centroid velocity (see Figure~2 on their paper).
+% The work by \citet{arthur2016turbulence} is the only one that includes the \ha{} emission line,
+% for this reason it will be the only one that we use for comparison.
+The power-law index obtained by \citet{arthur2016turbulence} is \(m \sim 1.17 \pm 0.08\) for \halpha,
+% and [\ion{O}{3}] emission lines and for [\ion{S}{2}] and [\ion{N}{2}] they found \(m \sim 0.8 \pm 0.1\). 
+with a correlation length of \SI{\sim 0.05}{pc} and velocity variance
+\(\sigma\pos^2= \SI{9.4}{km^{2 }.s^{-2}}\).
+This compares with our own values of
+% For the same \halpha\ observations, but considering high-velocity objects, we obtained a value of 
+\(m = 1.07 \pm 0.03\), \(r_0 = \SI{0.068 \pm 0.004}{pc}\)
+and \(\sigma\pos^2 = \SI{13 \pm 1}{ km^{2}.s^{-2}}\). 
 Since they are based on the same observational data,
-the differences of order 30\% between their results and our own
-are entirely due to the different methodologies employed.
+the differences of order 30\% between the \citet{arthur2016turbulence}
+results and our own are entirely due to the different methodologies employed.
+In the case of \(\sigma\pos^2\), their value is lower than ours since
+they masked out the locations of known high-velocity Herbig-Haro flows, whereas we do not.
 

### 2023-04-20 strucfunc_paper.tex
Finish edits to Lagoon section in Appendix C

@@
 A number of fifteen interferograms have been taken with different pointing directions of the telescope's optical axis in the nebula with an exposure time between 10 and 40 minutes. 
-The exposures are overlapped and fall into one square of a grid with a width of \SI{1}{arcmin} centered at \(\uptheta^{1}\)Ori C.
+The exposures are overlapped and fall into one square of a grid with a width of \SI{1}{arcmin} centered at \(\uptheta^{1}\)Ori~C.
 
@@
 A detailed description of the model fit is given in section~\ref{sec:example-results-orion} and will not be repeated here.
-Using the observed structure function and by simple linear interpolation the value of \(\sigma\pos^2 = \SI{9}{km^{2}.s^{-2}}\) is obtained at \(r_0 = \SI{0.05}{pc} \) (as comparison to the derived values from our model which are \(\sigma\pos^2 = \SI{13}{km^{2}.s^{-2}}\) and \(r_0 = \SI{0.07}{pc} \)).
-The observed value of \(2\sigma\pos^2\) corresponds to \(r = \SI{0.13}{pc} \),
-which corresponds to the total decorrelation length \(\tau_0\), see section~\ref{sec:comp-with-prev}). 
-The maximum \(B(r)\) value is \SI{23}{km^{2}.s^{-2}} at \(r = \SI{0.30}{pc}\),
+% The observed value of \(2\sigma\pos^2\) corresponds to \(r = \SI{0.13}{pc} \),
+% which corresponds to the total decorrelation length \(\tau_0\), see section~\ref{sec:comp-with-prev}). 
+At scales larger than the correlation length,
+a maximum \(B(r)\) value of \SI{23}{km^{2}.s^{-2}} is seen at \(r = \SI{0.30}{pc}\),
 beyond which the structure function declines to \SI{7}{km^{2}.s^{-2}} at \(r =  \SI{0.5}{pc}\). 
@@
 amplitude of the velocity fluctuations (see section~\ref{sec:limit-model-struct}).
+
+An alternative approach to determine the velocity variance and correlation length
+is to empirically measure \(\sigma\pos^2\) from the observations and then to use linear
+interpolation on the measured structure function to find the point where \(B(r_0) = \sigma\pos^2\).
+This yields \(\sigma\pos^2 = \SI{9}{km^{2}.s^{-2}}\) and \(r_0 = \SI{0.05}{pc} \),
+as compared to the model-derived values of \(\sigma\pos^2 = \SI{13}{km^{2}.s^{-2}}\) and \(r_0 = \SI{0.07}{pc} \)).
+The main reason for the discrepancy is the finite box effect
+discussed in section~\ref{sec:finite-box-effects} above, where it is shown
+that for homogeneous fluctuations it is necessary to sample a map of size \(L > 10 r_0\)
+in order to empirically determine \(\sigma\pos^2\).
+In the case of the Orion core observations, \(L = 7 r_0\),
+so the fluctuations are not fully sampled, leading
+to the empirical \(\sigma\pos^2\) being an underestimate.
+However, given the evidence for a radial gradient in the amplitude of the velocity fluctuations,
+it could be argued that the finite box effect is not so important as it would be for homogeneous fluctuations
+and it is instead the model-derived value of \(\sigma\pos^2\) that is an overestimate.
+
 % If we consider the first valid point of \(B(r)\) to be above the derived value of \(s_0\), which corresponds to \SI{0.3}{km^{2}.s^{-2}} at \(r = \SI{0.003}{pc} \) and use a linear relation to calculate the slope for \(\sigma\pos^2\) and \(2\sigma\pos^2\) we obtain \num{0.66} and \num{0.89}, respectively, while our derived value is \num{1}.
@@
 as mentioned above.
-Also consistent with this is a hook-like downturn in \(B(r)\) for \(r > 2 pc\)
+Also consistent with this is a hook-like downturn in \(B(r)\) for \(r > \SI{2}{pc}\)
 for the EON region.
@@
 
-The Lagoon Nebula (M8, NGC6523) is located at a distance of 1250 pc \citetext{\SI{1}{\arcsecond} = \SI{0.006}{pc} ; \citealp{2005A&A...430..941P}}.
-It contains the young stellar cluster NGC6530 and the region is illuminated by different massive stars of spectral types O and B, the hottest being 9 Sgr, type O4V \citep{Damiani:2017b}.
-Optically, the brightest part of the nebula is called 'Hourglass nebula' which surrounds and obscures the O7 star Herschel 36 \citep{1986AJ.....91..870W}.
-These stars gives an ionizing flux \(Q_0\) of \SI{e49.41}{photons.s^{-1}} (2 times higher compared to the Orion Nebula) and the luminosity in \ha{} of \SI{e37.47}{erg.s^{-1}} \citep{1984ApJ...287..116K}.
+The Lagoon Nebula (M8, NGC~6523) is located at a distance of \SI{1250}{pc}  \citetext{\SI{1}{\arcsecond} = \SI{0.006}{pc} ; \citealp{2005A&A...430..941P}}.
+It contains the young stellar cluster NGC~6530 and the region is illuminated by different massive stars of spectral types O and B, the hottest being 9~Sgr, type O4V \citep{Damiani:2017b}.
+The optically brightest part of the nebula is denoted the ``Hourglass nebula'',
+which is illuminated by the O7 star Herschel~36 \citep{1986AJ.....91..870W}.
+These stars gives an ionizing flux \(Q_0 = \SI{e49.41}{photons.s^{-1}}\) (2 times higher than in the Orion Nebula) and the luminosity in \ha{} is \SI{e37.47}{erg.s^{-1}} \citep{1984ApJ...287..116K}.
 The mean non-thermal linewidth in \ha{} is \SI{11.7 \pm 1.6}{km.s^{-1}} \citep{1973ApJ...183..851B}.
-The velocity field shows several expanding shells, related to the stellar population, and the massive protostar M8East-IR \citep{1984ApJ...278..170S} indicating that recent star formation. 
-A blueshifted, neutral layer is also in very good agreement with predictions of champagne-flow models of blister \hii{} regions \citep{Damiani:2017b}. 
+Molecular gas and ongoing star formation are present in the region around
+Herschel~36 \citep{Arias:2006e, Tiwari:2018a} and the lower-luminosity region
+M8~East \citep{1984ApJ...278..170S, Tiwari:2020a}.
+% The velocity field shows several expanding shells, related to the stellar population, and the massive protostar M8East-IR \citep{1984ApJ...278..170S} indicating that recent star formation.
+% A blueshifted, neutral layer is also in very good agreement with predictions of champagne-flow models of blister \hii{} regions \citep{Damiani:2017b}. 
 The properties of the nebula are reviewed by \citet{2008hsf2.book..533T}.
@@
 
-We follow the same procedure we use to describe the observed structure function of the Orion Nebula for the rest of the regions.
-The Figure~\ref{fig:strucfunc-fit-Galactic}c shows the structure function of the Lagoon nebula.
-This region presents a non-uniform behavior below the derived correlation length but still it is possible to see the characteristic ascending values of the structure function.
-The value of the observed \(\sigma\pos^2 = \SI{8}{km^{2}.s^{-2}}\) is obtained at \(r_0 = \SI{1}{pc} \) (in this case there is a good agreement with the derived values from our model which are \(\sigma\pos^2 = \SI{7}{km^{2}.s^{-2}}\) and \(r_0 = \SI{1}{pc} \)).
-The observed value of \(2\sigma\pos^2\) corresponds to \(r = \SI{2.5}{pc} \).
-From this point the structure function shows a 'reversed hook' behavior, which mean that there is a decrease in \(B(r)\) values up until \(r_0 = \SI{4}{pc} \)) for a value of \SI{11}{km^{2}.s^{-2}}, which from this point the structure function ascends until it reaches \SI{66}{km^{2}.s^{-2}} around \SI{20}{pc}.
-This may be because our observations doesn't cover and outer correlation region (see sections~\ref{sec:D-vs-r0}) or an indication of some periodic behavior (see sections~\ref{sec:limit-model-struct}).
-There aren't any points affected by the seeing (RMS) which has a value of \SI{0.01}{pc} (\(s_0\)=\SI{3.5}{\arcsecond}).
-If we consider the first point of this \(B(r)\) to be valid, which corresponds to \SI{0.55}{km^{2}.s^{-2}} at \(r = \SI{0.05}{pc} \) the slope for \(\sigma\pos^2\) and \(2\sigma\pos^2\) we obtain \num{0.89} and \num{0.86}, respectively, while our derived value is \num{1.26}.
+% We follow the same procedure we use to describe the observed structure function of the Orion Nebula for the rest of the regions.
+Figure~\ref{fig:strucfunc-fit-Galactic}c shows the structure function of the Lagoon nebula.
+The model fit gives \(\sigma\pos^2 = \SI{7 \pm 1}{km^{2}.s^{-2}}\), \(r_0 = \SI{1 \pm 0.2}{pc} \), and \(m = 1.26 \pm 0.2\).
+In this case, there is good agreement between the model value and empirically value of \(\sigma\pos^2\),
+indicating that finite box effects are unimportant.
+On the other hand, the model-derived \(m\) is steeper than would be naively derived
+from the observations, which is a symptom of the effects  of noise.
+At separations smaller than the correlation length, the structure function shows irregular oscillations about the mean ascending trend,
+which are a symptom of the relatively small number of spatial points in this source.
+
+At scales much larger than the correlation length
+the structure function begins to increase again, reaching a value of \SI{66}{km^{2}.s^{-2}} at \SI{20}{pc},
+which is greater than \(9 \sigma\pos^2\).
+As discussed in section~\ref{sec:evid-inhom-at}, this may be a sign of periodicity
+or a large-scale gradient in the velocity field.
+
+% There aren't any points affected by the seeing (RMS) which has a value of \SI{0.01}{pc} (\(s_0\)=\SI{3.5}{\arcsecond}).
+% If we consider the first point of this \(B(r)\) to be valid, which corresponds to \SI{0.55}{km^{2}.s^{-2}} at \(r = \SI{0.05}{pc} \) the slope for \(\sigma\pos^2\) and \(2\sigma\pos^2\) we obtain \num{0.89} and \num{0.86}, respectively, while our derived value is \num{1.26}.
 
@@
 \label{sec:comparison-lagoon}
-The Lagoon Nebula was previously studied by \citet{Chakraborty:1999a} using the [\ion{O}{3}] \Wav{5007} line.
-The structure function was computed on an area of \num{1} \(\times\) \SI{1}{arcmin^2} centered at Herschel 36.
-Compared to our which data spans between \num{0.1} and \SI{10}{pc}), their results cover smaller scales, between \num{0.012} and \SI{0.3}{pc}.
-\citet{Chakraborty:1999a} report a  law behavior of \(m = 0.46\)
-for all its range.
-They mentioned the nebular gas physical conditions and the presence of gradients as responsible for the discrepancy of the theoretical 2/3 value.
-No flattening of the structure function at the largest scales was seen, but that is to be expected due to the finite box effect (see Appendix~\ref{sec:finite-box-effects}), but argue the possibility that the turbulent energy input is at more than one spacial scale.
-With the aid of the 2D-autocorrelation function (using \(1/e\)) they found a characteristic turbulent scale of \SI{0.12}{pc}.
-We found \(r_0 = \SI{1 \pm 0.1}{pc}\) for this nebula, which is several times larger than the region mapped by \citet{Chakraborty:1999a}.
-On the other hand, the magnitude of the velocity dispersion found by these authors greatly exceeds our own measurements.
-For instance, they find \(B(r) = \SI{278}{km^2.s^{-2}}\) at \SI{0.2}{pc}, whereas we find \(B(r) \approx \SI{2}{km^2.s^{-2}}\) at the same scale, which corresponds to a discrepancy of more than a factor of a hundred in \(\sigma^2\pos\).
-This may be due in part to the fact that \citet{Chakraborty:1999a}
-observed a small and atypical part of the nebula known as the
-Hourglass region, which includes a cluster of very young stars
-\citep{Arias:2006e}. 
-In the case of the Orion Nebula we found that the velocity dispersion
-of the central region was larger than that of the extended nebula
-and this could be an example of a similar phenomenon,
-albeit to a more extreme degree.
-\citet{Chakraborty:1999a} mentioned a good agreement between \citet{1986ApJ...304..767O}  which show different HII regions structure functions slopes between \(m = 0.18 - 0.45\) and \citet{1987ApJ...317..676O} which cover an area around 9 Sgr in M8.
-The first investigation in the Lagoon nebula structure function is from \citet{1970A&A.....8..486L} which claims that a value of \(m = 2/3\) satisfies their observations agreeing with the Kolmogorov Law.
+The first investigation of the Lagoon nebula structure function is from \citet{1970A&A.....8..486L},
+who use Fabry-Perot observation of the \ha{} line to probe scales
+between \SI{0.7}{pc} and \SI{7}{pc}.
+They find a rising power-law behavior with slope of \(m = 0.64\),
+which is slightly smaller than the value we derive.
+However, given the very coarse binning in separation of their structure function,
+and the fact that they do not account for noise or the flattening of the structure function at large scales,
+their results are broadly consistent with ours,
+with the value of \( \sigma\pos^2 = \SI{16}{km^{2}.s^{-2}}\) at \(r = \SI{3.5}{pc}\) being almost
+identical to our own value at that scale.
+
+More recent measurements of the structure function of the Lagoon Nebula
+have used the [\ion{O}{3}] \Wav{5007} line and have probed smaller scales.
+\citep{1987ApJ...317..676O} used longslit observations at a small number of position angles
+to study the structure function over an area \(\num{2} \times \SI{2}{arcmin^2}\),
+centered on the nebula's principal ionizing star, 9~Sgr.
+However, it is hard to compare their results to ours, as they carry out
+a Gaussian decomposition of the line profile into two components, A and B,
+and analyse the structure function of the two components separately.
+The total variance of component A (the stronger and narrower of the two)
+is \SI{2}{km^{2}.s^{-2}} at scales \(< \SI{1}{pc}\),
+which is significantly smaller than our value of \SI{7}{km^{2}.s^{-2}},
+but this is not surprising since they are probing scales smaller than the
+correlation length and therefore suffer from a severe finite-box effect.
+Component~B on the other hand shows a much larger variance
+of \SI{13}{km^{2}.s^{-2}} and an essentially flat structure function.
+
+Another [\ion{O}{3}] \Wav{5007} study \citep{Chakraborty:1999a}
+calculated the structure function in the Hourglass region of the nebula:
+an area of \(\num{1} \times \SI{1}{arcmin^2}\) centered at Herschel~36.
+As compared to the data used in this paper, which spans between \num{0.1} and \SI{10}{pc}),
+their results cover smaller scales, between \num{0.012} and \SI{0.3}{pc}.
+\citet{Chakraborty:1999a} report a rising power-law behavior with slope of \(m = 0.46\) over the entire range.
+No flattening of the structure function at the largest scales was seen, but that is to be expected
+if the correlation length is larger than the size of the region mapped.
+The amplitude of the fluctuations is much higher (\(\sigma^2\pos = \SI{130}{km^2.s^{-2}}\)
+than we find for the wider nebula (\(\sigma^2\pos = \SI{7}{km^2.s^{-2}}\)),
+suggesting an even more extreme version of the inhomogeneity that we find in the Orion Nebula.
+This is supported by the fact that the Hourglass region also shows
+much larger line widths than the rest of the nebula \citep{Chakraborty:1999a},
+which is probably a symptom of the ongoing active star formation in that region.
 

### 2023-04-20 strucfunc_paper.tex
Javier changes 2023-04-20

--- 2023-04-18 strucfunc_paper.tex
@@
   S(r) =
-  \left[ \frac{1}{1 + a_1 s_0 / r_0} \right]
-  \left[ \frac{1}{1 + (a_2 s_0 / r)^{a_3}} \right]
+  \left[ \frac{1}{1 + 1.25 s_0 / r_0} \right]
+  \left[ \frac{1}{1 + (2.6 s_0 / r)^{1.5}} \right]
   ,
@@
 and \(r_0\) is the correlation length.
-\textcolor{red}{%
-  The exact values of the constants \(a_1\), \(a_2\), \(a_3\)
-  are found to depend slightly on the power law slope \(m\)
-  and the magnitude of the emissivity fluctuations \(\shortsig{E}\)
-  (see Appendix~\ref{sec:degr-struct-funct}).
-  We adopt the compromise values \(a_1 = 1.25\),
-  \(a_2 = 2.6\), and \(a_3 = 1.5\), which fit the numerical results to
-  within 20\% for \(0.8 < m < 1.2\) and \(0.5 < \shortsig{E} < 2.0\).}
 An example is shown by the green line in Figure~\ref{fig:model-strucfunc}a.
@@
   \left [
-\left (1+\frac{1.25 s_0}{r_0} \right) 
-\left(1+ \left (\frac{2.6 s_0}{r} \right) ^{2a} \right)
+\left (1+a_1\frac{s_0}{r_0} \right) 
+\left(1+ \left (a_2 \frac{ s_0}{r} \right) ^{a_3} \right)
   \right ]^{-1} ,
@@
 which is shown by dashed lines in \textcolor{red}{Figure \ref{fig:seeing-reduction}b}.
+\textcolor{red}{%
+  The exact values of the constants \(a_1\), \(a_2\), \(a_3\)
+  are found to depend slightly on the power law slope \(m\)
+  and the magnitude of the emissivity fluctuations \(\shortsig{E}\).
+  We adopt the compromise values \(a_1 = 1.25\),
+  \(a_2 = 2.6\), and \(a_3 = 1.5\), which fit the numerical results to
+  within 20\% for \(0.8 < m < 1.2\) and \(0.5 < \shortsig{E} < 2.0\).}
 The optimum value of the index \(a\) in this equation varies slightly

### 2023-04-21 reply-to-referee.txt
Write the reply to referee

			 ______________________

			    REPLY TO REFEREE

			  García-Vázquez et al
			 ______________________

,----
| will be happy to recommend the manuscript for publication after some
| clarification of some details:
| 
| To study the Finite box effects, as well as that of seeing the authors
| do an interesting exercise with idealized data (as fractional Brownian
| motion -fBm- 2D data modified to include a correlation taper).  This
| approach is very clear, but there is one issue that requires
| attention, and that is that of the projection from a 3D field to a 2D
| field.  In reality the density/velocity fields are three-dimensional
| but some information is lost in the projection to a 2D map.  For the
| exercise presented in appendix A, the authors use a 2D map that was
| modified to include the proper spectral index (n_2D = m +2) and a
| correlation length r_0, in reality one would have a 3D map with a
| spectral index (n_3D = m +3), which if integrated along the line of
| sight would change the spectral index from n_3D to n_2D (and within
| the transition some inertial range could be 'lost') .
| 
| In other words in the current version of the paper the r_0 is entirely
| in the plane of the sky, while in reality should correspond to the 3D
| field, and at the same time the transition from a 3D to a 2D map could
| curve more the structure functions.  I believe that it would be
| beneficial to obtain the 2D map from collapsing a 3D fBm (with an
| index m+3) and the same exponential taper used and verify that the
| main results hold, or discuss this an additional limitation.
`----

We thank the referee for the insightful comments. It is quite true that
our approach of directly simulating 2d maps is not strictly correct and
that we should really simulate three dimensional fields and then project
them down to two dimensions for further analysis. So, we have done this
and the results of Appendix A have now been completely replaced. It
turns out that the new results are extremely similar to the old ones, so
the changes to the text (highlighted in red in the manuscript) are
minimal.

One new issue that we had to grapple with in order to use this more
realistic approach is that we needed to simulate the three dimensional
emissivity field (assumed proportional to ionized density squared for H
alpha) as well as the three dimensional velocity field.  For this, we
used the results shown in our Figure 12 to estimate the variance in the
emissivity, which we assumed to follow a log-normal distribution.  For
the spatial properties of the emissivity fluctuations, we assumed that
the correlation length and power law index was the same as for the
velocity and that the velocity and emissivity fluctuations have no
mutual correlation.  We investigated three different values of the rms
emissivity dispersion: sigma_E = 0, 1, and 2 (in units of the mean
value). The results were very similar in all cases, and we only show the
sigma_E = 1 case in the paper, since this is the most appropriate for
the majority of our regions.

With the new results, we found an improved analytic approximation for
the effects of seeing (equation 15 and A1). We have therefore re-run all
of the model fits in section 4, but the results change by less than 1%.

We have also taken the opportunity to improve some of the descriptions
of individual regions in Appendix C.

### 2023-04-21 strucfunc_paper.tex
Write the reply to referee

@@
 so that \(s_0\) is indeterminate in the model fits
-(note the flat posterior histograms for \(s_0\) in Fig.~\ref{fig:corner-Galactic}c and d).
+%(note the flat posterior histograms for \(s_0\) in Fig.~\ref{fig:corner-Galactic}c and d).
 In addition, the effects of noise are also much greater,
@@
 but at the same time the degeneracies between parameters
-(Figure~\ref{fig:corner-ExtraGal})
+%(Figure~\ref{fig:corner-ExtraGal})
 lead to large uncertainties in the determination \(m\).
@@
 To that end, the last column in Table~\ref{tab:Res} lists the FWHM seeing width for each fit in units of arcsec.
-Disregarding the 3 sources where only upper limits can be determined,
-the mean and standard deviation are \SI{0.95(30)}{arcsec},
+Disregarding the 5 sources where only upper limits can be determined,
+the mean and standard deviation are \SI{1.17(20)}{arcsec},
 which is perfectly consistent with expectations for seeing from ground-based observations.
@@
 then the anticorrelation between \(m\) and \(s_0\)
-(see Figure~\ref{fig:corner-ExtraGal}a, b)
+%(see Figure~\ref{fig:corner-ExtraGal}a, b)
 would decrease the inferred \(m\) for NGC~595 while increasing it for NGC~604,
@@
 The relationship we find is
-\(\log r_0 = (0.95 \pm 0.33) \log D_{\hii} - (1.6 \pm 0.7)\),
+\(\log r_0 = (0.95 \pm 0.32) \log D_{\hii} - (1.6 \pm 0.7)\),
 which is very close to linear,
@@
 but that an accurate \(r_0\) can still be recovered from model fitting
-so long as \(r_0 < 0.33 L\).
+so long as \(r_0 < 0.20 L\).
 From our results (Table~\ref{tab:Res}) we find that \(r_0 \approx (0.08 \pm 0.01) L\),
@@
 The relationship we obtain is
-\( \langle \sigma\los \rangle = (1.04 \pm 0.44) \sigma\pos + (7.3 \pm 2.9)\),
+\( \langle \sigma\los \rangle = (1.03 \pm 0.43) \sigma\pos + (7.4 \pm 2.8)\),
 which can be compared with previous results
@@
 for which we obtain the power-law fit
-\(\log \sigma\pos = (0.25 \pm 0.10) \log L(\ha) - (9.9 \pm 4.0)\). 
+\(\log \sigma\pos = (0.25 \pm 0.11) \log L(\ha) - (9.1 \pm 4.3)\). 
 It is common to study the \(L\)--\(\sigma\) relationship,
@@
 This yields \(\sigma\pos^2 = \SI{9}{km^{2}.s^{-2}}\) and \(r_0 = \SI{0.05}{pc} \),
-as compared to the model-derived values of \(\sigma\pos^2 = \SI{13}{km^{2}.s^{-2}}\) and \(r_0 = \SI{0.07}{pc} \)).
+as compared to the model-derived values of \(\sigma\pos^2 = \SI{13}{km^{2}.s^{-2}}\) and \(r_0 = \SI{0.07}{pc} \).
 The main reason for the discrepancy is the finite box effect

### 2023-04-21 strucfunc_paper.tex
Javier changes 2023-04-21

@@
 This yields \(\sigma\pos^2 = \SI{9}{km^{2}.s^{-2}}\) and \(r_0 = \SI{0.05}{pc} \),
-as compared to the model-derived values of \(\sigma\pos^2 = \SI{13}{km^{2}.s^{-2}}\) and \(r_0 = \SI{0.07}{pc} \).
+as compared to the model-derived values of \(\sigma\pos^2 = \SI{13}{km^{2}.s^{-2}}\) and \(r_0 = \SI{0.07}{pc} \)).
 The main reason for the discrepancy is the finite box effect

### 2023-04-21 strucfunc_paper.tex
Finish revisions of Carina in Appendix C

--- 2023-04-21 strucfunc_paper.tex
@@
 The model fit gives \(\sigma\pos^2 = \SI{7 \pm 1}{km^{2}.s^{-2}}\), \(r_0 = \SI{1 \pm 0.2}{pc} \), and \(m = 1.26 \pm 0.2\).
-In this case, there is good agreement between the model value and empirically value of \(\sigma\pos^2\),
+In this case, there is good agreement between the model value and empirical value of \(\sigma\pos^2\),
 indicating that finite box effects are unimportant.
@@
 
-The Carina nebula is a large star-forming complex located at a distance of 2 350 pc \citetext{\SI{1}{\arcsecond} = \SI{0.01}{pc} ; \citealp{2006ApJ...644.1151S}}.
-It contains young clusters like Trumpler 14 and 16, and Collinder 228 from the Car OB1 association, one of the largest OB associations in the Galaxy.
-This OB association has more than 65 stars earlier than B0, and several Wolf-Rayet (WR) stars and the most luminous star is the blue variable $\eta$ Car.
+The Carina nebula is a large star-forming complex located at a distance of \SI{2 350}{pc} \citetext{\SI{1}{\arcsecond} = \SI{0.01}{pc}; \citealp{2006ApJ...644.1151S}}.
+It contains young clusters like Trumpler~14 and~16, and Collinder~228 from the Car~OB1 association, one of the largest OB associations in the Galaxy.
+This OB association has more than 65 stars earlier than B0, and several Wolf-Rayet (WR) stars and the most luminous star is the blue variable $\eta$~Car.
 The ionizing flux \(Q_0\) is \SI{e50.95}{photons.s^{-1}} \citep{2008hsf2.book..138S} (60 times higher compared to the Orion Nebula) and the luminosity in \ha{} of \SI{e39.01}{erg.s^{-1}}.
-As a star formation region, it presents several phenomena related with young stars as evaporating protoplanetary discs, erosion of large dust pillars and the triggering of a second generation of embedded stars and Herbig-Haro objects, to mention some \citetext{see \citealp{2008hsf2.book..138S} and reference therein}.
-This region can be consider as a bridge between the detailed star-formation regions like Orion, and much more distant regions like 30 Doradus.
+As a high-mass star formation region, it presents several phenomena related to young stars,
+such as evaporating protoplanetary discs, erosion of large dust pillars, and the triggering of a second generation of embedded stars and Herbig-Haro objects \citetext{see \citealp{2008hsf2.book..138S} and reference therein}.
+This region is at an intermediate scale between nearby regions like Orion
+that are dominated by a single star, and giant star formation regions such as 30~Doradus.
 
@@
 
-The Figure~\ref{fig:strucfunc-fit-Galactic}d shows the structure function of the Carina nebula.
-As the Lagoon nebula, the structure function of Carina also shows a non-uniform and a more disperse behavior below the correlation length.
-The value of the observed \(\sigma\pos^2 = \SI{18}{km^{2}.s^{-2}}\) is obtained at \(r_0 = \SI{0.5}{pc} \) (in this case there is a good agreement with the derived values from our model which are \(\sigma\pos^2 = \SI{18}{km^{2}.s^{-2}}\) and \(r_0 = \SI{0.5}{pc} \)).
-The observed value of \(2\sigma\pos^2\) corresponds to \(r = \SI{1.6}{pc} \).
-Above this separation, at larges scales, the structure function of the Carina nebula follows a pattern that resembles the homogeneous fluctuation of Figure~\ref{fig:model-strucfunc}a.
-Also, it can be argue that at large scales the behavior does not reflect purely the homogeneous fluctuations. 
-It seems that there are two  oscillating pattern at large scales.
-The first one, from \(r = \SI{1.7}{pc} \) to \SI{6}{pc} which has an spatial wavelength of \SI{\sim 2}{pc} and a dispersion of \SI{1}{km^{2}.s^{-2}}.
-The second one when \(r >\)\SI{6}{pc} until \SI{7}{pc} with a dispersion of \SI{3.5}{km^{2}.s^{-2}}.
-This fluctuations are around the value of 2\(\sigma^2\pos\) so it is possible that the dispersion is artificial because of the multi-fiber observations (see section~\ref{sec:flames-multi-fiber}).
-There aren't any points affected by the seeing (RMS) which has a value of \SI{0.015}{pc} (\(s_0\)=\SI{3.4}{\arcsecond}).
-If we consider the first point of this \(B(r)\) to be valid, which corresponds to \SI{4}{km^{2}.s^{-2}} at \(r = \SI{0.01}{pc} \) the slope for \(\sigma\pos^2\) and \(2\sigma\pos^2\) we obtain \num{0.38} and \num{0.43}, respectively, while our derived value is \num{1.16}.
+Figure~\ref{fig:strucfunc-fit-Galactic}d shows the structure function of the Carina nebula.
+The model fit gives \(\sigma\pos^2 = \SI{18 \pm 2}{km^{2}.s^{-2}}\), \(r_0 = \SI{0.6 \pm 0.1}{pc} \), and \(m = 1.2 \pm 0.3\).
+Again there is good agreement between the model value and empirically measured
+value of \(\sigma\pos^2\),
+indicating that finite box effects are unimportant. In addition, both noise and seeing are
+found to be unimportant. 
+Similarly to the Lagoon nebula,
+the structure function of Carina also shows a non-uniform and irregular behavior
+below the correlation length, which can again be ascribed to the sparse spatial sampling.
+As a result of this, the power-law slope determination is not very precise.
+
+On scales larger than the correlation length,
+the structure function of the Carina nebula is remarkably flat
+for \(r = 2\) to \SI{6}{pc},
+in good agreement with the prediction of homogeneous fluctuations
+(Figure~\ref{fig:model-strucfunc}a).
+But at the largest scales accesible to our observations, there is evidence for low-amplitude
+periodic fluctuations with a wavelength of \(\lambda \approx \SI{8}{pc}\),
+which corresponds to the typical separation
+between the individual star clusters that make up the complex
+(for instance, between Tr~14 and Tr~16).
 

### 2023-04-21 strucfunc_paper.tex
Nearly finished 30 Dor revision. All except comparison with previous

@@
 
-The 30 Doradus (Tarantula Nebula) nebula is located at a distance of \SI{49.9}{kpc} \citetext{\SI{1}{\arcsecond} = \SI{0.24}{pc} ; \citealp{2013Natur.495...76P}}.
+The giant \hii{} region 30~Doradus (Tarantula Nebula) is located at a distance of \SI{49.9}{kpc} \citetext{\SI{1}{\arcsecond} = \SI{0.24}{pc} ; \citealp{2013Natur.495...76P}}.
 It is a luminous star-forming region in the LMC (Large Magellanic Cloud) and is the most luminous complex in the Local Group \citep{1984ApJ...287..116K}.
-The central ionized region spans for \SI{40}{pc} and host the massive dense star cluster R136
-with ionizing output \(Q_0\) of is \SI{e51.40}{photons.s^{-1}} \citep{2020MNRAS.499.1918B} and the luminosity in \ha{} of \SI{e39.46}{erg.s^{-1}} (194 times higher compared to the Orion Nebula).
-%\citep{1991IAUS..148..145W}. %Note: check the bibliographic format
+The star cluster that energizes the region is NGC~2070, with a central core (known as R136)
+with ionizing luminosity \(Q_0 = \SI{e51.40}{photons.s^{-1}}\)  \citep{2020MNRAS.499.1918B},
+which produces an \ha{} luminosity of \SI{e39.46}{erg.s^{-1}} (200 times the Orion Nebula)
+for the central ionized region of size \SI{40}{pc}.
 The mean non-thermal linewidth in \ha{} is \SI{22}{km.s^{-1}} \citep{2013A&A...555A..60T}.
-It host the active star forming region NGC 2070 \citep{2013AJ....145...98W} where the star-formation rate has recently peaked \citep{2015ApJ...811...76C} and host a population of OB and WR stars \citep{2011A&A...530A.108E}.
+Star formation is still ongoing in NGC~2070 \citep{2013AJ....145...98W},
+although the star-formation rate peaked about \SI{4}{Myr} ago
+\citep{2015ApJ...811...76C} and it currently hosts some of the most massive stars known
+\citep{Kalari:2022p}
+and several Wolf-Rayet stars \citep{2011A&A...530A.108E}.
 This nebula is commonly used as a comparison for extragalactic star-forming regions.
@@
 The 30~Doradus structure function is shown in Figure~\ref{fig:strucfunc-fit-MC}a.
-The value of the observed \(\sigma\pos^2 = \SI{252}{km^{2}.s^{-2}}\) is obtained at \(r_0 = \SI{3}{pc} \) (the derived values from our model are \(\sigma\pos^2 = \SI{297}{km^{2}.s^{-2}}\) and \(r_0 = \SI{4}{pc} \)).
-The observed value of \(2\sigma\pos^2\) corresponds to \(r = \SI{13}{pc} \).
-The maximum \(B(r)\) value correspond to \SI{654}{km^{2}.s^{-2}} at \(r = \SI{21}{pc}\).
-From this value the \(B(r)\) values decrease and it is possible to observe a downturn in the structure function from to \SI{250}{km^{2}.s^{-2}} at \(r =  \SI{38}{pc}\) following the tapered fluctuations behavior.
-The seeing (RMS) value derived for this regions is \SI{0.16}{pc} (\(s_0\)=\SI{1.5}{\arcsecond}) and just one point of the structure function is below this value.
-Considering the first point above this \(s_0\) value to be valid, which corresponds to \SI{15}{km^{2}.s^{-2}} at \(r = \SI{0.2}{pc} \) the slope for \(\sigma\pos^2\) and \(2\sigma\pos^2\) we obtain \num{1.04} and \num{0.84}, respectively, while our derived value is \num{0.85}.
+The model-derived parameters are \(\sigma\pos^2 = \SI{297 \pm 40}{km^{2}.s^{-2}}\),
+\(r_0 = \SI{4\pm 1}{pc} \)), and \(m = 0.85 \pm 0.1\).  The empirically-derived variance is about
+15\% smaller, indicative of a moderate finite-box effect. On either measure,
+the region is a clear outlier in our sample, with a value of \(\sigma\pos^2\) that is
+more than three times larger than any other of our regions,
+as can be graphically appreciated from the velocity histograms in Figure~\ref{fig:pdfs}.
+
+At scales larger than the correlation length, the structure function has a maximum
+at \(r = \SI{20}{pc}\) and then falls at the largest scales.
+This behavior is similar to that seen in the Orion Nebula and might
+likewise be evidence for a decline of the fluctuation amplitude towards the outskirts.
+On the other hand, the sharp upward turn towards the maximum in \(B(r)\) is more reminiscent
+of the expectations for a periodic fluctuation (Figure~\ref{fig:model-strucfunc}b),
+in which case the wavelength would be of order the size of the map.
+Evidence for such a pattern can be seen directly in the velocity map
+(Figure~\ref{fig:velocity-maps}) as a red-blue asymmetry between the south-east
+and north-west, which is also seen in the kinematics of the O~stars
+\citep{Henault-Brunet:2012h}
+and has been interpreted as evidence for rotation of the cluster.
 

### 2023-04-23 strucfunc_paper.tex
Finish section on 30 Dor

@@
 
-\citet{Melnick:2021x} also investigated the structure function in 30~Doradus finding that the structure function is entirely flat on scales from \num{3} to \SI{200}{pc}.
-This does not agree with our results, since we establish the existence of correlations up to the maximum value of the structure function that occurs at \SI{20}{pc}, separation where a value of 2\(\sigma\pos^2\) is reached.
-The VLT FLAMES/GIRAFFE observations of \citet{Melnick:2021x} may not have had the resolution to resolve the correlations at small separations, however an inspection of its velocity map (figure 7 in their work) shows that the velocity distribution is not completely random.
-\citet{Melnick:2021x} \(\sigma\pos\) values range from \num{11.6} to \SI{18.2}{km.s^{-1}} for a diverse type of fits (see figure~15 on their paper).
-The first attempt at characterizing turbulence in a giant extragalactic \hii{} region, GEHR, was done by \citet{1961MNRAS.122....1F} with the 30~Doradus complex, finding no indication of turbulent motions between spatial scales of \num{10} and \SI{100}{pc}.
-The \citet{1961MNRAS.122....1F} is in broad agreement with the \citet{Melnick:2021x} results in which they consider profiles classified as singles.
-The large scales of our structure function falls between the two previous results.
-The previous happens at \SI{5}{pc} and \SI{40}{pc} (which covers small-to-intermediate scale for previous investigations and large scales for us) and for \(B(r)\) between \num{250} to \SI{600}{km^{2}.s^{-2}} where our results show a downward 'hook' pattern.
+\citet{1961MNRAS.122....1F} investigated the structure function in 30~Doradus by using
+spectra at \(N = 37\) different points, spread over a region of diameter \SI{150}{pc}
+and with minimum separation of \SI{4}{pc}.
+Velocities were measured by combining results from multiple spectral lines in
+the blue spectral region, the strongest being of [\ion{O}{2}], [\ion{O}{3}], and \hb{}.
+They found an essentially flat \(B(r)\) for \(r > \SI{10}{pc}\) with
+\(\sigma\pos^2 = \SI{130}{km.s^{-1}}\), which is roughly half the value that we determine for the
+central region of the nebula (of diameter \SI{30}{pc}).
+This implies that the amplitude of the fluctuations is falling with radius,
+similar to what we inferred above for the Orion Nebula.
+For the smallest separations, of order \SI{4}{pc}, they found that \(B(r)\) declined
+significantly, although an exact measurement was hampered by uncertainties in the
+correction for the effects of noise.
+This behavior is consistent with our own value of \(r_0 = \SI{4}{pc}\),
+suggesting that the correlation length is not greatly different
+in the wider area covered by their study.
+This is a clear difference from the Orion Nebula,
+where we find a significantly larger correlation length
+in the extended nebula than in the core.
+
+\citet{Melnick:1987a} used Fabry-Perot observations in \ha{} and [\ion{O}{3}]
+from \citet{Smith:1972a} to calculate
+the structure function over a region of diameter \SI{50}{pc},
+which is smaller than in \citet{1961MNRAS.122....1F}
+but with a slightly larger number of spatial samples (\(N = 44\)).
+They found an approximately flat \(B(r)\) for \(r > \SI{20}{pc}\)
+and a shallow rising power law, \(\text{index} \approx 0.16\), for \(r = 5\) to \SI{20}{pc},
+with \(\sigma\pos^2 \approx \SI{280}{km.s^{-1}}\).
+This is similar to our own results over the same range of separations,
+including the local peak in \(B(r)\) at \(r = \SI{20}{pc}\),
+which is clearly visible in Figure~A2 of \citet{Melnick:1987a}.
+The reason that \citeauthor{Melnick:1987a} measure such a shallow slope for their smallest
+separations is that they are only sampling the range from \(1.25 r_0 \to 5 r_0\),
+in which the structure function is tending toward its asymptotic value of \(2 \sigma\pos^2\).
+In order to measure the power-law portion of the structure function,
+it would be necessary to sample separations as small as \SI{1}{pc} or \SI{4}{arcsec}.
+
+\citet{Melnick:2021x} used \ha{} spectra from VLT FLAMES/GIRAFFE (see section~\ref{sec:flames-multi-fiber}) for \(N = 1668\) distinct fiber positions
+covering a region of diameter \SI{300}{pc}
+\citep{Torres-Flores:2013t}.
+They claim to find a completely flat structure function on scales from \num{3} to \SI{200}{pc},
+which seriously conflicts with our own observations at the lower end of this range.
+In particular, their two smallest separation bins are centered on \(r = 2.5\) and \SI{7.5}{pc},
+for which our own results yield \(B(r) / \sigma\los^2 \approx 0.7\) and \(1.3\),
+respectively (our Figure~\ref{fig:strucfunc-fit-MC}a),
+whereas they find \(B(r) / \sigma\los^2 \approx 2.0\) at all separations (see their Figure 15).
+We are at a loss to explain this discrepancy, which is inconsistent not only with our own results,
+but also with those of \citet{1961MNRAS.122....1F} and \citet{Melnick:1987a},
+who both found at least some evidence for a downturn in \(B(r)\) for \(r < \SI{10}{pc}\). 
+The result also seems to contradict the evidence of their own Figures~7 and~13,
+which show spatial coherence in the velocity field.
+If the structure function were truly flat, then blue shifted and red shifted profiles
+would be randomly mixed spatially, which is not observed.
 

### 2023-04-23 strucfunc_paper.tex
Improve the marking of changes
Define a macro \NEW to do it and use a red that is not so
garish. Also, make sure that spacing works right around section
headers, etc. And turn off link colorization to simplify things.

@@
 % Use more muted colors for links
-\hypersetup{colorlinks=True, linkcolor=blue!50!black, citecolor=black,
-  urlcolor=blue!50!black}
+% \hypersetup{colorlinks=True, linkcolor=blue!50!black, citecolor=black,
+%   urlcolor=blue!50!black}
+\hypersetup{hidelinks=True}
 
@@
 %%%%% AUTHORS - PLACE YOUR OWN COMMANDS HERE %%%%%
+
+% Mark new changes in red
+\definecolor{NEWcolor}{rgb}{0.7,0.2,0.1}
+\newcommand\startNEW{\color{NEWcolor}}
+\newcommand\stopNEW{\color{black}}
+\newcommand\NEW[1]{\startNEW #1\stopNEW\relax}
 
@@
 \begin{equation}\label{eq:ffs}
-  \color{red}
+  \startNEW
   S(r) =
@@
   ,
-  %  S(r) = \frac{
-  %   e^{-s_0 / r_0}
-  % }{
-  %   1+(2s_0 / r)^{2 / 3}
-  % } ,
+  \stopNEW
 \end{equation}
@@
 \colorlet{RED}{red}
-\section{\color{red}Degradation of the structure function due to observational limitations}
+\startNEW
+\section{Degradation of the structure function due to observational limitations}
 \label{sec:degr-struct-funct}
+\stopNEW
 % Studied in context of \(\Delta\)-variance by \citet{Bensch:2001l}.
@@
 the correlation length \(r_0\) and the velocity field variance \(\sigma\pos^2\). 
-The synthetic velocity maps are created using a modified version of the \textcolor{red}{\texttt{make\textunderscore{}3dfield}} command from the \texttt{turbustat} Python library \citep{Koch2019AJ....158....1K},
-which creates a \textcolor{red}{three-dimensional} fractional Brownian Motion field
+The synthetic velocity maps are created using a modified version of the \NEW{\texttt{make\textunderscore{}3dfield}} command from the \texttt{turbustat} Python library \citep{Koch2019AJ....158....1K},
+which creates a \NEW{three-dimensional} fractional Brownian Motion field
 \citep{Miville-Deschenes:2003a}
 based on a power-law energy spectrum in wavenumber \(k\), \(E(k) \propto k^{-n}\),
-where \textcolor{red}{\(n = m + 3\)} and with random phases. 
+where \NEW{\(n = m + 3\)} and with random phases. 
 Our modification multiplies the energy spectrum by a
@@
 
-{\color{red}%
-  In order to create 2D plane-of-sky velocity map, we first
+\startNEW
+In order to create a 2D plane-of-sky velocity map, we first
 create 3D cubes of fluctuating velocity and emissivity
@@
 }
-}
+\stopNEW
 
@@
 
-\subsection{\color{red}Finite box effects}
+\startNEW
+\subsection{Finite box effects}
 \label{sec:finite-box-effects}
+\stopNEW
 
@@
     The dashed line is an approximate analytic fit to these results
-    (\(\color{red}1 - e^{L / 4.0r_0}\)).
+    (\NEW{\(1 - e^{L / 4.0r_0}\)}).
     (b)~Determination of \(\sigma^2\) and \(r_0\) from fitting the model
@@
 
-\textcolor{red}{Figure~\ref{fig:finite-box}a} shows how we test for finite map effects by taking
-a simulated \textcolor{red}{1st moment map of} size \(512 \times 512\) pixels and iteratively
+\NEW{Figure~\ref{fig:finite-box}a} shows how we test for finite map effects by taking
+a simulated \NEW{1st moment map of} size \(512 \times 512\) pixels and iteratively
 dividing the full map into \(2 \times 2\) tiles.
@@
 The figure shows the result for \(j = 1\), 2, 3, and 4, in which the full map
-was generated with a correlation length \textcolor{red}{\(r_0 = 32\)~pixels}.
+was generated with a correlation length \NEW{\(r_0 = 32\)~pixels}.
 We then calculate the individual structure function for each tile and
 find the mean and standard deviation for each level of subdivision,
-showing the results in \textcolor{red}{Figure~\ref{fig:finite-box}b}.
+showing the results in \NEW{Figure~\ref{fig:finite-box}b}.
 It can be seen that the mean structure functions for each level
@@
 using the tile's own empirically measured structure function and variance.
-In \textcolor{red}{Figure~\ref{fig:finite-box-effect}a} we show how these
+In \NEW{Figure~\ref{fig:finite-box-effect}a} we show how these
 quantities deviate from the ``true'' values
@@
 heuristic model structure function of equation~\eqref{eq:model-strucfunc-ideal}.
-This is shown in \textcolor{red}{Figure~\ref{fig:finite-box-effect}b}, where it can be seen
-that the true parameters are reliably recovered so long as \textcolor{red}{\(L > 5 r_0\)},
+This is shown in \NEW{Figure~\ref{fig:finite-box-effect}b}, where it can be seen
+that the true parameters are reliably recovered so long as \NEW{\(L > 5 r_0\)},
 which is a roughly \SI{0.5}{dex} improvement over the purely empirical method.
@@
 
-\subsection{\color{red}Effects of seeing}
+\startNEW
+\subsection{Effects of seeing}
 \label{sec:effects-seeing-struc}
+\stopNEW
 
@@
     \(B(r, s_0) / B(r, s_0 = 0)\) as a function of separation \(r\),
-    with a separation of \textcolor{red}{\(2.6 s_0\)} indicated by a large filled circle on each curve.
+    with a separation of \NEW{\(2.6 s_0\)} indicated by a large filled circle on each curve.
     Dashed lines shows the empirical fit discussed in the text.
@@
 
-\textcolor{red}{Figure~\ref{fig:seeing-reduction}a} illustrates how four different
-synthetic \textcolor{red}{1st-moment maps of} size \(256\times256\) pixels
-and correlation length \textcolor{red}{\(r_0 = \SI{32}{pixels}\)}
+\NEW{Figure~\ref{fig:seeing-reduction}a} illustrates how four different
+synthetic \NEW{1st-moment maps of} size \(256\times256\) pixels
+and correlation length \NEW{\(r_0 = \SI{32}{pixels}\)}
 are affected by progressively broader gaussian seeing,
 with RMS width \(s_0 = 1\) to \SI{32}{pixels}.
-\textcolor{red}{%
+\NEW{%
   Note that the seeing is applied to each velocity channel of the
@@
 with different colors representing different values of \(s_0\).
-Results are shown for a power-law slope of \textcolor{red}{\(m = 1.0\)}
+Results are shown for a power-law slope of \NEW{\(m = 1.0\)}
 but we find very similar behaviour for other values of \(m\) within the range
@@
 %\end{equation}
-\begin{equation}\label{eq:seeingemp2}\color{red}
+\begin{equation}\label{eq:seeingemp2}
+  \startNEW
   S(r; s_0, r_0) = 
@@
   \right ]^{-1} ,
+  \stopNEW
 \end{equation}
-which is shown by dashed lines in \textcolor{red}{Figure \ref{fig:seeing-reduction}b}.
-\textcolor{red}{%
+which is shown by dashed lines in \NEW{Figure \ref{fig:seeing-reduction}b}.
+\NEW{%
   The exact values of the constants \(a_1\), \(a_2\), \(a_3\)
@@
 (supplementing section~\ref{sec:comp-with-prev}).
+
+% START of revised material
+\startNEW
 
@@
 have used the [\ion{O}{3}] \Wav{5007} line and have probed smaller scales.
-\citep{1987ApJ...317..676O} used longslit observations at a small number of position angles
+\citet{1987ApJ...317..676O} used longslit observations at a small number of position angles
 to study the structure function over an area \(\num{2} \times \SI{2}{arcmin^2}\),
@@
 
+% END of revised material
+\stopNEW
+
 \subsection{NGC 346}

### 2023-04-23 strucfunc_paper.tex
Finish revision of first NGC 346 section

@@
 \begin{table}
-\begin{center}\caption{Summary of properties of our \hii{} region sample.
-Diameters taken from Table 2 of \citet{1984ApJ...287..116K}.
-Mean non-thermal linewidth values (\(\langle \sigma\los \rangle\)) shown here are corrected considering equation \eqref{eq:sigma-los} which takes into account \(\sigma_{\mathrm{fs}}\).
-Non-corrected \(\langle \sigma\los \rangle\) values and other properties references are mentioned in the text.
-}
+  \begin{center}\caption{Summary of properties of our \hii{} region sample. Diameters are taken from Table 2 of \citet{1984ApJ...287..116K}.
+      \NEW{References for other properties are given in Appendix~\ref{sec:notes-individual-hii}.}
+      Mean non-thermal linewidth values (\(\langle \sigma\los \rangle\)) shown here are corrected considering equation \eqref{eq:sigma-los} which takes into account \(\sigma_{\mathrm{fs}}\). }
 \begin{tabular}{cCCCC}\toprule
@@
 
-% START of revised material
-\startNEW
-
+\startNEW
 \subsection{Orion Nebula}
 \label{sec:orion-nebula}
+\stopNEW
 
 The Orion Nebula (M42) is the prototype of a galactic \hii{} region located at a distance of 440 pc \citetext{\SI{1}{\arcsecond} = \SI{0.002}{pc}; \citealp{2008AJ....136.1566O}}.
-The O7 V star \(\uptheta^{1}\) Ori C is the most luminous and hottest star with an ionizing flux \(Q_0\) of \SI{e49.12}{photons.s^{-1}} \citep{2006A&A...448..351S} which translates to luminosity in \ha{} of \SI{e37.18}{erg.s^{-1}}.
-With other 3 B-type stars they form the Trapezium cluster.
+The O7 V star \(\uptheta^{1}\) Ori C is the most luminous and hottest star with an ionizing flux \(Q_0\) of \SI{e49.12}{photons.s^{-1}} \citep{2006A&A...448..351S},
+\startNEW
+dominating the ionization of the nebula, which has a
+\stopNEW
+luminosity in \ha{} of \SI{e37.18}{erg.s^{-1}}.
+With 3 other B-type stars they form the Trapezium cluster.
 The bright region that surrounds these massive ionizing stars is called the Huygens region.
 %In the southwest direction of the Huygens region there is a drop in the brightness as one approach a much larger region called Extended Orion Nebula \citetext{EON henceforth;  \citealp{2008Sci...319..309G}}
-The position of the Orion Nebula on the near side of the Orion Molecular Cloud (OMC-1) makes it an ongoing site of star formation with a large population of young stars,
+The position of the Orion Nebula \NEW{on the near side of} the Orion Molecular Cloud (OMC-1)
+\startNEW
+makes it an ongoing site of star formation with a large population of young stars,
+\stopNEW
 some of which are sources of stellar jets and Herbig-Haro objects \citep{1993ApJ...410..696O}.
@@
 
+\startNEW
 \subsubsection{Observed structure function and model fit}
 \label{sec:observ-struct-funct-orion}
+\stopNEW
 
@@
 % which corresponds to the total decorrelation length \(\tau_0\), see section~\ref{sec:comp-with-prev}).
+\startNEW
 At scales larger than the correlation length,
@@
 and it is instead the model-derived value of \(\sigma\pos^2\) that is an overestimate.
+\stopNEW
 
@@
 in order to reproduce the observed flat structure function.
-In turn, this implies that a true \(\sigma^2\pos = \SI{5}{km^2.s^{-2}}\),
+In turn, this implies that
+\startNEW
+the true velocity variance is
+\stopNEW
+\(\sigma^2\pos = \SI{5}{km^2.s^{-2}}\),
 which is lower than the \SI{7}{km^2.s^{-2}}
@@
 % The derived correlation length is \SI{0.5}{pc} which is above the \SI{0.3}{pc} required to determine the true correlation length but below the \SI{0.9}{pc} which guarantees that the fit can reliable determine \(r_0\).
+\startNEW
 Comparing the extended nebula with the core for the size scales where they overlap
@@
 tending to increase from the center to the outskirts of the nebula. 
+\stopNEW
 
 %The seeing width is much smaller than the angular scale of the observations
-
+\startNEW
 \subsubsection{Comparison with previous studies}
 \label{sec:comparison-orion}
-
-\citet{arthur2016turbulence} calculated the structure function of different emission lines in the inner Orion Nebula with varying degrees of ionization. 
+\stopNEW
+
+\citet{arthur2016turbulence}
+\startNEW
+calculated the structure function of different emission lines in the inner Orion Nebula with varying degrees of ionization.
 They found that higher ionization lines show a larger velocity dispersion
 and a steeper structure function slope.
-They also make a comparison with previous work (see Table~5 on their paper), finding a broad agreement in results and the dependence between ionization energy and slope and dispersion value.
+\stopNEW
+They also make a comparison with previous work (see Table~5 of their paper), finding a broad
+\startNEW
+agreement in derived structure function parameters
+and their dependence on ionization energy.
+\stopNEW
 % The work by \citet{arthur2016turbulence} is the only one that includes the \ha{} emission line,
 % for this reason it will be the only one that we use for comparison.
-The power-law index obtained by \citet{arthur2016turbulence} is \(m \sim 1.17 \pm 0.08\) for \halpha,
-% and [\ion{O}{3}] emission lines and for [\ion{S}{2}] and [\ion{N}{2}] they found \(m \sim 0.8 \pm 0.1\). 
+The power-law index obtained by \citet{arthur2016turbulence} is
+\startNEW
+\(m \sim 1.17 \pm 0.08\) for \halpha,
 with a correlation length of \SI{\sim 0.05}{pc} and velocity variance
@@
 This compares with our own values of
-% For the same \halpha\ observations, but considering high-velocity objects, we obtained a value of 
 \(m = 1.07 \pm 0.03\), \(r_0 = \SI{0.068 \pm 0.004}{pc}\)
@@
 they masked out the locations of known high-velocity Herbig-Haro flows, whereas we do not.
-
+\stopNEW
+
+\startNEW
 \subsection{Lagoon Nebula}
 \label{sec:lagoon-nebula}
+\stopNEW
 
@@
 It contains the young stellar cluster NGC~6530 and the region is illuminated by different massive stars of spectral types O and B, the hottest being 9~Sgr, type O4V \citep{Damiani:2017b}.
+\startNEW
 The optically brightest part of the nebula is denoted the ``Hourglass nebula'',
 which is illuminated by the O7 star Herschel~36 \citep{1986AJ.....91..870W}.
+\stopNEW
 These stars gives an ionizing flux \(Q_0 = \SI{e49.41}{photons.s^{-1}}\) (2 times higher than in the Orion Nebula) and the luminosity in \ha{} is \SI{e37.47}{erg.s^{-1}} \citep{1984ApJ...287..116K}.
 The mean non-thermal linewidth in \ha{} is \SI{11.7 \pm 1.6}{km.s^{-1}} \citep{1973ApJ...183..851B}.
+\startNEW
 Molecular gas and ongoing star formation are present in the region around
@@
 M8~East \citep{1984ApJ...278..170S, Tiwari:2020a}.
-% The velocity field shows several expanding shells, related to the stellar population, and the massive protostar M8East-IR \citep{1984ApJ...278..170S} indicating that recent star formation.
-% A blueshifted, neutral layer is also in very good agreement with predictions of champagne-flow models of blister \hii{} regions \citep{Damiani:2017b}. 
+\stopNEW
 The properties of the nebula are reviewed by \citet{2008hsf2.book..533T}.
 
+\startNEW
 \subsubsection{Observed structure function and model fit}
@@
 
-% We follow the same procedure we use to describe the observed structure function of the Orion Nebula for the rest of the regions.
 Figure~\ref{fig:strucfunc-fit-Galactic}c shows the structure function of the Lagoon nebula.
@@
 or a large-scale gradient in the velocity field.
-
-% There aren't any points affected by the seeing (RMS) which has a value of \SI{0.01}{pc} (\(s_0\)=\SI{3.5}{\arcsecond}).
-% If we consider the first point of this \(B(r)\) to be valid, which corresponds to \SI{0.55}{km^{2}.s^{-2}} at \(r = \SI{0.05}{pc} \) the slope for \(\sigma\pos^2\) and \(2\sigma\pos^2\) we obtain \num{0.89} and \num{0.86}, respectively, while our derived value is \num{1.26}.
-
+\stopNEW
+
+\startNEW
 \subsubsection{Comparison with previous studies}
@@
 if the correlation length is larger than the size of the region mapped.
-The amplitude of the fluctuations is much higher (\(\sigma^2\pos = \SI{130}{km^2.s^{-2}}\)
+The amplitude of the fluctuations is much higher (\(\sigma^2\pos = \SI{130}{km^2.s^{-2}}\))
 than we find for the wider nebula (\(\sigma^2\pos = \SI{7}{km^2.s^{-2}}\)),
@@
 which is probably a symptom of the ongoing active star formation in that region.
-
+\stopNEW
+
+\startNEW
 \subsection{Carina Nebula}
 \label{sec:carina-nebula}
+\stopNEW
 
@@
 such as evaporating protoplanetary discs, erosion of large dust pillars, and the triggering of a second generation of embedded stars and Herbig-Haro objects \citetext{see \citealp{2008hsf2.book..138S} and reference therein}.
+\startNEW
 This region is at an intermediate scale between nearby regions like Orion
 that are dominated by a single star, and giant star formation regions such as 30~Doradus.
-
+\stopNEW
+
+\startNEW
 \subsubsection{Observed structure function and model fit}
 \label{sec:observ-struct-funct-carina}
+\stopNEW
 
 Figure~\ref{fig:strucfunc-fit-Galactic}d shows the structure function of the Carina nebula.
+\startNEW
 The model fit gives \(\sigma\pos^2 = \SI{18 \pm 2}{km^{2}.s^{-2}}\), \(r_0 = \SI{0.6 \pm 0.1}{pc} \), and \(m = 1.2 \pm 0.3\).
@@
 (for instance, between Tr~14 and Tr~16).
+\stopNEW
 
@@
 
+\startNEW
 \subsection{30 Doradus}
 \label{sec:30-doradus}
-
-The giant \hii{} region 30~Doradus (Tarantula Nebula) is located at a distance of \SI{49.9}{kpc} \citetext{\SI{1}{\arcsecond} = \SI{0.24}{pc} ; \citealp{2013Natur.495...76P}}.
+\stopNEW
+
+The giant \hii{} region 30~Doradus (Tarantula Nebula) is located at a distance of \SI{49.9}{kpc} \citetext{\SI{1}{\arcsecond} = \SI{0.24}{pc}; \citealp{2013Natur.495...76P}}.
 It is a luminous star-forming region in the LMC (Large Magellanic Cloud) and is the most luminous complex in the Local Group \citep{1984ApJ...287..116K}.
+\startNEW
 The star cluster that energizes the region is NGC~2070, with a central core (known as R136)
@@
 for the central ionized region of size \SI{40}{pc}.
+\stopNEW
 The mean non-thermal linewidth in \ha{} is \SI{22}{km.s^{-1}} \citep{2013A&A...555A..60T}.
+\startNEW
 Star formation is still ongoing in NGC~2070 \citep{2013AJ....145...98W},
@@
 and several Wolf-Rayet stars \citep{2011A&A...530A.108E}.
+\stopNEW
 This nebula is commonly used as a comparison for extragalactic star-forming regions.
 
+\startNEW
 \subsubsection{Observed structure function and model fit}
@@
 and has been interpreted as evidence for rotation of the cluster.
-
+\stopNEW
+
+\startNEW
 \subsubsection{Comparison with previous studies}
@@
 would be randomly mixed spatially, which is not observed. 
-
-% END of revised material
-\stopNEW
-
+\stopNEW
+
+\startNEW
 \subsection{NGC 346}
 \label{sec:ngc-346}
+\stopNEW
 
@@
 It has more than 30 O stars that ionize N66, the largest \hii{} region \citep{2011ApJ...740...10D}.
-N66 has an ionizing output \(Q_0\) of \SI{e50.71}{photons.s^{-1}} (40 times higher compared to the Orion Nebula) and has a \ha{} luminosity of \SI{e38.77}{erg.s^{-1}} \citep{2010A&A...517A..39H,1984ApJ...287..116K}.
-Using a Gaussian single-component \citet{2003ApJ...586.1179D} find a corrected FWHM bulk turbulence of \SI{23.8}{km.s^{-1}}. 
+\NEW{The cluster}
+has an ionizing output \(Q_0\) of \SI{e50.71}{photons.s^{-1}} (40 times higher than the Orion Nebula) and \NEW{the \hii{} region has} an \ha{} luminosity of \SI{e38.77}{erg.s^{-1}} \citep{2010A&A...517A..39H,1984ApJ...287..116K}.
+\startNEW
+A supernova remnant is present in the region \citetext{J59.4\(-7210\), \citealp{Ye:1991d}}
+but it does not overlap with the MUSE field that we observe here \citep{Maggi:2019q}.
+High-resolution \ha{} spectroscopy of the \hii{} region
+gives a non-thermal velocity width of \(\sigma\los = \SI{10.1}{km.s^{-1}}\)
+\citep{2003ApJ...586.1179D}.
+\stopNEW
 \citet{2008ApJ...688.1050G} propose an expanding \hii{} region or bubble blown by the winds of the massive progenitor as a mechanism that shapes the recent star formation in this region, in addition to the photoionization from the OB stars.
@@
 
+\startNEW
 \subsubsection{Observed structure function and model fit}
 \label{sec:observ-struct-funct-346}
-
-The Figure~\ref{fig:strucfunc-fit-MC}b shows the structure function of NGC 346.
+\stopNEW
+
+Figure~\ref{fig:strucfunc-fit-MC}b shows the structure function of NGC 346.
 The value of the observed \(\sigma\pos^2 = \SI{30}{km^{2}.s^{-2}}\) is obtained at \(r_0 = \SI{2.3}{pc} \) (in this case there is a good agreement with the derived values from our model which are \(\sigma\pos^2 = \SI{33}{km^{2}.s^{-2}}\) and \(r_0 = \SI{2.4}{pc} \)).

### 2023-04-24 strucfunc_paper.tex
Finish revision of NGC 346

@@
 Figure~\ref{fig:strucfunc-fit-MC}b shows the structure function of NGC 346.
-The value of the observed \(\sigma\pos^2 = \SI{30}{km^{2}.s^{-2}}\) is obtained at \(r_0 = \SI{2.3}{pc} \) (in this case there is a good agreement with the derived values from our model which are \(\sigma\pos^2 = \SI{33}{km^{2}.s^{-2}}\) and \(r_0 = \SI{2.4}{pc} \)).
-The observed value of \(2\sigma\pos^2\) corresponds to \(r = \SI{10}{pc} \), though, at this scale the \(B(r)\) value is just below the \(2\sigma\pos^2\), but the structure function seems to plateau at those values.
-Above this scales the structure function shows a periodic pattern with a spatial wavelength of \SI{\sim 10}{pc} and a dispersion of \(\SI{6}{km^{2}.s^{-2}}\).
-Unlike the Carina nebula, this oscillating pattern is below the \(2\sigma\pos^2\) value.
-The seeing value is \SI{0.11}{pc} (\(s_0\)=\SI{0.9}{\arcsecond}) and just one point of the structure functions lies below this value.
-Considering the first point above this \(s_0\) value to be valid, which corresponds to \SI{2.5}{km^{2}.s^{-2}} at \(r = \SI{0.2}{pc} \) the slope for \(\sigma\pos^2\) and \(2\sigma\pos^2\) we obtain \num{1.01} and \num{0.81}, respectively, while our derived value is \num{0.95}.
+\startNEW
+The model-derived parameters are \(\sigma\pos^2 = \SI{33 \pm 3}{km^{2}.s^{-2}}\),
+\(r_0 = \SI{2.4\pm 0.3}{pc} \)), and \(m = 0.95 \pm 0.07\).
+These agree very well with the empirically derived parameters.
+At large scales, an oscillatory behavior in \(B(r)\) is observed for \(r > \SI{10}{pc}\),
+consistent with a periodic pattern with wavelength \(\lambda \approx \SI{15}{pc}\) and amplitude \(\SI{6}{km^{2}.s^{-2}}\).
+Inspection of the velocity field (Figure~\ref{fig:velocity-maps}) shows that this pattern is predominantly oriented along the north-south direction and corresponds to the spacing between the filaments of molecular gas.
+\stopNEW
 

### 2023-04-24 strucfunc_paper.tex
Finish the revision of Hubble V and X sections

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
+\usepackage{placeins}
 %%%%% AUTHORS - PLACE YOUR OWN COMMANDS HERE %%%%%
@@
 \appendix
-\colorlet{RED}{red}
+
+% Be more lenient about float placement
+\renewcommand\textfraction{0.0}
+\renewcommand\topfraction{1.0}
+\renewcommand\bottomfraction{1.0}
+
 \startNEW
@@
 with \(s_0\) as an additional free parameter for the models.
-\clearpage
+
+\FloatBarrier
 
@@
 %
-The irregular dwarf galaxy, NGC 6822, is located at a distance of 500 kpc \citetext{\SI{1}{\arcsecond} = \SI{2.42}{pc} ; \citealp{2012A&A...540A.135S}} and host the \hii{} regions Hubble X and Hubble V which are the brightest regions in the galaxy.
-
-Hubble V is located near the 'Hodge OB 8' OB association with a number of \num{\sim 36} young stellar objects \citep{2021MNRAS.507.5106K} and its core is powered by an O3 V star \citep{1999PASP..111.1382O}.
+The irregular dwarf galaxy, NGC 6822, is located at a distance of \SI{500}{kpc} \citetext{\SI{1}{\arcsecond} = \SI{2.42}{pc}; \citealp{2012A&A...540A.135S}} and hosts the \hii{} regions Hubble~X and Hubble~V which are the brightest regions in the galaxy
+\NEW{\citep{Hodge:1989c}}.
+
+Hubble V is located near the ``Hodge OB 8'' OB association with a number of \num{\sim 36} young stellar objects \citep{2021MNRAS.507.5106K} and its core is powered by an O3 V star \citep{1999PASP..111.1382O}.
 It has an ionizing output \(Q_0\) of \SI{e50.23}{photons.s^{-1}} (13 times higher compared to the Orion Nebula) and has a \ha{} luminosity of \SI{e38.30}{erg.s^{-1}}\citep{2002MNRAS.329..481B}.
-The mean non-thermal linewidth in \ha{} \SI{10.3 \pm 0.03}{km.s^{-1}} \citep{1986A&A...160..374H}.
-
-Hubble X is located near the 'Hodge OB 13' OB association with a number of \num{\sim 29} young stellar objects \citep{2021MNRAS.507.5106K} and its core is powered by and O4 V star \citep{1999PASP..111.1382O}.
+The mean non-thermal linewidth in \ha{} \(\sigma\los = \SI{10.3 \pm 0.03}{km.s^{-1}}\) \citep{1986A&A...160..374H}.
+
+Hubble X is located near the Hodge ``OB 13'' OB association with a number of \num{\sim 29} young stellar objects \citep{2021MNRAS.507.5106K} and its core is powered by an O4 V star \citep{1999PASP..111.1382O}.
 It has an ionizing output \(Q_0\) of \SI{e50.14}{photons.s^{-1}} (10 times higher compared to the Orion Nebula) and has a \ha{} luminosity of \SI{e38.21}{erg.s^{-1}} \citep{2002MNRAS.329..481B}.
-The mean non-thermal linewidth in \ha{} is \SI{10.5 \pm 0.02}{km.s^{-1}}  \citep{1986A&A...160..374H}.
-\citet{1993PASJ...45..693T} realize a study on the kinematics of both regions.
+The mean non-thermal linewidth in \ha{} is \(\sigma\los = \SI{10.5 \pm 0.02}{km.s^{-1}}\)  \citep{1986A&A...160..374H}.
+\citet{1993PASJ...45..693T} studies the kinematics of both regions.
 
@@
 In the Figure~\ref{fig:strucfunc-fit-ExtraGal}a we show the structure function of Hubble V.
-The value of the observed \(\sigma\pos^2 = \SI{8}{km^{2}.s^{-2}}\) is obtained at \(r_0 = \SI{3}{pc} \) (while the derived values from our model are \(\sigma\pos^2 = \SI{10}{km^{2}.s^{-2}}\) and \(r_0 = \SI{3.6}{pc} \)).
-The observed value of \(2\sigma\pos^2\) corresponds to \(r = \SI{31}{pc} \).
-The maximum \(B(r)\) value is \SI{18}{km^{2}.s^{-2}} at a separation of \SI{25}{pc}. 
-%The value of the seeing for this regions is \SI{0.5}{pc} (\(s_0\)=\SI{0.2}{\arcsecond}).
-From this value the \(B(r)\) values decrease and we observe a downturn in the structure function to \SI{9}{km^{2}.s^{-2}} at \(r =  \SI{70}{pc}\) following the tapered fluctuations behavior.
-But unlike the Orion core or 30~Dor the downturn is not as smooth, since it presents a small variation at \(r = \SI{\sim 40}{pc} \) 
-The seeing (RMS) value derived for this regions is \SI{0.5}{pc} (\(s_0\)=\SI{0.2}{\arcsecond}) and just one point of the structure function fall in the confidence interval..
-Considering the first point above this \(s_0\) value to be valid, which corresponds to \SI{2.2}{km^{2}.s^{-2}} at \(r = \SI{0.89}{pc} \) the slope for \(\sigma\pos^2\) and \(2\sigma\pos^2\) we obtain \num{1.06} and \num{0.55}, respectively, while our derived value is \num{0.81}.
+\startNEW
+The model-derived parameters are \(\sigma\pos^2 = \SI{10 \pm 3}{km^{2}.s^{-2}}\),
+\(r_0 = \SI{3.6 \pm 1.0}{pc} \)), and \(m = 0.8 \pm 0.3\).
+The velocity variance is slightly higher than the empirically derived value of \(\sigma\pos^2 = \SI{8}{km^{2}.s^{-2}}\) because the model-derived seeing is only 6 times smaller than the correlation length.
+
+At the largest scales, the structure function turns downward,
+as seen in Orion.
+However, inspection of the velocity map suggests that the explanation
+may be different in this source: the velocity varies more strongly across the short axis of the nebula than along its long axis.
+There is also marginal evidence for weak periodic fluctuations
+with wavelength \(\lambda \approx \SI{50}{pc}\).
+\stopNEW
 
 The Hubble X structure function is shown in Figure~\ref{fig:strucfunc-fit-ExtraGal}b.
-The value of the observed \(\sigma\pos^2 = \SI{13}{km^{2}.s^{-2}}\) is obtained at \(r_0 = \SI{4}{pc} \) (while the derived values from our model are \(\sigma\pos^2 = \SI{15}{km^{2}.s^{-2}}\) and \(r_0 = \SI{4}{pc} \)).
-The observed value of \(2\sigma\pos^2\) corresponds to \(r = \SI{15}{pc} \).
-The maximum \(B(r)\) value of \SI{31}{km^{2}.s^{-2}} is reached at a separation of \SI{36}{pc}.
-From scales \(> \SI{15}{pc}\) we see that the structure functions fluctuates around \(2\sigma\pos^2\) with a spatial wavelength of \(\sim \SI{30}{pc}\) with a dispersion of \SI{2.3}{km^{2}.s^{-2}}.
-Since these large scales values fluctuates around \(2\sigma\pos^2\) is also possible that the structure function follows a purely homogeneous fluctuations behavior, just not as marked as it is shown in section~\ref{sec:limit-model-struct}.
-The seeing is \SI{0.6}{pc} (\(s_0\)=\SI{0.24}{\arcsecond}) and as in Hubble V there is just one point of the structure function that falls in the \(s_0\) confidence interval.
-Considering the first point above this \(s_0\) value to be valid, which corresponds to \SI{2.6}{km^{2}.s^{-2}} at \(r = \SI{0.86}{pc} \) the slope for \(\sigma\pos^2\) and \(2\sigma\pos^2\) we obtain \num{1.04} and \num{0.80}, respectively, while our derived value is \num{1.02}.
+\startNEW
+The model-derived parameters are \(\sigma\pos^2 = \SI{15 \pm 3}{km^{2}.s^{-2}}\),
+\(r_0 = \SI{4.0 \pm 0.5}{pc} \)), and \(m = 1.0 \pm 0.2\),
+which again is slightly higher than the empirically derived value of \(\sigma\pos^2 = \SI{13}{km^{2}.s^{-2}}\) because the latter is reduced by the seeing.
+
+At the largest scales the structure function is approximately flat,
+consistent with homogeneous fluctuations. 
+\stopNEW
 

### 2023-04-24 strucfunc_paper.tex
Javier changes 2023-04-24
Finish revision of first part of M33 regions

@@
 % If you need two or more lines of authors, add an extra line using \newauthor
-\author[J. García Vázquez et al.]{
-  J. García Vázquez$^{1}$\thanks{
+\author[J. García-Vázquez et al.]{
+  J. García-Vázquez$^{1}$\thanks{
     E-mail: \href{mailto:jgarciav1600@alumno.ipn.mx}{jgarciav1600@alumno.ipn.mx}
@@
 
+\startNEW
 \subsection{NGC~595 and NGC~604 in M33}
 \label{sec:m33-ngc}
-
-M33 is the third largest galaxy in the Local Group located at the distance of 820 kpc \citetext{\SI{1}{\arcsecond} = \SI{4.07}{pc} ; \citealp{2015KamKinematics}} and is of morphological type SA(s)cd.
-The two brightest \hii{} regions in the galaxy are NGC 604 and NGC 595.
-
-NGC 595 is the second brightest giant \hii{} region in the M33 galaxy.
-Using HST/WFPC-2 images \citet{1996AJ....111.1128M} found approximately 250 stars of the OB type, 13 Supergiants and 10 WR, confirming previous candidates.
-\citet{1993AJ....105.1400D} use optical photometry to propose 11 WR stars. 
-The ionizing output \(Q_0\) is \SI{e50.88}{photons.s^{-1}} (60 times higher compared to the Orion Nebula) and has a luminosity in \ha{} of \SI{e38.95}{erg.s^{-1}}\citep{2002MNRAS.329..481B}.
-The mean non-thermal linewidth in \ha{} is \SI{16.8 \pm 0.1}{km.s^{-1}} \citep{lagrois2009multi}.
-\citet{lagrois2011} present a kinematic study of the regions using optical emission lines and and radio 21 cm line observations and find that \ha{} shell morphology that is related to the stellar winds of the several massive stars located in its interior.
-They proposed Champagne flows at the periphery of the molecular cloud leading to accelerated ionized material.
+\stopNEW
+
+M33 is the third largest galaxy in the Local Group,
+located at a distance of \SI{820}{kpc}
+\citetext{\SI{1}{\arcsecond} = \SI{4.07}{pc}; \citealp{2015KamKinematics}}
+and is of morphological type SA(s)cd.
+The two brightest \hii{} regions in the galaxy are NGC~604 and NGC~595.
+
+NGC 595 is the second most luminous giant \hii{} region in the M33 galaxy,
+\startNEW
+excited by a stellar population comprising
+250 OB stars, 13 hot supergiants, and 11 Wolf-Rayet stars \citep{1993AJ....105.1400D, 1996AJ....111.1128M}.
+\stopNEW
+The ionizing output \(Q_0\) is \SI{e50.88}{photons.s^{-1}} (60 times higher compared to the Orion Nebula) and
+the \hii{} region has a luminosity in \ha{} of \SI{e38.95}{erg.s^{-1}} \citep{2002MNRAS.329..481B}.
+The mean non-thermal linewidth in \ha{} is
+\(\sigma\los = \SI{16.8 \pm 0.1}{km.s^{-1}}\) \citep{lagrois2009multi}.
+\citet{lagrois2011} present a kinematic study of the regions using optical emission lines and and radio 21 cm line observations and find an \ha{} shell morphology that is related to the stellar winds of the several massive stars located in its interior.
+They proposed champagne flows at the periphery of the molecular cloud leading to accelerated ionized material.
 
@@
 
-NGC 604 is the second brightest \hii{} region in the Local Group after 30~Dor.
-Using photometry from the HST \citet{1996ApJ...456..174H} identified that the stars are separated into a primary cluster within NGC 604, and a secondary to the north of the region.
-In the primary there are \(\sim\)200 OB stars, candidate to red supergiants (RSGs) and the presence of WR stars.
-For the northern cluster they find eight luminous stars and no evolved massive stars.
-More Recently, \citet{2011MNRAS.411..235E} studied 10 WR stars and propose at least 4 RSGs candidates.
-\citet{2012AJ....143...43F} focused on the massive young stellar objects (MYSOs).
-The ionizing output \(Q_0\) is \SI{e51.35}{photons.s^{-1}} (175 times higher compared to the Orion Nebula) and has a \ha{} of \SI{e39.42}{erg.s^{-1}} \citep{2002MNRAS.329..481B}.
-The mean non-thermal linewidth in \ha{} is \SI{17.8 \pm 0.3}{km.s^{-1}} \citep{1986A&A...160..374H}.
-It is the brightest giant \hii{} region in the M33 galaxy and is visually dominated by a predominant big loop, many expanding shells and different size filaments.
+NGC 604 is the
+\startNEW
+most luminous \hii{} region in M33 and
+\stopNEW
+the second most luminous in the Local Group after 30~Dor.
+\startNEW
+The dominant stellar cluster is located in the center of the region and contains 200 OB stars and 4 Wolf-Rayet stars \citep{1996ApJ...456..174H, 2011MNRAS.411..235E}.
+The optically visible stars come from a population
+with an age of \SI{4}{Myr},
+although infrared observations detect the presence of
+ongoing massive star formation in the region
+\citep{2012AJ....143...43F, 2012ApJ...761....3M}.
+\stopNEW
+The ionizing output is \(Q_0 = \SI{e51.35}{photons.s^{-1}}\)
+(175 times higher than the Orion Nebula) and
+the region has an \ha{} luminosity of \SI{e39.42}{erg.s^{-1}} \citep{2002MNRAS.329..481B}.
+The mean non-thermal linewidth in \ha{} is
+\(\sigma\los = \SI{17.8 \pm 0.3}{km.s^{-1}}\) \citep{1986A&A...160..374H}.
+\startNEW
+The morphology of the region is strikingly similar to that of 30~Dor
+(see Figure~\ref{fig:hii-regions})
+\stopNEW
+and is visually dominated by a predominant big loop, many expanding shells and different size filaments.
 

### 2023-04-26 strucfunc_paper.tex
Revisions to discussion of line widths
Improve consistency in notation. Better explanation of all the panels
in Fig 12. Add a footnote about difference between mean LOS linewidth
and the LOS linewidth of the entire region.

@@
 \caption{
-  Panels a--g show histograms (blue) of the probability density function (PDF)
+  Panels a--g: Histograms (blue) of the probability density function (PDF)
   of the \ha{} surface brightness of \hii{} regions in our sample.
@@
   into pixels of size \(0.5 r_0\) before calculating the PDF.
-  Also shown are the RMS Mach number of three-dimensional
+  \startNEW
+  Panel~h: RMS Mach number of three-dimensional
   velocity fluctuations (panel~h)
-  and the ratio of plane-of-sky to line-of-sight velocity dispersions (panel~i),
-  each plotted as a function of the
+  as a function of the RMS fractional brightness fluctuation calculated from the PDFs.
+  The gray shaded area shows the range of predicted values
+  for the brightness fluctuations if they are entirely due to density
+  fluctuations formed by driven turbulence with the observed Mach number.
+  Panel~i: Ratio of plane-of-sky to line-of-sight velocity dispersions
+  as a function of the
   RMS fractional brightness fluctuations calculated from the PDFs.
+  The solid and dashed lines show the expected relationship for
+  the toy models of Appendix~\ref{sec:appar-veloc-fluct}. 
+  \stopNEW
 }
@@
 \label{sec:sigmapos-vs-sigmalos}
+\newcommand\siglosm{\ensuremath{\langle\sigma\los\rangle}}
 
@@
 finding
-\(\langle \sigma_{\text{los}} \rangle = (1.04 \pm 0.14) \sigma\pos + (8.15 \pm 0.93) \)
+\(\langle \sigma\los \rangle = (1.04 \pm 0.14) \sigma\pos + (8.15 \pm 0.93) \)
 for their sub-sample with higher resolution observations
@@
 ([\ion{S}{2}], [\ion{N}{2}], \ha, [\ion{O}{3}])
-in the Orion Nebula, finding \(\langle\sigma\los \approx 2 \sigma\pos\rangle\),
+in the Orion Nebula, finding \(\langle\sigma\los\rangle \approx 2 \sigma\pos\),
 which is shown by the dotted line in Figure~\ref{fig:los-vs-pos}.
@@
 At least three different explanations for the relation
-between \(\sigma\pos\) and \(\sigma\los\) have been proposed previously.
+between \(\sigma\pos\) and \(\siglosm\) have been proposed previously.
 The classic interpretation 
@@
 as discussed above in section \ref{sec:constancy-power-law}.
-Assuming that \(\sigma\los\) measures the true dispersion,
-then one would expect to find \(\sigma\pos / \sigma\los = (\LL /H)^{1/2}\),
+Assuming that \(\siglosm\) measures the true dispersion,
+then one would expect to find \(\sigma\pos / \siglosm = (\LL /H)^{1/2}\),
 where \(H\) is the line-of-sight depth of the emitting gas
@@
 % So H / r0 = 1.44 (los/pos)^2
-which yields \(H / r_0 \approx 1.44 (\sigma\los / \sigma\pos)^2\).
+which yields \(H / r_0 \approx 1.44 (\siglosm / \sigma\pos)^2\).
 From the results of Figure~\ref{fig:los-vs-pos} we would therefore find
@@
 as discussed in \citet{2011MNRAS.413..705L},
-is that \(\sigma\los\) includes a contribution due to
+is that \(\siglosm\) includes a contribution due to
 ordered large-scale velocity gradients
@@
 and that projection smoothing is negligible,
-one would predict \(\sigma\los = (\sigma\pos^2 + \vexp^2)^{1/2}\),
+one would predict \(\siglosm = (\sigma\pos^2 + \vexp^2)^{1/2}\),
 which is shown by the blue shaded-area in Figure~\ref{fig:los-vs-pos}
@@
 \vexp{} might increase in proportion to the turbulent velocity dispersion
-since that would predict that \(\sigma\los \propto \sigma\pos\),
+since that would predict that \(\siglosm \propto \sigma\pos\),
 which is inconsistent with the observations as discussed above.
@@
 This leads to a third potential explanation of the
-\(\sigma\pos\)--\(\sigma\los\) relationship.
+\(\sigma\pos\)--\(\siglosm\) relationship.
 In the limit that the direct contribution of
 turbulent velocity fluctuations is negligible
-and that \(\sigma\los\) is entirely due to ordered expansion along the line of sight,
+and that \(\siglosm\) is entirely due to ordered expansion along the line of sight,
 then a non-zero \(\sigma\pos\) can arise only from emissivity fluctuations,
@@
 This is compared with the behavior of the ratio
-\(\sigma\pos / \sigma\los\) for
+\(\sigma\pos / \siglosm\) for
 our observed sample in panel~i of Figure~\ref{fig:brightness-pdfs},
 in which the solid and dashed lines show results for different assumptions
-about the effects of velocity gradients on \(\sigma\los\).
+about the effects of velocity gradients on \(\siglosm\).
 Although the model does qualitatively reproduce the increase
-in \(\sigma\pos / \sigma\los\) with increasing \(\sigma_S\), the quantitative agreement
+in \(\sigma\pos / \siglosm\) with increasing \(\sigma_S\), the quantitative agreement
 is poor, with the model substantially overestimating the magnitude of
@@
 \citep{terlevich1981, Chavez:2014a}.
-In such studies, the velocity dispersion is invariably derived from the
-line widths (\(\sigma\los\)) since the spatially resolved observations
-necessary for measuring \(\sigma\pos\) are not available.
+In such studies, the velocity dispersion is usually derived from the
+line width  of the entire region (\(\sigma\los\)) since the spatially resolved observations
+necessary for measuring \(\sigma\pos\) are not available.%
+\NEW{\footnote{
+  \startNEW
+  The linewidth \(\sigma\los\) for the integrated emission of an \hii{} region
+  will be larger than the mean of the spatially resolved linewidths \siglosm{}
+  since it also includes the plane-of-sky fluctuations \(\sigma\pos\).
+  Given the results of section~\ref{sec:sigmapos-vs-sigmalos},
+  and assuming that the linear relationship of Figure~\ref{fig:los-vs-pos}
+  can be extrapolated to higher values, then the approximate
+  relation is \(\sigma\los = \sqrt{2}\,\siglosm\) for \(\sigma\los \gg \SI{10}{km.s^{-1}}\).
+  \stopNEW
+}}
 A reliable empirical \(L\)--\(\sigma\) relationship allows the use of bright photoionized
@@
 but not significantly so, given the uncertainty.
-Studies that rely on \(\sigma\los\) generally find that
+Studies that rely on \(\siglosm\) generally find that
 \(\sigma\) becomes insensitive to luminosity below about \(L(\ha) = \SI{e40}{erg.s^{-1}}\),
@@
 On the other hand,
-by using \(\sigma\pos\) instead of \(\sigma\los\),
+by using \(\sigma\pos\) instead of \(\siglosm\),
 we succeed in extending the same power-law relation
@@
 is that \(\sigma\pos\) is a better measure of the disordered turbulent motions within
-the \hii{} regions than \(\sigma\los\) since the latter
+the \hii{} regions than \(\siglosm\) since the latter
 is contaminated by large-scale ordered motions,
@@
 %(\(\sigma(\chem{CO}) \ll \sigma(\ha)\) in all regions
-%for both \(\sigma\los\) and \(\sigma\pos\))
+%for both \(\siglosm\) and \(\sigma\pos\))
 %might be thought to rule out the molecular gas kinematics
@@
   pass from the subsonic to the supersonic regime. 
-\item The non-thermal component of the emission line widths (\(\sigma\los\)) is found
+\item The non-thermal component of the emission line widths (\(\siglosm\)) is found
   to be proportional to the amplitude of the plane-of-sky velocity centroid fluctuations
   (\(\sigma\pos\)) with a slope of unity, but an offset such that
-  \(\sigma\los \approx \SI{10}{km.s^{-1}}\) when \(\sigma\pos = 0\)
+  \(\siglosm \approx \SI{10}{km.s^{-1}}\) when \(\sigma\pos = 0\)
   (section~\ref{sec:sigmapos-vs-sigmalos}).
-  This can be explained if \(\sigma\los\) is affected by ordered velocity fields,
+  This can be explained if \(\siglosm\) is affected by ordered velocity fields,
   such as radial expansion, which leave no imprint on \(\sigma\pos\),
   implying that \(\sigma\pos\) is a better diagnostic of turbulent fluctuations than
-  \(\sigma\los\), even though it is more challenging to measure.
+  \(\siglosm\), even though it is more challenging to measure.
 \item The amplitudes of \ha{} surface brightness fluctuations
@@
     \(\sigma\pos\),
-    and the mean RMS line width, \(\sigma\los\),
+    and the mean RMS line width, \(\siglosm\),
     both in units of the inter-layer velocity difference \(\beta\).
@@
   \\
-  \sigma\los &=   \frac{\alpha^{1/2}\beta}{1 + \alpha}.
+  \siglosm &=   \frac{\alpha^{1/2}\beta}{1 + \alpha}.
 \end{align}
@@
 }
-The line width \(\sigma\los/\beta\) behaves in the opposite sense, falling from
+The line width \(\siglosm/\beta\) behaves in the opposite sense, falling from
 a maximum value of \(0.5\) when \(\alpha = 0\) towards zero as \(\alpha \to \infty\),
@@
 within each layer that contributes an additional width of \(\beta/4\),
-which is assumed to add in quadrature with \(\sigma\los\).
+which is assumed to add in quadrature with \(\siglosm\).
 
@@
 In particular, their two smallest separation bins are centered on \(r = 2.5\) and \SI{7.5}{pc},
-for which our own results yield \(B(r) / \sigma\los^2 \approx 0.7\) and \(1.3\),
+for which our own results yield \(B(r) / \siglosm^2 \approx 0.7\) and \(1.3\),
 respectively (our Figure~\ref{fig:strucfunc-fit-MC}a),
-whereas they find \(B(r) / \sigma\los^2 \approx 2.0\) at all separations (see their Figure 15).
+whereas they find \(B(r) / \siglosm^2 \approx 2.0\) at all separations (see their Figure 15).
 We are at a loss to explain this discrepancy, which is inconsistent not only with our own results,

### 2023-04-26 strucfunc_paper.tex
Incomplete edits on NGC 595 and 606

@@
 High-resolution \ha{} spectroscopy of the \hii{} region
-gives a non-thermal velocity width of \(\sigma\los = \SI{10.1}{km.s^{-1}}\)
+gives a non-thermal velocity width of \(\siglosm = \SI{10.1}{km.s^{-1}}\)
 \citep{2003ApJ...586.1179D}.
@@
 It has an ionizing output \(Q_0\) of \SI{e50.23}{photons.s^{-1}} (13 times higher compared to the Orion Nebula) and has a \ha{} luminosity of \SI{e38.30}{erg.s^{-1}}\citep{2002MNRAS.329..481B}.
-The mean non-thermal linewidth in \ha{} \(\sigma\los = \SI{10.3 \pm 0.03}{km.s^{-1}}\) \citep{1986A&A...160..374H}.
+The mean non-thermal linewidth in \ha{} \(\siglosm = \SI{10.3 \pm 0.03}{km.s^{-1}}\) \citep{1986A&A...160..374H}.
 
@@
 It has an ionizing output \(Q_0\) of \SI{e50.14}{photons.s^{-1}} (10 times higher compared to the Orion Nebula) and has a \ha{} luminosity of \SI{e38.21}{erg.s^{-1}} \citep{2002MNRAS.329..481B}.
-The mean non-thermal linewidth in \ha{} is \(\sigma\los = \SI{10.5 \pm 0.02}{km.s^{-1}}\)  \citep{1986A&A...160..374H}.
+The mean non-thermal linewidth in \ha{} is \(\siglosm = \SI{10.5 \pm 0.02}{km.s^{-1}}\)  \citep{1986A&A...160..374H}.
 \citet{1993PASJ...45..693T} studies the kinematics of both regions.
@@
 
-In the Figure~\ref{fig:strucfunc-fit-ExtraGal}a we show the structure function of Hubble V.
+In Figure~\ref{fig:strucfunc-fit-ExtraGal}a we show the structure function of Hubble V.
 \startNEW
@@
 The mean non-thermal linewidth in \ha{} is
-\(\sigma\los = \SI{16.8 \pm 0.1}{km.s^{-1}}\) \citep{lagrois2009multi}.
+\(\siglosm = \SI{16.8 \pm 0.1}{km.s^{-1}}\) \citep{lagrois2009multi}.
 \citet{lagrois2011} present a kinematic study of the regions using optical emission lines and and radio 21 cm line observations and find an \ha{} shell morphology that is related to the stellar winds of the several massive stars located in its interior.
@@
 The mean non-thermal linewidth in \ha{} is
-\(\sigma\los = \SI{17.8 \pm 0.3}{km.s^{-1}}\) \citep{1986A&A...160..374H}.
+\(\siglosm = \SI{17.8 \pm 0.3}{km.s^{-1}}\) \citep{1986A&A...160..374H}.
 \startNEW
@@
 
-In the Figure~\ref{fig:strucfunc-fit-ExtraGal}c we show the structure function of NGC 595.
+In Figure~\ref{fig:strucfunc-fit-ExtraGal}c we show the structure function of NGC 595.
+The model-derived parameters are \(\sigma\pos^2 = \SI{53 \pm 5}{km^{2}.s^{-2}}\),
+\(r_0 = \SI{11 \pm 1.0}{pc} \)), and \(m = 1.4 \pm 0.2\).
 The value of the observed \(\sigma\pos^2 = \SI{44}{km^{2}.s^{-2}}\) is obtained at \(r_0 = \SI{10}{pc} \) (while the derived values from our model are \(\sigma\pos^2 = \SI{53}{km^{2}.s^{-2}}\) and \(r_0 = \SI{11}{pc} \)).
@@
 
+\startNEW
 \subsubsection{Comparison with previous studies}
 \label{sec:comparison-m33}
+
+\citet{lagrois2011} calculated the structure function for the \halpha\ emission line for NGC 595
+over a region of diameter \SI{300}{kpc} with a resolution of \SI{6.6}{pc.pixel^{-1}} \citep{lagrois2009multi}, presenting results for separations \(r \ge \SI{16.5}{pc}\).
+They found a total velocity variance of \(\sigma\pos^2 = \SI{35 \pm 2}{km^{2}.s^{-2}}\), which is smaller than our derived value of \(\sigma\pos^2 = \SI{53}{km^{2}.s^{-2}}\).
+
 For our NGC 595 \halpha\ emission line results there is no correspondence in the structure function from the previous investigations of \citet{lagrois2009multi} and \citet{lagrois2011}.
@@
 
+\stopNEW
+
 \section{Additional covariance corner plots for model fits}
@@
 {available online}.
+
 %

### 2023-04-26 strucfunc_paper.tex
Rewrite description of 3D to 2D mapping
Mention the delta kappa complications

@@
 based on a power-law energy spectrum in wavenumber \(k\), \(E(k) \propto k^{-n}\),
-where \NEW{\(n = m + 3\)} and with random phases. 
+and with random phases. 
 Our modification multiplies the energy spectrum by a
@@
 with RMS fractional width
-\(\shortsig{E} = 1.0\) that is typical of our sources
+\(\shortsig{E} = 1.0\), which is typical of our sources
 (see footnote~\ref{fn:brightness-fluctuations} and Figure~\ref{fig:brightness-pdfs} above).
@@
 and power law indices are equal.\footnote{%
+  \startNEW
   We have investigated departures from these assumptions and found that they
   make very little difference to the results.
-}
+  In particular, we have varied \(\shortsig{E}\) between
+  0.0 (constant emissivity) and 2.0 (very strong fluctuations,
+  as seen in 30~Doradus), and found that the fitting parameters
+  for the effects of seeing (see below) change by less than 20\%
+  \stopNEW
+}
+
+The 3-dimensional 2nd-order structure function slope is related to the power law index as \(m\DDD = n - 3\), but the slope, \(m\), of the 2-dimensional velocity
+structure function depends not only on velocity power law index, but also on the magnitude and power law index of the emissivity fluctuations via the quantity
+\(\delta\kappa\), with the relation being \(m = n - 2 + \delta\kappa\)
+(see section \ref{sec:constancy-power-law}).
+\citet{Brunt:2004a} found that \(\delta\kappa\) is a function of the Mach number for
+hydrodynamic turbulent box simulations, but we are unaware of any analytic prescription that would allow us to calculate \(\delta\kappa\) for
+the fractional Brownian motion models that we use here. 
+We therefore adopt an empirical approach by varying \(n\) until the
+resultant structure function slope matches a particular value in the
+range \(m = 0.8 \to 1.2\)
+that encompasses our observational results. 
+At each step, we estimate \(m\) by fitting our idealized model structure function
+(equation~\eqref{eq:model-strucfunc-ideal}, without the seeing and noise terms)
+to the structure function of the simulated velocity map.
+In the case of a uniform emissivity field (\(\shortsig{E} = 0\)),
+we find \(\delta\kappa \approx 0\),
+which is maximal projection smoothing, exactly as expected for a case that
+mimics incompressible turbulence.
+As the amplitude of the emissivity fluctuations increase,
+we find that \(\delta\kappa\) becomes increasingly negative,
+with \(\delta\kappa \approx -0.3\) for \(\shortsig{E} = 1\) (the case that we present here)
+and \(\delta\kappa \approx -0.55\) for \(\shortsig{E} = 2\).
+This is qualitatively consistent with the results in
+Figure~12a of \citet{Brunt:2004a}, although a quantitative
+comparison is hard to make, since they are not holding \(m\) constant
+in the way we do here. 
 \stopNEW
@@
   within 20\% for \(0.8 < m < 1.2\) and \(0.5 < \shortsig{E} < 2.0\).}
-The optimum value of the index \(a\) in this equation varies slightly
-with the power law slope \(m\) of the true structure function,
-but a compromise value of \(a = 0.75\) works tolerably well for \(m = 0.7\) to \(1.3\).
 We therefore use this equation to represent the seeing

### 2023-04-27 strucfunc_paper.tex
Further changes to the intro to Appendix A

@@
 \citep{Miville-Deschenes:2003a}
-based on a power-law energy spectrum in wavenumber \(k\), \(E(k) \propto k^{-n}\),
+based on a power-law energy spectrum in wavenumber \(k\), \(E(k) \propto k^{-n\DDD}\),
 and with random phases. 
@@
 
-The 3-dimensional 2nd-order structure function slope is related to the power law index as \(m\DDD = n - 3\), but the slope, \(m\), of the 2-dimensional velocity
-structure function depends not only on velocity power law index, but also on the magnitude and power law index of the emissivity fluctuations via the quantity
-\(\delta\kappa\), with the relation being \(m = n - 2 + \delta\kappa\)
-(see section \ref{sec:constancy-power-law}).
+\newcommand\DD{\ensuremath{_{\mathrm{2D}}}}
+The 3-dimensional 2nd-order structure function slope is related to the power law index as \(m\DDD = n\DDD - 3\), while the equivalent relation in two dimensions is \(m\DD = n\DD - 2\) for separations smaller than the line-of-sight
+depth of the emitting region.
+So long as the emissivity fluctuations are weak
+and uncorrelated with the velocity fluctuations, then \(n\DD = n\DDD\)
+\citep{Miville-Deschenes:2003a, Levrier:2004a},
+but if these conditions are not satisfied, then the structure function
+of the velocity centroids does not purely reflect the velocity power spectrum
+\citep{Brunt:2004a, Esquivel:2005a, Ossenkopf:2006a, Esquivel:2007b}
+and one has \(m\DD = n\DDD - 2 + \delta\kappa\) where \(\delta\kappa\) is a correction factor
+that accounts for the contribution to the structure function from
+column density fluctuations and cross terms (see section \ref{sec:constancy-power-law}).
+
 \citet{Brunt:2004a} found that \(\delta\kappa\) is a function of the Mach number for
-hydrodynamic turbulent box simulations, but we are unaware of any analytic prescription that would allow us to calculate \(\delta\kappa\) for
-the fractional Brownian motion models that we use here. 
-We therefore adopt an empirical approach by varying \(n\) until the
+hydrodynamic turbulent box simulations.  In principle,
+we could calculate \(\delta\kappa\) for
+the fractional Brownian motion models that we use here
+by using the analytic machinery of \citet{Esquivel:2007b},
+but we prefer instead to use a more empirical approach.
+We vary \(n\DDD\) until the
 resultant structure function slope matches a particular value in the
-range \(m = 0.8 \to 1.2\)
-that encompasses our observational results. 
-At each step, we estimate \(m\) by fitting our idealized model structure function
+range \(m\DD = 0.8 \to 1.2\)
+that encompasses our observational results.\footnote{%
+  Note that \(m\DD\) is written simply as \(m\) in the main text.
+}
+At each step, we estimate \(m\DD\) by fitting our idealized model structure function
 (equation~\eqref{eq:model-strucfunc-ideal}, without the seeing and noise terms)
@@
 which is maximal projection smoothing, exactly as expected for a case that
-mimics incompressible turbulence.
+mimics incompressible turbulence (see Appendix of \citealt{Miville-Deschenes:2003a}).
 As the amplitude of the emissivity fluctuations increase,
 we find that \(\delta\kappa\) becomes increasingly negative,
-with \(\delta\kappa \approx -0.3\) for \(\shortsig{E} = 1\) (the case that we present here)
+with \(\delta\kappa \approx -0.3\) for \(\shortsig{E} = 1\) (the case that we illustrate here)
 and \(\delta\kappa \approx -0.55\) for \(\shortsig{E} = 2\).

### 2023-04-27 strucfunc_paper.tex
Finish second subsection on NGC 595 and 604

@@
 \(r_0 = \SI{11 \pm 1.0}{pc} \)), and \(m = 1.4 \pm 0.2\).
-The value of the observed \(\sigma\pos^2 = \SI{44}{km^{2}.s^{-2}}\) is obtained at \(r_0 = \SI{10}{pc} \) (while the derived values from our model are \(\sigma\pos^2 = \SI{53}{km^{2}.s^{-2}}\) and \(r_0 = \SI{11}{pc} \)).
-The observed value of \(2\sigma\pos^2\) corresponds to \(r = \SI{21}{pc} \).
-The maximum \(B(r)\) value is \SI{104}{km^{2}.s^{-2}} at a separation of \SI{30}{pc}. 
-%For NGC 595 we see that the structure function plateau at this maximum \(B(r)\) value, which implies that the observed \(\sigma\pos^2\) is affected by the observational constraints.
-Until \(r_0 \sim \SI{55}{pc} \) the structure functions remains closely to the 'true' \(2\sigma\pos^2\), for the largest scale there is a decrease between  \(\SI{55}{pc} < r < \SI{110}{pc} \) where the structure function plateaus at the 'observed' \(2\sigma\pos^2\).
-Above \SI{110}{pc} we see a very disperse downturn  until \SI{54}{km^{2}.s^{-2}} at a separation of \SI{211}{pc}.
-The seeing (RMS) is \SI{2.1}{pc} (\(s_0\)=\SI{0.2}{\arcsecond}) and there are no points below this value.
-Considering the first point to be valid, which corresponds to \SI{2.5}{km^{2}.s^{-2}} at \(r = \SI{1.05}{pc} \) the slope for \(\sigma\pos^2\) and \(2\sigma\pos^2\) we obtain \num{1.27} and \num{1.18}, respectively, while our derived value is \num{1.38}.
-
-In the Figure~\ref{fig:strucfunc-fit-ExtraGal}d we show the structure function of NGC 604.
-The value of the observed \(\sigma\pos^2 = \SI{55}{km^{2}.s^{-2}}\) is obtained at \(r_0 = \SI{10}{pc} \) (while the derived values from our model are \(\sigma\pos^2 = \SI{86}{km^{2}.s^{-2}}\) and \(r_0 = \SI{12}{pc} \)).
-The observed value of \(2\sigma\pos^2\) corresponds to \(r = \SI{30}{pc} \).
-The maximum \(B(r)\) value is \SI{143}{km^{2}.s^{-2}} at a separation of \SI{55}{pc}. 
-NGC 604 structure function presents clear pattern of periodic oscillations between  \(\SI{30}{pc} < r < \SI{211}{pc} \).
-The spatial wavelength is \SI{ \sim 50}{pc}. 
-The minimum value of this periodic pattern is \SI{54}{km^{2}.s^{-2}} at \SI{135}{pc} 
-and finally it goes back up again at \SI{211}{pc} to a \(B(r)\) value of \SI{123}{km^{2}.s^{-2}}.
-The seeing is \SI{2.1}{pc} (\(s_0\)=\SI{1.2}{\arcsecond}) and the first three points structure function are below these value, which means that the seeing is heavily affecting this observations.
-This also is shown by the big difference bee tween the 'true model' (green dahed line) and our 'model' (solid orange lines).
-onsidering the first point above this \(s_0\) value to be valid, which corresponds to \SI{10}{km^{2}.s^{-2}} at \(r = \SI{3}{pc} \) the slope for \(\sigma\pos^2\) and \(2\sigma\pos^2\) we obtain \num{1.40} and \num{1.03}, respectively, while our derived value is \num{1.2}.
+The velocity variance is slightly higher than the observed value of \SI{44}{km^{2}.s^{-2}},
+indicative of a moderate finite box effect.
+At the largest scales, the structure function trends slowly downwards,
+which may be due to a radial decline in the amplitude of the turbulent velocity field,
+but the effect is less marked than in other regions, such as Orion.
+
+In  Figure~\ref{fig:strucfunc-fit-ExtraGal}d we show the structure function of NGC 604.
+The model-derived parameters are \(\sigma\pos^2 = \SI{84 \pm 20}{km^{2}.s^{-2}}\),
+\(r_0 = \SI{12 \pm 6}{pc} \)), and \(m = 0.8 \pm 0.2\).
+Again the model-derived velocity variance is higher than the observed value of \SI{55}{km^{2}.s^{-2}},
+which this time is due primarily to the fact that the
+derived correlation length is only 6 times higher than the RMS seeing width,
+so some of the small-scale fluctuation power is missing from the observations.
+Of all our sources, NGC~604 shows the largest difference between the inferred
+``true'' structure function and the observed one, so the derived parameters
+should be treated with caution.
+At the largest scales, the structure function shows a pronounced minimum
+at \(r \approx {150}{pc}\), which may be due to a periodic oscillation with \(\lambda \approx {300}{pc}\),
+which is slightly larger than the size of the map.
 

### 2023-04-27 strucfunc_paper.tex
Finish last part of NGC 595. Just 604 to go.

@@
 
+\startNEW
 \subsubsection{Observed structure function and model fit}
 \label{sec:observ-struct-funct-m33}
+\stopNEW
 
 In Figure~\ref{fig:strucfunc-fit-ExtraGal}c we show the structure function of NGC 595.
+\startNEW
 The model-derived parameters are \(\sigma\pos^2 = \SI{53 \pm 5}{km^{2}.s^{-2}}\),
-\(r_0 = \SI{11 \pm 1.0}{pc} \)), and \(m = 1.4 \pm 0.2\).
+\(r_0 = \SI{11 \pm 1.0}{pc} \)), and \(m = 1.36 \pm 0.15\).
 The velocity variance is slightly higher than the observed value of \SI{44}{km^{2}.s^{-2}},
@@
 but the effect is less marked than in other regions, such as Orion. 
+\stopNEW
 
 In  Figure~\ref{fig:strucfunc-fit-ExtraGal}d we show the structure function of NGC 604.
+\startNEW
 The model-derived parameters are \(\sigma\pos^2 = \SI{84 \pm 20}{km^{2}.s^{-2}}\),
@@
 which is slightly larger than the size of the map. 
+\stopNEW
 
@@
 They found a total velocity variance of \(\sigma\pos^2 = \SI{35 \pm 2}{km^{2}.s^{-2}}\), which is smaller than our derived value of \(\sigma\pos^2 = \SI{53}{km^{2}.s^{-2}}\).
-
-For our NGC 595 \halpha\ emission line results there is no correspondence in the structure function from the previous investigations of \citet{lagrois2009multi} and \citet{lagrois2011}.
-Our observations cover the brightest part of the region and have smaller resolution than theirs.
-As a consequence \citet{lagrois2009multi} and \citet{lagrois2011} structure functions results does not cover scales $<$10 pc, where in our results the correlation is taking place.
-One big difference is that \citet{lagrois2011} apply a  filter to the velocity field to get rid of non-turbulent movements.
-As a comparison, for the filtered turbulent parameters they chose to represent the turbulent field, the derive a total  decorrelation length (\(C(\tau_0) = 0\)) of \SI{43}{pc} and the power-law index they provide is \num{1.55 \pm 0.01}.
-Their velocity centroid \(\sigma\) is \SI{5.92 \pm 0.15}{km.s^{-1}} while we have \SI{7.3\pm 2}{km. s^{-1}} which fall within the uncertainties.
-Due to the different observations and methodologies a direct comparison between structure functions is not possible.
+Our map covers a smaller region, so part of the reason for this discrepancy may be
+a radial decline in the velocity variance, as mentioned above.
+Another reason may be that the angular resolution of the \citet{lagrois2009multi} map
+is of the same order as the correlation length, so some of the small-scale power is missing.
+
+\citet{lagrois2011} employ a novel technique based on filtering the
+bidimensional velocity field to remove large-scale non-turbulent motions
+before calculating the structure function.
+They find a total decorrelation length of \(\tau_0 = \SI{43}{pc}\) and a very steep
+power-law index of \(m = \num{1.55 \pm 0.1}\).
+As discussed in section~\ref{sec:comp-with-prev}, \(\tau_0\) is predicted to be 2--3 times larger than \(r_0\), given the way that we define the correlation length,
+but even taking this into account, our derived value is still smaller than theirs
+by at least 50\%.
+Although this may be due to the difference in the areas covered,
+it is more likely due to the lower resolution of the \citeauthor{lagrois2011} data.
+
+The power-law index is somewhat steeper than our own value,
+but in part this is due to differences in methodology:
+the width of the low-pass filter that \citeauthor{lagrois2011} use to remove large-scale
+motions is \SI{8}{pixels} or \SI{53}{pc}, which is comparable to the decorrelation length.
+As a result, subtracting the filtered data causes a clear steepening of the structure function,
+as can be seen in their Figure~6d.
+The unfiltered data can be seen to show a shallower slope, more consistent
+with our own results.
+Which result is more reliable is difficult to say, but could potentially be checked
+by experimenting on fake data in a similar fashion to our Appendix~\ref{sec:degr-struct-funct}.
+
+\stopNEW
 

### 2023-04-28 strucfunc_paper.tex
Finish revising the NGC 604 section

@@
   Ionized density fluctuations are too large to be explained by the action
-  of the turbulence in all but the highest luminosity sources.
+  of the turbulence in {\NEW{any}} but the highest luminosity sources.
   A variety of behaviors are seen on scales larger than the correlation length,
@@
 
-\stopNEW
-
-For NGC 604 there is good agreement in our structure function results and previous studies.
-This mainly because where are using the same TAURUS-II data as \citet{Melnick:2021x} and \citet{Medina-Tanco:1997a}.
-Despite this general agreement, the interpretations in each study is different.
-\citet{Medina-Tanco:1997a} conclude about a double regime acting on the kinetic energy spectrum.
-According to this double cascade, turbulence is being forced at scales of \(\approx\) \SI{10}{pc} while and energy cascade has developed down to the smallest scales and other, as an inverse cascade, extends up to scale of \(\approx\) \SI{70}{pc}.
-\citet{Medina-Tanco:1997a} mentioned different characteristic scale lengths, the most notorious is the \SI{\sim 10}{pc}, and they interpret it as possible source on energy associated with the expansion of shocks coming from wind bubbles.
-\citet{Melnick:2021x} addresses some issues with TAURUS II data while comparing profiles between the previous instrument TAURUS I where there exist a difference between observations (see section 4.1 on their paper).
-They mentioned that one problem with \citet{Medina-Tanco:1997a} structure function is that they didn't take into account the observational seeing.
-This would invalidate they results and \citet{Melnick:2021x} consider that taking out the structure function values that fall within this range would make the structure function flat at scales \(<\)\SI{10}{pc}, so they rule out \citet{Medina-Tanco:1997a} results.
-Finally they point out, and we agree, the importance of observing NGC 604 at higher spatial resolution. 
-Our Fig. \ref{fig:strucfunc-fit-ExtraGal}d shows in fact that there is a velocity structure in NGC 604. 
-None of the previous studies obtained a power-law index or correlation length for the structure function to compare our results.
+All previous studies of the structure function in NGC~604 are based
+on the same TAURUS-II observational dataset that we use here
+\citep{sabalisck1995supersonic}
+and the results are unsurprisingly similar to our own,
+although there are some differences in methodology and interpretation.
+For instance, \citet{Medina-Tanco:1997a} identify an apparent ``knee''
+in the structure function at \(r \approx \SI{10}{pc}\), which they interpret as
+evidence for a broken power law.
+However, in our own results the same feature is modeled as a combination
+of two effects:
+the natural flattening of
+the structure function for \(r > r_0\),
+plus a steepening at small scales due to the smoothing effects of the seeing. 
+\citet{Melnick:2021x} also analysed the same structure function and concluded that
+separations \(< \SI{2}{arcsec}\) should be discounted due to the seeing.
+The results of our experiments with synthetic observations (Appendix~\ref{sec:effects-seeing-struc})
+suggest that the situation is even worse than \citeauthor{Melnick:2021x} surmised
+and that scales up to \SI{5}{arcsec} will be affected by the seeing.
+On the other hand, if the effects of seeing are incorporated into the model structure function,
+as we have done here, then the data at these separations do not need to be discarded entirely.
 

### 2023-04-28 strucfunc_paper.tex
Revisions to section 4.4

@@
 
-However, there are two outlier values that deserve closer attention.
-NGC~595 has the lowest value of \SI{0.2}{arcsec}, which seems
-unrealistically small, especially given the higher values
-derived for the other sources, such as NGC~604,
-that were obtained with the same instrument.
-On the other hand, the 95\% credibility range extends as high as \SI{0.7}{arcsec},
-which does overlap with the range for NGC~604.
-If one were to take a common compromise seeing of \SI{0.7}{arcsec}
-for both sources (\(s_0 = \SI{1.2}{pc}\)),
-then the anticorrelation between \(m\) and \(s_0\)
-%(see Figure~\ref{fig:corner-ExtraGal}a, b)
-would decrease the inferred \(m\) for NGC~595 while increasing it for NGC~604,
-thus making the two slopes more closely similar.
-
-The inner Orion Nebula has the largest inferred seeing FWHM of \SI{2.4(4)}{arcsec},
-which is at least two times higher than the typical seeing measured during the observations
+\startNEW
+However, there are a few outlier values that deserve closer attention.
+NGC~595, Hubble~V, and Hubble~X all have model-derived upper limits to the
+seeing FWHM of about \SI{0.6}{arcsec}, which seems
+unrealistically small, especially given the higher value
+derived for NGC~604,
+which was observed with the same instrument.
+Unfortunately, we do not have access to the observing logs to check this,
+so we suggest extra caution in interpreting the fit results for these objects. 
+\stopNEW
+
+The inner Orion Nebula has the largest inferred seeing FWHM of \NEW{\SI{1.8(2)}{arcsec}},
+which is \NEW{nearly twice as high as} the typical seeing measured during the observations
 \citep{Doi:2004a}.

### 2023-04-28 reply-to-referee.txt
Update reply to referee

@@
 and the results of Appendix A have now been completely replaced. It
-turns out that the new results are extremely similar to the old ones, so
-the changes to the text (highlighted in red in the manuscript) are
-minimal.
+turns out that the new results are similar to the old ones, so the
+changes to the text (highlighted in red in the manuscript) are not
+large.
 
@@
 the effects of seeing (equation 15 and A1). We have therefore re-run all
-of the model fits in section 4, but the results change by less than 1%.
+of the model fits in section 4, but the only significant changes were in
+some of the derived seeing widths. None of the "interesting" parameters
+(sigma, r0, m) changed by more than 1%.
 
-We have also taken the opportunity to improve some of the descriptions
-of individual regions in Appendix C.
+We have also taken the opportunity to revise and improve the
+descriptions of individual regions in Appendix C. All substantial
+changes are marked in red.
+
+Finally, we have separated the online-only supplementary figures into a
+separate PDF file, as requested by the editor.

### 2023-04-28 strucfunc_paper.tex
Fix typo

@@
 The model-derived parameters are \(\sigma\pos^2 = \SI{53 \pm 5}{km^{2}.s^{-2}}\),
-\(r_0 = \SI{11 \pm 1.0}{pc} \)), and \(m = 1.36 \pm 0.15\).
+\(r_0 = \SI{11 \pm 1.0}{pc} \), and \(m = 1.36 \pm 0.15\).
 The velocity variance is slightly higher than the observed value of \SI{44}{km^{2}.s^{-2}},
@@
 At the largest scales, the structure function shows a pronounced minimum
-at \(r \approx {150}{pc}\), which may be due to a periodic oscillation with \(\lambda \approx {300}{pc}\),
+at \(r \approx \SI{150}{pc}\), which may be due to a periodic oscillation with \(\lambda \approx \SI{300}{pc}\),
 which is slightly larger than the size of the map. 

### 2023-04-28 strucfunc_paper.tex
Another typo

@@
   Panel~h: RMS Mach number of three-dimensional
-  velocity fluctuations (panel~h)
+  velocity fluctuations
   as a function of the RMS fractional brightness fluctuation calculated from the PDFs.

### 2023-05-09 strucfunc_paper.tex
Javier changes 2023-05-09

@@
 over all pairs of points that contribute to each radial bin.
-The uncertainty of each bin (blue error bars) is estimated
-as the standard deviation of these values divided by the square root of
-the number of contributing pairs.
+%The uncertainty of each bin (blue error bars) is estimated
+%as the standard deviation of these values divided by the square root of
+%the number of contributing pairs.
+\NEW{The uncertainty of each bin (blue error bars) is estimated
+as the fractional error of the respective \(B\obs(r)\) value.
+These values are indicated in the third column of the table given in the Appendix D. 
+In the same table, the forth and fifth columns show, as multiples of their respective fractional error, additional weight at small and large scales. 
+This is the case for the EON, and the regions observed using the FLAMES and the TAURUS instruments.}
 For most sources a fixed bin size of \SI{0.05}{dex} is used,
@@
 which is slightly larger than the size of the map. 
+On the other hand, if we fit the model for scales \(r \leq \SI{20}{pc}\), there is a decrease in the difference between the inferred ``true'' structure function and the observed one.
+With our current observations the fitting using less than half of the observational points cannot be justified; but with better quality observations and using our current model we would expect to derived more accurate parameters.
 \stopNEW

### 2023-05-09 strucfunc_paper.tex
Minor changes to Javier's text on error bars. Ready to resubmit!

@@
 %the number of contributing pairs.
-\NEW{The uncertainty of each bin (blue error bars) is estimated
-as the fractional error of the respective \(B\obs(r)\) value.
-These values are indicated in the third column of the table given in the Appendix D. 
-In the same table, the forth and fifth columns show, as multiples of their respective fractional error, additional weight at small and large scales. 
-This is the case for the EON, and the regions observed using the FLAMES and the TAURUS instruments.}
+\startNEW
+We judge the dominant source of error in \(B\obs(r)\) to be systematic,
+rather than random, so we set the uncertainty of each bin (blue error bars)
+as a constant fraction (2 to 8\%) of the observed value,
+as listed in column 3 of Table~D1 (see supplementary material).
+In some sources
+(EON, and the regions observed using the FLAMES and the TAURUS instruments)
+the uncertainty is increased by a factor of order two for a small number of bins
+at the smallest and largest scales (columns 4 and 5 of Table~D1).
+\stopNEW
 For most sources a fixed bin size of \SI{0.05}{dex} is used,

### 2023-06-02 strucfunc_paper.tex
Fix typo in equation in section 5.1, penultimate paragraph.
Javier changes for production

@@
 
-%\usepackage{orcidlink}
-
 \usepackage{upgreek}
@@
 \definecolor{NEWcolor}{rgb}{0.7,0.2,0.1}
-\newcommand\startNEW{\color{NEWcolor}}
+%\newcommand\startNEW{\color{NEWcolor}}
+\newcommand\startNEW{\color{black}}
 \newcommand\stopNEW{\color{black}}
@@
   Ionized density fluctuations are too large to be explained by the action
-  of the turbulence in {\NEW{any}} but the highest luminosity sources.
+  of the turbulence in any but the highest luminosity sources.
   A variety of behaviors are seen on scales larger than the correlation length,
@@
   \begin{center}\caption{Summary of properties of our \hii{} region sample. Diameters are taken from Table 2 of \citet{1984ApJ...287..116K}.
-      \NEW{References for other properties are given in Appendix~\ref{sec:notes-individual-hii}.}
+      References for other properties are given in Appendix~\ref{sec:notes-individual-hii}.
       Mean non-thermal linewidth values (\(\langle \sigma\los \rangle\)) shown here are corrected considering equation \eqref{eq:sigma-los} which takes into account \(\sigma_{\mathrm{fs}}\). }
@@
 show a negative curvature in log-log space at intermediate scales:
-\(d\log B/ d\log r < 0\).
+\(d^2 \log B/ d^2 \log r < 0\).
 This is caused primarily by the steepening due to seeing at small scales
@@
 JGV acknowledges and thanks CONACyT-Mexico for a PhD research scholarship. 
+A sincere thanks to the anonymous referee who help us improve the quality of our work.
 

### 2023-06-02 strucfunc_paper_plus.tex
Finish and submit the arxiv version of the paper

--- 2023-06-02 strucfunc_paper.tex
@@
 The Orion Nebula (M42) is the prototype of a galactic \hii{} region located at a distance of 440 pc \citetext{\SI{1}{\arcsecond} = \SI{0.002}{pc}; \citealp{2008AJ....136.1566O}}.
-The O7 V star \(\uptheta^{1}\) Ori C is the most luminous and hottest star with an ionizing flux \(Q_0\) of \SI{e49.12}{photons.s^{-1}} \citep{2006A&A...448..351S},
+The O7 V star \(\uptheta^{1}\) Ori C is the most luminous and hottest star with an ionizing flux \(Q_0\) of \SI{1.3e49}{photons.s^{-1}} \citep{2006A&A...448..351S},
 \startNEW
@@
 \stopNEW
-luminosity in \ha{} of \SI{e37.18}{erg.s^{-1}}.
+luminosity in \ha{} of \SI{1.5e37}{erg.s^{-1}}.
 With 3 other B-type stars they form the Trapezium cluster.
@@
 \stopNEW
-These stars gives an ionizing flux \(Q_0 = \SI{e49.41}{photons.s^{-1}}\) (2 times higher than in the Orion Nebula) and the luminosity in \ha{} is \SI{e37.47}{erg.s^{-1}} \citep{1984ApJ...287..116K}.
+These stars gives an ionizing flux \(Q_0 = \SI{2.6e49}{photons.s^{-1}}\) (2 times higher than in the Orion Nebula) and the luminosity in \ha{} is \SI{2.95e37}{erg.s^{-1}} \citep{1984ApJ...287..116K}.
 The mean non-thermal linewidth in \ha{} is \SI{11.7 \pm 1.6}{km.s^{-1}} \citep{1973ApJ...183..851B}.
@@
 This OB association has more than 65 stars earlier than B0, and several Wolf-Rayet (WR) stars and the most luminous star is the blue variable $\eta$~Car.
-The ionizing flux \(Q_0\) is \SI{e50.95}{photons.s^{-1}} \citep{2008hsf2.book..138S} (60 times higher compared to the Orion Nebula) and the luminosity in \ha{} of \SI{e39.01}{erg.s^{-1}}.
+The ionizing flux \(Q_0\) is \SI{8.9e50}{photons.s^{-1}} \citep{2008hsf2.book..138S} (60 times higher compared to the Orion Nebula) and the luminosity in \ha{} of \SI{e39}{erg.s^{-1}}.
 As a high-mass star formation region, it presents several phenomena related to young stars,
@@
 The star cluster that energizes the region is NGC~2070, with a central core (known as R136)
-with ionizing luminosity \(Q_0 = \SI{e51.40}{photons.s^{-1}}\)  \citep{2020MNRAS.499.1918B},
-which produces an \ha{} luminosity of \SI{e39.46}{erg.s^{-1}} (200 times the Orion Nebula)
+with ionizing luminosity \(Q_0 = \SI{2.5e51}{photons.s^{-1}}\)  \citep{2020MNRAS.499.1918B},
+which produces an \ha{} luminosity of \SI{2.9e39}{erg.s^{-1}} (200 times the Orion Nebula)
 for the central ionized region of size \SI{40}{pc}.
@@
 \NEW{The cluster}
-has an ionizing output \(Q_0\) of \SI{e50.71}{photons.s^{-1}} (40 times higher than the Orion Nebula) and \NEW{the \hii{} region has} an \ha{} luminosity of \SI{e38.77}{erg.s^{-1}} \citep{2010A&A...517A..39H,1984ApJ...287..116K}.
+has an ionizing output \(Q_0\) of \SI{5.1e50}{photons.s^{-1}} (40 times higher than the Orion Nebula) and \NEW{the \hii{} region has} an \ha{} luminosity of \SI{5.9e38}{erg.s^{-1}} \citep{2010A&A...517A..39H,1984ApJ...287..116K}.
 \startNEW
@@
 Hubble V is located near the ``Hodge OB 8'' OB association with a number of \num{\sim 36} young stellar objects \citep{2021MNRAS.507.5106K} and its core is powered by an O3 V star \citep{1999PASP..111.1382O}.
-It has an ionizing output \(Q_0\) of \SI{e50.23}{photons.s^{-1}} (13 times higher compared to the Orion Nebula) and has a \ha{} luminosity of \SI{e38.30}{erg.s^{-1}}\citep{2002MNRAS.329..481B}.
+It has an ionizing output \(Q_0\) of \SI{1.7e50}{photons.s^{-1}} (13 times higher compared to the Orion Nebula) and has a \ha{} luminosity of \SI{2e38}{erg.s^{-1}}\citep{2002MNRAS.329..481B}.
 The mean non-thermal linewidth in \ha{} \(\siglosm = \SI{10.3 \pm 0.03}{km.s^{-1}}\) \citep{1986A&A...160..374H}.
@@
 Hubble X is located near the Hodge ``OB 13'' OB association with a number of \num{\sim 29} young stellar objects \citep{2021MNRAS.507.5106K} and its core is powered by an O4 V star \citep{1999PASP..111.1382O}.
-It has an ionizing output \(Q_0\) of \SI{e50.14}{photons.s^{-1}} (10 times higher compared to the Orion Nebula) and has a \ha{} luminosity of \SI{e38.21}{erg.s^{-1}} \citep{2002MNRAS.329..481B}.
+It has an ionizing output \(Q_0\) of \SI{1.4e50}{photons.s^{-1}} (10 times higher compared to the Orion Nebula) and has a \ha{} luminosity of \SI{1.6e38}{erg.s^{-1}} \citep{2002MNRAS.329..481B}.
 The mean non-thermal linewidth in \ha{} is \(\siglosm = \SI{10.5 \pm 0.02}{km.s^{-1}}\)  \citep{1986A&A...160..374H}.
@@
 \stopNEW
-The ionizing output \(Q_0\) is \SI{e50.88}{photons.s^{-1}} (60 times higher compared to the Orion Nebula) and
-the \hii{} region has a luminosity in \ha{} of \SI{e38.95}{erg.s^{-1}} \citep{2002MNRAS.329..481B}.
+The ionizing output \(Q_0\) is \SI{7.6e50}{photons.s^{-1}} (60 times higher compared to the Orion Nebula) and
+the \hii{} region has a luminosity in \ha{} of \SI{8.9e38}{erg.s^{-1}} \citep{2002MNRAS.329..481B}.
 The mean non-thermal linewidth in \ha{} is
@@
 \stopNEW
-The ionizing output is \(Q_0 = \SI{e51.35}{photons.s^{-1}}\)
+The ionizing output is \(Q_0 = \SI{2.2e51}{photons.s^{-1}}\)
 (175 times higher than the Orion Nebula) and
-the region has an \ha{} luminosity of \SI{e39.42}{erg.s^{-1}} \citep{2002MNRAS.329..481B}.
+the region has an \ha{} luminosity of \SI{2.6e39}{erg.s^{-1}} \citep{2002MNRAS.329..481B}.
 The mean non-thermal linewidth in \ha{} is
@@
 
-\section{Additional covariance corner plots for model fits}
-\label{sec:addit-covar-corn}
-Supplementary material
-\href{https://github.com/will-henney/javier-strucfunc-paper/blob/main/supplementary_material_strucfunc_paper.pdf}
-{available online}.
+% ArXiv version has supplementary material included in same file
+\input{sf_appendix_D}
+
+% \section{Additional covariance corner plots for model fits}
+% \label{sec:addit-covar-corn}
+% Supplementary material
+% \href{https://github.com/will-henney/javier-strucfunc-paper/blob/main/supplementary_material_strucfunc_paper.pdf}
+% {available online}.
 
